### 2018-08-17 main.tex
Update on Overleaf.

\documentclass[english]{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{babel}
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage{fancyhdr}
\newcommand{\scidatalogo}{\includegraphics[height=36pt]{SciData_logo.jpg}}
\newcommand{\overleaflogo}{\includegraphics[height=36pt]{Overleaf-logo-300dpi.png}}
\pagestyle{fancy}
\fancyhf{}
\renewcommand{\headrulewidth}{0pt}
\setlength{\headheight}{40pt} 
\lhead{\textsc{\scidatalogo}}
\rhead{\textsc{\overleaflogo}}

\begin{document}

\title{PPA stuff (110 character maximum, inc. spaces)}

\author{Firstname Lastname\textsuperscript{1}, Firstname
Lastname\textsuperscript{2{*}}}

% https://www.nature.com/sdata/publish/for-authors#other-formats

\maketitle
\thispagestyle{fancy}

1. An affiliation 2. A different affiliation {*}corresponding author(s):
Firstname Lastname (email@address)
\begin{abstract}
This is a manuscript template for Data Descriptor submissions to \emph{Scientific
Data} (http://www.nature.com/scientificdata). The abstract must be
no longer than 170 words, and should succinctly describe the study,
the assay(s) performed, the resulting data, and the reuse potential,
but should not make any claims regarding new scientific findings.
No references are allowed in this section. 
\end{abstract}

\section*{Background \& Summary}

(700 words maximum) An overview of the study design, the assay(s)
performed, and the created data, including any background information
needed to put this study in the context of previous work and the literature.
The section should also briefly outline the broader goals that motivated
the creation of this dataset and the potential reuse value. We also
encourage authors to include a figure that provides a schematic overview
of the study and assay(s) design. This section and the other main
body sections of the manuscript should include citations to the literature
as needed \cite{cite1, cite2}. References should be included within the 
manuscript file itself as our system cannot accept BibTeX bibliography files. 
Authors who wish to use BibTeX to prepare their references should therefore 
copy the reference list from the .bbl file that BibTeX generates and paste it 
into the main manuscript .tex file (and delete the associated 
\textbackslash{}bibliography and \textbackslash{}bibliographystyle commands).

\section*{Methods}

The Methods should include detailed text describing any steps or procedures 
used in producing the data, including full descriptions of the experimental 
design, data acquisition assays, and any computational processing (e.g. 
normalization, image feature extraction). Related methods should be grouped 
under corresponding subheadings where possible, and methods should be described 
in enough detail to allow other researchers to interpret and repeat, if required, 
the full study. Specific data outputs should be explicitly referenced via data 
citation (see Data Records and Data Citations, below). Authors should cite 
previous descriptions of the methods under use, but ideally the method 
descriptions should be complete enough for others to understand and reproduce 
the methods and processing steps without referring to associated publications. 
There is no limit to the length of the Methods section.

\subsection*{Code availability}

For all studies using custom code in the generation or processing of datasets, 
a statement must be included here, indicating whether and how the code can be 
accessed, including any restrictions to access. This section should also include 
information on the versions of any software used, if relevant, and any specific 
variables or parameters used to generate, test, or process the current dataset.

\section*{Data Records}

Please explain each data record associated with this work, including
the repository where this information is stored, and an overview of
the data files and their formats. Each external data record should
be listed in Data Citation section at the end of this template, and 
records should be cited throughout the manuscript as, for example 
(Data Citation 1).

Tables should be used to support the data records, and should clearly indicate 
the samples and subjects, their provenance, and the experimental manipulations 
performed on each. They should also specify the data output resulting from each 
data-collection or analytical step, should these form part of the archived record. 
Please see the submission guidelines at the \emph{Scientific Data} website, and 
our Word templates for more information on preparing such tables.

\section*{Technical Validation}

This section presents any experiments or analyses that are needed
to support the technical quality of the dataset. This section may
be supported by up figures and tables, as needed. This is a required
section; authors must present information justifying the reliability
of their data.

\section*{Usage Notes}

Brief instructions that may help other researchers reuse these dataset.
This is an optional section, but strongly encouraged when helpful
to readers. This may include discussion of software packages that
are suitable for analyzing the assay data files, suggested downstream
processing steps (e.g. normalization, etc.), or tips for integrating
or comparing this with other datasets. If needed, authors are encouraged
to provide code, programs, or data processing workflows when they may help 
others analyse the data. We encourage authors to archive related code in 
a DOI-issuing archive when possible, but code may also be supplied as 
supplementary information files.

For studies involving privacy or safety controls on public access
to the data, this section should describe in detail these controls,
including how authors can apply to access the data, and what criteria
will be used to determine who may access the data, and any limitations
on data use.

\section*{Acknowledgements}

Text acknowledging non-author contributors. Acknowledgements should
be brief, and should not include thanks to anonymous referees and
editors, or effusive comments. Grant or contribution numbers may be
acknowledged. Author contributions Please describe briefly the contributions
of each author to this work on a separate line.

AK did this and that.

BG did this and that and the other.

\section*{Competing financial interests}

A competing financial interests statement is required for all accepted
papers published in \emph{Scientific Data}. If none exist simply write,
``The author(s) declare no competing financial interests''.

\section*{Figures Legends}

Figure should be referred to using a consistent numbering scheme through
the entire Data Descriptor. For initial submissions, authors may choose
to supply this document as a single PDF with embedded figures, but
separate figure image files must be provided for revisions and accepted
manuscripts. In most cases, a Data Descriptor should not contain more
than three figures, but more may be allowed when needed. We discourage
the inclusion of figures in the Supplementary Information \textendash{}
all key figures should be included here in the main Figure section.

Figure legends begin with a brief title sentence for the whole figure
and continue with a short description of what is shown in each panel,
as well as explaining any symbols used. Legend must total no more
than 350 words, and may contain literature references.

\section*{Tables}

Tables supporting the Data Descriptor. These can provide summary information
(sample numbers, demographics, etc.), but they should generally not
be used to present primary data (i.e. measurements). Tables containing
primary data should be submitted to an appropriate data repository.

Tables may be provided within the \LaTeX{} document or as separate
files (tab-delimited text or Excel files). Legends, where needed,
should be included here. Generally, a Data Descriptor should have
fewer than ten Tables, but more may be allowed when needed. Tables
may be of any size, but only Tables which fit onto a single printed
page will be included in the PDF version of the article (up to a maximum
of three).

\begin{thebibliography}{1}
\expandafter\ifx\csname url\endcsname\relax
  \def\url#1{\texttt{#1}}\fi
\expandafter\ifx\csname urlprefix\endcsname\relax\def\urlprefix{URL }\fi
\providecommand{\bibinfo}[2]{#2}
\providecommand{\eprint}[2][]{\url{#2}}

\bibitem{cite1}
\bibinfo{author}{Califano, A.}, \bibinfo{author}{Butte, A.~J.},
  \bibinfo{author}{Friend, S.}, \bibinfo{author}{Ideker, T.} \&
  \bibinfo{author}{Schadt, E.}
\newblock \bibinfo{title}{{Leveraging models of cell regulation and GWAS data
  in integrative network-based association studies}}.
\newblock \emph{\bibinfo{journal}{Nature Genetics}}
  \textbf{\bibinfo{volume}{44}}, \bibinfo{pages}{841--847}
  (\bibinfo{year}{2012}).

\bibitem{cite2}
\bibinfo{author}{Wang, R.} \emph{et~al.}
\newblock \bibinfo{title}{{PRIDE Inspector: a tool to visualize and validate MS
  proteomics data.}}
\newblock \emph{\bibinfo{journal}{Nature Biotechnology}}
  \textbf{\bibinfo{volume}{30}}, \bibinfo{pages}{135--137}
  (\bibinfo{year}{2012}).

\end{thebibliography}

\section*{Data Citations}

Bibliographic information for the data records described in the manuscript.

1. Lastname1, Initial1., Lastname2, Initial2., ...\& LastnameN, InitialN. \emph{Repository name} Dataset accession number or DOI (YYYY).

\end{document}

### 2020-03-18 main.tex
Update on Overleaf.

@@
 \usepackage{babel}
+\usepackage{svg}
+\usepackage{caption, booktabs}
 \usepackage{amsmath}
@@
 \usepackage{fancyhdr}
+\usepackage{todonotes}
+\usepackage[
+	colorlinks=true,
+	urlcolor=blue,
+	linkcolor=green
+]{hyperref}
 \newcommand{\scidatalogo}{\includegraphics[height=36pt]{SciData_logo.jpg}}
@@
 
-\title{PPA stuff (110 character maximum, inc. spaces)}
+% Vorgabe < 110 chars incl. spaces
+%  jetzt 109 Chars
+\title{Hemodynamic responses of the Parahippocampal Place Area to spatial cues in a movie and it's audio-description} 
+% alt:BOLD responses of the Parahippocampal Place Area correlate with spatial cues in a movie and it's audio-only variant
 
-\author{Firstname Lastname\textsuperscript{1}, Firstname
-Lastname\textsuperscript{2{*}}}
-
+\author{Christian O. Häusler\textsuperscript{1,2{*}}, Michael Hanke\textsuperscript{1}}
 % https://www.nature.com/sdata/publish/for-authors#other-formats
@@
 \thispagestyle{fancy}
+1. Psychoinformatics Lab, Institute of Neuroscience and Medicine, Brain \& Behaviour (INM-7), Research Centre Jülich, Jülich, Germany, 
+2. Institute of Systems Neuroscience, Medical Faculty, Heinrich Heine University, Düsseldorf, Germany 
+{*}corresponding author: Christian Olaf Häusler (der.haeusler@gmx.net)
 
-1. An affiliation 2. A different affiliation {*}corresponding author(s):
-Firstname Lastname (email@address)
 \begin{abstract}
-This is a manuscript template for Data Descriptor submissions to \emph{Scientific
-Data} (http://www.nature.com/scientificdata). The abstract must be
-no longer than 170 words, and should succinctly describe the study,
-the assay(s) performed, the resulting data, and the reuse potential,
-but should not make any claims regarding new scientific findings.
-No references are allowed in this section. 
+% Analysis Paper abstract: < 170 words
+% no references are allowed: 
+% new analysis of existing data of interest to a broad section of our audience
+% highlighting innovative examples of data reuse
+% may be used to present compelling new findings and conclusions derived from published data.
+% submissions using data previously published at Scientific Data are encouraged
+% submissions should exemplify reproducible research by clearly describing all steps in the analysis
+% providing supporting source code, and explaining how and where others may access all data underlying the analysis.
+Intro: PPA as classic example for an visual area
+Methods: fMRI data, studyforrest data set, general linear model
+Results: significant clusters in PPA, RSC, individual results in x of 15 subjects
+Conclusions: PPA nicht exclusively 
 \end{abstract}
+% Intro + Discussion = main text ~  3,000 words.
+% include figure providing schematic overview of the study and assay(s) design
+% -> ist overkill; Paradigma ist mit "Film ab" wenig kompliziert.
+\section{Introduction}
+% Bzgl. Zitationen (lasse alles so lange wie möglich in Kbibtext's .bib-Datei): \cite{cite1, cite2}
+% our system cannot accept BibTeX bibliography files; authors who wish to use BibTeX to prepare their references should therefore copy the reference list from the .bbl file that BibTeX generates and paste it into the main manuscript .tex file (and delete the associated  \textbackslash{}bibliography and \textbackslash{}bibliographystyle commands).
+Cognitive neuroscientists use brain imaging methods like blood oxygenation level-dependent functional magnetic resonance imaging (BOLD fMRI) to map perceptual and cognitive brain processes (e.g.
+viewing of landscapes, {epstein1998ppa}; or theory of mind {spunt2014validating}) to functional brain areas or networks.
+Brain mapping studies have traditionally employed small sets of carefully chosen, simplified stimuli to strictly control experimental conditions and facilitate functional isolation of brain areas.
+The disadvantage is that a limited number of simplified stimuli does not resemble our real-life experience and lacks external {westfall2016fixing} as well as ecological validity {hasson2004intersubject}.
+Additionally, brain mapping studies have traditionally averaged / usually average results across at least 10-15 subjects to improve the signal-to-noise-ratio (SNR).
+The disadvantage here is that the averaging approach does not  characterize brain functions at an individual level, a prerequisite for the application of brain imaging methods in individual diagnostics (cf.
+{dubois2016building})
 
-\section*{Background \& Summary}
+% Retrosplenial-Cortex kommt in der jetzigen Einleitung nicht vor, jedoch in Ergebnissen von Movie & Audio-Description
+% Muss spätestens in der Discussion diskutiert werden
+% bin auch am überlegen, ob ich in den Ergebnissen zu den sagitallen slices durch die PPAs noch sagitale Slices durch die RSCs dazunehme??
+A classic example of a functional, higher-level visual area is the "parahippocampal place area" (PPA) {epstein1998ppa; epstein1999parahippocampal}.
+The PPA is located in the posterior parahippocampal gyrus at the boundary to the anterior lingual gyrus and medial fusiform gyrus, both being part of the ventral visual stream [mishkin1982contribution; goodale1992separate].
+Increased hemodynamic activity in the PPA correlates with the perception of static pictures of landscapes or landmarks compared to pictures of tools or faces.
+According to the spatial layout hypothesis, the PPA is involved in processing the surface geometry of a visual stimulus and possibly in identifying scenes based on their spatial layout {epstein2010reliable}.
+Results generalize at a group average level to a) mental imagination of landscapes {ocraven2000mental} and b) haptic exploration of scenes {wolbers2011modality}, \todo{this needs some more glue.
+the following is not just about spoken stimuli} whereas results of a study using spoken, place-related sentences were unclear \todo{should be more specific.
+unclear could mean 'not well described'} {aziz2008modulation}:
+a) In a study conducted by {ocraven2000mental} participants viewed alternating blocks of pictures showing famous faces and familiar places during an initial experimental paradigm.
+In a subsequent paradigm, participants were instructed to "form a vivid mental image" of the previously viewed pictures.
+The PPA showed increased activation during imagination of places compared to faces but the imagination tasks showed a smaller activation level compared to the perceptual task.
+% Wolbers im Folgenden macht noch ne Connectivitäts-Analyse mit dem Occipital-Cortex; da ist dann keine Connectivity im Vergleich zum visuellen Paradigma; deshalb kann das laut ihm kein mental image sein: "the scene-related increase in coupling with the PPA was significantly stronger in multiple clusters in occipital cortex under visual than haptic stimulation (Figure 2B; Table S2)"
+b) In a block design study conducted by {wolbers2011modality} the PPA of sighted participants showed increased activation during a delayed matching-to-sample task of haptically explored scenes constructed from Lego bricks compared to haptically explored abstract geometric objects.
+% Aziz hat auf eine zweite Mail geantwortet: Sie hat kein Block-Design, sondern modelt die HRF über den jeweils gesamten Satz von ca. 2.8 Sekunden.
+c) To our knowledge only one study by {aziz2008modulation} correlated hemodynamic activity of the PPA with spoken sentences.
+Sentences described generic or famous places (e.g.
+“The Taj Mahal faces a long thin reflecting pool”) or faces  (e.g.
+“Marylin Monroe has a large square jaw").
+Participants were instructed to press a button whenever the sentence described an inaccurate or improbable fact.
+Surprisingly, activation in the left, but not right, PPA was significantly reduced \todo{reduced relative to what condition?} when participants listened to place-related sentences.
+Moreover, this effect was only observed in sentences involving famous places.
+% Frage: Review von Aminoff (2013) kommt nur kurz als "competing hypothesis"; muss man dann in der Discussion diskutieren, was ggf. gar nicht nötwendig ist, weil's darum im Grunde nicht geht
+In summary, studies suggest that the PPA does not exclusively respond to visual(ly) spatial information.
+This is consistent with a competing hypotheses stating the PPA does not process the spatial layout of a scene specifically but contextual associations in general {aminoff2006parahippocampal} for a review).
+Independent(ly) from competing theories (s.
+{aminoff2013role} for a review), it is still unacknowledged/ uncertain/ indeterminate if auditory stimuli lead to inhibitory or excitatory responses, or no change at all in the PPA.
 
-(700 words maximum) An overview of the study design, the assay(s)
-performed, and the created data, including any background information
-needed to put this study in the context of previous work and the literature.
-The section should also briefly outline the broader goals that motivated
-the creation of this dataset and the potential reuse value. We also
-encourage authors to include a figure that provides a schematic overview
-of the study and assay(s) design. This section and the other main
-body sections of the manuscript should include citations to the literature
-as needed \cite{cite1, cite2}. References should be included within the 
-manuscript file itself as our system cannot accept BibTeX bibliography files. 
-Authors who wish to use BibTeX to prepare their references should therefore 
-copy the reference list from the .bbl file that BibTeX generates and paste it 
-into the main manuscript .tex file (and delete the associated 
-\textbackslash{}bibliography and \textbackslash{}bibliographystyle commands).
+% coolness-faktor von natural stimuli ist in der Einleitung beinahe komplett raus
+% data-driven analyses vs. theory-driven analyses ist komplett raus
+% kann man in discussion bringen, muss man aber nicht ist ja dann offensichtlich
+All studies reviewed above used a small set of carefully designed, simplified stimuli to strictly control experimental conditions.
+They further relied on / implemented explicit judgment-based tasks to keep participants alert and paying attention.
+Thus, they cannot / could answer the question how the PPA might behave under life-like conditions.
+Natural stimuli like movies [hasson2008neurocinematics; sonkusare2019naturalistic] or narratives [honey2012not-lost; lerner2011topographic; silbert2014coupled] offer an easy to implement, (continuous,) complex, immersive stimulus that better resembles our experience of a continuous dynamic environment.
+% hier wird GLM nicht explizit erwähnt; denke, muss nicht so spezifisch sein
+In an early study [bartels2004mapping] manually annotated time points that depict faces and human bodies in a 22 minute clip of the movie \textit{Tomorrow Never Dies}.
+These time points correlated with increased hemodynamic activity in the "fusiform face area" {kanwisher1997ffa} and "extrastriate body area"{downing2001body-area} respectively.
+% hier wird ISC als solches nicht erwähnt
+{hasson2004intersubject} took an inverse approach using a 30 minute clip of the movie \textit{The Good, the Bad, the Ugly}.
+fMRI brain volumes showing the highest hemodynamic activity in the PPA [across (five) participants] were matched to the (temporally) correlating movie frames.
+Results revealed that frames depicted indoor and outdoor scenes including buildings and open fields.
+Both studies suggest functional specialization is preserved during free viewing of a movie when many areas respond simultaneously and interact [<- der Schlusssatz ist aus hasson und bartels plagiiert].
+Nevertheless, none of the reviewed study could investigate how the PPA responds to spatial clues that are embedded in a complex, audio-only stimulus.
 
-\section*{Methods}
+% ich habe einiges deiner Kommentare versucht einzubauen
+% wenn dir etwas nicht explizit genug ist, fühl dich, frei mir auf die Finger zu hauen oder es vorzugsweise bei wenig Aufwand direkt umzuformulieren;
+% bzgl.
+open source habe ich nichts geschrieben, weil ich nur weiß, das der Code veröffentlicht werden soll.
+Du hast die Vision diesbezüglich im Kopf und entsprechend auch kanonisch-prägnante Formulierungen und wo die am besten wie hinkommen
+% MIH:
+% 1. is such stimulus (more) suitable for distinguishing this cognitive process from others?
+% 2. given its suitability how do results (PPA-like response localization) differ from a standard visual/block-design localizer for: 
+% 1) complex visual stimulation without a task, and 
+% 2) complex auditory stimulation without an explicit imagery task
+% both aspects together can then be discussed in terms of the feasibility of (multi-dimensional) localizer development with naturalistic stimuli
+% Präteritum oder Präsens? Ist momentan gemischt; find's ok so.
+In this study, we analyze data of three publicly available datasets from the same set of 15 participants as part of the studyforrest data set (\href{http://www.studyforrest.org}{studyforrest.org}).
+We exploratorily investigate how the parrahippocampal gyrus responds to "spatially relevant" events embedded in a 2h audio-visual movie [hanke2016simultaneous] and it's audio-description of same length [hanke2014audiomovie].
+Results are compared to PPA localizations that were obtained from a dedicated visual localizer experiment [sengupta2016extension].
+Both natural stimuli were originally designed to entertain an audience and to capture attention free from any perceptual or behavioral task.
+We annotated events of the otherwise unknown temporal structure of both stimuli to be able to fit a theory-driven model.
+In/for the movie, we annotated different kinds of cinematographic cuts [haeusler2016annotation] as presumably "spatially relevant" events.
+Our rationale was that cuts re-orient the viewer in the depicted environment independent from the exact visual content in the movie frame following the cut.
+In/for the audio-description, we annotated clues about the missing visual content given by the narrator {haeusler2019annotation}.
+We correlated regressors drawn from the annotations in order to detect possible/possibly confounded regressors that might prevent functional isolation of the PPA.
+In conformity to the analyses performed in the studies reviewed above, we submitted our regressors to a standard multi-level, voxel-wise general linear model (GLM).
+For practical reasons (+++es war a) viel einfacher als visual content zu annotieren und ist b) viel interessanter weil non-visual+++) and encouraged by {aziz2008modulation} and {aminoff2013role}, we focus on the audio-description as a possible life-like substitute to individually localize a "visual area" in visually impaired persons.
 
-The Methods should include detailed text describing any steps or procedures 
-used in producing the data, including full descriptions of the experimental 
-design, data acquisition assays, and any computational processing (e.g. 
-normalization, image feature extraction). Related methods should be grouped 
-under corresponding subheadings where possible, and methods should be described 
-in enough detail to allow other researchers to interpret and repeat, if required, 
-the full study. Specific data outputs should be explicitly referenced via data 
-citation (see Data Records and Data Citations, below). Authors should cite 
-previous descriptions of the methods under use, but ideally the method 
-descriptions should be complete enough for others to understand and reproduce 
-the methods and processing steps without referring to associated publications. 
-There is no limit to the length of the Methods section.
+\todo[inline]{the last paragraph contains a bunch of methods already. I would reduce this to talk about
+the general approach: annotation of events, investigation of model quality, cross-analysis of datasets.
+Possibly cite https://psyarxiv.com/sdbqv/ and declare that this study is a concrete realization of that
+promise}
+
+\section{Methods}
+% Ich habe die zwei Methodenteile gemerged und vor allem gekürzt; 
+% Einige Stellen sind aber sicherlich noch zu lange; denn im Zweifel habe ich es stehen gelassen
+% Specific data outputs should be explicitly referenced via data citation (see Data Records and Data Citations, below). 
+An exhaustive description of the participants, stimulus creation, procedure, stimulation setup, and fMRI acquisition can be found in {hanke2014audiomovie} and {hanke2016simultaneous; sengupta2016extension}
+
+\todo{following is a brief summary of most important aspects}
+
+\todo[inline]{we should consider making a statement how often these datasets have been analyzed be
+independent groups already. if we do, they will all get an 'you have been cited' alter eventually}
+
+\subsection{Participants}
+% ggf. mit "Stimuli" zusammenfassen, weil sich das, dadurch dass die gleichen 15 in beiden Experimenten mitgemacht haben schwer prägnant trennen lässt.
+In the first \todo{better to give them labels in the initial paragraph above, we will be referring to them quite a bit} study, fifteen participants (all right-handed, age 21–38 years, mean age 26.6 years, 12 male) listened to the German audio-description (Koop, Michalski, Beckmann, Meinhardt \& Benecke, produced by Bayrischer Rundfunk, 2009) of the movie "Forrest Gump" (R.
+Zemeckis, Paramount Pictures, 1994) as an additional audio track for visually impaired listeners on Swiss public television.
+In the second study, the same 15 participants (21–39 years, mean age 29.4, six female) watched the audio-visual movie with dubbed German audio track.
+All participants reported to have normal hearing, normal or corrected-to-normal vision, and no known history of neurological disorders.
+In both studies, participants received monetary compensation and gave written informed consent for their participation and for public sharing of all obtained data in anonymized form.
+The studies had prior approval by the Ethics Committee of Otto-von-Guericke University of Magdeburg, Germany.
+
+\todo[inline]{i think the stimulus infos need to move from here into the section below}
+
+\subsection{Stimuli}
+% grey bars habe ich nicht erwähnt, obwohl sie - weil bei Lisas Stimuli überall anders - so viel Spaß gemacht haben
+The movie's audio track and the audio-description are largely identical.
+The plot is carried by an off-screen voice of the main character Forrest Gump.
+The audio-description's male narrator additionally verbalizes essential aspects of the visual scenery when there is no dialog, off-screen voice or relevant sound in the audio track.
+The audio-description was temporally aligned to the audio track of the German DVD release (Paramount Home Entertainment, Germany, 2002; PAL video, DE103519SV).
+A few scenes less relevant to the major plot were removed to create the "research cut" lasting $\approx$2h.
+Both stimuli were further processed (filtering, volume adjustments) to improve understandability / audibleness / audibility during MRI scanning.
+Finally, each stimulus was split into eight segments of approximately 15 minutes.
+Except for the first movie segment, each segment started with a snippet of at least six seconds immediately preceding the movie scene boundary used to split the segments.
+\todo{cite fig 3a from hanke2014}
+
+\subsection{Procedure}
+In both studies, participants filled out a questionnaire on their basic demographic information and familiarity with the audio-description or the movie.
+Participants were instructed to inhibit physical movements except for eye-movements, and otherwise to simply "enjoy the audiobook" or "enjoy the movie" respectively.
+Audio-description and movie segments were presented in chronological order with four segments in two fMRI sessions respectively.
+\todo{possibly cut the rest of the section} At the start recording session(s), participants listened to music from the movie’s closing credits segment to individually determine optimal stimulus volume.
+Participants were instructed to "maximize the volume of the stimulus without it becoming unpleasantly loud or causing acoustic distortions by overdriving the loudspeaker hardware".
+% unterscheidet sich ggf.
+zwischen Hörspiel / Film oder kann ganz raus?
+Between sessions, participants left the scanner for a break with a flexible duration. Structural images were obtained during the first study on a day different from the fMRI session.
+
+\subsection{Stimulation setup}
+Stimulation was implemented with PsychoPy v1.79 (with an early version of the MovieStim2 component later to be publicly released with \href{http://www.psychopy.org}{PsychoPy v1.81}; {peirce2007psychopy}) running on a computer with the \href{http://neuro.debian.net}{(Neuro)Debian} operating system [halchenko2012open].
+% Einige Dinge können m.M.n. raus; insb. das in den []-Klammern
+% habe es noch einmal drinnen gelassen, solltest Du die Dinge für wichtig halten
+In the auditory study, visual instructions were presented on a rear-projection screen inside scanner bore using an LCD projector (DLA-G150CL, JVC Ltd.).
+During the functional scans, the projector presented a medium gray screen with the primary purpose to illuminate a participant’s visual field in order to prevent premature fatigue.
+[The screen contained a solid black "fixation" dot that faded in and out at the beginning and end of a movie segment.]
+In the audio-visual study, visual instructions and stimuli were presented on a rear-projection screen using an LCD projector (JVC DLA RS66E, JVC Ltd., light transmission reduced to 13.7\% with a gray filter) connected to the stimulus computer [via a DVI extender system (Gefen EXT-DVI-142DLN with EXT-DVI-FM1000).
+The movie was shown at a viewing distance of 63\,cm in 720\,p resolution at full width on a 1280 *1024\,pixel screen with 60\,Hz video refresh rate and screen dimension of 26.5 * 21.2\,cm, corresponding to 23.75*13.5 or 23.75*10.25 when considering only the movie content and excluding the horizontal gray bars].
+% Hier hat es Unterschiede zwischen Hörspiel & Film geben? habe es wie folgt zusammengefasst; im Zweifel ist es eh noch zu ausführlich
+Auditory stimulation was delivered through an MR confon mkII+ driving custom-built in-ear headphones (HP-M01, MR confon GmbH, Magdeburg, Germany; {baumgart1998electrodynamic}) that reduced the scanner noise by at least 20–30 dB.
+Headphones were  fed from an Aureon 7.1 USB (Terratec) sound card through an optical connection.
+
+\subsection{fMRI data acquisition}
+In both studies, a total of 3599 volumes were recorded for each participant (451, 441, 438, 488, 462, 439, 542 and 338 volumes for movie segment 1–8 respectively).
+In the auditory study, a whole-body 7-Tesla Siemens MAGNETOM magnetic resonance scanner equipped with a local circularly polarized head transmit and a 32 channel brain receive coil (Nova Medical, Inc., Wilmington, MA, USA) acquired T2*-weighted echo-planar images (gradient-echo, 2\,s repetition time (TR), 22\,ms echo time, 0.78\,ms echo spacing, 1488\,Hz/Px bandwidth, generalized autocalibrating partially parallel acquisition, acceleration factor 3, 24 Hz/Px bandwidth in phase encoding direction)  using 36 axial slices (thickness 1.4\,mm, 1.4 x 1.4\,mm in-plane resolution, 224\,mm field-of-view, anterior-to-posterior phase encoding direction) with a 10 percent inter-slice gap were recorded in ascending order.
+Slices were oriented to include the ventral portions of frontal and occipital cortex while minimizing intersection with the eyeballs.
+The field-of-view was centred on the approximate location of Heschl's gyrus.
+% EPI images were online-corrected for motion and geometric distortions [Oh, S.
+et al.
+2012; In, M.
+\& Speck, O., 2012; Chung, J.
+et al., 2011+++].
+Auxiliary scans for slice alignment and motion- and distortion-correction were performed at the beginning of the first fMRI recording session and also after the break at the start of the recording for the second half of the movie.
+In the audio-visual study, a whole-body 3 Tesla Philips Achieva dStream MRI scanner equipped with a 32 channel head coil acquired T2*-weighted echo-planar images (gradient-echo, 2\,s repetition time (TR), 30\,ms echo time, 90 DEGREE flip angle, 1943\,Hz/Px bandwidth, parallel acquisition with sensitivity encoding (SENSE) reduction factor 2).
+35 axial slices (thickness 3.0\,mm, 10 \% inter-slice gap) with 80*80 voxels (3.0*3.0 mm of in-plane resolution), 240\,mm mm field-of-view (FoV) and an anterior-to-posterior phase encoding direction were recorded in ascending order.
+Philips’ “SmartExam” was used to automatically position slices in AC-PC orientation such that the topmost slice was located at the superior edge of the brain.
+
+\subsection{Stimulus Annotation}
+% wurde unter "Regressoren" zu Beginn der 1st-lvl-Analyse verschoben
+
+\section{Data analysis }
+% \todo{shouldn't this be also just in Methods?}
+% hier ggf. noch expliziter machen, dass die spatially downsampled sind
+% https://openneuro.org/datasets/ds000113 
+% denoised movie data: 
+% https://github.com/OpenNeuroDatasets/ds001769/tree/master/sub-01/ses-movie/func
+fMRI time series data were obtained from
+\href{''https://github.com/psychoinformatics-de/studyforrest-data-aligned''}{GitHub}.
+Data are already aligned to a subject-specific \href{''https://github.com/psychoinformatics-de/studyforrest-data-templatetransforms''}{3 Tesla BOLD template} \todo{cite sengupta2016 where this was first done and described, ie same image/data was used here} by a rigid body transformation in MCFLIRT ([jenkinson2002registration]) to correct for motion during scanning.
+All further analysis steps in the current study were carried out using tools of FSL v5.0.9 (\href{''https://www.fmrib.ox.ac.uk/fsl''}{FMRIB's Software Library};[smith2004fsl]; on a computer cluster running the \href{https://www.debian.org}{Debian} GNU/Linux operating system.
+Software packages were obtained from repositories of \href{http://neuro.debian.net}{NeuroDebian}([halchenko2012open]).
+
+\subsection{Preprocessing}
+Preprocessing (and statistical analysis) was carried out using FEAT v6.00 (FMRI Expert Analysis Tool;[woolrich2001autocorr]) as part of FSL.
+High-pass temporal filtering was applied to every segment using a Gaussian-weighted least-squares straight line with a cutoff period of 150\,s (sigma=75.0\,s) to remove low-frequency confounds.
+Slice-time correction was performed using Fourier-space time series phase-shifting.
+\todo{hmm, why did we do that (slicetiming)?} The brain was extracted from surrounding tissues using BET [smith2002BET].
+Data were spatially smoothed applying a Gaussian kernel with full width at half maximum (FWHM) of 4.0 mm.
+A grand-mean intensity normalization of the entire 4D dataset was performed by a single multiplicative factor.
+Correction for local autocorrelation in the time series (prewhitening) was applied using FILM (FMRIB’s Improved Linear Model).
+
+\subsection{Statistical analysis}
+A standard two-level general linear model (GLM) analysis was conducted in FEAT to create subject-specific results ($Z$-maps).
+A subsequent, third-level analysis averaged contrast estimates over subjects.
+
+\subsubsection{first-level}
+\paragraph{Regressors \todo{stimulus/statistical model?}}
+To build the regressors for the GLMs, we took advantage of two publicly available annotations of the stimuli's temporal structure.
+One annotation of speech occurring in the audio-description and movie {haeusler2019annotation}, and a second annotation of movie cuts and depicted locations \href{https://f1000research.com/articles/5-2273}{haeusler2016annotation}.
+As a first step, the annotations were split via (\href{"https://github.com/chrhaeusler/studyforrest-data-annotations/blob/master/code/researchcut2segments.py"}{python script} into eight parts corresponding to the eight segments used in the scanner.
+% wenn ich folgend den "null regressor" nehme, darf ich den ganzen Run - glaube ich - in der 2nd level Analyse gar nicht benutzen??
+For the auditory stimulus, we used nouns embedded in sentences spoken by the narrator.
+The nouns are categorized by the clue they provide about a cinematographic scene's environment \todo{maybe skip the names and just cite the table} (geo, geo-room; setting\_new, setting\_old), its inherent persons (female, female name; male, male name, person), a person's appearance (face, head; body, bodypart), and a scene's inherent objects (object, furniture).
+Details on procedure to annotate the stimuli on a single-world level and details on the rules to manually categorize the nouns can be found in the \href{"https://www.overleaf.com/project/5d4ab1b759001b5db6ea2bc3"}{corresponding paper}.
+We created 11 regressors from the XY (selected?) original categories by joining / merging some categories (female, females, fname; male, males, mname; face, head) into one regressor (sex\_f; sex\_m; fahead).
+The regressors were modeled as boxcar functions at the end of each noun with a duration of 200 ms (jetzt ist es über Wortlänge).
+If a segment did not contain a single event for a specific regressor, a null regressor was chosen for that segment.
+Five regressors related to the cinematographic cuts (s.
+below) were added to built contrasts of cross-modal negative control.
+Two regressors reflecting auditory (low-level) features (left-right loudness volume / amplitude???
+difference; root mean squared amplitude) aligned to the frame rate of (40\,ms) were modeled to reduce nuisance effects.
+An overview and short explanation of the 11 regressors and 5 + 2 additional nuisance regressors can be found in Table xy.
+% entgegen der Masterarbeit kommen hier für den Film keine Abbildungen zur Verdeutlichung, weniger Text; no cut erkläre ich nicht lang & breit
+% die regressoren settinge_new & setting_old aus dem Hörspiel habe ich meiner meinung nach unnötigerweise im Film mit-modelliert; lasse mich da aber auch umstimmen
+% -> noch mal reingucken; kamen im Grunde nur "auditorische Areale" als Cluster vor; umgekehrt gab's bei der visuellen Regressoren im Hörbuch keine sign. Cluster
+For the audio-visual stimulus, we categorized the depicted location in the frame following one of the 869 cuts in the movie to built five regressors: 1) unfamiliar setting (US), 2) familiar setting (FS), 3) locale switch (LS), 4) unfamiliar perspective (UP), 5) familiar perspective (FP).
+In order to build negative control contrasts, a sixth regressors was created by pseudo-randomly choosing frames present within a shot and apart from a cut.
+Regressors were modeled as boxcar function lasting 200\,ms after a cut.
+An overview and short explanation of the six regressors and the additional nuisance regressors reflecting (auditory and) visual low-level features can be found in Table xy.
+For both stimuli, regressors were convolved with a double gamma canonical hemodynamic response function (HRF).
+Their temporal derivatives were added to compensate for small timing differences [friston1998event].
+Six motion parameters were used as additional nuisance regressors.
+Finally, designs were filtered with the same high-pass filter (cutoff period of 150\,s) as the BOLD time series.
+
+\begin{table*}
+\caption{Regressors used in the analysis of the audio-description.
+\todo[inline]{make clear which stimulus each annotation is based on, and make clear(er) what defined an event.
+This could be a big table, because good defintions are important for judging the results}}
+\begin{tabular}{lll}
+\toprule
+\textbf{name} & \textbf{count} & \textbf{description} \\
+\midrule
+body & 66 & trunk of the body or overlaid clothes \\ 
+bpart & 69 & limbs and trousers \\ 
+facehead & 83 & face(parts) or head(parts) \\
+furniture & 50 & big inventory of rooms (insides/outsides) \\
+geo & 125 & immobile landmarks \\ 
+geo-room & 105 & elements defining a locale's spatial layout \\ 
+setting\_new & 86 & first-time mentioned setting \\ 
+setting\_old & 37 & recurring setting \\ 
+object & 284 & inanimate entities with firm boundaries \\ 
+sex\_f & 108 & female person(s), name \\ 
+sex\_m & 403 & male person(s), name \\ 
+vse\_new & 96 & control for movie cuts; s. table y \\
+vse\_old & 90 & control for movie cuts; s. table y \\
+vloc\_change & 89 & control for movie cuts; s. table y \\
+vpe\_new & 386 & control for movie cuts; s. table y \\
+vpe\_old & 208 & control for movie cuts; s. table y \\
+fg\_ad\_lrdiff & xx &  left-right volume difference \\
+fg\_ad\_rms & xx & root mean square amplitude \\ 
+\bottomrule
+\end{tabular}
+\end{table*}
+
+\begin{table*}
+\caption{Regressors used in the analysis of the movie.}
+\begin{tabular}{lll}
+\toprule
+\textbf{name} & \textbf{count} & \textbf{description} \\
+\midrule
+vse\_new & 96 & change of the camera position to a setting not depicted before \\
+vse\_old & 90 & change of the camera position to a recurring setting \\
+vloc\_change & 89 & change of the camera position to another locale within the same setting \\
+vpe\_new & 386 & change of the camera position within a locale not depicted before \\
+vpe\_old & 208 & change of the camera position within a recurring locale \\
+no\_cut & 148 & a continuous frame from the same camera position \\
+se\_new & 148 & audio-description's narrator; s. table x; KANN RAUS? \\
+se\_old & 148 & audio-description's narrator; s. table x; KANN RAUS? \\
+fg\_av\_ger\_lr & xx & left right +++???+++ in movie frame  \\
+fg\_av\_ger\_lrdiff & xx & left-right volume difference \\
+fg\_av\_ger\_pd & xx & perceptual differences of consecutive frames \\
+fg\_av\_ger\_rms & xx & root mean square amplitude \\
+fg\_av\_ger\_ud & xx & +++up down???+++ \\
+\bottomrule
+\end{tabular}
+\end{table*}
+\begin{figure}[htbp]
+  \centering
+%  \includesvg{regressors-corr.pdf}
+  \includegraphics[width=1.0\textwidth]{regressors-corr.pdf}
+  % MIH ignore such beautification issues, they are easy to fix at the very end with a manual intervention. Shifting the colorbar by hand to make it look nicer is no threat to reproducibility ;-)
+  \caption{\label{fig:Rorrelation of Regressors}Wo diese Abbildung bringen?
+Im Grunde ist es "Results".
+Ich denke, man kann am Ende des Abschnitts "Regressoren" der 1st-lvl-Analyse einen kurzen Hinweise bringen und alles hier in der Bildunterschrift  kurz erläutern; Discussion dazu kommt in der Discussion die geringen Korrelationen nicht selbstverständlich sind}
+\end{figure}
+\paragraph{audio contrasts of parameter estimate}
+% Überblick über die Kontraste geben, die tatsächlich am Ende im Paper berichtet werden -> am besten telefonisch klären
+% HIER ERZÄHLEN, WARUM VIELE KONTRASTE GERCHNET WURDEN und WARUM DER EINE COPE THE ONE AND ONLY IST
+
+\begin{table*}
+\caption{Contrasts of parameter estimates for the analysis of the audio-description.}
+% das sind die zusammengefassten Kurzversionen, d.h. nicht alle Regressoren sind explizit in dem COPEs ausformuliert
+\begin{tabular}{lll}
+\toprule
+\textbf{COPE nr.} & \textbf{description} & \textbf{aim} \\
+\midrule
+1 & geo, rgeo, se\_new, se\_old > non\_geo & PPA \\
+2 & geo, rgeo, se\_new > non\_geo & PPA \\
+3 & geo, rgeo > non\_geo & PPA <<-- THE COOL \\
+4 & geo > non\_geo & PPA \\
+5 & se\_new > non\_geo & PPA \\
+6 & se\_new, se\_old > non\_geo & PPA \\
+7 & se\_new > se\_old & PPA \\
+8 & body > all\_others (excl. bpart) & EBA \\
+9 & body, bpart > all\_others & EBA \\
+10 & body > non\_persons (excl. bpart) & EBA \\
+11 & body, bpart > non\_persons & EBA \\
+12 & body, bpart > non\_persons (excl. faHead) & EBA \\
+13 & fahead > all\_others & FFA \\
+14 & fahead > all\_others (excl. body/parts) & FFA \\
+15 & fahead > non\_persons & FFA \\
+16 & fahead > non\_persons (excl. body/parts) & FFA \\
+17 & obj > all\_others & LOC \\
+18 & obj > all\_others (excl. fahead) & LOC \\
+19 & obj > all\_others (excl. fahead, rgeo) & LOC \\
+20 & obj > persons & LOC \\
+21 & se\_old > se\_new & DMN \\
+22 & se\_old > non\_settings & DMN \\
+23 & se\_old > non\_geo & DMN \\
+24 & female > male & ??? \\
+25 & male > female & ??? \\
+26 & persons > non\_persons (excl. body/parts) & ??? \\
+27 & non\_persons (excl. body/parts) > persons & ??? \\
+28 & se\_new > se\_old & visual contr. \\
+29 & pe\_new > pe\_old & visual contr. \\
+30 & se\_new, pe\_new > se\_old, pe\_old & visual contr. \\
+31 & se\_new > pe\_old & visual contr. \\
+32 & se\_new > se\_old, pe\_old & visual contr. \\
+33 & se\_new, pe\_new > pe\_old & visual contr. \\
+34 & se\_old > se\_new & DMN  contr. \\
+35 & pe\_old > pe\_new &  DMN contr. \\
+36 & no\_cut > pe\_new, pe\_old & neg. control \\
+\bottomrule
+\end{tabular}
+\end{table*}
+
+\paragraph{video contrasts of parameter estimate}
+% Überblick über die Kontraste geben, die tatsächlich am Ende im Paper berichtet werden
+% ggf. irgendwo noch reinpressen, dass man damit fast alle schnitte in FG benutzt hat
+We created a contrast presumably correlating with increased hemodynamic activity in the PPA by contrasting different kind of cuts.
+This was done without controlling for the specific visual content depicted in the frame after each cut.
+The cinematographic rationale was that - over the course of a movie - cuts shift from establishing the setting and the spatial relationships within a setting at the beginning of a movie to depicting persons and objects more relevant to the subsequently evolved narrative later in the movie {brown2012cinematography; mercado2011filmmakers}.
+The neurocientific rationale was that activity in the PPA is greater when participants view novel versus repeated scenes resp.
+view-points {epstein1999parahippocampal}.
+Hence, we contrasted cuts to a setting occurring for the first time (vse\_new) and cuts within a locale depicted for the first time (vpe\_new) with shots to a recurring setting (vse\_old) and cuts within a recurring locale (vpe\_old).
+
+\begin{table*}
+\caption{COPEs for the movie.}
+\begin{tabular}{lll}
+\toprule
+\textbf{COPE nr. } & \textbf{description} & \textbf{aim} \\
+\midrule
+1 & geo, rgeo, se\_new, se\_old > non\_geo & PPA \\
+1 & se\_new > se\_old & PPA \\
+2 & pe\_new > pe\_old & PPA \\
+3 & se\_new, pe\_new > se\_old, pe\_old & PPA (the true and cool one) \\
+4 & se\_new > pe\_old & PPA \\
+5 & se\_new > se\_old, pe\_old & PPA \\
+6 & se\_new, pe\_new > pe\_old & PPA \\
+7 & pe\_new > se\_old, pe\_old & PPA \\
+8 & se\_old > se\_new & DMN \\
+9 & pe\_old > pe\_new & DMN \\
+10 & no\_cut > se\_new, se\_old & neg. control \\
+11 & no\_cut > se\_new & neg. control \\
+12 & no\_cut > se\_old & neg. control \\
+13 & no\_cut > pe\_new, pe\_old & neg. control \\
+14 & ao: se\_new > se\_old & audio control \\
+15 & ao: se\_old > se\_new & audio control \\
+\bottomrule
+\end{tabular}
+\end{table*}
+
+\paragraph{Registration \& smoothing: individuals vs. group}
+% hier wird's wie üblich bei Registrierung;
+% bitte gucken, ob korrekt wiedergeben, was ihr gemacht habt
+% wie besprochen sind hier die individuelle Results im subject space
+% später warpe ich individuelle 2nd-lvl-results "for visualization purposes" doch noch nach MNI 
+The GLM analysis that fitted each voxel's time course separately for each subject was performed in functional space preserving the orientation of the EPI images.
+Correction for local autocorrelation in the time series (prewhitening) was applied using FILM (FMRIB's Improved Linear Model) to improve estimation efficiency [woolrich2001autocorr].
+For subsequent subject-specific second level results, subject-specific BOLD T2* time series were anatomically aligned via linear transformation to a subject-specific, study-specific T2* template (s.
+\href{"https://github.com/psychoinformatics-de/studyforrest-data-templatetransforms/blob/master/sub-01/bold3Tp2/brain.nii.gz"}{example}) that served as standard space.
+For subsequent the third level results averaging contrasts of interest across subjects, time series were anatomically aligned via non-linear transformation [+++wie genau?+++] to a \href{"https://github.com/psychoinformatics-de/studyforrest-data-templatetransforms/blob/master/templates/grpbold3Tp2/brain.nii.gz"}{study-specific T2* group template}.
+To facilitate visualization and identification of cortical structures, this reference images was later co-registered to the MNI 152 template with an affine transformation (12 degrees of freedom)
+\subsubsection{second level}
+The second-level analyses which averaged contrast estimates over the eight stimulus segments were carried out using a fixed effects model, by forcing the random effects variance to zero in FLAME (FMRIB's Local Analysis of Mixed Effects) [beckmann2003general, woolrich2004multilevel].
+Z (Gaussianised T/F) statistic images were thresholded using clusters determined by Z>2.3 and a (corrected) cluster significance threshold of p=.05 [worsley2001statistical].
+\subsubsection{third level}
+Third level analyses which averaged contrast estimates over subjects were carried out using FLAME stage 1 with automatic outlier detection [beckmann2003general, woolrich2004multilevel, woolrich2008robust].
+Z (Gaussianised T/F) statistic images were thresholded using clusters determined by Z>3.4 and a (corrected) cluster significance threshold of p=.05 [Worsley, 2001].
+% Brain regions associated with observed clusters were determined with the Juelich Histological Atlas Eickhoff et al.
+(2005); Eickhoff et al.
+(2007), the Harvard-Oxford Cortical Atlas (Desikan et al., 2006), and with queries on the NeuroSynth database (Yarkoni et al., 2011) provided by FSL.
+% In order to determine if activated regions were spatially congruent with higher-visual functional areas (PPA, FFA, OFA, LOC and EBA), study-specific ROI masks generated by the mean of visual localizers in Sengupta et al.
+(2016) were used.
+
+\subsection{Das Post-FSL-Scripting-Gedöns}
+% Wahrscheinlicher ist, dass das Prozedere der Skripte nicht im Methodenteil berichtet werden muss
+% als Erläuterung in den Bildunterschriften im Ergebnisteil sollten reichen
+% -> die Skripte durchlaufen lassen und die Abbildungen in den Ergebnisteil samt Bildunterschriften einfügen
+\subsubsection{plot-group-and-individuals.py}
+
+\subsubsection{plot-bland-altman.py}
+
+% generate-masks.py; DO NOT TOUCH! 
+% FOR GROUP:
+% 0. In FSLeyes, manually created probabilistic brain lobe maps from \href{"https://doi.org/10.5281/zenodo.1470761"}{the MNI Structural Atlas} (./data/atlases/mni_prob_*.nii.gz)
+% 1.
+these brain lobe maps were aligned (via FSL's flirt -applyxf with 12 dof) to the \href{"https://github.com/psychoinformatics-de/studyforrest-data-templatetransforms/blob/master/templates/grpbold3Tp2/brain.nii.gz"}{study-specific T2* group template} (./data/atlases/grpbold3Tp2_mni_prob_*.nii.gz)
+% 2.
+from \href{"https://github.com/psychoinformatics-de/studyforrest-data-visualrois"} {sengupta2016extension}: UNIlateral probabilistic group ROI masks (data/masks/*_overlap.nii.gz) -> BIlateral probabilistic & binary grp ROI masks in grp space (.data/masks/bilat_???_prob.nii & .data/masks/bilat_???_binary.nii )
+% FOR SUBJECTS:
+% 1. bilateral grp ROI masks in grp space -> bilateral grp ROI masks in subject space (applywarp; sub-??/masks/grp_*_bin.nii.gz)
+% 2. probabilistic MNI mask -> subject space (via FSL's applywarp)
+% 3. merge probabilistic occipital & temporal mask in subject space
+%	(sub-??/masks/mni_prob_occip_tempo.nii.gz)
+% 4. created subject-specific FOV from 4d 7t audio drama time series
+%	(./sub-??/masks/ao_fov_mask.nii.gz)
+% 5. individual, unilateral ROIs from {sengupta2016extension} were joined and co-registered to MNI 152 (1mm) space, and binarized
+% 6. individual (un)thresholded zmaps (from the COPEs) were co-regi<wstered with MNI 152 (1mm) template.
+\section{Results (audio)}
+\begin{itemize}
+\item vgl. mit Ergebnis-Teilen anderer Localizer (in wievielen VPN funktioniert's etc.)
+\item   https://en.wikipedia.org/wiki/Bland%E2%80%93Altman_plot
+\end{itemize}
+
+\section{Results (movie)}
+\begin{itemize}
+\item lore ipsum
+\end{itemize}
+
+% MIH the discussion should primarily be anchored on the points the introduction concludes with.
+From my POV there is no need (and likely no space) to discuss results by stimulus type.
+Issue like different impact of attentional focus etc can be brought up in the joint paragraph that discussed how such a factor could have differentially impacted the results -- and if that would matter.
+\section{Discussion (audio)}
+
+\begin{itemize}
+\item Hanke et al.
+(2014): Compared to an audio-visual movie, this is a stimulus that leaves a much larger margin for inter-individual differences in imagining scenery, as well as actors' character and personality traits, while still preserving the time-locked presentation of information to a listener.
+At the same time, an auditory stimulus limits the effect of an attentional focus on the selection of a subset of simultaneously occurring auditory events, in contrast to the selection of different parts of the visual field.
+\item mental imagery hypthesis (s. O'Craven \& Kanwisher, 2000)
+\item Lerner (2011), Honey (2012), Silbert (2014) finden keine ISC in PPA? vgl. DataPaper bzgl. Hörbuch??
+\item setting\_new ist häufig vermischt mit anderer Kategorie "ein Arzt", "ein alter Film", "auf einer Straße", "im Fernsehen", "die drei Jungs", "die zwei im Bett", "Jenny als Teenager", "Forrest vor einem Buffet", "Kennedy", "Jenny kommt aus dem Wohnwagen ihrer Großmutter"
+\item  Soundscape macht es häufiger bereits vorher klar, dass Settingwechsel ist bzw. nicht erst das annotiere Substantiv
+\item object und (room)geo ist vermischt
+\item Retrospelinal Cortex ist in Probabilistic maps krasser als PPA.
+\end{itemize}
+
+\section{Discussion (movie)}
+\begin{itemize}
+\item lore ipsum
+\end{itemize}
+
+\section*{General Discussion}
+\begin{itemize}
+\item "Abfall" einer Film-Messung
+\item Story für parietale Aktivierung im Film -> räuml. Orientierung / Aufmerksamkeit 
+\item CONFOUNDS als klassisches Gegenargument gg. Filme (aber er ändert sich nicht über die Zeit, vgl. resting state)
+\item was sind für Film und Audiobook die Confounds? 
+\item Occipital Place Area (Nakamura, 2000), RSC
+\item Natural stimuli like movies [hasson2008neurocinematics; sonkusare2019naturalistic] or narratives [honey2012not-lost; lerner2011topographic; silbert2014coupled] offer an easy to implement, (continuous,) complex, immersive, task-free paradigm that more closely resembles our natural dynamic environment than traditional experimental designs.
+Compared to specifically designed paradigms, the complexity of a natural stimulus goes hand in hand with an unknown temporal structure unless the stimulus is - often manually - annotated [haeusler2016annotation; labs2015portrayed].
+\item Due to their continuity, complexity, and length, they offer a vast amount of data on a variety of brain functions like low-level perception, attention, comprehension, memory, emotions, or social interactions.
+This suggests the data can later be reused for variety of totally different, independent research questions, possibly on an individual level.
+\item aminoffr2013; jedoch zu non-spatial stuff: Although the PHC is commonly thought of as responding to visual stimuli, it has also been found to elicit activity for auditory stimuli [25,26,30,31] and to respond to odor stimuli [32–34].
+\end{itemize}
 
 \subsection*{Code availability}
-
-For all studies using custom code in the generation or processing of datasets, 
+% wo kommt dieser Abschnitt hin?
+% how to write Code availability statement
+% https://www.springernature.com/gp/authors/research-data-policy/data-availability-statements/12330880
+\emph{for all studies using custom code in the generation or processing of datasets, 
 a statement must be included here, indicating whether and how the code can be 
-accessed, including any restrictions to access. This section should also include 
-information on the versions of any software used, if relevant, and any specific 
-variables or parameters used to generate, test, or process the current dataset.
-
-\section*{Data Records}
-
-Please explain each data record associated with this work, including
-the repository where this information is stored, and an overview of
-the data files and their formats. Each external data record should
-be listed in Data Citation section at the end of this template, and 
-records should be cited throughout the manuscript as, for example 
-(Data Citation 1).
-
-Tables should be used to support the data records, and should clearly indicate 
-the samples and subjects, their provenance, and the experimental manipulations 
-performed on each. They should also specify the data output resulting from each 
-data-collection or analytical step, should these form part of the archived record. 
-Please see the submission guidelines at the \emph{Scientific Data} website, and 
-our Word templates for more information on preparing such tables.
-
-\section*{Technical Validation}
-
-This section presents any experiments or analyses that are needed
-to support the technical quality of the dataset. This section may
-be supported by up figures and tables, as needed. This is a required
-section; authors must present information justifying the reliability
-of their data.
-
-\section*{Usage Notes}
-
-Brief instructions that may help other researchers reuse these dataset.
-This is an optional section, but strongly encouraged when helpful
-to readers. This may include discussion of software packages that
-are suitable for analyzing the assay data files, suggested downstream
-processing steps (e.g. normalization, etc.), or tips for integrating
-or comparing this with other datasets. If needed, authors are encouraged
-to provide code, programs, or data processing workflows when they may help 
-others analyse the data. We encourage authors to archive related code in 
-a DOI-issuing archive when possible, but code may also be supplied as 
-supplementary information files.
-
-For studies involving privacy or safety controls on public access
-to the data, this section should describe in detail these controls,
-including how authors can apply to access the data, and what criteria
-will be used to determine who may access the data, and any limitations
-on data use.
+accessed, including any restrictions to access; include information on the versions 
+of any software used, if relevant, and any specific variables or parameters used to 
+generate, test, or process the current dataset. }
+\begin{itemize}
+\item wo kommt der Abschnitt hin?
+\end{itemize}
 
@@
 
-Text acknowledging non-author contributors. Acknowledgements should
+\emph{Text acknowledging non-author contributors. Acknowledgements should
 be brief, and should not include thanks to anonymous referees and
@@
 acknowledged. Author contributions Please describe briefly the contributions
-of each author to this work on a separate line.
-
+of each author to this work on a separate line.} 
 AK did this and that. 
-
 BG did this and that and the other.
+\begin{itemize}
+\item wo kommt der Abschnitt hin?
+\end{itemize}
 
@@
 
-A competing financial interests statement is required for all accepted
+\emph{A competing financial interests statement is required for all accepted
 papers published in \emph{Scientific Data}. If none exist simply write,
-``The author(s) declare no competing financial interests''.
+``The author(s) declare no competing financial interests''.}
+\begin{itemize}
+\item wo kommt der Abschnitt hin?
+\end{itemize}
 
@@
 
-Figure should be referred to using a consistent numbering scheme through
+\emph{Figure should be referred to using a consistent numbering scheme through
 the entire Data Descriptor. For initial submissions, authors may choose
@@
 the inclusion of figures in the Supplementary Information \textendash{}
-all key figures should be included here in the main Figure section.
+all key figures should be included here in the main Figure section.}
 
-Figure legends begin with a brief title sentence for the whole figure
+\emph{Figure legends begin with a brief title sentence for the whole figure
 and continue with a short description of what is shown in each panel,
 as well as explaining any symbols used. Legend must total no more
-than 350 words, and may contain literature references.
+than 350 words, and may contain literature references.} 
+\begin{itemize}
+\item wo kommt der Abschnitt hin?
+\end{itemize}
 
@@
 
-Tables supporting the Data Descriptor. These can provide summary information
+\emph{Tables supporting the Data Descriptor. These can provide summary information
 (sample numbers, demographics, etc.), but they should generally not
 be used to present primary data (i.e. measurements). Tables containing
-primary data should be submitted to an appropriate data repository.
+primary data should be submitted to an appropriate data repository.}
 
-Tables may be provided within the \LaTeX{} document or as separate
+\emph{Tables may be provided within the \LaTeX{} document or as separate
 files (tab-delimited text or Excel files). Legends, where needed,
@@
 page will be included in the PDF version of the article (up to a maximum
-of three).
+of three).}
+\begin{itemize}
+\item wo kommt der Abschnitt hin?
+\end{itemize}
 

### 2020-04-14 paper/main.tex
initial commit after migration from Overleaf

--- 2020-03-18 main.tex
@@
 \newcommand{\scidatalogo}{\includegraphics[height=36pt]{SciData_logo.jpg}}
-\newcommand{\overleaflogo}{\includegraphics[height=36pt]{Overleaf-logo-300dpi.png}}
 \pagestyle{fancy}
@@
 \lhead{\textsc{\scidatalogo}}
-\rhead{\textsc{\overleaflogo}}
 
@@
 \end{table*}
-\begin{figure}[htbp]
-  \centering
-%  \includesvg{regressors-corr.pdf}
-  \includegraphics[width=1.0\textwidth]{regressors-corr.pdf}
-  % MIH ignore such beautification issues, they are easy to fix at the very end with a manual intervention. Shifting the colorbar by hand to make it look nicer is no threat to reproducibility ;-)
-  \caption{\label{fig:Rorrelation of Regressors}Wo diese Abbildung bringen?
-Im Grunde ist es "Results".
-Ich denke, man kann am Ende des Abschnitts "Regressoren" der 1st-lvl-Analyse einen kurzen Hinweise bringen und alles hier in der Bildunterschrift  kurz erläutern; Discussion dazu kommt in der Discussion die geringen Korrelationen nicht selbstverständlich sind}
-\end{figure}
+
 \paragraph{audio contrasts of parameter estimate}

### 2020-04-14 paper/main.tex
add references.bib & citations to manuscript

@@
 \lhead{\textsc{\scidatalogo}}
+\usepackage{natbib}
 
@@
 
-\author{Christian O. Häusler\textsuperscript{1,2{*}}, Michael Hanke\textsuperscript{1}}
+\author{Christian~O.~Häusler\textsuperscript{1,2{*}}, Michael Hanke\textsuperscript{1,2}}
 % https://www.nature.com/sdata/publish/for-authors#other-formats
@@
 \thispagestyle{fancy}
+
 1. Psychoinformatics Lab, Institute of Neuroscience and Medicine, Brain \& Behaviour (INM-7), Research Centre Jülich, Jülich, Germany,
@@
 \begin{abstract}
-% Analysis Paper abstract: < 170 words
-% no references are allowed:
-% new analysis of existing data of interest to a broad section of our audience
+% < 170 words
+% new analysis of existing data
+% of interest to a broad section of our audience
 % highlighting innovative examples of data reuse
-% may be used to present compelling new findings and conclusions derived from published data.
-% submissions using data previously published at Scientific Data are encouraged
+% may be used to present compelling new findings & conclusions derived from published data.
 % submissions should exemplify reproducible research by clearly describing all steps in the analysis
@@
 \section{Introduction}
-% Bzgl. Zitationen (lasse alles so lange wie möglich in Kbibtext's .bib-Datei): \cite{cite1, cite2}
 % our system cannot accept BibTeX bibliography files; authors who wish to use BibTeX to prepare their references should therefore copy the reference list from the .bbl file that BibTeX generates and paste it into the main manuscript .tex file (and delete the associated  \textbackslash{}bibliography and \textbackslash{}bibliographystyle commands).
+
+% yeah, whatever. Arbeite erstmal mit der references.bib
+% und habe oben '\usepackage{natbib}' eingefügt
 Cognitive neuroscientists use brain imaging methods like blood oxygenation level-dependent functional magnetic resonance imaging (BOLD fMRI) to map perceptual and cognitive brain processes (e.g.
-viewing of landscapes, {epstein1998ppa}; or theory of mind {spunt2014validating}) to functional brain areas or networks.
+viewing of landscapes, \citep{epstein1998ppa}; or theory of mind \citep{spunt2014validating}) to functional brain areas or networks.
 Brain mapping studies have traditionally employed small sets of carefully chosen, simplified stimuli to strictly control experimental conditions and facilitate functional isolation of brain areas.
-The disadvantage is that a limited number of simplified stimuli does not resemble our real-life experience and lacks external {westfall2016fixing} as well as ecological validity {hasson2004intersubject}.
+The disadvantage is that a limited number of simplified stimuli does not resemble our real-life experience and lacks external \citep{westfall2016fixing} as well as ecological validity \citep{hasson2004intersubject}.
 Additionally, brain mapping studies have traditionally averaged / usually average results across at least 10-15 subjects to improve the signal-to-noise-ratio (SNR).
 The disadvantage here is that the averaging approach does not  characterize brain functions at an individual level, a prerequisite for the application of brain imaging methods in individual diagnostics (cf.
-{dubois2016building})
+\citep{dubois2016building})
 
@@
 % bin auch am überlegen, ob ich in den Ergebnissen zu den sagitallen slices durch die PPAs noch sagitale Slices durch die RSCs dazunehme??
-A classic example of a functional, higher-level visual area is the "parahippocampal place area" (PPA) {epstein1998ppa; epstein1999parahippocampal}.
-The PPA is located in the posterior parahippocampal gyrus at the boundary to the anterior lingual gyrus and medial fusiform gyrus, both being part of the ventral visual stream [mishkin1982contribution; goodale1992separate].
+A classic example of a functional, higher-level visual area is the ``parahippocampal place area'' (PPA) \citep{epstein1998ppa, epstein1999parahippocampal}.
+The PPA is located in the posterior parahippocampal gyrus at the boundary to the anterior lingual gyrus and medial fusiform gyrus, both being part of the ventral visual stream \citep{mishkin1982contribution, goodale1992separate}.
 Increased hemodynamic activity in the PPA correlates with the perception of static pictures of landscapes or landmarks compared to pictures of tools or faces.
-According to the spatial layout hypothesis, the PPA is involved in processing the surface geometry of a visual stimulus and possibly in identifying scenes based on their spatial layout {epstein2010reliable}.
-Results generalize at a group average level to a) mental imagination of landscapes {ocraven2000mental} and b) haptic exploration of scenes {wolbers2011modality}, \todo{this needs some more glue.
+According to the spatial layout hypothesis, the PPA is involved in processing the surface geometry of a visual stimulus and possibly in identifying scenes based on their spatial layout \citep{epstein2010reliable}.
+Results generalize at a group average level to a) mental imagination of landscapes \citep{ocraven2000mental} and b) haptic exploration of scenes \citep{wolbers2011modality}, \todo{this needs some more glue.
 the following is not just about spoken stimuli} whereas results of a study using spoken, place-related sentences were unclear \todo{should be more specific.
-unclear could mean 'not well described'} {aziz2008modulation}:
-a) In a study conducted by {ocraven2000mental} participants viewed alternating blocks of pictures showing famous faces and familiar places during an initial experimental paradigm.
-In a subsequent paradigm, participants were instructed to "form a vivid mental image" of the previously viewed pictures.
+unclear could mean 'not well described'} \citep{aziz2008modulation}:
+a) In a study conducted by \citep{ocraven2000mental} participants viewed alternating blocks of pictures showing famous faces and familiar places during an initial experimental paradigm.
+In a subsequent paradigm, participants were instructed to ``form a vivid mental image'' of the previously viewed pictures.
 The PPA showed increased activation during imagination of places compared to faces but the imagination tasks showed a smaller activation level compared to the perceptual task.
 % Wolbers im Folgenden macht noch ne Connectivitäts-Analyse mit dem Occipital-Cortex; da ist dann keine Connectivity im Vergleich zum visuellen Paradigma; deshalb kann das laut ihm kein mental image sein: "the scene-related increase in coupling with the PPA was significantly stronger in multiple clusters in occipital cortex under visual than haptic stimulation (Figure 2B; Table S2)"
-b) In a block design study conducted by {wolbers2011modality} the PPA of sighted participants showed increased activation during a delayed matching-to-sample task of haptically explored scenes constructed from Lego bricks compared to haptically explored abstract geometric objects.
+b) In a block design study conducted by \citep{wolbers2011modality} the PPA of sighted participants showed increased activation during a delayed matching-to-sample task of haptically explored scenes constructed from Lego bricks compared to haptically explored abstract geometric objects.
 % Aziz hat auf eine zweite Mail geantwortet: Sie hat kein Block-Design, sondern modelt die HRF über den jeweils gesamten Satz von ca. 2.8 Sekunden.
-c) To our knowledge only one study by {aziz2008modulation} correlated hemodynamic activity of the PPA with spoken sentences.
+c) To our knowledge only one study by \citep{aziz2008modulation} correlated hemodynamic activity of the PPA with spoken sentences.
 Sentences described generic or famous places (e.g.
-“The Taj Mahal faces a long thin reflecting pool”) or faces  (e.g.
-“Marylin Monroe has a large square jaw").
+``The Taj Mahal faces a long thin reflecting pool'') or faces  (e.g.
+``Marylin Monroe has a large square jaw'').
 Participants were instructed to press a button whenever the sentence described an inaccurate or improbable fact.
@@
 In summary, studies suggest that the PPA does not exclusively respond to visual(ly) spatial information.
-This is consistent with a competing hypotheses stating the PPA does not process the spatial layout of a scene specifically but contextual associations in general {aminoff2006parahippocampal} for a review).
+This is consistent with a competing hypotheses stating the PPA does not process the spatial layout of a scene specifically but contextual associations in general \citep{aminoff2006parahippocampal} for a review).
 Independent(ly) from competing theories (s.
-{aminoff2013role} for a review), it is still unacknowledged/ uncertain/ indeterminate if auditory stimuli lead to inhibitory or excitatory responses, or no change at all in the PPA.
+\citep{aminoff2013role} for a review), it is still unacknowledged/ uncertain/ indeterminate if auditory stimuli lead to inhibitory or excitatory responses, or no change at all in the PPA.
 
@@
 Thus, they cannot / could answer the question how the PPA might behave under life-like conditions.
-Natural stimuli like movies [hasson2008neurocinematics; sonkusare2019naturalistic] or narratives [honey2012not-lost; lerner2011topographic; silbert2014coupled] offer an easy to implement, (continuous,) complex, immersive stimulus that better resembles our experience of a continuous dynamic environment.
+Natural stimuli like movies \citep{hasson2008neurocinematics, sonkusare2019naturalistic} or narratives \citep{honey2012notlost, lerner2011topographic, silbert2014coupled} offer an easy to implement, (continuous,) complex, immersive stimulus that better resembles our experience of a continuous dynamic environment.
 % hier wird GLM nicht explizit erwähnt; denke, muss nicht so spezifisch sein
-In an early study [bartels2004mapping] manually annotated time points that depict faces and human bodies in a 22 minute clip of the movie \textit{Tomorrow Never Dies}.
-These time points correlated with increased hemodynamic activity in the "fusiform face area" {kanwisher1997ffa} and "extrastriate body area"{downing2001body-area} respectively.
+In an early study \citep{bartels2004mapping} manually annotated time points that depict faces and human bodies in a 22 minute clip of the movie \textit{Tomorrow Never Dies}.
+These time points correlated with increased hemodynamic activity in the ``fusiform face area'' \citep{kanwisher1997ffa} and ``extrastriate body area'' \citep{downing2001bodyarea} respectively.
 % hier wird ISC als solches nicht erwähnt
-{hasson2004intersubject} took an inverse approach using a 30 minute clip of the movie \textit{The Good, the Bad, the Ugly}.
+\citep{hasson2004intersubject} took an inverse approach using a 30 minute clip of the movie \textit{The Good, the Bad, the Ugly}.
 fMRI brain volumes showing the highest hemodynamic activity in the PPA [across (five) participants] were matched to the (temporally) correlating movie frames.
@@
 In this study, we analyze data of three publicly available datasets from the same set of 15 participants as part of the studyforrest data set (\href{http://www.studyforrest.org}{studyforrest.org}).
-We exploratorily investigate how the parrahippocampal gyrus responds to "spatially relevant" events embedded in a 2h audio-visual movie [hanke2016simultaneous] and it's audio-description of same length [hanke2014audiomovie].
-Results are compared to PPA localizations that were obtained from a dedicated visual localizer experiment [sengupta2016extension].
+We exploratorily investigate how the parrahippocampal gyrus responds to ``spatially relevant'' events embedded in a 2h audio-visual movie \citep{hanke2016simultaneous} and it's audio-description of same length \citep{hanke2014audiomovie}.
+Results are compared to PPA localizations that were obtained from a dedicated visual localizer experiment \citep{sengupta2016extension}.
 Both natural stimuli were originally designed to entertain an audience and to capture attention free from any perceptual or behavioral task.
 We annotated events of the otherwise unknown temporal structure of both stimuli to be able to fit a theory-driven model.
-In/for the movie, we annotated different kinds of cinematographic cuts [haeusler2016annotation] as presumably "spatially relevant" events.
+In/for the movie, we annotated different kinds of cinematographic cuts \citep{haeusler2016annotation} as presumably ``spatially relevant'' events.
 Our rationale was that cuts re-orient the viewer in the depicted environment independent from the exact visual content in the movie frame following the cut.
-In/for the audio-description, we annotated clues about the missing visual content given by the narrator {haeusler2019annotation}.
+In/for the audio-description, we annotated clues about the missing visual content given by the narrator \citep{haeusler2020spechanno}.
 We correlated regressors drawn from the annotations in order to detect possible/possibly confounded regressors that might prevent functional isolation of the PPA.
 In conformity to the analyses performed in the studies reviewed above, we submitted our regressors to a standard multi-level, voxel-wise general linear model (GLM).
-For practical reasons (+++es war a) viel einfacher als visual content zu annotieren und ist b) viel interessanter weil non-visual+++) and encouraged by {aziz2008modulation} and {aminoff2013role}, we focus on the audio-description as a possible life-like substitute to individually localize a "visual area" in visually impaired persons.
+For practical reasons (+++es war a) viel einfacher als visual content zu annotieren und ist b) viel interessanter weil non-visual+++) and encouraged by \citep{aziz2008modulation} and \citep{aminoff2013role}, we focus on the audio-description as a possible life-like substitute to individually localize a ``visual area'' in visually impaired persons.
 
@@
 % Specific data outputs should be explicitly referenced via data citation (see Data Records and Data Citations, below).
-An exhaustive description of the participants, stimulus creation, procedure, stimulation setup, and fMRI acquisition can be found in {hanke2014audiomovie} and {hanke2016simultaneous; sengupta2016extension}
+An exhaustive description of the participants, stimulus creation, procedure, stimulation setup, and fMRI acquisition can be found in \citep{hanke2014audiomovie} and \citep{hanke2016simultaneous, sengupta2016extension}
 
@@
 % ggf. mit "Stimuli" zusammenfassen, weil sich das, dadurch dass die gleichen 15 in beiden Experimenten mitgemacht haben schwer prägnant trennen lässt.
-In the first \todo{better to give them labels in the initial paragraph above, we will be referring to them quite a bit} study, fifteen participants (all right-handed, age 21–38 years, mean age 26.6 years, 12 male) listened to the German audio-description (Koop, Michalski, Beckmann, Meinhardt \& Benecke, produced by Bayrischer Rundfunk, 2009) of the movie "Forrest Gump" (R.
+In the first \todo{better to give them labels in the initial paragraph above, we will be referring to them quite a bit} study, fifteen participants (all right-handed, age 21–38 years, mean age 26.6 years, 12 male) listened to the German audio-description (Koop, Michalski, Beckmann, Meinhardt \& Benecke, produced by Bayrischer Rundfunk, 2009) of the movie ``Forrest Gump'' (R.
 Zemeckis, Paramount Pictures, 1994) as an additional audio track for visually impaired listeners on Swiss public television.
@@
 % grey bars habe ich nicht erwähnt, obwohl sie - weil bei Lisas Stimuli überall anders - so viel Spaß gemacht haben
-The movie's audio track and the audio-description are largely identical.
-The plot is carried by an off-screen voice of the main character Forrest Gump.
+The movie's audio track and the audio-description are largely identical. The plot is carried by an off-screen voice of the main character Forrest Gump.
 The audio-description's male narrator additionally verbalizes essential aspects of the visual scenery when there is no dialog, off-screen voice or relevant sound in the audio track.
-The audio-description was temporally aligned to the audio track of the German DVD release (Paramount Home Entertainment, Germany, 2002; PAL video, DE103519SV).
-A few scenes less relevant to the major plot were removed to create the "research cut" lasting $\approx$2h.
-Both stimuli were further processed (filtering, volume adjustments) to improve understandability / audibleness / audibility during MRI scanning.
+The audio-description was temporally aligned to the audio track of the German DVD release (Paramount Home Entertainment, Germany, 2002; PAL video, DE103519SV).A few scenes less relevant to the major plot were removed to create the ``research cut'' lasting $\approx$2h.
+Both stimuli were further processed (filtering, volume adjustments) to improve understandability / audibility during MRI scanning.
 Finally, each stimulus was split into eight segments of approximately 15 minutes.
-Except for the first movie segment, each segment started with a snippet of at least six seconds immediately preceding the movie scene boundary used to split the segments.
-\todo{cite fig 3a from hanke2014}
+Except for the first movie segment, each segment started with a snippet of at least six seconds immediately preceding the movie scene boundary used to split the segments (s.
+Figure 3a in \citep{hanke2014audiomovie}
 
@@
 \todo{possibly cut the rest of the section} At the start recording session(s), participants listened to music from the movie’s closing credits segment to individually determine optimal stimulus volume.
-Participants were instructed to "maximize the volume of the stimulus without it becoming unpleasantly loud or causing acoustic distortions by overdriving the loudspeaker hardware".
-% unterscheidet sich ggf.
-zwischen Hörspiel / Film oder kann ganz raus?
+Participants were instructed to ``maximize the volume of the stimulus without it becoming unpleasantly loud or causing acoustic distortions by overdriving the loudspeaker hardware''.
+% unterscheidet sich ggf. zwischen Hörspiel / Film oder kann ganz raus?
 Between sessions, participants left the scanner for a break with a flexible duration. Structural images were obtained during the first study on a day different from the fMRI session.
@@
 \subsection{Stimulation setup}
-Stimulation was implemented with PsychoPy v1.79 (with an early version of the MovieStim2 component later to be publicly released with \href{http://www.psychopy.org}{PsychoPy v1.81}; {peirce2007psychopy}) running on a computer with the \href{http://neuro.debian.net}{(Neuro)Debian} operating system [halchenko2012open].
+Stimulation was implemented with PsychoPy v1.79 (with an early version of the MovieStim2 component later to be publicly released with \href{http://www.psychopy.org}{PsychoPy v1.81}; \citep{peirce2007psychopy}) running on a computer with the \href{http://neuro.debian.net}{(Neuro)Debian} operating system \citep{halchenko2012open}.
 % Einige Dinge können m.M.n. raus; insb. das in den []-Klammern
@@
 During the functional scans, the projector presented a medium gray screen with the primary purpose to illuminate a participant’s visual field in order to prevent premature fatigue.
-[The screen contained a solid black "fixation" dot that faded in and out at the beginning and end of a movie segment.]
+[The screen contained a solid black ``fixation'' dot that faded in and out at the beginning and end of a movie segment.]
 In the audio-visual study, visual instructions and stimuli were presented on a rear-projection screen using an LCD projector (JVC DLA RS66E, JVC Ltd., light transmission reduced to 13.7\% with a gray filter) connected to the stimulus computer [via a DVI extender system (Gefen EXT-DVI-142DLN with EXT-DVI-FM1000).
@@
 % Hier hat es Unterschiede zwischen Hörspiel & Film geben? habe es wie folgt zusammengefasst; im Zweifel ist es eh noch zu ausführlich
-Auditory stimulation was delivered through an MR confon mkII+ driving custom-built in-ear headphones (HP-M01, MR confon GmbH, Magdeburg, Germany; {baumgart1998electrodynamic}) that reduced the scanner noise by at least 20–30 dB.
+Auditory stimulation was delivered through an MR confon mkII+ driving custom-built in-ear headphones (HP-M01, MR confon GmbH, Magdeburg, Germany; \citep{baumgart1998electrodynamic}) that reduced the scanner noise by at least 20–30 dB.
 Headphones were  fed from an Aureon 7.1 USB (Terratec) sound card through an optical connection.
@@
 In the audio-visual study, a whole-body 3 Tesla Philips Achieva dStream MRI scanner equipped with a 32 channel head coil acquired T2*-weighted echo-planar images (gradient-echo, 2\,s repetition time (TR), 30\,ms echo time, 90 DEGREE flip angle, 1943\,Hz/Px bandwidth, parallel acquisition with sensitivity encoding (SENSE) reduction factor 2).
-35 axial slices (thickness 3.0\,mm, 10 \% inter-slice gap) with 80*80 voxels (3.0*3.0 mm of in-plane resolution), 240\,mm mm field-of-view (FoV) and an anterior-to-posterior phase encoding direction were recorded in ascending order.
+35 axial slices (thickness 3.0\,mm, 10\% inter-slice gap) with 80*80 voxels (3.0*3.0 mm of in-plane resolution), 240\,mm mm field-of-view (FoV) and an anterior-to-posterior phase encoding direction were recorded in ascending order.
 Philips’ “SmartExam” was used to automatically position slices in AC-PC orientation such that the topmost slice was located at the superior edge of the brain.
@@
 \subsection{Stimulus Annotation}
-% wurde unter "Regressoren" zu Beginn der 1st-lvl-Analyse verschoben
+% einleitendes Blabla zu haeusler2020speechanno
+% deutlich machen, warum was wie annotiert wurde
+% ggf. angeben, dass die effektiv identisch waren
+% Florian hat zwei Regeln falsch verstanden, sonst war übereinstimmung >90%
+% Kategorie ``++'' enthält ausnahmesweise auch adverbiale Best. der Zeit.
+A further annotation of the audio-description's narrator was done manually: Two
+persons performed a categorization of nouns embedded in sentences spoken by the
+narrator to describe the movie's missing visual content.
+Categories focus on the cinematographic scene's environment, inherent objects, persons, and a person's appearance.
+A categorizing of nouns that serve as auditory cues about the movie's visual content.
+Comprised categories focus on the cinematographic scene's environment (geo, geo-room; setting\_new, setting\_old), inherent persons (female, female name; male, male name, person), their appearance (face, head; body, bodypart), and objects (object, furniture).
+A preliminary annotation according to the rules [entweder im laufenden Text oder in Tabelle], einer neuen Tabelle oder im laufenden Text was done by one person and corrected in several runs by the author.
+
+% Tabelle der Descriptive Nouns;
+% aus Speech-Anno Paper 'descriptive-statistics-anno.py' übernehmen & anpassen.
+% von allen \newcommands wurde das \ for dem Variablennamen entfernt
+% -> sind insofern alles Platzhalter bis das Skript fertig ist, das die Inputdatei schreibt.
+\begin{table*}[t]
+    \caption{Narrator's descriptive nouns. All categories sorted alphapetically. Examples are given in English.}
+\label{tab:descr-nouns}
+\begin{tabular}{llllllllllll}
+\toprule
+\textbf{category} & \textbf{rule} & \textbf{examples} & \textbf{all} & \textbf{1} & \textbf{2} & \textbf{3} & \textbf{4} & \textbf{5} & \textbf{6} & \textbf{7} & \textbf{8} \\
+\midrule
+body & trunk of the body; overlaid clothes & back, hip, shoulder; jacket, dress shirt & aDescrBodyAll & aDescrBodyI & aDescrBodyII & aDescrBodyIII & aDescrBodyIV & aDescrBodyV & aDescrBodyVI & aDescrBodyVII & aDescrBodyVIII \tabularnewline
+bodypart & limbs and trousers & arm, finger, leg, toe & aDescrBodypartAll & aDescrBodypartI & aDescrBodypartII & aDescrBodypartIII & aDescrBodypartIV & aDescrBodypartV & aDescrBodypartVI & aDescrBodypartVII & aDescrBodypartVIII\tabularnewline
+face & face or parts of it & face, ear, nose, mouth & aDescrFaceAll & aDescrFaceI & aDescrFaceII & aDescrFaceIII & aDescrFaceIV & aDescrFaceV & aDescrFaceVI & aDescrFaceVII & aDescrFaceVIII \tabularnewline
+female & female person & nurse, mother, woman & aDescrFemaleAll & aDescrFemaleI & aDescrFemaleII & aDescrFemaleIII & aDescrFemaleIV & aDescrFemaleV & aDescrFemaleVI & aDescrFemaleVII & aDescrFemaleVIII \tabularnewline
+females & female persons & women & aDescrFemalesAll & aDescrFemalesI & aDescrFemalesII & aDescrFemalesIII & aDescrFemalesIV & aDescrFemalesV & aDescrFemalesVI & aDescrFemalesVII & aDescrFemalesVIII \tabularnewline
+fname & female name & Jenny & aDescrFnameAll & aDescrFnameI & aDescrFnameII & aDescrFnameIII & aDescrFnameIV & aDescrFnameV & aDescrFnameVI & aDescrFnameVII & aDescrFnameVIII \tabularnewline
+furniture & movable objects insides/outsides & bench, bed, table, chair & aDescrFurnitureAll & aDescrFurnitureI & aDescrFurnitureII & aDescrFurnitureIII & aDescrFurnitureIV & aDescrFurnitureV & aDescrFurnitureVI & aDescrFurnitureVII & aDescrFurnitureVIII \tabularnewline
+geo & immobile landmarks & building, tree, street, alley, meadow, cornfield, river & aDescrGeoAll & aDescrGeoI & aDescrGeoII & aDescrGeoIII & aDescrGeoIV & aDescrGeoV & aDescrGeoVI & aDescrGeoVII & aDescrGeoVIII \tabularnewline
+geo-room & rooms / locales; elements defining a locale's spatial layout & living room; wall, door, window, floor, turf & aDescrGeoroomAll & aDescrGeoroomI & aDescrGeoroomII & aDescrGeoroomIII & aDescrGeoroomIV & aDescrGeoroomV & aDescrGeoroomVI & aDescrGeoroomVII & aDescrGeoroomVIII \tabularnewline
+head & non-face parts of the head; worn headgear & head, hair, ear, neck, helmet & aDescrHeadAll & aDescrHeadI & aDescrHeadII & aDescrHeadIII & aDescrHeadIV & aDescrHeadV & aDescrHeadVI & aDescrHeadVII & aDescrHeadVIII \tabularnewline
+male & male person & man, father, soldier & aDescrMaleAll & aDescrMaleI & aDescrMaleII & aDescrMaleIII & aDescrMaleIV & aDescrMaleV & aDescrMaleVI & aDescrMaleVII & aDescrMaleVIII \tabularnewline
+males & male persons & boys, opponents & aDescrMalesAll & aDescrMalesI & aDescrMalesII & aDescrMalesIII & aDescrMalesIV & aDescrMalesV & aDescrMalesVI & aDescrMalesVII & aDescrMalesVIII \tabularnewline
+mname & male name & Bubba, Kennedy & aDescrMnameAll & aDescrMnameI & aDescrMnameII & aDescrMnameIII & aDescrMnameIV & aDescrMnameV & aDescrMnameVI & aDescrMnameVII & aDescrMnameVIII \tabularnewline
+object & countable entity with firm boundarie & telephone, car & aDescrObjectAll & aDescrObjectI & aDescrObjectII & aDescrObjectIII & aDescrObjectIV & aDescrObjectV & aDescrObjectVI & aDescrObjectVII & aDescrObjectVIII \tabularnewline
+objects & countable entities with firm boundaries &  wheels, photos & aDescrObjectsAll & aDescrObjectsI & aDescrObjectsII & aDescrObjectsIII & aDescrObjectsIV & aDescrObjectsV & aDescrObjectsVI & aDescrObjectsVII & aDescrObjectsVIII \tabularnewline
+persons & concrete persons of unknown sex / gender & hippies, patients & aDescrPersonsAll & aDescrPersonsI & aDescrPersonsII & aDescrPersonsIII & aDescrPersonsIV & aDescrPersonsV & aDescrPersonsVI & aDescrPersonsVII & aDescrPersonsVIII \tabularnewline
+setting\_new & setting mentioned for the first time &  on a ``bridge'', on an ``alley'', on ``campus'' & aDescrSettingnewAll & aDescrSettingnewI & aDescrSettingnewII & aDescrSettingnewIII & aDescrSettingnewIV & aDescrSettingnewV & aDescrSettingnewVI & aDescrSettingnewVII & aDescrSettingnewVIII \tabularnewline
+setting\_rec & recurring setting & at the ``bus stop'' & aDescrSettingrecAll & aDescrSettingrec & aDescrSettingrecII & aDescrSettingrecIII & aDescrSettingrecIV & aDescrSettingrecV & aDescrSettingrecVI & aDescrSettingrecVII & aDescrSettingrecVIII \tabularnewline
+++ & nouns, adverbial adjectives and adverbs & in the ``evening'', it's ``daytime'', ``later'' &  aDescrAll & aDescrI & aDescrII & aDescrIII & aDescrIV & aDescrV & aDescrVI & aDescrVII & aDescrVIII \tabularnewline
+\bottomrule
+\end{tabular}
+\end{table*}
 
@@
 \href{''https://github.com/psychoinformatics-de/studyforrest-data-aligned''}{GitHub}.
-Data are already aligned to a subject-specific \href{''https://github.com/psychoinformatics-de/studyforrest-data-templatetransforms''}{3 Tesla BOLD template} \todo{cite sengupta2016 where this was first done and described, ie same image/data was used here} by a rigid body transformation in MCFLIRT ([jenkinson2002registration]) to correct for motion during scanning.
-All further analysis steps in the current study were carried out using tools of FSL v5.0.9 (\href{''https://www.fmrib.ox.ac.uk/fsl''}{FMRIB's Software Library};[smith2004fsl]; on a computer cluster running the \href{https://www.debian.org}{Debian} GNU/Linux operating system.
-Software packages were obtained from repositories of \href{http://neuro.debian.net}{NeuroDebian}([halchenko2012open]).
+Data are already aligned to a subject-specific \href{''https://github.com/psychoinformatics-de/studyforrest-data-templatetransforms''}{3 Tesla BOLD template} by a rigid body transformation in MCFLIRT \citep{jenkinson2002registration} to correct for motion during scanning.
+\citep{sengupta2016extension}.
+\todo{cite sengupta2016 where this was first done and described, ie same image/data was used here}
+All further analysis steps in the current study were carried out using tools of FSL v5.0.9 (\href{''https://www.fmrib.ox.ac.uk/fsl''}{FMRIB's Software Library};\citep{smith2004fsl}; on a computer cluster running the \href{https://www.debian.org}{Debian} GNU/Linux operating system.
+Software packages were obtained from repositories of \href{http://neuro.debian.net}{NeuroDebian} \citep{halchenko2012open}.
 
 \subsection{Preprocessing}
-Preprocessing (and statistical analysis) was carried out using FEAT v6.00 (FMRI Expert Analysis Tool;[woolrich2001autocorr]) as part of FSL.
+Preprocessing (and statistical analysis) was carried out using FEAT v6.00 (FMRI Expert Analysis Tool;\citep{woolrich2001autocorr}) as part of FSL.
 High-pass temporal filtering was applied to every segment using a Gaussian-weighted least-squares straight line with a cutoff period of 150\,s (sigma=75.0\,s) to remove low-frequency confounds.
-Slice-time correction was performed using Fourier-space time series phase-shifting.
-\todo{hmm, why did we do that (slicetiming)?} The brain was extracted from surrounding tissues using BET [smith2002BET].
+The brain was extracted from surrounding tissues using BET \citep{smith2002bet}.
 Data were spatially smoothed applying a Gaussian kernel with full width at half maximum (FWHM) of 4.0 mm.
@@
 To build the regressors for the GLMs, we took advantage of two publicly available annotations of the stimuli's temporal structure.
-One annotation of speech occurring in the audio-description and movie {haeusler2019annotation}, and a second annotation of movie cuts and depicted locations \href{https://f1000research.com/articles/5-2273}{haeusler2016annotation}.
+One annotation of speech occurring in the audio-description and movie [haeusler2020speechanno], and a second annotation of movie cuts and depicted locations \href{https://f1000research.com/articles/5-2273}{haeusler2016annotation}.
 As a first step, the annotations were split via (\href{"https://github.com/chrhaeusler/studyforrest-data-annotations/blob/master/code/researchcut2segments.py"}{python script} into eight parts corresponding to the eight segments used in the scanner.
@@
 For the auditory stimulus, we used nouns embedded in sentences spoken by the narrator.
-The nouns are categorized by the clue they provide about a cinematographic scene's environment \todo{maybe skip the names and just cite the table} (geo, geo-room; setting\_new, setting\_old), its inherent persons (female, female name; male, male name, person), a person's appearance (face, head; body, bodypart), and a scene's inherent objects (object, furniture).
+The nouns are categorized by the clue they provide about a cinematographic scene's environment \todo{maybe skip the names and just cite the table} (geo, geo-room; setting\_new, setting\_rec), its inherent persons (female, female name; male, male name, person), a person's appearance (face, head; body, bodypart), and a scene's inherent objects (object, furniture).
+% nope, kommt jetzt hier
 Details on procedure to annotate the stimuli on a single-world level and details on the rules to manually categorize the nouns can be found in the \href{"https://www.overleaf.com/project/5d4ab1b759001b5db6ea2bc3"}{corresponding paper}.
 We created 11 regressors from the XY (selected?) original categories by joining / merging some categories (female, females, fname; male, males, mname; face, head) into one regressor (sex\_f; sex\_m; fahead).
-The regressors were modeled as boxcar functions at the end of each noun with a duration of 200 ms (jetzt ist es über Wortlänge).
+% over length of each noun
+The regressors were modeled as boxcar functions at the end of each noun with a duration of 200 ms.
 If a segment did not contain a single event for a specific regressor, a null regressor was chosen for that segment.
-Five regressors related to the cinematographic cuts (s.
-below) were added to built contrasts of cross-modal negative control.
+Five regressors related to the cinematographic cuts (s. below) were added to built contrasts of cross-modal negative control.
 Two regressors reflecting auditory (low-level) features (left-right loudness volume / amplitude???
@@
 For both stimuli, regressors were convolved with a double gamma canonical hemodynamic response function (HRF).
-Their temporal derivatives were added to compensate for small timing differences [friston1998event].
-Six motion parameters were used as additional nuisance regressors.
-Finally, designs were filtered with the same high-pass filter (cutoff period of 150\,s) as the BOLD time series.
+Their temporal derivatives were added to compensate for small timing differences \citep{friston1998event}.
+Six motion parameters were used as additional nuisance regressors. Finally, designs were filtered with the same high-pass filter (cutoff period of 150\,s) as the BOLD time series.
 
@@
 The neurocientific rationale was that activity in the PPA is greater when participants view novel versus repeated scenes resp.
-view-points {epstein1999parahippocampal}.
+view-points \citep{epstein1999parahippocampal}.
 Hence, we contrasted cuts to a setting occurring for the first time (vse\_new) and cuts within a locale depicted for the first time (vpe\_new) with shots to a recurring setting (vse\_old) and cuts within a recurring locale (vpe\_old).
@@
 The GLM analysis that fitted each voxel's time course separately for each subject was performed in functional space preserving the orientation of the EPI images.
-Correction for local autocorrelation in the time series (prewhitening) was applied using FILM (FMRIB's Improved Linear Model) to improve estimation efficiency [woolrich2001autocorr].
+Correction for local autocorrelation in the time series (prewhitening) was applied using FILM (FMRIB's Improved Linear Model) to improve estimation efficiency \citep{woolrich2001autocorr}.
 For subsequent subject-specific second level results, subject-specific BOLD T2* time series were anatomically aligned via linear transformation to a subject-specific, study-specific T2* template (s.
@@
 \subsubsection{second level}
-The second-level analyses which averaged contrast estimates over the eight stimulus segments were carried out using a fixed effects model, by forcing the random effects variance to zero in FLAME (FMRIB's Local Analysis of Mixed Effects) [beckmann2003general, woolrich2004multilevel].
-Z (Gaussianised T/F) statistic images were thresholded using clusters determined by Z>2.3 and a (corrected) cluster significance threshold of p=.05 [worsley2001statistical].
+The second-level analyses which averaged contrast estimates over the eight stimulus segments were carried out using a fixed effects model, by forcing the random effects variance to zero in FLAME (FMRIB's Local Analysis of Mixed Effects) \citep{beckmann2003general, woolrich2004multilevel}.
+Z (Gaussianised T/F) statistic images were thresholded using clusters determined by Z>2.3 and a (corrected) cluster significance threshold of p=.05 \citep{worsley2001statistical}.
 \subsubsection{third level}
-Third level analyses which averaged contrast estimates over subjects were carried out using FLAME stage 1 with automatic outlier detection [beckmann2003general, woolrich2004multilevel, woolrich2008robust].
+Third level analyses which averaged contrast estimates over subjects were carried out using FLAME stage 1 with automatic outlier detection \citep{beckmann2003general, woolrich2004multilevel, woolrich2008robust}.
 Z (Gaussianised T/F) statistic images were thresholded using clusters determined by Z>3.4 and a (corrected) cluster significance threshold of p=.05 [Worsley, 2001].
@@
 generate, test, or process the current dataset. }
-\begin{itemize}
-\item wo kommt der Abschnitt hin?
-\end{itemize}
 
 \section*{Acknowledgements}
-
-\emph{Text acknowledging non-author contributors. Acknowledgements should
-be brief, and should not include thanks to anonymous referees and
-editors, or effusive comments. Grant or contribution numbers may be
-acknowledged. Author contributions Please describe briefly the contributions
-of each author to this work on a separate line.}
-AK did this and that.
-BG did this and that and the other.
-\begin{itemize}
-\item wo kommt der Abschnitt hin?
-\end{itemize}
+% Text acknowledging non-author contributors.
+Acknowledgements should be brief, and should not include thanks to anonymous referees and editors, or effusive comments.
+Grant or contribution numbers may be acknowledged.
+% Author contributions Please describe briefly the contributions of each author to this work on a separate line.
+\emph{COH did this and that.
+    MH did this and that.
+    We are grateful to \href{www.florianschurz.de}{Florian Schurz} who initiated doing the annotation of the descriptive nouns, and performed the preliminary annotation of nouns.}
 
 \section*{Competing financial interests}
-
 \emph{A competing financial interests statement is required for all accepted
@@
 ``The author(s) declare no competing financial interests''.}
-\begin{itemize}
-\item wo kommt der Abschnitt hin?
-\end{itemize}
 
 \section*{Figures Legends}
-
 \emph{Figure should be referred to using a consistent numbering scheme through
@@
 than 350 words, and may contain literature references.}
-\begin{itemize}
-\item wo kommt der Abschnitt hin?
-\end{itemize}
 
@@
 of three).}
-\begin{itemize}
-\item wo kommt der Abschnitt hin?
-\end{itemize}
 
-\begin{thebibliography}{1}
-\expandafter\ifx\csname url\endcsname\relax
-  \def\url#1{\texttt{#1}}\fi
-\expandafter\ifx\csname urlprefix\endcsname\relax\def\urlprefix{URL }\fi
-\providecommand{\bibinfo}[2]{#2}
-\providecommand{\eprint}[2][]{\url{#2}}
+{\small\bibliographystyle{unsrtnat}
+\bibliography{references}}
 
-\bibitem{cite1}
-\bibinfo{author}{Califano, A.}, \bibinfo{author}{Butte, A.~J.},
-  \bibinfo{author}{Friend, S.}, \bibinfo{author}{Ideker, T.} \&
-  \bibinfo{author}{Schadt, E.}
-\newblock \bibinfo{title}{{Leveraging models of cell regulation and GWAS data
-  in integrative network-based association studies}}.
-\newblock \emph{\bibinfo{journal}{Nature Genetics}}
-  \textbf{\bibinfo{volume}{44}}, \bibinfo{pages}{841--847}
-  (\bibinfo{year}{2012}).
-
-\bibitem{cite2}
-\bibinfo{author}{Wang, R.} \emph{et~al.}
-\newblock \bibinfo{title}{{PRIDE Inspector: a tool to visualize and validate MS
-  proteomics data.}}
-\newblock \emph{\bibinfo{journal}{Nature Biotechnology}}
-  \textbf{\bibinfo{volume}{30}}, \bibinfo{pages}{135--137}
-  (\bibinfo{year}{2012}).
-
-\end{thebibliography}
+%\begin{thebibliography}{1}
+%\expandafter\ifx\csname url\endcsname\relax
+%  \def\url#1{\texttt{#1}}\fi
+%\expandafter\ifx\csname urlprefix\endcsname\relax\def\urlprefix{URL }\fi
+%\providecommand{\bibinfo}[2]{#2}
+%\providecommand{\eprint}[2][]{\url{#2}}
+%
+%\bibitem{cite1}
+%\bibinfo{author}{Califano, A.}, \bibinfo{author}{Butte, A.~J.},
+%  \bibinfo{author}{Friend, S.}, \bibinfo{author}{Ideker, T.} \&
+%  \bibinfo{author}{Schadt, E.}
+%\newblock \bibinfo{title}{{Leveraging models of cell regulation and GWAS data
+%  in integrative network-based association studies}}.
+%\newblock \emph{\bibinfo{journal}{Nature Genetics}}
+%  \textbf{\bibinfo{volume}{44}}, \bibinfo{pages}{841--847}
+%  (\bibinfo{year}{2012}).
+%
+%\bibitem{cite2}
+%\bibinfo{author}{Wang, R.} \emph{et~al.}
+%\newblock \bibinfo{title}{{PRIDE Inspector: a tool to visualize and validate MS
+%  proteomics data.}}
+%\newblock \emph{\bibinfo{journal}{Nature Biotechnology}}
+%  \textbf{\bibinfo{volume}{30}}, \bibinfo{pages}{135--137}
+%  (\bibinfo{year}{2012}).
+%\end{thebibliography}
 

### 2020-04-15 paper/main.tex
revise introduction

@@
 
-% Vorgabe < 110 chars incl. spaces
+% Titel-Vorgabe < 110 chars incl. spaces
 %  jetzt 109 Chars
 \title{Hemodynamic responses of the Parahippocampal Place Area to spatial cues in a movie and it's audio-description}
-% alt:BOLD responses of the Parahippocampal Place Area correlate with spatial cues in a movie and it's audio-only variant
 
@@
 \end{abstract}
-% Intro + Discussion = main text ~ 3,000 words.
+% Vorgabe: Intro + Discussion = main text ~ 3,000 words.
 % include figure providing schematic overview of the study and assay(s) design
@@
 % our system cannot accept BibTeX bibliography files; authors who wish to use BibTeX to prepare their references should therefore copy the reference list from the .bbl file that BibTeX generates and paste it into the main manuscript .tex file (and delete the associated  \textbackslash{}bibliography and \textbackslash{}bibliographystyle commands).
-
 % yeah, whatever. Arbeite erstmal mit der references.bib
@@
 
-% Retrosplenial-Cortex kommt in der jetzigen Einleitung nicht vor, jedoch in Ergebnissen von Movie & Audio-Description
-% Muss spätestens in der Discussion diskutiert werden
-% bin auch am überlegen, ob ich in den Ergebnissen zu den sagitallen slices durch die PPAs noch sagitale Slices durch die RSCs dazunehme??
+% Retrosplenial Cortex kommt in Einleitung nicht vor
+% wird aufgrund der Ergebnisse AV und AO in Discussion diskutiert werden
+% -> in den geplanten Abbildungen / Slices aber nicht zu sehen
 A classic example of a functional, higher-level visual area is the ``parahippocampal place area'' (PPA) \citep{epstein1998ppa, epstein1999parahippocampal}.
@@
 According to the spatial layout hypothesis, the PPA is involved in processing the surface geometry of a visual stimulus and possibly in identifying scenes based on their spatial layout \citep{epstein2010reliable}.
-Results generalize at a group average level to a) mental imagination of landscapes \citep{ocraven2000mental} and b) haptic exploration of scenes \citep{wolbers2011modality}, \todo{this needs some more glue.
-the following is not just about spoken stimuli} whereas results of a study using spoken, place-related sentences were unclear \todo{should be more specific.
-unclear could mean 'not well described'} \citep{aziz2008modulation}:
-a) In a study conducted by \citep{ocraven2000mental} participants viewed alternating blocks of pictures showing famous faces and familiar places during an initial experimental paradigm.
+% Überblick
+At a group avergae level, results generalize to mental imagination of landscapes \citep{ocraven2000mental} and haptic exploration of scenes constructed from LEGO blocks \citep{wolbers2011modality}.
+% Egal, was ich folgend in der Überblick & später im Detail bzgl. Aziz (2008) schreibe, es wird wahrscheinlich nicht korrekt sein.
+% So wie ich es verstanden habe, hat Aziz den Unterschied zwischen PPA und FFA abgeguckt, aber diesen Unterschied im Kontrast zu object-related Sentences
+% Fig 3 dort; im Grunde kommt da aber überall nur uneinheitliche Grütze raus
+One study that used spoken, place-related sentences showed significantly decreased activation in the left and no modulation in the right-hemispheric PPA \citep{aziz2008modulation}.
+
+% Im Einzelnen
+In the study conducted by \citep{ocraven2000mental} participants viewed alternating blocks of pictures showing famous faces and familiar places during an initial experimental paradigm.
 In a subsequent paradigm, participants were instructed to ``form a vivid mental image'' of the previously viewed pictures.
 The PPA showed increased activation during imagination of places compared to faces but the imagination tasks showed a smaller activation level compared to the perceptual task.
-% Wolbers im Folgenden macht noch ne Connectivitäts-Analyse mit dem Occipital-Cortex; da ist dann keine Connectivity im Vergleich zum visuellen Paradigma; deshalb kann das laut ihm kein mental image sein: "the scene-related increase in coupling with the PPA was significantly stronger in multiple clusters in occipital cortex under visual than haptic stimulation (Figure 2B; Table S2)"
-b) In a block design study conducted by \citep{wolbers2011modality} the PPA of sighted participants showed increased activation during a delayed matching-to-sample task of haptically explored scenes constructed from Lego bricks compared to haptically explored abstract geometric objects.
+
+% Folgend: Wolbers.
+Er hat noch ne Connectivitäts-Analyse mit dem Occipital Cortex gemacht.
+Zum visuellen Paradigma ist da dann keine keine Connectivity im Vergleich zum visuellen Paradigma.
+Seine Interpretation: Es kann keine mental imagery sein:
+% "The scene-related increase in coupling with the PPA was significantly stronger in multiple clusters in occipital cortex under visual than haptic stimulation (Figure 2B; Table S2)"
+In the block design study conducted by \citep{wolbers2011modality} the PPA of sighted participants showed increased activation during a delayed matching-to-sample task of haptically explored scenes constructed from LEGO bricks compared to haptically explored abstract geometric objects.
+
 % Aziz hat auf eine zweite Mail geantwortet: Sie hat kein Block-Design, sondern modelt die HRF über den jeweils gesamten Satz von ca. 2.8 Sekunden.
-c) To our knowledge only one study by \citep{aziz2008modulation} correlated hemodynamic activity of the PPA with spoken sentences.
+% wie oben im Kommentar erwähnt: Ihre Method Section halte ich für etwas strange.Ich zeige dir ganz am Ende mal ihr Paper; hab die entsprechenden Stellen annotiert.
+Sonst wird hier im Detail Mist erzählt
+To our knowledge only one study by \citep{aziz2008modulation} correlated hemodynamic activity of the PPA with spoken sentences.
 Sentences described generic or famous places (e.g.
@@
 Participants were instructed to press a button whenever the sentence described an inaccurate or improbable fact.
-Surprisingly, activation in the left, but not right, PPA was significantly reduced \todo{reduced relative to what condition?} when participants listened to place-related sentences.
+Surprisingly, activation in the left, but not right, PPA was significantly reduced when participants listened to place-related sentences compared to listening to face-related sentences.
 Moreover, this effect was only observed in sentences involving famous places.
-% Frage: Review von Aminoff (2013) kommt nur kurz als "competing hypothesis"; muss man dann in der Discussion diskutieren, was ggf. gar nicht nötwendig ist, weil's darum im Grunde nicht geht
+
+% Review von Aminoff (2013) kommt nur kurz als "competing hypothesis"
+% muss man dann natürlich in der Discussion diskutieren,
+% was aber ggf. gar nicht notwendig ist, weil's darum gar bei uns gar nicht geht
 In summary, studies suggest that the PPA does not exclusively respond to visual(ly) spatial information.
@@
 
-% coolness-faktor von natural stimuli ist in der Einleitung beinahe komplett raus
-% data-driven analyses vs. theory-driven analyses ist komplett raus
-% kann man in discussion bringen, muss man aber nicht ist ja dann offensichtlich
-All studies reviewed above used a small set of carefully designed, simplified stimuli to strictly control experimental conditions.
+% Coolnessfaktor von naturalistic stimuli ist beinahe komplett raus
+% Data-driven vs. theory-driven analyses ist komplett raus
+% ggf. erwähnen, dass möglichst ähnliche und nicht fancy analysis gewählt wurde, um Replizierung der Ergebnisse, aber mit naturalistic stimuli zu gewährleisten.
+% -> vgl. Speech-Anno-Paper; in Discussion bringen
+All revied studies used a just a small set of carefully designed, simplified stimuli to strictly control experimental conditions.
 They further relied on / implemented explicit judgment-based tasks to keep participants alert and paying attention.
 Thus, they cannot / could answer the question how the PPA might behave under life-like conditions.
-Natural stimuli like movies \citep{hasson2008neurocinematics, sonkusare2019naturalistic} or narratives \citep{honey2012notlost, lerner2011topographic, silbert2014coupled} offer an easy to implement, (continuous,) complex, immersive stimulus that better resembles our experience of a continuous dynamic environment.
+Naturalistic stimuli like movies \citep{hasson2008neurocinematics, sonkusare2019naturalistic} or narratives \citep{honey2012not, lerner2011topographic, silbert2014coupled} offer an easy to implement, (continuous,) complex, immersive stimulus that better resembles our experience of a continuous dynamic environment.
 % hier wird GLM nicht explizit erwähnt; denke, muss nicht so spezifisch sein
-In an early study \citep{bartels2004mapping} manually annotated time points that depict faces and human bodies in a 22 minute clip of the movie \textit{Tomorrow Never Dies}.
-These time points correlated with increased hemodynamic activity in the ``fusiform face area'' \citep{kanwisher1997ffa} and ``extrastriate body area'' \citep{downing2001bodyarea} respectively.
-% hier wird ISC als solches nicht erwähnt
-\citep{hasson2004intersubject} took an inverse approach using a 30 minute clip of the movie \textit{The Good, the Bad, the Ugly}.
+Two early studies using naturalistic stimuli suggest functional specialization is preserved during free viewing of a movie when many areas respond simultaneously and interact [<- der Schlusssatz ist aus hasson und bartels plagiiert \citep{bartels2004mapping, hasson2004intersubject}
+
+% Bartels (2004) und Hasson (2004)
+\citep{bartels2004mapping} manually annotated time points that depict faces and human bodies in a 22 minute clip of the movie \textit{Tomorrow Never Dies}.
+Employing a general linear model to model hemodynamic activity, these time points correlated with increased activity in the ``fusiform face area'' \citep{kanwisher1997ffa} and ``extrastriate body area'' \citep{downing2001bodyarea} respectively.
+Employing a reverse intersubject correlation, \citep{hasson2004intersubject} took used a 30 minute clip of the movie \textit{The Good, the Bad, the Ugly}.
 fMRI brain volumes showing the highest hemodynamic activity in the PPA [across (five) participants] were matched to the (temporally) correlating movie frames.
 Results revealed that frames depicted indoor and outdoor scenes including buildings and open fields.
-Both studies suggest functional specialization is preserved during free viewing of a movie when many areas respond simultaneously and interact [<- der Schlusssatz ist aus hasson und bartels plagiiert].
-Nevertheless, none of the reviewed study could investigate how the PPA responds to spatial clues that are embedded in a complex, audio-only stimulus.
+Nevertheless, no study investigated how the PPA responds to spatial clues that are embedded in a complex, audio-only stimulus.
 
-% ich habe einiges deiner Kommentare versucht einzubauen
-% wenn dir etwas nicht explizit genug ist, fühl dich, frei mir auf die Finger zu hauen oder es vorzugsweise bei wenig Aufwand direkt umzuformulieren;
-% bzgl.
-open source habe ich nichts geschrieben, weil ich nur weiß, das der Code veröffentlicht werden soll.
+% Bzgl.
+Open Source der der Ergebnisse/Skripte: Dazu habe ich hier nichts geschrieben, weil ich nur weiß, das der Code veröffentlicht werden soll.
 Du hast die Vision diesbezüglich im Kopf und entsprechend auch kanonisch-prägnante Formulierungen und wo die am besten wie hinkommen
-% MIH:
-% 1. is such stimulus (more) suitable for distinguishing this cognitive process from others?
-% 2. given its suitability how do results (PPA-like response localization) differ from a standard visual/block-design localizer for:
-% 1) complex visual stimulation without a task, and
-% 2) complex auditory stimulation without an explicit imagery task
-% both aspects together can then be discussed in terms of the feasibility of (multi-dimensional) localizer development with naturalistic stimuli
+
 % Präteritum oder Präsens? Ist momentan gemischt; find's ok so.
-In this study, we analyze data of three publicly available datasets from the same set of 15 participants as part of the studyforrest data set (\href{http://www.studyforrest.org}{studyforrest.org}).
-We exploratorily investigate how the parrahippocampal gyrus responds to ``spatially relevant'' events embedded in a 2h audio-visual movie \citep{hanke2016simultaneous} and it's audio-description of same length \citep{hanke2014audiomovie}.
-Results are compared to PPA localizations that were obtained from a dedicated visual localizer experiment \citep{sengupta2016extension}.
+% N=14 is inner join of AV & AO
+\todo[inline]{
+    The next paragraphs contain a bunch of methods already; reduce this to talk about the general approach:
+    annotation of events,
+    investigation of model quality,
+    cross-analysis of datasets.
+    Possibly cite https://psyarxiv.com/sdbqv/
+    and declare that this study is a concrete realization of that promise
+}
+In this study, we analyze data of three publicly available datasets from the same set of 14 participants as part of the studyforrest data set (\href{http://www.studyforrest.org}{studyforrest.org}).
+We exploratorily investigate how the parahippocampal gyrus [or more general ``human brain''?] responds to ``spatially relevant'' events embedded in a 2h audio-visual movie \citep{hanke2016simultaneous} and its audio-description of the same length \citep{hanke2014audiomovie}.
+We compare these results to PPA localizations that were obtained from a dedicated visual localizer experiment \citep{sengupta2016extension}.
 Both natural stimuli were originally designed to entertain an audience and to capture attention free from any perceptual or behavioral task.
-We annotated events of the otherwise unknown temporal structure of both stimuli to be able to fit a theory-driven model.
+We annotated events in the otherwise unknown temporal structure of both stimuli.
 In/for the movie, we annotated different kinds of cinematographic cuts \citep{haeusler2016annotation} as presumably ``spatially relevant'' events.
 Our rationale was that cuts re-orient the viewer in the depicted environment independent from the exact visual content in the movie frame following the cut.
-In/for the audio-description, we annotated clues about the missing visual content given by the narrator \citep{haeusler2020spechanno}.
-We correlated regressors drawn from the annotations in order to detect possible/possibly confounded regressors that might prevent functional isolation of the PPA.
-In conformity to the analyses performed in the studies reviewed above, we submitted our regressors to a standard multi-level, voxel-wise general linear model (GLM).
-For practical reasons (+++es war a) viel einfacher als visual content zu annotieren und ist b) viel interessanter weil non-visual+++) and encouraged by \citep{aziz2008modulation} and \citep{aminoff2013role}, we focus on the audio-description as a possible life-like substitute to individually localize a ``visual area'' in visually impaired persons.
-
-\todo[inline]{the last paragraph contains a bunch of methods already. I would reduce this to talk about
-the general approach: annotation of events, investigation of model quality, cross-analysis of datasets.
-Possibly cite https://psyarxiv.com/sdbqv/ and declare that this study is a concrete realization of that
-promise}
+In/for the audio-description, we annotated verbal clues about the missing visual content given by the audio-description's additional narrator [citep{haeusler2020speechanno}].
+In conformity to the analyses performed in the studies using not-naturalistic stimuli, we employed a standard multi-level, voxel-wise general linear model (GLM) % in order to???
+% Practical reasons = Es war viel einfacher nouns der audio-description als Frameinhalt des Films zu annotieren
+For practical reasons, and encouraged by \citep{aziz2008modulation} and \citep{aminoff2013role}, we focus on the audio-description as a possible life-like stimulus free from any task to localize a ``visual area'' in individual study participants.
 
 \section{Methods}
-% Ich habe die zwei Methodenteile gemerged und vor allem gekürzt;
-% Einige Stellen sind aber sicherlich noch zu lange; denn im Zweifel habe ich es stehen gelassen
 % Specific data outputs should be explicitly referenced via data citation (see Data Records and Data Citations, below).
@@
 \section{Results (audio)}
-\begin{itemize}
-\item vgl. mit Ergebnis-Teilen anderer Localizer (in wievielen VPN funktioniert's etc.)
-\item   https://en.wikipedia.org/wiki/Bland%E2%80%93Altman_plot
-\end{itemize}
+% vgl. mit Ergebnis-Teilen anderer Localizer (in wievielen VPN funktioniert's etc.)
+% https://en.wikipedia.org/wiki/Bland%E2%80%93Altman_plot
 
 \section{Results (movie)}
-\begin{itemize}
-\item lore ipsum
-\end{itemize}
+lore ipsum
 
@@
 \section{Discussion (audio)}
-
-\begin{itemize}
-\item Hanke et al.
+% Hanke et al.
 (2014): Compared to an audio-visual movie, this is a stimulus that leaves a much larger margin for inter-individual differences in imagining scenery, as well as actors' character and personality traits, while still preserving the time-locked presentation of information to a listener.
 At the same time, an auditory stimulus limits the effect of an attentional focus on the selection of a subset of simultaneously occurring auditory events, in contrast to the selection of different parts of the visual field.
-\item mental imagery hypthesis (s. O'Craven \& Kanwisher, 2000)
-\item Lerner (2011), Honey (2012), Silbert (2014) finden keine ISC in PPA? vgl. DataPaper bzgl. Hörbuch??
-\item setting\_new ist häufig vermischt mit anderer Kategorie "ein Arzt", "ein alter Film", "auf einer Straße", "im Fernsehen", "die drei Jungs", "die zwei im Bett", "Jenny als Teenager", "Forrest vor einem Buffet", "Kennedy", "Jenny kommt aus dem Wohnwagen ihrer Großmutter"
-\item  Soundscape macht es häufiger bereits vorher klar, dass Settingwechsel ist bzw. nicht erst das annotiere Substantiv
-\item object und (room)geo ist vermischt
-\item Retrospelinal Cortex ist in Probabilistic maps krasser als PPA.
-\end{itemize}
+% mental imagery hypthesis (s. O'Craven \& Kanwisher, 2000)
+% Lerner (2011), Honey (2012), Silbert (2014) finden keine ISC in PPA? vgl. DataPaper bzgl. Hörbuch??
+% setting\_new ist häufig vermischt mit anderer Kategorie "ein Arzt", "ein alter Film", "auf einer Straße", "im Fernsehen", "die drei Jungs", "die zwei im Bett", "Jenny als Teenager", "Forrest vor einem Buffet", "Kennedy", "Jenny kommt aus dem Wohnwagen ihrer Großmutter"
+% Soundscape macht es häufiger bereits vorher klar, dass Settingwechsel ist bzw. nicht erst das annotiere Substantiv
+% object und (room)geo ist vermischt
+% Retrospelinal Cortex ist in Probabilistic maps krasser als PPA.
 
@@
 \section*{General Discussion}
-\begin{itemize}
-\item "Abfall" einer Film-Messung
-\item Story für parietale Aktivierung im Film -> räuml. Orientierung / Aufmerksamkeit
-\item CONFOUNDS als klassisches Gegenargument gg. Filme (aber er ändert sich nicht über die Zeit, vgl. resting state)
-\item was sind für Film und Audiobook die Confounds?
-\item Occipital Place Area (Nakamura, 2000), RSC
-\item Natural stimuli like movies [hasson2008neurocinematics; sonkusare2019naturalistic] or narratives [honey2012not-lost; lerner2011topographic; silbert2014coupled] offer an easy to implement, (continuous,) complex, immersive, task-free paradigm that more closely resembles our natural dynamic environment than traditional experimental designs.
-Compared to specifically designed paradigms, the complexity of a natural stimulus goes hand in hand with an unknown temporal structure unless the stimulus is - often manually - annotated [haeusler2016annotation; labs2015portrayed].
-\item Due to their continuity, complexity, and length, they offer a vast amount of data on a variety of brain functions like low-level perception, attention, comprehension, memory, emotions, or social interactions.
+% Data-driven vs. Analysis-Driven
+% "Abfall" einer Film-Messung
+% how do results (PPA-like response localization) differ from a standard visual/block-design localizer for:
+% feasibility of (multi-dimensional) localizer development with naturalistic stimuli
+% Story für parietale Aktivierung im Film -> räuml. Orientierung / Aufmerksamkeit
+% CONFOUNDS als klassisches Gegenargument gg. Filme (aber er ändert sich nicht über die Zeit, vgl. resting state)
+% was sind für Film und Audiobook die Confounds?
+% Occipital Place Area (Nakamura, 2000), RSC
+% Natural stimuli like movies \citep{hasson2008neurocinematics, sonkusare2019naturalistic} or narratives \citep{honey2012not, lerner2011topographic, silbert2014coupled} offer an easy to implement, (continuous,) complex, immersive, task-free paradigm that more closely resembles our natural dynamic environment than traditional experimental designs.
+Compared to specifically designed paradigms, the complexity of a natural stimulus goes hand in hand with an unknown temporal structure unless the stimulus is - often manually - annotated \citep{haeusler2016annotation, labs2015portrayed}.
+% Due to their continuity, complexity, and length, they offer a vast amount of data on a variety of brain functions like low-level perception, attention, comprehension, memory, emotions, or social interactions.
 This suggests the data can later be reused for variety of totally different, independent research questions, possibly on an individual level.
-\item aminoffr2013; jedoch zu non-spatial stuff: Although the PHC is commonly thought of as responding to visual stimuli, it has also been found to elicit activity for auditory stimuli [25,26,30,31] and to respond to odor stimuli [32–34].
-\end{itemize}
+% aminoffr2013; jedoch zu non-spatial stuff: Although the PHC is commonly thought of as responding to visual stimuli, it has also been found to elicit activity for auditory stimuli [25,26,30,31] and to respond to odor stimuli [32–34].
 

### 2020-04-15 paper/main.tex
revise method section until statistical analysis

@@
 % may be used to present compelling new findings & conclusions derived from published data.
-% submissions should exemplify reproducible research by clearly describing all steps in the analysis
-% providing supporting source code, and explaining how and where others may access all data underlying the analysis.
 Intro: PPA as classic example for an visual area
@@
 \end{abstract}
-% Vorgabe: Intro + Discussion = main text ~ 3,000 words.
-% include figure providing schematic overview of the study and assay(s) design
-% -> ist overkill; Paradigma ist mit "Film ab" wenig kompliziert.
+\todo[inline]{Vorgabe: Intro + Discussion = main text ~ 3,000 words}
+\todo[inline]{include figure providing schematic overview of the study and assay(s) design -> is overkill: Steht in den entsprechenden Veröffentlichungen \& Paradigma ist mit "Film ab" wenig kompliziert}
+\todo[inline]{our system cannot accept BibTeX bibliography files; authors who wish to use BibTeX to prepare their references should therefore copy the reference list from the .bbl file that BibTeX generates and paste it into the main manuscript .tex file (and delete the associated  \textbackslash{}bibliography and \textbackslash{}bibliographystyle commands); yeah, whatever.
+Arbeite erstmal mit der references.bib; und habe oben usepackage{natbib}' eingefügt}
 \section{Introduction}
-% our system cannot accept BibTeX bibliography files; authors who wish to use BibTeX to prepare their references should therefore copy the reference list from the .bbl file that BibTeX generates and paste it into the main manuscript .tex file (and delete the associated  \textbackslash{}bibliography and \textbackslash{}bibliographystyle commands).
-% yeah, whatever. Arbeite erstmal mit der references.bib
-% und habe oben '\usepackage{natbib}' eingefügt
 Cognitive neuroscientists use brain imaging methods like blood oxygenation level-dependent functional magnetic resonance imaging (BOLD fMRI) to map perceptual and cognitive brain processes (e.g.
@@
 \citep{dubois2016building})
-
-% Retrosplenial Cortex kommt in Einleitung nicht vor
-% wird aufgrund der Ergebnisse AV und AO in Discussion diskutiert werden
-% -> in den geplanten Abbildungen / Slices aber nicht zu sehen
+\todo[inline]{Retrosplenial Cortex kommt in Einleitung (momentan) nicht vor; wird aufgrund der Ergebnisse AV und AO in Discussion diskutiert werden; ist in den geplanten Abbildungen / Slices aber nicht zu sehen}
 A classic example of a functional, higher-level visual area is the ``parahippocampal place area'' (PPA) \citep{epstein1998ppa, epstein1999parahippocampal}.
@@
 At a group avergae level, results generalize to mental imagination of landscapes \citep{ocraven2000mental} and haptic exploration of scenes constructed from LEGO blocks \citep{wolbers2011modality}.
-% Egal, was ich folgend in der Überblick & später im Detail bzgl. Aziz (2008) schreibe, es wird wahrscheinlich nicht korrekt sein.
-% So wie ich es verstanden habe, hat Aziz den Unterschied zwischen PPA und FFA abgeguckt, aber diesen Unterschied im Kontrast zu object-related Sentences
-% Fig 3 dort; im Grunde kommt da aber überall nur uneinheitliche Grütze raus
 One study that used spoken, place-related sentences showed significantly decreased activation in the left and no modulation in the right-hemispheric PPA \citep{aziz2008modulation}.
+\todo[inline]{Egal, was ich folgend in der Überblick \& später im Detail bzgl.
+Aziz (2008) schreibe, es wird wahrscheinlich nicht korrekt sein; so wie ich es verstanden habe, hat Aziz den Unterschied zwischen PPA und FFA abgeguckt, aber diesen Unterschied im Kontrast zu object-related Sentences; s.
+dortige Fig 3; im Grunde kommt da aber überall nur uneinheitliche Grütze raus}
 
@@
 
-% Review von Aminoff (2013) kommt nur kurz als "competing hypothesis"
-% muss man dann natürlich in der Discussion diskutieren,
-% was aber ggf. gar nicht notwendig ist, weil's darum gar bei uns gar nicht geht
+\todo[inline]{Review von Aminoff (2013) kommt nur kurz als "competing hypothesis"; muss man dann natürlich in der Discussion diskutieren; was aber ggf.
+gar nicht notwendig ist, weil's darum gar bei uns gar nicht geht}
 In summary, studies suggest that the PPA does not exclusively respond to visual(ly) spatial information.
@@
 \citep{aminoff2013role} for a review), it is still unacknowledged/ uncertain/ indeterminate if auditory stimuli lead to inhibitory or excitatory responses, or no change at all in the PPA.
-
-% Coolnessfaktor von naturalistic stimuli ist beinahe komplett raus
-% Data-driven vs. theory-driven analyses ist komplett raus
-% ggf. erwähnen, dass möglichst ähnliche und nicht fancy analysis gewählt wurde, um Replizierung der Ergebnisse, aber mit naturalistic stimuli zu gewährleisten.
-% -> vgl. Speech-Anno-Paper; in Discussion bringen
+\todo[inline]{Coolnessfaktor von naturalistic stimuli ist beinahe komplett raus; Data-driven vs.
+theory-driven analyses ist komplett raus -> vgl.
+Speech-Anno-Paper; jedoch in Discussion bringen (s.
+dort); ggf.
+erwähnen, dass möglichst ähnliche und nicht fancy analysis gewählt wurde, um Replizierung der Ergebnisse, aber mit naturalistic stimuli zu gewährleisten.}
 All revied studies used a just a small set of carefully designed, simplified stimuli to strictly control experimental conditions.
@@
 Naturalistic stimuli like movies \citep{hasson2008neurocinematics, sonkusare2019naturalistic} or narratives \citep{honey2012not, lerner2011topographic, silbert2014coupled} offer an easy to implement, (continuous,) complex, immersive stimulus that better resembles our experience of a continuous dynamic environment.
-% hier wird GLM nicht explizit erwähnt; denke, muss nicht so spezifisch sein
 Two early studies using naturalistic stimuli suggest functional specialization is preserved during free viewing of a movie when many areas respond simultaneously and interact [<- der Schlusssatz ist aus hasson und bartels plagiiert \citep{bartels2004mapping, hasson2004intersubject}
@@
 % N=14 is inner join of AV & AO
-\todo[inline]{
-    The next paragraphs contain a bunch of methods already; reduce this to talk about the general approach:
-    annotation of events,
-    investigation of model quality,
-    cross-analysis of datasets.
-    Possibly cite https://psyarxiv.com/sdbqv/
+\todo[inline]{The next paragraphs contain a bunch of methods already; reduce this to talk about the general approach:
+    a) annotation of events,
+    b) investigation of model quality,
+    c) cross-analysis of datasets.
+    d) Possibly cite https://psyarxiv.com/sdbqv/
     and declare that this study is a concrete realization of that promise
@@
 \section{Methods}
-% Specific data outputs should be explicitly referenced via data citation (see Data Records and Data Citations, below).
-An exhaustive description of the participants, stimulus creation, procedure, stimulation setup, and fMRI acquisition can be found in \citep{hanke2014audiomovie} and \citep{hanke2016simultaneous, sengupta2016extension}
-
-\todo{following is a brief summary of most important aspects}
-
-\todo[inline]{we should consider making a statement how often these datasets have been analyzed be
-independent groups already. if we do, they will all get an 'you have been cited' alter eventually}
+\todo[inline]{Specific data outputs should be explicitly referenced via data citation (see Data Records and Data Citations, below)}
+\todo[inline]{MIH: we should consider making a statement how often these datasets have been analyzed be independent groups already -> Frage: ist die Liste auf psychoinformatics.de ist aktuell/erschöpfend?
+Ist dann schnell eingebaut}
+\todo[inline]{entsprechend der neuen Infos hier, oben das Ende der Einleitung kürzen}
+We used data from three publicly available datsets as part of the studyforrest dataset (\href{http://www.studyforrest.org}{studyforrest.org}) that has already been used by other research groups for independent research questions before.
+We used fMRI data from 14 subjects who took part in three different studies.
+Namely the same subjects were
+a) listening to the audio-description (AO study) \citep{hanke2014audiomovie}) of the movie ``Forrest Gump'', a dataset already used by [XY].
+b) watching the actual audio-visual movie (AV study) \citep{hanke2016simultaneous}, a dataset already used by [XY].
+c) participating in a dedicated block-wise visual localizer (LOC study) \citep{sengupta2016extension}, a dataset aready used by [XY].
+An exhaustive description of the participants, stimulus creation, procedure, stimulation setup, and fMRI acquisition can be found in the corresponding publications  \citep{hanke2014audiomovie, hanke2016simultaneous, sengupta2016extension}.
+Following is a brief summary of most important aspects.
+% Fokus auf die Naturalistic Stimuli; LOC study ist effektiv nicht mit drin
 
 \subsection{Participants}
-% ggf. mit "Stimuli" zusammenfassen, weil sich das, dadurch dass die gleichen 15 in beiden Experimenten mitgemacht haben schwer prägnant trennen lässt.
-In the first \todo{better to give them labels in the initial paragraph above, we will be referring to them quite a bit} study, fifteen participants (all right-handed, age 21–38 years, mean age 26.6 years, 12 male) listened to the German audio-description (Koop, Michalski, Beckmann, Meinhardt \& Benecke, produced by Bayrischer Rundfunk, 2009) of the movie ``Forrest Gump'' (R.
-Zemeckis, Paramount Pictures, 1994) as an additional audio track for visually impaired listeners on Swiss public television.
-In the second study, the same 15 participants (21–39 years, mean age 29.4, six female) watched the audio-visual movie with dubbed German audio track.
+% ich habe von den aligned data eine Intersection of 14 VPN von AO und AV
+% in der Speech-Anno-Validation (AO only) habe ich 19 VPN
+% es fehlt jeweils VP10
+In the AO study, twenty [+++also, ich habe nur Daten von 19 benutzt; VP10 hat keine (aligned) Daten+++] participants (all right-handed, age 21–38 years, mean age 26.6 years, 12 male) listened to the German audio-description \citep{ForrestGumpGermanAD} of the movie ``Forrest Gump'' \citep{ForrestGumpMovie} as an additional audio track for visually impaired listeners on Swiss public television.
+In the AV study, the same 15 participants [+++VP 10 wurde entpsrechend nicht genutzt+++] (21–39 years, mean age 29.4, six female) watched the audio-visual movie with dubbed German audio track \citep{ForrestGumpDVD}.
+% LOC study einarbeiten
+In the LOC study [].
+
 All participants reported to have normal hearing, normal or corrected-to-normal vision, and no known history of neurological disorders.
+% mit LOC study updaten
 In both studies, participants received monetary compensation and gave written informed consent for their participation and for public sharing of all obtained data in anonymized form.
@@
 
-\todo[inline]{i think the stimulus infos need to move from here into the section below}
-
 \subsection{Stimuli}
-% grey bars habe ich nicht erwähnt, obwohl sie - weil bei Lisas Stimuli überall anders - so viel Spaß gemacht haben
-The movie's audio track and the audio-description are largely identical. The plot is carried by an off-screen voice of the main character Forrest Gump.
+The movie's  \citep{ForrestGumpMovie} audio track and the audio-description \citep{ForrestGumpGermanAD} are largely identical.The plot is carried by an off-screen voice of the main character Forrest Gump.
 The audio-description's male narrator additionally verbalizes essential aspects of the visual scenery when there is no dialog, off-screen voice or relevant sound in the audio track.
-The audio-description was temporally aligned to the audio track of the German DVD release (Paramount Home Entertainment, Germany, 2002; PAL video, DE103519SV).A few scenes less relevant to the major plot were removed to create the ``research cut'' lasting $\approx$2h.
+The audio-description was temporally aligned to the audio track of the German DVD release.
+A few scenes less relevant to the major plot were removed to create the ``research cut'' lasting $\approx$2h.
 Both stimuli were further processed (filtering, volume adjustments) to improve understandability / audibility during MRI scanning.
@@
 Figure 3a in \citep{hanke2014audiomovie}
-
-\subsection{Procedure}
-In both studies, participants filled out a questionnaire on their basic demographic information and familiarity with the audio-description or the movie.
-Participants were instructed to inhibit physical movements except for eye-movements, and otherwise to simply "enjoy the audiobook" or "enjoy the movie" respectively.
-Audio-description and movie segments were presented in chronological order with four segments in two fMRI sessions respectively.
-\todo{possibly cut the rest of the section} At the start recording session(s), participants listened to music from the movie’s closing credits segment to individually determine optimal stimulus volume.
-Participants were instructed to ``maximize the volume of the stimulus without it becoming unpleasantly loud or causing acoustic distortions by overdriving the loudspeaker hardware''.
-% unterscheidet sich ggf. zwischen Hörspiel / Film oder kann ganz raus?
-Between sessions, participants left the scanner for a break with a flexible duration. Structural images were obtained during the first study on a day different from the fMRI session.
-
-\subsection{Stimulation setup}
-Stimulation was implemented with PsychoPy v1.79 (with an early version of the MovieStim2 component later to be publicly released with \href{http://www.psychopy.org}{PsychoPy v1.81}; \citep{peirce2007psychopy}) running on a computer with the \href{http://neuro.debian.net}{(Neuro)Debian} operating system \citep{halchenko2012open}.
-% Einige Dinge können m.M.n. raus; insb. das in den []-Klammern
-% habe es noch einmal drinnen gelassen, solltest Du die Dinge für wichtig halten
-In the auditory study, visual instructions were presented on a rear-projection screen inside scanner bore using an LCD projector (DLA-G150CL, JVC Ltd.).
-During the functional scans, the projector presented a medium gray screen with the primary purpose to illuminate a participant’s visual field in order to prevent premature fatigue.
-[The screen contained a solid black ``fixation'' dot that faded in and out at the beginning and end of a movie segment.]
-In the audio-visual study, visual instructions and stimuli were presented on a rear-projection screen using an LCD projector (JVC DLA RS66E, JVC Ltd., light transmission reduced to 13.7\% with a gray filter) connected to the stimulus computer [via a DVI extender system (Gefen EXT-DVI-142DLN with EXT-DVI-FM1000).
-The movie was shown at a viewing distance of 63\,cm in 720\,p resolution at full width on a 1280 *1024\,pixel screen with 60\,Hz video refresh rate and screen dimension of 26.5 * 21.2\,cm, corresponding to 23.75*13.5 or 23.75*10.25 when considering only the movie content and excluding the horizontal gray bars].
-% Hier hat es Unterschiede zwischen Hörspiel & Film geben? habe es wie folgt zusammengefasst; im Zweifel ist es eh noch zu ausführlich
-Auditory stimulation was delivered through an MR confon mkII+ driving custom-built in-ear headphones (HP-M01, MR confon GmbH, Magdeburg, Germany; \citep{baumgart1998electrodynamic}) that reduced the scanner noise by at least 20–30 dB.
-Headphones were  fed from an Aureon 7.1 USB (Terratec) sound card through an optical connection.
-
-\subsection{fMRI data acquisition}
-In both studies, a total of 3599 volumes were recorded for each participant (451, 441, 438, 488, 462, 439, 542 and 338 volumes for movie segment 1–8 respectively).
-In the auditory study, a whole-body 7-Tesla Siemens MAGNETOM magnetic resonance scanner equipped with a local circularly polarized head transmit and a 32 channel brain receive coil (Nova Medical, Inc., Wilmington, MA, USA) acquired T2*-weighted echo-planar images (gradient-echo, 2\,s repetition time (TR), 22\,ms echo time, 0.78\,ms echo spacing, 1488\,Hz/Px bandwidth, generalized autocalibrating partially parallel acquisition, acceleration factor 3, 24 Hz/Px bandwidth in phase encoding direction) using 36 axial slices (thickness 1.4\,mm, 1.4 x 1.4\,mm in-plane resolution, 224\,mm field-of-view, anterior-to-posterior phase encoding direction) with a 10 percent inter-slice gap were recorded in ascending order.
-Slices were oriented to include the ventral portions of frontal and occipital cortex while minimizing intersection with the eyeballs.
-The field-of-view was centred on the approximate location of Heschl's gyrus.
-% EPI images were online-corrected for motion and geometric distortions [Oh, S.
-et al.
-2012; In, M.
-\& Speck, O., 2012; Chung, J.
-et al., 2011+++].
-Auxiliary scans for slice alignment and motion- and distortion-correction were performed at the beginning of the first fMRI recording session and also after the break at the start of the recording for the second half of the movie.
-In the audio-visual study, a whole-body 3 Tesla Philips Achieva dStream MRI scanner equipped with a 32 channel head coil acquired T2*-weighted echo-planar images (gradient-echo, 2\,s repetition time (TR), 30\,ms echo time, 90 DEGREE flip angle, 1943\,Hz/Px bandwidth, parallel acquisition with sensitivity encoding (SENSE) reduction factor 2).
-35 axial slices (thickness 3.0\,mm, 10\% inter-slice gap) with 80*80 voxels (3.0*3.0 mm of in-plane resolution), 240\,mm mm field-of-view (FoV) and an anterior-to-posterior phase encoding direction were recorded in ascending order.
-Philips’ “SmartExam” was used to automatically position slices in AC-PC orientation such that the topmost slice was located at the superior edge of the brain.
+% LOC study?
 
 \subsection{Stimulus Annotation}
-% einleitendes Blabla zu haeusler2020speechanno
-% deutlich machen, warum was wie annotiert wurde
+\todo[inline]{einleitendes Blabla zu haeusler2020speechanno}
+\todo[inline]{allg. überarbeiten; deutlich machen, WARUM WAS WIE annotiert wurde}
+% Florian hat 2 Regeln falsch verstanden, sonst war übereinstimmung 90-95%
+% Kategorie ``++'' enthält ausnahmesweise auch adverbiale Best. der Zeit.
 % ggf. angeben, dass die effektiv identisch waren
-% Florian hat zwei Regeln falsch verstanden, sonst war übereinstimmung >90%
-% Kategorie ``++'' enthält ausnahmesweise auch adverbiale Best. der Zeit.
+\todo[inline]{aus Speech-Anno Paper 'descriptive-statistics-anno.py' übernehmen \& anpassen, um Statistiken und runcommand-file zu erstellen}
 A further annotation of the audio-description's narrator was done manually: Two
@@
 % Tabelle der Descriptive Nouns;
-% aus Speech-Anno Paper 'descriptive-statistics-anno.py' übernehmen & anpassen.
-% von allen \newcommands wurde das \ for dem Variablennamen entfernt
-% -> sind insofern alles Platzhalter bis das Skript fertig ist, das die Inputdatei schreibt.
+\todo[inline]{wenn decriptive-statistics-anno.py angepasst und Datei mit newcommands geschrieben, Schrägstrich vor die jeweiligen Platzhalter setzen, damit commands daraus werden; Caption hübsch machen}
 \begin{table*}[t]
-    \caption{Narrator's descriptive nouns. All categories sorted alphapetically. Examples are given in English.}
+    \caption{Narrator's descriptive nouns.
+All categories sorted alphapetically.
+Examples are given in English.
+Tabelle enthält bei den Counts Platzhalter für die commands, die ins .tex-file geschrieben werden.}
 \label{tab:descr-nouns}
@@
 body & trunk of the body; overlaid clothes & back, hip, shoulder; jacket, dress shirt & aDescrBodyAll & aDescrBodyI & aDescrBodyII & aDescrBodyIII & aDescrBodyIV & aDescrBodyV & aDescrBodyVI & aDescrBodyVII & aDescrBodyVIII \tabularnewline
-bodypart & limbs and trousers & arm, finger, leg, toe & aDescrBodypartAll & aDescrBodypartI & aDescrBodypartII & aDescrBodypartIII & aDescrBodypartIV & aDescrBodypartV & aDescrBodypartVI & aDescrBodypartVII & aDescrBodypartVIII\tabularnewline
+bodypart & limbs and trousers & arm, finger, leg, toe & aDescrBodypartAll & aDescrBodypartI & aDescrBodypartII & aDescrBodypartIII & aDescrBodypartIV & aDescrBodypartV & aDescrBodypartVI & aDescrBodypartVII & aDescrBodypartVIII \tabularnewline
 face & face or parts of it & face, ear, nose, mouth & aDescrFaceAll & aDescrFaceI & aDescrFaceII & aDescrFaceIII & aDescrFaceIV & aDescrFaceV & aDescrFaceVI & aDescrFaceVII & aDescrFaceVIII \tabularnewline
@@
 
-\section{Data analysis }
-% \todo{shouldn't this be also just in Methods?}
-% hier ggf. noch expliziter machen, dass die spatially downsampled sind
-% https://openneuro.org/datasets/ds000113
+\subsection{Procedure}
+In both studies, participants filled out a questionnaire on their basic demographic information and familiarity with the audio-description or the movie.
+Participants were instructed to inhibit physical movements except for eye-movements, and otherwise to simply "enjoy the audiobook" or "enjoy the movie" respectively.
+Audio-description and movie segments were presented in chronological order with four segments in two fMRI sessions respectively.
+Between sessions, participants left the scanner for a break with a flexible duration. Structural images were obtained during the first study on a day different from the fMRI session.
+% At the start (of each?) recording session, participants listened to music from the movie's closing credits segment to individually determine optimal stimulus volume.
+% Participants were instructed to ``maximize the volume of the stimulus without it becoming unpleasantly loud or causing acoustic distortions by overdriving the loudspeaker hardware''.
+
+\subsection{Stimulation setup}
+\todo[inline]{irrelevantes kürzen}
+In both studies, stimulation was implemented with PsychoPy v1.79 (with an early version of the MovieStim2 component later to be publicly released with \href{http://www.psychopy.org}{PsychoPy v1.81}; \citep{peirce2007psychopy}) running on a computer with the \href{http://neuro.debian.net}{(Neuro)Debian} operating system \citep{halchenko2012open}.
+In the AO study, visual instructions were presented on a rear-projection screen inside scanner bore using an LCD projector (DLA-G150CL, JVC Ltd.).
+During the functional scans, the projector presented a medium gray screen with the primary purpose to illuminate a participant’s visual field in order to prevent premature fatigue.
+[The screen contained a solid black ``fixation'' dot that faded in and out at the beginning and end of a movie segment.]
+In the AV study, visual instructions and stimuli were presented on a rear-projection screen using an LCD projector (JVC DLA RS66E, JVC Ltd., light transmission reduced to 13.7\% with a gray filter) connected to the stimulus computer [via a DVI extender system (Gefen EXT-DVI-142DLN with EXT-DVI-FM1000).
+The movie was shown at a viewing distance of 63\,cm in 720\,p resolution at full width on a 1280 *1024\,pixel screen with 60\,Hz video refresh rate and screen dimension of 26.5 * 21.2\,cm, corresponding to 23.75*13.5 or 23.75*10.25 when considering only the movie content and excluding the horizontal gray bars].
+In both studies [???] auditory stimulation was delivered through an MR confon mkII+ driving custom-built in-ear headphones (HP-M01, MR confon GmbH, Magdeburg, Germany; \citep{baumgart1998electrodynamic}) that reduced the scanner noise by at least 20–30 dB.
+Headphones were  fed from an Aureon 7.1 USB (Terratec) sound card through an optical connection.
+
+\subsection{fMRI data acquisition}
+\todo[inline]{irrelevantes kürzen}
+In both studies, a total of 3599 volumes were recorded for each participant (451, 441, 438, 488, 462, 439, 542 and 338 volumes for movie segment 1–8 respectively).
+In AO study, a whole-body 7-Tesla Siemens MAGNETOM magnetic resonance scanner equipped with a local circularly polarized head transmit and a 32 channel brain receive coil (Nova Medical, Inc., Wilmington, MA, USA) acquired T2*-weighted echo-planar images (gradient-echo, 2\,s repetition time (TR), 22\,ms echo time, 0.78\,ms echo spacing, 1488\,Hz/Px bandwidth, generalized autocalibrating partially parallel acquisition, acceleration factor 3, 24 Hz/Px bandwidth in phase encoding direction) using 36 axial slices (thickness 1.4\,mm, 1.4 x 1.4\,mm in-plane resolution, 224\,mm field-of-view, anterior-to-posterior phase encoding direction) with a 10 percent inter-slice gap were recorded in ascending order.
+Slices were oriented to include the ventral portions of frontal and occipital cortex while minimizing intersection with the eyeballs.
+The field-of-view was centred on the approximate location of Heschl's gyrus.
+[EPI images were online-corrected for motion and geometric distortions [Oh, S.
+et al.
+2012; In, M.
+\& Speck, O., 2012; Chung, J.
+et al., 2011+++].
+Auxiliary scans for slice alignment and motion- and distortion-correction were performed at the beginning of the first fMRI recording session and also after the break at the start of the recording for the second half of the movie].
+In the AV study, a whole-body 3 Tesla Philips Achieva dStream MRI scanner equipped with a 32 channel head coil acquired T2*-weighted echo-planar images (gradient-echo, 2\,s repetition time (TR), 30\,ms echo time, 90 DEGREE flip angle, 1943\,Hz/Px bandwidth, parallel acquisition with sensitivity encoding (SENSE) reduction factor 2).
+35 axial slices (thickness 3.0\,mm, 10\% inter-slice gap) with 80*80 voxels (3.0*3.0 mm of in-plane resolution), 240\,mm mm field-of-view (FoV) and an anterior-to-posterior phase encoding direction were recorded in ascending order.
+Philips' ``SmartExam'' was used to automatically position slices in AC-PC orientation such that the topmost slice was located at the superior edge of the brain.
+
+\subsection{Preprocessing}
+% DATA SOURCE
+\todo[inline]{hier ggf. expliziter erwähnen, dass AO spatially downsampled ist}
 % denoised movie data:
@@
 \href{''https://github.com/psychoinformatics-de/studyforrest-data-aligned''}{GitHub}.
-Data are already aligned to a subject-specific \href{''https://github.com/psychoinformatics-de/studyforrest-data-templatetransforms''}{3 Tesla BOLD template} by a rigid body transformation in MCFLIRT \citep{jenkinson2002registration} to correct for motion during scanning.
+Data are already aligned to a subject-specific \href{''https://github.com/psychoinformatics-de/studyforrest-data-templatetransforms''}{3 Tesla BOLD template} by a rigid body transformation in MCFLIRT \citep{jenkinson2002registration} to correct for motion during scanning
 \citep{sengupta2016extension}.
-\todo{cite sengupta2016 where this was first done and described, ie same image/data was used here}
+
+\todo[inline]{cite sengupta2016 where this was first done and described, ie same image/data was used here}
+
 All further analysis steps in the current study were carried out using tools of FSL v5.0.9 (\href{''https://www.fmrib.ox.ac.uk/fsl''}{FMRIB's Software Library};\citep{smith2004fsl}; on a computer cluster running the \href{https://www.debian.org}{Debian} GNU/Linux operating system.
@@
 
-\subsection{Preprocessing}
+% ACTUAL PREPROCESSING
 Preprocessing (and statistical analysis) was carried out using FEAT v6.00 (FMRI Expert Analysis Tool;\citep{woolrich2001autocorr}) as part of FSL.
@@
 % https://www.springernature.com/gp/authors/research-data-policy/data-availability-statements/12330880
+\todo[inline]{provide supporting source code, and explaining how and where others may access all data underlying the analysis}
 \emph{for all studies using custom code in the generation or processing of datasets,

### 2020-04-16 code/create-roi-overlaps.sh
add script to create visual roi overlaps from subdataset

@@ -1,0 +1,11 @@
+#!/bin/bash
+mkdir rois-and-masks
+datalad get inputs/studyforrest-data-visualrois/sub-*/rois/*.*
+datalad get inputs/studyforrest-data-visualrois/sub-*/2ndlvl.gfeat/cope*.feat/stats/zstat*.nii.gz
+datalad get inputs/studyforrest-data-visualrois/src/tnt/templates/grpbold3Tp2/brain.nii.gz
+datalad get inputs/studyforrest-data-visualrois/src/tnt/sub-??/bold3Tp2/in_grpbold3Tp2/subj2tmpl_warp.nii.gz
+
+cd inputs/studyforrest-data-visualrois
+./code/rois2manuscript
+mv *_overlap.nii.gz ../../rois-and-masks
+cd ../..

### 2020-04-29 paper/main.tex
add some notes to discussion
revise manuscript (& references) after feedback

@@
 We annotated events in the otherwise unknown temporal structure of both stimuli.
-In/for the movie, we annotated different kinds of cinematographic cuts \citep{haeusler2016annotation} as presumably ``spatially relevant'' events.
+In/for the movie, we annotated different kinds of cinematographic cuts \citep{haeusler2016cutanno} as presumably ``spatially relevant'' events.
 Our rationale was that cuts re-orient the viewer in the depicted environment independent from the exact visual content in the movie frame following the cut.
-In/for the audio-description, we annotated verbal clues about the missing visual content given by the audio-description's additional narrator [citep{haeusler2020speechanno}].
+In/for the audio-description, we annotated verbal clues about the missing visual content given by the audio-description's additional narrator \citep{haeusler2020speechanno}.
 In conformity to the analyses performed in the studies using not-naturalistic stimuli, we employed a standard multi-level, voxel-wise general linear model (GLM) % in order to???
@@
 Following is a brief summary of most important aspects.
-% Fokus auf die Naturalistic Stimuli; LOC study ist effektiv nicht mit drin
+\todo[inline]{Fokus des gesamten Methodenteils liegt auf den Naturalistic Stimuli; LOC study ist bisher effektiv nicht mit drin}
 
@@
 narrator to describe the movie's missing visual content.
-Categories focus on the cinematographic scene's environment, inherent objects, persons, and a person's appearance.
+Categories focus on the cinematographic scene's environment, inherent objects, persons, and a person's appearance (cf. table \ref{tab:descr-nouns})..
 A categorizing of nouns that serve as auditory cues about the movie's visual content.
 Comprised categories focus on the cinematographic scene's environment (geo, geo-room; setting\_new, setting\_old), inherent persons (female, female name; male, male name, person), their appearance (face, head; body, bodypart), and objects (object, furniture).
+The nouns are categorized by the clue they provide about a cinematographic scene's environment \todo{maybe skip the names and just cite the table} (geo, geo-room; setting\_new, setting\_rec), its inherent persons (female, female name; male, male name, person), a person's appearance (face, head; body, bodypart), and a scene's inherent objects (object, furniture).
 A preliminary annotation according to the rules [entweder im laufenden Text oder in Tabelle], einer neuen Tabelle oder im laufenden Text was done by one person and corrected in several runs by the author.
@@
 \subsection{Statistical analysis}
-A standard two-level general linear model (GLM) analysis was conducted in FEAT to create subject-specific results ($Z$-maps).
+For both naturalistic stimli, we conducted a standard two-level general linear model (GLM) analysis in FEAT to create subject-specific results ($Z$-maps).
 A subsequent, third-level analysis averaged contrast estimates over subjects.
@@
 \subsubsection{first-level}
-\paragraph{Regressors \todo{stimulus/statistical model?}}
-To build the regressors for the GLMs, we took advantage of two publicly available annotations of the stimuli's temporal structure.
-One annotation of speech occurring in the audio-description and movie [haeusler2020speechanno], and a second annotation of movie cuts and depicted locations \href{https://f1000research.com/articles/5-2273}{haeusler2016annotation}.
-As a first step, the annotations were split via (\href{"https://github.com/chrhaeusler/studyforrest-data-annotations/blob/master/code/researchcut2segments.py"}{python script} into eight parts corresponding to the eight segments used in the scanner.
-% wenn ich folgend den "null regressor" nehme, darf ich den ganzen Run - glaube ich - in der 2nd level Analyse gar nicht benutzen??
-For the auditory stimulus, we used nouns embedded in sentences spoken by the narrator.
-The nouns are categorized by the clue they provide about a cinematographic scene's environment \todo{maybe skip the names and just cite the table} (geo, geo-room; setting\_new, setting\_rec), its inherent persons (female, female name; male, male name, person), a person's appearance (face, head; body, bodypart), and a scene's inherent objects (object, furniture).
-% nope, kommt jetzt hier
-Details on procedure to annotate the stimuli on a single-world level and details on the rules to manually categorize the nouns can be found in the \href{"https://www.overleaf.com/project/5d4ab1b759001b5db6ea2bc3"}{corresponding paper}.
+\paragraph{Regressors}
+We used an annotation of movie cuts and depicted locations \citep{haeusler2016cutanno} and an annotation of speech \citep{haeusler2020speechanno} to create the FSL event files resp. regressors.
+First, both annotations were split via \href{"https://github.com/chrhaeusler/studyforrest-data-annotations/blob/master/code/researchcut2segments.py"}{python script} into eight parts corresponding to the eight segments used as stimuli during fMRI scanning.
+\todo[inline]{wenn ich folgend den "null regressor" nehme, darf ich den ganzen Run, glaube ich, in der 2nd level Analyse gar nicht benutzen??}
+For the AO stimulus, we used the narrator's ``descriptive nouns'' (cf. table \ref{tab:descr-nouns}.
 We created 11 regressors from the XY (selected?) original categories by joining / merging some categories (female, females, fname; male, males, mname; face, head) into one regressor (sex\_f; sex\_m; fahead).
+
+\todo[inline]{cross reference to fig:reg-corr}
+
+\begin{table*}[t]
+    \caption{Overview of the events to build the 18 regressors for analysis of the AO stimulus. The first column contains the number of the regressor in the design file of FSL \citep{smith2004fsl}.
+''fg\_ad\_lrdiff (left-right volume difference) and ``fg\_ad\_rms'' (root mean square loudness) represent low-level auditory nuissance regressors comprising one event for every movie frame (40ms).}
+\label{tab:regressors}
+\footnotesize
+\begin{tabular}{lp{3.5cm}lllllllll}
+\toprule
+\textbf{label} &  \textbf{description} & \textbf{all} & \textbf{1} & \textbf{2} & \textbf{3} & \textbf{4} & \textbf{5} & \textbf{6} & \textbf{7} & \textbf{8} \\
+\midrule
+body & XYleft-right volume difference & rBodyAll & rBodyI & rBodyII & rBodyIII & rBodyIV & rBodyV & rBodyVI & rBodyVII & rBodyVIII \tabularnewline
+
+fg\_ad\_lrdiff & left-right volume difference & rFgadlrdiffAll & rFgadlrdiffI & rFgadlrdiffII & rFgadlrdiffIII & rFgadlrdiffIV & rFgadlrdiffV & rFgadlrdiffVI & rFgadlrdiffVII & rFgadlrdiffVIII \tabularnewline
+fg\_ad\_rms & root mean square & rFgadrmsAll & rFgadrmsI & rFgadrmsII & rFgadrmsIII & rFgadrmsIV & rFgadrmsV & rFgadrmsVI & rFgadrmsVII & rFgadrmsVIII \tabularnewline
+\bottomrule
+\end{tabular}
+\end{table*}
+
 % over length of each noun
@@
 
+% From Poster:
+% 1. PPA shows increased activation during non-visual, complex auditory stimulation that provides incidental spatial information.
+% 2. only minor temporal correlation of regressors of the audio drama & movie that were not designed for experimental research.
+% 3. but still, alternative contrasts show significant clusters in auditory cortices.
+% 4. inter-individual differences: for two subjects, an alternative audio-contrast shows bilaterally significant clusters whereas the primary contrast shows no significant clusters.
+% 5. audio drama shows bilaterally increased activation in subject 4 in which the visual localizer shows an unilateral cluster.
+% 6. nevertheless, a  complex auditory stimulus might allow individual localization of a functionally defined brain region.
+% 7. results of other studies suggest7 the PPA does not exclusively process the ``spatial layout''" but ``contextual associations''.
+% 8. an audio drama might be suitable as ecologically more valid ``localizer'' for a variety of brain functions.
+
 \section{Discussion (movie)}
-\begin{itemize}
-\item lore ipsum
-\end{itemize}
+lore ipsum
 

### 2020-04-30 paper/main.tex
minor revisions

@@
 \usepackage{todonotes}
+\usepackage{units}
 \usepackage[
@@
 \begin{document}
+%\input{descr-stats-ao-events.tex}
+%\input{descr-stats-av-events.tex}
 
@@
 \end{abstract}
-\todo[inline]{Vorgabe: Intro + Discussion = main text ~ 3,000 words}
+\todo[inline]{Vorgabe: Intro + Discussion = main text ~ 3,000 words; einige offene Dinge sind folgend in Kommentaren und nicht als ToDo gemarkt}
 \todo[inline]{include figure providing schematic overview of the study and assay(s) design -> is overkill: Steht in den entsprechenden Veröffentlichungen \& Paradigma ist mit "Film ab" wenig kompliziert}
@@
 \todo[inline]{Egal, was ich folgend in der Überblick \& später im Detail bzgl.
-Aziz (2008) schreibe, es wird wahrscheinlich nicht korrekt sein; so wie ich es verstanden habe, hat Aziz den Unterschied zwischen PPA und FFA abgeguckt, aber diesen Unterschied im Kontrast zu object-related Sentences; s.
-dortige Fig 3; im Grunde kommt da aber überall nur uneinheitliche Grütze raus}
+Aziz (2008) schreibe, es wird wahrscheinlich nicht korrekt sein; so wie ich es verstanden habe, hat Aziz den Unterschied zwischen PPA und FFA angeguckt, aber diesen Unterschied im Kontrast zu object-related Sentences; s.
+dortige Fig 3; im Grunde kommt da aber überall nur uneinheitliche Grütze raus => bitte gemeinsam im Gespräch checken}
 
@@
 
-% Aziz hat auf eine zweite Mail geantwortet: Sie hat kein Block-Design, sondern modelt die HRF über den jeweils gesamten Satz von ca. 2.8 Sekunden.
+% Aziz hat auf eine zweite Mail geantwortet: Sie modelt die HRF über den jeweils gesamten Satz von ca. 2.8 Sekunden.
 % wie oben im Kommentar erwähnt: Ihre Method Section halte ich für etwas strange.Ich zeige dir ganz am Ende mal ihr Paper; hab die entsprechenden Stellen annotiert.
@@
 To our knowledge only one study by \citep{aziz2008modulation} correlated hemodynamic activity of the PPA with spoken sentences.
-Sentences described generic or famous places (e.g.
-``The Taj Mahal faces a long thin reflecting pool'') or faces  (e.g.
-``Marylin Monroe has a large square jaw'').
+Sentences described generic or famous places (e.g. ``The Taj Mahal faces a long thin reflecting pool'') or faces  (e.g. ``Marylin Monroe has a large square jaw'').
+\todo[inline]{\dots and compared those to a control condition of object-related sentences}
 Participants were instructed to press a button whenever the sentence described an inaccurate or improbable fact.
@@
 In summary, studies suggest that the PPA does not exclusively respond to visual(ly) spatial information.
-This is consistent with a competing hypotheses stating the PPA does not process the spatial layout of a scene specifically but contextual associations in general \citep{aminoff2006parahippocampal} for a review).
+This is consistent with a competing hypotheses stating the PPA does not process the spatial layout of a scene specifically but contextual associations in general (see \citep{aminoff2006parahippocampal} for a review).
 Independent(ly) from competing theories (s.
 \citep{aminoff2013role} for a review), it is still unacknowledged/ uncertain/ indeterminate if auditory stimuli lead to inhibitory or excitatory responses, or no change at all in the PPA.
+\todo[inline]{aber Huth, 2016, implizit; diskutiert PPA als solches jedoch gar nicht -> noch mal checken}
 \todo[inline]{Coolnessfaktor von naturalistic stimuli ist beinahe komplett raus; Data-driven vs.
@@
 Thus, they cannot / could answer the question how the PPA might behave under life-like conditions.
-Naturalistic stimuli like movies \citep{hasson2008neurocinematics, sonkusare2019naturalistic} or narratives \citep{honey2012not, lerner2011topographic, silbert2014coupled} offer an easy to implement, (continuous,) complex, immersive stimulus that better resembles our experience of a continuous dynamic environment.
-Two early studies using naturalistic stimuli suggest functional specialization is preserved during free viewing of a movie when many areas respond simultaneously and interact [<- der Schlusssatz ist aus hasson und bartels plagiiert \citep{bartels2004mapping, hasson2004intersubject}
+Naturalistic stimuli like movies \citep{hasson2008neurocinematics, sonkusare2019naturalistic} or narratives \citep{honey2012not, lerner2011topographic, silbert2014coupled} offer an easy to implement, (continuous,) complex, immersive stimuli that better resemble our experience of a continuous dynamic environment.
+Two early studies using naturalistic stimuli suggest functional specialization is preserved during free viewing of a movie when many areas respond simultaneously and interact [+++ der Schlusssatz ist aus hasson und bartels plagiiert \citep{bartels2004mapping, hasson2004intersubject}+++]
 
@@
 Employing a general linear model to model hemodynamic activity, these time points correlated with increased activity in the ``fusiform face area'' \citep{kanwisher1997ffa} and ``extrastriate body area'' \citep{downing2001bodyarea} respectively.
-Employing a reverse intersubject correlation, \citep{hasson2004intersubject} took used a 30 minute clip of the movie \textit{The Good, the Bad, the Ugly}.
-fMRI brain volumes showing the highest hemodynamic activity in the PPA [across (five) participants] were matched to the (temporally) correlating movie frames.
-Results revealed that frames depicted indoor and outdoor scenes including buildings and open fields.
+Employing a reverse intersubject correlation, \citep{hasson2004intersubject} used a 30 minute clip of the movie \textit{The Good, the Bad, the Ugly}.
+fMRI brain volumes showing the highest hemodynamic activity in the PPA [across (five) participants] were matched to the (temporally) corresponding movie frames.
+Results revealed that corresponding movie frames depicted indoor and outdoor scenes including buildings and open fields.
 Nevertheless, no study investigated how the PPA responds to spatial clues that are embedded in a complex, audio-only stimulus.
 
-% Bzgl.
-Open Source der der Ergebnisse/Skripte: Dazu habe ich hier nichts geschrieben, weil ich nur weiß, das der Code veröffentlicht werden soll.
-Du hast die Vision diesbezüglich im Kopf und entsprechend auch kanonisch-prägnante Formulierungen und wo die am besten wie hinkommen
+\todo[inline]{Bzgl.
+Open Source der Ergebnisse/Skripte: Dazu habe ich hier nichts geschrieben, weil ich nur weiß, das der Code veröffentlicht werden soll.
+Du hast die Vision diesbezüglich im Kopf und entsprechend auch kanonisch-prägnante Formulierungen und wo die am besten wie hinkommen}
 
@@
 In this study, we analyze data of three publicly available datasets from the same set of 14 participants as part of the studyforrest data set (\href{http://www.studyforrest.org}{studyforrest.org}).
-We exploratorily investigate how the parahippocampal gyrus [or more general ``human brain''?] responds to ``spatially relevant'' events embedded in a 2h audio-visual movie \citep{hanke2016simultaneous} and its audio-description of the same length \citep{hanke2014audiomovie}.
+We exploratorily investigate how the parahippocampal gyrus [or more general ``human brain''?] responds to ``spatially relevant'' events embedded in a 2h audio-visual movie \citep{hanke2016simultaneous} and its audio-description (i.e.
+the audio-only variant) of the same length \citep{hanke2014audiomovie}.
 We compare these results to PPA localizations that were obtained from a dedicated visual localizer experiment \citep{sengupta2016extension}.
+
 Both natural stimuli were originally designed to entertain an audience and to capture attention free from any perceptual or behavioral task.
@@
 In/for the audio-description, we annotated verbal clues about the missing visual content given by the audio-description's additional narrator \citep{haeusler2020speechanno}.
+
 In conformity to the analyses performed in the studies using not-naturalistic stimuli, we employed a standard multi-level, voxel-wise general linear model (GLM) % in order to???
@@
 \todo[inline]{Specific data outputs should be explicitly referenced via data citation (see Data Records and Data Citations, below)}
-\todo[inline]{MIH: we should consider making a statement how often these datasets have been analyzed be independent groups already -> Frage: ist die Liste auf psychoinformatics.de ist aktuell/erschöpfend?
-Ist dann schnell eingebaut}
-\todo[inline]{entsprechend der neuen Infos hier, oben das Ende der Einleitung kürzen}
-We used data from three publicly available datsets as part of the studyforrest dataset (\href{http://www.studyforrest.org}{studyforrest.org}) that has already been used by other research groups for independent research questions before.
-We used fMRI data from 14 subjects who took part in three different studies.
-Namely the same subjects were
+\todo[inline]{statement how often datasets have been analyzed be independent groups -> Frage: ist die Liste auf psychoinformatics.de ist aktuell/erschöpfend? Ist dann schnell eingebaut}
+We used data from three publicly available datsets as part of the studyforrest dataset (\href{http://www.studyforrest.org}{studyforrest.org}) that has already been used by other research groups for independent research questions before
+We used fMRI data from 14 subjects who took part in three different studies. Namely, the same subjects were
 a) listening to the audio-description (AO study) \citep{hanke2014audiomovie}) of the movie ``Forrest Gump'', a dataset already used by [XY].
@@
 Following is a brief summary of most important aspects.
-\todo[inline]{Fokus des gesamten Methodenteils liegt auf den Naturalistic Stimuli; LOC study ist bisher effektiv nicht mit drin}
+\todo[inline]{um Sengupta ergänzen}
 
 \subsection{Participants}
-% ich habe von den aligned data eine Intersection of 14 VPN von AO und AV
-% in der Speech-Anno-Validation (AO only) habe ich 19 VPN
-% es fehlt jeweils VP10
-In the AO study, twenty [+++also, ich habe nur Daten von 19 benutzt; VP10 hat keine (aligned) Daten+++] participants (all right-handed, age 21–38 years, mean age 26.6 years, 12 male) listened to the German audio-description \citep{ForrestGumpGermanAD} of the movie ``Forrest Gump'' \citep{ForrestGumpMovie} as an additional audio track for visually impaired listeners on Swiss public television.
-In the AV study, the same 15 participants [+++VP 10 wurde entpsrechend nicht genutzt+++] (21–39 years, mean age 29.4, six female) watched the audio-visual movie with dubbed German audio track \citep{ForrestGumpDVD}.
-% LOC study einarbeiten
-In the LOC study [].
+\todo[inline]{ich habe von den aligned data eine Intersection von 14 VPN aus AO und AV; in der Speech-Anno-Validation (7T only) habe ich 19 VPN; es fehlt jeweils VP10; demographische Daten bzgl.
+(Durchschnitts)Alter und Geschlecht ist folglich falsch}
+In the AO study, 19 participants (all right-handed, age 21–38 years, mean age 26.6 years, 12 male) listened to the German audio-description \citep{ForrestGumpGermanAD} of the movie ``Forrest Gump'' \citep{ForrestGumpMovie} as an additional audio track for visually impaired listeners on Swiss public television.
+In the AV study, the same 14 participants [+++VP 10 wurde nicht genutzt+++] (21–39 years, mean age 29.4, six female) watched the audio-visual movie with dubbed German audio track \citep{ForrestGumpDVD}.
+
+\todo[inline]{Daten zu Sengupta einarbeiten}
+In the LOC study\dots
 
@@
 \subsection{Stimuli}
-The movie's  \citep{ForrestGumpMovie} audio track and the audio-description \citep{ForrestGumpGermanAD} are largely identical.The plot is carried by an off-screen voice of the main character Forrest Gump.
-The audio-description's male narrator additionally verbalizes essential aspects of the visual scenery when there is no dialog, off-screen voice or relevant sound in the audio track.
+We used the German DVD release \citep{ForrestGumpDVD} of the audio-visual movie ``Forrest Gump'' \citep{ForrestGumpMovie} and its temporally aligned audio-description (i.e.
+the audio-only variant of the movie) that was broadcast as an additional audio track for visually impaired listeners on Swiss public televinsion \citep{ForrestGumpGermanAD}.
+The plot of the movie is already carried by an off-screen voice of the main character Forrest Gump.
+In the largely identical audio-description, a male narrator additionally describes essential aspects of the visual scenery when there is no off-screen voice, dialog, or other relevant auditory content.
 The audio-description was temporally aligned to the audio track of the German DVD release.
-A few scenes less relevant to the major plot were removed to create the ``research cut'' lasting $\approx$2h.
-Both stimuli were further processed (filtering, volume adjustments) to improve understandability / audibility during MRI scanning.
+A few scenes less relevant to the major plot were removed to create the ``research cut'' lasting $\approx$2h \citep{hanke2014audiomovie,hanke2016simultaneous}.
+Both stimuli were further processed (filtering, volume adjustments) to improve audibility during MRI scanning.
 Finally, each stimulus was split into eight segments of approximately 15 minutes.
 Except for the first movie segment, each segment started with a snippet of at least six seconds immediately preceding the movie scene boundary used to split the segments (s.
-Figure 3a in \citep{hanke2014audiomovie}
+Figure 3a in \citep{hanke2014audiomovie}.
+\todo[inline]{Sengupta: Stimuli}
 % LOC study?
@@
 \subsection{Stimulus Annotation}
-\todo[inline]{einleitendes Blabla zu haeusler2020speechanno}
-\todo[inline]{allg. überarbeiten; deutlich machen, WARUM WAS WIE annotiert wurde}
-% Florian hat 2 Regeln falsch verstanden, sonst war übereinstimmung 90-95%
 % Kategorie ``++'' enthält ausnahmesweise auch adverbiale Best. der Zeit.
-% ggf. angeben, dass die effektiv identisch waren
+\todo[inline]{WARUM WAS WIE annotiert wurde}
 \todo[inline]{aus Speech-Anno Paper 'descriptive-statistics-anno.py' übernehmen \& anpassen, um Statistiken und runcommand-file zu erstellen}
-A further annotation of the audio-description's narrator was done manually: Two
-persons performed a categorization of nouns embedded in sentences spoken by the
-narrator to describe the movie's missing visual content.
-Categories focus on the cinematographic scene's environment, inherent objects, persons, and a person's appearance (cf. table \ref{tab:descr-nouns})..
-A categorizing of nouns that serve as auditory cues about the movie's visual content.
-Comprised categories focus on the cinematographic scene's environment (geo, geo-room; setting\_new, setting\_old), inherent persons (female, female name; male, male name, person), their appearance (face, head; body, bodypart), and objects (object, furniture).
-The nouns are categorized by the clue they provide about a cinematographic scene's environment \todo{maybe skip the names and just cite the table} (geo, geo-room; setting\_new, setting\_rec), its inherent persons (female, female name; male, male name, person), a person's appearance (face, head; body, bodypart), and a scene's inherent objects (object, furniture).
-A preliminary annotation according to the rules [entweder im laufenden Text oder in Tabelle], einer neuen Tabelle oder im laufenden Text was done by one person and corrected in several runs by the author.
+We extended a publicly available annotation of speech \citep{haeusler2020speechanno} by manually annotating the audio-description's narrator:
+Two persons performed a categorization of nouns embedded in sentences spoken by the narrator to describe the movie's missing visual content.
+\todo[inline]{Warum wurden diese Kategorien so gewählt}
+\todo[inline]{Maybe just cite the table}
+The nouns were categorized by the clue they provide about the cinematographic scene's environment (geo, geo-room; setting\_new, setting\_old), its inherent persons (female, female name; male, male name, person), a person's appearance (face, head; body, bodypart), and a scene's inherent objects (object, furniture).
+See Table \ref{tab:descr-nouns} for a complete overview of all cateogries, [+++rules, counts, examples].
+
+A preliminary annotation by one person according to the rules [entweder im laufenden Text oder in einer [eigenständigen] Tabelle].
+Minor corrections due to incorrectly applied rules were by the author.
 
@@
 \todo[inline]{irrelevantes kürzen}
-In both studies, stimulation was implemented with PsychoPy v1.79 (with an early version of the MovieStim2 component later to be publicly released with \href{http://www.psychopy.org}{PsychoPy v1.81}; \citep{peirce2007psychopy}) running on a computer with the \href{http://neuro.debian.net}{(Neuro)Debian} operating system \citep{halchenko2012open}.
+In both studies, stimulation was implemented with \href{http://www.psychopy.org}{PsychoPy} \citep{peirce2007psychopy} running on a computer with the \href{http://neuro.debian.net}{(Neuro)Debian} operating system \citep{halchenko2012open}.
 In the AO study, visual instructions were presented on a rear-projection screen inside scanner bore using an LCD projector (DLA-G150CL, JVC Ltd.).
-During the functional scans, the projector presented a medium gray screen with the primary purpose to illuminate a participant’s visual field in order to prevent premature fatigue.
+During the functional scans, the projector presented a medium gray screen with the primary purpose to illuminate a participant's visual field in order to prevent premature fatigue.
 [The screen contained a solid black ``fixation'' dot that faded in and out at the beginning and end of a movie segment.]
-In the AV study, visual instructions and stimuli were presented on a rear-projection screen using an LCD projector (JVC DLA RS66E, JVC Ltd., light transmission reduced to 13.7\% with a gray filter) connected to the stimulus computer [via a DVI extender system (Gefen EXT-DVI-142DLN with EXT-DVI-FM1000).
-The movie was shown at a viewing distance of 63\,cm in 720\,p resolution at full width on a 1280 *1024\,pixel screen with 60\,Hz video refresh rate and screen dimension of 26.5 * 21.2\,cm, corresponding to 23.75*13.5 or 23.75*10.25 when considering only the movie content and excluding the horizontal gray bars].
-In both studies [???] auditory stimulation was delivered through an MR confon mkII+ driving custom-built in-ear headphones (HP-M01, MR confon GmbH, Magdeburg, Germany; \citep{baumgart1998electrodynamic}) that reduced the scanner noise by at least 20–30 dB.
+
+In the AV study, visual instructions and stimuli were presented on a rear-projection screen using an LCD projector (JVC DLA RS66E, JVC Ltd., light transmission reduced to \unit[13.7]{\%} with a gray filter) connected to the stimulus computer [via a DVI extender system (Gefen EXT-DVI-142DLN with EXT-DVI-FM1000).
+The movie was shown at a viewing distance of \unit[63]{cm} in \unit[720]{p} resolution at full width on a \unit[1280 $\times$ 1024]{pixel} screen with \unit[60]{Hz} video refresh rate and screen dimension of \unit[26.5 $\times$ 21.2]{cm}, corresponding to \unit[23.75 $\times$ 13.5] or \unit[23.75 $times$ 10.25]{cm} when considering only the movie content and excluding the horizontal gray bars.
+
+In both studies [+++???+++] auditory stimulation was delivered through an MR confon mkII+ driving custom-built in-ear headphones (HP-M01, MR confon GmbH, Magdeburg, Germany; \citep{baumgart1998electrodynamic}) that reduced the scanner noise by at least \unit[20–30]{dB}.
 Headphones were  fed from an Aureon 7.1 USB (Terratec) sound card through an optical connection.
@@
 \todo[inline]{irrelevantes kürzen}
-In both studies, a total of 3599 volumes were recorded for each participant (451, 441, 438, 488, 462, 439, 542 and 338 volumes for movie segment 1–8 respectively).
-In AO study, a whole-body 7-Tesla Siemens MAGNETOM magnetic resonance scanner equipped with a local circularly polarized head transmit and a 32 channel brain receive coil (Nova Medical, Inc., Wilmington, MA, USA) acquired T2*-weighted echo-planar images (gradient-echo, 2\,s repetition time (TR), 22\,ms echo time, 0.78\,ms echo spacing, 1488\,Hz/Px bandwidth, generalized autocalibrating partially parallel acquisition, acceleration factor 3, 24 Hz/Px bandwidth in phase encoding direction) using 36 axial slices (thickness 1.4\,mm, 1.4 x 1.4\,mm in-plane resolution, 224\,mm field-of-view, anterior-to-posterior phase encoding direction) with a 10 percent inter-slice gap were recorded in ascending order.
+In both studies, a total of 3599 volumes were recorded for each participant (451, 441, 438, 488, 462, 439, 542, and 338 volumes for movie segment 1–8 respectively).
+
+In the AO study, a whole-body \unit[7]{Tesla} Siemens MAGNETOM magnetic resonance scanner equipped with a local circularly polarized head transmit and a 32 channel brain receive coil (Nova Medical, Inc., Wilmington, MA, USA) acquired T2*-weighted echo-planar images
+(gradient-echo, \unit[2]{s} repetition time (TR), \unit[22]{ms} echo time, \unit[0.78]{ms} echo spacing, \unit[1488]{Hz/Px} bandwidth, generalized autocalibrating partially parallel acquisition, acceleration factor 3, \unit[2]{Hz/Px} bandwidth in phase encoding direction) using 36 axial slices (thickness \unit[1.4]{mm}, \unit[1.4 $\times$ 1.4]{mm} in-plane resolution, \unit[224]{mm} field-of-view, anterior-to-posterior phase encoding direction)
+with a 10 percent inter-slice gap were recorded in ascending order.
 Slices were oriented to include the ventral portions of frontal and occipital cortex while minimizing intersection with the eyeballs.
 The field-of-view was centred on the approximate location of Heschl's gyrus.
-[EPI images were online-corrected for motion and geometric distortions [Oh, S.
-et al.
-2012; In, M.
-\& Speck, O., 2012; Chung, J.
-et al., 2011+++].
-Auxiliary scans for slice alignment and motion- and distortion-correction were performed at the beginning of the first fMRI recording session and also after the break at the start of the recording for the second half of the movie].
-In the AV study, a whole-body 3 Tesla Philips Achieva dStream MRI scanner equipped with a 32 channel head coil acquired T2*-weighted echo-planar images (gradient-echo, 2\,s repetition time (TR), 30\,ms echo time, 90 DEGREE flip angle, 1943\,Hz/Px bandwidth, parallel acquisition with sensitivity encoding (SENSE) reduction factor 2).
-35 axial slices (thickness 3.0\,mm, 10\% inter-slice gap) with 80*80 voxels (3.0*3.0 mm of in-plane resolution), 240\,mm mm field-of-view (FoV) and an anterior-to-posterior phase encoding direction were recorded in ascending order.
+[+++EPI images were online-corrected for motion and geometric distortions [Oh, S. et al. 2012; In, M. \& Speck, O., 2012; Chung, J. et al., 2011].
+[Auxiliary scans for slice alignment and motion- and distortion-correction were performed at the beginning of the first fMRI recording session and also after the break at the start of the recording for the second half of the movie].
+
+In the AV study, a whole-body \unit[3]{Tesla} Philips Achieva dStream MRI scanner equipped with a 32 channel head coil acquired T2*-weighted echo-planar images (gradient-echo, \unit[2]{s} repetition time (TR), \unit[30]{ms} echo time, \unit[90]{$^{\circ}$} flip angle, \unit[1943]{Hz/Px} bandwidth, parallel acquisition with sensitivity encoding (SENSE) reduction factor 2).
+35 axial slices (thickness \unit[3.0]{mm}, \unit[10]{\%} inter-slice gap) with \unit[80 $\times$ 80]{voxels} (\unit[3.0 $\times$ 3.0]{mm} of in-plane resolution), \unit[240]{mm} field-of-view ) and an anterior-to-posterior phase encoding direction were recorded in ascending order.
 Philips' ``SmartExam'' was used to automatically position slices in AC-PC orientation such that the topmost slice was located at the superior edge of the brain.
@@
 \subsection{Preprocessing}
-% DATA SOURCE
-\todo[inline]{hier ggf. expliziter erwähnen, dass AO spatially downsampled ist}
-% denoised movie data:
-% https://github.com/OpenNeuroDatasets/ds001769/tree/master/sub-01/ses-movie/func
+% data source
+\todo[inline]{wie immer bzgl. Motion Correction und Registratziohier ggf. expliziter erwähnen, dass AO spatially downsampled ist}
+\todo[inline]{cite sengupta2016 where this was first done and described, ie same image/data was used here}
 fMRI time series data were obtained from
-\href{''https://github.com/psychoinformatics-de/studyforrest-data-aligned''}{GitHub}.
-Data are already aligned to a subject-specific \href{''https://github.com/psychoinformatics-de/studyforrest-data-templatetransforms''}{3 Tesla BOLD template} by a rigid body transformation in MCFLIRT \citep{jenkinson2002registration} to correct for motion during scanning
+\href{https://github.com/psychoinformatics-de/studyforrest-data-aligned}{GitHub}.
+Data are already aligned to a subject-specific \href{https://github.com/psychoinformatics-de/studyforrest-data-templatetransforms}{3 Tesla BOLD template} by a rigid body transformation in MCFLIRT \citep{jenkinson2002registration} to correct for motion during scanning
 \citep{sengupta2016extension}.
 
-\todo[inline]{cite sengupta2016 where this was first done and described, ie same image/data was used here}
-
-All further analysis steps in the current study were carried out using tools of FSL v5.0.9 (\href{''https://www.fmrib.ox.ac.uk/fsl''}{FMRIB's Software Library};\citep{smith2004fsl}; on a computer cluster running the \href{https://www.debian.org}{Debian} GNU/Linux operating system.
+% preprocessing intro
+All further analysis steps in the current study were carried out using tools of FSL v5.0.9 (\href{https://www.fmrib.ox.ac.uk/fsl}{FMRIB's Software Library};\citep{smith2004fsl}; on a computer cluster running the \href{https://www.debian.org}{Debian} GNU/Linux operating system.
 Software packages were obtained from repositories of \href{http://neuro.debian.net}{NeuroDebian} \citep{halchenko2012open}.
 
-% ACTUAL PREPROCESSING
+% actual preprocessing
 Preprocessing (and statistical analysis) was carried out using FEAT v6.00 (FMRI Expert Analysis Tool;\citep{woolrich2001autocorr}) as part of FSL.
-High-pass temporal filtering was applied to every segment using a Gaussian-weighted least-squares straight line with a cutoff period of 150\,s (sigma=75.0\,s) to remove low-frequency confounds.
+High-pass temporal filtering was applied to every segment using a Gaussian-weighted least-squares straight line with a cutoff period of \unit[150]{s} (sigma=\unit[75.0]{s}) to remove low-frequency confounds.
 The brain was extracted from surrounding tissues using BET \citep{smith2002bet}.
-Data were spatially smoothed applying a Gaussian kernel with full width at half maximum (FWHM) of 4.0 mm.
+Data were spatially smoothed applying a Gaussian kernel with full width at half maximum (FWHM) of \unit[4.0]{mm}.
 A grand-mean intensity normalization of the entire 4D dataset was performed by a single multiplicative factor.
-Correction for local autocorrelation in the time series (prewhitening) was applied using FILM (FMRIB’s Improved Linear Model).
+Correction for local autocorrelation in the time series (prewhitening) was applied using FILM (FMRIB's Improved Linear Model).
 
@@
 \midrule
-body & XYleft-right volume difference & rBodyAll & rBodyI & rBodyII & rBodyIII & rBodyIV & rBodyV & rBodyVI & rBodyVII & rBodyVIII \tabularnewline
-
+body & XY & rBodyAll & rBodyI & rBodyII & rBodyIII & rBodyIV & rBodyV & rBodyVI & rBodyVII & rBodyVIII \tabularnewline
 fg\_ad\_lrdiff & left-right volume difference & rFgadlrdiffAll & rFgadlrdiffI & rFgadlrdiffII & rFgadlrdiffIII & rFgadlrdiffIV & rFgadlrdiffV & rFgadlrdiffVI & rFgadlrdiffVII & rFgadlrdiffVIII \tabularnewline
@@
 % die regressoren settinge_new & setting_old aus dem Hörspiel habe ich meiner meinung nach unnötigerweise im Film mit-modelliert; lasse mich da aber auch umstimmen
+
 % -> noch mal reingucken; kamen im Grunde nur "auditorische Areale" als Cluster vor; umgekehrt gab's bei der visuellen Regressoren im Hörbuch keine sign. Cluster
 For the audio-visual stimulus, we categorized the depicted location in the frame following one of the 869 cuts in the movie to built five regressors: 1) unfamiliar setting (US), 2) familiar setting (FS), 3) locale switch (LS), 4) unfamiliar perspective (UP), 5) familiar perspective (FP).
+
 In order to build negative control contrasts, a sixth regressors was created by pseudo-randomly choosing frames present within a shot and apart from a cut.
@@
 An overview and short explanation of the six regressors and the additional nuisance regressors reflecting (auditory and) visual low-level features can be found in Table xy.
+
 For both stimuli, regressors were convolved with a double gamma canonical hemodynamic response function (HRF).
 Their temporal derivatives were added to compensate for small timing differences \citep{friston1998event}.
-Six motion parameters were used as additional nuisance regressors. Finally, designs were filtered with the same high-pass filter (cutoff period of 150\,s) as the BOLD time series.
+Six motion parameters were used as additional nuisance regressors. Finally, designs were filtered with the same high-pass filter (cutoff period of \unit[150]{s}) as the BOLD time series.
 

### 2020-04-30 code/descr-stats-events.py
add file "code/descr-stats-events.py"

@@ -1,0 +1,91 @@
+#!/usr/bin/env python3
+'''
+created on Fri April 30 2020
+author: Christian Olaf Haeusler
+'''
+from glob import glob
+import argparse
+import os.path
+
+
+no2alpha = {0: 'All',
+            1: 'I',
+            2: 'II',
+            3: 'III',
+            4: 'IV',
+            5: 'V',
+            6: 'VI',
+            7: 'VII',
+            8: 'VIII'
+            }
+
+
+def parse_arguments():
+    '''
+    '''
+    parser = argparse.ArgumentParser(
+        description='Counts events in EV3 files for every regressor'
+    )
+    parser.add_argument('-d',
+                        default='./events/onsets/',
+                        help='the directory that contains the segmented annotation')
+
+    parser.add_argument('-o',
+                        default=None,
+                        help='the output file. e.g. ./descr-stats-ao-events.tex')
+
+    args = parser.parse_args()
+
+    inDir = args.d
+    outFile = args.o
+
+    return inDir, outFile
+
+
+if __name__ == "__main__":
+    inDir, outFile = parse_arguments()
+
+    # search for event files in the given directory
+    pattern = os.path.join(inDir, '**/*.txt')
+    fPathes = sorted(glob(pattern, recursive=True))
+
+    if 'aomovie' in inDir:
+        stim = 'ao'
+    elif 'avmovie' in inDir:
+        stim = 'av'
+
+    # get a list of regressors from the event files
+    fileNames = [os.path.basename(path) for path in fPathes]
+    regressors = [os.path.splitext(fileName)[0] for fileName in fileNames]
+    regressors = sorted(list(set(regressors)))
+
+    toWrite = []
+    for regressor in regressors:
+        # filter list of all event files for the current loop's regressor
+        pattern = '/%s.txt' % regressor
+        regFiles = [ev3File for ev3File in fPathes if pattern in ev3File]
+
+        # count the lines (=events) per file/run
+        eventsPerRun = []
+        for regFile in regFiles:
+            noOfEvents = sum(1 for eventsPerRun in open(regFile))
+            eventsPerRun.append(noOfEvents)
+
+        # put the count for all events at the beginning of the list
+        eventsPerRun.insert(0, sum(eventsPerRun))
+
+        # build the lines for the current regressor to write to file
+        for run, count in enumerate(eventsPerRun):
+            regressor = regressor.capitalize()
+            run = no2alpha[run]
[…]

### 2020-04-30 paper/main.tex
Makefile & manuscript work with newcommand tex-files
add table for AO events

@@
 \begin{document}
-%\input{descr-stats-ao-events.tex}
-%\input{descr-stats-av-events.tex}
+\input{descr-stats-ao-events.tex}
+\input{descr-stats-av-events.tex}
 
@@
 
-A preliminary annotation by one person according to the rules [entweder im laufenden Text oder in einer [eigenständigen] Tabelle].
+A preliminary annotation was performed by one person according to the rules (see Table XYZ).
 Minor corrections due to incorrectly applied rules were by the author.
@@
 \paragraph{Regressors}
-We used an annotation of movie cuts and depicted locations \citep{haeusler2016cutanno} and an annotation of speech \citep{haeusler2020speechanno} to create the FSL event files resp. regressors.
-First, both annotations were split via \href{"https://github.com/chrhaeusler/studyforrest-data-annotations/blob/master/code/researchcut2segments.py"}{python script} into eight parts corresponding to the eight segments used as stimuli during fMRI scanning.
+\todo[inline]{cross reference to fig:reg-corr}
+We used an annotation of movie cuts and depicted locations \citep{haeusler2016cutanno}, and an annotation of speech \citep{haeusler2020speechanno} to create event files for FSL.
+% https://github.com/psychoinformatics-de/studyforrest-data-annotations/blob/master/code/researchcut2segments.py}
+First, both annotations were split into eight parts corresponding to the eight segments used as stimuli during fMRI scanning.
 \todo[inline]{wenn ich folgend den "null regressor" nehme, darf ich den ganzen Run, glaube ich, in der 2nd level Analyse gar nicht benutzen??}
-For the AO stimulus, we used the narrator's ``descriptive nouns'' (cf. table \ref{tab:descr-nouns}.
-We created 11 regressors from the XY (selected?) original categories by joining / merging some categories (female, females, fname; male, males, mname; face, head) into one regressor (sex\_f; sex\_m; fahead).
+For the AO stimulus, we used the narrator's ``descriptive nouns'' (see Table \ref{tab:descr-nouns}.
 
-\todo[inline]{cross reference to fig:reg-corr}
+\todo[inline]{some categories were pooled, because\dots}
 
+XY from the XY original categories were selected [+++why?+++], and some were pooled  original categories by joining / merging some categories resulting in 11 new categories.
+
+\todo[inline]{make clear which stimulus each annotation is based on, and make clear(er) what defined an event. This could be a big table, because good defintions are important for judging the results}
 \begin{table*}[t]
-    \caption{Overview of the events to build the 18 regressors for analysis of the AO stimulus. The first column contains the number of the regressor in the design file of FSL \citep{smith2004fsl}.
-''fg\_ad\_lrdiff (left-right volume difference) and ``fg\_ad\_rms'' (root mean square loudness) represent low-level auditory nuissance regressors comprising one event for every movie frame (40ms).}
-\label{tab:regressors}
+    \caption{Overview of events to build the 18 regressors for the analysis of the audio-only (AO) stimulus.
+Some of the original categories (female, females, fname; male, males, mname; face, head; see Table \ref{tab:descr-nouns}) were pooled into new categories (sex\_f; sex\_m; fahead)
+\texttt{fg\_ad\_lrdiff} (left-right volume difference) and \texttt{fg\_ad\_rms} (root mean square volume) represent one event for every movie frame (\unit[40]{ms}).}
+\label{tab:ao-events}
 \footnotesize
@@
 \midrule
-body & XY & rBodyAll & rBodyI & rBodyII & rBodyIII & rBodyIV & rBodyV & rBodyVI & rBodyVII & rBodyVIII \tabularnewline
-fg\_ad\_lrdiff & left-right volume difference & rFgadlrdiffAll & rFgadlrdiffI & rFgadlrdiffII & rFgadlrdiffIII & rFgadlrdiffIV & rFgadlrdiffV & rFgadlrdiffVI & rFgadlrdiffVII & rFgadlrdiffVIII \tabularnewline
-fg\_ad\_rms & root mean square & rFgadrmsAll & rFgadrmsI & rFgadrmsII & rFgadrmsIII & rFgadrmsIV & rFgadrmsV & rFgadrmsVI & rFgadrmsVII & rFgadrmsVIII \tabularnewline
+body & descr & \aoBodyAll & \aoBodyI & \aoBodyII & \aoBodyIII & \aoBodyIV & \aoBodyV & \aoBodyVI & \aoBodyVII & \aoBodyVIII \tabularnewline
+bpart & descr & \aoBpartAll & \aoBpartI & \aoBpartII & \aoBpartIII & \aoBpartIV & \aoBpartV & \aoBpartVI & \aoBpartVII & \aoBpartVIII \tabularnewline
+fahead & descr & \aoFaheadAll & \aoFaheadI & \aoFaheadII & \aoFaheadIII & \aoFaheadIV & \aoFaheadV & \aoFaheadVI & \aoFaheadVII & \aoFaheadVIII \tabularnewline
+furn & descr & \aoFurnAll & \aoFurnI & \aoFurnII & \aoFurnIII & \aoFurnIV & \aoFurnV & \aoFurnVI & \aoFurnVII & \aoFurnVIII \tabularnewline
+geo & descr & \aoGeoAll & \aoGeoI & \aoGeoII & \aoGeoIII & \aoGeoIV & \aoGeoV & \aoGeoVI & \aoGeoVII & \aoGeoVIII \tabularnewline
+groom & descr & \aoGroomAll & \aoGroomI & \aoGroomII & \aoGroomIII & \aoGroomIV & \aoGroomV & \aoGroomVI & \aoGroomVII & \aoGroomVIII \tabularnewline
+object & descr & \aoObjAll & \aoObjI & \aoObjII & \aoObjIII & \aoObjIV & \aoObjV & \aoObjVI & \aoObjVII & \aoObjVIII \tabularnewline
+se\_new & descr & \aoSenewAll & \aoSenewI & \aoSenewII & \aoSenewIII & \aoSenewIV & \aoSenewV & \aoSenewVI & \aoSenewVII & \aoSenewVIII \tabularnewline
+se\_old & descr & \aoSeoldAll & \aoSeoldI & \aoSeoldII & \aoSeoldIII & \aoSeoldIV & \aoSeoldV & \aoSeoldVI & \aoSeoldVII & \aoSeoldVIII \tabularnewline
+sex\_f & descr & \aoSexfAll & \aoSexfI & \aoSexfII & \aoSexfIII & \aoSexfIV & \aoSexfV & \aoSexfVI & \aoSexfVII & \aoSexfVIII \tabularnewline
+sex\_m & descr & \aoSexmAll & \aoSexmI & \aoSexmII & \aoSexmIII & \aoSexmIV & \aoSexmV & \aoSexmVI & \aoSexmVII & \aoSexmVIII \tabularnewline
+sex\_u & descr & \aoSexuAll & \aoSexuI & \aoSexuII & \aoSexuIII & \aoSexuIV & \aoSexuV & \aoSexuVI & \aoSexuVII & \aoSexuVIII \tabularnewline
+% vlo_ch has no events in segment 5. So indices are shifted
+vlo\_ch & descr & \aoVlochAll & \aoVlochI & \aoVlochII & \aoVlochIII & \aoVlochIV & 0 & \aoVlochV & \aoVlochVI & \aoVlochVII \tabularnewline
+vno\_cut & descr & \aoVnocutAll & \aoVnocutI & \aoVnocutII & \aoVnocutIII & \aoVnocutIV & \aoVnocutV & \aoVnocutVI & \aoVnocutVII & \aoVnocutVIII \tabularnewline
+vpe\_new & descr & \aoVpenewAll & \aoVpenewI & \aoVpenewII & \aoVpenewIII & \aoVpenewIV & \aoVpenewV & \aoVpenewVI & \aoVpenewVII & \aoVpenewVIII \tabularnewline
+% vpe_old has no events in 3. So the indices are shifted
+vpe\_old & descr & \aoVpeoldAll & \aoVpeoldI & \aoVpeoldII & 0 & \aoVpeoldIII & \aoVpeoldIV & \aoVpeoldV & \aoVpeoldVI & \aoVpeoldVII \tabularnewline
+vse\_new & descr & \aoVsenewAll & \aoVsenewI & \aoVsenewII & \aoVsenewIII & \aoVsenewIV & \aoVsenewV & \aoVsenewVI & \aoVsenewVII & \aoVsenewVIII \tabularnewline
+vse\_old & descr & \aoVseoldAll & \aoVseoldI & \aoVseoldII & \aoVseoldIII & \aoVseoldIV & \aoVseoldV & \aoVseoldVI & \aoVseoldVII & \aoVseoldVIII \tabularnewline
+fg\_ad\_lrdiff & left-right volume difference & \aoFgadlrdiffAll & \aoFgadlrdiffI & \aoFgadlrdiffII & \aoFgadlrdiffIII & \aoFgadlrdiffIV & \aoFgadlrdiffV & \aoFgadlrdiffVI & \aoFgadlrdiffVII & \aoFgadlrdiffVIII \tabularnewline
+fg\_ad\_rms & root mean square & \aoFgadrmsAll & \aoFgadrmsI & \aoFgadrmsII & \aoFgadrmsIII & \aoFgadrmsIV & \aoFgadrmsV & \aoFgadrmsVI & \aoFgadrmsVII & \aoFgadrmsVIII \tabularnewline
 \bottomrule
@@
 
-% over length of each noun
-The regressors were modeled as boxcar functions at the end of each noun with a duration of 200 ms.
-If a segment did not contain a single event for a specific regressor, a null regressor was chosen for that segment.
-Five regressors related to the cinematographic cuts (s. below) were added to built contrasts of cross-modal negative control.
-Two regressors reflecting auditory (low-level) features (left-right loudness volume / amplitude???
-difference; root mean squared amplitude) aligned to the frame rate of (40\,ms) were modeled to reduce nuisance effects.
-An overview and short explanation of the 11 regressors and 5 + 2 additional nuisance regressors can be found in Table xy.
-% entgegen der Masterarbeit kommen hier für den Film keine Abbildungen zur Verdeutlichung, weniger Text; no cut erkläre ich nicht lang & breit
-% die regressoren settinge_new & setting_old aus dem Hörspiel habe ich meiner meinung nach unnötigerweise im Film mit-modelliert; lasse mich da aber auch umstimmen
-
-% -> noch mal reingucken; kamen im Grunde nur "auditorische Areale" als Cluster vor; umgekehrt gab's bei der visuellen Regressoren im Hörbuch keine sign. Cluster
-For the audio-visual stimulus, we categorized the depicted location in the frame following one of the 869 cuts in the movie to built five regressors: 1) unfamiliar setting (US), 2) familiar setting (FS), 3) locale switch (LS), 4) unfamiliar perspective (UP), 5) familiar perspective (FP).
-
-In order to build negative control contrasts, a sixth regressors was created by pseudo-randomly choosing frames present within a shot and apart from a cut.
-Regressors were modeled as boxcar function lasting 200\,ms after a cut.
-An overview and short explanation of the six regressors and the additional nuisance regressors reflecting (auditory and) visual low-level features can be found in Table xy.
-
-For both stimuli, regressors were convolved with a double gamma canonical hemodynamic response function (HRF).
-Their temporal derivatives were added to compensate for small timing differences \citep{friston1998event}.
-Six motion parameters were used as additional nuisance regressors. Finally, designs were filtered with the same high-pass filter (cutoff period of \unit[150]{s}) as the BOLD time series.
-
 \begin{table*}
-\caption{Regressors used in the analysis of the audio-description.
-\todo[inline]{make clear which stimulus each annotation is based on, and make clear(er) what defined an event.
-This could be a big table, because good defintions are important for judging the results}}
+\caption{Regressors used in the analysis of the audio-description.}
 \begin{tabular}{lll}
@@
 \end{table*}
+% over length of each noun
+The regressors were modeled as boxcar functions at the end of each noun with a duration of 200 ms.
+If a segment did not contain a single event for a specific regressor, a null regressor was chosen for that segment.
+Five regressors related to the cinematographic cuts (s. below) were added to built contrasts of cross-modal negative control.
+Two regressors reflecting auditory (low-level) features (left-right loudness volume / amplitude???
+difference; root mean squared amplitude) aligned to the frame rate of (40\,ms) were modeled to reduce nuisance effects.
+An overview and short explanation of the 11 regressors and 5 + 2 additional nuisance regressors can be found in Table xy.
+% entgegen der Masterarbeit kommen hier für den Film keine Abbildungen zur Verdeutlichung, weniger Text; no cut erkläre ich nicht lang & breit
+% die regressoren settinge_new & setting_old aus dem Hörspiel habe ich meiner meinung nach unnötigerweise im Film mit-modelliert; lasse mich da aber auch umstimmen
+
+% -> noch mal reingucken; kamen im Grunde nur "auditorische Areale" als Cluster vor; umgekehrt gab's bei der visuellen Regressoren im Hörbuch keine sign. Cluster
+For the audio-visual stimulus, we categorized the depicted location in the frame following one of the 869 cuts in the movie to built five regressors: 1) unfamiliar setting (US), 2) familiar setting (FS), 3) locale switch (LS), 4) unfamiliar perspective (UP), 5) familiar perspective (FP).
+
+In order to build negative control contrasts, a sixth regressors was created by pseudo-randomly choosing frames present within a shot and apart from a cut.
+Regressors were modeled as boxcar function lasting 200\,ms after a cut.
+An overview and short explanation of the six regressors and the additional nuisance regressors reflecting (auditory and) visual low-level features can be found in Table xy.
+
+For both stimuli, regressors were convolved with a double gamma canonical hemodynamic response function (HRF).
+Their temporal derivatives were added to compensate for small timing differences \citep{friston1998event}.
+Six motion parameters were used as additional nuisance regressors. Finally, designs were filtered with the same high-pass filter (cutoff period of \unit[150]{s}) as the BOLD time series.
 

### 2020-05-02 paper/main.tex
revise table of AO events

@@
     \caption{Overview of events to build the 18 regressors for the analysis of the audio-only (AO) stimulus.
-Some of the original categories (female, females, fname; male, males, mname; face, head; see Table \ref{tab:descr-nouns}) were pooled into new categories (sex\_f; sex\_m; fahead)
+Some of the original categories (female, females, fname; male, males, mname; face, head; object, objects; see Table \ref{tab:descr-nouns}) were pooled into new categories (sex\_f; sex\_m; fahead; object)
 \texttt{fg\_ad\_lrdiff} (left-right volume difference) and \texttt{fg\_ad\_rms} (root mean square volume) represent one event for every movie frame (\unit[40]{ms}).}
@@
 \midrule
-body & descr & \aoBodyAll & \aoBodyI & \aoBodyII & \aoBodyIII & \aoBodyIV & \aoBodyV & \aoBodyVI & \aoBodyVII & \aoBodyVIII \tabularnewline
-bpart & descr & \aoBpartAll & \aoBpartI & \aoBpartII & \aoBpartIII & \aoBpartIV & \aoBpartV & \aoBpartVI & \aoBpartVII & \aoBpartVIII \tabularnewline
-fahead & descr & \aoFaheadAll & \aoFaheadI & \aoFaheadII & \aoFaheadIII & \aoFaheadIV & \aoFaheadV & \aoFaheadVI & \aoFaheadVII & \aoFaheadVIII \tabularnewline
-furn & descr & \aoFurnAll & \aoFurnI & \aoFurnII & \aoFurnIII & \aoFurnIV & \aoFurnV & \aoFurnVI & \aoFurnVII & \aoFurnVIII \tabularnewline
-geo & descr & \aoGeoAll & \aoGeoI & \aoGeoII & \aoGeoIII & \aoGeoIV & \aoGeoV & \aoGeoVI & \aoGeoVII & \aoGeoVIII \tabularnewline
-groom & descr & \aoGroomAll & \aoGroomI & \aoGroomII & \aoGroomIII & \aoGroomIV & \aoGroomV & \aoGroomVI & \aoGroomVII & \aoGroomVIII \tabularnewline
-object & descr & \aoObjAll & \aoObjI & \aoObjII & \aoObjIII & \aoObjIV & \aoObjV & \aoObjVI & \aoObjVII & \aoObjVIII \tabularnewline
-se\_new & descr & \aoSenewAll & \aoSenewI & \aoSenewII & \aoSenewIII & \aoSenewIV & \aoSenewV & \aoSenewVI & \aoSenewVII & \aoSenewVIII \tabularnewline
-se\_old & descr & \aoSeoldAll & \aoSeoldI & \aoSeoldII & \aoSeoldIII & \aoSeoldIV & \aoSeoldV & \aoSeoldVI & \aoSeoldVII & \aoSeoldVIII \tabularnewline
-sex\_f & descr & \aoSexfAll & \aoSexfI & \aoSexfII & \aoSexfIII & \aoSexfIV & \aoSexfV & \aoSexfVI & \aoSexfVII & \aoSexfVIII \tabularnewline
-sex\_m & descr & \aoSexmAll & \aoSexmI & \aoSexmII & \aoSexmIII & \aoSexmIV & \aoSexmV & \aoSexmVI & \aoSexmVII & \aoSexmVIII \tabularnewline
-sex\_u & descr & \aoSexuAll & \aoSexuI & \aoSexuII & \aoSexuIII & \aoSexuIV & \aoSexuV & \aoSexuVI & \aoSexuVII & \aoSexuVIII \tabularnewline
+body & trunk of the body or overlaid clothes & \aoBodyAll & \aoBodyI & \aoBodyII & \aoBodyIII & \aoBodyIV & \aoBodyV & \aoBodyVI & \aoBodyVII & \aoBodyVIII \tabularnewline
+bpart & limbs and trousers & \aoBpartAll & \aoBpartI & \aoBpartII & \aoBpartIII & \aoBpartIV & \aoBpartV & \aoBpartVI & \aoBpartVII & \aoBpartVIII \tabularnewline
+fahead & face(parts) or head(parts) & \aoFaheadAll & \aoFaheadI & \aoFaheadII & \aoFaheadIII & \aoFaheadIV & \aoFaheadV & \aoFaheadVI & \aoFaheadVII & \aoFaheadVIII \tabularnewline
+furn & big inventory of rooms (insides/outsides) & \aoFurnAll & \aoFurnI & \aoFurnII & \aoFurnIII & \aoFurnIV & \aoFurnV & \aoFurnVI & \aoFurnVII & \aoFurnVIII \tabularnewline
+geo & immobile landmarks & \aoGeoAll & \aoGeoI & \aoGeoII & \aoGeoIII & \aoGeoIV & \aoGeoV & \aoGeoVI & \aoGeoVII & \aoGeoVIII \tabularnewline
+groom & elements defining a locale's spatial layout & \aoGroomAll & \aoGroomI & \aoGroomII & \aoGroomIII & \aoGroomIV & \aoGroomV & \aoGroomVI & \aoGroomVII & \aoGroomVIII \tabularnewline
+object & inanimate entities with firm boundaries & \aoObjAll & \aoObjI & \aoObjII & \aoObjIII & \aoObjIV & \aoObjV & \aoObjVI & \aoObjVII & \aoObjVIII \tabularnewline
+se\_new & first-time mentioned setting & \aoSenewAll & \aoSenewI & \aoSenewII & \aoSenewIII & \aoSenewIV & \aoSenewV & \aoSenewVI & \aoSenewVII & \aoSenewVIII \tabularnewline
+se\_old & recurring setting & \aoSeoldAll & \aoSeoldI & \aoSeoldII & \aoSeoldIII & \aoSeoldIV & \aoSeoldV & \aoSeoldVI & \aoSeoldVII & \aoSeoldVIII \tabularnewline
+sex\_f & female person(s), name & \aoSexfAll & \aoSexfI & \aoSexfII & \aoSexfIII & \aoSexfIV & \aoSexfV & \aoSexfVI & \aoSexfVII & \aoSexfVIII \tabularnewline
+sex\_m & male person(s), name & \aoSexmAll & \aoSexmI & \aoSexmII & \aoSexmIII & \aoSexmIV & \aoSexmV & \aoSexmVI & \aoSexmVII & \aoSexmVIII \tabularnewline
+sex\_u & person(s) of unknown sex & \aoSexuAll & \aoSexuI & \aoSexuII & \aoSexuIII & \aoSexuIV & \aoSexuV & \aoSexuVI & \aoSexuVII & \aoSexuVIII \tabularnewline
 % vlo_ch has no events in segment 5. So indices are shifted
-vlo\_ch & descr & \aoVlochAll & \aoVlochI & \aoVlochII & \aoVlochIII & \aoVlochIV & 0 & \aoVlochV & \aoVlochVI & \aoVlochVII \tabularnewline
-vno\_cut & descr & \aoVnocutAll & \aoVnocutI & \aoVnocutII & \aoVnocutIII & \aoVnocutIV & \aoVnocutV & \aoVnocutVI & \aoVnocutVII & \aoVnocutVIII \tabularnewline
-vpe\_new & descr & \aoVpenewAll & \aoVpenewI & \aoVpenewII & \aoVpenewIII & \aoVpenewIV & \aoVpenewV & \aoVpenewVI & \aoVpenewVII & \aoVpenewVIII \tabularnewline
+vse\_new & control for movie cut & \aoVsenewAll & \aoVsenewI & \aoVsenewII & \aoVsenewIII & \aoVsenewIV & \aoVsenewV & \aoVsenewVI & \aoVsenewVII & \aoVsenewVIII \tabularnewline
+vse\_old & control for movie cut & \aoVseoldAll & \aoVseoldI & \aoVseoldII & \aoVseoldIII & \aoVseoldIV & \aoVseoldV & \aoVseoldVI & \aoVseoldVII & \aoVseoldVIII \tabularnewline
+vlo\_ch & control for movie cut & \aoVlochAll & \aoVlochI & \aoVlochII & \aoVlochIII & \aoVlochIV & 0 & \aoVlochV & \aoVlochVI & \aoVlochVII \tabularnewline
+vpe\_new & control for movie cut & \aoVpenewAll & \aoVpenewI & \aoVpenewII & \aoVpenewIII & \aoVpenewIV & \aoVpenewV & \aoVpenewVI & \aoVpenewVII & \aoVpenewVIII \tabularnewline
 % vpe_old has no events in 3. So the indices are shifted
-vpe\_old & descr & \aoVpeoldAll & \aoVpeoldI & \aoVpeoldII & 0 & \aoVpeoldIII & \aoVpeoldIV & \aoVpeoldV & \aoVpeoldVI & \aoVpeoldVII \tabularnewline
-vse\_new & descr & \aoVsenewAll & \aoVsenewI & \aoVsenewII & \aoVsenewIII & \aoVsenewIV & \aoVsenewV & \aoVsenewVI & \aoVsenewVII & \aoVsenewVIII \tabularnewline
-vse\_old & descr & \aoVseoldAll & \aoVseoldI & \aoVseoldII & \aoVseoldIII & \aoVseoldIV & \aoVseoldV & \aoVseoldVI & \aoVseoldVII & \aoVseoldVIII \tabularnewline
+vpe\_old & control for movie cut & \aoVpeoldAll & \aoVpeoldI & \aoVpeoldII & 0 & \aoVpeoldIII & \aoVpeoldIV & \aoVpeoldV & \aoVpeoldVI & \aoVpeoldVII \tabularnewline
 fg\_ad\_lrdiff & left-right volume difference & \aoFgadlrdiffAll & \aoFgadlrdiffI & \aoFgadlrdiffII & \aoFgadlrdiffIII & \aoFgadlrdiffIV & \aoFgadlrdiffV & \aoFgadlrdiffVI & \aoFgadlrdiffVII & \aoFgadlrdiffVIII \tabularnewline
-fg\_ad\_rms & root mean square & \aoFgadrmsAll & \aoFgadrmsI & \aoFgadrmsII & \aoFgadrmsIII & \aoFgadrmsIV & \aoFgadrmsV & \aoFgadrmsVI & \aoFgadrmsVII & \aoFgadrmsVIII \tabularnewline
-\bottomrule
-\end{tabular}
-\end{table*}
-
-\begin{table*}
-\caption{Regressors used in the analysis of the audio-description.}
-\begin{tabular}{lll}
-\toprule
-\textbf{name} & \textbf{count} & \textbf{description} \\
-\midrule
-body & 66 & trunk of the body or overlaid clothes \\
-bpart & 69 & limbs and trousers \\
-facehead & 83 & face(parts) or head(parts) \\
-furniture & 50 & big inventory of rooms (insides/outsides) \\
-geo & 125 & immobile landmarks \\
-geo-room & 105 & elements defining a locale's spatial layout \\
-setting\_new & 86 & first-time mentioned setting \\
-setting\_old & 37 & recurring setting \\
-object & 284 & inanimate entities with firm boundaries \\
-sex\_f & 108 & female person(s), name \\
-sex\_m & 403 & male person(s), name \\
-vse\_new & 96 & control for movie cuts; s. table y \\
-vse\_old & 90 & control for movie cuts; s. table y \\
-vloc\_change & 89 & control for movie cuts; s. table y \\
-vpe\_new & 386 & control for movie cuts; s. table y \\
-vpe\_old & 208 & control for movie cuts; s. table y \\
-fg\_ad\_lrdiff & xx &  left-right volume difference \\
-fg\_ad\_rms & xx & root mean square amplitude \\
+fg\_ad\_rms & root mean square loudness & \aoFgadrmsAll & \aoFgadrmsI & \aoFgadrmsII & \aoFgadrmsIII & \aoFgadrmsIV & \aoFgadrmsV & \aoFgadrmsVI & \aoFgadrmsVII & \aoFgadrmsVIII \tabularnewline
 \bottomrule

### 2020-05-02 paper/main.tex
add table for AV events

@@
 \caption{Overview of events to build the 18 regressors for the analysis of the audio-only (AO) stimulus.
-Some of the original categories (female, females, fname; male, males, mname; face, head; object, objects; see Table \ref{tab:descr-nouns}) were pooled into new categories (sex\_f; sex\_m; fahead; object)
-\texttt{fg\_ad\_lrdiff} (left-right volume difference) and \texttt{fg\_ad\_rms} (root mean square volume) represent one event for every movie frame (\unit[40]{ms}).}
+Some of the original categories (female, females, fname; male, males, mname; face, head; object, objects; see Table \ref{tab:descr-nouns}) were pooled into new categories (sex\_f; sex\_m; fahead; object).
+\texttt{fg\_ad\_lrdiff} (left-right volume difference) and
+\texttt{fg\_ad\_rms} (root mean square volume) represent one event for every movie frame (\unit[40]{ms}).
+For description of control condition for movie cuts see Table \ref{tab:av-events}}
 \label{tab:ao-events}
@@
 
-\begin{table*}
-\caption{Regressors used in the analysis of the movie.}
-\begin{tabular}{lll}
+\begin{table*}[t]
+    \caption{Overview of events to build the 14 regressors for the analysis of the audio-only (AV) stimulus.
+\texttt{fg\_av\_ger\_lr} (left-right difference in ??? of consecutive movie frame).
+\texttt{fg\_av\_ger\_pd} (perceptual differences of consecutive frames).
+\texttt{fg\_av\_ger\_ud} (up-down difference in ??? of consecutive movie frames).
+\texttt{fg\_av\_ger\_lrdiff} (left-right volume difference) and \texttt{fg\_av\_ger\_rms} (root mean square volume) represent one event for every movie frame (\unit[40]{ms}).
+For description of control condition for movie cuts see Table \ref{tab:ao-events}}
+\label{tab:av-events}
+\footnotesize
+\begin{tabular}{lp{3.5cm}lllllllll}
 \toprule
-\textbf{name} & \textbf{count} & \textbf{description} \\
+\textbf{label} &  \textbf{description} & \textbf{all} & \textbf{1} & \textbf{2} & \textbf{3} & \textbf{4} & \textbf{5} & \textbf{6} & \textbf{7} & \textbf{8} \\
 \midrule
-vse\_new & 96 & change of the camera position to a setting not depicted before \\
-vse\_old & 90 & change of the camera position to a recurring setting \\
-vloc\_change & 89 & change of the camera position to another locale within the same setting \\
-vpe\_new & 386 & change of the camera position within a locale not depicted before \\
-vpe\_old & 208 & change of the camera position within a recurring locale \\
-no\_cut & 148 & a continuous frame from the same camera position \\
-se\_new & 148 & audio-description's narrator; s. table x; KANN RAUS? \\
-se\_old & 148 & audio-description's narrator; s. table x; KANN RAUS? \\
-fg\_av\_ger\_lr & xx & left right +++???+++ in movie frame  \\
-fg\_av\_ger\_lrdiff & xx & left-right volume difference \\
-fg\_av\_ger\_pd & xx & perceptual differences of consecutive frames \\
-fg\_av\_ger\_rms & xx & root mean square amplitude \\
-fg\_av\_ger\_ud & xx & +++up down???+++ \\
-\bottomrule
+vse\_new &  change of the camera position to a setting not depicted before & \aoVsenewAll & \aoVsenewI & \aoVsenewII & \aoVsenewIII & \aoVsenewIV & \aoVsenewV & \aoVsenewVI & \aoVsenewVII & \aoVsenewVIII \tabularnewline
+vse\_old & change of the camera position to a recurring setting & \aoVseoldAll & \aoVseoldI & \aoVseoldII & \aoVseoldIII & \aoVseoldIV & \aoVseoldV & \aoVseoldVI & \aoVseoldVII & \aoVseoldVIII \tabularnewline
+vlo\_ch & change of the camera position to another locale within the same setting & \aoVlochAll & \aoVlochI & \aoVlochII & \aoVlochIII & \aoVlochIV & 0 & \aoVlochV & \aoVlochVI & \aoVlochVII \tabularnewline
+vpe\_new & change of the camera position within a locale not depicted before & \aoVpenewAll & \aoVpenewI & \aoVpenewII & \aoVpenewIII & \aoVpenewIV & \aoVpenewV & \aoVpenewVI & \aoVpenewVII & \aoVpenewVIII \tabularnewline
+% vpe_old has no events in 3. So the indices are shifted
+vpe\_old & change of the camera position within a recurring locale & \aoVpeoldAll & \aoVpeoldI & \aoVpeoldII & 0 & \aoVpeoldIII & \aoVpeoldIV & \aoVpeoldV & \aoVpeoldVI & \aoVpeoldVII \tabularnewline
+vno\_cut & a continuous frame from the same camera position & \avVnocutAll & \avVnocutI & \avVnocutII & 0 & \avVnocutIII & \avVnocutIV & \avVnocutV & \avVnocutVI & \avVnocutVII \tabularnewline
+se\_new & control for AO narrator & \aoSenewAll & \aoSenewI & \aoSenewII & \aoSenewIII & \aoSenewIV & \aoSenewV & \aoSenewVI & \aoSenewVII & \aoSenewVIII \tabularnewline
+se\_old & control for AO narrator & \aoSeoldAll & \aoSeoldI & \aoSeoldII & \aoSeoldIII & \aoSeoldIV & \aoSeoldV & \aoSeoldVI & \aoSeoldVII & \aoSeoldVIII \tabularnewline
+fg\_av\_ger\_lr & XYZ & \avFgavgerlrAll & \avFgavgerlrI & \avFgavgerlrII & \avFgavgerlrIII & \avFgavgerlrIV & \avFgavgerlrV & \avFgavgerlrVI & \avFgavgerlrVII & \avFgavgerlrVIII \tabularnewline
+fg\_av\_ger\_lrdiff & XYZ & \avFgavgerlrdiffAll & \avFgavgerlrdiffI & \avFgavgerlrdiffII & \avFgavgerlrdiffIII & \avFgavgerlrdiffIV & \avFgavgerlrdiffV & \avFgavgerlrdiffVI & \avFgavgerlrdiffVII & \avFgavgerlrdiffVIII \tabularnewline
+fg\_av\_ger\_ml & XYZ & \avFgavgermlAll & \avFgavgermlI & \avFgavgermlII & \avFgavgermlIII & \avFgavgermlIV & \avFgavgermlV & \avFgavgermlVI & \avFgavgermlVII & \avFgavgermlVIII \tabularnewline
+fg\_av\_ger\_pd & XYZ & \avFgavgerpdAll & \avFgavgerpdI & \avFgavgerpdII & \avFgavgerpdIII & \avFgavgerpdIV & \avFgavgerpdV & \avFgavgerpdVI & \avFgavgerpdVII & \avFgavgerpdVIII \tabularnewline
+fg\_av\_ger\_rms & XYZ & \avFgavgerrmsAll & \avFgavgerrmsI & \avFgavgerrmsII & \avFgavgerrmsIII & \avFgavgerrmsIV & \avFgavgerrmsV & \avFgavgerrmsVI & \avFgavgerrmsVII & \avFgavgerrmsVIII \tabularnewline
+fg\_av\_ger\_ud & XYZ & \avFgavgerudAll & \avFgavgerudI & \avFgavgerudII & \avFgavgerudIII & \avFgavgerudIV & \avFgavgerudV & \avFgavgerudVI & \avFgavgerudVII & \avFgavgerudVIII \tabularnewline
 \end{tabular}
 \end{table*}
+
 % over length of each noun
@@
 \end{document}
+\documentclass[english]{article}

### 2020-05-02 paper/main.tex
add table for AO COPEs

@@
 
-\begin{table*}
-\caption{Contrasts of parameter estimates for the analysis of the audio-description.}
-% das sind die zusammengefassten Kurzversionen, d.h. nicht alle Regressoren sind explizit in dem COPEs ausformuliert
+\begin{table*}[t]
+\caption{Contrasts of parameter estimates for the analysis of the audio-description.
+\texttt{all non-geo} = all non-geo related regressors except furniture.}
+\label{tab:ao-contrasts}
+\footnotesize
 \begin{tabular}{lll}
 \toprule
-\textbf{COPE nr.} & \textbf{description} & \textbf{aim} \\
+\textbf{nr.} &  \textbf{contrasted} & \textbf{aim/goal} \\
 \midrule
-1 & geo, rgeo, se\_new, se\_old > non\_geo & PPA \\
-2 & geo, rgeo, se\_new > non\_geo & PPA \\
-3 & geo, rgeo > non\_geo & PPA <<-- THE COOL \\
-4 & geo > non\_geo & PPA \\
-5 & se\_new > non\_geo & PPA \\
-6 & se\_new, se\_old > non\_geo & PPA \\
-7 & se\_new > se\_old & PPA \\
-8 & body > all\_others (excl. bpart) & EBA \\
-9 & body, bpart > all\_others & EBA \\
-10 & body > non\_persons (excl. bpart) & EBA \\
-11 & body, bpart > non\_persons & EBA \\
-12 & body, bpart > non\_persons (excl. faHead) & EBA \\
-13 & fahead > all\_others & FFA \\
-14 & fahead > all\_others (excl. body/parts) & FFA \\
-15 & fahead > non\_persons & FFA \\
-16 & fahead > non\_persons (excl. body/parts) & FFA \\
-17 & obj > all\_others & LOC \\
-18 & obj > all\_others (excl. fahead) & LOC \\
-19 & obj > all\_others (excl. fahead, rgeo) & LOC \\
-20 & obj > persons & LOC \\
-21 & se\_old > se\_new & DMN \\
-22 & se\_old > non\_settings & DMN \\
-23 & se\_old > non\_geo & DMN \\
-24 & female > male & ??? \\
-25 & male > female & ??? \\
-26 & persons > non\_persons (excl. body/parts) & ??? \\
-27 & non\_persons (excl. body/parts) > persons & ??? \\
-28 & se\_new > se\_old & visual contr. \\
-29 & pe\_new > pe\_old & visual contr. \\
-30 & se\_new, pe\_new > se\_old, pe\_old & visual contr. \\
-31 & se\_new > pe\_old & visual contr. \\
-32 & se\_new > se\_old, pe\_old & visual contr. \\
-33 & se\_new, pe\_new > pe\_old & visual contr. \\
-34 & se\_old > se\_new & DMN  contr. \\
-35 & pe\_old > pe\_new &  DMN contr. \\
-36 & no\_cut > pe\_new, pe\_old & neg. control \\
-\bottomrule
+1 & geo, groom > all non-geo & PPA \tabularnewline
+2 & geo, groom, se\_new > all non-geo & PPA \tabularnewline
+3 & room, se\_new, se\_old > all non-geo & PPA \tabularnewline
+4 & geo > all non-geo & PPA \tabularnewline
+5 & groom > all non-geo & PPA \tabularnewline
+6 & se\_new > all non-geo & PPA \tabularnewline
+7 & se\_new, se\_old > all non-geo & PPA \tabularnewline
+8 & se\_new > se\_old & PPA \tabularnewline
+9 & vse\_new > vpe\_old & control at moments of cuts \tabularnewline
+10 & vse\_new, vpe\_new > vse\_old, vpe\_old & control at moments of cuts \tabularnewline
+11 & vse\_new > vse\_old & control at moments of cuts \tabularnewline
+12 & vse\_new > vse\_old, vpe\_old & control at moments of cuts \tabularnewline
+13 & vse\_new, vpe\_new > vpe\_old & control at moments of cuts \tabularnewline
 \end{tabular}

### 2020-05-02 paper/main.tex
add table for AV COPEs

@@
 \paragraph{audio contrasts of parameter estimate}
-% Überblick über die Kontraste geben, die tatsächlich am Ende im Paper berichtet werden -> am besten telefonisch klären
-% HIER ERZÄHLEN, WARUM VIELE KONTRASTE GERCHNET WURDEN und WARUM DER EINE COPE THE ONE AND ONLY IST
+\todo[inline]{Warum ist COPE 1 die Nummer 1}
 
 \begin{table*}[t]
-\caption{Contrasts of parameter estimates for the analysis of the audio-description.
+\caption{Contrasts of parameter estimates for the analysis of the audio-description (AO).
 \texttt{all non-geo} = all non-geo related regressors except furniture.}
@@
 \paragraph{video contrasts of parameter estimate}
-% Überblick über die Kontraste geben, die tatsächlich am Ende im Paper berichtet werden
 % ggf. irgendwo noch reinpressen, dass man damit fast alle schnitte in FG benutzt hat
@@
 The cinematographic rationale was that - over the course of a movie - cuts shift from establishing the setting and the spatial relationships within a setting at the beginning of a movie to depicting persons and objects more relevant to the subsequently evolved narrative later in the movie {brown2012cinematography; mercado2011filmmakers}.
-The neurocientific rationale was that activity in the PPA is greater when participants view novel versus repeated scenes resp.
-view-points \citep{epstein1999parahippocampal}.
+The neurocientific rationale was that activity in the PPA is greater when participants view novel versus repeated scenes resp. view-points \citep{epstein1999parahippocampal}.
 Hence, we contrasted cuts to a setting occurring for the first time (vse\_new) and cuts within a locale depicted for the first time (vpe\_new) with shots to a recurring setting (vse\_old) and cuts within a recurring locale (vpe\_old).
 
-\begin{table*}
-\caption{COPEs for the movie.}
+\begin{table*}[t]
+    \caption{Contrasts of parameter estimates for the analysis of the audio-visual movie (AV).}
+\label{tab:av-contrasts}
+\footnotesize
 \begin{tabular}{lll}
 \toprule
-\textbf{COPE nr. } & \textbf{description} & \textbf{aim} \\
+\textbf{nr.} &  \textbf{contrasted} & \textbf{aim/goal} \\
 \midrule
-1 & geo, rgeo, se\_new, se\_old > non\_geo & PPA \\
-1 & se\_new > se\_old & PPA \\
-2 & pe\_new > pe\_old & PPA \\
-3 & se\_new, pe\_new > se\_old, pe\_old & PPA (the true and cool one) \\
-4 & se\_new > pe\_old & PPA \\
-5 & se\_new > se\_old, pe\_old & PPA \\
-6 & se\_new, pe\_new > pe\_old & PPA \\
-7 & pe\_new > se\_old, pe\_old & PPA \\
-8 & se\_old > se\_new & DMN \\
-9 & pe\_old > pe\_new & DMN \\
-10 & no\_cut > se\_new, se\_old & neg. control \\
-11 & no\_cut > se\_new & neg. control \\
-12 & no\_cut > se\_old & neg. control \\
-13 & no\_cut > pe\_new, pe\_old & neg. control \\
-14 & ao: se\_new > se\_old & audio control \\
-15 & ao: se\_old > se\_new & audio control \\
-\bottomrule
+1 & vse\_new > vpe\_old  & PPA \tabularnewline
+2 & vse\_new, vpe\_new > vse\_old, vpe\_old & PPA \tabularnewline
+3 & vse\_new > vse\_old & PPA \tabularnewline
+4 & vse\_new > vse\_old, vpe\_old & PPA \tabularnewline
+5 & vse\_new, vpe\_new > vpe\_old & PPA \tabularnewline
+6 & vno\_cut > vse\_new & negative control \tabularnewline
+7 & vno\_cut > vse\_old & negative control \tabularnewline
+8 & vno\_cut > vse\_new, vse\_old & negative control \tabularnewline
+9 & vno\_cut > vpe\_new, vpe\_old & negative control \tabularnewline
+10 & se\_new > se\_old & control for narrator \tabularnewline
 \end{tabular}

### 2020-05-04 paper/main.tex
add table for COPE1 group results (AO & AV)

@@
 \paragraph{video contrasts of parameter estimate}
-% ggf. irgendwo noch reinpressen, dass man damit fast alle schnitte in FG benutzt hat
 We created a contrast presumably correlating with increased hemodynamic activity in the PPA by contrasting different kind of cuts.
@@
 The neurocientific rationale was that activity in the PPA is greater when participants view novel versus repeated scenes resp. view-points \citep{epstein1999parahippocampal}.
+% ggf. irgendwo noch reinpressen, dass man damit fast alle schnitte in FG benutzt hat
 Hence, we contrasted cuts to a setting occurring for the first time (vse\_new) and cuts within a locale depicted for the first time (vpe\_new) with shots to a recurring setting (vse\_old) and cuts within a recurring locale (vpe\_old).
@@
 \section{Results (audio)}
-% vgl. mit Ergebnis-Teilen anderer Localizer (in wievielen VPN funktioniert's etc.)
-% https://en.wikipedia.org/wiki/Bland%E2%80%93Altman_plot
+
+\begin{table*}[t]
+    \caption{Significant clusters (Z-Threshold Z>3.4; p<.05 cluster-corrected) for the contrast \texttt{geo, groom > all non-geo} (audio-only stimulus).
+Clusters sorted by voxel size.
+The first brain structure given contains the voxel with the maximum Z-Value, followed by brain structures from posterior to anterior, and partially covered areas.}
+\label{tab:res-ao-group1}
+\begin{tabular}{rrrrrrrrrp{3cm}}
+\toprule
+& & & \multicolumn{3}{r}{max location (MNI)} & \multicolumn{3}{r}{center of gravity (MNI)} &
+\\ \cmidrule{4-6} \cmidrule{7-9}
+voxels & $p_{corr.}$ & Z-max & x & y & z  & x & y & z & structure \\
+\midrule
+188 & 5.96E-08 & 4.48 & -17.5 & -65.5 & 25.5 & -14.7 & -59.1 & 15.2 & XYZ \\
+164 & 2.38E-07 & 4.47 & 17.5 & -58 & 23 & 15.6 & -55.6 & 16 & XYZ \\
+83 & 0.000128 & 4.48 & 27.5 & -43 & -17 & 27.2 & -41.1 & -14 & XYZ \\
+73 & 0.000318 & 3.93 & -22.5 & -43 & -12 & -23.9 & -43.6 & -11.2 & XYZ \\
+63 & 0.000824 & 4.1 & 40 & -75.5 & 30.5 & 40.9 & -76.3 & 28.6 & XYZ \\
+37 & 0.0129 & 4.24 & -37.5 & -78 & 33 & -38.4 & -79.5 & 28.9 & XYZ \\
+\bottomrule
+\end{tabular}
+\end{table*}
 
 \section{Results (movie)}
-lore ipsum
+
+\begin{table*}[t]
+    \caption{Significant clusters (Z-Threshold Z>3.4; p<.05 cluster-corrected) for the contrast \texttt{vse\_new > vpe\_old} (audio-visual stimulus).
+Clusters sorted by voxel size.
+The first brain structure given contains the voxel with the maximum Z-Value, followed by brain structures from posterior to anterior, and partially covered areas.}
+\label{tab:res-ao-group1}
+\begin{tabular}{rrrrrrrrrp{3cm}}
+\toprule
+& & & \multicolumn{3}{r}{max location (MNI)} & \multicolumn{3}{r}{center of gravity (MNI)} &
+\\ \cmidrule{4-6} \cmidrule{7-9}
+voxels & $p_{corr.}$ & Z-max & x & y & z  & x & y & z & structure \\
+\midrule
+3003 & 0 & 5.31 & 22.5 & -45.5 & -12 & 4.53 & -63.3 & -3.72 \\
+154 & 6.56E-07 & 4.46 & -35 & -83 & 28 & -32.8 & -86.2 & 21.4 \\
+121 & 7.69E-06 & 4.65 & 25 & -80.5 & 25.5 & 23.7 & -83.8 & 25.4 \\
+\bottomrule
+\end{tabular}
+\end{table*}
 

### 2020-05-04 paper/main.tex
add brain regions to result tables

@@
 \midrule
-188 & 5.96E-08 & 4.48 & -17.5 & -65.5 & 25.5 & -14.7 & -59.1 & 15.2 & XYZ \\
-164 & 2.38E-07 & 4.47 & 17.5 & -58 & 23 & 15.6 & -55.6 & 16 & XYZ \\
-83 & 0.000128 & 4.48 & 27.5 & -43 & -17 & 27.2 & -41.1 & -14 & XYZ \\
-73 & 0.000318 & 3.93 & -22.5 & -43 & -12 & -23.9 & -43.6 & -11.2 & XYZ \\
-63 & 0.000824 & 4.1 & 40 & -75.5 & 30.5 & 40.9 & -76.3 & 28.6 & XYZ \\
-37 & 0.0129 & 4.24 & -37.5 & -78 & 33 & -38.4 & -79.5 & 28.9 & XYZ \\
+188 & 5.96E-08 & 4.48 & -17.5 & -65.5 & 25.5 & -14.7 & -59.1 & 15.2 & l. precuneus \\
+
+164 & 2.38E-07 & 4.47 & 17.5 & -58 & 23 & 15.6 & -55.6 & 16 & r. precuneus; \\
+
+83 & 0.000128 & 4.48 & 27.5 & -43 & -17 & 27.2 & -41.1 & -14 & r. temporal (occipital) fusiform c.; posterior parahippocampal g. \\
+
+73 & 0.000318 & 3.93 & -22.5 & -43 & -12 & -23.9 & -43.6 & -11.2 & l. lingual g.; temporal (occipital) fusiform g., posterior parahippocampal c. \\
+
+63 & 0.000824 & 4.1 & 40 & -75.5 & 30.5 & 40.9 & -76.3 & 28.6 & r. superior lateral occipital c. \\
+
+37 & 0.0129 & 4.24 & -37.5 & -78 & 33 & -38.4 & -79.5 & 28.9 & l. superior lateral occipital c. \\
 \bottomrule
@@
 \midrule
-3003 & 0 & 5.31 & 22.5 & -45.5 & -12 & 4.53 & -63.3 & -3.72 \\
-154 & 6.56E-07 & 4.46 & -35 & -83 & 28 & -32.8 & -86.2 & 21.4 \\
-121 & 7.69E-06 & 4.65 & 25 & -80.5 & 25.5 & 23.7 & -83.8 & 25.4 \\
+3003 & 0 & 5.31 & 22.5 & -45.5 & -12 & 4.53 & -63.3 & -3.72 & r. lingual gyrus; r cuneal c., intracalarine c., bilaterally occipital fusiform g., temporal fusiform c., posterior parahippocampal c.  \\
+154 & 6.56E-07 & 4.46 & -35 & -83 & 28 & -32.8 & -86.2 & 21.4 & l. superior lateral occipital c. \\
+121 & 7.69E-06 & 4.65 & 25 & -80.5 & 25.5 & 23.7 & -83.8 & 25.4 & r. superior lateral occipital cortex \\
 \bottomrule

### 2020-05-09 paper/main.tex
LaTex formatting madness; wrote statistical analysis section

@@
 
-1. Psychoinformatics Lab, Institute of Neuroscience and Medicine, Brain \& Behaviour (INM-7), Research Centre Jülich, Jülich, Germany,
+1. Psychoinformatics Lab, Institute of Neuroscience and Medicine, Brain \&
+Behaviour (INM-7), Research Centre Jülich, Jülich, Germany,
 2. Institute of Systems Neuroscience, Medical Faculty, Heinrich Heine University,  Düsseldorf, Germany
@@
 \begin{abstract}
-% < 170 words
-% new analysis of existing data
-% of interest to a broad section of our audience
-% highlighting innovative examples of data reuse
-% may be used to present compelling new findings & conclusions derived from published data.
-Intro: PPA as classic example for an visual area
-Methods: fMRI data, studyforrest data set, general linear model
-Results: significant clusters in PPA, RSC, individual results in x of 15 subjects
-Conclusions: PPA nicht exclusively
-\end{abstract}
-\todo[inline]{Vorgabe: Intro + Discussion = main text ~ 3,000 words; einige offene Dinge sind folgend in Kommentaren und nicht als ToDo gemarkt}
-\todo[inline]{include figure providing schematic overview of the study and assay(s) design -> is overkill: Steht in den entsprechenden Veröffentlichungen \& Paradigma ist mit "Film ab" wenig kompliziert}
-\todo[inline]{our system cannot accept BibTeX bibliography files; authors who wish to use BibTeX to prepare their references should therefore copy the reference list from the .bbl file that BibTeX generates and paste it into the main manuscript .tex file (and delete the associated  \textbackslash{}bibliography and \textbackslash{}bibliographystyle commands); yeah, whatever.
-Arbeite erstmal mit der references.bib; und habe oben usepackage{natbib}' eingefügt}
-\section{Introduction}
-Cognitive neuroscientists use brain imaging methods like blood oxygenation level-dependent functional magnetic resonance imaging (BOLD fMRI) to map perceptual and cognitive brain processes (e.g.
-viewing of landscapes, \citep{epstein1998ppa}; or theory of mind \citep{spunt2014validating}) to functional brain areas or networks.
-Brain mapping studies have traditionally employed small sets of carefully chosen, simplified stimuli to strictly control experimental conditions and facilitate functional isolation of brain areas.
-The disadvantage is that a limited number of simplified stimuli does not resemble our real-life experience and lacks external \citep{westfall2016fixing} as well as ecological validity \citep{hasson2004intersubject}.
-Additionally, brain mapping studies have traditionally averaged / usually average results across at least 10-15 subjects to improve the signal-to-noise-ratio (SNR).
-The disadvantage here is that the averaging approach does not characterize brain functions at an individual level, a prerequisite for the application of brain imaging methods in individual diagnostics (cf.
-\citep{dubois2016building})
-\todo[inline]{Retrosplenial Cortex kommt in Einleitung (momentan) nicht vor; wird aufgrund der Ergebnisse AV und AO in Discussion diskutiert werden; ist in den geplanten Abbildungen / Slices aber nicht zu sehen}
-A classic example of a functional, higher-level visual area is the ``parahippocampal place area'' (PPA) \citep{epstein1998ppa, epstein1999parahippocampal}.
-The PPA is located in the posterior parahippocampal gyrus at the boundary to the anterior lingual gyrus and medial fusiform gyrus, both being part of the ventral visual stream \citep{mishkin1982contribution, goodale1992separate}.
-Increased hemodynamic activity in the PPA correlates with the perception of static pictures of landscapes or landmarks compared to pictures of tools or faces.
-According to the spatial layout hypothesis, the PPA is involved in processing the surface geometry of a visual stimulus and possibly in identifying scenes based on their spatial layout \citep{epstein2010reliable}.
-% Überblick
-At a group avergae level, results generalize to mental imagination of landscapes \citep{ocraven2000mental} and haptic exploration of scenes constructed from LEGO blocks \citep{wolbers2011modality}.
-One study that used spoken, place-related sentences showed significantly decreased activation in the left and no modulation in the right-hemispheric PPA \citep{aziz2008modulation}.
-\todo[inline]{Egal, was ich folgend in der Überblick \& später im Detail bzgl.
-Aziz (2008) schreibe, es wird wahrscheinlich nicht korrekt sein; so wie ich es verstanden habe, hat Aziz den Unterschied zwischen PPA und FFA angeguckt, aber diesen Unterschied im Kontrast zu object-related Sentences; s.
-dortige Fig 3; im Grunde kommt da aber überall nur uneinheitliche Grütze raus => bitte gemeinsam im Gespräch checken}
+% < 170 words new analysis of existing data of interest to a broad section of
+% our audience highlighting innovative examples of data reuse may be used to
+% present compelling new findings & conclusions derived from published.
+Intro: PPA as classic example for an visual area; Methods: fMRI data
+studyforrest data set, general linear model; Results: significant clusters in
+PPA, RSC, individual results in x of 15 subjects; Conclusions: PPA nicht
+exclusively \end{abstract}
 
-% Im Einzelnen
-In the study conducted by \citep{ocraven2000mental} participants viewed alternating blocks of pictures showing famous faces and familiar places during an initial experimental paradigm.
-In a subsequent paradigm, participants were instructed to ``form a vivid mental image'' of the previously viewed pictures.
-The PPA showed increased activation during imagination of places compared to faces but the imagination tasks showed a smaller activation level compared to the perceptual task.
+\todo[inline]{Vorgabe: Intro + Discussion = main text ca. 3,000 words; einige
+offene einige Dinge sind folgend in Kommentaren und nicht als ToDo gemarkt}
 
-% Folgend: Wolbers.
-Er hat noch ne Connectivitäts-Analyse mit dem Occipital Cortex gemacht.
-Zum visuellen Paradigma ist da dann keine keine Connectivity im Vergleich zum visuellen Paradigma.
-Seine Interpretation: Es kann keine mental imagery sein:
-% "The scene-related increase in coupling with the PPA was significantly stronger in multiple clusters in occipital cortex under visual than haptic stimulation (Figure 2B; Table S2)"
-In the block design study conducted by \citep{wolbers2011modality} the PPA of sighted participants showed increased activation during a delayed matching-to-sample task of haptically explored scenes constructed from LEGO bricks compared to haptically explored abstract geometric objects.
+\todo[inline]{include figure providing schematic overview of the study and assay
+design -> is overkill: Steht in den entsprechenden Veröffentlichungen \&
+Paradigma ist mit "Film ab" wenig kompliziert}
 
-% Aziz hat auf eine zweite Mail geantwortet: Sie modelt die HRF über den jeweils gesamten Satz von ca. 2.8 Sekunden.
-% wie oben im Kommentar erwähnt: Ihre Method Section halte ich für etwas strange.Ich zeige dir ganz am Ende mal ihr Paper; hab die entsprechenden Stellen annotiert.
-Sonst wird hier im Detail Mist erzählt
-To our knowledge only one study by \citep{aziz2008modulation} correlated hemodynamic activity of the PPA with spoken sentences.
-Sentences described generic or famous places (e.g. ``The Taj Mahal faces a long thin reflecting pool'') or faces  (e.g. ``Marylin Monroe has a large square jaw'').
-\todo[inline]{\dots and compared those to a control condition of object-related sentences}
-Participants were instructed to press a button whenever the sentence described an inaccurate or improbable fact.
-Surprisingly, activation in the left, but not right, PPA was significantly reduced when participants listened to place-related sentences compared to listening to face-related sentences.
-Moreover, this effect was only observed in sentences involving famous places.
+\todo[inline]{our system cannot accept BibTeX bibliography files; authors who
+    wish to use BibTeX to prepare their references should therefore copy the
+    refernce list from the .bbl file that BibTeX generates and paste it into the
+    main manuscript .tex file (and delete the associated
+    \textbackslash{}bibliography and \textbackslash{}bibliographystyle
+commands)}
+
+\todo[inline]{Ich arbeite erstmal wie gehabt mit der references.bib
+    und habe oben usepackage{natbib}' eingefügt}
+
+\section{Introduction} Cognitive neuroscientists use brain imaging methods like
+blood oxygenation level-dependent functional magnetic resonance imaging (BOLD
+fMRI) to map perceptual and cognitive brain processes (e.g. viewing of
+landscapes, \citep{epstein1998ppa}; or theory of mind
+\citep{spunt2014validating}) to functional brain areas or networks. Brain
+mapping studies have traditionally employed small sets of carefully chosen,
+simplified stimuli to strictly control experimental conditions and facilitate
+functional isolation of brain areas. The disadvantage is that a limited number
+of simplified stimuli does not resemble our real-life experience and lacks
+external validity \citep{westfall2016fixing} as well as ecological validity
+\citep{hasson2004intersubject}. Additionally, brain mapping studies usually
+average results across at least 10-15 subjects to improve the
+signal-to-noise-ratio (SNR). The disadvantage here is that the averaging
+approach does not characterize brain functions at an individual level, a
+prerequisite for the application of brain imaging methods in individual
+diagnostics (cf. \citep{dubois2016building})
+
+\todo[inline]{Retrosplenial Cortex kommt in Einleitung bisher  nicht vor; wird
+aufgrund der Ergebnisse in AV und AO in Discussion diskutiert werden; cluster
+sind in den Abbildungen nicht zu sehen; kommen aber in (den Tabellen) der
+Results Section }
+
+% Was ist PPA?
+A classic example of a functional, higher-level visual area is the
+``parahippocampal place area'' (PPA) \citep{epstein1998ppa,
+epstein1999parahippocampal}. The PPA is located in the posterior parahippocampal
+gyrus at the boundary to the anterior lingual gyrus and medial fusiform gyrus,
+both being part of the ventral visual stream \citep{mishkin1982contribution,
+goodale1992separate}. Increased hemodynamic activity in the PPA correlates with
+the perception of static pictures of landscapes or landmarks compared to
+pictures of tools or faces.  According to the spatial layout hypothesis, the PPA
+is involved in processing the surface geometry of a visual stimulus and possibly
+in identifying scenes based on their spatial layout \citep{epstein2010reliable}.
+
+% Literature Review PPA: Einleitung
+At a group avergae level, results generalize to mental imagination of landscapes
+\citep{ocraven2000mental} and haptic exploration of scenes constructed from LEGO
+blocks \citep{wolbers2011modality}. One study that used spoken, place-related
+sentences showed significantly decreased activation in the left and no
+modulation in the right-hemispheric PPA \citep{aziz2008modulation}.
+
+% Studien im Einzelnen: O'Craven: Mental imagery
+In the study conducted by \citep{ocraven2000mental} participants viewed
+alternating blocks of pictures showing famous faces and familiar places during
+an initial experimental paradigm. In a subsequent paradigm, participants were
+instructed to ``form a vivid mental image'' of the previously viewed pictures.
+The PPA showed increased activation during imagination of places compared to
+faces but the imagination tasks showed a smaller activation level compared to
+the perceptual task.
+
+% Wolbers: haptic exploration
+In the block design study conducted by \citep{wolbers2011modality} the PPA of
+sighted participants showed increased activation during a delayed
+matching-to-sample task of haptically explored scenes constructed from LEGO
+bricks compared to haptically explored abstract geometric objects.
+
+\todo[inline]{Er hat noch eine Connectivitäts-Analyse mit dem Occipital Cortex
+gemacht. Im Vergleich zum visuellen Paradigma ist im haptischen Paradigma keine
+Connectivität. Interpretation: Es kann keine mental imagery sein}
+
+\todo[inline]{"The scene-related increase in coupling with the PPA was
+significantly stronger in multiple clusters in occipital cortex under visual
+than haptic stimulation (Figure 2B; Table S2)"}
+
+% Aziz (2008): place related sentences
+\todo[inline]{Aziz hat auf eine zweite Mail geantwortet: Sie modelt die HRF über
+den jeweils gesamten Satz von ca. 2.8 Sekunden}
+
+\todo[inline]{Ihre Method Section ist strange und es bei ihr überall eh nur
+    uneinheitliche Grütze heraus; Ich blicke nicht durch; was folgend kommt,
+    wird nicht vollständig korrekt sein. So wie ich es verstanden habe, hat sie
+    den Unterschied zwischen PPA und FFA angeguckt, aber diesen Unterschied im
+Kontrast zu object-related Sentences (dortige Fig 3; lass uns kurz im Gespräch
+drübergucken, ich habe die relvanten Abschnitte in der PDF markiert)}
+
+To our knowledge only one study by \citep{aziz2008modulation} correlated
+hemodynamic activity of the PPA with spoken sentences.  Sentences described
+generic or famous places (e.g. ``The Taj Mahal faces a long thin reflecting
+pool''), faces  (e.g. ``Marylin Monroe has a large square jaw''), or objects
+(e.g. ``The television has a long antenna')'. Participants were instructed to
+press a button whenever the sentence described an inaccurate or improbable fact.
+Surprisingly, activation in the left, but not right, PPA was significantly
+reduced when participants listened to place-related sentences compared to
+listening to face-related sentences. Moreover, this effect was only observed in
+sentences involving famous places.
 
@@
 gar nicht notwendig ist, weil's darum gar bei uns gar nicht geht}
-In summary, studies suggest that the PPA does not exclusively respond to visual(ly) spatial information.
-This is consistent with a competing hypotheses stating the PPA does not process the spatial layout of a scene specifically but contextual associations in general (see \citep{aminoff2006parahippocampal} for a review).
-Independent(ly) from competing theories (s.
-\citep{aminoff2013role} for a review), it is still unacknowledged/ uncertain/ indeterminate if auditory stimuli lead to inhibitory or excitatory responses, or no change at all in the PPA.
-\todo[inline]{aber Huth, 2016, implizit; diskutiert PPA als solches jedoch gar nicht -> noch mal checken}
-\todo[inline]{Coolnessfaktor von naturalistic stimuli ist beinahe komplett raus; Data-driven vs.
-theory-driven analyses ist komplett raus -> vgl.
-Speech-Anno-Paper; jedoch in Discussion bringen (s.
-dort); ggf.
-erwähnen, dass möglichst ähnliche und nicht fancy analysis gewählt wurde, um Replizierung der Ergebnisse, aber mit naturalistic stimuli zu gewährleisten.}
-All revied studies used a just a small set of carefully designed, simplified stimuli to strictly control experimental conditions.
-They further relied on / implemented explicit judgment-based tasks to keep participants alert and paying attention.
-Thus, they cannot / could answer the question how the PPA might behave under life-like conditions.
-Naturalistic stimuli like movies \citep{hasson2008neurocinematics, sonkusare2019naturalistic} or narratives \citep{honey2012not, lerner2011topographic, silbert2014coupled} offer an easy to implement, (continuous,) complex, immersive stimuli that better resemble our experience of a continuous dynamic environment.
+
+% Summary if literature review
+In summary, studies suggest that the PPA does not exclusively respond to
+visual(ly) spatial information. This is consistent with a competing hypotheses
+stating the PPA does not process the spatial layout of a scene specifically but
+contextual associations in general (\citep{aminoff2006parahippocampal,
+aminoff2013role}). It is still uncertain if auditory stimuli lead to inhibitory
+or excitatory responses, or no change at all in the PPA.
+
+\todo[inline]{aber Huth (2016) implizit; diskutiert PPA also solches jedoch
+nicht und macht voxel-wise encoding, was - glaube ich - über
+excitation/inhibition nichts aussagt -> Paper checken}
+
+% Shortcomings of previous studies; lack of research
+All revied studies used a just a small set of carefully designed, simplified
+stimuli to strictly control experimental conditions. They further relied on
+explicit judgment-based tasks to ensured that participants payed attention to
+the stimuli. This raises the question how the PPA behaves under life-like conditions.
+
+\todo[inline]{Data-driven vs. model-driven analyses ist komplett raus; in
+Discussion bringen (vgl. Speech-Anno-Paper}
+
+% Why naturalistic stimuli
+Naturalistic stimuli like movies \citep{hasson2008neurocinematics,
+sonkusare2019naturalistic} or narratives \citep{honey2012not,
+lerner2011topographic, silbert2014coupled} offer complex, continuous stimuli
+that better resemble our experience of a our dynamic environment.
+
+% Literature review naturalistic stimuli: Einleitung
 Two early studies using naturalistic stimuli suggest functional specialization is preserved during free viewing of a movie when many areas respond simultaneously and interact [+++ der Schlusssatz ist aus hasson und bartels plagiiert \citep{bartels2004mapping, hasson2004intersubject}+++]
 
-% Bartels (2004) und Hasson (2004)
-\citep{bartels2004mapping} manually annotated time points that depict faces and human bodies in a 22 minute clip of the movie \textit{Tomorrow Never Dies}.
-Employing a general linear model to model hemodynamic activity, these time points correlated with increased activity in the ``fusiform face area'' \citep{kanwisher1997ffa} and ``extrastriate body area'' \citep{downing2001bodyarea} respectively.
-Employing a reverse intersubject correlation, \citep{hasson2004intersubject} used a 30 minute clip of the movie \textit{The Good, the Bad, the Ugly}.
-fMRI brain volumes showing the highest hemodynamic activity in the PPA [across (five) participants] were matched to the (temporally) corresponding movie frames.
-Results revealed that corresponding movie frames depicted indoor and outdoor scenes including buildings and open fields.
+% Bartels (2004): Film + GLM (jedoch ohne PPA) und Hasson (2004)
+\citep{bartels2004mapping} manually annotated time points that depict faces and
+human bodies in a 22 minute clip of the movie \textit{Tomorrow Never Dies}
+[+++Ref+++].
+Employing a general linear model (GLM) to model hemodynamic activity, these time
+points correlated with increased activity in the ``fusiform face area''
+\citep{kanwisher1997ffa} and ``extrastriate body area''
+\citep{downing2001bodyarea} respectively.
+
+% Hasson (2004): Film + (reverse) ISC
+Employing a reverse intersubject correlation, \citep{hasson2004intersubject}
+used a 30 minute clip of the movie \textit{The Good, the Bad, the Ugly}
+[+++Ref+++]. fMRI
+brain volumes showing the highest hemodynamic activity in the PPA [across (five)
+participants] were matched to the temporally corresponding movie frames.
+Results revealed that corresponding movie frames depicted indoor and outdoor
+scenes including buildings and open fields.
+
+% Summary naturalistic stimuli
 Nevertheless, no study investigated how the PPA responds to spatial clues that are embedded in a complex, audio-only stimulus.
+\todo[inline]{Huth (2016) checken}
+
+\todo[inline]{The next paragraphs contain a bunch of methods already; reduce
+this to talk about the general approach:
+
+a) annotation of events
+
+b) investigation of model quality,
+
+c) cross-analysis of datasets
+
+d) Possibly cite https://psyarxiv.com/sdbqv/ and declare that this study is
+a concrete realization of that promise}
+
+\todo[inline]{Präteritum oder Präsens? Ist momentan gemischt; find's ok so}
+
+\todo[inline]{Inner join of AV \& AO: N=14}
+
+% What we did: Einleitung
+In this study, we analyze data of three publicly available datasets from the
+same set of 14 participants as part of the studyforrest data set
+(\href{http://www.studyforrest.org}{studyforrest.org}). We exploratorily
+investigate how the parahippocampal gyrus [or more general ``human brain''?]
+responds to ``spatially relevant'' events embedded in a 2h audio-visual movie
+\citep{hanke2016simultaneous} and its audio-description (i.e. the audio-only
+variant) of the same length \citep{hanke2014audiomovie}. We compare these
+results to PPA localizations that were obtained from a dedicated visual
+localizer experiment \citep{sengupta2016extension}.
+
+Both natural stimuli were originally designed to entertain an audience and to capture attention free from any perceptual or behavioral task.
+We annotated events in the otherwise unknown temporal structure of both stimuli.
+In/for the movie, we annotated different kinds of cinematographic cuts \citep{haeusler2016cutanno} as presumably ``spatially relevant'' events.
+Our rationale was that cuts re-orient the viewer in the depicted environment
+indepenten from the exact visual content in the movie frame following the cut.
+In/for the audio-description, we annotated verbal clues about the missing visual content given by the audio-description's additional narrator \citep{haeusler2020speechanno}.
+
+In conformity to the analyses performed in the studies using not-naturalistic stimuli, we employed a standard multi-level, voxel-wise general linear model (GLM) % in order to???
+\todo[inline]{in order to\dots}
+
+Encouraged by \citep{aziz2008modulation} and \citep{aminoff2013role}, we focus on the audio-description as a possible life-like stimulus free from any task to localize a ``visual area'' in individual study participants.
 
@@
 
-% Präteritum oder Präsens? Ist momentan gemischt; find's ok so.
-% N=14 is inner join of AV & AO
-\todo[inline]{The next paragraphs contain a bunch of methods already; reduce this to talk about the general approach:
-    a) annotation of events,
-    b) investigation of model quality,
-    c) cross-analysis of datasets.
-    d) Possibly cite https://psyarxiv.com/sdbqv/
-    and declare that this study is a concrete realization of that promise
-}
-In this study, we analyze data of three publicly available datasets from the same set of 14 participants as part of the studyforrest data set (\href{http://www.studyforrest.org}{studyforrest.org}).
-We exploratorily investigate how the parahippocampal gyrus [or more general ``human brain''?] responds to ``spatially relevant'' events embedded in a 2h audio-visual movie \citep{hanke2016simultaneous} and its audio-description (i.e.
-the audio-only variant) of the same length \citep{hanke2014audiomovie}.
-We compare these results to PPA localizations that were obtained from a dedicated visual localizer experiment \citep{sengupta2016extension}.
+\section{Methods}
 
-Both natural stimuli were originally designed to entertain an audience and to capture attention free from any perceptual or behavioral task.
-We annotated events in the otherwise unknown temporal structure of both stimuli.
-In/for the movie, we annotated different kinds of cinematographic cuts \citep{haeusler2016cutanno} as presumably ``spatially relevant'' events.
-Our rationale was that cuts re-orient the viewer in the depicted environment independent from the exact visual content in the movie frame following the cut.
-In/for the audio-description, we annotated verbal clues about the missing visual content given by the audio-description's additional narrator \citep{haeusler2020speechanno}.
+\todo[inline]{Specific data outputs should be explicitly referenced via data
+citation (see Data Records and Data Citations, below)}
 
-In conformity to the analyses performed in the studies using not-naturalistic stimuli, we employed a standard multi-level, voxel-wise general linear model (GLM) % in order to???
-% Practical reasons = Es war viel einfacher nouns der audio-description als Frameinhalt des Films zu annotieren
-For practical reasons, and encouraged by \citep{aziz2008modulation} and \citep{aminoff2013role}, we focus on the audio-description as a possible life-like stimulus free from any task to localize a ``visual area'' in individual study participants.
+We used data from three publicly available datsets as part of the studyforrest
+dataset (\href{http://www.studyforrest.org}{studyforrest.org}) that has already
+been used by other research groups for independent research questions before.
 
-\section{Methods}
-\todo[inline]{Specific data outputs should be explicitly referenced via data citation (see Data Records and Data Citations, below)}
-\todo[inline]{statement how often datasets have been analyzed be independent groups -> Frage: ist die Liste auf psychoinformatics.de ist aktuell/erschöpfend? Ist dann schnell eingebaut}
-We used data from three publicly available datsets as part of the studyforrest dataset (\href{http://www.studyforrest.org}{studyforrest.org}) that has already been used by other research groups for independent research questions before
 We used fMRI data from 14 subjects who took part in three different studies. Namely, the same subjects were
-a) listening to the audio-description (AO study) \citep{hanke2014audiomovie}) of the movie ``Forrest Gump'', a dataset already used by [XY].
-b) watching the actual audio-visual movie (AV study) \citep{hanke2016simultaneous}, a dataset already used by [XY].
-c) participating in a dedicated block-wise visual localizer (LOC study) \citep{sengupta2016extension}, a dataset aready used by [XY].
-An exhaustive description of the participants, stimulus creation, procedure, stimulation setup, and fMRI acquisition can be found in the corresponding publications  \citep{hanke2014audiomovie, hanke2016simultaneous, sengupta2016extension}.
-Following is a brief summary of most important aspects.
-\todo[inline]{um Sengupta ergänzen}
+
+a) listening to the audio-description (AO study; \citep{hanke2014audiomovie}) of
+the movie ``Forrest Gump'', a dataset already used by \citep{hu2017decoding}.
+b) watching the actual audio-visual movie (AV study;
+\citep{hanke2016simultaneous}, a dataset already used by
+\citep{ben2018hippocampal}. c) participating in a dedicated block-wise visual
+localizer (LOC study) \citep{sengupta2016extension}, a dataset aready used by
+\citep{jiahui2019predicting}.
+
+An exhaustive description of the participants, stimulus creation, procedure,
+stimulation setup, and fMRI acquisition can be found in the corresponding
+publications  \citep{hanke2014audiomovie, hanke2016simultaneous,
+sengupta2016extension}. Following is a brief summary of most important aspects.
+
+\todo[inline]{Alles um Sengupta ergänzen}
 
 \subsection{Participants}
-\todo[inline]{ich habe von den aligned data eine Intersection von 14 VPN aus AO und AV; in der Speech-Anno-Validation (7T only) habe ich 19 VPN; es fehlt jeweils VP10; demographische Daten bzgl.
-(Durchschnitts)Alter und Geschlecht ist folglich falsch}
-In the AO study, 19 participants (all right-handed, age 21–38 years, mean age 26.6 years, 12 male) listened to the German audio-description \citep{ForrestGumpGermanAD} of the movie ``Forrest Gump'' \citep{ForrestGumpMovie} as an additional audio track for visually impaired listeners on Swiss public television.
-In the AV study, the same 14 participants [+++VP 10 wurde nicht genutzt+++] (21–39 years, mean age 29.4, six female) watched the audio-visual movie with dubbed German audio track \citep{ForrestGumpDVD}.
 
-\todo[inline]{Daten zu Sengupta einarbeiten}
+\todo[inline]{inner join von AO \& AV: N=14; AO: N=19; es fehlt in beiden VP10;
+Angaben zu Alter (Durchschnitt; ggf. Range) und Geschlecht sind folglich falsch}
+
+In the AO study, 19 participants (all right-handed, age 21–38 years, mean age
+26.6 years, 12 male) listened to the German audio-description
+\citep{ForrestGumpGermanAD} of the movie ``Forrest Gump''
+\citep{ForrestGumpMovie} as an additional audio track for visually impaired
+listeners on Swiss public television. In the AV study, the same 14 participants
+(21–39 years, mean age 29.4, six female) watched the audio-visual movie with dubbed German audio track \citep{ForrestGumpDVD}.
+All participants reported to have normal hearing, normal or corrected-to-normal vision, and no known history of neurological disorders.
+
+\todo[inline]{Sengupta (2016)}
 In the LOC study\dots
 
-All participants reported to have normal hearing, normal or corrected-to-normal vision, and no known history of neurological disorders.
-% mit LOC study updaten
 In both studies, participants received monetary compensation and gave written informed consent for their participation and for public sharing of all obtained data in anonymized form.
@@
 \subsection{Stimuli}
-We used the German DVD release \citep{ForrestGumpDVD} of the audio-visual movie ``Forrest Gump'' \citep{ForrestGumpMovie} and its temporally aligned audio-description (i.e.
-the audio-only variant of the movie) that was broadcast as an additional audio track for visually impaired listeners on Swiss public televinsion \citep{ForrestGumpGermanAD}.
-The plot of the movie is already carried by an off-screen voice of the main character Forrest Gump.
-In the largely identical audio-description, a male narrator additionally describes essential aspects of the visual scenery when there is no off-screen voice, dialog, or other relevant auditory content.
-The audio-description was temporally aligned to the audio track of the German DVD release.
-A few scenes less relevant to the major plot were removed to create the ``research cut'' lasting $\approx$2h \citep{hanke2014audiomovie,hanke2016simultaneous}.
-Both stimuli were further processed (filtering, volume adjustments) to improve audibility during MRI scanning.
-Finally, each stimulus was split into eight segments of approximately 15 minutes.
-Except for the first movie segment, each segment started with a snippet of at least six seconds immediately preceding the movie scene boundary used to split the segments (s.
-Figure 3a in \citep{hanke2014audiomovie}.
-\todo[inline]{Sengupta: Stimuli}
-% LOC study?
+% stimulus name & references
+We used the German DVD release \citep{ForrestGumpDVD} of
+the audio-visual movie ``Forrest Gump'' \citep{ForrestGumpMovie} and its
+temporally aligned audio-description (i.e. the audio-only variant of the movie)
+that was broadcast as an additional audio track for visually impaired listeners
+on Swiss public televinsion \citep{ForrestGumpGermanAD}.
 
-\subsection{Stimulus Annotation}
+% difference in audio track AV vs. AO
+The plot of the movie is already carried by an off-screen voice of the main
+character Forrest Gump.  In the largely identical audio-description, a male
+narrator additionally describes essential aspects of the visual scenery when
+there is no off-screen voice, dialog, or other relevant auditory content.
+
+% stimulus creation
+The audio-description was temporally aligned to the audio track of the German
+DVD release. A few scenes less relevant to the major plot were removed to create
+the ``research cut'' lasting $\approx$2h
+\citep{hanke2014audiomovie, hanke2016simultaneous}. Both stimuli were further
+processed (filtering, volume adjustments) to improve audibility during MRI
+scanning. Finally, each stimulus was split into eight segments of approximately
+15 minutes.  Except for the first movie segment, each segment started with a
+snippet of at least six seconds immediately preceding the movie scene boundary
+used to split the segments (s. Figure 3a in \citep{hanke2014audiomovie}.
+
+\todo[inline]{Sengupta (2016)}
+
+\subsection{Naturalistic stimuli annotation}
+
+\todo[inline]{aus Speech-Anno Paper 'descriptive-statistics-anno.py' übernehmen \& anpassen, um Statistiken und runcommand-file zu erstellen}
+
+% annotation procedure
+We extended a publicly available annotation of speech \citep{haeusler2020speechanno} by manually annotating the audio-description's narrator: Two persons performed a categorization of nouns embedded in sentences spoken by the narrator to describe the movie's missing visual content.
+
+\todo[inline]{WARUM WAS WIE annotiert wurde; warum Kategorien so gewählt?}
+
+% noun categorization
 % Kategorie ``++'' enthält ausnahmesweise auch adverbiale Best. der Zeit.
-\todo[inline]{WARUM WAS WIE annotiert wurde}
-\todo[inline]{aus Speech-Anno Paper 'descriptive-statistics-anno.py' übernehmen \& anpassen, um Statistiken und runcommand-file zu erstellen}
-We extended a publicly available annotation of speech \citep{haeusler2020speechanno} by manually annotating the audio-description's narrator:
-Two persons performed a categorization of nouns embedded in sentences spoken by the narrator to describe the movie's missing visual content.
-\todo[inline]{Warum wurden diese Kategorien so gewählt}
-\todo[inline]{Maybe just cite the table}
-The nouns were categorized by the clue they provide about the cinematographic scene's environment (geo, geo-room; setting\_new, setting\_old), its inherent persons (female, female name; male, male name, person), a person's appearance (face, head; body, bodypart), and a scene's inherent objects (object, furniture).
-See Table \ref{tab:descr-nouns} for a complete overview of all cateogries, [+++rules, counts, examples].
+The nouns were categorized by the clue they provide about the cinematographic
+scene's environment (geo, geo-room; setting\_new, setting\_old), its inherent
+persons (female, female name; male, male name, person), a person's appearance
+(face, head; body, bodypart), and a scene's inherent objects (object,
+furniture). See Table \ref{tab:descr-nouns} for a complete overview of all
+cateogries [+++rules, counts, examples].
 
-A preliminary annotation was performed by one person according to the rules (see Table XYZ).
-Minor corrections due to incorrectly applied rules were by the author.
+A preliminary annotation was performed by one person according to the rules (see
+Table XYZ). Minor corrections due to incorrectly applied rules were by the
+author.
 
 % Tabelle der Descriptive Nouns;
-\todo[inline]{wenn decriptive-statistics-anno.py angepasst und Datei mit newcommands geschrieben, Schrägstrich vor die jeweiligen Platzhalter setzen, damit commands daraus werden; Caption hübsch machen}
+\todo[inline]{decr-stats-anno.py; Schrägstriche vor Platzhalter}
+
+\todo[inline]{Caption hübsch machen}
+
 \begin{table*}[t]
@@
         All categories sorted alphapetically.
-Examples are given in English.
-Tabelle enthält bei den Counts Platzhalter für die commands, die ins .tex-file geschrieben werden.}
+    Examples are given in English.}
 \label{tab:descr-nouns}
@@
 \subsection{Procedure}
-In both studies, participants filled out a questionnaire on their basic demographic information and familiarity with the audio-description or the movie.
-Participants were instructed to inhibit physical movements except for eye-movements, and otherwise to simply "enjoy the audiobook" or "enjoy the movie" respectively.
-Audio-description and movie segments were presented in chronological order with four segments in two fMRI sessions respectively.
-Between sessions, participants left the scanner for a break with a flexible duration. Structural images were obtained during the first study on a day different from the fMRI session.
-% At the start (of each?) recording session, participants listened to music from the movie's closing credits segment to individually determine optimal stimulus volume.
-% Participants were instructed to ``maximize the volume of the stimulus without it becoming unpleasantly loud or causing acoustic distortions by overdriving the loudspeaker hardware''.
+
+In both [all three] studies, participants filled out a questionnaire on their
+basic demographic information and familiarity with the audio-description or the
+movie. Participants were instructed to inhibit physical movements except for
+eye-movements, and otherwise to simply ``enjoy the audiobook'' or ``enjoy the
+movie'' respectively. Audio-description and movie segments were presented in
+chronological order with four segments in two fMRI sessions respectively.
+Between sessions, participants left the scanner for a break with a flexible
+duration. Structural images were obtained during the first study on a day
+different from the fMRI session.
 
 \subsection{Stimulation setup}
+
 \todo[inline]{irrelevantes kürzen}
 In both studies, stimulation was implemented with \href{http://www.psychopy.org}{PsychoPy} \citep{peirce2007psychopy} running on a computer with the \href{http://neuro.debian.net}{(Neuro)Debian} operating system \citep{halchenko2012open}.
-In the AO study, visual instructions were presented on a rear-projection screen inside scanner bore using an LCD projector (DLA-G150CL, JVC Ltd.).
-During the functional scans, the projector presented a medium gray screen with the primary purpose to illuminate a participant's visual field in order to prevent premature fatigue.
-[The screen contained a solid black ``fixation'' dot that faded in and out at the beginning and end of a movie segment.]
 
-In the AV study, visual instructions and stimuli were presented on a rear-projection screen using an LCD projector (JVC DLA RS66E, JVC Ltd., light transmission reduced to \unit[13.7]{\%} with a gray filter) connected to the stimulus computer [via a DVI extender system (Gefen EXT-DVI-142DLN with EXT-DVI-FM1000).
-The movie was shown at a viewing distance of \unit[63]{cm} in \unit[720]{p} resolution at full width on a \unit[1280 $\times$ 1024]{pixel} screen with \unit[60]{Hz} video refresh rate and screen dimension of \unit[26.5 $\times$ 21.2]{cm}, corresponding to \unit[23.75 $\times$ 13.5] or \unit[23.75 $times$ 10.25]{cm} when considering only the movie content and excluding the horizontal gray bars.
+In the AO study, visual instructions were presented on a rear-projection screen
+inside scanner bore using an LCD projector (DLA-G150CL, JVC Ltd.). During the
+functional scans, the projector presented a medium gray screen with the primary
+purpose to illuminate a participant's visual field in order to prevent premature
+fatigue. [The screen contained a solid black ``fixation'' dot that faded in and
+out at the beginning and end of a movie segment.]
+
+In the AV study, visual instructions and stimuli were presented on a
+rear-projection screen using an LCD projector (JVC DLA RS66E, JVC Ltd., light
+transmission reduced to \unit[13.7]{\%} with a gray filter) connected to the
+stimulus computer [via a DVI extender system (Gefen EXT-DVI-142DLN with
+EXT-DVI-FM1000)]. The movie was shown at a viewing distance of \unit[63]{cm} in
+\unit[720]{p} resolution at full width on a \unit[1280 $\times$ 1024]{pixel}
+screen with \unit[60]{Hz} video refresh rate and screen dimension of \unit[26.5
+$\times$ 21.2]{cm}, corresponding to \unit[23.75 $\times$ 13.5] or \unit[23.75
+$times$ 10.25]{cm} when considering only the movie content and excluding the
+horizontal gray bars.
 
@@
 \subsection{fMRI data acquisition}
+
 \todo[inline]{irrelevantes kürzen}
-In both studies, a total of 3599 volumes were recorded for each participant (451, 441, 438, 488, 462, 439, 542, and 338 volumes for movie segment 1–8 respectively).
 
-In the AO study, a whole-body \unit[7]{Tesla} Siemens MAGNETOM magnetic resonance scanner equipped with a local circularly polarized head transmit and a 32 channel brain receive coil (Nova Medical, Inc., Wilmington, MA, USA) acquired T2*-weighted echo-planar images
-(gradient-echo, \unit[2]{s} repetition time (TR), \unit[22]{ms} echo time, \unit[0.78]{ms} echo spacing, \unit[1488]{Hz/Px} bandwidth, generalized autocalibrating partially parallel acquisition, acceleration factor 3, \unit[2]{Hz/Px} bandwidth in phase encoding direction) using 36 axial slices (thickness \unit[1.4]{mm}, \unit[1.4 $\times$ 1.4]{mm} in-plane resolution, \unit[224]{mm} field-of-view, anterior-to-posterior phase encoding direction)
-with a 10 percent inter-slice gap were recorded in ascending order.
-Slices were oriented to include the ventral portions of frontal and occipital cortex while minimizing intersection with the eyeballs.
-The field-of-view was centred on the approximate location of Heschl's gyrus.
-[+++EPI images were online-corrected for motion and geometric distortions [Oh, S. et al. 2012; In, M. \& Speck, O., 2012; Chung, J. et al., 2011].
-[Auxiliary scans for slice alignment and motion- and distortion-correction were performed at the beginning of the first fMRI recording session and also after the break at the start of the recording for the second half of the movie].
+In both studies, a total of 3599 volumes were recorded for each participant
+(451, 441, 438, 488, 462, 439, 542, and 338 volumes for movie segment 1–8
+respectively).
 
-In the AV study, a whole-body \unit[3]{Tesla} Philips Achieva dStream MRI scanner equipped with a 32 channel head coil acquired T2*-weighted echo-planar images (gradient-echo, \unit[2]{s} repetition time (TR), \unit[30]{ms} echo time, \unit[90]{$^{\circ}$} flip angle, \unit[1943]{Hz/Px} bandwidth, parallel acquisition with sensitivity encoding (SENSE) reduction factor 2).
-35 axial slices (thickness \unit[3.0]{mm}, \unit[10]{\%} inter-slice gap) with \unit[80 $\times$ 80]{voxels} (\unit[3.0 $\times$ 3.0]{mm} of in-plane resolution), \unit[240]{mm} field-of-view ) and an anterior-to-posterior phase encoding direction were recorded in ascending order.
-Philips' ``SmartExam'' was used to automatically position slices in AC-PC orientation such that the topmost slice was located at the superior edge of the brain.
+% AO (Hanke, 2014)
+In the AO study, a whole-body \unit[7]{Tesla} Siemens MAGNETOM magnetic
+resonance scanner equipped with a local circularly polarized head transmit and a
+32 channel brain receive coil (Nova Medical, Inc., Wilmington, MA, USA) acquired
+T2*-weighted echo-planar images (gradient-echo, \unit[2]{s} repetition time
+(TR), \unit[22]{ms} echo time, \unit[0.78]{ms} echo spacing, \unit[1488]{Hz/Px}
+bandwidth, generalized autocalibrating partially parallel acquisition,
+acceleration factor 3, \unit[2]{Hz/Px} bandwidth in phase encoding direction).
+% slices & FOV
+36 axial slices (thickness \unit[1.4]{mm}, \unit[1.4 $\times$ 1.4]{mm} in-plane
+resolution, \unit[224]{mm} field-of-view, anterior-to-posterior phase encoding
+direction) with a 10 percent inter-slice gap were recorded in ascending order.
+Slices were oriented to include the ventral portions of frontal and order.
+Slices were oriented to include the ventral the ventral portions of frontal and
+occipital cortex while minimizing intersection with the eyeballs.  The field of
+view was centered on the approximate location of Heschl's gyrus.
+% motion correction
+EPI images were online-corrected for motion and geometric distortions [Oh, S. et
+al. 2012; In, M. \& Speck, O., 2012; Chung, J. et al., 2011]. Auxiliary scans
+for slice alignment and motion- and distortion-correction were performed at the
+beginning of the first fMRI recording session and also after the break at the
+start of the recording for the second half of the movie.
+
+% AV (Hanke, 2016)
+In the AV study, a whole-body \unit[3]{Tesla} Philips Achieva dStream MRI
+scanner equipped with a 32 channel head coil acquired T2*-weighted echo-planar
+images (gradient-echo, \unit[2]{s} repetition time (TR), \unit[30]{ms} echo
+time, \unit[90]{$^{\circ}$} flip angle, \unit[1943]{Hz/Px} bandwidth, parallel
+acquisition with sensitivity encoding (SENSE) reduction factor 2).
+% slices
+35 axial slices (thickness \unit[3.0]{mm}, \unit[10]{\%} inter-slice gap) with
+\unit[80 $\times$ 80]{voxels} (\unit[3.0 $\times$ 3.0]{mm} of in-plane
+resolution, \unit[240]{mm} field-of-view) and an anterior-to-posterior phase
+encoding direction were recorded in ascending order. Philips' ``SmartExam'' was
+used to automatically position slices in AC-PC orientation such that the topmost
+slice was located at the superior edge of the brain.
+\todo[inline]{In the LOC study\dots}
 
 \subsection{Preprocessing}
+
+\todo[inline]{bin wie immer bzgl. motion correction \& Templateerstellung unsicher}
+
+\todo[inline]{cite sengupta2016 where this was first done and described, ie same image/data was used here}
+
+\todo[inline]{downsampling der 7T Daten}
+
 % data source
-\todo[inline]{wie immer bzgl. Motion Correction und Registratziohier ggf. expliziter erwähnen, dass AO spatially downsampled ist}
-\todo[inline]{cite sengupta2016 where this was first done and described, ie same image/data was used here}
 fMRI time series data were obtained from
 \href{https://github.com/psychoinformatics-de/studyforrest-data-aligned}{GitHub}.
-Data are already aligned to a subject-specific \href{https://github.com/psychoinformatics-de/studyforrest-data-templatetransforms}{3 Tesla BOLD template} by a rigid body transformation in MCFLIRT \citep{jenkinson2002registration} to correct for motion during scanning
+Data are already aligned to a subject-specific
+\href{https://github.com/psychoinformatics-de/studyforrest-data-templatetransforms}{3
+Tesla BOLD template} by a rigid body transformation in MCFLIRT
+\citep{jenkinson2002registration} to correct for motion during scanning
 \citep{sengupta2016extension}.
@@
 % preprocessing intro
-All further analysis steps in the current study were carried out using tools of FSL v5.0.9 (\href{https://www.fmrib.ox.ac.uk/fsl}{FMRIB's Software Library};\citep{smith2004fsl}; on a computer cluster running the \href{https://www.debian.org}{Debian} GNU/Linux operating system.
-Software packages were obtained from repositories of \href{http://neuro.debian.net}{NeuroDebian} \citep{halchenko2012open}.
+All further analysis steps in the current study were carried out using tools of
+FSL v5.0.9 (\href{https://www.fmrib.ox.ac.uk/fsl}{FMRIB's Software
+Library}; \citep{smith2004fsl} on a computer cluster running the
+\href{https://www.debian.org}{Debian} GNU/Linux operating system. Software
+packages were obtained from repositories of
+\href{http://neuro.debian.net}{NeuroDebian} \citep{halchenko2012open}.
 
 % actual preprocessing
-Preprocessing (and statistical analysis) was carried out using FEAT v6.00 (FMRI Expert Analysis Tool;\citep{woolrich2001autocorr}) as part of FSL.
-High-pass temporal filtering was applied to every segment using a Gaussian-weighted least-squares straight line with a cutoff period of \unit[150]{s} (sigma=\unit[75.0]{s}) to remove low-frequency confounds.
+Preprocessing was carried out using FEAT v6.00 (FMRI Expert Analysis Tool;
+\citep{woolrich2001autocorr}) as part of FSL.
+% temporal filtering
+High-pass temporal filtering was applied to every segment using a
+Gaussian-weighted least-squares straight line with a cutoff period of
+\unit[150]{s} (sigma=\unit[75.0]{s}) to remove low-frequency confounds.
+% brain extraction
 The brain was extracted from surrounding tissues using BET \citep{smith2002bet}.
-Data were spatially smoothed applying a Gaussian kernel with full width at half maximum (FWHM) of \unit[4.0]{mm}.
-A grand-mean intensity normalization of the entire 4D dataset was performed by a single multiplicative factor.
-Correction for local autocorrelation in the time series (prewhitening) was applied using FILM (FMRIB's Improved Linear Model).
+% spatial smoothing
+Data were spatially smoothed applying a Gaussian kernel with full width at half
+maximum (FWHM) of \unit[4.0]{mm}.
+% normalization
+A grand-mean intensity normalization of the entire 4D dataset was performed by a
+single multiplicative factor.
+% pre-whithening
+Correction for local autocorrelation in the time series (prewhitening) was
+applied using FILM (FMRIB's Improved Linear Model; \citep{woolrich2001autocorr})
+to improve estimation efficiency \citep{woolrich2001autocorr}.
 
 \subsection{Statistical analysis}
-For both naturalistic stimli, we conducted a standard two-level general linear model (GLM) analysis in FEAT to create subject-specific results ($Z$-maps).
-A subsequent, third-level analysis averaged contrast estimates over subjects.
+
+For both naturalistic stimli, we conducted a standard two-level general linear
+model (GLM) analysis in FEAT to create subject-specific results ($Z$-maps)
+across the 8 segments for every subject. A subsequent, third-level analysis averaged contrast estimates over subjects.
 
 \subsubsection{first-level}
+
 \paragraph{Regressors}
-\todo[inline]{cross reference to fig:reg-corr}
-We used an annotation of movie cuts and depicted locations \citep{haeusler2016cutanno}, and an annotation of speech \citep{haeusler2020speechanno} to create event files for FSL.
+
+At the first level analyzing each segment for every subject, we created
+regressors for the AO data from the narrator's descriptive nouns (see Table
+\ref{tab:descr-nouns}) added to the annotation of speech
+\citep{haeusler2020speechanno}. For the AV stimulus, we created regressors from
+events provided by an annotation of movie cuts and depicted locations
+\citep{haeusler2016cutanno}.
 % https://github.com/psychoinformatics-de/studyforrest-data-annotations/blob/master/code/researchcut2segments.py}
-First, both annotations were split into eight parts corresponding to the eight segments used as stimuli during fMRI scanning.
-\todo[inline]{wenn ich folgend den "null regressor" nehme, darf ich den ganzen Run, glaube ich, in der 2nd level Analyse gar nicht benutzen??}
-For the AO stimulus, we used the narrator's ``descriptive nouns'' (see Table \ref{tab:descr-nouns}.
+First, both annotations were split into eight parts corresponding to the eight
+segments used as stimuli during fMRI scanning.
 
-\todo[inline]{some categories were pooled, because\dots}
+% AO events
+To create regressors for the AO analysis, XY from the XY original categories
+were selected [+++why?+++]. Some categories were pooled / joined / merged
+resulting in 11 new categories to provide more events per category per run.
+% categories taken from movie cut annotation
+Five categories were created from the annotation of movie cuts to capture
+variance of a change in soundscape after cuts and tu create contrasts of
+cross-modal negative control.
+% nuissance regressors
+Two regressors reflecting auditory (low-level) features (left-right difference
+in volume and root mean squared volume) aligned to the frame rate of
+(\unit[40]{ms}) were modeled to reduce nuisance effects.
+% siehe Tabelle
+An overview and short explanation of the 11 speech-related and 5 movie
+cut-related categories and the two low-level auditory features ca be found in
+Table \ref{tab:ao-events}.
 
-XY from the XY original categories were selected [+++why?+++], and some were pooled  original categories by joining / merging some categories resulting in 11 new categories.
-
-\todo[inline]{make clear which stimulus each annotation is based on, and make clear(er) what defined an event. This could be a big table, because good defintions are important for judging the results}
 \begin{table*}[t]
@@
 sex\_m & male person(s), name & \aoSexmAll & \aoSexmI & \aoSexmII & \aoSexmIII & \aoSexmIV & \aoSexmV & \aoSexmVI & \aoSexmVII & \aoSexmVIII \tabularnewline
-sex\_u & person(s) of unknown sex & \aoSexuAll & \aoSexuI & \aoSexuII & \aoSexuIII & \aoSexuIV & \aoSexuV & \aoSexuVI & \aoSexuVII & \aoSexuVIII \tabularnewline
 % vlo_ch has no events in segment 5. So indices are shifted
@@
 \end{table*}
+
+% AV events
+To create regressors for the AV analysis, we categorized the depicted location
+in the frame following one of the 869 cuts in the movie into five categories:
+1) unfamiliar setting (\texttt{vs\_new}),
+2) familiar setting (\texttt{vs\_old}),
+3) locale switch (\texttt{vlo\_ch}),
+4) unfamiliar perspective (\texttt{vpe\_new}), and
+5) familiar perspective (\texttt{vpe\_old}).
+% no cut condition
+A sixth regressors (\texttt{no\_cut}) was created to build negative control
+contrasts.
+\todo{how no\_cut condition was done; compare no\_speech oben und Masterarbeit}
+% how it was done
+Frames within a longer lasting were pseudo-randomly chosen by the following
+rationale:
+% siehe Tabelle
+An overview and short explanation of these six regressors and six additional
+event categories were of low-level auditory visual features of the movie can be
+found in Table \ref{tab:av-events}.
 
@@
 
-% over length of each noun
-The regressors were modeled as boxcar functions at the end of each noun with a duration of 200 ms.
-If a segment did not contain a single event for a specific regressor, a null regressor was chosen for that segment.
-Five regressors related to the cinematographic cuts (s. below) were added to built contrasts of cross-modal negative control.
-Two regressors reflecting auditory (low-level) features (left-right loudness volume / amplitude???
-difference; root mean squared amplitude) aligned to the frame rate of (40\,ms) were modeled to reduce nuisance effects.
-An overview and short explanation of the 11 regressors and 5 + 2 additional nuisance regressors can be found in Table xy.
-% entgegen der Masterarbeit kommen hier für den Film keine Abbildungen zur Verdeutlichung, weniger Text; no cut erkläre ich nicht lang & breit
-% die regressoren settinge_new & setting_old aus dem Hörspiel habe ich meiner meinung nach unnötigerweise im Film mit-modelliert; lasse mich da aber auch umstimmen
+% modeling of regressors from events
+For both stimuli, regressors created from nouns were modeled as boxcar functions
+from the beginning to the end of noun.  Regressors created from movie cuts were
+modeled as boxcar function lasting \unit[200]{ms} after a cut. Finally,
+regressors created from low-level percetual features were modeled as box car
+function from the beginning to the end of the corresponding movie frame lasting
+\unit[40]{ms}. All regressors were convolved with a double gamma canonical
+hemodynamic response function (HRF). Their temporal derivatives were added to
+compensate for small timing differences \citep{friston1998event}.
+% motion parameters
+Six motion parameters were used as additional nuisance regressors.
+% null regressors
+If a segment did not contain a single event for a specific regressor, a null
+regressor was chosen for that segment.
+\todo{wenn ich "null regressor" nehme, darf ich den ganzen Run, glaube ich, in
+der 2nd level Analyse gar nicht benutzen? Hatte, glaube ich, Jeanette Mumford in
+einem ihren Videos mal gesagt} Finally, designs were filtered with the same
+% high-pass filtering
+high-pass filter (cutoff period of \unit[150]{s}) as the BOLD time series.
+% siehe Tabelle für Correlation of regressors
+\todo[inline]{hier kommt die Abbildung ``correlation of regressors''; ref to
+fig:reg-corr}
 
-% -> noch mal reingucken; kamen im Grunde nur "auditorische Areale" als Cluster vor; umgekehrt gab's bei der visuellen Regressoren im Hörbuch keine sign. Cluster
-For the audio-visual stimulus, we categorized the depicted location in the frame following one of the 869 cuts in the movie to built five regressors: 1) unfamiliar setting (US), 2) familiar setting (FS), 3) locale switch (LS), 4) unfamiliar perspective (UP), 5) familiar perspective (FP).
-
-In order to build negative control contrasts, a sixth regressors was created by pseudo-randomly choosing frames present within a shot and apart from a cut.
-Regressors were modeled as boxcar function lasting 200\,ms after a cut.
-An overview and short explanation of the six regressors and the additional nuisance regressors reflecting (auditory and) visual low-level features can be found in Table xy.
-
-For both stimuli, regressors were convolved with a double gamma canonical hemodynamic response function (HRF).
-Their temporal derivatives were added to compensate for small timing differences \citep{friston1998event}.
-Six motion parameters were used as additional nuisance regressors. Finally, designs were filtered with the same high-pass filter (cutoff period of \unit[150]{s}) as the BOLD time series.
-
-\paragraph{audio contrasts of parameter estimate}
-\todo[inline]{Warum ist COPE 1 die Nummer 1}
+\paragraph{audio stimulus: contrasts of parameter estimate}
+\todo[inline]{Warum ist welche COPES so gemacht und warum COPE 1 die Nummer 1}
+% wieso, weshalb, warum
+See Table \ref{tab:ao-contrasts}
 
 \begin{table*}[t]
-\caption{Contrasts of parameter estimates for the analysis of the audio-description (AO).
+\caption{Contrasts of parameter estimates for the analysis of the audio-only
+    stimulus (AO).
 \texttt{all non-geo} = all non-geo related regressors except furniture.}
@@
 
-\paragraph{video contrasts of parameter estimate}
-We created a contrast presumably correlating with increased hemodynamic activity in the PPA by contrasting different kind of cuts.
-This was done without controlling for the specific visual content depicted in the frame after each cut.
-The cinematographic rationale was that - over the course of a movie - cuts shift from establishing the setting and the spatial relationships within a setting at the beginning of a movie to depicting persons and objects more relevant to the subsequently evolved narrative later in the movie {brown2012cinematography; mercado2011filmmakers}.
-The neurocientific rationale was that activity in the PPA is greater when participants view novel versus repeated scenes resp. view-points \citep{epstein1999parahippocampal}.
-% ggf. irgendwo noch reinpressen, dass man damit fast alle schnitte in FG benutzt hat
-Hence, we contrasted cuts to a setting occurring for the first time (vse\_new) and cuts within a locale depicted for the first time (vpe\_new) with shots to a recurring setting (vse\_old) and cuts within a recurring locale (vpe\_old).
+\paragraph{audio-visual stimulus: contrasts of parameter estimate}
+% wieso, weshalb, warum
+We created a contrast presumably correlating with increased hemodynamic activity
+in the PPA by contrasting different kind of cuts, noteably without controlling
+for the specific visual content depicted in the frame after each cut.
+% cinematographic rationale
+The cinematographic rationale was that - over the course of a movie - cuts shift
+from establishing the setting and the spatial relationships within a setting at
+the beginning of a movie to depicting persons and objects more relevant to the
+subsequently evolved narrative later in the movie {brown2012cinematography;
+mercado2011filmmakers}.
+% neuroscientific rationale
+The neurocientific rationale was that activity in the PPA is greater when
+participants view novel versus repeated scenes resp. view-points
+\citep{epstein1999parahippocampal}.
+% im Ergebnis
+Hence, we contrasted cuts to a setting occurring for the first time (vse\_new)
+and cuts within a locale depicted for the first time (vpe\_new) with shots to a
+recurring setting (vse\_old) and cuts within a recurring locale (vpe\_old).
 
@@
 \paragraph{Registration \& smoothing: individuals vs. group}
-% hier wird's wie üblich bei Registrierung;
-% bitte gucken, ob korrekt wiedergeben, was ihr gemacht habt
-% wie besprochen sind hier die individuelle Results im subject space
-% später warpe ich individuelle 2nd-lvl-results "for visualization purposes" doch noch nach MNI
-The GLM analysis that fitted each voxel's time course separately for each subject was performed in functional space preserving the orientation of the EPI images.
-Correction for local autocorrelation in the time series (prewhitening) was applied using FILM (FMRIB's Improved Linear Model) to improve estimation efficiency \citep{woolrich2001autocorr}.
-For subsequent subject-specific second level results, subject-specific BOLD T2* time series were anatomically aligned via linear transformation to a subject-specific, study-specific T2* template (s.
-\href{"https://github.com/psychoinformatics-de/studyforrest-data-templatetransforms/blob/master/sub-01/bold3Tp2/brain.nii.gz"}{example}) that served as standard space.
-For subsequent the third level results averaging contrasts of interest across subjects, time series were anatomically aligned via non-linear transformation [+++wie genau?+++] to a \href{"https://github.com/psychoinformatics-de/studyforrest-data-templatetransforms/blob/master/templates/grpbold3Tp2/brain.nii.gz"}{study-specific T2* group template}.
-To facilitate visualization and identification of cortical structures, this reference images was later co-registered to the MNI 152 template with an affine transformation (12 degrees of freedom)
+
+\todo[inline]{Wie immer bei Co-Registration: bitte prüfen, ob ich es richtig
+geschrieben habe}
+
+\todo[inline]{wie besprochen sind die individuelle Results im
+subject space und werden erst später für die Bland-Altman-Plots nach MNI
+transformiert}
+
+% anatomical alignment of single subjects
+The GLM analysis that fitted each voxel's time course separately for each
+subject was performed in functional space preserving the orientation of the EPI
+images. For subsequent subject-specific second level results, subject-specific
+BOLD T2* time series were anatomically aligned via linear transformation to a
+subject-specific, study-specific T2* template (s.
+\href{"https://github.com/psychoinformatics-de/studyforrest-data-templatetransforms/blob/master/sub-01/bold3Tp2/brain.nii.gz"}{example})
+that served as standard space.
+% anatomical alignment for group results
+For subsequent the third level results averaging contrasts of interest across
+subjects, time series were anatomically aligned via non-linear transformation
+[+++wie genau?+++] to a
+\href{"https://github.com/psychoinformatics-de/studyforrest-data-templatetransforms/blob/master/templates/grpbold3Tp2/brain.nii.gz"}{study-specific
+T2* group template}.
+% MNI co-registration
+To facilitate visualization and identification of cortical structures, this
+reference images was later co-registered to the MNI 152 template with an affine
+transformation (12 degrees of freedom)
+
 \subsubsection{second level}
-The second-level analyses which averaged contrast estimates over the eight stimulus segments were carried out using a fixed effects model, by forcing the random effects variance to zero in FLAME (FMRIB's Local Analysis of Mixed Effects) \citep{beckmann2003general, woolrich2004multilevel}.
-Z (Gaussianised T/F) statistic images were thresholded using clusters determined by Z>2.3 and a (corrected) cluster significance threshold of p=.05 \citep{worsley2001statistical}.
+% model
+The second-level analyses which averaged contrast estimates over the eight
+stimulus segments were carried out using a fixed effects model by forcing the
+random effects variance to zero in FLAME (FMRIB's Local Analysis of Mixed
+Effects; \citep{beckmann2003general, woolrich2004multilevel}.
+% thresholding
+(Gaussianised T/F) statistic images were thresholded using clusters determined
+by Z>2.3 and a (corrected) cluster significance threshold of p=.05
+\citep{worsley2001statistical}.
+
 \subsubsection{third level}
-Third level analyses which averaged contrast estimates over subjects were carried out using FLAME stage 1 with automatic outlier detection \citep{beckmann2003general, woolrich2004multilevel, woolrich2008robust}.
-Z (Gaussianised T/F) statistic images were thresholded using clusters determined by Z>3.4 and a (corrected) cluster significance threshold of p=.05 [Worsley, 2001].
-% Brain regions associated with observed clusters were determined with the Juelich Histological Atlas Eickhoff et al.
-(2005); Eickhoff et al.
-(2007), the Harvard-Oxford Cortical Atlas (Desikan et al., 2006), and with queries on the NeuroSynth database (Yarkoni et al., 2011) provided by FSL.
-% In order to determine if activated regions were spatially congruent with higher-visual functional areas (PPA, FFA, OFA, LOC and EBA), study-specific ROI masks generated by the mean of visual localizers in Sengupta et al.
-(2016) were used.
+% model
+Third level analyses which averaged contrast estimates over subjects were
+carried out using FLAME stage 1 with automatic outlier detection
+\citep{beckmann2003general, woolrich2004multilevel, woolrich2008robust}.
+% thresholding
+Z (Gaussianised T/F) statistic images were thresholded using clusters determined
+by Z>3.4 and a (corrected) cluster significance threshold of p=.05
+\citep{worsley2001statistical}.
+% brain region identification
+Brain regions associated with observed clusters were determined with the Juelich
+Histological Atlas \citep{eickhoff2005toolbox, eickhoff2007assignment} and the
+Harvard-Oxford Cortical Atlas \citep{desikan2006automated} provided by FSL.
+% PPA masks
+PPA ROI masks for individual subjects and a PPA group overlap mask were created
+from data provided by \citep{sengupta2016extension}.
 
-\subsection{Das Post-FSL-Scripting-Gedöns}
-% Wahrscheinlicher ist, dass das Prozedere der Skripte nicht im Methodenteil berichtet werden muss
-% als Erläuterung in den Bildunterschriften im Ergebnisteil sollten reichen
-% -> die Skripte durchlaufen lassen und die Abbildungen in den Ergebnisteil samt Bildunterschriften einfügen
+\subsection{Erstellung der Masken, spatial transformations}
+
 \subsubsection{plot-group-and-individuals.py}
@@
 % 6. individual (un)thresholded zmaps (from the COPEs) were co-regi<wstered with MNI 152 (1mm) template.
-\section{Results (audio)}
+
+\section{audio-only stimulus: results}
+Primary contrast, probability over contrasts (individual clusters per contrasts,
+individuelle Bland-Altman-Plots für primary contrast
 
@@
 188 & 5.96E-08 & 4.48 & -17.5 & -65.5 & 25.5 & -14.7 & -59.1 & 15.2 & l. precuneus \\
-
 164 & 2.38E-07 & 4.47 & 17.5 & -58 & 23 & 15.6 & -55.6 & 16 & r. precuneus; \\
-
 83 & 0.000128 & 4.48 & 27.5 & -43 & -17 & 27.2 & -41.1 & -14 & r. temporal (occipital) fusiform c.; posterior parahippocampal g. \\
-
 73 & 0.000318 & 3.93 & -22.5 & -43 & -12 & -23.9 & -43.6 & -11.2 & l. lingual g.; temporal (occipital) fusiform g., posterior parahippocampal c. \\
-
 63 & 0.000824 & 4.1 & 40 & -75.5 & 30.5 & 40.9 & -76.3 & 28.6 & r. superior lateral occipital c. \\
-
 37 & 0.0129 & 4.24 & -37.5 & -78 & 33 & -38.4 & -79.5 & 28.9 & l. superior lateral occipital c. \\
@@
 
-\section{Results (movie)}
+\section{audio-visual stimulus: results}
+Primary contrast, probability over contrasts (individual clusters per contrasts,
+individuelle Bland-Altman-Plots für primary contrast.
 

### 2020-05-11 code/descr-stats-anno.py
add script that creates counts for descriptive nouns

@@ -1,0 +1,151 @@
+#!/usr/bin/python3
+"""
+author: Christian Olaf Haeusler
+created on Friday October 22th 2019
+"""
+import argparse
+import csv
+# import spacy
+from collections import defaultdict
+
+
+SEGMENTS_OFFSETS = (
+    (0.00, 0.00),
+    (886.00, 0.00),
+    (1752.08, 0.08),  # third segment's start
+    (2612.16, 0.16),
+    (3572.20, 0.20),
+    (4480.28, 0.28),
+    (5342.36, 0.36),
+    (6410.44, 0.44),  # last segment's start
+    (7086.00, 0.00))  # movie's last time point
+
+no2alpha = {0: 'All',
+            1: 'I',
+            2: 'II',
+            3: 'III',
+            4: 'IV',
+            5: 'V',
+            6: 'VI',
+            7: 'VII',
+            8: 'VIII'
+            }
+
+
+def parse_arguments():
+    '''
+    '''
+    parser = argparse.ArgumentParser(
+        description='Saves decriptive statistics for the annotation of speech'
+    )
+    parser.add_argument('-i',
+                        default='annotation/fg_rscut_ad_ger_speech_tagged.tsv',
+                        help='The input file')
+
+    parser.add_argument('-o',
+                        required=False,
+                        default=None,
+                        help='the tex-file the statistics to write to')
+
+    args = parser.parse_args()
+
+    inFile = args.i
+    outFile = args.o
+
+    return inFile, outFile
+
+
+def read_file(inFile):
+    '''
+    '''
+    with open(inFile) as csvfile:
+        content = csv.reader(csvfile, delimiter='\t')
+        header = next(content, None)
+        content = [x for x in content]
+
+    return header, content
+
+
+def get_run_number(starts, onset):
+    '''
+    '''
+    for start in sorted(starts, reverse=True):
+        if float(onset) >= start:
+            run = starts.index(start)
+            break
+
+    return run
+
+
+def populate_nouns_count(nounsDict, data):
+    '''
+    '''
+    segmStarts = [start for start, offset in SEGMENTS_OFFSETS]
+
+    for line in data:
+        # check the run/segment we are in
+        run = get_run_number(segmStarts, line[0])
+        segment = str(run + 1)
+
+        # filter for lines that have an entry for descriptive nouns
+        if len(line) >= 9 and line[9] != '':
+            descrNoun = line[9].split(';')[0]
[…]

### 2020-05-12 paper/main.tex
manuscript works with tex file for newcommands
replace placeholders in table to commands

@@
 \input{descr-stats-av-events.tex}
+\input{descr-stats-anno.tex}
 
@@
 
-\todo[inline]{aus Speech-Anno Paper 'descriptive-statistics-anno.py' übernehmen \& anpassen, um Statistiken und runcommand-file zu erstellen}
+\todo[inline]{um Hinweis bzgl. AV ergänzen}
 
@@
 (face, head; body, bodypart), and a scene's inherent objects (object,
-furniture). See Table \ref{tab:descr-nouns} for a complete overview of all
+furniture). See Table \ref{tab:descr-nouns-counts} for a complete overview of all
 cateogries [+++rules, counts, examples].
@@
 author.
-
-% Tabelle der Descriptive Nouns;
-\todo[inline]{decr-stats-anno.py; Schrägstriche vor Platzhalter}
-
-\todo[inline]{Caption hübsch machen}
 
@@
     Examples are given in English.}
-\label{tab:descr-nouns}
+\label{tab:descr-nouns-count}
+\begin{tabular}{lll}
+\toprule
+\textbf{category} & \textbf{rule} & \textbf{examples} \\
+\midrule
+body & trunk of the body; overlaid clothes & back, hip, shoulder; jacket, dress
+shirt \tabularnewline
+\bottomrule
+\end{tabular}
+\end{table*}
+
+% Tabelle der Descriptive Nouns;
+\todo[inline]{Caption hübsch machen}
+
+\begin{table*}[t]
+    \caption{Narrator's descriptive nouns.
+        All categories sorted alphapetically.
+    Examples are given in English.}
+\label{tab:descr-nouns-count}
 \begin{tabular}{llllllllllll}
@@
 \midrule
-body & trunk of the body; overlaid clothes & back, hip, shoulder; jacket, dress shirt & aDescrBodyAll & aDescrBodyI & aDescrBodyII & aDescrBodyIII & aDescrBodyIV & aDescrBodyV & aDescrBodyVI & aDescrBodyVII & aDescrBodyVIII \tabularnewline
-bodypart & limbs and trousers & arm, finger, leg, toe & aDescrBodypartAll & aDescrBodypartI & aDescrBodypartII & aDescrBodypartIII & aDescrBodypartIV & aDescrBodypartV & aDescrBodypartVI & aDescrBodypartVII & aDescrBodypartVIII \tabularnewline
-face & face or parts of it & face, ear, nose, mouth & aDescrFaceAll & aDescrFaceI & aDescrFaceII & aDescrFaceIII & aDescrFaceIV & aDescrFaceV & aDescrFaceVI & aDescrFaceVII & aDescrFaceVIII \tabularnewline
-female & female person & nurse, mother, woman & aDescrFemaleAll & aDescrFemaleI & aDescrFemaleII & aDescrFemaleIII & aDescrFemaleIV & aDescrFemaleV & aDescrFemaleVI & aDescrFemaleVII & aDescrFemaleVIII \tabularnewline
-females & female persons & women & aDescrFemalesAll & aDescrFemalesI & aDescrFemalesII & aDescrFemalesIII & aDescrFemalesIV & aDescrFemalesV & aDescrFemalesVI & aDescrFemalesVII & aDescrFemalesVIII \tabularnewline
-fname & female name & Jenny & aDescrFnameAll & aDescrFnameI & aDescrFnameII & aDescrFnameIII & aDescrFnameIV & aDescrFnameV & aDescrFnameVI & aDescrFnameVII & aDescrFnameVIII \tabularnewline
-furniture & movable objects insides/outsides & bench, bed, table, chair & aDescrFurnitureAll & aDescrFurnitureI & aDescrFurnitureII & aDescrFurnitureIII & aDescrFurnitureIV & aDescrFurnitureV & aDescrFurnitureVI & aDescrFurnitureVII & aDescrFurnitureVIII \tabularnewline
-geo & immobile landmarks & building, tree, street, alley, meadow, cornfield, river & aDescrGeoAll & aDescrGeoI & aDescrGeoII & aDescrGeoIII & aDescrGeoIV & aDescrGeoV & aDescrGeoVI & aDescrGeoVII & aDescrGeoVIII \tabularnewline
-geo-room & rooms / locales; elements defining a locale's spatial layout & living room; wall, door, window, floor, turf & aDescrGeoroomAll & aDescrGeoroomI & aDescrGeoroomII & aDescrGeoroomIII & aDescrGeoroomIV & aDescrGeoroomV & aDescrGeoroomVI & aDescrGeoroomVII & aDescrGeoroomVIII \tabularnewline
-head & non-face parts of the head; worn headgear & head, hair, ear, neck, helmet & aDescrHeadAll & aDescrHeadI & aDescrHeadII & aDescrHeadIII & aDescrHeadIV & aDescrHeadV & aDescrHeadVI & aDescrHeadVII & aDescrHeadVIII \tabularnewline
-male & male person & man, father, soldier & aDescrMaleAll & aDescrMaleI & aDescrMaleII & aDescrMaleIII & aDescrMaleIV & aDescrMaleV & aDescrMaleVI & aDescrMaleVII & aDescrMaleVIII \tabularnewline
-males & male persons & boys, opponents & aDescrMalesAll & aDescrMalesI & aDescrMalesII & aDescrMalesIII & aDescrMalesIV & aDescrMalesV & aDescrMalesVI & aDescrMalesVII & aDescrMalesVIII \tabularnewline
-mname & male name & Bubba, Kennedy & aDescrMnameAll & aDescrMnameI & aDescrMnameII & aDescrMnameIII & aDescrMnameIV & aDescrMnameV & aDescrMnameVI & aDescrMnameVII & aDescrMnameVIII \tabularnewline
-object & countable entity with firm boundarie & telephone, car & aDescrObjectAll & aDescrObjectI & aDescrObjectII & aDescrObjectIII & aDescrObjectIV & aDescrObjectV & aDescrObjectVI & aDescrObjectVII & aDescrObjectVIII \tabularnewline
-objects & countable entities with firm boundaries &  wheels, photos & aDescrObjectsAll & aDescrObjectsI & aDescrObjectsII & aDescrObjectsIII & aDescrObjectsIV & aDescrObjectsV & aDescrObjectsVI & aDescrObjectsVII & aDescrObjectsVIII \tabularnewline
-persons & concrete persons of unknown sex / gender & hippies, patients & aDescrPersonsAll & aDescrPersonsI & aDescrPersonsII & aDescrPersonsIII & aDescrPersonsIV & aDescrPersonsV & aDescrPersonsVI & aDescrPersonsVII & aDescrPersonsVIII \tabularnewline
-setting\_new & setting mentioned for the first time &  on a ``bridge'', on an ``alley'', on ``campus'' & aDescrSettingnewAll & aDescrSettingnewI & aDescrSettingnewII & aDescrSettingnewIII & aDescrSettingnewIV & aDescrSettingnewV & aDescrSettingnewVI & aDescrSettingnewVII & aDescrSettingnewVIII \tabularnewline
-setting\_rec & recurring setting & at the ``bus stop'' & aDescrSettingrecAll & aDescrSettingrec & aDescrSettingrecII & aDescrSettingrecIII & aDescrSettingrecIV & aDescrSettingrecV & aDescrSettingrecVI & aDescrSettingrecVII & aDescrSettingrecVIII \tabularnewline
-++ & nouns, adverbial adjectives and adverbs & in the ``evening'', it's ``daytime'', ``later'' &  aDescrAll & aDescrI & aDescrII & aDescrIII & aDescrIV & aDescrV & aDescrVI & aDescrVII & aDescrVIII \tabularnewline
+body & trunk of the body; overlaid clothes & back, hip, shoulder; jacket, dress shirt & \anBodyAll & \anBodyI & \anBodyII & \anBodyIII & \anBodyIV & \anBodyV & \anBodyVI & \anBodyVII & \anBodyVIII \tabularnewline
+
+bodypart & limbs and trousers & arm, finger, leg, toe & \anBodypartAll & \anBodypartI & \anBodypartII & \anBodypartIII & \anBodypartIV & \anBodypartV & \anBodypartVI & \anBodypartVII & \anBodypartVIII \tabularnewline
+
+face & face or parts of it & face, ear, nose, mouth & \anFaceAll & \anFaceI & \anFaceII & \anFaceIII & \anFaceIV & \anFaceV & \anFaceVI & \anFaceVII & \anFaceVIII \tabularnewline
+
+female & female person & nurse, mother, woman & \anFemaleAll & \anFemaleI & \anFemaleII & \anFemaleIII & \anFemaleIV & \anFemaleV & \anFemaleVI & \anFemaleVII & \anFemaleVIII \tabularnewline
+
+females & female persons & women & \anFemalesAll & \anFemalesI & \anFemalesII & \anFemalesIII & \anFemalesIV & \anFemalesV & \anFemalesVI & \anFemalesVII & \anFemalesVIII \tabularnewline
+
+fname & female name & Jenny & \anFnameAll & \anFnameI & \anFnameII & \anFnameIII & \anFnameIV & \anFnameV & \anFnameVI & \anFnameVII & \anFnameVIII \tabularnewline
+
+furniture & movable objects insides/outsides & bench, bed, table, chair & \anFurnitureAll & \anFurnitureI & \anFurnitureII & \anFurnitureIII & \anFurnitureIV & \anFurnitureV & \anFurnitureVI & \anFurnitureVII & \anFurnitureVIII \tabularnewline
+
+geo & immobile landmarks & building, tree, street, alley, meadow, cornfield, river & \anGeoAll & \anGeoI & \anGeoII & \anGeoIII & \anGeoIV & \anGeoV & \anGeoVI & \anGeoVII & \anGeoVIII \tabularnewline
+
+geo-room & rooms / locales; elements defining a locale's spatial layout & living room; wall, door, window, floor, turf & \anGeoroomAll & \anGeoroomI & \anGeoroomII & \anGeoroomIII & \anGeoroomIV & \anGeoroomV & \anGeoroomVI & \anGeoroomVII & \anGeoroomVIII \tabularnewline
+
+head & non-face parts of the head; worn headgear & head, hair, ear, neck, helmet & \anHeadAll & \anHeadI & \anHeadII & \anHeadIII & \anHeadIV & \anHeadV & \anHeadVI & \anHeadVII & \anHeadVIII \tabularnewline
+
+male & male person & man, father, soldier & \anMaleAll & \anMaleI & \anMaleII & \anMaleIII & \anMaleIV & \anMaleV & \anMaleVI & \anMaleVII & \anMaleVIII \tabularnewline
+
+males & male persons & boys, opponents & \anMalesAll & \anMalesI & \anMalesII & \anMalesIII & \anMalesIV & \anMalesV & \anMalesVI & \anMalesVII & \anMalesVIII \tabularnewline
+
+mname & male name & Bubba, Kennedy & \anMnameAll & \anMnameI & \anMnameII & \anMnameIII & \anMnameIV & \anMnameV & \anMnameVI & \anMnameVII & \anMnameVIII \tabularnewline
+
+object & countable entity with firm boundarie & telephone, car & \anObjectAll & \anObjectI & \anObjectII & \anObjectIII & \anObjectIV & \anObjectV & \anObjectVI & \anObjectVII & \anObjectVIII \tabularnewline
+
+objects & countable entities with firm boundaries &  wheels, photos & \anObjectsAll & \anObjectsI & \anObjectsII & \anObjectsIII & \anObjectsIV & \anObjectsV & \anObjectsVI & \anObjectsVII & \anObjectsVIII \tabularnewline
+
+persons & concrete persons of unknown sex / gender & hippies, patients & \anPersonsAll & \anPersonsI & \anPersonsII & \anPersonsIII & \anPersonsIV & \anPersonsV & \anPersonsVI & \anPersonsVII & \anPersonsVIII \tabularnewline
+
+setting\_new & setting mentioned for the first time &  on a ``bridge'', on an ``alley'', on ``campus'' & \anSettingnewAll & \anSettingnewI & \anSettingnewII & \anSettingnewIII & \anSettingnewIV & \anSettingnewV & \anSettingnewVI & \anSettingnewVII & \anSettingnewVIII \tabularnewline
+
+setting\_rec & recurring setting & at the ``bus stop'' & \anSettingrecAll &
+\anSettingrecI & \anSettingrecII & \anSettingrecIII & \anSettingrecIV & \anSettingrecV & \anSettingrecVI & \anSettingrecVII & \anSettingrecVIII \tabularnewline
+++ & nouns, adverbial adjectives and adverbs & in the ``evening'', it's ``daytime'', ``later'' &  anAll & \anI & \anII & \anIII & \anIV & \anV & \anVI & \anVII & \anVIII \tabularnewline
+aDescrV & aDescrVI & aDescrVII & aDescrVIII \tabularnewline
 \bottomrule
@@
 regressors for the AO data from the narrator's descriptive nouns (see Table
-\ref{tab:descr-nouns}) added to the annotation of speech
+\ref{tab:descr-nouns-counts}) added to the annotation of speech
 \citep{haeusler2020speechanno}. For the AV stimulus, we created regressors from

### 2020-05-12 paper/main.tex
different table for nouns rules and counts

@@
 A preliminary annotation was performed by one person according to the rules (see
-Table XYZ). Minor corrections due to incorrectly applied rules were by the
-author.
-
+Table \ref{tab:descr-nouns-rules}). Minor corrections due to incorrectly applied
+rules were by the author.
+
+\todo[inline]{so ist die Tabelle zu breit; schrift kleiner oder Text kürzen?
+Könnte durchaus auch detaillierteren Text schreiben}
+
+% rules Tabelle für descriptiven nouns
 \begin{table*}[t]
-    \caption{Narrator's descriptive nouns.
-        All categories sorted alphapetically.
-    Examples are given in English.}
-\label{tab:descr-nouns-count}
+    \caption{Descriptive nouns spoken by the audio-description's narrator:
+    cateogries, annotation rules and examples (given in English).}
+\label{tab:descr-nouns-rules}
 \begin{tabular}{lll}
@@
 shirt \tabularnewline
+bodypart & limbs and trousers & arm, finger, leg, toe \tabularnewline
+face & face or parts of it & face, ear, nose, mouth \tabularnewline
+female & female person & nurse, mother, woman \tabularnewline
+females & female persons & women \tabularnewline
+fname & female name & Jenny \tabularnewline
+furniture & moveable objects insides and outsides & bench, bed, table, chair
+\tabularnewline
+geo & immobile landmarks & building, tree, street, alley, meadow, cornfield, river \tabularnewline
+geo-room & rooms (insides) or  locales (outsides) & living room; wall, door, window, floor, turf \tabularnewline
+head & non-face parts of the head; worn headgear & head, hair, ear, neck,
+helmet \tabularnewline
+male & male person & man, father, soldier \tabularnewline
+males & male persons & boys, opponents \tabularnewline
+mname & male name & Bubba, Kennedy \tabularnewline
+object & countable entity with firm boundarie & telephone, car \tabularnewline
+persons & concrete persons of unknown sex & hippies, patients \tabularnewline
+setting\_new & setting mentioned for the first time &  on a ``bridge'', on an ``alley'', on ``campus'' \tabularnewline
+setting\_rec & recurring setting & at the ``bus stop'' \tabularnewline
+++ & nouns, adverbial adjectives and adverbs & in the ``evening'', it's ``daytime'', ``later'' \tabularnewline
+
 \bottomrule
@@
 
-% Tabelle der Descriptive Nouns;
-\todo[inline]{Caption hübsch machen}
-
+% counts Tabelle für descriptiven nouns
 \begin{table*}[t]
-    \caption{Narrator's descriptive nouns.
-        All categories sorted alphapetically.
-    Examples are given in English.}
-\label{tab:descr-nouns-count}
-\begin{tabular}{llllllllllll}
+    \caption{Descriptive nouns spoken by the audio-descriptions narrator:
+        counts for the whole audio-only stimulus and its eight segments used
+        during fMRI scanning.}
+\label{tab:descr-nouns-counts}
+\begin{tabular}{llllllllll}
 \toprule
-\textbf{category} & \textbf{rule} & \textbf{examples} & \textbf{all} & \textbf{1} & \textbf{2} & \textbf{3} & \textbf{4} & \textbf{5} & \textbf{6} & \textbf{7} & \textbf{8} \\
+\textbf{category} & \textbf{all} & \textbf{1} & \textbf{2} & \textbf{3} & \textbf{4} & \textbf{5} & \textbf{6} & \textbf{7} & \textbf{8} \\
 \midrule
-body & trunk of the body; overlaid clothes & back, hip, shoulder; jacket, dress shirt & \anBodyAll & \anBodyI & \anBodyII & \anBodyIII & \anBodyIV & \anBodyV & \anBodyVI & \anBodyVII & \anBodyVIII \tabularnewline
-
-bodypart & limbs and trousers & arm, finger, leg, toe & \anBodypartAll & \anBodypartI & \anBodypartII & \anBodypartIII & \anBodypartIV & \anBodypartV & \anBodypartVI & \anBodypartVII & \anBodypartVIII \tabularnewline
-
-face & face or parts of it & face, ear, nose, mouth & \anFaceAll & \anFaceI & \anFaceII & \anFaceIII & \anFaceIV & \anFaceV & \anFaceVI & \anFaceVII & \anFaceVIII \tabularnewline
-
-female & female person & nurse, mother, woman & \anFemaleAll & \anFemaleI & \anFemaleII & \anFemaleIII & \anFemaleIV & \anFemaleV & \anFemaleVI & \anFemaleVII & \anFemaleVIII \tabularnewline
-
-females & female persons & women & \anFemalesAll & \anFemalesI & \anFemalesII & \anFemalesIII & \anFemalesIV & \anFemalesV & \anFemalesVI & \anFemalesVII & \anFemalesVIII \tabularnewline
-
-fname & female name & Jenny & \anFnameAll & \anFnameI & \anFnameII & \anFnameIII & \anFnameIV & \anFnameV & \anFnameVI & \anFnameVII & \anFnameVIII \tabularnewline
-
-furniture & movable objects insides/outsides & bench, bed, table, chair & \anFurnitureAll & \anFurnitureI & \anFurnitureII & \anFurnitureIII & \anFurnitureIV & \anFurnitureV & \anFurnitureVI & \anFurnitureVII & \anFurnitureVIII \tabularnewline
-
-geo & immobile landmarks & building, tree, street, alley, meadow, cornfield, river & \anGeoAll & \anGeoI & \anGeoII & \anGeoIII & \anGeoIV & \anGeoV & \anGeoVI & \anGeoVII & \anGeoVIII \tabularnewline
-
-geo-room & rooms / locales; elements defining a locale's spatial layout & living room; wall, door, window, floor, turf & \anGeoroomAll & \anGeoroomI & \anGeoroomII & \anGeoroomIII & \anGeoroomIV & \anGeoroomV & \anGeoroomVI & \anGeoroomVII & \anGeoroomVIII \tabularnewline
-
-head & non-face parts of the head; worn headgear & head, hair, ear, neck, helmet & \anHeadAll & \anHeadI & \anHeadII & \anHeadIII & \anHeadIV & \anHeadV & \anHeadVI & \anHeadVII & \anHeadVIII \tabularnewline
-
-male & male person & man, father, soldier & \anMaleAll & \anMaleI & \anMaleII & \anMaleIII & \anMaleIV & \anMaleV & \anMaleVI & \anMaleVII & \anMaleVIII \tabularnewline
-
-males & male persons & boys, opponents & \anMalesAll & \anMalesI & \anMalesII & \anMalesIII & \anMalesIV & \anMalesV & \anMalesVI & \anMalesVII & \anMalesVIII \tabularnewline
-
-mname & male name & Bubba, Kennedy & \anMnameAll & \anMnameI & \anMnameII & \anMnameIII & \anMnameIV & \anMnameV & \anMnameVI & \anMnameVII & \anMnameVIII \tabularnewline
-
-object & countable entity with firm boundarie & telephone, car & \anObjectAll & \anObjectI & \anObjectII & \anObjectIII & \anObjectIV & \anObjectV & \anObjectVI & \anObjectVII & \anObjectVIII \tabularnewline
-
-objects & countable entities with firm boundaries &  wheels, photos & \anObjectsAll & \anObjectsI & \anObjectsII & \anObjectsIII & \anObjectsIV & \anObjectsV & \anObjectsVI & \anObjectsVII & \anObjectsVIII \tabularnewline
-
-persons & concrete persons of unknown sex / gender & hippies, patients & \anPersonsAll & \anPersonsI & \anPersonsII & \anPersonsIII & \anPersonsIV & \anPersonsV & \anPersonsVI & \anPersonsVII & \anPersonsVIII \tabularnewline
-
-setting\_new & setting mentioned for the first time &  on a ``bridge'', on an ``alley'', on ``campus'' & \anSettingnewAll & \anSettingnewI & \anSettingnewII & \anSettingnewIII & \anSettingnewIV & \anSettingnewV & \anSettingnewVI & \anSettingnewVII & \anSettingnewVIII \tabularnewline
-
-setting\_rec & recurring setting & at the ``bus stop'' & \anSettingrecAll &
+body & \anBodyAll & \anBodyI & \anBodyII & \anBodyIII & \anBodyIV & \anBodyV & \anBodyVI & \anBodyVII & \anBodyVIII \tabularnewline
+bodypart &  \anBodypartAll & \anBodypartI & \anBodypartII & \anBodypartIII & \anBodypartIV & \anBodypartV & \anBodypartVI & \anBodypartVII & \anBodypartVIII \tabularnewline
+face & \anFaceAll & \anFaceI & \anFaceII & \anFaceIII & \anFaceIV & \anFaceV & \anFaceVI & \anFaceVII & \anFaceVIII \tabularnewline
+female & \anFemaleAll & \anFemaleI & \anFemaleII & \anFemaleIII & \anFemaleIV & \anFemaleV & \anFemaleVI & \anFemaleVII & \anFemaleVIII \tabularnewline
+females & \anFemalesAll & \anFemalesI & \anFemalesII & \anFemalesIII & \anFemalesIV & \anFemalesV & \anFemalesVI & \anFemalesVII & \anFemalesVIII \tabularnewline
+fname & \anFnameAll & \anFnameI & \anFnameII & \anFnameIII & \anFnameIV & \anFnameV & \anFnameVI & \anFnameVII & \anFnameVIII \tabularnewline
+furniture & \anFurnitureAll & \anFurnitureI & \anFurnitureII & \anFurnitureIII & \anFurnitureIV & \anFurnitureV & \anFurnitureVI & \anFurnitureVII & \anFurnitureVIII \tabularnewline
+geo & \anGeoAll & \anGeoI & \anGeoII & \anGeoIII & \anGeoIV & \anGeoV & \anGeoVI & \anGeoVII & \anGeoVIII \tabularnewline
+geo-room & \anGeoroomAll & \anGeoroomI & \anGeoroomII & \anGeoroomIII & \anGeoroomIV & \anGeoroomV & \anGeoroomVI & \anGeoroomVII & \anGeoroomVIII \tabularnewline
+head & \anHeadAll & \anHeadI & \anHeadII & \anHeadIII & \anHeadIV & \anHeadV & \anHeadVI & \anHeadVII & \anHeadVIII \tabularnewline
+male & \anMaleAll & \anMaleI & \anMaleII & \anMaleIII & \anMaleIV & \anMaleV & \anMaleVI & \anMaleVII & \anMaleVIII \tabularnewline
+males & \anMalesAll & \anMalesI & \anMalesII & \anMalesIII & \anMalesIV & \anMalesV & \anMalesVI & \anMalesVII & \anMalesVIII \tabularnewline
+mname & \anMnameAll & \anMnameI & \anMnameII & \anMnameIII & \anMnameIV & \anMnameV & \anMnameVI & \anMnameVII & \anMnameVIII \tabularnewline
+object & \anObjectAll & \anObjectI & \anObjectII & \anObjectIII & \anObjectIV & \anObjectV & \anObjectVI & \anObjectVII & \anObjectVIII \tabularnewline
+objects & \anObjectsAll & \anObjectsI & \anObjectsII & \anObjectsIII & \anObjectsIV & \anObjectsV & \anObjectsVI & \anObjectsVII & \anObjectsVIII \tabularnewline
+persons & \anPersonsAll & \anPersonsI & \anPersonsII & \anPersonsIII & \anPersonsIV & \anPersonsV & \anPersonsVI & \anPersonsVII & \anPersonsVIII \tabularnewline
+
+setting\_new & \anSettingnewAll & \anSettingnewI & \anSettingnewII & \anSettingnewIII & \anSettingnewIV & \anSettingnewV & \anSettingnewVI & \anSettingnewVII & \anSettingnewVIII \tabularnewline
+
+setting\_rec & \anSettingrecAll &
 \anSettingrecI & \anSettingrecII & \anSettingrecIII & \anSettingrecIV & \anSettingrecV & \anSettingrecVI & \anSettingrecVII & \anSettingrecVIII \tabularnewline
-++ & nouns, adverbial adjectives and adverbs & in the ``evening'', it's ``daytime'', ``later'' &  anAll & \anI & \anII & \anIII & \anIV & \anV & \anVI & \anVII & \anVIII \tabularnewline
-aDescrV & aDescrVI & aDescrVII & aDescrVIII \tabularnewline
+++ & \anAll & \anI & \anII & \anIII & \anIV & \anV & \anVI & \anVII & \anVIII \tabularnewline
 \bottomrule

### 2020-05-12 code/plot-corr-of-regressors.py
script that creates figures for correlation of regressors

@@ -1,0 +1,190 @@
+#!/usr/bin/env python3
+'''
+created on Sun March 29 2020
+author: Christian Olaf Haeusler
+'''
+from glob import glob
+import argparse
+import matplotlib
+import matplotlib.pyplot as plt
+import numpy as np
+import os
+import pandas as pd
+import re
+import seaborn as sns
+matplotlib.use('Agg')
+
+
+AO_USED = [1, 2, 3, 4, 5, 6, 7, 8, 9, 10, 11, 12, 13, 14, 15, 16, 17, 18]
+AO_NAMES = { 1: 'body',
+             2: 'bpart',
+             3: 'fahead',
+             4: 'furn',
+             5: 'geo',
+             6: 'groom',
+             7: 'object',
+             8: 'se_new',
+             9: 'se_old',
+            10: 'sex_f',
+            11: 'sex_m',
+            12: 'vse_new',
+            13: 'vse_old',
+            14: 'vlo_ch',
+            15: 'vpe_new',
+            16: 'vpe_old',
+            17: 'fg_ad_lrdiff',
+            18: 'fg_ad_rms'
+            }
+
+AV_USED = [1, 2, 3, 4, 5, 6, 7, 8, 9, 10, 11, 12, 13, 14]
+AV_NAMES = { 1: 'vse_new',
+             2: 'vse_old',
+             3: 'vlo_ch',
+             4: 'vpe_new',
+             5: 'vpe_old',
+             6: 'vno_cut',
+             7: 'se_new (ao)',
+             8: 'se_old (ao)',
+             9: 'fg_av_ger_lr',
+            10: 'fg_av_ger_lr_diff',
+            11: 'fg_av_ger_ml',
+            12: 'fg_av_ger_pd',
+            13: 'fg_av_ger_rms',
+            14: 'fg_av_ger_ud'
+            }
+
+def parse_arguments():
+    '''
+    '''
+    parser = argparse.ArgumentParser(
+        description="creates the correlation of convoluted regressors from \
+        a subject's 1st lvl results directories (= all single run dirs ")
+
+    parser.add_argument('-ao',
+                        default='inputs/studyforrest_ppa/'\
+                        'sub-01/run-1_audio-ppa-grp.feat/design.mat',
+                        help='pattern of path/file for 1st lvl design files')
+
+    parser.add_argument('-av',
+                        default='inputs/studyforrest_ppa/'\
+                        'sub-01/run-1_movie-ppa-grp.feat/design.mat',
[…]

### 2020-05-12 paper/main.tex
add figure to manuscript

@@
 
+\todo[inline]{in der Abbildung der Regressoren-Korrelationen sind jetzt alle
+    Regressoren drin; imo könnte man ein paar herausnehmen (die zur Kontrolle
+    benutzen Filmschnitt-Regressoren in der AO-Analyse, die zur Kontrolle
+    benutzen Descriptive-Nouns Regressoren (namentlich se\_new und se\_old), und ggf. [ein paar der] low-level features nuissance regressors.}
+
+\begin{figure*} \centering
+    \includegraphics[width=\linewidth]{figures/regressor-corr} \caption{Pearson
+        correlation coefficients of the regressors used in the analysis of the
+        audio-description (blue; see Table \ref{tab:ao-events} for a
+        description) and audio-visual movie (red; see Table
+        \ref{tab:av-events}). Regressors were convolved with FSL's
+        ``Double-Gamma HRF'' as a model of the hemodynamic response function,
+        temporally filtered with the same high-pass filter (cut-off
+        \unit[150]{s}) as the BOLD time series, and concatenated across runs
+    before performing the correlation.}
+    \label{fig:reg-corr}
+\end{figure*}
+
 \paragraph{audio stimulus: contrasts of parameter estimate}

### 2020-05-13 paper/main.tex
add info (stimuli, procedurem, fmri acq./setup) from Sengupta (2016)

@@
 
+\todo[inline]{Nach wie vor recht ausführlich; Reihenfolge der subsections mag
+``inkorrekt'' sein.}
+
+% Intro
 We used data from three publicly available datsets as part of the studyforrest
@@
 been used by other research groups for independent research questions before.
-
-We used fMRI data from 14 subjects who took part in three different studies. Namely, the same subjects were
-
+% used studies
+We fMRI data from three different studies. The same subjects were
+% AO
 a) listening to the audio-description (AO study; \citep{hanke2014audiomovie}) of
-the movie ``Forrest Gump'', a dataset already used by \citep{hu2017decoding}.
+the movie ``Forrest Gump'', a dataset already used by \citep{hu2017decoding, nguyen2016integration}.
+% AV
 b) watching the actual audio-visual movie (AV study;
 \citep{hanke2016simultaneous}, a dataset already used by
-\citep{ben2018hippocampal}. c) participating in a dedicated block-wise visual
-localizer (LOC study) \citep{sengupta2016extension}, a dataset aready used by
-\citep{jiahui2019predicting}.
+\citep{ben2018hippocampal}.
+% VIS
+c) participating in a dedicated six-category
+block-design visual localizer (VIS study) \citep{sengupta2016extension}, a dataset aready used by \citep{jiahui2019predicting}.
 
@@
 
-\todo[inline]{Alles um Sengupta ergänzen}
-
 \subsection{Participants}
@@
 \todo[inline]{inner join von AO \& AV: N=14; AO: N=19; es fehlt in beiden VP10;
-Angaben zu Alter (Durchschnitt; ggf. Range) und Geschlecht sind folglich falsch}
-
-In the AO study, 19 participants (all right-handed, age 21–38 years, mean age
-26.6 years, 12 male) listened to the German audio-description
+Angaben zu Alter (Durchschnitt; ggf. Range) und Geschlecht sind folglich falsch
+=> hier stehen lassen und unter Data erwähnen, dass die nicht benutzt wurde}
+% AO study
+In the AO study, 19 German native speakers (all right-handed, age 21–38 years,
+mean age 26.6 years, 12 male) listened to the German audio-description
 \citep{ForrestGumpGermanAD} of the movie ``Forrest Gump''
 \citep{ForrestGumpMovie} as an additional audio track for visually impaired
-listeners on Swiss public television. In the AV study, the same 14 participants
-(21–39 years, mean age 29.4, six female) watched the audio-visual movie with dubbed German audio track \citep{ForrestGumpDVD}.
-All participants reported to have normal hearing, normal or corrected-to-normal vision, and no known history of neurological disorders.
-
-\todo[inline]{Sengupta (2016)}
-In the LOC study\dots
-
-In both studies, participants received monetary compensation and gave written informed consent for their participation and for public sharing of all obtained data in anonymized form.
-The studies had prior approval by the Ethics Committee of Otto-von-Guericke University of Magdeburg, Germany.
+listeners on Swiss public television.  was Germin
+% AV study
+In the AV study, 15 participants (21–39 years, mean age 29.4, six female) of the
+prior AO study watched the audio-visual movie with dubbed German audio track
+\citep{ForrestGumpDVD}.
+% VIS study
+In the VIS study, the same 15 participants took part in a six-category
+block-design visual localizer.
+% participants' health
+All participants reported to have normal hearing, normal or corrected-to-normal
+vision, and no known history of neurological disorders.
+% compensation, consent and shit
+In all both studies, participants received monetary compensation and gave
+written informed consent for their participation and for public sharing of all
+obtained data in anonymized form. The studies had prior approval by the Ethics
+Committee of Otto-von-Guericke University of Magdeburg, Germany.
 
 \subsection{Stimuli}
-% stimulus name & references
+% AO & AV stimulus name & references
 We used the German DVD release \citep{ForrestGumpDVD} of
@@
 that was broadcast as an additional audio track for visually impaired listeners
-on Swiss public televinsion \citep{ForrestGumpGermanAD}.
-
-% difference in audio track AV vs. AO
+on Swiss public television \citep{ForrestGumpGermanAD}.
+% AO vs. AV: differences
 The plot of the movie is already carried by an off-screen voice of the main
@@
 
-% stimulus creation
+% AO & AV: stimulus creation
 The audio-description was temporally aligned to the audio track of the German
@@
 used to split the segments (s. Figure 3a in \citep{hanke2014audiomovie}.
-
-\todo[inline]{Sengupta (2016)}
+% AV: grey bars
+Black horizontal bars at the top and bottom of stimulus of the AV study were
+replaced with medium-gray bars of the same size in order to increase back-
+ground illumination for a more pleasant experience.
+
+% VIS study
+% picture categories
+All stimuli for the VIS study were used in a previous study
+\citep{haxby2011common}. There were 24 unique grayscale images (matched in
+luminance, size of 400 $\times$\unit[400]{px}) from each of six stimulus
+categories: human faces, human bodies without heads, small objects, houses and
+outdoor scenes comprising of nature and street scenes, and phase scrambled
+images. Mirrored views of these 24 $\times$ 6 images were also used as stimuli.
 
@@
 \subsection{Procedure}
-
-In both [all three] studies, participants filled out a questionnaire on their
-basic demographic information and familiarity with the audio-description or the
-movie. Participants were instructed to inhibit physical movements except for
+% questionnaire
+In all three studies, participants filled out a questionnaire on their basic
+demographic information (and familiarity with the audio-description or movie).
+% AO & AV: instructions
+Participants were instructed to inhibit physical movements except for
 eye-movements, and otherwise to simply ``enjoy the audiobook'' or ``enjoy the
-movie'' respectively. Audio-description and movie segments were presented in
-chronological order with four segments in two fMRI sessions respectively.
-Between sessions, participants left the scanner for a break with a flexible
-duration. Structural images were obtained during the first study on a day
-different from the fMRI session.
+movie'' respectively.
+% AO & AV: presentation & instructions
+Audio-description and movie segments were presented in chronological order with
+four segments in two fMRI sessions respectively.  Between sessions, participants
+left the scanner for a break with a flexible duration. Structural images were
+obtained during the first study on a day different from the fMRI session.
+% VIS: presentation & instructions
+In the VIS study, participants were presented with four block-design runs, with
+two \unit[16]{s} blocks per stimulus category in each run, while they also performed a one-back matching task to keep them attentive.
 
@@
 
-\todo[inline]{irrelevantes kürzen}
-In both studies, stimulation was implemented with \href{http://www.psychopy.org}{PsychoPy} \citep{peirce2007psychopy} running on a computer with the \href{http://neuro.debian.net}{(Neuro)Debian} operating system \citep{halchenko2012open}.
-
+% paradigm implementation
+In all three studies, stimulation was implemented with \href{http://www.psychopy.org}{PsychoPy} \citep{peirce2007psychopy} running on a computer with the \href{http://neuro.debian.net}{(Neuro)Debian} operating system \citep{halchenko2012open}.
+
+% AO
 In the AO study, visual instructions were presented on a rear-projection screen
@@
 
-In the AV study, visual instructions and stimuli were presented on a
+% AV & VIS
+In the AV and VIS study, visual instructions and stimuli were presented on a
 rear-projection screen using an LCD projector (JVC DLA RS66E, JVC Ltd., light
@@
 stimulus computer [via a DVI extender system (Gefen EXT-DVI-142DLN with
-EXT-DVI-FM1000)]. The movie was shown at a viewing distance of \unit[63]{cm} in
-\unit[720]{p} resolution at full width on a \unit[1280 $\times$ 1024]{pixel}
-screen with \unit[60]{Hz} video refresh rate and screen dimension of \unit[26.5
-$\times$ 21.2]{cm}, corresponding to \unit[23.75 $\times$ 13.5] or \unit[23.75
+EXT-DVI-FM1000)].
+% screen size
+The movie was shown at a viewing distance of \unit[63]{cm} in \unit[720]{p}
+resolution at full width on a \unit[1280 $\times$ 1024]{pixel} screen with
+\unit[60]{Hz} video refresh rate and screen dimension of \unit[26.5 $\times$
+21.2]{cm}.
+% angle of view: AV
+In the AV study, this corresponded to \unit[23.75 $\times$ 13.5] or \unit[23.75
 $times$ 10.25]{cm} when considering only the movie content and excluding the
 horizontal gray bars.
-
-In both studies [+++???+++] auditory stimulation was delivered through an MR confon mkII+ driving custom-built in-ear headphones (HP-M01, MR confon GmbH, Magdeburg, Germany; \citep{baumgart1998electrodynamic}) that reduced the scanner noise by at least \unit[20–30]{dB}.
-Headphones were  fed from an Aureon 7.1 USB (Terratec) sound card through an optical connection.
+% angle of view: VIS
+In the VIS study, stimulus images were displayed at a size of approximately
+\unit[10]$^{\circ}$ $\times$ \unit[10]$^{\circ}$ of visual angle.
+
+\todo[inline]{Ist richtig, dass auditory stimulation in beiden Experimenten die
+gleiche war?}
+
+% AO & AV: auditory stimulation
+In the AO and AV study, auditory stimulation was delivered through an MR confon
+mkII+ driving custom-built in-ear headphones (HP-M01, MR confon GmbH, Magdeburg,
+Germany; \citep{baumgart1998electrodynamic}) that reduced the scanner noise by
+at least \unit[20–30]{dB}. Headphones were fed from an Aureon 7.1 USB
+(Terratec) sound card through an optical connection.
 
@@
 
-% AO (Hanke, 2014)
+% AO
 In the AO study, a whole-body \unit[7]{Tesla} Siemens MAGNETOM magnetic
@@
 
-% AV (Hanke, 2016)
-In the AV study, a whole-body \unit[3]{Tesla} Philips Achieva dStream MRI
-scanner equipped with a 32 channel head coil acquired T2*-weighted echo-planar
-images (gradient-echo, \unit[2]{s} repetition time (TR), \unit[30]{ms} echo
-time, \unit[90]{$^{\circ}$} flip angle, \unit[1943]{Hz/Px} bandwidth, parallel
-acquisition with sensitivity encoding (SENSE) reduction factor 2).
+% AV & VIS
+In the AV and VIS study, a whole-body \unit[3]{Tesla} Philips Achieva dStream
+MRI scanner equipped with a 32 channel head coil acquired T2*-weighted
+echo-planar images (gradient-echo, \unit[2]{s} repetition time (TR),
+\unit[30]{ms} echo time, \unit[90]{$^{\circ}$} flip angle, \unit[1943]{Hz/Px}
+bandwidth, parallel acquisition with sensitivity encoding (SENSE) reduction
+factor 2).
 % slices
@@
 used to automatically position slices in AC-PC orientation such that the topmost
-slice was located at the superior edge of the brain.
-\todo[inline]{In the LOC study\dots}
+slice was located at the superior edge of the brain. This automatic slice
+positioning procedure was identical in the AV und VIS study and yielded a
+congruent geometry across paradigms.
 
@@
 
-\todo[inline]{downsampling der 7T Daten}
-
+\todo[inline]{Satz zum Downsampling der 7T Daten? => check github repo}
+
+\todo[inline]{subject 10 was dropped due to excessive motion: see Hanke 2016}
 % data source
@@
 \paragraph{Regressors}
+
+\todo[inline]{Nouns, die eigentlich zu einer anderen Kateogrie als setting\_new
+    or setting\_old gehören, aber einen Settingwechsel anzeigen, werden als
+Event eines der Settingwechsel zugehörig gezählt.}
 

### 2020-05-14 paper/main.tex
formatting changes in manuscript

@@
 
-\todo[inline]{Nach wie vor recht ausführlich; Reihenfolge der subsections mag
-``inkorrekt'' sein.}
-
-% Intro
-We used data from three publicly available datsets as part of the studyforrest
-dataset (\href{http://www.studyforrest.org}{studyforrest.org}) that has already
-been used by other research groups for independent research questions before.
+\todo[inline]{Nach wie vor sind Teile aus den Originalstudien ausführlich}
+
+\todo[inline]{Reihenfolge der subsections mag ``inkorrekt'' sein.}
+
+% intro
+We used data from three publicly available datsets, all being part of the
+studyforrest dataset (\href{http://www.studyforrest.org}{studyforrest.org})
+which has already been used by other research groups for independent research
+questions.
 % used studies
-We fMRI data from three different studies. The same subjects were
+The same subjects were
 % AO
 a) listening to the audio-description (AO study; \citep{hanke2014audiomovie}) of
-the movie ``Forrest Gump'', a dataset already used by \citep{hu2017decoding, nguyen2016integration}.
+the movie ``Forrest Gump'', a dataset already used by \citep{hu2017decoding,
+nguyen2016integration}.
 % AV
@@
 % VIS
-c) participating in a dedicated six-category
-block-design visual localizer (VIS study) \citep{sengupta2016extension}, a dataset aready used by \citep{jiahui2019predicting}.
-
+c) participating in a dedicated six-category block-design visual localizer (VIS
+study) \citep{sengupta2016extension}, a dataset aready used by
+\citep{jiahui2019predicting}.
+% see corresponding papers for details
 An exhaustive description of the participants, stimulus creation, procedure,
@@
 
-\todo[inline]{inner join von AO \& AV: N=14; AO: N=19; es fehlt in beiden VP10;
-Angaben zu Alter (Durchschnitt; ggf. Range) und Geschlecht sind folglich falsch
-=> hier stehen lassen und unter Data erwähnen, dass die nicht benutzt wurde}
+\todo[inline]{inner join von AO \& AV: N=14; AO: N=19; Exklusion von VP10 kommt
+unter ``Data''}
 % AO study
@@
 \citep{ForrestGumpMovie} as an additional audio track for visually impaired
-listeners on Swiss public television.  was Germin
+listeners on Swiss public television.
 % AV study
@@
 % compensation, consent and shit
-In all both studies, participants received monetary compensation and gave
-written informed consent for their participation and for public sharing of all
-obtained data in anonymized form. The studies had prior approval by the Ethics
-Committee of Otto-von-Guericke University of Magdeburg, Germany.
+In all studies, participants received monetary compensation and gave written
+informed consent for their participation and for public sharing of obtained
+data in anonymized form. The studies had prior approval by the Ethics Committee
+of Otto-von-Guericke University of Magdeburg, Germany.
 
@@
 % AO & AV stimulus name & references
-We used the German DVD release \citep{ForrestGumpDVD} of
-the audio-visual movie ``Forrest Gump'' \citep{ForrestGumpMovie} and its
-temporally aligned audio-description (i.e. the audio-only variant of the movie)
-that was broadcast as an additional audio track for visually impaired listeners
-on Swiss public television \citep{ForrestGumpGermanAD}.
+We used the German DVD release \citep{ForrestGumpDVD} of the audio-visual movie
+``Forrest Gump'' \citep{ForrestGumpMovie} and its temporally aligned
+audio-description (i.e. the audio-only variant of the movie) that was broadcast
+as an additional audio track for visually impaired listeners on Swiss public
+television \citep{ForrestGumpGermanAD}.
 % AO vs. AV: differences
 The plot of the movie is already carried by an off-screen voice of the main
-character Forrest Gump.  In the largely identical audio-description, a male
-narrator additionally describes essential aspects of the visual scenery when
-there is no off-screen voice, dialog, or other relevant auditory content.
+character Forrest Gump. In the largely identical audio-description, an
+additional male describes essential aspects of the visual scenery when there is
+no off-screen voice, dialog, or other relevant auditory content.
 
@@
 DVD release. A few scenes less relevant to the major plot were removed to create
-the ``research cut'' lasting $\approx$2h
-\citep{hanke2014audiomovie, hanke2016simultaneous}. Both stimuli were further
-processed (filtering, volume adjustments) to improve audibility during MRI
-scanning. Finally, each stimulus was split into eight segments of approximately
-15 minutes. Except for the first movie segment, each segment started with a
-snippet of at least six seconds immediately preceding the movie scene boundary
-used to split the segments (s. Figure 3a in \citep{hanke2014audiomovie}.
-% AV: grey bars
-Black horizontal bars at the top and bottom of stimulus of the AV study were
-replaced with medium-gray bars of the same size in order to increase back-
-ground illumination for a more pleasant experience.
-
-% VIS study
-% picture categories
+the ``research cut'' lasting $\approx$2h \citep{hanke2014audiomovie,
+hanke2016simultaneous}.
+% further processing
+Both stimuli were further processed (filtering, volume adjustments) to improve
+audibility during MRI scanning. Black horizontal bars at the top and bottom of
+the movie were replaced with medium-gray bars of the same size in order to
+increase background illumination for a more pleasant experience.
+% splitting
+Each stimulus was split into eight segments of approximately 15 minutes. Except
+for the first movie segment, each segment started with a snippet of at least six
+seconds immediately preceding the movie scene boundary used to split the
+segments (see Figure 3a in \citep{hanke2014audiomovie}.
+
+% VIS study picture categories
 All stimuli for the VIS study were used in a previous study
 \citep{haxby2011common}. There were 24 unique grayscale images (matched in
-luminance, size of 400 $\times$\unit[400]{px}) from each of six stimulus
+luminance, size of 400 $\times$\unit[400]{px}) for each of six stimulus
 categories: human faces, human bodies without heads, small objects, houses and
@@
 
-\todo[inline]{um Hinweis bzgl. AV ergänzen}
-
+% AV anno
+For the analysis of the AV data, we took advantage of a publicly available
+annotation of movie cuts and depicted location \citep{haeusler2016cutanno}.
+% AO anno
+For the analysis of the AO data, we extended another publicly available
+annotation of speech \citep{haeusler2020speechanno}. We manually annotated words
+spoken by the audio-description's narrator:
 % annotation procedure
-We extended a publicly available annotation of speech \citep{haeusler2020speechanno} by manually annotating the audio-description's narrator: Two persons performed a categorization of nouns embedded in sentences spoken by the narrator to describe the movie's missing visual content.
+Two persons performed a categorization of nouns embedded in sentences spoken by
+the narrator to describe the movie's missing visual content.
 
@@
 
-% noun categorization
-% Kategorie ``++'' enthält ausnahmesweise auch adverbiale Best. der Zeit.
+% categories Kategorie ``++'' enthält ausnahmesweise auch adverbiale Best. der
+% Zeit.
 The nouns were categorized by the clue they provide about the cinematographic
@@
 (face, head; body, bodypart), and a scene's inherent objects (object,
-furniture). See Table \ref{tab:descr-nouns-counts} for a complete overview of all
-cateogries [+++rules, counts, examples].
-
+furniture). See Table \ref{tab:descr-nouns-counts} for a complete overview of
+all cateogries [+++rules, counts, examples].
+% procedure
 A preliminary annotation was performed by one person according to the rules (see
@@
 In the VIS study, participants were presented with four block-design runs, with
-two \unit[16]{s} blocks per stimulus category in each run, while they also performed a one-back matching task to keep them attentive.
+two \unit[16]{s} blocks per stimulus category in each run, while they also
+performed a one-back matching task to keep them attentive.
 
@@
 \subsection{fMRI data acquisition}
-
-\todo[inline]{irrelevantes kürzen}
-
-In both studies, a total of 3599 volumes were recorded for each participant
-(451, 441, 438, 488, 462, 439, 542, and 338 volumes for movie segment 1–8
-respectively).
 
@@
 
+% no. of volumes
+A total of 3599 volumes were recorded for each participant in each of the
+naturalistic stimulus paradigms (451, 441, 438, 488, 462, 439, 542, and 338 volumes for segment 1–8 respectively).
+
 \subsection{Preprocessing}
@@
 
-\todo[inline]{cite sengupta2016 where this was first done and described, ie same image/data was used here}
+\todo[inline]{motion correction \& Templateerstellung: cite sengupta2016 where this was first done and described, ie same
+image/data was used here => dort finde ich nur links
+
+https://github.com/psychoinformatics-de/studyforrest-data-aligned/tree/master/code
+
+https://github.com/psychoinformatics-de/studyforrest-data-templatetransforms}
 
@@
 
-\todo[inline]{subject 10 was dropped due to excessive motion: see Hanke 2016}
 % data source
@@
 \citep{sengupta2016extension}.
+% exclusion of VP 10
+Data of one participant was dropped to due to invalid distortion correction
+during scanning of the AO stimulus
 
@@
 % wieso, weshalb, warum
+We created $t$-contrasts\dots
+% table reference
 See Table \ref{tab:ao-contrasts}

### 2020-05-14 code/convert-histological2grp-space.py
add script that converts probabilistic lobe masks to group space

@@ -1,0 +1,83 @@
+#!/usr/bin/env python3
+'''
+created on Thu May 15 2020
+author: Christian Olaf Haeusler
+'''
+from glob import glob
+import argparse
+import os
+import subprocess
+
+TNT_DIR = 'inputs/studyforrest-data-templatetransforms'
+
+def parse_arguments():
+    '''
+    '''
+    parser = argparse.ArgumentParser(
+        description="converts probabilistic brain lobe masks taken from \
+        Jülich Histological Atlas (part of FSL) and converts them into \
+        group space")
+
+    parser.add_argument('-i',
+                        default='rois-and-masks/mni_prob_*.nii.gz',
+                        help='pattern of Jülich Histological Atlas lobe files')
+
+    args = parser.parse_args()
+
+    inPattern = args.i
+
+    return inPattern
+
+
+def find_files(pattern):
+    '''
+    '''
+    foundFiles = glob(pattern)
+
+    return sorted(foundFiles)
+
+
+def mni_masks_2_grpbold2Tp(mniMask, outFpath, xfmRef, xfmMat):
+    '''transform MNI brain lobe mask to group BOLD 3T phase2 space
+    by calling FSL's flirt -applyxfm
+    '''
+
+    xfmInterp = 'trilinear'
+
+    if not os.path.exists(outFpath):
+        subprocess.call(
+            ['flirt',
+             '-applyxfm',
+             '-in', mniMask,
+             '-out', outFpath,
+             '-ref', xfmRef,
+             '-init', xfmMat,
+             '-interp', xfmInterp,
+             '-paddingsize', '0.0',
+             ]
+        )
+
+    return None
+
+
+if __name__ == "__main__":
+    # get the command line inputs
+    inPattern = parse_arguments()
+
+    lobeFpathes = find_files(inPattern)
+
+    # get the transformation matrix and reference image
+    xfmMat = os.path.join(TNT_DIR, 'templates/grpbold3Tp2/xfm/mni2tmpl_12dof.mat')
+    xfmRef = os.path.join(TNT_DIR, 'templates/grpbold3Tp2/brain.nii.gz')
+
+    if not os.path.exists(xfmRef):
+        subprocess.call(['datalad', 'get', xfmRef])
+
+    if not os.path.exists(xfmMat):
+        subprocess.call(['datalad', 'get', xfmMat])
+
[…]

### 2020-06-29 code/plot-group-and-individuals.py
add script that creates figures of stability, group & individual zmaps

@@ -1,0 +1,789 @@
+#!/usr/bin/env python3
+'''
+created on Fri June 05 2020
+author: Christian Olaf Haeusler
+'''
+
+import argparse
+from glob import glob
+import matplotlib as mpl
+import matplotlib.pyplot as plt
+import nibabel as nib
+from nilearn import plotting
+from nilearn.image import smooth_img
+import os
+import re
+import subprocess
+
+# underlying anatomical HD image
+anatImg = '/usr/share/data/fsl-mni152-templates/MNI152_T1_0.5mm.nii.gz'
+
+# T2* EPI group FoV
+audioMask = 'rois-and-masks/fov_tmpl_0.5.nii.gz'
+
+# PPA group masks co-registered to MNI152
+PROB_MASK_GRP = 'rois-and-masks/bilat_PPA_prob.nii.gz'
+BIN_MASK_GRP = 'rois-and-masks/bilat_PPA_binary.nii.gz'
+
+# contrasts for audio-only stimulus
+AO_COPE_PATTERN = 'inputs/studyforrest_ppa/3rd-lvl/'\
+    'audio-ppa_c?_z3.4.gfeat/cope1.feat/thresh_zstat1.nii.gz'
+# first six contrasts aim for PPA, rest are control contrasts
+AO_PPA_COPES = range(1, 7)
+# primary PPA contrast
+AUDIO_GRP = AO_COPE_PATTERN.replace('c?', 'c1')
+
+# contrasts of audio-visual stimulus
+AV_COPE_PATTERN = 'inputs/studyforrest_ppa/3rd-lvl/'\
+    'movie-ppa_c?_z3.4.gfeat/cope1.feat/thresh_zstat1.nii.gz'
+# first five contrasts aim for PPA, rests are control contrasts
+AV_PPA_COPES = range(1, 6)
+# primary PPA CONTRAST
+MOVIE_GRP = AV_COPE_PATTERN.replace('c?', 'c1')
+
+# pattern of primary contrasts of individual subjects
+AUDIO_IN_PATTERN = 'inputs/studyforrest_ppa/sub-??/'\
+    '2nd-lvl_audio-ppa-grp.gfeat/cope1.feat/thresh_zstat1.nii.gz'
+MOVIE_IN_PATTERN = 'inputs/studyforrest_ppa/sub-??/'\
[…]

### 2020-06-30 code/plot-bland-altman.py
add script that creates Bland-Altman-Plots

@@ -1,0 +1,404 @@
+#!/usr/bin/env python2
+# -*- coding: utf-8 -*-
+'''
+author: Christian Olaf Häusler
+created on Monday June 29 2020
+
+start ipython2.7 via
+'python2 -m IPython'
+
+'''
+
+from __future__ import print_function
+from glob import glob
+import argparse
+import numpy as np
+import os
+import pandas as pd
+import matplotlib.pyplot as plt
+import nibabel as nib
+import re
+import subprocess
+from mvpa2.datasets.mri import fmri_dataset
+from scipy.stats import gaussian_kde
+
+# check some stuff first
+print(os.getcwd())
+
+# bilateral PPA group mask
+# PPA_GRP_MASK = 'rois-and-masks/bilat_PPA_binary.nii.gz'
+
+# individual FOV mask of the audio drama fMRI data
+AO_FOV_PATTERN = 'rois-and-masks/sub-*/ao_fov_mask.nii.gz'
+
+# individual mask comprising occipital and temporal cortex
+OCCTEMP_MASK_PATTERN = 'rois-and-masks/sub-*/mni_prob_occip_tempo.nii.gz'
+
+# individual, bilateral PPA group mask but in subjects space
+PPA_GRP_SUBJ_PATTERN = 'rois-and-masks/sub-*/grp_PPA_bin.nii.gz'
+
+# binary mask(s) of individual visual localizer (in subject space)
+PPA_MASK_PATTERN = 'inputs/studyforrest-data-visualrois/'\
+    'sub-*/rois/?PPA_?_mask.nii.gz'
+# unthresholded zmap of individual visual localizer (in subject space)
+VLOC_ZMAP_PATTERN = 'inputs/studyforrest-data-visualrois/'\
+    'sub-*/2ndlvl.gfeat/cope*.feat/stats/zstat1.nii.gz'
+
+# contrast used by Sengupta et al. (2016) to create the PPA mask
+VLOC_VPN_COPES = {
+    'sub-01': 'cope8',
+    'sub-02': 'cope3',
+    'sub-03': 'cope3',
+    'sub-04': 'cope3',
+    'sub-05': 'cope3',
+    'sub-06': 'cope3',
+    'sub-09': 'cope3',
+    'sub-14': 'cope3',
+    'sub-15': 'cope3',
+    'sub-16': 'cope3',
+    'sub-17': 'cope3',
[…]

### 2020-07-01 paper/main.tex
some changes to manuscript & references.bib
revision of intro

@@
     wish to use BibTeX to prepare their references should therefore copy the
-    refernce list from the .bbl file that BibTeX generates and paste it into the
-    main manuscript .tex file (and delete the associated
-    \textbackslash{}bibliography and \textbackslash{}bibliographystyle
+    reference list from the .bbl file that BibTeX generates and paste it into
+    the main manuscript .tex file (and delete the associated
+    \textbackslash{}bipliography and \textbackslash{}bibliographystyle
 commands)}
-
-\todo[inline]{Ich arbeite erstmal wie gehabt mit der references.bib
-    und habe oben usepackage{natbib}' eingefügt}
 
@@
 prerequisite for the application of brain imaging methods in individual
-diagnostics (cf. \citep{dubois2016building})
+diagnostics (cf. \citep{dubois2016building, eickhoff2020towards})
 
@@
 
-% Was ist PPA?
+% What is the PPA?
 A classic example of a functional, higher-level visual area is the
@@
 
-% Literature Review PPA: Einleitung
-At a group avergae level, results generalize to mental imagination of landscapes
+% Literature Review PPA: Intro
+At a group average level, results generalize to mental imagination of landscapes
 \citep{ocraven2000mental} and haptic exploration of scenes constructed from LEGO
@@
 
-% Studien im Einzelnen: O'Craven: Mental imagery
+% Exemplary studies
+% O'Craven: Mental imagery
 In the study conducted by \citep{ocraven2000mental} participants viewed
@@
 
-\todo[inline]{Ihre Method Section ist strange und es bei ihr überall eh nur
-    uneinheitliche Grütze heraus; Ich blicke nicht durch; was folgend kommt,
+\todo[inline]{Ihre Method Section ist strange und es kommt bei ihr überall eh
+    nur uneinheitliche Grütze heraus; Ich blicke nicht durch; was folgend kommt,
     wird nicht vollständig korrekt sein. So wie ich es verstanden habe, hat sie
@@
 generic or famous places (e.g. ``The Taj Mahal faces a long thin reflecting
-pool''), faces  (e.g. ``Marylin Monroe has a large square jaw''), or objects
+pool''), faces  (e.g. ``Marilyn Monroe has a large square jaw''), or objects
 (e.g. ``The television has a long antenna')'. Participants were instructed to
@@
 visual(ly) spatial information. This is consistent with a competing hypotheses
-stating the PPA does not process the spatial layout of a scene specifically but
-contextual associations in general (\citep{aminoff2006parahippocampal,
+stating that the PPA does not process the spatial layout of a scene specifically
+but contextual associations in general (\citep{aminoff2006parahippocampal,
 aminoff2013role}). It is still uncertain if auditory stimuli lead to inhibitory
@@
 % Shortcomings of previous studies; lack of research
-All revied studies used a just a small set of carefully designed, simplified
+All reviewed studies used a just a small set of carefully designed, simplified
 stimuli to strictly control experimental conditions. They further relied on
-explicit judgment-based tasks to ensured that participants payed attention to
+explicit judgment-based tasks to ensure that participants payed attention to
 the stimuli. This raises the question how the PPA behaves under life-like conditions.
-
-\todo[inline]{Data-driven vs. model-driven analyses ist komplett raus; in
-Discussion bringen (vgl. Speech-Anno-Paper}
 
@@
 % Literature review naturalistic stimuli: Einleitung
-Two early studies using naturalistic stimuli suggest functional specialization is preserved during free viewing of a movie when many areas respond simultaneously and interact [+++ der Schlusssatz ist aus hasson und bartels plagiiert \citep{bartels2004mapping, hasson2004intersubject}+++]
+Two early studies using naturalistic stimuli suggest functional specialization
+of brain areas is preserved during movie watching when many perceptual and
+cognitive processes are triggered simultaneously \citep{bartels2004mapping, hasson2004intersubject}.
 
@@
 human bodies in a 22 minute clip of the movie \textit{Tomorrow Never Dies}
-[+++Ref+++].
+\citep{tomorrowneverdies}.
 Employing a general linear model (GLM) to model hemodynamic activity, these time
@@
 Employing a reverse intersubject correlation, \citep{hasson2004intersubject}
-used a 30 minute clip of the movie \textit{The Good, the Bad, the Ugly}
-[+++Ref+++]. fMRI
-brain volumes showing the highest hemodynamic activity in the PPA [across (five)
-participants] were matched to the temporally corresponding movie frames.
-Results revealed that corresponding movie frames depicted indoor and outdoor
-scenes including buildings and open fields.
+used a 30 minute clip of the movie \textit{The Good, the Bad, and the Ugly}
+\citep{goodbadugly} fMRI brain volumes showing the highest hemodynamic activity
+in the PPA [across (five) participants] were matched to the temporally
+corresponding movie frames. Results revealed that corresponding movie frames
+depicted indoor and outdoor scenes including buildings and open fields.
 
@@
 
-d) Possibly cite https://psyarxiv.com/sdbqv/ and declare that this study is
-a concrete realization of that promise}
-
-\todo[inline]{Präteritum oder Präsens? Ist momentan gemischt; find's ok so}
-
-\todo[inline]{Inner join of AV \& AO: N=14}
-
-% What we did: Einleitung
+d) Possibly cite https://psyarxiv.com/sdbqv/ (DuPre (2019). Nature abhors a
+paywall) and declare that this study is a concrete realization of that promise}
+
+% what we did data source
 In this study, we analyze data of three publicly available datasets from the
 same set of 14 participants as part of the studyforrest data set
-(\href{http://www.studyforrest.org}{studyforrest.org}). We exploratorily
-investigate how the parahippocampal gyrus [or more general ``human brain''?]
-responds to ``spatially relevant'' events embedded in a 2h audio-visual movie
-\citep{hanke2016simultaneous} and its audio-description (i.e. the audio-only
-variant) of the same length \citep{hanke2014audiomovie}. We compare these
-results to PPA localizations that were obtained from a dedicated visual
-localizer experiment \citep{sengupta2016extension}.
-
-Both natural stimuli were originally designed to entertain an audience and to capture attention free from any perceptual or behavioral task.
-We annotated events in the otherwise unknown temporal structure of both stimuli.
-In/for the movie, we annotated different kinds of cinematographic cuts \citep{haeusler2016cutanno} as presumably ``spatially relevant'' events.
-Our rationale was that cuts re-orient the viewer in the depicted environment
-indepenten from the exact visual content in the movie frame following the cut.
-In/for the audio-description, we annotated verbal clues about the missing visual content given by the audio-description's additional narrator \citep{haeusler2020speechanno}.
-
-In conformity to the analyses performed in the studies using not-naturalistic stimuli, we employed a standard multi-level, voxel-wise general linear model (GLM) % in order to???
-\todo[inline]{in order to\dots}
-
-Encouraged by \citep{aziz2008modulation} and \citep{aminoff2013role}, we focus on the audio-description as a possible life-like stimulus free from any task to localize a ``visual area'' in individual study participants.
+(\href{http://www.studyforrest.org}{studyforrest.org};
+\citep{hanke2014audiomovie, hanke2016simultaneous}).
+% PPA + movie + audio-description
+We annotated cuts in the movie ``Forrest Gump'', and words spoken by an
+additional narrator in the movie's audio-description (i.e. the movie's
+audio-only variant) to exploratorily investigate how the parahippocampal gyrus
+behaves during lifelike stimulation.
+% model-driven analysis
+In conformity to the analyses performed in the reviewed studies,  we also
+employed a standard multi-level, voxel-wise general linear model
+(GLM).\todo{why? in order to\dots}
+% focus on audio-description
+Encouraged by \citep{aziz2008modulation} and \citep{aminoff2013role}, we focus
+on the audio-description as a naturalistic, auditory-only paradigm free from any task to localize a ``visual area'' in individual study participants.
+% comparison to dedicated localizer
+Finally, we compare our results to results of a dedicated visual localizer
+experiment done with the same 14 participants \citep{sengupta2016extension}.
 
@@
 citation (see Data Records and Data Citations, below)}
-
-\todo[inline]{Nach wie vor sind Teile aus den Originalstudien ausführlich}
-
-\todo[inline]{Reihenfolge der subsections mag ``inkorrekt'' sein.}
+\todo[inline]{order of subsections possibly wrong}
+\todo[inline]{parts from original studies still detailed}
 
 % intro
-We used data from three publicly available datsets, all being part of the
+We used data from three publicly available datasets, all being part of the
 studyforrest dataset (\href{http://www.studyforrest.org}{studyforrest.org})
@@
 % used studies
+\todo{this is just loveless listing so far but it's 'complete'}
 The same subjects were
@@
 c) participating in a dedicated six-category block-design visual localizer (VIS
-study) \citep{sengupta2016extension}, a dataset aready used by
+study) \citep{sengupta2016extension}, a dataset already used by
 \citep{jiahui2019predicting}.
@@
 \subsection{Naturalistic stimuli annotation}
+
+Both natural stimuli were originally designed to entertain an audience and to capture attention free from any perceptual or behavioral task.
+We annotated events in the otherwise unknown temporal structure of both stimuli.
+In/for the movie, we annotated different kinds of cinematographic cuts \citep{haeusler2016cutanno} as presumably ``spatially relevant'' events.
+Our rationale was that cuts re-orient the viewer in the depicted environment
+independent from the exact visual content in the movie frame following the cut.
+In/for the audio-description, we annotated verbal clues about the missing visual content given by the audio-description's additional narrator \citep{haeusler2020speechanno}.
 
@@
 Compared to specifically designed paradigms, the complexity of a natural stimulus goes hand in hand with an unknown temporal structure unless the stimulus is - often manually - annotated \citep{haeusler2016annotation, labs2015portrayed}.
+\todo[inline]{why naturalistic stimuli are so cool: sinkusare2019,
+    eickhoff2020}
+\todo[inline]{model-driven vs. data-driven analyses}
 % Due to their continuity, complexity, and length, they offer a vast amount of data on a variety of brain functions like low-level perception, attention, comprehension, memory, emotions, or social interactions.

### 2020-07-01 paper/main.tex
revision of Methods until preprocessing

@@
 % what we did data source
-In this study, we analyze data of three publicly available datasets from the
-same set of 14 participants as part of the studyforrest data set
-(\href{http://www.studyforrest.org}{studyforrest.org};
-\citep{hanke2014audiomovie, hanke2016simultaneous}).
+In this study, we analyze functional data of the same 14 participants provided
+by the studyforrest dataset \href{http://www.studyforrest.org}{studyforrest.org}; \citep{hanke2014audiomovie, hanke2016simultaneous}).
 % PPA + movie + audio-description
@@
 % intro
-We used data from three publicly available datasets, all being part of the
-studyforrest dataset (\href{http://www.studyforrest.org}{studyforrest.org})
-which has already been used by other research groups for independent research
-questions.
+We used data from three publicly available datasets
+(\href{http://www.studyforrest.org}{studyforrest.org}) which have already been
+used by other research groups for independent research questions.
 % used studies
-\todo{this is just loveless listing so far but it's 'complete'}
-The same subjects were
+\todo{this is just loveless listing so far but it's 'complete'} The same
+subjects were
 % AO
@@
 the movie ``Forrest Gump'', a dataset already used by \citep{hu2017decoding,
-nguyen2016integration}.
+nguyen2016integration},
 % AV
@@
 \citep{hanke2016simultaneous}, a dataset already used by
-\citep{ben2018hippocampal}.
+\citep{ben2018hippocampal},
 % VIS
@@
 publications \citep{hanke2014audiomovie, hanke2016simultaneous,
-sengupta2016extension}. Following is a brief summary of most important aspects.
+sengupta2016extension}. Following is a summary of most important aspects.
 
 \subsection{Participants}
-
-\todo[inline]{inner join von AO \& AV: N=14; AO: N=19; Exklusion von VP10 kommt
-unter ``Data''}
 % AO study
-In the AO study, 19 German native speakers (all right-handed, age 21–38 years,
-mean age 26.6 years, 12 male) listened to the German audio-description
-\citep{ForrestGumpGermanAD} of the movie ``Forrest Gump''
-\citep{ForrestGumpMovie} as an additional audio track for visually impaired
-listeners on Swiss public television.
+In the AO study \citep{hanke2014audiomovie}, 20 German native speakers (all
+right-handed, age 21–38 years, mean age 26.6 years, 12 male) listened to the
+German audio-description \citep{ForrestGumpGermanAD} of the movie ``Forrest
+Gump'' \citep{ForrestGumpMovie} as an additional audio track for visually
+impaired listeners on Swiss public television.
 % AV study
-In the AV study, 15 participants (21–39 years, mean age 29.4, six female) of the
-prior AO study watched the audio-visual movie with dubbed German audio track
-\citep{ForrestGumpDVD}.
+In the AV study \citep{hanke2016simultaneous}, 15 participants (21–39 years,
+mean age 29.4, six female) of the prior AO study watched the audio-visual movie
+with dubbed German audio track \citep{ForrestGumpDVD}.
 % VIS study
-In the VIS study, the same 15 participants took part in a six-category
-block-design visual localizer.
+In the VIS study \citep{sengupta2016extension}, the same 15 participants took
+part in a six-category block-design visual localizer.
+
 % participants' health
@@
 In all studies, participants received monetary compensation and gave written
-informed consent for their participation and for public sharing of obtained
-data in anonymized form. The studies had prior approval by the Ethics Committee
-of Otto-von-Guericke University of Magdeburg, Germany.
+informed consent for their participation and for public sharing of obtained data
+in anonymized form. The studies had prior approval by the Ethics Committee of
+Otto-von-Guericke University of Magdeburg, Germany.
 
@@
 % AO vs. AV: differences
-The plot of the movie is already carried by an off-screen voice of the main
+The plot of the movie is already carried by an off-screen voice-over of the main
 character Forrest Gump. In the largely identical audio-description, an
-additional male describes essential aspects of the visual scenery when there is
-no off-screen voice, dialog, or other relevant auditory content.
+additional male narrator describes essential aspects of the visual scenery when
+there is no off-screen voice, dialog, or other relevant auditory content.
 
@@
 All stimuli for the VIS study were used in a previous study
-\citep{haxby2011common}. There were 24 unique grayscale images (matched in
+\citep{haxby2011common}. There were 24 unique greyscale images (matched in
 luminance, size of 400 $\times$\unit[400]{px}) for each of six stimulus
@@
 annotation of speech \citep{haeusler2020speechanno}. We manually annotated words
-spoken by the audio-description's narrator:
+spoken by the audio-description's narrator.
 % annotation procedure
 Two persons performed a categorization of nouns embedded in sentences spoken by
-the narrator to describe the movie's missing visual content.
-
-\todo[inline]{WARUM WAS WIE annotiert wurde; warum Kategorien so gewählt?}
-
+the narrator to describe the movie's missing visual content. Some categories
+were created in such a way to reflect the six stimulus categories used in the
+visual localizer experiment. Some additional categories were created to
+semantically cluster nouns into categories ``that were obvious to make
+sense''.\todo{yeah, well, sounds shit but that's basically it}.
 % categories Kategorie ``++'' enthält ausnahmesweise auch adverbiale Best. der
 % Zeit.
-The nouns were categorized by the clue they provide about the cinematographic
-scene's environment (geo, geo-room; setting\_new, setting\_old), its inherent
-persons (female, female name; male, male name, person), a person's appearance
-(face, head; body, bodypart), and a scene's inherent objects (object,
-furniture). See Table \ref{tab:descr-nouns-counts} for a complete overview of
-all cateogries [+++rules, counts, examples].
+More specifically, nouns were categorized by the clue they provide about the
+cinematographic scene's environment (geo, geo-room; setting\_new, setting\_old),
+its inherent persons (female, female name; male, male name, person), a person's
+appearance (face, head; body, bodypart), and a scene's inherent objects (object,
+furniture).
+% reference to table
+A complete overview of all categories, the rule for a word to belong to a
+category, and examples can be seen in Table \ref{tab:descr-nouns-rules}.
 % procedure
 A preliminary annotation was performed by one person according to the rules (see
-Table \ref{tab:descr-nouns-rules}). Minor corrections due to incorrectly applied
-rules were by the author.
+Table. Minor corrections due to incorrectly applied rules were by the author (s.
+Table \ref{tab:descr-nouns-counts} for the counts in the whole stimulus and the
+eight stimulus segments used during fMRI scanning).
 
@@
     \caption{Descriptive nouns spoken by the audio-description's narrator:
-    cateogries, annotation rules and examples (given in English).}
+    cateogries, annotation rules and examples (given in English). The categorie
+    \texttt{++} also contains adverbial adjectives and adverbs}
 \label{tab:descr-nouns-rules}
@@
 \tabularnewline
-geo & immobile landmarks & building, tree, street, alley, meadow, cornfield, river \tabularnewline
+geo & immobile landmarks & building, tree, street, alley, meadow, cornfield \tabularnewline
 geo-room & rooms (insides) or  locales (outsides) & living room; wall, door, window, floor, turf \tabularnewline
@@
 setting\_rec & recurring setting & at the ``bus stop'' \tabularnewline
-++ & nouns, adverbial adjectives and adverbs & in the ``evening'', it's ``daytime'', ``later'' \tabularnewline
+++ & cue regarding time & in the ``evening'', it's ``daytime'', ``later'' \tabularnewline
 
@@
 
-% counts Tabelle für descriptiven nouns
+% table of descriptive nouns counts
 \begin{table*}[t]
@@
 In all three studies, participants filled out a questionnaire on their basic
-demographic information (and familiarity with the audio-description or movie).
+demographic information and familiarity with the movie).
 % AO & AV: instructions
@@
 Audio-description and movie segments were presented in chronological order with
-four segments in two fMRI sessions respectively. Between sessions, participants
-left the scanner for a break with a flexible duration. Structural images were
-obtained during the first study on a day different from the fMRI session.
+four segments in two fMRI sessions. Between sessions, participants left the
+scanner for a break with a flexible duration. Structural images were obtained
+during the first study on a day different from the fMRI session.
+
 % VIS: presentation & instructions
@@
 In the AV study, this corresponded to \unit[23.75 $\times$ 13.5] or \unit[23.75
-$times$ 10.25]{cm} when considering only the movie content and excluding the
+$\times$ 10.25]{cm} when considering only the movie content and excluding the
 horizontal gray bars.
@@
 
-\todo[inline]{Ist richtig, dass auditory stimulation in beiden Experimenten die
-gleiche war?}
+\todo[inline]{auditory stimulation was the same in AO and AV?}
 
@@
 direction) with a 10 percent inter-slice gap were recorded in ascending order.
-Slices were oriented to include the ventral portions of frontal and order.
 Slices were oriented to include the ventral the ventral portions of frontal and
@@
 slice was located at the superior edge of the brain. This automatic slice
-positioning procedure was identical in the AV und VIS study and yielded a
+positioning procedure was identical in the AV and VIS study, and yielded a
 congruent geometry across paradigms.
@@
 A total of 3599 volumes were recorded for each participant in each of the
-naturalistic stimulus paradigms (451, 441, 438, 488, 462, 439, 542, and 338 volumes for segment 1–8 respectively).
+naturalistic stimulus paradigms (451, 441, 438, 488, 462, 439, 542, and 338 volumes for segment 1–8).
 
@@
 
-\todo[inline]{bin wie immer bzgl. motion correction \& Templateerstellung unsicher}
-
-\todo[inline]{motion correction \& Templateerstellung: cite sengupta2016 where this was first done and described, ie same
-image/data was used here => dort finde ich nur links
-
-https://github.com/psychoinformatics-de/studyforrest-data-aligned/tree/master/code
-
-https://github.com/psychoinformatics-de/studyforrest-data-templatetransforms}
-
+\todo[inline]{as usually I am pretty unsure about correct report of motion
+correction \& template creation}
 \todo[inline]{Satz zum Downsampling der 7T Daten? => check github repo}
-
-% data source
+% data sources
+% https://github.com/psychoinformatics-de/studyforrest-data-aligned/tree/master/code
+% https://github.com/psychoinformatics-de/studyforrest-data-templatetransforms}
 fMRI time series data were obtained from

### 2020-07-01 paper/main.tex
revision of Methodes until COPEs

@@
 fname & female name & Jenny \tabularnewline
-furniture & moveable objects insides and outsides & bench, bed, table, chair
+furniture & moveable furniture insides \& outsides & bench, bed, table, chair
 \tabularnewline
@@
 mname & male name & Bubba, Kennedy \tabularnewline
-object & countable entity with firm boundarie & telephone, car \tabularnewline
+object & countable entity with firm boundaries & telephone, car \tabularnewline
+objects & countable entities & wheels, plants \tabularnewline
 persons & concrete persons of unknown sex & hippies, patients \tabularnewline
-setting\_new & setting mentioned for the first time &  on a ``bridge'', on an ``alley'', on ``campus'' \tabularnewline
-setting\_rec & recurring setting & at the ``bus stop'' \tabularnewline
+setting\_new & noun cueing a new setting &  on a ``bridge'', on an ``alley'', on ``campus'' \tabularnewline
+setting\_rec & noun cueing a recurring setting & at the ``bus stop'' \tabularnewline
 ++ & cue regarding time & in the ``evening'', it's ``daytime'', ``later'' \tabularnewline
@@
 
-\todo[inline]{as usually I am pretty unsure about correct report of motion
-correction \& template creation}
-\todo[inline]{Satz zum Downsampling der 7T Daten? => check github repo}
+\todo[inline]{I revised part of motion correction/co-registration but as usually
+I am pretty unsure about correctness}
+\todo[inline]{Satz zum Downsampling der 7T Daten?}.
+
 % data sources
@@
 % https://github.com/psychoinformatics-de/studyforrest-data-templatetransforms}
-fMRI time series data were obtained from
-\href{https://github.com/psychoinformatics-de/studyforrest-data-aligned}{GitHub}.
-Data are already aligned to a subject-specific
-\href{https://github.com/psychoinformatics-de/studyforrest-data-templatetransforms}{3
-Tesla BOLD template} by a rigid body transformation in MCFLIRT
-\citep{jenkinson2002registration} to correct for motion during scanning
-\citep{sengupta2016extension}.
+fMRI time series of those 15 participants that took part in all three
+experiments were obtained from
+\href{https://github.com/psychoinformatics-de/studyforrest-data-aligned}{GitHubi}.
+Data were already corrected for motion and aligned by non-linear warping to a
+particpant-specific BOLD template image \citep{sengupta2016extension}.
 % exclusion of VP 10
-Data of one participant was dropped to due to invalid distortion correction
-during scanning of the AO stimulus
+Data of one participant were dropped to due to invalid distortion correction
+during scanning of the AO stimulus.
 
 % preprocessing intro
-All further analysis steps in the current study were carried out using tools of
+All further analysis steps of the current study were carried out using tools of
 FSL v5.0.9 (\href{https://www.fmrib.ox.ac.uk/fsl}{FMRIB's Software
@@
 applied using FILM (FMRIB's Improved Linear Model; \citep{woolrich2001autocorr})
-to improve estimation efficiency \citep{woolrich2001autocorr}.
+to improve estimation efficiency.
 
@@
 
-For both naturalistic stimli, we conducted a standard two-level general linear
+For both naturalistic stimuli, we conducted a standard two-level general linear
 model (GLM) analysis in FEAT to create subject-specific results ($Z$-maps)
@@
 
-\todo[inline]{Nouns, die eigentlich zu einer anderen Kateogrie als setting\_new
-    or setting\_old gehören, aber einen Settingwechsel anzeigen, werden als
-Event eines der Settingwechsel zugehörig gezählt.}
-
-At the first level analyzing each segment for every subject, we created
-regressors for the AO data from the narrator's descriptive nouns (see Table
-\ref{tab:descr-nouns-counts}) added to the annotation of speech
-\citep{haeusler2020speechanno}. For the AV stimulus, we created regressors from
-events provided by an annotation of movie cuts and depicted locations
-\citep{haeusler2016cutanno}.
+\todo[inline]{better speak of conditions than categories?}
+
+% AO: events
+For the analysis of the AO stimulus, we created regressors correlating with the
+occurrence of descriptive nouns spoken by the narrator that were added to the original annotation of speech \citep{haeusler2020speechanno}.
+% AV events
+For the AV stimulus, we created regressors correlating with annotated movie cuts \citep{haeusler2016cutanno}.
 % https://github.com/psychoinformatics-de/studyforrest-data-annotations/blob/master/code/researchcut2segments.py}
 First, both annotations were split into eight parts corresponding to the eight
-segments used as stimuli during fMRI scanning.
+stimulus segments.
 
 % AO events
-To create regressors for the AO analysis, XY from the XY original categories
-were selected [+++why?+++]. Some categories were pooled / joined / merged
-resulting in 11 new categories to provide more events per category per run.
+All of the original 19 categories of descriptive nouns except \texttt{++} were
+used as events. Some categories that were similar but offered only a small
+amount of counts were pooled resulting in eleven new categories (see Table
+\ref{tab:ao-events}). Events that fall into one of the two setting-related
+category but also into another category were treated as belonging to
+setting-related category (\texttt{se\_new} or \texttt{se\_old}).
+% null regressors
+If a segment did not contain an event of a category, a null regressor was chosen for that segment.
+\todo{wenn ich "null regressor" nehme, darf ich den ganzen Run, glaube ich, in
+der 2nd level Analyse gar nicht benutzen? Hatte, glaube ich, Jeanette Mumford in
+einem ihren Videos mal gesagt}
+% modeling as boxcar function
+Events were were modeled as boxcar function from onset to offset of each word.
 % categories taken from movie cut annotation
-Five categories were created from the annotation of movie cuts to capture
-variance of a change in soundscape after cuts and tu create contrasts of
-cross-modal negative control.
+Five additional categories were created from the annotation of movie cuts and
+modeled as impulse events to capture variance of a possibly confounding change
+of the soundscape after cuts, and to create contrasts of cross-modal negative control.
 % nuissance regressors
-Two regressors reflecting auditory (low-level) features (left-right difference
-in volume and root mean squared volume) aligned to the frame rate of
-(\unit[40]{ms}) were modeled to reduce nuisance effects.
-% siehe Tabelle
-An overview and short explanation of the 11 speech-related and 5 movie
-cut-related categories and the two low-level auditory features ca be found in
-Table \ref{tab:ao-events}.
+Lastly, we used continuous bins of information about two auditory features
+(left-right difference in volume and root mean square energy) that was averaged
+across the length of every movie frame (\unit[40]{ms}) via Python script to
+capture variance correlating with low-level perceptual processes.
+% Reference to table
+A short explanation and counts of the eleven speech-related event categories,
+the five movie cut-related categories, and the two low-level confounds can be
+found in Table \ref{tab:ao-events}.
 
 \begin{table*}[t]
-\caption{Overview of events to build the 18 regressors for the analysis of the audio-only (AO) stimulus.
-Some of the original categories (female, females, fname; male, males, mname; face, head; object, objects; see Table \ref{tab:descr-nouns}) were pooled into new categories (sex\_f; sex\_m; fahead; object).
+\caption{Overview of events to build the 18 regressors for the analysis of the
+audio-only (AO) stimulus. Some of the original categories (female, females,
+fname; male, males, mname; face, head; object, objects; see Table
+\ref{tab:descr-nouns}) were pooled into 11 new categories (sex\_f; sex\_m; fahead; object).
 \texttt{fg\_ad\_lrdiff} (left-right volume difference) and
 \texttt{fg\_ad\_rms} (root mean square volume) represent one event for every movie frame (\unit[40]{ms}).
-For description of control condition for movie cuts see Table \ref{tab:av-events}}
+For a description of the five control conditions for movie cuts see Table
+\ref{tab:av-events}.}
 \label{tab:ao-events}
@@
 fahead & face(parts) or head(parts) & \aoFaheadAll & \aoFaheadI & \aoFaheadII & \aoFaheadIII & \aoFaheadIV & \aoFaheadV & \aoFaheadVI & \aoFaheadVII & \aoFaheadVIII \tabularnewline
-furn & big inventory of rooms (insides/outsides) & \aoFurnAll & \aoFurnI & \aoFurnII & \aoFurnIII & \aoFurnIV & \aoFurnV & \aoFurnVI & \aoFurnVII & \aoFurnVIII \tabularnewline
+furn & moveable furniture insides \& outsides & \aoFurnAll & \aoFurnI & \aoFurnII & \aoFurnIII & \aoFurnIV & \aoFurnV & \aoFurnVI & \aoFurnVII & \aoFurnVIII \tabularnewline
 geo & immobile landmarks & \aoGeoAll & \aoGeoI & \aoGeoII & \aoGeoIII & \aoGeoIV & \aoGeoV & \aoGeoVI & \aoGeoVII & \aoGeoVIII \tabularnewline
@@
 fg\_ad\_lrdiff & left-right volume difference & \aoFgadlrdiffAll & \aoFgadlrdiffI & \aoFgadlrdiffII & \aoFgadlrdiffIII & \aoFgadlrdiffIV & \aoFgadlrdiffV & \aoFgadlrdiffVI & \aoFgadlrdiffVII & \aoFgadlrdiffVIII \tabularnewline
-fg\_ad\_rms & root mean square loudness & \aoFgadrmsAll & \aoFgadrmsI & \aoFgadrmsII & \aoFgadrmsIII & \aoFgadrmsIV & \aoFgadrmsV & \aoFgadrmsVI & \aoFgadrmsVII & \aoFgadrmsVIII \tabularnewline
+fg\_ad\_rms & root mean square (loudness) & \aoFgadrmsAll & \aoFgadrmsI & \aoFgadrmsII & \aoFgadrmsIII & \aoFgadrmsIV & \aoFgadrmsV & \aoFgadrmsVI & \aoFgadrmsVII & \aoFgadrmsVIII \tabularnewline
 \bottomrule
@@
 To create regressors for the AV analysis, we categorized the depicted location
-in the frame following one of the 869 cuts in the movie into five categories:
-1) unfamiliar setting (\texttt{vs\_new}),
-2) familiar setting (\texttt{vs\_old}),
-3) locale switch (\texttt{vlo\_ch}),
-4) unfamiliar perspective (\texttt{vpe\_new}), and
-5) familiar perspective (\texttt{vpe\_old}).
-% no cut condition
-A sixth regressors (\texttt{no\_cut}) was created to build negative control
-contrasts.
-\todo{how no\_cut condition was done; compare no\_speech oben und Masterarbeit}
-% how it was done
-Frames within a longer lasting were pseudo-randomly chosen by the following
-rationale:
-% siehe Tabelle
-An overview and short explanation of these six regressors and six additional
-event categories were of low-level auditory visual features of the movie can be
-found in Table \ref{tab:av-events}.
+in the frame following one of the 869 cuts into five categories
+(cf. Table \ref{tab:av-events}): 1) a cut into an unfamiliar setting
+(\texttt{vse\_new}), 2) familiar setting (\texttt{vse\_old}), 3) a switch of
+locale within a setting (\texttt{vlo\_ch}), 4) a cut into an unfamiliar
+perspective (\texttt{vpe\_new}), and 5) familiar perspective
+(\texttt{vpe\_old}).
+% null regressor
+Here again, a null regressor was chosen for segment if it did not an event for
+of a category.
+% no cut condition: intro
+A sixth regressors (\texttt{no\_cut}) serving a control condition and to created
+to build negative control contrasts. Frames within movie shots lasting at least
+\unit[20]{s} were pseudo-randomly chosen by the following rationale:
+% how they were fitted
+\texttt{no\_cut} event had to have a minimum distance of \unit[10]{s} to a movie
+cut and to another \texttt{no\_cut} events.
+% reference to table
+A short explanation and counts of these six categories modeled as impulse
+events, six additional event categories for low-level auditory and visual
+features of the movie (here again continuous bins lasting \unit[40]{ms}), can be found in Table \ref{tab:av-events}.
 
@@
     \caption{Overview of events to build the 14 regressors for the analysis of the audio-only (AV) stimulus.
-\texttt{fg\_av\_ger\_lr} (left-right difference in ??? of consecutive movie frame).
+\texttt{fg\_av\_ger\_lr} (left-right difference in [+++???+++] of
+consecutive movie frames).
 \texttt{fg\_av\_ger\_pd} (perceptual differences of consecutive frames).
-\texttt{fg\_av\_ger\_ud} (up-down difference in ??? of consecutive movie frames).
+\texttt{fg\_av\_ger\_ud} (up-down difference in [+++???+++] of consecutive movie frames).
 \texttt{fg\_av\_ger\_lrdiff} (left-right volume difference) and \texttt{fg\_av\_ger\_rms} (root mean square volume) represent one event for every movie frame (\unit[40]{ms}).
-For description of control condition for movie cuts see Table \ref{tab:ao-events}}
+For description of the two events categories of the audio-description's
+narrator (\texttt{se\_new} and \texttt{se\_old}) to build contrast
+of negative control see Table \ref{tab:ao-events}}
 \label{tab:av-events}
@@
 fg\_av\_ger\_lr & XYZ & \avFgavgerlrAll & \avFgavgerlrI & \avFgavgerlrII & \avFgavgerlrIII & \avFgavgerlrIV & \avFgavgerlrV & \avFgavgerlrVI & \avFgavgerlrVII & \avFgavgerlrVIII \tabularnewline
-fg\_av\_ger\_lrdiff & XYZ & \avFgavgerlrdiffAll & \avFgavgerlrdiffI & \avFgavgerlrdiffII & \avFgavgerlrdiffIII & \avFgavgerlrdiffIV & \avFgavgerlrdiffV & \avFgavgerlrdiffVI & \avFgavgerlrdiffVII & \avFgavgerlrdiffVIII \tabularnewline
-fg\_av\_ger\_ml & XYZ & \avFgavgermlAll & \avFgavgermlI & \avFgavgermlII & \avFgavgermlIII & \avFgavgermlIV & \avFgavgermlV & \avFgavgermlVI & \avFgavgermlVII & \avFgavgermlVIII \tabularnewline
-fg\_av\_ger\_pd & XYZ & \avFgavgerpdAll & \avFgavgerpdI & \avFgavgerpdII & \avFgavgerpdIII & \avFgavgerpdIV & \avFgavgerpdV & \avFgavgerpdVI & \avFgavgerpdVII & \avFgavgerpdVIII \tabularnewline
-fg\_av\_ger\_rms & XYZ & \avFgavgerrmsAll & \avFgavgerrmsI & \avFgavgerrmsII & \avFgavgerrmsIII & \avFgavgerrmsIV & \avFgavgerrmsV & \avFgavgerrmsVI & \avFgavgerrmsVII & \avFgavgerrmsVIII \tabularnewline
-fg\_av\_ger\_ud & XYZ & \avFgavgerudAll & \avFgavgerudI & \avFgavgerudII & \avFgavgerudIII & \avFgavgerudIV & \avFgavgerudV & \avFgavgerudVI & \avFgavgerudVII & \avFgavgerudVIII \tabularnewline
+fg\_av\_ger\_lrdiff & left-right volume difference & \avFgavgerlrdiffAll & \avFgavgerlrdiffI & \avFgavgerlrdiffII & \avFgavgerlrdiffIII & \avFgavgerlrdiffIV & \avFgavgerlrdiffV & \avFgavgerlrdiffVI & \avFgavgerlrdiffVII & \avFgavgerlrdiffVIII \tabularnewline
+fg\_av\_ger\_ml & +++???+++ & \avFgavgermlAll & \avFgavgermlI & \avFgavgermlII & \avFgavgermlIII & \avFgavgermlIV & \avFgavgermlV & \avFgavgermlVI & \avFgavgermlVII & \avFgavgermlVIII \tabularnewline
+fg\_av\_ger\_pd & +++???+++ & \avFgavgerpdAll & \avFgavgerpdI & \avFgavgerpdII & \avFgavgerpdIII & \avFgavgerpdIV & \avFgavgerpdV & \avFgavgerpdVI & \avFgavgerpdVII & \avFgavgerpdVIII \tabularnewline
+fg\_av\_ger\_rms & root mean square (loudness) & \avFgavgerrmsAll & \avFgavgerrmsI & \avFgavgerrmsII & \avFgavgerrmsIII & \avFgavgerrmsIV & \avFgavgerrmsV & \avFgavgerrmsVI & \avFgavgerrmsVII & \avFgavgerrmsVIII \tabularnewline
+fg\_av\_ger\_ud & +++???+++ & \avFgavgerudAll & \avFgavgerudI & \avFgavgerudII & \avFgavgerudIII & \avFgavgerudIV & \avFgavgerudV & \avFgavgerudVI & \avFgavgerudVII & \avFgavgerudVIII \tabularnewline
 \end{tabular}
@@
 % modeling of regressors from events
-For both stimuli, regressors created from nouns were modeled as boxcar functions
-from the beginning to the end of noun.  Regressors created from movie cuts were
-modeled as boxcar function lasting \unit[200]{ms} after a cut. Finally,
-regressors created from low-level percetual features were modeled as box car
-function from the beginning to the end of the corresponding movie frame lasting
-\unit[40]{ms}. All regressors were convolved with a double gamma canonical
-hemodynamic response function (HRF). Their temporal derivatives were added to
-compensate for small timing differences \citep{friston1998event}.
+Events of both stimuli were convolved with a double gamma hemodynamic response
+function (HRF).
+% reference to figure ``correlation of regressors''
+The Pearson correlation coefficients of the 13 regressors of the AO stimulus and
+12 regressors of the AV stimulus across the time course of all stimulus segments
+can be seen in Figure \ref{fig:reg-corr}.\todo{correct colors on horizontal
+line; drop control regressors from figure}
+% temporal derivatives
+Temporal derivatives were included in the design matrix to compensate for
+regional differences between modeled and actual HRF \citep{friston1998event}.
 % motion parameters
-Six motion parameters were used as additional nuisance regressors.
-% null regressors
-If a segment did not contain a single event for a specific regressor, a null
-regressor was chosen for that segment.
-\todo{wenn ich "null regressor" nehme, darf ich den ganzen Run, glaube ich, in
-der 2nd level Analyse gar nicht benutzen? Hatte, glaube ich, Jeanette Mumford in
-einem ihren Videos mal gesagt} Finally, designs were filtered with the same
+Six motion parameters were also used as additional nuisance regressors.
 % high-pass filtering
-high-pass filter (cutoff period of \unit[150]{s}) as the BOLD time series.
-% siehe Tabelle für Correlation of regressors
-\todo[inline]{hier kommt die Abbildung ``correlation of regressors''; ref to
-fig:reg-corr}
-
-\todo[inline]{in der Abbildung der Regressoren-Korrelationen sind jetzt alle
-    Regressoren drin; imo könnte man ein paar herausnehmen (die zur Kontrolle
-    benutzen Filmschnitt-Regressoren in der AO-Analyse, die zur Kontrolle
-    benutzen Descriptive-Nouns Regressoren (namentlich se\_new und se\_old), und ggf. [ein paar der] low-level features nuissance regressors.}
+Finally, designs were filtered with the same high-pass filter (cutoff period of
+\unit[150]{s}) as the BOLD time series.
 
@@
         description) and audio-visual movie (red; see Table
-        \ref{tab:av-events}). Regressors were convolved with FSL's
-        ``Double-Gamma HRF'' as a model of the hemodynamic response function,
-        temporally filtered with the same high-pass filter (cut-off
+        \ref{tab:av-events}). Regressors were created by convolving the events
+        with FSL's ``Double-Gamma HRF'' as a model of the hemodynamic response
+        function, temporally filtered with the same high-pass filter (cut-off
         \unit[150]{s}) as the BOLD time series, and concatenated across runs
-    before performing the correlation.}
-    \label{fig:reg-corr}
-\end{figure*}
+    before computing the correlation.} \label{fig:reg-corr} \end{figure*}
 

### 2020-07-02 paper/main.tex
revision until results

@@
 fname; male, males, mname; face, head; object, objects; see Table
-\ref{tab:descr-nouns}) were pooled into 11 new categories (sex\_f; sex\_m; fahead; object).
+\ref{tab:descr-nouns-rules}) were pooled into 11 new categories (sex\_f; sex\_m; fahead; object).
 \texttt{fg\_ad\_lrdiff} (left-right volume difference) and
@@
         \unit[150]{s}) as the BOLD time series, and concatenated across runs
-    before computing the correlation.} \label{fig:reg-corr} \end{figure*}
-
-\paragraph{audio stimulus: contrasts of parameter estimate}
-\todo[inline]{Warum ist welche COPES so gemacht und warum COPE 1 die Nummer 1}
-% wieso, weshalb, warum
-We created $t$-contrasts\dots
-% table reference
-See Table \ref{tab:ao-contrasts}
+    before computing the correlation.}
+    \label{fig:reg-corr}
+\end{figure*}
+
+\paragraph{AO: COPEs}
+
+\todo[inline]{Why done this way? Why is no. 1 the one?}
+% intro
+For the AO stimulus, we created eight $t$-contrasts that aimed to isolate the PPA and five contrasts
+for negative control purposes (see Table \ref{tab:ao-contrasts}).
+% PPA contrasts
+Contrasts 6-8: words belonging to the categories \texttt{se\_new} and
+\texttt{se\_old} were very vague in describing a scene compared to the richness
+of a picture. Hence, we assumed smaller probability of successfully isolating
+the PPA (+ recht geringe Anzahl verglichen mit geo, groom) (<- das kommt eher in
+Discussion der Kontraste/Ergebnisse).
+% furniture: blurred border between groom and object
+Furniture was not included in one of the contrast because it can be considered
+as an object or geometry-defining structure of a room.
+
+% negative control contrasts
+Contrasts 9-13 correspond to the contrasts 1-5 of the AV stimulus and served as
+negative controls because increased activation in the PPA could also be
+correlated with moment of cuts and a possible change in the soundscape of a
+scene.
 
 \begin{table*}[t]
-\caption{Contrasts of parameter estimates for the analysis of the audio-only
-    stimulus (AO).
-\texttt{all non-geo} = all non-geo related regressors except furniture.}
+    \caption{Contrasts of parameter estimates for the analysis of
+        the audio-only stimulus (AO).
+\texttt{all non-geo} = body, bodypart, fahead, object, sex\_f, sex\_m). Contrast
+1-8 aim to isolate the PPA.
+Contrast 9-13 serve as negative control at the moments of movie cuts
+with possible changes of the audio tracks soundscape (see Table \ref{tab:av-contrasts}}
+
 \label{tab:ao-contrasts}
@@
 \toprule
-\textbf{nr.} &  \textbf{contrasted} & \textbf{aim/goal} \\
+\textbf{nr.} &  \textbf{contrast} & \textbf{purpose} \\
 \midrule
@@
 2 & geo, groom, se\_new > all non-geo & PPA \tabularnewline
-3 & room, se\_new, se\_old > all non-geo & PPA \tabularnewline
+3 & gro
+om, se\_new, se\_old > all non-geo & PPA \tabularnewline
 4 & geo > all non-geo & PPA \tabularnewline
@@
 
-\paragraph{audio-visual stimulus: contrasts of parameter estimate}
-% wieso, weshalb, warum
-We created a contrast presumably correlating with increased hemodynamic activity
-in the PPA by contrasting different kind of cuts, noteably without controlling
-for the specific visual content depicted in the frame after each cut.
+\paragraph{AV: COPEs}
+
+\todo[inline]{change stability of contrast plot from 6 to 5 COPES (line 40 in
+script)}
+
+\todo[inline]{Why done this way? Why is no. 1 the one?}
+% intro
+For the AV stimulus, we created five contrasts presumably correlating with
+increased hemodynamic activity in the PPA by contrasting different kind of cuts.
+and five contrasts for negative control purposes.
+% no control for frames content
+Notably, this was done without an annotation of the visual content depicted in
+the frame after each cut and statistically controlling confounding variables.
 % cinematographic rationale
-The cinematographic rationale was that - over the course of a movie - cuts shift
-from establishing the setting and the spatial relationships within a setting at
-the beginning of a movie to depicting persons and objects more relevant to the
-subsequently evolved narrative later in the movie {brown2012cinematography;
-mercado2011filmmakers}.
+The cinematographic rationale was that movie tend to establishing the setting
+(\texttt{vse\_new}) and the spatial relationships within a setting
+(\texttt{vpe\_new}) at the beginning of a movie. Later in the movie, the field
+sizes of movie shots tend to decrease when switching back to already established
+settings (\texttt{vse\_old}). Shots within a recurring settings tend to shift to
+depicting persons and objects (\texttt{vpe\_old}) more relevant to the evolved
+narrative \citep{brown2012cinematography, mercado2011filmmakers}.
 % neuroscientific rationale
-The neurocientific rationale was that activity in the PPA is greater when
-participants view novel versus repeated scenes resp. view-points
+The neuroscientific rationale was that simply that activity in the PPA is
+greater when participants view novel versus repeated scenes or view-points.
 \citep{epstein1999parahippocampal}.
 % im Ergebnis
-Hence, we contrasted cuts to a setting occurring for the first time (vse\_new)
-and cuts within a locale depicted for the first time (vpe\_new) with shots to a
-recurring setting (vse\_old) and cuts within a recurring locale (vpe\_old).
+Hence, we created varying contrasts comparing a setting occurring for the first
+time and cuts within a locale depicted for the first time to cuts into recurring
+settings and cuts within a recurring locale.
 
@@
 
-\paragraph{Registration \& smoothing: individuals vs. group}
-
-\todo[inline]{Wie immer bei Co-Registration: bitte prüfen, ob ich es richtig
-geschrieben habe}
-
-\todo[inline]{wie besprochen sind die individuelle Results im
-subject space und werden erst später für die Bland-Altman-Plots nach MNI
-transformiert}
-
-% anatomical alignment of single subjects
+\paragraph{second level (+ alignment)}
+% single subjects (for Bland-Altman-Plots) 1st level
 The GLM analysis that fitted each voxel's time course separately for each
 subject was performed in functional space preserving the orientation of the EPI
-images. For subsequent subject-specific second level results, subject-specific
-BOLD T2* time series were anatomically aligned via linear transformation to a
-subject-specific, study-specific T2* template (s.
-\href{"https://github.com/psychoinformatics-de/studyforrest-data-templatetransforms/blob/master/sub-01/bold3Tp2/brain.nii.gz"}{example})
+images.
+% two ways of co-registration
+For subsequent second level results, we co-registered the subjects in two ways.
+% subject template (for Bland-Altman-Plot of unthresholded maps)
+% \href{"https://github.com/psychoinformatics-de/studyforrest-data-templatetransforms/blob/master/sub-01/bold3Tp2/brain.nii.gz"}{example})
+On the one hand, subject-specific BOLD T1* time series were anatomically aligned
+via linear transformation to a subject-specific, study-specific T1* template
 that served as standard space.
-% anatomical alignment for group results
-For subsequent the third level results averaging contrasts of interest across
-subjects, time series were anatomically aligned via non-linear transformation
-[+++wie genau?+++] to a
-\href{"https://github.com/psychoinformatics-de/studyforrest-data-templatetransforms/blob/master/templates/grpbold3Tp2/brain.nii.gz"}{study-specific
-T2* group template}.
-% MNI co-registration
-To facilitate visualization and identification of cortical structures, this
-reference images was later co-registered to the MNI 152 template with an affine
-transformation (12 degrees of freedom)
+% group template (for group and individual brain slices)
+% https://github.com/psychoinformatics-de/studyforrest-data-templatetransforms/blob/master/templates/grpbold3Tp2/brain.nii.gz"
+On the other hand, time series were aligned via non-linear transformation to a
+study-specific T2* group template.
+% MNI152
+This reference images was later co-registered to the MNI 152 template with an
+affine transformation (12 degrees of freedom) to facilitate visualization and
+identification of cortical structures,
 
@@
 % model
-The second-level analyses which averaged contrast estimates over the eight
+The second level analyses which averaged contrast estimates over the eight
 stimulus segments were carried out using a fixed effects model by forcing the
@@
 Effects; \citep{beckmann2003general, woolrich2004multilevel}.
-% thresholding
+% thresholding (Z>2.3 in subject-space; Z>3.4 in group space)
 (Gaussianised T/F) statistic images were thresholded using clusters determined
-by Z>2.3 and a (corrected) cluster significance threshold of p=.05
+by Z>3.4 and a (corrected) cluster significance threshold of p=.05
 \citep{worsley2001statistical}.
@@
 % model
-Third level analyses which averaged contrast estimates over subjects were
+The third level analysis which averaged contrast estimates over subjects were
 carried out using FLAME stage 1 with automatic outlier detection
@@
 \citep{worsley2001statistical}.
+
 % brain region identification
@@
 % PPA masks
-PPA ROI masks for individual subjects and a PPA group overlap mask were created
-from data provided by \citep{sengupta2016extension}.
-
-\subsection{Erstellung der Masken, spatial transformations}
-
-\subsubsection{plot-group-and-individuals.py}
-
-\subsubsection{plot-bland-altman.py}
-
-% generate-masks.py; DO NOT TOUCH!
-% FOR GROUP:
-% 0. In FSLeyes, manually created probabilistic brain lobe maps from \href{"https://doi.org/10.5281/zenodo.1470761"}{the MNI Structural Atlas} (./data/atlases/mni_prob_*.nii.gz)
-% 1.
-these brain lobe maps were aligned (via FSL's flirt -applyxf with 12 dof) to the \href{"https://github.com/psychoinformatics-de/studyforrest-data-templatetransforms/blob/master/templates/grpbold3Tp2/brain.nii.gz"}{study-specific T2* group template} (./data/atlases/grpbold3Tp2_mni_prob_*.nii.gz)
-% 2.
-from \href{"https://github.com/psychoinformatics-de/studyforrest-data-visualrois"} {sengupta2016extension}: UNIlateral probabilistic group ROI masks (data/masks/*_overlap.nii.gz) -> BIlateral probabilistic & binary grp ROI masks in grp space (.data/masks/bilat_???_prob.nii & .data/masks/bilat_???_binary.nii )
-% FOR SUBJECTS:
-% 1. bilateral grp ROI masks in grp space -> bilateral grp ROI masks in subject space (applywarp; sub-??/masks/grp_*_bin.nii.gz)
-% 2. probabilistic MNI mask -> subject space (via FSL's applywarp)
-% 3. merge probabilistic occipital & temporal mask in subject space
-%	(sub-??/masks/mni_prob_occip_tempo.nii.gz)
-% 4. created subject-specific FOV from 4d 7t audio drama time series
-%	(./sub-??/masks/ao_fov_mask.nii.gz)
-% 5. individual, unilateral ROIs from {sengupta2016extension} were joined and co-registered to MNI 152 (1mm) space, and binarized
-% 6. individual (un)thresholded zmaps (from the COPEs) were co-regi<wstered with MNI 152 (1mm) template.
+PPA ROI masks for individual subjects and a PPA group mask of individual PPAs overlapping were created from data provided by \citep{sengupta2016extension}.
 
@@
 % 8. an audio drama might be suitable as ecologically more valid ``localizer'' for a variety of brain functions.
+
+% Unterschiedliche Qualität der Kontrast
+% Warum wurde Kontrast 1 als Kontrast 1 gewählt; se\_new se\_old sind recht
+% vague in der Beschreibung der Szene verglichen mit Bild; Anzahl der Events
+% ergibt auch noch Sinn;
 

### 2020-07-02 code/plot-corr-of-regressors.py
corrections on script for regressor correlations

@@ -15,7 +15,7 @@ import seaborn as sns
 matplotlib.use('Agg')
 
 
-AO_USED = [1, 2, 3, 4, 5, 6, 7, 8, 9, 10, 11, 12, 13, 14, 15, 16, 17, 18]
+AO_USED = [1, 2, 3, 4, 5, 6, 7, 8, 9, 10, 11, 17, 18]
 AO_NAMES = { 1: 'body',
              2: 'bpart',
              3: 'fahead',
@@ -36,7 +36,7 @@ AO_NAMES = { 1: 'body',
             18: 'fg_ad_rms'
             }
 
-AV_USED = [1, 2, 3, 4, 5, 6, 7, 8, 9, 10, 11, 12, 13, 14]
+AV_USED = [1, 2, 3, 4, 5, 6, 9, 10, 11, 12, 13, 14]
 AV_NAMES = { 1: 'vse_new',
              2: 'vse_old',
              3: 'vlo_ch',
@@ -111,10 +111,10 @@ def plot_heatmap(matrix, outFpath):
     plt.yticks(rotation=0, fontsize=12)
 
     for x in range(0, len(AO_USED)):
-        plt.gca().get_xticklabels()[x].set_color('red')  # black = default
+        plt.gca().get_xticklabels()[x].set_color('blue')  # black = default
 
     for x in range(len(AO_USED), len(AO_USED) + len(AV_USED)):
-        plt.gca().get_xticklabels()[x].set_color('blue')
+        plt.gca().get_xticklabels()[x].set_color('red')
 
     for y in range(len(AO_USED), len(AO_USED) + len(AV_USED)):
         plt.gca().get_yticklabels()[y].set_color('red')

### 2020-07-02 paper/main.tex
add all figures showing brain slices

@@
 % intro
-For the AO stimulus, we created eight $t$-contrasts that aimed to isolate the PPA and five contrasts
-for negative control purposes (see Table \ref{tab:ao-contrasts}).
+For the AO stimulus, we created eight $t$-contrasts that aimed to isolate the PPA and five contrasts for negative control purposes (see Table \ref{tab:ao-contrasts}).
 % PPA contrasts
+\todo[inline]{settin-related regressors have small event count compared to
+geo/groom; probably more importan in discussion}
 Contrasts 6-8: words belonging to the categories \texttt{se\_new} and
@@
 of a picture. Hence, we assumed smaller probability of successfully isolating
-the PPA (+ recht geringe Anzahl verglichen mit geo, groom) (<- das kommt eher in
+the PPA.
 Discussion der Kontraste/Ergebnisse).
@@
 
-\section{audio-only stimulus: results}
-Primary contrast, probability over contrasts (individual clusters per contrasts,
-individuelle Bland-Altman-Plots für primary contrast
+\section{Results}
+% both stimuli
+% group results for primary contrasts
+% stability of contrasts
+% individual PPAs
+
+% AO stimulus
+% Bland-Altman-Plots
+
+\begin{figure*} \centering
+    \includegraphics[width=\linewidth]{figures/group-slices}
+    \caption{group results}
+    \label{fig:group-slices}
+\end{figure*}
+
+\begin{figure*} \centering
+    \includegraphics[width=\linewidth]{figures/stability-slices}
+    \caption{stability of contrasts}
+    \label{fig:stability-slices}
+\end{figure*}
+
+\begin{figure*} \centering
+    \includegraphics[width=\linewidth]{figures/subs-thresh-ppa}
+    \caption{indidvidual PPAs}
+    \label{fig:subs-thresh-ppa}
+\end{figure*}
 
@@
 Clusters sorted by voxel size.
-The first brain structure given contains the voxel with the maximum Z-Value, followed by brain structures from posterior to anterior, and partially covered areas.}
+The first brain structure given contains the voxel with the maximum Z-Value, followed by brain structures from posterior to anterior, and partially covered areas (l.
+= left; r.
+= right; c.
+= cortex; g.
+= gyrus).}
 \label{tab:res-ao-group1}
@@
 
-\section{audio-visual stimulus: results}
-Primary contrast, probability over contrasts (individual clusters per contrasts,
-individuelle Bland-Altman-Plots für primary contrast.
-
 \begin{table*}[t]
@@
 Clusters sorted by voxel size.
-The first brain structure given contains the voxel with the maximum Z-Value, followed by brain structures from posterior to anterior, and partially covered areas.}
+The first brain structure given contains the voxel with the maximum Z-Value,
+followed by brain structures from posterior to anterior, and partially covered
+areas (l. = left; r. = right; c. = cortex; g. = gyrus).}
 \label{tab:res-ao-group1}
@@
 \midrule
-3003 & 0 & 5.31 & 22.5 & -45.5 & -12 & 4.53 & -63.3 & -3.72 & r. lingual gyrus; r cuneal c., intracalarine c., bilaterally occipital fusiform g., temporal fusiform c., posterior parahippocampal c.  \\
+3003 & 0 & 5.31 & 22.5 & -45.5 & -12 & 4.53 & -63.3 & -3.72 & r. lingual g.; r
+cuneal c., intracalcarine c., bilaterally occipital fusiform g., temporal fusiform c., posterior parahippocampal c.  \\
 154 & 6.56E-07 & 4.46 & -35 & -83 & 28 & -32.8 & -86.2 & 21.4 & l. superior lateral occipital c. \\
@@
 Issue like different impact of attentional focus etc can be brought up in the joint paragraph that discussed how such a factor could have differentially impacted the results -- and if that would matter.
-\section{Discussion (audio)}
+\section{Discussion}
+
+\subsection{AO Discussion}
 % Hanke et al.
@@
 
-\section{Discussion (movie)}
+\subsection{AV discussion}
 lore ipsum

### 2020-07-02 paper/main.tex
add caption of group results figure

@@
 % intro
-For the AO stimulus, we created eight $t$-contrasts that aimed to isolate the PPA and five contrasts for negative control purposes (see Table \ref{tab:ao-contrasts}).
+For the AO stimulus, we created eight $t$-contrasts that aimed to isolate the
+PPA and five $t$-contrasts for negative control purposes (see Table \ref{tab:ao-contrasts}).
 % PPA contrasts
-\todo[inline]{settin-related regressors have small event count compared to
-geo/groom; probably more importan in discussion}
+\todo[inline]{setting-related regressors have small event count compared to
+geo/groom; probably more important in discussion}
 Contrasts 6-8: words belonging to the categories \texttt{se\_new} and
@@
 the PPA.
-Discussion der Kontraste/Ergebnisse).
 % furniture: blurred border between groom and object
@@
 % intro
-For the AV stimulus, we created five contrasts presumably correlating with
+For the AV stimulus, we created five $t$-contrasts presumably correlating with
 increased hemodynamic activity in the PPA by contrasting different kind of cuts.
-and five contrasts for negative control purposes.
+and five $t$-contrasts for negative control purposes.
 % no control for frames content
@@
 % two ways of co-registration
-For subsequent second level results, we co-registered the subjects in two ways.
+For the subsequent second level results, we co-registered the subjects in two ways.
 % subject template (for Bland-Altman-Plot of unthresholded maps)
@@
     \includegraphics[width=\linewidth]{figures/group-slices}
-    \caption{group results}
-    \label{fig:group-slices}
-\end{figure*}
+    \caption{Mixed-effects group-level (N=14) GLM results.  Significant clusters
+        (Z>3.4, p<0.05 cluster-corrected) are overlaid on the MNI152 T1-weighted
+        head template (grey).
+        Light grey: The audio-description's field-of-view
+        (cf. \citep{hanke2014audiomovie}).
+        Blue: the $t$-contrast comparing
+        geometry-related nouns to non geometry-related nouns spoken by the
+        audio-description's narrator (geo, groom > all non-geo).
+        Red: audio-visual movie (red).}
+    \label{fig:group-slices} \end{figure*}
 
@@
     \includegraphics[width=\linewidth]{figures/subs-thresh-ppa}
-    \caption{indidvidual PPAs}
+    \caption{individual PPAs}
     \label{fig:subs-thresh-ppa}

### 2020-07-04 paper/main.tex
in results, add references to tables/figures

@@
 A preliminary annotation was performed by one person according to the rules (see
-Table. Minor corrections due to incorrectly applied rules were by the author (s.
-Table \ref{tab:descr-nouns-counts} for the counts in the whole stimulus and the
-eight stimulus segments used during fMRI scanning).
+Table. Minor corrections due to incorrectly applied rules were by the author
+(see Table \ref{tab:descr-nouns-counts} for the counts in the whole stimulus and
+the eight stimulus segments used during fMRI scanning).
 
@@
 \section{Results}
-% both stimuli
-% group results for primary contrasts
-% stability of contrasts
-% individual PPAs
-
-% AO stimulus
-% Bland-Altman-Plots
-
-\begin{figure*} \centering
-    \includegraphics[width=\linewidth]{figures/group-slices}
-    \caption{Mixed-effects group-level (N=14) GLM results.  Significant clusters
-        (Z>3.4, p<0.05 cluster-corrected) are overlaid on the MNI152 T1-weighted
-        head template (grey).
-        Light grey: The audio-description's field-of-view
-        (cf. \citep{hanke2014audiomovie}).
-        Blue: the $t$-contrast comparing
-        geometry-related nouns to non geometry-related nouns spoken by the
-        audio-description's narrator (geo, groom > all non-geo).
-        Red: audio-visual movie (red).}
-    \label{fig:group-slices} \end{figure*}
+
+\subsection{stability contrasts}
+See Figure \ref{fig:stability-slices}.
+-> Tabelle machen
 
@@
 
-\begin{figure*} \centering
-    \includegraphics[width=\linewidth]{figures/subs-thresh-ppa}
-    \caption{individual PPAs}
-    \label{fig:subs-thresh-ppa}
-\end{figure*}
+\subsection{primary contrasts}
+See Figure \ref{fig:group-slices}.
+
+AO stimulus; See Table \ref{tab:res-ao-group1}
+
+AV stimulus; See Table \ref{tab:res-av-group1}
 
@@
 areas (l. = left; r. = right; c. = cortex; g. = gyrus).}
-\label{tab:res-ao-group1}
+\label{tab:res-av-group1}
 \begin{tabular}{rrrrrrrrrp{3cm}}
@@
 \end{table*}
+
+\begin{figure*} \centering
+    \includegraphics[width=\linewidth]{figures/group-slices}
+    \caption{Mixed-effects group-level (N=14) GLM results.  Significant clusters
+        (Z>3.4, p<0.05 cluster-corrected) are overlaid on the MNI152 T1-weighted
+        head template (grey).
+        Light grey: The audio-description's field-of-view
+        (cf. \citep{hanke2014audiomovie}).
+        Blue: the $t$-contrast comparing
+        geometry-related nouns to non geometry-related nouns spoken by the
+        audio-description's narrator (geo, groom > all non-geo).
+        Red: audio-visual movie (red).}
+    \label{fig:group-slices}
+\end{figure*}
+
+\subsection{individual results}
+See Figure \ref{fig:subs-thresh-ppa}; AO / AV to localizer ratios
+
+\begin{figure*} \centering
+    \includegraphics[width=\linewidth]{figures/subs-thresh-ppa}
+    \caption{individual PPAs}
+    \label{fig:subs-thresh-ppa}
+\end{figure*}
+
+\subsection{Bland-Altman-Plots}
+See Figure \ref{fig:bland-altman}
+
+\begin{figure*} \centering
+    \includegraphics[width=\linewidth]{figures/subjs_bland-altman.png}
+    \caption{Bland-Altman-Plots for individual subjects}
+    \label{fig:bland-altman}
+\end{figure*}
 

### 2020-07-04 paper/main.tex
some ideas for discussion scaffold

@@
 
-% MIH the discussion should primarily be anchored on the points the introduction concludes with.
-From my POV there is no need (and likely no space) to discuss results by stimulus type.
-Issue like different impact of attentional focus etc can be brought up in the joint paragraph that discussed how such a factor could have differentially impacted the results -- and if that would matter.
 \section{Discussion}
 
+\todo[inline]{MIH: discussion should primarily be anchored on the points the
+    introduction concludes with. From my POV there is no need (and likely no
+    space) to discuss results by stimulus type. Issue like different impact of
+    attentional focus etc can be brought up in the joint paragraph that
+    discussed how such a factor could have differentially impacted the results
+    and if that would matter.}
+
+\paragraph{From Poster}: 1. PPA shows increased activation during non-visual,
+complex auditory stimulation that provides incidental spatial information.
+
+2. only minor temporal correlation of regressors of the audio drama \& movie that were not designed for experimental research.
+
+3. but still, alternative contrasts show significant clusters in auditory
+cortices.
+
+4. inter-individual differences: for two subjects, an alternative audio-contrast
+shows bilaterally significant clusters whereas the primary contrast shows no
+significant clusters.
+
+5. audio drama shows bilaterally increased activation in subject 4 in which the
+visual localizer shows an unilateral cluster.
+
+6. nevertheless, a  complex auditory stimulus might allow individual
+localization of a functionally defined brain region.
+
+7. results of other studies suggest7 the PPA does not exclusively process the
+``spatial layout''" but ``contextual associations''.
+
+8. an audio drama might be suitable as ecologically more valid ``localizer'' for
+a variety of brain functions.
+
 \subsection{AO Discussion}
-% Hanke et al.
-(2014): Compared to an audio-visual movie, this is a stimulus that leaves a much larger margin for inter-individual differences in imagining scenery, as well as actors' character and personality traits, while still preserving the time-locked presentation of information to a listener.
-At the same time, an auditory stimulus limits the effect of an attentional focus on the selection of a subset of simultaneously occurring auditory events, in contrast to the selection of different parts of the visual field.
-% mental imagery hypthesis (s. O'Craven \& Kanwisher, 2000)
-% Lerner (2011), Honey (2012), Silbert (2014) finden keine ISC in PPA? vgl. DataPaper bzgl. Hörbuch??
-% setting\_new ist häufig vermischt mit anderer Kategorie "ein Arzt", "ein alter Film", "auf einer Straße", "im Fernsehen", "die drei Jungs", "die zwei im Bett", "Jenny als Teenager", "Forrest vor einem Buffet", "Kennedy", "Jenny kommt aus dem Wohnwagen ihrer Großmutter"
-% Soundscape macht es häufiger bereits vorher klar, dass Settingwechsel ist bzw. nicht erst das annotiere Substantiv
-% object und (room)geo ist vermischt
-% Retrospelinal Cortex ist in Probabilistic maps krasser als PPA.
-
-% From Poster:
-% 1. PPA shows increased activation during non-visual, complex auditory stimulation that provides incidental spatial information.
-% 2. only minor temporal correlation of regressors of the audio drama & movie that were not designed for experimental research.
-% 3. but still, alternative contrasts show significant clusters in auditory cortices.
-% 4. inter-individual differences: for two subjects, an alternative audio-contrast shows bilaterally significant clusters whereas the primary contrast shows no significant clusters.
-% 5. audio drama shows bilaterally increased activation in subject 4 in which the visual localizer shows an unilateral cluster.
-% 6. nevertheless, a  complex auditory stimulus might allow individual localization of a functionally defined brain region.
-% 7. results of other studies suggest7 the PPA does not exclusively process the ``spatial layout''" but ``contextual associations''.
-% 8. an audio drama might be suitable as ecologically more valid ``localizer'' for a variety of brain functions.
-
-% Unterschiedliche Qualität der Kontrast
-% Warum wurde Kontrast 1 als Kontrast 1 gewählt; se\_new se\_old sind recht
-% vague in der Beschreibung der Szene verglichen mit Bild; Anzahl der Events
-% ergibt auch noch Sinn;
+
+Hanke et al. (2014): Compared to an audio-visual movie, this is a stimulus that
+leaves a much larger margin for inter-individual differences in imagining
+scenery, as well as actors' character and personality traits, while still
+preserving the time-locked presentation of information to a listener. At the
+same time, an auditory stimulus limits the effect of an attentional focus on the
+selection of a subset of simultaneously occurring auditory events, in contrast
+to the selection of different parts of the visual field.
+
+aminoff2013: jedoch zu non-spatial stuff: Although the PHC is commonly thought
+of as responding to visual stimuli, it has also been found to elicit activity
+for auditory stimuli [25,26,30,31] and to respond to odor stimuli [32–34].
+
+Unterschiedliche Qualität der Kontrast: Warum wurde Kontrast 1 als Kontrast 1
+gewählt; se\_new se\_old sind recht vague in der Beschreibung der Szene
+verglichen mit Bild; Anzahl der Events ergibt auch noch Sinn
+
+setting\_new ist häufig vermischt mit anderer Kategorie "ein Arzt", "ein alter
+Film", "auf einer Straße", "im Fernsehen", "die drei Jungs", "die zwei im Bett",
+"Jenny als Teenager", "Forrest vor einem Buffet", "Kennedy", "Jenny kommt aus
+dem Wohnwagen ihrer Großmutter" Soundscape macht es häufiger bereits vorher
+klar, dass Settingwechsel ist bzw. nicht erst das annotiere Substantiv object
+und (room)geo ist vermischt Retrospelinal Cortex ist in Probabilistic maps
+krasser als PPA.
+
+Mental Imagery Hypthesis (s. O'Craven \& Kanwisher, 2000); Lerner (2011), Honey
+(2012), Silbert (2014) finden keine ISC in PPA? vgl. auch DataPaper bzgl.
+Hörbuch??
 
@@
 \section*{General Discussion}
-% Data-driven vs. Analysis-Driven
-% "Abfall" einer Film-Messung
-% how do results (PPA-like response localization) differ from a standard visual/block-design localizer for:
-% feasibility of (multi-dimensional) localizer development with naturalistic stimuli
-% Story für parietale Aktivierung im Film -> räuml. Orientierung / Aufmerksamkeit
-% CONFOUNDS als klassisches Gegenargument gg. Filme (aber er ändert sich nicht über die Zeit, vgl. resting state)
-% was sind für Film und Audiobook die Confounds?
-% Occipital Place Area (Nakamura, 2000), RSC
-% Natural stimuli like movies \citep{hasson2008neurocinematics, sonkusare2019naturalistic} or narratives \citep{honey2012not, lerner2011topographic, silbert2014coupled} offer an easy to implement, (continuous,) complex, immersive, task-free paradigm that more closely resembles our natural dynamic environment than traditional experimental designs.
-Compared to specifically designed paradigms, the complexity of a natural stimulus goes hand in hand with an unknown temporal structure unless the stimulus is - often manually - annotated \citep{haeusler2016annotation, labs2015portrayed}.
-\todo[inline]{why naturalistic stimuli are so cool: sinkusare2019,
-    eickhoff2020}
-\todo[inline]{model-driven vs. data-driven analyses}
-% Due to their continuity, complexity, and length, they offer a vast amount of data on a variety of brain functions like low-level perception, attention, comprehension, memory, emotions, or social interactions.
+
+\subsection{Data-driven vs. Analysis-Driven}
+"Abfall" einer Film-Messung
+
+\subsection{naturalistic vs. dedicated}
+how do results (PPA-like response localization) differ from a standard visual/block-design localizer for:
+
+\subsection{parietal and RSC activations}
+Story für parietale Aktivierung im Film -> räuml. Orientierung / Aufmerksamkeit
+
+\subsection{model-driven vs. data-driven analyses}
+Due to their continuity, complexity, and length, they offer a vast amount of data on a variety of brain functions like low-level perception, attention, comprehension, memory, emotions, or social interactions.
 This suggests the data can later be reused for variety of totally different, independent research questions, possibly on an individual level.
-% aminoffr2013; jedoch zu non-spatial stuff: Although the PHC is commonly thought of as responding to visual stimuli, it has also been found to elicit activity for auditory stimuli [25,26,30,31] and to respond to odor stimuli [32–34].
+
+\subsection{confounds in AO and AV}
+
+\subsection{multi-dimensional localizer???}
+feasibility of (multi-dimensional) localizer development with naturalistic
+stimuli.
+
+Natural stimuli like movies \citep{hasson2008neurocinematics,
+sonkusare2019naturalistic} or narratives \citep{honey2012not,
+lerner2011topographic, silbert2014coupled} offer an easy to implement,
+(continuous,) complex, immersive, task-free paradigm that more closely resembles
+our natural dynamic environment than traditional experimental designs.
+
+why naturalistic stimuli are so cool: sonkusare2019, eickhoff2020, hamilton
 

### 2020-07-06 paper/main.tex
draft of stability of contrasts results

@@
 For the analysis of the AO stimulus, we created regressors correlating with the
-occurrence of descriptive nouns spoken by the narrator that were added to the original annotation of speech \citep{haeusler2020speechanno}.
+occurrence of descriptive nouns spoken by the narrator that were added to the
+original annotation of speech \citep{haeusler2020speechanno}.
 % AV events
-For the AV stimulus, we created regressors correlating with annotated movie cuts \citep{haeusler2016cutanno}.
+For the AV stimulus, we created regressors correlating with annotated movie cuts
+\citep{haeusler2016cutanno}.
 % https://github.com/psychoinformatics-de/studyforrest-data-annotations/blob/master/code/researchcut2segments.py}
@@
 % null regressors
-If a segment did not contain an event of a category, a null regressor was chosen for that segment.
-\todo{wenn ich "null regressor" nehme, darf ich den ganzen Run, glaube ich, in
-der 2nd level Analyse gar nicht benutzen? Hatte, glaube ich, Jeanette Mumford in
-einem ihren Videos mal gesagt}
+If a segment did not contain an event of a category, a null regressor was chosen
+for that segment.  \todo{wenn ich "null regressor" nehme, darf ich den ganzen
+    Run, glaube ich, in der 2nd level Analyse gar nicht benutzen? Hatte, glaube
+    ich, Jeanette Mumford in einem ihren Videos mal gesagt}
 % modeling as boxcar function
@@
 modeled as impulse events to capture variance of a possibly confounding change
-of the soundscape after cuts, and to create contrasts of cross-modal negative control.
+of the soundscape after cuts, and to create contrasts of cross-modal negative
+control.
 % nuissance regressors
@@
 % Reference to table
-A short explanation and counts of the eleven speech-related event categories,
+An explanation and counts of the eleven speech-related event categories,
 the five movie cut-related categories, and the two low-level confounds can be
@@
         the audio-only stimulus (AO).
-\texttt{all non-geo} = body, bodypart, fahead, object, sex\_f, sex\_m). Contrast
+\texttt{all non-geo} = body, bodypart, fahead, object, sex\_f, sex\_m).
+Contrast
 1-8 aim to isolate the PPA.
-Contrast 9-13 serve as negative control at the moments of movie cuts
-with possible changes of the audio tracks soundscape (see Table \ref{tab:av-contrasts}}
+Contrasts 9-13 serve as negative control at the moments of movie cuts
+with possible changes of the audio tracks soundscape (see Table
+\ref{tab:av-contrasts}).}
 
@@
 
-\paragraph{second level (+ alignment)}
+\paragraph{alignment etc.}
 % single subjects (for Bland-Altman-Plots) 1st level
@@
 % two ways of co-registration
-For the subsequent second level results, we co-registered the subjects in two ways.
+For the subsequent second level results, we co-registered the subjects in two
+ways.
 % subject template (for Bland-Altman-Plot of unthresholded maps)
@@
 
-\subsubsection{second level}
+% second level
 % model
@@
 
-\subsubsection{third level}
+% third level
 % model
-The third level analysis which averaged contrast estimates over subjects were
+The third level analysis which averaged contrast estimates over subjects was
 carried out using FLAME stage 1 with automatic outlier detection
@@
 % thresholding
-Z (Gaussianised T/F) statistic images were thresholded using clusters determined
-by Z>3.4 and a (corrected) cluster significance threshold of p=.05
-\citep{worsley2001statistical}.
-
+Here again, Z (Gaussianised T/F) statistic images were thresholded using
+clusters determined by Z>3.4 and a (corrected) cluster significance threshold of
+p=.05 \citep{worsley2001statistical}.
 % brain region identification
@@
 
+\todo[inline]{I consider tables of significant clusters for every contrast as
+overkill. One contrast, the ``primary contrast'', appropriate.}
+
 \subsection{stability contrasts}
-See Figure \ref{fig:stability-slices}.
--> Tabelle machen
+The overlap of significant clusters of the 7 (well actually 8) contrast for the
+audio-description, and 5 contrasts computed for the movie can be found in Figure
+\ref{fig:stability-slices}.
+
+% AO
+\todo{alle noch einmal im einzelnen angucken; was ist mit COPE 8, der ist in der
+Abb. nicht drin; zeigt (noch) einer keine sign. cluster?}
+% PPA
+Six of seven AO contrasts show significant bilateral clusters in anterior
+regions of the group PPA overlap (which is temporal occipital fusiforim gyrus
+regarding to co-registered Harvard-Oxford Cortical Structural Atlas).
+% Precuneus = Retro Spenial Cortex ?
+Six of seven contrasts show significant clusters in the ventral precuneus /
+retrospenial cortex (RSC)
+
+% AV
+% PPA
+All five AV contrasts yielded significant bilateral clusters in (temporal)
+occipital, fusiform cortex showing congruency with the group overlap of
+individual PPA ROIs.
+% Lingual Gyrus
+Homologous clusters of three contrasts extend further into lingual gyrus.
+% RSC
+Three contrasts show significant bilateral clusters in RSC.
+% LOC
+Four contrasts show signficant bilateral clusters in laterial occipital cortex
 
@@
     \includegraphics[width=\linewidth]{figures/stability-slices}
-    \caption{stability of contrasts}
-    \label{fig:stability-slices}
+    \caption{Stability of contrasts. Overlap of significant clusters (Z>3.4;
+        p<.05, cluster corrected) of contrasts created to isolate the PPA. Blue:
+        contrasts 1-7 (see Table \ref{tab:ao-contrasts} for the
+    audio-description.}. Red: contrasts 1-5 (see Table \ref{tab:av-contrasts}
+    for the audio-visual movie. Black: outline of overlapping individual PPA
+    ROIs \citep{sengupta2016extension}.  \label{fig:stability-slices}
 \end{figure*}
@@
 
-\subsection{naturalistic vs. dedicated}
-how do results (PPA-like response localization) differ from a standard visual/block-design localizer for:
-
-\subsection{parietal and RSC activations}
-Story für parietale Aktivierung im Film -> räuml. Orientierung / Aufmerksamkeit
-
-\subsection{model-driven vs. data-driven analyses}
-Due to their continuity, complexity, and length, they offer a vast amount of data on a variety of brain functions like low-level perception, attention, comprehension, memory, emotions, or social interactions.
-This suggests the data can later be reused for variety of totally different, independent research questions, possibly on an individual level.
+\subsection{naturalistic vs. dedicated} how do results (PPA-like response
+localization) differ from a standard visual/block-design localizer for:
+
+\subsection{anterior (AO) vs. posterior (AV) PPA}
+
+\subsection{parietal and RSC activations} Story für parietale Aktivierung im
+Film -> räuml. Orientierung / Aufmerksamkeit
+
+\subsection{model-driven vs. data-driven analyses} Due to their continuity,
+complexity, and length, they offer a vast amount of data on a variety of brain
+functions like low-level perception, attention, comprehension, memory, emotions,
+or social interactions. This suggests the data can later be reused for variety
+of totally different, independent research questions, possibly on an individual
+level.
 

### 2020-07-06 code/plot-group-and-individuals.py

@@ -198,7 +198,7 @@ def process_stability(ao_prob, av_prob, outfpath):
     cax1 = fig.add_subplot(grid[12:13, 6:11])
     cmap = mpl.cm.Blues
     cmap = cmap.reversed()
-    norm = mpl.colors.Normalize(vmin=3.4, vmax=7.1)
+    norm = mpl.colors.Normalize(vmin=0, vmax=7)
     cb1 = mpl.colorbar.ColorbarBase(cax1,
                                     cmap=cmap,
                                     norm=norm,
@@ -212,7 +212,7 @@ def process_stability(ao_prob, av_prob, outfpath):
     cax2 = fig.add_subplot(grid[13:14, 6:11])
     cmap = mpl.cm.YlOrRd
     cmap = cmap.reversed()
-    norm = mpl.colors.Normalize(vmin=3.4, vmax=7.1)
+    norm = mpl.colors.Normalize(vmin=0, vmax=7)
     cb2 = mpl.colorbar.ColorbarBase(cax2,
                                     cmap=cmap,
                                     norm=norm,
@@ -220,7 +220,7 @@ def process_stability(ao_prob, av_prob, outfpath):
 
     # ticklabels and edge of the colorbar
     cax2.tick_params(colors='w')
-    cb2.set_label('Z value', color='w')
+    cb2.set_label('number of contrasts', color='w')
     cb2.outline.set_edgecolor('w')
 
     # shrinke the space between subplots

### 2020-07-06 code/plot-group-and-individuals.py
correct ticks and legends

@@ -183,9 +183,9 @@ def process_stability(ao_prob, av_prob, outfpath):
     blue = mpl.patches.Patch(color='#2474b7',
                              label='descriptive nouns (7 contrasts)')
     red = mpl.patches.Patch(color='#f03523',
-                            label='movie cuts (6 contrasts)',)
+                            label='movie cuts (5 contrasts)',)
     black = mpl.patches.Patch(color='#454545',
-                              label='individual PPA mask (Sengupta et al., 2016)')
+                              label='overlap of individual PPA masks (Sengupta et al., 2016)')
 
     legendAxis.legend(handles=[blue, red, black],
                       loc='upper center',
@@ -220,6 +220,7 @@ def process_stability(ao_prob, av_prob, outfpath):
 
     # ticklabels and edge of the colorbar
     cax2.tick_params(colors='w')
+    cax2.xaxis.set_ticks(list(range(8)))
     cb2.set_label('number of contrasts', color='w')
     cb2.outline.set_edgecolor('w')
 
@@ -353,11 +354,11 @@ def process_group_averages(outfpath):
     legendAxis = fig.add_subplot(grid[12:, :6])
 
     blue = mpl.patches.Patch(color='#2474b7',
-                             label='geo, groom > all non-geo')
+                             label='geo, groom > all non-geo (audio-description)')
     red = mpl.patches.Patch(color='#f03523',
-                            label='vse_new > vpe_old')
+                            label='vse_new > vpe_old (movie)')
     black = mpl.patches.Patch(color='#454545',
-                              label='individual PPA mask (Sengupta et al., 2016)')
+                              label='overlap of individual PPA masks (Sengupta et al., 2016)')
 
     legendAxis.legend(handles=[blue, red, black],
                       loc='upper center',
@@ -632,11 +633,11 @@ def add_legend_colobar_to_individuals(fig):
     legendAxis = fig.add_subplot(grid[6*3:6*3+3, 13:23])
 
     blue = mpl.patches.Patch(color='#2474b7',
-                             label='descriptive nouns')
+                             label='geo, groom > all non-geo (audio-description)')
     red = mpl.patches.Patch(color='#f03523',
-                            label='movie cuts',)
+                            label='vse_new > vpe_old (movie)',)
     black = mpl.patches.Patch(color='#454545',
-                              label='individual PPA mask')
+                              label='individual PPA mask (Sengupta et al., 2016)')
 
     legendAxis.legend(handles=[blue, red, black],
                       loc='center',

### 2020-07-08 paper/main.tex
how to write result & discussion as comments

@@
 %  jetzt 109 Chars
-\title{Hemodynamic responses of the Parahippocampal Place Area to spatial cues in a movie and it's audio-description}
+\title{Hemodynamic responses of the Parahippocampal Place Area to spatial cues in a movie and its audio-description}
 
@@
 
-\todo[inline]{I consider tables of significant clusters for every contrast as
-overkill. One contrast, the ``primary contrast'', appropriate.}
-
-\subsection{stability contrasts}
-The overlap of significant clusters of the 7 (well actually 8) contrast for the
-audio-description, and 5 contrasts computed for the movie can be found in Figure
-\ref{fig:stability-slices}.
-
+% HOW TO WRITE METHODS SEXTION
+% first paragraph (cause most readers don't read methods beforehand
+% summarizes the overall approach to the problem outlined in the intro
+% key innovative methods that were developed
+% -> gist of the methods that were used
+
+% subsequent paragraphs start with a sentence or two
+% that set up the question that the paragraph answers
+% e.g. ``To verify that there are no artifacts..''
+% What is the test-retest reliability of our measure?''
+% “We next tested whether Ca2+ flux through Ca2+ channels was involved.''
+% Middle of the paragraph presents data and logic that pertain to the question,
+% paragraph ends with a sentence that answers the question
+% For example, it may conclude that none of potential artifacts were detected.
+% Each paragraph convinces the reader of answer given in its last sentence.
+% The result of each paragraph is a logical statement
+
+\subsection{primary contrasts}
 % AO
-\todo{alle noch einmal im einzelnen angucken; was ist mit COPE 8, der ist in der
-Abb. nicht drin; zeigt (noch) einer keine sign. cluster?}
+The primary $t$-contrast for the audio-description comparing geometry-related
+nouns to non geometry-related nouns spoken by the audio-description's narrator
+(\texttt{geo, groom > all non-geo} yielded six significant clusters (see Table
+\ref{tab:res-ao-group1}, Figure \ref{fig:group-slices}).
+% precuneus
+Two homologous clusters in the ventral precuneus extending into the
+retrosplenial cortex.
 % PPA
-Six of seven AO contrasts show significant bilateral clusters in anterior
-regions of the group PPA overlap (which is temporal occipital fusiforim gyrus
-regarding to co-registered Harvard-Oxford Cortical Structural Atlas).
-% Precuneus = Retro Spenial Cortex ?
-Six of seven contrasts show significant clusters in the ventral precuneus /
-retrospenial cortex (RSC)
+Two homologous clusters in the lingual gyrus, occipital and temporal fusiform
+gyrus, and posterior parahippocampal cortex \todo{the clusters are small but
+that's what the Harvard-Oxford Atlas suggests, probably because at borders of
+the areas}.
+% LOC
+And finally, two homologous clusters in the superior lateral occipital cortex.
 
 % AV
-% PPA
-All five AV contrasts yielded significant bilateral clusters in (temporal)
-occipital, fusiform cortex showing congruency with the group overlap of
-individual PPA ROIs.
-% Lingual Gyrus
-Homologous clusters of three contrasts extend further into lingual gyrus.
-% RSC
-Three contrasts show significant bilateral clusters in RSC.
+The primary $t$-contrast for the movie comparing cuts to a new setting with cuts
+to a familiar perspective (\texttt{vse\_new > vpe\_old}) yielded three
+significant clusters (see Table \ref{tab:res-av-group1}, Figure
+\ref{fig:group-slices}).
 % LOC
-Four contrasts show signficant bilateral clusters in laterial occipital cortex
-
-\begin{figure*} \centering
-    \includegraphics[width=\linewidth]{figures/stability-slices}
-    \caption{Stability of contrasts. Overlap of significant clusters (Z>3.4;
-        p<.05, cluster corrected) of contrasts created to isolate the PPA. Blue:
-        contrasts 1-7 (see Table \ref{tab:ao-contrasts} for the
-    audio-description.}. Red: contrasts 1-5 (see Table \ref{tab:av-contrasts}
-    for the audio-visual movie. Black: outline of overlapping individual PPA
-    ROIs \citep{sengupta2016extension}.  \label{fig:stability-slices}
-\end{figure*}
-
-\subsection{primary contrasts}
-See Figure \ref{fig:group-slices}.
-
-AO stimulus; See Table \ref{tab:res-ao-group1}
-
-AV stimulus; See Table \ref{tab:res-av-group1}
+Two clusters in the superior lateral occipital cortex (left bigger than right).
+% PPA + others.
+And one one cluster spanning across the midline and comprising intracalcarine
+and cuneal cortex, lingual gyrus and restrosplenial cortex,  occipital fusiform
+gyrus and temporal fusiform gyrus, and parahippocampal cortex bilaterally.
 
 \begin{table*}[t]
-    \caption{Significant clusters (Z-Threshold Z>3.4; p<.05 cluster-corrected) for the contrast \texttt{geo, groom > all non-geo} (audio-only stimulus).
+    \caption{Significant clusters (Z-Threshold Z>3.4; p<.05 cluster-corrected)
+        of the primary $t$-contrast for the audio-description comparing
+        geometry-related nouns to non geometry-related nouns spoken by the
+        audio-description's narrator (\texttt{geo, groom > all non-geo}).
         Clusters sorted by voxel size.
-The first brain structure given contains the voxel with the maximum Z-Value, followed by brain structures from posterior to anterior, and partially covered areas (l.
-= left; r.
-= right; c.
-= cortex; g.
-= gyrus).}
+    The first brain structure given contains the voxel with the maximum Z-Value,
+followed by brain structures from posterior to anterior, and partially covered
+areas (l. = left; r. = right; c. = cortex; g. = gyrus).}
     \label{tab:res-ao-group1}
@@
 \begin{table*}[t]
-    \caption{Significant clusters (Z-Threshold Z>3.4; p<.05 cluster-corrected) for the contrast \texttt{vse\_new > vpe\_old} (audio-visual stimulus).
+    \caption{Significant clusters (Z-Threshold Z>3.4; p<.05 cluster-corrected)
+        of the primary $t$-contrast for the movie comparing cuts to a new
+        setting with cuts to a familiar perspective (\texttt{vse\_new >
+        vpe\_old}).
 Clusters sorted by voxel size.
@@
         (cf. \citep{hanke2014audiomovie}).
-        Blue: the $t$-contrast comparing
+        Blue: the primary $t$-contrast for the audio-description comparing
         geometry-related nouns to non geometry-related nouns spoken by the
-        audio-description's narrator (geo, groom > all non-geo).
-        Red: audio-visual movie (red).}
+        audio-description's narrator (\texttt{geo, groom > all non-geo}).
+        Red: the primary $t$-contrast for the movie comparing cuts to a new
+        setting with cuts to a familiar perspective (\texttt{vse\_new >
+        vpe\_old)}.
+        Black: outline of overlapping individual PPA ROIs.
+        \citep{sengupta2016extension}.}
     \label{fig:group-slices}
@@
     \includegraphics[width=\linewidth]{figures/subs-thresh-ppa}
-    \caption{individual PPAs}
+    \caption{Fixed-effects individual-level GLM results (Z>3.4, p<0.05
+        cluster-corrected). The brains of the 14 subjects are aligned via
+        non-linear transformation to a study-specific T2* group template that is
+    co-registered to the MNI152 template with an affine transformation (12
+degrees of freedom) to facilitate comparisons across subjects.
+        Light grey: The audio-description's field-of-view
+        (cf. \citep{hanke2014audiomovie}).
+        Blue: the primary $t$-contrast for the audio-description comparing
+        geometry-related nouns to non geometry-related nouns spoken by the
+        audio-description's narrator (\texttt{geo, groom > all non-geo}).
+        Red: the primary $t$-contrast for the movie comparing cuts to a new
+        setting with cuts to a familiar perspective (\texttt{vse\_new >
+        vpe\_old)}.
+        Black: outline of subject-specific PPA ROI.}
+
 \label{fig:subs-thresh-ppa}
@@
 
+\todo[inline]{I consider tables of significant clusters for every contrast as
+overkill. One contrast, the ``primary contrast'', is appropriate.}
+
+\subsection{stability contrasts}
+
+% why we did different contrasts
+We tested a variety of contrasts to ensure\dots ???
+
+% results
+The overlap of significant clusters of the 7 (well actually 8) contrast for the
+audio-description, and 5 contrasts computed for the movie can be found in Figure
+\ref{fig:stability-slices}.
+
+% AO
+\todo{alle noch einmal im einzelnen angucken; was ist mit COPE 8, der ist in der
+Abb. nicht drin; zeigt (noch) einer keine sign. cluster?}
+% PPA
+Six of seven AO contrasts show significant bilateral clusters in anterior
+regions of the group PPA overlap (which is temporal occipital fusiform gyrus
+regarding to co-registered Harvard-Oxford Cortical Structural Atlas).
+% Precuneus = retrosplenial cortex ?
+Six of seven contrasts show significant clusters in the ventral precuneus /
+retrosplenial cortex (RSC).
+
+% AV
+% PPA
+All five AV contrasts yielded significant bilateral clusters in (temporal)
+occipital, fusiform cortex showing congruency with the group overlap of
+individual PPA ROIs.
+% Lingual Gyrus
+Homologous clusters of three contrasts extend further into lingual gyrus.
+% RSC
+Three contrasts show significant bilateral clusters in RSC.
+% LOC
+Four contrasts show significant bilateral clusters in lateral occipital cortex
+
+\begin{figure*} \centering
+    \includegraphics[width=\linewidth]{figures/stability-slices}
+    \caption{Stability of contrasts. Overlap of significant clusters (Z>3.4;
+        p<.05, cluster corrected) of contrasts created to isolate the PPA
+        overlaid on the MNI152 T1-weighted head template (grey).
+        Light grey: The audio-description's field-of-view
+        (cf. \citep{hanke2014audiomovie}).
+        Blue: contrasts 1-7 for the audio-description (see Table \ref{tab:ao-contrasts}.
+        Red: contrasts 1-5 for the audio-visual movie (see Table \ref{tab:av-contrasts}.
+        Black: outline of overlapping individual PPA ROIs
+        \citep{sengupta2016extension}.}
+    \label{fig:stability-slices}
+\end{figure*}
+
 \section{Discussion}
+
+% Discussion explains how results fill gap identified in intro
+% provides caveats to the interpretation
+% describes how paper advances the field by providing new opportunities.
+
+% typically done by recapitulating the results, discussing limitations,
+% and then revealing how the central contribution may catalyze future progress.
+
+% first discussion paragraph is special in that it generally summarizes the
+% important findings from the results section -> give gist of results
+
+% following paragraphs in the discussion section starts by describing an area of weakness or strength of the paper.
+% It then evaluates the strength or weakness by linking it to the
+% relevant literature.
+
+% Discussion paragraphs often conclude by describing a clever, informal way of perceiving the contribution or by discussing future directions that can extend the contribution.
+
+% For example, the first paragraph may summarize the results, focusing on their meaning.
+
+% The second through fourth paragraphs may deal with potential weaknesses and with how the literature alleviates concerns or how future experiments can deal with these weaknesses.
+
+% The fifth paragraph may then culminate in a description of how the paper moves
+% the field forward.
+
+%Step by step, the reader thus learns to put the paper’s conclusions into the right context.
 

### 2020-07-08 paper/main.tex
revision of results

@@
 I am pretty unsure about correctness}
-\todo[inline]{Satz zum Downsampling der 7T Daten?}.
+\todo[inline]{Satz zum Downsampling der 7T Daten?}
 
@@
 % https://github.com/psychoinformatics-de/studyforrest-data-templatetransforms}
-fMRI time series of those 15 participants that took part in all three
-experiments were obtained from
-\href{https://github.com/psychoinformatics-de/studyforrest-data-aligned}{GitHubi}.
+fMRI time series of those 15 participants in the studyforrest dataset that took
+part in all three experiments were obtained from
+\href{https://github.com/psychoinformatics-de/studyforrest-data-aligned}{GitHub}.
 Data were already corrected for motion and aligned by non-linear warping to a
@@
 FSL v5.0.9 (\href{https://www.fmrib.ox.ac.uk/fsl}{FMRIB's Software
-Library}; \citep{smith2004fsl} on a computer cluster running the
+Library}; \citep{smith2004fsl}) on a computer cluster running the
 \href{https://www.debian.org}{Debian} GNU/Linux operating system. Software
@@
 % AV events
-For the AV stimulus, we created regressors correlating with annotated movie cuts
-\citep{haeusler2016cutanno}.
+For the AV stimulus, we created regressors correlating with movie cuts provided
+by a previously published annotation \citep{haeusler2016cutanno}.
 % https://github.com/psychoinformatics-de/studyforrest-data-annotations/blob/master/code/researchcut2segments.py}
+
+% procedure
 First, both annotations were split into eight parts corresponding to the eight
 stimulus segments.
-
 % AO events
-All of the original 19 categories of descriptive nouns except \texttt{++} were
-used as events. Some categories that were similar but offered only a small
+To create regressors for the AV analysis, we used all of the original 19
+categories of descriptive nouns except \texttt{++}.
+% pooling
+Some categories that were similar but offered only a small
 amount of counts were pooled resulting in eleven new categories (see Table
-\ref{tab:ao-events}). Events that fall into one of the two setting-related
-category but also into another category were treated as belonging to
+\ref{tab:ao-events}). Events that fell into one of the two setting-related
+category but also into another category were treated as belonging to the
 setting-related category (\texttt{se\_new} or \texttt{se\_old}).
+% modeling as boxcar function
+Events were were modeled as boxcar function from onset to offset of each word.
 % null regressors
@@
 for that segment.  \todo{wenn ich "null regressor" nehme, darf ich den ganzen
-    Run, glaube ich, in der 2nd level Analyse gar nicht benutzen? Hatte, glaube
-    ich, Jeanette Mumford in einem ihren Videos mal gesagt}
-% modeling as boxcar function
-Events were were modeled as boxcar function from onset to offset of each word.
+Run, glaube ich, in der 2nd level Analyse gar nicht benutzen? Hatte, glaube ich,
+Jeanette Mumford in einem ihren Videos mal gesagt}
 % categories taken from movie cut annotation
@@
 modeled as impulse events to capture variance of a possibly confounding change
-of the soundscape after cuts, and to create contrasts of cross-modal negative
+of the soundscape after a cut, and to create contrasts of cross-modal negative
 control.
@@
 (left-right difference in volume and root mean square energy) that was averaged
-across the length of every movie frame (\unit[40]{ms}) via Python script to
-capture variance correlating with low-level perceptual processes.
+across the length of every movie frame (\unit[40]{ms}) to capture variance
+correlating with low-level perceptual processes.
 % Reference to table
-An explanation and counts of the eleven speech-related event categories,
-the five movie cut-related categories, and the two low-level confounds can be
-found in Table \ref{tab:ao-events}.
+An explanation and counts of the eleven speech-related event categories, the
+five movie cut-related categories, and the two low-level confounds can be found
+in Table \ref{tab:ao-events}.
 
@@
 To create regressors for the AV analysis, we categorized the depicted location
-in the frame following one of the 869 cuts into five categories
-(cf. Table \ref{tab:av-events}): 1) a cut into an unfamiliar setting
-(\texttt{vse\_new}), 2) familiar setting (\texttt{vse\_old}), 3) a switch of
-locale within a setting (\texttt{vlo\_ch}), 4) a cut into an unfamiliar
-perspective (\texttt{vpe\_new}), and 5) familiar perspective
-(\texttt{vpe\_old}).
+in the frame following one of the 869 cuts into five categories (see Table
+\ref{tab:av-events}): 1) a cut into an unfamiliar setting (\texttt{vse\_new}),
+2) a cut into a familiar setting (\texttt{vse\_old}), 3) a switch of locale
+within a setting (\texttt{vlo\_ch}), 4) a cut to an unfamiliar perspective
+(\texttt{vpe\_new}), and 5) a cut to familiar perspective (\texttt{vpe\_old}).
 % null regressor
-Here again, a null regressor was chosen for segment if it did not an event for
-of a category.
+Here again, a null regressor was chosen for segment if it did not contain an
+event of specific category.
 % no cut condition: intro
-A sixth regressors (\texttt{no\_cut}) serving a control condition and to created
-to build negative control contrasts. Frames within movie shots lasting at least
+A sixth regressors (\texttt{no\_cut}) serving a control condition and to create
+negative control contrasts. Frames within movie shots lasting at least
 \unit[20]{s} were pseudo-randomly chosen by the following rationale:
@@
 \texttt{no\_cut} event had to have a minimum distance of \unit[10]{s} to a movie
-cut and to another \texttt{no\_cut} events.
+cut and to another \texttt{no\_cut} event.
 % reference to table
 A short explanation and counts of these six categories modeled as impulse
-events, six additional event categories for low-level auditory and visual
-features of the movie (here again continuous bins lasting \unit[40]{ms}), can be found in Table \ref{tab:av-events}.
+events, and six additional event categories for low-level auditory and visual
+features of the movie (here again continuous bins lasting \unit[40]{ms}) can be
+found in Table \ref{tab:av-events}.
 
@@
 % reference to figure ``correlation of regressors''
-The Pearson correlation coefficients of the 13 regressors of the AO stimulus and
-12 regressors of the AV stimulus across the time course of all stimulus segments
-can be seen in Figure \ref{fig:reg-corr}.\todo{correct colors on horizontal
-line; drop control regressors from figure}
+The Pearson correlation coefficients of the regressors of the AO and AV stimulus
+and across the time course of all stimulus segments can be seen in Figure
+\ref{fig:reg-corr}.
 % temporal derivatives
@@
         description) and audio-visual movie (red; see Table
-        \ref{tab:av-events}). Regressors were created by convolving the events
-        with FSL's ``Double-Gamma HRF'' as a model of the hemodynamic response
-        function, temporally filtered with the same high-pass filter (cut-off
-        \unit[150]{s}) as the BOLD time series, and concatenated across runs
-    before computing the correlation.}
+        \ref{tab:av-events}).
     \label{fig:reg-corr}
@@
 
-\todo[inline]{Why done this way? Why is no. 1 the one?}
+\todo[inline]{Why done this way? Why is no. 1 the one? Event count,
+se\_new and se\_old only vaguely describe the scene; narrator is often
+lacking behind dialogue and change in soundscape}
+
+\todo[inline]{contrasts are ordered by ``how well they make sense'' according to
+theory, ``quality of auditory cue'', and amount of events/data. Hence, the were
+assumed to result in more and more shitty results; at the moment all 8 contrasts
+are used in the result (figure)}
+
 % intro
-For the AO stimulus, we created eight $t$-contrasts that aimed to isolate the
-PPA and five $t$-contrasts for negative control purposes (see Table \ref{tab:ao-contrasts}).
-% PPA contrasts
-\todo[inline]{setting-related regressors have small event count compared to
-geo/groom; probably more important in discussion}
-Contrasts 6-8: words belonging to the categories \texttt{se\_new} and
-\texttt{se\_old} were very vague in describing a scene compared to the richness
-of a picture. Hence, we assumed smaller probability of successfully isolating
-the PPA.
-% furniture: blurred border between groom and object
-Furniture was not included in one of the contrast because it can be considered
-as an object or geometry-defining structure of a room.
-
+For the AO stimulus, we created eight $t$-contrasts to isolate presumably
+correlating with increased hemodynamic activity in the PPA by contrasting
+different kind descriptive nouns. % furniture: blurred border between groom and
+object Furniture was not included in one of the contrast because it can be
+considered as an object or geometry-defining structure of a room.
 % negative control contrasts
-Contrasts 9-13 correspond to the contrasts 1-5 of the AV stimulus and served as
-negative controls because increased activation in the PPA could also be
-correlated with moment of cuts and a possible change in the soundscape of a
-scene.
+Five $t$-contrasts (see Table \ref{tab:ao-contrasts} we created for negative
+control purposes to test if increased activation in the PPA was correlated with
+moment of cuts and therefore correlated with a possible change in the
+soundscape.
 
@@
 \texttt{all non-geo} = body, bodypart, fahead, object, sex\_f, sex\_m).
-Contrast
-1-8 aim to isolate the PPA.
+Contrast 1-8 aim to isolate the PPA.
 Contrasts 9-13 serve as negative control at the moments of movie cuts
@@
 
-\todo[inline]{change stability of contrast plot from 6 to 5 COPES (line 40 in
-script)}
-
 \todo[inline]{Why done this way? Why is no. 1 the one?}
@@
 increased hemodynamic activity in the PPA by contrasting different kind of cuts.
-and five $t$-contrasts for negative control purposes.
 % no control for frames content
 Notably, this was done without an annotation of the visual content depicted in
-the frame after each cut and statistically controlling confounding variables.
+the frame after each cut and thus without statistically controlling confounding
+variables.
 % cinematographic rationale
-The cinematographic rationale was that movie tend to establishing the setting
+% cut to new scenes: establishing shots
+The cinematographic rationale was that movie tend to establish the setting
 (\texttt{vse\_new}) and the spatial relationships within a setting
-(\texttt{vpe\_new}) at the beginning of a movie. Later in the movie, the field
-sizes of movie shots tend to decrease when switching back to already established
-settings (\texttt{vse\_old}). Shots within a recurring settings tend to shift to
-depicting persons and objects (\texttt{vpe\_old}) more relevant to the evolved
-narrative \citep{brown2012cinematography, mercado2011filmmakers}.
+(\texttt{vpe\_new}) at the beginning of a movie.
+% cut to recurrent scene
+Later in the movie, the field sizes of movie shots tend to decrease when
+switching back to already established settings (\texttt{vse\_old}).
+% similarly for shots within a scene
+Shots within a recurring settings tend to shift to depicting persons and objects
+(\texttt{vpe\_old}) more relevant to the evolved narrative \citep{brown2012cinematography, mercado2011filmmakers}.
 % neuroscientific rationale
@@
 settings and cuts within a recurring locale.
+% negative control
+Five additional $t$-contrasts we created for negative control purposes (see
+Table \ref{tab:av-contrasts}.
 
@@
 On the one hand, subject-specific BOLD T1* time series were anatomically aligned
-via linear transformation to a subject-specific, study-specific T1* template
-that served as standard space.
+via linear transformation to a subject-specific, study-specific T1* template.
 % group template (for group and individual brain slices)
@@
 % brain region identification
-Brain regions associated with observed clusters were determined with the Juelich
+Brain regions associated with observed clusters were determined with the Jülich
 Histological Atlas \citep{eickhoff2005toolbox, eickhoff2007assignment} and the
@@
 % PPA masks
-PPA ROI masks for individual subjects and a PPA group mask of individual PPAs overlapping were created from data provided by \citep{sengupta2016extension}.
+PPA ROI masks for individual subjects and a PPA group mask of individual PPA
+overlaps were created from data provided by \citep{sengupta2016extension}.
 
@@
 And one one cluster spanning across the midline and comprising intracalcarine
-and cuneal cortex, lingual gyrus and restrosplenial cortex,  occipital fusiform
+and cuneal cortex, lingual gyrus and retrosplenial cortex,  occipital fusiform
 gyrus and temporal fusiform gyrus, and parahippocampal cortex bilaterally.
@@
 
+Contrasts 6-8: words belonging to the categories \texttt{se\_new} and
+\texttt{se\_old} were very vague in describing a scene compared to the richness
+of a picture. Hence, we assumed smaller probability of successfully isolating
+the PPA.
+
 \subsection{AV discussion}

### 2020-07-08 code/plot-group-and-individuals.py

@@ -29,7 +29,7 @@ BIN_MASK_GRP = 'rois-and-masks/bilat_PPA_binary.nii.gz'
 AO_COPE_PATTERN = 'inputs/studyforrest_ppa/3rd-lvl/'\
     'audio-ppa_c?_z3.4.gfeat/cope1.feat/thresh_zstat1.nii.gz'
 # first six contrasts aim for PPA, rest are control contrasts
-AO_PPA_COPES = range(1, 7)
+AO_PPA_COPES = range(1, 9)
 # primary PPA contrast
 AUDIO_GRP = AO_COPE_PATTERN.replace('c?', 'c1')
 
@@ -198,7 +198,7 @@ def process_stability(ao_prob, av_prob, outfpath):
     cax1 = fig.add_subplot(grid[12:13, 6:11])
     cmap = mpl.cm.Blues
     cmap = cmap.reversed()
-    norm = mpl.colors.Normalize(vmin=0, vmax=7)
+    norm = mpl.colors.Normalize(vmin=0, vmax=8)
     cb1 = mpl.colorbar.ColorbarBase(cax1,
                                     cmap=cmap,
                                     norm=norm,
@@ -212,7 +212,7 @@ def process_stability(ao_prob, av_prob, outfpath):
     cax2 = fig.add_subplot(grid[13:14, 6:11])
     cmap = mpl.cm.YlOrRd
     cmap = cmap.reversed()
-    norm = mpl.colors.Normalize(vmin=0, vmax=7)
+    norm = mpl.colors.Normalize(vmin=0, vmax=8)
     cb2 = mpl.colorbar.ColorbarBase(cax2,
                                     cmap=cmap,
                                     norm=norm,
@@ -220,7 +220,7 @@ def process_stability(ao_prob, av_prob, outfpath):
 
     # ticklabels and edge of the colorbar
     cax2.tick_params(colors='w')
-    cax2.xaxis.set_ticks(list(range(8)))
+    cax2.xaxis.set_ticks(list(range(9)))
     cb2.set_label('number of contrasts', color='w')
     cb2.outline.set_edgecolor('w')
 
@@ -272,7 +272,7 @@ def plot_stability_slice(mode, coord,
                         threshold=0,
                         cmap=colorMap,
                         vmin=0,
-                        vmax=7,
+                        vmax=8,
                         alpha=1)
 
     # add the audio contrasts on top of the movie contrasts
@@ -282,7 +282,7 @@ def plot_stability_slice(mode, coord,
                         threshold=0,
[…]

### 2020-07-20 paper/main.tex
results for individual brain slices & Bland-Altman-Plots

@@
 \caption{Overview of events to build the 18 regressors for the analysis of the
-audio-only (AO) stimulus. Some of the original categories (female, females,
-fname; male, males, mname; face, head; object, objects; see Table
-\ref{tab:descr-nouns-rules}) were pooled into 11 new categories (sex\_f; sex\_m; fahead; object).
+audio-only (AO) stimulus. Some of the annotation's original categories
+    (female, females, fname; male, males, mname; face, head; object, objects;
+    see Table\ref{tab:descr-nouns-rules})
+    were pooled into 11 new categories (\texttt{sex\_f}; \texttt{sex\_m};
+    \texttt{fahead}; \texttt{object}).
 \texttt{fg\_ad\_lrdiff} (left-right volume difference) and
@@
 
-\begin{figure*} \centering
-    \includegraphics[width=\linewidth]{figures/regressor-corr} \caption{Pearson
+\begin{figure*}
+    \centering
+    \includegraphics[width=\linewidth]{figures/regressor-corr}
+    \caption{Pearson
         correlation coefficients of the regressors used in the analysis of the
@@
         description) and audio-visual movie (red; see Table
-        \ref{tab:av-events}).
+        \ref{tab:av-events}).}
     \label{fig:reg-corr}
@@
 \todo[inline]{contrasts are ordered by ``how well they make sense'' according to
-theory, ``quality of auditory cue'', and amount of events/data. Hence, the were
+theory, ``quality of auditory cue'', and amount of events/data. Hence, they were
 assumed to result in more and more shitty results; at the moment all 8 contrasts
@@
 % intro
-For the AO stimulus, we created eight $t$-contrasts to isolate presumably
-correlating with increased hemodynamic activity in the PPA by contrasting
-different kind descriptive nouns. % furniture: blurred border between groom and
-object Furniture was not included in one of the contrast because it can be
-considered as an object or geometry-defining structure of a room.
+For the AO stimulus, we created eight $t$-contrasts presumably correlating with
+increased hemodynamic activity in the PPA by contrasting different kind
+descriptive nouns.
+% furniture: blurred border between groom and object
+The categroy ``furniture'' (\texttt{furn} was not included in one of the
+contrast because it can be considered as an object or geometry-defining
+structure of a room.
 % negative control contrasts
@@
 2 & geo, groom, se\_new > all non-geo & PPA \tabularnewline
-3 & gro
-om, se\_new, se\_old > all non-geo & PPA \tabularnewline
+3 & groom, se\_new, se\_old > all non-geo & PPA \tabularnewline
 4 & geo > all non-geo & PPA \tabularnewline
@@
 
+\todo[inline]{at the moment I tend to reporting the stability of contrast first,
+and then go on to report the primary contrasts for group and individuals; both
+has pros and cons}
+
 % HOW TO WRITE METHODS SEXTION
@@
 % -> gist of the methods that were used
-
+The goal of this study was to exploratorily investigate how the PPA responds to
+auditory cues embedded in a naturalistic audio-only stimulus. We further aimed
+at comparing these results to results to an audio-visual naturalistic stimulus
+and to results from a dedicated visual localizer experiment.
+
+We did this by using GLM... blabla...
 % subsequent paragraphs start with a sentence or two
@@
 
+\todo[inline]{I consider tables of significant clusters for every contrast as
+overkill. One contrast, the ``primary contrast'', is appropriate.}
+
+\subsection{stability contrasts}
+
+% why we did different contrasts
+We tested a variety of contrasts to ensure\dots ???
+
+% results
+The overlap of significant clusters of the 7 (well actually 8) contrast for the
+audio-description, and 5 contrasts computed for the movie can be found in Figure
+\ref{fig:stability-slices}.
+
+% AO
+\todo{alle noch einmal im einzelnen angucken; was ist mit COPE 8, der ist in der
+Abb. nicht drin; zeigt (noch) einer keine sign. cluster?}
+% intro
+We combined different event categories to create eight contrasts that provided
+different congruency with the spatial layout hypothesis and different amount of
+data/events.
+% PPA
+Six of seven AO contrasts show significant bilateral clusters in anterior
+regions of the group PPA overlap (which is temporal occipital fusiform gyrus
+regarding to co-registered Harvard-Oxford Cortical Structural Atlas).
+% Precuneus = retrosplenial cortex ?
+Six of seven contrasts show significant clusters in the ventral precuneus /
+retrosplenial cortex (RSC).
+
+% AV
+% intro
+We also created five contrasts for the audio-visual stimulus by using different
+kind of cuts to be able to compare results across perceptual modalities.
+% PPA
+All five AV contrasts yielded significant bilateral clusters in (temporal)
+occipital, fusiform cortex showing congruency with the group overlap of
+individual PPA ROIs.
+% Lingual Gyrus
+Homologous clusters of three contrasts extend further into lingual gyrus.
+% RSC
+Three contrasts show significant bilateral clusters in RSC.
+% LOC
+Four contrasts show significant bilateral clusters in lateral occipital cortex
+
+\begin{figure*} \centering
+    \includegraphics[width=\linewidth]{figures/stability-slices}
+    \caption{Stability of contrasts. Overlap of significant clusters (Z>3.4;
+        p<.05, cluster corrected) of contrasts created to isolate the PPA
+        overlaid on the MNI152 T1-weighted head template (grey).
+        Light grey: The audio-description's field-of-view
+        (cf. \citep{hanke2014audiomovie}).
+        Blue: contrasts 1-7 for the audio-description (see Table \ref{tab:ao-contrasts}.
+        Red: contrasts 1-5 for the audio-visual movie (see Table \ref{tab:av-contrasts}.
+        Black: outline of overlapping individual PPA ROIs
+        \citep{sengupta2016extension}.}
+    \label{fig:stability-slices}
+\end{figure*}
+
 \subsection{primary contrasts}
-% AO
+% intro
+\todo{intro sentence regarding the primary contrasts}
+% the contrast in detail
 The primary $t$-contrast for the audio-description comparing geometry-related
@@
 gyrus, and posterior parahippocampal cortex \todo{the clusters are small but
-that's what the Harvard-Oxford Atlas suggests, probably because at borders of
-the areas}.
+that's what the Harvard-Oxford Atlas suggests, cluster is at borders of the
+areas}.
 % LOC
@@
 % AV
+% intro
+\todo{intro sentence regarding the primary contrasts}
+% the contrast in detail
 The primary $t$-contrast for the movie comparing cuts to a new setting with cuts
@@
 \begin{table*}[t]
-    \caption{Significant clusters (Z-Threshold Z>3.4; p<.05 cluster-corrected)
+    \caption{Significant clusters (z-threshold Z>3.4; p<.05 cluster-corrected)
         of the primary $t$-contrast for the audio-description comparing
@@
 \begin{table*}[t]
-    \caption{Significant clusters (Z-Threshold Z>3.4; p<.05 cluster-corrected)
+    \caption{Significant clusters (z-threshold Z>3.4; p<.05 cluster-corrected)
         of the primary $t$-contrast for the movie comparing cuts to a new
@@
     \caption{Mixed-effects group-level (N=14) GLM results. Significant clusters
-        (Z>3.4, p<0.05 cluster-corrected) are overlaid on the MNI152 T1-weighted
+        (Z>3.4, p<.05 cluster-corrected) are overlaid on the MNI152 T1-weighted
         head template (grey).
@@
         setting with cuts to a familiar perspective (\texttt{vse\_new >
-        vpe\_old)}.
+        vpe\_old}).
         Black: outline of overlapping individual PPA ROIs.
@@
 \subsection{individual results}
-See Figure \ref{fig:subs-thresh-ppa}; AO / AV to localizer ratios
+% why individual results in the first place.
+We also investigated localization performance of both naturalistic paradigms on
+the level of individual subjects. \todo{maybe report reason here, too: which
+subjects influence the group results the most? ``multiple localizer''?}
+% results in both subject and group space
+Time series of all subjects were analyzed both in subject space and group space.
+% why
+Analysis in group space (Z>3.4, p<.05 cluster-corrected) was performed for
+better comparison of results across participants.
+% ref to figure
+Figure \ref{fig:subs-thresh-ppa} depicts thresholded z-maps of the primary AO
+and AV $t$-contrast and the outline of the individual PPAs
+\citep{sengupta2016extension} overlayed on the MNI152 template (horizontal slice
+z=-11 for all subjects).
+
+% results in detail voxels of significant clusters in PPA ROI (and  RSC
+% liberally)
+% sub-01: PPA (l/r), AO (l/r), AV (-/r); RSC: AO (l/r), AV (-/-)
+% sub-02: PPA (l/r), AO (-/-), AV (-/r); RSC: AO (-/-), AV (-/-)
+% sub-03: PPA (l/r), AO (-/-), AV (-/r); RSC: AO (-/-), AV (-/-)
+% sub-04: PPA (-/r), AO (l/r), AV (-/r); RSC: AO (l/r), AV (-/-) !
+% sub-05: PPA (l/r), AO (-/-), AV (-/-); RSC: AO (-/-), AV (-/-)
+% sub-06: PPA (l/r), AO (l/r), AV (-/-); RSC: AO (l/-), AV (-/-)
+% sub-09: PPA (l/r), AO (l/-), AV (l/r); RSC: AO (l/r), AV (l/r)
+% sub-14: PPA (l/r), AO (l/r), AV (-/r); RSC: AO (l/r), AV (-/-)
+% sub-15: PPA (l/r), AO (l/r), AV (-/r); RSC: AO (l/r), AV (l/r)
+% sub-16: PPA (l/r), AO (l/r), AV (l/r); RSC: AO (l/r), AV (l/-)
+% sub-17: PPA (l/r), AO (l/r), AV (l/r); RSC: AO (l/r), AV (l/r)
+% sub-18: PPA (l/r), AO (l/r), AV (l/r); RSC: AO (l/r), AV (-/r)
+% sub-19: PPA (l/r), AO (l/r), AV (-/r); RSC: AO (l/r), AV (l/r)
+% sub-20: PPA (-/r), AO (-/-), AV (l/r); RSC: AO (-/-), AV (-/-)
+
+% PPA ROI (Sengupta et al., 2016)
+The dedicated localizer shows bilateral clusters in 12 subjects and unilateral
+right clusters in two subjects (sub-04, sub-20).
+
+% AO
+AO stimulus shows bilateral clusters in nine subjects, and one significant cluster in the
+left hemisphere in sub-09.
+% subj-04
+In sub-04, two homologous clusters are apparent, where the dedicated localizer
+yielded only one cluster in the right hemisphere.
+
+% AV
+AV shows homologous clusters in five subjects, and unilateral right clusters in
+seven subjects (of which one subjects also yielded just a unilateral cluster in
+the dedicated localizer).
+% difference to dedicated localizer
+In sub-20 bilateral, where the dedicated localizer yielded only one cluster in
+the right hemisphere
 
@@
     \includegraphics[width=\linewidth]{figures/subs-thresh-ppa}
-    \caption{Fixed-effects individual-level GLM results (Z>3.4, p<0.05
+    \caption{Fixed-effects individual-level GLM results (Z>3.4, p<.05
         cluster-corrected). The brains of the 14 subjects are aligned via
@@
         setting with cuts to a familiar perspective (\texttt{vse\_new >
-        vpe\_old)}.
+        vpe\_old}).
         Black: outline of subject-specific PPA ROI.}
-
 \label{fig:subs-thresh-ppa}
@@
 \subsection{Bland-Altman-Plots}
-See Figure \ref{fig:bland-altman}
+% why
+To better depict the agreement (and difference) between brain responses to the
+visual localizer and contrast 1 of the AO paradigm, we created
+Bland-Altman-Plots (see Figure \ref{fig:bland-altman}).
+% what do Bland-Altman-Plots show?
+The plots for the 14 subjects show the mean of z-values of two spatially
+corresponding voxels in unthresholded z-maps on the x-axis and their difference
+on the y-axis (dedicated localizer minus AO stimulus).
+% masking
+We constrained the number of voxels to voxels in the occipital and temporal
+lobes (grey) using the (probabilistic) Jülich Histological Atlas
+\citep{eickhoff2005toolbox, eickhoff2007assignment} to voxels located in the
+PPA overlap of all subjects (blue), and voxels in the individual PPA
+ROI(s)(red).
+
+% what we can see
+A shift of the distribution to voxels with a mean above zero can be seen the
+further we constrain voxels to the individual PPA (KDE plot for the x-axis).
+% but
+Values above the horizontal line depict voxels that show a higher z-value in the
+dedicated localizer, values below the horizontal line depict voxels that show
+higher z-values in the AO stimulus.
+
+\todo[inline]{the plots are ``biased'' in the PPA mask in such a way that they
+don't take into account that clusters are not 100 perc. congruent, meaning the
+AO stimulus has voxels in regions that are outside of the individual PPA ->
+probably bias to show higher values for the dedicated localizer (red voxels)}
 
@@
     \includegraphics[width=\linewidth]{figures/subjs_bland-altman.png}
-    \caption{Bland-Altman-Plots for individual subjects}
-    \label{fig:bland-altman}
-\end{figure*}
-
-\todo[inline]{I consider tables of significant clusters for every contrast as
-overkill. One contrast, the ``primary contrast'', is appropriate.}
-
-\subsection{stability contrasts}
-
-% why we did different contrasts
-We tested a variety of contrasts to ensure\dots ???
-
-% results
-The overlap of significant clusters of the 7 (well actually 8) contrast for the
-audio-description, and 5 contrasts computed for the movie can be found in Figure
-\ref{fig:stability-slices}.
-
-% AO
-\todo{alle noch einmal im einzelnen angucken; was ist mit COPE 8, der ist in der
-Abb. nicht drin; zeigt (noch) einer keine sign. cluster?}
-% PPA
-Six of seven AO contrasts show significant bilateral clusters in anterior
-regions of the group PPA overlap (which is temporal occipital fusiform gyrus
-regarding to co-registered Harvard-Oxford Cortical Structural Atlas).
-% Precuneus = retrosplenial cortex ?
-Six of seven contrasts show significant clusters in the ventral precuneus /
-retrosplenial cortex (RSC).
-
-% AV
-% PPA
-All five AV contrasts yielded significant bilateral clusters in (temporal)
-occipital, fusiform cortex showing congruency with the group overlap of
-individual PPA ROIs.
-% Lingual Gyrus
-Homologous clusters of three contrasts extend further into lingual gyrus.
-% RSC
-Three contrasts show significant bilateral clusters in RSC.
-% LOC
-Four contrasts show significant bilateral clusters in lateral occipital cortex
-
-\begin{figure*} \centering
-    \includegraphics[width=\linewidth]{figures/stability-slices}
-    \caption{Stability of contrasts. Overlap of significant clusters (Z>3.4;
-        p<.05, cluster corrected) of contrasts created to isolate the PPA
-        overlaid on the MNI152 T1-weighted head template (grey).
-        Light grey: The audio-description's field-of-view
-        (cf. \citep{hanke2014audiomovie}).
-        Blue: contrasts 1-7 for the audio-description (see Table \ref{tab:ao-contrasts}.
-        Red: contrasts 1-5 for the audio-visual movie (see Table \ref{tab:av-contrasts}.
-        Black: outline of overlapping individual PPA ROIs
-        \citep{sengupta2016extension}.}
-    \label{fig:stability-slices}
-\end{figure*}
+    \caption{Bland-Altman-Plots for individual subjects. The x-axis depicts the
+        mean of two spatially corresponding voxels in the unthresholded z-map of
+        the visual localizer and in the unthresholded z-map of contrast 1 of the
+        AO stimulus (KDE plot on the top). The y-axis depicts the difference of
+        two voxels (KDE plot on the right). The overlays depict voxels spatially
+        contrained to be located in the temporal and occipital cortex (grey),
+    PPA overlap of all subjects (blue), and individual PPA (red).}
+    \label{fig:bland-altman} \end{figure*}
 

### 2020-07-21 paper/main.tex
revision of introduction

@@
 
-\todo[inline]{Vorgabe: Intro + Discussion = main text ca. 3,000 words; einige
-offene einige Dinge sind folgend in Kommentaren und nicht als ToDo gemarkt}
-
-\todo[inline]{include figure providing schematic overview of the study and assay
-design -> is overkill: Steht in den entsprechenden Veröffentlichungen \&
-Paradigma ist mit "Film ab" wenig kompliziert}
+\todo[inline]{Intro + Discussion = main text; ca. 3,000 words; some minor
+    ``issues'' are in comments and not labeled as to do's}
 
@@
 
-\section{Introduction} Cognitive neuroscientists use brain imaging methods like
-blood oxygenation level-dependent functional magnetic resonance imaging (BOLD
-fMRI) to map perceptual and cognitive brain processes (e.g. viewing of
-landscapes, \citep{epstein1998ppa}; or theory of mind
-\citep{spunt2014validating}) to functional brain areas or networks. Brain
-mapping studies have traditionally employed small sets of carefully chosen,
-simplified stimuli to strictly control experimental conditions and facilitate
-functional isolation of brain areas. The disadvantage is that a limited number
-of simplified stimuli does not resemble our real-life experience and lacks
-external validity \citep{westfall2016fixing} as well as ecological validity
-\citep{hasson2004intersubject}. Additionally, brain mapping studies usually
-average results across at least 10-15 subjects to improve the
-signal-to-noise-ratio (SNR). The disadvantage here is that the averaging
-approach does not characterize brain functions at an individual level, a
-prerequisite for the application of brain imaging methods in individual
-diagnostics (cf. \citep{dubois2016building, eickhoff2020towards})
-
-\todo[inline]{Retrosplenial Cortex kommt in Einleitung bisher  nicht vor; wird
-aufgrund der Ergebnisse in AV und AO in Discussion diskutiert werden; cluster
-sind in den Abbildungen nicht zu sehen; kommen aber in (den Tabellen) der
-Results Section }
+\section{Introduction}
+
+% brain mapping via fMRI
+Cognitive neuroscientists use brain imaging methods like blood oxygenation
+level-dependent functional magnetic resonance imaging (BOLD fMRI) to map
+perceptual and cognitive brain processes (e.g. viewing of landscapes,
+\citep{epstein1998ppa}; or theory of mind \citep{spunt2014validating}) to
+functional brain areas or networks.
+% simplified stimuli
+Brain mapping studies have traditionally employed small sets of carefully
+chosen, simplified stimuli to strictly control experimental conditions.
+% disadvantage 1: validity
+Their disadvantage is that a limited number of simplified stimuli does not
+resemble our real-life experience and thus lack external validity
+\citep{westfall2016fixing} as well as ecological validity
+\citep{hasson2004intersubject}.
+% disadvantage 2: averaging for group results
+Additionally, brain mapping studies usually average results across at least
+10-15 subjects to improve the signal-to-noise-ratio (SNR). The disadvantage here
+is that the averaging approach does not characterize brain functions at an
+individual level, a prerequisite for the application of brain imaging methods in
+individual diagnostics (cf. \citep{dubois2016building, eickhoff2020towards}).
+
+\todo[inline]{RSC is not mentioned in the introduction but should (probably)
+shortly discussed in the, well discussion; RSC shows up in group results but
+mixed results in individual subjects}
 
@@
 ``parahippocampal place area'' (PPA) \citep{epstein1998ppa,
-epstein1999parahippocampal}. The PPA is located in the posterior parahippocampal
-gyrus at the boundary to the anterior lingual gyrus and medial fusiform gyrus,
-both being part of the ventral visual stream \citep{mishkin1982contribution,
-goodale1992separate}. Increased hemodynamic activity in the PPA correlates with
-the perception of static pictures of landscapes or landmarks compared to
-pictures of tools or faces.  According to the spatial layout hypothesis, the PPA
-is involved in processing the surface geometry of a visual stimulus and possibly
-in identifying scenes based on their spatial layout \citep{epstein2010reliable}.
-
-% Literature Review PPA: Intro
+epstein1999parahippocampal}.
+% anatomical location
+The PPA is located in the posterior parahippocampal gyrus at the boundary to the
+anterior lingual gyrus and medial fusiform gyrus, both being part of the ventral
+visual stream \citep{mishkin1982contribution, goodale1992separate}.
+% neural correlate of scene perception
+Increased hemodynamic activity in the PPA correlates with the perception of
+static pictures of landscapes or landmarks compared to pictures of tools or
+faces.
+% spatial layout hypothesis
+According to the spatial layout hypothesis, the PPA is involved in
+processing the surface geometry of a visual stimulus and possibly in identifying
+scenes based on their spatial layout \citep{epstein2010reliable}.
+
+% literature review overview 1: imagination & haptic exploration
 At a group average level, results generalize to mental imagination of landscapes
 \citep{ocraven2000mental} and haptic exploration of scenes constructed from LEGO
-blocks \citep{wolbers2011modality}. One study that used spoken, place-related
-sentences showed significantly decreased activation in the left and no
-modulation in the right-hemispheric PPA \citep{aziz2008modulation}.
-
-% Exemplary studies
+blocks \citep{wolbers2011modality}.
+% literature review overview 2: spoken sentences
+One study that used spoken, place-related sentences showed significantly
+decreased activation in the left and no modulation in the right-hemispheric PPA
+\citep{aziz2008modulation}.
+
+% literature review in detail
 % O'Craven: Mental imagery
@@
 \todo[inline]{Er hat noch eine Connectivitäts-Analyse mit dem Occipital Cortex
-gemacht. Im Vergleich zum visuellen Paradigma ist im haptischen Paradigma keine
-Connectivität. Interpretation: Es kann keine mental imagery sein}
-
-\todo[inline]{"The scene-related increase in coupling with the PPA was
-significantly stronger in multiple clusters in occipital cortex under visual
-than haptic stimulation (Figure 2B; Table S2)"}
+    gemacht. Im Vergleich zum visuellen Paradigma ist im haptischen Paradigma
+    keine Connectivität. Interpretation: Es kann keine mental imagery sein;
+    ``The scene-related increase in coupling with the PPA was significantly
+    stronger in multiple clusters in occipital cortex under visual than haptic
+    stimulation (Figure 2B; Table S2)''}
 
@@
 
-\todo[inline]{Ihre Method Section ist strange und es kommt bei ihr überall eh
-    nur uneinheitliche Grütze heraus; Ich blicke nicht durch; was folgend kommt,
-    wird nicht vollständig korrekt sein. So wie ich es verstanden habe, hat sie
-    den Unterschied zwischen PPA und FFA angeguckt, aber diesen Unterschied im
-Kontrast zu object-related Sentences (dortige Fig 3; lass uns kurz im Gespräch
-drübergucken, ich habe die relvanten Abschnitte in der PDF markiert)}
-
+\todo[inline]{lass uns kurz im Gespräch über Aziz Paper gucken; die relvanten
+    Abschnitte sind in der PDF markiert. Ihre Method Section ist ``strange'' und
+    im Grunde kommt überall nur uneinheitliche Grütze heraus; ich blicke nicht
+    durch, weshalb folgendes nicht vollständig korrekt sein wird;so wie ich es
+    verstanden habe, hat sie den Unterschied zwischen PPA und FFA angeguckt,
+aber diesen Unterschied im Kontrast zu object-related Sentences (dortige Fig 3;
+)}
+
+% Aziz' stimuli
 To our knowledge only one study by \citep{aziz2008modulation} correlated
@@
 generic or famous places (e.g. ``The Taj Mahal faces a long thin reflecting
-pool''), faces  (e.g. ``Marilyn Monroe has a large square jaw''), or objects
-(e.g. ``The television has a long antenna')'. Participants were instructed to
-press a button whenever the sentence described an inaccurate or improbable fact.
-Surprisingly, activation in the left, but not right, PPA was significantly
-reduced when participants listened to place-related sentences compared to
-listening to face-related sentences. Moreover, this effect was only observed in
-sentences involving famous places.
-
-\todo[inline]{Review von Aminoff (2013) kommt nur kurz als "competing hypothesis"; muss man dann natürlich in der Discussion diskutieren; was aber ggf.
-gar nicht notwendig ist, weil's darum gar bei uns gar nicht geht}
-
-% Summary if literature review
+pool''), faces  (``Marilyn Monroe has a large square jaw''), or objects (``The
+television has a long antenna'').
+% Aziz' tasks
+Participants were instructed to press a button whenever the sentence described
+an inaccurate or improbable fact.
+% Aziz' results
+Activation in the left, but not right, PPA was significantly reduced when
+participants listened to place-related sentences compared to listening to
+face-related sentences. Moreover, this effect was only observed in sentences
+involving famous places.
+
+\todo[inline]{I deleted sentences regarding Aminoff's
+    (\citep{aminoff2006parahippocampal, aminoff2013role}) competing ``contextual
+associations hypothesis'' because our paradigm does not touch that issue.}
+
+% summary if literature review
 In summary, studies suggest that the PPA does not exclusively respond to
-visual(ly) spatial information. This is consistent with a competing hypotheses
-stating that the PPA does not process the spatial layout of a scene specifically
-but contextual associations in general (\citep{aminoff2006parahippocampal,
-aminoff2013role}). It is still uncertain if auditory stimuli lead to inhibitory
-or excitatory responses, or no change at all in the PPA.
-
-\todo[inline]{aber Huth (2016) implizit; diskutiert PPA also solches jedoch
-nicht und macht voxel-wise encoding, was - glaube ich - über
-excitation/inhibition nichts aussagt -> Paper checken}
-
-% Shortcomings of previous studies; lack of research
-All reviewed studies used a just a small set of carefully designed, simplified
-stimuli to strictly control experimental conditions. They further relied on
-explicit judgment-based tasks to ensure that participants payed attention to
-the stimuli. This raises the question how the PPA behaves under life-like conditions.
-
-% Why naturalistic stimuli
+visually presented spatial information. Nevertheless, the question how the
+PPA responds to auditory stimuli is still open.
+
+\todo[inline]{but Huth et al. (2016) implicitly; but they do not discuss the
+PPA; moreover, they do voxel-wise encoding which doesn't say anything about
+excitation/inhibition}
+
+% shortcomings of previous studies: simplified stimuli
+All reviewed studies used a small set of carefully designed, simplified stimuli
+to strictly control experimental conditions.
+% shortcomings of previous studies: task-based paradigm
+They further relied on explicit judgment-based tasks to ensure that participants
+payed attention to the stimuli.
+% second question: life-like conditions
+This raises the second question which is how the PPA behaves under life-like
+conditions.
+% naturalistic stimuli
 Naturalistic stimuli like movies \citep{hasson2008neurocinematics,
@@
 
-% Literature review naturalistic stimuli: Einleitung
+% naturalistic stimuli review: intro
 Two early studies using naturalistic stimuli suggest functional specialization
@@
 cognitive processes are triggered simultaneously \citep{bartels2004mapping, hasson2004intersubject}.
-
-% Bartels (2004): Film + GLM (jedoch ohne PPA) und Hasson (2004)
+% Bartels (2004): Film + GLM (but surprisingly did not annotate landscapes)
 \citep{bartels2004mapping} manually annotated time points that depict faces and
@@
 \citep{tomorrowneverdies}.
+% Bartels: results
 Employing a general linear model (GLM) to model hemodynamic activity, these time
@@
 \citep{downing2001bodyarea} respectively.
-
 % Hasson (2004): Film + (reverse) ISC
@@
 used a 30 minute clip of the movie \textit{The Good, the Bad, and the Ugly}
-\citep{goodbadugly} fMRI brain volumes showing the highest hemodynamic activity
+\citep{goodbadugly}.
+% Hasson: method
+fMRI brain volumes showing the highest hemodynamic activity
 in the PPA [across (five) participants] were matched to the temporally
-corresponding movie frames. Results revealed that corresponding movie frames
+corresponding movie frames.
+% Hasson: results
+Results revealed that corresponding movie frames
 depicted indoor and outdoor scenes including buildings and open fields.
 
-% Summary naturalistic stimuli
-Nevertheless, no study investigated how the PPA responds to spatial clues that are embedded in a complex, audio-only stimulus.
-\todo[inline]{Huth (2016) checken}
-
-\todo[inline]{The next paragraphs contain a bunch of methods already; reduce
-this to talk about the general approach:
-
-a) annotation of events
-
-b) investigation of model quality,
-
-c) cross-analysis of datasets
-
-d) Possibly cite https://psyarxiv.com/sdbqv/ (DuPre (2019). Nature abhors a
-paywall) and declare that this study is a concrete realization of that promise}
-
-% what we did data source
-In this study, we analyze functional data of the same 14 participants provided
-by the studyforrest dataset \href{http://www.studyforrest.org}{studyforrest.org}; \citep{hanke2014audiomovie, hanke2016simultaneous}).
+% summary naturalistic stimuli
+Nevertheless, both studies used an audio-visual stimulus and thus do not address
+the question how the PPA responds to spatial clues that are embedded in a
+complex, audio-only stimulus.
+
+\todo[inline]{mih: Possibly cite https://psyarxiv.com/sdbqv/ (DuPre (2019).
+Nature abhors a paywall) and declare that this study is a concrete realization
+of that promise}
+
+% what we did: data source
+In this study, we analyze functional data of the same 14 participants being part
+of the studyforrest dataset
+(\href{http://www.studyforrest.org}{studyforrest.org};
+\citep{hanke2014audiomovie, hanke2016simultaneous}).
 % PPA + movie + audio-description
-We annotated cuts in the movie ``Forrest Gump'', and words spoken by an
-additional narrator in the movie's audio-description (i.e. the movie's
-audio-only variant) to exploratorily investigate how the parahippocampal gyrus
-behaves during lifelike stimulation.
-% model-driven analysis
-In conformity to the analyses performed in the reviewed studies,  we also
-employed a standard multi-level, voxel-wise general linear model
-(GLM).\todo{why? in order to\dots}
+We annotated cuts in the movie ``Forrest Gump'' \citep{ForrestGumpMovie}, and
+words spoken by an additional narrator in the movie's audio-description (i.e.
+the movie's audio-only variant; \citep{ForrestGumpGermanAD}) to exploratorily
+investigate how the parahippocampal gyrus behaves during movie watching and
+listening to an ``audiobook''.
 % focus on audio-description
-Encouraged by \citep{aziz2008modulation} and \citep{aminoff2013role}, we focus
-on the audio-description as a naturalistic, auditory-only paradigm free from any task to localize a ``visual area'' in individual study participants.
+Encouraged by \citep{aziz2008modulation}, we also employ a traditional GLM, and
+focus on the audio-description as a naturalistic, auditory-only paradigm free
+from any task to localize a ``visual area'' in individual study participants.
 % comparison to dedicated localizer
-Finally, we compare our results to results of a dedicated visual localizer
-experiment done with the same 14 participants \citep{sengupta2016extension}.
+We also compare our results to results of a dedicated visual localizer
+experiment done with the same participants \citep{sengupta2016extension}.
 
@@
 citation (see Data Records and Data Citations, below)}
-\todo[inline]{order of subsections possibly wrong}
-\todo[inline]{parts from original studies still detailed}
+\todo[inline]{current order of subsections might be ``non-canonical''}
+\todo[inline]{parts from original studies still detailed; feel free to delete
+sentences}
 
@@
 b) watching the actual audio-visual movie (AV study;
-\citep{hanke2016simultaneous}, a dataset already used by
+\citep{hanke2016simultaneous}), a dataset already used by
 \citep{ben2018hippocampal},
@@
 c) participating in a dedicated six-category block-design visual localizer (VIS
-study) \citep{sengupta2016extension}, a dataset already used by
+study; \citep{sengupta2016extension}), a dataset already used by
 \citep{jiahui2019predicting}.
@@
 stimulation setup, and fMRI acquisition can be found in the corresponding
-publications \citep{hanke2014audiomovie, hanke2016simultaneous,
-sengupta2016extension}. Following is a summary of most important aspects.
+publications. Following is a summary of most important aspects.
 

### 2020-07-21 paper/main.tex
revision of methods

@@
 ``Forrest Gump'' \citep{ForrestGumpMovie} and its temporally aligned
-audio-description (i.e. the audio-only variant of the movie) that was broadcast
-as an additional audio track for visually impaired listeners on Swiss public
-television \citep{ForrestGumpGermanAD}.
-% AO vs. AV: differences
-The plot of the movie is already carried by an off-screen voice-over of the main
-character Forrest Gump. In the largely identical audio-description, an
-additional male narrator describes essential aspects of the visual scenery when
-there is no off-screen voice, dialog, or other relevant auditory content.
+audio-description that was broadcast as an additional audio track for visually
+impaired listeners on Swiss public television \citep{ForrestGumpGermanAD}.
+% AV: voice-over
+The plot of the movie is already carried by an voice-over of the main character
+Forrest Gump.
+% AO: additional narrator
+In the largely identical audio-description, an additional male narrator
+describes essential aspects of the visual scenery when there is no off-screen
+voice, dialog, or other relevant auditory content.
 
@@
 DVD release. A few scenes less relevant to the major plot were removed to create
-the ``research cut'' lasting $\approx$2h \citep{hanke2014audiomovie,
+the ``research cut'' lasting $\approx$ \unit[2]{h} \citep{hanke2014audiomovie,
 hanke2016simultaneous}.
@@
 seconds immediately preceding the movie scene boundary used to split the
-segments (see Figure 3a in \citep{hanke2014audiomovie}.
+segments (see Figure 3a in \citep{hanke2014audiomovie}).
 
 % VIS study picture categories
-All stimuli for the VIS study were used in a previous study
-\citep{haxby2011common}. There were 24 unique greyscale images (matched in
+All stimuli for the VIS study were already used in a previous study
+\citep{haxby2011common}. There were 24 unique grayscale images (matched in
 luminance, size of 400 $\times$\unit[400]{px}) for each of six stimulus
@@
 
-Both natural stimuli were originally designed to entertain an audience and to capture attention free from any perceptual or behavioral task.
-We annotated events in the otherwise unknown temporal structure of both stimuli.
-In/for the movie, we annotated different kinds of cinematographic cuts \citep{haeusler2016cutanno} as presumably ``spatially relevant'' events.
-Our rationale was that cuts re-orient the viewer in the depicted environment
-independent from the exact visual content in the movie frame following the cut.
-In/for the audio-description, we annotated verbal clues about the missing visual content given by the audio-description's additional narrator \citep{haeusler2020speechanno}.
-
+% stimuli were not designed for research purposes
+Both natural stimuli were originally designed to entertain an audience and to
+capture attention free from any perceptual or behavioral task.
 % AV anno
 For the analysis of the AV data, we took advantage of a publicly available
-annotation of movie cuts and depicted location \citep{haeusler2016cutanno}.
+annotation of movie cuts and depicted locations \citep{haeusler2016cutanno}.
+In/for the movie, We annotated different kinds of cinematographic cuts
+\citep{haeusler2016cutanno} as presumably ``spatially relevant'' events.
+% rationale behind using movie cuts
+Our rationale was that cuts are ``spatially relevant'' events that re-orient the
+viewer in the depicted environment independent from the exact visual content in
+the movie frame following the cut.
+
 % AO anno
 For the analysis of the AO data, we extended another publicly available
-annotation of speech \citep{haeusler2020speechanno}. We manually annotated words
-spoken by the audio-description's narrator.
+annotation of speech \citep{haeusler2020speechanno} by annotating words embedded
+in sentences spoken by the audio-description's narrator.
 % annotation procedure
-Two persons performed a categorization of nouns embedded in sentences spoken by
-the narrator to describe the movie's missing visual content. Some categories
-were created in such a way to reflect the six stimulus categories used in the
-visual localizer experiment. Some additional categories were created to
-semantically cluster nouns into categories ``that were obvious to make
-sense''.\todo{yeah, well, sounds shit but that's basically it}.
-% categories Kategorie ``++'' enthält ausnahmesweise auch adverbiale Best. der
-% Zeit.
-More specifically, nouns were categorized by the clue they provide about the
+Two persons performed a categorization of nouns that describe the movie's
+missing visual content.
+% why and how of categories 1
+Some categories were created in such a way to reflect the six stimulus
+categories used in the visual localizer experiment.
+% why and how of categories 2
+Some additional categories were created to semantically cluster nouns into
+categories ``that were obvious to make sense''.\todo{yeah, well, sounds shit but
+that's basically it}
+% categories in detail
+Nouns were categorized by the verbal clue they provide about the
 cinematographic scene's environment (geo, geo-room; setting\_new, setting\_old),
@@
 furniture).
-% reference to table
-A complete overview of all categories, the rule for a word to belong to a
-category, and examples can be seen in Table \ref{tab:descr-nouns-rules}.
+% reference to table with rules and examples
+A complete overview of all 19 categories, the rule for a word to belong to a
+category, and examples can be seen in \ref{tab:descr-nouns-rules}.
 % procedure
-A preliminary annotation was performed by one person according to the rules (see
-Table. Minor corrections due to incorrectly applied rules were by the author
-(see Table \ref{tab:descr-nouns-counts} for the counts in the whole stimulus and
-the eight stimulus segments used during fMRI scanning).
-
-\todo[inline]{so ist die Tabelle zu breit; schrift kleiner oder Text kürzen?
-Könnte durchaus auch detaillierteren Text schreiben}
-
-% rules Tabelle für descriptiven nouns
+A preliminary annotation was performed by one person according to the rules.
+Minor corrections due to incorrectly applied rules were done by the author.
+% reference to table with counts
+The resulting counts for the whole stimulus and the eight stimulus
+segments used during fMRI scanning can be seen in Table \ref{tab:descr-nouns-counts}.
+
+\todo[inline]{currently table is to wide; smaller font? less text? rotate the table?}
+
+% table for descriptive nouns: categories, rules, examples counts
 \begin{table*}[t]
     \caption{Descriptive nouns spoken by the audio-description's narrator:
-    cateogries, annotation rules and examples (given in English). The categorie
-    \texttt{++} also contains adverbial adjectives and adverbs}
+    categories, annotation rules, and examples (given in English). The category
+    \texttt{++} also contains adverbial adjectives and adverbs.}
 \label{tab:descr-nouns-rules}
@@
 fname & female name & Jenny \tabularnewline
-furniture & moveable furniture insides \& outsides & bench, bed, table, chair
+furniture & movable furniture insides \& outsides & bench, bed, table, chair
 \tabularnewline
@@
 In all three studies, participants filled out a questionnaire on their basic
-demographic information and familiarity with the movie).
+demographic information and familiarity with the movie.
 % AO & AV: instructions
@@
 % paradigm implementation
-In all three studies, stimulation was implemented with \href{http://www.psychopy.org}{PsychoPy} \citep{peirce2007psychopy} running on a computer with the \href{http://neuro.debian.net}{(Neuro)Debian} operating system \citep{halchenko2012open}.
+In all three studies, stimulation was implemented with \href{http://www.psychopy.org}{PsychoPy} \citep{peirce2007psychopy} running on a computer with the NeuroDebian operating system \citep{halchenko2012open}.
 
@@
 All further analysis steps of the current study were carried out using tools of
-FSL v5.0.9 (\href{https://www.fmrib.ox.ac.uk/fsl}{FMRIB's Software
-Library}; \citep{smith2004fsl}) on a computer cluster running the
-\href{https://www.debian.org}{Debian} GNU/Linux operating system. Software
-packages were obtained from repositories of
+FSL v5.0.9 (\href{https://www.fmrib.ox.ac.uk/fsl}{FMRIB's Software Library};
+\citep{smith2004fsl}) on a computer cluster running the Debian GNU/Linux
+operating system. Software packages were obtained from repositories of
 \href{http://neuro.debian.net}{NeuroDebian} \citep{halchenko2012open}.
@@
 % temporal filtering
-High-pass temporal filtering was applied to every segment using a
+High-pass temporal filtering was applied to every stimulus segment using a
 Gaussian-weighted least-squares straight line with a cutoff period of
@@
 
-For both naturalistic stimuli, we conducted a standard two-level general linear
-model (GLM) analysis in FEAT to create subject-specific results ($Z$-maps)
-across the 8 segments for every subject. A subsequent, third-level analysis averaged contrast estimates over subjects.
+Similar to the reviewed studies employing simplified stimuli, we conducted a
+standard two-level general linear model (GLM) analysis to create
+subject-specific results ($Z$-maps) across the 8 segments for every subject. A
+subsequent, third-level analysis averaged contrast estimates over subjects.
 
@@
 % procedure
-First, both annotations were split into eight parts corresponding to the eight
-stimulus segments.
+Both annotations were split into eight parts corresponding to the eight stimulus
+segments.
 % AO events
@@
 % pooling
-Some categories that were similar but offered only a small
-amount of counts were pooled resulting in eleven new categories (see Table
-\ref{tab:ao-events}). Events that fell into one of the two setting-related
-category but also into another category were treated as belonging to the
-setting-related category (\texttt{se\_new} or \texttt{se\_old}).
+Some categories that were similar but offered only a small amount of counts were
+pooled resulting in eleven new categories (see Table \ref{tab:ao-events}) that
+served as experimental conditions.
+% setting beats other category
+Events that fell into one of the two setting-related category but also into
+another category were treated as belonging to the setting-related category
+(\texttt{se\_new} or \texttt{se\_old}).
 % modeling as boxcar function
@@
 If a segment did not contain an event of a category, a null regressor was chosen
-for that segment.  \todo{wenn ich "null regressor" nehme, darf ich den ganzen
+for that category in that segment.\todo{wenn ich "null regressor" nehme, darf ich den ganzen
 Run, glaube ich, in der 2nd level Analyse gar nicht benutzen? Hatte, glaube ich,
@@
 of the soundscape after a cut, and to create contrasts of cross-modal negative
-control.
+control (see details below).
 % nuissance regressors
@@
 \texttt{fg\_ad\_rms} (root mean square volume) represent one event for every movie frame (\unit[40]{ms}).
-For a description of the five control conditions for movie cuts see Table
-\ref{tab:av-events}.}
+For a description of the five control conditions for movie cuts see Table \ref{tab:av-events}.}
 \label{tab:ao-events}
@@
 \ref{tab:av-events}): 1) a cut into an unfamiliar setting (\texttt{vse\_new}),
-2) a cut into a familiar setting (\texttt{vse\_old}), 3) a switch of locale
+2) a cut into a familiar setting (\texttt{vse\_old}), 3) a switch of room/locale
 within a setting (\texttt{vlo\_ch}), 4) a cut to an unfamiliar perspective
-(\texttt{vpe\_new}), and 5) a cut to familiar perspective (\texttt{vpe\_old}).
+(\texttt{vpe\_new}), and 5) a cut to a familiar perspective (\texttt{vpe\_old}).
 % null regressor
@@
 % how they were fitted
-\texttt{no\_cut} event had to have a minimum distance of \unit[10]{s} to a movie
+a \texttt{no\_cut} event had to have a minimum distance of \unit[10]{s} to a movie
 cut and to another \texttt{no\_cut} event.
@@
 \texttt{fg\_av\_ger\_lrdiff} (left-right volume difference) and \texttt{fg\_av\_ger\_rms} (root mean square volume) represent one event for every movie frame (\unit[40]{ms}).
-For description of the two events categories of the audio-description's
+For description of the two event categories of the audio-description's
 narrator (\texttt{se\_new} and \texttt{se\_old}) to build contrast
-of negative control see Table \ref{tab:ao-events}}
+of negative control see Table \ref{tab:ao-events}.}
 \label{tab:av-events}
@@
 The Pearson correlation coefficients of the regressors of the AO and AV stimulus
-and across the time course of all stimulus segments can be seen in Figure
-\ref{fig:reg-corr}.
+across the time course of all segments can be seen in Figure \ref{fig:reg-corr}.
 % temporal derivatives
@@
 \todo[inline]{contrasts are ordered by ``how well they make sense'' according to
-theory, ``quality of auditory cue'', and amount of events/data. Hence, they were
-assumed to result in more and more shitty results; at the moment all 8 contrasts
-are used in the result (figure)}
+theory, and amount of events/data. Hence, they were assumed to result in more
+and more shitty results; at the moment all 8 contrasts are used in the result
+(figure) despite the low ranked COPEs yielded 0 result as kinda expected}
 
@@
 For the AO stimulus, we created eight $t$-contrasts presumably correlating with
-increased hemodynamic activity in the PPA by contrasting different kind
+increased hemodynamic activity in the PPA by contrasting different kind of
 descriptive nouns.
 % furniture: blurred border between groom and object
-The categroy ``furniture'' (\texttt{furn} was not included in one of the
-contrast because it can be considered as an object or geometry-defining
-structure of a room.
+The category ``furniture'' (\texttt{furn}) was not included in one of the
+contrasts as regressor if interest because it can be considered as an object or
+geometry-defining structure of a room/locale.
 % negative control contrasts
-Five $t$-contrasts (see Table \ref{tab:ao-contrasts} we created for negative
+Five $t$-contrasts (see Table \ref{tab:ao-contrasts}) we created for negative
 control purposes to test if increased activation in the PPA was correlated with
@@
 variables.
-% cinematographic rationale
-% cut to new scenes: establishing shots
-The cinematographic rationale was that movie tend to establish the setting
+% cinematographic rationale cut to new scenes: establishing shots
+The cinematographic rationale was that movies tend to establish the setting
 (\texttt{vse\_new}) and the spatial relationships within a setting
@@
 % similarly for shots within a scene
-Shots within a recurring settings tend to shift to depicting persons and objects
-(\texttt{vpe\_old}) more relevant to the evolved narrative \citep{brown2012cinematography, mercado2011filmmakers}.
+Moreover, shots within a recurring locale or settings tend to shift to depicting
+persons and objects (\texttt{vpe\_old}) more relevant to the evolved narrative
+\citep{brown2012cinematography, mercado2011filmmakers}.
 % neuroscientific rationale
-The neuroscientific rationale was that simply that activity in the PPA is
+The neuroscientific rationale was simply that activity in the PPA is
 greater when participants view novel versus repeated scenes or view-points.
@@
 Five additional $t$-contrasts we created for negative control purposes (see
-Table \ref{tab:av-contrasts}.
+Table \ref{tab:av-contrasts}).
 
@@
 The GLM analysis that fitted each voxel's time course separately for each
-subject was performed in functional space preserving the orientation of the EPI
-images.
+subject and segment was performed in functional space preserving the orientation
+of the EPI images.
 % two ways of co-registration
-For the subsequent second level results, we co-registered the subjects in two
+We co-registered the subjects in two
 ways.
@@
 % \href{"https://github.com/psychoinformatics-de/studyforrest-data-templatetransforms/blob/master/sub-01/bold3Tp2/brain.nii.gz"}{example})
-On the one hand, subject-specific BOLD T1* time series were anatomically aligned
-via linear transformation to a subject-specific, study-specific T1* template.
+On the one hand, subject-specific BOLD T2* time series were anatomically aligned
+via linear transformation to a subject-specific, study-specific T2* template.
 % group template (for group and individual brain slices)
@@
 % MNI152
-This reference images was later co-registered to the MNI 152 template with an
+This reference image was co-registered to the MNI 152 template with an
 affine transformation (12 degrees of freedom) to facilitate visualization and
-identification of cortical structures,
+identification of cortical structures.
 
@@
         p<.05, cluster corrected) of contrasts created to isolate the PPA
-        overlaid on the MNI152 T1-weighted head template (grey).
-        Light grey: The audio-description's field-of-view
+        overlaid on the MNI152 T1-weighted head template (gray).
+        Light gray: The audio-description's field-of-view
         (cf. \citep{hanke2014audiomovie}).
@@
         (Z>3.4, p<.05 cluster-corrected) are overlaid on the MNI152 T1-weighted
-        head template (grey).
-        Light grey: The audio-description's field-of-view
+        head template (gray).
+        Light gray: The audio-description's field-of-view
         (cf. \citep{hanke2014audiomovie}).
@@
 degrees of freedom) to facilitate comparisons across subjects.
-        Light grey: The audio-description's field-of-view
+        Light gray: The audio-description's field-of-view
         (cf. \citep{hanke2014audiomovie}).
@@
 We constrained the number of voxels to voxels in the occipital and temporal
-lobes (grey) using the (probabilistic) Jülich Histological Atlas
+lobes (gray) using the (probabilistic) Jülich Histological Atlas
 \citep{eickhoff2005toolbox, eickhoff2007assignment} to voxels located in the
@@
         two voxels (KDE plot on the right). The overlays depict voxels spatially
-        contrained to be located in the temporal and occipital cortex (grey),
+        contrained to be located in the temporal and occipital cortex (gray),
     PPA overlap of all subjects (blue), and individual PPA (red).}

### 2020-07-24 paper/main.tex
(small) revision of results

@@
 % two ways of co-registration
-We co-registered the subjects in two
-ways.
+We co-registered the subjects in two ways.
 % subject template (for Bland-Altman-Plot of unthresholded maps)
@@
 % MNI152
-This reference image was co-registered to the MNI 152 template with an
-affine transformation (12 degrees of freedom) to facilitate visualization and
+This reference image was co-registered to the MNI 152 template with an affine
+transformation (12 degrees of freedom) to facilitate visualization and
 identification of cortical structures.
@@
 
-% HOW TO WRITE METHODS SEXTION
-% first paragraph (cause most readers don't read methods beforehand
-% summarizes the overall approach to the problem outlined in the intro
-% key innovative methods that were developed
-% -> gist of the methods that were used
-The goal of this study was to exploratorily investigate how the PPA responds to
-auditory cues embedded in a naturalistic audio-only stimulus. We further aimed
-at comparing these results to results to an audio-visual naturalistic stimulus
-and to results from a dedicated visual localizer experiment.
-
-We did this by using GLM... blabla...
+% summary of methods: AO
+We used conventional GLM contrast to exploratorily investigate how the PPA
+responds to auditory cues embedded in a naturalistic audio-only stimulus.
+% summary of methods: AV
+We compare these results to results to an audio-visual naturalistic stimulus and
+to results from a dedicated visual localizer experiment.
+
 % subsequent paragraphs start with a sentence or two
@@
 % why we did different contrasts
-We tested a variety of contrasts to ensure\dots ???
+Despite having chosen a primary contrasts which we assumed to give the best
+results, we created a variety of contrasts to test if our approach yielded
+similar results across a variety of contrasts.
 
@@
 
-% AO
-\todo{alle noch einmal im einzelnen angucken; was ist mit COPE 8, der ist in der
-Abb. nicht drin; zeigt (noch) einer keine sign. cluster?}
-% intro
-We combined different event categories to create eight contrasts that provided
-different congruency with the spatial layout hypothesis and different amount of
-data/events.
-% PPA
-Six of seven AO contrasts show significant bilateral clusters in anterior
-regions of the group PPA overlap (which is temporal occipital fusiform gyrus
-regarding to co-registered Harvard-Oxford Cortical Structural Atlas).
+% AO eight contrasts
+For the analysis of the AO stimulus, we combined different event categories to
+create eight contrasts that provided different amount of data/events and
+decreasing congruency with the spatial layout hypothesis.
+% results in PPA
+Six of eight AO contrasts show significant bilateral clusters in anterior
+regions of the group PPA overlap.\todo[inline]{which is temporal occipital
+fusiform gyrus regarding to co-registered Harvard-Oxford Cortical Structural
+Atlas}
 % Precuneus = retrosplenial cortex ?
-Six of seven contrasts show significant clusters in the ventral precuneus /
+Six of eight contrasts show significant clusters in the ventral precuneus /
 retrosplenial cortex (RSC).
-
-% AV
-% intro
-We also created five contrasts for the audio-visual stimulus by using different
-kind of cuts to be able to compare results across perceptual modalities.
+% statement/answer
+This suggest results are reproducible in a variety of contrasts and do not
+depend on the design of one specific contrasts.
+
+% AV intro
+For the analysis of the AV stimulus, we created five contrasts for a cross-modal
+comparison.
 % PPA
@@
 individual PPA ROIs.
-% Lingual Gyrus
-Homologous clusters of three contrasts extend further into lingual gyrus.
+% lingual gyrus
+In three contrasts, these homologous clusters extend into the lingual gyri.
 % RSC
-Three contrasts show significant bilateral clusters in RSC.
+Further, three contrasts show significant homologous clusters in the RSC.
 % LOC
-Four contrasts show significant bilateral clusters in lateral occipital cortex
+Lastly, four contrasts show significant homologous clusters in lateral occipital
+cortices.
+% statement/answer
+Here again, we can show that results can in principle be accomplished by varying
+the design of the contrasts. Nevertheless, results are sensible to the amount of
+data used in the contrasts and it's congruency with the spatial layout
+hypothesis.
 
@@
     \caption{Stability of contrasts. Overlap of significant clusters (Z>3.4;
-        p<.05, cluster corrected) of contrasts created to isolate the PPA
-        overlaid on the MNI152 T1-weighted head template (gray).
-        Light gray: The audio-description's field-of-view
-        (cf. \citep{hanke2014audiomovie}).
-        Blue: contrasts 1-7 for the audio-description (see Table \ref{tab:ao-contrasts}.
-        Red: contrasts 1-5 for the audio-visual movie (see Table \ref{tab:av-contrasts}.
-        Black: outline of overlapping individual PPA ROIs
-        \citep{sengupta2016extension}.}
-    \label{fig:stability-slices}
+        p<.05, cluster corrected) of contrasts created to isolate the PPA.
+        Contrasts provide decreasing congruency with the spatial layout
+        hypthesis and/or progressively less data/events. The overlap across
+        contrasts is overlaid on the MNI152 T1-weighted head template (gray).
+        Light gray: The audio-description's field-of-view (cf.
+        \citep{hanke2014audiomovie}).  Blue: contrasts 1-7 for the
+        audio-description (see Table \ref{tab:ao-contrasts}.  Red: contrasts 1-5
+        for the audio-visual movie (see Table \ref{tab:av-contrasts}.  Black:
+        outline of overlapping individual PPA ROIs
+        \citep{sengupta2016extension}.} \label{fig:stability-slices}
     \end{figure*}
@@
 % intro
+For the primary contrast of the AO and AV stimulus, we report results on a group
+level, on an individual level. Finally, we compare individual results of the AO
+stimulus to the dedicated localizer paradigm.
+
 \todo{intro sentence regarding the primary contrasts}
@@
 The primary $t$-contrast for the audio-description comparing geometry-related
-nouns to non geometry-related nouns spoken by the audio-description's narrator
-(\texttt{geo, groom > all non-geo} yielded six significant clusters (see Table
-\ref{tab:res-ao-group1}, Figure \ref{fig:group-slices}).
+nouns to non geometry-related nouns spoken by narrator (\texttt{geo, groom > all
+non-geo} yielded six significant clusters (see Table \ref{tab:res-ao-group1},
+Figure \ref{fig:group-slices}).
+% PPA
+First, two fall into the anterior part of the visual localizer group overlap
+mask.
+% location
+They are located (in part) in the lingual gyrus, occipital and temporal fusiform
+gyrus, and posterior parahippocampal cortex \todo{the clusters are small but
+that's what the Harvard-Oxford Atlas suggests, clusterss are at borders of the
+areas}.
 % precuneus
-Two homologous clusters in the ventral precuneus extending into the
-retrosplenial cortex.
-% PPA
-Two homologous clusters in the lingual gyrus, occipital and temporal fusiform
-gyrus, and posterior parahippocampal cortex \todo{the clusters are small but
-that's what the Harvard-Oxford Atlas suggests, cluster is at borders of the
-areas}.
+Second, the contrasts yielded two homologous clusters in the ventral precuneus extending into the retrosplenial cortex.
 % LOC
-And finally, two homologous clusters in the superior lateral occipital cortex.
-
-% AV
-% intro
-\todo{intro sentence regarding the primary contrasts}
-% the contrast in detail
+Finally, two homologous clusters are located in the superior lateral occipital cortex.
+
+% AV intro
+For cross-modal comparison purposes, we also analyzed data from the audio-visual
+movie.
+% the primary contrast
 The primary $t$-contrast for the movie comparing cuts to a new setting with cuts
@@
 \ref{fig:group-slices}).
-% LOC
-Two clusters in the superior lateral occipital cortex (left bigger than right).
 % PPA + others.
@@
 gyrus and temporal fusiform gyrus, and parahippocampal cortex bilaterally.
+% LOC
+Two homologous clusters are located in the superior lateral occipital cortex
+(left bigger than right).
 
@@
         vpe\_old}).
-        Black: outline of overlapping individual PPA ROIs.
-        \citep{sengupta2016extension}.}
+        Black: outline of overlapping individual PPA ROIs      \citep{sengupta2016extension}.}
     \label{fig:group-slices}
@@
 % why
-Analysis in group space (Z>3.4, p<.05 cluster-corrected) was performed for
-better comparison of results across participants.
+For better comparison of results across participants, we report results of the
+analysis that was performed in group space (Z>3.4, p<.05 cluster-corrected).
 % ref to figure
@@
 right clusters in two subjects (sub-04, sub-20).
+% subjective threshold
+Noteworthy, ROIs were assessed by \citep{sengupta2016extension} by visually
+inspecting the unthresholded $z$-maps, and setting a subjectively best fitting
+$z$-threshold to isolate the PPA.
 
 % AO
-AO stimulus shows bilateral clusters in nine subjects, and one significant cluster in the
-left hemisphere in sub-09.
+In the current analysis of the AO stimulus, we find significant bilateral
+clusters in nine subjects, and one significant cluster in the left hemisphere of sub-09.
 % subj-04
@@
 % AV
-AV shows homologous clusters in five subjects, and unilateral right clusters in
-seven subjects (of which one subjects also yielded just a unilateral cluster in
-the dedicated localizer).
+For the AV stimulus, results show homologous clusters in five subjects, and
+unilateral right clusters in seven subjects (of which one subjects also yielded
+just a unilateral cluster in the dedicated localizer).
 % difference to dedicated localizer
@@
 % why
-To better depict the agreement (and difference) between brain responses to the
+To better depict the agreement (and difference) between indivudal results of the
 visual localizer and contrast 1 of the AO paradigm, we created
@@
 % what do Bland-Altman-Plots show?
-The plots for the 14 subjects show the mean of z-values of two spatially
-corresponding voxels in unthresholded z-maps on the x-axis and their difference
-on the y-axis (dedicated localizer minus AO stimulus).
+The plots for the 14 subjects show the mean of $z$-values of two spatially
+corresponding voxels in unthresholded z-maps on the x-axis and the difference of
+$z$-values of these two voxels on the y-axis (dedicated localizer minus AO
+stimulus).
 % masking
-We constrained the number of voxels to voxels in the occipital and temporal
-lobes (gray) using the (probabilistic) Jülich Histological Atlas
-\citep{eickhoff2005toolbox, eickhoff2007assignment} to voxels located in the
-PPA overlap of all subjects (blue), and voxels in the individual PPA
-ROI(s)(red).
-
+We constrained the number of voxels in three ways. Voxels were spatially
+contrained to a) voxels in the occipital and temporal lobes (gray; using the
+(probabilistic) Jülich Histological Atlas \citep{eickhoff2005toolbox,
+eickhoff2007assignment}), b) voxels located in the PPA overlap of all subjects
+(blue), and c) voxels in the individual PPA ROI(s)(red).
 % what we can see
@@
 higher z-values in the AO stimulus.
+
+\todo[inlin]{concluding statement for the paragraph}
 

### 2020-07-24 paper/main.tex
structure & some ideas for discussion

@@
 
-\todo[inline]{at the moment I tend to reporting the stability of contrast first,
-and then go on to report the primary contrasts for group and individuals; both
-has pros and cons}
+\todo[inline]{at the moment I think it is better to report the primary contrast
+fist and then report the stability of contrast; but that opinion changend twice
+already, so here in the text stability of contrast is still reported first}
 
@@
 
-% Discussion explains how results fill gap identified in intro
-% provides caveats to the interpretation
-% describes how paper advances the field by providing new opportunities.
-
-% typically done by recapitulating the results, discussing limitations,
-% and then revealing how the central contribution may catalyze future progress.
-
-% first discussion paragraph is special in that it generally summarizes the
-% important findings from the results section -> give gist of results
-
-% following paragraphs in the discussion section starts by describing an area of weakness or strength of the paper.
-% It then evaluates the strength or weakness by linking it to the
-% relevant literature.
-
-% Discussion paragraphs often conclude by describing a clever, informal way of perceiving the contribution or by discussing future directions that can extend the contribution.
-
-% For example, the first paragraph may summarize the results, focusing on their meaning.
-
-% The second through fourth paragraphs may deal with potential weaknesses and with how the literature alleviates concerns or how future experiments can deal with these weaknesses.
-
-% The fifth paragraph may then culminate in a description of how the paper moves
-% the field forward.
-
-%Step by step, the reader thus learns to put the paper’s conclusions into the right context.
-
 \todo[inline]{MIH: discussion should primarily be anchored on the points the
@@
 
-\paragraph{From Poster}: 1. PPA shows increased activation during non-visual,
-complex auditory stimulation that provides incidental spatial information.
-
-2. only minor temporal correlation of regressors of the audio drama \& movie that were not designed for experimental research.
-
-3. but still, alternative contrasts show significant clusters in auditory
-cortices.
-
-4. inter-individual differences: for two subjects, an alternative audio-contrast
-shows bilaterally significant clusters whereas the primary contrast shows no
-significant clusters.
-
-5. audio drama shows bilaterally increased activation in subject 4 in which the
-visual localizer shows an unilateral cluster.
-
-6. nevertheless, a  complex auditory stimulus might allow individual
-localization of a functionally defined brain region.
-
-7. results of other studies suggest7 the PPA does not exclusively process the
+% Discussion explains how results fill gap identified in intro
+% provides caveats to the interpretation
+% describes how paper advances the field by providing new opportunities.
+
+% typically done by recapitulating the results, discussing limitations,
+% and then revealing how the central contribution may catalyze future progress.
+
+% first discussion paragraph is special in that it generally summarizes the
+% important findings from the results section -> give gist of results
+
+% following paragraphs in the discussion section starts by describing an area of weakness or strength of the paper.
+% It then evaluates the strength or weakness by linking it to the
+% relevant literature.
+
+% Discussion paragraphs often conclude by describing a clever, informal way of perceiving the contribution or by discussing future directions that can extend the contribution.
+
+% For example, the first paragraph may summarize the results, focusing on their meaning.
+
+% The second through fourth paragraphs may deal with potential weaknesses and with how the literature alleviates concerns or how future experiments can deal with these weaknesses.
+
+% The fifth paragraph may then culminate in a description of how the paper moves
+% the field forward.
+
+%Step by step, the reader thus learns to put the paper’s conclusions into the right context.
+We used two naturalistic stimuli + annotation + GLM and investigated if we could
+isolate the PPA not just in an group average analysis but also on an individual
+level. We focus on the audio-only stimulus but performed a analysis for the AV
+stimulus as well (not controlling for frame content after cuts).
+
+% Correlation of regressors
+Events/Regressors are of little to no correlation despite stimulus was used as
+designed for entertainment purposes.
+
+\subsection{Group analysis}
+
+% AO stimulus
+% cluster location
+AO stimulus isolated spatially concise cluster in anterior part of group overlap mask/roi.
+% confounds
+2h audio-description offering sufficient events such that many confounding
+variables average out (but some anternative contrasts show clusters in auditory
+cortices)
+% summary statement
+This suggest spoken language cues correlate with increased activation in higher
+visual areas bilaterally.
+
+% RSC
+words to clusters in RSC? -> see Aminoff (20xx). What does the retrosplenial
+cortex do?
+
+% theory what the PPA does
+\todo[inline]{aminoff2013: jedoch zu non-spatial stuff: Although the PHC is
+commonly thought of as responding to visual stimuli, it has also been found to
+elicit activity for auditory stimuli [25,26,30,31] and to respond to odor
+stimuli [32–34].}
+% Mental Imagery Hypothesis
+Mental Imagery Hypthesis (s. O'Craven \& Kanwisher, 2000); Lerner (2011), Honey
+(2012), Silbert (2014) finden keine ISC in PPA? vgl. auch DataPaper bzgl.
+Hörbuch??
+% we
+We got not task not time to form a vivid mental image; if at all automatic
+on-the-fly process; further not task to keep subjects attentive to the stimulus
+and espcially spatial cues
+% PPA is not visual exclusively
+results of other studies suggest7 the PPA does not exclusively process the
 ``spatial layout''" but ``contextual associations''.
-
-8. an audio drama might be suitable as ecologically more valid ``localizer'' for
-a variety of brain functions.
-
-\subsection{AO Discussion}
-
-Hanke et al. (2014): Compared to an audio-visual movie, this is a stimulus that
-leaves a much larger margin for inter-individual differences in imagining
-scenery, as well as actors' character and personality traits, while still
-preserving the time-locked presentation of information to a listener. At the
-same time, an auditory stimulus limits the effect of an attentional focus on the
-selection of a subset of simultaneously occurring auditory events, in contrast
-to the selection of different parts of the visual field.
-
-aminoff2013: jedoch zu non-spatial stuff: Although the PHC is commonly thought
-of as responding to visual stimuli, it has also been found to elicit activity
-for auditory stimuli [25,26,30,31] and to respond to odor stimuli [32–34].
-
-Unterschiedliche Qualität der Kontrast: Warum wurde Kontrast 1 als Kontrast 1
-gewählt; se\_new se\_old sind recht vague in der Beschreibung der Szene
-verglichen mit Bild; Anzahl der Events ergibt auch noch Sinn
-
+% difference to Aziz
+Aziz modeled as boxcar from sentence onset to offset.
+
+% AV stimulus cluster location
+AV middle and posterior part of group overlap mask/roi.
+% confounds
+extending into more posterior regions (which exactly?).
+% not controlled frame content
+putativ function of those regions?
+% number of events?
+confounds to not average out in (early) visual areas.
+% nevertheless
+imo it's cool, that this approach of blindly averaging the frames' content works
+at all.
+
+\subsection{stability of contrasts}
+% why we did a couple of contrasts
+it's not cherry picking of one contrast.
+% declining quality of results
+contrasts were assumed to be of ``declining'' quality of results which turned
+out to be the case.
+% decreasing congruency and amount of data
+results are kinda stable and not just an accidental finding. Nevertheless,
+performance of functional isolation is sensitive to amount of data used and
+congruency of contrasts with spatial layout hypothesis.
+
+\subsection{individual analyses}
+% AO
+We were able to get isolated cluster in anterior part of individual PPA masks in
+majority of subjects.
+% one threshold for all
+Same threshold for all subjects, PPA ROIs were visually / subjectively chosen.
+% inter-individual differences
+\todo[inline]{which contrasts work better in some subjects?}
+% sub-xy
+AO yielded bilateral cluster whereas AV stimulus yielded XY and even the
+dedicated localizer yieled just one unilateral custer.
+
+% summary statement
+Results suggest naturalistic AO stimulus can be used as an non-visual localizer
+of a visual area in individual subjects.
+% with other words
+a  complex auditory stimulus might allow individual localization of a
+functionally defined brain region.
+% and again other words
+an audio drama might be suitable as ecologically more valid ``localizer'' for a
+variety of brain functions.
+% other example: speech areale
+other possibilities: low level features, stuff annotated in speech annotation
+
+% multiple localizer
+% PPA is just one example
+2h stimulus for just one process is long but chosen cognitive function is just
+one aspect that can be investigated with a complex naturalistic stimulus.
+
+% AV
+On individual level, mixed results for AV stimulus.
+% individual differences
+Individual differences when seeing a whole picture with many features vs. stream
+of serial auditory information providing incidential cues; spatial attention?
+\todo[inlin]{which contrast works better in which subjects?}
+
+% AO vs. AV
+AO vs. AV\dots
+\todo[inline]{Hanke et al. (2014): Compared to an audio-visual movie, this is a
+    stimulus that leaves a much larger margin for inter-individual differences
+    in imagining scenery, as well as actors' character and personality traits,
+    while still preserving the time-locked presentation of information to a
+    listener. At the same time, an auditory stimulus limits the effect of an
+    attentional focus on the selection of a subset of simultaneously occurring
+    auditory events, in contrast to the selection of different parts of the
+visual field}.
+
+\subsection{shortcommings}
+
+% spatial cues can belong to different categories
 setting\_new ist häufig vermischt mit anderer Kategorie "ein Arzt", "ein alter
@@
 "Jenny als Teenager", "Forrest vor einem Buffet", "Kennedy", "Jenny kommt aus
-dem Wohnwagen ihrer Großmutter" Soundscape macht es häufiger bereits vorher
-klar, dass Settingwechsel ist bzw. nicht erst das annotiere Substantiv object
-und (room)geo ist vermischt Retrospelinal Cortex ist in Probabilistic maps
-krasser als PPA.
-
-Mental Imagery Hypthesis (s. O'Craven \& Kanwisher, 2000); Lerner (2011), Honey
-(2012), Silbert (2014) finden keine ISC in PPA? vgl. auch DataPaper bzgl.
-Hörbuch??
-
-Contrasts 6-8: words belonging to the categories \texttt{se\_new} and
-\texttt{se\_old} were very vague in describing a scene compared to the richness
-of a picture. Hence, we assumed smaller probability of successfully isolating
-the PPA.
-
-\subsection{AV discussion}
-lore ipsum
-
-\section*{General Discussion}
-
-\subsection{Data-driven vs. Analysis-Driven}
-"Abfall" einer Film-Messung
-
-\subsection{naturalistic vs. dedicated} how do results (PPA-like response
-localization) differ from a standard visual/block-design localizer for:
-
-\subsection{anterior (AO) vs. posterior (AV) PPA}
-
-\subsection{parietal and RSC activations} Story für parietale Aktivierung im
-Film -> räuml. Orientierung / Aufmerksamkeit
+dem Wohnwagen ihrer Großmutter"
+% soundsscapes makes change of setting obvious before narrator kicks in
+Soundscape macht es häufiger bereits vorher klar, dass Settingwechsel ist bzw.
+nicht erst das annotiere Substantiv object und (room)geo ist vermischt
+Retrospelinal Cortex ist in Probabilistic maps krasser als PPA.
+
+% se_new and se_old
+especially relevant for contrasts 6-8: words belonging to the categories
+\texttt{se\_new} and \texttt{se\_old} were very vague in describing a scene
+compared to the richness of a picture. Hence, we assumed smaller probability of
+successfully isolating the PPA.
+
+\subsection{open question: anterior (AO) vs. posterior (AV) PPA}
 
@@
 
-\subsection{multi-dimensional localizer???}
-feasibility of (multi-dimensional) localizer development with naturalistic
-stimuli.
+\subsection{re-use of existing data for new, independent research questions}
+there is more in a complex naturalistic stimulus.
 

### 2020-08-05 paper/main.tex
revision of results

@@
 % furniture: blurred border between groom and object
-The category ``furniture'' (\texttt{furn}) was not included in one of the
-contrasts as regressor if interest because it can be considered as an object or
-geometry-defining structure of a room/locale.
+We did not use the category ``furniture'' (\texttt{furn}) as a regressor in one
+of the contrasts of interest because this category was considered to eighter
+count as object or a geometry-defining structure of a room/locale.
 % negative control contrasts
@@
 control purposes to test if increased activation in the PPA was correlated with
-moment of cuts and therefore correlated with a possible change in the
-soundscape.
+moments of cuts and therefore correlated with a possibly accompanying change in
+the soundscape (anticipating the narrator's cue of a switch to new setting, too).
 
@@
         the audio-only stimulus (AO).
-\texttt{all non-geo} = body, bodypart, fahead, object, sex\_f, sex\_m).
+\texttt{all non-geo} = body, bodypart, fahead, object, sex\_f, sex\_m.
 Contrast 1-8 aim to isolate the PPA.
@@
 % similarly for shots within a scene
-Moreover, shots within a recurring locale or settings tend to shift to depicting
-persons and objects (\texttt{vpe\_old}) more relevant to the evolved narrative
+Moreover, shots within a recurring locale or setting tend to shift to depicting
+persons and objects (\texttt{vpe\_old}) more relevant to the evolved plot
 \citep{brown2012cinematography, mercado2011filmmakers}.
@@
 \paragraph{alignment etc.}
+
+\todo[inline]{give references to the publications explaining the template
+creation; take a look at Sengupta (2016), and maybe speech-anno-paper}
 % single subjects (for Bland-Altman-Plots) 1st level
@@
 % MNI152
-This reference image was co-registered to the MNI 152 template with an affine
+This group template was co-registered to the MNI 152 template with an affine
 transformation (12 degrees of freedom) to facilitate visualization and
@@
 
-\todo[inline]{at the moment I think it is better to report the primary contrast
-fist and then report the stability of contrast; but that opinion changend twice
-already, so here in the text stability of contrast is still reported first}
-
 % summary of methods: AO
-We used conventional GLM contrast to exploratorily investigate how the PPA
-responds to auditory cues embedded in a naturalistic audio-only stimulus.
+We used conventional GLM contrasts to exploratorily investigate if auditory cues
+embedded in a naturalistic audio-only stimulus correlate with increased
+hemodynamic activity in the PPA.
 % summary of methods: AV
-We compare these results to results to an audio-visual naturalistic stimulus and
-to results from a dedicated visual localizer experiment.
+We compare these results on a group and individual level to results gained from
+an audio-visual naturalistic stimulus and to results from a dedicated visual
+localizer experiment.
 
@@
 
-\todo[inline]{I consider tables of significant clusters for every contrast as
-overkill. One contrast, the ``primary contrast'', is appropriate.}
-
-\subsection{stability contrasts}
-
-% why we did different contrasts
-Despite having chosen a primary contrasts which we assumed to give the best
-results, we created a variety of contrasts to test if our approach yielded
-similar results across a variety of contrasts.
-
-% results
-The overlap of significant clusters of the 7 (well actually 8) contrast for the
-audio-description, and 5 contrasts computed for the movie can be found in Figure
-\ref{fig:stability-slices}.
-
-% AO eight contrasts
-For the analysis of the AO stimulus, we combined different event categories to
-create eight contrasts that provided different amount of data/events and
-decreasing congruency with the spatial layout hypothesis.
-% results in PPA
-Six of eight AO contrasts show significant bilateral clusters in anterior
-regions of the group PPA overlap.\todo[inline]{which is temporal occipital
-fusiform gyrus regarding to co-registered Harvard-Oxford Cortical Structural
-Atlas}
-% Precuneus = retrosplenial cortex ?
-Six of eight contrasts show significant clusters in the ventral precuneus /
-retrosplenial cortex (RSC).
-% statement/answer
-This suggest results are reproducible in a variety of contrasts and do not
-depend on the design of one specific contrasts.
-
-% AV intro
-For the analysis of the AV stimulus, we created five contrasts for a cross-modal
-comparison.
-% PPA
-All five AV contrasts yielded significant bilateral clusters in (temporal)
-occipital, fusiform cortex showing congruency with the group overlap of
-individual PPA ROIs.
-% lingual gyrus
-In three contrasts, these homologous clusters extend into the lingual gyri.
-% RSC
-Further, three contrasts show significant homologous clusters in the RSC.
-% LOC
-Lastly, four contrasts show significant homologous clusters in lateral occipital
-cortices.
-% statement/answer
-Here again, we can show that results can in principle be accomplished by varying
-the design of the contrasts. Nevertheless, results are sensible to the amount of
-data used in the contrasts and it's congruency with the spatial layout
-hypothesis.
-
-\begin{figure*} \centering
-    \includegraphics[width=\linewidth]{figures/stability-slices}
-    \caption{Stability of contrasts. Overlap of significant clusters (Z>3.4;
-        p<.05, cluster corrected) of contrasts created to isolate the PPA.
-        Contrasts provide decreasing congruency with the spatial layout
-        hypthesis and/or progressively less data/events. The overlap across
-        contrasts is overlaid on the MNI152 T1-weighted head template (gray).
-        Light gray: The audio-description's field-of-view (cf.
-        \citep{hanke2014audiomovie}).  Blue: contrasts 1-7 for the
-        audio-description (see Table \ref{tab:ao-contrasts}.  Red: contrasts 1-5
-        for the audio-visual movie (see Table \ref{tab:av-contrasts}.  Black:
-        outline of overlapping individual PPA ROIs
-        \citep{sengupta2016extension}.} \label{fig:stability-slices}
-    \end{figure*}
-
 \subsection{primary contrasts}
-% intro
-For the primary contrast of the AO and AV stimulus, we report results on a group
-level, on an individual level. Finally, we compare individual results of the AO
-stimulus to the dedicated localizer paradigm.
-
-\todo{intro sentence regarding the primary contrasts}
+
+\todo[inline]{at the moment I think it is better to report the primary contrast
+fist and then report the stability of contrast; but that opinion changend twice
+already.}
+
+\todo[inline]{concluding statement for each paragraphs?}
+
 % the contrast in detail
 The primary $t$-contrast for the audio-description comparing geometry-related
-nouns to non geometry-related nouns spoken by narrator (\texttt{geo, groom > all
-non-geo} yielded six significant clusters (see Table \ref{tab:res-ao-group1},
-Figure \ref{fig:group-slices}).
+nouns to non geometry-related nouns spoken by the narrator (\texttt{geo, groom >
+all non-geo} yielded six significant clusters (see Table
+\ref{tab:res-ao-group1}, Figure \ref{fig:group-slices}).
 % PPA
-First, two fall into the anterior part of the visual localizer group overlap
-mask.
+Two homologous clusters are located in the anterior part of the visual localizer
+group overlap mask.
 % location
-They are located (in part) in the lingual gyrus, occipital and temporal fusiform
-gyrus, and posterior parahippocampal cortex \todo{the clusters are small but
-that's what the Harvard-Oxford Atlas suggests, clusterss are at borders of the
-areas}.
+More specifically, they are partially located in the lingual gyrus, occipital
+and temporal fusiform gyrus, and posterior parahippocampal cortex \todo{the
+    clusters are small but that's what the Harvard-Oxford Atlas suggests,
+    clusters are at borders of the areas; dunno how to report this; sound shitty
+to me}.
 % precuneus
-Second, the contrasts yielded two homologous clusters in the ventral precuneus extending into the retrosplenial cortex.
+Two additional clusters are located in the ventral precuneus extending into the
+retrosplenial cortex.
 % LOC
-Finally, two homologous clusters are located in the superior lateral occipital cortex.
+Finally, the contrast yielded two homologous clusters in the superior lateral
+occipital cortex.
 
@@
 For cross-modal comparison purposes, we also analyzed data from the audio-visual
-movie.
+movie by contrasting different kinds of movie cuts independent from the frames'
+visual content after the cuts.
 % the primary contrast
-The primary $t$-contrast for the movie comparing cuts to a new setting with cuts
+The movie's primary $t$-contrast that compared cuts to a new setting with cuts
 to a familiar perspective (\texttt{vse\_new > vpe\_old}) yielded three
@@
 % PPA + others.
-And one one cluster spanning across the midline and comprising intracalcarine
+One cluster spanning across the midline comprising parts of the intracalcarine
 and cuneal cortex, lingual gyrus and retrosplenial cortex, occipital fusiform
-gyrus and temporal fusiform gyrus, and parahippocampal cortex bilaterally.
+gyrus and temporal fusiform gyrus, and the parahippocampal cortex of both
+hemispheres.
 % LOC
-Two homologous clusters are located in the superior lateral occipital cortex
-(left bigger than right).
+Two additional homologous clusters are located in the superior lateral occipital
+cortex (left bigger than right).
 
@@
 We also investigated localization performance of both naturalistic paradigms on
-the level of individual subjects. \todo{maybe report reason here, too: which
-subjects influence the group results the most? ``multiple localizer''?}
+the level of individual subjects. \todo{maybe report the other reason here, too:
+which subjects influence the group results the most? ``multiple localizer''?}
 % results in both subject and group space
 Time series of all subjects were analyzed both in subject space and group space.
+% individual z-maps
+Results of the analyses that were performed in each subject's subject-space
+(unthresholded $z$-maps and thresholded $z$-maps with Z>2.3, p<.05) can be
+found in the accompanying dataset.
 % why
-For better comparison of results across participants, we report results of the
-analysis that was performed in group space (Z>3.4, p<.05 cluster-corrected).
+For better comparison of results across participants, we show results ($z$-maps;
+Z>3.4, p<.05 cluster-corrected) of the analyses that was performed in group
+space.
 % ref to figure
-Figure \ref{fig:subs-thresh-ppa} depicts thresholded z-maps of the primary AO
-and AV $t$-contrast and the outline of the individual PPAs
+Figure \ref{fig:subs-thresh-ppa} depicts thresholded $z$-maps of the primary AO
+and AV $t$-contrast, and the outline of the individual PPAs
 \citep{sengupta2016extension} overlayed on the MNI152 template (horizontal slice
 z=-11 for all subjects).
-
 % results in detail voxels of significant clusters in PPA ROI (and  RSC
@@
 inspecting the unthresholded $z$-maps, and setting a subjectively best fitting
-$z$-threshold to isolate the PPA.
-
+$z$-threshold to isolate a cluster in the PPA.
 % AO
@@
 yielded only one cluster in the right hemisphere.
-
 % AV
@@
 In sub-20 bilateral, where the dedicated localizer yielded only one cluster in
-the right hemisphere
+the right hemisphere.
 
@@
 To better depict the agreement (and difference) between indivudal results of the
-visual localizer and contrast 1 of the AO paradigm, we created
-Bland-Altman-Plots (see Figure \ref{fig:bland-altman}).
-% what do Bland-Altman-Plots show?
-The plots for the 14 subjects show the mean of $z$-values of two spatially
-corresponding voxels in unthresholded z-maps on the x-axis and the difference of
-$z$-values of these two voxels on the y-axis (dedicated localizer minus AO
-stimulus).
+visual localizer and contrast 1 of the AO paradigm, we created one
+Bland-Altman-Plots for each of the 14 subjects (see Figure
+\ref{fig:bland-altman}).
+% x-axis
+The x-axis of every subplot depicts the mean of $z$-values of two spatially
+corresponding voxels taken from a subject's unthresholded $z$-map.
+% y-axis
+The y-axis of every subplot depicts the difference of $z$-values of two
+spatially corresponding voxels (dedicated localizer minus AO stimulus).
 % masking
-We constrained the number of voxels in three ways. Voxels were spatially
-contrained to a) voxels in the occipital and temporal lobes (gray; using the
-(probabilistic) Jülich Histological Atlas \citep{eickhoff2005toolbox,
-eickhoff2007assignment}), b) voxels located in the PPA overlap of all subjects
-(blue), and c) voxels in the individual PPA ROI(s)(red).
-% what we can see
+We constrained the number of voxels in three ways as indicated by three colors
+(grey, blue, red).
+% masking in detail
+Voxels were spatially contrained to a) voxels located in the occipital and
+temporal lobes (gray; using the (probabilistic) Jülich Histological Atlas
+\citep{eickhoff2005toolbox, eickhoff2007assignment}), b) voxels located in the
+PPA overlap of all subjects (blue), and c) voxels located in the individual PPA
+ROI(s)(red).
+% top KDE plot
 A shift of the distribution to voxels with a mean above zero can be seen the
-further we constrain voxels to the individual PPA (KDE plot for the x-axis).
-% but
-Values above the horizontal line depict voxels that show a higher z-value in the
-dedicated localizer, values below the horizontal line depict voxels that show
-higher z-values in the AO stimulus.
-
-\todo[inlin]{concluding statement for the paragraph}
-
-\todo[inline]{the plots are ``biased'' in the PPA mask in such a way that they
-don't take into account that clusters are not 100 perc. congruent, meaning the
-AO stimulus has voxels in regions that are outside of the individual PPA ->
-probably bias to show higher values for the dedicated localizer (red voxels)}
+further we constrain voxels to the individual PPA (see KDE plot for the x-axis).
+% right KDE plot
+Values above the horizontal line depict voxels that show a higher $z$-value in
+the dedicated localizer, values below the horizontal line depict voxels that
+show higher $z$-value in the AO stimulus.
 
@@
 
+\subsection{stability contrasts}
+
+\todo[inline]{I consider tables of significant clusters for every contrast as
+overkill. One contrast, the ``primary contrast'', is appropriate.}
+
+% all AO contrasts
+% 1 geo, groom > non-geo:               PPA (l/r); RSC (l/r)
+% 2 geo, groom, se_new > non-geo:       PPA (l/r); RSC (l/r)
+% 3 groom, se_new, se_old > non-geo:    PPA (l/r); RSC (l/r)
+% 4 geo > all non-geo PPA               PPA (l/r); RSC (l/r)
+% 5 groom > all non-geo PPA             PPA (l/r); RSC (l/r)
+% 6 se_new > all non-geo PPA            PPA (l/r); RSC (l/r)
+% 7 se_new, se_old > all non-geo PPA               RSC (l/r)
+% 8 se_new > se_old                     nothing
+% 9 vse_new > vpe_old                              RSC (r)
+%10 vse_new, vpe_new > vse_old, vpe_old nothing
+%11 vse_new > vse_old                   nothing
+%12 vse_new > vse_old, vpe_old          nothing
+%13 vse_new, vpe_new > vpe_old          nothing
+
+% all AV contrasts
+% 1 vse_new > vpe_old: big bilateral cluster in PPA but also RSC, visual c.
+% 2 vse_new, vpe_new > vse_old, vpe_old:
+% group results are more more confined here
+% (but individual results were probably worse)
+% 3 vse_new > vse_old: PPA (l/r)
+% 4 vse_new > vse_old, vpe_old: PPA (l/r)
+% 5 vse_new, vpe_new > vpe_old: PPA (l/r) but also visual c.
+% 6 vno_cut > vse_new: nothing
+% 7 vno_cut > vse_old: nothing
+% 8 vno_cut > vse_new, vse_old: nothing
+% 9 vno_cut > vpe_new, vpe_old: nothing
+%10 se_new > se_old: right PPA
+
+% why we did different contrasts
+We created a variety of contrasts to test if our approach yielded
+similar results across similar contrasts and if localization performance
+decreases the further the contrasts deviate from the spatial layout hypothesis
+\todo{and the less data we use}.
+
+% results
+The overlap of significant clusters of 8 contrast for the audio-description, and
+5 contrasts computed for the movie can be found in Figure
+\ref{fig:stability-slices}.
+
+% AO eight contrasts
+For the analysis of the AO stimulus, we combined different event categories to
+create eight contrasts that provided different amount of data/events and
+decreasing congruency with the spatial layout hypothesis.
+% results in PPA
+Six of eight AO contrasts show significant bilateral clusters in anterior
+regions of the group PPA overlap.\todo[inline]{which is temporal occipital
+fusiform gyrus regarding to co-registered Harvard-Oxford Cortical Structural
+Atlas}
+% Precuneus = retrosplenial cortex ?
+Six of eight contrasts show significant clusters in the ventral precuneus /
+retrosplenial cortex (RSC).
+% statement/answer
+This suggest results are reproducible in a variety of contrasts and do not
+depend on the design of one specific contrasts.
+% results get ``worse''
+Further, the ability to functionally isolate the PPA decreases the more a
+contrast depends on (just) using \texttt{se\_new} and \texttt{se\_old}
+\todo{interpretation (-> discussion): this category is essentially filled with
+    nouns from other cateogries but nevertheless primarily cueing a change of
+    setting; setting changes are often anticipated by a change of soundscape,
+meaning the narrator lagges behind; well, and the more a contrasts only relies
+on these, the less data is available, because just two categories the more the
+contrast depends on (just) using se\_new or se\_old}
+
+% AV intro
+For the analysis of the AV stimulus, we created five contrasts for a cross-modal
+comparison.
+% PPA
+All five AV contrasts yielded significant bilateral clusters in (temporal)
+occipital, fusiform cortex showing congruency with the group overlap of
+individual PPA ROIs.
+% lingual gyrus
+In three contrasts, these homologous clusters extend into the lingual gyri.
+% RSC
+Further, three contrasts show significant homologous clusters in the RSC.
+% LOC
+Lastly, four contrasts show significant homologous clusters in lateral occipital
+cortices.
+% statement/answer
+Here again, we can show that results can in principle be accomplished by varying
+the design of the contrasts.
+
+\begin{figure*} \centering
+    \includegraphics[width=\linewidth]{figures/stability-slices}
+    \caption{Stability of contrasts. Overlap of significant clusters (Z>3.4;
+        p<.05, cluster corrected) of contrasts created to isolate the PPA.
+        Contrasts provide decreasing congruency with the spatial layout
+        hypthesis and/or progressively less data/events. The overlap across
+        contrasts is overlaid on the MNI152 T1-weighted head template (gray).
+        Light gray: The audio-description's field-of-view (cf.
+        \citep{hanke2014audiomovie}). Blue: contrasts 1-7 for the
+        audio-description (see Table \ref{tab:ao-contrasts}. Red: contrasts 1-5
+        for the audio-visual movie (see Table \ref{tab:av-contrasts}. Black:
+        outline of overlapping individual PPA ROIs
+        \citep{sengupta2016extension}.} \label{fig:stability-slices}
+    \end{figure*}
+
+\subsection{crossmodal and negative controls}
+
+\todo[inline]{shall results of these contrasts be reported as well? imo: the one
+who says a) should say b), too. At the moment the contrasts are just listed in
+the method section}
+
+\todo[inline]{there are only two control contrasts that yield significant
+    clusters: in AO stimulus using annotation of movie cuts (vse\_new >
+    pe\_old): right RSC; and in the AV stimulus using annotation of the narrator
+    (se\_new > se\_old): right PPA; this kinda suggest particpants use the
+soundscape for re-orienting (which still might be a bold claim)}
+
 \section{Discussion}
-
-\todo[inline]{MIH: discussion should primarily be anchored on the points the
-    introduction concludes with. From my POV there is no need (and likely no
-    space) to discuss results by stimulus type. Issue like different impact of
-    attentional focus etc can be brought up in the joint paragraph that
-    discussed how such a factor could have differentially impacted the results
-    and if that would matter.}
 
@@
 
-% following paragraphs in the discussion section starts by describing an area of weakness or strength of the paper.
-% It then evaluates the strength or weakness by linking it to the
-% relevant literature.
-
-% Discussion paragraphs often conclude by describing a clever, informal way of perceiving the contribution or by discussing future directions that can extend the contribution.
-
-% For example, the first paragraph may summarize the results, focusing on their meaning.
-
-% The second through fourth paragraphs may deal with potential weaknesses and with how the literature alleviates concerns or how future experiments can deal with these weaknesses.
+% following paragraphs in the discussion section starts by describing an area of
+% weakness or strength of the paper.  It then evaluates the strength or weakness
+% by linking it to the relevant literature.
+
+% Discussion paragraphs often conclude by describing a clever, informal way of
+% perceiving the contribution or by discussing future directions that can extend
+% the contribution.
+
+% For example, the first paragraph may summarize the results, focusing on their
+% meaning.
+
+% The second through fourth paragraphs may deal with potential weaknesses and
+% with how the literature alleviates concerns or how future experiments can deal
+% with these weaknesses.
 
@@
 
-%Step by step, the reader thus learns to put the paper’s conclusions into the right context.
+%Step by step, the reader thus learns to put the paper’s conclusions into the
+%right context.
+
+\todo[inline]{taylor it to points mentioned in the introduction (full circle)}
+
+\paragrap{intro}
 We used two naturalistic stimuli + annotation + GLM and investigated if we could
@@
 % individual differences
-Individual differences when seeing a whole picture with many features vs. stream
-of serial auditory information providing incidential cues; spatial attention?
-\todo[inlin]{which contrast works better in which subjects?}
+Individual differences when seeing a whole picture with many features vs.
+serialc auditory stream of information providing incidential cues; spatial attention?
+\todo[inline]{which contrast works better in which subjects?}
 
@@
 
-\subsection{shortcommings}
+\subsection{shortcomings}
 

### 2020-08-05 paper/main.tex
some more structure for discussion

@@
 
-\todo[inline]{taylor it to points mentioned in the introduction (full circle)}
-
-\paragrap{intro}
-We used two naturalistic stimuli + annotation + GLM and investigated if we could
-isolate the PPA not just in an group average analysis but also on an individual
-level. We focus on the audio-only stimulus but performed a analysis for the AV
-stimulus as well (not controlling for frame content after cuts).
-
-% Correlation of regressors
-Events/Regressors are of little to no correlation despite stimulus was used as
-designed for entertainment purposes.
-
-\subsection{Group analysis}
-
-% AO stimulus
-% cluster location
-AO stimulus isolated spatially concise cluster in anterior part of group overlap mask/roi.
-% confounds
-2h audio-description offering sufficient events such that many confounding
-variables average out (but some anternative contrasts show clusters in auditory
-cortices)
-% summary statement
-This suggest spoken language cues correlate with increased activation in higher
-visual areas bilaterally.
-
-% RSC
-words to clusters in RSC? -> see Aminoff (20xx). What does the retrosplenial
-cortex do?
-
-% theory what the PPA does
-\todo[inline]{aminoff2013: jedoch zu non-spatial stuff: Although the PHC is
-commonly thought of as responding to visual stimuli, it has also been found to
-elicit activity for auditory stimuli [25,26,30,31] and to respond to odor
-stimuli [32–34].}
-% Mental Imagery Hypothesis
-Mental Imagery Hypthesis (s. O'Craven \& Kanwisher, 2000); Lerner (2011), Honey
-(2012), Silbert (2014) finden keine ISC in PPA? vgl. auch DataPaper bzgl.
-Hörbuch??
-% we
-We got not task not time to form a vivid mental image; if at all automatic
-on-the-fly process; further not task to keep subjects attentive to the stimulus
-and espcially spatial cues
-% PPA is not visual exclusively
-results of other studies suggest7 the PPA does not exclusively process the
-``spatial layout''" but ``contextual associations''.
-% difference to Aziz
-Aziz modeled as boxcar from sentence onset to offset.
-
-% AV stimulus cluster location
-AV middle and posterior part of group overlap mask/roi.
-% confounds
-extending into more posterior regions (which exactly?).
-% not controlled frame content
-putativ function of those regions?
-% number of events?
-confounds to not average out in (early) visual areas.
-% nevertheless
-imo it's cool, that this approach of blindly averaging the frames' content works
-at all.
+\todo[inline]{tailor it to points mentioned in the introduction (full circle);
+print intro to avoid constant scrolling}
+
+\subsection{intro}
+\todo[inline]{summary of study goal and methods}
+% what we did
+We used two naturalistic stimuli and their annotations to create a GLM
+presumably correlating with hemodynamic activity in the PPA. We focused on the
+AO stimulus but also build contrasts for the AV stimulus for cross-modal
+control.
+
+\subsubsection{correlation of regressors} Both stimuli were not designed to
+maximize detection power in an fMRI experiment bu to entertain the audience.
+% why we created the correlation matrix in the first place
+We tested for correlation of stimulus features because a high degree of shared
+variance prevents detection power.
+% summary of results
+Results show only minor to no correlations of regressors across all stimulus
+segments
+% statement
+Hence depending on the stimulus features of interest, it is feasible to use
+specific stimulus features of a regular movie or audiobook for neuroscientific
+research questions.
+
+\subsection{group analysis}
+
+\subsubsection{AO stimulus}
+% AO stimulus cluster location
+The results of the AO stimulus yielded isolated clusters in the anterior part of
+the PPA ROI (overlap of individual PPAs taken from Sengupta et al.).
+% comparison to other studies using ISC
+\todo[inline]{check Wilson (2008), Lerner (2011), Honey (2012), Silbert (2014).
+Do they find ISC in PPA using an auditory stimulus? As far as I remember they
+don't}
+% diff to Aziz (2008)
+Unlike \citep{aziz2008modulation} we did not use whole sentences as events to
+model a hemodynamic response but the length of the word giving the cue about the
+visual content of a scene.
+% no task
+Compared to previous studies (O'Craven \& Kanwisher: mental imagery
+hypothesis)\todo{check this paper out} participants of our study were not
+instructed to form a vivid mental image of the stimulus but to ``enjoy the
+audiobook''.
+% naive to the research question
+Moreover, participants could not infer the perceptual process to be investigated
+by merely being submitted to the stimuli / experimental design.
+% concluding statement
+This suggest the PPA is involved in processing incidental spatial information
+embedded in a rich auditory stream, and this involvement does not rely on
+creating a mental imagery or deliberately paying close attention to spatial
+features.\todo{kinda similar to Wolbers (2011) who checked connectivity between
+    PPA and visual cortex during haptic exploration of LEGO scenes}
+
+% other
+\todo[inline]{Aminoff (2013). PPA's role in cognition regarding non-spatial
+    stuff: ``Although the PHC is commonly thought of as responding to visual
+    stimuli, it has also been found to elicit activity for auditory stimuli
+    [25,26,30,31] and to respond to odor stimuli [32–34]''.}
+% concluding statement
+In summary, our group results suggest that auditory spatial information does not
+just modulate activity in the PPA (depending on other factory like familiarity,
+XY; s. Aziz) but correlates with bilaterally increased
+activation.\todo{``modulate'' suggests causation}
+
+\subsubsection{AV stimulus}
+
+% location
+AV anterior, middle and posterior part of group overlap mask/roi.
+
+% difference in location/size to AO und VIS
+extending into more posterior regions; which exactly; known functions of theses
+areas
+% shortcomings + explanation
+shortcoming of not controlling visual content of the frames after the cut;
+% but
+nevertheless it's ``surprising'' that it works at all and the clusters located
+in systematically / bilaterally in (higher) visual areas; lot's of (non) visual
+features average out; and we are not using a dedicated stimulus
+% what should be done to improve
+make an annotation of frame's content
+
+\subsubsection{open question anterior vs. posterior PPA???}
+
+\subsubsection{Retrosplenial cortex}
+\todo[inline]{check location in primary contrast and in overlap of contrasts;
+atlases do not ``know'' RSC as such but provide other term(s)}
+\todo[inline]{cf. Aminoff (20xx). What does the retrosplenial cortex do?}
+Another region that showed significantly increased activity not just in the
+primary contrast but consistently across contrasts is ventral precuneus / RSC
+(check the overlap again to not talk shit; no atlas gives RSC as such)\dots
+
+\subsection{individual analyses}
+
+\subsubsection{AO stimulus}
+% intro
+Contrast 1 yielded isolated cluster in the anterior part of individual PPA masks
+in majority of subjects.
+% one threshold for all
+Contrary to Sengupta et al. (2016) results were archieved by using the same
+Z-value and significance threshold for all subjects, and not by visually
+expecting the results and choosing a subjectively best fitting threshold for
+each subject.
+\todo[inline]{what about the info in Bland-Altman-Plots; discussion of that info
+could range from 2 sentences to 2 paragraphs}
+% inter-individual differences
+\todo[inline]{which contrasts work better in some subjects?}
+% AO stimulus vs. AV stimulus
+\todo[inline]{Hanke et al. (2014): Compared to an audio-visual movie, this is a
+    stimulus that leaves a much larger margin for inter-individual differences
+    in imagining scenery, as well as actors' character and personality traits,
+    while still preserving the time-locked presentation of information to a
+    listener. At the same time, an auditory stimulus limits the effect of an
+    attentional focus on the selection of a subset of simultaneously occurring
+    auditory events, in contrast to the selection of different parts of the
+visual field}.
+% sub-xy
+AO yielded bilateral cluster whereas AV stimulus yielded XY and even the
+dedicated localizer yieled just one unilateral custer.\todo{what to do with
+that?}
+% summary statement group results a representative for group
+The individual results suggest that the group results are not driven by a couple
+of subjects.
+% auditory localizer
+Moreover, a complex but naturally engaging auditory stimulus like an audiobook
+might in principle be used as a non-visual localizer for a variety of brain
+functions in subjects who are not willing or able to follow task instructions
+during brain scanning.
+% PPA just an example
+The feature ``auditory spatial information'' is just one
+example of a stimulus feature that can be annotated and used to build a model.
+
+\subsubsection{AV stimulus}
+On individual level, mixed results for AV stimulus.
+\todo[inline]{which contrast works better in which subjects?}
+Individual differences when seeing a whole picture with many features vs.
+serialc auditory stream of information providing incidential cues; spatial attention?
+
+\paragraph{shortcomings of AV contrasts}
+visual confounds all over the place; obvious solution: annotate frames and track
+focus of attention (but gist of a frame vs. attentional focus)
 
@@
 
-\subsection{individual analyses}
-% AO
-We were able to get isolated cluster in anterior part of individual PPA masks in
-majority of subjects.
-% one threshold for all
-Same threshold for all subjects, PPA ROIs were visually / subjectively chosen.
-% inter-individual differences
-\todo[inline]{which contrasts work better in some subjects?}
-% sub-xy
-AO yielded bilateral cluster whereas AV stimulus yielded XY and even the
-dedicated localizer yieled just one unilateral custer.
-
-% summary statement
-Results suggest naturalistic AO stimulus can be used as an non-visual localizer
-of a visual area in individual subjects.
-% with other words
-a  complex auditory stimulus might allow individual localization of a
-functionally defined brain region.
-% and again other words
-an audio drama might be suitable as ecologically more valid ``localizer'' for a
-variety of brain functions.
-% other example: speech areale
-other possibilities: low level features, stuff annotated in speech annotation
-
-% multiple localizer
-% PPA is just one example
-2h stimulus for just one process is long but chosen cognitive function is just
-one aspect that can be investigated with a complex naturalistic stimulus.
-
-% AV
-On individual level, mixed results for AV stimulus.
-% individual differences
-Individual differences when seeing a whole picture with many features vs.
-serialc auditory stream of information providing incidential cues; spatial attention?
-\todo[inline]{which contrast works better in which subjects?}
-
-% AO vs. AV
-AO vs. AV\dots
-\todo[inline]{Hanke et al. (2014): Compared to an audio-visual movie, this is a
-    stimulus that leaves a much larger margin for inter-individual differences
-    in imagining scenery, as well as actors' character and personality traits,
-    while still preserving the time-locked presentation of information to a
-    listener. At the same time, an auditory stimulus limits the effect of an
-    attentional focus on the selection of a subset of simultaneously occurring
-    auditory events, in contrast to the selection of different parts of the
-visual field}.
-
-\subsection{shortcomings}
-
-% spatial cues can belong to different categories
+% spatial cues can belong to different indcategories
+resembling cuts to different scene in the movie by using ``similar'' cues in the
+audio-description did not work well; words are processes ``literally'' and not
+``wholistically'' or put in a wider ``context'' (but Aminoff?)
+%
 setting\_new ist häufig vermischt mit anderer Kategorie "ein Arzt", "ein alter
@@
 
-\subsection{open question: anterior (AO) vs. posterior (AV) PPA}
-
-\subsection{model-driven vs. data-driven analyses} Due to their continuity,
+\subsection{re-use of existing data for new, independent research questions}
+Due to their continuity,
 complexity, and length, they offer a vast amount of data on a variety of brain
@@
 
-\subsection{confounds in AO and AV}
-
-\subsection{re-use of existing data for new, independent research questions}
-there is more in a complex naturalistic stimulus.
-
+\subsection{model-driven vs. data-driven analyses}
 Natural stimuli like movies \citep{hasson2008neurocinematics,
@@
 \subsection*{Code availability}
-% wo kommt dieser Abschnitt hin?
-% how to write Code availability statement
+% wo kommt dieser Abschnitt hin?  how to write Code availability statement
 % https://www.springernature.com/gp/authors/research-data-policy/data-availability-statements/12330880
-\todo[inline]{provide supporting source code, and explaining how and where others may access all data underlying the analysis}
-\emph{for all studies using custom code in the generation or processing of datasets,
-a statement must be included here, indicating whether and how the code can be
-accessed, including any restrictions to access; include information on the versions
-of any software used, if relevant, and any specific variables or parameters used to
+\todo[inline]{provide supporting source code, and explaining how and where
+others may access all data underlying the analysis} \emph{for all studies using
+    custom code in the generation or processing of datasets, a statement must be
+    included here, indicating whether and how the code can be accessed,
+including any restrictions to access; include information on the versions of any
+software used, if relevant, and any specific variables or parameters used to
 generate, test, or process the current dataset. }

### 2020-08-11 paper/main.tex
revise structure of introduction

@@
 
+\todo[inline]{RSC is not mentioned in the introduction but should (probably)
+shortly discussed in the, well discussion; RSC shows up in group results but
+mixed results in individual subjects}
+
 % brain mapping via fMRI
@@
 functional brain areas or networks.
-% simplified stimuli
-Brain mapping studies have traditionally employed small sets of carefully
-chosen, simplified stimuli to strictly control experimental conditions.
-% disadvantage 1: validity
-Their disadvantage is that a limited number of simplified stimuli does not
-resemble our real-life experience and thus lack external validity
-\citep{westfall2016fixing} as well as ecological validity
-\citep{hasson2004intersubject}.
-% disadvantage 2: averaging for group results
-Additionally, brain mapping studies usually average results across at least
-10-15 subjects to improve the signal-to-noise-ratio (SNR). The disadvantage here
-is that the averaging approach does not characterize brain functions at an
-individual level, a prerequisite for the application of brain imaging methods in
-individual diagnostics (cf. \citep{dubois2016building, eickhoff2020towards}).
-
-\todo[inline]{RSC is not mentioned in the introduction but should (probably)
-shortly discussed in the, well discussion; RSC shows up in group results but
-mixed results in individual subjects}
-
 % What is the PPA?
-A classic example of a functional, higher-level visual area is the
+A classic example of a functionally defined, higher-level visual area is the
 ``parahippocampal place area'' (PPA) \citep{epstein1998ppa,
 epstein1999parahippocampal}.
-% anatomical location
-The PPA is located in the posterior parahippocampal gyrus at the boundary to the
-anterior lingual gyrus and medial fusiform gyrus, both being part of the ventral
-visual stream \citep{mishkin1982contribution, goodale1992separate}.
+% anatomical location != functional location
+The PPA is located in the posterior parahippocampal gyrus including adjacant
+regions of the fusiform gyrus \cite{epstein1998ppa} at the boundary to the anterior lingual gyrus \citep{epstein2008parahippocampal}.
 % neural correlate of scene perception
@@
 % spatial layout hypothesis
-According to the spatial layout hypothesis, the PPA is involved in
-processing the surface geometry of a visual stimulus and possibly in identifying
-scenes based on their spatial layout \citep{epstein2010reliable}.
-
+According to the spatial layout hypothesis, the PPA is involved in processing
+the surface geometry of a visual stimulus and possibly in identifying scenes
+based on their spatial layout \citep{epstein2010reliable}.
 % literature review overview 1: imagination & haptic exploration
@@
 bricks compared to haptically explored abstract geometric objects.
-
+% connectivity analysis by Wolbers
 \todo[inline]{Er hat noch eine Connectivitäts-Analyse mit dem Occipital Cortex
@@
 stimulation (Figure 2B; Table S2)''}
-
 % Aziz (2008): place related sentences
-\todo[inline]{Aziz hat auf eine zweite Mail geantwortet: Sie modelt die HRF über
-den jeweils gesamten Satz von ca. 2.8 Sekunden}
-
 \todo[inline]{lass uns kurz im Gespräch über Aziz Paper gucken; die relvanten
@@
     durch, weshalb folgendes nicht vollständig korrekt sein wird;so wie ich es
-    verstanden habe, hat sie den Unterschied zwischen PPA und FFA angeguckt,
-aber diesen Unterschied im Kontrast zu object-related Sentences (dortige Fig 3;
-)}
-
+verstanden habe, hat sie den Unterschied zwischen PPA und FFA angeguckt, aber
+diesen Unterschied im Kontrast zu object-related Sentences (dortige Fig 3)}
 % Aziz' stimuli
-To our knowledge only one study by \citep{aziz2008modulation} correlated
+To our knowledge only one study \citep{aziz2008modulation} correlated
 hemodynamic activity of the PPA with spoken sentences. Sentences described
@@
 % summary if literature review
-In summary, studies suggest that the PPA does not exclusively respond to
-visually presented spatial information. Nevertheless, the question how the
-PPA responds to auditory stimuli is still open.
-
-\todo[inline]{but Huth et al. (2016) implicitly; but they do not discuss the
-PPA; moreover, they do voxel-wise encoding which doesn't say anything about
-excitation/inhibition}
-
+In summary, studies suggest that the PPA does preferably but not exclusively
+respond to visually presented spatial information.
 % shortcomings of previous studies: simplified stimuli
-All reviewed studies used a small set of carefully designed, simplified stimuli
-to strictly control experimental conditions.
+Nevertheless, all reviewed studies have in common that they employed a small set
+of simplified stimuli to strictly control experimental conditions.
 % shortcomings of previous studies: task-based paradigm
-They further relied on explicit judgment-based tasks to ensure that participants
-payed attention to the stimuli.
-% second question: life-like conditions
-This raises the second question which is how the PPA behaves under life-like
-conditions.
+Further, they usually relied on explicit judgment-based tasks to ensure that
+participants payed attention to the stimuli.
+% disadvantage 1b: lack of validity
+Paradigms using block designs accompanied with a task have the disadvantage that
+they do not resemble our real-life experience and thus lack external validity
+\citep{westfall2016fixing} as well as ecological validity
+\citep{hasson2004intersubject}.
+% disadvantage 2a: averaging for group results
+Additionally, the reviewed studies averaged results across 7-11 subjects to
+improve the signal-to-noise-ratio (SNR).
+% disadvatage 2b: no individual level
+The disadvantage here is that the averaging approach does not characterize brain
+functions at an individual level, a prerequisite for the application of brain
+imaging methods in individual diagnostics (cf. \citep{dubois2016building,
+eickhoff2020towards}).
+% open questions
+This raises the question how the PPA behaves under life-like conditions, and how
+group results a driven by individuals subjects especially in response to
+audio-only stimulation\todo{``audio-only'' sounds meh}.
+% Huth (2016)
+\todo[inline]{but Huth et al. (2016) implicitly regarding audio-only; but they
+do not discuss the PPA; moreover, they do voxel-wise encoding which doesn't say
+anything about excitation/inhibition}
+
 % naturalistic stimuli
-Naturalistic stimuli like movies \citep{hasson2008neurocinematics,
-sonkusare2019naturalistic} or narratives \citep{honey2012not,
-lerner2011topographic, silbert2014coupled} offer complex, continuous stimuli
-that better resemble our experience of a our dynamic environment.
-
+Paradigms using naturalistic stimuli like movies
+\citep{hasson2008neurocinematics, sonkusare2019naturalistic} or narratives
+\citep{honey2012not, lerner2011topographic, silbert2014coupled} offer complex,
+continuous stimulation that better resemble our experience of a our dynamic
+environment.
 % naturalistic stimuli review: intro
@@
 of brain areas is preserved during movie watching when many perceptual and
-cognitive processes are triggered simultaneously \citep{bartels2004mapping, hasson2004intersubject}.
+cognitive processes are triggered simultaneously \citep{bartels2004mapping,
+hasson2004intersubject}.
 % Bartels (2004): Film + GLM (but surprisingly did not annotate landscapes)
@@
 % Hasson: method
-fMRI brain volumes showing the highest hemodynamic activity
-in the PPA [across (five) participants] were matched to the temporally
-corresponding movie frames.
+fMRI brain volumes showing the highest hemodynamic activity in the PPA [across
+(five) participants] were matched to the temporally corresponding movie frames.
 % Hasson: results
-Results revealed that corresponding movie frames
-depicted indoor and outdoor scenes including buildings and open fields.
-
+Results revealed that corresponding movie frames depicted indoor and outdoor
+scenes including buildings and open fields.
 % summary naturalistic stimuli
-Nevertheless, both studies used an audio-visual stimulus and thus do not address
-the question how the PPA responds to spatial clues that are embedded in a
-complex, audio-only stimulus.
-
-\todo[inline]{mih: Possibly cite https://psyarxiv.com/sdbqv/ (DuPre (2019).
-Nature abhors a paywall) and declare that this study is a concrete realization
-of that promise}
+Nevertheless, both studies used an audio-visual stimulus and again do not
+address the question how the investigated functional areas respond an audio-only
+stimulus.
+
+\todo[inline]{mih: Possibly cite DuPre (2019) and declare that this study is a
+    concrete realization; COH: I read it but don't know what/how to cite it for
+    any other reason than just to cite it (here or in discussion)}
 
 % what we did: data source
-In this study, we analyze functional data of the same 14 participants being part
-of the studyforrest dataset
-(\href{http://www.studyforrest.org}{studyforrest.org};
-\citep{hanke2014audiomovie, hanke2016simultaneous}).
+In the current study, we analyze publicly available functional data
+(studyforrest.org) of the same 14 participants watching a movie
+\citep{hanke2016simultaneous} and listening to an audiobook.
+\citep{hanke2014audiomovie}.
 % PPA + movie + audio-description
@@
 the movie's audio-only variant; \citep{ForrestGumpGermanAD}) to exploratorily
-investigate how the parahippocampal gyrus behaves during movie watching and
-listening to an ``audiobook''.
+investigate how the parahippocampal gyrus behaves during more life-like
+conditions free from any task.
 % focus on audio-description
-Encouraged by \citep{aziz2008modulation}, we also employ a traditional GLM, and
-focus on the audio-description as a naturalistic, auditory-only paradigm free
-from any task to localize a ``visual area'' in individual study participants.
+Encouraged by \citep{aziz2008modulation}, we focus on the audio-description as
+an audio-only paradigm and test its localization performance of a ``visual
+area'' in individual study participants.
 % comparison to dedicated localizer
-We also compare our results to results of a dedicated visual localizer
+Finally, we compare these results to results of a dedicated visual localizer
 experiment done with the same participants \citep{sengupta2016extension}.
@@
 We used data from three publicly available datasets
-(\href{http://www.studyforrest.org}{studyforrest.org}) which have already been
+(\href{http://www.studyforrest.org}{studyforrest.org}) that have already been
 used by other research groups for independent research questions.
 % used studies
-\todo{this is just loveless listing so far but it's 'complete'} The same
-subjects were
+\todo{this is just loveless listing so far} The same subjects were
 % AO
@@
 % AV: voice-over
-The plot of the movie is already carried by an voice-over of the main character
+The plot of the movie is already carried by a voice-over of the main character
 Forrest Gump.
@@
 % VIS study picture categories
-All stimuli for the VIS study were already used in a previous study
+All stimuli of the VIS study were already used in a previous study
 \citep{haxby2011common}. There were 24 unique grayscale images (matched in
 luminance, size of 400 $\times$\unit[400]{px}) for each of six stimulus
-categories: human faces, human bodies without heads, small objects, houses and
+categories: faces, bodies without heads, small objects, houses and
 outdoor scenes comprising of nature and street scenes, and phase scrambled
@@
 geo & immobile landmarks & \aoGeoAll & \aoGeoI & \aoGeoII & \aoGeoIII & \aoGeoIV & \aoGeoV & \aoGeoVI & \aoGeoVII & \aoGeoVIII \tabularnewline
-groom & elements defining a locale's spatial layout & \aoGroomAll & \aoGroomI & \aoGroomII & \aoGroomIII & \aoGroomIV & \aoGroomV & \aoGroomVI & \aoGroomVII & \aoGroomVIII \tabularnewline
+groom & elements defining geometry of local space & \aoGroomAll & \aoGroomI & \aoGroomII & \aoGroomIII & \aoGroomIV & \aoGroomV & \aoGroomVI & \aoGroomVII & \aoGroomVIII \tabularnewline
 object & inanimate entities with firm boundaries & \aoObjAll & \aoObjI & \aoObjII & \aoObjIII & \aoObjIV & \aoObjV & \aoObjVI & \aoObjVII & \aoObjVIII \tabularnewline
@@
 count as object or a geometry-defining structure of a room/locale.
+\todo[inline]{Epstein (2008): response to arrays of objects drawn from the rooms
+    but displayed on a blank background is quite weak [11]}
 % negative control contrasts
@@
 moments of cuts and therefore correlated with a possibly accompanying change in
-the soundscape (anticipating the narrator's cue of a switch to new setting, too).
+the soundscape (anticipating the narrator's cue of a switch to new setting,
+too).
 
@@
 % liberally)
-% sub-01: PPA (l/r), AO (l/r), AV (-/r); RSC: AO (l/r), AV (-/-)
-% sub-02: PPA (l/r), AO (-/-), AV (-/r); RSC: AO (-/-), AV (-/-)
-% sub-03: PPA (l/r), AO (-/-), AV (-/r); RSC: AO (-/-), AV (-/-)
-% sub-04: PPA (-/r), AO (l/r), AV (-/r); RSC: AO (l/r), AV (-/-) !
-% sub-05: PPA (l/r), AO (-/-), AV (-/-); RSC: AO (-/-), AV (-/-)
-% sub-06: PPA (l/r), AO (l/r), AV (-/-); RSC: AO (l/-), AV (-/-)
-% sub-09: PPA (l/r), AO (l/-), AV (l/r); RSC: AO (l/r), AV (l/r)
-% sub-14: PPA (l/r), AO (l/r), AV (-/r); RSC: AO (l/r), AV (-/-)
-% sub-15: PPA (l/r), AO (l/r), AV (-/r); RSC: AO (l/r), AV (l/r)
-% sub-16: PPA (l/r), AO (l/r), AV (l/r); RSC: AO (l/r), AV (l/-)
-% sub-17: PPA (l/r), AO (l/r), AV (l/r); RSC: AO (l/r), AV (l/r)
-% sub-18: PPA (l/r), AO (l/r), AV (l/r); RSC: AO (l/r), AV (-/r)
-% sub-19: PPA (l/r), AO (l/r), AV (-/r); RSC: AO (l/r), AV (l/r)
-% sub-20: PPA (-/r), AO (-/-), AV (l/r); RSC: AO (-/-), AV (-/-)
+% sub-01 (m): PPA (l/r), AO (l/r), AV (-/r); RSC: AO (l/r), AV (-/-)
+% sub-02 (m): PPA (l/r), AO (-/-), AV (-/r); RSC: AO (-/-), AV (-/-)
+% sub-03 (f): PPA (l/r), AO (-/-), AV (-/r); RSC: AO (-/-), AV (-/-)
+% sub-04 (f): PPA (-/r), AO (l/r), AV (-/r); RSC: AO (l/r), AV (-/-) !
+% sub-05 (m): PPA (l/r), AO (-/-), AV (-/-); RSC: AO (-/-), AV (-/-)
+% sub-06 (m): PPA (l/r), AO (l/r), AV (-/-); RSC: AO (l/-), AV (-/-)
+% sub-09 (m): PPA (l/r), AO (l/-), AV (l/r); RSC: AO (l/r), AV (l/r)
+% sub-14 (f): PPA (l/r), AO (l/r), AV (-/r); RSC: AO (l/r), AV (-/-)
+% sub-15 (m): PPA (l/r), AO (l/r), AV (-/r); RSC: AO (l/r), AV (l/r)
+% sub-16 (m): PPA (l/r), AO (l/r), AV (l/r); RSC: AO (l/r), AV (l/-)
+% sub-17 (m): PPA (l/r), AO (l/r), AV (l/r); RSC: AO (l/r), AV (l/r)
+% sub-18 (m): PPA (l/r), AO (l/r), AV (l/r); RSC: AO (l/r), AV (-/r)
+% sub-19 (f): PPA (l/r), AO (l/r), AV (-/r); RSC: AO (l/r), AV (l/r)
+% sub-20 (f): PPA (-/r), AO (-/-), AV (l/r); RSC: AO (-/-), AV (-/-)
 
@@
 % subjective threshold
-Noteworthy, ROIs were assessed by \citep{sengupta2016extension} by visually
-inspecting the unthresholded $z$-maps, and setting a subjectively best fitting
+Individual ROIs were assessed by \citep{sengupta2016extension} by visually
+inspecting unthresholded $z$-maps, and setting a subjectively best fitting
 $z$-threshold to isolate a cluster in the PPA.
@@
 In the current analysis of the AO stimulus, we find significant bilateral
-clusters in nine subjects, and one significant cluster in the left hemisphere of sub-09.
+clusters in nine subjects, and one significant cluster in the left hemisphere of
+sub-09.
 % subj-04
@@
 
-\todo[inline]{tailor it to points mentioned in the introduction (full circle);
-print intro to avoid constant scrolling}
-
 \subsection{intro}
-\todo[inline]{summary of study goal and methods}
+\todo[inline]{goal and what we did should probably in result section}
+% study goal
+The goal of this study was to investigate if increased hemodynamic activity in
+the PPA correlates with spatial information presented under more ecological
+valid conditions.\todo{cautious phrasing but still problematic: looking for
+confirmation}
 % what we did
-We used two naturalistic stimuli and their annotations to create a GLM
-presumably correlating with hemodynamic activity in the PPA. We focused on the
-AO stimulus but also build contrasts for the AV stimulus for cross-modal
-control.
-
-\subsubsection{correlation of regressors} Both stimuli were not designed to
-maximize detection power in an fMRI experiment bu to entertain the audience.
+We used annotations of a \unit[2]{h} movie and it's temporally aligned
+audio-description to create GLMs of hemodynamic activity resembling analyses
+of previous studies using simplified stimuli.
+
+\todo[inline]{summary of results like ``Our results demonstrate that\dots''}
+
+\subsubsection{correlation of regressors}
+% stimuli not designed for research purposes
+Both stimuli were not designed to for research purposes detection power in a
+fMRI experiment) but to entertain their audiences.
 % why we created the correlation matrix in the first place
-We tested for correlation of stimulus features because a high degree of shared
-variance prevents detection power.
+We first tested for correlation of stimulus features because a high degree of
+shared variance lowers detection power.
 % summary of results
 Results show only minor to no correlations of regressors across all stimulus
-segments
+segments.
 % statement
-Hence depending on the stimulus features of interest, it is feasible to use
-specific stimulus features of a regular movie or audiobook for neuroscientific
-research questions.
+Hence depending on the stimulus features of interest, it was feasible to use the
+annotated stimulus features for our research question.
 
@@
 % no task
-Compared to previous studies (O'Craven \& Kanwisher: mental imagery
-hypothesis)\todo{check this paper out} participants of our study were not
+Compared to \citep{ocraven2000mental} participants of our study were not
 instructed to form a vivid mental image of the stimulus but to ``enjoy the
-audiobook''.
+audiobook''. This procedure resembles experiencing the world around us in
+real-life more closely
 % naive to the research question
 Moreover, participants could not infer the perceptual process to be investigated
-by merely being submitted to the stimuli / experimental design.
-% concluding statement
-This suggest the PPA is involved in processing incidental spatial information
-embedded in a rich auditory stream, and this involvement does not rely on
-creating a mental imagery or deliberately paying close attention to spatial
-features.\todo{kinda similar to Wolbers (2011) who checked connectivity between
-    PPA and visual cortex during haptic exploration of LEGO scenes}
-
-% other
+by merely being exposed to the stimuli / experimental design. This suggests
+spatial information is processed in the PPA despite a lack of visual
+attention.\todo{bold claim here}
+% comparison to Wolbers
+Similarly to \citep{wolbers2011modality} who found increased activation in the
+PPA when blind study participants haptically explored scenes made out of LEGO
+blocks compared to other objects, our results support the hypthesis that
+increased activation in the PPA does not necessarily rely on creating a vivid
+mental image.
+% (visual or auditory) spatial attention
+Results further suggest activation does also not rely on deliberately paying
+auditory attention to spatial information embedded in a complex/rich auditory
+stimulus.\todo{kinda bold statement}
+% others
 \todo[inline]{Aminoff (2013). PPA's role in cognition regarding non-spatial
@@
 
+% RSC
+Epstein (2008): Neuroimaging studies of human navigation most com- monly
+activate the posterior parahippocampal and retro- splenial cortices [4–10],
+regions that also respond strongly during passive viewing of navigationally
+relevant visual stimuli such as scenes and buildings [11–14]. Consistent with
+these findings, damage to these areas often leads to wayfinding deficits [15].
+These results indicate that para- hippocampal and retrosplenial cortices are key
+nodes of the neuronal network that support spatial navigation in humans. But
+what are the specific functions of each of these nodes?
+% location
+A second focus of cortical activity during navigation tasks is found in the
+retrosplenial cortex-posterior cingulate- medial parietal region, near to the
+point where the calcarine sulcus joins the parietal-occipital sulcus.
+Retrosplenial cortex (BA 29 and 30) adjoins and is partially encircled by the
+posterior cingulate (BA 23 and 31) [51–56]; consequently, these labels are often
+used somewhat inter- changeably when describing the locations of functional
+activations. Because of these ambiguities, I use the term retrosplenial complex
+(RSC) to refer to this functional- defined scene-responsive region, which is not
+necessarily identical to the anatomically defined retrosplenial cortex [26].
+% function
+RSC is strongly active during scene viewing, scene imagery [25] and mental
+imagination of navigation through familiar environments [8]. In contrast to the
+PPA, in which place familiarity effects are usually quite small, RSC responds
+50% more strongly to familiar than to unfamiliar places [23,57], indicating that
+RSC is involved in recovery of long-term spatial knowledge about familiar
+environments. Further evidence for this idea comes from recent studies reporting
+that RSC activity was signifi- cantly greater when subjects reported the
+location of a campus scene than when they simply reported whether it was
+familiar or not [24] (Figure 3a) and that RSC activity during learning of a
+virtual-reality town corresponded to the total amount of survey knowledge
+acquired [58] (Figure 3b; see also Ref. [59] for similar results in mice).
+% summary
+The PPA and RSC seem to have distinct but complemen- tary roles during spatial
+navigation. The PPA encodes a representation of the local scene that enables it
+to be remembered and subsequently recognized, whereas RSC supports mechanisms
+that enable one to orient oneself within the broader spatial environment and to
+direct one’s movement towards navigational targets that are not cur- rently
+visible
+
+\paragraph{shortcomings of AO contrasts}
+% less ``scenes'' as such but more isolated ``landmarks
+
+%  se_new & se_old is often belongs to another (``hierarchical'' lower)
+%  category; interesting who PPA responds to words describing a scene as a whole
+%  (the gist) vs. landsmarks a scenes consists of
+
 \subsubsection{AV stimulus}
@@
 % location
-AV anterior, middle and posterior part of group overlap mask/roi.
-
-% difference in location/size to AO und VIS
-extending into more posterior regions; which exactly; known functions of theses
-areas
+Clusters of the analysis of the AV stimulus span the anterior, middle and
+posterior part of group overlap mask/roi.
+% difference in location/size to AO and VIS
+Compared to cluster of the AO stimulus, they further extend into more posterior
+regions.\todo[inline]{which exactly? check fsleyes again; known functions of
+these areas -> should be explainable by confounds in movie frames}
 % shortcomings + explanation
@@
 
+% Epstein (2008)
+In particular, anterior PHC might do more than just scene recognition; it might
+also have a more general role in spatial memory encoding [94].
+
 \subsubsection{Retrosplenial cortex}
@@
 
+\todo[inline]{here, A LOT could be discussed; possibilities: individual
+    ``preference'' to pay attention to spatial infos (which contradicts
+    statement above that attention is not a prerequisite; different level of
+    alterness during paradigms; different ``capability'' to process auditory
+spatial information (maybe correlating in behavior differences in navigational
+tas in navigational tasks}
+
 \subsubsection{AO stimulus}
@@
 Contrast 1 yielded isolated cluster in the anterior part of individual PPA masks
-in majority of subjects.
+in the majority of subjects.
 % one threshold for all
-Contrary to Sengupta et al. (2016) results were archieved by using the same
-Z-value and significance threshold for all subjects, and not by visually
-expecting the results and choosing a subjectively best fitting threshold for
-each subject.
+Contrary to Sengupta et al. (2016), results were not archieved by visually
+expecting unthresholded $z$-maps and choosing a subjectively best fitting
+threshold for each subjectiwere archieved but by using the same $Z$-value and
+significance threshold for all subjects.
+
 \todo[inline]{what about the info in Bland-Altman-Plots; discussion of that info
-could range from 2 sentences to 2 paragraphs}
+could range from 2 sentences to 2 paragraphs?}
+
 % inter-individual differences
-\todo[inline]{which contrasts work better in some subjects?}
-% AO stimulus vs. AV stimulus
+\todo[inline]{could also be discussed: in 1-3 subjects a different contrasts
+work ``better''.}
+% sub-04
+In sub-04, the VIS yielded one right-sided PPA, the AV stimulus yielded one
+right-sided significant cluster whereas the AO stimulus yielded two homologous
+clusters in the PPA.\todo{what to do with that?}
+% note
 \todo[inline]{Hanke et al. (2014): Compared to an audio-visual movie, this is a
@@
 visual field}.
-% sub-xy
-AO yielded bilateral cluster whereas AV stimulus yielded XY and even the
-dedicated localizer yieled just one unilateral custer.\todo{what to do with
-that?}
 % summary statement group results a representative for group
-The individual results suggest that the group results are not driven by a couple
-of subjects.
+In summary, the individual results suggest that the group results are not driven
+by a couple of subjects but still reveal individual differences.
+% PPA just an example
+The feature ``auditory spatial information'' is just one example of a stimulus
+feature that can be annotated and used to build a model.
 % auditory localizer
-Moreover, a complex but naturally engaging auditory stimulus like an audiobook
+Thus, a complex but naturally engaging auditory stimulus like an audiobook
 might in principle be used as a non-visual localizer for a variety of brain
@@
 during brain scanning.
-% PPA just an example
-The feature ``auditory spatial information'' is just one
-example of a stimulus feature that can be annotated and used to build a model.
 
 \subsubsection{AV stimulus}
+% intro
 On individual level, mixed results for AV stimulus.
@@
 dem Wohnwagen ihrer Großmutter"
+
 % soundsscapes makes change of setting obvious before narrator kicks in

### 2020-09-28 paper/main.tex
general makeover until discussion of indv. results

@@
 
-% Titel-Vorgabe < 110 chars incl. spaces
-%  jetzt 109 Chars
+% title has to be < 110 chars incl. spaces
+%  at the moment 109 Chars
 \title{Hemodynamic responses of the Parahippocampal Place Area to spatial cues in a movie and its audio-description}
 
-\author{Christian~O.~Häusler\textsuperscript{1,2{*}}, Michael Hanke\textsuperscript{1,2}}
+\author{Christian~O.~Häusler\textsuperscript{1,2{*}}, Michael
+Hanke\textsuperscript{1,2}}
 % https://www.nature.com/sdata/publish/for-authors#other-formats
@@
 1. Psychoinformatics Lab, Institute of Neuroscience and Medicine, Brain \&
-Behaviour (INM-7), Research Centre Jülich, Jülich, Germany,
-2. Institute of Systems Neuroscience, Medical Faculty, Heinrich Heine University,  Düsseldorf, Germany
-{*}corresponding author: Christian Olaf Häusler (der.haeusler@gmx.net)
+Behaviour (INM-7), Research Centre Jülich, Jülich, Germany, 2. Institute of
+Systems Neuroscience, Medical Faculty, Heinrich Heine University,  Düsseldorf,
+Germany {*}corresponding author: Christian Olaf Häusler (der.haeusler@gmx.net)
 
@@
 studyforrest data set, general linear model; Results: significant clusters in
-PPA, RSC, individual results in x of 15 subjects; Conclusions: PPA nicht
-exclusively \end{abstract}
-
-\todo[inline]{Intro + Discussion = main text; ca. 3,000 words; some minor
-    ``issues'' are in comments and not labeled as to do's}
+PPA, RSC, individual results in x of 15 subjects; Conclusions: results suggest
+generalizability to spoken language and is restricted to processing visual
+stimuli exclusively. \end{abstract}
 
@@
     the main manuscript .tex file (and delete the associated
-    \textbackslash{}bipliography and \textbackslash{}bibliographystyle
+    \textbackslash{}bibliography and \textbackslash{}bibliographystyle
 commands)}
@@
 
-\todo[inline]{RSC is not mentioned in the introduction but should (probably)
-shortly discussed in the, well discussion; RSC shows up in group results but
-mixed results in individual subjects}
+\todo[inline]{Limit for Intro + Discussion (main text) = ca. 3k words;
+intro is about 1k words (with to dos)}
+
+\todo[inline]{RSC is not mentioned in intro anymore but it shows up in group
+results (mixed in individual subjects) and therefore could be discussed}
 
@@
 % anatomical location != functional location
-The PPA is located in the posterior parahippocampal gyrus including adjacant
-regions of the fusiform gyrus \cite{epstein1998ppa} at the boundary to the anterior lingual gyrus \citep{epstein2008parahippocampal}.
+The PPA is located in the posterior parahippocampal gyrus including adjacent
+regions of the fusiform gyrus \cite{epstein1998ppa} and anterior lingual gyrus
+\citep{epstein2008parahippocampal}.
 % neural correlate of scene perception
@@
 % connectivity analysis by Wolbers
-\todo[inline]{Er hat noch eine Connectivitäts-Analyse mit dem Occipital Cortex
-    gemacht. Im Vergleich zum visuellen Paradigma ist im haptischen Paradigma
-    keine Connectivität. Interpretation: Es kann keine mental imagery sein;
-    ``The scene-related increase in coupling with the PPA was significantly
-stronger in multiple clusters in occipital cortex under visual than haptic
-stimulation (Figure 2B; Table S2)''}
+\todo[inline]{Wolbers performed connectivity analysis between PPA and occipital
+cortex, and compares connectivity during visual and haptic paradigm: ``The
+scene-related increase in coupling with the PPA was significantly stronger in
+multiple clusters in occipital cortex under visual than haptic stimulation
+(Figure 2B; Table S2)''}
 % Aziz (2008): place related sentences
 \todo[inline]{lass uns kurz im Gespräch über Aziz Paper gucken; die relvanten
-    Abschnitte sind in der PDF markiert. Ihre Method Section ist ``strange'' und
-    im Grunde kommt überall nur uneinheitliche Grütze heraus; ich blicke nicht
-    durch, weshalb folgendes nicht vollständig korrekt sein wird;so wie ich es
-verstanden habe, hat sie den Unterschied zwischen PPA und FFA angeguckt, aber
-diesen Unterschied im Kontrast zu object-related Sentences (dortige Fig 3)}
+Abschnitte sind in der PDF markiert. Ihre Method Section ist ``strange'' und im
+Grunde kommt überall nur uneinheitliche Grütze heraus; ich blicke nicht durch,
+weshalb folgendes nicht vollständig korrekt sein wird;so wie ich es verstanden
+habe, hat sie den Unterschied zwischen PPA und FFA angeguckt, aber diesen
+Unterschied im Kontrast zu object-related Sentences (dortige Fig 3)}
 % Aziz' stimuli
@@
 
-\todo[inline]{I deleted sentences regarding Aminoff's
-    (\citep{aminoff2006parahippocampal, aminoff2013role}) competing ``contextual
-associations hypothesis'' because our paradigm does not touch that issue.}
+\todo[inline]{I deleted sentences regarding competing ``contextual associations
+    hypothesis'' (\citep{aminoff2006parahippocampal, aminoff2013role}) because
+our events/regressors cannot touch that issue; might be interesting during
+discussion of anterior/posterior PPA.}
 
@@
 improve the signal-to-noise-ratio (SNR).
-% disadvatage 2b: no individual level
+% disadvantage 2b: no individual level
 The disadvantage here is that the averaging approach does not characterize brain
@@
 group results a driven by individuals subjects especially in response to
-audio-only stimulation\todo{``audio-only'' sounds meh}.
+audio-only stimulation\todo{``audio-only'' sounds meh; ``exclusively auditory
+stimulation''?}.
 % Huth (2016)
-\todo[inline]{but Huth et al. (2016) implicitly regarding audio-only; but they
-do not discuss the PPA; moreover, they do voxel-wise encoding which doesn't say
+\todo[inline]{Huth et al. (2016) implicitly regarding audio-only; but they do
+not discuss the PPA; in general, they do voxel-wise encoding which doesn't say
 anything about excitation/inhibition}
@@
 conditions free from any task.
+% traditional GLM
+We do this by analyzing our data by constructing GLM contrasts as canonically
+used to analyze data from tightly controlled paradigms.
 % focus on audio-description
@@
 
+\todo[inline]{maybe insert ``foreshadowing'' of results here?}
 \todo[inline]{Bzgl.
@@
 citation (see Data Records and Data Citations, below)}
+\todo[inline]{explain as introduction to every step why it woes done}
 \todo[inline]{current order of subsections might be ``non-canonical''}
-\todo[inline]{parts from original studies still detailed; feel free to delete
-sentences}
+\todo[inline]{parts from original studies might still be too detailed}
 
@@
 % used studies
-\todo{this is just loveless listing so far} The same subjects were
+The same subjects were
 % AO
@@
 the movie ``Forrest Gump'', a dataset already used by \citep{hu2017decoding,
-nguyen2016integration},
+nguyen2016integration},\todo{this is kind of a loveless list}
 % AV
@@
 \subsection{Naturalistic stimuli annotation}
-
+%todo
 % stimuli were not designed for research purposes
@@
 capture attention free from any perceptual or behavioral task.
+% AO annotation
+For the analysis of the AO data, we extended an publicly available annotation of
+speech \citep{haeusler2020speechanno} by further annotating words spoken by the
+audio-description's narrator.
+% annotation procedure
+Two persons performed a categorization of nouns that the narrator uses to
+describe the movie's missing visual content.
+% why and how of categories 1
+Some categories were created in such a way to reflect the six stimulus
+categories used in the visual localizer experiment.
+% why and how of categories 2
+Some additional categories were created to semantically cluster nouns into
+categories ``that were obvious to make sense''.\todo{yeah, well, sounds shit but
+that's basically it}
+% categories in detail
+Nouns were categorized by the verbal clue they provide about the cinematographic
+scene's environment (\texttt{geo}, \texttt{geo-room}; \texttt{setting\_new},
+\texttt{setting\_old}), its inherent persons (e.g. \texttt{female},
+\texttt{male}, \texttt{persons}), a person's body or worn clothes
+(\texttt{face}, \texttt{head}, \texttt{body}, \texttt{bodypart}), and a scene's
+inherent objects (\texttt{object}, \texttt{furniture}).
+% problem with hierarchical categories
+\todo[inline]{put stuff regarding hierarchical categories and heterogeneity
+here; counts in table show the counts of just the primary category; settings
+changes often (30-60 \%) belong to another category; most often it's geo but
+also object or male/mname/furniture; cf. Results and Discussion regarding
+stability of contrasts}
+% reference to table with rules and examples
+A complete overview of all 19 categories, the rule for a word to belong to a
+category, and examples can be seen in \ref{tab:descr-nouns-rules}.
+% procedure
+A preliminary annotation was performed by one person according to the rules.
+Minor corrections due to incorrectly applied rules were done by the author.
+% reference to table with counts
+The resulting counts for the whole stimulus and the eight stimulus segments used
+during fMRI scanning can be seen in Table \ref{tab:descr-nouns-counts}.
+
 % AV anno
@@
 
-% AO anno
-For the analysis of the AO data, we extended another publicly available
-annotation of speech \citep{haeusler2020speechanno} by annotating words embedded
-in sentences spoken by the audio-description's narrator.
-% annotation procedure
-Two persons performed a categorization of nouns that describe the movie's
-missing visual content.
-% why and how of categories 1
-Some categories were created in such a way to reflect the six stimulus
-categories used in the visual localizer experiment.
-% why and how of categories 2
-Some additional categories were created to semantically cluster nouns into
-categories ``that were obvious to make sense''.\todo{yeah, well, sounds shit but
-that's basically it}
-% categories in detail
-Nouns were categorized by the verbal clue they provide about the
-cinematographic scene's environment (geo, geo-room; setting\_new, setting\_old),
-its inherent persons (female, female name; male, male name, person), a person's
-appearance (face, head; body, bodypart), and a scene's inherent objects (object,
-furniture).
-% reference to table with rules and examples
-A complete overview of all 19 categories, the rule for a word to belong to a
-category, and examples can be seen in \ref{tab:descr-nouns-rules}.
-% procedure
-A preliminary annotation was performed by one person according to the rules.
-Minor corrections due to incorrectly applied rules were done by the author.
-% reference to table with counts
-The resulting counts for the whole stimulus and the eight stimulus
-segments used during fMRI scanning can be seen in Table \ref{tab:descr-nouns-counts}.
-
-\todo[inline]{currently table is to wide; smaller font? less text? rotate the table?}
+\todo[inline]{currently table is to wide; smaller font? less text? rotate the
+table?}
 
@@
     categories, annotation rules, and examples (given in English). The category
-    \texttt{++} also contains adverbial adjectives and adverbs.}
+    \texttt{++} also contains adverbial of time.}
 \label{tab:descr-nouns-rules}
@@
 \midrule
-body & trunk of the body; overlaid clothes & back, hip, shoulder; jacket, dress
-shirt \tabularnewline
+body & trunk of the body; overlaid clothes & back, hip, shoulder; jacket, dress, shirt \tabularnewline
 bodypart & limbs and trousers & arm, finger, leg, toe \tabularnewline
@@
 % paradigm implementation
-In all three studies, stimulation was implemented with \href{http://www.psychopy.org}{PsychoPy} \citep{peirce2007psychopy} running on a computer with the NeuroDebian operating system \citep{halchenko2012open}.
+In all three studies, stimulation was implemented with
+\href{http://www.psychopy.org}{PsychoPy} \citep{peirce2007psychopy} running on a
+computer with the NeuroDebian operating system \citep{halchenko2012open}.
 
@@
 I am pretty unsure about correctness}
-\todo[inline]{Satz zum Downsampling der 7T Daten?}
+\todo[inline]{what is missing: As I see it, AO must have been downsampled
+to 2.5x2.5x2.5 mm and AV must have been upsampled from 3.0 to 2.5mm}
 
@@
 Data were already corrected for motion and aligned by non-linear warping to a
-particpant-specific BOLD template image \citep{sengupta2016extension}.
+participant-specific BOLD template image \citep{sengupta2016extension}.
 % exclusion of VP 10
@@
 
-% actual preprocessing
+% my preprocessing
 Preprocessing was carried out using FEAT v6.00 (FMRI Expert Analysis Tool;
@@
 control (see details below).
-% nuissance regressors
+% nuisance regressors
 Lastly, we used continuous bins of information about two auditory features
@@
 geo & immobile landmarks & \aoGeoAll & \aoGeoI & \aoGeoII & \aoGeoIII & \aoGeoIV & \aoGeoV & \aoGeoVI & \aoGeoVII & \aoGeoVIII \tabularnewline
-groom & elements defining geometry of local space & \aoGroomAll & \aoGroomI & \aoGroomII & \aoGroomIII & \aoGroomIV & \aoGroomV & \aoGroomVI & \aoGroomVII & \aoGroomVIII \tabularnewline
+groom & elements defining geometry of room & \aoGroomAll & \aoGroomI & \aoGroomII & \aoGroomIII & \aoGroomIV & \aoGroomV & \aoGroomVI & \aoGroomVII & \aoGroomVIII \tabularnewline
 object & inanimate entities with firm boundaries & \aoObjAll & \aoObjI & \aoObjII & \aoObjIII & \aoObjIV & \aoObjV & \aoObjVI & \aoObjVII & \aoObjVIII \tabularnewline
@@
 % how they were fitted
-a \texttt{no\_cut} event had to have a minimum distance of \unit[10]{s} to a movie
-cut and to another \texttt{no\_cut} event.
+a \texttt{no\_cut} event had to have a minimum distance of \unit[10]{s} to a
+movie cut and to another \texttt{no\_cut} event.
 % reference to table
@@
 found in Table \ref{tab:av-events}.
+% modeling of regressors from events
+Events of both stimuli were convolved with a double gamma hemodynamic response
+function (HRF).
 
@@
 fg\_av\_ger\_lrdiff & left-right volume difference & \avFgavgerlrdiffAll & \avFgavgerlrdiffI & \avFgavgerlrdiffII & \avFgavgerlrdiffIII & \avFgavgerlrdiffIV & \avFgavgerlrdiffV & \avFgavgerlrdiffVI & \avFgavgerlrdiffVII & \avFgavgerlrdiffVIII \tabularnewline
-fg\_av\_ger\_ml & +++???+++ & \avFgavgermlAll & \avFgavgermlI & \avFgavgermlII & \avFgavgermlIII & \avFgavgermlIV & \avFgavgermlV & \avFgavgermlVI & \avFgavgermlVII & \avFgavgermlVIII \tabularnewline
-fg\_av\_ger\_pd & +++???+++ & \avFgavgerpdAll & \avFgavgerpdI & \avFgavgerpdII & \avFgavgerpdIII & \avFgavgerpdIV & \avFgavgerpdV & \avFgavgerpdVI & \avFgavgerpdVII & \avFgavgerpdVIII \tabularnewline
+fg\_av\_ger\_ml & +++++???+++++ & \avFgavgermlAll & \avFgavgermlI & \avFgavgermlII & \avFgavgermlIII & \avFgavgermlIV & \avFgavgermlV & \avFgavgermlVI & \avFgavgermlVII & \avFgavgermlVIII \tabularnewline
+fg\_av\_ger\_pd & +++++???+++++ & \avFgavgerpdAll & \avFgavgerpdI & \avFgavgerpdII & \avFgavgerpdIII & \avFgavgerpdIV & \avFgavgerpdV & \avFgavgerpdVI & \avFgavgerpdVII & \avFgavgerpdVIII \tabularnewline
 fg\_av\_ger\_rms & root mean square (loudness) & \avFgavgerrmsAll & \avFgavgerrmsI & \avFgavgerrmsII & \avFgavgerrmsIII & \avFgavgerrmsIV & \avFgavgerrmsV & \avFgavgerrmsVI & \avFgavgerrmsVII & \avFgavgerrmsVIII \tabularnewline
-fg\_av\_ger\_ud & +++???+++ & \avFgavgerudAll & \avFgavgerudI & \avFgavgerudII & \avFgavgerudIII & \avFgavgerudIV & \avFgavgerudV & \avFgavgerudVI & \avFgavgerudVII & \avFgavgerudVIII \tabularnewline
+fg\_av\_ger\_ud & +++++???+++++ & \avFgavgerudAll & \avFgavgerudI & \avFgavgerudII & \avFgavgerudIII & \avFgavgerudIV & \avFgavgerudV & \avFgavgerudVI & \avFgavgerudVII & \avFgavgerudVIII \tabularnewline
 \end{tabular}
@@
 
-% modeling of regressors from events
-Events of both stimuli were convolved with a double gamma hemodynamic response
-function (HRF).
 % reference to figure ``correlation of regressors''
-The Pearson correlation coefficients of the regressors of the AO and AV stimulus
-across the time course of all segments can be seen in Figure \ref{fig:reg-corr}.
+We computed the Pearson coefficients of the regressors across the eight segments
+of both naturalistic stimuli. Results demonstrate no to minor correlations
+(s. \ref{fig:reg-corr}) which suggest the models should not suffer from low
+detection power due to shared variance among regressors.
+
 % temporal derivatives
@@
 \todo[inline]{contrasts are ordered by ``how well they make sense'' according to
-theory, and amount of events/data. Hence, they were assumed to result in more
-and more shitty results; at the moment all 8 contrasts are used in the result
-(figure) despite the low ranked COPEs yielded 0 result as kinda expected}
+    theory, and amount of events/data; Hence, they were assumed to result in
+    more and more shitty results (s. introductory sentence in results); at the
+    moment all 8 contrasts are used in the result (figure) despite the low
+ranked COPEs yielded 0 result as kinda expected}
 
@@
 descriptive nouns.
-% furniture: blurred border between groom and object
+% furniture
 We did not use the category ``furniture'' (\texttt{furn}) as a regressor in one
-of the contrasts of interest because this category was considered to eighter
-count as object or a geometry-defining structure of a room/locale.
-\todo[inline]{Epstein (2008): response to arrays of objects drawn from the rooms
-    but displayed on a blank background is quite weak [11]}
+of the contrasts of interest because nouns in this category could either be
+considered as object or as a geometry-defining structure of a room.
+\todo[inline]{but: Epstein (2008): response to arrays of objects drawn from the
+rooms but displayed on a blank background is quite weak [11].}
 % negative control contrasts
@@
 \citep{epstein1999parahippocampal}.
-% im Ergebnis
+% hence, the following contrasts
 Hence, we created varying contrasts comparing a setting occurring for the first
@@
 
-\todo[inline]{give references to the publications explaining the template
-creation; take a look at Sengupta (2016), and maybe speech-anno-paper}
 % single subjects (for Bland-Altman-Plots) 1st level
@@
 On the one hand, subject-specific BOLD T2* time series were anatomically aligned
-via linear transformation to a subject-specific, study-specific T2* template.
+via linear transformation to a subject-specific, study-specific T2* template (cf
+. \citep{sengupta2016extension}).
 % group template (for group and individual brain slices)
@@
 On the other hand, time series were aligned via non-linear transformation to a
-study-specific T2* group template.
+study-specific T2* group template (cf. \citep{hanke2014audiomovie}).
 % MNI152
@@
 
-% summary of methods: AO
-We used conventional GLM contrasts to exploratorily investigate if auditory cues
-embedded in a naturalistic audio-only stimulus correlate with increased
-hemodynamic activity in the PPA.
-% summary of methods: AV
+% study goal
+The goal of this study was to investigate if increased hemodynamic activity in
+the PPA correlates with spatial information presented under more ecological
+valid conditions.\todo{cautious phrasing but still problematic: looking for
+confirmation}
+% what we did
+We used annotations of a \unit[2]{h} movie and it's temporally aligned
+audio-description to create conventional GLM contrasts of of modeled
+hemodynamic activity resembling analyses of previous studies using simplified
+stimuli.
+% comparison AO & AV
 We compare these results on a group and individual level to results gained from
@@
 
-% subsequent paragraphs start with a sentence or two
-% that set up the question that the paragraph answers
-% e.g. ``To verify that there are no artifacts..''
-% What is the test-retest reliability of our measure?''
-% “We next tested whether Ca2+ flux through Ca2+ channels was involved.''
-% Middle of the paragraph presents data and logic that pertain to the question,
-% paragraph ends with a sentence that answers the question
-% For example, it may conclude that none of potential artifacts were detected.
-% Each paragraph convinces the reader of answer given in its last sentence.
-% The result of each paragraph is a logical statement
-
 \subsection{primary contrasts}
 
+\todo[inline]{paragraphs start with a sentence or two that set up the question
+that the paragraph answers; e.g. ``To verify that there are no artifacts; What
+is the test-retest reliability of our measure?''}
+\todo[inline]{middle of the paragraph presents data and logic that pertain the question}
+\todo[inline]{paragraph ends with a sentence that answers the question via logical statement; for example, it may conclude that none of potential     artifacts were detected.
+Each paragraph convinces the reader of answer given
+in its last sentence}
+
 \todo[inline]{at the moment I think it is better to report the primary contrast
-fist and then report the stability of contrast; but that opinion changend twice
+fist and then report the stability of contrast; but that opinion changed twice
 already.}
@@
 \midrule
-3003 & 0 & 5.31 & 22.5 & -45.5 & -12 & 4.53 & -63.3 & -3.72 & r. lingual g.; r
-cuneal c., intracalcarine c., bilaterally occipital fusiform g., temporal fusiform c., posterior parahippocampal c.  \\
+3003 & 0 & 5.31 & 22.5 & -45.5 & -12 & 4.53 & -63.3 & -3.72 & r. lingual g.; r. cuneal c., intracalcarine c., bilaterally occipital fusiform g., temporal fusiform c., posterior parahippocampal c.  \\
 154 & 6.56E-07 & 4.46 & -35 & -83 & 28 & -32.8 & -86.2 & 21.4 & l. superior lateral occipital c. \\
@@
 \subsection{individual results}
+
+\todo[inline]{other reasons than localization performance? look which subjects influence the group results the most? ``multiple localizer''?}
 % why individual results in the first place.
 We also investigated localization performance of both naturalistic paradigms on
-the level of individual subjects. \todo{maybe report the other reason here, too:
-which subjects influence the group results the most? ``multiple localizer''?}
+the level of individual subjects.
 % results in both subject and group space
@@
 For the AV stimulus, results show homologous clusters in five subjects, and
-unilateral right clusters in seven subjects (of which one subjects also yielded
-just a unilateral cluster in the dedicated localizer).
+unilateral right clusters in seven subjects (of which one subjects yielded a
+unilateral cluster in the dedicated localizer).
 % difference to dedicated localizer
-In sub-20 bilateral, where the dedicated localizer yielded only one cluster in
-the right hemisphere.
+We find bilateral clusters in sub-20, in which the dedicated localizer yielded
+only one cluster in the right hemisphere.
 
@@
 % why
-To better depict the agreement (and difference) between indivudal results of the
-visual localizer and contrast 1 of the AO paradigm, we created one
+To better depict the agreement (and difference) between individual results of
+the visual localizer and contrast 1 of the AO paradigm, we created one
 Bland-Altman-Plots for each of the 14 subjects (see Figure
@@
 % masking in detail
-Voxels were spatially contrained to a) voxels located in the occipital and
+Voxels were spatially constrained to a) voxels located in the occipital and
 temporal lobes (gray; using the (probabilistic) Jülich Histological Atlas
@@
 
+\todo[inline]{at the moment (which changes regularly) this section should follow
+the other group results; depends on the ``final'' discussion.}
+
 \todo[inline]{I consider tables of significant clusters for every contrast as
-overkill. One contrast, the ``primary contrast'', is appropriate.}
+overkill. One contrast, the ``primary contrast'', is appropriate; s. comments
+for overview of individuals}
 
@@
 % why we did different contrasts
-We created a variety of contrasts to test if our approach yielded
-similar results across similar contrasts and if localization performance
-decreases the further the contrasts deviate from the spatial layout hypothesis
-\todo{and the less data we use}.
+We created a variety of contrasts to test a) if our approach yielded
+similar results across similar contrasts and b) if localization performance
+decreased when the contrast included categories that contained stimuli less
+congruent with the ``optimal'' stimulus type\todo{and the less data we use}.
 
@@
 Further, the ability to functionally isolate the PPA decreases the more a
-contrast depends on (just) using \texttt{se\_new} and \texttt{se\_old}
-\todo{interpretation (-> discussion): this category is essentially filled with
-    nouns from other cateogries but nevertheless primarily cueing a change of
-    setting; setting changes are often anticipated by a change of soundscape,
-meaning the narrator lagges behind; well, and the more a contrasts only relies
-on these, the less data is available, because just two categories the more the
-contrast depends on (just) using se\_new or se\_old}
+contrast depends on (just) using the categories \texttt{se\_new} and
+\texttt{se\_old} which were assumed to be problematic for a couple of reasons
+(s. discussion of stability of contrasts)
 
@@
         Contrasts provide decreasing congruency with the spatial layout
-        hypthesis and/or progressively less data/events. The overlap across
+        hypothesis and/or progressively less data/events. The overlap across
         contrasts is overlaid on the MNI152 T1-weighted head template (gray).
@@
 
-\subsection{crossmodal and negative controls}
-
-\todo[inline]{shall results of these contrasts be reported as well? imo: the one
-who says a) should say b), too. At the moment the contrasts are just listed in
-the method section}
+\subsection{cross-modal and negative controls}
+
+\todo[inline]{the contrasts are listed in the methods section. shall results of
+these contrasts be reported here as well?}
 
 \todo[inline]{there are only two control contrasts that yield significant
-    clusters: in AO stimulus using annotation of movie cuts (vse\_new >
-    pe\_old): right RSC; and in the AV stimulus using annotation of the narrator
-    (se\_new > se\_old): right PPA; this kinda suggest particpants use the
-soundscape for re-orienting (which still might be a bold claim)}
+clusters. AO stimulus using annotation of movie cuts (vse\_new > pe\_old): right
+RSC. AV stimulus using annotation of the narrator (se\_new > se\_old): right
+PPA.}
 
@@
 
-% Discussion explains how results fill gap identified in intro
-% provides caveats to the interpretation
-% describes how paper advances the field by providing new opportunities.
-
-% typically done by recapitulating the results, discussing limitations,
-% and then revealing how the central contribution may catalyze future progress.
-
-% first discussion paragraph is special in that it generally summarizes the
-% important findings from the results section -> give gist of results
-
-% following paragraphs in the discussion section starts by describing an area of
-% weakness or strength of the paper.  It then evaluates the strength or weakness
-% by linking it to the relevant literature.
+\todo[inline]{in general, the discussion explains how results fill gap
+identified in intro provides caveats to the interpretation describes how
+paper advances the field by providing new opportunities}
+
+\todo[inline]{typically done by recapitulating the results, discussing
+limitations, and then revealing how the central contribution may catalyze future
+progress}
+
+\todo[inline]{first paragraph summarizes the important findings from the results
+section, focusing on their meaning}
+
+\todo[inline]{We demonstrate\dots; we discovered\dots; our data provide
+evidence\dots}
+
+% previous studies
+Previous studies reported bilaterally increased hemodynamic activity in the PPA
+when participants were watching static pictures of landscape compared to face or
+objects \citep{epstein1998ppa, epstein1999parahippocampal} whereas a study using
+spoken sentences reported mixed results \citep{aziz2008modulation}.
+% what we wanted to test
+Hence, we tested if the perception of spatial cues embedded in an auditory
+narrative compared to non-spatial cues correlate with increased activation in
+the PPA.
+% ``how'' we did it
+By using analogous statistical models for three different experimental
+paradigms, we are able to compare results gained from a dedicated visual
+localizer to results we gained from a movie and the movie's audio-only variant.
+
+\todo[inline]{high-level summary/interpretation of results in one sentence here
+already?}
+
+\subsection{correlation of regressors}
+\todo[inline]{could maybe put into method section to save space here}
+% stimuli not designed for research purposes
+Both naturalistic stimuli were not designed to be used in a BOLD fMRI experiment
+but to entertain their audiences.
+% why correlation matrix  was created
+Thus, we first tested for correlation of regressors (s. \ref{fig:reg-corr}) that
+are based on the annotated stimulus features because a high degree of shared
+variance lowers detection power.
+% results of computing feature correlation
+Results show no to minor correlations of regressors across all stimulus
+segments.
+% encouraged by that we build contrasts (statement)
+Similarly to previous studies that used simplified stimuli to isolate the PPA,
+we created traditional voxel-wise GLMs that modeled and contrasted
+hemodynamic activity.
+
+% The second through fourth paragraphs may deal with potential weaknesses
+% linking it to the relevant literature or how future experiments can deal
+% with these weaknesses.
+
+% The fifth paragraph may then culminate in a description of how the paper moves
+% the field forward.
 
@@
 
-% For example, the first paragraph may summarize the results, focusing on their
-% meaning.
-
-% The second through fourth paragraphs may deal with potential weaknesses and
-% with how the literature alleviates concerns or how future experiments can deal
-% with these weaknesses.
-
-% The fifth paragraph may then culminate in a description of how the paper moves
-% the field forward.
-
-%Step by step, the reader thus learns to put the paper’s conclusions into the
+% step by step, the reader thus learns to put the paper’s conclusions into the
 %right context.
 
-\subsection{intro}
-\todo[inline]{goal and what we did should probably in result section}
-% study goal
-The goal of this study was to investigate if increased hemodynamic activity in
-the PPA correlates with spatial information presented under more ecological
-valid conditions.\todo{cautious phrasing but still problematic: looking for
-confirmation}
-% what we did
-We used annotations of a \unit[2]{h} movie and it's temporally aligned
-audio-description to create GLMs of hemodynamic activity resembling analyses
-of previous studies using simplified stimuli.
-
-\todo[inline]{summary of results like ``Our results demonstrate that\dots''}
-
-\subsubsection{correlation of regressors}
-% stimuli not designed for research purposes
-Both stimuli were not designed to for research purposes detection power in a
-fMRI experiment) but to entertain their audiences.
-% why we created the correlation matrix in the first place
-We first tested for correlation of stimulus features because a high degree of
-shared variance lowers detection power.
-% summary of results
-Results show only minor to no correlations of regressors across all stimulus
-segments.
-% statement
-Hence depending on the stimulus features of interest, it was feasible to use the
-annotated stimulus features for our research question.
-
-\subsection{group analysis}
+\subsection{group level}
+% intro
+We performed whole-brain analyses on an individual and group level. On the group
+level of both naturalistic stimuli, significantly increased activity in the PPA
+correlates with spatial events compared to non-spatial events.
 
 \subsubsection{AO stimulus}
+
+\todo[inline]{Do Wilson (2008), Lerner (2011), Honey (2012), Silbert (2014) find
+ISC in PPA using an auditory stimulus?}
 % AO stimulus cluster location
-The results of the AO stimulus yielded isolated clusters in the anterior part of
-the PPA ROI (overlap of individual PPAs taken from Sengupta et al.).
-% comparison to other studies using ISC
-\todo[inline]{check Wilson (2008), Lerner (2011), Honey (2012), Silbert (2014).
-Do they find ISC in PPA using an auditory stimulus? As far as I remember they
-don't}
+More specifically for the primary contrast of the AO stimulus, group results
+show spatially concise / restricted clusters in the anterior part of the PPA
+group overlap taken from \citep{sengupta2016extension}.
 % diff to Aziz (2008)
 Unlike \citep{aziz2008modulation} we did not use whole sentences as events to
-model a hemodynamic response but the length of the word giving the cue about the
-visual content of a scene.
-% no task
-Compared to \citep{ocraven2000mental} participants of our study were not
-instructed to form a vivid mental image of the stimulus but to ``enjoy the
-audiobook''. This procedure resembles experiencing the world around us in
-real-life more closely
-% naive to the research question
-Moreover, participants could not infer the perceptual process to be investigated
-by merely being exposed to the stimuli / experimental design. This suggests
-spatial information is processed in the PPA despite a lack of visual
-attention.\todo{bold claim here}
-% comparison to Wolbers
-Similarly to \citep{wolbers2011modality} who found increased activation in the
-PPA when blind study participants haptically explored scenes made out of LEGO
-blocks compared to other objects, our results support the hypthesis that
-increased activation in the PPA does not necessarily rely on creating a vivid
-mental image.
-% (visual or auditory) spatial attention
-Results further suggest activation does also not rely on deliberately paying
-auditory attention to spatial information embedded in a complex/rich auditory
-stimulus.\todo{kinda bold statement}
-% others
-\todo[inline]{Aminoff (2013). PPA's role in cognition regarding non-spatial
-stuff: ``Although the PHC is commonly thought of as responding to visual
-stimuli, it has also been found to elicit activity for auditory stimuli
-[25,26,30,31] and to respond to odor stimuli [32–34]''.}
-% concluding statement
-In summary, our group results suggest that auditory spatial information does not
+model a hemodynamic response but modeled an event from on- to offset of each
+word that was giving the cue about the movie's missing visual content of a
+scene.
+% conclusion
+our group results suggest that auditory spatial information does not
 just modulate activity in the PPA (depending on other factory like familiarity,
-XY; s. Aziz) but correlates with bilaterally increased
+XY; s. \citep{aziz2008modulation}) but correlates with bilaterally increased
 activation.\todo{``modulate'' suggests causation}
 
-% RSC
-Epstein (2008): Neuroimaging studies of human navigation most com- monly
-activate the posterior parahippocampal and retro- splenial cortices [4–10],
-regions that also respond strongly during passive viewing of navigationally
-relevant visual stimuli such as scenes and buildings [11–14]. Consistent with
-these findings, damage to these areas often leads to wayfinding deficits [15].
-These results indicate that para- hippocampal and retrosplenial cortices are key
-nodes of the neuronal network that support spatial navigation in humans. But
-what are the specific functions of each of these nodes?
-% location
-A second focus of cortical activity during navigation tasks is found in the
-retrosplenial cortex-posterior cingulate- medial parietal region, near to the
-point where the calcarine sulcus joins the parietal-occipital sulcus.
-Retrosplenial cortex (BA 29 and 30) adjoins and is partially encircled by the
-posterior cingulate (BA 23 and 31) [51–56]; consequently, these labels are often
-used somewhat inter- changeably when describing the locations of functional
-activations. Because of these ambiguities, I use the term retrosplenial complex
-(RSC) to refer to this functional- defined scene-responsive region, which is not
-necessarily identical to the anatomically defined retrosplenial cortex [26].
+% no task in Epstein
+An early study \citep{epstein1998ppa} that compared results from a paradigm that
+employed a (perceptual) judgment task of static pictures to a paradigm that did
+not let participant judge the same pictures.
+% results during no task
+Hemodynamic activity was less but still significantly increased when
+participants had no task to keep them alert and attentive to the stimuli.
+% we have no task neither
+Our paradigm is similar in that sense that our participants had no behavioral or
+cognitive task (e.g. forming a mental image of the stimuli; cf.
+\citep{ocraven2000mental})  but just had to ``enjoy the audio-description''.
+% but we are still different
+Nevertheless, our paradigm differs from previous studies because relevant
+stimulus features were incidentally embedded in a continuous auditory
+(or audio-visual) stream.
+% conclusion
+This embeddedness prevents participants from guessing the investigated
+perceptual process by just being exposed to the paradigm and mimics experiencing
+the world outside the lab more closely.
+% concluding statement: kinda automatic process
+The lack of a task further suggests verbal spatial information is processed in
+the PPA in an automatic fashion and does not necessarily rely on deliberately
+paying attention to spatial information.
+
+\paragraph{(non-existing) other cluster}
+% whole brain analysis
+Regarding confounding variables, we do not find significant clusters in e.g.
+early auditory cortices despite performing a whole brain analysis on data gained
+from a naturalistic stimulus paradigm.
+% conclusion
+This suggests that variance correlating with lower level auditory processes was
+averaged (out) across trials and/or regressed out by implementing the nuisance
+regressors.
+% shit was averaged out we did not even know of
+Further, unknown stimulus features we did not even annotate did not lead to a
+variety of significant cluster across the brain that hamper interpretation of
+results.
+% conclusion
+This provides further evidence that model-driven analyses can be run on data
+from naturalistic stimuli to isolate brain activity correlating with specific
+perceptual processes.
+% superior lateral occipital sulcus
+\todo[inline]{bilateral superior lateral occipital cortex}
+
+\paragraph{RSC}
+
+\todo[inline]{check location in primary contrast and in overlap of contrasts}
+
+\todo[inline]{from Epstein, 2008: Neuroimaging studies of human navigation most
+commonly activate the posterior parahippocampal and retrosplenial cortices
+[4–10], regions that also respond strongly during passive viewing of
+navigationally relevant visual stimuli such as scenes and buildings [11–14]
+\citep{epstein2008parahippocampal}.
+
+% but RSC
+Apart from the PPA, we find significantly increased activity in a functionally
+defined scene-responsive region often referred to as the retrosplenial cortex
+(RSC) in the primary contrast and consistently across the additional
+contrast\todo{how many exactly}.
+
+% location functionally defined
+This functionally defined RSC which is not necessarily identical to the
+anatomically defined retrosplenial cortex [26]
+\citep{epstein2008parahippocampal} is located in the retrosplenial cortex, and
+posterior cingulate region, near to the point where the calcarine sulcus joins
+the parietal-occipital sulcus \citep{epstein2008parahippocampal}.
+% anatomy of real RSC
+The Retrosplenial cortex (BA 29 and 30) adjoins and is partially encircled by
+the posterior cingulate (BA 23 and 31) [51–56]
+\citep{epstein2008parahippocampal}.
 % function
 RSC is strongly active during scene viewing, scene imagery [25] and mental
-imagination of navigation through familiar environments [8]. In contrast to the
-PPA, in which place familiarity effects are usually quite small, RSC responds
-50% more strongly to familiar than to unfamiliar places [23,57], indicating that
-RSC is involved in recovery of long-term spatial knowledge about familiar
-environments. Further evidence for this idea comes from recent studies reporting
-that RSC activity was signifi- cantly greater when subjects reported the
-location of a campus scene than when they simply reported whether it was
-familiar or not [24] (Figure 3a) and that RSC activity during learning of a
-virtual-reality town corresponded to the total amount of survey knowledge
-acquired [58] (Figure 3b; see also Ref. [59] for similar results in mice).
-% summary
-The PPA and RSC seem to have distinct but complemen- tary roles during spatial
-navigation. The PPA encodes a representation of the local scene that enables it
-to be remembered and subsequently recognized, whereas RSC supports mechanisms
-that enable one to orient oneself within the broader spatial environment and to
-direct one’s movement towards navigational targets that are not cur- rently
-visible
+imagination of navigation through familiar environments [8]
+\citep{epstein2008parahippocampal}.
+% conclusion
+Interpretation \& conclusion???\todo{cf.\citep{vann2009what}}
 
 \paragraph{shortcomings of AO contrasts}
-% less ``scenes'' as such but more isolated ``landmarks
-
-%  se_new & se_old is often belongs to another (``hierarchical'' lower)
-%  category; interesting who PPA responds to words describing a scene as a whole
-%  (the gist) vs. landsmarks a scenes consists of
+% no ``landscape'' category
+Notably, our primary contrasts compared verbal cues regarding landmarks
+(\texttt{geo}) and elements defining the geometry of a room (\texttt{groom}) to
+non-spatial cues. While in the visual domain pictures of landmarks correlate
+with significantly increased activity in the PPA pictures of whole landscapes
+are considered to be the ``optimal'' stimulus type (cf. Epstein (1998, 1999,
+2003, 2008).
+% our se_new & se_old
+Our auditory stimulus provided only a small amount of nouns that described the
+landscape as a whole (e.g. ``in a football stadium'')  and these events were
+pooled with other nouns that generally cued a switch to another scene into the
+heterogeneous categories \texttt{se\_new} (e.g. ``Forrest in front of a
+buffet'', ``in Greenbow'') and \texttt{se\_old} (e.g. ``at the bench'')
+% further studies
+Given that humans can identify the gist of a rich visual scene within the
+duration of a single fixation \citep{henderson2003human} further studies might
+investigate how homogeneous categories of vague verbal descriptions of a whole
+scene differ from verbal descriptions of concrete landmarks.
 
@@
 % location
-Clusters of the analysis of the AV stimulus span the anterior, middle and
-posterior part of group overlap mask/roi.
+Clusters of the analysis of the AV stimulus span the group overlap of individual
+PPAs from anterior to posterior and retrosplenial regions bilaterally.
 % difference in location/size to AO and VIS
-Compared to cluster of the AO stimulus, they further extend into more posterior
-regions.\todo[inline]{which exactly? check fsleyes again; known functions of
-these areas -> should be explainable by confounds in movie frames}
+Clusters also extend into more posterior regions (occipital fusiform gyrus,
+lingual gyrus, and intracalcarine cortex) \todo{s. neurosynth in fsleyes?}
 % shortcomings + explanation
-shortcoming of not controlling visual content of the frames after the cut;
-% but
-nevertheless it's ``surprising'' that it works at all and the clusters located
-in systematically / bilaterally in (higher) visual areas; lot's of (non) visual
-features average out; and we are not using a dedicated stimulus
-% what should be done to improve
-make an annotation of frame's content
-
-\subsubsection{open question anterior vs. posterior PPA???}
-
-% Epstein (2008)
-In particular, anterior PHC might do more than just scene recognition; it might
-also have a more general role in spatial memory encoding [94].
-
-\subsubsection{Retrosplenial cortex}
-\todo[inline]{check location in primary contrast and in overlap of contrasts;
-atlases do not ``know'' RSC as such but provide other term(s)}
-\todo[inline]{cf. Aminoff (20xx). What does the retrosplenial cortex do?}
-Another region that showed significantly increased activity not just in the
-primary contrast but consistently across contrasts is ventral precuneus / RSC
-(check the overlap again to not talk shit; no atlas gives RSC as such)\dots
+% confound of higher perception
+This can be attributed to the fact that we averaged the content of individual
+frames after a cut and did not control for confounding features like depicted
+faces or objects.
+% confounds of lower perception
+It further suggest low-level visual features were not averaged out leading to
+clusters spanning the intracalcarine cortex.
+% further studies
+Hence, further studies focusing on visual perception should annotate and model
+visual features of naturalistic stimuli more rigorously.
+%
+\todo[inline]{interpretation of clusters lateral occipital cortex?}
+\todo[inline]{discuss that we DID NOT find clusters that could be attributed to
+top-down / bottom-up attention, eye movements (FEF) (cf. corbetta2002control
+or memory (which memory)?}
+
+\subsubsection{stability of contrasts}
+% intro
+\todo[inline]{following logical structure is meh}
+% why we did a couple of contrasts
+For both stimuli we created additional contrasts that varied the amount of
+events available for the analysis and how well the annotated events within
+categories on average matched the stimulus type that we assumed to be
+preferentially processed in the PPA.
+% it shows two thing
+The results of the additional contrasts show two things. First, the
+bilaterally increased activation in the PPA does not depend on accidental
+findings but are stable across contrasts.
+% second: decline in isolation power
+Second, the ability to isolate clusters in the PPA declines nevertheless
+depending on the amount of events available to the statistical model. More
+importantly, isolation ability also declines depending on how well the used
+events within categories matched on average the preferred stimulus type.
+
+\paragraph{shortcomings: mixed events in AO categories}
+% mixed categories
+especially \texttt{se\_new} and \text{se\_old} (esp. in contrast 6-8) is often
+mixed
+% examples
+e.g. "ein Arzt", "ein alter Film", "auf einer Straße", "im Fernsehen", "die drei
+Jungs", "die zwei im Bett", "Jenny als Teenager", "Forrest vor einem Buffet",
+"Kennedy", "Jenny kommt aus dem Wohnwagen ihrer Großmutter";
+% hierarchical structure of annotation
+Switches from one setting to another offered the least amount of events in both
+stimuli. In the AO stimulus, this category shares events with nouns from other
+categories that served to cue the listener about a change of the setting ->
+words belong to more than one category but high-level category was used
+% soundscape
+Moreover, a change of the soundscape preceding the narrator's speech could also
+cue listeners about a change of the spatial environment\todo{check contrasts
+that use cuts across scenes but in the AO stimulus}
+% conclusion
+Hence, we assumed smaller probability of successfully isolating the PPA.
+% concluding statement
+In summary, the results of the additional contrasts suggest that increased
+activation within the PPA is not just an accidental finding. Nevertheless, the
+ability to isolate the PPA drops the less the amount of data are available and
+the less the events averaged to built a category match the preferred stimulus
+type processed in the PPA.
+% hypothesis
+Further, we hypothesize that not just semantic information but also the mere
+changes of a soundscape that cues a listener about a setting's spatial layout of
+could correlate with increased activity in the PPA
+% crinkling
+\todo[inline]{cf. arnott2008crinkling which find increased activations of PPA
+to sound made by objects}
 
@@
 
-\todo[inline]{here, A LOT could be discussed; possibilities: individual
-    ``preference'' to pay attention to spatial infos (which contradicts
-    statement above that attention is not a prerequisite; different level of
-    alterness during paradigms; different ``capability'' to process auditory
-spatial information (maybe correlating in behavior differences in navigational
-tas in navigational tasks}
+\todo[inline]{individual ``preference'' to pay attention to spatial infos (which
+contradicts statement above that attention is not a prerequisite}
+
+\todo[inline]{different level of alterness during paradigms}
+
+\todo[inline]{different ``capability'' to process auditory spatial information}
+
+\todo[inline]{individual differences: different contrasts should be used and
+then the best used for individual rois}
 
@@
 % one threshold for all
-Contrary to Sengupta et al. (2016), results were not archieved by visually
+Contrary to Sengupta et al. (2016), results were not archived by visually
 expecting unthresholded $z$-maps and choosing a subjectively best fitting
-threshold for each subjectiwere archieved but by using the same $Z$-value and
+threshold for each subject were archived but by using the same $Z$-value and
 significance threshold for all subjects.
@@
 
+\todo[inline]{shortcoming to task to attend to spatial information}
+
 \subsubsection{AV stimulus}
 % intro
-On individual level, mixed results for AV stimulus.
-\todo[inline]{which contrast works better in which subjects?}
-Individual differences when seeing a whole picture with many features vs.
-serialc auditory stream of information providing incidential cues; spatial attention?
+On individual level, mixed results for AV stimulus.  \todo[inline]{which
+contrast works better in which subjects?} Individual differences when seeing a
+whole picture with many features vs. serial auditory stream of information
+providing incidental cues; spatial attention?
 
@@
 
-\subsection{stability of contrasts}
-% why we did a couple of contrasts
-it's not cherry picking of one contrast.
-% declining quality of results
-contrasts were assumed to be of ``declining'' quality of results which turned
-out to be the case.
-% decreasing congruency and amount of data
-results are kinda stable and not just an accidental finding. Nevertheless,
-performance of functional isolation is sensitive to amount of data used and
-congruency of contrasts with spatial layout hypothesis.
-
-% spatial cues can belong to different indcategories
-resembling cuts to different scene in the movie by using ``similar'' cues in the
-audio-description did not work well; words are processes ``literally'' and not
-``wholistically'' or put in a wider ``context'' (but Aminoff?)
+\subsection{anterior vs posterior PPA}
+% connectivity
+Aminoff et al. (2013) regarding Baldassano (2013): There is some evidence from
+a human neuroimaging study examining functional connectivity of differences
+between anterior and posterior regions of the PHC that the anterior regions are
+more functionally connected to retrosplenial complex (RSC) and parietal
+cortices, whereas the posterior regions are more functionally connected to
+visual processing regions.
+
+% Baldassano (2013). Differential connectivity with Parahippocampal Place Area
+Baldassano (2013).  We utilize a functional connectivity measure for fMRI that
+can estimate connectivity differences at the voxel level. We provide the first
+direct evidence that anterior and posterior PPA exhibit distinct connectivity
+patterns, with anterior PPA more strongly connected to regions in the default
+mode network (including the parieto-medial temporal pathway) and posterior PPA
+more strongly connected to occipital visual regions. We show that object
+sensitivity in PPA also has an anterior–posterior gradient, with stronger
+responses to abstract objects in posterior PPA. These findings cast doubt on the
+traditional view of PPA as a single coherent region, and suggest that PPA is
+composed of one subregion specialized for the processing of low-level visual
+features and object shape, and a separate subregion more involved in memory and
+scene context.
+% Review in Baldassano
+In the last several years, a number of researchers have suggested that PPA could
+have multiple functional components. Differences in spatial frequency response
+(Rajimehr et al., 2011), varying deficits resulting from PPA lesions (Epstein,
+2008), PPA's overlap with multiple visual field maps (Arcaro et al., 2009), and
+a clustering meta-analysis (Sewards, 2011) all hint at the possibility that PPA
+may be comprised of at least two functionally distinct subunits along its
+posterior–anterior axis. However, studies explicitly searching for a dis-
+tinction between posterior and anterior PPA have failed to identify major
+differences (Cant and Xu, 2012; Epstein and Morgan, 2012).
+% anatomical studies in monkeys reviewed in Baldassano
+In short, these macaque parahippocampal regions exhibit an anterior–posterior
+gradient, with the anterior side most related to RSC and cIPL and the posterior
+side most related to ventral visual areas.
+% from Baldassano discussion
+Our results demonstrate that human PPA exhibits a gradient in con- nectivity
+along the anterior–posterior axis analogous to the gradient in connectivity
+along macaque TH/TF/TFO. This connectivity gradient was also paired with a
+functional gradient of sensitivity to scene and abstract object stimuli. These
+results present a challenge to current models of PPA function which assume that
+PPA is functionally homogeneous, and demonstrate that anterior and posterior PPA
+connect differentially to two distinct cortical networks.
+% but not independent
+Note that, although our data suggest that PPA might contain identifiable
+subregions, these subregions should not be considered as completely independent
+modules. Both subregions activate selectively to scenes, and the parahippocampal
+region (at least in macaques) is densely self-connected (Suzuki, 2009), implying
+that these subregions cooperate to build a complete representation of a scene.
+Their distinct connectivity properties, however, do suggest that each may be
+involved in specific aspects of visual and cognitive processing involved in the
+overarching goal of scene understanding. We discuss some possibilities for the
+functional roles of the subregions below.
+% posterior PPA
+Posterior PPA shows a stronger response to abstract objects than anterior PPA,
+and is more strongly connected to all of occipital visual cortex, including LOC
+and TOS. These regions have well-defined retinotopic maps (Arcaro et al., 2009;
+Nasr et al., 2011), and are associated with the perception of low-level visual
+features and object shape. Previous work has hinted that posterior PPA is more
+responsive to both simple visual textures and objects; Arcaro et al.  (2009)
+found that a posterior portion of PPA responded about four times as strongly to
+a flickering checker- board stimulus compared to an anterior portion, and that
+the response to objects was greater than the response to scrambled images only
+in the posterior portion. In other words, posterior PPA may be more visually
+responsive than anterior PPA.
+% LLA
+Our description of posterior PPA is in fact similar to the original proposal of
+Aguirre et al. for a “lingual landmark area” (LLA), slightly posterior to PPA,
+which was “specialized for the perception of visual stimuli with orienting
+value” (Aguirre et al., 1998) and carried out bottom-up perceptual analysis to
+recognize locations or landmarks (Cant and Goodale, 2007; Epstein et al., 1999).
+Although the LLA is no longer identified as an independent region from PPA in
+current studies, it is possible that the posterior portion of PPA corresponds to
+the properties of the proposed LLA, offering an explanation for why this region
+was localized more posteriorly than the full PPA.
+% Anterior PPA
+Anterior PPA is specifically connected to RSC, cIPL, medial PFC, and the lateral
+surface of the anterior temporal lobe. In addition, this portion of PPA is less
+visually responsive to both scenes and objects, with notably low sensitivity to
+abstract object stimuli.
+% DMN
+The set of regions connected more strongly to anterior PPA is strikingly similar
+to the Default Mode Network (DMN) (Buckner et al., 2008; Fox et al., 2005;
+Raichle et al., 2001), which is known to include the parahippocampal region. The
+only portions of the DMN that do not show differential connectivity to anterior
+PPA in our data are the rostral portion of the posterior cingulate cortex (PCC)
+and the superior frontal cortex.
+% PPA and DMN
+Although the DMN has been implicated in a large number of internally-focused
+tasks, one of its key roles involves autobiographical memory (Buckner et al.,
+2008). Models of recognition memory have previously identified parahippocampal
+cortex as primarily encoding spatial context information (Eichenbaum et al.,
+2007), and data from Aminoff et al. (2007) has suggested that an anterior
+portion of PPA may be involved in recall based on spatial context. Our results
+are con- sistent with anterior PPA playing a more central role in memory than
+posterior PPA, given anterior PPA's connectivity with the DMN.
 %
-setting\_new ist häufig vermischt mit anderer Kategorie "ein Arzt", "ein alter
-Film", "auf einer Straße", "im Fernsehen", "die drei Jungs", "die zwei im Bett",
-"Jenny als Teenager", "Forrest vor einem Buffet", "Kennedy", "Jenny kommt aus
-dem Wohnwagen ihrer Großmutter"
-
-% soundsscapes makes change of setting obvious before narrator kicks in
-Soundscape macht es häufiger bereits vorher klar, dass Settingwechsel ist bzw.
-nicht erst das annotiere Substantiv object und (room)geo ist vermischt
-Retrospelinal Cortex ist in Probabilistic maps krasser als PPA.
-
-% se_new and se_old
-especially relevant for contrasts 6-8: words belonging to the categories
-\texttt{se\_new} and \texttt{se\_old} were very vague in describing a scene
-compared to the richness of a picture. Hence, we assumed smaller probability of
-successfully isolating the PPA.
+PPA is known to represent global scene properties such as spatial expanse
+(Kravitz et al., 2011a; Park et al., 2011), and to construct global scene
+representations which are not predictable from responses to signature objects
+(MacEvoy and Epstein, 2011). Anterior PPA's connectivity to cIPL and RSC, along
+with its lower sensitivity to abstract objects, suggest that it may be more
+concerned with these types of spatial and non-object-based scene properties than
+posterior PPA. Future research contrasting global and object-based properties of
+scenes, however, would be necessary to test such a hypothesis.
+%
+The fact that anterior PPA had a lower sensitivity to our abstract object
+stimuli does not necessarily imply that this region does not use object
+information. Previous work has shown that PPA responds to objects that have
+spatial associations (Aminoff et al., 2007), are space-defining (Mullally and
+Maguire, 2011), and are navigationally-relevant (Janzen and Van Turennout,
+2004). These types of responses require spatial memory and cannot be based
+purely on visual features like object shape. If anterior PPA is involved in
+processing spatial context, then space-defining or navigationally-relevant
+objects could activate anterior PPA more strongly than our abstract objects,
+which were unfamiliar and provided no sense of context or orientation. Further
+experiments will be required to determine what type of object-related
+information is used in this region.
+% summary
+Unraveling the functions of the PPA has proven to be a challenging problem,
+given the region's involvement in a variety of scene perception and navigation
+tasks (Epstein, 2008). Our results imply that a complete model of PPA's
+functional properties must account for the differences in connectivity and
+function between anterior and posterior PPA. Although the precise roles of PPA's
+subregions are yet to be determined, our results and previous work suggest that
+posterior PPA is concerned primarily with perception of low-level visual
+features and object shape, while anterior PPA is involved in memory and global
+contextual processing.
+
+% contextual associations in anterior vs. posterior
+Aminoff et al. (2013): We propose that the general function of the PHC can be
+thought of as processing of contextual associations. A subregion of the
+posterior PHC is particularly optimized to process spatially organized
+contextual associations, whereas more anterior regions of the PHC are optimized
+to process contextual associations in other, non-spatial domains.
+% posterior PPA for visual visual associative information
+Spatial contextual associations are a dominant property of places and scenes,
+and thus scenes consistently activate this posterior subregion of the PHC (e.g.,
+PPA; Epstein, 1998). We of course do not argue that the PHC is not sensitive to
+spaces, places, and spatial information, but rather that it is sensitive to
+spatial stimuli because of the associative information (space-related
+associations) that such stimuli evoke.
+
+% Aminoff regarding contextual processing in the PHC and beyond
+Aminoff et al. (2013). It was critical to compare contextual processing of
+objects that are strongly related to a specific place (e.g., an oven is found in
+a kitchen) with contextual processing of objects that are highly associated with
+a context but not a specific place (e.g., a birthday cake is found at a birthday
+party, but the party can take place anywhere, at home, in a restaurant, at a
+park).  Activity elicited by these two types of contextual objects was compared
+with the activity elicited for objects that were only weakly associated with
+many contexts (e.g., a lamp). Differential activity was found in the PHC and the
+RSC, replicating the previous findings (Bar \& Aminoff, 2003, The
+parahippocampal\dots). Activity within the PHC, however, was distributed along
+an anterior–posterior axis, with activity related to spatial contexts focused in
+the posterior part of the PHC and activity evoked by non-spatial contexts
+focused in the more anterior part of the PHC (Bar \& Aminoff (2003) Cortical
+analysis of visual context; Aminoff et al. (2007) The parahippocampal cortex
+mediates spatial and nonspatial associations).
+
+\paragraph{contextual associations?}
+
+\todo[inline]{Aminoff discusses contextual associations in visual spatial
+processing, (episodic) memory; that could be discussed but the paradigm and
+contrasts do not provide material to say much about it other than wild
+speculations}
+
+% Aminoff (2013)
+It has been shown that the processing of strong, long-term, contextual
+associations elicits activity within the PHC, as well as the RSC (which includes
+regions of the retrosplenial cortex, extending into the posterior cingulate
+cortex, and the precuneus), the medial prefrontal cortex (MPFC), and the
+transverse occipital sulcus (TOS) (Figure 2) [2,3,59–67].
+
+\subsection{negative controls and cross-modal controls}
+
+\subsection{model-driven vs. data-driven analyses}
+Natural stimuli like movies \citep{hasson2008neurocinematics,
+sonkusare2019naturalistic} or narratives \citep{honey2012not,
+lerner2011topographic, silbert2014coupled} offer an easy to implement,
+(continuous,) complex, immersive, task-free paradigm that more closely resembles
+our natural dynamic environment than traditional experimental designs.
+
+why naturalistic stimuli are so cool: sonkusare2019, eickhoff2020, hamilton
+
+Naturalistic language processing can be approached with the analysis methods
+constructed to handle well-controlled experiments
 
@@
 of totally different, independent research questions, possibly on an individual
-level.
-
-\subsection{model-driven vs. data-driven analyses}
-Natural stimuli like movies \citep{hasson2008neurocinematics,
-sonkusare2019naturalistic} or narratives \citep{honey2012not,
-lerner2011topographic, silbert2014coupled} offer an easy to implement,
-(continuous,) complex, immersive, task-free paradigm that more closely resembles
-our natural dynamic environment than traditional experimental designs.
-
-why naturalistic stimuli are so cool: sonkusare2019, eickhoff2020, hamilton
+level; increased compliance in individual diagnostics in ``special'' populations
+where compliance is more difficult to archive (pediatric or psychiatric)
 

### 2020-10-05 paper/main.tex
restructure discussion

@@
 
-\todo[inline]{Limit for Intro + Discussion (main text) = ca. 3k words;
+\todo[inline]{Limit for main text (intro and discussion) = ca. 3k words;
 intro is about 1k words (with to dos)}
@@
 level-dependent functional magnetic resonance imaging (BOLD fMRI) to map
-perceptual and cognitive brain processes (e.g. viewing of landscapes,
-\citep{epstein1998ppa}; or theory of mind \citep{spunt2014validating}) to
+perceptual and cognitive brain processes (e.g. viewing of faces
+\citep{kanwisher1997ffa} or theory of mind \citep{spunt2014validating}) to
 functional brain areas or networks.
@@
 The PPA is located in the posterior parahippocampal gyrus including adjacent
-regions of the fusiform gyrus \cite{epstein1998ppa} and anterior lingual gyrus
-\citep{epstein2008parahippocampal}.
+regions of the fusiform gyrus and anterior lingual gyrus
+\citep{ epstein2008parahippocampal}.
 % neural correlate of scene perception
 Increased hemodynamic activity in the PPA correlates with the perception of
-static pictures of landscapes or landmarks compared to pictures of tools or
-faces.
+static pictures of landscapes, buildings or landmarks \citep{aguirre1998area, epstein2014neural, epstein1998ppa} compared to e.g. pictures of tools of faces.
 % spatial layout hypothesis
-According to the spatial layout hypothesis, the PPA is involved in processing
+[[According to the spatial layout hypothesis, the PPA is involved in processing
 the surface geometry of a visual stimulus and possibly in identifying scenes
-based on their spatial layout \citep{epstein2010reliable}.
+based on their spatial layout \citep{epstein2010reliable}.]]\todo{better delete}
 % literature review overview 1: imagination & haptic exploration
@@
 % O'Craven: Mental imagery
-In the study conducted by \citep{ocraven2000mental} participants viewed
+In the study conducted by \cite{ocraven2000mental} participants viewed
 alternating blocks of pictures showing famous faces and familiar places during
@@
 % Wolbers: haptic exploration
-In the block design study conducted by \citep{wolbers2011modality} the PPA of
+In the block design study conducted by \cite{wolbers2011modality} the PPA of
 sighted participants showed increased activation during a delayed
@@
 (Figure 2B; Table S2)''}
+
+\todo[inline]{following phrasing might be strange but necessary to delineate
+from Huth (2016); good voxel-wise semantic modeling regarding places in PPA but
+imo that does not say anything about excitation/inhibition; interestingly Huth
+mentions PPA during talks but it is not discussed in any paper and despite being
+promised none of his group came up with a paper regarding that topic}
 % Aziz (2008): place related sentences
-\todo[inline]{lass uns kurz im Gespräch über Aziz Paper gucken; die relvanten
-Abschnitte sind in der PDF markiert. Ihre Method Section ist ``strange'' und im
-Grunde kommt überall nur uneinheitliche Grütze heraus; ich blicke nicht durch,
-weshalb folgendes nicht vollständig korrekt sein wird;so wie ich es verstanden
-habe, hat sie den Unterschied zwischen PPA und FFA angeguckt, aber diesen
-Unterschied im Kontrast zu object-related Sentences (dortige Fig 3)}
+To our knowledge only one study \citep{aziz2008modulation} investigated how
+hemodynamic activity in the PPA differs between stimulus features of spoken
+language.
 % Aziz' stimuli
-To our knowledge only one study \citep{aziz2008modulation} correlated
-hemodynamic activity of the PPA with spoken sentences. Sentences described
-generic or famous places (e.g. ``The Taj Mahal faces a long thin reflecting
-pool''), faces  (``Marilyn Monroe has a large square jaw''), or objects (``The
-television has a long antenna'').
+\cite{aziz2008modulation} used sentences that described generic or famous places
+(e.g. ``The Taj Mahal faces a long thin reflecting pool''), faces  (``Marilyn
+Monroe has a large square jaw''), or objects (``The television has a long
+antenna'').
 % Aziz' tasks
@@
 involving famous places.
+% wtf did Aziz really do?
+\todo[inline]{lass uns bitte kurz im Gespräch über Aziz Paper gucken; die
+relvanten Abschnitte sind in der PDF markiert. Ihre Method Section ist
+``strange'' und im Grunde kommt überall nur uneinheitliche Grütze heraus; ich
+blicke nicht durch, weshalb geschriebenes nicht vollständig korrekt sein wird;
+so wie ich es verstanden habe, hat sie vier 2x2 ANOVAs den Unterschied zwischen
+PPA und FFA angeguckt, aber diesen Unterschied im Kontrast zu object-related
+Sentences (dortige Fig 3)}
 
@@
 functions at an individual level, a prerequisite for the application of brain
-imaging methods in individual diagnostics (cf. \citep{dubois2016building,
+imaging methods in individual diagnostics (cf. \cite{dubois2016building,
 eickhoff2020towards}).
@@
 group results a driven by individuals subjects especially in response to
-audio-only stimulation\todo{``audio-only'' sounds meh; ``exclusively auditory
-stimulation''?}.
-% Huth (2016)
-\todo[inline]{Huth et al. (2016) implicitly regarding audio-only; but they do
-not discuss the PPA; in general, they do voxel-wise encoding which doesn't say
-anything about excitation/inhibition}
+audio-only stimulation\todo{``audio-only'' sounds meh?}.
 
@@
 \citep{honey2012not, lerner2011topographic, silbert2014coupled} offer complex,
-continuous stimulation that better resemble our experience of a our dynamic
+continuous stimulation that better resemble the experience of our dynamic
 environment.
@@
 % Bartels (2004): Film + GLM (but surprisingly did not annotate landscapes)
-\citep{bartels2004mapping} manually annotated time points that depict faces and
+\cite{bartels2004mapping} manually annotated time points that depict faces and
 human bodies in a 22 minute clip of the movie \textit{Tomorrow Never Dies}
@@
 % Hasson (2004): Film + (reverse) ISC
-Employing a reverse intersubject correlation, \citep{hasson2004intersubject}
-used a 30 minute clip of the movie \textit{The Good, the Bad, and the Ugly}
+Employing a reverse intersubject correlation, \cite{hasson2004intersubject} used
+a 30 minute clip of the movie \textit{The Good, the Bad, and the Ugly}
 \citep{goodbadugly}.
@@
 Nevertheless, both studies used an audio-visual stimulus and again do not
-address the question how the investigated functional areas respond an audio-only
-stimulus.
+address the question how the investigated functional areas respond during an
+audio-only stimulus.
 
@@
 Encouraged by \citep{aziz2008modulation}, we focus on the audio-description as
-an audio-only paradigm and test its localization performance of a ``visual
-area'' in individual study participants.
-% comparison to dedicated localizer
-Finally, we compare these results to results of a dedicated visual localizer
-experiment done with the same participants \citep{sengupta2016extension}.
-
-\todo[inline]{maybe insert ``foreshadowing'' of results here?}
-\todo[inline]{Bzgl.
-Open Source der Ergebnisse/Skripte: Dazu habe ich hier nichts geschrieben, weil ich nur weiß, das der Code veröffentlicht werden soll.
-Du hast die Vision diesbezüglich im Kopf und entsprechend auch kanonisch-prägnante Formulierungen und wo die am besten wie hinkommen}
+an audio-only paradigm. We further test the audio-description's localization
+performance of a ``visual area'' in individual study participants by comparing
+our results to results of a dedicated visual localizer experiment done with the
+same participants \citep{sengupta2016extension}.
+% results
+Our results demonstrate that (a), (b), (c)... \todo{similar to abstract and
+conclusion}
+
+\todo[inline]{Bzgl. Open Source der Ergebnisse/Skripte: Dazu habe ich hier
+nichts geschrieben; probably something like ``all raw data, scripts, and
+results are available under xy as datalad/BIDS dataset''}
 
@@
 citation (see Data Records and Data Citations, below)}
-\todo[inline]{explain as introduction to every step why it woes done}
 \todo[inline]{current order of subsections might be ``non-canonical''}
-\todo[inline]{parts from original studies might still be too detailed}
+\todo[inline]{parts from original studies probably too detailed}
 
@@
 stimulation setup, and fMRI acquisition can be found in the corresponding
-publications. Following is a summary of most important aspects.
+publications. Following is a summary of the most important aspects.
 
@@
 German audio-description \citep{ForrestGumpGermanAD} of the movie ``Forrest
-Gump'' \citep{ForrestGumpMovie} as an additional audio track for visually
-impaired listeners on Swiss public television.
+Gump'' \citep{ForrestGumpMovie}.
 % AV study
@@
 We used the German DVD release \citep{ForrestGumpDVD} of the audio-visual movie
-``Forrest Gump'' \citep{ForrestGumpMovie} and its temporally aligned
-audio-description that was broadcast as an additional audio track for visually
-impaired listeners on Swiss public television \citep{ForrestGumpGermanAD}.
+``Forrest Gump'' \citep{ForrestGumpMovie} and its audio-description that was
+broadcast as an additional audio track for visually impaired listeners on Swiss
+public television \citep{ForrestGumpGermanAD}.
 % AV: voice-over
@@
 Each stimulus was split into eight segments of approximately 15 minutes. Except
-for the first movie segment, each segment started with a snippet of at least six
+for the first segment, each segment started with a snippet of at least six
 seconds immediately preceding the movie scene boundary used to split the
@@
 \subsection{Naturalistic stimuli annotation}
-%todo
-% stimuli were not designed for research purposes
-Both natural stimuli were originally designed to entertain an audience and to
-capture attention free from any perceptual or behavioral task.
+% todo stimuli were not designed for research purposes
+Both natural stimuli were originally designed to entertain their audiences and
+to capture attention free from any perceptual or behavioral task.
 % AO annotation
-For the analysis of the AO data, we extended an publicly available annotation of
-speech \citep{haeusler2020speechanno} by further annotating words spoken by the
-audio-description's narrator.
+Thus for the analysis of the AO data, we extended an publicly available
+annotation of speech \citep{haeusler2020speechanno} by further annotating words
+spoken by the audio-description's narrator.
 % annotation procedure
@@
 describe the movie's missing visual content.
-% why and how of categories 1
-Some categories were created in such a way to reflect the six stimulus
-categories used in the visual localizer experiment.
-% why and how of categories 2
-Some additional categories were created to semantically cluster nouns into
-categories ``that were obvious to make sense''.\todo{yeah, well, sounds shit but
-that's basically it}
 % categories in detail
@@
 inherent objects (\texttt{object}, \texttt{furniture}).
+% why and how of categories 1
+Some categories were created to reflect the six stimulus categories used in the
+visual localizer experiment (e.g. \texttt{geo}, \texttt{object}).
+% why and how of categories 2
+Other categories were created to semantically cluster some remaining nouns into
+additional categories (e.g. \texttt{fname}, \texttt{furniture})
 % problem with hierarchical categories
-\todo[inline]{put stuff regarding hierarchical categories and heterogeneity
-here; counts in table show the counts of just the primary category; settings
-changes often (30-60 \%) belong to another category; most often it's geo but
-also object or male/mname/furniture; cf. Results and Discussion regarding
-stability of contrasts}
+Notably, the categories \texttt{setting\_new} and \texttt{setting\_rec}
+comprise not just words that describe an abstract location (e.g. ``in
+Greenbow'') or a setting as whole (e.g. ``the platoon wades through a rice
+field'', ``in a disco''). They also comprise words that could count as a member
+of another categories in case the narrator uses these words to indicate a switch
+from one setting to another (e.g. ``near an old bus'').
 % reference to table with rules and examples
 A complete overview of all 19 categories, the rule for a word to belong to a
-category, and examples can be seen in \ref{tab:descr-nouns-rules}.
+category, and examples can be seen in Table \ref{tab:descr-nouns-rules}.
 % procedure
@@
 annotation of movie cuts and depicted locations \citep{haeusler2016cutanno}.
-In/for the movie, We annotated different kinds of cinematographic cuts
-\citep{haeusler2016cutanno} as presumably ``spatially relevant'' events.
 % rationale behind using movie cuts
 Our rationale was that cuts are ``spatially relevant'' events that re-orient the
-viewer in the depicted environment independent from the exact visual content in
-the movie frame following the cut.
+viewer within the environment depicted in the movie.
 
@@
 persons & concrete persons of unknown sex & hippies, patients \tabularnewline
-setting\_new & noun cueing a new setting &  on a ``bridge'', on an ``alley'', on ``campus'' \tabularnewline
+setting\_new & noun cueing an unfamiliar setting &  on a ``bridge'', on an ``alley'', on ``campus'' \tabularnewline
 setting\_rec & noun cueing a recurring setting & at the ``bus stop'' \tabularnewline
@@
 % questionnaire
-In all three studies, participants filled out a questionnaire on their basic
-demographic information and familiarity with the movie.
+Participants filled out a questionnaire on their basic demographic information
+and familiarity with the movie.
 % AO & AV: instructions
@@
 purpose to illuminate a participant's visual field in order to prevent premature
-fatigue. [The screen contained a solid black ``fixation'' dot that faded in and
-out at the beginning and end of a movie segment.]
+fatigue.
 
@@
 transmission reduced to \unit[13.7]{\%} with a gray filter) connected to the
-stimulus computer [via a DVI extender system (Gefen EXT-DVI-142DLN with
-EXT-DVI-FM1000)].
+stimulus computer.
 % screen size
@@
 resolution, \unit[224]{mm} field-of-view, anterior-to-posterior phase encoding
-direction) with a 10 percent inter-slice gap were recorded in ascending order.
-Slices were oriented to include the ventral the ventral portions of frontal and
+direction) with a \unit[10]{\%} inter-slice gap were recorded in ascending
+order.  Slices were oriented to include the ventral portions of frontal and
 occipital cortex while minimizing intersection with the eyeballs. The field of
@@
 MRI scanner equipped with a 32 channel head coil acquired T2*-weighted
-echo-planar images (gradient-echo, \unit[2]{s} repetition time (TR),
+echo-planar images (gradient-echo, \unit[2]{s} repetition time,
 \unit[30]{ms} echo time, \unit[90]{$^{\circ}$} flip angle, \unit[1943]{Hz/Px}
@@
 
-Similar to the reviewed studies employing simplified stimuli, we conducted a
-standard two-level general linear model (GLM) analysis to create
+Similarly to the reviewed studies that employed simplified stimuli, we conducted
+a standard two-level general linear model (GLM) analysis to create
 subject-specific results ($Z$-maps) across the 8 segments for every subject. A
@@
 For the AV stimulus, we created regressors correlating with movie cuts provided
-by a previously published annotation \citep{haeusler2016cutanno}.
+by another previously published annotation \citep{haeusler2016cutanno}.
 % https://github.com/psychoinformatics-de/studyforrest-data-annotations/blob/master/code/researchcut2segments.py}
@@
 % AO events
-To create regressors for the AV analysis, we used all of the original 19
-categories of descriptive nouns except \texttt{++}.
+To create regressors for the AO analysis, we used all of the original 19
+categories of descriptive nouns except ``\texttt{++}'' (i.e. cues regarding
+time).
 % pooling
 Some categories that were similar but offered only a small amount of counts were
-pooled resulting in eleven new categories (see Table \ref{tab:ao-events}) that
-served as experimental conditions.
+pooled resulting in eleven new categories that served as experimental conditions
+(see Table \ref{tab:ao-events}).
 % setting beats other category
-Events that fell into one of the two setting-related category but also into
-another category were treated as belonging to the setting-related category
-(\texttt{se\_new} or \texttt{se\_old}).
+Events that fell into one of the two setting-related categories
+(\texttt{se\_new} or \texttt{se\_old}) but also into another category were
+treated as belonging to the setting-related category (e.g. ``near an old bus'').
 % modeling as boxcar function
@@
 If a segment did not contain an event of a category, a null regressor was chosen
-for that category in that segment.\todo{wenn ich "null regressor" nehme, darf ich den ganzen
-Run, glaube ich, in der 2nd level Analyse gar nicht benutzen? Hatte, glaube ich,
-Jeanette Mumford in einem ihren Videos mal gesagt}
+for that category in that segment.\todo{wenn ich "null regressor" nehme, darf
+ich den ganzen Run, glaube ich, in der 2nd level Analyse gar nicht benutzen?
+Hatte, glaube ich, Jeanette Mumford in einem ihren Videos mal gesagt}
 % categories taken from movie cut annotation
@@
 object & inanimate entities with firm boundaries & \aoObjAll & \aoObjI & \aoObjII & \aoObjIII & \aoObjIV & \aoObjV & \aoObjVI & \aoObjVII & \aoObjVIII \tabularnewline
-se\_new & first-time mentioned setting & \aoSenewAll & \aoSenewI & \aoSenewII & \aoSenewIII & \aoSenewIV & \aoSenewV & \aoSenewVI & \aoSenewVII & \aoSenewVIII \tabularnewline
-se\_old & recurring setting & \aoSeoldAll & \aoSeoldI & \aoSeoldII & \aoSeoldIII & \aoSeoldIV & \aoSeoldV & \aoSeoldVI & \aoSeoldVII & \aoSeoldVIII \tabularnewline
+se\_new & noun cueing an unfamiliar setting & \aoSenewAll & \aoSenewI & \aoSenewII & \aoSenewIII & \aoSenewIV & \aoSenewV & \aoSenewVI & \aoSenewVII & \aoSenewVIII \tabularnewline
+se\_old & noun cueing a recurring setting & \aoSeoldAll & \aoSeoldI & \aoSeoldII & \aoSeoldIII & \aoSeoldIV & \aoSeoldV & \aoSeoldVI & \aoSeoldVII & \aoSeoldVIII \tabularnewline
 sex\_f & female person(s), name & \aoSexfAll & \aoSexfI & \aoSexfII & \aoSexfIII & \aoSexfIV & \aoSexfV & \aoSexfVI & \aoSexfVII & \aoSexfVIII \tabularnewline
@@
 (s. \ref{fig:reg-corr}) which suggest the models should not suffer from low
-detection power due to shared variance among regressors.
+detection power due to shared variance among regressors.\todo{sounds meh but
+don't know how do write it better}
 
@@
 
-\todo[inline]{Why done this way? Why is no. 1 the one? Event count,
-se\_new and se\_old only vaguely describe the scene; narrator is often
-lacking behind dialogue and change in soundscape}
-
-\todo[inline]{contrasts are ordered by ``how well they make sense'' according to
-    theory, and amount of events/data; Hence, they were assumed to result in
-    more and more shitty results (s. introductory sentence in results); at the
-    moment all 8 contrasts are used in the result (figure) despite the low
-ranked COPEs yielded 0 result as kinda expected}
+\todo[inline]{send me to hell for the following paragraphs but it is detailed at
+least}
+
+% we did a couple of contrasts and why
+We created eight $t$-contrasts for the AO stimulus (see Table
+\ref{tab:ao-contrasts}) and five $t$-contrasts for the AV stimulus (see Table
+\ref{tab:av-contrasts}) to test the stability of results across different
+contrasts and exclude accidental findings.
+% contrasts are of different quality
+We assumed all contrasts could in principle isolate the PPA. Nevertheless, we
+also assumed contrasts would differ in their isolation performance because they
+differ in how well the included event categories reflect on average the
+preferred stimulus type processed in the PPA.
+%
+Thus for each stimulus, we chose one ``primary contrast'' for a detailed report
+and discussion of the group-level and subject-specific results. Primary
+contrasts were chosen based on how well the used categories on average were
+assumed to match the preferred stimulus type in balance with the amount of
+available data / events.
 
 % intro
-For the AO stimulus, we created eight $t$-contrasts presumably correlating with
-increased hemodynamic activity in the PPA by contrasting different kind of
-descriptive nouns.
+In context of the AO stimulus, the categories \texttt{se\_new} and
+\texttt{se\_old} were problematic for a couple of reasons and thus are not
+included in the primary contrast:
+% sparse auditory, rich visually
+(a) they often only vaguely describe a scene (e.g. ``black and white film
+recordings'', ``in Greenbow'') whereas a picture of the verbally described scene
+would be perceptually richer,
+% hierarchical categories
+(b) They also comprise words that could count as a member of another categories
+in case the narrator uses these words to indicate a switch from one setting to
+another (e.g. ``Jenny as teenager'', ``near and old bus'')
+% soundscapes forestalls narrator
+(c) the narrator is often lacking behind a short dialogue or a change of the
+soundscape that already cue a change of settings.\todo{cf. contrast that uses
+cuts but in AO stimulus}
+% conclusion
+Hence, we assumed contrasts that (exclusively) used these two categories would
+induce noise and would be less successful in isolating the PPA.
+
 % furniture
-We did not use the category ``furniture'' (\texttt{furn}) as a regressor in one
-of the contrasts of interest because nouns in this category could either be
-considered as object or as a geometry-defining structure of a room.
-\todo[inline]{but: Epstein (2008): response to arrays of objects drawn from the
-rooms but displayed on a blank background is quite weak [11].}
+We did not use the category ``furniture'' (\texttt{furn}) as a
+regressor of interest in any contrasts because nouns in this category were
+usually big and heavy. In a serial stream of auditory information, participants
+could perceive furniture-related nouns as either a geometry-defining local scene
+element or as an isolated object. Hence we did not use this category as
+regressor of interest to reduce noise.
+
 % negative control contrasts
-Five $t$-contrasts (see Table \ref{tab:ao-contrasts}) we created for negative
-control purposes to test if increased activation in the PPA was correlated with
-moments of cuts and therefore correlated with a possibly accompanying change in
-the soundscape (anticipating the narrator's cue of a switch to new setting,
-too).
+Five $t$-contrasts (see Table \ref{tab:ao-contrasts}) we created as negative
+controls to test if increased activation in the PPA was correlated with
+moments of cuts and therefore possibly correlated with a accompanying change in
+the soundscape.\todo{cf. contrast that uses cuts but in AO stimulus}
 
 \begin{table*}[t]
-    \caption{Contrasts of parameter estimates for the analysis of
-        the audio-only stimulus (AO).
-\texttt{all non-geo} = body, bodypart, fahead, object, sex\_f, sex\_m.
-Contrast 1-8 aim to isolate the PPA.
-Contrasts 9-13 serve as negative control at the moments of movie cuts
-with possible changes of the audio tracks soundscape (see Table
-\ref{tab:av-contrasts}).}
+\caption{Contrasts of parameter estimates for the analysis of the audio-only stimulus (AO).
+Contrast 1-8 aim to isolate the PPA (\texttt{all non-geo} = body, bodypart,
+    fahead, object, sex\_f, sex\_m).
+Contrasts 9-13 serve as negative control at the moments of movie cuts that could
+    correlate with changes of the audio tracks soundscape (see Table \ref{tab:av-contrasts}).}
 
@@
 
-\todo[inline]{Why done this way? Why is no. 1 the one?}
+\todo[inline]{I think it's better to explain the rationale of the regressors
+here in the context of the contrasts and not already above in the list of
+created regressors}
+
 % intro
-For the AV stimulus, we created five $t$-contrasts presumably correlating with
-increased hemodynamic activity in the PPA by contrasting different kind of cuts.
-% no control for frames content
-Notably, this was done without an annotation of the visual content depicted in
-the frame after each cut and thus without statistically controlling confounding
-variables.
+In context of the AV stimulus, we categorized the frames following a movie cut
+irrespective of their concrete visual content and thus without controlling
+confounding variables (e.g. presence of faces). The rationale that this
+procedure would still be able to isolate the PPA was twofold.
 % cinematographic rationale cut to new scenes: establishing shots
@@
 % neuroscientific rationale
-The neuroscientific rationale was simply that activity in the PPA is
-greater when participants view novel versus repeated scenes or view-points.
+The neuroscientific rationale was simply that activity in the PPA is greater
+when participants view novel versus repeated scenes or view-points.
 \citep{epstein1999parahippocampal}.
@@
 \begin{table*}[t]
-    \caption{Contrasts of parameter estimates for the analysis of the audio-visual movie (AV).}
+    \caption{Contrasts of parameter estimates for the analysis of the audio-visual movie (AV).
+Contrast 1-5 aim to isolate the PPA.
+    Contrast 6-9 serve as negative control.
+    Contrast 10 serves as control for moments when the narrator cues the
+    listener about a switch of settings, events that could be correlated with a
+    switch of the soundscape.}
 \label{tab:av-contrasts}
@@
 We used annotations of a \unit[2]{h} movie and it's temporally aligned
-audio-description to create conventional GLM contrasts of of modeled
-hemodynamic activity resembling analyses of previous studies using simplified
-stimuli.
+audio-description to create canonical GLM contrasts of modeled hemodynamic
+activity resembling analyses of previous studies using simplified stimuli.
 % comparison AO & AV
@@
 
+\todo[inline]{the big question: where to put the ``stability of contrasts''? any
+position in the results has pro's and con's; at the moment they come last}
+
 \subsection{primary contrasts}
 
-\todo[inline]{paragraphs start with a sentence or two that set up the question
-that the paragraph answers; e.g. ``To verify that there are no artifacts; What
-is the test-retest reliability of our measure?''}
-\todo[inline]{middle of the paragraph presents data and logic that pertain the question}
-\todo[inline]{paragraph ends with a sentence that answers the question via logical statement; for example, it may conclude that none of potential     artifacts were detected.
-Each paragraph convinces the reader of answer given
-in its last sentence}
-
-\todo[inline]{at the moment I think it is better to report the primary contrast
-fist and then report the stability of contrast; but that opinion changed twice
-already.}
-
-\todo[inline]{concluding statement for each paragraphs?}
+\todo[inline]{paragraphs start with 1-2 sentences that set up the question
+that the paragraph answers; e.g. ``To verify that there are no artifacts''}
+
+\todo[inline]{middle of paragraph presents data and logic that pertain the
+question}
+
+\todo[inline]{paragraph ends with a concluding / logical statement}
 
 % the contrast in detail
-The primary $t$-contrast for the audio-description comparing geometry-related
-nouns to non geometry-related nouns spoken by the narrator (\texttt{geo, groom >
-all non-geo} yielded six significant clusters (see Table
-\ref{tab:res-ao-group1}, Figure \ref{fig:group-slices}).
+The primary $t$-contrast for the audio-description (\texttt{geo, groom > all
+non-geo}) that we used to isolate the PPA yielded six significant clusters (see
+Table \ref{tab:res-ao-group1}, Figure \ref{fig:group-slices}).
 % PPA
-Two homologous clusters are located in the anterior part of the visual localizer
-group overlap mask.
+Two homologous clusters are located in the anterior part of the PPA group
+overlap that we gained from the visual localizer experiment.
 % location
-More specifically, they are partially located in the lingual gyrus, occipital
-and temporal fusiform gyrus, and posterior parahippocampal cortex \todo{the
-    clusters are small but that's what the Harvard-Oxford Atlas suggests,
-    clusters are at borders of the areas; dunno how to report this; sound shitty
-to me}.
+More specifically, the clusters of the current analysis are at the borders of
+the posterior parahippocampal cortex, the occipital and temporal fusiform gyrus
+and lingual gyrus \todo{the clusters are small but that's what the
+Harvard-Oxford Atlas suggests, clusters are at the border of the reported areas;
+cf. location of PPA in the introduction clusters}.
 % precuneus
-Two additional clusters are located in the ventral precuneus extending into the
-retrosplenial cortex.
+Additionally , two additional clusters are located in the ventral precuneus
+extending into the retrosplenial cortex.
 % LOC
@@
 occipital cortex.
+\todo[inline]{any concluding statement here or merely report the clusters?}
 
@@
 For cross-modal comparison purposes, we also analyzed data from the audio-visual
-movie by contrasting different kinds of movie cuts independent from the frames'
-visual content after the cuts.
+movie by contrasting different kinds of movie cuts independent(ly) from the
+frames' visual content after the cuts.
 % the primary contrast
-The movie's primary $t$-contrast that compared cuts to a new setting with cuts
-to a familiar perspective (\texttt{vse\_new > vpe\_old}) yielded three
+The movie's primary $t$-contrast that compared cuts to an unfamiliar setting
+with cuts within familiar setting (\texttt{vse\_new > vpe\_old}) yielded three
 significant clusters (see Table \ref{tab:res-av-group1}, Figure
@@
 % PPA + others.
-One cluster spanning across the midline comprising parts of the intracalcarine
-and cuneal cortex, lingual gyrus and retrosplenial cortex, occipital fusiform
-gyrus and temporal fusiform gyrus, and the parahippocampal cortex of both
-hemispheres.
+One cluster spans across the midline and comprises, from posterior to anterior,
+parts of the intracalcarine and cuneal cortex, lingual gyrus and retrosplenial
+cortex, occipital fusiform gyrus and temporal fusiform gyrus, and the
+parahippocampal cortex of both hemispheres.
 % LOC
@@
 
-\todo[inline]{other reasons than localization performance? look which subjects influence the group results the most? ``multiple localizer''?}
+\todo[inline]{other reasons than localization performance?}
+
 % why individual results in the first place.
@@
 % results in both subject and group space
-Time series of all subjects were analyzed both in subject space and group space.
-% individual z-maps
-Results of the analyses that were performed in each subject's subject-space
-(unthresholded $z$-maps and thresholded $z$-maps with Z>2.3, p<.05) can be
-found in the accompanying dataset.
-% why
-For better comparison of results across participants, we show results ($z$-maps;
-Z>3.4, p<.05 cluster-corrected) of the analyses that was performed in group
-space.
+Time series of all subjects were analyzed both in group space and subject space.
+% report here in group space
+For better comparison of results across participants, we here report results
+($z$-maps; Z>3.4, p<.05 cluster-corrected) of the analyses that was performed in
+group space.
 % ref to figure
@@
 z=-11 for all subjects).
+% individual z-maps -> dataset
+Results of the analyses that were performed in each subject's subject-space
+(unthresholded $z$-maps and thresholded $z$-maps with Z>2.3, p<.05) can be found
+in the accompanying dataset.
 % results in detail voxels of significant clusters in PPA ROI (and  RSC
@@
 % PPA ROI (Sengupta et al., 2016)
-The dedicated localizer shows bilateral clusters in 12 subjects and unilateral
-right clusters in two subjects (sub-04, sub-20).
+The dedicated localizer \citep{sengupta2016extension} shows ROIs in 12 of 14
+subjects and unilateral right clusters in two subjects (sub-04, sub-20).
 % subjective threshold
-Individual ROIs were assessed by \citep{sengupta2016extension} by visually
-inspecting unthresholded $z$-maps, and setting a subjectively best fitting
-$z$-threshold to isolate a cluster in the PPA.
+Individual ROIs were assessed by visually inspecting unthresholded $z$-maps, and
+setting a subjectively best fitting $z$-threshold to isolate a ROI that matched
+the PPA.
 % AO
@@
 % subj-04
-In sub-04, two homologous clusters are apparent, where the dedicated localizer
+In sub-04, two homologous clusters are apparent, whereas the dedicated localizer
 yielded only one cluster in the right hemisphere.
@@
 % difference to dedicated localizer
-We find bilateral clusters in sub-20, in which the dedicated localizer yielded
+We find bilateral clusters in sub-20, whereas the dedicated localizer yielded
 only one cluster in the right hemisphere.
+
+\todo[inline]{concluding statements?}
 
@@
     \caption{Fixed-effects individual-level GLM results (Z>3.4, p<.05
-        cluster-corrected). The brains of the 14 subjects are aligned via
-        non-linear transformation to a study-specific T2* group template that is
-    co-registered to the MNI152 template with an affine transformation (12
-degrees of freedom) to facilitate comparisons across subjects.
-        Light gray: The audio-description's field-of-view
-        (cf. \citep{hanke2014audiomovie}).
-        Blue: the primary $t$-contrast for the audio-description comparing
-        geometry-related nouns to non geometry-related nouns spoken by the
+    cluster-corrected). To facilitate comparisons across subjects, individual
+    brains are aligned via non-linear transformation to a study-specific T2*
+    group template that is co-registered to the MNI152 template with an affine
+    transformation (12 degrees of freedom).
+    Light gray: The
+    audio-description's field-of-view (cf.  \citep{hanke2014audiomovie}).
+    Black: outline of the subject-specific PPA ROIs.
+    Blue:
+    the primary $t$-contrast for the audio-description comparing
+    geometry-related nouns to non-geometry-related nouns spoken by the
     audio-description's narrator (\texttt{geo, groom > all non-geo}).
-        Red: the primary $t$-contrast for the movie comparing cuts to a new
-        setting with cuts to a familiar perspective (\texttt{vse\_new >
-        vpe\_old}).
-        Black: outline of subject-specific PPA ROI.}
-\label{fig:subs-thresh-ppa}
-\end{figure*}
+    Red: the
+    primary $t$-contrast for the movie comparing cuts to an unfamiliar setting
+    with cuts within an familiar perspective (\texttt{vse\_new > vpe\_old}).
+    } \label{fig:subs-thresh-ppa} \end{figure*}
 
 \subsection{Bland-Altman-Plots}
-% why
+
+\todo[inline]{anything else to report here? seems more like just an explanation
+of the plots}
+
+% why it was done
 To better depict the agreement (and difference) between individual results of
-the visual localizer and contrast 1 of the AO paradigm, we created one
+the dedicated visual localizer and contrast 1 of the AO paradigm, we created one
 Bland-Altman-Plots for each of the 14 subjects (see Figure
@@
 
-\todo[inline]{at the moment (which changes regularly) this section should follow
-the other group results; depends on the ``final'' discussion.}
+\todo[inline]{as mentioned before: this section would also make sense to be at
+the top or middle of the results; I moved it back and forth A LOT already}
 
 \todo[inline]{I consider tables of significant clusters for every contrast as
-overkill. One contrast, the ``primary contrast'', is appropriate; s. comments
-for overview of individuals}
+overkill. One contrast, the ``primary contrast'', is appropriate}
+
+\todo[inline]{s. comments for overview of individually significant clusters}
 
@@
 % why we did different contrasts
-We created a variety of contrasts to test a) if our approach yielded
-similar results across similar contrasts and b) if localization performance
-decreased when the contrast included categories that contained stimuli less
-congruent with the ``optimal'' stimulus type\todo{and the less data we use}.
-
+We created different $t$-contrasts for the AO stimulus (see Table
+\ref{tab:ao-contrasts}) and for the AV stimulus (see Table
+\ref{tab:av-contrasts}) to test the stability of results across different
+contrasts and exclude accidental findings.
 % results
-The overlap of significant clusters of 8 contrast for the audio-description, and
-5 contrasts computed for the movie can be found in Figure
-\ref{fig:stability-slices}.
-
-% AO eight contrasts
-For the analysis of the AO stimulus, we combined different event categories to
-create eight contrasts that provided different amount of data/events and
-decreasing congruency with the spatial layout hypothesis.
+The overlap of significant clusters of the eight contrast for the
+audio-description, and five contrasts computed for the movie can be found in
+Figure \ref{fig:stability-slices}.
 % results in PPA
 Six of eight AO contrasts show significant bilateral clusters in anterior
-regions of the group PPA overlap.\todo[inline]{which is temporal occipital
-fusiform gyrus regarding to co-registered Harvard-Oxford Cortical Structural
-Atlas}
+regions of the group PPA overlap.\todo[inline]{temporal occipital fusiform gyrus
+according to Harvard-Oxford Cortical Structural Atlas}
 % Precuneus = retrosplenial cortex ?
-Six of eight contrasts show significant clusters in the ventral precuneus /
-retrosplenial cortex (RSC).
+Six of eight contrasts show significant clusters in the retrosplenial region
+(and ventral precuneus).
 % statement/answer
@@
 depend on the design of one specific contrasts.
-% results get ``worse''
-Further, the ability to functionally isolate the PPA decreases the more a
-contrast depends on (just) using the categories \texttt{se\_new} and
-\texttt{se\_old} which were assumed to be problematic for a couple of reasons
-(s. discussion of stability of contrasts)
+% individual results
+Notably, we chose one contrast to look into individual results of all subjects
+but individually a contrast different from the primary contrast might lead to
+better individual localization results.
 
@@
 
-\todo[inline]{in general, the discussion explains how results fill gap
-identified in intro provides caveats to the interpretation describes how
-paper advances the field by providing new opportunities}
+\todo[inline]{the biggest question: where does the discussion of the stability
+of contrasts fit the best?}
+
+\todo[inline]{in general: discussion explains how results fill gap identified in
+intro}
+
+\todo[inline]{provides caveats to the interpretation describes how paper advances the field by providing new opportunities}
 
@@
 
-\todo[inline]{We demonstrate\dots; we discovered\dots; our data provide
+\todo[inline]{e.g. We demonstrate\dots; we discovered\dots; our data provide
 evidence\dots}
@@
 % what we wanted to test
-Hence, we tested if the perception of spatial cues embedded in an auditory
-narrative compared to non-spatial cues correlate with increased activation in
-the PPA.
+Hence, we tested if the perception of verbal spatial cues embedded in an
+auditory narrative contrasted with non-spatial cues correlate with increased
+activation in the PPA.
 % ``how'' we did it
-By using analogous statistical models for three different experimental
-paradigms, we are able to compare results gained from a dedicated visual
-localizer to results we gained from a movie and the movie's audio-only variant.
+We use analogous statistical models in three different experimental paradigms to
+compare results gained from a dedicated visual localizer to results we gained
+from a movie and the movie's audio-description.
 
@@
 \subsection{correlation of regressors}
-\todo[inline]{could maybe put into method section to save space here}
+
+\todo[inline]{could maybe pasted into method section to save space here; a short
+interpretation is already given there already}
 % stimuli not designed for research purposes
@@
 are based on the annotated stimulus features because a high degree of shared
-variance lowers detection power.
+variance lowers detection power
 % results of computing feature correlation
@@
 % encouraged by that we build contrasts (statement)
-Similarly to previous studies that used simplified stimuli to isolate the PPA,
-we created traditional voxel-wise GLMs that modeled and contrasted
-hemodynamic activity.
+Thus we felt encouraged to create traditional/canonical voxel-wise GLMs that
+modeled and contrasted hemodynamic activity similarly to previous studies that
+used simplified stimuli.
 
@@
 \subsection{group level}
+
+\todo[inline]{discuss only PPA here}
 % intro
-We performed whole-brain analyses on an individual and group level. On the group
-level of both naturalistic stimuli, significantly increased activity in the PPA
-correlates with spatial events compared to non-spatial events.
+We performed whole-brain analyses on a group level and individual level. In both
+naturalistic stimuli, significantly increased activity in the PPA correlates
+with spatial events compared to non-spatial events.
 
@@
 % conclusion
-our group results suggest that auditory spatial information does not
-just modulate activity in the PPA (depending on other factory like familiarity,
-XY; s. \citep{aziz2008modulation}) but correlates with bilaterally increased
+Our group results suggest that auditory spatial information does not just
+modulate activity in the PPA (depending on other factors like familiarity; s.
+\citep{aziz2008modulation}) but correlates with bilaterally increased
 activation.\todo{``modulate'' suggests causation}
@@
 % no task in Epstein
-An early study \citep{epstein1998ppa} that compared results from a paradigm that
-employed a (perceptual) judgment task of static pictures to a paradigm that did
-not let participant judge the same pictures.
+An early block-design study \citep{epstein1998ppa} that compared results from a
+paradigm that employed a (perceptual) judgment task of static pictures to a
+paradigm without that task.
 % results during no task
@@
 % but we are still different
-Nevertheless, our paradigm differs from previous studies because relevant
-stimulus features were incidentally embedded in a continuous auditory
-(or audio-visual) stream.
+Our paradigm still differs from previous studies because the relevant stimulus
+features were incidentally embedded in a continuous auditory (or audio-visual)
+stream.
 % conclusion
-This embeddedness prevents participants from guessing the investigated
-perceptual process by just being exposed to the paradigm and mimics experiencing
-the world outside the lab more closely.
+This embeddedness prevents participants from making assumptions about the
+investigated perceptual process by just being exposed to the paradigm and thus
+mimics experiencing the world outside the lab more closely.
 % concluding statement: kinda automatic process
@@
 
+\paragraph{shortcomings of AO contrasts}
+% no ``landscape'' category
+Our primary contrasts compared verbal cues regarding landmarks ((\texttt{geo};
+often buildings or aspects of a whole scene) and elements defining the geometry
+of a room (\texttt{groom}) to non-spatial cues.
+% vs vision
+In the visual domain, whole landscapes and not pictures of landmarks are
+considered to be the ``optimal'' stimulus type (cf. Epstein (1998, 1999, 2003,
+2008).
+% our se_new & se_old
+The audio-description's narrator rarely described a whole landscape by a single
+word (e.g. ``in a football stadium'', ``Forrest is running through the jungle'')
+when the plot switch from one setting to another setting but usually by
+continuously adding more concrete spatial cues (e.g. landmarks like buildings,
+trees, and streets)
+% further studies
+Humans can identify the gist of a rich visual scene within the duration of a
+single fixation \citep{henderson2003human}. Hence, further studies might
+investigate if vague verbal descriptions of a scene as a whole lead to
+differential hemodynamic activity in the PPA compared to more concrete spatial
+cues.
+
+\subsubsection{AV stimulus}
+
+% location
+Clusters of the analysis of the AV stimulus span the group overlap of individual
+PPAs from anterior to posterior and retrosplenial regions bilaterally.
+% difference in location/size to AO and VIS
+Clusters also extend into more posterior regions (occipital fusiform gyrus,
+lingual gyrus, and intracalcarine cortex) \todo{s. neurosynth in fsleyes?}
+% confound of higher perception
+This can be attributed to the fact that we averaged the content of individual
+frames after a cut and did not control for confounding features like depicted
+faces or objects.
+% confounds of lower perception
+It further suggest low-level visual features were not averaged out leading to
+clusters spanning the intracalcarine cortex.
+% further studies
+Hence, further studies focusing on visual perception should annotate and model
+visual features of naturalistic stimuli more rigorously.
+
+\subsubsection{stability of contrasts}
+
+% why we did a couple of contrasts
+For both stimuli we created additional contrasts that varied the amount of
+events available for the analysis and how well the annotated events within
+categories on average matched the stimulus type that we assumed to be
+preferentially processed in the PPA.
+% it shows two thing
+\todo[inline]{in how many clusters are how many overlapping clusters}
+% no incidental findings
+The results of the additional contrasts suggest that increased activation within
+the PPA is not just an accidental finding.  The bilaterally increased activation
+in the PPA does not depend on accidental findings but are stable across
+contrasts.
+% decline in isolation power
+Nevertheless, the ability to isolate the PPA drops the less the amount of data
+are available and the less the events averaged to built a category match the
+preferred stimulus type processed in the PPA.
+% decline b)
+Second, the ability to isolate clusters in the PPA declines nevertheless
+depending on the amount of events available to the statistical model. More
+importantly, isolation ability also declines depending on how well the used
+events within categories matched on average the preferred stimulus type. (cf.
+\texttt{se\_new} and \text{se\_old} in contrast 6-8)
+% concluding statement hypothesis
+Moreover, nouns of the narrator cueing a switch to another setting are often
+forestalled by changes of the soundscape.
+% arnott
+\todo[inline]{arnott2008crinkling find increased activations of PPA to sound
+made by objects}
+% hypothesis
+We hypothesize that not just semantic information but also the mere changes of a
+soundscape that cues a listener about a setting's spatial layout of could
+correlate with increased activity in the PPA.
+
+\todo[inline]{arnott2008 might be a good opportunity to switch to more general
+assumption of ``contextual information'' and combine that switch with
+anterior/posterior discussion}
+
+\paragraph{bilateral superior lateral occipital cortex}
+
+\todo[inline]{e.g. Dilks, Kanwisher (2013). The Occipital Place Area Is Causally
+and Selectively Involved in Scene Perception?}
+
+\paragraph{RSC}
+
+\todo[inline]{check location in primary contrast and in overlap of contrasts}
+
+% but RSC
+Apart from the PPA, we find significantly increased activity consistently across
+contrast in the retrosplenial cortex (RSC).\todo{how many exactly?}
+
+% location functionally defined
+In context of a scene-responsive region, the RSC is functionally defined and not
+necessarily identical to the anatomically defined retrosplenial cortex [26]
+\citep{epstein2008parahippocampal}.
+% location
+The RSC is located in the retrosplenial cortex, and posterior cingulate region,
+near to the point where the calcarine sulcus joins the parietal-occipital sulcus
+\citep{epstein2008parahippocampal}.
+% anatomy of real RSC
+The Retrosplenial cortex (BA 29 and 30) adjoins and is partially encircled by
+the posterior cingulate (BA 23 and 31) [51–56]
+\citep{epstein2008parahippocampal}.
+% function
+RSC is strongly active during scene viewing, scene imagery [25] and mental
+imagination of navigation through familiar environments [8]
+\citep{epstein2008parahippocampal}.
+% conclusion
+\todo[inline]{interpretation?; cf.\citep{vann2009what}}
+
+\todo[inline]{conclusion?}
+
+\subsection{anterior vs posterior PPA: contextual associations}
+
+% Aminoff (2013)
+Aminoff (2013) in general: processing of strong,
+long-term, contextual associations elicits activity within the PHC, as well as
+the RSC (which includes regions of the retrosplenial cortex, extending into the
+posterior cingulate cortex, and the precuneus), the medial prefrontal cortex
+(MPFC), and the transverse occipital sulcus (TOS) (Figure 2) [2,3,59–67].
+
+% contextual associations in anterior vs. posterior
+Aminoff et al. (2013): We propose that the general function of the PHC can be
+thought of as processing of contextual associations. A subregion of the
+posterior PHC is particularly optimized to process spatially organized
+contextual associations, whereas more anterior regions of the PHC are optimized
+to process contextual associations in other, non-spatial domains.
+% posterior PPA for visual visual associative information
+Spatial contextual associations are a dominant property of places and scenes,
+and thus scenes consistently activate this posterior subregion of the PHC (e.g.,
+PPA; Epstein, 1998). We do not argue that the PHC is not sensitive to
+spaces, places, and spatial information, but rather that it is sensitive to
+spatial stimuli because of the associative information (space-related
+associations) that such stimuli evoke.
+
+% Aminoff regarding contextual processing in the PHC and beyond
+Aminoff et al. (2013). We compared contextual processing of
+objects that are strongly related to a specific place (e.g., an oven is found in
+a kitchen) with contextual processing of objects that are highly associated with
+a context but not a specific place (e.g., a birthday cake is found at a birthday
+party, but the party can take place anywhere, at home, in a restaurant, at a
+park). Activity elicited by these two types of contextual objects was compared
+with the activity elicited for objects that were only weakly associated with
+many contexts (e.g., a lamp). Differential activity was found in the PHC and the
+RSC, replicating the previous findings (Bar \& Aminoff, 2003, The
+parahippocampal\dots).
+% results
+Activity within the PHC, however, was distributed along
+an anterior–posterior axis, with activity related to spatial contexts focused in
+the posterior part of the PHC and activity evoked by non-spatial contexts
+focused in the more anterior part of the PHC (Bar \& Aminoff, 2003, Cortical
+analysis of visual context; Aminoff et al., 2007, The parahippocampal cortex
+mediates spatial and nonspatial associations).
+
+\subsection{anterior vs posterior PPA}
+% connectivity
+Aminoff et al. (2013) regarding Baldassano (2013): some evidence from a human
+neuroimaging study examining functional connectivity of differences between
+anterior and posterior regions of the PHC show that the anterior regions are
+more functionally connected to retrosplenial complex (RSC) and parietal
+cortices, whereas the posterior regions are more functionally connected to
+visual processing regions.
+
+% Baldassano (2013). Differential connectivity with Parahippocampal Place Area
+Baldassano (2013). We utilize a functional connectivity measure for fMRI that
+can estimate connectivity differences at the voxel level. We provide the first
+direct evidence that anterior and posterior PPA exhibit distinct connectivity
+patterns. Anterior PPA is more strongly connected to regions in the default mode
+network (including the parieto-medial temporal pathway). Posterior PPA more
+strongly connected to occipital visual regions.
+% gradient
+We show that object sensitivity in PPA also has an anterior–posterior gradient,
+with stronger responses to abstract objects in posterior PPA.
+% summary
+Our results (and previous work) suggest that posterior PPA is concerned
+primarily with perception of low-level visual features and object shape, while
+anterior PPA is involved in memory and global contextual processing.
+
+% from Baldassano discussion
+Our results demonstrate that PPA exhibits a gradient in connectivity along
+anterior–posterior axis (analogous to the gradient in connectivity along macaque
+TH/TF/TFO). The connectivity gradient was also paired with a functional gradient
+of sensitivity to scene and abstract object stimuli. These results demonstrate
+that anterior and posterior PPA connect differentially to two distinct cortical
+networks.
+% but not independent
+Our data suggest that PPA might contain identifiable subregions, but subregions
+should not be considered as completely independent modules. Both subregions
+activate selectively to scenes, and the parahippocampal region (at least in
+macaques) is densely self-connected (Suzuki, 2009), implying that these
+subregions cooperate to build a complete representation of a scene.  Their
+distinct connectivity properties, however, suggests that each may be involved in
+specific aspects of visual and cognitive processing involved in the overarching
+goal of scene understanding.
+% posterior PPA
+Posterior PPA shows a stronger response to abstract objects than anterior PPA,
+and is more strongly connected to all of occipital visual cortex, including LOC
+and TOS. These regions have well-defined retinotopic maps (Arcaro et al., 2009;
+Nasr et al., 2011), and are associated with the perception of low-level visual
+features and object shape. Previous work has hinted that posterior PPA is more
+responsive to both simple visual textures and objects; Arcaro et al. (2009)
+found that a posterior portion of PPA responded about four times as strongly to
+a flickering checker-board stimulus compared to an anterior portion, and that
+the response to objects was greater than the response to scrambled images only
+in the posterior portion => posterior PPA may be more visually responsive than
+anterior PPA.
+% LLA
+Our description of posterior PPA is in fact similar to the original proposal of
+Aguirre et al. for a “lingual landmark area” (LLA), slightly posterior to PPA,
+which was “specialized for the perception of visual stimuli with orienting
+value” (Aguirre et al., 1998) and carried out bottom-up perceptual analysis to
+recognize locations or landmarks (Cant and Goodale, 2007; Epstein et al., 1999).
+Although the LLA is no longer identified as an independent region from PPA in
+current studies, it is possible that the posterior portion of PPA corresponds to
+the properties of the proposed LLA, offering an explanation for why this region
+was localized more posteriorly than the full PPA.
+% Anterior PPA
+Anterior PPA is specifically connected to RSC, cIPL, medial PFC, and the lateral
+surface of the anterior temporal lobe. In addition, this portion of PPA is less
+visually responsive to both scenes and objects, with notably low sensitivity to
+abstract object stimuli.
+
+% DMN
+The set of regions connected more strongly to anterior PPA is strikingly similar
+to the Default Mode Network (DMN) (Buckner et al., 2008; Fox et al., 2005;
+Raichle et al., 2001), which is known to include the parahippocampal region. The
+only portions of the DMN that do not show differential connectivity to anterior
+PPA in our data are the rostral portion of the posterior cingulate cortex (PCC)
+and the superior frontal cortex.
+% PPA and DMN
+DMN has been implicated in a large number of internally-focused
+tasks, one of its key roles involves autobiographical memory (Buckner et al.,
+2008). Models of recognition memory have previously identified parahippocampal
+cortex as primarily encoding spatial context information (Eichenbaum et al.,
+2007). Data from Aminoff et al. (2007) has suggested that an anterior
+portion of PPA may be involved in recall based on spatial context. Our results
+are consistent with anterior PPA playing a more central role in memory than
+posterior PPA, given anterior PPA's connectivity with the DMN.
+%
+The fact that anterior PPA had a lower sensitivity to our abstract object
+stimuli does not necessarily imply that this region does not use object
+information. Previous work has shown that PPA responds to objects that have
+spatial associations (Aminoff et al., 2007), are space-defining (Mullally and
+Maguire, 2011), and are navigationally-relevant (Janzen and Van Turennout,
+2004). These types of responses require spatial memory and cannot be based
+purely on visual features like object shape. If anterior PPA is involved in
+processing spatial context, then space-defining or navigationally-relevant
+objects could activate anterior PPA more strongly than our abstract objects,
+which were unfamiliar and provided no sense of context or orientation. Further
+experiments will be required to determine what type of object-related
+information is used in this region.
+
 \paragraph{(non-existing) other cluster}
+
+\todo[inline]{AV stimulus: we DID NOT find clusters that could be attributed to
+top-down / bottom-up attention, eye movements (FEF) (cf. corbetta2002control)
+or memory (which memory)?}
+
 % whole brain analysis
@@
 perceptual processes.
-% superior lateral occipital sulcus
-\todo[inline]{bilateral superior lateral occipital cortex}
-
-\paragraph{RSC}
-
-\todo[inline]{check location in primary contrast and in overlap of contrasts}
-
-\todo[inline]{from Epstein, 2008: Neuroimaging studies of human navigation most
-commonly activate the posterior parahippocampal and retrosplenial cortices
-[4–10], regions that also respond strongly during passive viewing of
-navigationally relevant visual stimuli such as scenes and buildings [11–14]
-\citep{epstein2008parahippocampal}.
-
-% but RSC
-Apart from the PPA, we find significantly increased activity in a functionally
-defined scene-responsive region often referred to as the retrosplenial cortex
-(RSC) in the primary contrast and consistently across the additional
-contrast\todo{how many exactly}.
-
-% location functionally defined
-This functionally defined RSC which is not necessarily identical to the
-anatomically defined retrosplenial cortex [26]
-\citep{epstein2008parahippocampal} is located in the retrosplenial cortex, and
-posterior cingulate region, near to the point where the calcarine sulcus joins
-the parietal-occipital sulcus \citep{epstein2008parahippocampal}.
-% anatomy of real RSC
-The Retrosplenial cortex (BA 29 and 30) adjoins and is partially encircled by
-the posterior cingulate (BA 23 and 31) [51–56]
-\citep{epstein2008parahippocampal}.
-% function
-RSC is strongly active during scene viewing, scene imagery [25] and mental
-imagination of navigation through familiar environments [8]
-\citep{epstein2008parahippocampal}.
+
+\subsection{individual analyses}
+
+\todo{how to discuss Bland-Altman-Plots? Please, let's talk about that shortly}
+
+\todo{discussion of individual differences? what do the results suggest???}
+
+\subsubsection{AO stimulus}
+
+\todo[inline]{shortcoming: no task to attend to spatial information}
+
+\todo[inline]{different level of alertness during paradigms}
+
+\todo[inline]{individual ``preference'' to pay attention to
+spatial infos (which contradicts statement above that attention is not a
+prerequisite)}
+
+\todo[inline]{different ``capability'' to process auditory spatial information}
+
+% intro
+We checked the results of the primary contrast also on the level of individual
+subjects to ``test'' the audio-description's performance as a functional
+localizer compared to the dedicated visual localizer paradigm.\todo{hm, sounds
+meh}
+% results of dedicated localizer
+The dedicated localizer \citep{sengupta2016extension} yielded bilateral ROIs in
+12 of 14 subjects and unilateral right ROI in two subjects (sub-04, sub-20).
+% in the current study
+The audio-description's primary contrast yielded significant bilateral clusters
+in 9 of 14 subjects (of which sub-04 shows just right-lateralized PPA ROI)  and
+an unilateral significant cluster in one subject.
+% difference
+Notably, we here used a ``one fits all approach`` whereas
+\citep{sengupta2016extension} chose the best fitting $z$-threshold in a
+subject's unthresholded $z$-maps by visual judgment and used the best of three
+alternative contrasts (strict, relaxed, or simple contrast).
+% quote from Hanke (2014)
+Hanke et al. (2014): Compared to AV stimulus, the AO stimulus leaves a much
+larger margin for inter-individual differences in imagining scenery, as well as
+actors' character and personality traits, while still preserving the time-locked
+presentation of information to a listener. At the same time, the AO stimulus
+limits the effect of an attentional focus on the selection of a subset of
+simultaneously occurring auditory events, in contrast to the selection of
+different parts of the visual field.
 % conclusion
-Interpretation \& conclusion???\todo{cf.\citep{vann2009what}}
-
-\paragraph{shortcomings of AO contrasts}
-% no ``landscape'' category
-Notably, our primary contrasts compared verbal cues regarding landmarks
-(\texttt{geo}) and elements defining the geometry of a room (\texttt{groom}) to
-non-spatial cues. While in the visual domain pictures of landmarks correlate
-with significantly increased activity in the PPA pictures of whole landscapes
-are considered to be the ``optimal'' stimulus type (cf. Epstein (1998, 1999,
-2003, 2008).
-% our se_new & se_old
-Our auditory stimulus provided only a small amount of nouns that described the
-landscape as a whole (e.g. ``in a football stadium'')  and these events were
-pooled with other nouns that generally cued a switch to another scene into the
-heterogeneous categories \texttt{se\_new} (e.g. ``Forrest in front of a
-buffet'', ``in Greenbow'') and \texttt{se\_old} (e.g. ``at the bench'')
-% further studies
-Given that humans can identify the gist of a rich visual scene within the
-duration of a single fixation \citep{henderson2003human} further studies might
-investigate how homogeneous categories of vague verbal descriptions of a whole
-scene differ from verbal descriptions of concrete landmarks.
-
-\subsubsection{AV stimulus}
-
-% location
-Clusters of the analysis of the AV stimulus span the group overlap of individual
-PPAs from anterior to posterior and retrosplenial regions bilaterally.
-% difference in location/size to AO and VIS
-Clusters also extend into more posterior regions (occipital fusiform gyrus,
-lingual gyrus, and intracalcarine cortex) \todo{s. neurosynth in fsleyes?}
-% shortcomings + explanation
-% confound of higher perception
-This can be attributed to the fact that we averaged the content of individual
-frames after a cut and did not control for confounding features like depicted
-faces or objects.
-% confounds of lower perception
-It further suggest low-level visual features were not averaged out leading to
-clusters spanning the intracalcarine cortex.
-% further studies
-Hence, further studies focusing on visual perception should annotate and model
-visual features of naturalistic stimuli more rigorously.
-%
-\todo[inline]{interpretation of clusters lateral occipital cortex?}
-\todo[inline]{discuss that we DID NOT find clusters that could be attributed to
-top-down / bottom-up attention, eye movements (FEF) (cf. corbetta2002control
-or memory (which memory)?}
-
-\subsubsection{stability of contrasts}
-% intro
-\todo[inline]{following logical structure is meh}
-% why we did a couple of contrasts
-For both stimuli we created additional contrasts that varied the amount of
-events available for the analysis and how well the annotated events within
-categories on average matched the stimulus type that we assumed to be
-preferentially processed in the PPA.
-% it shows two thing
-The results of the additional contrasts show two things. First, the
-bilaterally increased activation in the PPA does not depend on accidental
-findings but are stable across contrasts.
-% second: decline in isolation power
-Second, the ability to isolate clusters in the PPA declines nevertheless
-depending on the amount of events available to the statistical model. More
-importantly, isolation ability also declines depending on how well the used
-events within categories matched on average the preferred stimulus type.
-
-\paragraph{shortcomings: mixed events in AO categories}
-% mixed categories
-especially \texttt{se\_new} and \text{se\_old} (esp. in contrast 6-8) is often
-mixed
-% examples
-e.g. "ein Arzt", "ein alter Film", "auf einer Straße", "im Fernsehen", "die drei
-Jungs", "die zwei im Bett", "Jenny als Teenager", "Forrest vor einem Buffet",
-"Kennedy", "Jenny kommt aus dem Wohnwagen ihrer Großmutter";
-% hierarchical structure of annotation
-Switches from one setting to another offered the least amount of events in both
-stimuli. In the AO stimulus, this category shares events with nouns from other
-categories that served to cue the listener about a change of the setting ->
-words belong to more than one category but high-level category was used
-% soundscape
-Moreover, a change of the soundscape preceding the narrator's speech could also
-cue listeners about a change of the spatial environment\todo{check contrasts
-that use cuts across scenes but in the AO stimulus}
-% conclusion
-Hence, we assumed smaller probability of successfully isolating the PPA.
-% concluding statement
-In summary, the results of the additional contrasts suggest that increased
-activation within the PPA is not just an accidental finding. Nevertheless, the
-ability to isolate the PPA drops the less the amount of data are available and
-the less the events averaged to built a category match the preferred stimulus
-type processed in the PPA.
-% hypothesis
-Further, we hypothesize that not just semantic information but also the mere
-changes of a soundscape that cues a listener about a setting's spatial layout of
-could correlate with increased activity in the PPA
-% crinkling
-\todo[inline]{cf. arnott2008crinkling which find increased activations of PPA
-to sound made by objects}
-
-\subsection{individual analyses}
-
-\todo[inline]{individual ``preference'' to pay attention to spatial infos (which
-contradicts statement above that attention is not a prerequisite}
-
-\todo[inline]{different level of alterness during paradigms}
-
-\todo[inline]{different ``capability'' to process auditory spatial information}
-
-\todo[inline]{individual differences: different contrasts should be used and
-then the best used for individual rois}
-
-\subsubsection{AO stimulus}
-% intro
-Contrast 1 yielded isolated cluster in the anterior part of individual PPA masks
-in the majority of subjects.
-% one threshold for all
-Contrary to Sengupta et al. (2016), results were not archived by visually
-expecting unthresholded $z$-maps and choosing a subjectively best fitting
-threshold for each subject were archived but by using the same $Z$-value and
-significance threshold for all subjects.
-
-\todo[inline]{what about the info in Bland-Altman-Plots; discussion of that info
-could range from 2 sentences to 2 paragraphs?}
-
-% inter-individual differences
-\todo[inline]{could also be discussed: in 1-3 subjects a different contrasts
-work ``better''.}
-% sub-04
-In sub-04, the VIS yielded one right-sided PPA, the AV stimulus yielded one
-right-sided significant cluster whereas the AO stimulus yielded two homologous
-clusters in the PPA.\todo{what to do with that?}
-% note
-\todo[inline]{Hanke et al. (2014): Compared to an audio-visual movie, this is a
-    stimulus that leaves a much larger margin for inter-individual differences
-    in imagining scenery, as well as actors' character and personality traits,
-    while still preserving the time-locked presentation of information to a
-    listener. At the same time, an auditory stimulus limits the effect of an
-    attentional focus on the selection of a subset of simultaneously occurring
-    auditory events, in contrast to the selection of different parts of the
-visual field}.
-% summary statement group results a representative for group
-In summary, the individual results suggest that the group results are not driven
-by a couple of subjects but still reveal individual differences.
-% PPA just an example
-The feature ``auditory spatial information'' is just one example of a stimulus
-feature that can be annotated and used to build a model.
-% auditory localizer
-Thus, a complex but naturally engaging auditory stimulus like an audiobook
-might in principle be used as a non-visual localizer for a variety of brain
-functions in subjects who are not willing or able to follow task instructions
-during brain scanning.
-
-\todo[inline]{shortcoming to task to attend to spatial information}
+Our results suggest that a naturalistic auditory stimulus is suitable to
+localize (the anterior part) of a higher-level visual area in the majority of
+subjects.
+% individual contrasts
+Nevertheless, studies that primary aim for individual results should
+choose individual thresholds and test more than just one contrast to gain the
+best (?) individual ROIs.\todo{``best'' always sounds kind of judgmental}
 
@@
 % intro
-On individual level, mixed results for AV stimulus.  \todo[inline]{which
-contrast works better in which subjects?} Individual differences when seeing a
-whole picture with many features vs. serial auditory stream of information
-providing incidental cues; spatial attention?
-
-\paragraph{shortcomings of AV contrasts}
+On individual level, mixed results for AV stimulus.
+\todo{give the numbers}
+
+\todo[inline]{which contrast works better in which subjects?; if focus is
+individual diagnostics take the individually best contrasts; cf. Sengupta}
+
+% shortcomings
 visual confounds all over the place; obvious solution: annotate frames and track
@@
 
-\subsection{anterior vs posterior PPA}
-% connectivity
-Aminoff et al. (2013) regarding Baldassano (2013): There is some evidence from
-a human neuroimaging study examining functional connectivity of differences
-between anterior and posterior regions of the PHC that the anterior regions are
-more functionally connected to retrosplenial complex (RSC) and parietal
-cortices, whereas the posterior regions are more functionally connected to
-visual processing regions.
-
-% Baldassano (2013). Differential connectivity with Parahippocampal Place Area
-Baldassano (2013).  We utilize a functional connectivity measure for fMRI that
-can estimate connectivity differences at the voxel level. We provide the first
-direct evidence that anterior and posterior PPA exhibit distinct connectivity
-patterns, with anterior PPA more strongly connected to regions in the default
-mode network (including the parieto-medial temporal pathway) and posterior PPA
-more strongly connected to occipital visual regions. We show that object
-sensitivity in PPA also has an anterior–posterior gradient, with stronger
-responses to abstract objects in posterior PPA. These findings cast doubt on the
-traditional view of PPA as a single coherent region, and suggest that PPA is
-composed of one subregion specialized for the processing of low-level visual
-features and object shape, and a separate subregion more involved in memory and
-scene context.
-% Review in Baldassano
-In the last several years, a number of researchers have suggested that PPA could
-have multiple functional components. Differences in spatial frequency response
-(Rajimehr et al., 2011), varying deficits resulting from PPA lesions (Epstein,
-2008), PPA's overlap with multiple visual field maps (Arcaro et al., 2009), and
-a clustering meta-analysis (Sewards, 2011) all hint at the possibility that PPA
-may be comprised of at least two functionally distinct subunits along its
-posterior–anterior axis. However, studies explicitly searching for a dis-
-tinction between posterior and anterior PPA have failed to identify major
-differences (Cant and Xu, 2012; Epstein and Morgan, 2012).
-% anatomical studies in monkeys reviewed in Baldassano
-In short, these macaque parahippocampal regions exhibit an anterior–posterior
-gradient, with the anterior side most related to RSC and cIPL and the posterior
-side most related to ventral visual areas.
-% from Baldassano discussion
-Our results demonstrate that human PPA exhibits a gradient in con- nectivity
-along the anterior–posterior axis analogous to the gradient in connectivity
-along macaque TH/TF/TFO. This connectivity gradient was also paired with a
-functional gradient of sensitivity to scene and abstract object stimuli. These
-results present a challenge to current models of PPA function which assume that
-PPA is functionally homogeneous, and demonstrate that anterior and posterior PPA
-connect differentially to two distinct cortical networks.
-% but not independent
-Note that, although our data suggest that PPA might contain identifiable
-subregions, these subregions should not be considered as completely independent
-modules. Both subregions activate selectively to scenes, and the parahippocampal
-region (at least in macaques) is densely self-connected (Suzuki, 2009), implying
-that these subregions cooperate to build a complete representation of a scene.
-Their distinct connectivity properties, however, do suggest that each may be
-involved in specific aspects of visual and cognitive processing involved in the
-overarching goal of scene understanding. We discuss some possibilities for the
-functional roles of the subregions below.
-% posterior PPA
-Posterior PPA shows a stronger response to abstract objects than anterior PPA,
-and is more strongly connected to all of occipital visual cortex, including LOC
-and TOS. These regions have well-defined retinotopic maps (Arcaro et al., 2009;
-Nasr et al., 2011), and are associated with the perception of low-level visual
-features and object shape. Previous work has hinted that posterior PPA is more
-responsive to both simple visual textures and objects; Arcaro et al.  (2009)
-found that a posterior portion of PPA responded about four times as strongly to
-a flickering checker- board stimulus compared to an anterior portion, and that
-the response to objects was greater than the response to scrambled images only
-in the posterior portion. In other words, posterior PPA may be more visually
-responsive than anterior PPA.
-% LLA
-Our description of posterior PPA is in fact similar to the original proposal of
-Aguirre et al. for a “lingual landmark area” (LLA), slightly posterior to PPA,
-which was “specialized for the perception of visual stimuli with orienting
-value” (Aguirre et al., 1998) and carried out bottom-up perceptual analysis to
-recognize locations or landmarks (Cant and Goodale, 2007; Epstein et al., 1999).
-Although the LLA is no longer identified as an independent region from PPA in
-current studies, it is possible that the posterior portion of PPA corresponds to
-the properties of the proposed LLA, offering an explanation for why this region
-was localized more posteriorly than the full PPA.
-% Anterior PPA
-Anterior PPA is specifically connected to RSC, cIPL, medial PFC, and the lateral
-surface of the anterior temporal lobe. In addition, this portion of PPA is less
-visually responsive to both scenes and objects, with notably low sensitivity to
-abstract object stimuli.
-% DMN
-The set of regions connected more strongly to anterior PPA is strikingly similar
-to the Default Mode Network (DMN) (Buckner et al., 2008; Fox et al., 2005;
-Raichle et al., 2001), which is known to include the parahippocampal region. The
-only portions of the DMN that do not show differential connectivity to anterior
-PPA in our data are the rostral portion of the posterior cingulate cortex (PCC)
-and the superior frontal cortex.
-% PPA and DMN
-Although the DMN has been implicated in a large number of internally-focused
-tasks, one of its key roles involves autobiographical memory (Buckner et al.,
-2008). Models of recognition memory have previously identified parahippocampal
-cortex as primarily encoding spatial context information (Eichenbaum et al.,
-2007), and data from Aminoff et al. (2007) has suggested that an anterior
-portion of PPA may be involved in recall based on spatial context. Our results
-are con- sistent with anterior PPA playing a more central role in memory than
-posterior PPA, given anterior PPA's connectivity with the DMN.
-%
-PPA is known to represent global scene properties such as spatial expanse
-(Kravitz et al., 2011a; Park et al., 2011), and to construct global scene
-representations which are not predictable from responses to signature objects
-(MacEvoy and Epstein, 2011). Anterior PPA's connectivity to cIPL and RSC, along
-with its lower sensitivity to abstract objects, suggest that it may be more
-concerned with these types of spatial and non-object-based scene properties than
-posterior PPA. Future research contrasting global and object-based properties of
-scenes, however, would be necessary to test such a hypothesis.
-%
-The fact that anterior PPA had a lower sensitivity to our abstract object
-stimuli does not necessarily imply that this region does not use object
-information. Previous work has shown that PPA responds to objects that have
-spatial associations (Aminoff et al., 2007), are space-defining (Mullally and
-Maguire, 2011), and are navigationally-relevant (Janzen and Van Turennout,
-2004). These types of responses require spatial memory and cannot be based
-purely on visual features like object shape. If anterior PPA is involved in
-processing spatial context, then space-defining or navigationally-relevant
-objects could activate anterior PPA more strongly than our abstract objects,
-which were unfamiliar and provided no sense of context or orientation. Further
-experiments will be required to determine what type of object-related
-information is used in this region.
-% summary
-Unraveling the functions of the PPA has proven to be a challenging problem,
-given the region's involvement in a variety of scene perception and navigation
-tasks (Epstein, 2008). Our results imply that a complete model of PPA's
-functional properties must account for the differences in connectivity and
-function between anterior and posterior PPA. Although the precise roles of PPA's
-subregions are yet to be determined, our results and previous work suggest that
-posterior PPA is concerned primarily with perception of low-level visual
-features and object shape, while anterior PPA is involved in memory and global
-contextual processing.
-
-% contextual associations in anterior vs. posterior
-Aminoff et al. (2013): We propose that the general function of the PHC can be
-thought of as processing of contextual associations. A subregion of the
-posterior PHC is particularly optimized to process spatially organized
-contextual associations, whereas more anterior regions of the PHC are optimized
-to process contextual associations in other, non-spatial domains.
-% posterior PPA for visual visual associative information
-Spatial contextual associations are a dominant property of places and scenes,
-and thus scenes consistently activate this posterior subregion of the PHC (e.g.,
-PPA; Epstein, 1998). We of course do not argue that the PHC is not sensitive to
-spaces, places, and spatial information, but rather that it is sensitive to
-spatial stimuli because of the associative information (space-related
-associations) that such stimuli evoke.
-
-% Aminoff regarding contextual processing in the PHC and beyond
-Aminoff et al. (2013). It was critical to compare contextual processing of
-objects that are strongly related to a specific place (e.g., an oven is found in
-a kitchen) with contextual processing of objects that are highly associated with
-a context but not a specific place (e.g., a birthday cake is found at a birthday
-party, but the party can take place anywhere, at home, in a restaurant, at a
-park).  Activity elicited by these two types of contextual objects was compared
-with the activity elicited for objects that were only weakly associated with
-many contexts (e.g., a lamp). Differential activity was found in the PHC and the
-RSC, replicating the previous findings (Bar \& Aminoff, 2003, The
-parahippocampal\dots). Activity within the PHC, however, was distributed along
-an anterior–posterior axis, with activity related to spatial contexts focused in
-the posterior part of the PHC and activity evoked by non-spatial contexts
-focused in the more anterior part of the PHC (Bar \& Aminoff (2003) Cortical
-analysis of visual context; Aminoff et al. (2007) The parahippocampal cortex
-mediates spatial and nonspatial associations).
-
-\paragraph{contextual associations?}
-
-\todo[inline]{Aminoff discusses contextual associations in visual spatial
-processing, (episodic) memory; that could be discussed but the paradigm and
-contrasts do not provide material to say much about it other than wild
-speculations}
-
-% Aminoff (2013)
-It has been shown that the processing of strong, long-term, contextual
-associations elicits activity within the PHC, as well as the RSC (which includes
-regions of the retrosplenial cortex, extending into the posterior cingulate
-cortex, and the precuneus), the medial prefrontal cortex (MPFC), and the
-transverse occipital sulcus (TOS) (Figure 2) [2,3,59–67].
+Individual differences when seeing a whole picture with many features vs. serial
+auditory stream of information providing incidental cues; spatial attention?
 
@@
 
-\subsection{model-driven vs. data-driven analyses}
-Natural stimuli like movies \citep{hasson2008neurocinematics,
+\todo[inline]{could be mentioned in a few sentences. But above topics a far too
+much still}
+
+\section{Conclusions}
+
+\todo[inline]{template has no section ``conclusion'' -> use the last paragraph}
+
+% natural stimulation
+Intro: Natural stimuli like movies \citep{hasson2008neurocinematics,
 sonkusare2019naturalistic} or narratives \citep{honey2012not,
@@
 our natural dynamic environment than traditional experimental designs.
-
-why naturalistic stimuli are so cool: sonkusare2019, eickhoff2020, hamilton
-
-Naturalistic language processing can be approached with the analysis methods
-constructed to handle well-controlled experiments
-
-\subsection{re-use of existing data for new, independent research questions}
-Due to their continuity,
-complexity, and length, they offer a vast amount of data on a variety of brain
-functions like low-level perception, attention, comprehension, memory, emotions,
-or social interactions. This suggests the data can later be reused for variety
-of totally different, independent research questions, possibly on an individual
-level; increased compliance in individual diagnostics in ``special'' populations
-where compliance is more difficult to archive (pediatric or psychiatric)
+% why naturalisti stimuli are so cool
+(see also \citep{sonkusare2019naturalistic, eickhoff2020towards,
+hamilton2018revolution})
+% re-use of data for independent research question
+Due to their continuity, complexity, and length, they offer a vast amount of
+data on a variety of brain functions like low-level perception, attention,
+comprehension, memory, emotions, or social interactions. This suggests the data
+can later be reused for variety of totally different, independent research
+questions, possibly on an individual level; increased compliance in individual
+diagnostics in ``special'' populations where compliance is more difficult to
+archive (pediatric or psychiatric)
+
+% we annotated a couple of features to build contrasts
+Method: The feature ``auditory spatial information'' is just one example of a
+stimulus feature that can be annotated and used to build a model.
+% data-driven vs. model-driven
+Why we used a traditional GLM...
+
+% results
+Results: Our results demonstrate...
+
+% conclusion auditory localizer
+Conclusion: Thus, a complex but naturally engaging auditory stimulus like an
+audiobook might in principle be used as a non-visual localizer for a variety of
+brain functions in subjects who are not willing or able to follow task
+instructions during brain scanning.
 

### 2020-10-12 paper/main.tex
restructure (and mess up) discussion

@@
 
-\todo[inline]{RSC is not mentioned in intro anymore but it shows up in group
-results (mixed in individual subjects) and therefore could be discussed}
+\todo[inline]{retrosplenial cortex is not mentioned in intro anymore but it
+shows up in group results (mixed in individual subjects) and therefore should
+be discussed}
 
@@
 \citep{kanwisher1997ffa} or theory of mind \citep{spunt2014validating}) to
-functional brain areas or networks.
+functional brain areas or networks.\todo{kinda aggressive introductory
+sentence}.
 % What is the PPA?
@@
 regions of the fusiform gyrus and anterior lingual gyrus
-\citep{ epstein2008parahippocampal}.
+\citep{epstein2008parahippocampal}.
 % neural correlate of scene perception
 Increased hemodynamic activity in the PPA correlates with the perception of
-static pictures of landscapes, buildings or landmarks \citep{aguirre1998area, epstein2014neural, epstein1998ppa} compared to e.g. pictures of tools of faces.
+static pictures of landscapes, buildings or landmarks \citep{aguirre1998area,
+epstein2014neural, epstein1998ppa} compared to e.g. pictures of tools of faces.
 % spatial layout hypothesis
@@
 
-\todo[inline]{I deleted sentences regarding competing ``contextual associations
-    hypothesis'' (\citep{aminoff2006parahippocampal, aminoff2013role}) because
-our events/regressors cannot touch that issue; might be interesting during
+\todo[inline]{``contextual associations hypothesis''
+(\citep{aminoff2006parahippocampal, aminoff2013role}) does not show up in intro
+anymore; events/regressors cannot touch that issue; might be interesting during
 discussion of anterior/posterior PPA.}
@@
 beginning of the first fMRI recording session and also after the break at the
-start of the recording for the second half of the movie.
+start of the recording for the second half of the movie.\todo{references to bib}
 
@@
 \todo[inline]{I consider tables of significant clusters for every contrast as
-overkill. One contrast, the ``primary contrast'', is appropriate}
-
-\todo[inline]{s. comments for overview of individually significant clusters}
-
-% all AO contrasts
-% 1 geo, groom > non-geo:               PPA (l/r); RSC (l/r)
-% 2 geo, groom, se_new > non-geo:       PPA (l/r); RSC (l/r)
-% 3 groom, se_new, se_old > non-geo:    PPA (l/r); RSC (l/r)
-% 4 geo > all non-geo PPA               PPA (l/r); RSC (l/r)
-% 5 groom > all non-geo PPA             PPA (l/r); RSC (l/r)
-% 6 se_new > all non-geo PPA            PPA (l/r); RSC (l/r)
-% 7 se_new, se_old > all non-geo PPA               RSC (l/r)
-% 8 se_new > se_old                     nothing
-% 9 vse_new > vpe_old                              RSC (r)
-%10 vse_new, vpe_new > vse_old, vpe_old nothing
-%11 vse_new > vse_old                   nothing
-%12 vse_new > vse_old, vpe_old          nothing
-%13 vse_new, vpe_new > vpe_old          nothing
-
-% all AV contrasts
-% 1 vse_new > vpe_old: big bilateral cluster in PPA but also RSC, visual c.
-% 2 vse_new, vpe_new > vse_old, vpe_old:
-% group results are more more confined here
-% (but individual results were probably worse)
-% 3 vse_new > vse_old: PPA (l/r)
-% 4 vse_new > vse_old, vpe_old: PPA (l/r)
-% 5 vse_new, vpe_new > vpe_old: PPA (l/r) but also visual c.
-% 6 vno_cut > vse_new: nothing
-% 7 vno_cut > vse_old: nothing
-% 8 vno_cut > vse_new, vse_old: nothing
-% 9 vno_cut > vpe_new, vpe_old: nothing
-%10 se_new > se_old: right PPA
+overkill. Tables for just the ``primary contrast'', seems more appropriate}
+
+\todo[inline]{s. comments for overview of sign. clusters in all contrasts}
 
@@
 contrasts and exclude accidental findings.
+
+% all AO contrasts
+% 1 PPA (l/r); RSC (l/r), LOC (l/r)
+% 2 PPA (l/r); RSC (l/r), LOC (l/r), r. sup.temp.C., r.fr.pole; putamen; etc
+% 3 PPA (l/r); RSC (l/r), LOC (l/r),l&r sup.temp.C., anterior cing., paracing.
+% 4 PPA (l/r); RSC (l/r), LOC (l/r)
+% 5 PPA (l/r); RSC (l/r), LOC (-/-)
+% 6 PPA (l/r); RSC (l/r), LOC (l/-), l&r sup.temp.C.; medial pref. c., precun
+% 7 PPA (-/-); RSC (l/r), LOC (l/-), l&r sup.temp.C
+% 8 PPA (-/-); RSC (-/-), LOC (-/-)
+% control contrasts
+% 9 PPA (-/-); RSC (-/r), LOC (-/-), left pars triangularis
+%10 PPA (-/-); RSC (-/-), LOC (-/-)
+%11 PPA (-/-); RSC (-/-), LOC (-/-),
+%12 PPA (-/-); RSC (-/-), LOC (-/-), right posterior hippocampus
+%13 PPA (-/-); RSC (-/-), LOC (-/-)
+
 % results
@@
 % results in PPA
-Six of eight AO contrasts show significant bilateral clusters in anterior
-regions of the group PPA overlap.\todo[inline]{temporal occipital fusiform gyrus
-according to Harvard-Oxford Cortical Structural Atlas}
+In the analysis of the AO stimulus, six of eight contrasts show significant
+bilateral clusters in anterior regions of the group PPA
+overlap.\todo[inline]{temporal occipital fusiform gyrus according to
+Harvard-Oxford Cortical Structural Atlas}
 % Precuneus = retrosplenial cortex ?
-Six of eight contrasts show significant clusters in the retrosplenial region
-(and ventral precuneus).
+Seven of eight contrasts show bilaterally significant clusters in the
+retrosplenial region (and ventral precuneus).
 % statement/answer
@@
 better individual localization results.
+% transverse occipital sulcus
+\todo[inline]{transverse occipital sulcus / occipital place area? in 6 of 8
+contrasts}
+% confounds
+but confounds: right superior temporal gyrus (4 contrasts); left superior
+temporal gyrus (3 contrasts); some prefrontal clusters that show up in two
+contrasts
+% control in AO contrasts
+\todo[inline]{control contrast essentially almost all none results; s. comments}
+
+% all AV contrasts
+% 1 PPA (l/r); RSC (l/r), LOC (l/r), VisC (l/r), intracalcarine, cuneal, ling.c
+% 2 PPA (l/r); RSC (-/-), LOC (l/r), VisC (-/-)
+% 3 PPA (l/r); RSC (-/-), LOC (-/-), VisC (-/r), occ. fusisf. g.
+% 4 PPA (l/r); RSC (l/r), LOC (l/r), VisC (-/-), lingual g., occ. fusif. g.
+% 5 PPA (l/r); RSC (l/r), LOC (l/r), VisC (-/-), occ. fusif. g.
+% control contrasts
+% 6 nothing
+% 7 nothing
+% 8 nothing
+% 9 nothing
+%10 se_new > se_old (nouns in AV stim): LOC (l/r)
+% right PPA, bilateral sup. lat. occ. c., superior parietal lobe (right)
 
@@
 the design of the contrasts.
+% control AV
+\todo[inline]{control in AV stim: se\_new > se\_old (nouns in AV stim): LOC
+(l/r), right PPA, bilateral sup. lat. occ. c., superior parietal lobe (right)}
 
@@
         Light gray: The audio-description's field-of-view (cf.
-        \citep{hanke2014audiomovie}). Blue: contrasts 1-7 for the
+        \citep{hanke2014audiomovie}). Blue: contrasts 1-8 for the
         audio-description (see Table \ref{tab:ao-contrasts}. Red: contrasts 1-5
@@
 
-\todo[inline]{provides caveats to the interpretation describes how paper advances the field by providing new opportunities}
+\todo[inline]{provides caveats to the interpretation describes how paper
+advances the field by providing new opportunities}
 
@@
 
-\todo[inline]{e.g. We demonstrate\dots; we discovered\dots; our data provide
-evidence\dots}
-
-% previous studies
-Previous studies reported bilaterally increased hemodynamic activity in the PPA
-when participants were watching static pictures of landscape compared to face or
-objects \citep{epstein1998ppa, epstein1999parahippocampal} whereas a study using
-spoken sentences reported mixed results \citep{aziz2008modulation}.
-% what we wanted to test
-Hence, we tested if the perception of verbal spatial cues embedded in an
+% previous studies: visual
+On the one hand, previous studies reported bilaterally increased hemodynamic
+activity in the PPA when participants were watching static pictures of landscape
+compared to face or objects (e.g. \citep{epstein1998ppa,
+epstein1999parahippocampal})
+% previous study: auditory
+On the other hand, a study using spoken sentences reported mixed results
+\citep{aziz2008modulation}.
+% what we did
+Hence, we use analogous statistical models in three different experimental
+paradigms to compare results gained from a dedicated visual localizer to results
+we gained from a movie and the movie's audio-description.
+% We focus
+Our results suggest that the perception of verbal spatial cues embedded in an
 auditory narrative contrasted with non-spatial cues correlate with increased
-activation in the PPA.
-% ``how'' we did it
-We use analogous statistical models in three different experimental paradigms to
-compare results gained from a dedicated visual localizer to results we gained
-from a movie and the movie's audio-description.
-
-\todo[inline]{high-level summary/interpretation of results in one sentence here
-already?}
+activation in the PPA of both hemispheres.
 
@@
 \todo[inline]{could maybe pasted into method section to save space here; a short
-interpretation is already given there already}
+interpretation is given there already}
 % stimuli not designed for research purposes
@@
 % intro
-We performed whole-brain analyses on a group level and individual level. In both
-naturalistic stimuli, significantly increased activity in the PPA correlates
-with spatial events compared to non-spatial events.
+We performed whole-brain analyses on data from the audio-visual movie and its
+audio-description. We chose one contrast of each stimulus to be investigated not
+just on a group level but also on the level of individual subjects. Additional
+contrasts were tested to investigate the stability of results across contrasts
+when contrasted categories and the amount of available data is varied.
 
@@
 
-\todo[inline]{Do Wilson (2008), Lerner (2011), Honey (2012), Silbert (2014) find
-ISC in PPA using an auditory stimulus?}
 % AO stimulus cluster location
-More specifically for the primary contrast of the AO stimulus, group results
-show spatially concise / restricted clusters in the anterior part of the PPA
-group overlap taken from \citep{sengupta2016extension}.
+Group results of the AO stimulus' primary contrast yielded spatially
+concise / restricted clusters in the anterior part of the PPA group overlap
+taken from \citep{sengupta2016extension}.
 % diff to Aziz (2008)
 Unlike \citep{aziz2008modulation} we did not use whole sentences as events to
-model a hemodynamic response but modeled an event from on- to offset of each
-word that was giving the cue about the movie's missing visual content of a
-scene.
+model a hemodynamic responses but modeled from on- to offset of single words
+that cue the listener about the movie's missing visual content.
 % conclusion
@@
 % no task in Epstein
-An early block-design study \citep{epstein1998ppa} that compared results from a
-paradigm that employed a (perceptual) judgment task of static pictures to a
-paradigm without that task.
+An early block-design study \citep{epstein1998ppa} compared results from a
+paradigm that employed a (perceptual) judgment task of static pictures to a to
+the same paradigm but without that task.
 % results during no task
@@
 % but we are still different
-Our paradigm still differs from previous studies because the relevant stimulus
-features were incidentally embedded in a continuous auditory (or audio-visual)
+Nevertheless, our paradigm still differs from previous studies because the
+relevant stimulus features were incidentally embedded in a continuous auditory
 stream.
@@
 \paragraph{shortcomings of AO contrasts}
-% no ``landscape'' category
-Our primary contrasts compared verbal cues regarding landmarks ((\texttt{geo};
-often buildings or aspects of a whole scene) and elements defining the geometry
-of a room (\texttt{groom}) to non-spatial cues.
-% vs vision
-In the visual domain, whole landscapes and not pictures of landmarks are
+% optimal stimulus type in vision
+In the visual domain, landscapes and not pictures of landmarks or buildings are
 considered to be the ``optimal'' stimulus type (cf. Epstein (1998, 1999, 2003,
-2008).
-% our se_new & se_old
-The audio-description's narrator rarely described a whole landscape by a single
-word (e.g. ``in a football stadium'', ``Forrest is running through the jungle'')
-when the plot switch from one setting to another setting but usually by
-continuously adding more concrete spatial cues (e.g. landmarks like buildings,
-trees, and streets)
+2008).\todo{check references}
+% cateogries in primary contrasts
+In the current study's primary contrast, we compared verbal cues regarding
+landmarks ((\texttt{geo}; often buildings or other single aspects of a whole
+scene) and elements defining the geometry of a room/locale (\texttt{groom}) to
+non-spatial cues.
+% we did not choose se\_new and se\_old
+Notably, we did not choose the categories that contained switches from one
+setting to another (texttt{se\_new} and texttt{se\_old}) which one might assume
+to contain the auditory equivalent to the ``optimal'' visual stimulus type.
+% why not se\_new or se\_old
+These categories were actually heterogeneous: they rarely contained whole (but
+also vague) descriptions of landscapes (e.g. ``in a football stadium'',
+``Forrest is running through the jungle''), mostly landmarks or buildings,
+and they also contained non-spatial cues.\todo{repeat examples from method
+section}.
 % further studies
-Humans can identify the gist of a rich visual scene within the duration of a
-single fixation \citep{henderson2003human}. Hence, further studies might
-investigate if vague verbal descriptions of a scene as a whole lead to
-differential hemodynamic activity in the PPA compared to more concrete spatial
-cues.
+Given that humans can identify the gist of a rich visual scene within the
+duration of a single fixation \citep{henderson2003human} further studies might
+investigate if categories of vague verbal descriptions of a landscape as a whole
+lead to differential hemodynamic activity in the PPA compared to more concrete
+spatial cues.
 
 \subsubsection{AV stimulus}
-
 % location
-Clusters of the analysis of the AV stimulus span the group overlap of individual
-PPAs from anterior to posterior and retrosplenial regions bilaterally.
+Group results of the AV stimulus' primary contrast yielded bilateral clusters
+that span the group overlap of individual PPAs from anterior to posterior and
+expand into retrosplenial regions.
 % difference in location/size to AO and VIS
-Clusters also extend into more posterior regions (occipital fusiform gyrus,
-lingual gyrus, and intracalcarine cortex) \todo{s. neurosynth in fsleyes?}
+Clusters also expand into more posterior regions (occipital fusiform gyrus,
+lingual gyrus, and intracalcarine cortex) \todo{what overlaps with group ROI?}
 % confound of higher perception
@@
 visual features of naturalistic stimuli more rigorously.
-
-\subsubsection{stability of contrasts}
+\todo[inline]{concluding statement to cross-modality of results?}
+
+\subsection{stability of contrasts}
 
@@
 preferentially processed in the PPA.
-% it shows two thing
-\todo[inline]{in how many clusters are how many overlapping clusters}
+
+\subsubsection{PPA}
+% PPA AO
+Regarding contrasts of the AO stimulus, six of eight contrasts show
+significant bilateral clusters in the anterior part of the group PPA.
+% PPA AV
+Regarding contrasts of the AV stimulus, x of y contrasts show significant
+bilateral clusters in the PPA but extending into posterior regions
 % no incidental findings
-The results of the additional contrasts suggest that increased activation within
-the PPA is not just an accidental finding.  The bilaterally increased activation
-in the PPA does not depend on accidental findings but are stable across
-contrasts.
-% decline in isolation power
-Nevertheless, the ability to isolate the PPA drops the less the amount of data
-are available and the less the events averaged to built a category match the
-preferred stimulus type processed in the PPA.
-% decline b)
-Second, the ability to isolate clusters in the PPA declines nevertheless
-depending on the amount of events available to the statistical model. More
-importantly, isolation ability also declines depending on how well the used
-events within categories matched on average the preferred stimulus type. (cf.
-\texttt{se\_new} and \text{se\_old} in contrast 6-8)
-% concluding statement hypothesis
+Results of the additional contrasts suggest that bilaterally increased
+activation in the PPA does not depend on accidental findings but is are stable
+across contrasts of the movie and the audio-description.
+% anterior vs. posterior?
+
+\subsubsection{localization performance and noise}
+% overall good isolation;  whole brain analysis and not many random clusters
+Despite performing a whole brain analysis on naturalistic stimuli with many
+uncontrolled stimuli we do not find many random clusters in single contrasts or
+even systematically across contrasts\todo{good god but that's essentially it}.
+% shit was averaged out we did not even know of
+Further, unknown stimulus features we did not even annotate did not lead to a
+variety of significant cluster across the brain that hamper interpretation of
+results.
+% movie: attention, and shit
+\todo[inline]{where are no clusters? e.g. top-down / bottom-up
+attention, eye movements (FEF) (cf. corbetta2002control) or memory (which
+memory)?}
+
+% BUT: amount of data
+Nevertheless, localization performance depends on the amount of available
+data\todo{give examples of contrast using less events in AV and AO}.
+% BUT: match of the stimulus type/averaged events
+Further, localization performance is also influenced by how well events
+within categories matched on average the preferred stimulus type.
+% AV: frame content
+In the AV stimulus, we averaged different kind of movie cuts regardless to the
+movie frames content.
+\todo[inline]{how well spatially constrained are the clusters?}
+% AO: stimulus categories
 Moreover, nouns of the narrator cueing a switch to another setting are often
-forestalled by changes of the soundscape.
+forestalled by changes of the soundscape.\todo{cross-modal control contrasts;
+all negative results at moment of cuts but vse\_new > pe\_old): right RSC.}
 % arnott
-\todo[inline]{arnott2008crinkling find increased activations of PPA to sound
-made by objects}
+\todo[inline]{e.g. arnott2008crinkling find increased activations of PPA to
+sound made by objects}
 % hypothesis
@@
 correlate with increased activity in the PPA.
-
-\todo[inline]{arnott2008 might be a good opportunity to switch to more general
-assumption of ``contextual information'' and combine that switch with
-anterior/posterior discussion}
-
-\paragraph{bilateral superior lateral occipital cortex}
-
-\todo[inline]{e.g. Dilks, Kanwisher (2013). The Occipital Place Area Is Causally
-and Selectively Involved in Scene Perception?}
-
-\paragraph{RSC}
-
-\todo[inline]{check location in primary contrast and in overlap of contrasts}
-
-% but RSC
-Apart from the PPA, we find significantly increased activity consistently across
-contrast in the retrosplenial cortex (RSC).\todo{how many exactly?}
-
-% location functionally defined
-In context of a scene-responsive region, the RSC is functionally defined and not
-necessarily identical to the anatomically defined retrosplenial cortex [26]
-\citep{epstein2008parahippocampal}.
-% location
-The RSC is located in the retrosplenial cortex, and posterior cingulate region,
-near to the point where the calcarine sulcus joins the parietal-occipital sulcus
-\citep{epstein2008parahippocampal}.
-% anatomy of real RSC
-The Retrosplenial cortex (BA 29 and 30) adjoins and is partially encircled by
-the posterior cingulate (BA 23 and 31) [51–56]
-\citep{epstein2008parahippocampal}.
-% function
-RSC is strongly active during scene viewing, scene imagery [25] and mental
-imagination of navigation through familiar environments [8]
-\citep{epstein2008parahippocampal}.
+% AO: superior temporal cortex
+Nevertheless in four of nine contrasts of the AO stimulus, we find significant
+clusters in superior auditory cortices (including early auditory
+cortices?)\todo{which exactly}
 % conclusion
-\todo[inline]{interpretation?; cf.\citep{vann2009what}}
-
-\todo[inline]{conclusion?}
+This suggests that variance correlating with lower level auditory processes was
+(not) averaged (out) across trials\todo{which contrasts; A1 \& low-level
+nuisance regressors?}
+
+% conclusion: AO and AV stability
+In summary, our results across add further evidence that model-driven analyses
+can be run on data from naturalistic stimuli to isolate brain activity
+correlating with specific perceptual processes.
+% but
+Nevertheless isolation performance relies on how well the model captures
+different aspects of the stimuli's feature space.
+
+\subsubsection{other systematics: anterior vs. posterior, RSC and OPA}
+
+% intro
+Nevertheless, results across contrasts of both stimuli show significant clusters
+constrained to the anterior part of the PPA in contrasts of the AO stimulus, and
+significant clusters in the retrosplenial cortices and superior lateral cortices
+in both naturalistic stimuli.
 
 \subsection{anterior vs posterior PPA: contextual associations}
+
+\todo[inline]{at the moment it makes more sense to discuss it sooner; but it
+kinda depends on stuff that is happening in the RSA too}
 
@@
 
-\paragraph{(non-existing) other cluster}
-
-\todo[inline]{AV stimulus: we DID NOT find clusters that could be attributed to
-top-down / bottom-up attention, eye movements (FEF) (cf. corbetta2002control)
-or memory (which memory)?}
-
-% whole brain analysis
-Regarding confounding variables, we do not find significant clusters in e.g.
-early auditory cortices despite performing a whole brain analysis on data gained
-from a naturalistic stimulus paradigm.
+\paragraph{RSC (in both stimuli)}
+
+\todo[inline]{check location in primary contrast and in overlap of contrasts}
+
+% but RSC
+Apart from the PPA, we find significantly increased activity consistently across
+contrast of both contrasts in the retrosplenial cortex (RSC).\todo{how many
+exactly?}
+
+% location functionally defined
+In context of a scene-responsive region, the RSC is functionally defined and not
+necessarily identical to the anatomically defined retrosplenial cortex [26]
+\citep{epstein2008parahippocampal}.
+% location
+The RSC is located in the retrosplenial cortex, and posterior cingulate region,
+near to the point where the calcarine sulcus joins the parietal-occipital sulcus
+\citep{epstein2008parahippocampal}.
+% anatomy of real RSC
+The Retrosplenial cortex (BA 29 and 30) adjoins and is partially encircled by
+the posterior cingulate (BA 23 and 31) [51–56]
+\citep{epstein2008parahippocampal}.
+% function
+RSC is strongly active during scene viewing, scene imagery [25] and mental
+imagination of navigation through familiar environments [8]
+\citep{epstein2008parahippocampal}.
 % conclusion
-This suggests that variance correlating with lower level auditory processes was
-averaged (out) across trials and/or regressed out by implementing the nuisance
-regressors.
-% shit was averaged out we did not even know of
-Further, unknown stimulus features we did not even annotate did not lead to a
-variety of significant cluster across the brain that hamper interpretation of
-results.
-% conclusion
-This provides further evidence that model-driven analyses can be run on data
-from naturalistic stimuli to isolate brain activity correlating with specific
-perceptual processes.
+\todo[inline]{interpretation?; cf.\citep{vann2009what}}
+
+\todo[inline]{conclusion?}
+
+\paragraph{superior lateral occipital cortex (in both stimuli)}
+
+\todo[inline]{e.g. Dilks, Kanwisher (2013). The Occipital Place Area Is Causally
+and Selectively Involved in Scene Perception?}
+
+\subsection{negative controls and cross-modal controls}
+
+\todo[inline]{could be mentioned in a few sentences. But above topics a far too
+much still; better embed somewhere above}
 
@@
 
-\subsection{negative controls and cross-modal controls}
-
-\todo[inline]{could be mentioned in a few sentences. But above topics a far too
-much still}
-
 \section{Conclusions}

### 2020-10-12 code/plot-group-and-individuals.py

@@ -181,7 +181,7 @@ def process_stability(ao_prob, av_prob, outfpath):
     legendAxis = fig.add_subplot(grid[12:, :6])
 
     blue = mpl.patches.Patch(color='#2474b7',
-                             label='descriptive nouns (7 contrasts)')
+                             label='descriptive nouns (8 contrasts)')
     red = mpl.patches.Patch(color='#f03523',
                             label='movie cuts (5 contrasts)',)
     black = mpl.patches.Patch(color='#454545',

### 2020-10-13 paper/main.tex
notes/text at the end of result section

@@
 \todo[inline]{following phrasing might be strange but necessary to delineate
-from Huth (2016); good voxel-wise semantic modeling regarding places in PPA but
-imo that does not say anything about excitation/inhibition; interestingly Huth
-mentions PPA during talks but it is not discussed in any paper and despite being
-promised none of his group came up with a paper regarding that topic}
+from Huth (2016); they do voxel-wise semantic modeling regarding places in PPA
+but imo that does not say anything about excitation/inhibition; interestingly
+Huth mentions PPA during talks but it is not discussed in any paper and despite
+being promised none of his group came up with a paper regarding that topic}
 % Aziz (2008): place related sentences
@@
 % problem with hierarchical categories
+\todo[inline]{compare the following with Methods: AO contrasts \& Discussion}
 Notably, the categories \texttt{setting\_new} and \texttt{setting\_rec}
@@
 EPI images were online-corrected for motion and geometric distortions [Oh, S. et
-al. 2012; In, M. \& Speck, O., 2012; Chung, J. et al., 2011]. Auxiliary scans
-for slice alignment and motion- and distortion-correction were performed at the
-beginning of the first fMRI recording session and also after the break at the
-start of the recording for the second half of the movie.\todo{references to bib}
-
+al. 2012; In, M. \& Speck, O., 2012; Chung, J. et al., 2011]\todo{references to
+bib if this paragraph stays in the paper}. Auxiliary scans for slice alignment
+and motion- and distortion-correction were performed at the beginning of the
+first fMRI recording session and also after the break at the start of the
+recording for the second half of the movie.
 % AV & VIS
@@
 MRI scanner equipped with a 32 channel head coil acquired T2*-weighted
-echo-planar images (gradient-echo, \unit[2]{s} repetition time,
-\unit[30]{ms} echo time, \unit[90]{$^{\circ}$} flip angle, \unit[1943]{Hz/Px}
-bandwidth, parallel acquisition with sensitivity encoding (SENSE) reduction
-factor 2).
+echo-planar images (gradient-echo, \unit[2]{s} repetition time, \unit[30]{ms}
+echo time, \unit[90]{$^{\circ}$} flip angle, \unit[1943]{Hz/Px} bandwidth,
+parallel acquisition with sensitivity encoding (SENSE) reduction factor 2).
 % slices
@@
 A total of 3599 volumes were recorded for each participant in each of the
-naturalistic stimulus paradigms (451, 441, 438, 488, 462, 439, 542, and 338 volumes for segment 1–8).
+naturalistic stimulus paradigms (451, 441, 438, 488, 462, 439, 542, and 338
+volumes for segment 1–8).
 
@@
 We computed the Pearson coefficients of the regressors across the eight segments
-of both naturalistic stimuli. Results demonstrate no to minor correlations
-(s. \ref{fig:reg-corr}) which suggest the models should not suffer from low
-detection power due to shared variance among regressors.\todo{sounds meh but
-don't know how do write it better}
+of both naturalistic stimuli. Results demonstrate no to minor correlations (s.
+\ref{fig:reg-corr}) which suggest the models should not suffer from low
+detection power due to shared variance among regressors.
+%
+\todo{sounds meh but don't know how do write it better; results of correlations
+are given here already; maybe the short discussion (cf. very beginning of
+discussion) of these correlation could be put here too which will saves space in
+the main text; but mixing methods/results/discussion is not absolutely "clean"}
 
@@
 preferred stimulus type processed in the PPA.
-%
+% selection of the primary contrast
 Thus for each stimulus, we chose one ``primary contrast'' for a detailed report
@@
 
+\todo[inline]{compare the following with annotation \& Discussion}
 % intro
@@
 (c) the narrator is often lacking behind a short dialogue or a change of the
-soundscape that already cue a change of settings.\todo{cf. contrast that uses
+soundscape that already cue a change of settings.
 cuts but in AO stimulus}
@@
 induce noise and would be less successful in isolating the PPA.
+
+% negative control contrasts
+Five $t$-contrasts (see Table \ref{tab:ao-contrasts}) we created as negative
+controls to test if increased activation in the PPA was correlated with
+moments of cuts and therefore possibly correlated with a accompanying change in
+the soundscape.\todo{all essentially almost null results}
 
@@
 regressor of interest to reduce noise.
-
-% negative control contrasts
-Five $t$-contrasts (see Table \ref{tab:ao-contrasts}) we created as negative
-controls to test if increased activation in the PPA was correlated with
-moments of cuts and therefore possibly correlated with a accompanying change in
-the soundscape.\todo{cf. contrast that uses cuts but in AO stimulus}
 
@@
 Table \ref{tab:av-contrasts}).
+\todo[inline]{all null results; except cope 10 (nouns of narrator but in movie):
+right PPA, bilat sup. lat. occ. cortec, LOC (l/r), right superior parietal
+lobe).
 
@@
 % precuneus
-Additionally , two additional clusters are located in the ventral precuneus
+Additionally, two additional clusters are located in the ventral precuneus
 extending into the retrosplenial cortex.
@@
 
+\todo[inline]{I consider tables of significant clusters for every contrast as
+overkill. Tables for just the ``primary contrast'', seems more appropriate; the
+level of details explained depends on the discussion; atm moment I feel it
+should be discussed more than expected; hence, following some notes as to dos}
+
 \todo[inline]{as mentioned before: this section would also make sense to be at
 the top or middle of the results; I moved it back and forth A LOT already}
-
-\todo[inline]{I consider tables of significant clusters for every contrast as
-overkill. Tables for just the ``primary contrast'', seems more appropriate}
 
@@
 Harvard-Oxford Cortical Structural Atlas}
-% Precuneus = retrosplenial cortex ?
-Seven of eight contrasts show bilaterally significant clusters in the
-retrosplenial region (and ventral precuneus).
 % statement/answer
@@
 but individually a contrast different from the primary contrast might lead to
-better individual localization results.
+better individual localization results.\todo{concluding statements often feel
+like interpretation/discussion to me}
+
+% Precuneus = retrosplenial cortex ?
+\todo[inline]{Seven of eight contrasts show bilaterally significant clusters in
+the retrosplenial region (and ventral precuneus)}.
+
 % transverse occipital sulcus
 \todo[inline]{transverse occipital sulcus / occipital place area? in 6 of 8
-contrasts}
+contrasts (4 bilaterally)}
+
 % confounds
-but confounds: right superior temporal gyrus (4 contrasts); left superior
-temporal gyrus (3 contrasts); some prefrontal clusters that show up in two
-contrasts
+\todo[inline]{``other clusters'' (confounds?): right superior temporal gyrus (4
+contrasts); left superior temporal gyrus (3 contrasts); some prefrontal clusters
+that show up in two contrasts}
+
 % control in AO contrasts
@@
 occipital, fusiform cortex showing congruency with the group overlap of
-individual PPA ROIs.
+individual PPA ROIs.\todo{must be in posterior PPA as well}
 % lingual gyrus
-In three contrasts, these homologous clusters extend into the lingual gyri.
+In three contrasts, these homologous clusters extend into the lingual
+gyri.\todo[inline]{check regions and contrasts that are located outside of the
+PPA; border of lingus belongs to PPA}
 % RSC
@@
 Here again, we can show that results can in principle be accomplished by varying
-the design of the contrasts.
+the design of the contrasts.\todo{concluding statement =
+interpretation/discussion?}
+
 % control AV
@@
 Clusters also expand into more posterior regions (occipital fusiform gyrus,
-lingual gyrus, and intracalcarine cortex) \todo{what overlaps with group ROI?}
+lingual gyrus, and intracalcarine cortex)\todo{which of these regions overlap
+with group ROI? which regions show clusters but do not overlap with PPA?}
 % confound of higher perception
@@
 visual features of naturalistic stimuli more rigorously.
-\todo[inline]{concluding statement to cross-modality of results?}
+\todo[inline]{concluding statement regarding AV vs AO and cross-modality of results?}
 

### 2020-10-13 paper/main.tex
corrections in discussion of group results

@@
 Unlike \citep{aziz2008modulation} we did not use whole sentences as events to
-model a hemodynamic responses but modeled from on- to offset of single words
+model hemodynamic responses but modeled from on- to offset of single words
 that cue the listener about the movie's missing visual content.
@@
 
-% no task in Epstein
-An early block-design study \citep{epstein1998ppa} compared results from a
-paradigm that employed a (perceptual) judgment task of static pictures to a to
-the same paradigm but without that task.
+% transition to task topic
+Moreover unlike most previous studies, our paradigm was free of any task.
+%
+Nevertheless, one early block-design study \citep{epstein1998ppa} compared
+results from a paradigm that employed a (perceptual) judgment task of static
+pictures to the same paradigm but without that task.
 % results during no task
@@
 % but we are still different
-Nevertheless, our paradigm still differs from previous studies because the
-relevant stimulus features were incidentally embedded in a continuous auditory
-stream.
+Our paradigm still differs from previous studies because the relevant stimulus
+features were incidentally embedded in a continuous auditory stream.
 % conclusion
@@
 \paragraph{shortcomings of AO contrasts}
+
+\todo[inline]{cf. Methods: annotation \& Methods: AO copes}
 % optimal stimulus type in vision
@@
 % why not se\_new or se\_old
-These categories were actually heterogeneous: they rarely contained whole (but
-also vague) descriptions of landscapes (e.g. ``in a football stadium'',
-``Forrest is running through the jungle''), mostly landmarks or buildings,
-and they also contained non-spatial cues.\todo{repeat examples from method
-section}.
+These categories were actually heterogeneous: they rarely contained whole (and
+thus vague) descriptions of landscapes (e.g. ``in a football stadium'',
+``Forrest is running through the jungle'') but mostly landmarks or buildings,
+and also non-spatial cues.\todo{repeat examples from method section}.
 % further studies
@@
 duration of a single fixation \citep{henderson2003human} further studies might
-investigate if categories of vague verbal descriptions of a landscape as a whole
-lead to differential hemodynamic activity in the PPA compared to more concrete
-spatial cues.
+investigate if categories of wholistic but vague verbal descriptions of
+landscapes correlate with differential hemodynamic activity in the PPA compared
+to more concrete spatial cues.
 
@@
 % further studies
-Hence, further studies focusing on visual perception should annotate and model
-visual features of naturalistic stimuli more rigorously.
-\todo[inline]{concluding statement regarding AV vs AO and cross-modality of results?}
+Since the capability to isolate clusters or networks correlating with specific
+perceptual (or cognitive) processes is influenced by the amount of annotated
+stimulus features further studies focusing on visual perception should annotate
+and model visual features of naturalistic stimuli more rigorously.\todo{ouf,
+okay...}
+% cross-modal control purpose?
+\todo[inline]{concluding statement regarding AV vs AO and cross-modality of
+results?}
 

### 2020-10-13 paper/main.tex
discussion: stability of contrast madness

@@
 
+\todo[inline]{the pain starts exactly here}
+
 % why we did a couple of contrasts
@@
 % PPA AV
-Regarding contrasts of the AV stimulus, x of y contrasts show significant
+Regarding contrasts of the AV stimulus, all five contrasts show significant
 bilateral clusters in the PPA but extending into posterior regions
@@
 across contrasts of the movie and the audio-description.
-% anterior vs. posterior?
-
-\subsubsection{localization performance and noise}
-% overall good isolation;  whole brain analysis and not many random clusters
-Despite performing a whole brain analysis on naturalistic stimuli with many
-uncontrolled stimuli we do not find many random clusters in single contrasts or
-even systematically across contrasts\todo{good god but that's essentially it}.
-% shit was averaged out we did not even know of
-Further, unknown stimulus features we did not even annotate did not lead to a
-variety of significant cluster across the brain that hamper interpretation of
-results.
-% movie: attention, and shit
+
+% but
+Nevertheless, results suggest that localization performance depends on the
+amount of available data and how well the feature space is modeled.
+% what's going on
+Despite performing a whole brain analysis, we do not find many (random) clusters
+in single contrasts or even systematically across contrasts that hamper the
+interpretation of results.\todo[inline]{god forgive me for this paragraph}.
+
+% other clusters
 \todo[inline]{where are no clusters? e.g. top-down / bottom-up
@@
 % BUT: amount of data
-Nevertheless, localization performance depends on the amount of available
-data\todo{give examples of contrast using less events in AV and AO}.
-% BUT: match of the stimulus type/averaged events
-Further, localization performance is also influenced by how well events
-within categories matched on average the preferred stimulus type.
-% AV: frame content
-In the AV stimulus, we averaged different kind of movie cuts regardless to the
-movie frames content.
-\todo[inline]{how well spatially constrained are the clusters?}
+Nevertheless, localization performance is influenced on the amount of available
+data\todo{give examples of contrast using less events in AV and AO} and well
+events within categories matched on average the preferred stimulus type.
+% example AV: data amount and category homogeneity
+For example in the AV stimulus, we averaged different kind of movie cuts
+regardless to the movie frames content.\todo[inline]{how well spatially
+constrained are the clusters?}
 % AO: stimulus categories
-Moreover, nouns of the narrator cueing a switch to another setting are often
-forestalled by changes of the soundscape.\todo{cross-modal control contrasts;
-all negative results at moment of cuts but vse\_new > pe\_old): right RSC.}
+For example in the AO stimulus, nouns of the narrator that cue a switch to
+another setting belong to different categories (s. above).
+% AO: number of events
+\todo[inline]{Number of events in which contrasts?}
+% example for data amount AO: superior temporal cortex
+In four of nine contrasts of the AO stimulus, we find significant
+clusters in superior auditory cortices (including early auditory
+cortices?)\todo{which exactly}
+% conclusion
+This suggests that variance correlating with lower level auditory processes was
+(not) averaged (out) across trials\todo{which contrasts; A1 \& low-level
+nuisance regressors?}
+% foreshadowing of narrator by soundscape
+Further, verbal cues are regularly forestalled by changes of the
+soundscape.\todo{cross-modal control contrasts; all negative results at moment
+of cuts but vse\_new > pe\_old): right RSC.}
 % arnott
@@
 correlate with increased activity in the PPA.
-% AO: superior temporal cortex
-Nevertheless in four of nine contrasts of the AO stimulus, we find significant
-clusters in superior auditory cortices (including early auditory
-cortices?)\todo{which exactly}
-% conclusion
-This suggests that variance correlating with lower level auditory processes was
-(not) averaged (out) across trials\todo{which contrasts; A1 \& low-level
-nuisance regressors?}
-
 % conclusion: AO and AV stability

### 2020-10-13 paper/main.tex
discussion: stability of contrast v2

@@
 % but
-Nevertheless, results suggest that localization performance depends on the
+Results also suggest that localization performance depends on the
 amount of available data and how well the feature space is modeled.
@@
 interpretation of results.\todo[inline]{god forgive me for this paragraph}.
-
-% other clusters
-\todo[inline]{where are no clusters? e.g. top-down / bottom-up
-attention, eye movements (FEF) (cf. corbetta2002control) or memory (which
-memory)?}
+% null results regarding attention and eye movements
+For example in the AV results, we do not find significant clusters that could be
+attributed to cognitive processes like attention, eye movements, or
+memory.\todo{which kind of memory}
 
 % BUT: amount of data
-Nevertheless, localization performance is influenced on the amount of available
-data\todo{give examples of contrast using less events in AV and AO} and well
+Nevertheless, localization performance is influenced by the amount of available
+data\todo{give examples of contrast using less events in AV and AO} and how well
 events within categories matched on average the preferred stimulus type.
@@
 constrained are the clusters?}
+% results
+As a result, clusters are more widespread and reach into early visual cortex.
+
+\todo[inline]{first: number of available events -> ``noise''}
+
+\todo[inline]{second: category match -> ``localization performance''}
+
 % AO: stimulus categories
 For example in the AO stimulus, nouns of the narrator that cue a switch to
-another setting belong to different categories (s. above).
-% AO: number of events
-\todo[inline]{Number of events in which contrasts?}
+another setting belong to different categories (s. above).\todo[inline]{Number
+of events in which contrasts?}
 % example for data amount AO: superior temporal cortex
-In four of nine contrasts of the AO stimulus, we find significant
-clusters in superior auditory cortices (including early auditory
-cortices?)\todo{which exactly}
+In four of nine contrasts of the AO stimulus, we find significant clusters in
+superior auditory cortices (including early auditory cortices?)\todo{which
+exactly}
 % conclusion

### 2020-10-15 paper/main.tex
Fixes to make the manuscript build
Some notes

@@
 \section{Introduction}
-
+\todo[inline]{I wonder whether we should make a general point: The construction
+  of contrasts of interests feels "messy". But this is a consequence of the
+  inability to filter the stimulus material. That "messy" part is usually not obvious from a manuscript.
+  Here we have a fixed, complex stimulus, and we have to operationalize our questions with whatever we
+have at hand. This is not necessarily exact, and looking at the robustness is a feature, not a problem}
 \todo[inline]{Limit for main text (intro and discussion) = ca. 3k words;
@@
 % literature review overview 1: imagination & haptic exploration
-At a group average level, results generalize to mental imagination of landscapes
+At a group average level, results generalize \todo{MIH: more specific? what generalizes? just some location?} to mental imagination of landscapes
 \citep{ocraven2000mental} and haptic exploration of scenes constructed from LEGO
@@
 sighted participants showed increased activation during a delayed
-matching-to-sample task of haptically explored scenes constructed from LEGO
+match-to-sample task of haptically explored scenes constructed from LEGO
 bricks compared to haptically explored abstract geometric objects.
@@
 group results a driven by individuals subjects especially in response to
-audio-only stimulation\todo{``audio-only'' sounds meh?}.
+audio-only stimulation\todo{``audio-only'' sounds meh?, MIH: Yes, and comes out of nowhere}.
 
@@
 % PPA + movie + audio-description
-We annotated cuts in the movie ``Forrest Gump'' \citep{ForrestGumpMovie}, and
+We annotated cuts \todo{MIH: only cuts relevant?} in the movie ``Forrest Gump'' \citep{ForrestGumpMovie}, and
 words spoken by an additional narrator in the movie's audio-description (i.e.
@@
 \ref{tab:av-contrasts}) to test the stability of results across different
-contrasts and exclude accidental findings.
+contrasts and exclude accidental \todo{MIH: what does this mean? exclude incidental findings? sounds like we made it look pretty...} findings.
 % contrasts are of different quality
@@
 in case the narrator uses these words to indicate a switch from one setting to
-another (e.g. ``Jenny as teenager'', ``near and old bus'')
+another (e.g. ``Jenny as teenager'', ``near an old bus'')
 % soundscapes forestalls narrator
@@
 soundscape that already cue a change of settings.
-cuts but in AO stimulus}
+cuts but in AO stimulus
 % conclusion
@@
 right PPA, bilat sup. lat. occ. cortec, LOC (l/r), right superior parietal
-lobe).
+lobe).}
 

### 2020-10-19 paper/main.tex
adjust captions of figures

@@
 group results a driven by individuals subjects especially in response to
-audio-only stimulation\todo{``audio-only'' sounds meh?, MIH: Yes, and comes out of nowhere}.
+auditory stimulus\todo{this comes out of nowhere}.
 
@@
 Nevertheless, both studies used an audio-visual stimulus and again do not
-address the question how the investigated functional areas respond during an
-audio-only stimulus.
+address the question how the investigated functional areas respond during
+auditory stimulation.
 
@@
 Encouraged by \citep{aziz2008modulation}, we focus on the audio-description as
-an audio-only paradigm. We further test the audio-description's localization
+an exclusively auditory paradigm. We further test the audio-description's localization
 performance of a ``visual area'' in individual study participants by comparing
@@
         (cf. \citep{hanke2014audiomovie}).
-        Blue: the primary $t$-contrast for the audio-description comparing
-        geometry-related nouns to non geometry-related nouns spoken by the
-        audio-description's narrator (\texttt{geo, groom > all non-geo}).
-        Red: the primary $t$-contrast for the movie comparing cuts to a new
-        setting with cuts to a familiar perspective (\texttt{vse\_new >
-        vpe\_old}).
-        Black: outline of overlapping individual PPA ROIs      \citep{sengupta2016extension}.}
+        Black: outline of overlapping individual PPA ROIs.
+        The results of audio-description's primary $t$-contrast (blue) that
+        compares geometry-related nouns to non geometry-related nouns spoken by
+        the audio-description's narrator (\texttt{geo, groom > all non-geo})
+        are overlaid over the movie's primary $t$-contrast (blue) that compares
+        cuts to a new setting with cuts to a familiar perspective
+        (\texttt{vse\_new > vpe\_old}).
+   \citep{sengupta2016extension}.}
     \label{fig:group-slices}
@@
     transformation (12 degrees of freedom).
-    Light gray: The
-    audio-description's field-of-view (cf.  \citep{hanke2014audiomovie}).
+    The results of audio-description's primary $t$-contrast (blue) that
+    compares geometry-related nouns to non geometry-related nouns spoken by
+    the audio-description's narrator (\texttt{geo, groom > all non-geo})
+    are overlaid over the movie's primary $t$-contrast (blue) that compares
+    cuts to new setting with cuts to a familiar perspective
+    (\texttt{vse\_new > vpe\_old}).
     Black: outline of the subject-specific PPA ROIs.
-    Blue:
-    the primary $t$-contrast for the audio-description comparing
-    geometry-related nouns to non-geometry-related nouns spoken by the
-    audio-description's narrator (\texttt{geo, groom > all non-geo}).
-    Red: the
-    primary $t$-contrast for the movie comparing cuts to an unfamiliar setting
-    with cuts within an familiar perspective (\texttt{vse\_new > vpe\_old}).
-    } \label{fig:subs-thresh-ppa} \end{figure*}
+    Light gray: The audio-description's field-of-view (cf.
+    \citep{hanke2014audiomovie}).}
+\label{fig:subs-thresh-ppa} \end{figure*}
 
@@
         p<.05, cluster corrected) of contrasts created to isolate the PPA.
-        Contrasts provide decreasing congruency with the spatial layout
-        hypothesis and/or progressively less data/events. The overlap across
-        contrasts is overlaid on the MNI152 T1-weighted head template (gray).
+        The audio-description's contrasts 1-8 (blue; \ref{tab:ao-contrasts})
+        are overlaid over the audio-visual movie's contrasts 1-5 (red;
+        \ref{tab:av-contrasts}), both on top of the MNI152 T1-weighted head
+        template (gray).
+        Black: outline of overlapping individual PPA ROIs.
         Light gray: The audio-description's field-of-view (cf.
-        \citep{hanke2014audiomovie}). Blue: contrasts 1-8 for the
-        audio-description (see Table \ref{tab:ao-contrasts}. Red: contrasts 1-5
-        for the audio-visual movie (see Table \ref{tab:av-contrasts}. Black:
-        outline of overlapping individual PPA ROIs
-        \citep{sengupta2016extension}.} \label{fig:stability-slices}
+        \citep{hanke2014audiomovie}).}
+    \label{fig:stability-slices}
     \end{figure*}

### 2020-10-20 code/plot-group-and-individuals.py
change z coordinate to -11

@@ -155,7 +155,7 @@ def process_stability(ao_prob, av_prob, outfpath):
     # coronal slice
     ax2 = fig.add_subplot(grid[0:12, 4:8])
     mode = 'z'
-    coord = [-9]
+    coord = [-11]
     # call the function that handles details of the plotting
     plot_stability_slice(mode,
                          coord,
@@ -332,7 +332,7 @@ def process_group_averages(outfpath):
     # plot axial / horizontal plane
     ax2 = fig.add_subplot(grid[0:12, 4:8])
     mode = 'z'
-    coord = [-9]
+    coord = [-11]
     plot_grp_slice(mode, coord,
                    BIN_MASK_GRP,
                    MOVIE_GRP,

### 2020-10-20 paper/main.tex
add info about individuals to results

@@
 
+\todo[inline]{change coordinates of figure to z=-11 as it is in the slices of
+individuals}
+
 % AV intro
@@
 % sub-01 (m): PPA (l/r), AO (l/r), AV (-/r); RSC: AO (l/r), AV (-/-)
-% sub-02 (m): PPA (l/r), AO (-/-), AV (-/r); RSC: AO (-/-), AV (-/-)
+% sub-02 (m): PPA (l/r), AO (-/-), AV (l/-); RSC: AO (-/-), AV (-/-)
 % sub-03 (f): PPA (l/r), AO (-/-), AV (-/r); RSC: AO (-/-), AV (-/-)
@@
 clusters in nine subjects, and one significant cluster in the left hemisphere of
-sub-09.
+sub-09 that within or overlapping with the PPA ROI.
 % subj-04
 In sub-04, two homologous clusters are apparent, whereas the dedicated localizer
-yielded only one cluster in the right hemisphere.
+(and AV stimulus) yielded only one cluster in the right hemisphere.
 % AV
-For the AV stimulus, results show homologous clusters in five subjects, and
-unilateral right clusters in seven subjects (of which one subjects yielded a
-unilateral cluster in the dedicated localizer).
+For the AV stimulus, results show homologous clusters in five subjects,
+unilateral right clusters in sixn subjects (of which one subjects yielded a
+unilateral cluster in the dedicated localizer), and a unilateral left cluster in
+one subject.
 % difference to dedicated localizer
-We find bilateral clusters in sub-20, whereas the dedicated localizer yielded
+We find homologous clusters in sub-20, whereas the dedicated localizer yielded
 only one cluster in the right hemisphere.
@@
     \caption{Fixed-effects individual-level GLM results (Z>3.4, p<.05
-    cluster-corrected). To facilitate comparisons across subjects, individual
-    brains are aligned via non-linear transformation to a study-specific T2*
-    group template that is co-registered to the MNI152 template with an affine
-    transformation (12 degrees of freedom).
-    The results of audio-description's primary $t$-contrast (blue) that
-    compares geometry-related nouns to non geometry-related nouns spoken by
-    the audio-description's narrator (\texttt{geo, groom > all non-geo})
-    are overlaid over the movie's primary $t$-contrast (blue) that compares
-    cuts to new setting with cuts to a familiar perspective
-    (\texttt{vse\_new > vpe\_old}).
-    Black: outline of the subject-specific PPA ROIs.
-    Light gray: The audio-description's field-of-view (cf.
-    \citep{hanke2014audiomovie}).}
-\label{fig:subs-thresh-ppa} \end{figure*}
+        cluster-corrected).
+        Individual brains are aligned via non-linear
+        transformation to a study-specific T2* group template that is
+        co-registered to the MNI152 template with an affine transformation (12
+        degrees of freedom).
+        The results of audio-description's primary
+        $t$-contrast (blue) that compares geometry-related nouns to non
+        geometry-related nouns spoken by the audio-description's narrator
+        (\texttt{geo, groom > all non-geo}) are overlaid over the movie's
+        primary $t$-contrast (blue) that compares cuts to new setting with cuts
+        to a familiar perspective (\texttt{vse\_new > vpe\_old}).
+        Black:
+        outline of subject-specific PPA ROIs.
+        Light gray: The
+        audio-description's field-of-view (cf. \citep{hanke2014audiomovie}).
+        To facilitate comparisons across subjects, we chose the same horizontal
+        slice (x=-11) for all subjects. Thus, the figure does not depict the
+        left cluster of the AV stimulus in sub-09 and sub-18, and the right
+        cluster of the AV stimulus in sub-15.}
+    \label{fig:subs-thresh-ppa}
+\end{figure*}
 

### 2020-10-28 paper/main.tex
rewrite intro

@@
 \section{Introduction}
-\todo[inline]{I wonder whether we should make a general point: The construction
-  of contrasts of interests feels "messy". But this is a consequence of the
-  inability to filter the stimulus material. That "messy" part is usually not obvious from a manuscript.
-  Here we have a fixed, complex stimulus, and we have to operationalize our questions with whatever we
-have at hand. This is not necessarily exact, and looking at the robustness is a feature, not a problem}
+
 \todo[inline]{Limit for main text (intro and discussion) = ca. 3k words;
@@
 
-\todo[inline]{retrosplenial cortex is not mentioned in intro anymore but it
-shows up in group results (mixed in individual subjects) and therefore should
-be discussed}
+\todo[inline]{studies regarding naturalistic stimuli are dropped (Hasson,
+2004: reverse correlation in PPA; Bartels, 2004: FFA and EBA). That should be
+okay since we focus on the auditory part which should be clearer now; Hasson /
+Bartels might shortly be mentioned in the discussion though}
+
+\todo[inline]{mih: Possibly cite DuPre (2019) and declare that this study is a
+    concrete realization; COH: I read it but don't know what/how to cite it for
+    any other reason than just to cite it (here or in discussion)}
 
 % brain mapping via fMRI
-Cognitive neuroscientists use brain imaging methods like blood oxygenation
-level-dependent functional magnetic resonance imaging (BOLD fMRI) to map
-perceptual and cognitive brain processes (e.g. viewing of faces
-\citep{kanwisher1997ffa} or theory of mind \citep{spunt2014validating}) to
-functional brain areas or networks.\todo{kinda aggressive introductory
-sentence}.
+Humans can perceive and make sense of their daily environment casually and
+seemingly without any effort. Cognitive neuroscientists use brain imaging
+techniques to map seemingly effortless perceptual and cognitive processes like
+seeing and recognizing faces (e.g. \citep{kanwisher1997ffa}) to functional brain
+areas or networks.
 % What is the PPA?
-A classic example of a functionally defined, higher-level visual area is the
-``parahippocampal place area'' (PPA) \citep{epstein1998ppa,
-epstein1999parahippocampal}.
+A classic example of a higher-level visual area is the ``parahippocampal place
+area'' (PPA) \citep{epstein1998ppa, epstein1999parahippocampal}.
 % anatomical location != functional location
@@
 regions of the fusiform gyrus and anterior lingual gyrus
-\citep{epstein2008parahippocampal}.
+\citep{epstein2008parahippocampal}, and thus not anatomically but functionally
+defined:
 % neural correlate of scene perception
-Increased hemodynamic activity in the PPA correlates with the perception of
-static pictures of landscapes, buildings or landmarks \citep{aguirre1998area,
-epstein2014neural, epstein1998ppa} compared to e.g. pictures of tools of faces.
-% spatial layout hypothesis
-[[According to the spatial layout hypothesis, the PPA is involved in processing
-the surface geometry of a visual stimulus and possibly in identifying scenes
-based on their spatial layout \citep{epstein2010reliable}.]]\todo{better delete}
+increased hemodynamic activity is observed in the PPA when subjects view
+pictures of landscapes, buildings or landmarks (compared to e.g. pictures of
+tools or faces) during blood oxygenation level-dependent functional magnetic
+resonance imaging (BOLD fMRI) \citep{aguirre1998area, epstein2014neural,
+epstein1998ppa}.
+
+\todo[inline]{The following review of O'Craven and Wolbers could be shortened.
+Keeping the small paragraph regarding Aziz should make the focus on auditory
+perception clearer. What do you think?}
 % literature review overview 1: imagination & haptic exploration
-At a group average level, results generalize \todo{MIH: more specific? what generalizes? just some location?} to mental imagination of landscapes
-\citep{ocraven2000mental} and haptic exploration of scenes constructed from LEGO
-blocks \citep{wolbers2011modality}.
-% literature review overview 2: spoken sentences
-One study that used spoken, place-related sentences showed significantly
-decreased activation in the left and no modulation in the right-hemispheric PPA
-\citep{aziz2008modulation}.
-
-% literature review in detail
-% O'Craven: Mental imagery
-In the study conducted by \cite{ocraven2000mental} participants viewed
-alternating blocks of pictures showing famous faces and familiar places during
-an initial experimental paradigm. In a subsequent paradigm, participants were
-instructed to ``form a vivid mental image'' of the previously viewed pictures.
+Increased hemodynamic activity in the PPA generalizes to mental imagination of
+landscapes \citep{ocraven2000mental} and haptic exploration of scenes
+constructed from LEGO blocks \citep{wolbers2011modality}.
+% O'Craven: watching pictures
+In a study conducted by \cite{ocraven2000mental} participants viewed alternating
+blocks of pictures showing famous faces and familiar places during an initial
+experimental paradigm.
+% O'Craven: mental imagery
+In a subsequent paradigm, participants were instructed to ``form a vivid mental
+image'' of the previously viewed pictures.
+% O'Craven results
 The PPA showed increased activation during imagination of places compared to
@@
 the perceptual task.
-
 % Wolbers: haptic exploration
-In the block design study conducted by \cite{wolbers2011modality} the PPA of
-sighted participants showed increased activation during a delayed
-match-to-sample task of haptically explored scenes constructed from LEGO
-bricks compared to haptically explored abstract geometric objects.
-% connectivity analysis by Wolbers
+In a block design study conducted by \cite{wolbers2011modality} the PPA of
+[sighted] participants showed increased activation during a delayed
+match-to-sample task of haptically explored scenes constructed from LEGO bricks
+compared to haptically explored abstract geometric objects.
+% Wolbers: connectivity analysis
 \todo[inline]{Wolbers performed connectivity analysis between PPA and occipital
     cortex, and compares connectivity during visual and haptic paradigm: ``The
-scene-related increase in coupling with the PPA was significantly stronger in
-multiple clusters in occipital cortex under visual than haptic stimulation
-(Figure 2B; Table S2)''}
+    scene-related increase in coupling with the PPA was significantly stronger
+    in multiple clusters in occipital cortex under visual than haptic
+stimulation (Figure 2B; Table S2)''}
 
@@
 being promised none of his group came up with a paper regarding that topic}
+
 % Aziz (2008): place related sentences
 To our knowledge only one study \citep{aziz2008modulation} investigated how
-hemodynamic activity in the PPA differs between stimulus features of spoken
-language.
+hemodynamic activity in the PPA differs between different semantic stimulus
+categories occuring in spoken language.
 % Aziz' stimuli
@@
 
-\todo[inline]{``contextual associations hypothesis''
-(\citep{aminoff2006parahippocampal, aminoff2013role}) does not show up in intro
-anymore; events/regressors cannot touch that issue; might be interesting during
-discussion of anterior/posterior PPA.}
-
 % summary if literature review
@@
 respond to visually presented spatial information.
-% shortcomings of previous studies: simplified stimuli
-Nevertheless, all reviewed studies have in common that they employed a small set
-of simplified stimuli to strictly control experimental conditions.
-% shortcomings of previous studies: task-based paradigm
-Further, they usually relied on explicit judgment-based tasks to ensure that
-participants payed attention to the stimuli.
-% disadvantage 1b: lack of validity
-Paradigms using block designs accompanied with a task have the disadvantage that
-they do not resemble our real-life experience and thus lack external validity
-\citep{westfall2016fixing} as well as ecological validity
+% three things in common
+Nevertheless, the reviewed studies usually had three things in common.
+% designed stimulus set
+First, they employed a small sets of carefully chosen stimuli. Further, stimuli
+were conceptualized to control confounding variables (e.g. color, luminance,
+size, sentence length), a process that is often not reported in
+detail.\todo{check that}
+% block-design & task
+Second, studies used block-designed paradigms to maximize detection power.
+Further, they usually employed explicit perceptual judgment to keep participants
+paying attention to the stimuli.
+% averaging
+Third, the reviewed studies averaged results across 7-11 subjects to improve
+signal-to-noise ratio (SNR).
+% disadvantages
+Conceptualized stimuli, block-design experiments and the averaging approach have
+their merits but also disandvantages.
+% designed stimulus set
+First, small sets of conceptualized stimuli presented on experimental blocks
+poorly resembles our rich and multidimensional environment that our brains are
+accommodated to [sonkusare2019naturalistic].
+% block-design & task
+Second, study participants can and will become aware about which perceptual
+process is examined in the study by merely being exposed to the experimental
+paradigm.
+% inference: validity is poor
+Thus, small sets of conceptualized stimuli and block-design experiment lack
+external validity \citep{westfall2016fixing} as well as ecological validity
 \citep{hasson2004intersubject}.
-% disadvantage 2a: averaging for group results
-Additionally, the reviewed studies averaged results across 7-11 subjects to
-improve the signal-to-noise-ratio (SNR).
-% disadvantage 2b: no individual level
-The disadvantage here is that the averaging approach does not characterize brain
-functions at an individual level, a prerequisite for the application of brain
-imaging methods in individual diagnostics (cf. \cite{dubois2016building,
-eickhoff2020towards}).
-% open questions
-This raises the question how the PPA behaves under life-like conditions, and how
-group results a driven by individuals subjects especially in response to
-auditory stimulus\todo{this comes out of nowhere}.
-
-% naturalistic stimuli
-Paradigms using naturalistic stimuli like movies
-\citep{hasson2008neurocinematics, sonkusare2019naturalistic} or narratives
-\citep{honey2012not, lerner2011topographic, silbert2014coupled} offer complex,
-continuous stimulation that better resemble the experience of our dynamic
-environment.
-% naturalistic stimuli review: intro
-Two early studies using naturalistic stimuli suggest functional specialization
-of brain areas is preserved during movie watching when many perceptual and
-cognitive processes are triggered simultaneously \citep{bartels2004mapping,
-hasson2004intersubject}.
-% Bartels (2004): Film + GLM (but surprisingly did not annotate landscapes)
-\cite{bartels2004mapping} manually annotated time points that depict faces and
-human bodies in a 22 minute clip of the movie \textit{Tomorrow Never Dies}
-\citep{tomorrowneverdies}.
-% Bartels: results
-Employing a general linear model (GLM) to model hemodynamic activity, these time
-points correlated with increased activity in the ``fusiform face area''
-\citep{kanwisher1997ffa} and ``extrastriate body area''
-\citep{downing2001bodyarea} respectively.
-% Hasson (2004): Film + (reverse) ISC
-Employing a reverse intersubject correlation, \cite{hasson2004intersubject} used
-a 30 minute clip of the movie \textit{The Good, the Bad, and the Ugly}
-\citep{goodbadugly}.
-% Hasson: method
-fMRI brain volumes showing the highest hemodynamic activity in the PPA [across
-(five) participants] were matched to the temporally corresponding movie frames.
-% Hasson: results
-Results revealed that corresponding movie frames depicted indoor and outdoor
-scenes including buildings and open fields.
-% summary naturalistic stimuli
-Nevertheless, both studies used an audio-visual stimulus and again do not
-address the question how the investigated functional areas respond during
-auditory stimulation.
-
-\todo[inline]{mih: Possibly cite DuPre (2019) and declare that this study is a
-    concrete realization; COH: I read it but don't know what/how to cite it for
-    any other reason than just to cite it (here or in discussion)}
-
-% what we did: data source
-In the current study, we analyze publicly available functional data
-(studyforrest.org) of the same 14 participants watching a movie
-\citep{hanke2016simultaneous} and listening to an audiobook.
-\citep{hanke2014audiomovie}.
-% PPA + movie + audio-description
-We annotated cuts \todo{MIH: only cuts relevant?} in the movie ``Forrest Gump'' \citep{ForrestGumpMovie}, and
-words spoken by an additional narrator in the movie's audio-description (i.e.
-the movie's audio-only variant; \citep{ForrestGumpGermanAD}) to exploratorily
-investigate how the parahippocampal gyrus behaves during more life-like
-conditions free from any task.
-% traditional GLM
-We do this by analyzing our data by constructing GLM contrasts as canonically
-used to analyze data from tightly controlled paradigms.
-% focus on audio-description
-Encouraged by \citep{aziz2008modulation}, we focus on the audio-description as
-an exclusively auditory paradigm. We further test the audio-description's localization
-performance of a ``visual area'' in individual study participants by comparing
-our results to results of a dedicated visual localizer experiment done with the
-same participants \citep{sengupta2016extension}.
+% disadvantage of averaging
+Lastly, averaging data across subjects increases the SNR but does not
+characterize brain functions at an individual level, a prerequisite for the
+application of brain imaging methods in individual diagnostics (cf.
+\cite{dubois2016building, eickhoff2020towards}).
+
+% We are different
+In this study, we operationalize the perception of landscapes and landmarks
+(compared to e.g. faces and objects) differently from the reviewed studies by
+using two fixed naturalistic stimuli (see \citep{hamilton2018revolution,
+hasson2008neurocinematics, sonkusare2019naturalistic} for reviews).
+% open research question
+Here, we investigate if increased activation in the PPA correlates with
+incidental ``spatial events'' in a Hollywood movie and its corresponding
+audio-description (i.e. the audio-only variant of the movie).
+% annotation
+We annotated words spoken by the narrator of the audio-description of the movie
+``Forrest Gump'' \citep{ForrestGumpMovie} as well as cuts and depicted locations
+in the audio-visual movie to be able to operationalize the perception of
+landscapes and landmarks (compared to e.g. persons and objects).
+% public data
+We then analyze publicly available data
+(\href{http://www.studyforrest.org}{studyforrest.org}) from the same subjects
+that listened to the audio-description and watched the movie during fMRI
+scanning.
+% first: group level AO
+First, general linear model (GLM) contrasts based on the audio-description's
+annotation are used to test if we could isolate the PPA with an auditory
+stimulus on a group level.
+% second: group level AV
+Second as conceptual/cross-modal control, we compare results of the
+audio-description to results based on the annotation of the movie.
+% individual results
+Lastly focussing on the audio-description, we compare results on the level of
+individual subjects to results of a block-designed visual localizer experiment
+done with the same individuals \citep{sengupta2016extension}.
 % results
-Our results demonstrate that (a), (b), (c)... \todo{similar to abstract and
-conclusion}
+\todo[inline]{following paragraph will be similar to abstract and conclusion}
+Our results demonstrate that (a), (b), (c).
 
@@
 
+\todo[inline]{current order of subsections might be ``non-canonical''}
+
+\todo[inline]{parts from original studies probably too detailed}
+
 \todo[inline]{Specific data outputs should be explicitly referenced via data
 citation (see Data Records and Data Citations, below)}
-\todo[inline]{current order of subsections might be ``non-canonical''}
-\todo[inline]{parts from original studies probably too detailed}
 
@@
 the movie ``Forrest Gump'', a dataset already used by \citep{hu2017decoding,
-nguyen2016integration},\todo{this is kind of a loveless list}
+nguyen2016integration},
 % AV
@@
 % todo stimuli were not designed for research purposes
-Both natural stimuli were originally designed to entertain their audiences and
-to capture attention free from any perceptual or behavioral task.
+Both natural stimuli were not design to isolate a specific brain area but to
+entertain their audiences free from any perceptual or behavioral task.
+% fixed stimuli and operationalization
+We annotated the temporal structure of the fixed stimuls material to
+operationalize the perception of different stimulus features (e.g. the
+perception of landmarks and faces) and create GLM contrasts in the subsequent
+data analysis.
 % AO annotation
-Thus for the analysis of the AO data, we extended an publicly available
-annotation of speech \citep{haeusler2020speechanno} by further annotating words
-spoken by the audio-description's narrator.
+For the analysis of the AO data, we extended an publicly available annotation of
+speech \citep{haeusler2020speechanno} by further annotating words spoken by the
+audio-description's narrator.
 % annotation procedure
@@
 % problem with hierarchical categories
-\todo[inline]{compare the following with Methods: AO contrasts \& Discussion}
-Notably, the categories \texttt{setting\_new} and \texttt{setting\_rec}
-comprise not just words that describe an abstract location (e.g. ``in
-Greenbow'') or a setting as whole (e.g. ``the platoon wades through a rice
-field'', ``in a disco''). They also comprise words that could count as a member
-of another categories in case the narrator uses these words to indicate a switch
-from one setting to another (e.g. ``near an old bus'').
+Notably, the categories \texttt{setting\_new} and \texttt{setting\_rec} comprise
+not just words that describe an abstract location (e.g. ``in Greenbow'') or a
+setting as whole (e.g. ``the platoon wades through a rice field'', ``in a
+disco''). They also comprise words that could count as a member of another
+categories in case the narrator uses these words to indicate a switch from one
+setting to another (e.g. ``near an old bus'').
 % reference to table with rules and examples
@@
 acceleration factor 3, \unit[2]{Hz/Px} bandwidth in phase encoding direction).
-% slices & FOV
+% slices
 36 axial slices (thickness \unit[1.4]{mm}, \unit[1.4 $\times$ 1.4]{mm} in-plane
@@
 direction) with a \unit[10]{\%} inter-slice gap were recorded in ascending
-order.  Slices were oriented to include the ventral portions of frontal and
-occipital cortex while minimizing intersection with the eyeballs. The field of
-view was centered on the approximate location of Heschl's gyrus.
+order.
+% slice orientation
+Slices were oriented to include the ventral portions of frontal and occipital
+cortex while minimizing intersection with the eyeballs.
+% FOV
+The field of view was centered on the approximate location of Heschl's gyrus.
 % motion correction
-EPI images were online-corrected for motion and geometric distortions [Oh, S. et
-al. 2012; In, M. \& Speck, O., 2012; Chung, J. et al., 2011]\todo{references to
-bib if this paragraph stays in the paper}. Auxiliary scans for slice alignment
-and motion- and distortion-correction were performed at the beginning of the
-first fMRI recording session and also after the break at the start of the
-recording for the second half of the movie.
+EPI images were online-corrected for motion and geometric distortions [+++Oh, S.
+et al. 2012; In, M. \& Speck, O., 2012; Chung, J. et al., 2011+++]
+% auxiliary scans
+Auxiliary scans for slice alignment and motion- and distortion-correction were
+performed at the beginning of the first fMRI recording session and also after
+the break at the start of the recording for the second half of the movie.
 % AV & VIS
@@
 resolution, \unit[240]{mm} field-of-view) and an anterior-to-posterior phase
-encoding direction were recorded in ascending order. Philips' ``SmartExam'' was
-used to automatically position slices in AC-PC orientation such that the topmost
-slice was located at the superior edge of the brain. This automatic slice
-positioning procedure was identical in the AV and VIS study, and yielded a
-congruent geometry across paradigms.
+encoding direction were recorded in ascending order.
+% slice positioning
+Philips' ``SmartExam'' was used to automatically position slices in AC-PC
+orientation such that the topmost slice was located at the superior edge of the
+brain. This automatic slice positioning procedure was identical in the AV and
+VIS study, and yielded a congruent geometry across paradigms.
 
@@
 
-\todo[inline]{I revised part of motion correction/co-registration but as usually
-I am pretty unsure about correctness}
+\todo[inline]{part regarding motion correction/co-registration might be
+incorrect}
+
 \todo[inline]{what is missing: As I see it, AO must have been downsampled
-to 2.5x2.5x2.5 mm and AV must have been upsampled from 3.0 to 2.5mm}
+to 2.5x2.5x2.5 mm and AV must have been upsampled from 3.0 to 2.5mm??}
 
@@
 \texttt{fg\_av\_ger\_lr} (left-right difference in [+++???+++] of
-consecutive movie frames).
-\texttt{fg\_av\_ger\_pd} (perceptual differences of consecutive frames).
+consecutive movie frames).\texttt{fg\_av\_ger\_pd} (perceptual differences of
+consecutive frames).
 \texttt{fg\_av\_ger\_ud} (up-down difference in [+++???+++] of consecutive movie frames).
@@
 of both naturalistic stimuli. Results demonstrate no to minor correlations (s.
-\ref{fig:reg-corr}) which suggest the models should not suffer from low
+Figure \ref{fig:reg-corr}) which suggest the models should not suffer from low
 detection power due to shared variance among regressors.
 %
-\todo{sounds meh but don't know how do write it better; results of correlations
-are given here already; maybe the short discussion (cf. very beginning of
-discussion) of these correlation could be put here too which will saves space in
-the main text; but mixing methods/results/discussion is not absolutely "clean"}
+\todo[inline]{sounds meh but don't know how do write it better; results of
+    correlations are given here already; maybe the short discussion (cf. very
+    beginning of discussion) of these correlation could be put here too which
+    will saves space in the main text; but mixing methods/results/discussion is
+not absolutely "clean"}
 
@@
 \paragraph{AO: COPEs}
+
+ \todo[inline]{I wonder whether we should make a general
+    point: The construction of contrasts of interests feels "messy". But this is
+    a consequence of the inability to filter the stimulus material. That "messy"
+    part is usually not obvious from a manuscript.  Here we have a fixed,
+complex stimulus, and we have to operationalize our questions with whatever we
+have at hand. This is not necessarily exact, and looking at the robustness is a
+feature, not a problem}
 
@@
 \todo[inline]{any concluding statement here or merely report the clusters?}
-
-\todo[inline]{change coordinates of figure to z=-11 as it is in the slices of
-individuals}
 
@@
 \todo[inline]{Seven of eight contrasts show bilaterally significant clusters in
-the retrosplenial region (and ventral precuneus)}.
+the retrosplenial region (and ventral precuneus)}
 
@@
 in single contrasts or even systematically across contrasts that hamper the
-interpretation of results.\todo[inline]{god forgive me for this paragraph}.
+interpretation of results.\todo[inline]{god forgive me for this paragraph}
 % null results regarding attention and eye movements
@@
 % Aminoff (2013)
-Aminoff (2013) in general: processing of strong,
-long-term, contextual associations elicits activity within the PHC, as well as
-the RSC (which includes regions of the retrosplenial cortex, extending into the
-posterior cingulate cortex, and the precuneus), the medial prefrontal cortex
-(MPFC), and the transverse occipital sulcus (TOS) (Figure 2) [2,3,59–67].
+\citep{aminoff2006parahippocampal, aminoff2013role}; Aminoff (2013) in general:
+processing of strong, long-term, contextual associations elicits activity within
+the PHC, as well as the RSC (which includes regions of the retrosplenial cortex,
+extending into the posterior cingulate cortex, and the precuneus), the medial
+prefrontal cortex (MPFC), and the transverse occipital sulcus (TOS) (Figure 2)
+[2,3,59–67].
 
@@
 % why naturalisti stimuli are so cool
-(see also \citep{sonkusare2019naturalistic, eickhoff2020towards,
-hamilton2018revolution})
+(see also \citep{sonkusare2019naturalistic, eickhoff2020towards,hamilton2018revolution})
 % re-use of data for independent research question

### 2020-10-28 paper/main.tex
rewrite intro2

@@
 seemingly without any effort. Cognitive neuroscientists use brain imaging
-techniques to map seemingly effortless perceptual and cognitive processes like
-seeing and recognizing faces (e.g. \citep{kanwisher1997ffa}) to functional brain
-areas or networks.
+techniques to map perceptual and cognitive processes (e.g. seeing and
+recognizing faces; \citep{kanwisher1997ffa}) to functional brain areas or
+networks.
 % What is the PPA?

### 2020-11-03 paper/main.tex
revision of result section

@@
 
-\todo[inline]{Limit for main text (intro and discussion) = ca. 3k words;
-intro is about 1k words (with to dos)}
-
-\todo[inline]{studies regarding naturalistic stimuli are dropped (Hasson,
-2004: reverse correlation in PPA; Bartels, 2004: FFA and EBA). That should be
-okay since we focus on the auditory part which should be clearer now; Hasson /
+\todo[inline]{Limit for main text (intro and discussion) = ca. 3k words;}
+
+\todo[inline]{studies regarding naturalistic stimuli are dropped (Hasson, 2004:
+reverse correlation in PPA; Bartels, 2004: GLM, FFA and EBA). That should be okay since we focus on the auditory part which should be clearer now; Hasson /
 Bartels might shortly be mentioned in the discussion though}
@@
 hemodynamic activity in the PPA differs between different semantic stimulus
-categories occuring in spoken language.
+categories occurring in spoken language.
 % Aziz' stimuli
@@
 size, sentence length), a process that is often not reported in
-detail.\todo{check that}
+detail.\todo{really? check that}
 % block-design & task
@@
 Conceptualized stimuli, block-design experiments and the averaging approach have
-their merits but also disandvantages.
+their merits but also disadvantages.
 % designed stimulus set
@@
 
-% We are different
-In this study, we operationalize the perception of landscapes and landmarks
-(compared to e.g. faces and objects) differently from the reviewed studies by
-using two fixed naturalistic stimuli (see \citep{hamilton2018revolution,
-hasson2008neurocinematics, sonkusare2019naturalistic} for reviews).
-% open research question
-Here, we investigate if increased activation in the PPA correlates with
-incidental ``spatial events'' in a Hollywood movie and its corresponding
-audio-description (i.e. the audio-only variant of the movie).
-% annotation
-We annotated words spoken by the narrator of the audio-description of the movie
-``Forrest Gump'' \citep{ForrestGumpMovie} as well as cuts and depicted locations
-in the audio-visual movie to be able to operationalize the perception of
-landscapes and landmarks (compared to e.g. persons and objects).
+% Open research question
+In this study, we investigate if increased activation in the PPA correlates with
+incidental ``spatial information'' in the audio-description of the Hollywood
+movie ``Forrest Gump'' (i.e. the audio-only variant of the movie) and, for
+cross-modal comparison, in the (actual) audio-visual movie (itself).
+% we are different
+Since we did not design the given naturalistic stimuli (see
+\citep{hamilton2018revolution, hasson2008neurocinematics,
+sonkusare2019naturalistic} for reviews) for optimal localization performance of
+the PPA, we operationalize the perception of landscapes and landmarks (compared
+to e.g. faces and objects) differently from the reviewed studies.
+% operationalization via annotation
+Here, we annotated words spoken by the narrator of the audio-description as well
+as cuts and depicted locations in the movie.
 % public data
@@
 
-\todo[inline]{current order of subsections might be ``non-canonical''}
-
-\todo[inline]{parts from original studies probably too detailed}
-
 \todo[inline]{Specific data outputs should be explicitly referenced via data
 citation (see Data Records and Data Citations, below)}
+
+\todo[inline]{parts from original studies probably too detailed}
+
+\todo[inline]{current order of subsections might be ``non-canonical''}
 
@@
 Notably, the categories \texttt{setting\_new} and \texttt{setting\_rec} comprise
-not just words that describe an abstract location (e.g. ``in Greenbow'') or a
-setting as whole (e.g. ``the platoon wades through a rice field'', ``in a
-disco''). They also comprise words that could count as a member of another
+not just words that describe an abstract location (e.g. ) or a setting as whole
+(e.g. ``in Greenbow'', ``in a disco'', ``the platoon wades through a rice
+field''). They also comprise words that could count as a member of another
 categories in case the narrator uses these words to indicate a switch from one
@@
 
-\subsubsection{first-level}
-
-\paragraph{Regressors}
-
 \todo[inline]{better speak of conditions than categories?}
 
+% first level analysis
+% regressors
 % AO: events
@@
 
-% AV events
+% AV regressors/events
 To create regressors for the AV analysis, we categorized the depicted location
@@
 
-\paragraph{AO: COPEs}
-
- \todo[inline]{I wonder whether we should make a general
-    point: The construction of contrasts of interests feels "messy". But this is
-    a consequence of the inability to filter the stimulus material. That "messy"
+\todo[inline]{MH: construction of contrasts of interests feels "messy";
+     consequence of the inability to filter the stimulus material. That "messy"
      part is usually not obvious from a manuscript. Here we have a fixed,
-complex stimulus, and we have to operationalize our questions with whatever we
-have at hand. This is not necessarily exact, and looking at the robustness is a
-feature, not a problem}
-
-\todo[inline]{send me to hell for the following paragraphs but it is detailed at
-least}
-
-% we did a couple of contrasts and why
+     complex stimulus, and we have to operationalize our questions with whatever
+     we have at hand. This is not necessarily exact, and looking at the
+ robustness is a feature, not a problem; COH: did not change a lot of text tbh
+ but should be clearer now.}
+
+% we have fixed stimuli
+Compared to previous studies we did not design the stimulus material and
+experimentally controlled conditions for the
+purpose of optimal localization performance since we used fixed stimuli.
+% 8 + 5 contrasts
 We created eight $t$-contrasts for the AO stimulus (see Table
 \ref{tab:ao-contrasts}) and five $t$-contrasts for the AV stimulus (see Table
-\ref{tab:av-contrasts}) to test the stability of results across different
-contrasts and exclude accidental \todo{MIH: what does this mean? exclude incidental findings? sounds like we made it look pretty...} findings.
+\ref{tab:av-contrasts}) to operationalize ``spatial perception'' compared to
+``non-spatial'' perception.\todo{big ouff\dots}
+% test for robustness
+Creating more than just one contrast for the two
+fixed stimuli also let us test for/the robustness of our results across varying
+ways operationalization.
 % contrasts are of different quality
@@
 
-\todo[inline]{compare the following with annotation \& Discussion}
-% intro
+% AO COPEs: intro
 In context of the AO stimulus, the categories \texttt{se\_new} and
-\texttt{se\_old} were problematic for a couple of reasons and thus are not
-included in the primary contrast:
+\texttt{se\_old} were problematic for three reasons and thus are not included in
+the primary contrast:
 % sparse auditory, rich visually
-(a) they often only vaguely describe a scene (e.g. ``black and white film
-recordings'', ``in Greenbow'') whereas a picture of the verbally described scene
-would be perceptually richer,
+(a) they often only vaguely describe a scene (e.g. ``in Greenbow'', ``in a
+disco'', ''black and white film recordings'') whereas a picture of the verbally
+described scene would be perceptually richer,
 % hierarchical categories
-(b) They also comprise words that could count as a member of another categories
-in case the narrator uses these words to indicate a switch from one setting to
+(b) they also comprise words that could count as a member of another category in
+case the narrator uses these words to indicate a switch from one setting to
 another (e.g. ``Jenny as teenager'', ``near an old bus'')
@@
 (c) the narrator is often lacking behind a short dialogue or a change of the
-soundscape that already cue a change of settings.
-cuts but in AO stimulus
+soundscape that already cue a change of settings.  cuts but in AO stimulus
 % conclusion
@@
 induce noise and would be less successful in isolating the PPA.
-
-% negative control contrasts
-Five $t$-contrasts (see Table \ref{tab:ao-contrasts}) we created as negative
-controls to test if increased activation in the PPA was correlated with
-moments of cuts and therefore possibly correlated with a accompanying change in
-the soundscape.\todo{all essentially almost null results}
-
 % furniture
@@
 regressor of interest to reduce noise.
+% negative control contrasts
+Five $t$-contrasts (see Table \ref{tab:ao-contrasts}) we created as negative
+controls to test if increased activation in the PPA was correlated with
+moments of cuts and therefore possibly correlated with a accompanying change in
+the soundscape.
 
 \begin{table*}[t]
-\caption{Contrasts of parameter estimates for the analysis of the audio-only stimulus (AO).
-Contrast 1-8 aim to isolate the PPA (\texttt{all non-geo} = body, bodypart,
-    fahead, object, sex\_f, sex\_m).
-Contrasts 9-13 serve as negative control at the moments of movie cuts that could
-    correlate with changes of the audio tracks soundscape (see Table \ref{tab:av-contrasts}).}
-
+\caption{Contrasts of parameter estimates for the analysis of the audio-only
+    stimulus (AO). Contrast 1-8 aim to isolate the PPA (\texttt{all non-geo} =
+    body, bodypart, fahead, object, sex\_f, sex\_m).
+    Contrasts 9-13 serve as negative control at the moments of movie cuts that
+    could correlate with changes of the audio tracks soundscape (see Table
+    \ref{tab:av-contrasts}).}
 \label{tab:ao-contrasts}
@@
 
-\paragraph{AV: COPEs}
-
-\todo[inline]{I think it's better to explain the rationale of the regressors
+\todo[inline]{MH: I think it's better to explain the rationale of the regressors
 here in the context of the contrasts and not already above in the list of
-created regressors}
-
-% intro
+created regressors: COH: yes, I checked that. Above is just a short
+list/explanation except for ``no cut'' condition. imo it makes more sense to
+explain it there but maybe I cannot get the reason why you think it fits here
+better}
+
+% AV COPEs: intro
 In context of the AV stimulus, we categorized the frames following a movie cut
@@
 % negative control
-Five additional $t$-contrasts we created for negative control purposes (see
-Table \ref{tab:av-contrasts}).
-\todo[inline]{all null results; except cope 10 (nouns of narrator but in movie):
-right PPA, bilat sup. lat. occ. cortec, LOC (l/r), right superior parietal
-lobe).}
+Five additional $t$-contrasts we created for negative control purposes
+(see Table \ref{tab:av-contrasts}) by using regressors based on regressors of
+the AO stimulus.
 
@@
 
-\paragraph{alignment etc.}
-
+% alignments
 % single subjects (for Bland-Altman-Plots) 1st level
@@
 On the one hand, subject-specific BOLD T2* time series were anatomically aligned
-via linear transformation to a subject-specific, study-specific T2* template (cf
-. \citep{sengupta2016extension}).
+via linear transformation to a subject-specific, study-specific T2* template
+(cf. \citep{sengupta2016extension}).
 % group template (for group and individual brain slices)
@@
 
+\todo[inline]{I consider tables of significant clusters for all contrasts as
+overkill. Maybe in ``supporting material'' or reference to dataset?  all sign.
+clusters of all contrasts are in the comments}
+
 % study goal
@@
 % what we did
-We used annotations of a \unit[2]{h} movie and it's temporally aligned
-audio-description to create canonical GLM contrasts of modeled hemodynamic
-activity resembling analyses of previous studies using simplified stimuli.
-% comparison AO & AV
-We compare these results on a group and individual level to results gained from
-an audio-visual naturalistic stimulus and to results from a dedicated visual
-localizer experiment.
-
-\todo[inline]{the big question: where to put the ``stability of contrasts''? any
-position in the results has pro's and con's; at the moment they come last}
-
-\subsection{primary contrasts}
+We annotated a \unit[2]{h} movie and its temporally aligned audio-description to
+create GLM contrasts similar to previous studies that used simplified stimuli.
+% group level
+On a group average level, we compare results gained from both naturalistic
+stimuli to results gained from a visual localizer experiment.
+% individual level
+On the level single subjects, we also assess localization performance of a
+``visual area'' using the auditory stimulus.
+
+% all AO contrasts
+% 1 PPA (l/r); RSC (l/r), LOC (l/r)
+% 2 PPA (l/r); RSC (l/r), LOC (l/r), r. sup.temp.C., r.fr.pole; putamen; etc
+% 3 PPA (l/r); RSC (l/r), LOC (l/r),l&r sup.temp.C., anterior cing., paracing.
+% 4 PPA (l/r); RSC (l/r), LOC (l/r)
+% 5 PPA (l/r); RSC (l/r), LOC (-/-)
+% 6 PPA (l/r); RSC (l/r), LOC (l/-), l&r sup.temp.C.; medial pref. c., precun
+% 7 PPA (-/-); RSC (l/r), LOC (l/-), l&r sup.temp.C
+% 8 PPA (-/-); RSC (-/-), LOC (-/-)
+% ---------- control contrasts ----------
+% 9 PPA (-/-); RSC (-/r), LOC (-/-), left pars triangularis
+%10 PPA (-/-); RSC (-/-), LOC (-/-)
+%11 PPA (-/-); RSC (-/-), LOC (-/-),
+%12 PPA (-/-); RSC (-/-), LOC (-/-), right posterior hippocampus
+%13 PPA (-/-); RSC (-/-), LOC (-/-) results: PPA
+
+% all AV contrasts
+% 1 PPA (l/r); RSC (l/r), LOC (l/r), VisC (l/r),
+% intracalcarine, cuneal, ling.c
+% 2 PPA (l/r); RSC (-/-), LOC (l/r), VisC (-/-)
+% 3 PPA (l/r); RSC (-/-), LOC (-/-), VisC (-/r), occ. fusisf. g.
+% 4 PPA (l/r); RSC (l/r), LOC (l/r), VisC (-/-), lingual g., occ. fusif. g.
+% 5 PPA (l/r); RSC (l/r), LOC (l/r), VisC (-/-), occ. fusif. g.
+% ---------- control contrasts ----------
+% 6 nothing
+% 7 nothing
+% 8 nothing
+% 9 nothing
+%10 se_new > se_old (nouns but in AV stimulus):
+% LOC (l/r) right PPA, bilateral sup. lat. occ. c., sup. parietal lobe (right)
+
+\subsection{Group results (all AO + AV PPA contrasts)}
 
 \todo[inline]{paragraphs start with 1-2 sentences that set up the question
-that the paragraph answers; e.g. ``To verify that there are no artifacts''}
-
-\todo[inline]{middle of paragraph presents data and logic that pertain the
+that the paragraph answers; e.g. ``To verify that\dots''}
+
+\todo[inline]{middle of paragraph presents data \& logic that pertain the
 question}
@@
 
-% the contrast in detail
+% intro
+First on a group average level, we tested if we could isolate the PPA using GLM
+contrasts based on the audio-description's annotation of speech.
+% primary AO contrast
 The primary $t$-contrast for the audio-description (\texttt{geo, groom > all
-non-geo}) that we used to isolate the PPA yielded six significant clusters (see
-Table \ref{tab:res-ao-group1}, Figure \ref{fig:group-slices}).
-% PPA
+non-geo}) yielded six significant clusters (see Table \ref{tab:res-ao-group1},
+Figure \ref{fig:group-slices}).
+% overlap with ROI
 Two homologous clusters are located in the anterior part of the PPA group
 overlap that we gained from the visual localizer experiment.
-% location
-More specifically, the clusters of the current analysis are at the borders of
-the posterior parahippocampal cortex, the occipital and temporal fusiform gyrus
-and lingual gyrus \todo{the clusters are small but that's what the
-Harvard-Oxford Atlas suggests, clusters are at the border of the reported areas;
-cf. location of PPA in the introduction clusters}.
+% in detail
+specifically, the clusters of the current analysis are at the borders of the
+posterior parahippocampal cortex, the occipital and temporal fusiform gyrus and
+lingual gyrus.
 % precuneus
-Additionally, two additional clusters are located in the ventral precuneus
-extending into the retrosplenial cortex.
+Two additional clusters are located in the ventral precuneus extending into the
+retrosplenial cortex.
 % LOC
-Finally, the contrast yielded two homologous clusters in the superior lateral
-occipital cortex.
+Finally, two homologous clusters are located in the superior lateral occipital
+cortex.
+% concluding statement
 \todo[inline]{any concluding statement here or merely report the clusters?}
 
-% AV intro
-For cross-modal comparison purposes, we also analyzed data from the audio-visual
-movie by contrasting different kinds of movie cuts independent(ly) from the
-frames' visual content after the cuts.
-% the primary contrast
-The movie's primary $t$-contrast that compared cuts to an unfamiliar setting
-with cuts within familiar setting (\texttt{vse\_new > vpe\_old}) yielded three
-significant clusters (see Table \ref{tab:res-av-group1}, Figure
-\ref{fig:group-slices}).
-% PPA + others.
-One cluster spans across the midline and comprises, from posterior to anterior,
-parts of the intracalcarine and cuneal cortex, lingual gyrus and retrosplenial
-cortex, occipital fusiform gyrus and temporal fusiform gyrus, and the
-parahippocampal cortex of both hemispheres.
-% LOC
-Two additional homologous clusters are located in the superior lateral occipital
-cortex (left bigger than right).
-
+% table group results primary AO contrast
 \begin{table*}[t]
@@
 
+% figure group results primary AO & AV contrasts
+\begin{figure*} \centering
+    \includegraphics[width=\linewidth]{figures/group-slices}
+    \caption{Mixed-effects group-level (N=14) GLM results. Significant clusters
+        (Z>3.4, p<.05 cluster-corrected) are overlaid on the MNI152 T1-weighted
+        head template (gray).
+        Light gray: The audio-description's field-of-view
+        (cf. \citep{hanke2014audiomovie}).
+        Black: outline of overlapping individual PPA ROIs.
+        The results of audio-description's primary $t$-contrast (blue) that
+        compares geometry-related nouns to non geometry-related nouns spoken by
+        the audio-description's narrator (\texttt{geo, groom > all non-geo})
+        are overlaid over the movie's primary $t$-contrast (blue) that compares
+        cuts to a new setting with cuts to a familiar perspective
+        (\texttt{vse\_new > vpe\_old})
+   \citep{sengupta2016extension}.}
+    \label{fig:group-slices}
+\end{figure*}
+
+% all eight AO PPA contrasts
+In order to test the robustness of our findings, we created seven additional
+$t$-contrasts for the AO stimulus (see Table \ref{tab:ao-contrasts}).
+% results
+Six of the overall eight AO contrasts show significant bilateral clusters in
+anterior regions of the group PPA overlap (see Figure
+\ref{fig:stability-slices}.\todo{discuss that contrasts make ``less and less''
+sense}
+% statement/answer
+Results suggest that our findings do not depend on one specific contrasts but
+are robust across differently designed contrasts.
+% question
+\todo[inline]{concluding statement often feels like interpretation/discussion.
+Dunno if that is okay.}
+
+% precuneus = retrosplenial cortex ?
+\todo[inline]{significant clusters in other regions than PPA could or should (?)
+also be reported? Following is a short list:}
+% ventral precuneus = retrosplenial cortex?
+7 contrasts: bilateral clusters in RSC (and ventral precuneus);
+% transverse occipital sulcus = occipital place area
+6 contrasts (4 bilat.): transverse occipital sulcus (= OPA?);\todo{check again}
+% confounds
+4 contrasts: right superior temporal gyrus; 3 contrasts: left superior temporal
+gyrus; 3 contrasts: some (smallish) prefrontal clusters
+
+% AO negative control contrasts
+\todo[inline]{control contrast at moment of cuts but in the audio-description
+(contrasts 9-13) could be, if at all, mentioned here already; at the moment
+negative control contrasts come last combined for AO \& AV at the end}
+
+% figure group results of robustness across all AO & AV contrasts
+\begin{figure*} \centering
+    \includegraphics[width=\linewidth]{figures/stability-slices}
+    \caption{Stability of contrasts. Overlap of significant clusters (Z>3.4;
+        p<.05, cluster corrected) of contrasts created to isolate the PPA.
+        The audio-description's contrasts 1-8 (blue; \ref{tab:ao-contrasts})
+        are overlaid over the audio-visual movie's contrasts 1-5 (red;
+        \ref{tab:av-contrasts}), both on top of the MNI152 T1-weighted head
+        template (gray).
+        Black: outline of overlapping individual PPA ROIs.
+        Light gray: The audio-description's field-of-view (cf.
+        \citep{hanke2014audiomovie}).}
+    \label{fig:stability-slices}
+    \end{figure*}
+
+% AV intro
+Second as conceptual/cross-modal control of the group average results, we
+analyzed data from the audio-visual movie by contrasting different kinds of
+movie cuts independent(ly) from the frames' visual content following the cuts.
+% AV primary contrast
+The movie's primary $t$-contrast that compared cuts to an unfamiliar setting
+with cuts within familiar setting (\texttt{vse\_new > vpe\_old}) yielded three
+significant clusters (see Table \ref{tab:res-av-group1}, Figure
+\ref{fig:group-slices}).
+% PPA (others the clusters extend into).
+One cluster spans across the midline and comprises (reported from posterior to
+anterior), parts of the intracalcarine and cuneal cortex, the lingual gyrus and
+retrosplenial cortex, the occipital and temporal fusiform gyrus and the
+parahippocampal cortex in both hemispheres.
+% LOC
+Two additional homologous clusters are located in the superior lateral occipital
+cortex (left bigger than right).
+
 \begin{table*}[t]
@@
 
-\begin{figure*} \centering
-    \includegraphics[width=\linewidth]{figures/group-slices}
-    \caption{Mixed-effects group-level (N=14) GLM results. Significant clusters
-        (Z>3.4, p<.05 cluster-corrected) are overlaid on the MNI152 T1-weighted
-        head template (gray).
-        Light gray: The audio-description's field-of-view
-        (cf. \citep{hanke2014audiomovie}).
-        Black: outline of overlapping individual PPA ROIs.
-        The results of audio-description's primary $t$-contrast (blue) that
-        compares geometry-related nouns to non geometry-related nouns spoken by
-        the audio-description's narrator (\texttt{geo, groom > all non-geo})
-        are overlaid over the movie's primary $t$-contrast (blue) that compares
-        cuts to a new setting with cuts to a familiar perspective
-        (\texttt{vse\_new > vpe\_old}).
-   \citep{sengupta2016extension}.}
-    \label{fig:group-slices}
-\end{figure*}
+% all eight AV PPA contrasts
+Here again in order to test the robustness of our findings, we created four
+additional $t$-contrasts for the AV stimulus (see Table \ref{tab:av-contrasts}).
+%% results: PPA
+All of the overall five AV contrasts yielded significant bilateral clusters (in
+that overlap with the PPA group mask/overlap [biggest overlap in posterior part
+of group ROI = temporal occipital fusiform cortex] (see Figure
+\ref{fig:stability-slices}).
+% lingual gyrus
+In three contrasts, these homologous clusters extend into the lingual gyri.
+% to do
+\todo[inline]{check regions again for posterior PPA (cf. text/clusters regarding
+group results); border of lingual gyrus belongs to PPA}
+% RSC
+Further, three contrasts show significant homologous clusters in the RSC.
+% LOC
+Lastly, four contrasts show significant homologous clusters in lateral occipital
+cortices.
+% concluding statement
+Here again, we can show that results can in principle be accomplished by varying
+the design of the contrasts.
+% question
+\todo[inline]{concluding statement = interpretation/discussion?}
+
+\subsection{negative controls}
+
+\todo[inline]{these contrasts are listed in the methods section. Shall results
+of these contrasts be reported here (at all) as well?}
+
+% AO stimulus
+AO stimulus (using annotation of movie cuts) all null results except: contrast 9
+(vse\_new > pe\_old): right RSC
+% correlation of these nouns with cuts
+(cf. Figure \ref{fig:reg-corr}: nouns that cue change to a new setting are
+``somewhat'' correlated with cuts to a new setting; nouns that cue change to a
+familiar setting are somewhat correlated with cuts to a familiar setting).
+
+% AV stimulus
+AV stimulus. All contrasts using ``no cut condition'' > x yield null results.
+The contrast that uses the narrator's nouns but in the AV stimulus (se\_new >
+se\_old): right PPA, bilateral sup. lat. occ. cortex; LOC (l/r), right superior
+parietal lobe; here again: these kind of nouns and these kind of cuts are
+correlated.
 
@@
     \label{fig:bland-altman} \end{figure*}
-
-\subsection{stability contrasts}
-
-\todo[inline]{I consider tables of significant clusters for every contrast as
-overkill. Tables for just the ``primary contrast'', seems more appropriate; the
-level of details explained depends on the discussion; atm moment I feel it
-should be discussed more than expected; hence, following some notes as to dos}
-
-\todo[inline]{as mentioned before: this section would also make sense to be at
-the top or middle of the results; I moved it back and forth A LOT already}
-
-\todo[inline]{s. comments for overview of sign. clusters in all contrasts}
-
-% why we did different contrasts
-We created different $t$-contrasts for the AO stimulus (see Table
-\ref{tab:ao-contrasts}) and for the AV stimulus (see Table
-\ref{tab:av-contrasts}) to test the stability of results across different
-contrasts and exclude accidental findings.
-
-% all AO contrasts
-% 1 PPA (l/r); RSC (l/r), LOC (l/r)
-% 2 PPA (l/r); RSC (l/r), LOC (l/r), r. sup.temp.C., r.fr.pole; putamen; etc
-% 3 PPA (l/r); RSC (l/r), LOC (l/r),l&r sup.temp.C., anterior cing., paracing.
-% 4 PPA (l/r); RSC (l/r), LOC (l/r)
-% 5 PPA (l/r); RSC (l/r), LOC (-/-)
-% 6 PPA (l/r); RSC (l/r), LOC (l/-), l&r sup.temp.C.; medial pref. c., precun
-% 7 PPA (-/-); RSC (l/r), LOC (l/-), l&r sup.temp.C
-% 8 PPA (-/-); RSC (-/-), LOC (-/-)
-% control contrasts
-% 9 PPA (-/-); RSC (-/r), LOC (-/-), left pars triangularis
-%10 PPA (-/-); RSC (-/-), LOC (-/-)
-%11 PPA (-/-); RSC (-/-), LOC (-/-),
-%12 PPA (-/-); RSC (-/-), LOC (-/-), right posterior hippocampus
-%13 PPA (-/-); RSC (-/-), LOC (-/-)
-
-% results
-The overlap of significant clusters of the eight contrast for the
-audio-description, and five contrasts computed for the movie can be found in
-Figure \ref{fig:stability-slices}.
-% results in PPA
-In the analysis of the AO stimulus, six of eight contrasts show significant
-bilateral clusters in anterior regions of the group PPA
-overlap.\todo[inline]{temporal occipital fusiform gyrus according to
-Harvard-Oxford Cortical Structural Atlas}
-% statement/answer
-This suggest results are reproducible in a variety of contrasts and do not
-depend on the design of one specific contrasts.
-% individual results
-Notably, we chose one contrast to look into individual results of all subjects
-but individually a contrast different from the primary contrast might lead to
-better individual localization results.\todo{concluding statements often feel
-like interpretation/discussion to me}
-
-% Precuneus = retrosplenial cortex ?
-\todo[inline]{Seven of eight contrasts show bilaterally significant clusters in
-the retrosplenial region (and ventral precuneus)}
-
-% transverse occipital sulcus
-\todo[inline]{transverse occipital sulcus / occipital place area? in 6 of 8
-contrasts (4 bilaterally)}
-
-% confounds
-\todo[inline]{``other clusters'' (confounds?): right superior temporal gyrus (4
-contrasts); left superior temporal gyrus (3 contrasts); some prefrontal clusters
-that show up in two contrasts}
-
-% control in AO contrasts
-\todo[inline]{control contrast essentially almost all none results; s. comments}
-
-% all AV contrasts
-% 1 PPA (l/r); RSC (l/r), LOC (l/r), VisC (l/r), intracalcarine, cuneal, ling.c
-% 2 PPA (l/r); RSC (-/-), LOC (l/r), VisC (-/-)
-% 3 PPA (l/r); RSC (-/-), LOC (-/-), VisC (-/r), occ. fusisf. g.
-% 4 PPA (l/r); RSC (l/r), LOC (l/r), VisC (-/-), lingual g., occ. fusif. g.
-% 5 PPA (l/r); RSC (l/r), LOC (l/r), VisC (-/-), occ. fusif. g.
-% control contrasts
-% 6 nothing
-% 7 nothing
-% 8 nothing
-% 9 nothing
-%10 se_new > se_old (nouns in AV stim): LOC (l/r)
-% right PPA, bilateral sup. lat. occ. c., superior parietal lobe (right)
-
-% AV intro
-For the analysis of the AV stimulus, we created five contrasts for a cross-modal
-comparison.
-% PPA
-All five AV contrasts yielded significant bilateral clusters in (temporal)
-occipital, fusiform cortex showing congruency with the group overlap of
-individual PPA ROIs.\todo{must be in posterior PPA as well}
-% lingual gyrus
-In three contrasts, these homologous clusters extend into the lingual
-gyri.\todo[inline]{check regions and contrasts that are located outside of the
-PPA; border of lingus belongs to PPA}
-% RSC
-Further, three contrasts show significant homologous clusters in the RSC.
-% LOC
-Lastly, four contrasts show significant homologous clusters in lateral occipital
-cortices.
-% statement/answer
-Here again, we can show that results can in principle be accomplished by varying
-the design of the contrasts.\todo{concluding statement =
-interpretation/discussion?}
-
-% control AV
-\todo[inline]{control in AV stim: se\_new > se\_old (nouns in AV stim): LOC
-(l/r), right PPA, bilateral sup. lat. occ. c., superior parietal lobe (right)}
-
-\begin{figure*} \centering
-    \includegraphics[width=\linewidth]{figures/stability-slices}
-    \caption{Stability of contrasts. Overlap of significant clusters (Z>3.4;
-        p<.05, cluster corrected) of contrasts created to isolate the PPA.
-        The audio-description's contrasts 1-8 (blue; \ref{tab:ao-contrasts})
-        are overlaid over the audio-visual movie's contrasts 1-5 (red;
-        \ref{tab:av-contrasts}), both on top of the MNI152 T1-weighted head
-        template (gray).
-        Black: outline of overlapping individual PPA ROIs.
-        Light gray: The audio-description's field-of-view (cf.
-        \citep{hanke2014audiomovie}).}
-    \label{fig:stability-slices}
-    \end{figure*}
-
-\subsection{cross-modal and negative controls}
-
-\todo[inline]{the contrasts are listed in the methods section. shall results of
-these contrasts be reported here as well?}
-
-\todo[inline]{there are only two control contrasts that yield significant
-clusters. AO stimulus using annotation of movie cuts (vse\_new > pe\_old): right
-RSC. AV stimulus using annotation of the narrator (se\_new > se\_old): right
-PPA.}
 
@@
 
+% individual results
+Notably, we chose one contrast to look into individual results of all subjects
+but individually a contrast different from the primary contrast might lead to
+better individual localization results.
+
 \subsubsection{AO stimulus}

### 2020-11-04 paper/main.tex
revision of discussion until anterior vs. posterior PPA

@@
 % results
-\todo[inline]{following paragraph will be similar to abstract and conclusion}
+\todo[inline]{following paragraph will be similar to abstract, intro to
+discussion and conclusion}
 Our results demonstrate that (a), (b), (c).
@@
 anterior regions of the group PPA overlap (see Figure
-\ref{fig:stability-slices}.\todo{discuss that contrasts make ``less and less''
-sense}
+\ref{fig:stability-slices}.\todo{Discussion: discuss that contrasts make ``less
+and less'' sense}
 % statement/answer
@@
 % question
-\todo[inline]{concluding statement often feels like interpretation/discussion.
-Dunno if that is okay.}
+\todo[inline]{concluding statement often feels like interpretation/discussion}
 
@@
 % transverse occipital sulcus = occipital place area
-6 contrasts (4 bilat.): transverse occipital sulcus (= OPA?);\todo{check again}
+6 contrasts (4 bilat.): transverse occipital sulcus (= OPA?);\todo{AO: clusters
+are more lateral; AV: clusters are more medial}
 % confounds
@@
 In three contrasts, these homologous clusters extend into the lingual gyri.
-% to do
-\todo[inline]{check regions again for posterior PPA (cf. text/clusters regarding
-group results); border of lingual gyrus belongs to PPA}
 % RSC
@@
 parietal lobe; here again: these kind of nouns and these kind of cuts are
-correlated.
+correlated (cf. Figure \ref{fig:reg-corr}).
 
@@
 Time series of all subjects were analyzed both in group space and subject space.
+% individual z-maps -> dataset
+Results of the analyses that were performed in each subject's subject-space
+(unthresholded $z$-maps and thresholded $z$-maps with Z>2.3, p<.05 cluster
+corrected) can be found in the accompanying dataset.
 % report here in group space
@@
 and AV $t$-contrast, and the outline of the individual PPAs
-\citep{sengupta2016extension} overlayed on the MNI152 template (horizontal slice
-z=-11 for all subjects).
-% individual z-maps -> dataset
-Results of the analyses that were performed in each subject's subject-space
-(unthresholded $z$-maps and thresholded $z$-maps with Z>2.3, p<.05) can be found
-in the accompanying dataset.
+\citep{sengupta2016extension} overlayed on the MNI152 template (transversal slice z=-11 for all subjects).
+
 % results in detail voxels of significant clusters in PPA ROI (and  RSC
@@
 % PPA ROI (Sengupta et al., 2016)
-The dedicated localizer \citep{sengupta2016extension} shows ROIs in 12 of 14
-subjects and unilateral right clusters in two subjects (sub-04, sub-20).
-% subjective threshold
-Individual ROIs were assessed by visually inspecting unthresholded $z$-maps, and
-setting a subjectively best fitting $z$-threshold to isolate a ROI that matched
-the PPA.
+The dedicated localizer \citep{sengupta2016extension} yielded bilateral ROIs in
+12 of 14 subjects and a unilateral right clusters in two subjects (sub-04,
+sub-20).
+% procedure in Sengupta
+Individual ROIs were assessed by visually inspecting unthresholded $z$-maps of
+three different contrasts, and setting a subjectively best fitting $z$-threshold
+to isolate a ROI that matched the PPA.
 % AO
-In the current analysis of the AO stimulus, we find significant bilateral
-clusters in nine subjects, and one significant cluster in the left hemisphere of
-sub-09 that within or overlapping with the PPA ROI.
+In the current analysis of the AO stimulus, we use the same AO (and AV) contrast
+for all subjects. We find statistically significant bilateral clusters in nine
+subjects, and one cluster in the left hemisphere of sub-09 that are within or
+overlapping with the PPA ROI.
 % subj-04
@@
 % AV
-For the AV stimulus, results show homologous clusters in five subjects,
-unilateral right clusters in sixn subjects (of which one subjects yielded a
+Results of the AV contrast yield homologous clusters in five subjects,
+unilateral right clusters in six subjects (of which one subjects yielded a
 unilateral cluster in the dedicated localizer), and a unilateral left cluster in
@@
 only one cluster in the right hemisphere.
-
-\todo[inline]{concluding statements?}
+% concluding statement
+\todo[inline]{concluding statement that does not sound like
+interpretation/discussion?}
 
@@
 
-\subsection{Bland-Altman-Plots}
-
-\todo[inline]{anything else to report here? seems more like just an explanation
-of the plots}
-
-% why it was done
-To better depict the agreement (and difference) between individual results of
-the dedicated visual localizer and contrast 1 of the AO paradigm, we created one
+\todo[inline]{anything else to report in the following paragraph? seems more
+like just an explanation of the plots}
+% Bland-Altman-Plots: why they were done
+To better depict/convey the agreement and difference between individual results
+of the dedicated visual localizer and the primary AO contrast, we created one
 Bland-Altman-Plots for each of the 14 subjects (see Figure
@@
 % masking
-We constrained the number of voxels in three ways as indicated by three colors
-(grey, blue, red).
-% masking in detail
 Voxels were spatially constrained to a) voxels located in the occipital and
-temporal lobes (gray; using the (probabilistic) Jülich Histological Atlas
+temporal lobes (gray; using the probabilistic Jülich Histological Atlas
 \citep{eickhoff2005toolbox, eickhoff2007assignment}), b) voxels located in the
@@
 
-\todo[inline]{the biggest question: where does the discussion of the stability
-of contrasts fit the best?}
-
-\todo[inline]{in general: discussion explains how results fill gap identified in
+\todo[inline]{the structure is as follows at the moment: correlation of
+regressors; AO group; AV group; robustness AO + AV; anterior vs posterior PPA;
+other clusters significant across contrasts (= retrosplenial cortex and
+occipital place area)}
+
+\todo[inline]{discussion explains how results fill gap identified in
 intro}
 
-\todo[inline]{provides caveats to the interpretation describes how paper
+\todo[inline]{provides caveats to the interpretation describes how the paper
 advances the field by providing new opportunities}
@@
 % previous studies: visual
-On the one hand, previous studies reported bilaterally increased hemodynamic
-activity in the PPA when participants were watching static pictures of landscape
-compared to face or objects (e.g. \citep{epstein1998ppa,
-epstein1999parahippocampal})
-% previous study: auditory
-On the other hand, a study using spoken sentences reported mixed results
-\citep{aziz2008modulation}.
-% what we did
-Hence, we use analogous statistical models in three different experimental
-paradigms to compare results gained from a dedicated visual localizer to results
-we gained from a movie and the movie's audio-description.
-% We focus
-Our results suggest that the perception of verbal spatial cues embedded in an
-auditory narrative contrasted with non-spatial cues correlate with increased
-activation in the PPA of both hemispheres.
+Previous studies reported bilaterally increased hemodynamic activity in the PPA
+when participants were watching static pictures of landscape compared to face or
+objects (e.g. \citep{epstein1998ppa, epstein1999parahippocampal}) whereas one
+study using spoken sentences reported mixed results \citep{aziz2008modulation}.
+% we use similar statistical models but with naturalistic stimuli
+Here, we use statistical models that are similar to previous studies that used
+small sets of experimentally controlled stimuli to investigate hemodynamic brain
+responses during two naturalistic stimuli.
+% more than just one contrast
+We computed varying GLM contrasts that differed in the contrasted categories and
+the amount of available data to test the robustness of our findings in both
+stimuli.
+% comparison to localizer experiment
+We compare results of the primary contrast of each stimulus on the level of
+individual subjects to results that we gained from a dedicated visual localizer
+paradigm done with the same subjects \citep{sengupta2016extension}.
+% summary of results main finding
+Results of our whole-brain analyses suggest that the perception of verbal
+``spatial information'' embedded in an auditory narrative contrasted with
+``non-spatial information'' correlate with increased activation in the PPA of
+both hemispheres.
+% to do
+\todo[inline]{this is just the main finding; other possible ``honourable''
+mentions like robustness of results, AV stimulus, individual results?}
 
@@
 
-\todo[inline]{could maybe pasted into method section to save space here; a short
-interpretation is given there already}
+\todo[inline]{Following paragraph could pasted into method section to save space
+here; a short interpretation is given there already; so methods/ results/
+discussion are not absolutely separated there already}
 % stimuli not designed for research purposes
@@
 
-\subsection{group level}
-
-\todo[inline]{discuss only PPA here}
-% intro
-We performed whole-brain analyses on data from the audio-visual movie and its
-audio-description. We chose one contrast of each stimulus to be investigated not
-just on a group level but also on the level of individual subjects. Additional
-contrasts were tested to investigate the stability of results across contrasts
-when contrasted categories and the amount of available data is varied.
-
-\subsubsection{AO stimulus}
-
-% AO stimulus cluster location
-Group results of the AO stimulus' primary contrast yielded spatially
-concise / restricted clusters in the anterior part of the PPA group overlap
-taken from \citep{sengupta2016extension}.
+\subsection{group level: AO \& AV (PPA only)}
+
+% AO stimulus
+Group results of the AO stimulus' primary contrast yielded spatially concise
+clusters in the anterior part of the PPA group overlap taken from
+\citep{sengupta2016extension}.
 % diff to Aziz (2008)
 Unlike \citep{aziz2008modulation} we did not use whole sentences as events to
-model hemodynamic responses but modeled from on- to offset of single words
-that cue the listener about the movie's missing visual content.
+model hemodynamic responses but modeled from on- to offset of single words that
+cue the listener about the movie's missing visual content.
 % conclusion
@@
 
-% transition to task topic
-Moreover unlike most previous studies, our paradigm was free of any task.
-%
+% Previous studies used tasks
+Usually studies that use small sets of experimentally controlled stimuli also
+employ a task to keep subjects attentive to the stimuli.
+% but epstein1998
 Nevertheless, one early block-design study \citep{epstein1998ppa} compared
@@
 Our paradigm still differs from previous studies because the relevant stimulus
-features were incidentally embedded in a continuous auditory stream.
+features were incidentally embedded in a continuous stream of auditory
+information.
 % conclusion
@@
 
-\paragraph{shortcomings of AO contrasts}
+\todo[inline]{following: how to frame it (better) that AV merely serves as
+conceptual control?; imo should be a small section anyway}
+% AV stimulus
+Group results of the AV stimulus' primary contrast yielded bilateral clusters
+that span the group overlap of individual PPAs from anterior to posterior and
+expand into retrosplenial regions.
+% difference in location/size to AO and VIS
+Clusters also expand into more posterior regions (occipital fusiform gyrus,
+lingual gyrus, and intracalcarine cortex).\todo{which of these regions (do not
+overlap) with group ROI?}
+% confound of higher perception
+This can be attributed to the fact that we averaged the content of individual
+frames after a cut and did not control for confounding features like depicted
+faces or objects.
+% confounds of lower perception
+It further suggest low-level visual features were not averaged out leading to
+clusters spanning the intracalcarine cortex.
+% cross-modal control purpose?
+\todo[inline]{concluding statement regarding AV vs AO and cross-modality of
+results?}
+
+\subsection{stability of contrasts}
+
+% why we did a couple of contrasts
+For both stimuli we created additional contrasts that varied the amount of
+events available for the analysis and how well the annotated events within
+categories on average matched the stimulus type that we assumed to be
+preferentially processed in the PPA.
+% PPA AO
+Regarding contrasts of the AO stimulus, six of eight contrasts show significant
+bilateral clusters in the anterior part of the group PPA.
+% PPA AV
+Regarding contrasts of the AV stimulus, all five contrasts show significant
+bilateral clusters in the PPA but extending into posterior regions.
+% results indicate robustness
+Results of the additional contrasts indicate that our findings are robust across
+contrasts and do not depend on the design of one specific contrasts.
+
+% but
+Nevertheless, results also suggest that localization performance depends on the
+amount of available data and how well the feature space is modeled.
+% example
+For example, contrast 8 of the AO stimulus (\texttt{se\_new} > texttt{se\_old})
+that used the most heterogeneous categories comprising the least amount of
+events yielded neither a significant cluster in the right-hemispheric nor
+left-hemispheric PPA ROI.
+% concluding statement
+Hence, investigators using model-driven analyses have to consider how many
+events a stimulus to be chosen may provide and how homogeneous the events to be
+averaged might be.
+
+% ``confounding'' clusters
+Despite performing a whole brain analysis, we do not find many (random) clusters
+in single contrasts or even systematically across contrasts that hamper the
+interpretation of results.\todo{ouff\dots}
+% AV: null results regarding attention and eye movements
+For example in the AV results, we do not find significant clusters that could be
+attributed to cognitive processes like attention, eye movements(, or
+memory).\todo{which kind of memory}
+% AO: auditory cortices
+For example in the AO results, contrasts that compare (among other categories)
+verbal cues about the change of a setting (\texttt{se\_new} > \texttt{se\_old})
+to categories that do not cue a change of a setting (contrasts 2, 3, 6, 7) show
+significant clusters in (primary and secondary) auditory cortices.\todo{``poor
+job of nuisance regressors?}
+% averaging vs. nuisance regressors
+This suggests that variance correlating with lower level auditory processes was
+not averaged out across trials and nuisance regressors did not do their fucking
+job (it is still kinda innate in the contrast).
+% possible reason
+This could be attributed to a possible change of the soundscape and/or increased
+volume when the narrative switches to a new setting.
+% concluding statement
+Thus, investigators that use model-driven methods to investigate brain functions
+using naturalistic stimuli should (extensively) annotate the stimulus material
+and test for correlations among variables.
+
+\subsection{consistencies across contrasts}
+
+\subsubsection{anterior vs. posterior PPA}
+
+% intro
+Notably, results of the AO contrasts consistently yielded significant clusters
+spatially constrained to the anterior part of the PPA group overlap (and
+anterior part of significant clusters of the AV contrasts).
+
+\todo[inline]{following are quotes from references for brainstorming what might
+theoretically make sense}
+
+% connectivity
+\citep{aminoff2013role} regarding \citep{baldassano2013differential}: a
+neuroimaging study examining functional connectivity of differences between
+anterior and posterior regions of the PHC show that anterior regions are more
+functionally connected to retrosplenial complex (RSC) and parietal cortices,
+whereas the posterior regions are more functionally connected to visual
+processing regions.
+
+% Baldassano (2013). Differential connectivity with Parahippocampal Place Area
+\citep{baldassano2013differential}, from abstract: We utilize a functional
+connectivity measure for fMRI that can estimate connectivity differences at the
+voxel level. We provide the first direct evidence that anterior and posterior
+PPA exhibit distinct connectivity patterns. Anterior PPA is more strongly
+connected to regions in the default mode network (including the parieto-medial
+temporal pathway). Posterior PPA more strongly connected to occipital visual
+regions.
+% gradient
+Object sensitivity in the PPA also has an anterior–posterior gradient, with
+stronger responses to abstract objects in posterior PPA.
+% summary
+Results (and previous work) suggest that posterior PPA is concerned primarily
+with perception of low-level visual features and object shape, while anterior
+PPA is involved in memory and global contextual processing.
+
+% from Baldassano discussion
+\citep{baldassano2013differential}, from discussion: our results demonstrate
+that PPA exhibits a gradient in connectivity along anterior–posterior axis
+(analogous to the gradient in connectivity along macaque TH/TF/TFO). The
+connectivity gradient was also paired with a functional gradient of sensitivity
+to scene and abstract object stimuli. Results demonstrate that anterior and
+posterior PPA connect differentially to two distinct cortical networks.
+% but not independent
+Data suggest that PPA might contain identifiable subregions, but subregions
+should not be considered as completely independent modules. Both subregions
+activate selectively to scenes, and the parahippocampal region (at least in
+macaques) is densely self-connected (Suzuki, 2009), implying that these
+subregions cooperate to build a complete representation of a scene. Their
+distinct connectivity properties, however, suggests that each may be involved in
+specific aspects of visual and cognitive processing involved in the overarching
+goal of scene understanding.
+
+% posterior PPA
+Posterior PPA shows a stronger response to abstract objects than anterior PPA,
+and is more strongly connected to all of occipital visual cortex, including LOC
+and TOS. These regions have well-defined retinotopic maps (Arcaro et al., 2009;
+Nasr et al., 2011), and are associated with the perception of low-level visual
+features and object shape. Previous work has hinted that posterior PPA is more
+responsive to both simple visual textures and objects; Arcaro et al. (2009)
+found that a posterior portion of PPA responded about four times as strongly to
+a flickering checker-board stimulus compared to an anterior portion, and that
+the response to objects was greater than the response to scrambled images only
+in the posterior portion => posterior PPA may be more visually responsive than
+anterior PPA.
+% LLA
+Our description of posterior PPA is in fact similar to the original proposal of
+Aguirre et al. for a “lingual landmark area” (LLA), slightly posterior to PPA,
+which was “specialized for the perception of visual stimuli with orienting
+value” (Aguirre et al., 1998) and carried out bottom-up perceptual analysis to
+recognize locations or landmarks (Cant and Goodale, 2007; Epstein et al., 1999).
+Although the LLA is no longer identified as an independent region from PPA in
+current studies, it is possible that the posterior portion of PPA corresponds to
+the properties of the proposed LLA, offering an explanation for why this region
+was localized more posteriorly than the full PPA.
+
+% Anterior PPA
+Anterior PPA is specifically connected to RSC, cIPL, medial PFC, and the lateral
+surface of the anterior temporal lobe. This portion of PPA is less visually
+responsive to both scenes and objects, with notably low sensitivity to abstract
+object stimuli.
+
+% DMN
+\citep{baldassano2013differential} regarding DMN: the set of regions connected
+more strongly to anterior PPA is strikingly similar to the Default Mode Network
+(DMN) (Buckner et al., 2008; Fox et al., 2005; Raichle et al., 2001), which is
+known to include the parahippocampal region. The only portions of the DMN that
+do not show differential connectivity to anterior PPA in our data are the
+rostral portion of the posterior cingulate cortex (PCC) and the superior frontal
+cortex.
+% PPA and DMN
+DMN has been implicated in a large number of internally-focused tasks, one of
+its key roles involves autobiographical memory (Buckner et al., 2008). Models of
+recognition memory have previously identified parahippocampal cortex as
+primarily encoding spatial context information (Eichenbaum et al., 2007). Data
+from Aminoff et al. (2007) has suggested that an anterior portion of PPA may be
+involved in recall based on spatial context. Our results are consistent with
+anterior PPA playing a more central role in memory than posterior PPA, given
+anterior PPA's connectivity with the DMN.
+%
+The fact that anterior PPA had a lower sensitivity to our abstract object
+stimuli does not necessarily imply that this region does not use object
+information. Previous work has shown that PPA responds to objects that have
+spatial associations (Aminoff et al., 2007), are space-defining (Mullally and
+Maguire, 2011), and are navigationally-relevant (Janzen and Van Turennout,
+2004). These types of responses require spatial memory and cannot be based
+purely on visual features like object shape. If anterior PPA is involved in
+processing spatial context, then space-defining or navigationally-relevant
+objects could activate anterior PPA more strongly than our abstract objects,
+which were unfamiliar and provided no sense of context or orientation. Further
+experiments will be required to determine what type of object-related
+information is used in this region.
+
+\subsubsection{anterior vs posterior PPA: contextual associations}
+
+\todo[inline]{discussing PPA in context of contextual associations might provide
+a smooth transition to (possibly) following discussion of RSC}
+
+% Aminoff (2013)
+\citep{aminoff2013role} in general (s. also \citep{aminoff2006parahippocampal}:
+processing of strong, long-term, contextual associations elicits activity within
+the PHC, as well as the RSC (which includes regions of the retrosplenial cortex,
+extending into the posterior cingulate cortex, and the precuneus), the medial
+prefrontal cortex (MPFC), and the transverse occipital sulcus (TOS) (Figure 2)
+[2,3,59–67].
+
+% contextual associations in anterior vs. posterior
+\citep{aminoff2006parahippocampal}: We propose that the general function of the
+PHC can be thought of as processing of contextual associations. A subregion of
+the posterior PHC is particularly optimized to process spatially organized
+contextual associations, whereas more anterior regions of the PHC are optimized
+to process contextual associations in other, non-spatial domains.
+% posterior PPA for visual visual associative information
+Spatial contextual associations are a dominant property of places and scenes,
+and thus scenes consistently activate this posterior subregion of the PHC (e.g.,
+PPA; Epstein, 1998). We do not argue that the PHC is not sensitive to spaces,
+places, and spatial information, but rather that it is sensitive to spatial
+stimuli because of the associative information (space-related associations) that
+such stimuli evoke.
+
+% Aminoff regarding contextual processing in the PHC and beyond
+\citep{aminoff2006parahippocampal} regarding contextual associations processing
+in PHC and beyond: We compared contextual processing of objects that are
+strongly related to a specific place (e.g., an oven is found in a kitchen) with
+contextual processing of objects that are highly associated with a context but
+not a specific place (e.g., a birthday cake is found at a birthday party, but
+the party can take place anywhere, at home, in a restaurant, at a park).
+Activity elicited by these two types of contextual objects was compared with the
+activity elicited for objects that were only weakly associated with many
+contexts (e.g., a lamp). Differential activity was found in the PHC and the RSC,
+replicating the previous findings (Bar \& Aminoff, 2003, The
+parahippocampal\dots).
+% results
+\citep{aminoff2006parahippocampal} Activity within the PHC, however, was
+distributed along an anterior–posterior axis, with activity related to spatial
+contexts focused in the posterior part of the PHC and activity evoked by
+non-spatial contexts focused in the more anterior part of the PHC (Bar \&
+Aminoff, 2003, Cortical analysis of visual context; Aminoff et al., 2007, The
+parahippocampal cortex mediates spatial and nonspatial associations).
+
+\subsubsection{RSC (in both stimuli)}
+
+\todo[inline]{check location in primary contrast and overlap across contrasts}
+
+% but RSC
+Apart from the PPA, we find significantly increased activity consistently across
+contrast of both contrasts in the retrosplenial cortex (RSC).
+
+\todo[inline]{give numbers of contrast in AO \& AV that show sign. clusters in
+RSC}
+
+% location functionally defined
+In context of a scene-responsive region, the RSC is functionally defined and not
+necessarily identical to the anatomically defined retrosplenial cortex [26]
+\citep{epstein2008parahippocampal}.
+% location
+The RSC is located in the retrosplenial cortex, and posterior cingulate region,
+near to the point where the calcarine sulcus joins the parietal-occipital sulcus
+\citep{epstein2008parahippocampal}.
+% anatomy of real RSC
+The Retrosplenial cortex (BA 29 and 30) adjoins and is partially encircled by
+the posterior cingulate (BA 23 and 31) [51–56]
+\citep{epstein2008parahippocampal}.
+% function
+RSC is strongly active during scene viewing, scene imagery [25] and mental
+imagination of navigation through familiar environments [8]
+\citep{epstein2008parahippocampal}.
+
+% discussion of what the RSC does
+\todo[inline]{interpretation: cf.\citep{vann2009what} and paper that reference
+her}
+% conclusion
+\todo[inline]{conclusion?}
+
+\subsubsection{superior lateral occipital cortex (OPA; in both stimuli)}
+
+\todo[inline]{check location in primary contrast and in overlap of contrasts}
+
+\todo[inline]{give numbers of contrast in AO \& AV that show sign. clusters in
+RSC}
+
+\todo[inline]{e.g. Bettencourt (2013). The Role of Transverse Occipital Sulcus
+in Scene Perception; Dilks, Kanwisher (2013). The Occipital Place Area Is
+Causally and Selectively Involved in Scene Perception?}
+
+\subsection{negative controls and cross-modal controls}
+
+\todo[inline]{could be mentioned in a few sentences. But above topics a far too
+much still; better embed somewhere above}
+
+\subsection{individual analyses}
+
+\todo[inline]{how to discuss Bland-Altman-Plots? Please, let's talk about that
+shortly}
+
+\todo[inline]{discussion of individual differences? what do the results
+suggest???}
+
+\subsubsection{AO stimulus}
+
+% intro
+We checked the results of the primary contrast also on the level of individual
+subjects to ``test'' the audio-description's performance as a functional
+localizer compared to the dedicated visual localizer paradigm.\todo{hm, sounds
+meh}
+% results of dedicated localizer
+The dedicated localizer \citep{sengupta2016extension} yielded bilateral ROIs in
+12 of 14 subjects and unilateral right ROI in two subjects (sub-04, sub-20).
+% in the current study
+The audio-description's primary contrast yielded significant bilateral clusters
+in 9 of 14 subjects (of which sub-04 shows just right-lateralized PPA ROI)  and
+an unilateral significant cluster in one subject.
+% difference
+Notably, we here used a ``one fits all approach`` whereas
+\citep{sengupta2016extension} chose the best fitting $z$-threshold in a
+subject's unthresholded $z$-maps by visual judgment and used the best of three
+alternative contrasts (strict, relaxed, or simple contrast).
+
+% quote from Hanke (2014)
+\citep{hanke2014audiomovie}: Compared to AV stimulus, the AO stimulus leaves a
+much larger margin for inter-individual differences in imagining scenery, as
+well as actors' character and personality traits, while still preserving the
+time-locked presentation of information to a listener. At the same time, the AO
+stimulus limits the effect of an attentional focus on the selection of a subset
+of simultaneously occurring auditory events, in contrast to the selection of
+different parts of the visual field.
+
+% conclusion
+Our results suggest that a naturalistic auditory stimulus is suitable to
+localize (the anterior part) of a higher-level visual area in the majority of
+subjects.
+% individual contrasts
+Nevertheless, studies that primary aim for individual results should
+choose individual thresholds and test more than just one contrast to gain the
+best (?) individual ROIs.\todo{``best'' always sounds kind of judgmental}
+% individual results
+Notably, we chose one contrast to look into individual results of all subjects
+but individually a contrast different from the primary contrast might lead to
+better individual localization results.
+
+\todo[inline]{which contrast works better in which subjects?; if focus is
+individual diagnostics take the individually best contrasts; cf. Sengupta}
+
+\todo[inline]{different ``capability'' to process auditory spatial information}
+
+\todo[inline]{individual ``preference'' to pay attention to
+spatial infos (which contradicts statement above that attention is not a
+prerequisite)}
+
+\subsubsection{AV stimulus}
+
+\todo[inline]{was not aim of the study in the first place but conceptual
+control}
+
+On individual level, mixed results for AV stimulus.
+
+\subsection{shortcomings in general}
+
+\subsubsection{AO contrast}
 
@@
 duration of a single fixation \citep{henderson2003human} further studies might
-investigate if categories of wholistic but vague verbal descriptions of
+investigate if categories of holistic but vague verbal descriptions of
 landscapes correlate with differential hemodynamic activity in the PPA compared
 to more concrete spatial cues.
-
-\subsubsection{AV stimulus}
-% location
-Group results of the AV stimulus' primary contrast yielded bilateral clusters
-that span the group overlap of individual PPAs from anterior to posterior and
-expand into retrosplenial regions.
-% difference in location/size to AO and VIS
-Clusters also expand into more posterior regions (occipital fusiform gyrus,
-lingual gyrus, and intracalcarine cortex)\todo{which of these regions overlap
-with group ROI? which regions show clusters but do not overlap with PPA?}
-% confound of higher perception
-This can be attributed to the fact that we averaged the content of individual
-frames after a cut and did not control for confounding features like depicted
-faces or objects.
-% confounds of lower perception
-It further suggest low-level visual features were not averaged out leading to
-clusters spanning the intracalcarine cortex.
-% further studies
-Since the capability to isolate clusters or networks correlating with specific
-perceptual (or cognitive) processes is influenced by the amount of annotated
-stimulus features further studies focusing on visual perception should annotate
-and model visual features of naturalistic stimuli more rigorously.\todo{ouf,
-okay...}
-% cross-modal control purpose?
-\todo[inline]{concluding statement regarding AV vs AO and cross-modality of
-results?}
-
-\subsection{stability of contrasts}
-
-\todo[inline]{the pain starts exactly here}
-
-% why we did a couple of contrasts
-For both stimuli we created additional contrasts that varied the amount of
-events available for the analysis and how well the annotated events within
-categories on average matched the stimulus type that we assumed to be
-preferentially processed in the PPA.
-
-\subsubsection{PPA}
-% PPA AO
-Regarding contrasts of the AO stimulus, six of eight contrasts show
-significant bilateral clusters in the anterior part of the group PPA.
-% PPA AV
-Regarding contrasts of the AV stimulus, all five contrasts show significant
-bilateral clusters in the PPA but extending into posterior regions
-% no incidental findings
-Results of the additional contrasts suggest that bilaterally increased
-activation in the PPA does not depend on accidental findings but is are stable
-across contrasts of the movie and the audio-description.
-
-% but
-Results also suggest that localization performance depends on the
-amount of available data and how well the feature space is modeled.
-% what's going on
-Despite performing a whole brain analysis, we do not find many (random) clusters
-in single contrasts or even systematically across contrasts that hamper the
-interpretation of results.\todo[inline]{god forgive me for this paragraph}
-% null results regarding attention and eye movements
-For example in the AV results, we do not find significant clusters that could be
-attributed to cognitive processes like attention, eye movements, or
-memory.\todo{which kind of memory}
-
-% BUT: amount of data
-Nevertheless, localization performance is influenced by the amount of available
-data\todo{give examples of contrast using less events in AV and AO} and how well
-events within categories matched on average the preferred stimulus type.
-% example AV: data amount and category homogeneity
-For example in the AV stimulus, we averaged different kind of movie cuts
-regardless to the movie frames content.\todo[inline]{how well spatially
-constrained are the clusters?}
-% results
-As a result, clusters are more widespread and reach into early visual cortex.
-
-\todo[inline]{first: number of available events -> ``noise''}
-
-\todo[inline]{second: category match -> ``localization performance''}
 
@@
 of events in which contrasts?}
-% example for data amount AO: superior temporal cortex
-In four of nine contrasts of the AO stimulus, we find significant clusters in
-superior auditory cortices (including early auditory cortices?)\todo{which
-exactly}
-% conclusion
-This suggests that variance correlating with lower level auditory processes was
-(not) averaged (out) across trials\todo{which contrasts; A1 \& low-level
-nuisance regressors?}
 % foreshadowing of narrator by soundscape
@@
 
-\subsubsection{other systematics: anterior vs. posterior, RSC and OPA}
-
-% intro
-Nevertheless, results across contrasts of both stimuli show significant clusters
-constrained to the anterior part of the PPA in contrasts of the AO stimulus, and
-significant clusters in the retrosplenial cortices and superior lateral cortices
-in both naturalistic stimuli.
-
-\subsection{anterior vs posterior PPA: contextual associations}
-
-\todo[inline]{at the moment it makes more sense to discuss it sooner; but it
-kinda depends on stuff that is happening in the RSA too}
-
-% Aminoff (2013)
-\citep{aminoff2006parahippocampal, aminoff2013role}; Aminoff (2013) in general:
-processing of strong, long-term, contextual associations elicits activity within
-the PHC, as well as the RSC (which includes regions of the retrosplenial cortex,
-extending into the posterior cingulate cortex, and the precuneus), the medial
-prefrontal cortex (MPFC), and the transverse occipital sulcus (TOS) (Figure 2)
-[2,3,59–67].
-
-% contextual associations in anterior vs. posterior
-Aminoff et al. (2013): We propose that the general function of the PHC can be
-thought of as processing of contextual associations. A subregion of the
-posterior PHC is particularly optimized to process spatially organized
-contextual associations, whereas more anterior regions of the PHC are optimized
-to process contextual associations in other, non-spatial domains.
-% posterior PPA for visual visual associative information
-Spatial contextual associations are a dominant property of places and scenes,
-and thus scenes consistently activate this posterior subregion of the PHC (e.g.,
-PPA; Epstein, 1998). We do not argue that the PHC is not sensitive to
-spaces, places, and spatial information, but rather that it is sensitive to
-spatial stimuli because of the associative information (space-related
-associations) that such stimuli evoke.
-
-% Aminoff regarding contextual processing in the PHC and beyond
-Aminoff et al. (2013). We compared contextual processing of
-objects that are strongly related to a specific place (e.g., an oven is found in
-a kitchen) with contextual processing of objects that are highly associated with
-a context but not a specific place (e.g., a birthday cake is found at a birthday
-party, but the party can take place anywhere, at home, in a restaurant, at a
-park). Activity elicited by these two types of contextual objects was compared
-with the activity elicited for objects that were only weakly associated with
-many contexts (e.g., a lamp). Differential activity was found in the PHC and the
-RSC, replicating the previous findings (Bar \& Aminoff, 2003, The
-parahippocampal\dots).
-% results
-Activity within the PHC, however, was distributed along
-an anterior–posterior axis, with activity related to spatial contexts focused in
-the posterior part of the PHC and activity evoked by non-spatial contexts
-focused in the more anterior part of the PHC (Bar \& Aminoff, 2003, Cortical
-analysis of visual context; Aminoff et al., 2007, The parahippocampal cortex
-mediates spatial and nonspatial associations).
-
-\subsection{anterior vs posterior PPA}
-% connectivity
-Aminoff et al. (2013) regarding Baldassano (2013): some evidence from a human
-neuroimaging study examining functional connectivity of differences between
-anterior and posterior regions of the PHC show that the anterior regions are
-more functionally connected to retrosplenial complex (RSC) and parietal
-cortices, whereas the posterior regions are more functionally connected to
-visual processing regions.
-
-% Baldassano (2013). Differential connectivity with Parahippocampal Place Area
-Baldassano (2013). We utilize a functional connectivity measure for fMRI that
-can estimate connectivity differences at the voxel level. We provide the first
-direct evidence that anterior and posterior PPA exhibit distinct connectivity
-patterns. Anterior PPA is more strongly connected to regions in the default mode
-network (including the parieto-medial temporal pathway). Posterior PPA more
-strongly connected to occipital visual regions.
-% gradient
-We show that object sensitivity in PPA also has an anterior–posterior gradient,
-with stronger responses to abstract objects in posterior PPA.
-% summary
-Our results (and previous work) suggest that posterior PPA is concerned
-primarily with perception of low-level visual features and object shape, while
-anterior PPA is involved in memory and global contextual processing.
-
-% from Baldassano discussion
-Our results demonstrate that PPA exhibits a gradient in connectivity along
-anterior–posterior axis (analogous to the gradient in connectivity along macaque
-TH/TF/TFO). The connectivity gradient was also paired with a functional gradient
-of sensitivity to scene and abstract object stimuli. These results demonstrate
-that anterior and posterior PPA connect differentially to two distinct cortical
-networks.
-% but not independent
-Our data suggest that PPA might contain identifiable subregions, but subregions
-should not be considered as completely independent modules. Both subregions
-activate selectively to scenes, and the parahippocampal region (at least in
-macaques) is densely self-connected (Suzuki, 2009), implying that these
-subregions cooperate to build a complete representation of a scene.  Their
-distinct connectivity properties, however, suggests that each may be involved in
-specific aspects of visual and cognitive processing involved in the overarching
-goal of scene understanding.
-% posterior PPA
-Posterior PPA shows a stronger response to abstract objects than anterior PPA,
-and is more strongly connected to all of occipital visual cortex, including LOC
-and TOS. These regions have well-defined retinotopic maps (Arcaro et al., 2009;
-Nasr et al., 2011), and are associated with the perception of low-level visual
-features and object shape. Previous work has hinted that posterior PPA is more
-responsive to both simple visual textures and objects; Arcaro et al. (2009)
-found that a posterior portion of PPA responded about four times as strongly to
-a flickering checker-board stimulus compared to an anterior portion, and that
-the response to objects was greater than the response to scrambled images only
-in the posterior portion => posterior PPA may be more visually responsive than
-anterior PPA.
-% LLA
-Our description of posterior PPA is in fact similar to the original proposal of
-Aguirre et al. for a “lingual landmark area” (LLA), slightly posterior to PPA,
-which was “specialized for the perception of visual stimuli with orienting
-value” (Aguirre et al., 1998) and carried out bottom-up perceptual analysis to
-recognize locations or landmarks (Cant and Goodale, 2007; Epstein et al., 1999).
-Although the LLA is no longer identified as an independent region from PPA in
-current studies, it is possible that the posterior portion of PPA corresponds to
-the properties of the proposed LLA, offering an explanation for why this region
-was localized more posteriorly than the full PPA.
-% Anterior PPA
-Anterior PPA is specifically connected to RSC, cIPL, medial PFC, and the lateral
-surface of the anterior temporal lobe. In addition, this portion of PPA is less
-visually responsive to both scenes and objects, with notably low sensitivity to
-abstract object stimuli.
-
-% DMN
-The set of regions connected more strongly to anterior PPA is strikingly similar
-to the Default Mode Network (DMN) (Buckner et al., 2008; Fox et al., 2005;
-Raichle et al., 2001), which is known to include the parahippocampal region. The
-only portions of the DMN that do not show differential connectivity to anterior
-PPA in our data are the rostral portion of the posterior cingulate cortex (PCC)
-and the superior frontal cortex.
-% PPA and DMN
-DMN has been implicated in a large number of internally-focused
-tasks, one of its key roles involves autobiographical memory (Buckner et al.,
-2008). Models of recognition memory have previously identified parahippocampal
-cortex as primarily encoding spatial context information (Eichenbaum et al.,
-2007). Data from Aminoff et al. (2007) has suggested that an anterior
-portion of PPA may be involved in recall based on spatial context. Our results
-are consistent with anterior PPA playing a more central role in memory than
-posterior PPA, given anterior PPA's connectivity with the DMN.
-%
-The fact that anterior PPA had a lower sensitivity to our abstract object
-stimuli does not necessarily imply that this region does not use object
-information. Previous work has shown that PPA responds to objects that have
-spatial associations (Aminoff et al., 2007), are space-defining (Mullally and
-Maguire, 2011), and are navigationally-relevant (Janzen and Van Turennout,
-2004). These types of responses require spatial memory and cannot be based
-purely on visual features like object shape. If anterior PPA is involved in
-processing spatial context, then space-defining or navigationally-relevant
-objects could activate anterior PPA more strongly than our abstract objects,
-which were unfamiliar and provided no sense of context or orientation. Further
-experiments will be required to determine what type of object-related
-information is used in this region.
-
-\paragraph{RSC (in both stimuli)}
-
-\todo[inline]{check location in primary contrast and in overlap of contrasts}
-
-% but RSC
-Apart from the PPA, we find significantly increased activity consistently across
-contrast of both contrasts in the retrosplenial cortex (RSC).\todo{how many
-exactly?}
-
-% location functionally defined
-In context of a scene-responsive region, the RSC is functionally defined and not
-necessarily identical to the anatomically defined retrosplenial cortex [26]
-\citep{epstein2008parahippocampal}.
-% location
-The RSC is located in the retrosplenial cortex, and posterior cingulate region,
-near to the point where the calcarine sulcus joins the parietal-occipital sulcus
-\citep{epstein2008parahippocampal}.
-% anatomy of real RSC
-The Retrosplenial cortex (BA 29 and 30) adjoins and is partially encircled by
-the posterior cingulate (BA 23 and 31) [51–56]
-\citep{epstein2008parahippocampal}.
-% function
-RSC is strongly active during scene viewing, scene imagery [25] and mental
-imagination of navigation through familiar environments [8]
-\citep{epstein2008parahippocampal}.
-% conclusion
-\todo[inline]{interpretation?; cf.\citep{vann2009what}}
-
-\todo[inline]{conclusion?}
-
-\paragraph{superior lateral occipital cortex (in both stimuli)}
-
-\todo[inline]{e.g. Dilks, Kanwisher (2013). The Occipital Place Area Is Causally
-and Selectively Involved in Scene Perception?}
-
-\subsection{negative controls and cross-modal controls}
-
-\todo[inline]{could be mentioned in a few sentences. But above topics a far too
-much still; better embed somewhere above}
-
-\subsection{individual analyses}
-
-\todo{how to discuss Bland-Altman-Plots? Please, let's talk about that shortly}
-
-\todo{discussion of individual differences? what do the results suggest???}
-
-% individual results
-Notably, we chose one contrast to look into individual results of all subjects
-but individually a contrast different from the primary contrast might lead to
-better individual localization results.
-
-\subsubsection{AO stimulus}
-
-\todo[inline]{shortcoming: no task to attend to spatial information}
-
-\todo[inline]{different level of alertness during paradigms}
-
-\todo[inline]{individual ``preference'' to pay attention to
-spatial infos (which contradicts statement above that attention is not a
-prerequisite)}
-
-\todo[inline]{different ``capability'' to process auditory spatial information}
-
-% intro
-We checked the results of the primary contrast also on the level of individual
-subjects to ``test'' the audio-description's performance as a functional
-localizer compared to the dedicated visual localizer paradigm.\todo{hm, sounds
-meh}
-% results of dedicated localizer
-The dedicated localizer \citep{sengupta2016extension} yielded bilateral ROIs in
-12 of 14 subjects and unilateral right ROI in two subjects (sub-04, sub-20).
-% in the current study
-The audio-description's primary contrast yielded significant bilateral clusters
-in 9 of 14 subjects (of which sub-04 shows just right-lateralized PPA ROI)  and
-an unilateral significant cluster in one subject.
-% difference
-Notably, we here used a ``one fits all approach`` whereas
-\citep{sengupta2016extension} chose the best fitting $z$-threshold in a
-subject's unthresholded $z$-maps by visual judgment and used the best of three
-alternative contrasts (strict, relaxed, or simple contrast).
-% quote from Hanke (2014)
-Hanke et al. (2014): Compared to AV stimulus, the AO stimulus leaves a much
-larger margin for inter-individual differences in imagining scenery, as well as
-actors' character and personality traits, while still preserving the time-locked
-presentation of information to a listener. At the same time, the AO stimulus
-limits the effect of an attentional focus on the selection of a subset of
-simultaneously occurring auditory events, in contrast to the selection of
-different parts of the visual field.
-% conclusion
-Our results suggest that a naturalistic auditory stimulus is suitable to
-localize (the anterior part) of a higher-level visual area in the majority of
-subjects.
-% individual contrasts
-Nevertheless, studies that primary aim for individual results should
-choose individual thresholds and test more than just one contrast to gain the
-best (?) individual ROIs.\todo{``best'' always sounds kind of judgmental}
-
 \subsubsection{AV stimulus}
-% intro
-On individual level, mixed results for AV stimulus.
-\todo{give the numbers}
-
-\todo[inline]{which contrast works better in which subjects?; if focus is
-individual diagnostics take the individually best contrasts; cf. Sengupta}
 
@@
 auditory stream of information providing incidental cues; spatial attention?
+
+% further studies
+Since the capability to isolate clusters or networks correlating with specific
+perceptual (or cognitive) processes is influenced by the amount of annotated
+stimulus features further studies focusing on visual perception should annotate
+and model visual features of naturalistic stimuli more rigorously.\todo{ouf,
+okay...}
+
+\subsubsection{pros \& cons of natural stimuli (esp. narrative) as localizer}
+
+\todo[inline]{shortcoming: no task to attend to spatial information}
+
+\todo[inline]{different level of alertness during paradigms}
 

### 2020-11-05 paper/main.tex
restructuring of discussion of individual (AO) results

@@
 
-\todo[inline]{how to discuss Bland-Altman-Plots? Please, let's talk about that
-shortly}
-
-\todo[inline]{discussion of individual differences? what do the results
-suggest???}
-
 \subsubsection{AO stimulus}
 
+\todo[inline]{``problem'': if discussion of anterior vs. posterior PPA above
+turns out that anterior PPA is a submodul of the PPA we do not localize a
+``visual area'' with an auditory stimulus}
+
+\todo[inline]{how to discuss Bland-Altman-Plots? Let's talk about that
+shortly please}
+
+todo[inline]{in 11 subjects there are voxels of higher z-score (in the PPA ROI)
+    in the AO contrast than in the contrast of the visual localizer -> should
+    all be in the anterior part of the PPA ROI, i.e. the area that belongs to
+    the significant cluster of the AO contrast}
+
 % intro
-We checked the results of the primary contrast also on the level of individual
-subjects to ``test'' the audio-description's performance as a functional
-localizer compared to the dedicated visual localizer paradigm.\todo{hm, sounds
-meh}
+In order to test the audio-description's performance as a functional localizers,
+we also compared the results of the audio-description's primary contrast to
+results of the dedicated visualizer on the level of individual subjects.
 % results of dedicated localizer
 The dedicated localizer \citep{sengupta2016extension} yielded bilateral ROIs in
-12 of 14 subjects and unilateral right ROI in two subjects (sub-04, sub-20).
+12 of 14 subjects and a unilateral right ROI in two subjects (sub-04, sub-20).
 % in the current study
@@
 in 9 of 14 subjects (of which sub-04 shows just right-lateralized PPA ROI)  and
-an unilateral significant cluster in one subject.
-% difference
-Notably, we here used a ``one fits all approach`` whereas
+a unilateral significant cluster in one subject.
+% conclusion
+Results of our exploratory analyses suggest that a naturalistic auditory
+stimulus is suitable to localize (the anterior part) of a higher-level visual
+area in the majority of subjects.
+
+% one threshold for all
+Here we used a ``one threshold fits all approach`` whereas
 \citep{sengupta2016extension} chose the best fitting $z$-threshold in a
-subject's unthresholded $z$-maps by visual judgment and used the best of three
-alternative contrasts (strict, relaxed, or simple contrast).
+subject's unthresholded $z$-maps by visual judgment and the ``best fitting''
+threshold.
+% one contrast for all
+Moreover, we chose the same contrast to look at individual results of all
+subjects.
+% chose the best contrast in the future
+Similarly to \citep{sengupta2016extension} that chose the ``best'' of three
+alternative contrasts (strict, relaxed, or simple contrast), future studies that
+aim for individual diagnostics / ROI localization should also test more than one
+contrast to gain the ``best'' individual ROIs.\todo{``best'' sounds pretty
+shitty}
 
@@
 
-% conclusion
-Our results suggest that a naturalistic auditory stimulus is suitable to
-localize (the anterior part) of a higher-level visual area in the majority of
-subjects.
-% individual contrasts
-Nevertheless, studies that primary aim for individual results should
-choose individual thresholds and test more than just one contrast to gain the
-best (?) individual ROIs.\todo{``best'' always sounds kind of judgmental}
-% individual results
-Notably, we chose one contrast to look into individual results of all subjects
-but individually a contrast different from the primary contrast might lead to
-better individual localization results.
-
-\todo[inline]{which contrast works better in which subjects?; if focus is
-individual diagnostics take the individually best contrasts; cf. Sengupta}
-
-\todo[inline]{different ``capability'' to process auditory spatial information}
+\todo[inline]{discussion of individual differences? what do the results
+suggest? Differences in alterness, attention to spatial information,
+predisposition? ``capability'' to process auditory spatial information?}
 
@@
 
-\todo[inline]{was not aim of the study in the first place but conceptual
-control}
-
-On individual level, mixed results for AV stimulus.
+\todo[inline]{was not aim of the study; AV ROIs are in the plot of individual
+    slices but not in the Bland-Altman-Plots}
 
@@
 
+% future studies: stimulus material
+Future studies should probably use a different narrative that models the feature
+space of spatial information ``better'' (provides more events that are more
+easily classified to belong to distinctive categories).
+
 \subsubsection{AV stimulus}

### 2020-11-05 paper/main.tex
restructuring of discussion of shortcomings

@@
 categories in case the narrator uses these words to indicate a switch from one
-setting to another (e.g. ``near an old bus'').
+setting to another (e.g. ``Jenny as a teenager'').
 % reference to table with rules and examples
@@
 (\texttt{se\_new} or \texttt{se\_old}) but also into another category were
-treated as belonging to the setting-related category (e.g. ``near an old bus'').
+treated as belonging to the setting-related category (e.g. ``Jenny as a
+teenager'').
 % modeling as boxcar function
@@
 case the narrator uses these words to indicate a switch from one setting to
-another (e.g. ``Jenny as teenager'', ``near an old bus'')
+another (e.g. ``Jenny as a teenager'')
 % soundscapes forestalls narrator
@@
 
+\todo[inline]{shortcoming: no task to attend to spatial information}
+
+\todo[inline]{different level of alertness during paradigms}
+
 % intro
@@
 % we did not choose se\_new and se\_old
-Notably, we did not choose the categories that contained switches from one
-setting to another (texttt{se\_new} and texttt{se\_old}) which one might assume
-to contain the auditory equivalent to the ``optimal'' visual stimulus type.
+We did not choose the categories that contained switches from one setting to
+another (\texttt{se\_new} and \texttt{se\_old}) which one might assume to
+contain the auditory equivalent to the ``optimal'' visual stimulus type.
 % why not se\_new or se\_old
-These categories were actually heterogeneous: they rarely contained whole (and
-thus vague) descriptions of landscapes (e.g. ``in a football stadium'',
-``Forrest is running through the jungle'') but mostly landmarks or buildings,
-and also non-spatial cues.\todo{repeat examples from method section}.
+The categories \texttt{se\_new} and \texttt{se\_old} were actually
+heterogeneous: they rarely contained whole and thus a vague verbal descriptions
+of landscapes (e.g. ``in a football stadium'', ``Forrest is running through the
+jungle'') but mostly landmarks or buildings, and also non-spatial
+cues (e.g. ``Jenny as a teenager``).
 % further studies
@@
 
-% AO: stimulus categories
-For example in the AO stimulus, nouns of the narrator that cue a switch to
-another setting belong to different categories (s. above).\todo[inline]{Number
-of events in which contrasts?}
+% future studies
+Futures studies should chose a auditory narrative that better samples the
+feature space correlating with the brain process to be investigated.
+% future studies: stimulus material
+Future studies should probably use a different narrative that models the feature
+space of spatial information ``better'' (provides more events that are more
+easily classified to belong to distinctive categories).
+
+\tod[inline]{hypothesis of increased activation correlation with changes in the
+    soundscape; cf. control contrasts (e.g. \texttt{vse\_new} >
+    \texttt{pe\_old}).
 % foreshadowing of narrator by soundscape
 Further, verbal cues are regularly forestalled by changes of the
-soundscape.\todo{cross-modal control contrasts; all negative results at moment
-of cuts but vse\_new > pe\_old): right RSC.}
+soundscape.
 % arnott
@@
 correlate with increased activity in the PPA.
-% conclusion: AO and AV stability
-In summary, our results across add further evidence that model-driven analyses
-can be run on data from naturalistic stimuli to isolate brain activity
-correlating with specific perceptual processes.
-% but
-Nevertheless isolation performance relies on how well the model captures
-different aspects of the stimuli's feature space.
-
-% future studies: stimulus material
-Future studies should probably use a different narrative that models the feature
-space of spatial information ``better'' (provides more events that are more
-easily classified to belong to distinctive categories).
 
@@
 
+\todo[inline]{imo opening the pandora's box of the AV shortcomings especially at
+the end of the paper should be kept to a minimum of text}
+
+% focus of study
+The focus of the current study was to investigate if signficantly increased
+hemodynamic activity in the PPA correlates with spatial information (compared to
+``non-spatial'' information) during a naturalistic auditory stimulus.
 % shortcomings
-visual confounds all over the place; obvious solution: annotate frames and track
-focus of attention (but gist of a frame vs. attentional focus)
-
-Individual differences when seeing a whole picture with many features vs. serial
-auditory stream of information providing incidental cues; spatial attention?
-
+Results of the AV stimulus that we ran as a conceptual control are tempered by
+using different kind of movie cuts regardless of the visual content of the movie
+frame after the respective cuts.
+% which leads to the ``blurred'' results
+Hence we got visual confounds / clusters extending in to early visual areas.
 % further studies
@@
 stimulus features further studies focusing on visual perception should annotate
-and model visual features of naturalistic stimuli more rigorously.\todo{ouf,
-okay...}
+and model visual features of naturalistic stimuli more rigorously.
+% solution
+Future studies that aim to use a movie to localize different visual areas should
+extensively annotate the content of frames (e.g. using the open-source solution
+``Pliers'' for feature extraction from a visual naturalistic stimulus;
+\citep{mcnamara2017developing}) and record the subject's visual attention via
+eye-tracking.
 
 \subsubsection{pros \& cons of natural stimuli (esp. narrative) as localizer}
-
-\todo[inline]{shortcoming: no task to attend to spatial information}
-
-\todo[inline]{different level of alertness during paradigms}
 
@@
 Results: Our results demonstrate...
+
+% conclusion: AO and AV stability
+In summary, our results across add further evidence that model-driven analyses
+can be run on data from naturalistic stimuli to isolate brain activity
+correlating with specific perceptual processes.
+% but
+Nevertheless isolation performance relies on how well the model captures
+different aspects of the stimuli's feature space.
 

### 2020-11-05 paper/main.tex
fix latex syntax
restructure quotes of anterior vs. posterior PPA

@@
 % Baldassano (2013). Differential connectivity with Parahippocampal Place Area
-\citep{baldassano2013differential}, from abstract: We utilize a functional
-connectivity measure for fMRI that can estimate connectivity differences at the
-voxel level. We provide the first direct evidence that anterior and posterior
-PPA exhibit distinct connectivity patterns. Anterior PPA is more strongly
-connected to regions in the default mode network (including the parieto-medial
-temporal pathway). Posterior PPA more strongly connected to occipital visual
-regions.
+\citep{baldassano2013differential} in general: anterior and posterior PPA
+exhibit distinct connectivity patterns; object sensitivity in the PPA also has
+an anterior-posterior gradient; connectivity gradient was also paired with a
+functional gradient of sensitivity to scene and abstract object stimuli.
+
 % gradient
-Object sensitivity in the PPA also has an anterior–posterior gradient, with
-stronger responses to abstract objects in posterior PPA.
-% summary
-Results (and previous work) suggest that posterior PPA is concerned primarily
-with perception of low-level visual features and object shape, while anterior
-PPA is involved in memory and global contextual processing.
-
-% from Baldassano discussion
-\citep{baldassano2013differential}, from discussion: our results demonstrate
-that PPA exhibits a gradient in connectivity along anterior–posterior axis
-(analogous to the gradient in connectivity along macaque TH/TF/TFO). The
-connectivity gradient was also paired with a functional gradient of sensitivity
-to scene and abstract object stimuli. Results demonstrate that anterior and
-posterior PPA connect differentially to two distinct cortical networks.
-% but not independent
 Data suggest that PPA might contain identifiable subregions, but subregions
@@
 activate selectively to scenes, and the parahippocampal region (at least in
-macaques) is densely self-connected (Suzuki, 2009), implying that these
+macaques) is densely self- connected (Suzuki, 2009), implying that these
 subregions cooperate to build a complete representation of a scene. Their
@@
 
-% posterior PPA
-Posterior PPA shows a stronger response to abstract objects than anterior PPA,
-and is more strongly connected to all of occipital visual cortex, including LOC
-and TOS. These regions have well-defined retinotopic maps (Arcaro et al., 2009;
-Nasr et al., 2011), and are associated with the perception of low-level visual
-features and object shape. Previous work has hinted that posterior PPA is more
-responsive to both simple visual textures and objects; Arcaro et al. (2009)
-found that a posterior portion of PPA responded about four times as strongly to
-a flickering checker-board stimulus compared to an anterior portion, and that
-the response to objects was greater than the response to scrambled images only
-in the posterior portion => posterior PPA may be more visually responsive than
-anterior PPA.
-% LLA
-Our description of posterior PPA is in fact similar to the original proposal of
+% from Baldassano discussion
+\citep{baldassano2013differential} regarding posterior PPA: posterior regions
+are more functionally connected to visual processing regions; posterior PPA more
+strongly connected to occipital visual regions; stronger responses to abstract
+objects in posterior PPA; posterior PPA is concerned primarily with perception
+of low-level visual fea- tures and object shape.
+
+\citep{baldassano2013differential} discussion of posterior PPA: Posterior PPA
+shows a stronger response to abstract objects than anterior PPA, and is more
+strongly connected to all of occipital visual cortex, including LOC and TOS.
+These regions have well-defined retinotopic maps (Arcaro et al., 2009; Nasr et
+al., 2011), and are associated with the perception of low-level visual features
+and object shape. Previous work has hinted that posterior PPA is more responsive
+to both simple visual textures and objects; Arcaro et al. (2009) found that a
+posterior portion of PPA responded about four times as strongly to a flickering
+checker-board stimulus compared to an anterior portion, and that the response to
+objects was greater than the response to scrambled images only in the posterior
+portion => posterior PPA may be more visually responsive than anterior PPA. Our
+description of posterior PPA is in fact similar to the original proposal of
 Aguirre et al. for a “lingual landmark area” (LLA), slightly posterior to PPA,
@@
 current studies, it is possible that the posterior portion of PPA corresponds to
-the properties of the proposed LLA, offering an explanation for why this region
+the properties of the proposed LLA, offring an explanation for why this region
 was localized more posteriorly than the full PPA.
 
-% Anterior PPA
-Anterior PPA is specifically connected to RSC, cIPL, medial PFC, and the lateral
-surface of the anterior temporal lobe. This portion of PPA is less visually
-responsive to both scenes and objects, with notably low sensitivity to abstract
-object stimuli.
-
-% DMN
+\citep{baldassano2013differential} regarding anterior PPA: anterior regions are
+more functionally connected to retrosplenial complex (RSC) and parietal
+cortices; anterior PPA is more strongly connected to regions in the default mode
+network (including the parieto-medial temporal pathway); anterior PPA is
+involved in memory and global contextual processing; anterior PPA is
+specifically connected to RSC, cIPL, medial PFC, and the lateral surface of the
+anterior temporal lobe. This portion of PPA is less visually responsive to both
+scenes and objects, with notably low sensitivity to abstract object stimuli.
+
 \citep{baldassano2013differential} regarding DMN: the set of regions connected
@@
 rostral portion of the posterior cingulate cortex (PCC) and the superior frontal
-cortex.
-% PPA and DMN
-DMN has been implicated in a large number of internally-focused tasks, one of
-its key roles involves autobiographical memory (Buckner et al., 2008). Models of
-recognition memory have previously identified parahippocampal cortex as
-primarily encoding spatial context information (Eichenbaum et al., 2007). Data
-from Aminoff et al. (2007) has suggested that an anterior portion of PPA may be
-involved in recall based on spatial context. Our results are consistent with
-anterior PPA playing a more central role in memory than posterior PPA, given
-anterior PPA's connectivity with the DMN.
-%
-The fact that anterior PPA had a lower sensitivity to our abstract object
-stimuli does not necessarily imply that this region does not use object
-information. Previous work has shown that PPA responds to objects that have
-spatial associations (Aminoff et al., 2007), are space-defining (Mullally and
-Maguire, 2011), and are navigationally-relevant (Janzen and Van Turennout,
-2004). These types of responses require spatial memory and cannot be based
-purely on visual features like object shape. If anterior PPA is involved in
-processing spatial context, then space-defining or navigationally-relevant
-objects could activate anterior PPA more strongly than our abstract objects,
-which were unfamiliar and provided no sense of context or orientation. Further
-experiments will be required to determine what type of object-related
-information is used in this region.
+cortex.  DMN has been implicated in a large number of internally-focused tasks,
+one of its key roles involves autobiographical memory (Buckner et al., 2008).
+Models of recognition memory have previously identified parahippocampal cor- tex
+as primarily encoding spatial context information (Eichenbaum et al., 2007).
+Data from Aminoff et al. (2007) has suggested that an anterior portion of PPA
+may be involved in recall based on spatial context. Our results are consistent
+with anterior PPA playing a more central role in memory than posterior PPA,
+given anterior PPA's connectivity with the DMN. The fact that anterior PPA had a
+lower sensitivity to our abstract object stimuli does not necessarily im ply
+that this region does not use object information. Previous work has shown that
+PPA responds to objects that have spatial associations (Aminoff et al., 2007),
+are space-defining (Mullally and Maguire, 2011), and are navigationally-
+relevant (Janzen and Van Turennout, 2004). These types of responses require
+spatial memory and cannot be based purely on visual features like object shape.
+If anterior PPA is involved in processing spatial context, then space-defining
+or navigationally-relevant objects could activate anterior PPA more strongly
+than our abstract objects, which were unfamiliar and provided no sense of
+context or orientation. Further experiments will be required to determine what
+type of object-related information is used in this region.
 
@@
 
-\tod[inline]{hypothesis of increased activation correlation with changes in the
+\todo[inline]{hypothesis of increased activation correlation with changes in the
     soundscape; cf. control contrasts (e.g. \texttt{vse\_new} >
-    \texttt{pe\_old}).
+    \texttt{pe\_old})}.
 % foreshadowing of narrator by soundscape
-Further, verbal cues are regularly forestalled by changes of the
-soundscape.
+Further, verbal cues are regularly forestalled by changes of the soundscape.
 % arnott

### 2020-11-05 paper/main.tex
restructure quotes of anterior vs. posterior PPA v2

@@
 exhibit distinct connectivity patterns; object sensitivity in the PPA also has
-an anterior-posterior gradient; connectivity gradient was also paired with a
-functional gradient of sensitivity to scene and abstract object stimuli.
+an anterior-posterior gradient of sensitivity to scene and abstract object
+stimuli.
 
@@
 activate selectively to scenes, and the parahippocampal region (at least in
-macaques) is densely self- connected (Suzuki, 2009), implying that these
-subregions cooperate to build a complete representation of a scene. Their
-distinct connectivity properties, however, suggests that each may be involved in
-specific aspects of visual and cognitive processing involved in the overarching
-goal of scene understanding.
+macaques) is densely selfconnected (Suzuki, 2009), implying that these
+subregions cooperate to build a complete representation of a scene.
+%
+Their distinct connectivity properties, however, suggests that each may be
+involved in specific aspects of visual and cognitive processing involved in the
+overarching goal of scene understanding.
 
@@
 \citep{baldassano2013differential} regarding posterior PPA: posterior regions
-are more functionally connected to visual processing regions; posterior PPA more
-strongly connected to occipital visual regions; stronger responses to abstract
-objects in posterior PPA; posterior PPA is concerned primarily with perception
-of low-level visual fea- tures and object shape.
+are more functionally connected to visual processing / occipital visual regions;
+stronger responses to abstract objects in posterior PPA; posterior PPA is
+concerned primarily with perception of low-level visual features and object
+shape.
 
@@
 strongly connected to all of occipital visual cortex, including LOC and TOS.
+%
 These regions have well-defined retinotopic maps (Arcaro et al., 2009; Nasr et
 al., 2011), and are associated with the perception of low-level visual features
-and object shape. Previous work has hinted that posterior PPA is more responsive
-to both simple visual textures and objects; Arcaro et al. (2009) found that a
-posterior portion of PPA responded about four times as strongly to a flickering
-checker-board stimulus compared to an anterior portion, and that the response to
-objects was greater than the response to scrambled images only in the posterior
-portion => posterior PPA may be more visually responsive than anterior PPA. Our
-description of posterior PPA is in fact similar to the original proposal of
+and object shape.
+%
+Previous work has hinted that posterior PPA is more responsive to both simple
+visual textures and objects; Arcaro et al. (2009) found that a posterior portion
+of PPA responded about four times as strongly to a flickering checker-board
+stimulus compared to an anterior portion, and that the response to objects was
+greater than the response to scrambled images only in the posterior portion =>
+posterior PPA may be more visually responsive than anterior PPA.
+%
+Our description of posterior PPA is in fact similar to the original proposal of
 Aguirre et al. for a “lingual landmark area” (LLA), slightly posterior to PPA,
@@
 recognize locations or landmarks (Cant and Goodale, 2007; Epstein et al., 1999).
+%
 Although the LLA is no longer identified as an independent region from PPA in
@@
 cortices; anterior PPA is more strongly connected to regions in the default mode
-network (including the parieto-medial temporal pathway); anterior PPA is
-involved in memory and global contextual processing; anterior PPA is
-specifically connected to RSC, cIPL, medial PFC, and the lateral surface of the
-anterior temporal lobe. This portion of PPA is less visually responsive to both
-scenes and objects, with notably low sensitivity to abstract object stimuli.
+network (including the parieto-medial temporal pathway)
+%
+anterior PPA is involved in memory and global contextual processing; anterior
+PPA is specifically connected to RSC, cIPL, medial PFC, and the lateral surface
+of the anterior temporal lobe.
+%
+This portion of PPA is less visually responsive
+to both scenes and objects, with notably low sensitivity to abstract object
+stimuli.
 
@@
 (DMN) (Buckner et al., 2008; Fox et al., 2005; Raichle et al., 2001), which is
-known to include the parahippocampal region. The only portions of the DMN that
-do not show differential connectivity to anterior PPA in our data are the
-rostral portion of the posterior cingulate cortex (PCC) and the superior frontal
-cortex.  DMN has been implicated in a large number of internally-focused tasks,
-one of its key roles involves autobiographical memory (Buckner et al., 2008).
-Models of recognition memory have previously identified parahippocampal cor- tex
-as primarily encoding spatial context information (Eichenbaum et al., 2007).
+known to include the parahippocampal region.
+%
+The only portions of the DMN that do not show differential connectivity to
+anterior PPA in our data are the rostral portion of the posterior cingulate
+cortex (PCC) and the superior frontal cortex.  DMN has been implicated in a
+large number of internally-focused tasks, one of its key roles involves
+autobiographical memory (Buckner et al., 2008).  Models of recognition memory
+have previously identified parahippocampal cortex as primarily encoding spatial
+context information (Eichenbaum et al., 2007).
+%
 Data from Aminoff et al. (2007) has suggested that an anterior portion of PPA
-may be involved in recall based on spatial context. Our results are consistent
-with anterior PPA playing a more central role in memory than posterior PPA,
-given anterior PPA's connectivity with the DMN. The fact that anterior PPA had a
-lower sensitivity to our abstract object stimuli does not necessarily im ply
-that this region does not use object information. Previous work has shown that
-PPA responds to objects that have spatial associations (Aminoff et al., 2007),
-are space-defining (Mullally and Maguire, 2011), and are navigationally-
-relevant (Janzen and Van Turennout, 2004). These types of responses require
-spatial memory and cannot be based purely on visual features like object shape.
+may be involved in recall based on spatial context.
+%
+Our results are consistent with anterior PPA playing a more central role in
+memory than posterior PPA, given anterior PPA's connectivity with the DMN. The
+fact that anterior PPA had a lower sensitivity to our abstract object stimuli
+does not necessarily im ply that this region does not use object information.
+%
+Previous work has shown that PPA responds to objects that have spatial
+associations (Aminoff et al., 2007), are space-defining (Mullally and Maguire,
+2011), and are navigationally-relevant (Janzen and Van Turennout, 2004).
+%
+These types of responses require spatial memory and cannot be based purely on
+visual features like object shape.#
+%
 If anterior PPA is involved in processing spatial context, then space-defining
@@
 than our abstract objects, which were unfamiliar and provided no sense of
-context or orientation. Further experiments will be required to determine what
-type of object-related information is used in this region.
+context or orientation.
+%
+Further experiments will be required to determine what type of object-related
+information is used in this region.
 

### 2020-11-11 paper/main.tex
correction of latex syntax
restructure quotes of contextual associations
abstract, adjustments to intro & results

@@
 % our audience highlighting innovative examples of data reuse may be used to
-% present compelling new findings & conclusions derived from published.
-Intro: PPA as classic example for an visual area; Methods: fMRI data
-studyforrest data set, general linear model; Results: significant clusters in
-PPA, RSC, individual results in x of 15 subjects; Conclusions: results suggest
-generalizability to spoken language and is restricted to processing visual
-stimuli exclusively. \end{abstract}
+% present compelling new findings & conclusions derived from published.  intro
+Neuroimaging studies have parcellated the human brain into distinct functional
+regions.
+% PPA
+The ``parahippocampal place area'' is classically considered to be a higher
+visual area as increased hemodynamic activity in the PPA correlates/is
+correlated with the perception of static pictures of landscapes (or landmarks)
+compared to pictures of faces or objects.
+% What we do
+In the current study, we exploratorily tested if spatial information embedded in
+the audio-description of a Hollywood movie (i.e. the movie's soundtrack with an
+additional narrator) the audio-visual movie can be used to isolate the PPA on a
+group average level and in individual subjects.
+%
+We use publicly available functional magnetic resonance imaging data
+(studyforrest.org) to build canonical general linear model (GLM) $t$-contrasts
+and compare current results to results that we gained from a dedicated visual
+localizer experiment conducted with the same 14 participants.
+% compare to visual localizer experiment group results
+On a group average level, our results show significantly increased activation in
+the PPA but restricted to its anterior part [as well as in the retrosplenial and
+lateral occipital cortex] of both hemispheres.
+% individual results
+On an individual level, results show significant bilateral clusters in the
+anterior PPA of nine subjects and significant unilateral clusters in two
+subjects.
+% conclusion: generalizability
+Results suggest that increased activation in the PPA during the perception of
+static pictures generalizes to the perception of auditorily presented spatial
+information.
+% conclusion: PPA has subregions
+Lastly, our results provides further evidence that the PPA can be divided into
+functional subregions.\todo{kinda bold statements; this depends on the data \&
+discussion}\end{abstract}
 
@@
 were conceptualized to control confounding variables (e.g. color, luminance,
-size, sentence length), a process that is often not reported in
-detail.\todo{really? check that}
+size, spatial frequencies, sentence length), a process that is often not
+reported in detail.\todo{they usually just say ``we made the black \& white}
 % block-design & task
@@
 % individual results
-Lastly focussing on the audio-description, we compare results on the level of
+Lastly, focussing on the audio-description, we compare results on the level of
 individual subjects to results of a block-designed visual localizer experiment
@@
 
-\todo[inline]{I consider tables of significant clusters for all contrasts as
-overkill. Maybe in ``supporting material'' or reference to dataset?  all sign.
-clusters of all contrasts are in the comments}
-
 % study goal
@@
 
+\todo[inline]{subheadings are still in for better readability; structure could
+be changed; at the moment its AO (PPA in primary contrast, robustness of PPA;
+other clusters across contrasts), then the same for AV}
+
 \todo[inline]{paragraphs start with 1-2 sentences that set up the question
@@
 \todo[inline]{paragraph ends with a concluding / logical statement}
+
+\subsubsection{PPA in AO: primary contrasts}
 
@@
 
+\subsubsection{PPA in AO: robustness across contrasts}
+
+\todo[inline]{I consider tables of significant clusters in PPA for all contrasts
+as overkill. Maybe in ``supporting material'' or reference to dataset? all sign.
+clusters of all contrasts are in the comments}
+
 % all eight AO PPA contrasts
@@
 anterior regions of the group PPA overlap (see Figure
-\ref{fig:stability-slices}.\todo{Discussion: discuss that contrasts make ``less
-and less'' sense}
 % statement/answer
 Results suggest that our findings do not depend on one specific contrasts but
-are robust across differently designed contrasts.
+are robust across differently designed
+contrasts.\ref{fig:stability-slices}).\todo[inline]{Discussion: discuss that
+contrasts make ``less and less'' sense}
 % question
 \todo[inline]{concluding statement often feels like interpretation/discussion}
-
-% precuneus = retrosplenial cortex ?
-\todo[inline]{significant clusters in other regions than PPA could or should (?)
-also be reported? Following is a short list:}
-% ventral precuneus = retrosplenial cortex?
-7 contrasts: bilateral clusters in RSC (and ventral precuneus);
-% transverse occipital sulcus = occipital place area
-6 contrasts (4 bilat.): transverse occipital sulcus (= OPA?);\todo{AO: clusters
-are more lateral; AV: clusters are more medial}
-% confounds
-4 contrasts: right superior temporal gyrus; 3 contrasts: left superior temporal
-gyrus; 3 contrasts: some (smallish) prefrontal clusters
-
-% AO negative control contrasts
-\todo[inline]{control contrast at moment of cuts but in the audio-description
-(contrasts 9-13) could be, if at all, mentioned here already; at the moment
-negative control contrasts come last combined for AO \& AV at the end}
+% question 2
 
@@
 
+\subsubsection{other sign. clusters across AO contrasts}
+% precuneus = retrosplenial cortex ?
+\todo[inline]{significant clusters in other regions than PPA could or should (?)
+also be reported? Following is a short list; depends on the discussion I guess}
+% ventral precuneus = retrosplenial cortex?
+7 contrasts: bilateral clusters in RSC (and ventral precuneus);
+% transverse occipital sulcus = occipital place area
+6 contrasts (4 bilat.): transverse occipital sulcus (= OPA?);\todo{AO: clusters
+are more lateral; AV: clusters are more medial}
+% confounds
+4 contrasts: right superior temporal gyrus; 3 contrasts: left superior temporal
+gyrus; 3 contrasts: some (smallish) prefrontal clusters
+
+\subsubsection{PPA in AV: primary contrasts}
 % AV intro
@@
 
+\subsubsection{PPA in AV: robustness + other clusters across contrasts}
+
 % all eight AV PPA contrasts
@@
 \ref{fig:stability-slices}).
-% lingual gyrus
-In three contrasts, these homologous clusters extend into the lingual gyri.
-% RSC
-Further, three contrasts show significant homologous clusters in the RSC.
-% LOC
-Lastly, four contrasts show significant homologous clusters in lateral occipital
-cortices.
 % concluding statement
@@
 
-\subsection{negative controls}
-
-\todo[inline]{these contrasts are listed in the methods section. Shall results
-of these contrasts be reported here (at all) as well?}
+\subsection{negative controls in AO and AV}
+
+\todo[inline]{contrasts are mentioned in the method section for the purpose of
+    completeness. Shall results be reported (and later discussed)? Following is
+a short overview}
 
@@
 AO stimulus (using annotation of movie cuts) all null results except: contrast 9
-(vse\_new > pe\_old): right RSC
+(vse\_new > pe\_old): right RSC.
 % correlation of these nouns with cuts
-(cf. Figure \ref{fig:reg-corr}: nouns that cue change to a new setting are
-``somewhat'' correlated with cuts to a new setting; nouns that cue change to a
-familiar setting are somewhat correlated with cuts to a familiar setting).
+Compare Figure \ref{fig:reg-corr}: nouns that cue change to a new setting are
+correlated  with cuts to a new setting (vse\_new; r$\approx$0.3; second highest
+correlation of a verbal cue category with a cut category.
 
@@
 se\_old): right PPA, bilateral sup. lat. occ. cortex; LOC (l/r), right superior
-parietal lobe; here again: these kind of nouns and these kind of cuts are
-correlated (cf. Figure \ref{fig:reg-corr}).
+parietal lobe. Compate Figure \ref{fig:reg-corr}: nouns that cue change to a new
+setting are correlated  with cuts to a new setting (vse\_new; r$\approx$0.3;
+second highest correlation of a verbal cue category with a cut category; AND:
+nouns that cue change to a familiar setting are somewhat correlated with cuts to
+a familiar setting (se\_old; r$\approx$0.4; highest correlation of a verbal
+category with a cut category).
 
@@
 These types of responses require spatial memory and cannot be based purely on
-visual features like object shape.#
+visual features like object shape.
 %
@@
 \citep{aminoff2006parahippocampal}: We propose that the general function of the
-PHC can be thought of as processing of contextual associations. A subregion of
-the posterior PHC is particularly optimized to process spatially organized
-contextual associations, whereas more anterior regions of the PHC are optimized
-to process contextual associations in other, non-spatial domains.
+PHC can be thought of as processing of contextual associations.
+%
+A subregion of the posterior PHC is particularly optimized to process spatially
+organized contextual associations, whereas more anterior regions of the PHC are
+optimized to process contextual associations in other, non-spatial domains.
 % posterior PPA for visual visual associative information
@@
 and thus scenes consistently activate this posterior subregion of the PHC (e.g.,
-PPA; Epstein, 1998). We do not argue that the PHC is not sensitive to spaces,
+PPA; Epstein, 1998).
+%
+We do not argue that the PHC is not sensitive to spaces,
 places, and spatial information, but rather that it is sensitive to spatial
@@
 the party can take place anywhere, at home, in a restaurant, at a park).
+% method
 Activity elicited by these two types of contextual objects was compared with the
 activity elicited for objects that were only weakly associated with many
-contexts (e.g., a lamp). Differential activity was found in the PHC and the RSC,
+contexts (e.g., a lamp).
+% results
+Differential activity was found in the PHC and the RSC,
 replicating the previous findings (Bar \& Aminoff, 2003, The
 parahippocampal\dots).
-% results
+% results 2
 \citep{aminoff2006parahippocampal} Activity within the PHC, however, was

### 2020-11-11 code/plot-bland-altman.py

@@ -170,10 +170,14 @@ def process_df(subj, zmaps_df, out_path):
     ppa_ind_masked1 = zmap1.as_matrix()[zmaps_df['ppa_ind'].as_matrix() > 0]
     ppa_ind_masked2 = zmap2.as_matrix()[zmaps_df['ppa_ind'].as_matrix() > 0]
 
+    ao_ind_masked1 = zmap1.as_matrix()[zmaps_df['ao_ind'].as_matrix() > 0]
+    ao_ind_masked2 = zmap2.as_matrix()[zmaps_df['ao_ind'].as_matrix() > 0]
+
     datasets = [
         [zmap1, zmap2],
         [ppa_grp_masked1, ppa_grp_masked2],
-        [ppa_ind_masked1, ppa_ind_masked2]
+        [ppa_ind_masked1, ppa_ind_masked2],
+        [ao_ind_masked1, ao_ind_masked2]
     ]
 
     means_list = [compute_means(data1, data2) for data1, data2 in datasets]
@@ -194,6 +198,7 @@ def process_df(subj, zmaps_df, out_path):
 
     ax_scatter.text(5.1, 5.8, subj, fontsize=16, fontweight='bold')
 
+    # plot voxel within occipitotemporal cortex
     plot_blandaltman(ax_scatter,
                      means_list[0],
                      diffs_list[0],
@@ -201,6 +206,7 @@ def process_df(subj, zmaps_df, out_path):
                      c='darkgrey',
                      s=2)
 
+    # plot voxels within PPA group overlap
     plot_blandaltman(ax_scatter,
                      means_list[1],
                      diffs_list[1],
@@ -208,11 +214,20 @@ def process_df(subj, zmaps_df, out_path):
                      c='royalblue',
                      s=2)
 
+    # plot voxels within individual PPA ROI
     plot_blandaltman(ax_scatter,
                      means_list[2],
                      diffs_list[2],
                      alpha=1,
                      c='r',
+                     s=2)
+
+    # plot voxels within (thresholded) individual AO zmap
+    plot_blandaltman(ax_scatter,
+                     means_list[3],
+                     diffs_list[3],
+                     alpha=0.5,
+                     c='y',
                      s=2)
 
     plot_histogram(ax_xhist, ax_yhist,
@@ -229,6 +244,15 @@ def process_df(subj, zmaps_df, out_path):
                    means_list[2], diffs_list[2],
                    alpha=1,
                    color='r')
+
+    try:
[…]

### 2020-11-11 paper/main.tex
restructure discussion of anterior vs posterior PPA

@@
 
-% third level
-% model
+% third level model
 The third level analysis which averaged contrast estimates over subjects was
@@
 % PPA masks
-PPA ROI masks for individual subjects and a PPA group mask of individual PPA
-overlaps were created from data provided by \citep{sengupta2016extension}.
+PPA region of interest (ROI) masks for individual subjects and a PPA group mask
+of individual PPA overlaps were created from data provided by
+\citep{sengupta2016extension}.
 
@@
 Previous studies reported bilaterally increased hemodynamic activity in the PPA
-when participants were watching static pictures of landscape compared to face or
-objects (e.g. \citep{epstein1998ppa, epstein1999parahippocampal}) whereas one
-study using spoken sentences reported mixed results \citep{aziz2008modulation}.
+when participants were watching static pictures of landscape compared to
+pictures of faces or objects (e.g. \citep{epstein1998ppa,
+epstein1999parahippocampal}) whereas one study using spoken sentences reported
+mixed results \citep{aziz2008modulation}.
 % we use similar statistical models but with naturalistic stimuli
@@
 ``spatial information'' embedded in an auditory narrative contrasted with
-``non-spatial information'' correlate with increased activation in the PPA of
-both hemispheres.
+``non-spatial information'' is correlated with increased activation in the
+anterior PPA of both hemispheres.
 % to do
@@
 % but we are still different
-Our paradigm still differs from previous studies because the relevant stimulus
-features were incidentally embedded in a continuous stream of auditory
+Our paradigm still differs from \citep{epstein1998ppa} because the relevant
+stimulus features were incidentally embedded in a continuous stream of auditory
 information.
 % conclusion
-This embeddedness prevents participants from making assumptions about the
+The embeddedness prevents participants from making assumptions about the
 investigated perceptual process by just being exposed to the paradigm and thus
@@
 % concluding statement: kinda automatic process
-The lack of a task further suggests verbal spatial information is processed in
-the PPA in an automatic fashion and does not necessarily rely on deliberately
+The lack of a task further suggests that verbal spatial information is processed
+in the PPA in an automatic fashion and does not necessarily rely on deliberately
 paying attention to spatial information.
@@
 Group results of the AV stimulus' primary contrast yielded bilateral clusters
-that span the group overlap of individual PPAs from anterior to posterior and
-expand into retrosplenial regions.
+that span the group overlap of individual PPA ROIs from anterior to posterior.
 % difference in location/size to AO and VIS
@@
 % confound of higher perception
-This can be attributed to the fact that we averaged the content of individual
-frames after a cut and did not control for confounding features like depicted
-faces or objects.
-% confounds of lower perception
-It further suggest low-level visual features were not averaged out leading to
-clusters spanning the intracalcarine cortex.
+This larger extension, especially into the primary visual cortex, can be
+attributed to the fact that we averaged the content of individual frames after a
+cut and did not control for confounding features like depicted faces or
+objects,and low-level visual features.
 % cross-modal control purpose?
@@
 Regarding contrasts of the AO stimulus, six of eight contrasts show significant
-bilateral clusters in the anterior part of the group PPA.
+bilateral clusters in the anterior part of the group PPA overlap.
 % PPA AV
 Regarding contrasts of the AV stimulus, all five contrasts show significant
-bilateral clusters in the PPA but extending into posterior regions.
+bilateral clusters in the PPA but extending into more posterior brain regions.
 % results indicate robustness
-Results of the additional contrasts indicate that our findings are robust across
-contrasts and do not depend on the design of one specific contrasts.
+Thus, the results of the additional contrasts indicate that our findings are
+robust across contrasts and do not depend on the design of one specific
+contrasts.
 
@@
 events yielded neither a significant cluster in the right-hemispheric nor
-left-hemispheric PPA ROI.
+left-hemispheric PPA.
 % concluding statement
@@
 not averaged out across trials and nuisance regressors did not do their fucking
-job (it is still kinda innate in the contrast).
+job (still, it is kinda innate in the contrast).\todo{the word ''fuck`` is not
+acceptable}
 % possible reason
@@
 anterior part of significant clusters of the AV contrasts).
-
-\todo[inline]{following are quotes from references for brainstorming what might
-theoretically make sense}
+% intro to connectivity and object gradient
+Previous studies suggest that posterior and anterior part of the PPA show both a
+difference in connectivity profiles \citep{baldassano2013differential} and a
+gradient in sensitivity to scene and abstract object stimuli
+\citep{arcaro2009retinotopic, aminoff2007parahippocampal,
+baldassano2013differential}.
+% high level summary: posterior
+
+\paragraph{posterior: connectivity \& object sensitivity}
+
+% Baldassano (2013): Our description of posterior PPA is in fact similar to the
+% original proposal of Aguirre et al. for a “lingual landmark area” (LLA),
+% slightly posterior to PPA, which was “specialized for the perception of visual
+% stimuli with orienting value” (Aguirre et al., 1998) and carried out bottom-up
+% perceptual analysis to recognize locations or landmarks (Cant and Goodale,
+% 2007; Epstein et al., 1999). Although the LLA is no longer identified as an
+% independent region from PPA in current studies, it is possible that the
+% posterior portion of PPA corresponds to the properties of the proposed LLA,
+% offering an explanation for why this region was localized more posteriorly
+% than the full PPA.
 
 % connectivity
-\citep{aminoff2013role} regarding \citep{baldassano2013differential}: a
-neuroimaging study examining functional connectivity of differences between
-anterior and posterior regions of the PHC show that anterior regions are more
-functionally connected to retrosplenial complex (RSC) and parietal cortices,
-whereas the posterior regions are more functionally connected to visual
-processing regions.
-
-% Baldassano (2013). Differential connectivity with Parahippocampal Place Area
-\citep{baldassano2013differential} in general: anterior and posterior PPA
-exhibit distinct connectivity patterns; object sensitivity in the PPA also has
-an anterior-posterior gradient of sensitivity to scene and abstract object
-stimuli.
-
-% gradient
-Data suggest that PPA might contain identifiable subregions, but subregions
-should not be considered as completely independent modules. Both subregions
-activate selectively to scenes, and the parahippocampal region (at least in
-macaques) is densely selfconnected (Suzuki, 2009), implying that these
-subregions cooperate to build a complete representation of a scene.
+The posterior PPA is more functionally connected to the occipital visual cortex,
+including lateral occipital cortex (LOC) and transverse occipital sulcus (TOS)
+\citep{baldassano2013differential}.
+% LOC and TOS
+[These regions have well-defined retinotopic maps (Arcaro et al., 2009; Nasr et
+al., 2011), and are associated with the perception of low-level visual features
+and object shape \citep{baldassano2013differential}.]
+% object sensitivity
+Previous work has hinted that posterior PPA is more responsive to both simple
+visual textures and (abstract) objects \citep{arcaro2009retinotopic,
+baldassano2013differential}.
 %
-Their distinct connectivity properties, however, suggests that each may be
-involved in specific aspects of visual and cognitive processing involved in the
-overarching goal of scene understanding.
-
-% from Baldassano discussion
-\citep{baldassano2013differential} regarding posterior PPA: posterior regions
-are more functionally connected to visual processing / occipital visual regions;
-stronger responses to abstract objects in posterior PPA; posterior PPA is
-concerned primarily with perception of low-level visual features and object
-shape.
-
-\citep{baldassano2013differential} discussion of posterior PPA: Posterior PPA
-shows a stronger response to abstract objects than anterior PPA, and is more
-strongly connected to all of occipital visual cortex, including LOC and TOS.
+The posterior portion of PPA responded about four times as strongly to a
+flickering checker-board stimulus compared to an anterior portion, and that the
+response to objects was greater than the response to scrambled images only in
+the posterior portion => posterior PPA may be more visually responsive than
+anterior PPA \citep{arcaro2009retinotopic}.
+% in summary: posterior
+In summary, the posterior PPA is more concerned with perception of low-level
+visual features and object shape.
+
+\paragraph{anterior: connectivity \& (non) contextual sensitivity}
+
+The anterior PPA is more functionally connected to the RSC and parietal cortices
+(caudal inferior parietal lobe; cIPL)[, medial PFC, and the lateral surface of
+the anterior temporal lobe] \citep{baldassano2013differential}.
+% default mode network
+[anterior PPA is also more strongly connected to regions in the default mode
+network (including the parieto-medial temporal pathway).
+\citep{baldassano2013differential}.]
+% DMN details
+The set of regions connected more strongly to anterior PPA is strikingly similar
+to the Default Mode Network (DMN) (Buckner et al., 2008; Fox et al., 2005;
+Raichle et al., 2001), which is known to include the parahippocampal region (the
+only portions of the DMN that do not show differential connectivity to anterior
+PPA in our data are the rostral portion of the posterior cingulate cortex (PCC)
+and the superior frontal cortex) \citep{baldassano2013differential}.
+% DMN and contextual association
+DMN has been implicated in a large number of internally-focused tasks, one of
+its key roles involves autobiographical memory (Buckner et al., 2008).  Models
+of recognition memory have previously identified parahippocampal cortex as
+primarily encoding spatial context information (Eichenbaum et al., 2007)
+\citep{baldassano2013differential}.
+% Baldassano regarding Aminoff
+Data from \citep{aminoff2007parahippocampal} has suggested that an anterior
+portion of PPA may be involved in recall based on spatial context
+\citep{baldassano2013differential}.
 %
-These regions have well-defined retinotopic maps (Arcaro et al., 2009; Nasr et
-al., 2011), and are associated with the perception of low-level visual features
-and object shape.
+Given anterior PPA's connectivity with the DMN.Our results are consistent with
+anterior PPA playing a more central role in memory than posterior PPA
+\citep{baldassano2013differential}.
+
+% object sensitivity
+The anterior PPA is less visually responsive to both scenes and objects, with
+notably low sensitivity to abstract object stimuli, and more involved in memory
+and global contextual processing \todo{quotes???}
 %
-Previous work has hinted that posterior PPA is more responsive to both simple
-visual textures and objects; Arcaro et al. (2009) found that a posterior portion
-of PPA responded about four times as strongly to a flickering checker-board
-stimulus compared to an anterior portion, and that the response to objects was
-greater than the response to scrambled images only in the posterior portion =>
-posterior PPA may be more visually responsive than anterior PPA.
-%
-Our description of posterior PPA is in fact similar to the original proposal of
-Aguirre et al. for a “lingual landmark area” (LLA), slightly posterior to PPA,
-which was “specialized for the perception of visual stimuli with orienting
-value” (Aguirre et al., 1998) and carried out bottom-up perceptual analysis to
-recognize locations or landmarks (Cant and Goodale, 2007; Epstein et al., 1999).
-%
-Although the LLA is no longer identified as an independent region from PPA in
-current studies, it is possible that the posterior portion of PPA corresponds to
-the properties of the proposed LLA, offring an explanation for why this region
-was localized more posteriorly than the full PPA.
-
-\citep{baldassano2013differential} regarding anterior PPA: anterior regions are
-more functionally connected to retrosplenial complex (RSC) and parietal
-cortices; anterior PPA is more strongly connected to regions in the default mode
-network (including the parieto-medial temporal pathway)
-%
-anterior PPA is involved in memory and global contextual processing; anterior
-PPA is specifically connected to RSC, cIPL, medial PFC, and the lateral surface
-of the anterior temporal lobe.
-%
-This portion of PPA is less visually responsive
-to both scenes and objects, with notably low sensitivity to abstract object
-stimuli.
-
-\citep{baldassano2013differential} regarding DMN: the set of regions connected
-more strongly to anterior PPA is strikingly similar to the Default Mode Network
-(DMN) (Buckner et al., 2008; Fox et al., 2005; Raichle et al., 2001), which is
-known to include the parahippocampal region.
-%
-The only portions of the DMN that do not show differential connectivity to
-anterior PPA in our data are the rostral portion of the posterior cingulate
-cortex (PCC) and the superior frontal cortex.  DMN has been implicated in a
-large number of internally-focused tasks, one of its key roles involves
-autobiographical memory (Buckner et al., 2008).  Models of recognition memory
-have previously identified parahippocampal cortex as primarily encoding spatial
-context information (Eichenbaum et al., 2007).
-%
-Data from Aminoff et al. (2007) has suggested that an anterior portion of PPA
-may be involved in recall based on spatial context.
-%
-Our results are consistent with anterior PPA playing a more central role in
-memory than posterior PPA, given anterior PPA's connectivity with the DMN. The
-fact that anterior PPA had a lower sensitivity to our abstract object stimuli
-does not necessarily im ply that this region does not use object information.
+The fact that anterior PPA had a lower sensitivity to our abstract object
+stimuli does not necessarily imply that this region does not use object
+information \citep{baldassano2013differential}.
 %
@@
 2011), and are navigationally-relevant (Janzen and Van Turennout, 2004).
+
+\paragraph{conclusion: subregions}
+
+\todo[inline]{re-read Baldassano (2013)}
+
+\todo[inline]{discussing PPA in context of contextual associations might provide
+a smooth transition to (possibly) following discussion of RSC}
+
+% Aminoff
+\citep{aminoff2013role} in general (s. also \citep{aminoff2007parahippocampal}:
+processing of strong, long-term, contextual associations elicits activity within
+the PHC, as well as the RSC (which includes regions of the retrosplenial cortex,
+extending into the posterior cingulate cortex, and the precuneus), the medial
+prefrontal cortex (MPFC), and the transverse occipital sulcus (TOS) (Figure 2)
+[2,3,59–67].
+% Aminoff: contextual associations in anterior vs. posterior
+\citep{aminoff2007parahippocampal} propose that a subregion of the posterior PHC
+is particularly optimized to process spatially organized contextual
+associations, whereas more anterior regions of the PHC are optimized to process
+contextual associations in other, non-spatial domains.
+% posterior PPA for visual visual associative information
+Spatial contextual associations are a dominant property of places and scenes,
+and thus scenes consistently activate this posterior subregion of the PHC (e.g.,
+PPA; Epstein, 1998).
+%
+We do not argue that the PHC is not sensitive to spaces, places, and spatial
+information, but rather that it is sensitive to spatial stimuli because of the
+associative information (space-related associations) that such stimuli evoke.
+
+% Aminoff regarding contextual processing in the PHC and beyond
+\citep{aminoff2007parahippocampal}: We compared contextual processing of objects
+that are strongly related to a specific place (e.g., an oven is found in a
+kitchen) with contextual processing of objects that are highly associated with a
+context but not a specific place (e.g., a birthday cake is found at a birthday
+party, but the party can take place anywhere, at home, in a restaurant, at a
+park).
+% method
+Activity elicited by these two types of contextual objects was compared with the
+activity elicited for objects that were only weakly associated with many
+contexts (e.g., a lamp).
+% results
+Differential activity was found in the PHC and the RSC, replicating the previous
+findings (Bar \& Aminoff, 2003, The parahippocampal\dots).
+% results 2
+\citep{aminoff2007parahippocampal} Activity within the PHC, however, was
+distributed along an anterior–posterior axis, with activity related to spatial
+contexts focused in the posterior part of the PHC and activity evoked by
+non-spatial contexts focused in the more anterior part of the PHC (Bar \&
+Aminoff, 2003, Cortical analysis of visual context; Aminoff et al., 2007, The
+parahippocampal cortex mediates spatial and nonspatial associations).
+
+% Baldassano (2013): PPA subregions
+Data suggest that PPA might contain identifiable subregions, but subregions
+should not be considered as completely independent modules. Both subregions
+activate selectively to scenes, implying that these subregions cooperate to
+build a complete representation of a scene [that sentence is taken from
+\citep{baldassano2013differential}].
+% Baldassano (2013): conclusion
+Their distinct connectivity properties, however, suggests that each may be
+involved in specific aspects of visual and cognitive processing involved in the
+overarching goal of scene understanding.
 %
@@
 information is used in this region.
-
-\subsubsection{anterior vs posterior PPA: contextual associations}
-
-\todo[inline]{discussing PPA in context of contextual associations might provide
-a smooth transition to (possibly) following discussion of RSC}
-
-% Aminoff (2013)
-\citep{aminoff2013role} in general (s. also \citep{aminoff2006parahippocampal}:
-processing of strong, long-term, contextual associations elicits activity within
-the PHC, as well as the RSC (which includes regions of the retrosplenial cortex,
-extending into the posterior cingulate cortex, and the precuneus), the medial
-prefrontal cortex (MPFC), and the transverse occipital sulcus (TOS) (Figure 2)
-[2,3,59–67].
-
-% contextual associations in anterior vs. posterior
-\citep{aminoff2006parahippocampal}: We propose that the general function of the
-PHC can be thought of as processing of contextual associations.
-%
-A subregion of the posterior PHC is particularly optimized to process spatially
-organized contextual associations, whereas more anterior regions of the PHC are
-optimized to process contextual associations in other, non-spatial domains.
-% posterior PPA for visual visual associative information
-Spatial contextual associations are a dominant property of places and scenes,
-and thus scenes consistently activate this posterior subregion of the PHC (e.g.,
-PPA; Epstein, 1998).
-%
-We do not argue that the PHC is not sensitive to spaces,
-places, and spatial information, but rather that it is sensitive to spatial
-stimuli because of the associative information (space-related associations) that
-such stimuli evoke.
-
-% Aminoff regarding contextual processing in the PHC and beyond
-\citep{aminoff2006parahippocampal} regarding contextual associations processing
-in PHC and beyond: We compared contextual processing of objects that are
-strongly related to a specific place (e.g., an oven is found in a kitchen) with
-contextual processing of objects that are highly associated with a context but
-not a specific place (e.g., a birthday cake is found at a birthday party, but
-the party can take place anywhere, at home, in a restaurant, at a park).
-% method
-Activity elicited by these two types of contextual objects was compared with the
-activity elicited for objects that were only weakly associated with many
-contexts (e.g., a lamp).
-% results
-Differential activity was found in the PHC and the RSC,
-replicating the previous findings (Bar \& Aminoff, 2003, The
-parahippocampal\dots).
-% results 2
-\citep{aminoff2006parahippocampal} Activity within the PHC, however, was
-distributed along an anterior–posterior axis, with activity related to spatial
-contexts focused in the posterior part of the PHC and activity evoked by
-non-spatial contexts focused in the more anterior part of the PHC (Bar \&
-Aminoff, 2003, Cortical analysis of visual context; Aminoff et al., 2007, The
-parahippocampal cortex mediates spatial and nonspatial associations).
 
@@
 
-\subsubsection{superior lateral occipital cortex (OPA; in both stimuli)}
+\subsubsection{superior lateral occipital cortex (TOC / OPA?)}
 
@@
 
-\todo[inline]{give numbers of contrast in AO \& AV that show sign. clusters in
-RSC}
+\todo[inline]{numbers of contrast in AO \& AV that show sign. clusters in
+LOC}
 
@@
     in Scene Perception; Dilks, Kanwisher (2013). The Occipital Place Area Is
-Causally and Selectively Involved in Scene Perception?}
+    Causally and Selectively Involved in Scene Perception; Grill-Spector (2003).
+    The neural basis of object perception; Nakamura (2000). Functional
+    delineation of the human occipito-temporal areas; Nasr (2011).
+    Scene-selective cortical regions in human and nonhuman primates; Hasson
+    (2003). Large-scale mirror-symmetry organization; MacEvoy and Epstein
+    (2007). Position selectivity in scene- and object-responsive\dots; Dilks
+(2011). Mirror-image sensitivity and invariance in object \& scene processing}
 

### 2020-11-18 paper/main.tex
restructure quotes aPPA vs pPPA

@@
 %  at the moment 109 Chars
-\title{Hemodynamic responses of the Parahippocampal Place Area to spatial cues in a movie and its audio-description}
+\title{Hemodynamic responses of the anterior "parahippocampal place area" (PPA) to a Hollywood movie's audio-description}
 
@@
 Neuroimaging studies have parcellated the human brain into distinct functional
-regions.
+areas.
 % PPA
@@
 % intro
-Notably, results of the AO contrasts consistently yielded significant clusters
+Results of the AO contrasts consistently yielded significant clusters
 spatially constrained to the anterior part of the PPA group overlap (and
@@
 % intro to connectivity and object gradient
-Previous studies suggest that posterior and anterior part of the PPA show both a
-difference in connectivity profiles \citep{baldassano2013differential} and a
-gradient in sensitivity to scene and abstract object stimuli
+[kind of complete overview of (references):] Previous studies suggest that
+posterior and anterior part of the PPA show differences in
+% connectivity
+a) connectivity profiles \citep{baldassano2013differential, baldassano2016two}[+
+Nasr et al., 2013; Silson et al., 2016a],
+% scenes vs abstract objects
+b) a gradient in sensitivity scene and abstract object stimuli
 \citep{arcaro2009retinotopic, aminoff2007parahippocampal,
-baldassano2013differential}.
-% high level summary: posterior
-
-\paragraph{posterior: connectivity \& object sensitivity}
-
-% Baldassano (2013): Our description of posterior PPA is in fact similar to the
-% original proposal of Aguirre et al. for a “lingual landmark area” (LLA),
-% slightly posterior to PPA, which was “specialized for the perception of visual
-% stimuli with orienting value” (Aguirre et al., 1998) and carried out bottom-up
-% perceptual analysis to recognize locations or landmarks (Cant and Goodale,
-% 2007; Epstein et al., 1999). Although the LLA is no longer identified as an
-% independent region from PPA in current studies, it is possible that the
-% posterior portion of PPA corresponds to the properties of the proposed LLA,
-% offering an explanation for why this region was localized more posteriorly
-% than the full PPA.
+baldassano2013differential},
+% low-level scene features
+c) differences in response to low-level scene features [Nasr et al., 2014;
+Silson et al., 2015; Baldassano et al., 2016a,b; Watson et al., 2016],
+% high-level scene features
+d) high-level scene features [Park et al., 2014; Aminoff and Tarr, 2015; Linsley
+and Macevoy, 2015; Marchette et al., 2015],
+% TMS
+e) stimulation studies [Rafique et al., 2015] \citep{baldassano2016two}
+
+\paragraph{posterior PPA (pPPA)}
 
 % connectivity
-The posterior PPA is more functionally connected to the occipital visual cortex,
-including lateral occipital cortex (LOC) and transverse occipital sulcus (TOS)
-\citep{baldassano2013differential}.
+The posterior PPA is more [strongly] functionally connected to the occipital
+visual cortex, including lateral occipital cortex (LOC) and transverse occipital
+sulcus (TOS) \citep{baldassano2013differential, baldassano2016two}.
 % LOC and TOS
@@
 and object shape \citep{baldassano2013differential}.]
+
+%
+Increased activity within the pPHC during viewing of scenes relative to objects
+has been suggested to reflect regional specialization for visuospatial processes
+related to the extraction of scene layout information [Epstein,
+2008]\citep{baumann2016functional}.
+
+% high-level visual features
+Higher-level visual features also drive response patterns in these regions
+[Bryan et al., 2016]. They are hypothesized to be involved in extracting visual
+environmental features that can be used for navigation [Marchette et al., 2015;
+Julian et al., 2016; Kamps et al., 2016]. However, neither OPA nor posterior PPA
+show reliable familiarity effects [Epstein et al., 2007b; see further discussion
+below]\citep{baldassano2016two}.
+%
+The idea that the pPHC serves a dedicated role in visuospatial processing is
+further supported by studies showing that this brain region is sensitive to
+changes in basic visuospatial properties such as the shape and spatial frequency
+of abstract geometric objects and layouts [Rajimehr et al., 2011; Zeidman et
+al., 2012]\citep{baumann2016functional}.
+
 % object sensitivity
-Previous work has hinted that posterior PPA is more responsive to both simple
-visual textures and (abstract) objects \citep{arcaro2009retinotopic,
-baldassano2013differential}.
-%
-The posterior portion of PPA responded about four times as strongly to a
-flickering checker-board stimulus compared to an anterior portion, and that the
-response to objects was greater than the response to scrambled images only in
-the posterior portion => posterior PPA may be more visually responsive than
-anterior PPA \citep{arcaro2009retinotopic}.
-% in summary: posterior
-In summary, the posterior PPA is more concerned with perception of low-level
-visual features and object shape.
-
-\paragraph{anterior: connectivity \& (non) contextual sensitivity}
-
-The anterior PPA is more functionally connected to the RSC and parietal cortices
-(caudal inferior parietal lobe; cIPL)[, medial PFC, and the lateral surface of
-the anterior temporal lobe] \citep{baldassano2013differential}.
-% default mode network
-[anterior PPA is also more strongly connected to regions in the default mode
-network (including the parieto-medial temporal pathway).
-\citep{baldassano2013differential}.]
-% DMN details
-The set of regions connected more strongly to anterior PPA is strikingly similar
-to the Default Mode Network (DMN) (Buckner et al., 2008; Fox et al., 2005;
-Raichle et al., 2001), which is known to include the parahippocampal region (the
-only portions of the DMN that do not show differential connectivity to anterior
-PPA in our data are the rostral portion of the posterior cingulate cortex (PCC)
-and the superior frontal cortex) \citep{baldassano2013differential}.
-% DMN and contextual association
-DMN has been implicated in a large number of internally-focused tasks, one of
-its key roles involves autobiographical memory (Buckner et al., 2008).  Models
-of recognition memory have previously identified parahippocampal cortex as
-primarily encoding spatial context information (Eichenbaum et al., 2007)
+The pPPA is more responsive to both simple visual textures and (abstract)
+objects \citep{arcaro2009retinotopic, baldassano2013differential}:
+%
+The pPPA responded about four times as strongly to a
+flickering checker-board stimulus compared to an anterior portion
+\citep{arcaro2009retinotopic}.
+%
+The response to objects was greater than the
+response to scrambled images only in the posterior portion
+\citep{arcaro2009retinotopic}.
+
+% low-level features
+OPA and pPPA have been shown to be closely related to the visual content of a
+stimulus. Even low-level manipulations of spatial frequency [Rajimehr et al.,
+2011; Kauffmann et al., 2015; Watson et al., 2016] or rectilinearity [Nasr et
+al., 2014] can drive responses in these regions \citep{baldassano2016two}.
+
+% baumann2016functionl
+We observed that pPHC is more strongly modulated bilaterally by the visual
+properties of the stimulus material (as evidenced by strong responses in the
+picture-scene conditions and no significant response in the word-object
+conditions)\citep{baumann2016functional}.
+%
+Our current study [and findings of Baldassano et al. (2013)] suggest that the
+functional topographic segregation of the PHC is underpinned by corresponding
+segregated connectivity patterns. Findings are consistent with a model of
+parahippocampal function in which visual information is projected from occipital
+and temporal areas to the pPHC [Libby et al., 2012], where encoding of
+visuospatial information takes place (a process that is computationally more
+demanding for complex stimuli such as scenes than for simple ones such as
+objects; Chai et al., 2010)\citep{baumann2016functional}.
+
+\paragraph{posterior network}
+
+% baldassano2016two
+The 1st (posterior) network [of two networks] includes
+pPPA and OPA/TOS. pPPA (retinotopic maps PHC1 \& PHC2) and OPA/TOS contain
+retinotopic maps and are not strongly coupled to the hippocampus at rest
+\citep{baldassano2016two}.
+
+% baldassano20160two: Neurosynth meta-analysis
+\citep{baldassano2016two}'s ``meta-analysis'' using Neurosynth: we compare the
+query ``scene'' (47 studies) with the query ``episodic memory, navigation, past
+future'' (125 studie).
+%
+Results: voxels significant only in the scene meta-analysis were concentrated in
+the posterior network (66\% in posterior network, 18\% in anterior, 16\% in
+other) % baldassano2016two: meta-analysis
+\citep{baldassano2016two} Voxels significant in both the scene and
+memory/navigation meta-analyses tended to fall near the border between the two
+networks and divided approximately equally among them (44\% posterior, 53\%
+anterior, 4\% other).
+%
+\citep{baldassano2016two} Voxels significant only in the memory/navigation
+meta-analysis were spread more widely across the cortex, but were concentrated
+more in the anterior than the posterior network (16\% posterior, 42\% anterior,
+42\% other).
+
+% interpretation
+Interpretation: visual scene activations tend to be posterior to the memory
+activations along the parahippocampal gyrus. [The transition point corresponds
+almost exactly to the division between our two networks. Dorsally, we also
+observe a separation between the reverse inference maps, with scene and memory
+activations falling into our two separate networks \citep{baldassano2016two}.]
+
+\paragraph{anterior PPA (aPPA)}
+
+The specific properties of aPPA have been less well studied, since it was not
+recognized as a separate region within the PPA until recently
+\citep{baldassano2016two}.
+
+% anterior PPA
+The anterior PPA is more [strongly] functionally connected to the RSC and
+parietal cortices (caudal inferior parietal lobe; cIPL)[, medial PFC, and the
+lateral surface of the anterior temporal lobe]
+\citep{baldassano2013differential, baldassano2016two}.
+
+% object sensitivity
+The aPPA is less visually responsive to both scenes\todo{check their paradigm \&
+result section} and objects, with notably low sensitivity to abstract object
+stimuli \citep{baldassano2013differential}.
+%
+Results suggest that aPPA may be more concerned with these types of spatial and
+non-object-based scene properties [= global scene properties such as spatial
+expanse] than posterior PPA \citep{baldassano2013differential}\todo{check if
+quoted correctly}.
+
+\citep{baldassano2016two} The aPPA is
+% category
+a) driven more by high-level category information than by spatial frequency
+content [Watson et al., 2016],
+% locations
+b) to represent real-world locations (even from perceptually distinct views)[
+Marchette et al., 2015],
+% associations
+c) to encode object co-occurrences [Aminoff and Tarr, 2015], and
+% scene size
+d) to represent real-world physical scene size [Park et al., 2014]
+\citep{baldassano2016two}.
+% spaciousness
+Its representation of scene spaciousness draws on prior knowledge about the
+typical size of different scene categories, since it is affected by the presence
+of diagnostic objects [Linsley and Macevoy, 2015]\citep{baldassano2016two}.
+
+\paragraph{anterior network}
+
+% baldassano2016two's networks
+\citep{baldassano2016two} The anterior network (the 2nd of two networks)
+consists of the caudal inferior parietal lobule (cIPL), RSC, and aPPA, which
+connect to the hippocampus (especially anterior hippocampus). These regions are
+implicated in both visual and nonvisual tasks, including episodic memory and
+navigation] \citep{baldassano2016two}.
+% baldassano2016connectivity
+The anterior network [that includes aPPA] exhibits much higher resting-state
+hippocampal coupling (especially to anterior hippocampus), suggesting that
+memory- and navigation-related functions are primarily restricted to the
+anterior network \citep{baldassano2016two}.
+
+% The memory and navigational network
+The network of parahippocampal, retrosplenial, and posterior parietal regions
+that we identify has been emerged independently in many different fields of
+neuroimaging, outside of scene perception.
+%
+Meta-analyses of internally directed tasks, such as theory of mind,
+autobiographical memory, and prospection, have identified this as a core,
+reoccurring network [Spreng et al., 2009; Kim,2010; Yeo et al., 2015 (component
+C10 of ?)]. It comprises a subset of the broader default mode regions, but
+functional and anatomical evidence suggests that it is a distinct, coherent
+subnetwork [Andrews-Hanna et al., 2010, 2014; Yeo et al.,
+2011]\citep{baldassano2016two}.
+%
+The broad set of tasks that recruit this network have been summarized in various
+ways, such as ``scene construction'' (Hassabis and Maguire, 2007), ``mnemonic
+scene construction'' [Andrews-Hanna et al., 2010], ``long-timescale
+integration'' [Hasson et al., 2015], or ``relational processing'' [Eichenbaum
+and Cohen, 2014].
+%
+A review of memory studies referred to this network as the posterior medial
+memory system, and proposed that it is involved in any task requiring
+``situation models'' relating entities, actions, and outcomes [Ranganath and
+Ritchey, 2012]\citep{baldassano2016two}.
+
+% hippocampus
+The network has strong functional connections to the hippocampus, which has been
+implicated in a broad set of cognitive tasks involving ``cognitive maps'' for
+organizing declarative memories, spatial routes, and even social dimensions
+[Eichenbaum and Cohen, 2014; Schiller et al., 2015]. During perception, the
+hippocampus binds together visual elements of an image [Olsen et al., 2012;
+Warren et al., 2012; Zeidman et al., 2015], which is especially important for
+scene stimuli [Lee et al., 2005a,b; Graham et al., 2006; Hodgetts et al., 2016].
+The hippocamppus then stores this representation into long-term memory [Ryan and
+Cohen, 2004]\citep{baldassano2016two}.
+%
+Our results suggest that only the anterior scene regions interface directly with
+the hippocampus, potentially enabling the construction of hippocampal
+environmental representations, and retrieval of relevant memories and
+navigational information for a presented or imagined
+scene\citep{baldassano2016two}.
+
+\paragraph{conclusion \& interpetation: subregions}
+
+% conclusion by Baldassano (2013): PPA subregions
+Data suggest that PPA might contain identifiable subregions, but subregions
+should not be considered as completely independent modules.
+%
+Both subregions activate selectively to scenes, implying that these subregions
+cooperate to build a complete representation of a scene
 \citep{baldassano2013differential}.
-% Baldassano regarding Aminoff
-Data from \citep{aminoff2007parahippocampal} has suggested that an anterior
-portion of PPA may be involved in recall based on spatial context
-\citep{baldassano2013differential}.
-%
-Given anterior PPA's connectivity with the DMN.Our results are consistent with
-anterior PPA playing a more central role in memory than posterior PPA
-\citep{baldassano2013differential}.
-
-% object sensitivity
-The anterior PPA is less visually responsive to both scenes and objects, with
-notably low sensitivity to abstract object stimuli, and more involved in memory
-and global contextual processing \todo{quotes???}
-%
-The fact that anterior PPA had a lower sensitivity to our abstract object
-stimuli does not necessarily imply that this region does not use object
-information \citep{baldassano2013differential}.
-%
-Previous work has shown that PPA responds to objects that have spatial
-associations (Aminoff et al., 2007), are space-defining (Mullally and Maguire,
-2011), and are navigationally-relevant (Janzen and Van Turennout, 2004).
-
-\paragraph{conclusion: subregions}
-
-\todo[inline]{re-read Baldassano (2013)}
-
-\todo[inline]{discussing PPA in context of contextual associations might provide
-a smooth transition to (possibly) following discussion of RSC}
-
-% Aminoff
-\citep{aminoff2013role} in general (s. also \citep{aminoff2007parahippocampal}:
-processing of strong, long-term, contextual associations elicits activity within
-the PHC, as well as the RSC (which includes regions of the retrosplenial cortex,
-extending into the posterior cingulate cortex, and the precuneus), the medial
-prefrontal cortex (MPFC), and the transverse occipital sulcus (TOS) (Figure 2)
-[2,3,59–67].
-% Aminoff: contextual associations in anterior vs. posterior
-\citep{aminoff2007parahippocampal} propose that a subregion of the posterior PHC
-is particularly optimized to process spatially organized contextual
-associations, whereas more anterior regions of the PHC are optimized to process
-contextual associations in other, non-spatial domains.
+
+We do not argue that the PHC is not sensitive to spaces, places, and spatial
+information, but rather that it is sensitive to spatial stimuli because of the
+associative information (space-related associations) that such stimuli evoke
+\citep{aminoff2013role}.
 % posterior PPA for visual visual associative information
@@
 and thus scenes consistently activate this posterior subregion of the PHC (e.g.,
-PPA; Epstein, 1998).
-%
-We do not argue that the PHC is not sensitive to spaces, places, and spatial
-information, but rather that it is sensitive to spatial stimuli because of the
-associative information (space-related associations) that such stimuli evoke.
-
-% Aminoff regarding contextual processing in the PHC and beyond
-\citep{aminoff2007parahippocampal}: We compared contextual processing of objects
-that are strongly related to a specific place (e.g., an oven is found in a
-kitchen) with contextual processing of objects that are highly associated with a
-context but not a specific place (e.g., a birthday cake is found at a birthday
-party, but the party can take place anywhere, at home, in a restaurant, at a
-park).
-% method
-Activity elicited by these two types of contextual objects was compared with the
-activity elicited for objects that were only weakly associated with many
-contexts (e.g., a lamp).
-% results
-Differential activity was found in the PHC and the RSC, replicating the previous
-findings (Bar \& Aminoff, 2003, The parahippocampal\dots).
-% results 2
-\citep{aminoff2007parahippocampal} Activity within the PHC, however, was
-distributed along an anterior–posterior axis, with activity related to spatial
-contexts focused in the posterior part of the PHC and activity evoked by
-non-spatial contexts focused in the more anterior part of the PHC (Bar \&
-Aminoff, 2003, Cortical analysis of visual context; Aminoff et al., 2007, The
-parahippocampal cortex mediates spatial and nonspatial associations).
-
-% Baldassano (2013): PPA subregions
-Data suggest that PPA might contain identifiable subregions, but subregions
-should not be considered as completely independent modules. Both subregions
-activate selectively to scenes, implying that these subregions cooperate to
-build a complete representation of a scene [that sentence is taken from
-\citep{baldassano2013differential}].
-% Baldassano (2013): conclusion
+PPA; epstein1998ppa)\citep{aminoff2013role}.
+
+% baldassano2013: functional contrast
+The fact that aPPA had a lower sensitivity to our abstract object stimuli does
+not necessarily imply that this region does not use object information
+\citep{baldassano2013differential}.
+% baldassano2013: connectivity
 Their distinct connectivity properties, however, suggests that each may be
@@
 %
-These types of responses require spatial memory and cannot be based purely on
-visual features like object shape.
+Previous work has shown that PPA responds to objects that have spatial
+associations [Aminoff et al., 2007], are space-defining [Mullally and Maguire,
+2011], and are navigationally-relevant [Janzen and Van Turennout, 2004]. These
+types of responses require spatial memory and cannot be based purely on visual
+features like object shape.
 %
@@
 than our abstract objects, which were unfamiliar and provided no sense of
-context or orientation.
-%
-Further experiments will be required to determine what type of object-related
-information is used in this region.
+context or orientation \citep{baldassano2013differential}. Further experiments
+will be required to determine what type of object-related information is used in
+this region \citep{baldassano2013differential}.
+
+% baldassano2016two
+\citep{baldassano2016two}: We propose that scene processing is fundamentally
+divided into two collaborating but distinct networks
+%
+One is focused on the visual features of a scene image. The other is related to
+contextual retrieval and navigation.
+%
+Under this framework, scene perception is less the function of a unified set of
+distributed neural machinery and more of ``an ongoing dialogue between the
+material and symbolic aspects of the past and the continuously unfolding
+present'' (Baker, 2012, in The Word Hoard).
+%
+\citep{baldassano2016two} with respect to natural scene perception: one can
+imagine at least two separable functions:
+%
+1) processing the specific visual features present in the current glance of a
+scene,
+%
+2) and connecting that to the stable, high-level knowledge of where the place
+exists in the world, what has happened here in the past, and what possible
+actions we could take here in the future \citep{baldassano2016two}.
+%
+For most cognitive and physical tasks we undertake in real-world places, the
+specific visual attributes we perceive are just a means to this end, of
+recalling and updating information about the physical environment; ``the
+essential feature of a landmark is not its design, but the place it holds in a
+city’s memory'' [Muschamp, 2006, in New York Times]\citep{baldassano2016two}.
+
+\subsubsection{contextual associations: Baumann 2016}
+
+% visuospatial and mnemonic processes
+The PHC plays a key role in both visuospatial analysis of scenes [Epstein et
+al., 1999, 2003; Park and Chun, 2009; Rajimehr et al., 2011] and (contextual)
+mnemonic processing [Aminoff et al., 2013, Bar and Aminoff, 2003; Düzel et al.,
+    2003; Janzen and van Turennout, 2004; Baumann et al., 2010; Wegman and
+Janzen, 2011] \citep{baumann2016functional}
+% associative processing
+The PCH has been implicated in the integration and retrieval of contextual
+associations in memory [Aminoff et al., 2013; Bar and Aminoff, 2003; Bar et al.,
+2008a, 2008b].
+
+Contextual associations: relations between objects and conditions that describe,
+represent, and bring meaning to an environment [Aminoff et al., 2013]
+\citep{baumann2016functional}.
+%
+Examples: objects that commonly co-occur, such as a refrigerator and an oven
+(typically in a kitchen) or familiar spatial configurations of objects, (rows of
+tables and chairs in a school classroom). According to this view, activity in
+the parahippocampal cortex reflects modality-independent retrieval of contextual
+information from memory, such as which objects typically occur in a given scene
+and where they are likely to be located relative to one another
+\citep{baumann2016functional}.
+
+%
+However, it has remained unclear whether these two processes are functionally
+and anatomically segregated within the parahippocampal cortex
+\citep{baumann2016functional}.
+%
+We provide evidence for a dissociation between neural activation patterns
+associated with visuospatial analysis of scenes and contextual mnemonic
+processing along the parahippocampal longitudinal axis
+\citep{baumann2016functional}.
+
+%
+\citep{baumann2016functional} paradigm: We measure parahippocampal responses
+while participants engaged in a task that required them to judge the contextual
+relatedness of scene and object pairs, which were presented either as words or
+pictures \citep{baumann2016functional}.
+%
+Participants judged the contextual relatedness of scene and object pairs (“bike”
+\& “bell” are a contextually congruent object– object pair, “sofa” \&
+“microscope” are incongruent; “boat” \& “lake” are a contextually congruent
+object–scene pair, “tractor” \& “hotel” are
+incongruent)\citep{baumann2016functional}.
+%
+Each pair was presented either in printed-word format or in a combined
+word–picture format. That allowed us to present pictorial objects and scenes in
+isolation (Fig. 1)\citep{baumann2016functional}.
+%
+To identify visuospatial regions of the PHC, we tested for voxels with greater
+activity for picture–scene trials than for picture–object trials over and above
+activity differences elicited by the comparison of word–scene trials and word–
+object trials\citep{baumann2016functional}.
+%
+Additionally to locate context-related regions of the PHC, we tested for voxels
+that were selectively active during the contextual judgment task regardless of
+the type of stimulus (scenes vs objects) or presentation modality (word vs
+picture)\citep{baumann2016functional}.
+
+%
+Results: aPHC is more active during contextual
+judgments regardless of stimulus category (scenes vs objects) or modality (word
+vs picture).
+%
+The left aPHC was active in all contextual judgment task conditions. This
+suggests a functional segregation, with posterior sections of the PHC supporting
+visuospatial processing of scenes and anterior sections of the left PHC involved
+in contextual associative processing\citep{baumann2016functional}.
+%
+It is important to note that, whereas our study only examined retrieval-related
+activity for object–object and object–scene relationships, findings from prior
+studies suggest that the functions of the aPHC are not limited to these types of
+material, but should also be involved in the retrieval of associations involving
+other stimulus categories such as faces [Düzel et al., 2003; Kirwan and Stark,
+2004]\citep{baumann2016functional}.
+
+%
+Interpretation: Activation maxima associated with visuospatial and mnemonic
+processes were spatially segregated, providing support for the existence of
+functionally distinct subregions along the PHC longitudinal axis and suggesting
+that the PHC serves as a functional interface between perception and memory
+systems\citep{baumann2016functional}.
+%
+This anatomical segregation of function [cf. their results] suggests a
+predominantly perceptual role for the pPHC and a mnemonic role for the anterior
+parahippocampal cortex (Note: the anterior parahippocampal cortex should not be
+confused with the anterior portion of the parahippocampal gyrus, which includes
+the perirhinal cortex; Ranganath and Ritchey,
+2012.)\citep{baumann2016functional}.
+%
+We suggest that the aPHC encodes incoming information in an amodal format and
+acts as an interface with other memory regions, including the hippocampal,
+retrosplenial, and perirhinal memory systems (see Ranganath and Ritchey, 2012,
+for an review)\citep{baumann2016functional}.
+%
+Linsley and McEvoy (2015) found (using an fMRI searchlight analysis) that
+activity patterns in the aPHC were strongly modulated by the presence of objects
+in scenes; patterns in the pPHC were not modulated. This again suggests that the
+aPHC is more concerned with contextual than visuospatial analysis of scene
+images\citep{baumann2016functional}.
+
+%
+Hypothesis: Moreover, it is conceivable that different categories of contextual
+associations (e.g., spatial, temporal, affective, etc.) cluster in different
+subregions within the aPHC.  High-resolution fMRI and analysis techniques such
+as adaptation fMRI [Krekelberg et al., 2006] or multivoxel pattern
+classification [Norman et al., 2006] could be used to determine any such
+finegrained functional topography within the parahippocampal cortex]
+
+\subsubsection{contextual associations: Aminoff 2013 (review) + 2015}
+
+% memory
+Models of recognition memory have previously identified parahippocampal cortex
+as primarily encoding spatial context information (Eichenbaum et al., 2007)
+\citep{baldassano2013differential}.
+
+% contextual associations in anterior vs. posterior
+\citep{aminoff2013role} proposed that the general function of the PHC can be
+thought of as processing of contextual associations. Activity within the PHC is
+distributed along an anterior–posterior axis:
+% pPPA
+Activity related to spatial contexts is focused in the posterior part of the PHC
+=> posterior subregion of PHC is particularly optimized to process spatially
+organized contextual associations.
+% aPPA
+Activity evoked by non-spatial contexts focused in the more anterior part of the
+PHC (optimized to process contextual associations in other, non-spatial domains)
+[bar2003cortical, aminoff2007parahippocampal] \citep{aminoff2013role}.
+
+% Aminoff regarding contextual processing in the PHC and beyond
+\citep{aminoff2013role} regarding method in [aminoff2007parahippocampal]: we
+compared contextual processing of objects that are strongly related to a
+specific place (oven is found in a kitchen) with contextual processing of
+objects that are highly associated with a context but not a specific place
+(birthday cake is found at a birthday party; but the party can take place
+anywhere)\citep{aminoff2013role}.
+%
+Activity elicited by these two types of contextual objects was compared with the
+activity elicited for objects that were only weakly associated with many
+contexts (e.g., a lamp) \citep{aminoff2013role}.
+% results
+Differential activity was found in the PHC and the RSC, replicating the previous
+findings [Bar \& Aminoff (2003) The parahippocampal\dots]
+\citep{aminoff2013role}.
+
+\citep{baumann2016functional} zu \citep{aminoff2015associative}:
+% pPHC
+pPHC showed increased activity when participants viewed (alrady familiar)
+spatial configurations of meaningless shapes (regardless of their individual
+identities);
+% aPHC
+aPHC was more active during the display of (already familiar) meaningless shapes
+(regardless of their spatial configuration).
+%
+These findings can be interpreted as suggestive of pPHC visuospatial processes
+and aPHC contextual processes \citep{baumann2016functional}.
+
+\paragraph{Abstract}
+
+\citep{aminoff2015associative} How are complex visual entities such as scenes
+represented in the human brain? Along what visual and semantic dimensions are
+scenes encoded in memory?
+%
+One hypothesis: global spatial properties provide a basis for categorizing the
+neural response patterns arising from scenes \citep{aminoff2015associative}.
+%
+In contrast, non-spatial properties, such as single objects, also account for
+variance in neural responses\citep{aminoff2015associative}.
+
+%
+The list of critical scene dimensions has continued to grow (sometimes in a
+contradictory manner), coming to encompass properties such as geometric layout,
+big/small, crowded/sparse, and
+three-dimensionality\citep{aminoff2015associative}.
+%
+We demonstrate that these dimensions may be better understood within the more
+general framework of associative properties\citep{aminoff2015associative}.
+%
+Across both the perceptual and semantic domains, features of scene
+representations are related to one another through learned
+associations\citep{aminoff2015associative}.
+
+%
+We investigated whether different types of relations, all falling under the
+heading of associative processing, reliably recruit specific components of the
+network of brain regions known to be scene
+selective\citep{aminoff2015associative}.
+%
+Critically, the components of such associations are consistent with the
+dimensions that are typically invoked to account for scene understanding and its
+neural bases\citep{aminoff2015associative}.
+
+Results: We show that non-scene stimuli displaying novel associations across
+identities or locations recruit putatively scene-selective regions of the human
+brain (the parahippocampal/lingual region, the retrosplenial complex, and the
+transverse occipital sulcus/occipital place area)\citep{aminoff2015associative}.
+%
+Moreover, we find that the voxel-wise neural patterns arising from these
+associations are significantly correlated with the neural patterns arising from
+everyday scenes providing evidence whether the same encoding principals underlie
+both types of processing\citep{aminoff2015associative}.
+
+%
+Interpretation: Results provide evidence for the hypothesis that the neural
+representation of scenes is better understood within the broader theoretical
+framework of associative processing\citep{aminoff2015associative}.
+%
+Results also demonstrate a division of labor that arises across scene-selective
+regions when processing associations and scenes providing better understanding
+of the functional roles of each region within the cortical network that mediates
+scene processing\citep{aminoff2015associative}.
+
+\paragraph{Intro}
+
+Scenes are complex stimuli containing rich, statistically regular information
+about objects, background, context, semantics, and spatial layout at multiple
+scales\citep{aminoff2015associative}.
+%
+As a core component of scene understanding we extract and learn these
+regularities (for example, coming to know that certain objects typically appear
+together or that certain objects are likely to appear in a given spatial
+relationship [1–3])\citep{aminoff2015associative}.
+%
+Critically, these associated regularities are not only useful in defining scene
+categories, but also in predicting which other objects and relations are likely
+to occur within a scene [5]\citep{aminoff2015associative}.
+
+% a-modality
+Features of any kind of mental representation, irrespective as to whether that
+representation is nominally visual, linguistic, etc., are related to one another
+via learned associations\citep{aminoff2015associative}.
+%
+These associations are not necessarily modality-specific (for example, visual
+representations are likely to carry many semantic and affective associations not
+directly present in the image)\citep{aminoff2015associative}.
+%
+With respect to scene understanding, we construe contextual associative
+processing as a more semantically-driven process in which associations are not
+arbitrary relations, but rather relations that emerge as a consequence of their
+shared context within the larger scene.
+%
+Associations are not simply frequently co-occurring features pairs; instead they
+are pairs that both co-occur and add meaning to scenes
+\citep{aminoff2015associative}.
+%
+Furthermore, the mechanism by which scenes are perceived, recognized, and
+understood, is through means of processing the associations elicited from
+components of the scene \citep{aminoff2015associative}.
+
+%
+At the core of neurally-based theories of scene perception are the issues of the
+computations and representations instantiated in each of these brain regions.
+The literature has focused on more on the latter, characterizing the nature of
+the information encoded about scenes\citep{aminoff2015associative}.
+%
+It has been suggested that scenes are analyzed in terms of their spatial global
+properties, such as the ‘spatial envelope’, which takes into account a scene’s
+overall spatial structure and layout [20,21]\citep{aminoff2015associative}.
+%
+Empirically, it has been demonstrated that these global properties are salient
+cues for categorizing scenes in both behavior [22] and in patterns of neural
+activity [23–26]\citep{aminoff2015associative}.
+%
+Compared to other factors that characterize scenes (i.e., content and
+depth), the expanse of the scene (i.e. its spatial boundary) has been found to
+be the most effective in accounting for variations in the neural responses
+within scene-selective brain regions [23,24]\citep{aminoff2015associative}.
+%
+Generally, spatial information defining the geometric layout of a scene has
+often been implicated in determining the neural responses arising from
+scene-selective brain regions [27]\citep{aminoff2015associative}.
+
+%
+In contrast, non-spatial properties can account for variations in the neural
+responses associated with scene processing and representation\citep{aminoff2015associative}.
+%
+For example, Harel et al. [11], found that the neural encoding of scenes
+captures information about single objects (i.e., non-spatial) as well as
+background spatial properties\citep{aminoff2015associative}.
+%
+Supporting this point, strongly contextualized objects also elicit neural
+activity within scene-selective cortex [28,29]\citep{aminoff2015associative}.
+
+%
+Finally, objects present as the contents of a scene can also modulate activity
+in scene-selective regions\citep{aminoff2015associative}.
+%
+For example, scenes where the most salient object carries strong contextual
+associations (e.g., a scene with a parking meter) recruit scene-selective
+regions more than do scenes with a salient object carrying weak contextual asso-
+ciations (e.g., a scene with a squirrel) [30]\citep{aminoff2015associative}.
+%
+Overall, scene-selective brain regions are encoding a rich collection of
+information, including global and local properties, spatial background infor-
+mation, and individual object tokens\citep{aminoff2015associative}.
+
+%
+One concern with the current state of the field is that the list of critical
+properties keeps growing (e.g., big/small, crowded/sparse, three-dimensionality
+[31–33]), with some theories seemingly contradicting others about which
+properties are critical in scene understanding\citep{aminoff2015associative}.
+%
+We posit that many dimensions of scene understanding may be better understood
+within a more general framework in which scenes are encoded with respect to
+their associative properties [28,30,34,35]\citep{aminoff2015associative}.
+%
+Associative properties are not restricted to the spatial or the global domain,
+and can account for why information regarding spatial layout and single objects
+play an important role in scene understanding and concomitant neural
+responses\citep{aminoff2015associative}.
+%
+Associative processing not only offers an explanation for what particular kinds
+of information are present in scene representation (e.g., objects and spatial
+information), but also a basis for explaining how and why this information is
+important\citep{aminoff2015associative}.
+%
+For instance, on average, spatial layout and global properties may carry more
+associative information, and thus are typically prominent in accounts of the
+mechanisms mediating scene recognition\citep{aminoff2015associative}.
+%
+Consider expanse, a salient, organizing principle within scene representations:
+expanse may be construed as a superordinate category strongly associated with
+many other properties of a scene, for instance nature, navigating, hiking, and,
+therefore, is likely to be strongly predictive of additional scene
+information\citep{aminoff2015associative}.
+
+%
+To test the idea that associative processing is inherent in scene understanding,
+we explore whether the network of brain regions recruited in scene perception is
+also recruited when processing non-scene-like stimuli that contain associative
+information\citep{aminoff2015associative}.
+%
+The critical point being that if these regions are active when processing the
+associations learned between non-scene-like novel stimuli than these regions
+must not be involved in only processing the visual properties of the scene, but
+rather, are processing what is associated with the components of the scene as
+learned from previous experience\citep{aminoff2015associative}.
+%
+we focus on the associative processing of concurrent object identities (i.e.,
+semantic associations) and spatial relations between objects (i.e., spatial
+associations)\citep{aminoff2015associative}.
+%
+Of course, other domains of associative processing, for example, diagnostic
+mid-level features, almost surely play some role as
+well\citep{aminoff2015associative}.
+%
+For both semantic and spatial associations, we predict that the three
+typically-identified scene-selective brain areas, the PPA, RSC, and OPA, will
+all exhibit selective activity for both scenes and for associations in general,
+without necessarily having any obvious “scene-like”
+qualities\citep{aminoff2015associative}.
+
+%
+We are positing that scene processing is best understood as, at least in part,
+arising from a more general mechanism–that of associative
+processing\citep{aminoff2015associative}.
+%
+The fact that this mechanism is more general does not make it vague. Our point
+is that learning and encoding relations between tokens (“associations”) is a
+fundamental process across many cognitive domains and, critically, this process
+has explanatory validity for scene processing\citep{aminoff2015associative}.
+%
+Reframing scene processing as involving a more general mechanism helps
+articulate the means by which scene perception
+occurs\citep{aminoff2015associative}.
+
+%
+Participants were scanned while they engaged in processing either everyday
+scenes or associations between meaningless shapes\citep{aminoff2015associative}.
+%
+For the latter condition, participants, immediately prior to the scanning
+session, performed a task (unrelated to the associations) in which they
+implicitly learned spatial or identity associations between configurations of
+novel shapes (Fig 1)\citep{aminoff2015associative}.
+%
+First, to compare brain activity from learning novel associations to the
+processing of scenes, we correlated the distributed, voxel-by-voxel pattern of
+activities arising from these two conditions, thereby testing whether similar
+neural mechanisms mediate both general associative processing and scene
+perception\citep{aminoff2015associative}.
+%
+Second, consistent with previous work ([28,31,34,37]) we asked whether the
+neural encoding of scenes shifts across associ- ation types–from non-spatial or
+semantic scene properties to spatial scene properties–as one moves from the
+anterior to the posterior PPA\citep{aminoff2015associative}.
+%
+These analyses shed light on the hypothesis that a single underlying
+principle, associative processing, accounts for how scenes are represented in
+the brain\citep{aminoff2015associative}.
+
+%
+Although prior studies have manipulated spatial and identity associations by
+having participants learn meaningless patterns of shapes [34], ours is the first
+study to directly compare such associative processing with the processing of
+everyday scenes\citep{aminoff2015associative}.
+%
+Moreover, we include two new baselines to better understand whereby effects of
+associations arise: weak contextual objects and scrambled images. Finally, we
+are careful to collect an additional independent dataset to functionally define
+scene-selective regions\citep{aminoff2015associative}.
+%
+These new conditions are all advances (in terms of explicating the processing of
+scene-selection regions) relative to our earlier study in which we used the same
+shapes and trained participants over a two-week period [34]\citep{aminoff2015associative}.
+%
+We also include several methodological changes: training was much briefer; the
+task was changed from an explicit task to an implicit task; a spatial-only
+associative condition was included to isolate spatial processing independently
+of identity associations; and the no-associa- tion condition provides a better
+control in that it now shows the same number of shapes as the association
+condition (i.e., 3)\citep{aminoff2015associative}.
+
+\paragraph{Method}
+
+\paragraph{Results (just aPPA vs. pPPA)}
+
+%
+The general principle of associative processing may apply broadly across
+scene-selective ROIs. Nevertheless, there is some evidence that within the
+parahippocampal region, anterior and posterior regions may support different
+kinds of associations [34,37,40,41]\citep{aminoff2015associative}.
+%
+We posit: aPPA processes non-spatial associations such as those realized in the
+ID condition. pPPA process spatial associations such as those realized in the SP
+condition\citep{aminoff2015associative}.
+%
+We tested this hypothesis by examining two contrasts within scene-selective PHC
+regions: SP versus NA and ID versus NA\citep{aminoff2015associative}.
+%
+To identify the appropriate scene-selective ROIs for this analysis, we used the
+scenes versus baseline contrast to capture all scene-related activity within
+parahippocampal cortex\citep{aminoff2015associative}.
+%
+Within these subregions, only those voxels that demonstrated significant
+scene-related activity from the scenes versus objects/scrambled localizer were
+analyzed\citep{aminoff2015associative}.
+%
+However, observed scene-related activity within the parahippocampal/lingual
+region extended beyond the posterior border of the parahippocampal cortex and
+into the lingual gyrus\citep{aminoff2015associative}.
+%
+To capture these responses, we also included these more posterior voxels as the
+most posterior subregion, giving us a total of five subregions covering the PPA
+from anterior to posterior regions\citep{aminoff2015associative}.
+
+%
+Data were analyzed examining both the average activity within each subregion,
+and the distributed pattern of activity in each subregion correlated with the
+pattern for scenes\citep{aminoff2015associative}.
+%
+The pattern of average activity across subregions supports a division of labor
+in which anterior subregions showed the largest differences in the ID versus NA
+contrast relative to the SP versus NA contrast, while posterior subregions
+showed the largest differences in the SP versus NA contrast relative to the ID
+versus NA contrast\citep{aminoff2015associative}.
+%
+In the LH PPA this was significant in both in the interaction of Association by
+Subregion (F(4,56) = 5.85, p < .001) and critically, in the linear interaction
+contrast (F(1,14) = 8.05, p < .01)\citep{aminoff2015associative}.
+%
+The significance of this linear contrast indicates that the transition from
+identity to spatial associative processing may be construed as a gradient from
+anterior to posterior regions of parahippocampal cortex. However, the same
+Association by Subregion interaction was not observed in the RH PPA\citep{aminoff2015associative}.
+
+%
+To examine whether identity and spatial associations also capture
+functionally-relevant properties within scenes, we examined the similarity
+between the voxel-wise pattern of BOLD responses elicited by identity
+associations and real-world scenes, and by spatial associations and real-world
+scenes\citep{aminoff2015associative}.
+%
+We hypothesized that, to the degree that these two types of associations are
+intrinsic to scene processing, similar patterns of activation across each of the
+two association conditions and real-world scenes would identify those
+(potentially separable) neural substrates supporting the representation of these
+kinds of associations\citep{aminoff2015associative}.
+%
+Unthresholded t-values for the ID versus NA and SP versus NA contrasts within
+each of the five PPA subregions were ex- tracted for each voxel and then
+cross-correlated within each subregion with the real-world scenes versus
+objects/scrambled contrast\citep{aminoff2015associative}.
+%
+In LH PPA the interaction within an omnibus ANOVA [the two factors being
+Subregion (moving from the most posterior to the most anteri- or) x Association
+(identity or spatial)] was significant (F(4,56) = 2.69, p < .04) as well as the
+critical linear x linear trend analysis (F(1,14) = 7.57, p < .016) (Fig 3A)\citep{aminoff2015associative}.
+%
+Consistent with our analysis of average activity within these subregions, this
+interaction was not observed in the RH PPA (F(1,14) = 1.22, n.s.) (S1 Fig)\citep{aminoff2015associative}.
+%
+However, it is worth noting that within the right hemisphere, the correlation
+between spatial associations and real-world scenes did exhibit the predicted
+pattern whereby the strongest correlation was observed in posterior subregions
+of PPA, with a progressively lower correlation being observed moving in a
+posterior to anterior direction (S1 Fig)\citep{aminoff2015associative}.
+
+%
+Our results indicate that the organization of PPA with respect to associative
+processing is a gradient in which posterior subregions of PPA are biased towards
+spatial associations and anterior subregions of PPA are biased towards identity
+associations\citep{aminoff2015associative}.
+%
+Additional support for this claim is shown in Fig 3B, where instead of dividing
+the PPA into five equal subregions, the correlation was run over progressively
+more and more of the PPA, starting from the most posterior subregion and adding
+subregions until the entire PPA was taken into account\citep{aminoff2015associative};
+%
+As illustrated, the most extreme ends of the PPA show the strongest biases
+towards capturing the similarity of either spatial associations and scenes, or
+identity associations and scenes \citep{aminoff2015associative}
+%
+whereas if the whole PPA were to be surveyed, these differences would be masked.
+Of note, this gradient appears to be truly continuous across posterior and
+anterior portions of the PPA–even considering only the posterior PPA, we observe
+a gradient in which the strongest preference for spatial associations is found
+in the most posterior portions of the posterior
+PPA \citep{aminoff2015associative}.
+%
+Similarly, considering only the anterior PPA, we observe a gradient in which the
+strongest preference for identity associations is found in the most anterior
+portions of the anterior PPA \citep{aminoff2015associative}.
+
+\paragraph{Discussion (just aPP vs pPPA)}
+
+ Building on our general results regarding associative processing, our current
+ findings also establish some specialization (at least in preference) for the
+ processing of associative information across the PPA
+ \citep{aminoff2015associative}.
+%
+pPPA is preferentially recruited by spatial associations while anterior PPA is
+preferentially recruited by semantic (i.e., non-spatial) associations
+\citep{aminoff2015associative}.
+%
+A functional distinction between anterior and posterior PPA has been reported
+previously. In particular, this distinction has been based on PPA responses when
+processing objects associated with spatial contexts (i.e., contexts associated
+with specific places, for example, an oven and a kitchen) and when processing
+objects associated with non-spatial contexts (i.e., contexts not tied to
+specific places, for example, champagne with New Year’s Eve) [28,34,37,40,41]
+\citep{aminoff2015associative}.
+%
+Here we explicitly investigated this spatial/non-spatial distinction by
+isolating the two association types in simple, novel stimuli and then relating
+these controlled stimuli to the processing of real-world scenes containing
+similar associations \citep{aminoff2015associative}.
+%
+We predicted that this Association-Type x Scene correlation would reveal the
+expected posterior to anterior progression with spatial properties within scenes
+selectively recruiting posterior PPA and non-spatial, identity properties within
+scenes selectively recruiting anterior PPA\citep{aminoff2015associative}.
+%
+Moreover, we expected that this functional division would be continuous, with
+the similarity in BOLD responses elicited by scenes and trained spatial
+associations decreasing in a posterior to anterior direction
+\citep{aminoff2015associative}.
+%
+In contrast, the similarity in BOLD responses elicited by scenes and trained
+identity associations was predicted to decrease in an anterior to posterior
+direction.  These predictions were confirmed in our
+study\citep{aminoff2015associative}.
+
+%
+This information processing gradient may lie within a broader, more general
+organization of the PHG\citep{aminoff2015associative}.
+%
+The gradient of processing identity or non-spatial associative information may
+continue through the neighboring perirhinal cortex, which is thought to be
+involved in object and person recognition particularly with regard to combining
+different fea- tures of knowledge, such as a stop sign is red
+[42]\citep{aminoff2015associative}.
+%
+In contrast, the pPPA border regions where mid-level visual information is
+processed, which may be more sensitive to spatial
+information\citep{aminoff2015associative}.
+%
+We do note, however, that this interaction was only observed in the left
+hemisphere, although the right hemisphere demonstrated a similar gradient of
+specialization in spatial processing from posterior to
+anterior\citep{aminoff2015associative}.
+%
+However, the activity related to identity processing was less well organized.
+This pattern of results is somewhat consistent with the fact that the left
+hemisphere is often implicated in more semantically-oriented processing, for
+example, scene categorization, whereas the right hemisphere has been implicated
+in more spatial processing, for example, as in the visual details between
+different exemplars of the same category [10]\citep{aminoff2015associative}.
+%
+These patterns hint that the right hemisphere PPA may play a larger role in the
+processing of the spatial relations within scenes and a lessor role in the
+processing of scene semantics\citep{aminoff2015associative}.
+%
+In sum, our current functional view of the PPA is as a gradient in which
+progressively different scene dimensions come to be
+instantiated\citep{aminoff2015associative}.
+
+\paragraph{Discussion: division of labor in the PPA, RSC and OPA}
+
+The PPA, RSC, and OPA were all strongly engaged in both associative processing
+and in scene perception\citep{aminoff2015associative}.
+%
+However, it is unlikely that these three regions play entirely redundant roles
+in scene understanding–a conclusion supported by the differences we observed
+between the SP, ID, and SPID conditions\citep{aminoff2015associative}.
+%
+In particular, we suggest that the PPA involves the processing of multiple scene
+dimensions that reflect different kinds of associative information (e.g.,
+spatial and identity)\citep{aminoff2015associative}.
+%
+In contrast, both the RSC and OPA were both more sensitive to identity
+associations, whether appearing in isolation or in conjunction with spatial
+associations. Elsewhere we have suggested that the RSC processes the
+prototypical representation of context, termed a “context frame,” which contains
+information regarding both the key objects and the spatial relations be- tween
+them [28,43]\citep{aminoff2015associative}.
+%
+For example a context frame of bathroom would include information regarding a
+shower, toilet, sink, toothbrush, mirror, as well as spatial information such as
+the mirror is typically located above the sink\citep{aminoff2015associative}.
+%
+Our present data support this suggestion, indicating that the RSC is involved in
+both spatial and identity associative processing. Moreover, responses in the RSC
+were the most predictive of learning: better learning elicited higher neural
+activity in the RSC, specifically in the conjoined SPID
+condition\citep{aminoff2015associative}.
+%
+As such, the RSC, as the highest level of associative processing, may be
+involved in the long-term encoding of contextual associations, that is, the
+context frame, where both spatial and non-spatial associations are
+processed\citep{aminoff2015associative}.
+%
+In contrast, the OPA lies in close proximity to the IPS, a region that has
+anatomical connections with both the ventral stream, potentially conveying
+identity information, and the dorsal stream, potentially conveying spatial
+information [44,45]\citep{aminoff2015associative}.
+%
+This provides the anatomical architecture to combine both identity and spatial
+information within a unified contextual
+representation\citep{aminoff2015associative}.
+%
+Future studies are needed to explore the specific anatomical connections with
+the OPA regions, examining whether it is similarly connected to both the dorsal
+and ventral pathways\citep{aminoff2015associative}.
+
+%
+Interestingly, our study also found the neural signal related to the processing
+of spatial associations from the OPA was negatively correlated with
+learning\citep{aminoff2015associative}.
+%
+That is, the better the learning of spatial associations, the lower the response
+of the OPA relative to the control condition. Because the OPA is more posterior
+than the PPA and RSC, it may be involved in earlier stages of scene processing
+[16–18]\citep{aminoff2015associative}.
+%
+Our results build on this, suggesting that the initial processing of spatial
+associations occurs in the OPA, whereas more complex analysis of spatial
+contextual associations, with increased learning, may occur in, progressively,
+the PPA and RSC\citep{aminoff2015associative}.
+
+\paragraph{Conclusions}
+
+Our results move beyond simply describing which brain regions are selectively
+recruited by visual scene processing\citep{aminoff2015associative}.
+%
+We invoke associative processing as a computationally-definable construct for
+predicting the spatial organization of scene-related activity across different
+scene properties\citep{aminoff2015associative}.
+%
+Consequently, we suggest that the neural mediators of scene processing should
+not be construed as encapsulated visual modules, but rather as manifestations of
+associations that reflect the interaction between visual recognition processes
+and the application of long-term memories arising from past experiences (Aminoff
+et al., 2013)\citep{aminoff2015associative}.
+%
+Within this framework, scene processing is not a purely bottom-up visual
+process, but rather is an interactive process in which we are constantly
+considering–in the form of both spatial and non-spatial associations– our past
+experiences to generate predictions, expectations, and constraints about our
+physical environment\citep{aminoff2015associative}.
+
+%
+More specifically, we suggest that general associative processing mechanisms are
+sensitive to frequently occurring or repeated relations within scenes, including
+object identities that co- occur, spatial relations between the objects, and
+spatial locations for individual objects, all of which facilitate the
+recognition and categorization of visual scenes\citep{aminoff2015associative}.
+%
+As such, the collection of associations that help to define a scene provides a
+context for individual elements within that scene\citep{aminoff2015associative}.
+%
+For example, a towel hanging on a rack near a shower would most likely be a
+bathroom towel, whereas the same towel lying flat on the sand near an umbrella
+would most likely be a beach towel\citep{aminoff2015associative}.
+%
+We contend that the parsing of these sorts of contextual associations within
+scenes is fundamental to scene understanding, and that scene understanding
+construed as such, can then influence cognitive processing in myriad
+ways\citep{aminoff2015associative}.
+
+%
+Within the human brain, we argue that the neural bases for the application of
+contextual knowledge is a functional gradient spanning different types of
+associations instantiated across the PPA, and contextually-mediated
+representations within the RSC and OPA\citep{aminoff2015associative}.
+%
+Most saliently, our observations of selectivity for spatial and identity
+associations provide compelling evidence that the neural representation of
+visual scenes is best understood as a consequence of the asso- ciative
+processing in both the spatial and non-spatial
+domains\citep{aminoff2015associative}.
 
@@
 \todo[inline]{check location in primary contrast and overlap across contrasts}
+
+\todo[inline]{report numbers of contrast in AO \& AV that show sign. clusters in
+RSC}
 
@@
 contrast of both contrasts in the retrosplenial cortex (RSC).
-
-\todo[inline]{give numbers of contrast in AO \& AV that show sign. clusters in
-RSC}
 
@@
 
+% Aminoff 2013
+Processing of strong, long-term, contextual associations elicits activity within
+the PHC, as well as the RSC (which includes regions of the retrosplenial cortex,
+extending into the posterior cingulate cortex, and the precuneus), the medial
+prefrontal cortex (MPFC), and the transverse occipital sulcus (TOS) (Figure 2)
+[2,3,59–67] \citep{aminoff2013role}.
+
 % discussion of what the RSC does
@@
 
+\citep{aminoff2015associative}: Three regions of the cortex that have bee
+identified as responding selectively to visual scenes: the PHC/lingual region
+(commonly referred to as the “parahippocampal place area”) [8–12]),
+retrosplenial complex (including the retrosplenial cortex and portions of the
+posterior cingulate and precuneus, RSC) [13–15]), and a lateral occipital region
+termed the “occipital place area” (OPA; also referred to as the transverse
+occipital sulcus, TOS) [16–18]).
+%
+All three of these brain regions are functionally defined by comparing the BOLD
+signals–as measured by fMRI–arising from viewing scenes to those arising from
+viewing objects or faces (e.g., [19])\citep{aminoff2015associative}.
+
+% baldassano2016two
+RSC: appears to be most directly involved in orienting the viewer to the
+structure of the environment (both within and beyond the borders of the
+presented image) for the purpose of navigational planning; it encodes both
+absolute location and facing direction [Vass and Epstein, 2013; Epstein and
+Vass, 2014; Marchette et al., 2014], integrates across views presented in a
+panoramic sequence [Park and Chun, 2009], and shows strong familiarity effects
+[Epstein et al., 2007a,b]\citep{baldassano2016two}.
+
+% contrasting the two networks
+Several previous studies have already shown differential effects within these
+two networks. Contrasting the functional connectivity patterns of RSC versus OPA
+or lateral occipital cortex (LOC; Nasr et al., 2013) or anterior versus
+posterior PPA [Baldassano et al., 2013] show a division between the two
+networks, consistent with our results. Contrasting scene-specific activity with
+general (image or word) memory retrieval showed an anterior versus posterior
+distinction in PPA and cIPL/OPA, with only more anterior regions (aPPA and cIPL,
+along with RSC) responding to content-independent retrieval tasks [Johnson and
+Rugg, 2007; Fairhall et al., 2014]\citep{baldassano2016two}.
+
 \subsubsection{superior lateral occipital cortex (TOC / OPA?)}
@@
 
-\todo[inline]{e.g. Bettencourt (2013). The Role of Transverse Occipital Sulcus
-    in Scene Perception; Dilks, Kanwisher (2013). The Occipital Place Area Is
-    Causally and Selectively Involved in Scene Perception; Grill-Spector (2003).
-    The neural basis of object perception; Nakamura (2000). Functional
-    delineation of the human occipito-temporal areas; Nasr (2011).
-    Scene-selective cortical regions in human and nonhuman primates; Hasson
-    (2003). Large-scale mirror-symmetry organization; MacEvoy and Epstein
-    (2007). Position selectivity in scene- and object-responsive\dots; Dilks
-(2011). Mirror-image sensitivity and invariance in object \& scene processing}
+\todo[inline]{e.g.
+Nakamura (2000). Functional delineation of the human occipito-temporal areas;
+Bettencourt (2013). The Role of Transverse Occipital Sulcus in Scene Perception;
+Dilks, Kanwisher (2013). The Occipital Place Area Is Causally and Selectively Involved in Scene Perception;
+Grill-Spector (2003). The neural basis of object perception;
+Nasr (2011). Scene-selective cortical regions in human and nonhuman primates;
+Hasson (2003). Large-scale mirror-symmetry organization;
+MacEvoy and Epstein (2007). Position selectivity in scene- and object-responsive\dots;
+Dilks (2011). Mirror-image sensitivity and invariance in object \& scene processing}
+
+%
+\citep{baldassano2016two} functional difference pPPA vs. OPA: functional
+distinction between pPPA and OPA is currently unclear. Previous work has
+speculated about the purpose of the apparent ventral and dorsal ``duplication''
+of regions sensitive to large landmarks, proposing that it may be related to
+different output goals (e.g., action planning in OPA, object recognition in
+pPPA)[Konkle and Caramazza, 2013], or to different input connections (e.g.,
+lower visual field processing in OPA, upper visual field processing in
+pPPA)[Kravitz et al., 2013; Silson et al., 2015]. OPA and pPPA may also use
+information from different visual eccentricities: OPA processing less
+peripheral, relatively high-resolution environmental features. pPPA processing
+more peripheral, large-scale geometry, and context [Baldassano et al.,
+2016a]\citep{baldassano2016two}.
 
@@
 \subsection{individual analyses}
+
+An examination of these results on an individual participant basis reveals that
+this pattern remains highly reliable and, therefore, does not appear to be a
+by-product of group averaging across slightly offset discrete functional
+subregions[aminoff2015associative].
 

### 2020-11-18 paper/main.tex
restructure quotes aPPA vs pPPA

@@
 %
-\citep{baumann2016functional} paradigm: We measure parahippocampal responses
-while participants engaged in a task that required them to judge the contextual
+\citep{baumann2016functional} paradigm: We measure PHC responses while
+participants engaged in a task that required them to judge the contextual
 relatedness of scene and object pairs, which were presented either as words or
@@
 %
-Results: aPHC is more active during contextual
-judgments regardless of stimulus category (scenes vs objects) or modality (word
-vs picture).
+Results: aPHC is more active during contextual judgments regardless of stimulus
+category (scenes vs objects) or modality (word vs picture).
 %

### 2020-11-19 paper/main.tex
shorten Baumann quote

@@
 anterior part of significant clusters of the AV contrasts).
+
 % intro to connectivity and object gradient
-[kind of complete overview of (references):] Previous studies suggest that
+Kind of complete overview of (references): Previous studies suggest that
 posterior and anterior part of the PPA show differences in
@@
 future'' (125 studie).
+
 %
@@
 % visuospatial and mnemonic processes
-The PHC plays a key role in both visuospatial analysis of scenes [Epstein et
-al., 1999, 2003; Park and Chun, 2009; Rajimehr et al., 2011] and (contextual)
-mnemonic processing [Aminoff et al., 2013, Bar and Aminoff, 2003; Düzel et al.,
-    2003; Janzen and van Turennout, 2004; Baumann et al., 2010; Wegman and
-Janzen, 2011] \citep{baumann2016functional}
+The PHC plays a key role in
+%
+a) visuospatial analysis of scenes [Epstein et al., 1999, 2003; Park and Chun,
+2009; Rajimehr et al., 2011] and
+%
+b) (contextual) mnemonic processing [Aminoff et al., 2013, Bar and Aminoff,
+2003; Düzel et al., 2003; Janzen and van Turennout, 2004; Baumann et al., 2010;
+Wegman and Janzen, 2011] \citep{baumann2016functional}
+
 % associative processing
@@
 associations in memory [Aminoff et al., 2013; Bar and Aminoff, 2003; Bar et al.,
-2008a, 2008b].
-
-Contextual associations: relations between objects and conditions that describe,
-represent, and bring meaning to an environment [Aminoff et al., 2013]
-\citep{baumann2016functional}.
-%
-Examples: objects that commonly co-occur, such as a refrigerator and an oven
-(typically in a kitchen) or familiar spatial configurations of objects, (rows of
-tables and chairs in a school classroom). According to this view, activity in
-the parahippocampal cortex reflects modality-independent retrieval of contextual
-information from memory, such as which objects typically occur in a given scene
-and where they are likely to be located relative to one another
-\citep{baumann2016functional}.
-
-%
-However, it has remained unclear whether these two processes are functionally
-and anatomically segregated within the parahippocampal cortex
-\citep{baumann2016functional}.
+2008a, 2008b]. According to this view, activity in PHC reflects
+modality-independent retrieval of contextual information from memory, such as
+which objects typically occur in a given scene and where they are likely to be
+located relative to one another (contextual associations: relations between
+objects and conditions that describe, represent, and bring meaning to an
+environment [Aminoff et al., 2013]) \citep{baumann2016functional}.
+
 %
@@
 %
-\citep{baumann2016functional} paradigm: We measure PHC responses while
-participants engaged in a task that required them to judge the contextual
-relatedness of scene and object pairs, which were presented either as words or
-pictures \citep{baumann2016functional}.
+Paradigm: Participants had to judge the contextual relatedness of scene and
+object pairs (presented either as words or pictures)
+\citep{baumann2016functional}.
 %
@@
 isolation (Fig. 1)\citep{baumann2016functional}.
-%
-To identify visuospatial regions of the PHC, we tested for voxels with greater
-activity for picture–scene trials than for picture–object trials over and above
-activity differences elicited by the comparison of word–scene trials and word–
-object trials\citep{baumann2016functional}.
-%
-Additionally to locate context-related regions of the PHC, we tested for voxels
-that were selectively active during the contextual judgment task regardless of
-the type of stimulus (scenes vs objects) or presentation modality (word vs
+
+%
+1) To identify visuospatial regions of the PHC, we tested for voxels with
+greater activity for picture–scene trials than for picture–object trials over
+and above activity differences elicited by the comparison of word–scene trials
+and word– object trials\citep{baumann2016functional}.
+%
+2) To locate context-related regions of the PHC, we tested for voxels that were
+selectively active during the contextual judgment task regardless of the type of
+stimulus (scenes vs objects) or presentation modality (word vs
 picture)\citep{baumann2016functional}.

### 2020-11-19 paper/main.tex
shorten Aminoff 2015

@@
 % pPHC
-pPHC showed increased activity when participants viewed (alrady familiar)
+pPHC showed increased activity when participants viewed (already familiar)
 spatial configurations of meaningless shapes (regardless of their individual
@@
 
-\citep{aminoff2015associative} How are complex visual entities such as scenes
-represented in the human brain? Along what visual and semantic dimensions are
-scenes encoded in memory?
-%
-One hypothesis: global spatial properties provide a basis for categorizing the
-neural response patterns arising from scenes \citep{aminoff2015associative}.
-%
-In contrast, non-spatial properties, such as single objects, also account for
-variance in neural responses\citep{aminoff2015associative}.
-
-%
-The list of critical scene dimensions has continued to grow (sometimes in a
-contradictory manner), coming to encompass properties such as geometric layout,
-big/small, crowded/sparse, and
-three-dimensionality\citep{aminoff2015associative}.
-%
-We demonstrate that these dimensions may be better understood within the more
-general framework of associative properties\citep{aminoff2015associative}.
+\citep{aminoff2015associative} How are scenes represented in the human brain?
+Along what visual and semantic dimensions are scenes encoded in memory?
+%
+
+Hypothesis:
+%
+a) global spatial properties provide a basis for categorizing the neural
+response patterns arising from scenes
+%
+b) non-spatial properties, such as single objects, also account for variance in
+neural responses
+
+%
+The list of critical scene dimensions has continued to grow encompassing
+properties such as geometric layout, big/small, crowded/sparse, and
+three-dimensionality.
+%
+These dimensions may be better understood within the more general framework of
+associative properties \citep{aminoff2015associative}.
 %
@@
 We investigated whether different types of relations, all falling under the
-heading of associative processing, reliably recruit specific components of the
-network of brain regions known to be scene
-selective\citep{aminoff2015associative}.
+heading of associative processing, reliably regions of brain networks known to
+be scene selective\citep{aminoff2015associative}.
 %
@@
 transverse occipital sulcus/occipital place area)\citep{aminoff2015associative}.
+
 %
@@
 %
-Interpretation: Results provide evidence for the hypothesis that the neural
-representation of scenes is better understood within the broader theoretical
-framework of associative processing\citep{aminoff2015associative}.
+Interpretation: Results provide evidence that the neural representation of
+scenes is better understood within the broader theoretical framework of
+associative processing\citep{aminoff2015associative}.
 %
@@
 about objects, background, context, semantics, and spatial layout at multiple
-scales\citep{aminoff2015associative}.
+scales.
 %
 As a core component of scene understanding we extract and learn these
-regularities (for example, coming to know that certain objects typically appear
-together or that certain objects are likely to appear in a given spatial
-relationship [1–3])\citep{aminoff2015associative}.
-%
-Critically, these associated regularities are not only useful in defining scene
-categories, but also in predicting which other objects and relations are likely
-to occur within a scene [5]\citep{aminoff2015associative}.
+regularities (certain objects typically appear together
+[1–3]).
+%
+Associated regularities are useful in defining scene as well as in predicting
+which other objects and relations are likely to occur within a scene
+[5].
 
@@
 representation is nominally visual, linguistic, etc., are related to one another
-via learned associations\citep{aminoff2015associative}.
+via learned associations.
 %
@@
 representations are likely to carry many semantic and affective associations not
-directly present in the image)\citep{aminoff2015associative}.
+directly present in the image).
+
 %
@@
 Associations are not simply frequently co-occurring features pairs; instead they
-are pairs that both co-occur and add meaning to scenes
-\citep{aminoff2015associative}.
+are pairs that both co-occur and add meaning to scenes.
 %
@@
 understood, is through means of processing the associations elicited from
-components of the scene \citep{aminoff2015associative}.
+components of the scene.
 
@@
 computations and representations instantiated in each of these brain regions.
-The literature has focused on more on the latter, characterizing the nature of
-the information encoded about scenes\citep{aminoff2015associative}.
+The literature has focused on more the representations, characterizing the
+nature of the information encoded about scenes.
 %
@@
 properties, such as the ‘spatial envelope’, which takes into account a scene’s
-overall spatial structure and layout [20,21]\citep{aminoff2015associative}.
-%
-Empirically, it has been demonstrated that these global properties are salient
+overall spatial structure and layout [20,21].
+%
+Empirically, it has been demonstrated that global properties are salient
 cues for categorizing scenes in both behavior [22] and in patterns of neural
-activity [23–26]\citep{aminoff2015associative}.
-%
-Compared to other factors that characterize scenes (i.e., content and
-depth), the expanse of the scene (i.e. its spatial boundary) has been found to
-be the most effective in accounting for variations in the neural responses
-within scene-selective brain regions [23,24]\citep{aminoff2015associative}.
+activity [23–26].
+
+%
+Compared to other factors that characterize scenes (i.e., content and depth),
+the expanse of the scene (i.e. its spatial boundary) has been found to be the
+most effective in accounting for variations in the neural responses within
+scene-selective brain regions [23,24].
 %
@@
 often been implicated in determining the neural responses arising from
-scene-selective brain regions [27]\citep{aminoff2015associative}.
+scene-selective brain regions [27].
 
@@
 In contrast, non-spatial properties can account for variations in the neural
-responses associated with scene processing and representation\citep{aminoff2015associative}.
+responses associated with scene processing and
+representation.
 %
@@
 captures information about single objects (i.e., non-spatial) as well as
-background spatial properties\citep{aminoff2015associative}.
+background spatial properties.
 %
 Supporting this point, strongly contextualized objects also elicit neural
-activity within scene-selective cortex [28,29]\citep{aminoff2015associative}.
+activity within scene-selective cortex [28,29].
 
@@
 Finally, objects present as the contents of a scene can also modulate activity
-in scene-selective regions\citep{aminoff2015associative}.
+in scene-selective regions.
 %
@@
 associations (e.g., a scene with a parking meter) recruit scene-selective
-regions more than do scenes with a salient object carrying weak contextual asso-
-ciations (e.g., a scene with a squirrel) [30]\citep{aminoff2015associative}.
+regions more than do scenes with a salient object carrying weak contextual
+associations (e.g., a scene with a squirrel) [30].
+
 %
 Overall, scene-selective brain regions are encoding a rich collection of
-information, including global and local properties, spatial background infor-
-mation, and individual object tokens\citep{aminoff2015associative}.
-
-%
-One concern with the current state of the field is that the list of critical
-properties keeps growing (e.g., big/small, crowded/sparse, three-dimensionality
-[31–33]), with some theories seemingly contradicting others about which
-properties are critical in scene understanding\citep{aminoff2015associative}.
-%
-We posit that many dimensions of scene understanding may be better understood
-within a more general framework in which scenes are encoded with respect to
-their associative properties [28,30,34,35]\citep{aminoff2015associative}.
+information, including global and local properties, spatial background
+information, and individual object tokens.
+
+%
+The list of critical properties keeps growing (e.g., big/small, crowded/sparse,
+three-dimensionality [31–33]), some seemingly contradicting others about which
+properties are critical in scene understanding.
+%
+Scene understanding may be better understood within a more general framework in
+which scenes are encoded with respect to their associative properties
+[28,30,34,35].
 %
@@
 play an important role in scene understanding and concomitant neural
-responses\citep{aminoff2015associative}.
-%
-Associative processing not only offers an explanation for what particular kinds
+responses.
+
+%
+Associative processing offers an explanation for what particular kinds
 of information are present in scene representation (e.g., objects and spatial
-information), but also a basis for explaining how and why this information is
-important\citep{aminoff2015associative}.
+information) and a basis for explaining how and why this information is
+important.
 %
@@
 associative information, and thus are typically prominent in accounts of the
-mechanisms mediating scene recognition\citep{aminoff2015associative}.
-%
-Consider expanse, a salient, organizing principle within scene representations:
-expanse may be construed as a superordinate category strongly associated with
-many other properties of a scene, for instance nature, navigating, hiking, and,
-therefore, is likely to be strongly predictive of additional scene
-information\citep{aminoff2015associative}.
+mechanisms mediating scene recognition.
 
@@
 also recruited when processing non-scene-like stimuli that contain associative
-information\citep{aminoff2015associative}.
-%
-The critical point being that if these regions are active when processing the
-associations learned between non-scene-like novel stimuli than these regions
-must not be involved in only processing the visual properties of the scene, but
-rather, are processing what is associated with the components of the scene as
-learned from previous experience\citep{aminoff2015associative}.
-%
-we focus on the associative processing of concurrent object identities (i.e.,
+information.
+
+%
+If these regions are active when processing the associations learned between
+non-scene-like novel stimuli than these regions must not be involved in only
+processing the visual properties of the scene, but rather, are processing what
+is associated with the components of the scene as learned from previous
+experience.
+
+%
+We focus on the associative processing of concurrent object identities (i.e.,
 semantic associations) and spatial relations between objects (i.e., spatial
-associations)\citep{aminoff2015associative}.
-%
-Of course, other domains of associative processing, for example, diagnostic
-mid-level features, almost surely play some role as
-well\citep{aminoff2015associative}.
+associations).
+
 %
@@
 without necessarily having any obvious “scene-like”
-qualities\citep{aminoff2015associative}.
+qualities.
 
@@
 arising from a more general mechanism–that of associative
-processing\citep{aminoff2015associative}.
+processing.
 %
@@
 fundamental process across many cognitive domains and, critically, this process
-has explanatory validity for scene processing\citep{aminoff2015associative}.
+has explanatory validity for scene processing.
 %
@@
 articulate the means by which scene perception
-occurs\citep{aminoff2015associative}.
+occurs.
 
@@
 Participants were scanned while they engaged in processing either everyday
-scenes or associations between meaningless shapes\citep{aminoff2015associative}.
-%
-For the latter condition, participants, immediately prior to the scanning
-session, performed a task (unrelated to the associations) in which they
-implicitly learned spatial or identity associations between configurations of
-novel shapes (Fig 1)\citep{aminoff2015associative}.
+scenes or associations between meaningless shapes.
+%
+For processing of meaningless shapes, participants performed a task (prior to
+scanning; unrelated to the associations) in which they implicitly learned
+spatial or identity associations between configurations of novel shapes (Fig
+1).
+
 %
@@
 neural mechanisms mediate both general associative processing and scene
-perception\citep{aminoff2015associative}.
+perception.
+
 %
 Second, consistent with previous work ([28,31,34,37]) we asked whether the
-neural encoding of scenes shifts across associ- ation types–from non-spatial or
+neural encoding of scenes shifts across association types–from non-spatial or
 semantic scene properties to spatial scene properties–as one moves from the
-anterior to the posterior PPA\citep{aminoff2015associative}.
-%
-These analyses shed light on the hypothesis that a single underlying
-principle, associative processing, accounts for how scenes are represented in
-the brain\citep{aminoff2015associative}.
+anterior to the posterior PPA.
+%
+These analyses shed light on the hypothesis that a single underlying principle,
+associative processing, accounts for how scenes are represented in the
+brain.
 
@@
 study to directly compare such associative processing with the processing of
-everyday scenes\citep{aminoff2015associative}.
-%
-Moreover, we include two new baselines to better understand whereby effects of
+everyday scenes.
+
+%
+We include two new baselines to better understand whereby effects of
 associations arise: weak contextual objects and scrambled images. Finally, we
 are careful to collect an additional independent dataset to functionally define
-scene-selective regions\citep{aminoff2015associative}.
+scene-selective regions.
+
 %
@@
 scene-selection regions) relative to our earlier study in which we used the same
-shapes and trained participants over a two-week period [34]\citep{aminoff2015associative}.
-%
-We also include several methodological changes: training was much briefer; the
-task was changed from an explicit task to an implicit task; a spatial-only
-associative condition was included to isolate spatial processing independently
-of identity associations; and the no-associa- tion condition provides a better
-control in that it now shows the same number of shapes as the association
-condition (i.e., 3)\citep{aminoff2015associative}.
+shapes and trained participants over a two-week period [34].
+%
+We also include several methodological changes: a spatial-only associative
+condition was included to isolate spatial processing independently of identity
+associations; and the no-association condition provides a better control in that
+it now shows the same number of shapes as the association condition (i.e., 3).
 
@@
 %
-The general principle of associative processing may apply broadly across
-scene-selective ROIs. Nevertheless, there is some evidence that within the
-parahippocampal region, anterior and posterior regions may support different
-kinds of associations [34,37,40,41]\citep{aminoff2015associative}.
-%
-We posit: aPPA processes non-spatial associations such as those realized in the
-ID condition. pPPA process spatial associations such as those realized in the SP
-condition\citep{aminoff2015associative}.
+There is some evidence that within the parahippocampal region, anterior and
+posterior regions may support different kinds of associations
+[34,37,40,41].
+%
+a) aPPA processes non-spatial associations (as realized in the ID condition)
+%
+b) pPPA process spatial associations (as realized in the SP
+condition.
 %
 We tested this hypothesis by examining two contrasts within scene-selective PHC
-regions: SP versus NA and ID versus NA\citep{aminoff2015associative}.
-%
-To identify the appropriate scene-selective ROIs for this analysis, we used the
-scenes versus baseline contrast to capture all scene-related activity within
-parahippocampal cortex\citep{aminoff2015associative}.
-%
-Within these subregions, only those voxels that demonstrated significant
-scene-related activity from the scenes versus objects/scrambled localizer were
-analyzed\citep{aminoff2015associative}.
-%
-However, observed scene-related activity within the parahippocampal/lingual
-region extended beyond the posterior border of the parahippocampal cortex and
-into the lingual gyrus\citep{aminoff2015associative}.
-%
-To capture these responses, we also included these more posterior voxels as the
-most posterior subregion, giving us a total of five subregions covering the PPA
-from anterior to posterior regions\citep{aminoff2015associative}.
-
-%
-Data were analyzed examining both the average activity within each subregion,
-and the distributed pattern of activity in each subregion correlated with the
-pattern for scenes\citep{aminoff2015associative}.
+regions: SP versus NA and ID versus NA.
+(we used the scenes versus baseline contrast to capture all scene-related
+activity within parahippocampal cortex).
+
 %
 The pattern of average activity across subregions supports a division of labor
-in which anterior subregions showed the largest differences in the ID versus NA
-contrast relative to the SP versus NA contrast, while posterior subregions
-showed the largest differences in the SP versus NA contrast relative to the ID
-versus NA contrast\citep{aminoff2015associative}.
+in which
+%
+a) anterior subregions showed the largest differences in the ID versus NA
+contrast relative to the SP versus NA contrast, while
+%
+b) posterior subregions showed the largest differences in the SP versus NA
+contrast relative to the ID versus NA contrast.
 %
@@
 Subregion (F(4,56) = 5.85, p < .001) and critically, in the linear interaction
-contrast (F(1,14) = 8.05, p < .01)\citep{aminoff2015associative}.
+contrast (F(1,14) = 8.05, p < .01).
 %
@@
 anterior to posterior regions of parahippocampal cortex. However, the same
-Association by Subregion interaction was not observed in the RH PPA\citep{aminoff2015associative}.
+Association by Subregion interaction was not observed in the RH
+PPA.
 
@@
 associations and real-world scenes, and by spatial associations and real-world
-scenes\citep{aminoff2015associative}.
+scenes.
 %
@@
 (potentially separable) neural substrates supporting the representation of these
-kinds of associations\citep{aminoff2015associative}.
+kinds of associations.
+
 %
 Unthresholded t-values for the ID versus NA and SP versus NA contrasts within
-each of the five PPA subregions were ex- tracted for each voxel and then
+each of the five PPA subregions were extracted for each voxel and then
 cross-correlated within each subregion with the real-world scenes versus
-objects/scrambled contrast\citep{aminoff2015associative}.
+objects/scrambled contrast.
 %
@@
 (identity or spatial)] was significant (F(4,56) = 2.69, p < .04) as well as the
-critical linear x linear trend analysis (F(1,14) = 7.57, p < .016) (Fig 3A)\citep{aminoff2015associative}.
+critical linear x linear trend analysis (F(1,14) = 7.57, p < .016) (Fig
+3A).
 %
 Consistent with our analysis of average activity within these subregions, this
-interaction was not observed in the RH PPA (F(1,14) = 1.22, n.s.) (S1 Fig)\citep{aminoff2015associative}.
+interaction was not observed in the RH PPA (F(1,14) = 1.22, n.s.) (S1
+Fig).
 %
@@
 of PPA, with a progressively lower correlation being observed moving in a
-posterior to anterior direction (S1 Fig)\citep{aminoff2015associative}.
-
-%
-Our results indicate that the organization of PPA with respect to associative
+posterior to anterior direction (S1 Fig).
+
+%
+=> Our results indicate that the organization of PPA with respect to associative
 processing is a gradient in which posterior subregions of PPA are biased towards
 spatial associations and anterior subregions of PPA are biased towards identity
-associations\citep{aminoff2015associative}.
+associations.
+
 %
@@
 more and more of the PPA, starting from the most posterior subregion and adding
-subregions until the entire PPA was taken into account\citep{aminoff2015associative};
+subregions until the entire PPA was taken into account;
 %
@@
 towards capturing the similarity of either spatial associations and scenes, or
-identity associations and scenes \citep{aminoff2015associative}
+identity associations and scenes.
 %
@@
 in the most posterior portions of the posterior
-PPA \citep{aminoff2015associative}.
+PPA.
 %
@@
 strongest preference for identity associations is found in the most anterior
-portions of the anterior PPA \citep{aminoff2015associative}.
+portions of the anterior PPA.
 
@@
 
- Building on our general results regarding associative processing, our current
- findings also establish some specialization (at least in preference) for the
- processing of associative information across the PPA
- \citep{aminoff2015associative}.
+Results suggest some specialization (at least in preference) for the processing
+of associative information across the PPA.
 %
 pPPA is preferentially recruited by spatial associations while anterior PPA is
-preferentially recruited by semantic (i.e., non-spatial) associations
-\citep{aminoff2015associative}.
+preferentially recruited by semantic (i.e., non-spatial) associations.
+
 %
@@
 objects associated with non-spatial contexts (i.e., contexts not tied to
-specific places, for example, champagne with New Year’s Eve) [28,34,37,40,41]
-\citep{aminoff2015associative}.
-%
-Here we explicitly investigated this spatial/non-spatial distinction by
+specific places, for example, champagne with New Year’s Eve) [28,34,37,40,41].
+
+%
+Here, we explicitly investigated this spatial/non-spatial distinction by
 isolating the two association types in simple, novel stimuli and then relating
 these controlled stimuli to the processing of real-world scenes containing
-similar associations \citep{aminoff2015associative}.
+similar associations.
 %
@@
 selectively recruiting posterior PPA and non-spatial, identity properties within
-scenes selectively recruiting anterior PPA\citep{aminoff2015associative}.
+scenes selectively recruiting anterior PPA.
 %
@@
 the similarity in BOLD responses elicited by scenes and trained spatial
-associations decreasing in a posterior to anterior direction
-\citep{aminoff2015associative}.
+associations decreasing in a posterior to anterior direction.
 %
@@
 identity associations was predicted to decrease in an anterior to posterior
-direction.  These predictions were confirmed in our
-study\citep{aminoff2015associative}.
+direction. These predictions were confirmed in our study.
 
@@
 This information processing gradient may lie within a broader, more general
-organization of the PHG\citep{aminoff2015associative}.
+organization of the PHG.
 %
@@
 different fea- tures of knowledge, such as a stop sign is red
-[42]\citep{aminoff2015associative}.
+[42].
 %
@@
 processed, which may be more sensitive to spatial
-information\citep{aminoff2015associative}.
+information.
 %
@@
 specialization in spatial processing from posterior to
-anterior\citep{aminoff2015associative}.
+anterior.
+
 %
@@
 in more spatial processing, for example, as in the visual details between
-different exemplars of the same category [10]\citep{aminoff2015associative}.
+different exemplars of the same category [10].
 %
@@
 processing of the spatial relations within scenes and a lessor role in the
-processing of scene semantics\citep{aminoff2015associative}.
+processing of scene semantics.
 %
@@
 progressively different scene dimensions come to be
-instantiated\citep{aminoff2015associative}.
+instantiated.
 
@@
 The PPA, RSC, and OPA were all strongly engaged in both associative processing
-and in scene perception\citep{aminoff2015associative}.
+and in scene perception.
+
 %
@@
 in scene understanding–a conclusion supported by the differences we observed
-between the SP, ID, and SPID conditions\citep{aminoff2015associative}.
+between the SP, ID, and SPID conditions.
 %
@@
 dimensions that reflect different kinds of associative information (e.g.,
-spatial and identity)\citep{aminoff2015associative}.
-%
-In contrast, both the RSC and OPA were both more sensitive to identity
-associations, whether appearing in isolation or in conjunction with spatial
-associations. Elsewhere we have suggested that the RSC processes the
-prototypical representation of context, termed a “context frame,” which contains
-information regarding both the key objects and the spatial relations be- tween
-them [28,43]\citep{aminoff2015associative}.
+spatial and identity).
+
+%
+RSC and OPA were both more sensitive to identity associations, whether appearing
+in isolation or in conjunction with spatial associations. Elsewhere we have
+suggested that the RSC processes the prototypical representation of context,
+termed a “context frame,” which contains information regarding both the key
+objects and the spatial relations be- tween them
+[28,43].
 %
@@
 shower, toilet, sink, toothbrush, mirror, as well as spatial information such as
-the mirror is typically located above the sink\citep{aminoff2015associative}.
+the mirror is typically located above the sink.
+
 %
@@
 activity in the RSC, specifically in the conjoined SPID
-condition\citep{aminoff2015associative}.
+condition.
 %
@@
 context frame, where both spatial and non-spatial associations are
-processed\citep{aminoff2015associative}.
+processed.
+
 %
@@
 identity information, and the dorsal stream, potentially conveying spatial
-information [44,45]\citep{aminoff2015associative}.
+information [44,45].
 %
@@
 information within a unified contextual
-representation\citep{aminoff2015associative}.
+representation.
 %
@@
 the OPA regions, examining whether it is similarly connected to both the dorsal
-and ventral pathways\citep{aminoff2015associative}.
+and ventral pathways.
 
@@
 of spatial associations from the OPA was negatively correlated with
-learning\citep{aminoff2015associative}.
+learning.
 %
@@
 than the PPA and RSC, it may be involved in earlier stages of scene processing
-[16–18]\citep{aminoff2015associative}.
+[16–18].
 %
@@
 contextual associations, with increased learning, may occur in, progressively,
-the PPA and RSC\citep{aminoff2015associative}.
+the PPA and RSC.
 
@@
 
-Our results move beyond simply describing which brain regions are selectively
-recruited by visual scene processing\citep{aminoff2015associative}.
 %
@@
 predicting the spatial organization of scene-related activity across different
-scene properties\citep{aminoff2015associative}.
-%
-Consequently, we suggest that the neural mediators of scene processing should
-not be construed as encapsulated visual modules, but rather as manifestations of
-associations that reflect the interaction between visual recognition processes
-and the application of long-term memories arising from past experiences (Aminoff
-et al., 2013)\citep{aminoff2015associative}.
+scene properties.
+%
+we suggest that the neural mediators of scene processing should not be construed
+as encapsulated visual modules, but rather as manifestations of associations
+that reflect the interaction between visual recognition processes and the
+application of long-term memories arising from past experiences (Aminoff et al.,
+2013).
 %
@@
 experiences to generate predictions, expectations, and constraints about our
-physical environment\citep{aminoff2015associative}.
-
-%
-More specifically, we suggest that general associative processing mechanisms are
-sensitive to frequently occurring or repeated relations within scenes, including
-object identities that co- occur, spatial relations between the objects, and
-spatial locations for individual objects, all of which facilitate the
-recognition and categorization of visual scenes\citep{aminoff2015associative}.
+physical environment.
+
+%
+We suggest that general associative processing mechanisms are sensitive to
+frequently occurring or repeated relations within scenes, including object
+identities that co-occur, spatial relations between the objects, and spatial
+locations for individual objects, all of which facilitate the recognition and
+categorization of visual scenes.
 %
 As such, the collection of associations that help to define a scene provides a
-context for individual elements within that scene\citep{aminoff2015associative}.
+context for individual elements within that scene.
 %
@@
 bathroom towel, whereas the same towel lying flat on the sand near an umbrella
-would most likely be a beach towel\citep{aminoff2015associative}.
+would most likely be a beach towel.
 %
@@
 construed as such, can then influence cognitive processing in myriad
-ways\citep{aminoff2015associative}.
+ways.
 
@@
 associations instantiated across the PPA, and contextually-mediated
-representations within the RSC and OPA\citep{aminoff2015associative}.
+representations within the RSC and OPA.
 %
@@
 visual scenes is best understood as a consequence of the asso- ciative
-processing in both the spatial and non-spatial
-domains\citep{aminoff2015associative}.
+processing in both the spatial and non-spatial domains.
 

### 2020-11-21 paper/main.tex
Down from 50 to 35 pages
Turn off note renderin
shorten anterior vs posterior

@@
 \usepackage{fancyhdr}
+% \usepackage[disable]{todonotes}
 \usepackage{todonotes}
 \usepackage{units}
+\usepackage[left=2cm,right=4cm,top=2cm,bottom=2cm]{geometry}
 \usepackage[
@@
 
-\todo[inline]{parts from original studies probably too detailed}
-
-\todo[inline]{current order of subsections might be ``non-canonical''}
-
 % intro
@@
 Notably, the categories \texttt{setting\_new} and \texttt{setting\_rec} comprise
-not just words that describe an abstract location (e.g. ) or a setting as whole
-(e.g. ``in Greenbow'', ``in a disco'', ``the platoon wades through a rice
-field''). They also comprise words that could count as a member of another
-categories in case the narrator uses these words to indicate a switch from one
-setting to another (e.g. ``Jenny as a teenager'').
+not just words that describe a setting as a whole (e.g. ``in Greenbow'', ``in a
+disco'', ``the platoon wades through a rice field''). They also comprise words
+that could count as a member of another categories in case the narrator uses
+these words to indicate a switch from one setting to another (e.g. ``Jenny as a
+teenager'').
 % reference to table with rules and examples
@@
 viewer within the environment depicted in the movie.
-
-\todo[inline]{currently table is to wide; smaller font? less text? rotate the
-table?}
 
@@
 the PPA correlates with spatial information presented under more ecological
-valid conditions.\todo{cautious phrasing but still problematic: looking for
-confirmation}
+valid conditions.
 % what we did
@@
 
-\subsection{Group results (all AO + AV PPA contrasts)}
-
-\todo[inline]{subheadings are still in for better readability; structure could
-be changed; at the moment its AO (PPA in primary contrast, robustness of PPA;
-other clusters across contrasts), then the same for AV}
+\subsection{Group results}
 
@@
 
-\subsubsection{PPA in AO: primary contrasts}
+\subsubsection{AO: PPA in primary contrast}
 
@@
 
-\subsubsection{PPA in AO: robustness across contrasts}
+\subsubsection{AO: robustness of PPA across contrasts}
 
@@
 anterior regions of the group PPA overlap (see Figure
+\ref{fig:stability-slices}).
 % statement/answer
 Results suggest that our findings do not depend on one specific contrasts but
-are robust across differently designed
-contrasts.\ref{fig:stability-slices}).\todo[inline]{Discussion: discuss that
-contrasts make ``less and less'' sense}
+are robust across differently designed contrasts.
 % question
 \todo[inline]{concluding statement often feels like interpretation/discussion}
-% question 2
+%
+\todo[inline]{Discussion: discuss that contrasts make ``less and less'' sense}
 
@@
 
-\subsubsection{other sign. clusters across AO contrasts}
+\subsubsection{AO: other significant clusters across contrasts}
 % precuneus = retrosplenial cortex ?
@@
 % ventral precuneus = retrosplenial cortex?
-7 contrasts: bilateral clusters in RSC (and ventral precuneus);
+So far, just a short list => 7 contrasts: bilateral clusters in RSC (and ventral
+precuneus);
 % transverse occipital sulcus = occipital place area
-6 contrasts (4 bilat.): transverse occipital sulcus (= OPA?);\todo{AO: clusters
-are more lateral; AV: clusters are more medial}
+6 contrasts (4 bilateral, 2 unilateral): lateral occipiatal cortex (transverse
+occipital sulcus; occipiatal place area?; AO clusters are more lateral, AV
+cluster are more medial (\& caudal) but AO \& AV clusters overlap)
 % confounds
-4 contrasts: right superior temporal gyrus; 3 contrasts: left superior temporal
-gyrus; 3 contrasts: some (smallish) prefrontal clusters
-
-\subsubsection{PPA in AV: primary contrasts}
+4 contrasts: right superior temporal gyrus (auditory cortices); 3 contrasts:
+left superior temporal gyrus; 3 contrasts: some (smallish) prefrontal clusters
+
+\subsubsection{AV: PPA in primary contrast}
 % AV intro
@@
 
-\subsubsection{PPA in AV: robustness + other clusters across contrasts}
+\subsubsection{AV: robustness of PPA across contrasts}
 
@@
 %% results: PPA
-All of the overall five AV contrasts yielded significant bilateral clusters (in
-that overlap with the PPA group mask/overlap [biggest overlap in posterior part
-of group ROI = temporal occipital fusiform cortex] (see Figure
-\ref{fig:stability-slices}).
+All of the overall five AV contrasts yielded significant bilateral clusters that
+overlap with the PPA group overlap (see Figure \ref{fig:stability-slices}).
+[biggest overlap in posterior part of PPA group overlap  = temporal occipital
+fusiform cortex] .
 % concluding statement
@@
 
-\subsection{negative controls in AO and AV}
+\subsubsection{AV: other signficant clusters across contrasts}
+
+\subsubsection{AO \& AV: (negative) control contrasts}
 
@@
 
-\todo[inline]{the structure is as follows at the moment: correlation of
+\todo[inline]{structure is as follows: correlation of
 regressors; AO group; AV group; robustness AO + AV; anterior vs posterior PPA;
@@
 \todo[inline]{following: how to frame it (better) that AV merely serves as
-conceptual control?; imo should be a small section anyway}
+conceptual control?; imo discussion of AV should be short anyway}
 % AV stimulus
@@
 For example in the AV results, we do not find significant clusters that could be
-attributed to cognitive processes like attention, eye movements(, or
-memory).\todo{which kind of memory}
+attributed to cognitive processes like attention, eye movements[, or
+memory].\todo{which kind of memory}
 % AO: auditory cortices
@@
 This suggests that variance correlating with lower level auditory processes was
-not averaged out across trials and nuisance regressors did not do their fucking
-job (still, it is kinda innate in the contrast).\todo{the word ''fuck`` is not
-acceptable}
+not averaged out across trials and nuisance regressors did not capture enough
+variance.\todo{ouf\dots}
 % possible reason
@@
 % intro
-Results of the AO contrasts consistently yielded significant clusters
-spatially constrained to the anterior part of the PPA group overlap (and
-anterior part of significant clusters of the AV contrasts).
-
-% intro to connectivity and object gradient
-Kind of complete overview of (references): Previous studies suggest that
-posterior and anterior part of the PPA show differences in
+Results of the AO contrasts consistently yielded significant clusters spatially
+constrained to the anterior part of both the PPA group overlap and significant
+clusters of the AV contrasts.
+
+% but
+Previous studies suggest that the PPA is not a functionally homogeneous area but
+consists of submodules that ``activate selectively to scenes'' and ``cooperate
+to build a complete representation of a scene''
+\citep{baldassano2013differential}.
+
+%
+The anterior and posterior PPA show:
 % connectivity
-a) connectivity profiles \citep{baldassano2013differential, baldassano2016two}[+
-Nasr et al., 2013; Silson et al., 2016a],
+a) differences in connectivity profiles [Nasr et al., 2013; Silson et al.,
+2016a] \citep{baldassano2013differential, baldassano2016two},
+% low-level scene features
+b) different responses to low-level scene features [Nasr et al., 2014; Silson et
+al., 2015; Baldassano et al., 2016a,b; Watson et al.,
+2016]\citep{baldassano2016two},
+% high-level scene features
+c) different responses to high-level scene features [Park et al., 2014; Aminoff
+and Tarr, 2015; Linsley and Macevoy, 2015; Marchette et al.,
+2015]\citep{baldassano2016two},
 % scenes vs abstract objects
-b) a gradient in sensitivity scene and abstract object stimuli
+c) a gradient in functional sensitivity to scenes and abstract object stimuli
 \citep{arcaro2009retinotopic, aminoff2007parahippocampal,
-baldassano2013differential},
-% low-level scene features
-c) differences in response to low-level scene features [Nasr et al., 2014;
-Silson et al., 2015; Baldassano et al., 2016a,b; Watson et al., 2016],
-% high-level scene features
-d) high-level scene features [Park et al., 2014; Aminoff and Tarr, 2015; Linsley
-and Macevoy, 2015; Marchette et al., 2015],
+baldassano2013differential}, and
 % TMS
-e) stimulation studies [Rafique et al., 2015] \citep{baldassano2016two}
-
-\paragraph{posterior PPA (pPPA)}
+e) differences in stimulation studies [+++Rafique et al.,
+2015+++]\citep{baldassano2016two}.  \paragraph{posterior PPA}
 
 % connectivity
-The posterior PPA is more [strongly] functionally connected to the occipital
+The posterior PPA is more strongly functionally connected to the occipital
 visual cortex, including lateral occipital cortex (LOC) and transverse occipital
@@
 % LOC and TOS
-[These regions have well-defined retinotopic maps (Arcaro et al., 2009; Nasr et
-al., 2011), and are associated with the perception of low-level visual features
-and object shape \citep{baldassano2013differential}.]
-
-%
-Increased activity within the pPHC during viewing of scenes relative to objects
-has been suggested to reflect regional specialization for visuospatial processes
-related to the extraction of scene layout information [Epstein,
-2008]\citep{baumann2016functional}.
-
-% high-level visual features
-Higher-level visual features also drive response patterns in these regions
-[Bryan et al., 2016]. They are hypothesized to be involved in extracting visual
-environmental features that can be used for navigation [Marchette et al., 2015;
-Julian et al., 2016; Kamps et al., 2016]. However, neither OPA nor posterior PPA
-show reliable familiarity effects [Epstein et al., 2007b; see further discussion
-below]\citep{baldassano2016two}.
-%
-The idea that the pPHC serves a dedicated role in visuospatial processing is
-further supported by studies showing that this brain region is sensitive to
-changes in basic visuospatial properties such as the shape and spatial frequency
-of abstract geometric objects and layouts [Rajimehr et al., 2011; Zeidman et
-al., 2012]\citep{baumann2016functional}.
+These regions have well-defined retinotopic maps [+++Arcaro et al., 2009; Nasr
+et al., 2011+++], and are associated with the perception of low-level visual
+features and object shape \citep{baldassano2013differential}.
 
 % object sensitivity
-The pPPA is more responsive to both simple visual textures and (abstract)
-objects \citep{arcaro2009retinotopic, baldassano2013differential}:
-%
-The pPPA responded about four times as strongly to a
-flickering checker-board stimulus compared to an anterior portion
-\citep{arcaro2009retinotopic}.
-%
-The response to objects was greater than the
-response to scrambled images only in the posterior portion
-\citep{arcaro2009retinotopic}.
-
-% low-level features
-OPA and pPPA have been shown to be closely related to the visual content of a
-stimulus. Even low-level manipulations of spatial frequency [Rajimehr et al.,
-2011; Kauffmann et al., 2015; Watson et al., 2016] or rectilinearity [Nasr et
-al., 2014] can drive responses in these regions \citep{baldassano2016two}.
-
-% baumann2016functionl
-We observed that pPHC is more strongly modulated bilaterally by the visual
-properties of the stimulus material (as evidenced by strong responses in the
-picture-scene conditions and no significant response in the word-object
-conditions)\citep{baumann2016functional}.
-%
-Our current study [and findings of Baldassano et al. (2013)] suggest that the
-functional topographic segregation of the PHC is underpinned by corresponding
-segregated connectivity patterns. Findings are consistent with a model of
-parahippocampal function in which visual information is projected from occipital
-and temporal areas to the pPHC [Libby et al., 2012], where encoding of
-visuospatial information takes place (a process that is computationally more
-demanding for complex stimuli such as scenes than for simple ones such as
-objects; Chai et al., 2010)\citep{baumann2016functional}.
-
-\paragraph{posterior network}
-
-% baldassano2016two
-The 1st (posterior) network [of two networks] includes
-pPPA and OPA/TOS. pPPA (retinotopic maps PHC1 \& PHC2) and OPA/TOS contain
-retinotopic maps and are not strongly coupled to the hippocampus at rest
-\citep{baldassano2016two}.
-
-% baldassano20160two: Neurosynth meta-analysis
-\citep{baldassano2016two}'s ``meta-analysis'' using Neurosynth: we compare the
-query ``scene'' (47 studies) with the query ``episodic memory, navigation, past
-future'' (125 studie).
-
-%
-Results: voxels significant only in the scene meta-analysis were concentrated in
-the posterior network (66\% in posterior network, 18\% in anterior, 16\% in
-other) % baldassano2016two: meta-analysis
-\citep{baldassano2016two} Voxels significant in both the scene and
-memory/navigation meta-analyses tended to fall near the border between the two
-networks and divided approximately equally among them (44\% posterior, 53\%
-anterior, 4\% other).
-%
-\citep{baldassano2016two} Voxels significant only in the memory/navigation
-meta-analysis were spread more widely across the cortex, but were concentrated
-more in the anterior than the posterior network (16\% posterior, 42\% anterior,
-42\% other).
-
-% interpretation
-Interpretation: visual scene activations tend to be posterior to the memory
-activations along the parahippocampal gyrus. [The transition point corresponds
-almost exactly to the division between our two networks. Dorsally, we also
-observe a separation between the reverse inference maps, with scene and memory
-activations falling into our two separate networks \citep{baldassano2016two}.]
-
-\paragraph{anterior PPA (aPPA)}
-
-The specific properties of aPPA have been less well studied, since it was not
-recognized as a separate region within the PPA until recently
-\citep{baldassano2016two}.
-
-% anterior PPA
-The anterior PPA is more [strongly] functionally connected to the RSC and
-parietal cortices (caudal inferior parietal lobe; cIPL)[, medial PFC, and the
+lower-level features: The pPPA is more responsive to both simple visual textures
+and (abstract) objects \citep{arcaro2009retinotopic,
+baldassano2013differential}:
+%
+The pPPA responded about four times as strongly to a flickering checker-board
+stimulus compared to an anterior portion \citep{arcaro2009retinotopic}.
+%
+The response to objects was greater than the response to scrambled images only
+in the posterior portion \citep{arcaro2009retinotopic}.
+
+%
+high-level features: Higher-level visual features also drive response patterns
+in these regions [Bryan et al., 2016].
+
+\paragraph{anterior PPA}
+
+The anterior PPA is more strongly functionally connected to the RSC and parietal
+cortices (caudal inferior parietal lobe; cIPL; cIPL was defined using the
+Eickhoff–Zilles PGp probabilistic cytoarchitectonic map)[, medial PFC, and the
 lateral surface of the anterior temporal lobe]
 \citep{baldassano2013differential, baldassano2016two}.
-
-% object sensitivity
-The aPPA is less visually responsive to both scenes\todo{check their paradigm \&
-result section} and objects, with notably low sensitivity to abstract object
-stimuli \citep{baldassano2013differential}.
-%
-Results suggest that aPPA may be more concerned with these types of spatial and
-non-object-based scene properties [= global scene properties such as spatial
-expanse] than posterior PPA \citep{baldassano2013differential}\todo{check if
-quoted correctly}.
 
@@
 \citep{baldassano2016two}.
+
+% object sensitivity
+The aPPA is less visually responsive to both scenes and objects, with notably
+low sensitivity to abstract object stimuli \citep{baldassano2013differential}.
+%
+Results suggest that aPPA may be more concerned with global scene properties
+(such as spatial expanse) and non-object-based scene properties than posterior
+PPA \citep{baldassano2013differential}.
+
 % spaciousness
@@
 
-\paragraph{anterior network}
-
-% baldassano2016two's networks
-\citep{baldassano2016two} The anterior network (the 2nd of two networks)
-consists of the caudal inferior parietal lobule (cIPL), RSC, and aPPA, which
-connect to the hippocampus (especially anterior hippocampus). These regions are
-implicated in both visual and nonvisual tasks, including episodic memory and
-navigation] \citep{baldassano2016two}.
-% baldassano2016connectivity
-The anterior network [that includes aPPA] exhibits much higher resting-state
-hippocampal coupling (especially to anterior hippocampus), suggesting that
-memory- and navigation-related functions are primarily restricted to the
-anterior network \citep{baldassano2016two}.
-
-% The memory and navigational network
-The network of parahippocampal, retrosplenial, and posterior parietal regions
-that we identify has been emerged independently in many different fields of
-neuroimaging, outside of scene perception.
-%
-Meta-analyses of internally directed tasks, such as theory of mind,
-autobiographical memory, and prospection, have identified this as a core,
-reoccurring network [Spreng et al., 2009; Kim,2010; Yeo et al., 2015 (component
-C10 of ?)]. It comprises a subset of the broader default mode regions, but
-functional and anatomical evidence suggests that it is a distinct, coherent
-subnetwork [Andrews-Hanna et al., 2010, 2014; Yeo et al.,
-2011]\citep{baldassano2016two}.
-%
-The broad set of tasks that recruit this network have been summarized in various
-ways, such as ``scene construction'' (Hassabis and Maguire, 2007), ``mnemonic
-scene construction'' [Andrews-Hanna et al., 2010], ``long-timescale
-integration'' [Hasson et al., 2015], or ``relational processing'' [Eichenbaum
-and Cohen, 2014].
-%
-A review of memory studies referred to this network as the posterior medial
-memory system, and proposed that it is involved in any task requiring
-``situation models'' relating entities, actions, and outcomes [Ranganath and
-Ritchey, 2012]\citep{baldassano2016two}.
-
-% hippocampus
-The network has strong functional connections to the hippocampus, which has been
-implicated in a broad set of cognitive tasks involving ``cognitive maps'' for
-organizing declarative memories, spatial routes, and even social dimensions
-[Eichenbaum and Cohen, 2014; Schiller et al., 2015]. During perception, the
-hippocampus binds together visual elements of an image [Olsen et al., 2012;
-Warren et al., 2012; Zeidman et al., 2015], which is especially important for
-scene stimuli [Lee et al., 2005a,b; Graham et al., 2006; Hodgetts et al., 2016].
-The hippocamppus then stores this representation into long-term memory [Ryan and
-Cohen, 2004]\citep{baldassano2016two}.
-%
-Our results suggest that only the anterior scene regions interface directly with
-the hippocampus, potentially enabling the construction of hippocampal
-environmental representations, and retrieval of relevant memories and
-navigational information for a presented or imagined
-scene\citep{baldassano2016two}.
-
-\paragraph{conclusion \& interpetation: subregions}
-
-% conclusion by Baldassano (2013): PPA subregions
-Data suggest that PPA might contain identifiable subregions, but subregions
-should not be considered as completely independent modules.
-%
-Both subregions activate selectively to scenes, implying that these subregions
-cooperate to build a complete representation of a scene
-\citep{baldassano2013differential}.
-
-We do not argue that the PHC is not sensitive to spaces, places, and spatial
-information, but rather that it is sensitive to spatial stimuli because of the
-associative information (space-related associations) that such stimuli evoke
-\citep{aminoff2013role}.
-% posterior PPA for visual visual associative information
-Spatial contextual associations are a dominant property of places and scenes,
-and thus scenes consistently activate this posterior subregion of the PHC (e.g.,
-PPA; epstein1998ppa)\citep{aminoff2013role}.
-
-% baldassano2013: functional contrast
-The fact that aPPA had a lower sensitivity to our abstract object stimuli does
-not necessarily imply that this region does not use object information
-\citep{baldassano2013differential}.
-% baldassano2013: connectivity
-Their distinct connectivity properties, however, suggests that each may be
+\paragraph{conclusion: subregions}
+
+%
+although our data suggest that PPA might contain identifiable subregions, these
+subregions should not be considered as completely independent modules. Both
+subregions activate selectively to scenes, and the parahippocampal region (at
+least in macaques) is densely self-connected (Suzuki 2009), implying that these
+subregions cooperate to build a complete representation of a scene.
+%
+Their distinct connectivity properties, however, do suggest that each may be
 involved in specific aspects of visual and cognitive processing involved in the
 overarching goal of scene understanding.
+
+%
+The fact that anterior PPA had a lower sensitivity to our abstract object
+stimuli does not necessarily imply that this region does not use object
+information\citep{baldassano2013differential}.
 %
 Previous work has shown that PPA responds to objects that have spatial
-associations [Aminoff et al., 2007], are space-defining [Mullally and Maguire,
-2011], and are navigationally-relevant [Janzen and Van Turennout, 2004]. These
-types of responses require spatial memory and cannot be based purely on visual
-features like object shape.
-%
-If anterior PPA is involved in processing spatial context, then space-defining
-or navigationally-relevant objects could activate anterior PPA more strongly
-than our abstract objects, which were unfamiliar and provided no sense of
-context or orientation \citep{baldassano2013differential}. Further experiments
-will be required to determine what type of object-related information is used in
-this region \citep{baldassano2013differential}.
-
-% baldassano2016two
+associations [Aminoff et al. 2007], are space-defining [Mullally and Maguire
+2011], and are navigationally-relevant [Janzen and Van Turennout 2004].
+%
+These types of responses require spatial memory and cannot be based purely on
+visual features like object shape. If anterior PPA is involved in processing
+spatial context, then space-defining or navigationally-relevant objects could
+activate anterior PPA more strongly than our abstract objects, which were
+unfamiliar and provided no sense of context or orientation.
+%
+Further experiments will be required to determine whether what type of
+object-related information is used in this region
+\citep{baldassano2013differential}.
+
+\paragraph{contextual associations}
+
+%
+The PCH has been implicated in the integration and retrieval of contextual
+associations in memory [Aminoff et al., 2013; Bar and Aminoff, 2003; Bar et al.,
+2008a, 2008b].
+%
+According to this view, activity in PHC reflects modality-independent retrieval
+of contextual information from memory (contextual associations: relations
+between objects and conditions that describe, represent, and bring meaning to an
+environment; such as which objects typically occur in a given scene and where
+they are likely to be located relative to one another; [Aminoff et al., 2013])
+\citep{baumann2016functional}.
+
+Results: aPHC is more active during contextual judgments regardless of stimulus
+category (scenes vs objects) or modality (word vs picture)
+\citep{baumann2016functional}.
+%
+The left aPHC was active in all contextual judgment task conditions. This
+suggests a functional segregation, with posterior sections of the PHC supporting
+visuospatial processing of scenes and anterior sections of the left PHC involved
+in contextual associative processing\citep{baumann2016functional}.
+
+%
 \citep{baldassano2016two}: We propose that scene processing is fundamentally
@@
 present'' (Baker, 2012, in The Word Hoard).
+
 %
@@
 
-\subsubsection{contextual associations: Baumann 2016}
-
-% visuospatial and mnemonic processes
-The PHC plays a key role in
-%
-a) visuospatial analysis of scenes [Epstein et al., 1999, 2003; Park and Chun,
-2009; Rajimehr et al., 2011] and
-%
-b) (contextual) mnemonic processing [Aminoff et al., 2013, Bar and Aminoff,
-2003; Düzel et al., 2003; Janzen and van Turennout, 2004; Baumann et al., 2010;
-Wegman and Janzen, 2011] \citep{baumann2016functional}
-
-% associative processing
-The PCH has been implicated in the integration and retrieval of contextual
-associations in memory [Aminoff et al., 2013; Bar and Aminoff, 2003; Bar et al.,
-2008a, 2008b]. According to this view, activity in PHC reflects
-modality-independent retrieval of contextual information from memory, such as
-which objects typically occur in a given scene and where they are likely to be
-located relative to one another (contextual associations: relations between
-objects and conditions that describe, represent, and bring meaning to an
-environment [Aminoff et al., 2013]) \citep{baumann2016functional}.
-
-%
-We provide evidence for a dissociation between neural activation patterns
-associated with visuospatial analysis of scenes and contextual mnemonic
-processing along the parahippocampal longitudinal axis
-\citep{baumann2016functional}.
-
-%
-Paradigm: Participants had to judge the contextual relatedness of scene and
-object pairs (presented either as words or pictures)
-\citep{baumann2016functional}.
-%
-Participants judged the contextual relatedness of scene and object pairs (“bike”
-\& “bell” are a contextually congruent object– object pair, “sofa” \&
-“microscope” are incongruent; “boat” \& “lake” are a contextually congruent
-object–scene pair, “tractor” \& “hotel” are
-incongruent)\citep{baumann2016functional}.
-%
-Each pair was presented either in printed-word format or in a combined
-word–picture format. That allowed us to present pictorial objects and scenes in
-isolation (Fig. 1)\citep{baumann2016functional}.
-
-%
-1) To identify visuospatial regions of the PHC, we tested for voxels with
-greater activity for picture–scene trials than for picture–object trials over
-and above activity differences elicited by the comparison of word–scene trials
-and word– object trials\citep{baumann2016functional}.
-%
-2) To locate context-related regions of the PHC, we tested for voxels that were
-selectively active during the contextual judgment task regardless of the type of
-stimulus (scenes vs objects) or presentation modality (word vs
-picture)\citep{baumann2016functional}.
-
-%
-Results: aPHC is more active during contextual judgments regardless of stimulus
-category (scenes vs objects) or modality (word vs picture).
-%
-The left aPHC was active in all contextual judgment task conditions. This
-suggests a functional segregation, with posterior sections of the PHC supporting
-visuospatial processing of scenes and anterior sections of the left PHC involved
-in contextual associative processing\citep{baumann2016functional}.
-%
-It is important to note that, whereas our study only examined retrieval-related
-activity for object–object and object–scene relationships, findings from prior
-studies suggest that the functions of the aPHC are not limited to these types of
-material, but should also be involved in the retrieval of associations involving
-other stimulus categories such as faces [Düzel et al., 2003; Kirwan and Stark,
-2004]\citep{baumann2016functional}.
-
-%
-Interpretation: Activation maxima associated with visuospatial and mnemonic
+%
+Activation maxima associated with visuospatial and mnemonic
 processes were spatially segregated, providing support for the existence of
@@
 systems\citep{baumann2016functional}.
-%
-This anatomical segregation of function [cf. their results] suggests a
-predominantly perceptual role for the pPHC and a mnemonic role for the anterior
-parahippocampal cortex (Note: the anterior parahippocampal cortex should not be
-confused with the anterior portion of the parahippocampal gyrus, which includes
-the perirhinal cortex; Ranganath and Ritchey,
+
+Results suggests a predominantly perceptual role for the pPHC and a mnemonic
+role for the anterior parahippocampal cortex (Note: the anterior parahippocampal
+cortex should not be confused with the anterior portion of the parahippocampal
+gyrus, which includes the perirhinal cortex; Ranganath and Ritchey,
 2012.)\citep{baumann2016functional}.
-%
+
 We suggest that the aPHC encodes incoming information in an amodal format and
@@
 for an review)\citep{baumann2016functional}.
-%
-Linsley and McEvoy (2015) found (using an fMRI searchlight analysis) that
-activity patterns in the aPHC were strongly modulated by the presence of objects
-in scenes; patterns in the pPHC were not modulated. This again suggests that the
-aPHC is more concerned with contextual than visuospatial analysis of scene
-images\citep{baumann2016functional}.
-
-%
-Hypothesis: Moreover, it is conceivable that different categories of contextual
-associations (e.g., spatial, temporal, affective, etc.) cluster in different
-subregions within the aPHC.  High-resolution fMRI and analysis techniques such
-as adaptation fMRI [Krekelberg et al., 2006] or multivoxel pattern
-classification [Norman et al., 2006] could be used to determine any such
-finegrained functional topography within the parahippocampal cortex]
-
-\subsubsection{contextual associations: Aminoff 2013 (review) + 2015}
-
-% memory
-Models of recognition memory have previously identified parahippocampal cortex
-as primarily encoding spatial context information (Eichenbaum et al., 2007)
-\citep{baldassano2013differential}.
-
-% contextual associations in anterior vs. posterior
-\citep{aminoff2013role} proposed that the general function of the PHC can be
-thought of as processing of contextual associations. Activity within the PHC is
-distributed along an anterior–posterior axis:
-% pPPA
-Activity related to spatial contexts is focused in the posterior part of the PHC
-=> posterior subregion of PHC is particularly optimized to process spatially
-organized contextual associations.
-% aPPA
-Activity evoked by non-spatial contexts focused in the more anterior part of the
-PHC (optimized to process contextual associations in other, non-spatial domains)
-[bar2003cortical, aminoff2007parahippocampal] \citep{aminoff2013role}.
-
-% Aminoff regarding contextual processing in the PHC and beyond
-\citep{aminoff2013role} regarding method in [aminoff2007parahippocampal]: we
-compared contextual processing of objects that are strongly related to a
-specific place (oven is found in a kitchen) with contextual processing of
-objects that are highly associated with a context but not a specific place
-(birthday cake is found at a birthday party; but the party can take place
-anywhere)\citep{aminoff2013role}.
-%
-Activity elicited by these two types of contextual objects was compared with the
-activity elicited for objects that were only weakly associated with many
-contexts (e.g., a lamp) \citep{aminoff2013role}.
-% results
-Differential activity was found in the PHC and the RSC, replicating the previous
-findings [Bar \& Aminoff (2003) The parahippocampal\dots]
-\citep{aminoff2013role}.
-
-\citep{baumann2016functional} zu \citep{aminoff2015associative}:
-% pPHC
-pPHC showed increased activity when participants viewed (already familiar)
-spatial configurations of meaningless shapes (regardless of their individual
-identities);
-% aPHC
-aPHC was more active during the display of (already familiar) meaningless shapes
-(regardless of their spatial configuration).
-%
-These findings can be interpreted as suggestive of pPHC visuospatial processes
-and aPHC contextual processes \citep{baumann2016functional}.
-
-\paragraph{Abstract}
-
-\citep{aminoff2015associative} How are scenes represented in the human brain?
-Along what visual and semantic dimensions are scenes encoded in memory?
-%
-
-Hypothesis:
-%
-a) global spatial properties provide a basis for categorizing the neural
-response patterns arising from scenes
-%
-b) non-spatial properties, such as single objects, also account for variance in
-neural responses
-
-%
-The list of critical scene dimensions has continued to grow encompassing
-properties such as geometric layout, big/small, crowded/sparse, and
-three-dimensionality.
-%
-These dimensions may be better understood within the more general framework of
-associative properties \citep{aminoff2015associative}.
-%
-Across both the perceptual and semantic domains, features of scene
-representations are related to one another through learned
-associations\citep{aminoff2015associative}.
-
-%
-We investigated whether different types of relations, all falling under the
-heading of associative processing, reliably regions of brain networks known to
-be scene selective\citep{aminoff2015associative}.
-%
-Critically, the components of such associations are consistent with the
-dimensions that are typically invoked to account for scene understanding and its
-neural bases\citep{aminoff2015associative}.
-
-Results: We show that non-scene stimuli displaying novel associations across
-identities or locations recruit putatively scene-selective regions of the human
-brain (the parahippocampal/lingual region, the retrosplenial complex, and the
-transverse occipital sulcus/occipital place area)\citep{aminoff2015associative}.
-
-%
-Moreover, we find that the voxel-wise neural patterns arising from these
-associations are significantly correlated with the neural patterns arising from
-everyday scenes providing evidence whether the same encoding principals underlie
-both types of processing\citep{aminoff2015associative}.
-
-%
-Interpretation: Results provide evidence that the neural representation of
-scenes is better understood within the broader theoretical framework of
-associative processing\citep{aminoff2015associative}.
-%
-Results also demonstrate a division of labor that arises across scene-selective
-regions when processing associations and scenes providing better understanding
-of the functional roles of each region within the cortical network that mediates
-scene processing\citep{aminoff2015associative}.
-
-\paragraph{Intro}
-
-Scenes are complex stimuli containing rich, statistically regular information
-about objects, background, context, semantics, and spatial layout at multiple
-scales.
-%
-As a core component of scene understanding we extract and learn these
-regularities (certain objects typically appear together
-[1–3]).
-%
-Associated regularities are useful in defining scene as well as in predicting
-which other objects and relations are likely to occur within a scene
-[5].
-
-% a-modality
-Features of any kind of mental representation, irrespective as to whether that
-representation is nominally visual, linguistic, etc., are related to one another
-via learned associations.
-%
-These associations are not necessarily modality-specific (for example, visual
-representations are likely to carry many semantic and affective associations not
-directly present in the image).
-
-%
-With respect to scene understanding, we construe contextual associative
-processing as a more semantically-driven process in which associations are not
-arbitrary relations, but rather relations that emerge as a consequence of their
-shared context within the larger scene.
-%
-Associations are not simply frequently co-occurring features pairs; instead they
-are pairs that both co-occur and add meaning to scenes.
-%
-Furthermore, the mechanism by which scenes are perceived, recognized, and
-understood, is through means of processing the associations elicited from
-components of the scene.
-
-%
-At the core of neurally-based theories of scene perception are the issues of the
-computations and representations instantiated in each of these brain regions.
-The literature has focused on more the representations, characterizing the
-nature of the information encoded about scenes.
-%
-It has been suggested that scenes are analyzed in terms of their spatial global
-properties, such as the ‘spatial envelope’, which takes into account a scene’s
-overall spatial structure and layout [20,21].
-%
-Empirically, it has been demonstrated that global properties are salient
-cues for categorizing scenes in both behavior [22] and in patterns of neural
-activity [23–26].
-
-%
-Compared to other factors that characterize scenes (i.e., content and depth),
-the expanse of the scene (i.e. its spatial boundary) has been found to be the
-most effective in accounting for variations in the neural responses within
-scene-selective brain regions [23,24].
-%
-Generally, spatial information defining the geometric layout of a scene has
-often been implicated in determining the neural responses arising from
-scene-selective brain regions [27].
-
-%
-In contrast, non-spatial properties can account for variations in the neural
-responses associated with scene processing and
-representation.
-%
-For example, Harel et al. [11], found that the neural encoding of scenes
-captures information about single objects (i.e., non-spatial) as well as
-background spatial properties.
-%
-Supporting this point, strongly contextualized objects also elicit neural
-activity within scene-selective cortex [28,29].
-
-%
-Finally, objects present as the contents of a scene can also modulate activity
-in scene-selective regions.
-%
-For example, scenes where the most salient object carries strong contextual
-associations (e.g., a scene with a parking meter) recruit scene-selective
-regions more than do scenes with a salient object carrying weak contextual
-associations (e.g., a scene with a squirrel) [30].
-
-%
-Overall, scene-selective brain regions are encoding a rich collection of
-information, including global and local properties, spatial background
-information, and individual object tokens.
-
-%
-The list of critical properties keeps growing (e.g., big/small, crowded/sparse,
-three-dimensionality [31–33]), some seemingly contradicting others about which
-properties are critical in scene understanding.
-%
-Scene understanding may be better understood within a more general framework in
-which scenes are encoded with respect to their associative properties
-[28,30,34,35].
-%
-Associative properties are not restricted to the spatial or the global domain,
-and can account for why information regarding spatial layout and single objects
-play an important role in scene understanding and concomitant neural
-responses.
-
-%
-Associative processing offers an explanation for what particular kinds
-of information are present in scene representation (e.g., objects and spatial
-information) and a basis for explaining how and why this information is
-important.
-%
-For instance, on average, spatial layout and global properties may carry more
-associative information, and thus are typically prominent in accounts of the
-mechanisms mediating scene recognition.
-
-%
-To test the idea that associative processing is inherent in scene understanding,
-we explore whether the network of brain regions recruited in scene perception is
-also recruited when processing non-scene-like stimuli that contain associative
-information.
-
-%
-If these regions are active when processing the associations learned between
-non-scene-like novel stimuli than these regions must not be involved in only
-processing the visual properties of the scene, but rather, are processing what
-is associated with the components of the scene as learned from previous
-experience.
-
-%
-We focus on the associative processing of concurrent object identities (i.e.,
-semantic associations) and spatial relations between objects (i.e., spatial
-associations).
-
-%
-For both semantic and spatial associations, we predict that the three
-typically-identified scene-selective brain areas, the PPA, RSC, and OPA, will
-all exhibit selective activity for both scenes and for associations in general,
-without necessarily having any obvious “scene-like”
-qualities.
-
-%
-We are positing that scene processing is best understood as, at least in part,
-arising from a more general mechanism–that of associative
-processing.
-%
-The fact that this mechanism is more general does not make it vague. Our point
-is that learning and encoding relations between tokens (“associations”) is a
-fundamental process across many cognitive domains and, critically, this process
-has explanatory validity for scene processing.
-%
-Reframing scene processing as involving a more general mechanism helps
-articulate the means by which scene perception
-occurs.
-
-%
-Participants were scanned while they engaged in processing either everyday
-scenes or associations between meaningless shapes.
-%
-For processing of meaningless shapes, participants performed a task (prior to
-scanning; unrelated to the associations) in which they implicitly learned
-spatial or identity associations between configurations of novel shapes (Fig
-1).
-
-%
-First, to compare brain activity from learning novel associations to the
-processing of scenes, we correlated the distributed, voxel-by-voxel pattern of
-activities arising from these two conditions, thereby testing whether similar
-neural mechanisms mediate both general associative processing and scene
-perception.
-
-%
-Second, consistent with previous work ([28,31,34,37]) we asked whether the
-neural encoding of scenes shifts across association types–from non-spatial or
-semantic scene properties to spatial scene properties–as one moves from the
-anterior to the posterior PPA.
-%
-These analyses shed light on the hypothesis that a single underlying principle,
-associative processing, accounts for how scenes are represented in the
-brain.
-
-%
-Although prior studies have manipulated spatial and identity associations by
-having participants learn meaningless patterns of shapes [34], ours is the first
-study to directly compare such associative processing with the processing of
-everyday scenes.
-
-%
-We include two new baselines to better understand whereby effects of
-associations arise: weak contextual objects and scrambled images. Finally, we
-are careful to collect an additional independent dataset to functionally define
-scene-selective regions.
-
-%
-These new conditions are all advances (in terms of explicating the processing of
-scene-selection regions) relative to our earlier study in which we used the same
-shapes and trained participants over a two-week period [34].
-%
-We also include several methodological changes: a spatial-only associative
-condition was included to isolate spatial processing independently of identity
-associations; and the no-association condition provides a better control in that
-it now shows the same number of shapes as the association condition (i.e., 3).
-
-\paragraph{Method}
-
-\paragraph{Results (just aPPA vs. pPPA)}
-
-%
-There is some evidence that within the parahippocampal region, anterior and
-posterior regions may support different kinds of associations
-[34,37,40,41].
-%
-a) aPPA processes non-spatial associations (as realized in the ID condition)
-%
-b) pPPA process spatial associations (as realized in the SP
-condition.
-%
-We tested this hypothesis by examining two contrasts within scene-selective PHC
-regions: SP versus NA and ID versus NA.
-(we used the scenes versus baseline contrast to capture all scene-related
-activity within parahippocampal cortex).
-
-%
-The pattern of average activity across subregions supports a division of labor
-in which
-%
-a) anterior subregions showed the largest differences in the ID versus NA
-contrast relative to the SP versus NA contrast, while
-%
-b) posterior subregions showed the largest differences in the SP versus NA
-contrast relative to the ID versus NA contrast.
-%
-In the LH PPA this was significant in both in the interaction of Association by
-Subregion (F(4,56) = 5.85, p < .001) and critically, in the linear interaction
-contrast (F(1,14) = 8.05, p < .01).
-%
-The significance of this linear contrast indicates that the transition from
-identity to spatial associative processing may be construed as a gradient from
-anterior to posterior regions of parahippocampal cortex. However, the same
-Association by Subregion interaction was not observed in the RH
-PPA.
-
-%
-To examine whether identity and spatial associations also capture
-functionally-relevant properties within scenes, we examined the similarity
-between the voxel-wise pattern of BOLD responses elicited by identity
-associations and real-world scenes, and by spatial associations and real-world
-scenes.
-%
-We hypothesized that, to the degree that these two types of associations are
-intrinsic to scene processing, similar patterns of activation across each of the
-two association conditions and real-world scenes would identify those
-(potentially separable) neural substrates supporting the representation of these
-kinds of associations.
-
-%
-Unthresholded t-values for the ID versus NA and SP versus NA contrasts within
-each of the five PPA subregions were extracted for each voxel and then
-cross-correlated within each subregion with the real-world scenes versus
-objects/scrambled contrast.
-%
-In LH PPA the interaction within an omnibus ANOVA [the two factors being
-Subregion (moving from the most posterior to the most anteri- or) x Association
-(identity or spatial)] was significant (F(4,56) = 2.69, p < .04) as well as the
-critical linear x linear trend analysis (F(1,14) = 7.57, p < .016) (Fig
-3A).
-%
-Consistent with our analysis of average activity within these subregions, this
-interaction was not observed in the RH PPA (F(1,14) = 1.22, n.s.) (S1
-Fig).
-%
-However, it is worth noting that within the right hemisphere, the correlation
-between spatial associations and real-world scenes did exhibit the predicted
-pattern whereby the strongest correlation was observed in posterior subregions
-of PPA, with a progressively lower correlation being observed moving in a
-posterior to anterior direction (S1 Fig).
-
-%
-=> Our results indicate that the organization of PPA with respect to associative
-processing is a gradient in which posterior subregions of PPA are biased towards
-spatial associations and anterior subregions of PPA are biased towards identity
-associations.
-
-%
-Additional support for this claim is shown in Fig 3B, where instead of dividing
-the PPA into five equal subregions, the correlation was run over progressively
-more and more of the PPA, starting from the most posterior subregion and adding
-subregions until the entire PPA was taken into account;
-%
-As illustrated, the most extreme ends of the PPA show the strongest biases
-towards capturing the similarity of either spatial associations and scenes, or
-identity associations and scenes.
-%
-whereas if the whole PPA were to be surveyed, these differences would be masked.
-Of note, this gradient appears to be truly continuous across posterior and
-anterior portions of the PPA–even considering only the posterior PPA, we observe
-a gradient in which the strongest preference for spatial associations is found
-in the most posterior portions of the posterior
-PPA.
-%
-Similarly, considering only the anterior PPA, we observe a gradient in which the
-strongest preference for identity associations is found in the most anterior
-portions of the anterior PPA.
-
-\paragraph{Discussion (just aPP vs pPPA)}
-
-Results suggest some specialization (at least in preference) for the processing
-of associative information across the PPA.
-%
-pPPA is preferentially recruited by spatial associations while anterior PPA is
-preferentially recruited by semantic (i.e., non-spatial) associations.
-
-%
-A functional distinction between anterior and posterior PPA has been reported
-previously. In particular, this distinction has been based on PPA responses when
-processing objects associated with spatial contexts (i.e., contexts associated
-with specific places, for example, an oven and a kitchen) and when processing
-objects associated with non-spatial contexts (i.e., contexts not tied to
-specific places, for example, champagne with New Year’s Eve) [28,34,37,40,41].
-
-%
-Here, we explicitly investigated this spatial/non-spatial distinction by
-isolating the two association types in simple, novel stimuli and then relating
-these controlled stimuli to the processing of real-world scenes containing
-similar associations.
-%
-We predicted that this Association-Type x Scene correlation would reveal the
-expected posterior to anterior progression with spatial properties within scenes
-selectively recruiting posterior PPA and non-spatial, identity properties within
-scenes selectively recruiting anterior PPA.
-%
-Moreover, we expected that this functional division would be continuous, with
-the similarity in BOLD responses elicited by scenes and trained spatial
-associations decreasing in a posterior to anterior direction.
-%
-In contrast, the similarity in BOLD responses elicited by scenes and trained
-identity associations was predicted to decrease in an anterior to posterior
-direction. These predictions were confirmed in our study.
-
-%
-This information processing gradient may lie within a broader, more general
-organization of the PHG.
-%
-The gradient of processing identity or non-spatial associative information may
-continue through the neighboring perirhinal cortex, which is thought to be
-involved in object and person recognition particularly with regard to combining
-different fea- tures of knowledge, such as a stop sign is red
-[42].
-%
-In contrast, the pPPA border regions where mid-level visual information is
-processed, which may be more sensitive to spatial
-information.
-%
-We do note, however, that this interaction was only observed in the left
-hemisphere, although the right hemisphere demonstrated a similar gradient of
-specialization in spatial processing from posterior to
-anterior.
-
-%
-However, the activity related to identity processing was less well organized.
-This pattern of results is somewhat consistent with the fact that the left
-hemisphere is often implicated in more semantically-oriented processing, for
-example, scene categorization, whereas the right hemisphere has been implicated
-in more spatial processing, for example, as in the visual details between
-different exemplars of the same category [10].
-%
-These patterns hint that the right hemisphere PPA may play a larger role in the
-processing of the spatial relations within scenes and a lessor role in the
-processing of scene semantics.
-%
-In sum, our current functional view of the PPA is as a gradient in which
-progressively different scene dimensions come to be
-instantiated.
-
-\paragraph{Discussion: division of labor in the PPA, RSC and OPA}
-
-The PPA, RSC, and OPA were all strongly engaged in both associative processing
-and in scene perception.
-
-%
-However, it is unlikely that these three regions play entirely redundant roles
-in scene understanding–a conclusion supported by the differences we observed
-between the SP, ID, and SPID conditions.
-%
-In particular, we suggest that the PPA involves the processing of multiple scene
-dimensions that reflect different kinds of associative information (e.g.,
-spatial and identity).
-
-%
-RSC and OPA were both more sensitive to identity associations, whether appearing
-in isolation or in conjunction with spatial associations. Elsewhere we have
-suggested that the RSC processes the prototypical representation of context,
-termed a “context frame,” which contains information regarding both the key
-objects and the spatial relations be- tween them
-[28,43].
-%
-For example a context frame of bathroom would include information regarding a
-shower, toilet, sink, toothbrush, mirror, as well as spatial information such as
-the mirror is typically located above the sink.
-
-%
-Our present data support this suggestion, indicating that the RSC is involved in
-both spatial and identity associative processing. Moreover, responses in the RSC
-were the most predictive of learning: better learning elicited higher neural
-activity in the RSC, specifically in the conjoined SPID
-condition.
-%
-As such, the RSC, as the highest level of associative processing, may be
-involved in the long-term encoding of contextual associations, that is, the
-context frame, where both spatial and non-spatial associations are
-processed.
-
-%
-In contrast, the OPA lies in close proximity to the IPS, a region that has
-anatomical connections with both the ventral stream, potentially conveying
-identity information, and the dorsal stream, potentially conveying spatial
-information [44,45].
-%
-This provides the anatomical architecture to combine both identity and spatial
-information within a unified contextual
-representation.
-%
-Future studies are needed to explore the specific anatomical connections with
-the OPA regions, examining whether it is similarly connected to both the dorsal
-and ventral pathways.
-
-%
-Interestingly, our study also found the neural signal related to the processing
-of spatial associations from the OPA was negatively correlated with
-learning.
-%
-That is, the better the learning of spatial associations, the lower the response
-of the OPA relative to the control condition. Because the OPA is more posterior
-than the PPA and RSC, it may be involved in earlier stages of scene processing
-[16–18].
-%
-Our results build on this, suggesting that the initial processing of spatial
-associations occurs in the OPA, whereas more complex analysis of spatial
-contextual associations, with increased learning, may occur in, progressively,
-the PPA and RSC.
-
-\paragraph{Conclusions}
-
-%
-We invoke associative processing as a computationally-definable construct for
-predicting the spatial organization of scene-related activity across different
-scene properties.
-%
-we suggest that the neural mediators of scene processing should not be construed
-as encapsulated visual modules, but rather as manifestations of associations
-that reflect the interaction between visual recognition processes and the
-application of long-term memories arising from past experiences (Aminoff et al.,
-2013).
-%
-Within this framework, scene processing is not a purely bottom-up visual
-process, but rather is an interactive process in which we are constantly
-considering–in the form of both spatial and non-spatial associations– our past
-experiences to generate predictions, expectations, and constraints about our
-physical environment.
-
-%
-We suggest that general associative processing mechanisms are sensitive to
-frequently occurring or repeated relations within scenes, including object
-identities that co-occur, spatial relations between the objects, and spatial
-locations for individual objects, all of which facilitate the recognition and
-categorization of visual scenes.
-%
-As such, the collection of associations that help to define a scene provides a
-context for individual elements within that scene.
-%
-For example, a towel hanging on a rack near a shower would most likely be a
-bathroom towel, whereas the same towel lying flat on the sand near an umbrella
-would most likely be a beach towel.
-%
-We contend that the parsing of these sorts of contextual associations within
-scenes is fundamental to scene understanding, and that scene understanding
-construed as such, can then influence cognitive processing in myriad
-ways.
-
-%
-Within the human brain, we argue that the neural bases for the application of
-contextual knowledge is a functional gradient spanning different types of
-associations instantiated across the PPA, and contextually-mediated
-representations within the RSC and OPA.
-%
-Most saliently, our observations of selectivity for spatial and identity
-associations provide compelling evidence that the neural representation of
-visual scenes is best understood as a consequence of the asso- ciative
-processing in both the spatial and non-spatial domains.
 

### 2020-11-23 paper/main.tex
shorten review of anterior vs. posterior PPA

@@
 resonance imaging (BOLD fMRI) \citep{aguirre1998area, epstein2014neural,
-epstein1998ppa}.
+epstein1998ppa, troiani2012object}.
 
@@
 Results of the AO contrasts consistently yielded significant clusters spatially
-constrained to the anterior part of both the PPA group overlap and significant
-clusters of the AV contrasts.
-
-% but
-Previous studies suggest that the PPA is not a functionally homogeneous area but
-consists of submodules that ``activate selectively to scenes'' and ``cooperate
-to build a complete representation of a scene''
-\citep{baldassano2013differential}.
-
-%
-The anterior and posterior PPA show:
-% connectivity
-a) differences in connectivity profiles [Nasr et al., 2013; Silson et al.,
-2016a] \citep{baldassano2013differential, baldassano2016two},
-% low-level scene features
-b) different responses to low-level scene features [Nasr et al., 2014; Silson et
-al., 2015; Baldassano et al., 2016a,b; Watson et al.,
-2016]\citep{baldassano2016two},
-% high-level scene features
-c) different responses to high-level scene features [Park et al., 2014; Aminoff
-and Tarr, 2015; Linsley and Macevoy, 2015; Marchette et al.,
-2015]\citep{baldassano2016two},
-% scenes vs abstract objects
-c) a gradient in functional sensitivity to scenes and abstract object stimuli
-\citep{arcaro2009retinotopic, aminoff2007parahippocampal,
-baldassano2013differential}, and
-% TMS
-e) differences in stimulation studies [+++Rafique et al.,
-2015+++]\citep{baldassano2016two}.  \paragraph{posterior PPA}
-
-% connectivity
-The posterior PPA is more strongly functionally connected to the occipital
-visual cortex, including lateral occipital cortex (LOC) and transverse occipital
-sulcus (TOS) \citep{baldassano2013differential, baldassano2016two}.
-% LOC and TOS
-These regions have well-defined retinotopic maps [+++Arcaro et al., 2009; Nasr
-et al., 2011+++], and are associated with the perception of low-level visual
-features and object shape \citep{baldassano2013differential}.
-
-% object sensitivity
-lower-level features: The pPPA is more responsive to both simple visual textures
-and (abstract) objects \citep{arcaro2009retinotopic,
-baldassano2013differential}:
-%
-The pPPA responded about four times as strongly to a flickering checker-board
-stimulus compared to an anterior portion \citep{arcaro2009retinotopic}.
-%
-The response to objects was greater than the response to scrambled images only
-in the posterior portion \citep{arcaro2009retinotopic}.
-
-%
-high-level features: Higher-level visual features also drive response patterns
-in these regions [Bryan et al., 2016].
-
-\paragraph{anterior PPA}
-
-The anterior PPA is more strongly functionally connected to the RSC and parietal
-cortices (caudal inferior parietal lobe; cIPL; cIPL was defined using the
-Eickhoff–Zilles PGp probabilistic cytoarchitectonic map)[, medial PFC, and the
-lateral surface of the anterior temporal lobe]
+constrained to the anterior part of the PPA group overlap (and to the anterior
+part of significant clusters of the AV contrasts).
+% PPA might have submodules
+Previous studies provide evidence that the posterior PPA (pPPA) and anterior PPA
+(aPPA) show differences in both functional connectivity profiles and in
+response to low- and high-level visual features.
+
+% posterior connectivity
+The pPPA is more strongly functionally connected to the occipital visual cortex
 \citep{baldassano2013differential, baldassano2016two}.
-
-\citep{baldassano2016two} The aPPA is
-% category
-a) driven more by high-level category information than by spatial frequency
-content [Watson et al., 2016],
-% locations
-b) to represent real-world locations (even from perceptually distinct views)[
-Marchette et al., 2015],
-% associations
-c) to encode object co-occurrences [Aminoff and Tarr, 2015], and
-% scene size
-d) to represent real-world physical scene size [Park et al., 2014]
-\citep{baldassano2016two}.
-
-% object sensitivity
-The aPPA is less visually responsive to both scenes and objects, with notably
-low sensitivity to abstract object stimuli \citep{baldassano2013differential}.
-%
-Results suggest that aPPA may be more concerned with global scene properties
-(such as spatial expanse) and non-object-based scene properties than posterior
-PPA \citep{baldassano2013differential}.
-
-% spaciousness
-Its representation of scene spaciousness draws on prior knowledge about the
-typical size of different scene categories, since it is affected by the presence
-of diagnostic objects [Linsley and Macevoy, 2015]\citep{baldassano2016two}.
+% including lateral occipital cortex (LOC) and transverse occipital sulcus (TOS)
+% functionality
+The pPPA is functionally more responsive than aPPA to low-level features of
+(abstract) objects or scenes \citep{baldassano2013differential,
+nasr2014thinking, rajimehr2011parahippocampal}.
+
+% anterior
+The anterior PPA is more strongly functionally connected to portions of the
+default mode network, including caudal inferior parietal lobe (cIPL), the
+restrosplenial complex (RSC), medial PFC and the lateral surface of the anterior
+temporal lobe \citep{baldassano2013differential, baldassano2016two}
+% anterior cIPL is defined using the Eickhoff–Zilles PGp probabilistic
+% cytoarchitectonic map
+The aPPA is functionally more responsive than pPPA to high-level features of
+objects (e.g. spatial contextual associations
+\citep{aminoff2007parahippocampal, aminoff2015associative} and scenes (e.g.
+real-word size \citep{park2015parametric}; a scene's abstract identity/category
+\citep{marchette2015outside, watson2016patterns}).
 
@@
 
-%
-although our data suggest that PPA might contain identifiable subregions, these
-subregions should not be considered as completely independent modules. Both
-subregions activate selectively to scenes, and the parahippocampal region (at
-least in macaques) is densely self-connected (Suzuki 2009), implying that these
-subregions cooperate to build a complete representation of a scene.
+data suggest that the PPA is not a ally homogeneous area buconsists of
+submodules that ``activate selectively to scenes'' and ``cooperate to build a
+complete representation of a scene'' \citep{baldassano2013differential}.
+
+%
+Our data suggest that PPA might contain identifiable subregions, but these
+subregions should not be considered as completely independent modules.
+%
+Both subregions activate selectively to scenes, and the parahippocampal region
+(at least in macaques) is densely self-connected (Suzuki 2009), implying that
+these subregions cooperate to build a complete representation of a scene.
 %
@@
 stimuli does not necessarily imply that this region does not use object
-information\citep{baldassano2013differential}.
+information \citep{baldassano2013differential}.
 %
@@
 \citep{baldassano2013differential}.
+
+%
+\citep{baldassano2016two}: We propose that scene processing is fundamentally
+divided into two collaborating but distinct networks
+%
+One is focused on the visual features of a scene image. The other is related to
+contextual retrieval and navigation.
+%
+Under this framework, scene perception is less the function of a unified set of
+distributed neural machinery and more of ``an ongoing dialogue between the
+material and symbolic aspects of the past and the continuously unfolding
+present'' (Baker, 2012, in The Word Hoard).
+
+%
+\citep{baldassano2016two} with respect to natural scene perception: one can
+imagine at least two separable functions:
+%
+1) processing the specific visual features present in the current glance of a
+scene,
+%
+2) and connecting that to the stable, high-level knowledge of where the place
+exists in the world, what has happened here in the past, and what possible
+actions we could take here in the future \citep{baldassano2016two}.
+%
+For most cognitive and physical tasks we undertake in real-world places, the
+specific visual attributes we perceive are just a means to this end, of
+recalling and updating information about the physical environment; ``the
+essential feature of a landmark is not its design, but the place it holds in a
+city’s memory'' [Muschamp, 2006, in New York Times]\citep{baldassano2016two}.
 
@@
 %
-\citep{baldassano2016two}: We propose that scene processing is fundamentally
-divided into two collaborating but distinct networks
-%
-One is focused on the visual features of a scene image. The other is related to
-contextual retrieval and navigation.
-%
-Under this framework, scene perception is less the function of a unified set of
-distributed neural machinery and more of ``an ongoing dialogue between the
-material and symbolic aspects of the past and the continuously unfolding
-present'' (Baker, 2012, in The Word Hoard).
-
-%
-\citep{baldassano2016two} with respect to natural scene perception: one can
-imagine at least two separable functions:
-%
-1) processing the specific visual features present in the current glance of a
-scene,
-%
-2) and connecting that to the stable, high-level knowledge of where the place
-exists in the world, what has happened here in the past, and what possible
-actions we could take here in the future \citep{baldassano2016two}.
-%
-For most cognitive and physical tasks we undertake in real-world places, the
-specific visual attributes we perceive are just a means to this end, of
-recalling and updating information about the physical environment; ``the
-essential feature of a landmark is not its design, but the place it holds in a
-city’s memory'' [Muschamp, 2006, in New York Times]\citep{baldassano2016two}.
-
-%
 Activation maxima associated with visuospatial and mnemonic
@@
 retrosplenial, and perirhinal memory systems (see Ranganath and Ritchey, 2012,
-for an review)\citep{baumann2016functional}.
-
-\subsubsection{RSC (in both stimuli)}
+
+\subsubsection{retrosplenial cortex (RSC)}
 
@@
 contrast of both contrasts in the retrosplenial cortex (RSC).
-
 % location functionally defined
-In context of a scene-responsive region, the RSC is functionally defined and not
+As a scene-responsive region, the RSC is functionally defined and not
 necessarily identical to the anatomically defined retrosplenial cortex [26]
+\citep{epstein2008parahippocampal}.
+% function
+The RSC is strongly active during scene viewing, scene imagery [25] and mental
+imagination of navigation through familiar environments [8]
 \citep{epstein2008parahippocampal}.
@@
 \citep{epstein2008parahippocampal}.
-% function
-RSC is strongly active during scene viewing, scene imagery [25] and mental
-imagination of navigation through familiar environments [8]
-\citep{epstein2008parahippocampal}.
-
-% Aminoff 2013
-Processing of strong, long-term, contextual associations elicits activity within
-the PHC, as well as the RSC (which includes regions of the retrosplenial cortex,
-extending into the posterior cingulate cortex, and the precuneus), the medial
-prefrontal cortex (MPFC), and the transverse occipital sulcus (TOS) (Figure 2)
-[2,3,59–67] \citep{aminoff2013role}.
 
 % discussion of what the RSC does
-\todo[inline]{interpretation: cf.\citep{vann2009what} and paper that reference
-her}
+interpretation cf.: \citep{vann2009what, chrastil2018heterogeneity,
+silson2019posterior}
 % conclusion
-\todo[inline]{conclusion?}
 
@@
 %
-\citep{baldassano2016two} functional difference pPPA vs. OPA: functional
-distinction between pPPA and OPA is currently unclear. Previous work has
-speculated about the purpose of the apparent ventral and dorsal ``duplication''
-of regions sensitive to large landmarks, proposing that it may be related to
-different output goals (e.g., action planning in OPA, object recognition in
-pPPA)[Konkle and Caramazza, 2013], or to different input connections (e.g.,
-lower visual field processing in OPA, upper visual field processing in
-pPPA)[Kravitz et al., 2013; Silson et al., 2015]. OPA and pPPA may also use
-information from different visual eccentricities: OPA processing less
+\citep{baldassano2016two} regarding functional difference pPPA vs. OPA:
+functional distinction between pPPA and OPA is currently unclear. Previous work
+has speculated about the purpose of the apparent ventral and dorsal
+``duplication'' of regions sensitive to large landmarks, proposing that it may
+be related to different output goals (e.g., action planning in OPA, object
+recognition in pPPA)[Konkle and Caramazza, 2013], or to different input
+connections (e.g., lower visual field processing in OPA, upper visual field
+processing in pPPA)[Kravitz et al., 2013; Silson et al., 2015]. OPA and pPPA may
+also use information from different visual eccentricities: OPA processing less
 peripheral, relatively high-resolution environmental features. pPPA processing
 more peripheral, large-scale geometry, and context [Baldassano et al.,
-2016a]\citep{baldassano2016two}.
+2016a] \citep{baldassano2016two}.
 

### 2020-11-23 paper/main.tex
clean putative functions of PPA subregions

@@
 The pPPA is functionally more responsive than aPPA to low-level features of
-(abstract) objects or scenes \citep{baldassano2013differential,
+scenes or (abstract) objects \citep{baldassano2013differential,
 nasr2014thinking, rajimehr2011parahippocampal}.
@@
 The aPPA is functionally more responsive than pPPA to high-level features of
-objects (e.g. spatial contextual associations
-\citep{aminoff2007parahippocampal, aminoff2015associative} and scenes (e.g.
-real-word size \citep{park2015parametric}; a scene's abstract identity/category
-\citep{marchette2015outside, watson2016patterns}).
+scenes (e.g. real-word size \citep{park2015parametric}; a scene's abstract
+identity/category \citep{marchette2015outside, watson2016patterns}) and objects
+(e.g. spatial contextual associations \citep{aminoff2007parahippocampal,
+aminoff2013role}).
+
+\todo[inline]{the mother of total confusion: in Aminoff (2007, 2013): anterior
+    PPA = spatial associations, region anterior to PPA = non-spatial
+    associations; but in Aminoff (2015): posterior PPA = spatial associations
+    and anterior PPA = non-spatial associations; hence: complete bullshit;
+ignore Aminoff (2015) due to various reasons}
 
@@
 
-data suggest that the PPA is not a ally homogeneous area buconsists of
-submodules that ``activate selectively to scenes'' and ``cooperate to build a
+The PPA is not a functionally homogeneous area but consists of
+subregions that ``activate selectively to scenes'' and ``cooperate to build a
 complete representation of a scene'' \citep{baldassano2013differential}.
-
 %
-Our data suggest that PPA might contain identifiable subregions, but these
-subregions should not be considered as completely independent modules.
-%
-Both subregions activate selectively to scenes, and the parahippocampal region
-(at least in macaques) is densely self-connected (Suzuki 2009), implying that
-these subregions cooperate to build a complete representation of a scene.
-%
-Their distinct connectivity properties, however, do suggest that each may be
+Their distinct connectivity properties do suggest that each may be
 involved in specific aspects of visual and cognitive processing involved in the
-overarching goal of scene understanding.
+overarching goal of scene understanding \citep{baldassano2013differential}.
 
@@
 stimuli does not necessarily imply that this region does not use object
-information \citep{baldassano2013differential}.
+information \citep{baldassano2013differential}. Previous work has shown that PPA
+responds to objects that have spatial associations [Aminoff et al. 2007], are
+space-defining [Mullally and Maguire 2011], and are navigationally-relevant
+[Janzen and Van Turennout 2004]. These types of responses require spatial memory
+and cannot be based purely on visual features like object shape.
+\citep{baldassano2013differential}.
+
 %
-Previous work has shown that PPA responds to objects that have spatial
-associations [Aminoff et al. 2007], are space-defining [Mullally and Maguire
-2011], and are navigationally-relevant [Janzen and Van Turennout 2004].
-%
-These types of responses require spatial memory and cannot be based purely on
-visual features like object shape. If anterior PPA is involved in processing
-spatial context, then space-defining or navigationally-relevant objects could
-activate anterior PPA more strongly than our abstract objects, which were
-unfamiliar and provided no sense of context or orientation.
+[If anterior PPA is involved in processing spatial context, then space-defining
+or navigationally-relevant objects could activate anterior PPA more strongly
+than our abstract objects, which were unfamiliar and provided no sense of
+context or orientation.
 %
@@
 object-related information is used in this region
-\citep{baldassano2013differential}.
-
-%
-\citep{baldassano2016two}: We propose that scene processing is fundamentally
-divided into two collaborating but distinct networks
-%
-One is focused on the visual features of a scene image. The other is related to
-contextual retrieval and navigation.
-%
-Under this framework, scene perception is less the function of a unified set of
-distributed neural machinery and more of ``an ongoing dialogue between the
-material and symbolic aspects of the past and the continuously unfolding
-present'' (Baker, 2012, in The Word Hoard).
-
-%
-\citep{baldassano2016two} with respect to natural scene perception: one can
-imagine at least two separable functions:
-%
-1) processing the specific visual features present in the current glance of a
-scene,
-%
-2) and connecting that to the stable, high-level knowledge of where the place
-exists in the world, what has happened here in the past, and what possible
-actions we could take here in the future \citep{baldassano2016two}.
-%
-For most cognitive and physical tasks we undertake in real-world places, the
-specific visual attributes we perceive are just a means to this end, of
-recalling and updating information about the physical environment; ``the
-essential feature of a landmark is not its design, but the place it holds in a
-city’s memory'' [Muschamp, 2006, in New York Times]\citep{baldassano2016two}.
-
-\paragraph{contextual associations}
-
-%
-The PCH has been implicated in the integration and retrieval of contextual
-associations in memory [Aminoff et al., 2013; Bar and Aminoff, 2003; Bar et al.,
-2008a, 2008b].
-%
-According to this view, activity in PHC reflects modality-independent retrieval
-of contextual information from memory (contextual associations: relations
-between objects and conditions that describe, represent, and bring meaning to an
-environment; such as which objects typically occur in a given scene and where
-they are likely to be located relative to one another; [Aminoff et al., 2013])
-\citep{baumann2016functional}.
-
-Results: aPHC is more active during contextual judgments regardless of stimulus
-category (scenes vs objects) or modality (word vs picture)
-\citep{baumann2016functional}.
-%
-The left aPHC was active in all contextual judgment task conditions. This
-suggests a functional segregation, with posterior sections of the PHC supporting
-visuospatial processing of scenes and anterior sections of the left PHC involved
-in contextual associative processing\citep{baumann2016functional}.
-
-%
-Activation maxima associated with visuospatial and mnemonic
-processes were spatially segregated, providing support for the existence of
-functionally distinct subregions along the PHC longitudinal axis and suggesting
-that the PHC serves as a functional interface between perception and memory
-systems\citep{baumann2016functional}.
-
-Results suggests a predominantly perceptual role for the pPHC and a mnemonic
-role for the anterior parahippocampal cortex (Note: the anterior parahippocampal
-cortex should not be confused with the anterior portion of the parahippocampal
-gyrus, which includes the perirhinal cortex; Ranganath and Ritchey,
-2012.)\citep{baumann2016functional}.
-
-We suggest that the aPHC encodes incoming information in an amodal format and
-acts as an interface with other memory regions, including the hippocampal,
-retrosplenial, and perirhinal memory systems (see Ranganath and Ritchey, 2012,
+\citep{baldassano2013differential}.]
 
@@
 
-\citep{aminoff2015associative}: Three regions of the cortex that have bee
-identified as responding selectively to visual scenes: the PHC/lingual region
-(commonly referred to as the “parahippocampal place area”) [8–12]),
-retrosplenial complex (including the retrosplenial cortex and portions of the
-posterior cingulate and precuneus, RSC) [13–15]), and a lateral occipital region
-termed the “occipital place area” (OPA; also referred to as the transverse
-occipital sulcus, TOS) [16–18]).
-%
-All three of these brain regions are functionally defined by comparing the BOLD
-signals–as measured by fMRI–arising from viewing scenes to those arising from
-viewing objects or faces (e.g., [19])\citep{aminoff2015associative}.
-
 % baldassano2016two
-RSC: appears to be most directly involved in orienting the viewer to the
-structure of the environment (both within and beyond the borders of the
-presented image) for the purpose of navigational planning; it encodes both
-absolute location and facing direction [Vass and Epstein, 2013; Epstein and
-Vass, 2014; Marchette et al., 2014], integrates across views presented in a
-panoramic sequence [Park and Chun, 2009], and shows strong familiarity effects
-[Epstein et al., 2007a,b]\citep{baldassano2016two}.
-
-% contrasting the two networks
-Several previous studies have already shown differential effects within these
-two networks. Contrasting the functional connectivity patterns of RSC versus OPA
-or lateral occipital cortex (LOC; Nasr et al., 2013) or anterior versus
-posterior PPA [Baldassano et al., 2013] show a division between the two
-networks, consistent with our results. Contrasting scene-specific activity with
-general (image or word) memory retrieval showed an anterior versus posterior
-distinction in PPA and cIPL/OPA, with only more anterior regions (aPPA and cIPL,
-along with RSC) responding to content-independent retrieval tasks [Johnson and
-Rugg, 2007; Fairhall et al., 2014]\citep{baldassano2016two}.
+\citep{baldassano2016two}: RSC appears to be most directly
+involved in orienting the viewer to the structure of the environment (both
+within and beyond the borders of the presented image) for the purpose of
+navigational planning; it encodes both absolute location and facing direction
+[Vass and Epstein, 2013; Epstein and Vass, 2014; Marchette et al., 2014],
+integrates across views presented in a panoramic sequence [Park and Chun, 2009],
+and shows strong familiarity effects [Epstein et al., 2007a,b]
+\citep{baldassano2016two}.
 
@@
 %
-\citep{baldassano2016two} regarding functional difference pPPA vs. OPA:
+\citep{baldassano2016two} regarding functional difference pPPA vs. OPA: The
 functional distinction between pPPA and OPA is currently unclear. Previous work
@@
 peripheral, relatively high-resolution environmental features. pPPA processing
-more peripheral, large-scale geometry, and context [Baldassano et al.,
-2016a] \citep{baldassano2016two}.
+more peripheral, large-scale geometry, and context [Baldassano et al., 2016a]
+\citep{baldassano2016two}.
 

### 2020-12-02 paper/main.tex
Prep for sharing with Simon
add Simons comments

@@
 \usepackage{fancyhdr}
-% \usepackage[disable]{todonotes}
-\usepackage{todonotes}
+\usepackage[disable]{todonotes}
+% \usepackage{todonotes}
 \usepackage{units}
@@
 	colorlinks=true,
-	urlcolor=blue,
-	linkcolor=green
+	citecolor=black,
+  urlcolor=black,
+	linkcolor=black
 ]{hyperref}
@@
 Germany {*}corresponding author: Christian Olaf Häusler (der.haeusler@gmx.net)
+
+\todo[inline]{Simon als Autor adden}
+
+\todo[inline]{zweiten Satz: PPA ist die Region im ventral stream, die mehr auf
+    static landscapes denn Gesichter reagiert. Ansonsten klingt es so, als ob
+    PPA unabhängig von der Funktion definiert ist; dritte Satz ist irgendwie
+    falsch konstruiert (narrative... audiovisual movie); ``significant increased
+    activation in PPA'': PPA a priori durch localizer definiert? Oder ist der
+    increase die Definition der PPA; Beschreibungen sind auf der einen seite
+    sehr detailliert, aber der Vergleich mit dem localizer wird nicht explizit
+erwähnt; Clou der ganzen Geschichte ist doch: Man braucht keinen separaten
+Localizer, oder? Das kommt bisher nur bedingt rüber}
 
@@
 
+\todo[inline]{Den Start finde ich etwas komisch. "Cognitive neuroscientists use"
+klingt sehr nach einer aktiven distanzierung}
+
+\todo[inline]{Ich würde am Start definitiv kurz in die funktionelle
+    Spezialisierung des visuellen Systems und die Organisation des ventralen
+Streams einführen. Die kurze Darstellung der PPA ist dann aber gut}
+
+\todo[inline]{Der Schwung zu Sprache (wobei speech auch erst am Satzende kommt)
+ist zu hart, da kommt man als Leser nicht gut mit}
+
+\todo[inline]{ie "Kritik" an bisherigen PPA Studien finde ich insgesamt OK,
+wobei nicht ganz klar wird, was genau das schlechte an "conceptualized" ist. Das
+löst sich erst am Ende mit der "ecological validity" einigermaßen auf}
+
+\todo[inline]{Aus meiner Sicht könnte die Motivation für die aktuelle Studie
+    noch stärker werden. Du nennst zwar einige Schwächen, aber dann geht es sehr
+    unvermittelt in Details der Studie. Meine Präferenz ist es eher, nochmal
+    ganz klar zu sagen, warum es jetzt diese Studie braucht und was sie zum Feld
+beitragen soll}
+
+\todo[inline]{Damit zusammen hängend: Das Konzept der aktuellen Arbeit (place
+information aus einem ongoing context zu verwenden) und warum das die Probleme
+löst, würde ich auch noch etwas klarer darstellen. Du setzt zu viel voraus}
+
+\todo[inline]{Das "then we analyzed publically available data" ist sehr
+verwirrend, da es doch davor auch um StudyForest geht}
+
 \section{Introduction}
+
+\todo[inline]{describe ``localize / isolate'' in other words}
 
@@
 
+\todo[inline]{as mit dem "already used by" verwirrt eher}
+
+\todo[inline]{Der StudyForest datansatz ist gut und knapp beschrieben. Die
+Stimuli im VIS datensatz brauchen aber glaube ich etwas mehr erklärung}
+
+\todo[inline]{Ich würde mal die Frage antizipieren, wie gut passen die
+Annotationen zu den VIS Stimuli. Und die müsste meiner Meinung nach doppelt
+beantwortet werden. a) Durch genauere Beschreibung von VIS, b) durch genauere
+Ausführungen, wie welche Annotation dazu passt}
+
 % intro
@@
 \subsection{Stimuli}
+
+\todo[inline]{merge Stimuli and ``Procedure'' (s. below)}
+
 % AO & AV stimulus name & references
@@
 \subsection{Naturalistic stimuli annotation}
+
+\todo[inline]{Bei AV habt ihr cuts und locations benutzt? Cuts können doch auch
+zwischen zwei Gesichtern sein?!?}
+
 % todo stimuli were not designed for research purposes
@@
 
+\todo[inline]{Table 2 ist relativ kryptisch bzw für jemanden, der sich zum
+    ersten Mal damit auseinander setzt kaum zu verstehen. Auch ist der Bezug zum
+GLM unklar, d.h., was davon wird verwendet und was verbirgt sich dahinter}
+
+\todo[inline]{Ich merke das mal hier an: Die Tables stehen an ganz merkwürdigen
+Positionen, das passt nicht zum Text und verwirrt ungemein}
+
 % table for descriptive nouns: categories, rules, examples counts
@@
 \subsection{Procedure}
+
+\todo[inline]{Procedure (2.4.) ist nicht zwingend nötig bzw nicht als
+separater Abschnitt}
+
 % questionnaire
@@
 \subsection{fMRI data acquisition}
+
+\todo[inline]{shorten this subsection a lot}
 
@@
 
+\todo[inline]{Ich würde abschnitt 2.8 teilen (in die regressors, die dann mit
+der beschreibung der annotation kombinieren, und die eigentliche statistik)}
+
+\todo[inline]{Ich weiss nicht, ob es die etwas wild zwischendrin stehenden
+    tables waren, die oft komplizierten Beschreibungen, die Länge des
+    Abschnittes, oder alles zusammen, aber ich habe mich mit 2.8 extrem schwer
+    getan. Bitte lass den Reviewer nicht mit dem selben Gefühl rausgehen. Gut
+strukturiert, einfach und klar ist immer vom Vorteil}
+
 Similarly to the reviewed studies that employed simplified stimuli, we conducted
@@
 \todo[inline]{better speak of conditions than categories?}
+
+\todo[inline]{Das mit den "five additional categories" habe ich nicht
+    verstanden. Überhaupt finde ich die ganze Beschreibung relativ schwer zu
+durchdrungen, und ich glaube damit werde ich nicht alleine sein.}
+
+\todo[inline]{Gab es ein separates null-event für jeden zeitraum zwischen zwei
+annotierten events oder war das ein regressor der immer wieder kam?}
+
+\todo[inline]{Ich würde vorschlagen, dass Du Dich auf die Regressoren / Events
+    konzentrierst, die hier wichtig sind, um die Komplexität zu reduzieren. Die
+    aber dafür besser erklären (was heißt "unfamilar perspective"? Ab wann ist
+ein setting "familiar"?}
 
@@
 % nuisance regressors
+\todo[inline]{"Continuous bins lasting 40ms" ?!?}
+%
 Lastly, we used continuous bins of information about two auditory features
@@
 \begin{table*}[t]
-    \caption{Overview of events to build the 14 regressors for the analysis of the audio-only (AV) stimulus.
-\texttt{fg\_av\_ger\_lr} (left-right difference in [+++???+++] of
-consecutive movie frames).\texttt{fg\_av\_ger\_pd} (perceptual differences of
-consecutive frames).
-\texttt{fg\_av\_ger\_ud} (up-down difference in [+++???+++] of consecutive movie frames).
-\texttt{fg\_av\_ger\_lrdiff} (left-right volume difference) and \texttt{fg\_av\_ger\_rms} (root mean square volume) represent one event for every movie frame (\unit[40]{ms}).
+    \caption{Overview of events to build the 14 regressors for the analysis of
+        the audio-visual (AV) stimulus.
+        \texttt{fg\_av\_ger\_pd} (perceptual differences of consecutive frames),
+        \texttt{fg\_av\_ger\_ml} (mean luminance of a frame),
+        \texttt{fg\_av\_ger\_lr} (difference in mean luminance of left and
+        right half),
+        \texttt{fg\_av\_ger\_ud} (difference in mean luminance of upper and
+        lower half),
+        \texttt{fg\_av\_ger\_lrdiff} (left-right volume difference), and
+        \texttt{fg\_av\_ger\_rms} (root mean square volume) represent one event
+        for every movie frame (\unit[40]{ms}).
         For description of the two event categories of the audio-description's
@@
 se\_old & control for AO narrator & \aoSeoldAll & \aoSeoldI & \aoSeoldII & \aoSeoldIII & \aoSeoldIV & \aoSeoldV & \aoSeoldVI & \aoSeoldVII & \aoSeoldVIII \tabularnewline
-fg\_av\_ger\_lr & XYZ & \avFgavgerlrAll & \avFgavgerlrI & \avFgavgerlrII & \avFgavgerlrIII & \avFgavgerlrIV & \avFgavgerlrV & \avFgavgerlrVI & \avFgavgerlrVII & \avFgavgerlrVIII \tabularnewline
+fg\_av\_ger\_lr & left-right luminance difference & \avFgavgerlrAll & \avFgavgerlrI & \avFgavgerlrII & \avFgavgerlrIII & \avFgavgerlrIV & \avFgavgerlrV & \avFgavgerlrVI & \avFgavgerlrVII & \avFgavgerlrVIII \tabularnewline
 fg\_av\_ger\_lrdiff & left-right volume difference & \avFgavgerlrdiffAll & \avFgavgerlrdiffI & \avFgavgerlrdiffII & \avFgavgerlrdiffIII & \avFgavgerlrdiffIV & \avFgavgerlrdiffV & \avFgavgerlrdiffVI & \avFgavgerlrdiffVII & \avFgavgerlrdiffVIII \tabularnewline
-fg\_av\_ger\_ml & +++++???+++++ & \avFgavgermlAll & \avFgavgermlI & \avFgavgermlII & \avFgavgermlIII & \avFgavgermlIV & \avFgavgermlV & \avFgavgermlVI & \avFgavgermlVII & \avFgavgermlVIII \tabularnewline
-fg\_av\_ger\_pd & +++++???+++++ & \avFgavgerpdAll & \avFgavgerpdI & \avFgavgerpdII & \avFgavgerpdIII & \avFgavgerpdIV & \avFgavgerpdV & \avFgavgerpdVI & \avFgavgerpdVII & \avFgavgerpdVIII \tabularnewline
+fg\_av\_ger\_ml & mean luminance & \avFgavgermlAll & \avFgavgermlI & \avFgavgermlII & \avFgavgermlIII & \avFgavgermlIV & \avFgavgermlV & \avFgavgermlVI & \avFgavgermlVII & \avFgavgermlVIII \tabularnewline
+fg\_av\_ger\_pd & perceptual difference & \avFgavgerpdAll & \avFgavgerpdI & \avFgavgerpdII & \avFgavgerpdIII & \avFgavgerpdIV & \avFgavgerpdV & \avFgavgerpdVI & \avFgavgerpdVII & \avFgavgerpdVIII \tabularnewline
 fg\_av\_ger\_rms & root mean square (loudness) & \avFgavgerrmsAll & \avFgavgerrmsI & \avFgavgerrmsII & \avFgavgerrmsIII & \avFgavgerrmsIV & \avFgavgerrmsV & \avFgavgerrmsVI & \avFgavgerrmsVII & \avFgavgerrmsVIII \tabularnewline
-fg\_av\_ger\_ud & +++++???+++++ & \avFgavgerudAll & \avFgavgerudI & \avFgavgerudII & \avFgavgerudIII & \avFgavgerudIV & \avFgavgerudV & \avFgavgerudVI & \avFgavgerudVII & \avFgavgerudVIII \tabularnewline
+fg\_av\_ger\_ud & upper-lower luminance difference & \avFgavgerudAll & \avFgavgerudI & \avFgavgerudII & \avFgavgerudIII & \avFgavgerudIV & \avFgavgerudV & \avFgavgerudVI & \avFgavgerudVII & \avFgavgerudVIII \tabularnewline
 \end{tabular}
@@
 
+%
+\todo[inline]{Die Abkürzungen in Figure 1: Da steigt keiner hinter}
+
+\todo[inline]{Habe jetzt lange darüber gebrütet: Es gibt also kaum eine
+Korrelation zwischen AO und AV?; Also, außer bei fg\_av\_ger\_lr\_diff (wobei da keiner weiss, was das bedeutet)}
 % reference to figure ``correlation of regressors''
@@
         description) and audio-visual movie (red; see Table
-        \ref{tab:av-events}).}
+        \ref{tab:av-events}) rounded to the nearest tenth.
+        The correlation
+        between the two stimuli's root mean square loudness and between their
+        left-right difference in loudness yielded the highest correlation
+        values (\texttt{fg\_ad\_rms} and \texttt{fg\_av\_ger\_rms}, r=.7635
+        \texttt{fg\_ad\_lrdiff} and \texttt{fg\_av\_ger\_lrdiff}, r=.7749).}
     \label{fig:reg-corr}
@@
 
+%
+ \todo[inline]{Das mit den 8 kontrasten und 5 kontrasten habe ich nicht intuitiv
+ durchblickt. Was wurde da gegen was kontrastiert?}
 % we have fixed stimuli
@@
 (c) the narrator is often lacking behind a short dialogue or a change of the
-soundscape that already cue a change of settings.  cuts but in AO stimulus
+soundscape that already cue a change of settings.
 % conclusion
@@
 
+\todo[inline]{give reference to Neurovault.com}
+
+\todo[inline]{- Bitte sauber differenzieren zwischen "Lokalisation der PPA" und
+    "Antwortverhalten einer vorab definierten PPA". Ich habe den Eindruck, dass
+Du oft das erste machst es aber als das zweite beschreibst}
+
+\todo[inline]{Der vergleich mit VIS kommt bestenfalls en passant, VIS selber
+wird gar nicht berichtet wäre aber wichtig zum andocken an die Literatur}
+
+\todo[inline]{Es ist zwar hier nicht der Fokus, aber ich würde sehr darauf
+wetten, dass Reviewer danach fragen: Wie sieht es im vergleich dazu mit Faces
+aus?}
+
+\todo[inline]{Figure 2 und 3: ich würde da wahrscheinlich weiter rein zoomen um
+genauer den visuellen Kortex zu zeigen. Vor allem aber muss man sagen, dass bei
+FFA/PPA etc eigentlich flatmaps bzw inflated brains, also surface-darstellungen
+standard sind}
+
+\todo[inline]{Die Anzahl der Überlappungen in Figure 3 ist schwer abzulesen,
+hier lieber eine andere Farbskala (spectral sequence?) nutzen}
+
+\todo[inline]{Das mit den cuts to new vs familar setting wird irgendwie nie so
+richtig in den PPA kontext eingeordnet. Bzw. ich glaube ich bin verwirrt. Warum
+ist das der hauptkontrast und nicht das viel näher liegende places vs faces?}
+
+\todo[inline]{Noch etwas, das wahrscheinlich gefragt wird: Wie sehen die
+Antworten innerhalb der "klassisch definierten" PPA für die verschiedenen
+regressoren bzw.  kategorien derselben (zumindest aber places vs faces) aus?}
+
+\todo[inline]{Wenn ich mir Figure 4 anschaue, würde ich sagen, dass AO besser
+die VIS-PPA "trifft" als AV. Das ist zumindest sehr überraschend, oder?}
+
+\todo[inline]{Figure 5 ist irre kompliziert. Welche Areale habt ihr als masks
+genommen, FFA ist ja kartiert (Julia caspers)}
+
 % study goal
@@
 
+\todo[inline]{which contrast yielded NO clusters?}
+
 \todo[inline]{I consider tables of significant clusters in PPA for all contrasts
@@
 \subsection{individual results}
+
+\todo[inline]{say why slice -11 was chosen}
 
@@
 \begin{figure*} \centering
-    \includegraphics[width=\linewidth]{figures/subjs_bland-altman.png}
+    \includegraphics[width=.8\linewidth]{figures/subjs_bland-altman.png}
     \caption{Bland-Altman-Plots for individual subjects. The x-axis depicts the
@@
 \section{Discussion}
+
+\todo[inline]{Ich finde die result-synopsis noch nicht optimal. Vielleicht gehe
+ich aber auch mit der falschen Perspektive ran? Für mich würde der Vergleich
+"localizer vs naturalistic" im vordergrund stehen, AO vs AV dann eine sehr
+spannende aber logisch nachgeschaltete Frage sein.}
+
+\todo[inline]{Bei ergebnissen und Diskussionen zu Stability fehlt mir irgendwie
+immer der Kontext, wie sich die kontraste denn unterschieden haben und welche
+davon z.B. im Ergebnis wo von den anderen abgewichen haben. Das würde ja
+wichtige Hinweise geben}
+
+\todo[inline]{VIS vs AV vs AO: Wer liefert was über die PPA. Dieser Vergleich
+bzw. die Diskussion über gemeinsamkeiten und unterschiede fehlt mir etwas}
+
+\todo[inline]{RSC etc: Irgendwie waren die bis zu diskussion eher ein
+afterthought. Daher etwas überraschend, vielleicht in Einleitung und Results
+schon mehr bringen}
 
@@
 
-\subsection{stability of contrasts}
+\subsection{robustness of contrasts}
 
@@
 \subsection{shortcomings in general}
+
+\todo[inline]{Würde nicht so sehr auf Shortcomings eingehen}
 
@@
 
+\todo[inline]{AV: field size decreases later in the movie; this is a confound
+based on cinematography => the stimulus changes over time}
+
 \todo[inline]{imo opening the pandora's box of the AV shortcomings especially at
@@
 
+\todo[inline]{Conclusions aber irgendwie frage ich mich das relativ durchgehen):
+Warum ist der Fokus so sehr auf Audiobook / AO, während AV doch eigentlich more
+natural and engaging ist?}
+
 % natural stimulation
@@
 
-% conclusion: AO and AV stability
+% conclusion: AO and AV robustness
 In summary, our results across add further evidence that model-driven analyses

### 2020-12-03 paper/main.tex
revision of intro and stimuli & procedure

@@
 
-\author{Christian~O.~Häusler\textsuperscript{1,2{*}}, Michael
-Hanke\textsuperscript{1,2}}
+\author{
+    Christian~O.~Häusler\textsuperscript{1,2{*}},
+    Simon B. Eickhoff\textsuperscript{1,2},
+    Michael Hanke\textsuperscript{1,2}}
 % https://www.nature.com/sdata/publish/for-authors#other-formats
@@
 
-\todo[inline]{Simon als Autor adden}
-
-\todo[inline]{zweiten Satz: PPA ist die Region im ventral stream, die mehr auf
-    static landscapes denn Gesichter reagiert. Ansonsten klingt es so, als ob
-    PPA unabhängig von der Funktion definiert ist; dritte Satz ist irgendwie
-    falsch konstruiert (narrative... audiovisual movie); ``significant increased
-    activation in PPA'': PPA a priori durch localizer definiert? Oder ist der
-    increase die Definition der PPA; Beschreibungen sind auf der einen seite
-    sehr detailliert, aber der Vergleich mit dem localizer wird nicht explizit
-erwähnt; Clou der ganzen Geschichte ist doch: Man braucht keinen separaten
-Localizer, oder? Das kommt bisher nur bedingt rüber}
+\todo[inline]{Clou der ganzen Geschichte ist doch: Man braucht keinen separaten
+Localizer, oder? Das kommt bisher nur bedingt rüber; COH: well, if you also want
+to have the ``visual part'' of the PPA then you need a visual paradigm}
 
@@
 % PPA
-The ``parahippocampal place area'' is classically considered to be a higher
-visual area as increased hemodynamic activity in the PPA correlates/is
-correlated with the perception of static pictures of landscapes (or landmarks)
-compared to pictures of faces or objects.
+A region in the human hippocampal cortex termed ``parahippocampal place area''
+is classically considered to be a higher visual area as increased hemodynamic
+activity in the PPA correlates with the perception of static pictures of
+landscapes compared to pictures of faces or objects.
 % What we do
 In the current study, we exploratorily tested if spatial information embedded in
-the audio-description of a Hollywood movie (i.e. the movie's soundtrack with an
-additional narrator) the audio-visual movie can be used to isolate the PPA on a
-group average level and in individual subjects.
+a Hollywood movie and its audio-description of (i.e. the movie's soundtrack with
+an additional narrator) correlates with increased hemodynamic activity in the
+PPA.
 %
@@
 % compare to visual localizer experiment group results
-On a group average level, our results show significantly increased activation in
-the PPA but restricted to its anterior part [as well as in the retrosplenial and
-lateral occipital cortex] of both hemispheres.
+On a group average level, results of our whole brain analyses show
+significantly increased activation restricted to the anterior part of the PPA
+that was defined using the visual localizer [as well as in the retrosplenial
+and lateral occipital cortex] of both hemispheres.
 % individual results
@@
 
-\todo[inline]{Den Start finde ich etwas komisch. "Cognitive neuroscientists use"
-klingt sehr nach einer aktiven distanzierung}
-
-\todo[inline]{Ich würde am Start definitiv kurz in die funktionelle
-    Spezialisierung des visuellen Systems und die Organisation des ventralen
-Streams einführen. Die kurze Darstellung der PPA ist dann aber gut}
-
-\todo[inline]{Der Schwung zu Sprache (wobei speech auch erst am Satzende kommt)
-ist zu hart, da kommt man als Leser nicht gut mit}
-
-\todo[inline]{ie "Kritik" an bisherigen PPA Studien finde ich insgesamt OK,
-wobei nicht ganz klar wird, was genau das schlechte an "conceptualized" ist. Das
-löst sich erst am Ende mit der "ecological validity" einigermaßen auf}
-
-\todo[inline]{Aus meiner Sicht könnte die Motivation für die aktuelle Studie
-    noch stärker werden. Du nennst zwar einige Schwächen, aber dann geht es sehr
-    unvermittelt in Details der Studie. Meine Präferenz ist es eher, nochmal
-    ganz klar zu sagen, warum es jetzt diese Studie braucht und was sie zum Feld
-beitragen soll}
-
-\todo[inline]{Damit zusammen hängend: Das Konzept der aktuellen Arbeit (place
-information aus einem ongoing context zu verwenden) und warum das die Probleme
-löst, würde ich auch noch etwas klarer darstellen. Du setzt zu viel voraus}
-
-\todo[inline]{Das "then we analyzed publically available data" ist sehr
-verwirrend, da es doch davor auch um StudyForest geht}
-
 \section{Introduction}
@@
 Humans can perceive and make sense of their daily environment casually and
-seemingly without any effort. Cognitive neuroscientists use brain imaging
-techniques to map perceptual and cognitive processes (e.g. seeing and
-recognizing faces; \citep{kanwisher1997ffa}) to functional brain areas or
-networks.
-% What is the PPA?
-A classic example of a higher-level visual area is the ``parahippocampal place
-area'' (PPA) \citep{epstein1998ppa, epstein1999parahippocampal}.
+seemingly without any effort.
+%
+Studies in the field of neuropsychology and neuroimaging (e.g.
+\citep{penfield1950cerebral, fox1984noninvasive}) have shown that different
+parts of the brain are specialized for different cognitive and perceptual
+functions.
+%%%%%%%%%%%%%%%%%%%%%% trenne diese Sätze %%%%%%%%%%%%%%5
+The occipital cortex is considered to be primarily involved in the early stages
+of visual perception and giving rise to two distinct pathways of processing
+different kind of visual information:
+% dorsal vs ventral pathway
+a dorsal pathway that leads into the parietal lob (the ``where pathway''), and a
+ventral pathway that leads into into the temporal lobe (the ``what pathway'')
+\citep{goodale1992separat, mishkin1982contribution}.
+%
+A classic example of a higher-level visual area in the ventral pathway is the
+``parahippocampal place area'' (PPA) \citep{epstein1998ppa,
+epstein1999parahippocampal}.
 % anatomical location != functional location
@@
 regions of the fusiform gyrus and anterior lingual gyrus
-\citep{epstein2008parahippocampal}, and thus not anatomically but functionally
-defined:
+\citep{epstein2008parahippocampal}, and thus is not anatomically but
+functionally defined:
 % neural correlate of scene perception
@@
 perception clearer. What do you think?}
+
+\todo[inline]{Der Schwung zu Sprache (wobei speech auch erst am Satzende kommt)
+ist zu hart, da kommt man als Leser nicht gut mit}
+
 % literature review overview 1: imagination & haptic exploration
@@
 landscapes \citep{ocraven2000mental} and haptic exploration of scenes
-constructed from LEGO blocks \citep{wolbers2011modality}.
+constructed from LEGO blocks \citep{wolbers2011modality} whereas a study using
+spoken sentences yielded mixed results \citep{aziz2008modulation}.
 % O'Craven: watching pictures
@@
 % three things in common
-Nevertheless, the reviewed studies usually had three things in common.
+The reviewed studies usually had three things in common that come along with
+advantages but also disadvantages:
 % designed stimulus set
-First, they employed a small sets of carefully chosen stimuli. Further, stimuli
-were conceptualized to control confounding variables (e.g. color, luminance,
-size, spatial frequencies, sentence length), a process that is often not
-reported in detail.\todo{they usually just say ``we made the black \& white}
+First, they employed a small sets of carefully chosen and conceptualized
+stimuli.
 % block-design & task
 Second, studies used block-designed paradigms to maximize detection power.
-Further, they usually employed explicit perceptual judgment to keep participants
-paying attention to the stimuli.
-% averaging
-Third, the reviewed studies averaged results across 7-11 subjects to improve
-signal-to-noise ratio (SNR).
-% disadvantages
-Conceptualized stimuli, block-design experiments and the averaging approach have
-their merits but also disadvantages.
-% designed stimulus set
-First, small sets of conceptualized stimuli presented on experimental blocks
-poorly resembles our rich and multidimensional environment that our brains are
-accommodated to [sonkusare2019naturalistic].
-% block-design & task
-Second, study participants can and will become aware about which perceptual
-process is examined in the study by merely being exposed to the experimental
-paradigm.
-% inference: validity is poor
-Thus, small sets of conceptualized stimuli and block-design experiment lack
-external validity \citep{westfall2016fixing} as well as ecological validity
-\citep{hasson2004intersubject}.
-% disadvantage of averaging
-Lastly, averaging data across subjects increases the SNR but does not
+Further, they usually employed an explicit perceptual judgment task.
+%
+Block-design studies that use conceptualized stimuli and a task have the
+advantages of controlling confounding variables (e.g. color, luminance, size,
+spatial frequencies, sentence length), maximizing detection power, and keeping
+participants paying attention to the stimuli.
+% disandvantage of stimuli and block
+Nevertheless, small sets of conceptualized stimuli and block-design paradigms
+lack external and ecological validity \citep{westfall2016fixing,
+hasson2004intersubject} because they poorly resemble how we, free of a[n
+explicit] perceptual task, experience our rich/multidimensional and continuous
+environment that our brains are accommodated to
+\citep{sonkusare2019naturalistic}.
+% Moreover, study participants can and will become aware about which perceptual
+% process is examined in the study by merely being exposed to the experimental
+% paradigm.
+Lastly, the reviewed studies averaged results across 7-11 subjects.
+% averaging pros and cons
+The averaging approch improves signal-to-noise ratio (SNR) but does not
 characterize brain functions at an individual level, a prerequisite for the
@@
 
+\todo[inline]{SE: make motivation of study clearer; gap in research; how it
+    (might) adance(s) the field; make clearer how current study solves the
+    problem; COH: I revised this part, it's clearer at least
+if I read it now}
+
 % Open research question
-In this study, we investigate if increased activation in the PPA correlates with
-incidental ``spatial information'' in the audio-description of the Hollywood
-movie ``Forrest Gump'' (i.e. the audio-only variant of the movie) and, for
-cross-modal comparison, in the (actual) audio-visual movie (itself).
-% we are different
-Since we did not design the given naturalistic stimuli (see
+In this study, we investigate if increased hemodynamic activity in the PPA
+correlates with ``spatial information'' presented under more ecologically valid
+conditions.
+% we are different We used two naturalistic
+Therefore, we annotated perceptual information embedded in two [perceptual]
+rich/multidimensional and continuous naturalistic stimuli (see
 \citep{hamilton2018revolution, hasson2008neurocinematics,
-sonkusare2019naturalistic} for reviews) for optimal localization performance of
-the PPA, we operationalize the perception of landscapes and landmarks (compared
-to e.g. faces and objects) differently from the reviewed studies.
-% operationalization via annotation
-Here, we annotated words spoken by the narrator of the audio-description as well
-as cuts and depicted locations in the movie.
-% public data
-We then analyze publicly available data
-(\href{http://www.studyforrest.org}{studyforrest.org}) from the same subjects
-that listened to the audio-description and watched the movie during fMRI
-scanning.
+sonkusare2019naturalistic} for reviews):
+% audio-description
+a) the audio-description of the Hollywood movie ``Forrest Gump'' (i.e. the
+audio-only variant of the movie), and
+% audio-visual
+b) the [actual] audio-visual movie [itself].
+% studyforrest dataset
+We then analyzed corresponding fMRI data from the same subjects that listened
+to the audio-description and watched the audio-visual movie as part of the
+publicly available studyforrest dataset
+(\href{http://www.studyforrest.org}{studyforrest.org}).
 % first: group level AO
-First, general linear model (GLM) contrasts based on the audio-description's
-annotation are used to test if we could isolate the PPA with an auditory
-stimulus on a group level.
+First on a group average level, general linear model (GLM) contrasts based on
+the audio-description's annotation are used to test if spatial information
+embedded in an exclusively auditory stimulus correlates with increased
+hemodynamic activity in the PPA that we defined using a block-designed visual
+localizer experiment done with the same subjects \citep{sengupta2016extension}.
 % second: group level AV
 Second as conceptual/cross-modal control, we compare results of the
-audio-description to results based on the annotation of the movie.
+audio-description to GLM results based on the annotation of the movie.
 % individual results
-Lastly, focussing on the audio-description, we compare results on the level of
-individual subjects to results of a block-designed visual localizer experiment
-done with the same individuals \citep{sengupta2016extension}.
+Lastly on the level of individual subjects and focussing on the
+audio-description [as a possible substitute for a visual localizer], we compare
+results of the naturalistic stimuli to results of the visual localizer
+\citep{sengupta2016extension}.
 % results
 \todo[inline]{following paragraph will be similar to abstract, intro to
-discussion and conclusion}
-Our results demonstrate that (a), (b), (c).
+discussion and conclusion} Our results demonstrate that (a), (b), (c).
 
@@
 
-\todo[inline]{as mit dem "already used by" verwirrt eher}
-
-\todo[inline]{Der StudyForest datansatz ist gut und knapp beschrieben. Die
-Stimuli im VIS datensatz brauchen aber glaube ich etwas mehr erklärung}
-
-\todo[inline]{Ich würde mal die Frage antizipieren, wie gut passen die
-Annotationen zu den VIS Stimuli. Und die müsste meiner Meinung nach doppelt
-beantwortet werden. a) Durch genauere Beschreibung von VIS, b) durch genauere
-Ausführungen, wie welche Annotation dazu passt}
-
 % intro
-We used data from three publicly available datasets
-(\href{http://www.studyforrest.org}{studyforrest.org}) that have already been
-used by other research groups for independent research questions.
+We used three subdatasets of the publicly available studyforrest dataset
+(\href{http://www.studyforrest.org}{studyforrest.org}) that has already been
+used by other research groups for independent research questions
+(e.g. \citep{ben2018hippocampal, jiahui2019predicting, hu2017decoding,
+lettieri2019emotionotopy, nguyen2016integration}).
 % used studies
@@
 a) listening to the audio-description (AO study; \citep{hanke2014audiomovie}) of
-the movie ``Forrest Gump'', a dataset already used by \citep{hu2017decoding,
-nguyen2016integration},
+the movie ``Forrest Gump'',
 % AV
 b) watching the actual audio-visual movie (AV study;
-\citep{hanke2016simultaneous}), a dataset already used by
-\citep{ben2018hippocampal},
+\citep{hanke2016simultaneous}), and
 % VIS
 c) participating in a dedicated six-category block-design visual localizer (VIS
-study; \citep{sengupta2016extension}), a dataset already used by
-\citep{jiahui2019predicting}.
+study; \citep{sengupta2016extension}).
 % see corresponding papers for details
@@
 
-\subsection{Stimuli}
-
-\todo[inline]{merge Stimuli and ``Procedure'' (s. below)}
+\subsection{Stimuli and Procedure}
+
+\todo[inline]{Ich würde mal die Frage antizipieren, wie gut passen die
+Annotationen zu den VIS Stimuli. Und die müsste meiner Meinung nach doppelt
+beantwortet werden. a) Durch genauere Beschreibung von VIS, b) durch genauere
+Ausführungen, wie welche Annotation dazu passt}
 
@@
 segments (see Figure 3a in \citep{hanke2014audiomovie}).
+% procedure: questionnaire
+Subjects filled out a questionnaire on their basic demographic information
+and familiarity with the movie.
+% AO & AV: instructions
+Before the experiment, participants were instructed to inhibit physical
+movements except for eye-movements, and otherwise to simply ``enjoy the
+audiobook'' or ``enjoy the movie'' respectively.
+% AO & AV: presentation & instructions
+Audio-description and movie segments were presented in chronological order with
+four segments in two fMRI sessions. Between sessions, participants left the
+scanner for a break with a flexible duration. Structural images were obtained
+during the first study on a day different from the fMRI session.
+
+\todo[inline]{contrary to claims in Sengupta, the pictures are NOT the same
+as used in Haxby, 2011; sets might have an intersection though}
 
@@
 All stimuli of the VIS study were already used in a previous study
-\citep{haxby2011common}. There were 24 unique grayscale images (matched in
-luminance, size of 400 $\times$\unit[400]{px}) for each of six stimulus
-categories: faces, bodies without heads, small objects, houses and
-outdoor scenes comprising of nature and street scenes, and phase scrambled
-images. Mirrored views of these 24 $\times$ 6 images were also used as stimuli.
+\citep{haxby2011common}. There were 24 unique grayscale images (s. Figure 2 in
+\citep{sengupta2016extension}) ) for each of six stimulus categories:
+% category details
+faces (cropped from original background presented on a medium-gray background),
+bodies (female and male without heads in clothes; medium-gray background),
+objects (e.g. binoculars, screw, chair, mug; medium-gray background), houses
+(medium-gray background) and outdoor scenes comprising of nature and street
+scenes, and phase scrambled images.
+% mirror images
+Mirrored views of these 24 $\times$ 6 images were also used as stimuli.
+% controlled luminance and size
+Images were matched in luminance and size of 400 $\times$\unit[400]{px}
+(displayed at a size of approximately
+\unit[10]{$^{\circ}$}$\times$\unit[10]{$^{\circ}$} visual angle.
+% procedure: presentation & instructions
+During the experiment, subjects were presented with four block-design runs, with
+two \unit[16]{s} blocks per stimulus category in each run.
+% temporal progression
+Each image was shown for \unit[900]{ms} and images were separated by a fixation
+cross lasting \unit[100]{ms}.
+% task
+Subjects also performed a one-back matching task to keep them attentive.
 
 \subsection{Naturalistic stimuli annotation}
+
+\todo[inline]{Ich würde abschnitt 2.8 (statistical analysis) teilen:
+    a) die regressors, die dann mit der beschreibung der annotation kombinieren
+    b) die eigentliche statistik)}
 
@@
 
+%
+Since we did not design the given naturalistic stimuli for optimal localization
+performance of the PPA, we operationalized the perception of landscapes and
+landmarks (compared to e.g. faces and objects) by annotating words spoken by the
+narrator of the audio-description as well as cuts and depicted locations in the
+movie.
 % todo stimuli were not designed for research purposes
@@
 \todo[inline]{Table 2 ist relativ kryptisch bzw für jemanden, der sich zum
-    ersten Mal damit auseinander setzt kaum zu verstehen. Auch ist der Bezug zum
-GLM unklar, d.h., was davon wird verwendet und was verbirgt sich dahinter}
+ersten Mal damit auseinander setzt kaum zu verstehen. Auch ist der Bezug zum GLM
+unklar, d.h., was davon wird verwendet und was verbirgt sich dahinter}
 
@@
 % table for descriptive nouns: categories, rules, examples counts
-\begin{table*}[t]
-    \caption{Descriptive nouns spoken by the audio-description's narrator:
-    categories, annotation rules, and examples (given in English). The category
-    \texttt{++} also contains adverbial of time.}
-\label{tab:descr-nouns-rules}
-\begin{tabular}{lll}
-\toprule
+\begin{table*}[t] \caption{Descriptive nouns spoken by the audio-description's
+            narrator: categories, annotation rules, and examples (given in
+            English). The category \texttt{++} also contains adverbial of time.}
+            \label{tab:descr-nouns-rules} \begin{tabular}{lll} \toprule
                 \textbf{category} & \textbf{rule} & \textbf{examples} \\
-\midrule
-body & trunk of the body; overlaid clothes & back, hip, shoulder; jacket, dress, shirt \tabularnewline
-bodypart & limbs and trousers & arm, finger, leg, toe \tabularnewline
-face & face or parts of it & face, ear, nose, mouth \tabularnewline
-female & female person & nurse, mother, woman \tabularnewline
-females & female persons & women \tabularnewline
-fname & female name & Jenny \tabularnewline
-furniture & movable furniture insides \& outsides & bench, bed, table, chair
-\tabularnewline
-geo & immobile landmarks & building, tree, street, alley, meadow, cornfield \tabularnewline
-geo-room & rooms (insides) or  locales (outsides) & living room; wall, door, window, floor, turf \tabularnewline
-head & non-face parts of the head; worn headgear & head, hair, ear, neck,
-helmet \tabularnewline
-male & male person & man, father, soldier \tabularnewline
-males & male persons & boys, opponents \tabularnewline
-mname & male name & Bubba, Kennedy \tabularnewline
-object & countable entity with firm boundaries & telephone, car \tabularnewline
-objects & countable entities & wheels, plants \tabularnewline
-persons & concrete persons of unknown sex & hippies, patients \tabularnewline
-setting\_new & noun cueing an unfamiliar setting &  on a ``bridge'', on an ``alley'', on ``campus'' \tabularnewline
-setting\_rec & noun cueing a recurring setting & at the ``bus stop'' \tabularnewline
-++ & cue regarding time & in the ``evening'', it's ``daytime'', ``later'' \tabularnewline
-
-\bottomrule
-\end{tabular}
-\end{table*}
+                \midrule body & trunk of the body; overlaid clothes & back, hip,
+                shoulder; jacket, dress, shirt \tabularnewline bodypart & limbs
+                and trousers & arm, finger, leg, toe \tabularnewline face & face
+                or parts of it & face, ear, nose, mouth \tabularnewline female &
+                female person & nurse, mother, woman \tabularnewline females &
+                female persons & women \tabularnewline fname & female name &
+                Jenny \tabularnewline furniture & movable furniture insides \&
+                outsides & bench, bed, table, chair \tabularnewline geo &
+                immobile landmarks & building, tree, street, alley, meadow,
+                cornfield \tabularnewline geo-room & rooms (insides) or  locales
+                (outsides) & living room; wall, door, window, floor, turf
+                \tabularnewline head & non-face parts of the head; worn headgear
+                & head, hair, ear, neck, helmet \tabularnewline male & male
+                person & man, father, soldier \tabularnewline males & male
+                persons & boys, opponents \tabularnewline mname & male name &
+                Bubba, Kennedy \tabularnewline object & countable entity with
+                firm boundaries & telephone, car \tabularnewline objects &
+                countable entities & wheels, plants \tabularnewline persons &
+                concrete persons of unknown sex & hippies, patients
+                \tabularnewline setting\_new & noun cueing an unfamiliar setting
+                &  on a ``bridge'', on an ``alley'', on ``campus''
+                \tabularnewline setting\_rec & noun cueing a recurring setting &
+                at the ``bus stop'' \tabularnewline ++ & cue regarding time & in
+                the ``evening'', it's ``daytime'', ``later'' \tabularnewline
+
+\bottomrule \end{tabular} \end{table*}
 
 % table of descriptive nouns counts
-\begin{table*}[t]
-    \caption{Descriptive nouns spoken by the audio-descriptions narrator:
-        counts for the whole audio-only stimulus and its eight segments used
-        during fMRI scanning.}
-\label{tab:descr-nouns-counts}
-\begin{tabular}{llllllllll}
-\toprule
-\textbf{category} & \textbf{all} & \textbf{1} & \textbf{2} & \textbf{3} & \textbf{4} & \textbf{5} & \textbf{6} & \textbf{7} & \textbf{8} \\
-\midrule
-body & \anBodyAll & \anBodyI & \anBodyII & \anBodyIII & \anBodyIV & \anBodyV & \anBodyVI & \anBodyVII & \anBodyVIII \tabularnewline
-bodypart &  \anBodypartAll & \anBodypartI & \anBodypartII & \anBodypartIII & \anBodypartIV & \anBodypartV & \anBodypartVI & \anBodypartVII & \anBodypartVIII \tabularnewline
-face & \anFaceAll & \anFaceI & \anFaceII & \anFaceIII & \anFaceIV & \anFaceV & \anFaceVI & \anFaceVII & \anFaceVIII \tabularnewline
-female & \anFemaleAll & \anFemaleI & \anFemaleII & \anFemaleIII & \anFemaleIV & \anFemaleV & \anFemaleVI & \anFemaleVII & \anFemaleVIII \tabularnewline
-females & \anFemalesAll & \anFemalesI & \anFemalesII & \anFemalesIII & \anFemalesIV & \anFemalesV & \anFemalesVI & \anFemalesVII & \anFemalesVIII \tabularnewline
-fname & \anFnameAll & \anFnameI & \anFnameII & \anFnameIII & \anFnameIV & \anFnameV & \anFnameVI & \anFnameVII & \anFnameVIII \tabularnewline
-furniture & \anFurnitureAll & \anFurnitureI & \anFurnitureII & \anFurnitureIII & \anFurnitureIV & \anFurnitureV & \anFurnitureVI & \anFurnitureVII & \anFurnitureVIII \tabularnewline
-geo & \anGeoAll & \anGeoI & \anGeoII & \anGeoIII & \anGeoIV & \anGeoV & \anGeoVI & \anGeoVII & \anGeoVIII \tabularnewline
-geo-room & \anGeoroomAll & \anGeoroomI & \anGeoroomII & \anGeoroomIII & \anGeoroomIV & \anGeoroomV & \anGeoroomVI & \anGeoroomVII & \anGeoroomVIII \tabularnewline
-head & \anHeadAll & \anHeadI & \anHeadII & \anHeadIII & \anHeadIV & \anHeadV & \anHeadVI & \anHeadVII & \anHeadVIII \tabularnewline
-male & \anMaleAll & \anMaleI & \anMaleII & \anMaleIII & \anMaleIV & \anMaleV & \anMaleVI & \anMaleVII & \anMaleVIII \tabularnewline
-males & \anMalesAll & \anMalesI & \anMalesII & \anMalesIII & \anMalesIV & \anMalesV & \anMalesVI & \anMalesVII & \anMalesVIII \tabularnewline
-mname & \anMnameAll & \anMnameI & \anMnameII & \anMnameIII & \anMnameIV & \anMnameV & \anMnameVI & \anMnameVII & \anMnameVIII \tabularnewline
-object & \anObjectAll & \anObjectI & \anObjectII & \anObjectIII & \anObjectIV & \anObjectV & \anObjectVI & \anObjectVII & \anObjectVIII \tabularnewline
-objects & \anObjectsAll & \anObjectsI & \anObjectsII & \anObjectsIII & \anObjectsIV & \anObjectsV & \anObjectsVI & \anObjectsVII & \anObjectsVIII \tabularnewline
-persons & \anPersonsAll & \anPersonsI & \anPersonsII & \anPersonsIII & \anPersonsIV & \anPersonsV & \anPersonsVI & \anPersonsVII & \anPersonsVIII \tabularnewline
-
-setting\_new & \anSettingnewAll & \anSettingnewI & \anSettingnewII & \anSettingnewIII & \anSettingnewIV & \anSettingnewV & \anSettingnewVI & \anSettingnewVII & \anSettingnewVIII \tabularnewline
-
-setting\_rec & \anSettingrecAll &
-\anSettingrecI & \anSettingrecII & \anSettingrecIII & \anSettingrecIV & \anSettingrecV & \anSettingrecVI & \anSettingrecVII & \anSettingrecVIII \tabularnewline
-++ & \anAll & \anI & \anII & \anIII & \anIV & \anV & \anVI & \anVII & \anVIII \tabularnewline
-\bottomrule
-\end{tabular}
-\end{table*}
-
-\subsection{Procedure}
-
-\todo[inline]{Procedure (2.4.) ist nicht zwingend nötig bzw nicht als
-separater Abschnitt}
-
-% questionnaire
-Participants filled out a questionnaire on their basic demographic information
-and familiarity with the movie.
-% AO & AV: instructions
-Participants were instructed to inhibit physical movements except for
-eye-movements, and otherwise to simply ``enjoy the audiobook'' or ``enjoy the
-movie'' respectively.
-% AO & AV: presentation & instructions
-Audio-description and movie segments were presented in chronological order with
-four segments in two fMRI sessions. Between sessions, participants left the
-scanner for a break with a flexible duration. Structural images were obtained
-during the first study on a day different from the fMRI session.
-
-% VIS: presentation & instructions
-In the VIS study, participants were presented with four block-design runs, with
-two \unit[16]{s} blocks per stimulus category in each run, while they also
-performed a one-back matching task to keep them attentive.
+\begin{table*}[t] \caption{Descriptive nouns spoken by the audio-descriptions
+        narrator: counts for the whole audio-only stimulus and its eight
+    segments used during fMRI scanning.} \label{tab:descr-nouns-counts}
+    \begin{tabular}{llllllllll} \toprule \textbf{category} & \textbf{all} &
+        \textbf{1} & \textbf{2} & \textbf{3} & \textbf{4} & \textbf{5} &
+        \textbf{6} & \textbf{7} & \textbf{8} \\ \midrule body & \anBodyAll &
+        \anBodyI & \anBodyII & \anBodyIII & \anBodyIV & \anBodyV & \anBodyVI &
+        \anBodyVII & \anBodyVIII \tabularnewline bodypart &  \anBodypartAll &
+        \anBodypartI & \anBodypartII & \anBodypartIII & \anBodypartIV &
+        \anBodypartV & \anBodypartVI & \anBodypartVII & \anBodypartVIII
+        \tabularnewline face & \anFaceAll & \anFaceI & \anFaceII & \anFaceIII &
+        \anFaceIV & \anFaceV & \anFaceVI & \anFaceVII & \anFaceVIII
+        \tabularnewline female & \anFemaleAll & \anFemaleI & \anFemaleII &
+        \anFemaleIII & \anFemaleIV & \anFemaleV & \anFemaleVI & \anFemaleVII &
+        \anFemaleVIII \tabularnewline females & \anFemalesAll & \anFemalesI &
+        \anFemalesII & \anFemalesIII & \anFemalesIV & \anFemalesV & \anFemalesVI
+        & \anFemalesVII & \anFemalesVIII \tabularnewline fname & \anFnameAll &
+        \anFnameI & \anFnameII & \anFnameIII & \anFnameIV & \anFnameV &
+        \anFnameVI & \anFnameVII & \anFnameVIII \tabularnewline furniture &
+        \anFurnitureAll & \anFurnitureI & \anFurnitureII & \anFurnitureIII &
+        \anFurnitureIV & \anFurnitureV & \anFurnitureVI & \anFurnitureVII &
+        \anFurnitureVIII \tabularnewline geo & \anGeoAll & \anGeoI & \anGeoII &
+        \anGeoIII & \anGeoIV & \anGeoV & \anGeoVI & \anGeoVII & \anGeoVIII
+        \tabularnewline geo-room & \anGeoroomAll & \anGeoroomI & \anGeoroomII &
+        \anGeoroomIII & \anGeoroomIV & \anGeoroomV & \anGeoroomVI &
+        \anGeoroomVII & \anGeoroomVIII \tabularnewline head & \anHeadAll &
+        \anHeadI & \anHeadII & \anHeadIII & \anHeadIV & \anHeadV & \anHeadVI &
+        \anHeadVII & \anHeadVIII \tabularnewline male & \anMaleAll & \anMaleI &
+        \anMaleII & \anMaleIII & \anMaleIV & \anMaleV & \anMaleVI & \anMaleVII &
+        \anMaleVIII \tabularnewline males & \anMalesAll & \anMalesI & \anMalesII
+        & \anMalesIII & \anMalesIV & \anMalesV & \anMalesVI & \anMalesVII &
+        \anMalesVIII \tabularnewline mname & \anMnameAll & \anMnameI &
+        \anMnameII & \anMnameIII & \anMnameIV & \anMnameV & \anMnameVI &
+        \anMnameVII & \anMnameVIII \tabularnewline object & \anObjectAll &
+        \anObjectI & \anObjectII & \anObjectIII & \anObjectIV & \anObjectV &
+        \anObjectVI & \anObjectVII & \anObjectVIII \tabularnewline objects &
+        \anObjectsAll & \anObjectsI & \anObjectsII & \anObjectsIII &
+        \anObjectsIV & \anObjectsV & \anObjectsVI & \anObjectsVII &
+        \anObjectsVIII \tabularnewline persons & \anPersonsAll & \anPersonsI &
+        \anPersonsII & \anPersonsIII & \anPersonsIV & \anPersonsV & \anPersonsVI
+        & \anPersonsVII & \anPersonsVIII \tabularnewline
+
+setting\_new & \anSettingnewAll & \anSettingnewI & \anSettingnewII &
+\anSettingnewIII & \anSettingnewIV & \anSettingnewV & \anSettingnewVI &
+\anSettingnewVII & \anSettingnewVIII \tabularnewline
+
+setting\_rec & \anSettingrecAll & \anSettingrecI & \anSettingrecII &
+\anSettingrecIII & \anSettingrecIV & \anSettingrecV & \anSettingrecVI &
+\anSettingrecVII & \anSettingrecVIII \tabularnewline ++ & \anAll & \anI & \anII
+& \anIII & \anIV & \anV & \anVI & \anVII & \anVIII \tabularnewline \bottomrule
+\end{tabular} \end{table*}
 
@@
 Germany; \citep{baumgart1998electrodynamic}) that reduced the scanner noise by
-at least \unit[20–30]{dB}. Headphones were fed from an Aureon 7.1 USB
-(Terratec) sound card through an optical connection.
+at least \unit[20–30]{dB}. Headphones were fed from an Aureon 7.1 USB (Terratec)
+sound card through an optical connection.
 
@@
 
-\todo[inline]{what is missing: As I see it, AO must have been downsampled
-to 2.5x2.5x2.5 mm and AV must have been upsampled from 3.0 to 2.5mm??}
+\todo[inline]{what is missing: As I see it, AO must have been downsampled to
+2.5x2.5x2.5 mm and AV must have been upsampled from 3.0 to 2.5mm??}
 
@@
 
-\todo[inline]{Ich würde abschnitt 2.8 teilen (in die regressors, die dann mit
-der beschreibung der annotation kombinieren, und die eigentliche statistik)}
-
 \todo[inline]{Ich weiss nicht, ob es die etwas wild zwischendrin stehenden
@@
 
+\todo[inline]{Ich würde abschnitt 2.8 teilen (in die regressors, die dann mit
+der beschreibung der annotation kombinieren, und die eigentliche statistik)}
+
 Similarly to the reviewed studies that employed simplified stimuli, we conducted
@@
 
-\todo[inline]{Das mit den "five additional categories" habe ich nicht
-    verstanden. Überhaupt finde ich die ganze Beschreibung relativ schwer zu
-durchdrungen, und ich glaube damit werde ich nicht alleine sein.}
-
-\todo[inline]{Gab es ein separates null-event für jeden zeitraum zwischen zwei
-annotierten events oder war das ein regressor der immer wieder kam?}
-
 \todo[inline]{Ich würde vorschlagen, dass Du Dich auf die Regressoren / Events
-    konzentrierst, die hier wichtig sind, um die Komplexität zu reduzieren. Die
-    aber dafür besser erklären (was heißt "unfamilar perspective"? Ab wann ist
-ein setting "familiar"?}
-
-% first level analysis
-% regressors
-% AO: events
+konzentrierst, die hier wichtig sind, um die Komplexität zu reduzieren. Die aber
+dafür besser erklären (was heißt "unfamilar perspective"? Ab wann ist ein
+setting "familiar"?}
+
+\subsubsection{Annotation of naturalistic stimuli}
+
+\subsubsection{Regressors}
+
+% first level analysis regressors AO: events
 For the analysis of the AO stimulus, we created regressors correlating with the
@@
 Events were were modeled as boxcar function from onset to offset of each word.
+
+\todo[inline]{Gab es ein separates null-event für jeden zeitraum zwischen zwei
+annotierten events oder war das ein regressor der immer wieder kam?}
 % null regressors
@@
 Hatte, glaube ich, Jeanette Mumford in einem ihren Videos mal gesagt}
+
+\todo[inline]{Das mit den "five additional categories" habe ich nicht
+verstanden. Überhaupt finde ich die ganze Beschreibung relativ schwer zu
+durchdrungen, und ich glaube damit werde ich nicht alleine sein.}
 % categories taken from movie cut annotation
@@
 
-\begin{table*}[t]
-\caption{Overview of events to build the 18 regressors for the analysis of the
-audio-only (AO) stimulus. Some of the annotation's original categories
-    (female, females, fname; male, males, mname; face, head; object, objects;
-    see Table\ref{tab:descr-nouns-rules})
-    were pooled into 11 new categories (\texttt{sex\_f}; \texttt{sex\_m};
-    \texttt{fahead}; \texttt{object}).
-\texttt{fg\_ad\_lrdiff} (left-right volume difference) and
-\texttt{fg\_ad\_rms} (root mean square volume) represent one event for every movie frame (\unit[40]{ms}).
-For a description of the five control conditions for movie cuts see Table \ref{tab:av-events}.}
-\label{tab:ao-events}
-\footnotesize
-\begin{tabular}{lp{3.5cm}lllllllll}
-\toprule
-\textbf{label} &  \textbf{description} & \textbf{all} & \textbf{1} & \textbf{2} & \textbf{3} & \textbf{4} & \textbf{5} & \textbf{6} & \textbf{7} & \textbf{8} \\
-\midrule
-body & trunk of the body or overlaid clothes & \aoBodyAll & \aoBodyI & \aoBodyII & \aoBodyIII & \aoBodyIV & \aoBodyV & \aoBodyVI & \aoBodyVII & \aoBodyVIII \tabularnewline
-bpart & limbs and trousers & \aoBpartAll & \aoBpartI & \aoBpartII & \aoBpartIII & \aoBpartIV & \aoBpartV & \aoBpartVI & \aoBpartVII & \aoBpartVIII \tabularnewline
-fahead & face(parts) or head(parts) & \aoFaheadAll & \aoFaheadI & \aoFaheadII & \aoFaheadIII & \aoFaheadIV & \aoFaheadV & \aoFaheadVI & \aoFaheadVII & \aoFaheadVIII \tabularnewline
-furn & moveable furniture insides \& outsides & \aoFurnAll & \aoFurnI & \aoFurnII & \aoFurnIII & \aoFurnIV & \aoFurnV & \aoFurnVI & \aoFurnVII & \aoFurnVIII \tabularnewline
-geo & immobile landmarks & \aoGeoAll & \aoGeoI & \aoGeoII & \aoGeoIII & \aoGeoIV & \aoGeoV & \aoGeoVI & \aoGeoVII & \aoGeoVIII \tabularnewline
-groom & elements defining geometry of room & \aoGroomAll & \aoGroomI & \aoGroomII & \aoGroomIII & \aoGroomIV & \aoGroomV & \aoGroomVI & \aoGroomVII & \aoGroomVIII \tabularnewline
-object & inanimate entities with firm boundaries & \aoObjAll & \aoObjI & \aoObjII & \aoObjIII & \aoObjIV & \aoObjV & \aoObjVI & \aoObjVII & \aoObjVIII \tabularnewline
-se\_new & noun cueing an unfamiliar setting & \aoSenewAll & \aoSenewI & \aoSenewII & \aoSenewIII & \aoSenewIV & \aoSenewV & \aoSenewVI & \aoSenewVII & \aoSenewVIII \tabularnewline
-se\_old & noun cueing a recurring setting & \aoSeoldAll & \aoSeoldI & \aoSeoldII & \aoSeoldIII & \aoSeoldIV & \aoSeoldV & \aoSeoldVI & \aoSeoldVII & \aoSeoldVIII \tabularnewline
-sex\_f & female person(s), name & \aoSexfAll & \aoSexfI & \aoSexfII & \aoSexfIII & \aoSexfIV & \aoSexfV & \aoSexfVI & \aoSexfVII & \aoSexfVIII \tabularnewline
-sex\_m & male person(s), name & \aoSexmAll & \aoSexmI & \aoSexmII & \aoSexmIII & \aoSexmIV & \aoSexmV & \aoSexmVI & \aoSexmVII & \aoSexmVIII \tabularnewline
+\begin{table*}[t] \caption{Overview of events to build the 18 regressors for the
+        analysis of the audio-only (AO) stimulus. Some of the annotation's
+        original categories (female, females, fname; male, males, mname; face,
+        head; object, objects; see Table\ref{tab:descr-nouns-rules}) were pooled
+        into 11 new categories (\texttt{sex\_f}; \texttt{sex\_m};
+        \texttt{fahead}; \texttt{object}).  \texttt{fg\_ad\_lrdiff} (left-right
+        volume difference) and \texttt{fg\_ad\_rms} (root mean square volume)
+        represent one event for every movie frame (\unit[40]{ms}).  For a
+        description of the five control conditions for movie cuts see Table
+        \ref{tab:av-events}.} \label{tab:ao-events} \footnotesize
+        \begin{tabular}{lp{3.5cm}lllllllll} \toprule \textbf{label} &
+            \textbf{description} & \textbf{all} & \textbf{1} & \textbf{2} &
+            \textbf{3} & \textbf{4} & \textbf{5} & \textbf{6} & \textbf{7} &
+            \textbf{8} \\ \midrule body & trunk of the body or overlaid clothes
+            & \aoBodyAll & \aoBodyI & \aoBodyII & \aoBodyIII & \aoBodyIV &
+            \aoBodyV & \aoBodyVI & \aoBodyVII & \aoBodyVIII \tabularnewline
+            bpart & limbs and trousers & \aoBpartAll & \aoBpartI & \aoBpartII &
+            \aoBpartIII & \aoBpartIV & \aoBpartV & \aoBpartVI & \aoBpartVII &
+            \aoBpartVIII \tabularnewline fahead & face(parts) or head(parts) &
+            \aoFaheadAll & \aoFaheadI & \aoFaheadII & \aoFaheadIII & \aoFaheadIV
+            & \aoFaheadV & \aoFaheadVI & \aoFaheadVII & \aoFaheadVIII
+            \tabularnewline furn & moveable furniture insides \& outsides &
+            \aoFurnAll & \aoFurnI & \aoFurnII & \aoFurnIII & \aoFurnIV &
+            \aoFurnV & \aoFurnVI & \aoFurnVII & \aoFurnVIII \tabularnewline geo
+            & immobile landmarks & \aoGeoAll & \aoGeoI & \aoGeoII & \aoGeoIII &
+            \aoGeoIV & \aoGeoV & \aoGeoVI & \aoGeoVII & \aoGeoVIII
+            \tabularnewline groom & elements defining geometry of room &
+            \aoGroomAll & \aoGroomI & \aoGroomII & \aoGroomIII & \aoGroomIV &
+            \aoGroomV & \aoGroomVI & \aoGroomVII & \aoGroomVIII \tabularnewline
+            object & inanimate entities with firm boundaries & \aoObjAll &
+            \aoObjI & \aoObjII & \aoObjIII & \aoObjIV & \aoObjV & \aoObjVI &
+            \aoObjVII & \aoObjVIII \tabularnewline se\_new & noun cueing an
+            unfamiliar setting & \aoSenewAll & \aoSenewI & \aoSenewII &
+            \aoSenewIII & \aoSenewIV & \aoSenewV & \aoSenewVI & \aoSenewVII &
+            \aoSenewVIII \tabularnewline se\_old & noun cueing a recurring
+            setting & \aoSeoldAll & \aoSeoldI & \aoSeoldII & \aoSeoldIII &
+            \aoSeoldIV & \aoSeoldV & \aoSeoldVI & \aoSeoldVII & \aoSeoldVIII
+            \tabularnewline sex\_f & female person(s), name & \aoSexfAll &
+            \aoSexfI & \aoSexfII & \aoSexfIII & \aoSexfIV & \aoSexfV & \aoSexfVI
+            & \aoSexfVII & \aoSexfVIII \tabularnewline sex\_m & male person(s),
+            name & \aoSexmAll & \aoSexmI & \aoSexmII & \aoSexmIII & \aoSexmIV &
+            \aoSexmV & \aoSexmVI & \aoSexmVII & \aoSexmVIII \tabularnewline
 % vlo_ch has no events in segment 5. So indices are shifted
-vse\_new & control for movie cut & \aoVsenewAll & \aoVsenewI & \aoVsenewII & \aoVsenewIII & \aoVsenewIV & \aoVsenewV & \aoVsenewVI & \aoVsenewVII & \aoVsenewVIII \tabularnewline
-vse\_old & control for movie cut & \aoVseoldAll & \aoVseoldI & \aoVseoldII & \aoVseoldIII & \aoVseoldIV & \aoVseoldV & \aoVseoldVI & \aoVseoldVII & \aoVseoldVIII \tabularnewline
-vlo\_ch & control for movie cut & \aoVlochAll & \aoVlochI & \aoVlochII & \aoVlochIII & \aoVlochIV & 0 & \aoVlochV & \aoVlochVI & \aoVlochVII \tabularnewline
-vpe\_new & control for movie cut & \aoVpenewAll & \aoVpenewI & \aoVpenewII & \aoVpenewIII & \aoVpenewIV & \aoVpenewV & \aoVpenewVI & \aoVpenewVII & \aoVpenewVIII \tabularnewline
+vse\_new & control for movie cut & \aoVsenewAll & \aoVsenewI & \aoVsenewII &
+\aoVsenewIII & \aoVsenewIV & \aoVsenewV & \aoVsenewVI & \aoVsenewVII &
+\aoVsenewVIII \tabularnewline vse\_old & control for movie cut & \aoVseoldAll &
+\aoVseoldI & \aoVseoldII & \aoVseoldIII & \aoVseoldIV & \aoVseoldV & \aoVseoldVI
+& \aoVseoldVII & \aoVseoldVIII \tabularnewline vlo\_ch & control for movie cut &
+\aoVlochAll & \aoVlochI & \aoVlochII & \aoVlochIII & \aoVlochIV & 0 & \aoVlochV
+& \aoVlochVI & \aoVlochVII \tabularnewline vpe\_new & control for movie cut &
+\aoVpenewAll & \aoVpenewI & \aoVpenewII & \aoVpenewIII & \aoVpenewIV &
+\aoVpenewV & \aoVpenewVI & \aoVpenewVII & \aoVpenewVIII \tabularnewline
 % vpe_old has no events in 3. So the indices are shifted
-vpe\_old & control for movie cut & \aoVpeoldAll & \aoVpeoldI & \aoVpeoldII & 0 & \aoVpeoldIII & \aoVpeoldIV & \aoVpeoldV & \aoVpeoldVI & \aoVpeoldVII \tabularnewline
-fg\_ad\_lrdiff & left-right volume difference & \aoFgadlrdiffAll & \aoFgadlrdiffI & \aoFgadlrdiffII & \aoFgadlrdiffIII & \aoFgadlrdiffIV & \aoFgadlrdiffV & \aoFgadlrdiffVI & \aoFgadlrdiffVII & \aoFgadlrdiffVIII \tabularnewline
-fg\_ad\_rms & root mean square (loudness) & \aoFgadrmsAll & \aoFgadrmsI & \aoFgadrmsII & \aoFgadrmsIII & \aoFgadrmsIV & \aoFgadrmsV & \aoFgadrmsVI & \aoFgadrmsVII & \aoFgadrmsVIII \tabularnewline
-\bottomrule
-\end{tabular}
-\end{table*}
+vpe\_old & control for movie cut & \aoVpeoldAll & \aoVpeoldI & \aoVpeoldII & 0 &
+\aoVpeoldIII & \aoVpeoldIV & \aoVpeoldV & \aoVpeoldVI & \aoVpeoldVII
+\tabularnewline fg\_ad\_lrdiff & left-right volume difference & \aoFgadlrdiffAll
+& \aoFgadlrdiffI & \aoFgadlrdiffII & \aoFgadlrdiffIII & \aoFgadlrdiffIV &
+\aoFgadlrdiffV & \aoFgadlrdiffVI & \aoFgadlrdiffVII & \aoFgadlrdiffVIII
+\tabularnewline fg\_ad\_rms & root mean square (loudness) & \aoFgadrmsAll &
+\aoFgadrmsI & \aoFgadrmsII & \aoFgadrmsIII & \aoFgadrmsIV & \aoFgadrmsV &
+\aoFgadrmsVI & \aoFgadrmsVII & \aoFgadrmsVIII \tabularnewline \bottomrule
+\end{tabular} \end{table*}
 
@@
 
-\begin{table*}[t]
-    \caption{Overview of events to build the 14 regressors for the analysis of
-        the audio-visual (AV) stimulus.
-        \texttt{fg\_av\_ger\_pd} (perceptual differences of consecutive frames),
-        \texttt{fg\_av\_ger\_ml} (mean luminance of a frame),
-        \texttt{fg\_av\_ger\_lr} (difference in mean luminance of left and
-        right half),
-        \texttt{fg\_av\_ger\_ud} (difference in mean luminance of upper and
-        lower half),
+\begin{table*}[t] \caption{Overview of events to build the 14 regressors for the
+        analysis of the audio-visual (AV) stimulus.  \texttt{fg\_av\_ger\_pd}
+        (perceptual differences of consecutive frames), \texttt{fg\_av\_ger\_ml}
+        (mean luminance of a frame), \texttt{fg\_av\_ger\_lr} (difference in
+        mean luminance of left and right half), \texttt{fg\_av\_ger\_ud}
+        (difference in mean luminance of upper and lower half),
         \texttt{fg\_av\_ger\_lrdiff} (left-right volume difference), and
         \texttt{fg\_av\_ger\_rms} (root mean square volume) represent one event
-        for every movie frame (\unit[40]{ms}).
-        For description of the two event categories of the audio-description's
-        narrator (\texttt{se\_new} and \texttt{se\_old}) to build contrast
-        of negative control see Table \ref{tab:ao-events}.}
-\label{tab:av-events}
-\footnotesize
-\begin{tabular}{lp{3.5cm}lllllllll}
-\toprule
-\textbf{label} &  \textbf{description} & \textbf{all} & \textbf{1} & \textbf{2} & \textbf{3} & \textbf{4} & \textbf{5} & \textbf{6} & \textbf{7} & \textbf{8} \\
-\midrule
-vse\_new &  change of the camera position to a setting not depicted before & \aoVsenewAll & \aoVsenewI & \aoVsenewII & \aoVsenewIII & \aoVsenewIV & \aoVsenewV & \aoVsenewVI & \aoVsenewVII & \aoVsenewVIII \tabularnewline
-vse\_old & change of the camera position to a recurring setting & \aoVseoldAll & \aoVseoldI & \aoVseoldII & \aoVseoldIII & \aoVseoldIV & \aoVseoldV & \aoVseoldVI & \aoVseoldVII & \aoVseoldVIII \tabularnewline
-vlo\_ch & change of the camera position to another locale within the same setting & \aoVlochAll & \aoVlochI & \aoVlochII & \aoVlochIII & \aoVlochIV & 0 & \aoVlochV & \aoVlochVI & \aoVlochVII \tabularnewline
-vpe\_new & change of the camera position within a locale not depicted before & \aoVpenewAll & \aoVpenewI & \aoVpenewII & \aoVpenewIII & \aoVpenewIV & \aoVpenewV & \aoVpenewVI & \aoVpenewVII & \aoVpenewVIII \tabularnewline
+        for every movie frame (\unit[40]{ms}).  For description of the two event
+        categories of the audio-description's narrator (\texttt{se\_new} and
+        \texttt{se\_old}) to build contrast of negative control see Table
+        \ref{tab:ao-events}.} \label{tab:av-events} \footnotesize
+        \begin{tabular}{lp{3.5cm}lllllllll} \toprule \textbf{label} &
+            \textbf{description} & \textbf{all} & \textbf{1} & \textbf{2} &
+            \textbf{3} & \textbf{4} & \textbf{5} & \textbf{6} & \textbf{7} &
+            \textbf{8} \\ \midrule vse\_new &  change of the camera position to
+            a setting not depicted before & \aoVsenewAll & \aoVsenewI &
+            \aoVsenewII & \aoVsenewIII & \aoVsenewIV & \aoVsenewV & \aoVsenewVI
+            & \aoVsenewVII & \aoVsenewVIII \tabularnewline vse\_old & change of
+            the camera position to a recurring setting & \aoVseoldAll &
+            \aoVseoldI & \aoVseoldII & \aoVseoldIII & \aoVseoldIV & \aoVseoldV &
+            \aoVseoldVI & \aoVseoldVII & \aoVseoldVIII \tabularnewline vlo\_ch &
+            change of the camera position to another locale within the same
+            setting & \aoVlochAll & \aoVlochI & \aoVlochII & \aoVlochIII &
+            \aoVlochIV & 0 & \aoVlochV & \aoVlochVI & \aoVlochVII
+            \tabularnewline vpe\_new & change of the camera position within a
+            locale not depicted before & \aoVpenewAll & \aoVpenewI & \aoVpenewII
+            & \aoVpenewIII & \aoVpenewIV & \aoVpenewV & \aoVpenewVI &
+            \aoVpenewVII & \aoVpenewVIII \tabularnewline
 % vpe_old has no events in 3. So the indices are shifted
-vpe\_old & change of the camera position within a recurring locale & \aoVpeoldAll & \aoVpeoldI & \aoVpeoldII & 0 & \aoVpeoldIII & \aoVpeoldIV & \aoVpeoldV & \aoVpeoldVI & \aoVpeoldVII \tabularnewline
-vno\_cut & a continuous frame from the same camera position & \avVnocutAll & \avVnocutI & \avVnocutII & 0 & \avVnocutIII & \avVnocutIV & \avVnocutV & \avVnocutVI & \avVnocutVII \tabularnewline
-se\_new & control for AO narrator & \aoSenewAll & \aoSenewI & \aoSenewII & \aoSenewIII & \aoSenewIV & \aoSenewV & \aoSenewVI & \aoSenewVII & \aoSenewVIII \tabularnewline
-se\_old & control for AO narrator & \aoSeoldAll & \aoSeoldI & \aoSeoldII & \aoSeoldIII & \aoSeoldIV & \aoSeoldV & \aoSeoldVI & \aoSeoldVII & \aoSeoldVIII \tabularnewline
-fg\_av\_ger\_lr & left-right luminance difference & \avFgavgerlrAll & \avFgavgerlrI & \avFgavgerlrII & \avFgavgerlrIII & \avFgavgerlrIV & \avFgavgerlrV & \avFgavgerlrVI & \avFgavgerlrVII & \avFgavgerlrVIII \tabularnewline
-fg\_av\_ger\_lrdiff & left-right volume difference & \avFgavgerlrdiffAll & \avFgavgerlrdiffI & \avFgavgerlrdiffII & \avFgavgerlrdiffIII & \avFgavgerlrdiffIV & \avFgavgerlrdiffV & \avFgavgerlrdiffVI & \avFgavgerlrdiffVII & \avFgavgerlrdiffVIII \tabularnewline
-fg\_av\_ger\_ml & mean luminance & \avFgavgermlAll & \avFgavgermlI & \avFgavgermlII & \avFgavgermlIII & \avFgavgermlIV & \avFgavgermlV & \avFgavgermlVI & \avFgavgermlVII & \avFgavgermlVIII \tabularnewline
-fg\_av\_ger\_pd & perceptual difference & \avFgavgerpdAll & \avFgavgerpdI & \avFgavgerpdII & \avFgavgerpdIII & \avFgavgerpdIV & \avFgavgerpdV & \avFgavgerpdVI & \avFgavgerpdVII & \avFgavgerpdVIII \tabularnewline
-fg\_av\_ger\_rms & root mean square (loudness) & \avFgavgerrmsAll & \avFgavgerrmsI & \avFgavgerrmsII & \avFgavgerrmsIII & \avFgavgerrmsIV & \avFgavgerrmsV & \avFgavgerrmsVI & \avFgavgerrmsVII & \avFgavgerrmsVIII \tabularnewline
-fg\_av\_ger\_ud & upper-lower luminance difference & \avFgavgerudAll & \avFgavgerudI & \avFgavgerudII & \avFgavgerudIII & \avFgavgerudIV & \avFgavgerudV & \avFgavgerudVI & \avFgavgerudVII & \avFgavgerudVIII \tabularnewline
-\end{tabular}
-\end{table*}
+vpe\_old & change of the camera position within a recurring locale &
+\aoVpeoldAll & \aoVpeoldI & \aoVpeoldII & 0 & \aoVpeoldIII & \aoVpeoldIV &
+\aoVpeoldV & \aoVpeoldVI & \aoVpeoldVII \tabularnewline vno\_cut & a continuous
+frame from the same camera position & \avVnocutAll & \avVnocutI & \avVnocutII &
+0 & \avVnocutIII & \avVnocutIV & \avVnocutV & \avVnocutVI & \avVnocutVII
+\tabularnewline se\_new & control for AO narrator & \aoSenewAll & \aoSenewI &
+\aoSenewII & \aoSenewIII & \aoSenewIV & \aoSenewV & \aoSenewVI & \aoSenewVII &
+\aoSenewVIII \tabularnewline se\_old & control for AO narrator & \aoSeoldAll &
+\aoSeoldI & \aoSeoldII & \aoSeoldIII & \aoSeoldIV & \aoSeoldV & \aoSeoldVI &
+\aoSeoldVII & \aoSeoldVIII \tabularnewline fg\_av\_ger\_lr & left-right
+luminance difference & \avFgavgerlrAll & \avFgavgerlrI & \avFgavgerlrII &
+\avFgavgerlrIII & \avFgavgerlrIV & \avFgavgerlrV & \avFgavgerlrVI &
+\avFgavgerlrVII & \avFgavgerlrVIII \tabularnewline fg\_av\_ger\_lrdiff &
+left-right volume difference & \avFgavgerlrdiffAll & \avFgavgerlrdiffI &
+\avFgavgerlrdiffII & \avFgavgerlrdiffIII & \avFgavgerlrdiffIV &
+\avFgavgerlrdiffV & \avFgavgerlrdiffVI & \avFgavgerlrdiffVII &
+\avFgavgerlrdiffVIII \tabularnewline fg\_av\_ger\_ml & mean luminance &
+\avFgavgermlAll & \avFgavgermlI & \avFgavgermlII & \avFgavgermlIII &
+\avFgavgermlIV & \avFgavgermlV & \avFgavgermlVI & \avFgavgermlVII &
+\avFgavgermlVIII \tabularnewline fg\_av\_ger\_pd & perceptual difference &
+\avFgavgerpdAll & \avFgavgerpdI & \avFgavgerpdII & \avFgavgerpdIII &
+\avFgavgerpdIV & \avFgavgerpdV & \avFgavgerpdVI & \avFgavgerpdVII &
+\avFgavgerpdVIII \tabularnewline fg\_av\_ger\_rms & root mean square (loudness)
+& \avFgavgerrmsAll & \avFgavgerrmsI & \avFgavgerrmsII & \avFgavgerrmsIII &
+\avFgavgerrmsIV & \avFgavgerrmsV & \avFgavgerrmsVI & \avFgavgerrmsVII &
+\avFgavgerrmsVIII \tabularnewline fg\_av\_ger\_ud & upper-lower luminance
+difference & \avFgavgerudAll & \avFgavgerudI & \avFgavgerudII & \avFgavgerudIII
+& \avFgavgerudIV & \avFgavgerudV & \avFgavgerudVI & \avFgavgerudVII &
+\avFgavgerudVIII \tabularnewline \end{tabular} \end{table*}
 
@@
 \todo[inline]{Habe jetzt lange darüber gebrütet: Es gibt also kaum eine
-Korrelation zwischen AO und AV?; Also, außer bei fg\_av\_ger\_lr\_diff (wobei da keiner weiss, was das bedeutet)}
+Korrelation zwischen AO und AV?; Also, außer bei fg\_av\_ger\_lr\_diff (wobei da
+keiner weiss, was das bedeutet)}
 % reference to figure ``correlation of regressors''
@@
 
-\begin{figure*}
-    \centering
-    \includegraphics[width=\linewidth]{figures/regressor-corr}
-    \caption{Pearson
+\begin{figure*} \centering
+    \includegraphics[width=\linewidth]{figures/regressor-corr} \caption{Pearson
         correlation coefficients  of the regressors used in the analysis of the
         audio-description (blue; see Table \ref{tab:ao-events} for a
-        description) and audio-visual movie (red; see Table
-        \ref{tab:av-events}) rounded to the nearest tenth.
-        The correlation
-        between the two stimuli's root mean square loudness and between their
-        left-right difference in loudness yielded the highest correlation
-        values (\texttt{fg\_ad\_rms} and \texttt{fg\_av\_ger\_rms}, r=.7635
-        \texttt{fg\_ad\_lrdiff} and \texttt{fg\_av\_ger\_lrdiff}, r=.7749).}
-    \label{fig:reg-corr}
+        description) and audio-visual movie (red; see Table \ref{tab:av-events})
+        rounded to the nearest tenth.  The correlation between the two stimuli's
+        root mean square loudness and between their left-right difference in
+        loudness yielded the highest correlation values (\texttt{fg\_ad\_rms}
+        and \texttt{fg\_av\_ger\_rms}, r=.7635 \texttt{fg\_ad\_lrdiff} and
+        \texttt{fg\_av\_ger\_lrdiff}, r=.7749).} \label{fig:reg-corr}
     \end{figure*}
@@
     consequence of the inability to filter the stimulus material. That "messy"
-     part is usually not obvious from a manuscript. Here we have a fixed,
-     complex stimulus, and we have to operationalize our questions with whatever
-     we have at hand. This is not necessarily exact, and looking at the
- robustness is a feature, not a problem; COH: did not change a lot of text tbh
- but should be clearer now.}
+    part is usually not obvious from a manuscript. Here we have a fixed, complex
+    stimulus, and we have to operationalize our questions with whatever we have
+at hand. This is not necessarily exact, and looking at the robustness is a
+feature, not a problem; COH: did not change a lot of text tbh but should be
+clearer now.}
 
@@
 Compared to previous studies we did not design the stimulus material and
-experimentally controlled conditions for the
-purpose of optimal localization performance since we used fixed stimuli.
+experimentally controlled conditions for the purpose of optimal localization
+performance since we used fixed stimuli.
 % 8 + 5 contrasts
@@
 % test for robustness
-Creating more than just one contrast for the two
-fixed stimuli also let us test for/the robustness of our results across varying
-ways operationalization.
+Creating more than just one contrast for the two fixed stimuli also let us test
+for/the robustness of our results across varying ways operationalization.
 % contrasts are of different quality
@@
 % furniture
-We did not use the category ``furniture'' (\texttt{furn}) as a
-regressor of interest in any contrasts because nouns in this category were
-usually big and heavy. In a serial stream of auditory information, participants
-could perceive furniture-related nouns as either a geometry-defining local scene
-element or as an isolated object. Hence we did not use this category as
-regressor of interest to reduce noise.
+We did not use the category ``furniture'' (\texttt{furn}) as a regressor of
+interest in any contrasts because nouns in this category were usually big and
+heavy. In a serial stream of auditory information, participants could perceive
+furniture-related nouns as either a geometry-defining local scene element or as
+an isolated object. Hence we did not use this category as regressor of interest
+to reduce noise.
 % negative control contrasts
 Five $t$-contrasts (see Table \ref{tab:ao-contrasts}) we created as negative
-controls to test if increased activation in the PPA was correlated with
-moments of cuts and therefore possibly correlated with a accompanying change in
-the soundscape.
-
-\begin{table*}[t]
-\caption{Contrasts of parameter estimates for the analysis of the audio-only
-    stimulus (AO). Contrast 1-8 aim to isolate the PPA (\texttt{all non-geo} =
-    body, bodypart, fahead, object, sex\_f, sex\_m).
-    Contrasts 9-13 serve as negative control at the moments of movie cuts that
-    could correlate with changes of the audio tracks soundscape (see Table
-    \ref{tab:av-contrasts}).}
-\label{tab:ao-contrasts}
-\footnotesize
-\begin{tabular}{lll}
-\toprule
-\textbf{nr.} &  \textbf{contrast} & \textbf{purpose} \\
-\midrule
-1 & geo, groom > all non-geo & PPA \tabularnewline
-2 & geo, groom, se\_new > all non-geo & PPA \tabularnewline
-3 & groom, se\_new, se\_old > all non-geo & PPA \tabularnewline
-4 & geo > all non-geo & PPA \tabularnewline
-5 & groom > all non-geo & PPA \tabularnewline
-6 & se\_new > all non-geo & PPA \tabularnewline
-7 & se\_new, se\_old > all non-geo & PPA \tabularnewline
-8 & se\_new > se\_old & PPA \tabularnewline
-9 & vse\_new > vpe\_old & control at moments of cuts \tabularnewline
-10 & vse\_new, vpe\_new > vse\_old, vpe\_old & control at moments of cuts \tabularnewline
-11 & vse\_new > vse\_old & control at moments of cuts \tabularnewline
-12 & vse\_new > vse\_old, vpe\_old & control at moments of cuts \tabularnewline
-13 & vse\_new, vpe\_new > vpe\_old & control at moments of cuts \tabularnewline
-\end{tabular}
+controls to test if increased activation in the PPA was correlated with moments
+of cuts and therefore possibly correlated with a accompanying change in the
+soundscape.
+
+\begin{table*}[t] \caption{Contrasts of parameter estimates for the analysis of
+        the audio-only stimulus (AO). Contrast 1-8 aim to isolate the PPA
+        (\texttt{all non-geo} = body, bodypart, fahead, object, sex\_f, sex\_m).
+        Contrasts 9-13 serve as negative control at the moments of movie cuts
+        that could correlate with changes of the audio tracks soundscape (see
+        Table \ref{tab:av-contrasts}).} \label{tab:ao-contrasts} \footnotesize
+        \begin{tabular}{lll} \toprule \textbf{nr.} &  \textbf{contrast} &
+            \textbf{purpose} \\ \midrule 1 & geo, groom > all non-geo & PPA
+            \tabularnewline 2 & geo, groom, se\_new > all non-geo & PPA
+            \tabularnewline 3 & groom, se\_new, se\_old > all non-geo & PPA
+            \tabularnewline 4 & geo > all non-geo & PPA \tabularnewline 5 &
+            groom > all non-geo & PPA \tabularnewline 6 & se\_new > all non-geo
+            & PPA \tabularnewline 7 & se\_new, se\_old > all non-geo & PPA
+            \tabularnewline 8 & se\_new > se\_old & PPA \tabularnewline 9 &
+            vse\_new > vpe\_old & control at moments of cuts \tabularnewline 10
+            & vse\_new, vpe\_new > vse\_old, vpe\_old & control at moments of
+            cuts \tabularnewline 11 & vse\_new > vse\_old & control at moments
+            of cuts \tabularnewline 12 & vse\_new > vse\_old, vpe\_old & control
+            at moments of cuts \tabularnewline 13 & vse\_new, vpe\_new >
+            vpe\_old & control at moments of cuts \tabularnewline \end{tabular}
     \end{table*}
@@
 % negative control
-Five additional $t$-contrasts we created for negative control purposes
-(see Table \ref{tab:av-contrasts}) by using regressors based on regressors of
-the AO stimulus.
-
-\begin{table*}[t]
-    \caption{Contrasts of parameter estimates for the analysis of the audio-visual movie (AV).
-Contrast 1-5 aim to isolate the PPA.
-    Contrast 6-9 serve as negative control.
-    Contrast 10 serves as control for moments when the narrator cues the
-    listener about a switch of settings, events that could be correlated with a
-    switch of the soundscape.}
-\label{tab:av-contrasts}
-\footnotesize
-\begin{tabular}{lll}
-\toprule
-\textbf{nr.} &  \textbf{contrast} & \textbf{purpose} \\
-\midrule
-1 & vse\_new > vpe\_old & PPA \tabularnewline
-2 & vse\_new, vpe\_new > vse\_old, vpe\_old & PPA \tabularnewline
-3 & vse\_new > vse\_old & PPA \tabularnewline
-4 & vse\_new > vse\_old, vpe\_old & PPA \tabularnewline
-5 & vse\_new, vpe\_new > vpe\_old & PPA \tabularnewline
-6 & vno\_cut > vse\_new & negative control \tabularnewline
-7 & vno\_cut > vse\_old & negative control \tabularnewline
-8 & vno\_cut > vse\_new, vse\_old & negative control \tabularnewline
-9 & vno\_cut > vpe\_new, vpe\_old & negative control \tabularnewline
-10 & se\_new > se\_old & control for narrator \tabularnewline
-\end{tabular}
-\end{table*}
-
-% alignments
-% single subjects (for Bland-Altman-Plots) 1st level
+Five additional $t$-contrasts we created for negative control purposes (see
+Table \ref{tab:av-contrasts}) by using regressors based on regressors of the AO
+stimulus.
+
+\begin{table*}[t] \caption{Contrasts of parameter estimates for the analysis of
+        the audio-visual movie (AV).  Contrast 1-5 aim to isolate the PPA.
+        Contrast 6-9 serve as negative control.  Contrast 10 serves as control
+        for moments when the narrator cues the listener about a switch of
+    settings, events that could be correlated with a switch of the soundscape.}
+    \label{tab:av-contrasts} \footnotesize \begin{tabular}{lll} \toprule
+        \textbf{nr.} &  \textbf{contrast} & \textbf{purpose} \\ \midrule 1 &
+        vse\_new > vpe\_old & PPA \tabularnewline 2 & vse\_new, vpe\_new >
+        vse\_old, vpe\_old & PPA \tabularnewline 3 & vse\_new > vse\_old & PPA
+        \tabularnewline 4 & vse\_new > vse\_old, vpe\_old & PPA \tabularnewline
+        5 & vse\_new, vpe\_new > vpe\_old & PPA \tabularnewline 6 & vno\_cut >
+        vse\_new & negative control \tabularnewline 7 & vno\_cut > vse\_old &
+        negative control \tabularnewline 8 & vno\_cut > vse\_new, vse\_old &
+        negative control \tabularnewline 9 & vno\_cut > vpe\_new, vpe\_old &
+        negative control \tabularnewline 10 & se\_new > se\_old & control for
+        narrator \tabularnewline \end{tabular} \end{table*}
+
+% alignments single subjects (for Bland-Altman-Plots) 1st level
 The GLM analysis that fitted each voxel's time course separately for each
@@
 
-% second level
-% model
+% second level model
 The second level analyses which averaged contrast estimates over the eight
@@
     soundscape; cf. control contrasts (e.g. \texttt{vse\_new} >
-    \texttt{pe\_old})}.
+    \texttt{pe\_old}).}
 % foreshadowing of narrator by soundscape

### 2020-12-04 paper/main.tex
move stimulus annotation to statistical analysis
table moving madness

@@
 We use publicly available functional magnetic resonance imaging data
-(studyforrest.org) to build canonical general linear model (GLM) $t$-contrasts
-and compare current results to results that we gained from a dedicated visual
-localizer experiment conducted with the same 14 participants.
+(studyforrest.org) of 14 subjects to build canonical general linear model (GLM)
+$t$-contrasts and compare current results to results that we gained from a
+dedicated visual localizer experiment conducted with same participants.
 % compare to visual localizer experiment group results
-On a group average level, results of our whole brain analyses show
-significantly increased activation restricted to the anterior part of the PPA
-that was defined using the visual localizer [as well as in the retrosplenial
-and lateral occipital cortex] of both hemispheres.
+On a group average level, results of our whole brain analyses show significantly
+increased activation restricted to the anterior part of the PPA that was defined
+using the visual localizer [as well as in the retrosplenial and lateral
+occipital cortex] of both hemispheres.
 % individual results
@@
 functions.
-%%%%%%%%%%%%%%%%%%%%%% trenne diese Sätze %%%%%%%%%%%%%%5
+% occipital cortex for vision -> two pathways
 The occipital cortex is considered to be primarily involved in the early stages
@@
 \citep{goodale1992separat, mishkin1982contribution}.
-%
+% PPA
 A classic example of a higher-level visual area in the ventral pathway is the
@@
 Further, they usually employed an explicit perceptual judgment task.
-%
+% conceptualized stimuli and blockl: disadvantages
 Block-design studies that use conceptualized stimuli and a task have the
@@
 participants paying attention to the stimuli.
-% disandvantage of stimuli and block
+% conceptualized stimuli and block: disadvantages
 Nevertheless, small sets of conceptualized stimuli and block-design paradigms
@@
 
-\todo[inline]{Ich würde mal die Frage antizipieren, wie gut passen die
-Annotationen zu den VIS Stimuli. Und die müsste meiner Meinung nach doppelt
-beantwortet werden. a) Durch genauere Beschreibung von VIS, b) durch genauere
-Ausführungen, wie welche Annotation dazu passt}
-
 % AO & AV stimulus name & references
@@
 % controlled luminance and size
-Images were matched in luminance and size of 400 $\times$\unit[400]{px}
+Images were matched in luminance and size of 400$\times$\unit[400]{px}
 (displayed at a size of approximately
-\unit[10]{$^{\circ}$}$\times$\unit[10]{$^{\circ}$} visual angle.
+\unit[10]{$^{\circ}$}$\times$\unit[10]{$^{\circ}$} visual angle).
 % procedure: presentation & instructions
@@
 
-\subsection{Naturalistic stimuli annotation}
-
-\todo[inline]{Ich würde abschnitt 2.8 (statistical analysis) teilen:
-    a) die regressors, die dann mit der beschreibung der annotation kombinieren
-    b) die eigentliche statistik)}
-
-\todo[inline]{Bei AV habt ihr cuts und locations benutzt? Cuts können doch auch
-zwischen zwei Gesichtern sein?!?}
-
-%
-Since we did not design the given naturalistic stimuli for optimal localization
-performance of the PPA, we operationalized the perception of landscapes and
-landmarks (compared to e.g. faces and objects) by annotating words spoken by the
-narrator of the audio-description as well as cuts and depicted locations in the
-movie.
-% todo stimuli were not designed for research purposes
+\subsection{Stimulation setup}
+
+% paradigm implementation
+In all three studies, stimulation was implemented with
+\href{http://www.psychopy.org}{PsychoPy} \citep{peirce2007psychopy} running on a
+computer with the NeuroDebian operating system \citep{halchenko2012open}.
+
+% AO
+In the AO study, visual instructions were presented on a rear-projection screen
+inside scanner bore using an LCD projector (DLA-G150CL, JVC Ltd.). During the
+functional scans, the projector presented a medium gray screen with the primary
+purpose to illuminate a participant's visual field in order to prevent premature
+fatigue.
+
+% AV & VIS
+In the AV and VIS study, visual instructions and stimuli were presented on a
+rear-projection screen using an LCD projector (JVC DLA RS66E, JVC Ltd., light
+transmission reduced to \unit[13.7]{\%} with a gray filter) connected to the
+stimulus computer.
+% screen size
+The movie was shown at a viewing distance of \unit[63]{cm} in \unit[720]{p}
+resolution at full width on a \unit[1280 $\times$ 1024]{pixel} screen with
+\unit[60]{Hz} video refresh rate and screen dimension of \unit[26.5 $\times$
+21.2]{cm}.
+% angle of view: AV
+In the AV study, this corresponded to \unit[23.75 $\times$ 13.5] or \unit[23.75
+$\times$ 10.25]{cm} when considering only the movie content and excluding the
+horizontal gray bars.
+% angle of view: VIS
+In the VIS study, stimulus images were displayed at a size of approximately
+\unit[10]$^{\circ}$ $\times$ \unit[10]$^{\circ}$ of visual angle.
+
+\todo[inline]{auditory stimulation was the same in AO and AV?}
+
+% AO & AV: auditory stimulation
+In the AO and AV study, auditory stimulation was delivered through an MR confon
+mkII+ driving custom-built in-ear headphones (HP-M01, MR confon GmbH, Magdeburg,
+Germany; \citep{baumgart1998electrodynamic}) that reduced the scanner noise by
+at least \unit[20–30]{dB}. Headphones were fed from an Aureon 7.1 USB (Terratec)
+sound card through an optical connection.
+
+\subsection{fMRI data acquisition}
+
+\todo[inline]{shorten this subsection a lot}
+
+% AO
+In the AO study, a whole-body \unit[7]{Tesla} Siemens MAGNETOM magnetic
+resonance scanner equipped with a local circularly polarized head transmit and a
+32 channel brain receive coil (Nova Medical, Inc., Wilmington, MA, USA) acquired
+T2*-weighted echo-planar images (gradient-echo, \unit[2]{s} repetition time
+(TR), \unit[22]{ms} echo time, \unit[0.78]{ms} echo spacing, \unit[1488]{Hz/Px}
+bandwidth, generalized autocalibrating partially parallel acquisition,
+acceleration factor 3, \unit[2]{Hz/Px} bandwidth in phase encoding direction).
+% slices
+36 axial slices (thickness \unit[1.4]{mm}, \unit[1.4 $\times$ 1.4]{mm} in-plane
+resolution, \unit[224]{mm} field-of-view, anterior-to-posterior phase encoding
+direction) with a \unit[10]{\%} inter-slice gap were recorded in ascending
+order.
+% slice orientation
+Slices were oriented to include the ventral portions of frontal and occipital
+cortex while minimizing intersection with the eyeballs.
+% FOV
+The field of view was centered on the approximate location of Heschl's gyrus.
+% motion correction
+EPI images were online-corrected for motion and geometric distortions [+++Oh, S.
+et al. 2012; In, M. \& Speck, O., 2012; Chung, J. et al., 2011+++]
+% auxiliary scans
+Auxiliary scans for slice alignment and motion- and distortion-correction were
+performed at the beginning of the first fMRI recording session and also after
+the break at the start of the recording for the second half of the movie.
+% AV & VIS
+In the AV and VIS study, a whole-body \unit[3]{Tesla} Philips Achieva dStream
+MRI scanner equipped with a 32 channel head coil acquired T2*-weighted
+echo-planar images (gradient-echo, \unit[2]{s} repetition time, \unit[30]{ms}
+echo time, \unit[90]{$^{\circ}$} flip angle, \unit[1943]{Hz/Px} bandwidth,
+parallel acquisition with sensitivity encoding (SENSE) reduction factor 2).
+% slices
+35 axial slices (thickness \unit[3.0]{mm}, \unit[10]{\%} inter-slice gap) with
+\unit[80 $\times$ 80]{voxels} (\unit[3.0 $\times$ 3.0]{mm} of in-plane
+resolution, \unit[240]{mm} field-of-view) and an anterior-to-posterior phase
+encoding direction were recorded in ascending order.
+% slice positioning
+Philips' ``SmartExam'' was used to automatically position slices in AC-PC
+orientation such that the topmost slice was located at the superior edge of the
+brain. This automatic slice positioning procedure was identical in the AV and
+VIS study, and yielded a congruent geometry across paradigms.
+% no. of volumes
+A total of 3599 volumes were recorded for each participant in each of the
+naturalistic stimulus paradigms (451, 441, 438, 488, 462, 439, 542, and 338
+volumes for segment 1–8).
+
+\subsection{Preprocessing}
+
+\todo[inline]{part regarding motion correction/co-registration might be
+incorrect}
+
+\todo[inline]{what is missing: As I see it, AO must have been downsampled to
+2.5x2.5x2.5 mm and AV must have been upsampled from 3.0 to 2.5mm??}
+
+% data sources
+% https://github.com/psychoinformatics-de/studyforrest-data-aligned/tree/master/code
+% https://github.com/psychoinformatics-de/studyforrest-data-templatetransforms}
+fMRI time series of those 15 participants in the studyforrest dataset that took
+part in all three experiments were obtained from
+\href{https://github.com/psychoinformatics-de/studyforrest-data-aligned}{GitHub}.
+Data were already corrected for motion and aligned by non-linear warping to a
+participant-specific BOLD template image \citep{sengupta2016extension}.
+% exclusion of VP 10
+Data of one participant were dropped to due to invalid distortion correction
+during scanning of the AO stimulus.
+
+% preprocessing intro
+All further analysis steps of the current study were carried out using tools of
+FSL v5.0.9 (\href{https://www.fmrib.ox.ac.uk/fsl}{FMRIB's Software Library};
+\citep{smith2004fsl}) on a computer cluster running the Debian GNU/Linux
+operating system. Software packages were obtained from repositories of
+\href{http://neuro.debian.net}{NeuroDebian} \citep{halchenko2012open}.
+
+% my preprocessing
+Preprocessing was carried out using FEAT v6.00 (FMRI Expert Analysis Tool;
+\citep{woolrich2001autocorr}) as part of FSL.
+% temporal filtering
+High-pass temporal filtering was applied to every stimulus segment using a
+Gaussian-weighted least-squares straight line with a cutoff period of
+\unit[150]{s} (sigma=\unit[75.0]{s}) to remove low-frequency confounds.
+% brain extraction
+The brain was extracted from surrounding tissues using BET \citep{smith2002bet}.
+% spatial smoothing
+Data were spatially smoothed applying a Gaussian kernel with full width at half
+maximum (FWHM) of \unit[4.0]{mm}.
+% normalization
+A grand-mean intensity normalization of the entire 4D dataset was performed by a
+single multiplicative factor.
+% pre-whithening
+Correction for local autocorrelation in the time series (prewhitening) was
+applied using FILM (FMRIB's Improved Linear Model; \citep{woolrich2001autocorr})
+to improve estimation efficiency.
+
+\subsection{Statistical analysis}
+
+% intro
+Similarly to the reviewed studies that employed simplified stimuli, we conducted
+a standard two-level general linear model (GLM) analysis to create
+subject-specific results ($Z$-maps) across the 8 segments for every subject. A
+subsequent, third-level analysis averaged contrast estimates over subjects.
+
+\subsubsection{Annotation of naturalistic stimuli}
+
+\todo[inline]{Ich weiss nicht, ob es die etwas wild zwischendrin stehenden
+    tables waren, die oft komplizierten Beschreibungen, die Länge des
+    Abschnittes, oder alles zusammen, aber ich habe mich mit 2.8 extrem schwer
+    getan. Bitte lass den Reviewer nicht mit dem selben Gefühl rausgehen. Gut
+strukturiert, einfach und klar ist immer vom Vorteil}
+
+\todo[inline]{SE: focus on the events that are relevant to the analysis to
+reduce complexity and explain these better}
+
+\todo[inline]{Simon suggested to put paragraphs regarding annotation here,
+    followed by a subsection ``Regressors''. Additionally imo, it makes sense to
+    build one subsection ``Stimulus annotations \& regressors'' to have a
+    structure of ``AO (anno \& regressors); AV (anno \& regressors'' instead of
+AO \& AV (annotation), AO \& AV (regressors)``.}
+
+\todo[inline]{Ich würde mal die Frage antizipieren, wie gut passen die
+Annotationen zu den VIS Stimuli. Und die müsste meiner Meinung nach doppelt
+beantwortet werden. a) Durch genauere Beschreibung von VIS, b) durch genauere
+Ausführungen, wie welche Annotation dazu passt}
+
+% intro
+Since we did not design the naturalistic stimuli for detection power, we
+operationalized the perception of landscapes and landmarks (compared to e.g.
+faces and objects) by annotating words spoken by the narrator of the
+audio-description as well as cuts and depicted locations in the movie.
+% stimuli not designed for research purposes
 Both natural stimuli were not design to isolate a specific brain area but to
@@
 
+\todo[inline]{Table 2 ist relativ kryptisch bzw für jemanden, der sich zum
+ersten Mal damit auseinander setzt kaum zu verstehen. Auch ist der Bezug zum GLM
+unklar, d.h., was davon wird verwendet und was verbirgt sich dahinter}
+
+% table for descriptive nouns: categories, rules, examples counts
+% table for descriptive nouns: categories, rules, examples counts
+\begin{table*}[h!]
+    \caption{Descriptive nouns spoken by the audio-description's narrator that
+        served as a basis to build the regressors
+(see Table \ref{tab:ao-events}):
+    categories, annotation rules, and examples (given in English).
+    % The category \texttt{++} also contains adverbial of time.
+}
+\label{tab:descr-nouns-rules}
+\begin{tabular}{lll}
+\toprule
+\textbf{category} & \textbf{rule} & \textbf{examples} \\
+\midrule
+body & trunk of the body; overlaid clothes & back, hip, shoulder; jacket, dress, shirt \tabularnewline
+bodypart & limbs and trousers & arm, finger, leg, toe \tabularnewline
+face & face or parts of it & face, ear, nose, mouth \tabularnewline
+female & female person & nurse, mother, woman \tabularnewline
+females & female persons & women \tabularnewline
+fname & female name & Jenny \tabularnewline
+furniture & movable furniture insides \& outsides & bench, bed, table, chair
+\tabularnewline
+geo & immobile landmarks & building, tree, street, alley, meadow, cornfield \tabularnewline
+geo-room & rooms (insides) or  locales (outsides) & living room; wall, door, window, floor, turf \tabularnewline
+head & non-face parts of the head; worn headgear & head, hair, ear, neck,
+helmet \tabularnewline
+male & male person & man, father, soldier \tabularnewline
+males & male persons & boys, opponents \tabularnewline
+mname & male name & Bubba, Kennedy \tabularnewline
+object & countable entity with firm boundaries & telephone, car \tabularnewline
+objects & countable entities & wheels, plants \tabularnewline
+persons & concrete persons of unknown sex & hippies, patients \tabularnewline
+setting\_new & noun cueing an unfamiliar setting &  on a ``bridge'', on an ``alley'', on ``campus'' \tabularnewline
+setting\_rec & noun cueing a recurring setting & at the ``bus stop'' \tabularnewline
+% ++ & cue regarding time & in the ``evening'', it's ``daytime'', ``later'' \tabularnewline
+\bottomrule
+\end{tabular}
+\end{table*}
+
+% table of descriptive nouns counts
+\begin{table*}[h!]
+    \caption{Descriptive nouns spoken by the audio-descriptions narrator:
+        counts for the whole audio-only stimulus and its eight segments used
+        during fMRI scanning.}
+\label{tab:descr-nouns-counts}
+\begin{tabular}{llllllllll}
+\toprule
+\textbf{category} & \textbf{all} & \textbf{1} & \textbf{2} & \textbf{3} & \textbf{4} & \textbf{5} & \textbf{6} & \textbf{7} & \textbf{8} \\
+\midrule
+body & \anBodyAll & \anBodyI & \anBodyII & \anBodyIII & \anBodyIV & \anBodyV & \anBodyVI & \anBodyVII & \anBodyVIII \tabularnewline
+bodypart &  \anBodypartAll & \anBodypartI & \anBodypartII & \anBodypartIII & \anBodypartIV & \anBodypartV & \anBodypartVI & \anBodypartVII & \anBodypartVIII \tabularnewline
+face & \anFaceAll & \anFaceI & \anFaceII & \anFaceIII & \anFaceIV & \anFaceV & \anFaceVI & \anFaceVII & \anFaceVIII \tabularnewline
+female & \anFemaleAll & \anFemaleI & \anFemaleII & \anFemaleIII & \anFemaleIV & \anFemaleV & \anFemaleVI & \anFemaleVII & \anFemaleVIII \tabularnewline
+females & \anFemalesAll & \anFemalesI & \anFemalesII & \anFemalesIII & \anFemalesIV & \anFemalesV & \anFemalesVI & \anFemalesVII & \anFemalesVIII \tabularnewline
+fname & \anFnameAll & \anFnameI & \anFnameII & \anFnameIII & \anFnameIV & \anFnameV & \anFnameVI & \anFnameVII & \anFnameVIII \tabularnewline
+furniture & \anFurnitureAll & \anFurnitureI & \anFurnitureII & \anFurnitureIII & \anFurnitureIV & \anFurnitureV & \anFurnitureVI & \anFurnitureVII & \anFurnitureVIII \tabularnewline
+geo & \anGeoAll & \anGeoI & \anGeoII & \anGeoIII & \anGeoIV & \anGeoV & \anGeoVI & \anGeoVII & \anGeoVIII \tabularnewline
+geo-room & \anGeoroomAll & \anGeoroomI & \anGeoroomII & \anGeoroomIII & \anGeoroomIV & \anGeoroomV & \anGeoroomVI & \anGeoroomVII & \anGeoroomVIII \tabularnewline
+head & \anHeadAll & \anHeadI & \anHeadII & \anHeadIII & \anHeadIV & \anHeadV & \anHeadVI & \anHeadVII & \anHeadVIII \tabularnewline
+male & \anMaleAll & \anMaleI & \anMaleII & \anMaleIII & \anMaleIV & \anMaleV & \anMaleVI & \anMaleVII & \anMaleVIII \tabularnewline
+males & \anMalesAll & \anMalesI & \anMalesII & \anMalesIII & \anMalesIV & \anMalesV & \anMalesVI & \anMalesVII & \anMalesVIII \tabularnewline
+mname & \anMnameAll & \anMnameI & \anMnameII & \anMnameIII & \anMnameIV & \anMnameV & \anMnameVI & \anMnameVII & \anMnameVIII \tabularnewline
+object & \anObjectAll & \anObjectI & \anObjectII & \anObjectIII & \anObjectIV & \anObjectV & \anObjectVI & \anObjectVII & \anObjectVIII \tabularnewline
+objects & \anObjectsAll & \anObjectsI & \anObjectsII & \anObjectsIII & \anObjectsIV & \anObjectsV & \anObjectsVI & \anObjectsVII & \anObjectsVIII \tabularnewline
+persons & \anPersonsAll & \anPersonsI & \anPersonsII & \anPersonsIII & \anPersonsIV & \anPersonsV & \anPersonsVI & \anPersonsVII & \anPersonsVIII \tabularnewline
+setting\_new & \anSettingnewAll & \anSettingnewI & \anSettingnewII & \anSettingnewIII & \anSettingnewIV & \anSettingnewV & \anSettingnewVI & \anSettingnewVII & \anSettingnewVIII \tabularnewline
+setting\_rec & \anSettingrecAll &
+\anSettingrecI & \anSettingrecII & \anSettingrecIII & \anSettingrecIV & \anSettingrecV & \anSettingrecVI & \anSettingrecVII & \anSettingrecVIII \tabularnewline
+% ++ & \anAll & \anI & \anII & \anIII & \anIV & \anV & \anVI & \anVII & \anVIII \tabularnewline
+\bottomrule
+\end{tabular}
+\end{table*}
+
+\todo[inline]{Bei AV habt ihr cuts und locations benutzt? Cuts können doch auch
+zwischen zwei Gesichtern sein?!?}
+
+\todo[inline]{besser erklären (was heißt "unfamilar perspective"? Ab wann ist
+ein setting "familiar"?)}
+
 % AV anno
@@
 viewer within the environment depicted in the movie.
-
-\todo[inline]{Table 2 ist relativ kryptisch bzw für jemanden, der sich zum
-ersten Mal damit auseinander setzt kaum zu verstehen. Auch ist der Bezug zum GLM
-unklar, d.h., was davon wird verwendet und was verbirgt sich dahinter}
-
-\todo[inline]{Ich merke das mal hier an: Die Tables stehen an ganz merkwürdigen
-Positionen, das passt nicht zum Text und verwirrt ungemein}
-
-% table for descriptive nouns: categories, rules, examples counts
-\begin{table*}[t] \caption{Descriptive nouns spoken by the audio-description's
-            narrator: categories, annotation rules, and examples (given in
-            English). The category \texttt{++} also contains adverbial of time.}
-            \label{tab:descr-nouns-rules} \begin{tabular}{lll} \toprule
-                \textbf{category} & \textbf{rule} & \textbf{examples} \\
-                \midrule body & trunk of the body; overlaid clothes & back, hip,
-                shoulder; jacket, dress, shirt \tabularnewline bodypart & limbs
-                and trousers & arm, finger, leg, toe \tabularnewline face & face
-                or parts of it & face, ear, nose, mouth \tabularnewline female &
-                female person & nurse, mother, woman \tabularnewline females &
-                female persons & women \tabularnewline fname & female name &
-                Jenny \tabularnewline furniture & movable furniture insides \&
-                outsides & bench, bed, table, chair \tabularnewline geo &
-                immobile landmarks & building, tree, street, alley, meadow,
-                cornfield \tabularnewline geo-room & rooms (insides) or  locales
-                (outsides) & living room; wall, door, window, floor, turf
-                \tabularnewline head & non-face parts of the head; worn headgear
-                & head, hair, ear, neck, helmet \tabularnewline male & male
-                person & man, father, soldier \tabularnewline males & male
-                persons & boys, opponents \tabularnewline mname & male name &
-                Bubba, Kennedy \tabularnewline object & countable entity with
-                firm boundaries & telephone, car \tabularnewline objects &
-                countable entities & wheels, plants \tabularnewline persons &
-                concrete persons of unknown sex & hippies, patients
-                \tabularnewline setting\_new & noun cueing an unfamiliar setting
-                &  on a ``bridge'', on an ``alley'', on ``campus''
-                \tabularnewline setting\_rec & noun cueing a recurring setting &
-                at the ``bus stop'' \tabularnewline ++ & cue regarding time & in
-                the ``evening'', it's ``daytime'', ``later'' \tabularnewline
-
-\bottomrule \end{tabular} \end{table*}
-
-% table of descriptive nouns counts
-\begin{table*}[t] \caption{Descriptive nouns spoken by the audio-descriptions
-        narrator: counts for the whole audio-only stimulus and its eight
-    segments used during fMRI scanning.} \label{tab:descr-nouns-counts}
-    \begin{tabular}{llllllllll} \toprule \textbf{category} & \textbf{all} &
-        \textbf{1} & \textbf{2} & \textbf{3} & \textbf{4} & \textbf{5} &
-        \textbf{6} & \textbf{7} & \textbf{8} \\ \midrule body & \anBodyAll &
-        \anBodyI & \anBodyII & \anBodyIII & \anBodyIV & \anBodyV & \anBodyVI &
-        \anBodyVII & \anBodyVIII \tabularnewline bodypart &  \anBodypartAll &
-        \anBodypartI & \anBodypartII & \anBodypartIII & \anBodypartIV &
-        \anBodypartV & \anBodypartVI & \anBodypartVII & \anBodypartVIII
-        \tabularnewline face & \anFaceAll & \anFaceI & \anFaceII & \anFaceIII &
-        \anFaceIV & \anFaceV & \anFaceVI & \anFaceVII & \anFaceVIII
-        \tabularnewline female & \anFemaleAll & \anFemaleI & \anFemaleII &
-        \anFemaleIII & \anFemaleIV & \anFemaleV & \anFemaleVI & \anFemaleVII &
-        \anFemaleVIII \tabularnewline females & \anFemalesAll & \anFemalesI &
-        \anFemalesII & \anFemalesIII & \anFemalesIV & \anFemalesV & \anFemalesVI
-        & \anFemalesVII & \anFemalesVIII \tabularnewline fname & \anFnameAll &
-        \anFnameI & \anFnameII & \anFnameIII & \anFnameIV & \anFnameV &
-        \anFnameVI & \anFnameVII & \anFnameVIII \tabularnewline furniture &
-        \anFurnitureAll & \anFurnitureI & \anFurnitureII & \anFurnitureIII &
-        \anFurnitureIV & \anFurnitureV & \anFurnitureVI & \anFurnitureVII &
-        \anFurnitureVIII \tabularnewline geo & \anGeoAll & \anGeoI & \anGeoII &
-        \anGeoIII & \anGeoIV & \anGeoV & \anGeoVI & \anGeoVII & \anGeoVIII
-        \tabularnewline geo-room & \anGeoroomAll & \anGeoroomI & \anGeoroomII &
-        \anGeoroomIII & \anGeoroomIV & \anGeoroomV & \anGeoroomVI &
-        \anGeoroomVII & \anGeoroomVIII \tabularnewline head & \anHeadAll &
-        \anHeadI & \anHeadII & \anHeadIII & \anHeadIV & \anHeadV & \anHeadVI &
-        \anHeadVII & \anHeadVIII \tabularnewline male & \anMaleAll & \anMaleI &
-        \anMaleII & \anMaleIII & \anMaleIV & \anMaleV & \anMaleVI & \anMaleVII &
-        \anMaleVIII \tabularnewline males & \anMalesAll & \anMalesI & \anMalesII
-        & \anMalesIII & \anMalesIV & \anMalesV & \anMalesVI & \anMalesVII &
-        \anMalesVIII \tabularnewline mname & \anMnameAll & \anMnameI &
-        \anMnameII & \anMnameIII & \anMnameIV & \anMnameV & \anMnameVI &
-        \anMnameVII & \anMnameVIII \tabularnewline object & \anObjectAll &
-        \anObjectI & \anObjectII & \anObjectIII & \anObjectIV & \anObjectV &
-        \anObjectVI & \anObjectVII & \anObjectVIII \tabularnewline objects &
-        \anObjectsAll & \anObjectsI & \anObjectsII & \anObjectsIII &
-        \anObjectsIV & \anObjectsV & \anObjectsVI & \anObjectsVII &
-        \anObjectsVIII \tabularnewline persons & \anPersonsAll & \anPersonsI &
-        \anPersonsII & \anPersonsIII & \anPersonsIV & \anPersonsV & \anPersonsVI
-        & \anPersonsVII & \anPersonsVIII \tabularnewline
-
-setting\_new & \anSettingnewAll & \anSettingnewI & \anSettingnewII &
-\anSettingnewIII & \anSettingnewIV & \anSettingnewV & \anSettingnewVI &
-\anSettingnewVII & \anSettingnewVIII \tabularnewline
-
-setting\_rec & \anSettingrecAll & \anSettingrecI & \anSettingrecII &
-\anSettingrecIII & \anSettingrecIV & \anSettingrecV & \anSettingrecVI &
-\anSettingrecVII & \anSettingrecVIII \tabularnewline ++ & \anAll & \anI & \anII
-& \anIII & \anIV & \anV & \anVI & \anVII & \anVIII \tabularnewline \bottomrule
-\end{tabular} \end{table*}
-
-\subsection{Stimulation setup}
-
-% paradigm implementation
-In all three studies, stimulation was implemented with
-\href{http://www.psychopy.org}{PsychoPy} \citep{peirce2007psychopy} running on a
-computer with the NeuroDebian operating system \citep{halchenko2012open}.
-
-% AO
-In the AO study, visual instructions were presented on a rear-projection screen
-inside scanner bore using an LCD projector (DLA-G150CL, JVC Ltd.). During the
-functional scans, the projector presented a medium gray screen with the primary
-purpose to illuminate a participant's visual field in order to prevent premature
-fatigue.
-
-% AV & VIS
-In the AV and VIS study, visual instructions and stimuli were presented on a
-rear-projection screen using an LCD projector (JVC DLA RS66E, JVC Ltd., light
-transmission reduced to \unit[13.7]{\%} with a gray filter) connected to the
-stimulus computer.
-% screen size
-The movie was shown at a viewing distance of \unit[63]{cm} in \unit[720]{p}
-resolution at full width on a \unit[1280 $\times$ 1024]{pixel} screen with
-\unit[60]{Hz} video refresh rate and screen dimension of \unit[26.5 $\times$
-21.2]{cm}.
-% angle of view: AV
-In the AV study, this corresponded to \unit[23.75 $\times$ 13.5] or \unit[23.75
-$\times$ 10.25]{cm} when considering only the movie content and excluding the
-horizontal gray bars.
-% angle of view: VIS
-In the VIS study, stimulus images were displayed at a size of approximately
-\unit[10]$^{\circ}$ $\times$ \unit[10]$^{\circ}$ of visual angle.
-
-\todo[inline]{auditory stimulation was the same in AO and AV?}
-
-% AO & AV: auditory stimulation
-In the AO and AV study, auditory stimulation was delivered through an MR confon
-mkII+ driving custom-built in-ear headphones (HP-M01, MR confon GmbH, Magdeburg,
-Germany; \citep{baumgart1998electrodynamic}) that reduced the scanner noise by
-at least \unit[20–30]{dB}. Headphones were fed from an Aureon 7.1 USB (Terratec)
-sound card through an optical connection.
-
-\subsection{fMRI data acquisition}
-
-\todo[inline]{shorten this subsection a lot}
-
-% AO
-In the AO study, a whole-body \unit[7]{Tesla} Siemens MAGNETOM magnetic
-resonance scanner equipped with a local circularly polarized head transmit and a
-32 channel brain receive coil (Nova Medical, Inc., Wilmington, MA, USA) acquired
-T2*-weighted echo-planar images (gradient-echo, \unit[2]{s} repetition time
-(TR), \unit[22]{ms} echo time, \unit[0.78]{ms} echo spacing, \unit[1488]{Hz/Px}
-bandwidth, generalized autocalibrating partially parallel acquisition,
-acceleration factor 3, \unit[2]{Hz/Px} bandwidth in phase encoding direction).
-% slices
-36 axial slices (thickness \unit[1.4]{mm}, \unit[1.4 $\times$ 1.4]{mm} in-plane
-resolution, \unit[224]{mm} field-of-view, anterior-to-posterior phase encoding
-direction) with a \unit[10]{\%} inter-slice gap were recorded in ascending
-order.
-% slice orientation
-Slices were oriented to include the ventral portions of frontal and occipital
-cortex while minimizing intersection with the eyeballs.
-% FOV
-The field of view was centered on the approximate location of Heschl's gyrus.
-% motion correction
-EPI images were online-corrected for motion and geometric distortions [+++Oh, S.
-et al. 2012; In, M. \& Speck, O., 2012; Chung, J. et al., 2011+++]
-% auxiliary scans
-Auxiliary scans for slice alignment and motion- and distortion-correction were
-performed at the beginning of the first fMRI recording session and also after
-the break at the start of the recording for the second half of the movie.
-% AV & VIS
-In the AV and VIS study, a whole-body \unit[3]{Tesla} Philips Achieva dStream
-MRI scanner equipped with a 32 channel head coil acquired T2*-weighted
-echo-planar images (gradient-echo, \unit[2]{s} repetition time, \unit[30]{ms}
-echo time, \unit[90]{$^{\circ}$} flip angle, \unit[1943]{Hz/Px} bandwidth,
-parallel acquisition with sensitivity encoding (SENSE) reduction factor 2).
-% slices
-35 axial slices (thickness \unit[3.0]{mm}, \unit[10]{\%} inter-slice gap) with
-\unit[80 $\times$ 80]{voxels} (\unit[3.0 $\times$ 3.0]{mm} of in-plane
-resolution, \unit[240]{mm} field-of-view) and an anterior-to-posterior phase
-encoding direction were recorded in ascending order.
-% slice positioning
-Philips' ``SmartExam'' was used to automatically position slices in AC-PC
-orientation such that the topmost slice was located at the superior edge of the
-brain. This automatic slice positioning procedure was identical in the AV and
-VIS study, and yielded a congruent geometry across paradigms.
-
-% no. of volumes
-A total of 3599 volumes were recorded for each participant in each of the
-naturalistic stimulus paradigms (451, 441, 438, 488, 462, 439, 542, and 338
-volumes for segment 1–8).
-
-\subsection{Preprocessing}
-
-\todo[inline]{part regarding motion correction/co-registration might be
-incorrect}
-
-\todo[inline]{what is missing: As I see it, AO must have been downsampled to
-2.5x2.5x2.5 mm and AV must have been upsampled from 3.0 to 2.5mm??}
-
-% data sources
-% https://github.com/psychoinformatics-de/studyforrest-data-aligned/tree/master/code
-% https://github.com/psychoinformatics-de/studyforrest-data-templatetransforms}
-fMRI time series of those 15 participants in the studyforrest dataset that took
-part in all three experiments were obtained from
-\href{https://github.com/psychoinformatics-de/studyforrest-data-aligned}{GitHub}.
-Data were already corrected for motion and aligned by non-linear warping to a
-participant-specific BOLD template image \citep{sengupta2016extension}.
-% exclusion of VP 10
-Data of one participant were dropped to due to invalid distortion correction
-during scanning of the AO stimulus.
-
-% preprocessing intro
-All further analysis steps of the current study were carried out using tools of
-FSL v5.0.9 (\href{https://www.fmrib.ox.ac.uk/fsl}{FMRIB's Software Library};
-\citep{smith2004fsl}) on a computer cluster running the Debian GNU/Linux
-operating system. Software packages were obtained from repositories of
-\href{http://neuro.debian.net}{NeuroDebian} \citep{halchenko2012open}.
-
-% my preprocessing
-Preprocessing was carried out using FEAT v6.00 (FMRI Expert Analysis Tool;
-\citep{woolrich2001autocorr}) as part of FSL.
-% temporal filtering
-High-pass temporal filtering was applied to every stimulus segment using a
-Gaussian-weighted least-squares straight line with a cutoff period of
-\unit[150]{s} (sigma=\unit[75.0]{s}) to remove low-frequency confounds.
-% brain extraction
-The brain was extracted from surrounding tissues using BET \citep{smith2002bet}.
-% spatial smoothing
-Data were spatially smoothed applying a Gaussian kernel with full width at half
-maximum (FWHM) of \unit[4.0]{mm}.
-% normalization
-A grand-mean intensity normalization of the entire 4D dataset was performed by a
-single multiplicative factor.
-% pre-whithening
-Correction for local autocorrelation in the time series (prewhitening) was
-applied using FILM (FMRIB's Improved Linear Model; \citep{woolrich2001autocorr})
-to improve estimation efficiency.
-
-\subsection{Statistical analysis}
-
-\todo[inline]{Ich weiss nicht, ob es die etwas wild zwischendrin stehenden
-    tables waren, die oft komplizierten Beschreibungen, die Länge des
-    Abschnittes, oder alles zusammen, aber ich habe mich mit 2.8 extrem schwer
-    getan. Bitte lass den Reviewer nicht mit dem selben Gefühl rausgehen. Gut
-strukturiert, einfach und klar ist immer vom Vorteil}
-
-\todo[inline]{Ich würde abschnitt 2.8 teilen (in die regressors, die dann mit
-der beschreibung der annotation kombinieren, und die eigentliche statistik)}
-
-Similarly to the reviewed studies that employed simplified stimuli, we conducted
-a standard two-level general linear model (GLM) analysis to create
-subject-specific results ($Z$-maps) across the 8 segments for every subject. A
-subsequent, third-level analysis averaged contrast estimates over subjects.
-
-\todo[inline]{better speak of conditions than categories?}
-
-\todo[inline]{Ich würde vorschlagen, dass Du Dich auf die Regressoren / Events
-konzentrierst, die hier wichtig sind, um die Komplexität zu reduzieren. Die aber
-dafür besser erklären (was heißt "unfamilar perspective"? Ab wann ist ein
-setting "familiar"?}
-
-\subsubsection{Annotation of naturalistic stimuli}
 
@@
 
-\begin{table*}[t] \caption{Overview of events to build the 18 regressors for the
+\begin{table*}[h!]
+    \caption{Overview of events to build the 18 regressors for the
         analysis of the audio-only (AO) stimulus. Some of the annotation's
@@
         description of the five control conditions for movie cuts see Table
-        \ref{tab:av-events}.} \label{tab:ao-events} \footnotesize
-        \begin{tabular}{lp{3.5cm}lllllllll} \toprule \textbf{label} &
-            \textbf{description} & \textbf{all} & \textbf{1} & \textbf{2} &
-            \textbf{3} & \textbf{4} & \textbf{5} & \textbf{6} & \textbf{7} &
-            \textbf{8} \\ \midrule body & trunk of the body or overlaid clothes
-            & \aoBodyAll & \aoBodyI & \aoBodyII & \aoBodyIII & \aoBodyIV &
-            \aoBodyV & \aoBodyVI & \aoBodyVII & \aoBodyVIII \tabularnewline
-            bpart & limbs and trousers & \aoBpartAll & \aoBpartI & \aoBpartII &
-            \aoBpartIII & \aoBpartIV & \aoBpartV & \aoBpartVI & \aoBpartVII &
-            \aoBpartVIII \tabularnewline fahead & face(parts) or head(parts) &
-            \aoFaheadAll & \aoFaheadI & \aoFaheadII & \aoFaheadIII & \aoFaheadIV
-            & \aoFaheadV & \aoFaheadVI & \aoFaheadVII & \aoFaheadVIII
-            \tabularnewline furn & moveable furniture insides \& outsides &
-            \aoFurnAll & \aoFurnI & \aoFurnII & \aoFurnIII & \aoFurnIV &
-            \aoFurnV & \aoFurnVI & \aoFurnVII & \aoFurnVIII \tabularnewline geo
-            & immobile landmarks & \aoGeoAll & \aoGeoI & \aoGeoII & \aoGeoIII &
-            \aoGeoIV & \aoGeoV & \aoGeoVI & \aoGeoVII & \aoGeoVIII
-            \tabularnewline groom & elements defining geometry of room &
-            \aoGroomAll & \aoGroomI & \aoGroomII & \aoGroomIII & \aoGroomIV &
-            \aoGroomV & \aoGroomVI & \aoGroomVII & \aoGroomVIII \tabularnewline
-            object & inanimate entities with firm boundaries & \aoObjAll &
-            \aoObjI & \aoObjII & \aoObjIII & \aoObjIV & \aoObjV & \aoObjVI &
-            \aoObjVII & \aoObjVIII \tabularnewline se\_new & noun cueing an
-            unfamiliar setting & \aoSenewAll & \aoSenewI & \aoSenewII &
-            \aoSenewIII & \aoSenewIV & \aoSenewV & \aoSenewVI & \aoSenewVII &
-            \aoSenewVIII \tabularnewline se\_old & noun cueing a recurring
-            setting & \aoSeoldAll & \aoSeoldI & \aoSeoldII & \aoSeoldIII &
-            \aoSeoldIV & \aoSeoldV & \aoSeoldVI & \aoSeoldVII & \aoSeoldVIII
-            \tabularnewline sex\_f & female person(s), name & \aoSexfAll &
-            \aoSexfI & \aoSexfII & \aoSexfIII & \aoSexfIV & \aoSexfV & \aoSexfVI
-            & \aoSexfVII & \aoSexfVIII \tabularnewline sex\_m & male person(s),
-            name & \aoSexmAll & \aoSexmI & \aoSexmII & \aoSexmIII & \aoSexmIV &
-            \aoSexmV & \aoSexmVI & \aoSexmVII & \aoSexmVIII \tabularnewline
+        \ref{tab:av-events}.}
+\label{tab:ao-events} \footnotesize
+\begin{tabular}{lp{3.5cm}lllllllll}
+\toprule \textbf{label} & \textbf{description} & \textbf{all} & \textbf{1} & \textbf{2} & \textbf{3} & \textbf{4} & \textbf{5} & \textbf{6} & \textbf{7} & \textbf{8} \\
+\midrule
+body & trunk of the body or overlaid clothes & \aoBodyAll & \aoBodyI & \aoBodyII
+& \aoBodyIII & \aoBodyIV & \aoBodyV & \aoBodyVI & \aoBodyVII & \aoBodyVIII
+\tabularnewline
+bpart & limbs and trousers & \aoBpartAll & \aoBpartI & \aoBpartII & \aoBpartIII & \aoBpartIV & \aoBpartV & \aoBpartVI & \aoBpartVII & \aoBpartVIII
+\tabularnewline
+fahead & face(parts) or head(parts) & \aoFaheadAll & \aoFaheadI & \aoFaheadII & \aoFaheadIII & \aoFaheadIV & \aoFaheadV & \aoFaheadVI & \aoFaheadVII & \aoFaheadVIII
+\tabularnewline
+furn & moveable furniture insides \& outsides & \aoFurnAll & \aoFurnI & \aoFurnII & \aoFurnIII & \aoFurnIV & \aoFurnV & \aoFurnVI & \aoFurnVII & \aoFurnVIII
+\tabularnewline
+geo & immobile landmarks & \aoGeoAll & \aoGeoI & \aoGeoII & \aoGeoIII & \aoGeoIV & \aoGeoV & \aoGeoVI & \aoGeoVII & \aoGeoVIII
+\tabularnewline
+groom & elements defining geometry of room & \aoGroomAll & \aoGroomI & \aoGroomII & \aoGroomIII & \aoGroomIV & \aoGroomV & \aoGroomVI & \aoGroomVII & \aoGroomVIII
+\tabularnewline
+object & inanimate entities with firm boundaries & \aoObjAll & \aoObjI & \aoObjII & \aoObjIII & \aoObjIV & \aoObjV & \aoObjVI & \aoObjVII & \aoObjVIII
+\tabularnewline
+se\_new & noun cueing an unfamiliar setting & \aoSenewAll & \aoSenewI & \aoSenewII & \aoSenewIII & \aoSenewIV & \aoSenewV & \aoSenewVI & \aoSenewVII & \aoSenewVIII
+\tabularnewline
+se\_old & noun cueing a recurring setting & \aoSeoldAll & \aoSeoldI & \aoSeoldII & \aoSeoldIII & \aoSeoldIV & \aoSeoldV & \aoSeoldVI & \aoSeoldVII & \aoSeoldVIII
+\tabularnewline
+sex\_f & female person(s), name & \aoSexfAll & \aoSexfI & \aoSexfII & \aoSexfIII & \aoSexfIV & \aoSexfV & \aoSexfVI & \aoSexfVII & \aoSexfVIII
+\tabularnewline
+sex\_m & male person(s), name & \aoSexmAll & \aoSexmI & \aoSexmII & \aoSexmIII & \aoSexmIV & \aoSexmV & \aoSexmVI & \aoSexmVII & \aoSexmVIII
+\tabularnewline
 % vlo_ch has no events in segment 5. So indices are shifted
@@
 \aoVsenewIII & \aoVsenewIV & \aoVsenewV & \aoVsenewVI & \aoVsenewVII &
-\aoVsenewVIII \tabularnewline vse\_old & control for movie cut & \aoVseoldAll &
-\aoVseoldI & \aoVseoldII & \aoVseoldIII & \aoVseoldIV & \aoVseoldV & \aoVseoldVI
-& \aoVseoldVII & \aoVseoldVIII \tabularnewline vlo\_ch & control for movie cut &
+\aoVsenewVIII
+\tabularnewline
+vse\_old & control for movie cut & \aoVseoldAll & \aoVseoldI & \aoVseoldII & \aoVseoldIII & \aoVseoldIV & \aoVseoldV & \aoVseoldVI & \aoVseoldVII & \aoVseoldVIII
+\tabularnewline
+vlo\_ch & control for movie cut &
 \aoVlochAll & \aoVlochI & \aoVlochII & \aoVlochIII & \aoVlochIV & 0 & \aoVlochV
-& \aoVlochVI & \aoVlochVII \tabularnewline vpe\_new & control for movie cut &
-\aoVpenewAll & \aoVpenewI & \aoVpenewII & \aoVpenewIII & \aoVpenewIV &
-\aoVpenewV & \aoVpenewVI & \aoVpenewVII & \aoVpenewVIII \tabularnewline
+& \aoVlochVI & \aoVlochVII
+\tabularnewline
+vpe\_new & control for movie cut & \aoVpenewAll & \aoVpenewI & \aoVpenewII & \aoVpenewIII & \aoVpenewIV & \aoVpenewV & \aoVpenewVI & \aoVpenewVII & \aoVpenewVIII
+\tabularnewline
 % vpe_old has no events in 3. So the indices are shifted
@@
 \aoVpeoldIII & \aoVpeoldIV & \aoVpeoldV & \aoVpeoldVI & \aoVpeoldVII
-\tabularnewline fg\_ad\_lrdiff & left-right volume difference & \aoFgadlrdiffAll
-& \aoFgadlrdiffI & \aoFgadlrdiffII & \aoFgadlrdiffIII & \aoFgadlrdiffIV &
+\tabularnewline
+fg\_ad\_lrdiff & left-right volume difference & \aoFgadlrdiffAll & \aoFgadlrdiffI & \aoFgadlrdiffII & \aoFgadlrdiffIII & \aoFgadlrdiffIV &
 \aoFgadlrdiffV & \aoFgadlrdiffVI & \aoFgadlrdiffVII & \aoFgadlrdiffVIII
-\tabularnewline fg\_ad\_rms & root mean square (loudness) & \aoFgadrmsAll &
+\tabularnewline
+fg\_ad\_rms & root mean square (loudness) & \aoFgadrmsAll &
 \aoFgadrmsI & \aoFgadrmsII & \aoFgadrmsIII & \aoFgadrmsIV & \aoFgadrmsV &
-\aoFgadrmsVI & \aoFgadrmsVII & \aoFgadrmsVIII \tabularnewline \bottomrule
-\end{tabular} \end{table*}
+\aoFgadrmsVI & \aoFgadrmsVII & \aoFgadrmsVIII
+\tabularnewline
+\bottomrule
+\end{tabular}
+\end{table*}
 
@@
 
-\begin{table*}[t] \caption{Overview of events to build the 14 regressors for the
-        analysis of the audio-visual (AV) stimulus.  \texttt{fg\_av\_ger\_pd}
-        (perceptual differences of consecutive frames), \texttt{fg\_av\_ger\_ml}
-        (mean luminance of a frame), \texttt{fg\_av\_ger\_lr} (difference in
-        mean luminance of left and right half), \texttt{fg\_av\_ger\_ud}
-        (difference in mean luminance of upper and lower half),
+\begin{table*}[h!]
+    \caption{Overview of events to build the 14 regressors for the analysis of
+        the audio-visual (AV) stimulus.
+        \texttt{fg\_av\_ger\_pd} (perceptual differences of consecutive frames),
+        \texttt{fg\_av\_ger\_ml} (mean luminance of a frame),
+        \texttt{fg\_av\_ger\_lr} (difference in mean luminance of left and right
+        half),
+        \texttt{fg\_av\_ger\_ud} (difference in mean luminance of upper and
+        lower half),
         \texttt{fg\_av\_ger\_lrdiff} (left-right volume difference), and
         \texttt{fg\_av\_ger\_rms} (root mean square volume) represent one event
-        for every movie frame (\unit[40]{ms}).  For description of the two event
-        categories of the audio-description's narrator (\texttt{se\_new} and
-        \texttt{se\_old}) to build contrast of negative control see Table
-        \ref{tab:ao-events}.} \label{tab:av-events} \footnotesize
-        \begin{tabular}{lp{3.5cm}lllllllll} \toprule \textbf{label} &
-            \textbf{description} & \textbf{all} & \textbf{1} & \textbf{2} &
-            \textbf{3} & \textbf{4} & \textbf{5} & \textbf{6} & \textbf{7} &
-            \textbf{8} \\ \midrule vse\_new &  change of the camera position to
-            a setting not depicted before & \aoVsenewAll & \aoVsenewI &
-            \aoVsenewII & \aoVsenewIII & \aoVsenewIV & \aoVsenewV & \aoVsenewVI
-            & \aoVsenewVII & \aoVsenewVIII \tabularnewline vse\_old & change of
-            the camera position to a recurring setting & \aoVseoldAll &
-            \aoVseoldI & \aoVseoldII & \aoVseoldIII & \aoVseoldIV & \aoVseoldV &
-            \aoVseoldVI & \aoVseoldVII & \aoVseoldVIII \tabularnewline vlo\_ch &
-            change of the camera position to another locale within the same
-            setting & \aoVlochAll & \aoVlochI & \aoVlochII & \aoVlochIII &
-            \aoVlochIV & 0 & \aoVlochV & \aoVlochVI & \aoVlochVII
-            \tabularnewline vpe\_new & change of the camera position within a
-            locale not depicted before & \aoVpenewAll & \aoVpenewI & \aoVpenewII
-            & \aoVpenewIII & \aoVpenewIV & \aoVpenewV & \aoVpenewVI &
-            \aoVpenewVII & \aoVpenewVIII \tabularnewline
+        for every movie frame (\unit[40]{ms}).
+        For description of the two event categories of the audio-description's
+        narrator (\texttt{se\_new} and \texttt{se\_old}) to build contrast of
+        negative control see Table
+\ref{tab:ao-events}.}
+\label{tab:av-events}
+\footnotesize
+\begin{tabular}{lp{3.5cm}lllllllll} \toprule \textbf{label} & \textbf{description} & \textbf{all} & \textbf{1} & \textbf{2} & \textbf{3} & \textbf{4} & \textbf{5} & \textbf{6} & \textbf{7} & \textbf{8} \\
+\midrule
+vse\_new &  change of the camera position to a setting not depicted before & \aoVsenewAll & \aoVsenewI & \aoVsenewII & \aoVsenewIII & \aoVsenewIV & \aoVsenewV & \aoVsenewVI & \aoVsenewVII & \aoVsenewVIII
+\tabularnewline vse\_old & change of the camera position to a recurring setting & \aoVseoldAll & \aoVseoldI & \aoVseoldII & \aoVseoldIII & \aoVseoldIV & \aoVseoldV & \aoVseoldVI & \aoVseoldVII & \aoVseoldVIII
+\tabularnewline
+vlo\_ch & change of the camera position to another locale within the same setting & \aoVlochAll & \aoVlochI & \aoVlochII & \aoVlochIII & \aoVlochIV & 0 & \aoVlochV & \aoVlochVI & \aoVlochVII
+\tabularnewline
+vpe\_new & change of the camera position within a locale not depicted before & \aoVpenewAll & \aoVpenewI & \aoVpenewII & \aoVpenewIII & \aoVpenewIV & \aoVpenewV & \aoVpenewVI & \aoVpenewVII & \aoVpenewVIII
+\tabularnewline
 % vpe_old has no events in 3. So the indices are shifted
@@
 \aoVpeoldAll & \aoVpeoldI & \aoVpeoldII & 0 & \aoVpeoldIII & \aoVpeoldIV &
-\aoVpeoldV & \aoVpeoldVI & \aoVpeoldVII \tabularnewline vno\_cut & a continuous
-frame from the same camera position & \avVnocutAll & \avVnocutI & \avVnocutII &
-0 & \avVnocutIII & \avVnocutIV & \avVnocutV & \avVnocutVI & \avVnocutVII
-\tabularnewline se\_new & control for AO narrator & \aoSenewAll & \aoSenewI &
-\aoSenewII & \aoSenewIII & \aoSenewIV & \aoSenewV & \aoSenewVI & \aoSenewVII &
-\aoSenewVIII \tabularnewline se\_old & control for AO narrator & \aoSeoldAll &
-\aoSeoldI & \aoSeoldII & \aoSeoldIII & \aoSeoldIV & \aoSeoldV & \aoSeoldVI &
-\aoSeoldVII & \aoSeoldVIII \tabularnewline fg\_av\_ger\_lr & left-right
-luminance difference & \avFgavgerlrAll & \avFgavgerlrI & \avFgavgerlrII &
-\avFgavgerlrIII & \avFgavgerlrIV & \avFgavgerlrV & \avFgavgerlrVI &
-\avFgavgerlrVII & \avFgavgerlrVIII \tabularnewline fg\_av\_ger\_lrdiff &
-left-right volume difference & \avFgavgerlrdiffAll & \avFgavgerlrdiffI &
-\avFgavgerlrdiffII & \avFgavgerlrdiffIII & \avFgavgerlrdiffIV &
-\avFgavgerlrdiffV & \avFgavgerlrdiffVI & \avFgavgerlrdiffVII &
-\avFgavgerlrdiffVIII \tabularnewline fg\_av\_ger\_ml & mean luminance &
-\avFgavgermlAll & \avFgavgermlI & \avFgavgermlII & \avFgavgermlIII &
-\avFgavgermlIV & \avFgavgermlV & \avFgavgermlVI & \avFgavgermlVII &
-\avFgavgermlVIII \tabularnewline fg\_av\_ger\_pd & perceptual difference &
-\avFgavgerpdAll & \avFgavgerpdI & \avFgavgerpdII & \avFgavgerpdIII &
-\avFgavgerpdIV & \avFgavgerpdV & \avFgavgerpdVI & \avFgavgerpdVII &
-\avFgavgerpdVIII \tabularnewline fg\_av\_ger\_rms & root mean square (loudness)
-& \avFgavgerrmsAll & \avFgavgerrmsI & \avFgavgerrmsII & \avFgavgerrmsIII &
-\avFgavgerrmsIV & \avFgavgerrmsV & \avFgavgerrmsVI & \avFgavgerrmsVII &
-\avFgavgerrmsVIII \tabularnewline fg\_av\_ger\_ud & upper-lower luminance
-difference & \avFgavgerudAll & \avFgavgerudI & \avFgavgerudII & \avFgavgerudIII
-& \avFgavgerudIV & \avFgavgerudV & \avFgavgerudVI & \avFgavgerudVII &
-\avFgavgerudVIII \tabularnewline \end{tabular} \end{table*}
+\aoVpeoldV & \aoVpeoldVI & \aoVpeoldVII
+\tabularnewline
+vno\_cut & a continuous frame from the same camera position & \avVnocutAll & \avVnocutI & \avVnocutII & 0 & \avVnocutIII & \avVnocutIV & \avVnocutV & \avVnocutVI & \avVnocutVII
+\tabularnewline
+se\_new & control for AO narrator & \aoSenewAll & \aoSenewI & \aoSenewII & \aoSenewIII & \aoSenewIV & \aoSenewV & \aoSenewVI & \aoSenewVII & \aoSenewVIII
+\tabularnewline
+se\_old & control for AO narrator & \aoSeoldAll & \aoSeoldI & \aoSeoldII & \aoSeoldIII & \aoSeoldIV & \aoSeoldV & \aoSeoldVI & \aoSeoldVII & \aoSeoldVIII
+\tabularnewline
+fg\_av\_ger\_lr & left-right luminance difference & \avFgavgerlrAll & \avFgavgerlrI & \avFgavgerlrII & \avFgavgerlrIII & \avFgavgerlrIV & \avFgavgerlrV & \avFgavgerlrVI & \avFgavgerlrVII & \avFgavgerlrVIII
+\tabularnewline
+fg\_av\_ger\_lrdiff & left-right volume difference & \avFgavgerlrdiffAll & \avFgavgerlrdiffI & \avFgavgerlrdiffII & \avFgavgerlrdiffIII & \avFgavgerlrdiffIV & \avFgavgerlrdiffV & \avFgavgerlrdiffVI & \avFgavgerlrdiffVII & \avFgavgerlrdiffVIII
+\tabularnewline
+fg\_av\_ger\_ml & mean luminance & \avFgavgermlAll & \avFgavgermlI & \avFgavgermlII & \avFgavgermlIII & \avFgavgermlIV & \avFgavgermlV & \avFgavgermlVI & \avFgavgermlVII & \avFgavgermlVIII
+\tabularnewline
+fg\_av\_ger\_pd & perceptual difference & \avFgavgerpdAll & \avFgavgerpdI & \avFgavgerpdII & \avFgavgerpdIII & \avFgavgerpdIV & \avFgavgerpdV & \avFgavgerpdVI & \avFgavgerpdVII & \avFgavgerpdVIII
+\tabularnewline
+fg\_av\_ger\_rms & root mean square (loudness) & \avFgavgerrmsAll & \avFgavgerrmsI & \avFgavgerrmsII & \avFgavgerrmsIII & \avFgavgerrmsIV & \avFgavgerrmsV & \avFgavgerrmsVI & \avFgavgerrmsVII & \avFgavgerrmsVIII
+\tabularnewline
+fg\_av\_ger\_ud & upper-lower luminance difference & \avFgavgerudAll & \avFgavgerudI & \avFgavgerudII & \avFgavgerudIII & \avFgavgerudIV & \avFgavgerudV & \avFgavgerudVI & \avFgavgerudVII & \avFgavgerudVIII
+\tabularnewline
+\end{tabular}
+\end{table*}
 
@@
 
-\begin{table*}[t] \caption{Contrasts of parameter estimates for the analysis of
-        the audio-only stimulus (AO). Contrast 1-8 aim to isolate the PPA
-        (\texttt{all non-geo} = body, bodypart, fahead, object, sex\_f, sex\_m).
-        Contrasts 9-13 serve as negative control at the moments of movie cuts
-        that could correlate with changes of the audio tracks soundscape (see
-        Table \ref{tab:av-contrasts}).} \label{tab:ao-contrasts} \footnotesize
-        \begin{tabular}{lll} \toprule \textbf{nr.} &  \textbf{contrast} &
-            \textbf{purpose} \\ \midrule 1 & geo, groom > all non-geo & PPA
-            \tabularnewline 2 & geo, groom, se\_new > all non-geo & PPA
-            \tabularnewline 3 & groom, se\_new, se\_old > all non-geo & PPA
-            \tabularnewline 4 & geo > all non-geo & PPA \tabularnewline 5 &
-            groom > all non-geo & PPA \tabularnewline 6 & se\_new > all non-geo
-            & PPA \tabularnewline 7 & se\_new, se\_old > all non-geo & PPA
-            \tabularnewline 8 & se\_new > se\_old & PPA \tabularnewline 9 &
-            vse\_new > vpe\_old & control at moments of cuts \tabularnewline 10
-            & vse\_new, vpe\_new > vse\_old, vpe\_old & control at moments of
-            cuts \tabularnewline 11 & vse\_new > vse\_old & control at moments
-            of cuts \tabularnewline 12 & vse\_new > vse\_old, vpe\_old & control
-            at moments of cuts \tabularnewline 13 & vse\_new, vpe\_new >
-            vpe\_old & control at moments of cuts \tabularnewline \end{tabular}
-    \end{table*}
-
 \todo[inline]{MH: I think it's better to explain the rationale of the regressors
@@
 
-\begin{table*}[t] \caption{Contrasts of parameter estimates for the analysis of
-        the audio-visual movie (AV).  Contrast 1-5 aim to isolate the PPA.
-        Contrast 6-9 serve as negative control.  Contrast 10 serves as control
-        for moments when the narrator cues the listener about a switch of
-    settings, events that could be correlated with a switch of the soundscape.}
-    \label{tab:av-contrasts} \footnotesize \begin{tabular}{lll} \toprule
-        \textbf{nr.} &  \textbf{contrast} & \textbf{purpose} \\ \midrule 1 &
-        vse\_new > vpe\_old & PPA \tabularnewline 2 & vse\_new, vpe\_new >
-        vse\_old, vpe\_old & PPA \tabularnewline 3 & vse\_new > vse\_old & PPA
-        \tabularnewline 4 & vse\_new > vse\_old, vpe\_old & PPA \tabularnewline
-        5 & vse\_new, vpe\_new > vpe\_old & PPA \tabularnewline 6 & vno\_cut >
-        vse\_new & negative control \tabularnewline 7 & vno\_cut > vse\_old &
-        negative control \tabularnewline 8 & vno\_cut > vse\_new, vse\_old &
-        negative control \tabularnewline 9 & vno\_cut > vpe\_new, vpe\_old &
-        negative control \tabularnewline 10 & se\_new > se\_old & control for
-        narrator \tabularnewline \end{tabular} \end{table*}
+\begin{table*}[h!]
+\caption{Contrasts of parameter estimates for the analysis of the audio-only stimulus (AO).
+Contrast 1-8 aim to isolate the PPA (\texttt{all non-geo} = body, bodypart,
+    fahead, object, sex\_f, sex\_m).
+Contrasts 9-13 serve as negative control at the moments of movie cuts that could
+    correlate with changes of the audio tracks soundscape (see Table \ref{tab:av-contrasts}).}
+\label{tab:ao-contrasts}
+\footnotesize
+\begin{tabular}{lll}
+\toprule
+\textbf{nr.} &  \textbf{contrast} & \textbf{purpose} \\
+\midrule
+1 & geo, groom > all non-geo & PPA \tabularnewline
+2 & geo, groom, se\_new > all non-geo & PPA \tabularnewline
+3 & groom, se\_new, se\_old > all non-geo & PPA \tabularnewline
+4 & geo > all non-geo & PPA \tabularnewline
+5 & groom > all non-geo & PPA \tabularnewline
+6 & se\_new > all non-geo & PPA \tabularnewline
+7 & se\_new, se\_old > all non-geo & PPA \tabularnewline
+8 & se\_new > se\_old & PPA \tabularnewline
+9 & vse\_new > vpe\_old & control at moments of cuts \tabularnewline
+10 & vse\_new, vpe\_new > vse\_old, vpe\_old & control at moments of cuts \tabularnewline
+11 & vse\_new > vse\_old & control at moments of cuts \tabularnewline
+12 & vse\_new > vse\_old, vpe\_old & control at moments of cuts \tabularnewline
+13 & vse\_new, vpe\_new > vpe\_old & control at moments of cuts \tabularnewline
+\end{tabular}
+\end{table*}
+
+\begin{table*}[h!]
+    \caption{Contrasts of parameter estimates for the analysis of the audio-visual movie (AV).
+Contrast 1-5 aim to isolate the PPA.
+    Contrast 6-9 serve as negative control.
+    Contrast 10 serves as control for moments when the narrator cues the
+    listener about a switch of settings, events that could be correlated with a
+    switch of the soundscape.}
+\label{tab:av-contrasts}
+\footnotesize
+\begin{tabular}{lll}
+\toprule
+\textbf{nr.} &  \textbf{contrast} & \textbf{purpose} \\
+\midrule
+1 & vse\_new > vpe\_old & PPA \tabularnewline
+2 & vse\_new, vpe\_new > vse\_old, vpe\_old & PPA \tabularnewline
+3 & vse\_new > vse\_old & PPA \tabularnewline
+4 & vse\_new > vse\_old, vpe\_old & PPA \tabularnewline
+5 & vse\_new, vpe\_new > vpe\_old & PPA \tabularnewline
+6 & vno\_cut > vse\_new & negative control \tabularnewline
+7 & vno\_cut > vse\_old & negative control \tabularnewline
+8 & vno\_cut > vse\_new, vse\_old & negative control \tabularnewline
+9 & vno\_cut > vpe\_new, vpe\_old & negative control \tabularnewline
+10 & se\_new > se\_old & control for narrator \tabularnewline
+\end{tabular}
+\end{table*}
 

### 2020-12-04 paper/main.tex
restructure annotation and regressors

@@
 \usepackage{babel}
+\usepackage{comment}
 \usepackage{svg}
@@
 
-\todo[inline]{describe ``localize / isolate'' in other words}
-
 \todo[inline]{Limit for main text (intro and discussion) = ca. 3k words;}
@@
 Further, they usually employed an explicit perceptual judgment task.
-% conceptualized stimuli and blockl: disadvantages
+% conceptualized stimuli and block: disadvantages
 Block-design studies that use conceptualized stimuli and a task have the
@@
 % averaging pros and cons
-The averaging approch improves signal-to-noise ratio (SNR) but does not
+The averaging approach improves signal-to-noise ratio (SNR) but does not
 characterize brain functions at an individual level, a prerequisite for the
@@
 \todo[inline]{SE: make motivation of study clearer; gap in research; how it
-    (might) adance(s) the field; make clearer how current study solves the
+    (might) advance(s) the field; make clearer how current study solves the
     problem; COH: I revised this part, it's clearer at least
@@
 during scanning of the AO stimulus.
-
 % preprocessing intro
@@
 
-\subsubsection{Annotation of naturalistic stimuli}
-
-\todo[inline]{Ich weiss nicht, ob es die etwas wild zwischendrin stehenden
-    tables waren, die oft komplizierten Beschreibungen, die Länge des
-    Abschnittes, oder alles zusammen, aber ich habe mich mit 2.8 extrem schwer
-    getan. Bitte lass den Reviewer nicht mit dem selben Gefühl rausgehen. Gut
-strukturiert, einfach und klar ist immer vom Vorteil}
+\subsubsection{Stimulus annotation and regressors}
+
+\todo[inline]{SE: habe mich mit 2.8 extrem schwer getan: Länge des Abschnitts,
+oft komplizierten Beschreibungen}
 
@@
 
-\todo[inline]{Simon suggested to put paragraphs regarding annotation here,
-    followed by a subsection ``Regressors''. Additionally imo, it makes sense to
-    build one subsection ``Stimulus annotations \& regressors'' to have a
-    structure of ``AO (anno \& regressors); AV (anno \& regressors'' instead of
-AO \& AV (annotation), AO \& AV (regressors)``.}
-
-\todo[inline]{Ich würde mal die Frage antizipieren, wie gut passen die
-Annotationen zu den VIS Stimuli. Und die müsste meiner Meinung nach doppelt
-beantwortet werden. a) Durch genauere Beschreibung von VIS, b) durch genauere
+\todo[inline]{SE: wie gut passen die Annotationen zu den VIS Stimuli -> genauere
 Ausführungen, wie welche Annotation dazu passt}
@@
 Since we did not design the naturalistic stimuli for detection power, we
-operationalized the perception of landscapes and landmarks (compared to e.g.
-faces and objects) by annotating words spoken by the narrator of the
-audio-description as well as cuts and depicted locations in the movie.
-% stimuli not designed for research purposes
-Both natural stimuli were not design to isolate a specific brain area but to
-entertain their audiences free from any perceptual or behavioral task.
-% fixed stimuli and operationalization
-We annotated the temporal structure of the fixed stimuls material to
-operationalize the perception of different stimulus features (e.g. the
-perception of landmarks and faces) and create GLM contrasts in the subsequent
-data analysis.
+annotated the temporal structure of the fixed stimuls material to operationalize
+the perception of different stimulus features and create regressors for the
+following GLM analysis.
+
+\paragraph{audio-description: annotation}
+
 % AO annotation
-For the analysis of the AO data, we extended an publicly available annotation of
+For the analysis of the AO data, we extended a publicly available annotation of
 speech \citep{haeusler2020speechanno} by further annotating words spoken by the
@@
 Two persons performed a categorization of nouns that the narrator uses to
-describe the movie's missing visual content.
-% categories in detail
-Nouns were categorized by the verbal clue they provide about the cinematographic
-scene's environment (\texttt{geo}, \texttt{geo-room}; \texttt{setting\_new},
-\texttt{setting\_old}), its inherent persons (e.g. \texttt{female},
-\texttt{male}, \texttt{persons}), a person's body or worn clothes
-(\texttt{face}, \texttt{head}, \texttt{body}, \texttt{bodypart}), and a scene's
-inherent objects (\texttt{object}, \texttt{furniture}).
+describe the movie's missing visual content based on a set of rules.
+% reference to table with rules and examples
+A complete overview of all 18 categories, the rule for a word to belong to a
+category, and examples can be seen in Table \ref{tab:descr-nouns-rules}.
+% procedure
+A preliminary annotation was performed by one person according to the rules.
+Minor corrections due to incorrectly applied rules were done by the author.
 % why and how of categories 1
-Some categories were created to reflect the six stimulus categories used in the
-visual localizer experiment (e.g. \texttt{geo}, \texttt{object}).
+Some categories reflect the verbal counterpart of the stimulus categories that
+were used in the visual localizer experiment (e.g. \texttt{body}, \texttt{face},
+\texttt{head}, \texttt{object}, \texttt{setting\_new}, and
+\texttt{setting\_rec}).
 % why and how of categories 2
 Other categories were created to semantically cluster some remaining nouns into
-additional categories (e.g. \texttt{fname}, \texttt{furniture})
-% problem with hierarchical categories
+categories that had no counterpart in the visual localizer experiment (e.g.
+\texttt{bodypart}, \texttt{female}, \texttt{fname}, \texttt{furniture},
+\texttt{geo}, \texttt{geo-room}, \texttt{male}, and \texttt{persons}).
+% categories in detail
+%Nouns were categorized by the verbal clue they provide about the
+%cinematographic scene's environment (\texttt{geo}, \texttt{geo-room};
+%\texttt{setting\_new}, \texttt{setting\_old}), its inherent persons (e.g.
+%\texttt{female}, \texttt{male}, \texttt{persons}), a person's body or worn
+%clothes (\texttt{face}, \texttt{head}, \texttt{body}, \texttt{bodypart}), and a
+%scene's inherent objects (\texttt{object}, \texttt{furniture}).  problem with
+%hierarchical categories
 Notably, the categories \texttt{setting\_new} and \texttt{setting\_rec} comprise
@@
 teenager'').
-% reference to table with rules and examples
-A complete overview of all 19 categories, the rule for a word to belong to a
-category, and examples can be seen in Table \ref{tab:descr-nouns-rules}.
-% procedure
-A preliminary annotation was performed by one person according to the rules.
-Minor corrections due to incorrectly applied rules were done by the author.
-% reference to table with counts
-The resulting counts for the whole stimulus and the eight stimulus segments used
-during fMRI scanning can be seen in Table \ref{tab:descr-nouns-counts}.
-
-\todo[inline]{Table 2 ist relativ kryptisch bzw für jemanden, der sich zum
-ersten Mal damit auseinander setzt kaum zu verstehen. Auch ist der Bezug zum GLM
-unklar, d.h., was davon wird verwendet und was verbirgt sich dahinter}
-
-% table for descriptive nouns: categories, rules, examples counts
+
 % table for descriptive nouns: categories, rules, examples counts
 \begin{table*}[h!]
-    \caption{Descriptive nouns spoken by the audio-description's narrator that
-        served as a basis to build the regressors
-(see Table \ref{tab:ao-events}):
-    categories, annotation rules, and examples (given in English).
+    \caption{Categories and rules to categorize the descriptive nouns spoken by
+        the audio-description's narrator. These categories served as a basis to
+        build the regressors of the GLM (cf. Table \ref{tab:ao-events}).
+        Examples are given in English.
         % The category \texttt{++} also contains adverbial of time.
@@
 \midrule
-body & trunk of the body; overlaid clothes & back, hip, shoulder; jacket, dress, shirt \tabularnewline
-bodypart & limbs and trousers & arm, finger, leg, toe \tabularnewline
-face & face or parts of it & face, ear, nose, mouth \tabularnewline
-female & female person & nurse, mother, woman \tabularnewline
-females & female persons & women \tabularnewline
-fname & female name & Jenny \tabularnewline
+body & trunk of the body; overlaid clothes & back, hip, shoulder; jacket, dress, shirt
+\tabularnewline
+bodypart & limbs and trousers & arm, finger, leg, toe
+\tabularnewline
+face & face or parts of it & face, ear, nose, mouth
+\tabularnewline
+female & female person & nurse, mother, woman
+\tabularnewline
+females & female persons & women
+\tabularnewline
+fname & female name & Jenny
+\tabularnewline
 furniture & movable furniture insides \& outsides & bench, bed, table, chair
@@
 geo & immobile landmarks & building, tree, street, alley, meadow, cornfield \tabularnewline
-geo-room & rooms (insides) or  locales (outsides) & living room; wall, door, window, floor, turf \tabularnewline
+geo-room & rooms (insides) or  locales (outsides) & living room; wall, door,
+window, floor, turf
+\tabularnewline
 head & non-face parts of the head; worn headgear & head, hair, ear, neck,
-helmet \tabularnewline
-male & male person & man, father, soldier \tabularnewline
-males & male persons & boys, opponents \tabularnewline
-mname & male name & Bubba, Kennedy \tabularnewline
-object & countable entity with firm boundaries & telephone, car \tabularnewline
-objects & countable entities & wheels, plants \tabularnewline
-persons & concrete persons of unknown sex & hippies, patients \tabularnewline
-setting\_new & noun cueing an unfamiliar setting &  on a ``bridge'', on an ``alley'', on ``campus'' \tabularnewline
-setting\_rec & noun cueing a recurring setting & at the ``bus stop'' \tabularnewline
+helmet
+\tabularnewline
+male & male person & man, father, soldier
+\tabularnewline
+males & male persons & boys, opponents
+\tabularnewline
+mname & male name & Bubba, Kennedy
+\tabularnewline
+object & countable entity with firm boundaries & telephone, car
+\tabularnewline
+objects & countable entities & wheels, plants
+\tabularnewline
+persons & concrete persons of unknown sex & hippies, patients
+\tabularnewline
+setting\_new & a setting occurring for the first time & on a ``bridge'', on an ``alley'', on ``campus''
+\tabularnewline
+setting\_rec & a recurring setting & at the ``bus stop'' \tabularnewline
 % ++ & cue regarding time & in the ``evening'', it's ``daytime'', ``later'' \tabularnewline
@@
 
-% table of descriptive nouns counts
+\todo[inline]{Table 2 ist relativ kryptisch bzw für jemanden, der sich zum
+    ersten Mal damit auseinander setzt kaum zu verstehen. Auch ist der Bezug zum
+    GLM unklar, d.h., was davon wird verwendet und was verbirgt sich dahinter;
+    COH: I dropped the table of counts per segment.  The information is
+    redundant since the counts are not the count of events of the actual
+regressors (cf. Table \ref{tab:av-events})}
+
+\begin{comment}
+% nouns counts
+The resulting counts for the whole stimulus and the eight stimulus segments used
+during fMRI scanning can be seen in Table \ref{tab:descr-nouns-counts}.
+
 \begin{table*}[h!]
@@
 
-\todo[inline]{Bei AV habt ihr cuts und locations benutzt? Cuts können doch auch
-zwischen zwei Gesichtern sein?!?}
-
-\todo[inline]{besser erklären (was heißt "unfamilar perspective"? Ab wann ist
-ein setting "familiar"?)}
-
-% AV anno
-For the analysis of the AV data, we took advantage of a publicly available
-annotation of movie cuts and depicted locations \citep{haeusler2016cutanno}.
-% rationale behind using movie cuts
-Our rationale was that cuts are ``spatially relevant'' events that re-orient the
-viewer within the environment depicted in the movie.
-
-\subsubsection{Regressors}
-
+\end{comment}
+
+% AO regressors
+\begin{table*}[h!]
+    \caption{Overview of events to build the 18 regressors for the
+        analysis of the audio-only (AO) stimulus. Some of the annotation's
+        original categories (female, females, fname; male, males, mname; face,
+        head; object, objects; see Table\ref{tab:descr-nouns-rules}) were pooled
+        into 11 new categories (\texttt{sex\_f}; \texttt{sex\_m};
+        \texttt{fahead}; \texttt{object}).  \texttt{fg\_ad\_lrdiff} (left-right
+        volume difference) and \texttt{fg\_ad\_rms} (root mean square volume)
+        represent one event for every movie frame (\unit[40]{ms}). For a
+        description of the five control conditions for movie cuts see Table
+        \ref{tab:av-events}.}
+\label{tab:ao-events} \footnotesize
+\begin{tabular}{lp{3.5cm}lllllllll}
+\toprule \textbf{label} & \textbf{description} & \textbf{all} & \textbf{1} & \textbf{2} & \textbf{3} & \textbf{4} & \textbf{5} & \textbf{6} & \textbf{7} & \textbf{8} \\
+\midrule
+body & trunk of the body or overlaid clothes & \aoBodyAll & \aoBodyI & \aoBodyII
+& \aoBodyIII & \aoBodyIV & \aoBodyV & \aoBodyVI & \aoBodyVII & \aoBodyVIII
+\tabularnewline
+bpart & limbs and trousers & \aoBpartAll & \aoBpartI & \aoBpartII & \aoBpartIII & \aoBpartIV & \aoBpartV & \aoBpartVI & \aoBpartVII & \aoBpartVIII
+\tabularnewline
+fahead & face(parts) or head(parts) & \aoFaheadAll & \aoFaheadI & \aoFaheadII & \aoFaheadIII & \aoFaheadIV & \aoFaheadV & \aoFaheadVI & \aoFaheadVII & \aoFaheadVIII
+\tabularnewline
+furn & moveable furniture insides \& outsides & \aoFurnAll & \aoFurnI & \aoFurnII & \aoFurnIII & \aoFurnIV & \aoFurnV & \aoFurnVI & \aoFurnVII & \aoFurnVIII
+\tabularnewline
+geo & immobile landmarks & \aoGeoAll & \aoGeoI & \aoGeoII & \aoGeoIII & \aoGeoIV & \aoGeoV & \aoGeoVI & \aoGeoVII & \aoGeoVIII
+\tabularnewline
+groom & elements defining geometry of room & \aoGroomAll & \aoGroomI & \aoGroomII & \aoGroomIII & \aoGroomIV & \aoGroomV & \aoGroomVI & \aoGroomVII & \aoGroomVIII
+\tabularnewline
+object & inanimate entities with firm boundaries & \aoObjAll & \aoObjI & \aoObjII & \aoObjIII & \aoObjIV & \aoObjV & \aoObjVI & \aoObjVII & \aoObjVIII
+\tabularnewline
+se\_new & noun cueing an unfamiliar setting & \aoSenewAll & \aoSenewI & \aoSenewII & \aoSenewIII & \aoSenewIV & \aoSenewV & \aoSenewVI & \aoSenewVII & \aoSenewVIII
+\tabularnewline
+se\_old & noun cueing a recurring setting & \aoSeoldAll & \aoSeoldI & \aoSeoldII & \aoSeoldIII & \aoSeoldIV & \aoSeoldV & \aoSeoldVI & \aoSeoldVII & \aoSeoldVIII
+\tabularnewline
+sex\_f & female person(s), name & \aoSexfAll & \aoSexfI & \aoSexfII & \aoSexfIII & \aoSexfIV & \aoSexfV & \aoSexfVI & \aoSexfVII & \aoSexfVIII
+\tabularnewline
+sex\_m & male person(s), name & \aoSexmAll & \aoSexmI & \aoSexmII & \aoSexmIII & \aoSexmIV & \aoSexmV & \aoSexmVI & \aoSexmVII & \aoSexmVIII
+\tabularnewline
+% vlo_ch has no events in segment 5. So indices are shifted
+vse\_new & control for movie cut & \aoVsenewAll & \aoVsenewI & \aoVsenewII &
+\aoVsenewIII & \aoVsenewIV & \aoVsenewV & \aoVsenewVI & \aoVsenewVII &
+\aoVsenewVIII
+\tabularnewline
+vse\_old & control for movie cut & \aoVseoldAll & \aoVseoldI & \aoVseoldII & \aoVseoldIII & \aoVseoldIV & \aoVseoldV & \aoVseoldVI & \aoVseoldVII & \aoVseoldVIII
+\tabularnewline
+vlo\_ch & control for movie cut &
+\aoVlochAll & \aoVlochI & \aoVlochII & \aoVlochIII & \aoVlochIV & 0 & \aoVlochV
+& \aoVlochVI & \aoVlochVII
+\tabularnewline
+vpe\_new & control for movie cut & \aoVpenewAll & \aoVpenewI & \aoVpenewII & \aoVpenewIII & \aoVpenewIV & \aoVpenewV & \aoVpenewVI & \aoVpenewVII & \aoVpenewVIII
+\tabularnewline
+% vpe_old has no events in 3. So the indices are shifted
+vpe\_old & control for movie cut & \aoVpeoldAll & \aoVpeoldI & \aoVpeoldII & 0 &
+\aoVpeoldIII & \aoVpeoldIV & \aoVpeoldV & \aoVpeoldVI & \aoVpeoldVII
+\tabularnewline
+fg\_ad\_lrdiff & left-right volume difference & \aoFgadlrdiffAll & \aoFgadlrdiffI & \aoFgadlrdiffII & \aoFgadlrdiffIII & \aoFgadlrdiffIV &
+\aoFgadlrdiffV & \aoFgadlrdiffVI & \aoFgadlrdiffVII & \aoFgadlrdiffVIII
+\tabularnewline
+fg\_ad\_rms & root mean square (loudness) & \aoFgadrmsAll &
+\aoFgadrmsI & \aoFgadrmsII & \aoFgadrmsIII & \aoFgadrmsIV & \aoFgadrmsV &
+\aoFgadrmsVI & \aoFgadrmsVII & \aoFgadrmsVIII
+\tabularnewline
+\bottomrule
+\end{tabular}
+\end{table*}
+
+\paragraph{audio-description: regressors}
 % first level analysis regressors AO: events
@@
 
+% modeling of regressors from events
+Events of both stimuli were convolved with a double gamma hemodynamic response
+function (HRF).
+
+\paragraph{movie: annotation}
+
+% AV anno
+For the analysis of the AV data, we took advantage of a publicly available
+annotation of movie cuts and depicted locations \citep{haeusler2016cutanno}.
+% rationale behind using movie cuts
+Our rationale was that cuts are ``spatially relevant'' events that re-orient the
+viewer within the environment depicted in the movie.
+
+\todo[inline]{Bei AV habt ihr cuts und locations benutzt? Cuts können doch auch
+zwischen zwei Gesichtern sein?!?; COH: that should be clearer now as the
+explanation of the regressors immediately follows the description of the
+annotation}
+
+\todo[inline]{besser erklären (was heißt "unfamilar perspective"? Ab wann ist
+ein setting "familiar"?)}
+
+\paragraph{movie: regressors}
+
+% AV regressors
 \begin{table*}[h!]
-    \caption{Overview of events to build the 18 regressors for the
-        analysis of the audio-only (AO) stimulus. Some of the annotation's
-        original categories (female, females, fname; male, males, mname; face,
-        head; object, objects; see Table\ref{tab:descr-nouns-rules}) were pooled
-        into 11 new categories (\texttt{sex\_f}; \texttt{sex\_m};
-        \texttt{fahead}; \texttt{object}).  \texttt{fg\_ad\_lrdiff} (left-right
-        volume difference) and \texttt{fg\_ad\_rms} (root mean square volume)
-        represent one event for every movie frame (\unit[40]{ms}). For a
-        description of the five control conditions for movie cuts see Table
-        \ref{tab:av-events}.}
-\label{tab:ao-events} \footnotesize
-\begin{tabular}{lp{3.5cm}lllllllll}
-\toprule \textbf{label} & \textbf{description} & \textbf{all} & \textbf{1} & \textbf{2} & \textbf{3} & \textbf{4} & \textbf{5} & \textbf{6} & \textbf{7} & \textbf{8} \\
+    \caption{Overview of events to build the 14 regressors for the analysis of
+        the audio-visual (AV) stimulus.
+        \texttt{fg\_av\_ger\_pd} (perceptual differences of consecutive frames),
+        \texttt{fg\_av\_ger\_ml} (mean luminance of a frame),
+        \texttt{fg\_av\_ger\_lr} (difference in mean luminance of left and right
+        half),
+        \texttt{fg\_av\_ger\_ud} (difference in mean luminance of upper and
+        lower half),
+        \texttt{fg\_av\_ger\_lrdiff} (left-right volume difference), and
+        \texttt{fg\_av\_ger\_rms} (root mean square volume) represent one event
+        for every movie frame (\unit[40]{ms}).
+        For description of the two event categories of the audio-description's
+        narrator (\texttt{se\_new} and \texttt{se\_old}) to build contrast of
+        negative control see Table
+\ref{tab:ao-events}.}
+\label{tab:av-events}
+\footnotesize
+\begin{tabular}{lp{3.5cm}lllllllll} \toprule \textbf{label} & \textbf{description} & \textbf{all} & \textbf{1} & \textbf{2} & \textbf{3} & \textbf{4} & \textbf{5} & \textbf{6} & \textbf{7} & \textbf{8} \\
 \midrule
-body & trunk of the body or overlaid clothes & \aoBodyAll & \aoBodyI & \aoBodyII
-& \aoBodyIII & \aoBodyIV & \aoBodyV & \aoBodyVI & \aoBodyVII & \aoBodyVIII
-\tabularnewline
-bpart & limbs and trousers & \aoBpartAll & \aoBpartI & \aoBpartII & \aoBpartIII & \aoBpartIV & \aoBpartV & \aoBpartVI & \aoBpartVII & \aoBpartVIII
-\tabularnewline
-fahead & face(parts) or head(parts) & \aoFaheadAll & \aoFaheadI & \aoFaheadII & \aoFaheadIII & \aoFaheadIV & \aoFaheadV & \aoFaheadVI & \aoFaheadVII & \aoFaheadVIII
-\tabularnewline
-furn & moveable furniture insides \& outsides & \aoFurnAll & \aoFurnI & \aoFurnII & \aoFurnIII & \aoFurnIV & \aoFurnV & \aoFurnVI & \aoFurnVII & \aoFurnVIII
-\tabularnewline
-geo & immobile landmarks & \aoGeoAll & \aoGeoI & \aoGeoII & \aoGeoIII & \aoGeoIV & \aoGeoV & \aoGeoVI & \aoGeoVII & \aoGeoVIII
-\tabularnewline
-groom & elements defining geometry of room & \aoGroomAll & \aoGroomI & \aoGroomII & \aoGroomIII & \aoGroomIV & \aoGroomV & \aoGroomVI & \aoGroomVII & \aoGroomVIII
-\tabularnewline
-object & inanimate entities with firm boundaries & \aoObjAll & \aoObjI & \aoObjII & \aoObjIII & \aoObjIV & \aoObjV & \aoObjVI & \aoObjVII & \aoObjVIII
-\tabularnewline
-se\_new & noun cueing an unfamiliar setting & \aoSenewAll & \aoSenewI & \aoSenewII & \aoSenewIII & \aoSenewIV & \aoSenewV & \aoSenewVI & \aoSenewVII & \aoSenewVIII
-\tabularnewline
-se\_old & noun cueing a recurring setting & \aoSeoldAll & \aoSeoldI & \aoSeoldII & \aoSeoldIII & \aoSeoldIV & \aoSeoldV & \aoSeoldVI & \aoSeoldVII & \aoSeoldVIII
-\tabularnewline
-sex\_f & female person(s), name & \aoSexfAll & \aoSexfI & \aoSexfII & \aoSexfIII & \aoSexfIV & \aoSexfV & \aoSexfVI & \aoSexfVII & \aoSexfVIII
-\tabularnewline
-sex\_m & male person(s), name & \aoSexmAll & \aoSexmI & \aoSexmII & \aoSexmIII & \aoSexmIV & \aoSexmV & \aoSexmVI & \aoSexmVII & \aoSexmVIII
-\tabularnewline
-% vlo_ch has no events in segment 5. So indices are shifted
-vse\_new & control for movie cut & \aoVsenewAll & \aoVsenewI & \aoVsenewII &
-\aoVsenewIII & \aoVsenewIV & \aoVsenewV & \aoVsenewVI & \aoVsenewVII &
-\aoVsenewVIII
-\tabularnewline
-vse\_old & control for movie cut & \aoVseoldAll & \aoVseoldI & \aoVseoldII & \aoVseoldIII & \aoVseoldIV & \aoVseoldV & \aoVseoldVI & \aoVseoldVII & \aoVseoldVIII
-\tabularnewline
-vlo\_ch & control for movie cut &
-\aoVlochAll & \aoVlochI & \aoVlochII & \aoVlochIII & \aoVlochIV & 0 & \aoVlochV
-& \aoVlochVI & \aoVlochVII
-\tabularnewline
-vpe\_new & control for movie cut & \aoVpenewAll & \aoVpenewI & \aoVpenewII & \aoVpenewIII & \aoVpenewIV & \aoVpenewV & \aoVpenewVI & \aoVpenewVII & \aoVpenewVIII
+vse\_new &  change of the camera position to a setting not depicted before & \aoVsenewAll & \aoVsenewI & \aoVsenewII & \aoVsenewIII & \aoVsenewIV & \aoVsenewV & \aoVsenewVI & \aoVsenewVII & \aoVsenewVIII
+\tabularnewline vse\_old & change of the camera position to a recurring setting & \aoVseoldAll & \aoVseoldI & \aoVseoldII & \aoVseoldIII & \aoVseoldIV & \aoVseoldV & \aoVseoldVI & \aoVseoldVII & \aoVseoldVIII
+\tabularnewline
+vlo\_ch & change of the camera position to another locale within the same setting & \aoVlochAll & \aoVlochI & \aoVlochII & \aoVlochIII & \aoVlochIV & 0 & \aoVlochV & \aoVlochVI & \aoVlochVII
+\tabularnewline
+vpe\_new & change of the camera position within a locale not depicted before & \aoVpenewAll & \aoVpenewI & \aoVpenewII & \aoVpenewIII & \aoVpenewIV & \aoVpenewV & \aoVpenewVI & \aoVpenewVII & \aoVpenewVIII
 \tabularnewline
 % vpe_old has no events in 3. So the indices are shifted
-vpe\_old & control for movie cut & \aoVpeoldAll & \aoVpeoldI & \aoVpeoldII & 0 &
-\aoVpeoldIII & \aoVpeoldIV & \aoVpeoldV & \aoVpeoldVI & \aoVpeoldVII
-\tabularnewline
-fg\_ad\_lrdiff & left-right volume difference & \aoFgadlrdiffAll & \aoFgadlrdiffI & \aoFgadlrdiffII & \aoFgadlrdiffIII & \aoFgadlrdiffIV &
-\aoFgadlrdiffV & \aoFgadlrdiffVI & \aoFgadlrdiffVII & \aoFgadlrdiffVIII
-\tabularnewline
-fg\_ad\_rms & root mean square (loudness) & \aoFgadrmsAll &
-\aoFgadrmsI & \aoFgadrmsII & \aoFgadrmsIII & \aoFgadrmsIV & \aoFgadrmsV &
-\aoFgadrmsVI & \aoFgadrmsVII & \aoFgadrmsVIII
-\tabularnewline
-\bottomrule
+vpe\_old & change of the camera position within a recurring locale &
+\aoVpeoldAll & \aoVpeoldI & \aoVpeoldII & 0 & \aoVpeoldIII & \aoVpeoldIV &
+\aoVpeoldV & \aoVpeoldVI & \aoVpeoldVII
+\tabularnewline
+vno\_cut & a continuous frame from the same camera position & \avVnocutAll & \avVnocutI & \avVnocutII & 0 & \avVnocutIII & \avVnocutIV & \avVnocutV & \avVnocutVI & \avVnocutVII
+\tabularnewline
+se\_new & control for AO narrator & \aoSenewAll & \aoSenewI & \aoSenewII & \aoSenewIII & \aoSenewIV & \aoSenewV & \aoSenewVI & \aoSenewVII & \aoSenewVIII
+\tabularnewline
+se\_old & control for AO narrator & \aoSeoldAll & \aoSeoldI & \aoSeoldII & \aoSeoldIII & \aoSeoldIV & \aoSeoldV & \aoSeoldVI & \aoSeoldVII & \aoSeoldVIII
+\tabularnewline
+fg\_av\_ger\_lr & left-right luminance difference & \avFgavgerlrAll & \avFgavgerlrI & \avFgavgerlrII & \avFgavgerlrIII & \avFgavgerlrIV & \avFgavgerlrV & \avFgavgerlrVI & \avFgavgerlrVII & \avFgavgerlrVIII
+\tabularnewline
+fg\_av\_ger\_lrdiff & left-right volume difference & \avFgavgerlrdiffAll & \avFgavgerlrdiffI & \avFgavgerlrdiffII & \avFgavgerlrdiffIII & \avFgavgerlrdiffIV & \avFgavgerlrdiffV & \avFgavgerlrdiffVI & \avFgavgerlrdiffVII & \avFgavgerlrdiffVIII
+\tabularnewline
+fg\_av\_ger\_ml & mean luminance & \avFgavgermlAll & \avFgavgermlI & \avFgavgermlII & \avFgavgermlIII & \avFgavgermlIV & \avFgavgermlV & \avFgavgermlVI & \avFgavgermlVII & \avFgavgermlVIII
+\tabularnewline
+fg\_av\_ger\_pd & perceptual difference & \avFgavgerpdAll & \avFgavgerpdI & \avFgavgerpdII & \avFgavgerpdIII & \avFgavgerpdIV & \avFgavgerpdV & \avFgavgerpdVI & \avFgavgerpdVII & \avFgavgerpdVIII
+\tabularnewline
+fg\_av\_ger\_rms & root mean square (loudness) & \avFgavgerrmsAll & \avFgavgerrmsI & \avFgavgerrmsII & \avFgavgerrmsIII & \avFgavgerrmsIV & \avFgavgerrmsV & \avFgavgerrmsVI & \avFgavgerrmsVII & \avFgavgerrmsVIII
+\tabularnewline
+fg\_av\_ger\_ud & upper-lower luminance difference & \avFgavgerudAll & \avFgavgerudI & \avFgavgerudII & \avFgavgerudIII & \avFgavgerudIV & \avFgavgerudV & \avFgavgerudVI & \avFgavgerudVII & \avFgavgerudVIII
+\tabularnewline
 \end{tabular}
@@
 
-\begin{table*}[h!]
-    \caption{Overview of events to build the 14 regressors for the analysis of
-        the audio-visual (AV) stimulus.
-        \texttt{fg\_av\_ger\_pd} (perceptual differences of consecutive frames),
-        \texttt{fg\_av\_ger\_ml} (mean luminance of a frame),
-        \texttt{fg\_av\_ger\_lr} (difference in mean luminance of left and right
-        half),
-        \texttt{fg\_av\_ger\_ud} (difference in mean luminance of upper and
-        lower half),
-        \texttt{fg\_av\_ger\_lrdiff} (left-right volume difference), and
-        \texttt{fg\_av\_ger\_rms} (root mean square volume) represent one event
-        for every movie frame (\unit[40]{ms}).
-        For description of the two event categories of the audio-description's
-        narrator (\texttt{se\_new} and \texttt{se\_old}) to build contrast of
-        negative control see Table
-\ref{tab:ao-events}.}
-\label{tab:av-events}
-\footnotesize
-\begin{tabular}{lp{3.5cm}lllllllll} \toprule \textbf{label} & \textbf{description} & \textbf{all} & \textbf{1} & \textbf{2} & \textbf{3} & \textbf{4} & \textbf{5} & \textbf{6} & \textbf{7} & \textbf{8} \\
-\midrule
-vse\_new &  change of the camera position to a setting not depicted before & \aoVsenewAll & \aoVsenewI & \aoVsenewII & \aoVsenewIII & \aoVsenewIV & \aoVsenewV & \aoVsenewVI & \aoVsenewVII & \aoVsenewVIII
-\tabularnewline vse\_old & change of the camera position to a recurring setting & \aoVseoldAll & \aoVseoldI & \aoVseoldII & \aoVseoldIII & \aoVseoldIV & \aoVseoldV & \aoVseoldVI & \aoVseoldVII & \aoVseoldVIII
-\tabularnewline
-vlo\_ch & change of the camera position to another locale within the same setting & \aoVlochAll & \aoVlochI & \aoVlochII & \aoVlochIII & \aoVlochIV & 0 & \aoVlochV & \aoVlochVI & \aoVlochVII
-\tabularnewline
-vpe\_new & change of the camera position within a locale not depicted before & \aoVpenewAll & \aoVpenewI & \aoVpenewII & \aoVpenewIII & \aoVpenewIV & \aoVpenewV & \aoVpenewVI & \aoVpenewVII & \aoVpenewVIII
-\tabularnewline
-% vpe_old has no events in 3. So the indices are shifted
-vpe\_old & change of the camera position within a recurring locale &
-\aoVpeoldAll & \aoVpeoldI & \aoVpeoldII & 0 & \aoVpeoldIII & \aoVpeoldIV &
-\aoVpeoldV & \aoVpeoldVI & \aoVpeoldVII
-\tabularnewline
-vno\_cut & a continuous frame from the same camera position & \avVnocutAll & \avVnocutI & \avVnocutII & 0 & \avVnocutIII & \avVnocutIV & \avVnocutV & \avVnocutVI & \avVnocutVII
-\tabularnewline
-se\_new & control for AO narrator & \aoSenewAll & \aoSenewI & \aoSenewII & \aoSenewIII & \aoSenewIV & \aoSenewV & \aoSenewVI & \aoSenewVII & \aoSenewVIII
-\tabularnewline
-se\_old & control for AO narrator & \aoSeoldAll & \aoSeoldI & \aoSeoldII & \aoSeoldIII & \aoSeoldIV & \aoSeoldV & \aoSeoldVI & \aoSeoldVII & \aoSeoldVIII
-\tabularnewline
-fg\_av\_ger\_lr & left-right luminance difference & \avFgavgerlrAll & \avFgavgerlrI & \avFgavgerlrII & \avFgavgerlrIII & \avFgavgerlrIV & \avFgavgerlrV & \avFgavgerlrVI & \avFgavgerlrVII & \avFgavgerlrVIII
-\tabularnewline
-fg\_av\_ger\_lrdiff & left-right volume difference & \avFgavgerlrdiffAll & \avFgavgerlrdiffI & \avFgavgerlrdiffII & \avFgavgerlrdiffIII & \avFgavgerlrdiffIV & \avFgavgerlrdiffV & \avFgavgerlrdiffVI & \avFgavgerlrdiffVII & \avFgavgerlrdiffVIII
-\tabularnewline
-fg\_av\_ger\_ml & mean luminance & \avFgavgermlAll & \avFgavgermlI & \avFgavgermlII & \avFgavgermlIII & \avFgavgermlIV & \avFgavgermlV & \avFgavgermlVI & \avFgavgermlVII & \avFgavgermlVIII
-\tabularnewline
-fg\_av\_ger\_pd & perceptual difference & \avFgavgerpdAll & \avFgavgerpdI & \avFgavgerpdII & \avFgavgerpdIII & \avFgavgerpdIV & \avFgavgerpdV & \avFgavgerpdVI & \avFgavgerpdVII & \avFgavgerpdVIII
-\tabularnewline
-fg\_av\_ger\_rms & root mean square (loudness) & \avFgavgerrmsAll & \avFgavgerrmsI & \avFgavgerrmsII & \avFgavgerrmsIII & \avFgavgerrmsIV & \avFgavgerrmsV & \avFgavgerrmsVI & \avFgavgerrmsVII & \avFgavgerrmsVIII
-\tabularnewline
-fg\_av\_ger\_ud & upper-lower luminance difference & \avFgavgerudAll & \avFgavgerudI & \avFgavgerudII & \avFgavgerudIII & \avFgavgerudIV & \avFgavgerudV & \avFgavgerudVI & \avFgavgerudVII & \avFgavgerudVIII
-\tabularnewline
-\end{tabular}
-\end{table*}
-
-%
-\todo[inline]{Die Abkürzungen in Figure 1: Da steigt keiner hinter}
-
-\todo[inline]{Habe jetzt lange darüber gebrütet: Es gibt also kaum eine
-Korrelation zwischen AO und AV?; Also, außer bei fg\_av\_ger\_lr\_diff (wobei da
-keiner weiss, was das bedeutet)}
+\paragraph{regressor correlations}
+
 % reference to figure ``correlation of regressors''
@@
 
+\todo[inline]{Die Abkürzungen in Figure 1: Da steigt keiner hinter}
+
+\todo[inline]{Habe jetzt lange darüber gebrütet: Es gibt also kaum eine
+Korrelation zwischen AO und AV?; Also, außer bei fg\_av\_ger\_lr\_diff (wobei da
+keiner weiss, was das bedeutet)}
+
 \begin{figure*} \centering
@@
         root mean square loudness and between their left-right difference in
-        loudness yielded the highest correlation values (\texttt{fg\_ad\_rms}
-        and \texttt{fg\_av\_ger\_rms}, r=.7635 \texttt{fg\_ad\_lrdiff} and
-        \texttt{fg\_av\_ger\_lrdiff}, r=.7749).} \label{fig:reg-corr}
+        loudness yielded the highest correlation values
+        (\texttt{fg\_ad\_rms} and \texttt{fg\_av\_ger\_rms}, r=.7635;
+        \texttt{fg\_ad\_lrdiff} and \texttt{fg\_av\_ger\_lrdiff}, r=.7749).}
+\label{fig:reg-corr}
 \end{figure*}
 
-\todo[inline]{MH: construction of contrasts of interests feels "messy";
-    consequence of the inability to filter the stimulus material. That "messy"
-    part is usually not obvious from a manuscript. Here we have a fixed, complex
-    stimulus, and we have to operationalize our questions with whatever we have
-at hand. This is not necessarily exact, and looking at the robustness is a
-feature, not a problem; COH: did not change a lot of text tbh but should be
-clearer now.}
-
-%
+\subsubsection{Contrasts}
+
 \todo[inline]{Das mit den 8 kontrasten und 5 kontrasten habe ich nicht intuitiv

### 2020-12-06 paper/main.tex
better explain AO and AV categories and regressors

@@
 % AO annotation
-For the analysis of the AO data, we extended a publicly available annotation of
-speech \citep{haeusler2020speechanno} by further annotating words spoken by the
-audio-description's narrator.
+For the analysis of the AO stumulus, we extended a publicly available annotation
+of speech \citep{haeusler2020speechanno} by further annotating words spoken by
+the audio-description's narrator.
 % annotation procedure
@@
 Notably, the categories \texttt{setting\_new} and \texttt{setting\_rec} comprise
-not just words that describe a setting as a whole (e.g. ``in Greenbow'', ``in a
-disco'', ``the platoon wades through a rice field''). They also comprise words
-that could count as a member of another categories in case the narrator uses
-these words to indicate a switch from one setting to another (e.g. ``Jenny as a
-teenager'').
+not just words that describe a setting as a whole (e.g. ``[in] Greenbow'', ``[in
+a] disco'', ``[the platoon wades through a] rice field''). They also comprise
+words that could count as a member of another categories in case the narrator
+uses these words to indicate a switch from one setting to another (e.g. ``[a]
+physician'').
 
@@
 
-\todo[inline]{Table 2 ist relativ kryptisch bzw für jemanden, der sich zum
+\todo[inline]{SE: Table 2 ist relativ kryptisch bzw für jemanden, der sich zum
     ersten Mal damit auseinander setzt kaum zu verstehen. Auch ist der Bezug zum
@@
 \paragraph{audio-description: regressors}
-% first level analysis regressors AO: events
-For the analysis of the AO stimulus, we created regressors correlating with the
-occurrence of descriptive nouns spoken by the narrator that were added to the
-original annotation of speech \citep{haeusler2020speechanno}.
-% AV events
-For the AV stimulus, we created regressors correlating with movie cuts provided
-by another previously published annotation \citep{haeusler2016cutanno}.
-% https://github.com/psychoinformatics-de/studyforrest-data-annotations/blob/master/code/researchcut2segments.py}
-
-% procedure
-Both annotations were split into eight parts corresponding to the eight stimulus
-segments.
-% AO events
-To create regressors for the AO analysis, we used all of the original 19
-categories of descriptive nouns except ``\texttt{++}'' (i.e. cues regarding
-time).
-% pooling
-Some categories that were similar but offered only a small amount of counts were
-pooled resulting in eleven new categories that served as experimental conditions
-(see Table \ref{tab:ao-events}).
-% setting beats other category
-Events that fell into one of the two setting-related categories
+
+% pooling of categories
+To create the regressor for the GLM of the AO stimulus, some of
+the original 18 categories that were similar but offered only a small amount of
+counts were pooled resulting in eleven new categories [that served as
+experimental conditionso] (see Table \ref{tab:ao-events}).
+% handling of se_new and se_old
+Moreover, events that fell into one of the two setting-related categories
 (\texttt{se\_new} or \texttt{se\_old}) but also into another category were
-treated as belonging to the setting-related category (e.g. ``Jenny as a
-teenager'').
+treated as belonging to the setting-related category (e.g. ``[a] physician'').
 % modeling as boxcar function
@@
 \todo[inline]{Gab es ein separates null-event für jeden zeitraum zwischen zwei
-annotierten events oder war das ein regressor der immer wieder kam?}
+annotierten events oder war das ein regressor der immer wieder kam? COH: uhm,
+sorry, what? the following explanation must be misleading?}
 % null regressors
-If a segment did not contain an event of a category, a null regressor was chosen
-for that category in that segment.\todo{wenn ich "null regressor" nehme, darf
-ich den ganzen Run, glaube ich, in der 2nd level Analyse gar nicht benutzen?
-Hatte, glaube ich, Jeanette Mumford in einem ihren Videos mal gesagt}
-
-\todo[inline]{Das mit den "five additional categories" habe ich nicht
+If a stimulus segment did not contain an event of a category, a null regressor
+was chosen for that category in that segment.\todo{wenn ich "null regressor"
+    nehme, darf ich den ganzen Run, glaube ich, in der 2nd level Analyse gar
+    nicht benutzen?  Hatte, glaube ich, Jeanette Mumford in einem ihren Videos
+mal gesagt}
+
+\todo[inline]{SE: das mit den "five additional categories" habe ich nicht
 verstanden. Überhaupt finde ich die ganze Beschreibung relativ schwer zu
-durchdrungen, und ich glaube damit werde ich nicht alleine sein.}
+durchdrungen, und ich glaube damit werde ich nicht alleine sein. COH: }
 % categories taken from movie cut annotation
-Five additional categories were created from the annotation of movie cuts and
-modeled as impulse events to capture variance of a possibly confounding change
-of the soundscape after a cut, and to create contrasts of cross-modal negative
-control (see details below).
+To create contrasts of cross-modal negative control and to capture variance of a
+possibly confounding change of the soundscape after a cut, we also implemented
+the five movie cut-related regressors used in the GLM of the AV stimulus (see
+details below) in the model of the AO stimulus.
 % nuisance regressors
-\todo[inline]{"Continuous bins lasting 40ms" ?!?}
+\todo[inline]{"Continuous bins lasting 40ms" ?!?; COH: goddamnit! I've rewritten
+    this explanation a lot and finally stuck to the phrasing written in
+    \citep{wilson2008beyond} who did the same}
 %
-Lastly, we used continuous bins of information about two auditory features
-(left-right difference in volume and root mean square energy) that was averaged
-across the length of every movie frame (\unit[40]{ms}) to capture variance
-correlating with low-level perceptual processes.
+Lastly, we created two nuisance regressors based on left-right difference in
+volume and root mean square energy averaged across the length of every movie
+frame (\unit[40]{ms}) to capture variance correlating with low-level perceptual
+processes.
 % Reference to table
-An explanation and counts of the eleven speech-related event categories, the
-five movie cut-related categories, and the two low-level confounds can be found
-in Table \ref{tab:ao-events}.
-
-% modeling of regressors from events
-Events of both stimuli were convolved with a double gamma hemodynamic response
-function (HRF).
+An overview and the respective counts of the eleven speech-related event
+categories, the five movie cut-related categories, and the two low-level
+confounds can be found in Table \ref{tab:ao-events}.
 
@@
 
-\todo[inline]{Bei AV habt ihr cuts und locations benutzt? Cuts können doch auch
-zwischen zwei Gesichtern sein?!?; COH: that should be clearer now as the
-explanation of the regressors immediately follows the description of the
-annotation}
-
-\todo[inline]{besser erklären (was heißt "unfamilar perspective"? Ab wann ist
-ein setting "familiar"?)}
-
 \paragraph{movie: regressors}
+
+% AV events
+For the analysis of the AV stimulus, we used a previously published annotation
+[of the 869] movie cuts and depicted locations \citep{haeusler2016cutanno} to
+created regressors based on the kind of location that is depicted in the movie
+frame after each cut.
 
@@
 
+% todo
+\todo[inline]{besser erklären (was heißt "unfamilar perspective"? Ab wann ist
+ein setting "familiar"?; COH: should be clearer now; maybe rephrase into a
+couple of sentences to improve readability}
 % AV regressors/events
-To create regressors for the AV analysis, we categorized the depicted location
-in the frame following one of the 869 cuts into five categories (see Table
-\ref{tab:av-events}): 1) a cut into an unfamiliar setting (\texttt{vse\_new}),
-2) a cut into a familiar setting (\texttt{vse\_old}), 3) a switch of room/locale
-within a setting (\texttt{vlo\_ch}), 4) a cut to an unfamiliar perspective
-(\texttt{vpe\_new}), and 5) a cut to a familiar perspective (\texttt{vpe\_old}).
+Each location was put into one of the following five categories (see Table
+\ref{tab:av-events}):
+%
+1) a cut switching to a setting that was depicted for the first time
+(\texttt{vse\_new}),
+%
+2) a cut switching to a setting that was already depicted earlier in the movie
+(\texttt{vse\_old}; e.g. a cut to the recurring waiting bench at the bus stop),
+%
+3) a cut switching to another locale within a setting (\texttt{vlo\_ch}; e.g. a
+cut from first to the second floor in Forrest's house),
+%
+4) a cut to another camera position within a setting or locale that was depicted
+for the first time (\texttt{vpe\_new}), and
+%
+5) a cut to another camera position within a setting or locale that was already
+depicted before (\texttt{vpe\_old}).
+
+% to do
+\todo[inline]{Bei AV habt ihr cuts und locations benutzt? Cuts können doch auch
+zwischen zwei Gesichtern sein?!?; COH: that should be clearer now as the
+explanation of the regressors immediately follows the description of the
+annotation}
+% irrespectible of visual content
+Notably, categorization was performed irrespectively of a movie frame's precise
+content and thus without controlling confounding variables (e.g. presence of
+faces).
+
+%%%%%% do not speak of isolate %%%%%%
+% AV COPEs: intro
+The rationale that this procedure would still be able to isolate the PPA was
+twofold.
+% cinematographic rationale cut to new scenes: establishing shots
+The cinematographic rationale was that movies tend to establish the setting
+(\texttt{vse\_new}) and the spatial relationships within a setting
+(\texttt{vpe\_new}) at the beginning of a movie.
+% cut to recurrent scene
+Later in the movie, the field sizes of movie shots tend to decrease when
+switching back to already established settings (\texttt{vse\_old}).
+% similarly for shots within a scene
+Moreover, shots within a recurring locale or setting tend to shift to depicting
+persons and objects (\texttt{vpe\_old}) more relevant to the evolved plot
+\citep{brown2012cinematography, mercado2011filmmakers}.
+% neuroscientific rationale
+The neuroscientific rationale was simply that activity in the PPA is greater
+when participants view novel versus repeated scenes or view-points.
+\citep{epstein1999parahippocampal, grill2006repetition}.
+
 % null regressor
@@
 
-% AV COPEs: intro
-In context of the AV stimulus, we categorized the frames following a movie cut
-irrespective of their concrete visual content and thus without controlling
-confounding variables (e.g. presence of faces). The rationale that this
-procedure would still be able to isolate the PPA was twofold.
-% cinematographic rationale cut to new scenes: establishing shots
-The cinematographic rationale was that movies tend to establish the setting
-(\texttt{vse\_new}) and the spatial relationships within a setting
-(\texttt{vpe\_new}) at the beginning of a movie.
-% cut to recurrent scene
-Later in the movie, the field sizes of movie shots tend to decrease when
-switching back to already established settings (\texttt{vse\_old}).
-% similarly for shots within a scene
-Moreover, shots within a recurring locale or setting tend to shift to depicting
-persons and objects (\texttt{vpe\_old}) more relevant to the evolved plot
-\citep{brown2012cinematography, mercado2011filmmakers}.
-% neuroscientific rationale
-The neuroscientific rationale was simply that activity in the PPA is greater
-when participants view novel versus repeated scenes or view-points.
-\citep{epstein1999parahippocampal}.
-% hence, the following contrasts
-Hence, we created varying contrasts comparing a setting occurring for the first
+% following contrasts
+We created varying contrasts comparing a setting occurring for the first
 time and cuts within a locale depicted for the first time to cuts into recurring

### 2020-12-06 paper/main.tex
revise descriptions of contrasts v1

@@
 confounds can be found in Table \ref{tab:ao-events}.
+% convolving
+Events for all regressors of the AV stimulus were convolved with a
+double gamma hemodynamic response function (HRF).
 
@@
 created regressors based on the kind of location that is depicted in the movie
-frame after each cut.
+frame after a cut.
 
@@
 
-% todo
 \todo[inline]{besser erklären (was heißt "unfamilar perspective"? Ab wann ist
@@
 couple of sentences to improve readability}
+
 % AV regressors/events
@@
 
-% to do
-\todo[inline]{Bei AV habt ihr cuts und locations benutzt? Cuts können doch auch
-zwischen zwei Gesichtern sein?!?; COH: that should be clearer now as the
-explanation of the regressors immediately follows the description of the
-annotation}
 % irrespectible of visual content
@@
 faces).
-
-%%%%%% do not speak of isolate %%%%%%
 % AV COPEs: intro
-The rationale that this procedure would still be able to isolate the PPA was
-twofold.
+The rationale that this approach would still yield categories correlating with
+increased hemodynamic activity in the PPA was twofold.
 % cinematographic rationale cut to new scenes: establishing shots
@@
 % neuroscientific rationale
-The neuroscientific rationale was simply that activity in the PPA is greater
-when participants view novel versus repeated scenes or view-points.
+The neuroscientific rationale was that activity in the PPA is greater when
+participants view novel versus repeated scenes or view-points.
 \citep{epstein1999parahippocampal, grill2006repetition}.
-
 % null regressor
-Here again, a null regressor was chosen for segment if it did not contain an
-event of specific category.
+As for the regressors for AO stimulus, a null regressor was chosen for a
+regressor in a segment if that segment did not contain an event of the
+corresponding category.
 % no cut condition: intro
-A sixth regressors (\texttt{no\_cut}) serving a control condition and to create
-negative control contrasts. Frames within movie shots lasting at least
-\unit[20]{s} were pseudo-randomly chosen by the following rationale:
-% how they were fitted
-a \texttt{no\_cut} event had to have a minimum distance of \unit[10]{s} to a
-movie cut and to another \texttt{no\_cut} event.
+A sixth regressors of pseudo-randomly chosen frames (\texttt{no\_cut}) was
+created as a control condition and to create negative control contrasts:
+% procedure
+Frames were drawn from movie shots lasting at least \unit[20]{s} and had to have
+a minimum distance of \unit[10]{s} to a movie cut and to another
+\texttt{no\_cut} event.
+
+\todo[inline]{mention low-level feature events for AV here as well}
+
 % reference to table
@@
 events, and six additional event categories for low-level auditory and visual
-features of the movie (here again continuous bins lasting \unit[40]{ms}) can be
-found in Table \ref{tab:av-events}.
-% modeling of regressors from events
-Events of both stimuli were convolved with a double gamma hemodynamic response
-function (HRF).
+features of the movie can be found in Table \ref{tab:av-events}.
+% convolving
+Events for all regressors of the AV stimulus were convolved with a
+double gamma hemodynamic response function (HRF).
 
@@
 durchblickt. Was wurde da gegen was kontrastiert?}
-% we have fixed stimuli
-Compared to previous studies we did not design the stimulus material and
-experimentally controlled conditions for the purpose of optimal localization
-performance since we used fixed stimuli.
-% 8 + 5 contrasts
-We created eight $t$-contrasts for the AO stimulus (see Table
-\ref{tab:ao-contrasts}) and five $t$-contrasts for the AV stimulus (see Table
-\ref{tab:av-contrasts}) to operationalize ``spatial perception'' compared to
-``non-spatial'' perception.\todo{big ouff\dots}
-% test for robustness
-Creating more than just one contrast for the two fixed stimuli also let us test
-for/the robustness of our results across varying ways operationalization.
-% contrasts are of different quality
-We assumed all contrasts could in principle isolate the PPA. Nevertheless, we
-also assumed contrasts would differ in their isolation performance because they
-differ in how well the included event categories reflect on average the
-preferred stimulus type processed in the PPA.
-% selection of the primary contrast
-Thus for each stimulus, we chose one ``primary contrast'' for a detailed report
-and discussion of the group-level and subject-specific results. Primary
-contrasts were chosen based on how well the used categories on average were
-assumed to match the preferred stimulus type in balance with the amount of
-available data / events.
-
-% AO COPEs: intro
-In context of the AO stimulus, the categories \texttt{se\_new} and
-\texttt{se\_old} were problematic for three reasons and thus are not included in
-the primary contrast:
-% sparse auditory, rich visually
-(a) they often only vaguely describe a scene (e.g. ``in Greenbow'', ``in a
-disco'', ''black and white film recordings'') whereas a picture of the verbally
-described scene would be perceptually richer,
+
+% why several contrasts
+To test the robustness of our approach,  we created several contrasts for every
+stimulus.
+%
+We operationalized the perception of spatial information compared to the
+perception of ``non-spatial'' information differently in eight $t$-contrasts for
+the AO stimulus (see Table \ref{tab:ao-contrasts}) and five $t$-contrasts for
+the AV stimulus (see Table \ref{tab:av-contrasts}).
+% reason: robustness
+We assumed all contrasts could in principle correlate with increased hemodynamic
+activity in the PPA.
+% but we expect differences because
+Nevertheless, we also assumed contrasts would differ in \todo{differ in what?
+``localization performance'' isn't well phrased. How ``well'', ``nice'' the
+results are?} since used event categories differed a) in how well the averaged
+events reflected spatial information, and b) in event counts
+% thus: primary contrasts
+We chose one ``primary contrast'' for every stimulus before running the
+analyses.
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+In the primary contrast of the AO stimulus we contrasted \texttt{geo} and
+\texttt{groom} with all non-geometry related categories
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+In the primary contrast of the AV stimulus we contrasted
+
+% selection criteria for primary contrast.
+The selection criterion for the primary contrast of each stimulus was a
+subjectively good balance between a) how well categories on average were assumed
+to match the preferred stimulus type, and b) the amount of available data /
+events.\todo{oh, lord!}
+
+% for example, AO stimulus AO COPEs: intro
+For example, the categories \texttt{se\_new} and \texttt{se\_old} of the AO
+stimulus were not included in the primary contrast because
+% heterogeneous category
+a) categories comprise words that could count as a member of another category
+(e.g. ``[a] physician''),
+% richness of verbal description vs. picture
+b) nouns only vaguely described a scene (e.g. ``[in] Greenbow'', ``[in a]
+disco'', ''[black and white] film recordings'') [compared to whole, perceptually
+richer pictures], and
 % hierarchical categories
-(b) they also comprise words that could count as a member of another category in
-case the narrator uses these words to indicate a switch from one setting to
-another (e.g. ``Jenny as a teenager'')
-% soundscapes forestalls narrator
-(c) the narrator is often lacking behind a short dialogue or a change of the
-soundscape that already cue a change of settings.
-% conclusion
-Hence, we assumed contrasts that (exclusively) used these two categories would
-induce noise and would be less successful in isolating the PPA.
+c) the narrator is often lacking behind a short dialogue or a change of the
+soundscape that might already cued a change of settings.
 % furniture
-We did not use the category ``furniture'' (\texttt{furn}) as a regressor of
-interest in any contrasts because nouns in this category were usually big and
-heavy. In a serial stream of auditory information, participants could perceive
-furniture-related nouns as either a geometry-defining local scene element or as
-an isolated object. Hence we did not use this category as regressor of interest
-to reduce noise.
-% negative control contrasts
+The category ``furniture'' (\texttt{furn}) was not used as a regressor of
+interest in any contrast.
+%
+In a serial stream of auditory information, these nouns could be perceived
+differently by different subjects as either a geometry-defining scene elements
+or as an isolated object.
+
+% why not locale change
+
+\paragraph{control contrasts: AO \& AV}
+
+% intro
+
+% AO
 Five $t$-contrasts (see Table \ref{tab:ao-contrasts}) we created as negative
@@
 
-\todo[inline]{MH: I think it's better to explain the rationale of the regressors
-    here in the context of the contrasts and not already above in the list of
-    created regressors: COH: yes, I checked that. Above is just a short
-    list/explanation except for ``no cut'' condition. imo it makes more sense to
-explain it there but maybe I cannot get the reason why you think it fits here
-better}
-
-% following contrasts
-We created varying contrasts comparing a setting occurring for the first
-time and cuts within a locale depicted for the first time to cuts into recurring
-settings and cuts within a recurring locale.
+% AV
 % negative control
@@
 \begin{table*}[h!]
-\caption{Contrasts of parameter estimates for the analysis of the audio-only stimulus (AO).
-Contrast 1-8 aim to isolate the PPA (\texttt{all non-geo} = body, bodypart,
-    fahead, object, sex\_f, sex\_m).
-Contrasts 9-13 serve as negative control at the moments of movie cuts that could
-    correlate with changes of the audio tracks soundscape (see Table \ref{tab:av-contrasts}).}
+\caption{Contrasts of parameter estimates for the analysis of the audio-only
+    stimulus (AO).
+    Contrast 1-8 aim to isolate the PPA.
+    \texttt{non-spatial categories} refers to the to the categories
+    \texttt{body}, \texttt{bodypart}, \texttt{fahead},
+    \texttt{object}, \texttt{sex\_f}, \texttt{sex\_m}.
+    Contrasts 9-13 serve as negative control contrasts at the moments of movie
+    cuts (see Table \ref{tab:av-contrasts}).}
 \label{tab:ao-contrasts}
@@
 \midrule
-1 & geo, groom > all non-geo & PPA \tabularnewline
-2 & geo, groom, se\_new > all non-geo & PPA \tabularnewline
-3 & groom, se\_new, se\_old > all non-geo & PPA \tabularnewline
-4 & geo > all non-geo & PPA \tabularnewline
-5 & groom > all non-geo & PPA \tabularnewline
-6 & se\_new > all non-geo & PPA \tabularnewline
-7 & se\_new, se\_old > all non-geo & PPA \tabularnewline
-8 & se\_new > se\_old & PPA \tabularnewline
+1 & geo, groom > non-spatial categories & PPA \tabularnewline
+2 & geo, groom, se\_new > non-spatial categories & PPA \tabularnewline
+3 & groom, se\_new, se\_old > non-spatial  & PPA \tabularnewline
+4 & geo > non-spatial categories & PPA \tabularnewline
+5 & groom > non-spatial categories & PPA \tabularnewline
+6 & se\_new > non-spatial categories & PPA \tabularnewline
+7 & se\_new, se\_old > non-spatial categories & PPA \tabularnewline
+8 & se\_new > se\_old & non-spatial categories & PPA \tabularnewline
 9 & vse\_new > vpe\_old & control at moments of cuts \tabularnewline
@@
 \begin{table*}[h!]
-    \caption{Contrasts of parameter estimates for the analysis of the audio-visual movie (AV).
+\caption{Contrasts of parameter estimates for the analysis of the
+    audio-visual movie (AV).
     Contrast 1-5 aim to isolate the PPA.

### 2020-12-07 paper/main.tex
revise descriptions of contrasts v2

@@
 
-\todo[inline]{SE: habe mich mit 2.8 extrem schwer getan: Länge des Abschnitts,
-oft komplizierten Beschreibungen}
-
 \todo[inline]{SE: focus on the events that are relevant to the analysis to
@@
 geo & immobile landmarks & building, tree, street, alley, meadow, cornfield \tabularnewline
-geo-room & rooms (insides) or  locales (outsides) & living room; wall, door,
-window, floor, turf
+geo-room & rooms \& locales or geometry-defining elements & living room; wall, door, window, floor
 \tabularnewline
@@
     COH: I dropped the table of counts per segment.  The information is
-    redundant since the counts are not the count of events of the actual
+    redundant since the counts are not the counts of events of the actual
 regressors (cf. Table \ref{tab:av-events})}
@@
 \tabularnewline
-groom & elements defining geometry of room & \aoGroomAll & \aoGroomI & \aoGroomII & \aoGroomIII & \aoGroomIV & \aoGroomV & \aoGroomVI & \aoGroomVII & \aoGroomVIII
+groom & rooms \& locales or geometry-defining elements & \aoGroomAll & \aoGroomI & \aoGroomII & \aoGroomIII & \aoGroomIV & \aoGroomV & \aoGroomVI & \aoGroomVII & \aoGroomVIII
 \tabularnewline
@@
 
-\todo[inline]{SE: das mit den "five additional categories" habe ich nicht
-verstanden. Überhaupt finde ich die ganze Beschreibung relativ schwer zu
-durchdrungen, und ich glaube damit werde ich nicht alleine sein. COH: }
 % categories taken from movie cut annotation
@@
     this explanation a lot and finally stuck to the phrasing written in
-    \citep{wilson2008beyond} who did the same}
+    \citep{wilson2008beyond} who did the same; it is rephrased now though}
 %
@@
 \tabularnewline
-vno\_cut & a continuous frame from the same camera position & \avVnocutAll & \avVnocutI & \avVnocutII & 0 & \avVnocutIII & \avVnocutIV & \avVnocutV & \avVnocutVI & \avVnocutVII
+vno\_cut & frames within a continuous movie shot & \avVnocutAll & \avVnocutI & \avVnocutII & 0 & \avVnocutIII & \avVnocutIV & \avVnocutV & \avVnocutVI & \avVnocutVII
 \tabularnewline
@@
 A sixth regressors of pseudo-randomly chosen frames (\texttt{no\_cut}) was
-created as a control condition and to create negative control contrasts:
+created as a control condition to create negative control contrasts:
 % procedure
@@
 
-\todo[inline]{Die Abkürzungen in Figure 1: Da steigt keiner hinter}
-
-\todo[inline]{Habe jetzt lange darüber gebrütet: Es gibt also kaum eine
-Korrelation zwischen AO und AV?; Also, außer bei fg\_av\_ger\_lr\_diff (wobei da
-keiner weiss, was das bedeutet)}
+\todo[inline]{Die Abkürzungen in Figure 1: Da steigt keiner hinter; habe jetzt
+lange darüber gebrütet: Es gibt also kaum eine Korrelation zwischen AO und AV?;
+Also, außer bei fg\_av\_ger\_lr\_diff (wobei da keiner weiss, was das bedeutet)}
 
@@
 
-% why several contrasts
-To test the robustness of our approach,  we created several contrasts for every
-stimulus.
-%
-We operationalized the perception of spatial information compared to the
-perception of ``non-spatial'' information differently in eight $t$-contrasts for
-the AO stimulus (see Table \ref{tab:ao-contrasts}) and five $t$-contrasts for
-the AV stimulus (see Table \ref{tab:av-contrasts}).
+% intro
+To test the robustness our approach, we operationalized the perception of
+spatial information compared to the perception of ``non-spatial'' information
+differently in eight $t$-contrasts for the AO stimulus (see Table
+\ref{tab:ao-contrasts}) and five $t$-contrasts for the AV stimulus (see Table
+\ref{tab:av-contrasts}).
 % reason: robustness
@@
 % but we expect differences because
-Nevertheless, we also assumed contrasts would differ in \todo{differ in what?
-``localization performance'' isn't well phrased. How ``well'', ``nice'' the
-results are?} since used event categories differed a) in how well the averaged
-events reflected spatial information, and b) in event counts
+Nevertheless, we also assumed contrasts would differ in [?] \todo{differ in
+what?  ``localization performance'' isn't well phrased. How ``well'', ``nice''
+the results are?} since the event categories differed a) in how well the
+averaged events reflected spatial information, and b) in event counts.
 % thus: primary contrasts
@@
 analyses.
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-In the primary contrast of the AO stimulus we contrasted \texttt{geo} and
-\texttt{groom} with all non-geometry related categories
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-In the primary contrast of the AV stimulus we contrasted
-
 % selection criteria for primary contrast.
@@
 
-% for example, AO stimulus AO COPEs: intro
-For example, the categories \texttt{se\_new} and \texttt{se\_old} of the AO
-stimulus were not included in the primary contrast because
+% AO: primary contrast
+In the primary contrast of the AO stimulus, we contrasted landmarks
+\texttt{geo}, and rooms and geometry-defining objects \texttt{geo-room} with all non-geometry related categories (\texttt{body},
+\texttt{bodypart}, \texttt{fahead}, \texttt{object}, \texttt{sex\_f},
+\texttt{sex\_m}) except \texttt{furniture}.
+
+% why se_new & se_old were not used in the primary contrasts
+The categories of nouns cueing a setting that occured for the first time
+(\texttt{se\_new}) or a setting that recurred during the plot (\texttt{se\_old})
+were not included in the primary contrast because
 % heterogeneous category
@@
 The category ``furniture'' (\texttt{furn}) was not used as a regressor of
-interest in any contrast.
-%
-In a serial stream of auditory information, these nouns could be perceived
-differently by different subjects as either a geometry-defining scene elements
-or as an isolated object.
-
-% why not locale change
+interest in any contrast because these nouns could be perceived differently by
+different subjects as either a geometry-defining scene element or as an isolated
+object.
+
+% AV primary contrast
+In the primary contrast of the AV stimulus, we contrasted cuts to a setting that
+was not depicted before (\texttt{vs\_new}) to cuts that we accompanied with a
+change of the camera position within a setting that was already occurring
+previously (\texttt{vpe\_old}).
+% why
+We assumed these categories on average best represent events that trigger
+perception of space versus objects or faces.\todo{syntax?}
 
@@
 % intro
-
-% AO
-Five $t$-contrasts (see Table \ref{tab:ao-contrasts}) we created as negative
-controls to test if increased activation in the PPA was correlated with moments
-of cuts and therefore possibly correlated with a accompanying change in the
-soundscape.
-
-% AV
-% negative control
-Five additional $t$-contrasts we created for negative control purposes (see
-Table \ref{tab:av-contrasts}) by using regressors based on regressors of the AO
-stimulus.
+Finally, we created several contrasts as negative control for both stimuli.
+% AO stimulus
+For the AO stimulus, we created five $t$-contrasts (see Table
+\ref{tab:ao-contrasts}) to test if increased activation in the PPA was
+correlated with moments of cuts possibly correlated with a accompanying change
+in the soundscape.
+% AV stimulus
+For the AV stimulus, four $t$-contrasts were created contrasting the no-cut
+condition (texttt{vno\_cut} for negative control purposes (see Table
+\ref{tab:av-contrasts}) by using regressors based on regressors of the AO
+stimulus. One contrast (\texttt{vs\_new} > \texttt{vpe\_old})  was created by
+contrasting nouns spoken by the narrator.
 
@@
 7 & se\_new, se\_old > non-spatial categories & PPA \tabularnewline
-8 & se\_new > se\_old & non-spatial categories & PPA \tabularnewline
+8 & se\_new > se\_old > non-spatial categories & PPA \tabularnewline
 9 & vse\_new > vpe\_old & control at moments of cuts \tabularnewline
@@
     listener about a switch of settings, events that could be correlated with a
-    switch of the soundscape.}
+    change of the soundscape.}
 \label{tab:av-contrasts}
@@
 9 & vno\_cut > vpe\_new, vpe\_old & negative control \tabularnewline
-10 & se\_new > se\_old & control for narrator \tabularnewline
+10 & se\_new > se\_old & control for (missing) narrator \tabularnewline
 \end{tabular}

### 2020-12-07 paper/main.tex
cleaning todos

@@
 
-\todo[inline]{Clou der ganzen Geschichte ist doch: Man braucht keinen separaten
-Localizer, oder? Das kommt bisher nur bedingt rüber; COH: well, if you also want
-to have the ``visual part'' of the PPA then you need a visual paradigm}
+\todo[inline]{SE: Clou der ganzen Geschichte ist doch: Man braucht keinen
+separaten Localizer, oder? Das kommt bisher nur bedingt rüber; COH: well, if you
+also want to have the ``visual part'' of the PPA then you need a visual
+paradigm}
 
@@
 
-\todo[inline]{Der Schwung zu Sprache (wobei speech auch erst am Satzende kommt)
-ist zu hart, da kommt man als Leser nicht gut mit}
+\todo[inline]{SE: Der Schwung zu Sprache (wobei speech auch erst am Satzende
+kommt) ist zu hart, da kommt man als Leser nicht gut mit}
 
@@
 \todo[inline]{SE: focus on the events that are relevant to the analysis to
-reduce complexity and explain these better}
+reduce complexity and explain these better; COH: revised but maybe still not
+``optimal''}
 
 \todo[inline]{SE: wie gut passen die Annotationen zu den VIS Stimuli -> genauere
-Ausführungen, wie welche Annotation dazu passt}
+Ausführungen, wie welche Annotation dazu passt; COH: revised but maybe still not
+``optimal''}
 
@@
 
-\todo[inline]{mention low-level feature events for AV here as well}
+\todo[inline]{mention low-level feature events for AV here as well and not just
+in the figure caption}
 
@@
 
-\todo[inline]{Die Abkürzungen in Figure 1: Da steigt keiner hinter; habe jetzt
-lange darüber gebrütet: Es gibt also kaum eine Korrelation zwischen AO und AV?;
-Also, außer bei fg\_av\_ger\_lr\_diff (wobei da keiner weiss, was das bedeutet)}
+\todo[inline]{SE: Die Abkürzungen in Figure 1: Da steigt keiner hinter; habe
+jetzt lange darüber gebrütet: Es gibt also kaum eine Korrelation zwischen AO und
+AV?; Also, außer bei fg\_av\_ger\_lr\_diff (wobei da keiner weiss, was das
+bedeutet)}
 
@@
 
-\todo[inline]{Das mit den 8 kontrasten und 5 kontrasten habe ich nicht intuitiv
-durchblickt. Was wurde da gegen was kontrastiert?}
+\todo[inline]{SE: Das mit den 8 kontrasten und 5 kontrasten habe ich nicht
+intuitiv durchblickt. Was wurde da gegen was kontrastiert? COH: revised but
+maybe still not optimal}
 
@@
 
-\todo[inline]{give reference to Neurovault.com}
-
-\todo[inline]{- Bitte sauber differenzieren zwischen "Lokalisation der PPA" und
+\todo[inline]{SE: sauber differenzieren zwischen "Lokalisation der PPA" und
     "Antwortverhalten einer vorab definierten PPA". Ich habe den Eindruck, dass
@@
 
-\todo[inline]{Der vergleich mit VIS kommt bestenfalls en passant, VIS selber
-wird gar nicht berichtet wäre aber wichtig zum andocken an die Literatur}
-
-\todo[inline]{Es ist zwar hier nicht der Fokus, aber ich würde sehr darauf
-wetten, dass Reviewer danach fragen: Wie sieht es im vergleich dazu mit Faces
-aus?}
-
-\todo[inline]{Figure 2 und 3: ich würde da wahrscheinlich weiter rein zoomen um
-genauer den visuellen Kortex zu zeigen. Vor allem aber muss man sagen, dass bei
-FFA/PPA etc eigentlich flatmaps bzw inflated brains, also surface-darstellungen
-standard sind}
-
-\todo[inline]{Die Anzahl der Überlappungen in Figure 3 ist schwer abzulesen,
-hier lieber eine andere Farbskala (spectral sequence?) nutzen}
-
-\todo[inline]{Das mit den cuts to new vs familar setting wird irgendwie nie so
-richtig in den PPA kontext eingeordnet. Bzw. ich glaube ich bin verwirrt. Warum
-ist das der hauptkontrast und nicht das viel näher liegende places vs faces?}
-
-\todo[inline]{Noch etwas, das wahrscheinlich gefragt wird: Wie sehen die
-Antworten innerhalb der "klassisch definierten" PPA für die verschiedenen
-regressoren bzw.  kategorien derselben (zumindest aber places vs faces) aus?}
-
-\todo[inline]{Wenn ich mir Figure 4 anschaue, würde ich sagen, dass AO besser
-die VIS-PPA "trifft" als AV. Das ist zumindest sehr überraschend, oder?}
-
-\todo[inline]{Figure 5 ist irre kompliziert. Welche Areale habt ihr als masks
-genommen, FFA ist ja kartiert (Julia caspers)}
+\todo[inline]{SE: Vergleich mit VIS kommt bestenfalls en passant; VIS selber
+wird gar nicht berichtet, wäre aber wichtig zum Andocken an Literatur}
+
+\todo[inline]{SE: würde wetten, dass Reviewer fragen: Wie sieht es im vergleich
+dazu mit Faces aus?}
+
+\todo[inline]{SE: Figures with group results: würde da wahrscheinlich weiter
+rein zoomen, um genauer den visuellen Kortex zu zeigen; vor allem muss man
+sagen: bei FFA/PPA etc sind flatmaps/inflated brains standard}
+
+\todo[inline]{SE: overlap of clusters/contrasts: Anzahl der Überlappungen ist
+schwer abzulesen; lieber eine andere Farbskala (spectral sequence?) nutzen}
+
+\todo[inline]{SE: cuts to new vs familar setting wird irgendwie nie so
+richtig in den PPA kontext eingeordnet. Warum ist das Hauptkontrast und nicht
+das viel näher liegende places vs faces? COH: should at least be clearer after
+revision of method section}
+
+\todo[inline]{SE: Wie sehen die Antworten innerhalb der "klassisch definierten" PPA für die verschiedenen regressoren bzw. kategorien derselben (zumindest aber places vs faces) aus?}
+
+\todo[inline]{individual results: AO trifft besser die VIS-PPA "trifft" als AV. Das ist zumindest sehr überraschend, oder?}
+
+\todo[inline]{Bland-Altman-Plots: Welche Areale habt ihr als masks
+genommen, FFA ist ja kartiert (Julia Caspers)}
 
@@
 ``visual area'' using the auditory stimulus.
+% NeuroVault
+Unthreholded $z$-maps of all contrasts on a group level as well as individual
+results of the primary contrasts can be found at
+\href{https://neurovault.org/collections/KADGMGVZ/}{NeuroVault}.\todo{still
+private collection}
 
@@
 
-\todo[inline]{say why slice -11 was chosen}
-
 \todo[inline]{other reasons than localization performance?}
@@
 and AV $t$-contrast, and the outline of the individual PPAs
-\citep{sengupta2016extension} overlayed on the MNI152 template (transversal slice z=-11 for all subjects).
+\citep{sengupta2016extension} overlayed on the MNI152 template (transversal
+slice z=-11 for all subjects was chosen as it depicts voxels of significant
+clusters in almost all subjects).
 
@@
         To facilitate comparisons across subjects, we chose the same horizontal
-        slice (x=-11) for all subjects. Thus, the figure does not depict the
-        left cluster of the AV stimulus in sub-09 and sub-18, and the right
-        cluster of the AV stimulus in sub-15.}
+        slice (x=-11) for all subjects as this slice depicts voxels of
+        significant clusters in almost all subjects.
+        The figure does not show voxels of the left cluster of the AV stimulus
+        in sub-09 and sub-18, and voxels of right cluster of the AV stimulus in
+        sub-15.}
     \label{fig:subs-thresh-ppa}
@@
 \begin{figure*} \centering
-    \includegraphics[width=.8\linewidth]{figures/subjs_bland-altman.png}
+    \includegraphics[scale=0.28]{figures/subjs_bland-altman.png}
     \caption{Bland-Altman-Plots for individual subjects. The x-axis depicts the
@@
 
-\todo[inline]{Ich finde die result-synopsis noch nicht optimal. Vielleicht gehe
-ich aber auch mit der falschen Perspektive ran? Für mich würde der Vergleich
+\todo[inline]{SE: die result-synopsis noch nicht optimal. Vielleicht gehe ich
+aber auch mit der falschen Perspektive ran? Für mich würde der Vergleich
 "localizer vs naturalistic" im vordergrund stehen, AO vs AV dann eine sehr
@@
 
-\todo[inline]{Bei ergebnissen und Diskussionen zu Stability fehlt mir irgendwie
-immer der Kontext, wie sich die kontraste denn unterschieden haben und welche
-davon z.B. im Ergebnis wo von den anderen abgewichen haben. Das würde ja
+\todo[inline]{SE: Bei Ergebnissen \& Diskussionen zu Stability fehlt mir
+irgendwie immer der Kontext, wie sich die Kontraste denn unterschieden haben und
+welche davon z.B. im Ergebnis wo von den anderen abgewichen haben. Das würde ja
 wichtige Hinweise geben}
 
-\todo[inline]{VIS vs AV vs AO: Wer liefert was über die PPA. Dieser Vergleich
-bzw. die Diskussion über gemeinsamkeiten und unterschiede fehlt mir etwas}
-
-\todo[inline]{RSC etc: Irgendwie waren die bis zu diskussion eher ein
+\todo[inline]{SE: VIS vs AV vs AO: Wer liefert was über die PPA. Dieser
+Vergleich bzw. die Diskussion über Gemeinsamkeiten \& Unterschiede fehlt mir
+etwas}
+
+\todo[inline]{SE: RSC etc: Irgendwie waren die bis zu Diskussion eher ein
 afterthought. Daher etwas überraschend, vielleicht in Einleitung und Results

### 2020-12-08 paper/main.tex
cleaning todos2

@@
 Lastly, our results provides further evidence that the PPA can be divided into
-functional subregions.\todo{kinda bold statements; this depends on the data \&
-discussion}\end{abstract}
+functional subregions.\end{abstract}
 
@@
 % why and how of categories 2
-Other categories were created to semantically cluster some remaining nouns into
+Other categories were created to semantically cluster remaining nouns into
 categories that had no counterpart in the visual localizer experiment (e.g.
@@
 \texttt{sex\_m}) except \texttt{furniture}.
-
 % why se_new & se_old were not used in the primary contrasts
@@
 % why
-We assumed these categories on average best represent events that trigger
-perception of space versus objects or faces.\todo{syntax?}
+We assumed that movie frames in these categories on average best represent
+events that trigger perception of space versus objects or faces.\todo{syntax?}
 
@@
     "Antwortverhalten einer vorab definierten PPA". Ich habe den Eindruck, dass
-Du oft das erste machst es aber als das zweite beschreibst}
+Du oft das erste machst es aber als das zweite beschreibst; COH: ??? we do
+whole-brain analysies, so probably ``localization'', }
 
 \todo[inline]{SE: Vergleich mit VIS kommt bestenfalls en passant; VIS selber
-wird gar nicht berichtet, wäre aber wichtig zum Andocken an Literatur}
+wird gar nicht berichtet, wäre aber wichtig zum Andocken an Literatur; COH: }
 
 \todo[inline]{SE: würde wetten, dass Reviewer fragen: Wie sieht es im vergleich
-dazu mit Faces aus?}
+dazu mit Faces aus? COH: yeah, well, I made the contrasts similar to Sengupta
+and considered the contrast to an average of all ``non-spatial'' stuff
+appropriate; should be cleare in the method section (s. ``Contrasts'')}
 
@@
 
-\todo[inline]{SE: Wie sehen die Antworten innerhalb der "klassisch definierten" PPA für die verschiedenen regressoren bzw. kategorien derselben (zumindest aber places vs faces) aus?}
-
-\todo[inline]{individual results: AO trifft besser die VIS-PPA "trifft" als AV. Das ist zumindest sehr überraschend, oder?}
+\todo[inline]{SE: Wie sehen die Antworten innerhalb der "klassisch definierten"
+PPA für die verschiedenen regressoren bzw. kategorien derselben (zumindest aber
+places vs faces) aus? COH: ???}
+
+\todo[inline]{individual results: AO trifft besser die VIS-PPA "trifft" als AV.
+Das ist zumindest sehr überraschend, oder?; COH: actually it isn't because the
+of blindly averaging the actual frame content in the categories of movie cuts
+(cf. shortcomings); this ``cross-modal control things'' seems to more confuse
+than having its merits}
 
 \todo[inline]{Bland-Altman-Plots: Welche Areale habt ihr als masks
-genommen, FFA ist ja kartiert (Julia Caspers)}
+genommen, FFA ist ja kartiert (Julia Caspers); COH: probaly the caption was
+invisible in the version Simon got? changed the size of the figure so the
+caption is now on the page}
 
@@
 afterthought. Daher etwas überraschend, vielleicht in Einleitung und Results
-schon mehr bringen}
+schon mehr bringen; COH: afterthought, for sure; It was highly probable that RSC
+would show up but it wasn't aim of the study (had no ROIs for it anyway); imo
+this is an issue of story telling vs. hypotheses after results}
 

### 2020-12-10 paper/main.tex
cleaning todos2
some changes to report of group results

@@
 \usepackage{fancyhdr}
-\usepackage[disable]{todonotes}
-% \usepackage{todonotes}
+% \usepackage[disable]{todonotes}
+\usepackage{todonotes}
 \usepackage{units}
@@
 paradigm}
+
+\todo[inline]{most of phrases containing the word ``isolate'' is gone; doing the
+    revision of the result section I realized that we probably should
+    ``somehow'' add that clusters should not be all over the place but spatially
+    constrained to the parahippocampal and neighbouring cortices, because
+    naturalistic stimulus / possibly confounding variables}
 
@@
 \todo[inline]{SE: Vergleich mit VIS kommt bestenfalls en passant; VIS selber
-wird gar nicht berichtet, wäre aber wichtig zum Andocken an Literatur; COH: }
+wird gar nicht berichtet, wäre aber wichtig zum Andocken an Literatur; COH: yes,
+maybe reference Sengupta who are interested in the details? en passant makes
+more sense here imo}
 
@@
 rein zoomen, um genauer den visuellen Kortex zu zeigen; vor allem muss man
-sagen: bei FFA/PPA etc sind flatmaps/inflated brains standard}
+sagen: bei FFA/PPA etc sind flatmaps/inflated brains standard; imo it is
+important that we do not have clusters all over the brain}
 
 \todo[inline]{SE: overlap of clusters/contrasts: Anzahl der Überlappungen ist
-schwer abzulesen; lieber eine andere Farbskala (spectral sequence?) nutzen}
+schwer abzulesen; lieber eine andere Farbskala (spectral sequence?) nutzen; COH:
+yes, I know it is kinda difficult, tried my best to choose/tweak the color map}
 
@@
 \todo[inline]{individual results: AO trifft besser die VIS-PPA "trifft" als AV.
-Das ist zumindest sehr überraschend, oder?; COH: actually it isn't because the
-of blindly averaging the actual frame content in the categories of movie cuts
-(cf. shortcomings); this ``cross-modal control things'' seems to more confuse
-than having its merits}
+    Das ist zumindest sehr überraschend, oder?; COH: actually it isn't because
+    of blindly averaging the actual frame content in the categories of movie
+    cuts (cf. methods/regressors, discussion/shortcomings); this ``cross-modal
+    control things'' seems to more confuse than having its merits}
 
@@
 
+\todo[inline]{following is one exemplary sentence that would benefit from also
+mentioning that clusters should not be all over the brain which could be the
+case because naturalistic paradigm / confounding variables etc.}
+
 % study goal
-The goal of this study was to investigate if increased hemodynamic activity in
-the PPA correlates with spatial information presented under more ecological
-valid conditions.
-% what we did
-We annotated a \unit[2]{h} movie and its temporally aligned audio-description to
-create GLM contrasts similar to previous studies that used simplified stimuli.
+The goal of this study was to investigate if cues about the spatial layout
+embedded in two naturalistic stimuli correlate with increased hemodynamic
+activity in the PPA that was define by using a visual localizer experiment
+within the same subjects \citep{sengupta2016extension}.
+% what we did We
+annotated a \unit[2]{h} movie and its temporally aligned audio-description to
+create GLM contrasts similar to previous studies that used conceptualized
+stimuli.
 % group level
 On a group average level, we compare results gained from both naturalistic
-stimuli to results gained from a visual localizer experiment.
+stimuli to results gained from the visual localizer.
 % individual level
 On the level single subjects, we also assess localization performance of a
-``visual area'' using the auditory stimulus.
+``visual area'' using the auditory stimulus.\todo{``localization'' performance}
 % NeuroVault
 Unthreholded $z$-maps of all contrasts on a group level as well as individual
-results of the primary contrasts can be found at
+results of the primary $t$-contrasts can be found at
 \href{https://neurovault.org/collections/KADGMGVZ/}{NeuroVault}.\todo{still
@@
 % intro
-First on a group average level, we tested if we could isolate the PPA using GLM
-contrasts based on the audio-description's annotation of speech.
+First on a group average level, we tested if results of a whole-brain analysis
+based on the audio-description's annotation would lead to increased hemodynamic
+activity in the PPA.
 % primary AO contrast
-The primary $t$-contrast for the audio-description (\texttt{geo, groom > all
-non-geo}) yielded six significant clusters (see Table \ref{tab:res-ao-group1},
-Figure \ref{fig:group-slices}).
+The primary $t$-contrast for the audio-description (\texttt{geo, groom} >
+non-spatial noun categories) yielded six significant clusters (see Table
+\ref{tab:res-ao-group1}, Figure \ref{fig:group-slices}).
 % overlap with ROI
@@
 % in detail
-specifically, the clusters of the current analysis are at the borders of the
+Specifically, the clusters of the current analysis are at the borders of the
 posterior parahippocampal cortex, the occipital and temporal fusiform gyrus and
@@
 % all eight AO PPA contrasts
-In order to test the robustness of our findings, we created seven additional
+In order to test the robustness of our findings, we created overall eight
 $t$-contrasts for the AO stimulus (see Table \ref{tab:ao-contrasts}).
 % results
-Six of the overall eight AO contrasts show significant bilateral clusters in
-anterior regions of the group PPA overlap (see Figure
-\ref{fig:stability-slices}).
+All contrasts except contrast 7 (\texttt{se\_new}, \texttt{se\_old} >
+non-spatial categories) and contrast 8 (\texttt{se\_new} > non-spatial
+categories) yielded significant bilateral clusters in anterior regions of the
+group PPA overlap (see Figure \ref{fig:stability-slices}).
 % statement/answer
@@
     \includegraphics[width=\linewidth]{figures/stability-slices}
-    \caption{Stability of contrasts. Overlap of significant clusters (Z>3.4;
-        p<.05, cluster corrected) of contrasts created to isolate the PPA.
+    \caption{Overlap of significant clusters (Z>3.4; p<.05, cluster corrected)
         The audio-description's contrasts 1-8 (blue; \ref{tab:ao-contrasts})
         are overlaid over the audio-visual movie's contrasts 1-5 (red;
-        \ref{tab:av-contrasts}), both on top of the MNI152 T1-weighted head
-        template (gray).
+        \ref{tab:av-contrasts}) that were used to [isolate] the PPA
+        Cluster are overlaid on top of the MNI152 T1-weighted head template
+        (gray).
         Black: outline of overlapping individual PPA ROIs.
@@
 
-\subsubsection{AO: other significant clusters across contrasts}
+\paragraph{AO: other significant clusters across contrasts}
 % precuneus = retrosplenial cortex ?
 \todo[inline]{significant clusters in other regions than PPA could or should (?)
-also be reported? Following is a short list; depends on the discussion I guess}
-% ventral precuneus = retrosplenial cortex?
-So far, just a short list => 7 contrasts: bilateral clusters in RSC (and ventral
-precuneus);
-% transverse occipital sulcus = occipital place area
-6 contrasts (4 bilateral, 2 unilateral): lateral occipiatal cortex (transverse
-occipital sulcus; occipiatal place area?; AO clusters are more lateral, AV
-cluster are more medial (\& caudal) but AO \& AV clusters overlap)
-% confounds
-4 contrasts: right superior temporal gyrus (auditory cortices); 3 contrasts:
-left superior temporal gyrus; 3 contrasts: some (smallish) prefrontal clusters
+also be reported? Following is a short list; depends on the discussion I guess;
+anyhow: clusters are not ``random'' but make sense which speaks for the use of
+naturalistic stimuli}
+
+\begin{itemize}
+\item RSC (and ventral precuneus): 7 contrasts (all bilateral)
+\item lateral occipiatal cortex: 6 contrasts (4 bilateral, 2 unilateral =
+    transverse occipital sulcus / occipiatal place area?; AO \& AV clusters
+    overlap but AO clusters are more lateral, AV cluster are more medial \&
+    caudal)
+\item right superior temporal gyrus (auditory cortices): 4 contrasts
+\item (smallish) prefrontal clusters: 3 contrasts (non-overlapping)
+\end{itemize}
 
@@
 % AV intro
-Second as conceptual/cross-modal control of the group average results, we
-analyzed data from the audio-visual movie by contrasting different kinds of
-movie cuts independent(ly) from the frames' visual content following the cuts.
+As conceptual/cross-modal control of the group average results, we also analyzed
+data from the audio-visual movie by contrasting different kinds of movie cuts
+independent(ly) from the frames' visual content following the cut.
 % AV primary contrast
-The movie's primary $t$-contrast that compared cuts to an unfamiliar setting
-with cuts within familiar setting (\texttt{vse\_new > vpe\_old}) yielded three
-significant clusters (see Table \ref{tab:res-av-group1}, Figure
+The movie's primary $t$-contrast that compared cuts to a setting that was not
+depicted before to a recurring setting (\texttt{vse\_new > vpe\_old}) yielded
+three significant clusters (see Table \ref{tab:res-av-group1}, Figure
 \ref{fig:group-slices}).
 % PPA (others the clusters extend into).
-One cluster spans across the midline and comprises (reported from posterior to
-anterior), parts of the intracalcarine and cuneal cortex, the lingual gyrus and
-retrosplenial cortex, the occipital and temporal fusiform gyrus and the
-parahippocampal cortex in both hemispheres.
+One cluster spans across the midline and comprises, parts of the intracalcarine
+and cuneal cortex, the lingual gyrus and retrosplenial cortex, the occipital and
+temporal fusiform gyrus and the parahippocampal cortex (reported from posterior
+to anterior) in both hemispheres.
 % LOC
@@
 \caption{Significant clusters (z-threshold Z>3.4; p<.05 cluster-corrected)
-        of the primary $t$-contrast for the movie comparing cuts to a new
-        setting with cuts to a familiar perspective (\texttt{vse\_new >
-        vpe\_old}).
+    of the primary $t$-contrast for the audio-visual movie comparing cuts to a
+    setting that was not depicted before to a recurring setting
+    (\texttt{vse\_new > vpe\_old}).
     Clusters sorted by voxel size.
     The first brain structure given contains the voxel with the maximum Z-Value,
-followed by brain structures from posterior to anterior, and partially covered
-areas (l. = left; r. = right; c. = cortex; g. = gyrus).}
+    followed by brain structures from posterior to anterior, and partially
+    covered areas (l. = left; r. = right; c. = cortex; g. = gyrus).}
 \label{tab:res-av-group1}
@@
 
-\subsubsection{AV: other signficant clusters across contrasts}
+\paragraph{AV: other signficant clusters across contrasts}
+
+\begin{itemize}
+\item lateral occipital cortex: 4 contrasts (all bilateral)
+\end{itemize}
 
@@
 \todo[inline]{contrasts are mentioned in the method section for the purpose of
-    completeness. Shall results be reported (and later discussed)? Following is
-a short overview}
+completeness. Shall results be reported (and later discussed)?}
 
@@
 % AV stimulus
-AV stimulus. All contrasts using ``no cut condition'' > x yield null results.
+AV stimulus. All contrasts using ``no cut condition'' > XY yield null results.
 The contrast that uses the narrator's nouns but in the AV stimulus (se\_new >

### 2020-12-10 paper/main.tex
some changes to report of individual results

@@
 ventral pathway that leads into into the temporal lobe (the ``what pathway'')
-\citep{goodale1992separat, mishkin1982contribution}.
+\citep{goodale1992separate, mishkin1982contribution}.
 % PPA
@@
 
-\todo[inline]{contrasts are mentioned in the method section for the purpose of
-completeness. Shall results be reported (and later discussed)?}
+\todo[inline]{for completeness, contrasts are mentioned in the method section.
+Shall results be reported (and later discussed)?}
 
@@
 % why individual results in the first place.
-We also investigated localization performance of both naturalistic paradigms on
-the level of individual subjects.
+We also investigated [localization performance] of both naturalistic paradigms
+on the level of individual subjects.\todo{depends on ``naturalistic stimulus for
+localization''}
 % results in both subject and group space
 Time series of all subjects were analyzed both in group space and subject space.
-% individual z-maps -> dataset
-Results of the analyses that were performed in each subject's subject-space
-(unthresholded $z$-maps and thresholded $z$-maps with Z>2.3, p<.05 cluster
-corrected) can be found in the accompanying dataset.
-% report here in group space
+ space
 For better comparison of results across participants, we here report results
@@
 clusters in almost all subjects).
+% individual z-maps -> dataset
+Results of the analyses that were performed in each subject's subject-space
+(unthresholded $z$-maps and thresholded $z$-maps with Z>2.3, p<.05 cluster
+corrected) can be found at
+\href{https://neurovault.org/collections/KADGMGVZ/}{NeuroVault}.\todo{still
+private collection} .
+% report here in group
 
@@
 % PPA ROI (Sengupta et al., 2016)
-The dedicated localizer \citep{sengupta2016extension} yielded bilateral ROIs in
-12 of 14 subjects and a unilateral right clusters in two subjects (sub-04,
-sub-20).
+The visual localizer experiment \citep{sengupta2016extension} yielded bilateral
+clusters in 12 of 14 subjects and a unilateral right clusters in two subjects
+(sub-04, sub-20) that were defined as the PPA.\todo{this is probably the part
+that Simon considered as/too ``en passant''}
 % procedure in Sengupta
-Individual ROIs were assessed by visually inspecting unthresholded $z$-maps of
+Individual PPAs were assessed by visually inspecting unthresholded $z$-maps of
 three different contrasts, and setting a subjectively best fitting $z$-threshold
-to isolate a ROI that matched the PPA.
+to define an area in the parahippocampal gyrus [and adjacent regions of the
+fusiform gyrus and anterior lingual gyrus].
 % AO
@@
 subjects, and one cluster in the left hemisphere of sub-09 that are within or
-overlapping with the PPA ROI.
+overlapping with the individual PPA.
 % subj-04
@@
 unilateral right clusters in six subjects (of which one subjects yielded a
-unilateral cluster in the dedicated localizer), and a unilateral left cluster in
+unilateral cluster in the visual localizer), and a unilateral left cluster in
 one subject.
 % difference to dedicated localizer
-We find homologous clusters in sub-20, whereas the dedicated localizer yielded
-only one cluster in the right hemisphere.
+We find homologous clusters in sub-20, whereas the dedicated visual localizer
+yielded only one cluster in the right hemisphere.
 % concluding statement
@@
 To better depict/convey the agreement and difference between individual results
-of the dedicated visual localizer and the primary AO contrast, we created one
+of the visual localizer and the primary AO contrast, we created one
 Bland-Altman-Plots for each of the 14 subjects (see Figure
@@
 \citep{eickhoff2005toolbox, eickhoff2007assignment}), b) voxels located in the
-PPA overlap of all subjects (blue), and c) voxels located in the individual PPA
-ROI(s)(red).
+PPA overlap of all subjects (blue), and c) voxels located in individual PPA(s)
+(red).
 % top KDE plot
@@
         AO stimulus (KDE plot on the top). The y-axis depicts the difference of
-        two voxels (KDE plot on the right). The overlays depict voxels spatially
-        contrained to be located in the temporal and occipital cortex (gray),
-    PPA overlap of all subjects (blue), and individual PPA (red).}
+        two voxels (KDE plot on the right).
+        The overlays depict voxels spatially contrained to be located in the
+        temporal and occipital cortex (gray),
+        PPA overlap of all subjects (blue),
+        and individual PPA(s) (red).}
     \label{fig:bland-altman} \end{figure*}

### 2020-12-11 paper/main.tex
minor changes to discussion of group

@@
 Unthreholded $z$-maps of all contrasts on a group level as well as individual
-results of the primary $t$-contrasts can be found at
-\href{https://neurovault.org/collections/KADGMGVZ/}{NeuroVault}.\todo{still
+results of the primary $t$-contrasts for both naturalistic stimuli can be found
+at \href{https://neurovault.org/collections/KADGMGVZ/}{NeuroVault}.\todo{still
 private collection}
@@
 \subsection{Group results}
-
-\todo[inline]{paragraphs start with 1-2 sentences that set up the question
-that the paragraph answers; e.g. ``To verify that\dots''}
-
-\todo[inline]{middle of paragraph presents data \& logic that pertain the
-question}
-
-\todo[inline]{paragraph ends with a concluding / logical statement}
 
@@
 
-\todo[inline]{which contrast yielded NO clusters?}
-
-\todo[inline]{I consider tables of significant clusters in PPA for all contrasts
-as overkill. Maybe in ``supporting material'' or reference to dataset? all sign.
-clusters of all contrasts are in the comments}
+\todo[inline]{tables of significant clusters all contrasts = overkill!? Link to NeuoVault is added; sign. clusters of all contrasts are listed in the comments}
 
@@
 welche davon z.B. im Ergebnis wo von den anderen abgewichen haben. Das würde ja
-wichtige Hinweise geben}
+wichtige Hinweise geben; COH: imo discussing that will let the paper get way out
+of hand}
 
@@
 would show up but it wasn't aim of the study (had no ROIs for it anyway); imo
-this is an issue of story telling vs. hypotheses after results}
-
-\todo[inline]{structure is as follows: correlation of
-regressors; AO group; AV group; robustness AO + AV; anterior vs posterior PPA;
-other clusters significant across contrasts (= retrosplenial cortex and
-occipital place area)}
+this is an issue of ``nice story telling'' vs. HARKing}
 
@@
 % we use similar statistical models but with naturalistic stimuli
-Here, we use statistical models that are similar to previous studies that used
-small sets of experimentally controlled stimuli to investigate hemodynamic brain
-responses during two naturalistic stimuli.
+Similarly to previous studies that used small sets of experimentally controlled
+stimuli, we also used GLMs to investigate hemodynamic brain activity during two
+naturalistic stimuli.
 % more than just one contrast
-We computed varying GLM contrasts that differed in the contrasted categories and
-the amount of available data to test the robustness of our findings in both
-stimuli.
+For both naturalistic stimuli, we computed several $t$-contrasts that differed
+in the contrasted categories of stimulus features and the amount of available
+data to test the robustness of our findings.
 % comparison to localizer experiment
 We compare results of the primary contrast of each stimulus on the level of
-individual subjects to results that we gained from a dedicated visual localizer
-paradigm done with the same subjects \citep{sengupta2016extension}.
+individual subjects to results that we gained from a visual localizer experiment
+done with the same subjects \citep{sengupta2016extension}.
 % summary of results main finding
@@
 % to do
-\todo[inline]{this is just the main finding; other possible ``honourable''
-mentions like robustness of results, AV stimulus, individual results?}
+Other possible ``honourable'' mentions (here? and in the following discussion?)
+\begin{itemize}
+    \item RSC
+    \item what could be LOC / OPA
+    \item AV; should (shortly) be discussed
+    \item robustness (imo shortly discussed; it is about robustness not about
+        how all contrasts are different in detail and how results differ in
+        detail; yes, totally interesting but out of scope
+    \item discuss negative contrasts?
+\end{itemize}
 
@@
 % stimuli not designed for research purposes
-Both naturalistic stimuli were not designed to be used in a BOLD fMRI experiment
-but to entertain their audiences.
-% why correlation matrix  was created
-Thus, we first tested for correlation of regressors (s. \ref{fig:reg-corr}) that
-are based on the annotated stimulus features because a high degree of shared
-variance lowers detection power
+The audio-description and the movie were not designed to be used in a BOLD fMRI
+experiment but to entertain their audiences.
+%
+As a results, stimulus features that we annotated to create the regressors could
+have been correlated leading to shared variance that lowers detection power.
+% computing the correlations
+Hence, we first tested for correlation of regressors within and across both
+naturalistic stimuli (s. Figure \ref{fig:reg-corr})
 % results of computing feature correlation
-Results show no to minor correlations of regressors across all stimulus
-segments.
+Results show no to minor correlations of regressors with regressors of the same
+stimulus.
 % encouraged by that we build contrasts (statement)
-Thus we felt encouraged to create traditional/canonical voxel-wise GLMs that
+Thus, we felt encouraged to create traditional/canonical voxel-wise GLMs that
 modeled and contrasted hemodynamic activity similarly to previous studies that
-used simplified stimuli.
+used conceptualized stimuli.
 
@@
 
+\todo[inline]{I read Aziz again: visual localizer: radius of 16 mm around peak
+    voxel in each hemisphere = PPA; sentence experiment: reduced activity only
+    in left PPA, and only for famous places vs famous faces; I think they ran
+    their f-test on the average of the PPA voxels! anyway: their analysis is
+complicated, yet not sophisticated}
+
 % AO stimulus
 Group results of the AO stimulus' primary contrast yielded spatially concise
-clusters in the anterior part of the PPA group overlap taken from
-\citep{sengupta2016extension}.
+clusters in the anterior part of the PPA group overlap that we gained from a
+visual localizer experiment \citep{sengupta2016extension}.
 % diff to Aziz (2008)
-Unlike \citep{aziz2008modulation} we did not use whole sentences as events to
-model hemodynamic responses but modeled from on- to offset of single words that
-cue the listener about the movie's missing visual content.
+Unlike \citep{aziz2008modulation} who modeled events from on- to offset of
+sentences (describing unknown and famous places and faces), we modeled events
+from on- to offset of single words (that cue the listener about the missing
+visual content).
 % conclusion
-Our group results suggest that auditory spatial information does not just
-modulate activity in the PPA (depending on other factors like familiarity; s.
-\citep{aziz2008modulation}) but correlates with bilaterally increased
-activation.\todo{``modulate'' suggests causation}
-
-% Previous studies used tasks
+\citep{aziz2008modulation} found significantly increased activity in only the
+left PPA and only for sentences describing famous places compared to famous
+faces. Contrary, our group results suggest that auditory spatial information
+compared to non-spatial information correlates with bilaterally increased
+activation in its anterior.\todo{nice! and\dots?}
+
+% tasks in previous studies
 Usually studies that use small sets of experimentally controlled stimuli also
@@
 % but we are still different
-Our paradigm still differs from \citep{epstein1998ppa} because the relevant
+Our paradigm still differs from \citep{epstein1998ppa} because the modeled
 stimulus features were incidentally embedded in a continuous stream of auditory
 information.
-% conclusion
-The embeddedness prevents participants from making assumptions about the
-investigated perceptual process by just being exposed to the paradigm and thus
-mimics experiencing the world outside the lab more closely.
 % concluding statement: kinda automatic process
-The lack of a task further suggests that verbal spatial information is processed
-in the PPA in an automatic fashion and does not necessarily rely on deliberately
-paying attention to spatial information.
-
-\todo[inline]{following: how to frame it (better) that AV merely serves as
-conceptual control?; imo discussion of AV should be short anyway}
+The lack of a task suggests that verbal spatial information is processed in the
+anterior PPA in an automatic fashion and does not necessarily rely on
+deliberately paying attention to verbal spatial information.
+%
+Further, the incidential occurrence of modeled features prevents participants
+from making assumptions about the investigated perceptual process by just being
+exposed to the paradigm which mimics experiencing the world outside the lab more
+closely.
+
 % AV stimulus
@@
 % cross-modal control purpose?
+\todo[inline]{better frame that it is conceptual/cross-modal control; but what
+do the results tell us? yes, it ``kinda works'' but \dots?}
 \todo[inline]{concluding statement regarding AV vs AO and cross-modality of
@@
 % why we did a couple of contrasts
-For both stimuli we created additional contrasts that varied the amount of
+For both stimuli we created several contrasts that varied the amount of
 events available for the analysis and how well the annotated events within
@@
 % but
-Nevertheless, results also suggest that localization performance depends on the
-amount of available data and how well the feature space is modeled.
+Nevertheless, results also suggest that ``localization performance'' depends on
+the amount of available data and how well the feature space is modeled.
 % example
@@
 % ``confounding'' clusters
-Despite performing a whole brain analysis, we do not find many (random) clusters
+Despite performing a whole brain analysis, we do not find many [random] clusters
 in single contrasts or even systematically across contrasts that hamper the
@@
 % AO: auditory cortices
-For example in the AO results, contrasts that compare (among other categories)
-verbal cues about the change of a setting (\texttt{se\_new} > \texttt{se\_old})
-to categories that do not cue a change of a setting (contrasts 2, 3, 6, 7) show
-significant clusters in (primary and secondary) auditory cortices.\todo{``poor
-job of nuisance regressors?}
+Nevertheless, contrasts of the AO stimulus that compare verbal cues about the
+change of a setting (\texttt{se\_new} or \texttt{se\_old}) to categories that do
+not cue a change of a setting (contrasts 2, 3, 6, 7) show significant clusters
+in (primary and secondary) auditory cortices.\todo{``poor job of nuisance
+regressors?}
 % averaging vs. nuisance regressors
@@
 % possible reason
-This could be attributed to a possible change of the soundscape and/or increased
-volume when the narrative switches to a new setting.
+This could be attributed to a possible change of the soundscape when the
+narrative switches to a new setting.
 % concluding statement
@@
 Results of the AO contrasts consistently yielded significant clusters spatially
-constrained to the anterior part of the PPA group overlap (and to the anterior
-part of significant clusters of the AV contrasts).
+constrained to the anterior part of the PPA group overlap [and to the anterior
+part of significant clusters of the AV contrasts].
 % PPA might have submodules
 Previous studies provide evidence that the posterior PPA (pPPA) and anterior PPA
-(aPPA) show differences in both functional connectivity profiles and in
-response to low- and high-level visual features.
+(aPPA) show differences in both functional connectivity profiles and in response
+to low- and high-level visual features.
 
@@
 % functionality
-The pPPA is functionally more responsive than aPPA to low-level features of
-scenes or (abstract) objects \citep{baldassano2013differential,
+Moreover, the pPPA is functionally more responsive than the aPPA to low-level
+features of scenes or (abstract) objects \citep{baldassano2013differential,
 nasr2014thinking, rajimehr2011parahippocampal}.
@@
 % anterior
-The anterior PPA is more strongly functionally connected to portions of the
-default mode network, including caudal inferior parietal lobe (cIPL), the
-restrosplenial complex (RSC), medial PFC and the lateral surface of the anterior
-temporal lobe \citep{baldassano2013differential, baldassano2016two}
+The aPPA is more strongly functionally connected to portions of the default mode
+network, including caudal inferior parietal lobe (cIPL), the restrosplenial
+complex (RSC), medial PFC and the lateral surface of the anterior temporal lobe
+\citep{baldassano2013differential, baldassano2016two}
 % anterior cIPL is defined using the Eickhoff–Zilles PGp probabilistic
 % cytoarchitectonic map
-The aPPA is functionally more responsive than pPPA to high-level features of
-scenes (e.g. real-word size \citep{park2015parametric}; a scene's abstract
-identity/category \citep{marchette2015outside, watson2016patterns}) and objects
-(e.g. spatial contextual associations \citep{aminoff2007parahippocampal,
+Moreover, the aPPA is functionally more responsive than pPPA to high-level
+features of scenes (e.g. real-word size \citep{park2015parametric}; a scene's
+abstract identity/category \citep{marchette2015outside, watson2016patterns}) and
+objects (e.g. spatial contextual associations \citep{aminoff2007parahippocampal,
 aminoff2013role}).
 
-\todo[inline]{the mother of total confusion: in Aminoff (2007, 2013): anterior
-    PPA = spatial associations, region anterior to PPA = non-spatial
-    associations; but in Aminoff (2015): posterior PPA = spatial associations
-    and anterior PPA = non-spatial associations; hence: complete bullshit;
+\todo[inline]{the mother of total confusion: Aminoff shifts the PPA along the
+    anterior-poster axis depending on the publication; in Aminoff (2007, 2013):
+    anterior PPA = spatial associations, region anterior to (!) PPA =
+    non-spatial associations; in Aminoff (2015): posterior PPA = spatial
+associations, anterior PPA = non-spatial associations; hence: complete bullshit;
 ignore Aminoff (2015) due to various reasons}
@@
 
-The PPA is not a functionally homogeneous area but consists of
-subregions that ``activate selectively to scenes'' and ``cooperate to build a
-complete representation of a scene'' \citep{baldassano2013differential}.
+The PPA is not a functionally homogeneous area but consists of subregions that
+``activate selectively to scenes'' and ``cooperate to build a complete
+representation of a scene'' \citep{baldassano2013differential}.
 %
-Their distinct connectivity properties do suggest that each may be
-involved in specific aspects of visual and cognitive processing involved in the
-overarching goal of scene understanding \citep{baldassano2013differential}.
+Their distinct connectivity properties do suggest that each may be involved in
+specific aspects of visual and cognitive processing involved in the overarching
+goal of scene understanding \citep{baldassano2013differential}.
 
@@
 % baldassano2016two
-\citep{baldassano2016two}: RSC appears to be most directly
-involved in orienting the viewer to the structure of the environment (both
-within and beyond the borders of the presented image) for the purpose of
-navigational planning; it encodes both absolute location and facing direction
-[Vass and Epstein, 2013; Epstein and Vass, 2014; Marchette et al., 2014],
-integrates across views presented in a panoramic sequence [Park and Chun, 2009],
-and shows strong familiarity effects [Epstein et al., 2007a,b]
-\citep{baldassano2016two}.
+\citep{baldassano2016two}: RSC appears to be most directly involved in orienting
+the viewer to the structure of the environment (both within and beyond the
+borders of the presented image) for the purpose of navigational planning; it
+encodes both absolute location and facing direction [Vass and Epstein, 2013;
+Epstein and Vass, 2014; Marchette et al., 2014], integrates across views
+presented in a panoramic sequence [Park and Chun, 2009], and shows strong
+familiarity effects [Epstein et al., 2007a,b] \citep{baldassano2016two}.
 
@@
 
-\todo[inline]{check location in primary contrast and in overlap of contrasts}
-
-\todo[inline]{numbers of contrast in AO \& AV that show sign. clusters in
-LOC}
-
-\todo[inline]{e.g.
-Nakamura (2000). Functional delineation of the human occipito-temporal areas;
-Bettencourt (2013). The Role of Transverse Occipital Sulcus in Scene Perception;
-Dilks, Kanwisher (2013). The Occipital Place Area Is Causally and Selectively Involved in Scene Perception;
-Grill-Spector (2003). The neural basis of object perception;
-Nasr (2011). Scene-selective cortical regions in human and nonhuman primates;
-Hasson (2003). Large-scale mirror-symmetry organization;
-MacEvoy and Epstein (2007). Position selectivity in scene- and object-responsive\dots;
-Dilks (2011). Mirror-image sensitivity and invariance in object \& scene processing}
+\begin{itemize}
+
+\item Bettencourt (2013). The Role of Transverse Occipital Sulcus in Scene
+Perception \item Dilks, Kanwisher (2013). The Occipital Place Area Is Causally
+and Selectively Involved in Scene Perception \item Nasr (2011). Scene-selective
+    cortical regions in human and nonhuman primates \item Dilks (2011).
+    Mirror-image sensitivity and invariance in object \& scene processing \item
+    MacEvoy and Epstein (2007). Position selectivity in scene- and
+object-responsive \item Grill-Spector (2003). The neural basis of object
+    perception \item Hasson (2003). Large-scale mirror-symmetry organization
+    \item Nakamura (2000). Functional delineation of the human occipito-temporal
+        areas \end{itemize}
 
@@
 \subsubsection{AO stimulus}
-
-\todo[inline]{``problem'': if discussion of anterior vs. posterior PPA above
-turns out that anterior PPA is a submodul of the PPA we do not localize a
-``visual area'' with an auditory stimulus}
 

### 2020-12-11 paper/main.tex
minor changes to discussion of robustness

@@
 
-\todo[inline]{following is one exemplary sentence that would benefit from also
-mentioning that clusters should not be all over the brain which could be the
-case because naturalistic paradigm / confounding variables etc.}
-
 % study goal
@@
 % what we did We
-annotated a \unit[2]{h} movie and its temporally aligned audio-description to
+We annotated a \unit[2]{h} movie and its temporally aligned audio-description to
 create GLM contrasts similar to previous studies that used conceptualized
@@
 % why we did a couple of contrasts
-For both stimuli we created several contrasts that varied the amount of
-events available for the analysis and how well the annotated events within
-categories on average matched the stimulus type that we assumed to be
-preferentially processed in the PPA.
+For both stimuli we created several contrasts that varied the amount of events
+available for the analysis and how well the annotated events within categories
+on average matched the stimulus type that we assumed to be preferentially
+processed in the PPA.
 % PPA AO
@@
 Regarding contrasts of the AV stimulus, all five contrasts show significant
-bilateral clusters in the PPA but extending into more posterior brain regions.
+bilateral clusters in the PPA but also extending into more posterior brain
+regions.
 % results indicate robustness
 Thus, the results of the additional contrasts indicate that our findings are
-robust across contrasts and do not depend on the design of one specific
+robust across contrasts do not depend on the design of one specific
 contrasts.
@@
 % but
-Nevertheless, results also suggest that ``localization performance'' depends on
-the amount of available data and how well the feature space is modeled.
+Nevertheless, results are still influcended by [sensitive to] the amount of
+available data and how well the feature space is modeled.
 % example
@@
 For example in the AV results, we do not find significant clusters that could be
-attributed to cognitive processes like attention, eye movements[, or
-memory].\todo{which kind of memory}
+attributed to cognitive processes like attention or eye movements\todo{should
+already be mentioned in disc. of primary contrasts}
 % AO: auditory cortices
 Nevertheless, contrasts of the AO stimulus that compare verbal cues about the
-change of a setting (\texttt{se\_new} or \texttt{se\_old}) to categories that do
-not cue a change of a setting (contrasts 2, 3, 6, 7) show significant clusters
-in (primary and secondary) auditory cortices.\todo{``poor job of nuisance
-regressors?}
+change of a setting (\texttt{se\_new} or \texttt{se\_old}) to all non-spatial
+categories (cf. contrasts 2, 3, 6, 7) show significant clusters in (primary and
+secondary) auditory cortices.
 % averaging vs. nuisance regressors
@@
 % possible reason
-This could be attributed to a possible change of the soundscape when the
-narrative switches to a new setting.
+Significant clusters in auditory cortices could be correlating with a possible
+change of the soundscape when the narrator of the audio-description (or a cut in
+the movie) switches to a another setting.
 % concluding statement
@@
 
-todo[inline]{in 11 subjects there are voxels of higher z-score (in the PPA ROI)
+\todo[inline]{in 11 subjects there are voxels of higher z-score (in the PPA ROI)
     in the AO contrast than in the contrast of the visual localizer -> should

### 2020-12-11 paper/main.tex
changes to discussion of anterior vs posterior 1

@@
 % PPA might have submodules
-Previous studies provide evidence that the posterior PPA (pPPA) and anterior PPA
-(aPPA) show differences in both functional connectivity profiles and in response
-to low- and high-level visual features.
-
-% posterior connectivity
-The pPPA is more strongly functionally connected to the occipital visual cortex
-\citep{baldassano2013differential, baldassano2016two}.
+Previous studies provide evidence that the PPA can be devided into functionally
+subregions that might process different stimulus features [during visual scene
+perception].
+% posterior: functionality
+The posterior PPA (pPPA) is functionally more responsive than the anterior PPA
+(aPPA) to low-level features of scenes or (abstract) objects
+\citep{baldassano2013differential, nasr2014thinking,
+rajimehr2011parahippocampal}.
+% anterior cIPL is defined using the Eickhoff–Zilles PGp probabilistic
+% cytoarchitectonic map
+The aPPA is functionally more responsive than pPPA to high-level features of
+scenes (e.g. real-word size \citep{park2015parametric}; a scene's abstract
+identity/category \citep{marchette2015outside, watson2016patterns}) and objects
+(e.g. spatial contextual associations \citep{aminoff2007parahippocampal,
+aminoff2013role}).
+% connectivity
+Moreover, pPPA and aPPA show differences in connectivity profiles.
+% posterior
+The pPPA is more strongly functionally connected to the occipital
+visual cortex than the aPPA \citep{baldassano2013differential,
+baldassano2016two}.
 % including lateral occipital cortex (LOC) and transverse occipital sulcus (TOS)
-% functionality
-Moreover, the pPPA is functionally more responsive than the aPPA to low-level
-features of scenes or (abstract) objects \citep{baldassano2013differential,
-nasr2014thinking, rajimehr2011parahippocampal}.
-
 % anterior
@@
 complex (RSC), medial PFC and the lateral surface of the anterior temporal lobe
-\citep{baldassano2013differential, baldassano2016two}
-% anterior cIPL is defined using the Eickhoff–Zilles PGp probabilistic
-% cytoarchitectonic map
-Moreover, the aPPA is functionally more responsive than pPPA to high-level
-features of scenes (e.g. real-word size \citep{park2015parametric}; a scene's
-abstract identity/category \citep{marchette2015outside, watson2016patterns}) and
-objects (e.g. spatial contextual associations \citep{aminoff2007parahippocampal,
-aminoff2013role}).
+\citep{baldassano2013differential, baldassano2016two}.
 

### 2020-12-14 paper/main.tex
changes to discussion of anterior vs posterior 2

@@
 % nuisance regressors
-\todo[inline]{"Continuous bins lasting 40ms" ?!?; COH: goddamnit! I've rewritten
+\todo[inline]{"Continuous bins lasting 40ms?"; COH: goddamnit! I've rewritten
     this explanation a lot and finally stuck to the phrasing written in
@@
 %
-\todo[inline]{sounds meh but don't know how do write it better; results of
-    correlations are given here already; maybe the short discussion (cf. very
-    beginning of discussion) of these correlation could be put here too which
-    will saves space in the main text; but mixing methods/results/discussion is
-not absolutely "clean"}
+\todo[inline]{discussion of the regressors correlation at the very beginning of
+discussion could be pasted here; will save space there but will mix methods/
+results/ discussion here}
 
@@
 
+\todo[inline]{the mother of total confusion: Aminoff shifts the PPA along the
+    anterior-poster axis depending on publication;
+    in Aminoff (2007, 2013):
+    anterior PPA = spatial associations,
+    region anterior to (!) PPA = non-spatial associations;
+    in Aminoff (2015):
+    posterior PPA = spatial associations,
+    anterior PPA = non-spatial associations;
+    hence: complete bullshit;
+    ignore Aminoff (2015) due to various reasons}
+
 % intro
@@
 % posterior
-The pPPA is more strongly functionally connected to the occipital
-visual cortex than the aPPA \citep{baldassano2013differential,
-baldassano2016two}.
+The pPPA is more strongly functionally connected to the occipital visual cortex
+than the aPPA \citep{baldassano2013differential, baldassano2016two}.
 % including lateral occipital cortex (LOC) and transverse occipital sulcus (TOS)
@@
 \citep{baldassano2013differential, baldassano2016two}.
-
-\todo[inline]{the mother of total confusion: Aminoff shifts the PPA along the
-    anterior-poster axis depending on the publication; in Aminoff (2007, 2013):
-    anterior PPA = spatial associations, region anterior to (!) PPA =
-    non-spatial associations; in Aminoff (2015): posterior PPA = spatial
-associations, anterior PPA = non-spatial associations; hence: complete bullshit;
-ignore Aminoff (2015) due to various reasons}
-
-\paragraph{conclusion: subregions}
-
-The PPA is not a functionally homogeneous area but consists of subregions that
-``activate selectively to scenes'' and ``cooperate to build a complete
-representation of a scene'' \citep{baldassano2013differential}.
-%
-Their distinct connectivity properties do suggest that each may be involved in
-specific aspects of visual and cognitive processing involved in the overarching
-goal of scene understanding \citep{baldassano2013differential}.
-
-%
-The fact that anterior PPA had a lower sensitivity to our abstract object
-stimuli does not necessarily imply that this region does not use object
-information \citep{baldassano2013differential}. Previous work has shown that PPA
-responds to objects that have spatial associations [Aminoff et al. 2007], are
-space-defining [Mullally and Maguire 2011], and are navigationally-relevant
-[Janzen and Van Turennout 2004]. These types of responses require spatial memory
-and cannot be based purely on visual features like object shape.
-\citep{baldassano2013differential}.
-
-%
-[If anterior PPA is involved in processing spatial context, then space-defining
-    or navigationally-relevant objects could activate anterior PPA more strongly
-    than our abstract objects, which were unfamiliar and provided no sense of
-    context or orientation.
-%
-Further experiments will be required to determine whether what type of
-object-related information is used in this region
-\citep{baldassano2013differential}.]
+% conclusion: subregions
+According to the hypothesis by \citep{baldassano2013differential} the PPA
+consists of subregions that activate selectively to scenes and ``cooperate to
+build a complete representation of a scene''.
+% Their distinct connectivity properties do suggest that each may be involved in
+% specific aspects of visual and cognitive processing involved in the
+% overarching goal of scene understanding \citep{baldassano2013differential}.
+% The fact that anterior PPA had a lower sensitivity to our abstract object
+% stimuli does not necessarily imply that this region does not use object
+% information \citep{baldassano2013differential}. Previous work has shown that
+% PPA responds to objects that have spatial associations [Aminoff et al. 2007],
+% are space-defining [Mullally and Maguire 2011], and are
+% navigationally-relevant [Janzen and Van Turennout 2004]. These types of
+% responses require spatial memory and cannot be based purely on visual features
+% like object shape. \citep{baldassano2013differential}.
+Our results add further evidence that the PPA is not a homogeneous area but can
+be devided into functionally subregions.
+% pPPA
+Results of your study suggest that the pPPA is more concerned with visual
+aspects of spatial information as exclusively inherent in visual stimuli like
+pictures or movies.
+% aPPA
+The aPPA might be more concerned with non-visual aspects of spatial information
+(e.g. spatial contextual information \citep{aminoff2013role,
+aminoff2015associative, baumann2016functional}) inherent in both visual and
+verbal stimuli.
 
@@
 Apart from the PPA, we find significantly increased activity consistently across
-contrast of both contrasts in the retrosplenial cortex (RSC).
+contrasts of both stimuli in the retrosplenial cortex (RSC).
 % location functionally defined

### 2020-12-14 paper/main.tex
revise discussion of individual results

@@
 \begin{itemize}
-\item lateral occipital cortex: 4 contrasts (all bilateral)
+    \item RSC: 3 contrasts (all bilat; vse\_new > vpe\_old; vse\_new >
+        vse\_old, vpe\_old; vse\_new, vpe\_new > vpe\_old)
+    \item lateral occipital cortex: 4 contrasts (all except vse\_new > vse\_old; all bilateral)
 \end{itemize}
@@
 
+\todo[inline]{convey better that we do not have lots of ``random clusters''}
+
 \todo[inline]{discussion explains how results fill gap identified in
@@
 anterior PPA of both hemispheres.
+
 % to do
-Other possible ``honourable'' mentions (here? and in the following discussion?)
+\todo[inline]{Other possible ``honourable'' mentions; here (?), and in the
+following discussion?}
+
 \begin{itemize}
@@
 % results of computing feature correlation
-Results show no to minor correlations of regressors with regressors of the same
-stimulus.
+Results reveal no to minor correlations of regressors with regressors of the
+same stimulus.
 % encouraged by that we build contrasts (statement)
@@
 For example in the AV results, we do not find significant clusters that could be
-attributed to cognitive processes like attention or eye movements\todo{should
-already be mentioned in disc. of primary contrasts}
+attributed to cognitive processes like attention or eye movements\todo{could
+    already already be mentioned in discussion of primary contrasts}
 % AO: auditory cortices
@@
 
-\todo[inline]{check location in primary contrast and overlap across contrasts}
-
-\todo[inline]{report numbers of contrast in AO \& AV that show sign. clusters in
-RSC}
-
 % but RSC
-Apart from the PPA, we find significantly increased activity consistently across
-contrasts of both stimuli in the retrosplenial cortex (RSC).
+Apart from the PPA, we find significantly increased activity in the
+retrosplenial cortex (RSC) consistently across contrasts of both stimuli (AO
+stimulus: 7 contrasts; AV stimulus: 3 contrasts).
 % location functionally defined
-As a scene-responsive region, the RSC is functionally defined and not
-necessarily identical to the anatomically defined retrosplenial cortex [26]
-\citep{epstein2008parahippocampal}.
-% function
-The RSC is strongly active during scene viewing, scene imagery [25] and mental
-imagination of navigation through familiar environments [8]
+The RSC as a scene-selective region is not necessarily spatially congruent with
+the anatomically defined retrosplenial cortex [26] (BA 29 and 30)
+\citep{epstein2008parahippocampal} but functionally defined as the posterior
+medial region that exhibits increased hemodynamic activity to visual scenes and
+during mental imagination trough familiar environments [8]
 \citep{epstein2008parahippocampal}.
 % location
-The RSC is located in the retrosplenial cortex, and posterior cingulate region,
-near to the point where the calcarine sulcus joins the parietal-occipital sulcus
+This functionally defined RSC is located in the retrosplenial cortex, and
+posterior cingulate region (BA 23 and 31) [51–56], near to the point where the
+calcarine sulcus joins the parietal-occipital sulcus
 \citep{epstein2008parahippocampal}.
-% anatomy of real RSC
-The Retrosplenial cortex (BA 29 and 30) adjoins and is partially encircled by
-the posterior cingulate (BA 23 and 31) [51–56]
-\citep{epstein2008parahippocampal}.
 
 % discussion of what the RSC does
-interpretation cf.: \citep{vann2009what, chrastil2018heterogeneity,
-silson2019posterior}
-% conclusion
-
-% baldassano2016two
-\citep{baldassano2016two}: RSC appears to be most directly involved in orienting
-the viewer to the structure of the environment (both within and beyond the
-borders of the presented image) for the purpose of navigational planning; it
-encodes both absolute location and facing direction [Vass and Epstein, 2013;
-Epstein and Vass, 2014; Marchette et al., 2014], integrates across views
-presented in a panoramic sequence [Park and Chun, 2009], and shows strong
-familiarity effects [Epstein et al., 2007a,b] \citep{baldassano2016two}.
+interpretation cf.:
+\begin{itemize}
+    \item \citep{chrastil2018heterogeneity}
+    \item \citep{vann2009what}
+    \item \citep{silson2019posterior}
+    \item \citep{baldassano2016two}: RSC appears to be most directly involved in orienting the viewer to the structure of the environment (both within and beyond the borders of the presented image) for the purpose of navigational planning; it encodes both absolute location and facing direction [Vass and Epstein, 2013; Epstein and Vass, 2014; Marchette et al., 2014], integrates across views presented in a panoramic sequence [Park and Chun, 2009], and shows strong familiarity effects [Epstein et al., 2007a,b].
+\end{itemize}
 
@@
 \begin{itemize}
-
 \item Bettencourt (2013). The Role of Transverse Occipital Sulcus in Scene
-Perception \item Dilks, Kanwisher (2013). The Occipital Place Area Is Causally
-and Selectively Involved in Scene Perception \item Nasr (2011). Scene-selective
-    cortical regions in human and nonhuman primates \item Dilks (2011).
-    Mirror-image sensitivity and invariance in object \& scene processing \item
-    MacEvoy and Epstein (2007). Position selectivity in scene- and
-object-responsive \item Grill-Spector (2003). The neural basis of object
-    perception \item Hasson (2003). Large-scale mirror-symmetry organization
+    Perception
+\item Dilks, Kanwisher (2013). The Occipital Place Area Is Causally and
+    Selectively Involved in Scene Perception
+\item Nasr (2011). Scene-selective cortical regions in human and nonhuman
+    primates
+\item Dilks (2011). Mirror-image sensitivity and invariance in object \& scene
+    processing
+\item MacEvoy and Epstein (2007). Position selectivity in scene- and
+    object-responsive
+\item Grill-Spector (2003). The neural basis of object perception
+\item Hasson (2003). Large-scale mirror-symmetry organization
 \item Nakamura (2000). Functional delineation of the human occipito-temporal
-        areas \end{itemize}
-
-%
-\citep{baldassano2016two} regarding functional difference pPPA vs. OPA: The
-functional distinction between pPPA and OPA is currently unclear. Previous work
-has speculated about the purpose of the apparent ventral and dorsal
-``duplication'' of regions sensitive to large landmarks, proposing that it may
-be related to different output goals (e.g., action planning in OPA, object
-recognition in pPPA)[Konkle and Caramazza, 2013], or to different input
-connections (e.g., lower visual field processing in OPA, upper visual field
-processing in pPPA)[Kravitz et al., 2013; Silson et al., 2015]. OPA and pPPA may
-also use information from different visual eccentricities: OPA processing less
-peripheral, relatively high-resolution environmental features. pPPA processing
-more peripheral, large-scale geometry, and context [Baldassano et al., 2016a]
-\citep{baldassano2016two}.
+    areas
+\item \citep{baldassano2016two} regarding functional difference pPPA vs. OPA:
+    The functional distinction is unclear.
+    Previous work has speculated about the purpose of the apparent ventral and
+    dorsal ``duplication'' of regions sensitive to large landmarks, proposing
+    that it may be related to different output goals (e.g., action planning in
+    OPA, object recognition in pPPA)[Konkle and Caramazza, 2013], or to
+    different input connections (e.g., lower visual field processing in OPA,
+    upper visual field processing in pPPA)[Kravitz et al., 2013; Silson et al.,
+    2015].
+    OPA and pPPA may also use information from different visual
+    eccentricities: OPA processing less peripheral, relatively high-resolution
+    environmental features. pPPA processing more peripheral, large-scale
+    geometry, and context [Baldassano et al., 2016a]
+\end{itemize}
 
@@
 
-An examination of these results on an individual participant basis reveals that
-this pattern remains highly reliable and, therefore, does not appear to be a
-by-product of group averaging across slightly offset discrete functional
-subregions[aminoff2015associative].
-
-\subsubsection{AO stimulus}
-
-\todo[inline]{how to discuss Bland-Altman-Plots? Let's talk about that
-shortly please}
-
-\todo[inline]{in 11 subjects there are voxels of higher z-score (in the PPA ROI)
-    in the AO contrast than in the contrast of the visual localizer -> should
-    all be in the anterior part of the PPA ROI, i.e. the area that belongs to
-    the significant cluster of the AO contrast}
-
-\todo[inline]{shortcoming: no task to attend to spatial information}
-
-\todo[inline]{different level of alertness during paradigms}
+\todo[inline]{how to discuss Bland-Altman-Plots???}
+
+\todo[inline]{dunno if this is meaningful: z-scores in the anterior part of
+    PPA are higher in AO contrasts than in contrast of localizer}
 
 % intro
-In order to test the audio-description's performance as a functional localizers,
-we also compared the results of the audio-description's primary contrast to
-results of the dedicated visualizer on the level of individual subjects.
+To test if an auditory narrative could substitute a visual localizer experiment,
+we also examined the results of the primary AO contrast on the level of
+individual subjects.
 % results of dedicated localizer
-The dedicated localizer \citep{sengupta2016extension} yielded bilateral ROIs in
-12 of 14 subjects and a unilateral right ROI in two subjects (sub-04, sub-20).
+The visual localizer \citep{sengupta2016extension} revealed bilateral ROIs in 12
+of 14 subjects and a unilateral right ROI in two subjects (sub-04, sub-20).
 % in the current study
 The audio-description's primary contrast yielded significant bilateral clusters
-in 9 of 14 subjects (of which sub-04 shows just right-lateralized PPA ROI)  and
-a unilateral significant cluster in one subject.
+in 9 of 14 subjects (of which sub-04 shows just right-lateralized PPA ROI) and a
+unilateral significant cluster in one subject.
+%
+Whereas \citep{sengupta2016extension} chose the subjectively ``best fitting
+$z$-threshold in a subject's unthresholded $z$-map by visual judgment, we used a
+``one threshold fits all approach`` (Z>3.4, p<.05 cluster-corrected).
+% group vs individual
+Results on an inidividual level reveal that significant cluster are located in
+the anterior part of individual PPA ROIs. Thus, the pattern that was revealed on
+a group level is not just a by-product of the averaging process but can reliably
+be found in individual study participants.
 % conclusion
-Results of our exploratory analyses suggest that a naturalistic auditory
-stimulus is suitable to localize (the anterior part) of a higher-level visual
-area in the majority of subjects.
-
-% one threshold for all
-Here we used a ``one threshold fits all approach`` whereas
-\citep{sengupta2016extension} chose the best fitting $z$-threshold in a
-subject's unthresholded $z$-maps by visual judgment and the ``best fitting''
-threshold.
-% one contrast for all
-Moreover, we chose the same contrast to look at individual results of all
-subjects.
+Lastly, our exploratory analyses suggest that a naturalistic auditory stimulus
+is in principle suitable to localize (the anterior part) of a higher-level
+visual area in the majority of subjects.
 % chose the best contrast in the future
@@
 
-% quote from Hanke (2014)
-\citep{hanke2014audiomovie}: Compared to AV stimulus, the AO stimulus leaves a
-much larger margin for inter-individual differences in imagining scenery, as
-well as actors' character and personality traits, while still preserving the
-time-locked presentation of information to a listener. At the same time, the AO
-stimulus limits the effect of an attentional focus on the selection of a subset
-of simultaneously occurring auditory events, in contrast to the selection of
-different parts of the visual field.
-
 \todo[inline]{discussion of individual differences? what do the results
@@
 
-\todo[inline]{was not aim of the study; AV ROIs are in the plot of individual
-    slices but not in the Bland-Altman-Plots}
+\todo[inline]{was not aim of study; results of primary AV contrasts are in plots
+    if individual; Bland-Altman-Plots focus on primary AO contrast alone}
 
@@
 \todo[inline]{Würde nicht so sehr auf Shortcomings eingehen}
+
+\todo[inline]{shortcoming: no task to attend to spatial information}
+
+\todo[inline]{different level of alertness during paradigms}
 
@@
 
-\subsubsection{pros \& cons of natural stimuli (esp. narrative) as localizer}
+\subsubsection{zpros \& cons of natural stimuli (esp. narrative) as localizer}
+
+% quote from Hanke (2014)
+\citep{hanke2014audiomovie}: the AO stimulus leaves a much larger margin for
+inter-individual differences in imagining scenery.  The AO stimulus limits the
+effect of an attentional focus on the selection of a subset of simultaneously
+occurring auditory events, in contrast to the selection of different parts of
+the visual field.
 

### 2020-12-14 paper/main.tex
some revision of end of discussion

@@
 
-\subsection{shortcomings in general}
-
-\todo[inline]{Würde nicht so sehr auf Shortcomings eingehen}
-
-\todo[inline]{shortcoming: no task to attend to spatial information}
+\subsection{shortcomings}
+
+\todo[inline]{SE: Würde nicht so sehr auf Shortcomings eingehen}
 
@@
 
-\todo[inline]{cf. Methods: annotation \& Methods: AO copes}
 % optimal stimulus type in vision
@@
 landmarks ((\texttt{geo}; often buildings or other single aspects of a whole
-scene) and elements defining the geometry of a room/locale (\texttt{groom}) to
-non-spatial cues.
+scene) and elements defining the geometry of a room or locale (\texttt{groom}) to non-spatial cues.
 % we did not choose se\_new and se\_old
@@
 to more concrete spatial cues.
-
 % future studies
-Futures studies should chose a auditory narrative that better samples the
-feature space correlating with the brain process to be investigated.
-% future studies: stimulus material
-Future studies should probably use a different narrative that models the feature
-space of spatial information ``better'' (provides more events that are more
-easily classified to belong to distinctive categories).
-
-\todo[inline]{hypothesis of increased activation correlation with changes in the
-    soundscape; cf. control contrasts (e.g. \texttt{vse\_new} >
-    \texttt{pe\_old}).}
-% foreshadowing of narrator by soundscape
-Further, verbal cues are regularly forestalled by changes of the soundscape.
+Hence, future studies might investigate if a homogenous category of wholistic
+but vague verbal descriptions (e.g. ``a mountain landscape'') compared to a
+homogenous categories of more specific verbal descriptions of landmarks (e.g.
+``a beacon'') or houses (e.g. ``farmhouse'', ``apartment building'') lead to
+different levels of hemodynamic activity.
+
+%
+\todo[inline]{shortcoming but nice hypothesis imo}
+%
+Cuts probably correlate with change in setting; change in soundscape anticipates
+narrator (would lower detection power) or occurs in parallel with narrator; cf.
+correlation of cuts to other setting (independent of familiarity) with nouns
+that cue change of setting; cf. control contrasts [which ones?]
 % arnott
-\todo[inline]{e.g. arnott2008crinkling find increased activations of PPA to
-sound made by objects}
 % hypothesis
@@
 correlate with increased activity in the PPA.
+% arnott
+\todo[inline]{e.g. arnott2008crinkling finds increased activations in PPA to
+sounds made by objects (that reveil object's material/identity)}
 
@@
 
-\subsubsection{zpros \& cons of natural stimuli (esp. narrative) as localizer}
-
-% quote from Hanke (2014)
-\citep{hanke2014audiomovie}: the AO stimulus leaves a much larger margin for
-inter-individual differences in imagining scenery.  The AO stimulus limits the
-effect of an attentional focus on the selection of a subset of simultaneously
-occurring auditory events, in contrast to the selection of different parts of
-the visual field.
-
 \section{Conclusions}
 
+\todo[inline]{SE: frage ich mich das beim Durchgehen: Warum ist der Fokus so
+sehr auf Audiobook / AO, während AV doch eigentlich more natural and engaging
+ist? COH: at the moment, the discussion is not tailored to the topic
+``naturalistic stimulus as substitute to localizer'' as it is not and should not
+be the main focus}
+
 \todo[inline]{template has no section ``conclusion'' -> use the last paragraph}
 
-\todo[inline]{Conclusions aber irgendwie frage ich mich das relativ durchgehen):
-Warum ist der Fokus so sehr auf Audiobook / AO, während AV doch eigentlich more
-natural and engaging ist?}
-
 % natural stimulation
-Intro: Natural stimuli like movies \citep{hasson2008neurocinematics,
-sonkusare2019naturalistic} or narratives \citep{honey2012not,
-lerner2011topographic, silbert2014coupled} offer an easy to implement,
-(continuous,) complex, immersive, task-free paradigm that more closely resembles
-our natural dynamic environment than traditional experimental designs.
-% why naturalisti stimuli are so cool
-(see also \citep{sonkusare2019naturalistic, eickhoff2020towards,hamilton2018revolution})
-% re-use of data for independent research question
-Due to their continuity, complexity, and length, they offer a vast amount of
-data on a variety of brain functions like low-level perception, attention,
-comprehension, memory, emotions, or social interactions. This suggests the data
-can later be reused for variety of totally different, independent research
-questions, possibly on an individual level; increased compliance in individual
-diagnostics in ``special'' populations where compliance is more difficult to
-archive (pediatric or psychiatric)
-
-% we annotated a couple of features to build contrasts
-Method: The feature ``auditory spatial information'' is just one example of a
-stimulus feature that can be annotated and used to build a model.
-% data-driven vs. model-driven
-Why we used a traditional GLM...
-
-% results
-Results: Our results demonstrate...
-
-% conclusion: AO and AV robustness
-In summary, our results across add further evidence that model-driven analyses
-can be run on data from naturalistic stimuli to isolate brain activity
+Natural stimuli like movies \citep{eickhoff2020towards,
+hasson2008neurocinematics, sonkusare2019naturalistic} or narratives
+\citep{hamilton2018revolution, honey2012not, lerner2011topographic,
+silbert2014coupled, wilson2008beyond} offer an easy to implement, (continuous,)
+complex, immersive, task-free paradigm that more closely resembles our natural
+dynamic environment than traditional experimental designs.
+
+\begin{itemize}
+\item We reuse public data for independent research question
+\item GLM based on annotations to operationalize ``spatial perception''
+\item Our results add evidence that model-driven analyses based in annotations
+can be run on data from naturalistic stimuli to ``localize'' brain activity
 correlating with specific perceptual processes.
-% but
-Nevertheless isolation performance relies on how well the model captures
+\item ``localization performance'' relies on how well the model captures
 different aspects of the stimuli's feature space.
-
-% conclusion auditory localizer
-Conclusion: Thus, a complex but naturally engaging auditory stimulus like an
+\item PPA is functionally heterogenous region
+\item a complex but naturally engaging auditory stimulus like an
 audiobook might in principle be used as a non-visual localizer for a variety of
 brain functions in subjects who are not willing or able to follow task
-instructions during brain scanning.
+instructions during brain scanning [would state that explicitly in the summary
+at the end].
+\end{itemize}
+
+% \citep{hanke2014audiomovie}: the AO stimulus leaves a much larger margin for
+% inter-individual differences in imagining scenery. The AO stimulus limits the
+% effect of an attentional focus on the selection of a subset of simultaneously
+% occurring auditory events, in contrast to the selection of different parts of
+% the visual field.
 

### 2020-12-14 paper/main.tex
formatting

@@
 AV?; Also, außer bei fg\_av\_ger\_lr\_diff (wobei da keiner weiss, was das
-bedeutet)}
+bedeutet); COH: what is better: reference to table as it is now (more precise,
+but harder to read) or use non-cryptic words in the figure?}
 

### 2020-12-15 paper/main.tex
Some light editing of the intro, remove most comments

@@
 
-\todo[inline]{most of phrases containing the word ``isolate'' is gone; doing the
+\todo[inline]{doing the
     revision of the result section I realized that we probably should
@@
 
-\todo[inline]{studies regarding naturalistic stimuli are dropped (Hasson, 2004:
-reverse correlation in PPA; Bartels, 2004: GLM, FFA and EBA). That should be okay since we focus on the auditory part which should be clearer now; Hasson /
-Bartels might shortly be mentioned in the discussion though}
-
-\todo[inline]{mih: Possibly cite DuPre (2019) and declare that this study is a
-    concrete realization; COH: I read it but don't know what/how to cite it for
-    any other reason than just to cite it (here or in discussion)}
-
 % brain mapping via fMRI
@@
 
-\todo[inline]{The following review of O'Craven and Wolbers could be shortened.
-Keeping the small paragraph regarding Aziz should make the focus on auditory
-perception clearer. What do you think?}
-
-\todo[inline]{SE: Der Schwung zu Sprache (wobei speech auch erst am Satzende
-kommt) ist zu hart, da kommt man als Leser nicht gut mit}
-
 % literature review overview 1: imagination & haptic exploration
@@
 % Wolbers: connectivity analysis
-\todo[inline]{Wolbers performed connectivity analysis between PPA and occipital
-    cortex, and compares connectivity during visual and haptic paradigm: ``The
-    scene-related increase in coupling with the PPA was significantly stronger
-    in multiple clusters in occipital cortex under visual than haptic
-stimulation (Figure 2B; Table S2)''}
-
-\todo[inline]{following phrasing might be strange but necessary to delineate
-from Huth (2016); they do voxel-wise semantic modeling regarding places in PPA
-but imo that does not say anything about excitation/inhibition; interestingly
-Huth mentions PPA during talks but it is not discussed in any paper and despite
-being promised none of his group came up with a paper regarding that topic}
 
@@
 categories occurring in spoken language.
+\todo{phrasing might be strange but aims to delineate
+from Huth (2016); they do voxel-wise semantic modeling regarding places in PPA
+but imo that does not say anything about excitation/inhibition}
 % Aziz' stimuli
@@
 % three things in common
-The reviewed studies usually had three things in common that come along with
-advantages but also disadvantages:
+All reviewed studies share three common aspects:
 % designed stimulus set
@@
 % block-design & task
-Second, studies used block-designed paradigms to maximize detection power.
-Further, they usually employed an explicit perceptual judgment task.
+Second, studies used block-design paradigms to maximize detection power.
+Further, they usually employed an explicit (perceptual) judgment task.
 % conceptualized stimuli and block: disadvantages
 Block-design studies that use conceptualized stimuli and a task have the
-advantages of controlling confounding variables (e.g. color, luminance, size,
+advantage of controlling confounding variables (e.g. color, luminance, size,
 spatial frequencies, sentence length), maximizing detection power, and keeping
@@
 \cite{dubois2016building, eickhoff2020towards}).
-
-\todo[inline]{SE: make motivation of study clearer; gap in research; how it
-    (might) advance(s) the field; make clearer how current study solves the
-    problem; COH: I revised this part, it's clearer at least
-if I read it now}
 
@@
 discussion and conclusion} Our results demonstrate that (a), (b), (c).
-
-\todo[inline]{Bzgl. Open Source der Ergebnisse/Skripte: Dazu habe ich hier
-nichts geschrieben; probably something like ``all raw data, scripts, and
-results are available under xy as datalad/BIDS dataset''}
 

### 2020-12-15 paper/main.tex
Standardize on audio-description (AD) not audio-only (AO)
You actually introduce it as such, and I think this is a much better
term that makes clear that this is a narrative, and not just the sound
track of the movie.

@@
 % audio-description
-a) the audio-description of the Hollywood movie ``Forrest Gump'' (i.e. the
-audio-only variant of the movie), and
+a) the audio-description (AD) of the Hollywood movie ``Forrest Gump'',
+and
 % audio-visual
-b) the [actual] audio-visual movie [itself].
+b) the original audio-visual (AV) movie.
 % studyforrest dataset
@@
 (\href{http://www.studyforrest.org}{studyforrest.org}).
-% first: group level AO
+% first: group level AD
 First on a group average level, general linear model (GLM) contrasts based on
@@
 The same subjects were
-% AO
-a) listening to the audio-description (AO study; \citep{hanke2014audiomovie}) of
+% AD
+a) listening to the audio-description (AD study; \citep{hanke2014audiomovie}) of
 the movie ``Forrest Gump'',
@@
 \subsection{Participants}
-% AO study
-In the AO study \citep{hanke2014audiomovie}, 20 German native speakers (all
+% AD study
+In the AD study \citep{hanke2014audiomovie}, 20 German native speakers (all
 right-handed, age 21–38 years, mean age 26.6 years, 12 male) listened to the
@@
 In the AV study \citep{hanke2016simultaneous}, 15 participants (21–39 years,
-mean age 29.4, six female) of the prior AO study watched the audio-visual movie
+mean age 29.4, six female) of the prior AD study watched the audio-visual movie
 with dubbed German audio track \citep{ForrestGumpDVD}.
@@
 
-% AO & AV stimulus name & references
+% AD & AV stimulus name & references
 We used the German DVD release \citep{ForrestGumpDVD} of the audio-visual movie
@@
 Forrest Gump.
-% AO: additional narrator
+% AD: additional narrator
 In the largely identical audio-description, an additional male narrator
@@
 
-% AO & AV: stimulus creation
+% AD & AV: stimulus creation
 The audio-description was temporally aligned to the audio track of the German
@@
 and familiarity with the movie.
-% AO & AV: instructions
+% AD & AV: instructions
 Before the experiment, participants were instructed to inhibit physical
@@
 audiobook'' or ``enjoy the movie'' respectively.
-% AO & AV: presentation & instructions
+% AD & AV: presentation & instructions
 Audio-description and movie segments were presented in chronological order with
@@
 
-% AO
-In the AO study, visual instructions were presented on a rear-projection screen
+% AD
+In the AD study, visual instructions were presented on a rear-projection screen
 inside scanner bore using an LCD projector (DLA-G150CL, JVC Ltd.). During the
@@
 
-\todo[inline]{auditory stimulation was the same in AO and AV?}
-
-% AO & AV: auditory stimulation
-In the AO and AV study, auditory stimulation was delivered through an MR confon
+\todo[inline]{auditory stimulation was the same in AD and AV?}
+
+% AD & AV: auditory stimulation
+In the AD and AV study, auditory stimulation was delivered through an MR confon
 mkII+ driving custom-built in-ear headphones (HP-M01, MR confon GmbH, Magdeburg,
@@
 
-% AO
-In the AO study, a whole-body \unit[7]{Tesla} Siemens MAGNETOM magnetic
+% AD
+In the AD study, a whole-body \unit[7]{Tesla} Siemens MAGNETOM magnetic
 resonance scanner equipped with a local circularly polarized head transmit and a
@@
 
-\todo[inline]{what is missing: As I see it, AO must have been downsampled to
+\todo[inline]{what is missing: As I see it, AD must have been downsampled to
 2.5x2.5x2.5 mm and AV must have been upsampled from 3.0 to 2.5mm??}
@@
 Data of one participant were dropped to due to invalid distortion correction
-during scanning of the AO stimulus.
+during scanning of the AD stimulus.
 % preprocessing intro
@@
 
-% AO annotation
-For the analysis of the AO stumulus, we extended a publicly available annotation
+% AD annotation
+For the analysis of the AD stumulus, we extended a publicly available annotation
 of speech \citep{haeusler2020speechanno} by further annotating words spoken by
@@
 
-% AO regressors
+% AD regressors
 \begin{table*}[h!]
     \caption{Overview of events to build the 18 regressors for the
-        analysis of the audio-only (AO) stimulus. Some of the annotation's
+        analysis of the audio-only (AD) stimulus. Some of the annotation's
         original categories (female, females, fname; male, males, mname; face,
@@
 % pooling of categories
-To create the regressor for the GLM of the AO stimulus, some of
+To create the regressor for the GLM of the AD stimulus, some of
 the original 18 categories that were similar but offered only a small amount of
@@
 the five movie cut-related regressors used in the GLM of the AV stimulus (see
-details below) in the model of the AO stimulus.
+details below) in the model of the AD stimulus.
 % nuisance regressors
@@
 \tabularnewline
-se\_new & control for AO narrator & \aoSenewAll & \aoSenewI & \aoSenewII & \aoSenewIII & \aoSenewIV & \aoSenewV & \aoSenewVI & \aoSenewVII & \aoSenewVIII
-\tabularnewline
-se\_old & control for AO narrator & \aoSeoldAll & \aoSeoldI & \aoSeoldII & \aoSeoldIII & \aoSeoldIV & \aoSeoldV & \aoSeoldVI & \aoSeoldVII & \aoSeoldVIII
+se\_new & control for AD narrator & \aoSenewAll & \aoSenewI & \aoSenewII & \aoSenewIII & \aoSenewIV & \aoSenewV & \aoSenewVI & \aoSenewVII & \aoSenewVIII
+\tabularnewline
+se\_old & control for AD narrator & \aoSeoldAll & \aoSeoldI & \aoSeoldII & \aoSeoldIII & \aoSeoldIV & \aoSeoldV & \aoSeoldVI & \aoSeoldVII & \aoSeoldVIII
 \tabularnewline
@@
 % null regressor
-As for the regressors for AO stimulus, a null regressor was chosen for a
+As for the regressors for AD stimulus, a null regressor was chosen for a
 regressor in a segment if that segment did not contain an event of the
@@
 \todo[inline]{SE: Die Abkürzungen in Figure 1: Da steigt keiner hinter; habe
-jetzt lange darüber gebrütet: Es gibt also kaum eine Korrelation zwischen AO und
+jetzt lange darüber gebrütet: Es gibt also kaum eine Korrelation zwischen AD und
 AV?; Also, außer bei fg\_av\_ger\_lr\_diff (wobei da keiner weiss, was das
@@
 spatial information compared to the perception of ``non-spatial'' information
-differently in eight $t$-contrasts for the AO stimulus (see Table
+differently in eight $t$-contrasts for the AD stimulus (see Table
 \ref{tab:ao-contrasts}) and five $t$-contrasts for the AV stimulus (see Table
@@
 
-% AO: primary contrast
-In the primary contrast of the AO stimulus, we contrasted landmarks
+% AD: primary contrast
+In the primary contrast of the AD stimulus, we contrasted landmarks
 \texttt{geo}, and rooms and geometry-defining objects \texttt{geo-room} with all non-geometry related categories (\texttt{body},
@@
 
-\paragraph{control contrasts: AO \& AV}
+\paragraph{control contrasts: AD \& AV}
 
@@
 Finally, we created several contrasts as negative control for both stimuli.
-% AO stimulus
-For the AO stimulus, we created five $t$-contrasts (see Table
+% AD stimulus
+For the AD stimulus, we created five $t$-contrasts (see Table
 \ref{tab:ao-contrasts}) to test if increased activation in the PPA was
@@
 condition (texttt{vno\_cut} for negative control purposes (see Table
-\ref{tab:av-contrasts}) by using regressors based on regressors of the AO
+\ref{tab:av-contrasts}) by using regressors based on regressors of the AD
 stimulus. One contrast (\texttt{vs\_new} > \texttt{vpe\_old})  was created by
@@
 \caption{Contrasts of parameter estimates for the analysis of the audio-only
-    stimulus (AO).
+    stimulus (AD).
     Contrast 1-8 aim to isolate the PPA.
@@
 
-\todo[inline]{individual results: AO trifft besser die VIS-PPA "trifft" als AV.
+\todo[inline]{individual results: AD trifft besser die VIS-PPA "trifft" als AV.
     Das ist zumindest sehr überraschend, oder?; COH: actually it isn't because
@@
 
-% all AO contrasts
+% all AD contrasts
 % 1 PPA (l/r); RSC (l/r), LOC (l/r)
@@
 
-\subsubsection{AO: PPA in primary contrast}
+\subsubsection{AD: PPA in primary contrast}
 
@@
 activity in the PPA.
-% primary AO contrast
+% primary AD contrast
 The primary $t$-contrast for the audio-description (\texttt{geo, groom} >
@@
 
-% table group results primary AO contrast
+% table group results primary AD contrast
 \begin{table*}[t]
@@
 
-% figure group results primary AO & AV contrasts
+% figure group results primary AD & AV contrasts
 \begin{figure*} \centering
@@
 
-\subsubsection{AO: robustness of PPA across contrasts}
+\subsubsection{AD: robustness of PPA across contrasts}
 
@@
 
-% all eight AO PPA contrasts
+% all eight AD PPA contrasts
 In order to test the robustness of our findings, we created overall eight
-$t$-contrasts for the AO stimulus (see Table \ref{tab:ao-contrasts}).
+$t$-contrasts for the AD stimulus (see Table \ref{tab:ao-contrasts}).
 % results
@@
 
-% figure group results of robustness across all AO & AV contrasts
+% figure group results of robustness across all AD & AV contrasts
 \begin{figure*} \centering
@@
 
-\paragraph{AO: other significant clusters across contrasts}
+\paragraph{AD: other significant clusters across contrasts}
 % precuneus = retrosplenial cortex ?
@@
 \item lateral occipiatal cortex: 6 contrasts (4 bilateral, 2 unilateral =
-    transverse occipital sulcus / occipiatal place area?; AO \& AV clusters
-    overlap but AO clusters are more lateral, AV cluster are more medial \&
+    transverse occipital sulcus / occipiatal place area?; AD \& AV clusters
+    overlap but AD clusters are more lateral, AV cluster are more medial \&
     caudal)
@@
 
-\subsubsection{AO \& AV: (negative) control contrasts}
+\subsubsection{AD \& AV: (negative) control contrasts}
 
@@
 
-% AO stimulus
-AO stimulus (using annotation of movie cuts) all null results except: contrast 9
+% AD stimulus
+AD stimulus (using annotation of movie cuts) all null results except: contrast 9
 (vse\_new > pe\_old): right RSC.
@@
 % ref to figure
-Figure \ref{fig:subs-thresh-ppa} depicts thresholded $z$-maps of the primary AO
+Figure \ref{fig:subs-thresh-ppa} depicts thresholded $z$-maps of the primary AD
 and AV $t$-contrast, and the outline of the individual PPAs
@@
 % liberally)
-% sub-01 (m): PPA (l/r), AO (l/r), AV (-/r); RSC: AO (l/r), AV (-/-)
-% sub-02 (m): PPA (l/r), AO (-/-), AV (l/-); RSC: AO (-/-), AV (-/-)
-% sub-03 (f): PPA (l/r), AO (-/-), AV (-/r); RSC: AO (-/-), AV (-/-)
-% sub-04 (f): PPA (-/r), AO (l/r), AV (-/r); RSC: AO (l/r), AV (-/-) !
-% sub-05 (m): PPA (l/r), AO (-/-), AV (-/-); RSC: AO (-/-), AV (-/-)
-% sub-06 (m): PPA (l/r), AO (l/r), AV (-/-); RSC: AO (l/-), AV (-/-)
-% sub-09 (m): PPA (l/r), AO (l/-), AV (l/r); RSC: AO (l/r), AV (l/r)
-% sub-14 (f): PPA (l/r), AO (l/r), AV (-/r); RSC: AO (l/r), AV (-/-)
-% sub-15 (m): PPA (l/r), AO (l/r), AV (-/r); RSC: AO (l/r), AV (l/r)
-% sub-16 (m): PPA (l/r), AO (l/r), AV (l/r); RSC: AO (l/r), AV (l/-)
-% sub-17 (m): PPA (l/r), AO (l/r), AV (l/r); RSC: AO (l/r), AV (l/r)
-% sub-18 (m): PPA (l/r), AO (l/r), AV (l/r); RSC: AO (l/r), AV (-/r)
-% sub-19 (f): PPA (l/r), AO (l/r), AV (-/r); RSC: AO (l/r), AV (l/r)
-% sub-20 (f): PPA (-/r), AO (-/-), AV (l/r); RSC: AO (-/-), AV (-/-)
+% sub-01 (m): PPA (l/r), AD (l/r), AV (-/r); RSC: AD (l/r), AV (-/-)
+% sub-02 (m): PPA (l/r), AD (-/-), AV (l/-); RSC: AD (-/-), AV (-/-)
+% sub-03 (f): PPA (l/r), AD (-/-), AV (-/r); RSC: AD (-/-), AV (-/-)
+% sub-04 (f): PPA (-/r), AD (l/r), AV (-/r); RSC: AD (l/r), AV (-/-) !
+% sub-05 (m): PPA (l/r), AD (-/-), AV (-/-); RSC: AD (-/-), AV (-/-)
+% sub-06 (m): PPA (l/r), AD (l/r), AV (-/-); RSC: AD (l/-), AV (-/-)
+% sub-09 (m): PPA (l/r), AD (l/-), AV (l/r); RSC: AD (l/r), AV (l/r)
+% sub-14 (f): PPA (l/r), AD (l/r), AV (-/r); RSC: AD (l/r), AV (-/-)
+% sub-15 (m): PPA (l/r), AD (l/r), AV (-/r); RSC: AD (l/r), AV (l/r)
+% sub-16 (m): PPA (l/r), AD (l/r), AV (l/r); RSC: AD (l/r), AV (l/-)
+% sub-17 (m): PPA (l/r), AD (l/r), AV (l/r); RSC: AD (l/r), AV (l/r)
+% sub-18 (m): PPA (l/r), AD (l/r), AV (l/r); RSC: AD (l/r), AV (-/r)
+% sub-19 (f): PPA (l/r), AD (l/r), AV (-/r); RSC: AD (l/r), AV (l/r)
+% sub-20 (f): PPA (-/r), AD (-/-), AV (l/r); RSC: AD (-/-), AV (-/-)
 
@@
 fusiform gyrus and anterior lingual gyrus].
-% AO
-In the current analysis of the AO stimulus, we use the same AO (and AV) contrast
+% AD
+In the current analysis of the AD stimulus, we use the same AD (and AV) contrast
 for all subjects. We find statistically significant bilateral clusters in nine
@@
 To better depict/convey the agreement and difference between individual results
-of the visual localizer and the primary AO contrast, we created one
+of the visual localizer and the primary AD contrast, we created one
 Bland-Altman-Plots for each of the 14 subjects (see Figure
@@
 The y-axis of every subplot depicts the difference of $z$-values of two
-spatially corresponding voxels (dedicated localizer minus AO stimulus).
+spatially corresponding voxels (dedicated localizer minus AD stimulus).
 % masking
@@
 the dedicated localizer, values below the horizontal line depict voxels that
-show higher $z$-value in the AO stimulus.
+show higher $z$-value in the AD stimulus.
 
@@
         the visual localizer and in the unthresholded z-map of contrast 1 of the
-        AO stimulus (KDE plot on the top). The y-axis depicts the difference of
+        AD stimulus (KDE plot on the top). The y-axis depicts the difference of
         two voxels (KDE plot on the right).
@@
 aber auch mit der falschen Perspektive ran? Für mich würde der Vergleich
-"localizer vs naturalistic" im vordergrund stehen, AO vs AV dann eine sehr
+"localizer vs naturalistic" im vordergrund stehen, AD vs AV dann eine sehr
 spannende aber logisch nachgeschaltete Frage sein.}
@@
 
-\todo[inline]{SE: VIS vs AV vs AO: Wer liefert was über die PPA. Dieser
+\todo[inline]{SE: VIS vs AV vs AD: Wer liefert was über die PPA. Dieser
 Vergleich bzw. die Diskussion über Gemeinsamkeiten \& Unterschiede fehlt mir
@@
 
-\subsection{group level: AO \& AV (PPA only)}
+\subsection{group level: AD \& AV (PPA only)}
 
@@
 
-% AO stimulus
-Group results of the AO stimulus' primary contrast yielded spatially concise
+% AD stimulus
+Group results of the AD stimulus' primary contrast yielded spatially concise
 clusters in the anterior part of the PPA group overlap that we gained from a
@@
 that span the group overlap of individual PPA ROIs from anterior to posterior.
-% difference in location/size to AO and VIS
+% difference in location/size to AD and VIS
 Clusters also expand into more posterior regions (occipital fusiform gyrus,
@@
 do the results tell us? yes, it ``kinda works'' but \dots?}
-\todo[inline]{concluding statement regarding AV vs AO and cross-modality of
+\todo[inline]{concluding statement regarding AV vs AD and cross-modality of
 results?}
@@
 processed in the PPA.
-% PPA AO
-Regarding contrasts of the AO stimulus, six of eight contrasts show significant
+% PPA AD
+Regarding contrasts of the AD stimulus, six of eight contrasts show significant
 bilateral clusters in the anterior part of the group PPA overlap.
@@
 % example
-For example, contrast 8 of the AO stimulus (\texttt{se\_new} > texttt{se\_old})
+For example, contrast 8 of the AD stimulus (\texttt{se\_new} > texttt{se\_old})
 that used the most heterogeneous categories comprising the least amount of
@@
     already already be mentioned in discussion of primary contrasts}
-% AO: auditory cortices
-Nevertheless, contrasts of the AO stimulus that compare verbal cues about the
+% AD: auditory cortices
+Nevertheless, contrasts of the AD stimulus that compare verbal cues about the
 change of a setting (\texttt{se\_new} or \texttt{se\_old}) to all non-spatial
@@
 % intro
-Results of the AO contrasts consistently yielded significant clusters spatially
+Results of the AD contrasts consistently yielded significant clusters spatially
 constrained to the anterior part of the PPA group overlap [and to the anterior
@@
 Apart from the PPA, we find significantly increased activity in the
-retrosplenial cortex (RSC) consistently across contrasts of both stimuli (AO
+retrosplenial cortex (RSC) consistently across contrasts of both stimuli (AD
 stimulus: 7 contrasts; AV stimulus: 3 contrasts).
@@
 \todo[inline]{dunno if this is meaningful: z-scores in the anterior part of
-    PPA are higher in AO contrasts than in contrast of localizer}
+    PPA are higher in AD contrasts than in contrast of localizer}
 
@@
 To test if an auditory narrative could substitute a visual localizer experiment,
-we also examined the results of the primary AO contrast on the level of
+we also examined the results of the primary AD contrast on the level of
 individual subjects.
@@
 \todo[inline]{was not aim of study; results of primary AV contrasts are in plots
-    if individual; Bland-Altman-Plots focus on primary AO contrast alone}
+    if individual; Bland-Altman-Plots focus on primary AD contrast alone}
 
@@
 
-\subsubsection{AO contrast}
+\subsubsection{AD contrast}
 
@@
 \todo[inline]{SE: frage ich mich das beim Durchgehen: Warum ist der Fokus so
-sehr auf Audiobook / AO, während AV doch eigentlich more natural and engaging
+sehr auf Audiobook / AD, während AV doch eigentlich more natural and engaging
 ist? COH: at the moment, the discussion is not tailored to the topic
@@
 
-% \citep{hanke2014audiomovie}: the AO stimulus leaves a much larger margin for
-% inter-individual differences in imagining scenery. The AO stimulus limits the
+% \citep{hanke2014audiomovie}: the AD stimulus leaves a much larger margin for
+% inter-individual differences in imagining scenery. The AD stimulus limits the
 % effect of an attentional focus on the selection of a subset of simultaneously

### 2020-12-15 paper/main.tex
Shorten methods

@@
 % intro
-We used three subdatasets of the publicly available studyforrest dataset
-(\href{http://www.studyforrest.org}{studyforrest.org}) that has already been
-used by other research groups for independent research questions
+We used three components of the publicly available
+\href{http://www.studyforrest.org}{studyforrest.org} dataset that has already been
+used by other research groups in independent studies
 (e.g. \citep{ben2018hippocampal, jiahui2019predicting, hu2017decoding,
@@
 % AV
-b) watching the actual audio-visual movie (AV study;
+b) watching the original movie (AV study;
 \citep{hanke2016simultaneous}), and
@@
 The audio-description was temporally aligned to the audio track of the German
-DVD release. A few scenes less relevant to the major plot were removed to create
-the ``research cut'' lasting $\approx$ \unit[2]{h} \citep{hanke2014audiomovie,
+DVD release. A few scenes, less relevant to the main plot, were removed to create
+the ``research cut'' lasting \unit[$\approx$2]{h} \citep{hanke2014audiomovie,
 hanke2016simultaneous}.
@@
 Both stimuli were further processed (filtering, volume adjustments) to improve
-audibility during MRI scanning. Black horizontal bars at the top and bottom of
-the movie were replaced with medium-gray bars of the same size in order to
-increase background illumination for a more pleasant experience.
+audibility during MRI scanning.
 % splitting
-Each stimulus was split into eight segments of approximately 15 minutes. Except
-for the first segment, each segment started with a snippet of at least six
-seconds immediately preceding the movie scene boundary used to split the
-segments (see Figure 3a in \citep{hanke2014audiomovie}).
-% procedure: questionnaire
-Subjects filled out a questionnaire on their basic demographic information
-and familiarity with the movie.
+Each stimulus was split into eight segments of approximately \unit[15]{minutes}.
 % AD & AV: instructions
 Before the experiment, participants were instructed to inhibit physical
-movements except for eye-movements, and otherwise to simply ``enjoy the
-audiobook'' or ``enjoy the movie'' respectively.
+movements except for eye-movements, and otherwise to simply ``enjoy''.
 % AD & AV: presentation & instructions
@@
 during the first study on a day different from the fMRI session.
-
-\todo[inline]{contrary to claims in Sengupta, the pictures are NOT the same
-as used in Haxby, 2011; sets might have an intersection though}
 
@@
 scenes, and phase scrambled images.
-% mirror images
-Mirrored views of these 24 $\times$ 6 images were also used as stimuli.
 % controlled luminance and size
@@
 
-% paradigm implementation
-In all three studies, stimulation was implemented with
-\href{http://www.psychopy.org}{PsychoPy} \citep{peirce2007psychopy} running on a
-computer with the NeuroDebian operating system \citep{halchenko2012open}.
-
 % AD
 In the AD study, visual instructions were presented on a rear-projection screen
-inside scanner bore using an LCD projector (DLA-G150CL, JVC Ltd.). During the
+inside scanner bore. During the
 functional scans, the projector presented a medium gray screen with the primary
@@
 fatigue.
-
 % AV & VIS
 In the AV and VIS study, visual instructions and stimuli were presented on a
-rear-projection screen using an LCD projector (JVC DLA RS66E, JVC Ltd., light
-transmission reduced to \unit[13.7]{\%} with a gray filter) connected to the
-stimulus computer.
+rear-projection screen
 % screen size
-The movie was shown at a viewing distance of \unit[63]{cm} in \unit[720]{p}
-resolution at full width on a \unit[1280 $\times$ 1024]{pixel} screen with
-\unit[60]{Hz} video refresh rate and screen dimension of \unit[26.5 $\times$
-21.2]{cm}.
-% angle of view: AV
-In the AV study, this corresponded to \unit[23.75 $\times$ 13.5] or \unit[23.75
-$\times$ 10.25]{cm} when considering only the movie content and excluding the
-horizontal gray bars.
+at a viewing distance of \unit[63]{cm}, with a movie frame projection size of
+\unit[23.75 $\times$ 10.25]{cm}.\todo{replace with visual angle size, in line with VIS}
 % angle of view: VIS
@@
 
-\todo[inline]{auditory stimulation was the same in AD and AV?}
-
 % AD & AV: auditory stimulation
-In the AD and AV study, auditory stimulation was delivered through an MR confon
-mkII+ driving custom-built in-ear headphones (HP-M01, MR confon GmbH, Magdeburg,
-Germany; \citep{baumgart1998electrodynamic}) that reduced the scanner noise by
-at least \unit[20–30]{dB}. Headphones were fed from an Aureon 7.1 USB (Terratec)
-sound card through an optical connection.
+Auditory stimulation was implemented using custom in-ear (AD), or over-the-ear
+headphones (AV), which reduced the scanner noise by
+at least \unit[20–30]{dB}.
 
@@
 
-\todo[inline]{shorten this subsection a lot}
-
-% AD
-In the AD study, a whole-body \unit[7]{Tesla} Siemens MAGNETOM magnetic
-resonance scanner equipped with a local circularly polarized head transmit and a
-32 channel brain receive coil (Nova Medical, Inc., Wilmington, MA, USA) acquired
-T2*-weighted echo-planar images (gradient-echo, \unit[2]{s} repetition time
-(TR), \unit[22]{ms} echo time, \unit[0.78]{ms} echo spacing, \unit[1488]{Hz/Px}
-bandwidth, generalized autocalibrating partially parallel acquisition,
-acceleration factor 3, \unit[2]{Hz/Px} bandwidth in phase encoding direction).
-% slices
-36 axial slices (thickness \unit[1.4]{mm}, \unit[1.4 $\times$ 1.4]{mm} in-plane
-resolution, \unit[224]{mm} field-of-view, anterior-to-posterior phase encoding
-direction) with a \unit[10]{\%} inter-slice gap were recorded in ascending
-order.
+Gradient-echo fMRI data for the AD study were acquired using a \unit[7]{Tesla}
+Siemens MAGNETOM magnetic resonance scanner equipped with a 32 channel brain
+receive coil at \unit[2]{s} repetition time (TR) with 36 axial slices (thickness
+\unit[1.4]{mm}, \unit[1.4 $\times$ 1.4]{mm} in-plane resolution, \unit[224]{mm}
+field-of-view, anterior-to-posterior phase encoding direction) and a
+\unit[10]{\%} inter-slice gap, recorded in ascending order.
 % slice orientation
@@
 % motion correction
-EPI images were online-corrected for motion and geometric distortions [+++Oh, S.
-et al. 2012; In, M. \& Speck, O., 2012; Chung, J. et al., 2011+++]
-% auxiliary scans
-Auxiliary scans for slice alignment and motion- and distortion-correction were
-performed at the beginning of the first fMRI recording session and also after
-the break at the start of the recording for the second half of the movie.
+EPI images were online-corrected for motion and geometric distortions.
+
 % AV & VIS
-In the AV and VIS study, a whole-body \unit[3]{Tesla} Philips Achieva dStream
-MRI scanner equipped with a 32 channel head coil acquired T2*-weighted
-echo-planar images (gradient-echo, \unit[2]{s} repetition time, \unit[30]{ms}
-echo time, \unit[90]{$^{\circ}$} flip angle, \unit[1943]{Hz/Px} bandwidth,
-parallel acquisition with sensitivity encoding (SENSE) reduction factor 2).
+In the AV and VIS study, a \unit[3]{Tesla} Philips Achieva dStream
+MRI scanner with a 32 channel head coil acquired gradient-echo fMRI data
+at \unit[2]{s} repetition time with
 % slices
@@
 resolution, \unit[240]{mm} field-of-view) and an anterior-to-posterior phase
-encoding direction were recorded in ascending order.
-% slice positioning
-Philips' ``SmartExam'' was used to automatically position slices in AC-PC
-orientation such that the topmost slice was located at the superior edge of the
-brain. This automatic slice positioning procedure was identical in the AV and
-VIS study, and yielded a congruent geometry across paradigms.
+encoding direction, recorded in ascending order.
 % no. of volumes
 A total of 3599 volumes were recorded for each participant in each of the
-naturalistic stimulus paradigms (451, 441, 438, 488, 462, 439, 542, and 338
-volumes for segment 1–8).
+naturalistic stimulus paradigms (AD and AV).
 

### 2020-12-15 paper/main.tex
Revise and correct preprocessing description

@@
 
-\todo[inline]{part regarding motion correction/co-registration might be
-incorrect}
-
-\todo[inline]{what is missing: As I see it, AD must have been downsampled to
-2.5x2.5x2.5 mm and AV must have been upsampled from 3.0 to 2.5mm??}
-
 % data sources
@@
 % https://github.com/psychoinformatics-de/studyforrest-data-templatetransforms}
-fMRI time series of those 15 participants in the studyforrest dataset that took
-part in all three experiments were obtained from
-\href{https://github.com/psychoinformatics-de/studyforrest-data-aligned}{GitHub}.
-Data were already corrected for motion and aligned by non-linear warping to a
-participant-specific BOLD template image \citep{sengupta2016extension}.
+All analyses presented here are based on previously published fMRI data
+(\url{https://github.com/psychoinformatics-de/studyforrest-data-aligned}).
+Of those 15 participants in the studyforrest dataset that took
+part in all three experiments,
 % exclusion of VP 10
-Data of one participant were dropped to due to invalid distortion correction
+data of one participant were dropped to due to invalid distortion correction
 during scanning of the AD stimulus.
+Data were previously corrected for motion, aligned with and re-sliced onto a
+participant-specific BOLD template image \citep{sengupta2016extension}
+(uniform spatial resolution of \unit[2.5$\times$2.5$\times$2.5]{mm} for both
+AD and AV data).
 % preprocessing intro
-All further analysis steps of the current study were carried out using tools of
+All analyses presented here were carried out using
 FSL v5.0.9 (\href{https://www.fmrib.ox.ac.uk/fsl}{FMRIB's Software Library};
@@
 % my preprocessing
-Preprocessing was carried out using FEAT v6.00 (FMRI Expert Analysis Tool;
-\citep{woolrich2001autocorr}) as part of FSL.
+Preprocessing was performed by FEAT v6.00 (FMRI Expert Analysis Tool;
+\citep{woolrich2001autocorr}) as shipped with FSL.
 % temporal filtering

### 2020-12-15 paper/main.tex
Thoughts on the methods

@@
 \subsection{Statistical analysis}
+
+Thoughts on the general structure here: what it is (just based on headlines):
+
+\begin{itemize}
+  \item Detail on statistical model
+  \item Detail on how annotation was done for AD
+  \item Detail on how regressors were built for AD
+  \item Detail on how annotation was done for AV
+  \item Detail on how regressors were built for AV
+  \item Detail on how regressors correlate
+  \item How contrasts were built
+\end{itemize}
+
+\noindent what it could be:
+
+Remind what the key question/story is (and what is it, actually?)
+
+At the moment is think it is:
+
+\begin{itemize}
+  \item the PPA is not just a visual area
+  \item it's presumed function can be mapped onto a natural stimulus (not just with an orthogonal task, but without any task)
+  \item visual information is not necessary to observe differential activation congruent with PPA function in the PPA
+\end{itemize}
+
+a suitable method structure (for these aspects, and probably right after the stimulus description) could be:
+\begin{itemize}
+  \item What is the key strategy to address this question?
+(conduct "semantically analog" analyses on all three datasets, this could largely go to the end of the intro).
+Which specific cognitive processing to we contrast in AD vs AV
+  \item Which ingredients to we need to make this happen? (take existing annotations, and define congruent contrasts based
+    on regressors that are built from the respective annotations, available annotations could be described in a dedicated section in the methods)
+  \item What do we need to check in order to ensure that subsequent analyses are valid? (is the necessary information in the natural stimuli uncorrelated enough? negative controls)
+\end{itemize}
 

### 2020-12-15 paper/main.tex
More thoughts

@@
 \title{Hemodynamic responses of the anterior "parahippocampal place area" (PPA) to a Hollywood movie's audio-description}
+%\title{Stimulus and paradigm selection impacts localization of "parahippocampal place area" (PPA)}
 
@@
 Lastly, our results provides further evidence that the PPA can be divided into
-functional subregions.\end{abstract}
+functional subregions.
+
+Key finding: We observe brain activation congruent with presumed PPA function
+in the (anterior) location of the PPA, based on high-level semantic information
+in an auditory stimulus.
+
+\end{abstract}
 
@@
 \end{itemize}
+
+Question:
+- how valid is localization of proposed PPA function given standard localizers?
+- why three datasets?
+  - VIS: connection to the literature; problem: stimulus validity re PPA function
+  - AV: more valid stimulus (given real-world); problem operationalize PPA function (there is *one* way to do it)
+  - AD: alternative stimulus for propsed function; similar but different operationalization problem
 

### 2020-12-16 paper/main.tex
rewrite abstract; plan for structure

--- 2020-12-15 paper/main.tex
@@
 
-% title has to be < 110 chars incl. spaces
-%  at the moment 109 Chars
-\title{Hemodynamic responses of the anterior "parahippocampal place area" (PPA) to a Hollywood movie's audio-description}
+% title has to be < 110 chars incl. spaces at the moment 109 Chars
+\title{A matter of operationalization: Paradigm and stimulus [feature] selection
+impacts localization of "parahippocampal place area"}
 
@@
 landscapes compared to pictures of faces or objects.
-% What we do
-In the current study, we exploratorily tested if spatial information embedded in
-a Hollywood movie and its audio-description of (i.e. the movie's soundtrack with
-an additional narrator) correlates with increased hemodynamic activity in the
-PPA.
-%
-We use publicly available functional magnetic resonance imaging data
-(studyforrest.org) of 14 subjects to build canonical general linear model (GLM)
-$t$-contrasts and compare current results to results that we gained from a
-dedicated visual localizer experiment conducted with same participants.
-% compare to visual localizer experiment group results
-On a group average level, results of our whole brain analyses show significantly
-increased activation restricted to the anterior part of the PPA that was defined
-using the visual localizer [as well as in the retrosplenial and lateral
-occipital cortex] of both hemispheres.
-% individual results
-On an individual level, results show significant bilateral clusters in the
-anterior PPA of nine subjects and significant unilateral clusters in two
-subjects.
+% AV, AD: operationalization
+In this study, we explore different ways to operationalize spatial perception in
+14 subjects that were watching an audio-visual Hollywood movie and listened to
+the audio-description of the same movie (studyforrest.org).
+% auditory localizer?
+Focussing on the audio-description, we further test if an auditory narrative
+could substitute localize a ``visual area'' in individual subjects.
+% GLM
+For each naturalistic stimulus, we model hemodynamic activity via several
+general linear model (GLM) $t$-contrasts that are based on stimulus annotations
+/ selected stimulus features.
+% VIS
+Current results are compared to results of classic visual localizer experiment
+that we conducted previously to localize the PPA in the same participants
+\citep{sengupata2016extension}.
+% results: group AV
+On a group level, results of our current approach to operationalize the
+perception of space during a movie reveal significantly increased hemodynamic
+activity spatially overlapping with the PPA but also extending into early visual
+cortices.
+% results: group AD
+Results of the audio-description reveal significant activation restricted to the
+anterior part of the PPA.
+% results: individual AD
+On an individual level, results of the audio-description show significant
+bilateral clusters in the anterior PPA of nine subjects and significant
+unilateral clusters in two subjects.
 % conclusion: generalizability
 Results suggest that increased activation in the PPA during the perception of
-static pictures generalizes to the perception of auditorily presented spatial
-information.
+static pictures generalizes to the perception of spatial information embedded in
+an audio-visual movie and an exclusively auditory stimulus.
 % conclusion: PPA has subregions
-Lastly, our results provides further evidence that the PPA can be divided into
-functional subregions.\end{abstract}
+Our results provides further evidence that the PPA can be divided into
+functional subregions.
+% localizer substitute
+An auditory narrative might substitute a visual paradigm to localize the PPAs
+anterior part in visually impaired subjects.\todo{very bold claim to be written
+in the abstract}
+
+\end{abstract}
+\todo[inline]{RSC \& LOC are not mentioned in the abstract (anymore)}
 
@@
 commands)}
+
+\section*{Keywords}
+% maximal 8
+fMRI, naturalistic stimulus, spatial perception, vision, language, speech,
+narrative, studyforrest
+
+\pagebreak[4]
+
+\section*{Plan}
+
+\noindent Abstract:
+
+\begin{itemize}
+\item missing: the exact (!) presumed PPA function? spatial perception, scene
+    representation, spatial layout hypothesis, associative processing? the list
+    is endless when it comes what the PPA processes exactly (in pictures)
+\item operationalization in two naturalistic stimuli (ecological validity not
+    mentioned anymore)
+\item AV: ?
+\item AD: also as functional localizers
+\item Results: ``spatial perception'' can differently operationalized via
+    naturalistic stimuli -> we get similar results; AD is restricted to
+    anterior PPA; narrative as ``visual localizer''(??)
+\end{itemize}
+
+\noindent Intro:
+
+\begin{itemize}
+\item presumed function of the PPA? -> spatial layout hypothesis and,
+    unfortunately, others
+\item question: is localization of proposed PPA function using visual localizer
+    valid?
+\item why do we use three datasets? To answer question (of presumed function of
+    PPA?) that is usually operationalized using pictures (but: big controversy
+what exactly in pictures the PPA processes; Aminoff tries to unify the
+    arguments)
+\item VIS: connection to literature; problem: stimulus validity re PPA function
+\item AV: more ecologically valid; problem: of operationalization; why did we do
+    it the done way (-> probably issue of method section)
+\item AD: alternative stimulus for proposed function but verbal/semantic
+    information
+\end{itemize}
+
+\noindent Method (after stimulus description):
+
+\begin{itemize}
+\item key strategy to address this question
+\item which specific cognitive processing do we contrast in AD vs. AV?
+\item ``ingredients'' to make it happen? we have some annotations at hand;
+    define congruent contrasts based on regressors that are built from
+    annotations; available annotations could be described in a dedicated
+    section (COH: should be shorty and very high-level; details probably will
+    confuse the shit out of readers)
+\item what do we need to check to ensure subsequent analyses are valid (COH:
+    this is the part that is the most elusive to me when it comes to precise
+    phrasing)? a) correlation of regressors, b) negative controls
+\end{itemize}
+
+\pagebreak[4]
 

### 2021-01-07 paper/main.tex
Title improvement(?)
Should have little impact on the manuscript itself
rewrite intro

@@
 
-% title has to be < 110 chars incl. spaces at the moment 109 Chars
-\title{A matter of operationalization: Paradigm and stimulus [feature] selection
-impacts localization of "parahippocampal place area"}
+% title has to be < 110 chars incl. spaces at the moment 106 Chars
+\title{Processing of visual and non-visual naturalistic spatial information in
+  the "parahippocampal place area"}
 
@@
 14 subjects that were watching an audio-visual Hollywood movie and listened to
-the audio-description of the same movie (studyforrest.org).
+the movie's audio-description (studyforrest.org).
 % auditory localizer?
 Focussing on the audio-description, we further test if an auditory narrative
-could substitute localize a ``visual area'' in individual subjects.
+could localize a ``visual area'' in individual subjects.
 % GLM
@@
 
-\noindent Abstract:
+\noindent Intro:
 
 \begin{itemize}
-\item missing: the exact (!) presumed PPA function? spatial perception, scene
-    representation, spatial layout hypothesis, associative processing? the list
-    is endless when it comes what the PPA processes exactly (in pictures)
-\item operationalization in two naturalistic stimuli (ecological validity not
-    mentioned anymore)
-\item AV: ?
-\item AD: also as functional localizers
-\item Results: ``spatial perception'' can differently operationalized via
-    naturalistic stimuli -> we get similar results; AD is restricted to
-    anterior PPA; narrative as ``visual localizer''(??)
-\end{itemize}
-
-\noindent Intro:
-
-\begin{itemize}
-\item presumed function of the PPA? -> spatial layout hypothesis and,
-    unfortunately, others
-\item question: is localization of proposed PPA function using visual localizer
-    valid?
-\item why do we use three datasets? To answer question (of presumed function of
-    PPA?) that is usually operationalized using pictures (but: big controversy
-what exactly in pictures the PPA processes; Aminoff tries to unify the
-    arguments)
-\item VIS: connection to literature; problem: stimulus validity re PPA function
-\item AV: more ecologically valid; problem: of operationalization; why did we do
-    it the done way (-> probably issue of method section)
-\item AD: alternative stimulus for proposed function but verbal/semantic
-    information
+\item Struktur des letzten Absatzes finde ich
+    bisher nicht so geil (Hypothesen kommen recht spät (d.h. nach Methode),
+    Results folgen direkt darauf
 \end{itemize}
@@
 \item key strategy to address this question
+\item auch VIS hat mehrere Kontraste
+\item neuer Abschnitt 2.6: all regressoren und Kontraste; Kontraste sind abiträr
+    aber ist ok; 2.7: eigentliche Statistische Analyse
 \item which specific cognitive processing do we contrast in AD vs. AV?
@@
     phrasing)? a) correlation of regressors, b) negative controls
+\end{itemize}
+
+\noindent Results
+
+\begin{itemize}
+\item mehrere Kontraste in VIS genommen, hier einer berichtet: Teil aus
+    Discussion in Results hochnehmen
+\end{itemize}
+
+\noindent Discussion
+\begin{itemize}
+    \item \citep{bartels2004mapping, hasson2004intersubject}
+    \item VIS: "best contrast was chosen"
 \end{itemize}
@@
 
-% Open research question
-In this study, we investigate if increased hemodynamic activity in the PPA
-correlates with ``spatial information'' presented under more ecologically valid
-conditions.
-% we are different We used two naturalistic
-Therefore, we annotated perceptual information embedded in two [perceptual]
-rich/multidimensional and continuous naturalistic stimuli (see
+% open question
+In this study, we investigate if increased hemodynamic activity in the PPA that
+is usually revealed by contrasting blocks of pictures can also be revealed by
+contrasting selected stimulus features that incidentially occur under more
+ecologically conditions.
+% we use 2 naturalistic stimuli
+To answer this question, we operationalized the perception of both visual and
+auditory spatial information using two naturalistic stimuli (see
 \citep{hamilton2018revolution, hasson2008neurocinematics,
-sonkusare2019naturalistic} for reviews):
-% audio-description
-a) the audio-description (AD) of the Hollywood movie ``Forrest Gump'',
-and
-% audio-visual
-b) the original audio-visual (AV) movie.
-% studyforrest dataset
-We then analyzed corresponding fMRI data from the same subjects that listened
-to the audio-description and watched the audio-visual movie as part of the
-publicly available studyforrest dataset
-(\href{http://www.studyforrest.org}{studyforrest.org}).
-% first: group level AD
-First on a group average level, general linear model (GLM) contrasts based on
-the audio-description's annotation are used to test if spatial information
-embedded in an exclusively auditory stimulus correlates with increased
-hemodynamic activity in the PPA that we defined using a block-designed visual
-localizer experiment done with the same subjects \citep{sengupta2016extension}.
-% second: group level AV
-Second as conceptual/cross-modal control, we compare results of the
-audio-description to GLM results based on the annotation of the movie.
-% individual results
-Lastly on the level of individual subjects and focussing on the
-audio-description [as a possible substitute for a visual localizer], we compare
-results of the naturalistic stimuli to results of the visual localizer
+sonkusare2019naturalistic} for reviews).
+% AV stimulus
+The operationalization of visual perception is based on an annotation of cuts
+and depicted locations in the audio-visual movie ``Forrest Gump'' (AV stimulus).
+% AO stimulus
+The operationalization of auditory perception is based on an annotation of
+speech occurring in the movie's audio-description (AD stimulus).
+% GLM contrasts
+Based on these annotations, we created several general linear model (GLM)
+contrast to analyze the corresponding publicly available fMRI datasets
+(\href{http://www.studyforrest.org}{studyforrest.org}) of each naturalistic
+stimulus \citep{hanke2016simultaneous, hanke2014audiomovie}.
+% varying amount of data
+Contrasts vary in HOW WELL / HOW MUCH DATA.\todo{rewrite if it should be
+mentioned}
+
+% hypo a
+We hypothesize[d] that whole-brain analyses will/would reveal increased
+hemodynamic activity in the PPA as functionally defined by a visual localizer
+experiment using static pictures done with the same subjects
 \citep{sengupta2016extension}.
-% results
-\todo[inline]{following paragraph will be similar to abstract, intro to
-discussion and conclusion} Our results demonstrate that (a), (b), (c).
+% hypo b
+Focussing on the [``cleaner operationalization'' of the] audio-description, we
+further hypothesize[d] that an exclusively auditory stimulus can/could
+substitute a block-design experiment using pictures to localize a ``visual
+area'' in individual subjects.
+% results: group
+On a group average level,
+% operationalization in naturalistic stimuli
+results demonstrate that our approach based on annotations [of two ecologically
+more valid stimuli] to operationalize spatial perception lead to increased
+hemodynamic activity in [roughly] the same brain regions as a block-designed
+visual localizer experiment.\todo{interpretation?}
+% anterior vs. posterior
+On both a group and individual subject level, a comparison of results from the
+three datasets also suggests functional differences between the anterior and
+posterior PPA.
+% what does it mean
+The current data add evidence to the hypothesis that the PPA might consist of
+submodules that work together during visual perception of landscapes (cf.
+\citep{baldassano2013differential}).
+%
+Lasty, our results suggest that the PPA's anterior part can be localized in
+individual subjects by contrasting high-level semantic information occurring in
+an auditory naturalistic stimulus.
+
+\todo[inline]{the topic anteriorer vs. posterior is mentioned first at the very
+and of the intro and occurrs as "surprising" in the intro as in our results
+(it's mentioned in the abstract though)}
 
@@
 \todo[inline]{Discussion: discuss that contrasts make ``less and less'' sense}
+
+\todo[inline]{figure caption: mention / explain other clusters}
 

### 2021-01-12 paper/main.tex
revise Intro and Method

@@
 paradigm}
-
-\todo[inline]{doing the
-    revision of the result section I realized that we probably should
-    ``somehow'' add that clusters should not be all over the place but spatially
-    constrained to the parahippocampal and neighbouring cortices, because
-    naturalistic stimulus / possibly confounding variables}
 
@@
 \begin{itemize}
-\item Struktur des letzten Absatzes finde ich
-    bisher nicht so geil (Hypothesen kommen recht spät (d.h. nach Methode),
-    Results folgen direkt darauf
+    \item structure of last paragraph might be meh: methods/our approach
+-> hypotheses -> results; readers might assume HARKing?
 \end{itemize}
 
-\noindent Method (after stimulus description):
+\noindent Method:
 
 \begin{itemize}
-\item key strategy to address this question
-\item auch VIS hat mehrere Kontraste
-\item neuer Abschnitt 2.6: all regressoren und Kontraste; Kontraste sind abiträr
-    aber ist ok; 2.7: eigentliche Statistische Analyse
-\item which specific cognitive processing do we contrast in AD vs. AV?
-\item ``ingredients'' to make it happen? we have some annotations at hand;
-    define congruent contrasts based on regressors that are built from
-    annotations; available annotations could be described in a dedicated
-    section (COH: should be shorty and very high-level; details probably will
-    confuse the shit out of readers)
-\item what do we need to check to ensure subsequent analyses are valid (COH:
-    this is the part that is the most elusive to me when it comes to precise
-    phrasing)? a) correlation of regressors, b) negative controls
+
+\item at the moment "Annotation, Regressors and Contrasts" follows
+    "Preprocessing" (right before "Statistical Analysis" as we agreed on); going
+        back and forth a couple of times, imo there is no perfect location (at
+        least in case we do not split that part into "Annotation" and
+        "Regressors \& Contrasts" again.
+
+\item structure of ``Annotation, Regressors \& Contrasts'' !! -> everything has
+    pros and cons (at the moment lots of subheading since easier to navigate);
+    at the moment I think (again) it makes more sense to mention AD first since
+    it is the focus of the movie and the AV serves as, well, what exactly?
+
+\item what do we need to check to ensure subsequent analyses are valid;
+    a) correlation of regressors (first "sanity check" but more a prerequisite)
+    b) negative controls (actual sanity check)
+
 \end{itemize}
@@
 hemodynamic activity in the PPA differs between different semantic stimulus
-categories occurring in spoken language.
-\todo{phrasing might be strange but aims to delineate
-from Huth (2016); they do voxel-wise semantic modeling regarding places in PPA
-but imo that does not say anything about excitation/inhibition}
+categories occurring in spoken language.\todo{phrasing to delineate from Huth
+(2016); imo voxel-wise semantic modeling says nothing about
+excitation/inhibition}
 % Aziz' stimuli
@@
 is usually revealed by contrasting blocks of pictures can also be revealed by
-contrasting selected stimulus features that incidentially occur under more
+contrasting selected stimulus features that incidentally occur under more
 ecologically conditions.
@@
 We hypothesize[d] that whole-brain analyses will/would reveal increased
-hemodynamic activity in the PPA as functionally defined by a visual localizer
-experiment using static pictures done with the same subjects
-\citep{sengupta2016extension}.
+hemodynamic activity spatially constrained \todo{i.e. not activity all over the
+place} to the PPA as functionally defined by a visual localizer experiment using
+pictures done with the same subjects.  \citep{sengupta2016extension}.
 % hypo b
@@
 more valid stimuli] to operationalize spatial perception lead to increased
-hemodynamic activity in [roughly] the same brain regions as a block-designed
-visual localizer experiment.\todo{interpretation?}
+hemodynamic activity in [roughly] the same brain regions the block-designed
+visual localizer.\todo{interpretation?}
 % anterior vs. posterior
@@
 %
-Lasty, our results suggest that the PPA's anterior part can be localized in
+Lastly, our results suggest that the PPA's anterior part can be localized in
 individual subjects by contrasting high-level semantic information occurring in
@@
 
-\todo[inline]{the topic anteriorer vs. posterior is mentioned first at the very
-and of the intro and occurrs as "surprising" in the intro as in our results
-(it's mentioned in the abstract though)}
+\todo[inline]{the topic anterior vs. posterior is mentioned at the end of the
+intro for the first time; might be "surprising" but that is in line how the
+story went (it's mentioned in the abstract though)}
 
@@
 We used three components of the publicly available
-\href{http://www.studyforrest.org}{studyforrest.org} dataset that has already been
-used by other research groups in independent studies
-(e.g. \citep{ben2018hippocampal, jiahui2019predicting, hu2017decoding,
+\href{http://www.studyforrest.org}{studyforrest.org} dataset that has already
+been used by other research groups in independent studies (e.g.
+\citep{ben2018hippocampal, jiahui2019predicting, hu2017decoding,
 lettieri2019emotionotopy, nguyen2016integration}).
@@
 % AV
-b) watching the original movie (AV study;
-\citep{hanke2016simultaneous}), and
+b) watching the original movie (AV study; \citep{hanke2016simultaneous}), and
 % VIS
@@
 All stimuli of the VIS study were already used in a previous study
-\citep{haxby2011common}. There were 24 unique grayscale images (s. Figure 2 in
-\citep{sengupta2016extension}) ) for each of six stimulus categories:
+\citep{haxby2011common}.\todo{I guess they only report the ones they
+designed themselves in detail? -> check again}
+%
+There were 24 unique grayscale images (s. Figure 2 in
+\citep{sengupta2016extension}) for each of six stimulus categories:
 % category details
@@
 rear-projection screen
-% screen size
-at a viewing distance of \unit[63]{cm}, with a movie frame projection size of
-\unit[23.75 $\times$ 10.25]{cm}.\todo{replace with visual angle size, in line with VIS}
+% screen size \unit[23.75 $\times$ 10.25]{cm}
+at a viewing distance of \unit[63]{cm}, with a movie frame projection size
+approximately \unit[21.3]$^{\circ}$ $\times$ \unit[9.3]$^{\circ}$.
 % angle of view: VIS
@@
 \unit[10]$^{\circ}$ $\times$ \unit[10]$^{\circ}$ of visual angle.
-
 % AD & AV: auditory stimulation
@@
 
-\subsection{Statistical analysis}
-
-% intro
-Similarly to the reviewed studies that employed simplified stimuli, we conducted
-a standard two-level general linear model (GLM) analysis to create
-subject-specific results ($Z$-maps) across the 8 segments for every subject. A
-subsequent, third-level analysis averaged contrast estimates over subjects.
-
-\subsubsection{Stimulus annotation and regressors}
+\subsection{Annotation, regressors, contrasts}
+
+\todo[inline]{SE: wie gut passen die Annotationen zu den VIS Stimuli -> genauere
+Ausführungen, wie welche Annotation dazu passt; COH: revised but maybe still not
+``optimal''}
 
@@
 
-\todo[inline]{SE: wie gut passen die Annotationen zu den VIS Stimuli -> genauere
-Ausführungen, wie welche Annotation dazu passt; COH: revised but maybe still not
-``optimal''}
-
-% intro
-Since we did not design the naturalistic stimuli for detection power, we
-annotated the temporal structure of the fixed stimuls material to operationalize
-the perception of different stimulus features and create regressors for the
-following GLM analysis.
-
-\paragraph{audio-description: annotation}
+\todo[inline]{key strategy to address research question -> operationalize
+    perception of spatial information in naturalistic stimuli that are
+ecologically more valid}
+
+% traditionally
+Traditionally, researchers specifically design stimuli that presumably would
+trigger the perceptual process of interest while also controlling confounding
+variables (e.g. color, luminance).
+% our approach: annotation and regressors
+Naturalistic stimuli [might] more closely mimic how we experience the world
+around us but have the drawback that they are usually fix and that their
+temporal structure of embedded stimulus features is unknown.\todo{phrasing}
+% annotation ftw
+Hence, we annotated a variety of stimulus features that later served as a basis
+for GLM regressors.
+% contrasts
+Based on these regressors, we then created $t$-contrasts that we presumed to
+subtract variance correlating with the perception of non-spatial information
+from variance correlating with the perception of spatial information.
+
+\subsubsection{Annotations \& regressors}
+
+\paragraph{Audio-description: annotation}
 
 % AD annotation
-For the analysis of the AD stumulus, we extended a publicly available annotation
+For the analysis of the AD stimulus, we extended a publicly available annotation
 of speech \citep{haeusler2020speechanno} by further annotating words spoken by
@@
 category, and examples can be seen in Table \ref{tab:descr-nouns-rules}.
-% procedure
+% preliminary annotation
 A preliminary annotation was performed by one person according to the rules.
+% corrections
 Minor corrections due to incorrectly applied rules were done by the author.
@@
 % pooling of categories
-To create the regressor for the GLM of the AD stimulus, some of
-the original 18 categories that were similar but offered only a small amount of
-counts were pooled resulting in eleven new categories [that served as
-experimental conditionso] (see Table \ref{tab:ao-events}).
+To create the regressor for the GLM of the AD stimulus, some of the original 18
+categories that were similar but offered only a small amount of counts were
+pooled resulting in eleven new categories [that served as experimental
+conditionso] (see Table \ref{tab:ao-events}).
 % handling of se_new and se_old
@@
 % AV anno
-For the analysis of the AV data, we took advantage of a publicly available
-annotation of movie cuts and depicted locations \citep{haeusler2016cutanno}.
+For the analysis of the AV stimulus, we took advantage of a previously published
+annotation of [the 869] movie cuts and the depicted location after each cut
+\citep{haeusler2016cutanno}.
+
+\paragraph{movie: regressors}
+
 % rationale behind using movie cuts
 Our rationale was that cuts are ``spatially relevant'' events that re-orient the
-viewer within the environment depicted in the movie.
-
-\paragraph{movie: regressors}
-
-% AV events
-For the analysis of the AV stimulus, we used a previously published annotation
-[of the 869] movie cuts and depicted locations \citep{haeusler2016cutanno} to
-created regressors based on the kind of location that is depicted in the movie
-frame after a cut.
+viewer within the environment of the movie by either by changing the perspective
+within a setting or switching to another setting.
 
@@
 % AV regressors/events
-Each location was put into one of the following five categories (see Table
+Each cut was put into one of the following five categories (see Table
 \ref{tab:av-events}):
@@
 %
-4) a cut to another camera position within a setting or locale that was depicted
-for the first time (\texttt{vpe\_new}), and
+4) a cut to another camera position within a setting or locale (e.g. room) that
+was depicted for the first time (\texttt{vpe\_new}), and
 %
@@
 
-% irrespectible of visual content
+% irrespective of visual content
 Notably, categorization was performed irrespectively of a movie frame's precise
@@
 The neuroscientific rationale was that activity in the PPA is greater when
-participants view novel versus repeated scenes or view-points.
+participants view novel versus repeated scenes or view-points
 \citep{epstein1999parahippocampal, grill2006repetition}.
@@
 
-\paragraph{regressor correlations}
-
-% reference to figure ``correlation of regressors''
-We computed the Pearson coefficients of the regressors across the eight segments
-of both naturalistic stimuli. Results demonstrate no to minor correlations (s.
-Figure \ref{fig:reg-corr}) which suggest the models should not suffer from low
-detection power due to shared variance among regressors.
-%
-\todo[inline]{discussion of the regressors correlation at the very beginning of
-discussion could be pasted here; will save space there but will mix methods/
-results/ discussion here}
-
 % temporal derivatives
@@
 \unit[150]{s}) as the BOLD time series.
+
+\paragraph{regressor correlations}
+
+% stimuli not designed for research purposes
+The audio-description and the movie were not designed to be used in a BOLD fMRI
+experiment but to entertain their audiences.
+% fixed time course; detection power
+Since we annotated events in fixed time courses that could not experimentally
+manipulated, regressors that are based on these events could be correlated
+leading to shared variance and thus low detection power of subsequent analyses.
+% correlations within stimuli and across stimuli
+Hence, we first tested for correlation of regressors across the eight segments
+of each stimulus and correlations of regressors across both stimuli (s. Figure
+\ref{fig:reg-corr})
+% correlations within each stimulus
+The computed Pearson correlation coefficients demonstrate no to minor
+correlations of regressors of the same stimulus [which suggest the models should
+not suffer from low detection power due to shared variance among regressors].
+% correlations across stimuli
+The highest correlations are apparent between auditory low-level confounds
+across stimuli. This was expected and served as ``sanity check'' since the
+audio-track of the audio-description is the audio-track of the movie but
+featuring the additional narrator (s. Figure \ref{fig:reg-corr}).
+% encouraged by that we build contrasts (statement)
+As a result, we felt encouraged to create voxel-wise GLM $t$-contrasts similarly
+to previous studies that used controlled stimuli.
 
@@
 
-\todo[inline]{SE: Das mit den 8 kontrasten und 5 kontrasten habe ich nicht
-intuitiv durchblickt. Was wurde da gegen was kontrastiert? COH: revised but
-maybe still not optimal}
-
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% "ingredients" to answer our questions (cf. intro); we have annotations; define
+% congruent contrasts based on regressors based on annotations
+
+% repeat key question (cf. end of intro)
+The key question of the current study was if a) we could operationalize the
+perceptual processes in an audio-visual and exclusively auditory
+naturalistic stimulus and if b) contrasting that fcompared to an
+operationalization of non-spatial perception  would yield to increased
+hemodynamic activity in the PPA as defined by a visual localizer experiment.
+% difference (kinda repetition)
+Instead of carefully selecting and designing conceptualized/simplified stimuli
+that we assumed to match the proposed perceptual processes, we selected and
+categorized stimulus features (movie cuts and spoken nouns) that are embedded in
+two naturalistic stimuli.
 % intro
-To test the robustness our approach, we operationalized the perception of
-spatial information compared to the perception of ``non-spatial'' information
-differently in eight $t$-contrasts for the AD stimulus (see Table
+To test the robustness of our approach, we operationalized the
+perception of spatial information compared to the perception of ``non-spatial''
+information differently in eight $t$-contrasts for the AD stimulus (see Table
 \ref{tab:ao-contrasts}) and five $t$-contrasts for the AV stimulus (see Table
@@
 the results are?} since the event categories differed a) in how well the
-averaged events reflected spatial information, and b) in event counts.
+averaged events reflected spatial information, and b) in available data (i.e.
+event counts).\todo{make ref to what is no "Audio-description: annotation"}
 % thus: primary contrasts
-We chose one ``primary contrast'' for every stimulus before running the
-analyses.
+For each stimulus, we chose one contrast to be ``primary contrast'' for further
+inspection and a detailed report.
 % selection criteria for primary contrast.
@@
 to match the preferred stimulus type, and b) the amount of available data /
-events.\todo{oh, lord!}
+events.
 
@@
 In the primary contrast of the AD stimulus, we contrasted landmarks
-\texttt{geo}, and rooms and geometry-defining objects \texttt{geo-room} with all non-geometry related categories (\texttt{body},
-\texttt{bodypart}, \texttt{fahead}, \texttt{object}, \texttt{sex\_f},
-\texttt{sex\_m}) except \texttt{furniture}.
+\texttt{geo}, and rooms and geometry-defining objects \texttt{geo-room} with all
+non-geometry related categories (\texttt{body}, \texttt{bodypart},
+\texttt{fahead}, \texttt{object}, \texttt{sex\_f}, \texttt{sex\_m}) except
+\texttt{furniture}.
 % why se_new & se_old were not used in the primary contrasts
@@
 events that trigger perception of space versus objects or faces.\todo{syntax?}
+
+\todo[inline]{one could write more about the different contrast in Segupta et
+al. here, but imo it's sufficient to point that out in the results given that
+all subjects except two used the strict set given contrasts of VIS study and
+that the ``best working'' will be used}
+
+\todo[inline]{Nevertheless, state it in one sentence and check Berman, M. G. et al. Evaluating functional localizers: The case of the FFA. NeuroImage 50, 56–71 (2010)}
+
+Similarly to \citep{sengupta2016extension} that chose the ``best'' of three
+alternative contrasts (strict, relaxed, or simple contrast), future studies that
+aim for individual diagnostics / ROI localization should also test more than one
+contrast to gain the ``best'' individual ROIs.\todo{``best'' sounds pretty
+shitty}
 
@@
 
+\subsection{Statistical analysis}
+
+% intro
+Similarly to the reviewed studies that employed simplified stimuli, we conducted
+a standard two-level general linear model (GLM) analysis to create
+subject-specific results ($Z$-maps) across the 8 segments for every subject. A
+subsequent, third-level analysis averaged contrast estimates over subjects.
+
 % alignments single subjects (for Bland-Altman-Plots) 1st level
@@
 \item RSC (and ventral precuneus): 7 contrasts (all bilateral)
-\item lateral occipiatal cortex: 6 contrasts (4 bilateral, 2 unilateral =
+\item lateral occipital cortex: 6 contrasts (4 bilateral, 2 unilateral =
     transverse occipital sulcus / occipiatal place area?; AD \& AV clusters
@@
 
-\paragraph{AV: other signficant clusters across contrasts}
+\paragraph{AV: other significant clusters across contrasts}
 
@@
 se\_old): right PPA, bilateral sup. lat. occ. cortex; LOC (l/r), right superior
-parietal lobe. Compate Figure \ref{fig:reg-corr}: nouns that cue change to a new
+parietal lobe. Compare Figure \ref{fig:reg-corr}: nouns that cue change to a new
 setting are correlated  with cuts to a new setting (vse\_new; r$\approx$0.3;
@@
 
-\subsection{correlation of regressors}
-
-\todo[inline]{Following paragraph could pasted into method section to save space
-here; a short interpretation is given there already; so methods/ results/
-discussion are not absolutely separated there already}
-% stimuli not designed for research purposes
-The audio-description and the movie were not designed to be used in a BOLD fMRI
-experiment but to entertain their audiences.
-%
-As a results, stimulus features that we annotated to create the regressors could
-have been correlated leading to shared variance that lowers detection power.
-% computing the correlations
-Hence, we first tested for correlation of regressors within and across both
-naturalistic stimuli (s. Figure \ref{fig:reg-corr})
-% results of computing feature correlation
-Results reveal no to minor correlations of regressors with regressors of the
-same stimulus.
-% encouraged by that we build contrasts (statement)
-Thus, we felt encouraged to create traditional/canonical voxel-wise GLMs that
-modeled and contrasted hemodynamic activity similarly to previous studies that
-used conceptualized stimuli.
-
 % The second through fourth paragraphs may deal with potential weaknesses
@@
 %
-Further, the incidential occurrence of modeled features prevents participants
+Further, the incidental occurrence of modeled features prevents participants
 from making assumptions about the investigated perceptual process by just being
@@
 % but
-Nevertheless, results are still influcended by [sensitive to] the amount of
+Nevertheless, results are still influenced by [sensitive to] the amount of
 available data and how well the feature space is modeled.
@@
 % group vs individual
-Results on an inidividual level reveal that significant cluster are located in
+Results on an individual level reveal that significant cluster are located in
 the anterior part of individual PPA ROIs. Thus, the pattern that was revealed on
@@
 \todo[inline]{discussion of individual differences? what do the results
-suggest? Differences in alterness, attention to spatial information,
+suggest? Differences in alertness, attention to spatial information,
 predisposition? ``capability'' to process auditory spatial information?}
@@
 landmarks ((\texttt{geo}; often buildings or other single aspects of a whole
-scene) and elements defining the geometry of a room or locale (\texttt{groom}) to non-spatial cues.
+scene) and elements defining the geometry of a room or locale (\texttt{groom})
+to non-spatial cues.
 % we did not choose se\_new and se\_old
@@
 of landscapes (e.g. ``in a football stadium'', ``Forrest is running through the
-jungle'') but mostly landmarks or buildings, and also non-spatial
-cues (e.g. ``Jenny as a teenager``).
+jungle'') but mostly landmarks or buildings, and also non-spatial cues (e.g.
+``Jenny as a teenager``).
 % further studies
@@
 \todo[inline]{AV: field size decreases later in the movie; this is a confound
-based on cinematography => the stimulus changes over time}
+based on cinematography => the stimulus changes over time; AV analysis exploits
+confound structure}
 
@@
 % focus of study
-The focus of the current study was to investigate if signficantly increased
+The focus of the current study was to investigate if significantly increased
 hemodynamic activity in the PPA correlates with spatial information (compared to

### 2021-01-12 paper/main.tex
comment
Light abstract editing

--- 2021-01-07 paper/main.tex
@@
 % AV, AD: operationalization
-In this study, we explore different ways to operationalize spatial perception in
+In this study, we explore different ways to operationalize spatial perception\todo{not sure if this is just perception} in
 14 subjects that were watching an audio-visual Hollywood movie and listened to
@@
 % auditory localizer?
-Focussing on the audio-description, we further test if an auditory narrative
+Focussing on the audio-description, we test if an auditory narrative
 could localize a ``visual area'' in individual subjects.
@@
 For each naturalistic stimulus, we model hemodynamic activity via several
-general linear model (GLM) $t$-contrasts that are based on stimulus annotations
-/ selected stimulus features.
+general linear model (GLM) $t$-contrasts that are based on annotations
+of selected stimulus features.
 % VIS
 Current results are compared to results of classic visual localizer experiment
-that we conducted previously to localize the PPA in the same participants
-\citep{sengupata2016extension}.
+that we conducted previously to localize the PPA in the same participants.
+% no refs in abstract (probably)
+%\citep{sengupata2016extension}.
 % results: group AV
-On a group level, results of our current approach to operationalize the
-perception of space during a movie reveal significantly increased hemodynamic
-activity spatially overlapping with the PPA but also extending into early visual
+On a group level, results for a visual movie stimulus show significantly increased hemodynamic
+activity spatially overlapping with a traditionally localized PPA but also extending into earlier visual
 cortices.
 % results: group AD
-Results of the audio-description reveal significant activation restricted to the
+Results for the audio-description stimulus reveal significant activation restricted to the
 anterior part of the PPA.

### 2021-01-12 paper/main.tex

--- 2021-01-12 paper/main.tex
@@
 
+\todo[inline]{I am currently stuck here}
 % repeat key question (cf. end of intro)

### 2021-01-12 paper/main.tex
Intro comment

@@
 substitute a block-design experiment using pictures to localize a ``visual
-area'' in individual subjects.
+area'' in individual subjects.\todo{needs short statement on why one would even want that}
 % results: group

### 2021-01-12 paper/main.tex
Method/Result structure comments

@@
 \subsection{Annotation, regressors, contrasts}
-
+\todo[inline]{why not strip contrasts from this section and call it "Event modeling"?}
 \todo[inline]{SE: wie gut passen die Annotationen zu den VIS Stimuli -> genauere
@@
 \subsubsection{Annotations \& regressors}
+\todo[inline]{maybe call this "annotation" and put 'Audio-description: annotation' and 'movie: annotation' in it together, and have a subsequent section "event models"}
 
@@
 \subsubsection{Contrasts}
-
+\todo[inline]{this should likely move into statistical analysis, and be resolved as an individual section}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 \section{Results}
+\todo[inline]{we have to decide how we want to present this: a) by stimulus or b) by analysis type. With the present abstract I am leaning towards (a), but we should debate that}
 

### 2021-01-12 paper/main.tex
restructure event modeling in methods v1

--- 2021-01-12 paper/main.tex
@@
 
-\subsection{Annotation, regressors, contrasts}
-
-\todo[inline]{SE: wie gut passen die Annotationen zu den VIS Stimuli -> genauere
-Ausführungen, wie welche Annotation dazu passt; COH: revised but maybe still not
-``optimal''}
+\subsection{Event modeling}
 
@@
 ``optimal''}
-
-\todo[inline]{key strategy to address research question -> operationalize
-    perception of spatial information in naturalistic stimuli that are
-ecologically more valid}
 
@@
 Hence, we annotated a variety of stimulus features that later served as a basis
-for GLM regressors.
-% contrasts
-Based on these regressors, we then created $t$-contrasts that we presumed to
-subtract variance correlating with the perception of non-spatial information
-from variance correlating with the perception of spatial information.
-
-\subsubsection{Annotations \& regressors}
-
-\paragraph{Audio-description: annotation}
+(for GLM regressors) to model hemodynamic responses.
+
+\subsubsection{Events (based on annotations)}
+
+\todo[inline]{mention low-level confound annotations here or (as it is now) in
+modeling}
+
+\paragraph{movie}
+% AV anno
+For the analysis of the AV stimulus, we took advantage of a previously published
+annotation of [the 869] movie cuts and the depicted location after each cut
+\citep{haeusler2016cutanno}.
+% rationale to use that annotation rationale behind using movie cuts
+Our rationale was that cuts are ``spatially relevant'' events that re-orient the
+viewer within the environment of the movie by either changing the perspective
+within a setting or switching to another setting.
+% AV regressors/events
+Each cut was put into one of the following five categories (see Table
+\ref{tab:av-events}):
+%
+1) a cut switching to a setting that was depicted for the first time
+(\texttt{vse\_new}),
+%
+2) a cut switching to a setting that was already depicted earlier in the movie
+(\texttt{vse\_old}; e.g. a cut to the recurring waiting bench at the bus stop),
+%
+3) a cut switching to another locale within a setting (\texttt{vlo\_ch}; e.g. a
+cut from first to the second floor in Forrest's house),
+%
+4) a cut to another camera position within a setting or locale (e.g. room) that
+was depicted for the first time (\texttt{vpe\_new}), and
+%
+5) a cut to another camera position within a setting or locale that was already
+depicted before (\texttt{vpe\_old}).
+
+% irrespective of visual content
+Notably, categorization was performed irrespectively of a movie frame's precise
+content and thus without controlling confounding variables (e.g. presence of
+faces).
+% AV COPEs: intro
+The rationale that this approach would still yield categories correlating with
+increased hemodynamic activity in the PPA was twofold.
+% cinematographic rationale cut to new scenes: establishing shots
+The cinematographic rationale was that movies tend to establish the setting
+(\texttt{vse\_new}) and the spatial relationships within a setting
+(\texttt{vpe\_new}) at the beginning of a movie.
+% cut to recurrent scene
+Later in the movie, the field sizes of movie shots tend to decrease when
+switching back to already established settings (\texttt{vse\_old}).
+% similarly for shots within a scene
+Moreover, shots within a recurring locale or setting tend to shift to depicting
+persons and objects (\texttt{vpe\_old}) more relevant to the evolved plot
+\citep{brown2012cinematography, mercado2011filmmakers}.
+% neuroscientific rationale
+The neuroscientific rationale was that activity in the PPA is greater when
+participants view novel versus repeated scenes or view-points
+\citep{epstein1999parahippocampal, grill2006repetition}.
+
+% AV regressors
+\begin{table*}[h!]
+    \caption{Overview of events to build the 14 regressors for the analysis of
+        the audio-visual (AV) stimulus.
+        \texttt{fg\_av\_ger\_pd} (perceptual differences of consecutive frames),
+        \texttt{fg\_av\_ger\_ml} (mean luminance of a frame),
+        \texttt{fg\_av\_ger\_lr} (difference in mean luminance of left and right
+        half),
+        \texttt{fg\_av\_ger\_ud} (difference in mean luminance of upper and
+        lower half),
+        \texttt{fg\_av\_ger\_lrdiff} (left-right volume difference), and
+        \texttt{fg\_av\_ger\_rms} (root mean square volume) represent one event
+        for every movie frame (\unit[40]{ms}).
+        For description of the two event categories of the audio-description's
+        narrator (\texttt{se\_new} and \texttt{se\_old}) to build contrast of
+        negative control see Table
+\ref{tab:ao-events}.}
+\label{tab:av-events}
+\footnotesize
+\begin{tabular}{lp{3.5cm}lllllllll} \toprule \textbf{label} & \textbf{description} & \textbf{all} & \textbf{1} & \textbf{2} & \textbf{3} & \textbf{4} & \textbf{5} & \textbf{6} & \textbf{7} & \textbf{8} \\
+\midrule
+vse\_new &  change of the camera position to a setting not depicted before & \aoVsenewAll & \aoVsenewI & \aoVsenewII & \aoVsenewIII & \aoVsenewIV & \aoVsenewV & \aoVsenewVI & \aoVsenewVII & \aoVsenewVIII
+\tabularnewline vse\_old & change of the camera position to a recurring setting & \aoVseoldAll & \aoVseoldI & \aoVseoldII & \aoVseoldIII & \aoVseoldIV & \aoVseoldV & \aoVseoldVI & \aoVseoldVII & \aoVseoldVIII
+\tabularnewline
+vlo\_ch & change of the camera position to another locale within the same setting & \aoVlochAll & \aoVlochI & \aoVlochII & \aoVlochIII & \aoVlochIV & 0 & \aoVlochV & \aoVlochVI & \aoVlochVII
+\tabularnewline
+vpe\_new & change of the camera position within a locale not depicted before & \aoVpenewAll & \aoVpenewI & \aoVpenewII & \aoVpenewIII & \aoVpenewIV & \aoVpenewV & \aoVpenewVI & \aoVpenewVII & \aoVpenewVIII
+\tabularnewline
+% vpe_old has no events in 3. So the indices are shifted
+vpe\_old & change of the camera position within a recurring locale &
+\aoVpeoldAll & \aoVpeoldI & \aoVpeoldII & 0 & \aoVpeoldIII & \aoVpeoldIV &
+\aoVpeoldV & \aoVpeoldVI & \aoVpeoldVII
+\tabularnewline
+vno\_cut & frames within a continuous movie shot & \avVnocutAll & \avVnocutI & \avVnocutII & 0 & \avVnocutIII & \avVnocutIV & \avVnocutV & \avVnocutVI & \avVnocutVII
+\tabularnewline
+se\_new & control for AD narrator & \aoSenewAll & \aoSenewI & \aoSenewII & \aoSenewIII & \aoSenewIV & \aoSenewV & \aoSenewVI & \aoSenewVII & \aoSenewVIII
+\tabularnewline
+se\_old & control for AD narrator & \aoSeoldAll & \aoSeoldI & \aoSeoldII & \aoSeoldIII & \aoSeoldIV & \aoSeoldV & \aoSeoldVI & \aoSeoldVII & \aoSeoldVIII
+\tabularnewline
+fg\_av\_ger\_lr & left-right luminance difference & \avFgavgerlrAll & \avFgavgerlrI & \avFgavgerlrII & \avFgavgerlrIII & \avFgavgerlrIV & \avFgavgerlrV & \avFgavgerlrVI & \avFgavgerlrVII & \avFgavgerlrVIII
+\tabularnewline
+fg\_av\_ger\_lrdiff & left-right volume difference & \avFgavgerlrdiffAll & \avFgavgerlrdiffI & \avFgavgerlrdiffII & \avFgavgerlrdiffIII & \avFgavgerlrdiffIV & \avFgavgerlrdiffV & \avFgavgerlrdiffVI & \avFgavgerlrdiffVII & \avFgavgerlrdiffVIII
+\tabularnewline
+fg\_av\_ger\_ml & mean luminance & \avFgavgermlAll & \avFgavgermlI & \avFgavgermlII & \avFgavgermlIII & \avFgavgermlIV & \avFgavgermlV & \avFgavgermlVI & \avFgavgermlVII & \avFgavgermlVIII
+\tabularnewline
+fg\_av\_ger\_pd & perceptual difference & \avFgavgerpdAll & \avFgavgerpdI & \avFgavgerpdII & \avFgavgerpdIII & \avFgavgerpdIV & \avFgavgerpdV & \avFgavgerpdVI & \avFgavgerpdVII & \avFgavgerpdVIII
+\tabularnewline
+fg\_av\_ger\_rms & root mean square (loudness) & \avFgavgerrmsAll & \avFgavgerrmsI & \avFgavgerrmsII & \avFgavgerrmsIII & \avFgavgerrmsIV & \avFgavgerrmsV & \avFgavgerrmsVI & \avFgavgerrmsVII & \avFgavgerrmsVIII
+\tabularnewline
+fg\_av\_ger\_ud & upper-lower luminance difference & \avFgavgerudAll & \avFgavgerudI & \avFgavgerudII & \avFgavgerudIII & \avFgavgerudIV & \avFgavgerudV & \avFgavgerudVI & \avFgavgerudVII & \avFgavgerudVIII
+\tabularnewline
+\end{tabular}
+\end{table*}
+
+\paragraph{Audio-description}
+
+\todo[inline]{SE: wie gut passen die Annotationen zu den VIS Stimuli -> genauere
+Ausführungen, wie welche Annotation dazu passt; COH: revised but maybe still not
+``optimal''}
 
@@
 % reference to table with rules and examples
-A complete overview of all 18 categories, the rule for a word to belong to a
-category, and examples can be seen in Table \ref{tab:descr-nouns-rules}.
+A complete overview of all 18 noun categories, the rule for a word to belong to
+a category, and examples can be seen in Table \ref{tab:descr-nouns-rules}.
 % preliminary annotation
@@
 %hierarchical categories
-Notably, the categories \texttt{setting\_new} and \texttt{setting\_rec} comprise
-not just words that describe a setting as a whole (e.g. ``[in] Greenbow'', ``[in
-a] disco'', ``[the platoon wades through a] rice field''). They also comprise
-words that could count as a member of another categories in case the narrator
-uses these words to indicate a switch from one setting to another (e.g. ``[a]
+The categories \texttt{setting\_new} and \texttt{setting\_rec} comprise not just
+words that describe a setting as a whole (e.g. ``[in] Greenbow'', ``[in a]
+disco'', ``[the platoon wades through a] rice field''). They also comprise words
+that could count as a member of another categories in case the narrator uses
+these words to indicate a switch from one setting to another (e.g. ``[a]
 physician'').
+% how it was handled
+These nouns were flagged with both category during the initial annotation
+procedure. In context of the current analyses these word are considered to
+belong exclusively to the higher-level category of changing a setting
+(\texttt{se\_new} or \texttt{se\_old}).\todo{if you know what I mean}
+% pooling of categories
+Lastly, some categories that were semantically similar categories that offer
+only a small amount of counts were pooled resulting in 11 final categories (see
+Table \ref{tab:ao-events}) that were used as event categories [to model
+different hemodynamic responses].
 
@@
     \caption{Categories and rules to categorize the descriptive nouns spoken by
-        the audio-description's narrator. These categories served as a basis to
-        build the regressors of the GLM (cf. Table \ref{tab:ao-events}).
+        the audio-description's narrator. Some of these initial 18 noun
+        categories were pooled resulting in 11 event categories that served as
+        a basis to build the regressors of the GLM
+        (cf. Table \ref{tab:ao-events}).
         Examples are given in English.
@@
 
+\subsubsection{Modeling}
+
 \paragraph{audio-description: regressors}
 
-% pooling of categories
-To create the regressor for the GLM of the AD stimulus, some of the original 18
-categories that were similar but offered only a small amount of counts were
-pooled resulting in eleven new categories [that served as experimental
-conditionso] (see Table \ref{tab:ao-events}).
-% handling of se_new and se_old
-Moreover, events that fell into one of the two setting-related categories
-(\texttt{se\_new} or \texttt{se\_old}) but also into another category were
-treated as belonging to the setting-related category (e.g. ``[a] physician'').
 % modeling as boxcar function
@@
 
-\paragraph{movie: annotation}
-
-% AV anno
-For the analysis of the AV stimulus, we took advantage of a previously published
-annotation of [the 869] movie cuts and the depicted location after each cut
-\citep{haeusler2016cutanno}.
-
 \paragraph{movie: regressors}
-
-% rationale behind using movie cuts
-Our rationale was that cuts are ``spatially relevant'' events that re-orient the
-viewer within the environment of the movie by either by changing the perspective
-within a setting or switching to another setting.
-
-% AV regressors
-\begin{table*}[h!]
-    \caption{Overview of events to build the 14 regressors for the analysis of
-        the audio-visual (AV) stimulus.
-        \texttt{fg\_av\_ger\_pd} (perceptual differences of consecutive frames),
-        \texttt{fg\_av\_ger\_ml} (mean luminance of a frame),
-        \texttt{fg\_av\_ger\_lr} (difference in mean luminance of left and right
-        half),
-        \texttt{fg\_av\_ger\_ud} (difference in mean luminance of upper and
-        lower half),
-        \texttt{fg\_av\_ger\_lrdiff} (left-right volume difference), and
-        \texttt{fg\_av\_ger\_rms} (root mean square volume) represent one event
-        for every movie frame (\unit[40]{ms}).
-        For description of the two event categories of the audio-description's
-        narrator (\texttt{se\_new} and \texttt{se\_old}) to build contrast of
-        negative control see Table
-\ref{tab:ao-events}.}
-\label{tab:av-events}
-\footnotesize
-\begin{tabular}{lp{3.5cm}lllllllll} \toprule \textbf{label} & \textbf{description} & \textbf{all} & \textbf{1} & \textbf{2} & \textbf{3} & \textbf{4} & \textbf{5} & \textbf{6} & \textbf{7} & \textbf{8} \\
-\midrule
-vse\_new &  change of the camera position to a setting not depicted before & \aoVsenewAll & \aoVsenewI & \aoVsenewII & \aoVsenewIII & \aoVsenewIV & \aoVsenewV & \aoVsenewVI & \aoVsenewVII & \aoVsenewVIII
-\tabularnewline vse\_old & change of the camera position to a recurring setting & \aoVseoldAll & \aoVseoldI & \aoVseoldII & \aoVseoldIII & \aoVseoldIV & \aoVseoldV & \aoVseoldVI & \aoVseoldVII & \aoVseoldVIII
-\tabularnewline
-vlo\_ch & change of the camera position to another locale within the same setting & \aoVlochAll & \aoVlochI & \aoVlochII & \aoVlochIII & \aoVlochIV & 0 & \aoVlochV & \aoVlochVI & \aoVlochVII
-\tabularnewline
-vpe\_new & change of the camera position within a locale not depicted before & \aoVpenewAll & \aoVpenewI & \aoVpenewII & \aoVpenewIII & \aoVpenewIV & \aoVpenewV & \aoVpenewVI & \aoVpenewVII & \aoVpenewVIII
-\tabularnewline
-% vpe_old has no events in 3. So the indices are shifted
-vpe\_old & change of the camera position within a recurring locale &
-\aoVpeoldAll & \aoVpeoldI & \aoVpeoldII & 0 & \aoVpeoldIII & \aoVpeoldIV &
-\aoVpeoldV & \aoVpeoldVI & \aoVpeoldVII
-\tabularnewline
-vno\_cut & frames within a continuous movie shot & \avVnocutAll & \avVnocutI & \avVnocutII & 0 & \avVnocutIII & \avVnocutIV & \avVnocutV & \avVnocutVI & \avVnocutVII
-\tabularnewline
-se\_new & control for AD narrator & \aoSenewAll & \aoSenewI & \aoSenewII & \aoSenewIII & \aoSenewIV & \aoSenewV & \aoSenewVI & \aoSenewVII & \aoSenewVIII
-\tabularnewline
-se\_old & control for AD narrator & \aoSeoldAll & \aoSeoldI & \aoSeoldII & \aoSeoldIII & \aoSeoldIV & \aoSeoldV & \aoSeoldVI & \aoSeoldVII & \aoSeoldVIII
-\tabularnewline
-fg\_av\_ger\_lr & left-right luminance difference & \avFgavgerlrAll & \avFgavgerlrI & \avFgavgerlrII & \avFgavgerlrIII & \avFgavgerlrIV & \avFgavgerlrV & \avFgavgerlrVI & \avFgavgerlrVII & \avFgavgerlrVIII
-\tabularnewline
-fg\_av\_ger\_lrdiff & left-right volume difference & \avFgavgerlrdiffAll & \avFgavgerlrdiffI & \avFgavgerlrdiffII & \avFgavgerlrdiffIII & \avFgavgerlrdiffIV & \avFgavgerlrdiffV & \avFgavgerlrdiffVI & \avFgavgerlrdiffVII & \avFgavgerlrdiffVIII
-\tabularnewline
-fg\_av\_ger\_ml & mean luminance & \avFgavgermlAll & \avFgavgermlI & \avFgavgermlII & \avFgavgermlIII & \avFgavgermlIV & \avFgavgermlV & \avFgavgermlVI & \avFgavgermlVII & \avFgavgermlVIII
-\tabularnewline
-fg\_av\_ger\_pd & perceptual difference & \avFgavgerpdAll & \avFgavgerpdI & \avFgavgerpdII & \avFgavgerpdIII & \avFgavgerpdIV & \avFgavgerpdV & \avFgavgerpdVI & \avFgavgerpdVII & \avFgavgerpdVIII
-\tabularnewline
-fg\_av\_ger\_rms & root mean square (loudness) & \avFgavgerrmsAll & \avFgavgerrmsI & \avFgavgerrmsII & \avFgavgerrmsIII & \avFgavgerrmsIV & \avFgavgerrmsV & \avFgavgerrmsVI & \avFgavgerrmsVII & \avFgavgerrmsVIII
-\tabularnewline
-fg\_av\_ger\_ud & upper-lower luminance difference & \avFgavgerudAll & \avFgavgerudI & \avFgavgerudII & \avFgavgerudIII & \avFgavgerudIV & \avFgavgerudV & \avFgavgerudVI & \avFgavgerudVII & \avFgavgerudVIII
-\tabularnewline
-\end{tabular}
-\end{table*}
 
@@
 
-% AV regressors/events
-Each cut was put into one of the following five categories (see Table
-\ref{tab:av-events}):
-%
-1) a cut switching to a setting that was depicted for the first time
-(\texttt{vse\_new}),
-%
-2) a cut switching to a setting that was already depicted earlier in the movie
-(\texttt{vse\_old}; e.g. a cut to the recurring waiting bench at the bus stop),
-%
-3) a cut switching to another locale within a setting (\texttt{vlo\_ch}; e.g. a
-cut from first to the second floor in Forrest's house),
-%
-4) a cut to another camera position within a setting or locale (e.g. room) that
-was depicted for the first time (\texttt{vpe\_new}), and
-%
-5) a cut to another camera position within a setting or locale that was already
-depicted before (\texttt{vpe\_old}).
-
-% irrespective of visual content
-Notably, categorization was performed irrespectively of a movie frame's precise
-content and thus without controlling confounding variables (e.g. presence of
-faces).
-% AV COPEs: intro
-The rationale that this approach would still yield categories correlating with
-increased hemodynamic activity in the PPA was twofold.
-% cinematographic rationale cut to new scenes: establishing shots
-The cinematographic rationale was that movies tend to establish the setting
-(\texttt{vse\_new}) and the spatial relationships within a setting
-(\texttt{vpe\_new}) at the beginning of a movie.
-% cut to recurrent scene
-Later in the movie, the field sizes of movie shots tend to decrease when
-switching back to already established settings (\texttt{vse\_old}).
-% similarly for shots within a scene
-Moreover, shots within a recurring locale or setting tend to shift to depicting
-persons and objects (\texttt{vpe\_old}) more relevant to the evolved plot
-\citep{brown2012cinematography, mercado2011filmmakers}.
-% neuroscientific rationale
-The neuroscientific rationale was that activity in the PPA is greater when
-participants view novel versus repeated scenes or view-points
-\citep{epstein1999parahippocampal, grill2006repetition}.
 % null regressor
@@
 
-\subsubsection{Contrasts}
-
+\subsection{Statistical analysis}
+
+% contrasts
+Based on these regressors, we then created $t$-contrasts that we presumed to
+subtract variance correlating with the perception of non-spatial information
+from variance correlating with the perception of spatial information.
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 
-\todo[inline]{I am currently stuck here}
 % repeat key question (cf. end of intro)
@@
 two naturalistic stimuli.
+
+\subsubsection{Contrasts}
+
 % intro
@@
 
-\subsection{Statistical analysis}
+\subsubsection{model testing / GLM computations}
+
+To test our model, we ran several $t$-contrasts as part of a GLM for each
+stimulus.
 

### 2021-01-12 paper/main.tex
restructure event modeling in methods v2

@@
 
-\item at the moment "Annotation, Regressors and Contrasts" follows
-    "Preprocessing" (right before "Statistical Analysis" as we agreed on); going
-        back and forth a couple of times, imo there is no perfect location (at
-        least in case we do not split that part into "Annotation" and
-        "Regressors \& Contrasts" again.
-
-\item structure of ``Annotation, Regressors \& Contrasts'' !! -> everything has
-    pros and cons (at the moment lots of subheading since easier to navigate);
-    at the moment I think (again) it makes more sense to mention AD first since
-    it is the focus of the movie and the AV serves as, well, what exactly?
+\item confound regressors von modeling hoch zu eventes
+
+\item revise captions of Table 1 + 3
 
@@
 Images were matched in luminance and size of 400$\times$\unit[400]{px}
-(displayed at a size of approximately
-\unit[10]{$^{\circ}$}$\times$\unit[10]{$^{\circ}$} visual angle).
 % procedure: presentation & instructions
@@
 around us but have the drawback that they are usually fix and that their
-temporal structure of embedded stimulus features is unknown.\todo{phrasing}
+temporal structure of embedded stimulus features is unknown.
 % annotation ftw
@@
 
-\subsubsection{Events (based on annotations)}
-
-\todo[inline]{mention low-level confound annotations here or (as it is now) in
-modeling}
+\subsubsection{Events}
 
@@
 \citep{epstein1999parahippocampal, grill2006repetition}.
+% no cut condition: intro
+In order to create a control condition, a sixth category (\texttt{no\_cut}) was
+created by pseudo-randomly drawing movie frames from continuous movie shots that
+lasted longer than \unit[20]{s}.
+% no cuts: how
+Events were drawn from movie shots in such a way that each event had a minimum
+temporal distance of at least \unit[10]{s} to a movie cut and to another
+\texttt{no\_cut} event.
+
+\paragraph{AV confounds}
+
+% visual confounds -> cf. table
+
+% audio-track confounds
+Lastly, we created two nuisance regressors based on left-right difference in
+volume and root mean square energy averaged across the length of every movie
+frame (\unit[40]{ms}) to capture variance correlating with low-level perceptual
+processes.
+
+\todo[inline]{SE: Continuous bins lasting 40ms?}
 
@@
 
-\paragraph{Audio-description}
+\paragraph{audio-description}
 
@@
 describe the movie's missing visual content based on a set of rules.
-% reference to table with rules and examples
-A complete overview of all 18 noun categories, the rule for a word to belong to
-a category, and examples can be seen in Table \ref{tab:descr-nouns-rules}.
 % preliminary annotation
@@
 Minor corrections due to incorrectly applied rules were done by the author.
+% reference to table with rules and examples
+A complete overview of all 18 noun categories, the rule for a word to belong to
+a category, and examples can be seen in Table \ref{tab:descr-nouns-rules}.
 % why and how of categories 1
@@
 % how it was handled
-These nouns were flagged with both category during the initial annotation
+These nouns were flagged with both categories during the initial annotation
 procedure. In context of the current analyses these word are considered to
 belong exclusively to the higher-level category of changing a setting
-(\texttt{se\_new} or \texttt{se\_old}).\todo{if you know what I mean}
+(\texttt{se\_new} or \texttt{se\_old}).
 % pooling of categories
-Lastly, some categories that were semantically similar categories that offer
-only a small amount of counts were pooled resulting in 11 final categories (see
-Table \ref{tab:ao-events}) that were used as event categories [to model
-different hemodynamic responses].
+Lastly, some noun categories that were semantically similar and offered only a
+small amount of counts were pooled resulting in 11 final event categories (see
+Table \ref{tab:ao-events}). These event categories were then used to model
+hemodynamic responses.
+
+\paragraph{AD confounds}
+
+% audio confounds -> cf. AV & table
+
+% final reference to table
+An overview and the respective counts of the eleven speech-related event
+categories, the five movie cut-related categories, and the two low-level
+confounds can be found in Table \ref{tab:ao-events}.
 
@@
 \end{table*}
-
-\todo[inline]{SE: Table 2 ist relativ kryptisch bzw für jemanden, der sich zum
-    ersten Mal damit auseinander setzt kaum zu verstehen. Auch ist der Bezug zum
-    GLM unklar, d.h., was davon wird verwendet und was verbirgt sich dahinter;
-    COH: I dropped the table of counts per segment. The information is
-    redundant since the counts are not the counts of events of the actual
-regressors (cf. Table \ref{tab:av-events})}
-
-\begin{comment}
-% nouns counts
-The resulting counts for the whole stimulus and the eight stimulus segments used
-during fMRI scanning can be seen in Table \ref{tab:descr-nouns-counts}.
-
-\begin{table*}[h!]
-    \caption{Descriptive nouns spoken by the audio-descriptions narrator:
-        counts for the whole audio-only stimulus and its eight segments used
-        during fMRI scanning.}
-\label{tab:descr-nouns-counts}
-\begin{tabular}{llllllllll}
-\toprule
-\textbf{category} & \textbf{all} & \textbf{1} & \textbf{2} & \textbf{3} & \textbf{4} & \textbf{5} & \textbf{6} & \textbf{7} & \textbf{8} \\
-\midrule
-body & \anBodyAll & \anBodyI & \anBodyII & \anBodyIII & \anBodyIV & \anBodyV & \anBodyVI & \anBodyVII & \anBodyVIII \tabularnewline
-bodypart &  \anBodypartAll & \anBodypartI & \anBodypartII & \anBodypartIII & \anBodypartIV & \anBodypartV & \anBodypartVI & \anBodypartVII & \anBodypartVIII \tabularnewline
-face & \anFaceAll & \anFaceI & \anFaceII & \anFaceIII & \anFaceIV & \anFaceV & \anFaceVI & \anFaceVII & \anFaceVIII \tabularnewline
-female & \anFemaleAll & \anFemaleI & \anFemaleII & \anFemaleIII & \anFemaleIV & \anFemaleV & \anFemaleVI & \anFemaleVII & \anFemaleVIII \tabularnewline
-females & \anFemalesAll & \anFemalesI & \anFemalesII & \anFemalesIII & \anFemalesIV & \anFemalesV & \anFemalesVI & \anFemalesVII & \anFemalesVIII \tabularnewline
-fname & \anFnameAll & \anFnameI & \anFnameII & \anFnameIII & \anFnameIV & \anFnameV & \anFnameVI & \anFnameVII & \anFnameVIII \tabularnewline
-furniture & \anFurnitureAll & \anFurnitureI & \anFurnitureII & \anFurnitureIII & \anFurnitureIV & \anFurnitureV & \anFurnitureVI & \anFurnitureVII & \anFurnitureVIII \tabularnewline
-geo & \anGeoAll & \anGeoI & \anGeoII & \anGeoIII & \anGeoIV & \anGeoV & \anGeoVI & \anGeoVII & \anGeoVIII \tabularnewline
-geo-room & \anGeoroomAll & \anGeoroomI & \anGeoroomII & \anGeoroomIII & \anGeoroomIV & \anGeoroomV & \anGeoroomVI & \anGeoroomVII & \anGeoroomVIII \tabularnewline
-head & \anHeadAll & \anHeadI & \anHeadII & \anHeadIII & \anHeadIV & \anHeadV & \anHeadVI & \anHeadVII & \anHeadVIII \tabularnewline
-male & \anMaleAll & \anMaleI & \anMaleII & \anMaleIII & \anMaleIV & \anMaleV & \anMaleVI & \anMaleVII & \anMaleVIII \tabularnewline
-males & \anMalesAll & \anMalesI & \anMalesII & \anMalesIII & \anMalesIV & \anMalesV & \anMalesVI & \anMalesVII & \anMalesVIII \tabularnewline
-mname & \anMnameAll & \anMnameI & \anMnameII & \anMnameIII & \anMnameIV & \anMnameV & \anMnameVI & \anMnameVII & \anMnameVIII \tabularnewline
-object & \anObjectAll & \anObjectI & \anObjectII & \anObjectIII & \anObjectIV & \anObjectV & \anObjectVI & \anObjectVII & \anObjectVIII \tabularnewline
-objects & \anObjectsAll & \anObjectsI & \anObjectsII & \anObjectsIII & \anObjectsIV & \anObjectsV & \anObjectsVI & \anObjectsVII & \anObjectsVIII \tabularnewline
-persons & \anPersonsAll & \anPersonsI & \anPersonsII & \anPersonsIII & \anPersonsIV & \anPersonsV & \anPersonsVI & \anPersonsVII & \anPersonsVIII \tabularnewline
-setting\_new & \anSettingnewAll & \anSettingnewI & \anSettingnewII & \anSettingnewIII & \anSettingnewIV & \anSettingnewV & \anSettingnewVI & \anSettingnewVII & \anSettingnewVIII \tabularnewline
-setting\_rec & \anSettingrecAll &
-\anSettingrecI & \anSettingrecII & \anSettingrecIII & \anSettingrecIV & \anSettingrecV & \anSettingrecVI & \anSettingrecVII & \anSettingrecVIII \tabularnewline
-% ++ & \anAll & \anI & \anII & \anIII & \anIV & \anV & \anVI & \anVII & \anVIII \tabularnewline
-\bottomrule
-\end{tabular}
-\end{table*}
-
-\end{comment}
 
@@
 
-\subsubsection{Modeling}
-
-\paragraph{audio-description: regressors}
-
+\subsubsection{Hemodynamic Modeling}
+
+% movie events
+The events of the movie cut related categories and \texttt{no\_cut} events were
+modeled as impulse events [lenght = 20 ms?].\todo[actually, that might not be
+true}
+
+AV:
+% convolving
+
+AO:
 % modeling as boxcar function
@@
 
-\todo[inline]{Gab es ein separates null-event für jeden zeitraum zwischen zwei
-annotierten events oder war das ein regressor der immer wieder kam? COH: uhm,
-sorry, what? the following explanation must be misleading?}
-% null regressors
+\todo[inline]{SE: gab es ein separates null-event für jeden zeitraum zwischen
+zwei annotierten events oder war das ein regressor der immer wieder kam?}
+
+% AD: null regressors
 If a stimulus segment did not contain an event of a category, a null regressor
-was chosen for that category in that segment.\todo{wenn ich "null regressor"
-    nehme, darf ich den ganzen Run, glaube ich, in der 2nd level Analyse gar
-    nicht benutzen?  Hatte, glaube ich, Jeanette Mumford in einem ihren Videos
-mal gesagt}
-
-% categories taken from movie cut annotation
-To create contrasts of cross-modal negative control and to capture variance of a
-possibly confounding change of the soundscape after a cut, we also implemented
-the five movie cut-related regressors used in the GLM of the AV stimulus (see
-details below) in the model of the AD stimulus.
-% nuisance regressors
-\todo[inline]{"Continuous bins lasting 40ms?"; COH: goddamnit! I've rewritten
-    this explanation a lot and finally stuck to the phrasing written in
-    \citep{wilson2008beyond} who did the same; it is rephrased now though}
-%
-Lastly, we created two nuisance regressors based on left-right difference in
-volume and root mean square energy averaged across the length of every movie
-frame (\unit[40]{ms}) to capture variance correlating with low-level perceptual
-processes.
-% Reference to table
-An overview and the respective counts of the eleven speech-related event
-categories, the five movie cut-related categories, and the two low-level
-confounds can be found in Table \ref{tab:ao-events}.
-% convolving
-Events for all regressors of the AV stimulus were convolved with a
-double gamma hemodynamic response function (HRF).
-
-\paragraph{movie: regressors}
-
-\todo[inline]{besser erklären (was heißt "unfamilar perspective"? Ab wann ist
-ein setting "familiar"?; COH: should be clearer now; maybe rephrase into a
-couple of sentences to improve readability}
-
-% null regressor
+was chosen for that category in that segment.
+% AV: null regressor
 As for the regressors for AD stimulus, a null regressor was chosen for a
@@
 corresponding category.
-% no cut condition: intro
-A sixth regressors of pseudo-randomly chosen frames (\texttt{no\_cut}) was
-created as a control condition to create negative control contrasts:
-% procedure
-Frames were drawn from movie shots lasting at least \unit[20]{s} and had to have
-a minimum distance of \unit[10]{s} to a movie cut and to another
-\texttt{no\_cut} event.
-
-\todo[inline]{mention low-level feature events for AV here as well and not just
-in the figure caption}
-
-% reference to table
-A short explanation and counts of these six categories modeled as impulse
-events, and six additional event categories for low-level auditory and visual
-features of the movie can be found in Table \ref{tab:av-events}.
+
 % convolving
-Events for all regressors of the AV stimulus were convolved with a
+Events for all regressors of the AV and AO timulus were convolved with a
 double gamma hemodynamic response function (HRF).
-
 % temporal derivatives
@@
 
+\todo[inline]{regressors of other stimulus in GLM of other stimulus}
+% categories taken from movie cut annotation
+Maybe only say in table caption: To create contrasts of cross-modal negative
+control and to capture variance of a possibly confounding change of the
+soundscape after a cut, we also implemented the five movie cut-related
+regressors used in the GLM of the AV stimulus (see details below) in the model
+of the AD stimulus.
+
 % contrasts
@@
 two naturalistic stimuli.
+
+\paragraph{included regressors}
+
+% AO events in AV
+
+% AV events in AO
 

### 2021-01-13 paper/main.tex
revise annotation related tables

@@
 
-\item confound regressors von modeling hoch zu eventes
-
-\item revise captions of Table 1 + 3
+\item revise captions of Table 1 + 3; regressors that are based on the other
+    stimulus for control purposes are now dropped from the table; but mention in
+        Statistical Analysis / Statistical Model)
 
@@
 
-\todo[inline]{SE: focus on the events that are relevant to the analysis to
-reduce complexity and explain these better; COH: revised but maybe still not
-``optimal''}
-
 % traditionally
@@
 
-\paragraph{AV confounds}
-
-% visual confounds -> cf. table
-
-% audio-track confounds
-Lastly, we created two nuisance regressors based on left-right difference in
-volume and root mean square energy averaged across the length of every movie
-frame (\unit[40]{ms}) to capture variance correlating with low-level perceptual
-processes.
-
-\todo[inline]{SE: Continuous bins lasting 40ms?}
-
 % AV regressors
 \begin{table*}[h!]
-    \caption{Overview of events to build the 14 regressors for the analysis of
-        the audio-visual (AV) stimulus.
+    \caption{Overview of annotations and event counts in the whole audio-visual
+    movie and individual stimulus segments.
     \texttt{fg\_av\_ger\_pd} (perceptual differences of consecutive frames),
@@
     for every movie frame (\unit[40]{ms}).
-        For description of the two event categories of the audio-description's
-        narrator (\texttt{se\_new} and \texttt{se\_old}) to build contrast of
-        negative control see Table
-\ref{tab:ao-events}.}
+    % For description of the two event categories of the audio-description's
+    % narrator (\texttt{se\_new} and \texttt{se\_old}) to build contrast of
+    % negative control see Table \ref{tab:ao-events}.
+    }
 \label{tab:av-events}
@@
 \tabularnewline
-se\_new & control for AD narrator & \aoSenewAll & \aoSenewI & \aoSenewII & \aoSenewIII & \aoSenewIV & \aoSenewV & \aoSenewVI & \aoSenewVII & \aoSenewVIII
-\tabularnewline
-se\_old & control for AD narrator & \aoSeoldAll & \aoSeoldI & \aoSeoldII & \aoSeoldIII & \aoSeoldIV & \aoSeoldV & \aoSeoldVI & \aoSeoldVII & \aoSeoldVIII
-\tabularnewline
+% se\_new & control for AD narrator & \aoSenewAll & \aoSenewI & \aoSenewII & \aoSenewIII & \aoSenewIV & \aoSenewV & \aoSenewVI & \aoSenewVII & \aoSenewVIII
+% \tabularnewline
+% se\_old & control for AD narrator & \aoSeoldAll & \aoSeoldI & \aoSeoldII & \aoSeoldIII & \aoSeoldIV & \aoSeoldV & \aoSeoldVI & \aoSeoldVII & \aoSeoldVIII
+% \tabularnewline
 fg\_av\_ger\_lr & left-right luminance difference & \avFgavgerlrAll & \avFgavgerlrI & \avFgavgerlrII & \avFgavgerlrIII & \avFgavgerlrIV & \avFgavgerlrV & \avFgavgerlrVI & \avFgavgerlrVII & \avFgavgerlrVIII
@@
 \tabularnewline
-fg\_av\_ger\_rms & root mean square (loudness) & \avFgavgerrmsAll & \avFgavgerrmsI & \avFgavgerrmsII & \avFgavgerrmsIII & \avFgavgerrmsIV & \avFgavgerrmsV & \avFgavgerrmsVI & \avFgavgerrmsVII & \avFgavgerrmsVIII
+fg\_av\_ger\_rms & root mean square volume & \avFgavgerrmsAll & \avFgavgerrmsI & \avFgavgerrmsII & \avFgavgerrmsIII & \avFgavgerrmsIV & \avFgavgerrmsV & \avFgavgerrmsVI & \avFgavgerrmsVII & \avFgavgerrmsVIII
 \tabularnewline
@@
 % pooling of categories
-Lastly, some noun categories that were semantically similar and offered only a
+Some noun categories that were semantically similar and offered only a
 small amount of counts were pooled resulting in 11 final event categories (see
@@
 
-\paragraph{AD confounds}
-
-% audio confounds -> cf. AV & table
-
-% final reference to table
-An overview and the respective counts of the eleven speech-related event
-categories, the five movie cut-related categories, and the two low-level
-confounds can be found in Table \ref{tab:ao-events}.
-
 % table for descriptive nouns: categories, rules, examples counts
@@
     \caption{Categories and rules to categorize the descriptive nouns spoken by
-        the audio-description's narrator. Some of these initial 18 noun
-        categories were pooled resulting in 11 event categories that served as
-        a basis to build the regressors of the GLM
+        the audio-description's narrator.
+        Examples are given in English.
+        Some of these initial 18 noun categories were pooled resulting in 11
+        event categories that served as a basis to build the regressors of the
+        GLM
         (cf. Table \ref{tab:ao-events}).
-        Examples are given in English.
         % The category \texttt{++} also contains adverbial of time.
@@
 \begin{table*}[h!]
-    \caption{Overview of events to build the 18 regressors for the
-        analysis of the audio-only (AD) stimulus. Some of the annotation's
-        original categories (female, females, fname; male, males, mname; face,
-        head; object, objects; see Table\ref{tab:descr-nouns-rules}) were pooled
-        into 11 new categories (\texttt{sex\_f}; \texttt{sex\_m};
-        \texttt{fahead}; \texttt{object}).  \texttt{fg\_ad\_lrdiff} (left-right
-        volume difference) and \texttt{fg\_ad\_rms} (root mean square volume)
-        represent one event for every movie frame (\unit[40]{ms}). For a
-        description of the five control conditions for movie cuts see Table
-        \ref{tab:av-events}.}
+    \caption{Overview of annotations and event counts in the whole
+    audio-description and individual stimulus segments.
+    Some of the annotation's original categories (female, females, fname; male,
+    males, mname; face, head; object, objects;
+    see Table\ref{tab:descr-nouns-rules}) were pooled
+    into 11 new categories (\texttt{sex\_f}; \texttt{sex\_m}; \texttt{fahead};
+    \texttt{object}), \texttt{fg\_ad\_lrdiff} (left-right volume difference)
+    and \texttt{fg\_ad\_rms} (root mean square volume) represent one event for
+    every movie frame (\unit[40]{ms}).
+    % For a description of the five control conditions for movie cuts see
+    % Table \ref{tab:av-events}.
+    }
 \label{tab:ao-events} \footnotesize
@@
 % vlo_ch has no events in segment 5. So indices are shifted
-vse\_new & control for movie cut & \aoVsenewAll & \aoVsenewI & \aoVsenewII &
-\aoVsenewIII & \aoVsenewIV & \aoVsenewV & \aoVsenewVI & \aoVsenewVII &
-\aoVsenewVIII
-\tabularnewline
-vse\_old & control for movie cut & \aoVseoldAll & \aoVseoldI & \aoVseoldII & \aoVseoldIII & \aoVseoldIV & \aoVseoldV & \aoVseoldVI & \aoVseoldVII & \aoVseoldVIII
-\tabularnewline
-vlo\_ch & control for movie cut &
-\aoVlochAll & \aoVlochI & \aoVlochII & \aoVlochIII & \aoVlochIV & 0 & \aoVlochV
-& \aoVlochVI & \aoVlochVII
-\tabularnewline
-vpe\_new & control for movie cut & \aoVpenewAll & \aoVpenewI & \aoVpenewII & \aoVpenewIII & \aoVpenewIV & \aoVpenewV & \aoVpenewVI & \aoVpenewVII & \aoVpenewVIII
-\tabularnewline
+%vse\_new & control for movie cut & \aoVsenewAll & \aoVsenewI & \aoVsenewII & \aoVsenewIII & \aoVsenewIV & \aoVsenewV & \aoVsenewVI & \aoVsenewVII & \aoVsenewVIII
+%\tabularnewline
+%vse\_old & control for movie cut & \aoVseoldAll & \aoVseoldI & \aoVseoldII & \aoVseoldIII & \aoVseoldIV & \aoVseoldV & \aoVseoldVI & \aoVseoldVII & \aoVseoldVIII
+%\tabularnewline
+%vlo\_ch & control for movie cut & \aoVlochAll & \aoVlochI & \aoVlochII & \aoVlochIII & \aoVlochIV & 0 & \aoVlochV & \aoVlochVI & \aoVlochVII
+%\tabularnewline
+%vpe\_new & control for movie cut & \aoVpenewAll & \aoVpenewI & \aoVpenewII & \aoVpenewIII & \aoVpenewIV & \aoVpenewV & \aoVpenewVI & \aoVpenewVII & \aoVpenewVIII
+%\tabularnewline
 % vpe_old has no events in 3. So the indices are shifted
-vpe\_old & control for movie cut & \aoVpeoldAll & \aoVpeoldI & \aoVpeoldII & 0 &
-\aoVpeoldIII & \aoVpeoldIV & \aoVpeoldV & \aoVpeoldVI & \aoVpeoldVII
-\tabularnewline
+%vpe\_old & control for movie cut & \aoVpeoldAll & \aoVpeoldI & \aoVpeoldII & 0 & \aoVpeoldIII & \aoVpeoldIV & \aoVpeoldV & \aoVpeoldVI & \aoVpeoldVII
+% \tabularnewline
 fg\_ad\_lrdiff & left-right volume difference & \aoFgadlrdiffAll & \aoFgadlrdiffI & \aoFgadlrdiffII & \aoFgadlrdiffIII & \aoFgadlrdiffIV &
@@
 \tabularnewline
-fg\_ad\_rms & root mean square (loudness) & \aoFgadrmsAll &
+fg\_ad\_rms & root mean square volume & \aoFgadrmsAll &
 \aoFgadrmsI & \aoFgadrmsII & \aoFgadrmsIII & \aoFgadrmsIV & \aoFgadrmsV &
@@
 
+\paragraph{Confounds for both}
+
+\todo[inline]{Die Events für die low-level confounds habe erstmal hier
+beschrieben; btw: Das Verschieben des Sounds in den Segmenten spiegelt sich
+wahrscheinlich auch in den unterschiedlichen Counts der Events je Segment wider
+(AV Bild vs AV Sound vs AO Sound)}
+
+% intro
+Lastly, we algorithmically annotated the temporal
+structure of low-level perceptual features to create nuisance regressors.
+% visual shit
+For the AV stimulus, we computed the mean luminance of a movie frame
+(\unit[40]{ms}), the difference in mean luminance of each frame's left and right
+half, the difference in mean luminance of the lower and upper half, and finally
+the perceptual differene of consecutive frames.
+% auditory shit
+Finally, we computed the left-right difference in volume and root mean
+square energy averaged across the length of every movie frame (\unit[40]{ms}) of
+both audio-tracks.
+
 \subsubsection{Hemodynamic Modeling}
@@
 The events of the movie cut related categories and \texttt{no\_cut} events were
-modeled as impulse events [lenght = 20 ms?].\todo[actually, that might not be
+modeled as impulse events [lenght = 20 ms?].\todo{actually, that might not be
 true}

### 2021-01-13 paper/main.tex
minor changes until statistical analysis

@@
 % intro
-Lastly, we algorithmically annotated the temporal
-structure of low-level perceptual features to create nuisance regressors.
+Lastly, we algorithmically annotated the temporal structure of low-level
+perceptual features to create nuisance regressors.
 % visual shit
@@
 half, the difference in mean luminance of the lower and upper half, and finally
-the perceptual differene of consecutive frames.
+the perceptual difference of consecutive frames.
 % auditory shit
-Finally, we computed the left-right difference in volume and root mean
-square energy averaged across the length of every movie frame (\unit[40]{ms}) of
-both audio-tracks.
+Finally, we computed the left-right difference in volume and root mean square
+energy averaged across the length of every movie frame (\unit[40]{ms}) of both
+audio-tracks.
 
@@
 modeled as impulse events [lenght = 20 ms?].\todo{actually, that might not be
-true}
-
-AV:
-% convolving
-
-AO:
+true}.
+%
+Nouns were modeled from onset to offset of each word, low-level confounds from
+onset to offset of the corresponding movie frame AO:
 % modeling as boxcar function
 Events were were modeled as boxcar function from onset to offset of each word.
-
-\todo[inline]{SE: gab es ein separates null-event für jeden zeitraum zwischen
-zwei annotierten events oder war das ein regressor der immer wieder kam?}
-
-% AD: null regressors
-If a stimulus segment did not contain an event of a category, a null regressor
-was chosen for that category in that segment.
-% AV: null regressor
-As for the regressors for AD stimulus, a null regressor was chosen for a
-regressor in a segment if that segment did not contain an event of the
-corresponding category.
-
 % convolving
-Events for all regressors of the AV and AO timulus were convolved with a
-double gamma hemodynamic response function (HRF).
-% temporal derivatives
-Temporal derivatives were included in the design matrix to compensate for
-regional differences between modeled and actual HRF \citep{friston1998event}.
-% motion parameters
-Six motion parameters were also used as additional nuisance regressors.
-% high-pass filtering
-Finally, designs were filtered with the same high-pass filter (cutoff period of
-\unit[150]{s}) as the BOLD time series.
-
-\paragraph{regressor correlations}
-
-% stimuli not designed for research purposes
-The audio-description and the movie were not designed to be used in a BOLD fMRI
-experiment but to entertain their audiences.
+Events for all regressors of the AV and AO stimulus were convolved with a double
+gamma hemodynamic response function (HRF).
+% we checked correlations
+Since the time-series of modeled hemodynamic activity were based on events in
+stimuli that were not designed for research, we then tested if time-series were
+correlated (i.e. share variance) leading to low detection power in subsequent
+analyses\todo{pick your favorite}.
 % fixed time course; detection power
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 Since we annotated events in fixed time courses that could not experimentally
-manipulated, regressors that are based on these events could be correlated
-leading to shared variance and thus low detection power of subsequent analyses.
+manipulated, the modeled time-series [of hemodynamic activity] based on these
+events could be correlated leading to shared variance and thus low detection
+power of subsequent analyses.
 % correlations within stimuli and across stimuli
-Hence, we first tested for correlation of regressors across the eight segments
-of each stimulus and correlations of regressors across both stimuli (s. Figure
+Hence, we tested for correlation of regressors across the eight segments of each
+stimulus and also for correlations of regressors across both stimuli (s. Figure
 \ref{fig:reg-corr})
@@
 The computed Pearson correlation coefficients demonstrate no to minor
-correlations of regressors of the same stimulus [which suggest the models should
-not suffer from low detection power due to shared variance among regressors].
+correlations of modeled hemodynamic time-series belonging to the same stimulus.
 % correlations across stimuli
 The highest correlations are apparent between auditory low-level confounds
-across stimuli. This was expected and served as ``sanity check'' since the
-audio-track of the audio-description is the audio-track of the movie but
-featuring the additional narrator (s. Figure \ref{fig:reg-corr}).
+across stimuli (\texttt{fg\_ad\_rms} and \texttt{fg\_av\_ger\_rms}, r=.7635;
+\texttt{fg\_ad\_lrdiff} and \texttt{fg\_av\_ger\_lrdiff}, r=.7749). This was
+expected and served as ``sanity check'' since the audio-track of the
+audio-description is the audio-track of the movie but featuring the additional
+narrator (s. Figure \ref{fig:reg-corr}).
 % encouraged by that we build contrasts (statement)
@@
         description) and audio-visual movie (red; see Table \ref{tab:av-events})
-        rounded to the nearest tenth.  The correlation between the two stimuli's
+        rounded to the nearest tenth.
+        The correlation between the two stimuli's
         root mean square loudness and between their left-right difference in
@@
 
-\paragraph{included regressors}
-
-% AO events in AV
-
-% AV events in AO
+\paragraph{Design Matrix}
+
+\todo[inline]{I created the part "design matrix" cause following parts are
+usually written in the "regressor paragraph" in publications but do not really
+fit in the subsection above}
+
+\todo[inline]{SE: gab es ein separates null-event für jeden zeitraum zwischen
+zwei annotierten events oder war das ein regressor der immer wieder kam?}
+
+% null regressors
+If a stimulus segment did not contain an event of a category (e.g. no event of
+\texttt{vpe\_old} in segment 3 of the movie; cf. Table \ref{tab:ao-events}), a
+null regressor was chosen for that category in that segment.
+
+% temporal derivatives
+Temporal derivatives were included in the design matrix to compensate for
+regional differences between modeled and actual HRF \citep{friston1998event}.
+% motion parameters
+Six motion parameters were also used as additional nuisance regressors.
+% high-pass filtering
+Finally, designs were filtered with the same high-pass filter (cutoff period of
+\unit[150]{s}) as the BOLD time series.
 

### 2021-01-15 paper/main.tex
analysis: explain design matrices

@@
 The events of the movie cut related categories and \texttt{no\_cut} events were
-modeled as impulse events [lenght = 20 ms?].\todo{actually, that might not be
-true}.
+modeled as impulse events.\todo{actually, it was a box car of 200 ms after
+starting with the cut}.
 %
@@
 % we checked correlations
-Since the time-series of modeled hemodynamic activity were based on events in
-stimuli that were not designed for research, we then tested if time-series were
-correlated (i.e. share variance) leading to low detection power in subsequent
-analyses\todo{pick your favorite}.
-% fixed time course; detection power
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-Since we annotated events in fixed time courses that could not experimentally
-manipulated, the modeled time-series [of hemodynamic activity] based on these
-events could be correlated leading to shared variance and thus low detection
-power of subsequent analyses.
+Since we annotated events in naturalistic stimuli and thus fixed time courses
+that could not experimentally manipulated, the modeled time-series [of
+hemodynamic activity] based on these events could be correlated leading to
+shared variance and thus low detection power of subsequent analyses.
 % correlations within stimuli and across stimuli
@@
 \texttt{fg\_ad\_lrdiff} and \texttt{fg\_av\_ger\_lrdiff}, r=.7749). This was
-expected and served as ``sanity check'' since the audio-track of the
+expected and served as a ``sanity check'' since the audio-track of the
 audio-description is the audio-track of the movie but featuring the additional
@@
 
-\begin{figure*} \centering
+\begin{figure*}[h!]
+\centering
     \includegraphics[width=\linewidth]{figures/regressor-corr} \caption{Pearson
@@
 
-\todo[inline]{regressors of other stimulus in GLM of other stimulus}
-% categories taken from movie cut annotation
-Maybe only say in table caption: To create contrasts of cross-modal negative
-control and to capture variance of a possibly confounding change of the
-soundscape after a cut, we also implemented the five movie cut-related
-regressors used in the GLM of the AV stimulus (see details below) in the model
-of the AD stimulus.
-
-% contrasts
-Based on these regressors, we then created $t$-contrasts that we presumed to
-subtract variance correlating with the perception of non-spatial information
-from variance correlating with the perception of spatial information.
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% "ingredients" to answer our questions (cf. intro); we have annotations; define
-% congruent contrasts based on regressors based on annotations
-
-% repeat key question (cf. end of intro)
-The key question of the current study was if a) we could operationalize the
-perceptual processes in an audio-visual and exclusively auditory
-naturalistic stimulus and if b) contrasting that fcompared to an
-operationalization of non-spatial perception  would yield to increased
-hemodynamic activity in the PPA as defined by a visual localizer experiment.
-% difference (kinda repetition)
-Instead of carefully selecting and designing conceptualized/simplified stimuli
-that we assumed to match the proposed perceptual processes, we selected and
-categorized stimulus features (movie cuts and spoken nouns) that are embedded in
-two naturalistic stimuli.
+% level 1 and 2; similarly to the reviewed studies that employed designed
+% stimuli; we "based on stimulus annotations"
+We then tested our modeled hemodynamic responses by conducting standard
+two-level general linear model (GLM) analyses to create subject-specific results
+($Z$-maps) across the 8 segments for every subject and each stimulus.
+% level 3
+Subsequent, third-level analyses averaged contrast estimates over subjects.
 
@@
 
-\todo[inline]{I created the part "design matrix" cause following parts are
-usually written in the "regressor paragraph" in publications but do not really
-fit in the subsection above}
-
-\todo[inline]{SE: gab es ein separates null-event für jeden zeitraum zwischen
-zwei annotierten events oder war das ein regressor der immer wieder kam?}
-
-% null regressors
-If a stimulus segment did not contain an event of a category (e.g. no event of
-\texttt{vpe\_old} in segment 3 of the movie; cf. Table \ref{tab:ao-events}), a
-null regressor was chosen for that category in that segment.
-
+% AV design matrix
+For the first level analysis of the AV stimulus, the modeled hemodynamic
+responses related to all movie cuts (including \texttt{no\_cut}) and six
+low-level perceptual confounds were included as regressors in the design matrix
+(s. Table \ref{tab:av-events}).
+% AD regressors in AV AD design matrix
+For the first level analysis of the AD stimulus, the modeled hemodynamic
+responses related to all noun categories and the two low-level perceptual
+confounds were included (s. Table \ref{tab:ao-events}).
+% AD regressors in AV
+To create a contrasts of cross-modal control in the analysis of the AV stimulus,
+we also implemented the regressors based on nouns used by the
+audio-description's narrator to cue switches to another setting (categories
+\texttt{se\_new} and \texttt{se\_old}).
+% AV regressors in AV
+To create contrasts of cross-modal negative control in the analysis of the AD
+stimulus [and to capture variance of a possibly confounding change of the
+soundscape after a cut], we implemented the movie cut-related regressors
+(excluding \texttt{no\_cut}).
+% both stimuli: null regressors
+In analyses of both stimuli, a null regressor was chosen for a event category in
+a segment, if that segment did not contain an event of the category (e.g. no
+event of \texttt{vpe\_old} in segment 3; cf. Table \ref{tab:ao-events}).
 % temporal derivatives
@@
 
-\subsubsection{Contrasts}
+\paragraph{PPA Contrasts} \todo{maybe repeat key questions (cf. intro) here}
 
 % intro
-To test the robustness of our approach, we operationalized the
+To test the robustness of our approach, we then operationalized the
 perception of spatial information compared to the perception of ``non-spatial''
@@
 events.
+
+% AV primary contrast
+In the primary contrast of the AV stimulus, we contrasted cuts to a setting that
+was not depicted before (\texttt{vs\_new}) to cuts that we accompanied with a
+change of the camera position within a setting that was already occurring
+previously (\texttt{vpe\_old}).
+% why
+We assumed that movie frames in these categories on average best represent
+events that trigger perception of space versus e.g. objects or
+faces.
 
@@
 
-% AV primary contrast
-In the primary contrast of the AV stimulus, we contrasted cuts to a setting that
-was not depicted before (\texttt{vs\_new}) to cuts that we accompanied with a
-change of the camera position within a setting that was already occurring
-previously (\texttt{vpe\_old}).
-% why
-We assumed that movie frames in these categories on average best represent
-events that trigger perception of space versus objects or faces.\todo{syntax?}
-
 \todo[inline]{one could write more about the different contrast in Segupta et
@@
 
-\paragraph{control contrasts: AD \& AV}
+\paragraph{Control contrasts}
 
@@
 \subsubsection{model testing / GLM computations}
-
-To test our model, we ran several $t$-contrasts as part of a GLM for each
-stimulus.
-
-% intro
-Similarly to the reviewed studies that employed simplified stimuli, we conducted
-a standard two-level general linear model (GLM) analysis to create
-subject-specific results ($Z$-maps) across the 8 segments for every subject. A
-subsequent, third-level analysis averaged contrast estimates over subjects.
 

### 2021-01-18 paper/main.tex
restructure contrasts section

@@
 
-\item revise captions of Table 1 + 3; regressors that are based on the other
-    stimulus for control purposes are now dropped from the table; but mention in
-        Statistical Analysis / Statistical Model)
-
-\item what do we need to check to ensure subsequent analyses are valid;
-    a) correlation of regressors (first "sanity check" but more a prerequisite)
-    b) negative controls (actual sanity check)
+    \item Zwischenüberschriften rausnehmen, wenn Struktur so in Ordnung
+
+    \item revise captions of Table 1 + 3 (regressors based on annotation of
+    the other FG stimulus are now dropped from the table but mentioned in
+    section "statistial model / contrasts")
 
@@
 \begin{itemize}
-\item mehrere Kontraste in VIS genommen, hier einer berichtet: Teil aus
-    Discussion in Results hochnehmen
+\item adjust structure of results to structure of discussion
+\item ggf. berichten welcher der drei VIS Kontraste für welche VP genommen
+    wurde
 \end{itemize}
@@
 \begin{itemize}
+\item umschreiben gemäß neuer Schwerpunktsetzung in Intro \& Method-Section
     \item \citep{bartels2004mapping, hasson2004intersubject}
-    \item VIS: "best contrast was chosen"
+    \item mehr zum Thema VIS( "best contrast was chosen")
 \end{itemize}
@@
 The events of the movie cut related categories and \texttt{no\_cut} events were
-modeled as impulse events.\todo{actually, it was a box car of 200 ms after
-starting with the cut}.
+modeled as impulse events.\todo{actually, it was a box car of 200 ms starting
+with the cut}.
 %
@@
 correlations of modeled hemodynamic time-series belonging to the same stimulus.
-% correlations across stimuli
+% (highest) correlations across stimuli
 The highest correlations are apparent between auditory low-level confounds
-across stimuli (\texttt{fg\_ad\_rms} and \texttt{fg\_av\_ger\_rms}, r=.7635;
-\texttt{fg\_ad\_lrdiff} and \texttt{fg\_av\_ger\_lrdiff}, r=.7749). This was
-expected and served as a ``sanity check'' since the audio-track of the
+across stimuli (\texttt{fg\_av\_ger\_rms} and \texttt{fg\_ad\_rms}, r=.7635;
+\texttt{fg\_av\_ger\_lrdiff} and \texttt{fg\_ad\_lrdiff} and , r=.7749).
+% no surprise
+This was expected and served as a ``sanity check'' since the audio-track of the
 audio-description is the audio-track of the movie but featuring the additional
@@
 
-\paragraph{PPA Contrasts} \todo{maybe repeat key questions (cf. intro) here}
-
+\paragraph{PPA Contrasts}
+
+In this study, we investigated if increased hemodynamic activty in the PPA that
+is usually defined by contrasting blocks of pictures can also be revealed by
+contrasting selected stimulus features that we annotated in a audio-visual movie
+and its audio-description.
 % intro
-To test the robustness of our approach, we then operationalized the
-perception of spatial information compared to the perception of ``non-spatial''
-information differently in eight $t$-contrasts for the AD stimulus (see Table
+To test the robustness of our approach, we operationalized the perception of
+spatial information compared to the perception of ``non-spatial'' information
+differently in eight $t$-contrasts for the AD stimulus (see Table
 \ref{tab:ao-contrasts}) and five $t$-contrasts for the AV stimulus (see Table
@@
 averaged events reflected spatial information, and b) in available data (i.e.
-event counts).\todo{make ref to what is no "Audio-description: annotation"}
+event counts).
+% difference to Sengupta; Berman et al. (2010). Evaluating functional localizers
+(2010) Notably, localization of the PPA in individual subjects that was done by
+\citep{sengupta2016extension} using the established approach of contrasting
+blocks of pictures is based on one contrast for each subjects (cf. Table 3 in
+\citep{sengupta2016extension}) that was chosen post-hoc from a set of three
+contrasts (\textit{strict}, \textit{relaxed}, and \textit{simple} contrast
+\citep{sengupta2016extension}).\todo{maybe add note regarding Berman (2010);
+but they did FFA}
 % thus: primary contrasts
-For each stimulus, we chose one contrast to be ``primary contrast'' for further
-inspection and a detailed report.
+Here, we chose one contrast to be ``primary contrast'' for later detailed
+inspection and report.
 % selection criteria for primary contrast.
@@
 to match the preferred stimulus type, and b) the amount of available data /
-events.
-
-% AV primary contrast
+% AV: primary contrast
 In the primary contrast of the AV stimulus, we contrasted cuts to a setting that
@@
 We assumed that movie frames in these categories on average best represent
-events that trigger perception of space versus e.g. objects or
-faces.
-
+events that trigger perception of space versus e.g. objects or faces.
 % AD: primary contrast
@@
 
-\todo[inline]{one could write more about the different contrast in Segupta et
-al. here, but imo it's sufficient to point that out in the results given that
-all subjects except two used the strict set given contrasts of VIS study and
-that the ``best working'' will be used}
-
-\todo[inline]{Nevertheless, state it in one sentence and check Berman, M. G. et al. Evaluating functional localizers: The case of the FFA. NeuroImage 50, 56–71 (2010)}
-
-Similarly to \citep{sengupta2016extension} that chose the ``best'' of three
-alternative contrasts (strict, relaxed, or simple contrast), future studies that
-aim for individual diagnostics / ROI localization should also test more than one
-contrast to gain the ``best'' individual ROIs.\todo{``best'' sounds pretty
-shitty}
-
 \paragraph{Control contrasts}
@@
 Finally, we created several contrasts as negative control for both stimuli.
+% AV: no cut > cut
+For the AV stimulus, four $t$-contrasts were created contrasting the no-cut
+regressor (texttt{vno\_cut} to cut-related regressors \ref{tab:av-contrasts}).
+% AV: narrator
+One contrast (\texttt{vs\_new} > \texttt{vpe\_old}) was created by
+contrasting nouns spoken by the narrator.
+\todo[inline]{why was done? narrator and cuts to other setting are "somewhat"
+correlated; and now what? -> cf. results and discussion}
 % AD stimulus
@@
 \ref{tab:ao-contrasts}) to test if increased activation in the PPA was
-correlated with moments of cuts possibly correlated with a accompanying change
-in the soundscape.
-% AV stimulus
-For the AV stimulus, four $t$-contrasts were created contrasting the no-cut
-condition (texttt{vno\_cut} for negative control purposes (see Table
-\ref{tab:av-contrasts}) by using regressors based on regressors of the AD
-stimulus. One contrast (\texttt{vs\_new} > \texttt{vpe\_old})  was created by
-contrasting nouns spoken by the narrator.
+correlated with moments of cuts as cuts might possibly be correlated with a
+change of the soundscape also giving an auditory cue of switching to another
+setting.
+
+\begin{table*}[h!]
+\caption{Contrasts of parameter estimates for the analysis of the
+    audio-visual movie (AV).
+    Contrast 1-5 aim to isolate the PPA.
+    Contrast 6-9 serve as negative control.
+    Contrast 10 serves as control for moments when the narrator cues the
+    listener about a switch of settings, events that could be correlated with a
+    change of the soundscape.}
+\label{tab:av-contrasts}
+\footnotesize
+\begin{tabular}{lll}
+\toprule
+\textbf{nr.} &  \textbf{contrast} & \textbf{purpose} \\
+\midrule
+1 & vse\_new > vpe\_old & PPA \tabularnewline
+2 & vse\_new, vpe\_new > vse\_old, vpe\_old & PPA \tabularnewline
+3 & vse\_new > vse\_old & PPA \tabularnewline
+4 & vse\_new > vse\_old, vpe\_old & PPA \tabularnewline
+5 & vse\_new, vpe\_new > vpe\_old & PPA \tabularnewline
+6 & vno\_cut > vse\_new & negative control \tabularnewline
+7 & vno\_cut > vse\_old & negative control \tabularnewline
+8 & vno\_cut > vse\_new, vse\_old & negative control \tabularnewline
+9 & vno\_cut > vpe\_new, vpe\_old & negative control \tabularnewline
+10 & se\_new > se\_old & control for (missing) narrator \tabularnewline
+\end{tabular}
+\end{table*}
 
@@
 
-\begin{table*}[h!]
-\caption{Contrasts of parameter estimates for the analysis of the
-    audio-visual movie (AV).
-    Contrast 1-5 aim to isolate the PPA.
-    Contrast 6-9 serve as negative control.
-    Contrast 10 serves as control for moments when the narrator cues the
-    listener about a switch of settings, events that could be correlated with a
-    change of the soundscape.}
-\label{tab:av-contrasts}
-\footnotesize
-\begin{tabular}{lll}
-\toprule
-\textbf{nr.} &  \textbf{contrast} & \textbf{purpose} \\
-\midrule
-1 & vse\_new > vpe\_old & PPA \tabularnewline
-2 & vse\_new, vpe\_new > vse\_old, vpe\_old & PPA \tabularnewline
-3 & vse\_new > vse\_old & PPA \tabularnewline
-4 & vse\_new > vse\_old, vpe\_old & PPA \tabularnewline
-5 & vse\_new, vpe\_new > vpe\_old & PPA \tabularnewline
-6 & vno\_cut > vse\_new & negative control \tabularnewline
-7 & vno\_cut > vse\_old & negative control \tabularnewline
-8 & vno\_cut > vse\_new, vse\_old & negative control \tabularnewline
-9 & vno\_cut > vpe\_new, vpe\_old & negative control \tabularnewline
-10 & se\_new > se\_old & control for (missing) narrator \tabularnewline
-\end{tabular}
-\end{table*}
-
-\subsubsection{model testing / GLM computations}
+\paragraph{GLM computations \& stuff}
 

### 2021-01-18 paper/main.tex
results: rearrange blocks of text

@@
 \begin{itemize}
-
     \item Zwischenüberschriften rausnehmen, wenn Struktur so in Ordnung
-
     \item revise captions of Table 1 + 3 (regressors based on annotation of
@@
     section "statistial model / contrasts")
-
 \end{itemize}
@@
 \begin{itemize}
-\item adjust structure of results to structure of discussion
+    \item Simons Kommentare, bei denen ich mitunter anderer Meinung bin
     \item ggf. berichten welcher der drei VIS Kontraste für welche VP genommen
     wurde
+    \item location of tables \& figures is pretty confusing at the moment
 \end{itemize}
@@
 \unit[150]{s}) as the BOLD time series.
+
+\todo[inline]{SE: würde wetten, dass Reviewer fragen: Wie sieht es im vergleich
+dazu mit Faces aus? COH: yeah, well, I made the contrasts similar to Sengupta
+and considered the contrast to an average of all ``non-spatial'' stuff
+appropriate; should be cleare in the method section (s. ``Contrasts'')}
+
+\todo[inline]{SE: cuts to new vs familar setting wird irgendwie nie so
+richtig in den PPA kontext eingeordnet. Warum ist das Hauptkontrast und nicht
+das viel näher liegende places vs faces? COH: places vs. face = simple set in
+Sengupta; here, we follow the strict set used in Sengupta; tbh, not mentioned in
+detail}
 
@@
 \section{Results}
-\todo[inline]{we have to decide how we want to present this: a) by stimulus or b) by analysis type. With the present abstract I am leaning towards (a), but we should debate that}
 
@@
 
-\todo[inline]{SE: würde wetten, dass Reviewer fragen: Wie sieht es im vergleich
-dazu mit Faces aus? COH: yeah, well, I made the contrasts similar to Sengupta
-and considered the contrast to an average of all ``non-spatial'' stuff
-appropriate; should be cleare in the method section (s. ``Contrasts'')}
-
 \todo[inline]{SE: Figures with group results: würde da wahrscheinlich weiter
 rein zoomen, um genauer den visuellen Kortex zu zeigen; vor allem muss man
-sagen: bei FFA/PPA etc sind flatmaps/inflated brains standard; imo it is
+sagen: bei FFA/PPA etc sind flatmaps/inflated brains standard; COH: imo it is
 important that we do not have clusters all over the brain}
@@
 yes, I know it is kinda difficult, tried my best to choose/tweak the color map}
-
-\todo[inline]{SE: cuts to new vs familar setting wird irgendwie nie so
-richtig in den PPA kontext eingeordnet. Warum ist das Hauptkontrast und nicht
-das viel näher liegende places vs faces? COH: should at least be clearer after
-revision of method section}
 
@@
 
-\subsection{Group results}
-
-\subsubsection{AD: PPA in primary contrast}
+\subsection{Primary contrasts}
 
@@
 activity in the PPA.
-% primary AD contrast
+
+\subsubsection{group}
+% AV intro
+As conceptual/cross-modal control of the group average results, we also analyzed
+data from the audio-visual movie by contrasting different kinds of movie cuts
+independent(ly) from the frames' visual content following the cut.
+% AV primary contrast
+The movie's primary $t$-contrast that compared cuts to a setting that was not
+depicted before to a recurring setting (\texttt{vse\_new > vpe\_old}) yielded
+three significant clusters (see Table \ref{tab:res-av-group1}, Figure
+\ref{fig:group-slices}).
+% PPA (others the clusters extend into).
+One cluster spans across the midline and comprises, parts of the intracalcarine
+and cuneal cortex, the lingual gyrus and retrosplenial cortex, the occipital and
+temporal fusiform gyrus and the parahippocampal cortex (reported from posterior
+to anterior) in both hemispheres.
+% LOC
+Two additional homologous clusters are located in the superior lateral occipital
+cortex (left bigger than right).
+
+% AD
 The primary $t$-contrast for the audio-description (\texttt{geo, groom} >
@@
 
+% figure group results primary AD & AV contrasts
+\begin{figure*}[h!] \centering
+    \includegraphics[width=\linewidth]{figures/group-slices}
+    \caption{Mixed-effects group-level (N=14) GLM results. Significant clusters
+        (Z>3.4, p<.05 cluster-corrected) are overlaid on the MNI152 T1-weighted
+        head template (gray).
+        Light gray: The audio-description's field-of-view
+        (cf. \citep{hanke2014audiomovie}).
+        Black: outline of overlapping individual PPA ROIs.
+        The results of audio-description's primary $t$-contrast (blue) that
+        compares geometry-related nouns to non geometry-related nouns spoken by
+        the audio-description's narrator (\texttt{geo, groom > all non-geo})
+        are overlaid over the movie's primary $t$-contrast (blue) that compares
+        cuts to a new setting with cuts to a familiar perspective
+        (\texttt{vse\_new > vpe\_old})
+   \citep{sengupta2016extension}.}
+    \label{fig:group-slices}
+\end{figure*}
+
+\begin{table*}[h!]
+\caption{Significant clusters (z-threshold Z>3.4; p<.05 cluster-corrected)
+    of the primary $t$-contrast for the audio-visual movie comparing cuts to a
+    setting that was not depicted before to a recurring setting
+    (\texttt{vse\_new > vpe\_old}).
+    Clusters sorted by voxel size.
+    The first brain structure given contains the voxel with the maximum Z-Value,
+    followed by brain structures from posterior to anterior, and partially
+    covered areas (l. = left; r. = right; c. = cortex; g. = gyrus).}
+\label{tab:res-av-group1}
+\begin{tabular}{rrrrrrrrrp{3cm}}
+\toprule
+& & & \multicolumn{3}{r}{max location (MNI)} & \multicolumn{3}{r}{center of gravity (MNI)} &
+\\ \cmidrule{4-6} \cmidrule{7-9}
+voxels & $p_{corr.}$ & Z-max & x & y & z  & x & y & z & structure \\
+\midrule
+3003 & 0 & 5.31 & 22.5 & -45.5 & -12 & 4.53 & -63.3 & -3.72 & r. lingual g.; r. cuneal c., intracalcarine c., bilaterally occipital fusiform g., temporal fusiform c., posterior parahippocampal c.  \\
+154 & 6.56E-07 & 4.46 & -35 & -83 & 28 & -32.8 & -86.2 & 21.4 & l. superior lateral occipital c. \\
+121 & 7.69E-06 & 4.65 & 25 & -80.5 & 25.5 & 23.7 & -83.8 & 25.4 & r. superior lateral occipital cortex \\
+\bottomrule
+\end{tabular}
+\end{table*}
+
 % table group results primary AD contrast
-\begin{table*}[t]
+\begin{table*}[h!]
     \caption{Significant clusters (z-threshold Z>3.4; p<.05 cluster-corrected)
@@
 
-% figure group results primary AD & AV contrasts
-\begin{figure*} \centering
-    \includegraphics[width=\linewidth]{figures/group-slices}
-    \caption{Mixed-effects group-level (N=14) GLM results. Significant clusters
-        (Z>3.4, p<.05 cluster-corrected) are overlaid on the MNI152 T1-weighted
-        head template (gray).
-        Light gray: The audio-description's field-of-view
-        (cf. \citep{hanke2014audiomovie}).
-        Black: outline of overlapping individual PPA ROIs.
-        The results of audio-description's primary $t$-contrast (blue) that
-        compares geometry-related nouns to non geometry-related nouns spoken by
-        the audio-description's narrator (\texttt{geo, groom > all non-geo})
-        are overlaid over the movie's primary $t$-contrast (blue) that compares
-        cuts to a new setting with cuts to a familiar perspective
-        (\texttt{vse\_new > vpe\_old})
-   \citep{sengupta2016extension}.}
-    \label{fig:group-slices}
-\end{figure*}
-
-\subsubsection{AD: robustness of PPA across contrasts}
-
-\todo[inline]{tables of significant clusters all contrasts = overkill!? Link to NeuoVault is added; sign. clusters of all contrasts are listed in the comments}
-
-% all eight AD PPA contrasts
-In order to test the robustness of our findings, we created overall eight
-$t$-contrasts for the AD stimulus (see Table \ref{tab:ao-contrasts}).
-% results
-All contrasts except contrast 7 (\texttt{se\_new}, \texttt{se\_old} >
-non-spatial categories) and contrast 8 (\texttt{se\_new} > non-spatial
-categories) yielded significant bilateral clusters in anterior regions of the
-group PPA overlap (see Figure \ref{fig:stability-slices}).
-% statement/answer
-Results suggest that our findings do not depend on one specific contrasts but
-are robust across differently designed contrasts.
-% question
-\todo[inline]{concluding statement often feels like interpretation/discussion}
-%
-\todo[inline]{Discussion: discuss that contrasts make ``less and less'' sense}
-
-\todo[inline]{figure caption: mention / explain other clusters}
-
-% figure group results of robustness across all AD & AV contrasts
-\begin{figure*} \centering
-    \includegraphics[width=\linewidth]{figures/stability-slices}
-    \caption{Overlap of significant clusters (Z>3.4; p<.05, cluster corrected)
-        The audio-description's contrasts 1-8 (blue; \ref{tab:ao-contrasts})
-        are overlaid over the audio-visual movie's contrasts 1-5 (red;
-        \ref{tab:av-contrasts}) that were used to [isolate] the PPA
-        Cluster are overlaid on top of the MNI152 T1-weighted head template
-        (gray).
-        Black: outline of overlapping individual PPA ROIs.
-        Light gray: The audio-description's field-of-view (cf.
-        \citep{hanke2014audiomovie}).}
-    \label{fig:stability-slices}
-    \end{figure*}
-
-\paragraph{AD: other significant clusters across contrasts}
-% precuneus = retrosplenial cortex ?
-\todo[inline]{significant clusters in other regions than PPA could or should (?)
-also be reported? Following is a short list; depends on the discussion I guess;
-anyhow: clusters are not ``random'' but make sense which speaks for the use of
-naturalistic stimuli}
-
-\begin{itemize}
-\item RSC (and ventral precuneus): 7 contrasts (all bilateral)
-\item lateral occipital cortex: 6 contrasts (4 bilateral, 2 unilateral =
-    transverse occipital sulcus / occipiatal place area?; AD \& AV clusters
-    overlap but AD clusters are more lateral, AV cluster are more medial \&
-    caudal)
-\item right superior temporal gyrus (auditory cortices): 4 contrasts
-\item (smallish) prefrontal clusters: 3 contrasts (non-overlapping)
-\end{itemize}
-
-\subsubsection{AV: PPA in primary contrast}
-% AV intro
-As conceptual/cross-modal control of the group average results, we also analyzed
-data from the audio-visual movie by contrasting different kinds of movie cuts
-independent(ly) from the frames' visual content following the cut.
-% AV primary contrast
-The movie's primary $t$-contrast that compared cuts to a setting that was not
-depicted before to a recurring setting (\texttt{vse\_new > vpe\_old}) yielded
-three significant clusters (see Table \ref{tab:res-av-group1}, Figure
-\ref{fig:group-slices}).
-% PPA (others the clusters extend into).
-One cluster spans across the midline and comprises, parts of the intracalcarine
-and cuneal cortex, the lingual gyrus and retrosplenial cortex, the occipital and
-temporal fusiform gyrus and the parahippocampal cortex (reported from posterior
-to anterior) in both hemispheres.
-% LOC
-Two additional homologous clusters are located in the superior lateral occipital
-cortex (left bigger than right).
-
-\begin{table*}[t]
-\caption{Significant clusters (z-threshold Z>3.4; p<.05 cluster-corrected)
-    of the primary $t$-contrast for the audio-visual movie comparing cuts to a
-    setting that was not depicted before to a recurring setting
-    (\texttt{vse\_new > vpe\_old}).
-    Clusters sorted by voxel size.
-    The first brain structure given contains the voxel with the maximum Z-Value,
-    followed by brain structures from posterior to anterior, and partially
-    covered areas (l. = left; r. = right; c. = cortex; g. = gyrus).}
-\label{tab:res-av-group1}
-\begin{tabular}{rrrrrrrrrp{3cm}}
-\toprule
-& & & \multicolumn{3}{r}{max location (MNI)} & \multicolumn{3}{r}{center of gravity (MNI)} &
-\\ \cmidrule{4-6} \cmidrule{7-9}
-voxels & $p_{corr.}$ & Z-max & x & y & z  & x & y & z & structure \\
-\midrule
-3003 & 0 & 5.31 & 22.5 & -45.5 & -12 & 4.53 & -63.3 & -3.72 & r. lingual g.; r. cuneal c., intracalcarine c., bilaterally occipital fusiform g., temporal fusiform c., posterior parahippocampal c.  \\
-154 & 6.56E-07 & 4.46 & -35 & -83 & 28 & -32.8 & -86.2 & 21.4 & l. superior lateral occipital c. \\
-121 & 7.69E-06 & 4.65 & 25 & -80.5 & 25.5 & 23.7 & -83.8 & 25.4 & r. superior lateral occipital cortex \\
-\bottomrule
-\end{tabular}
-\end{table*}
-
-\subsubsection{AV: robustness of PPA across contrasts}
-
-% all eight AV PPA contrasts
-Here again in order to test the robustness of our findings, we created four
-additional $t$-contrasts for the AV stimulus (see Table \ref{tab:av-contrasts}).
-%% results: PPA
-All of the overall five AV contrasts yielded significant bilateral clusters that
-overlap with the PPA group overlap (see Figure \ref{fig:stability-slices}).
-[biggest overlap in posterior part of PPA group overlap  = temporal occipital
-fusiform cortex] .
-% concluding statement
-Here again, we can show that results can in principle be accomplished by varying
-the design of the contrasts.
-% question
-\todo[inline]{concluding statement = interpretation/discussion?}
-
-\paragraph{AV: other significant clusters across contrasts}
-
-\begin{itemize}
-    \item RSC: 3 contrasts (all bilat; vse\_new > vpe\_old; vse\_new >
-        vse\_old, vpe\_old; vse\_new, vpe\_new > vpe\_old)
-    \item lateral occipital cortex: 4 contrasts (all except vse\_new > vse\_old; all bilateral)
-\end{itemize}
-
-\subsubsection{AD \& AV: (negative) control contrasts}
-
-\todo[inline]{for completeness, contrasts are mentioned in the method section.
-Shall results be reported (and later discussed)?}
-
-% AD stimulus
-AD stimulus (using annotation of movie cuts) all null results except: contrast 9
-(vse\_new > pe\_old): right RSC.
-% correlation of these nouns with cuts
-Compare Figure \ref{fig:reg-corr}: nouns that cue change to a new setting are
-correlated  with cuts to a new setting (vse\_new; r$\approx$0.3; second highest
-correlation of a verbal cue category with a cut category.
-
-% AV stimulus
-AV stimulus. All contrasts using ``no cut condition'' > XY yield null results.
-The contrast that uses the narrator's nouns but in the AV stimulus (se\_new >
-se\_old): right PPA, bilateral sup. lat. occ. cortex; LOC (l/r), right superior
-parietal lobe. Compare Figure \ref{fig:reg-corr}: nouns that cue change to a new
-setting are correlated  with cuts to a new setting (vse\_new; r$\approx$0.3;
-second highest correlation of a verbal cue category with a cut category; AND:
-nouns that cue change to a familiar setting are somewhat correlated with cuts to
-a familiar setting (se\_old; r$\approx$0.4; highest correlation of a verbal
-category with a cut category).
-
-\subsection{individual results}
+\subsubsection{individuals}
 
 \todo[inline]{other reasons than localization performance?}
+
+\todo[inline]{make focus on AD clearer}
 
@@
 
-\begin{figure*} \centering
+\begin{figure*}[h!]
+\centering
     \includegraphics[width=\linewidth]{figures/subs-thresh-ppa}
@@
 
-\begin{figure*} \centering
+\begin{figure*}[h!]
+\centering
     \includegraphics[scale=0.28]{figures/subjs_bland-altman.png}
@@
         and individual PPA(s) (red).}
-    \label{fig:bland-altman} \end{figure*}
+    \label{fig:bland-altman}
+\end{figure*}
+
+\subsection{Robustness of PPA across contrasts}
+
+\subsubsection{AV}
+
+% all eight AV PPA contrasts
+Here again in order to test the robustness of our findings, we created four
+additional $t$-contrasts for the AV stimulus (see Table \ref{tab:av-contrasts}).
+%% results: PPA
+All of the overall five AV contrasts yielded significant bilateral clusters that
+overlap with the PPA group overlap (see Figure \ref{fig:stability-slices}).
+[biggest overlap in posterior part of PPA group overlap  = temporal occipital
+fusiform cortex] .
+% concluding statement
+Here again, we can show that results can in principle be accomplished by varying
+the design of the contrasts.
+% question
+\todo[inline]{concluding statement = interpretation/discussion?}
+
+\subsubsection{AD}
+
+\todo[inline]{tables of significant clusters all contrasts = overkill!? Link to NeuoVault is added; sign. clusters of all contrasts are listed in the comments}
+
+% all eight AD PPA contrasts
+In order to test the robustness of our findings, we created overall eight
+$t$-contrasts for the AD stimulus (see Table \ref{tab:ao-contrasts}).
+% results
+All contrasts except contrast 7 (\texttt{se\_new}, \texttt{se\_old} >
+non-spatial categories) and contrast 8 (\texttt{se\_new} > non-spatial
+categories) yielded significant bilateral clusters in anterior regions of the
+group PPA overlap (see Figure \ref{fig:stability-slices}).
+% statement/answer
+Results suggest that our findings do not depend on one specific contrasts but
+are robust across differently designed contrasts.
+% question
+\todo[inline]{concluding statement often feels like interpretation/discussion}
+%
+\todo[inline]{Discussion: discuss that contrasts make ``less and less'' sense}
+
+\todo[inline]{figure caption: mention / explain other clusters}
+
+% figure group results of robustness across all AD & AV contrasts
+\begin{figure*}[h!]
+\centering
+    \includegraphics[width=\linewidth]{figures/stability-slices}
+    \caption{Overlap of significant clusters (Z>3.4; p<.05, cluster corrected)
+        The audio-description's contrasts 1-8 (blue; \ref{tab:ao-contrasts})
+        are overlaid over the audio-visual movie's contrasts 1-5 (red;
+        \ref{tab:av-contrasts}) that were used to [isolate] the PPA
+        Cluster are overlaid on top of the MNI152 T1-weighted head template
+        (gray).
+        Black: outline of overlapping individual PPA ROIs.
+        Light gray: The audio-description's field-of-view (cf.
+        \citep{hanke2014audiomovie}).}
+    \label{fig:stability-slices}
+\end{figure*}
+
+\subsection{Non-PPA clusters across contrasts}
+
+% precuneus = retrosplenial cortex ?
+\todo[inline]{significant clusters in other regions than PPA could or should (?)
+also be reported? Following is a short list; depends on the discussion I guess;
+anyhow: clusters are not ``random'' but make sense which speaks for the use of
+naturalistic stimuli}
+
+\subsubsection{AV}
+
+\begin{itemize}
+    \item RSC: 3 contrasts (all bilat; vse\_new > vpe\_old; vse\_new >
+        vse\_old, vpe\_old; vse\_new, vpe\_new > vpe\_old)
+    \item lateral occipital cortex: 4 contrasts (all except vse\_new > vse\_old; all bilateral)
+\end{itemize}
+
+\subsubsection{AD}
+
+\begin{itemize}
+\item RSC (and ventral precuneus): 7 contrasts (all bilateral)
+\item lateral occipital cortex: 6 contrasts (4 bilateral, 2 unilateral =
+    transverse occipital sulcus / occipiatal place area?; AD \& AV clusters
+    overlap but AD clusters are more lateral, AV cluster are more medial \&
+    caudal)
+\item right superior temporal gyrus (auditory cortices): 4 contrasts
+\item (smallish) prefrontal clusters: 3 contrasts (non-overlapping)
+\end{itemize}
+
+\subsection{control contrasts (AV \& AD)}
+
+\todo[inline]{for completeness, contrasts are mentioned in the method section.
+Shall results be reported (and later discussed)?}
+
+% AD stimulus
+AD stimulus (using annotation of movie cuts) all null results except: contrast 9
+(vse\_new > pe\_old): right RSC.
+% correlation of these nouns with cuts
+Compare Figure \ref{fig:reg-corr}: nouns that cue change to a new setting are
+correlated  with cuts to a new setting (vse\_new; r$\approx$0.3; second highest
+correlation of a verbal cue category with a cut category.
+
+% AV stimulus
+AV stimulus. All contrasts using ``no cut condition'' > XY yield null results.
+The contrast that uses the narrator's nouns but in the AV stimulus (se\_new >
+se\_old): right PPA, bilateral sup. lat. occ. cortex; LOC (l/r), right superior
+parietal lobe. Compare Figure \ref{fig:reg-corr}: nouns that cue change to a new
+setting are correlated  with cuts to a new setting (vse\_new; r$\approx$0.3;
+second highest correlation of a verbal cue category with a cut category; AND:
+nouns that cue change to a familiar setting are somewhat correlated with cuts to
+a familiar setting (se\_old; r$\approx$0.4; highest correlation of a verbal
+category with a cut category).
 

### 2021-01-18 paper/main.tex
adjust text of group (& individual) results

@@
 place} to the PPA as functionally defined by a visual localizer experiment using
-pictures done with the same subjects.  \citep{sengupta2016extension}.
+pictures done with the same subjects \citep{sengupta2016extension}.
+
+We hypothesize[d] that an exclusively auditory stimulus can/could localize
+``visual area'' in individual subjects and thus possibly substitute a
+block-design experiment using pictures.
 % hypo b
-Focussing on the [``cleaner operationalization'' of the] audio-description, we
-further hypothesize[d] that an exclusively auditory stimulus can/could
-substitute a block-design experiment using pictures to localize a ``visual
-area'' in individual subjects.\todo{needs short statement on why one would even want that}
+Further, we hypothesize[d] that an exclusively auditory stimulus can/could
+localize the PPA in individual subjects, and thus substitute a visual experiment
+be which would be more practicable to assess brain functions in visually
+impaired persons.\todo{phrasing}
 % results: group
@@
 embedded in two naturalistic stimuli correlate with increased hemodynamic
-activity in the PPA that was define by using a visual localizer experiment
+activity in the PPA that was defined using a visual localizer experiment
 within the same subjects \citep{sengupta2016extension}.
@@
 We annotated a \unit[2]{h} movie and its temporally aligned audio-description to
-create GLM contrasts similar to previous studies that used conceptualized
-stimuli.
+create GLM contrasts similar to previous studies that used static pictures.
 % group level
@@
 % individual level
-On the level single subjects, we also assess localization performance of a
-``visual area'' using the auditory stimulus.\todo{``localization'' performance}
+On the level single subjects, we also assess the performance of a naturalistic
+auditory stimulus as a substitute for a visual paradigm to localize the
+PPA.\todo{``localize''}
 % NeuroVault
@@
 % intro
-First on a group average level, we tested if results of a whole-brain analysis
-based on the audio-description's annotation would lead to increased hemodynamic
-activity in the PPA.
+First, we tested if results of a whole-brain analysis based stimulus annotations
+would lead to increased hemodynamic activity in the PPA.
 
@@
 % AV intro
-As conceptual/cross-modal control of the group average results, we also analyzed
-data from the audio-visual movie by contrasting different kinds of movie cuts
-independent(ly) from the frames' visual content following the cut.
+First, we analyzed data from the audio-visual movie offering visual but
+ecologically more valid stimulation.
 % AV primary contrast
@@
 
-% AD
+% AD intro
+Second, we analyzed data from the movie's audio-description offering exclusively
+auditory stimulation.
+% AD primary contrast
 The primary $t$-contrast for the audio-description (\texttt{geo, groom} >
@@
 
-\todo[inline]{other reasons than localization performance?}
-
-\todo[inline]{make focus on AD clearer}
-
-% why individual results in the first place.
-We also investigated [localization performance] of both naturalistic paradigms
-on the level of individual subjects.\todo{depends on ``naturalistic stimulus for
-localization''}
-% results in both subject and group space
-Time series of all subjects were analyzed both in group space and subject space.
- space
-For better comparison of results across participants, we here report results
-($z$-maps; Z>3.4, p<.05 cluster-corrected) of the analyses that was performed in
-group space.
-% ref to figure
-Figure \ref{fig:subs-thresh-ppa} depicts thresholded $z$-maps of the primary AD
-and AV $t$-contrast, and the outline of the individual PPAs
-\citep{sengupta2016extension} overlayed on the MNI152 template (transversal
-slice z=-11 for all subjects was chosen as it depicts voxels of significant
-clusters in almost all subjects).
-% individual z-maps -> dataset
-Results of the analyses that were performed in each subject's subject-space
-(unthresholded $z$-maps and thresholded $z$-maps with Z>2.3, p<.05 cluster
-corrected) can be found at
-\href{https://neurovault.org/collections/KADGMGVZ/}{NeuroVault}.\todo{still
-private collection} .
-% report here in group
+\todo[inline]{imo no need to mention it here but mention in discussion that
+results are not driven by outliers when discussing ``localization'' performance}
 
@@
 
-% PPA ROI (Sengupta et al., 2016)
+% intro
+Third, we investigated result from both naturalistic paradigms on the level of
+individual subjects.
+%
+Focussing on the AD stimulus, wee hypothesize[d] that an exclusively auditory
+stimulus can/could localize ``visual area'' in individual subjects and thus
+possibly substitute a paradigm using blocks of pictures.
+% AD results in
+Time series of all subjects were analyzed both in group space and subject space.
+For better comparions of subjects, we here report results from the analyses
+performed in group space ($z$-maps; Z>3.4, p<.05 cluster-corrected).
+% ref to figure
+Figure \ref{fig:subs-thresh-ppa} depicts thresholded $z$-maps of the primary AD
+and AV $t$-contrast, and the outline of overlapped, individual PPAs
+\citep{sengupta2016extension}.
+% MNI space
+The $z$-maps and PPA outline are overlayed on the co-registered MNI152 template.
+% one slice to show them all
+Transversal slice of z=-11 was chosen as it depicts [at least some] voxels of
+significant clusters in almost all subjects.
+% individual z-maps -> dataset
+Results of the analyses that were performed in each subject's subject-space
+(unthresholded $z$-maps and thresholded $z$-maps, Z>2.3, p<.05 cluster
+corrected) can be found at
+\href{https://neurovault.org/collections/KADGMGVZ/}{NeuroVault}.\todo{still
+private collection} .
+% report here in group
+
+\todo[inline]{following is probably the part that Simon considered as en
+passant}
+
+\todo[inline]{if we here report procedure of Sengupta as detailed as
+it is now, we probably need to explain the differences between strict, relaxed,
+simple in more detail in the method section and not just reference to Sengupta}
+
+% Sengupta et al., 2016
 The visual localizer experiment \citep{sengupta2016extension} yielded bilateral
-clusters in 12 of 14 subjects and a unilateral right clusters in two subjects
-(sub-04, sub-20) that were defined as the PPA.\todo{this is probably the part
-that Simon considered as/too ``en passant''}
-% procedure in Sengupta
-Individual PPAs were assessed by visually inspecting unthresholded $z$-maps of
-three different contrasts, and setting a subjectively best fitting $z$-threshold
-to define an area in the parahippocampal gyrus [and adjacent regions of the
-fusiform gyrus and anterior lingual gyrus].
-% AD
-In the current analysis of the AD stimulus, we use the same AD (and AV) contrast
+[parahippocampal] clusters in 12 of 14 subjects and a unilateral right clusters
+in two subjects (sub-04, sub-20).
+% Sengupta: 1 of 3
+Individual PPAs were assessed by visually inspecting thresholded $z$-maps
+(Z>1.64, p<.05 cluster corrected) of three different $t$-contrasts
+(\textit{strict}, \textit{relaxed}, and \textit{simple} stimulus set, cf.
+\citep{sengupta2016extension}).
+% Sengupta: procedure a)
+Starting with the most conservative contrast (strict set) and a threshold of t =
+2.5, we looked for clusters with at least 20 voxels (using AFNI).
+%
+We titrated [?] the threshold in the range of [2, 3] until we found an isolated
+cluster for the PPA.
+% Sengupta: procedure b)
+If a cluster was not found or not isolated, we used a contrast from the relaxed
+set, or finally the simple set, and repeated the process until we found a
+cluster that matched the expected anatomical location based on literature
+\citep{epstein1998ppa}.
+
+% current analyses: one contrast to localize them all
+In the current analyses, we use same contrast of each naturalistic stimulus for
+all subjects
+
 for all subjects. We find statistically significant bilateral clusters in nine
@@
 % concluding statement
-\todo[inline]{concluding statement that does not sound like
-interpretation/discussion?}
 

### 2021-01-18 paper/main.tex
adjust text of individual results

@@
 %
-Focussing on the AD stimulus, wee hypothesize[d] that an exclusively auditory
+Focussing on the AD stimulus, we hypothesize[d] that an exclusively auditory
 stimulus can/could localize ``visual area'' in individual subjects and thus
-possibly substitute a paradigm using blocks of pictures.
-% AD results in
-Time series of all subjects were analyzed both in group space and subject space.
-For better comparions of subjects, we here report results from the analyses
-performed in group space ($z$-maps; Z>3.4, p<.05 cluster-corrected).
-% ref to figure
-Figure \ref{fig:subs-thresh-ppa} depicts thresholded $z$-maps of the primary AD
-and AV $t$-contrast, and the outline of overlapped, individual PPAs
-\citep{sengupta2016extension}.
-% MNI space
-The $z$-maps and PPA outline are overlayed on the co-registered MNI152 template.
-% one slice to show them all
-Transversal slice of z=-11 was chosen as it depicts [at least some] voxels of
-significant clusters in almost all subjects.
-% individual z-maps -> dataset
-Results of the analyses that were performed in each subject's subject-space
-(unthresholded $z$-maps and thresholded $z$-maps, Z>2.3, p<.05 cluster
-corrected) can be found at
-\href{https://neurovault.org/collections/KADGMGVZ/}{NeuroVault}.\todo{still
-private collection} .
-% report here in group
+possibly substitute a visual paradigm using blocks of pictures.
 
@@
 The visual localizer experiment \citep{sengupta2016extension} yielded bilateral
-[parahippocampal] clusters in 12 of 14 subjects and a unilateral right clusters
+[parahippocampal] clusters in 12 of 14 subjects and an unilateral right clusters
 in two subjects (sub-04, sub-20).
@@
 
-% current analyses: one contrast to localize them all
-In the current analyses, we use same contrast of each naturalistic stimulus for
-all subjects
-
-for all subjects. We find statistically significant bilateral clusters in nine
-subjects, and one cluster in the left hemisphere of sub-09 that are within or
-overlapping with the individual PPA.
+% naturalisti stimuli: intro
+In the current study, time series of all subjects were analyzed both in subject
+space and group space.
+% subject space -> NeuroVault
+Results of the analyses that were performed in each subject's [subject-]space
+(unthresholded $z$-maps and thresholded $z$-maps, Z>2.3, p<.05 cluster
+corrected) can be found at
+\href{https://neurovault.org/collections/KADGMGVZ/}{NeuroVault}. \todo{still
+private collection}
+% here report in group space
+For better comparions of subjects, we here report results from the analyses
+performed in group space. % ($z$-maps; Z>3.4, p<.05 cluster-corrected).
+% one contrast to localize them all; "...and Z>3.4 for all"
+Contrary to the procedure in \citep{sengupta2016extension}, we used the same
+contrast of each naturalistic stimulus and the same threshold (Z>3.4, p<.05
+cluster corrected) for all subjects.
+
+% AV
+Results of the primary AV contrast yielded statistically significant bilateral
+clusters in five subjects, unilateral right clusters in six subjects (of
+which one subjects yielded a unilateral cluster in the visual localizer), and a
+unilateral left cluster in one subject.
+% difference to dedicated localizer
+We find homologous clusters in sub-20, whereas the dedicated visual localizer
+yielded only one cluster in the right hemisphere.
+
+% report here in group
+Results of the primary AD contrast yielded stastically significant bilateral
+clusters in nine subjects, and one cluster in the left hemisphere of sub-09,
+that are within or overlapping with the individual PPA.
 % subj-04
@@
 (and AV stimulus) yielded only one cluster in the right hemisphere.
-% AV
-Results of the AV contrast yield homologous clusters in five subjects,
-unilateral right clusters in six subjects (of which one subjects yielded a
-unilateral cluster in the visual localizer), and a unilateral left cluster in
-one subject.
-% difference to dedicated localizer
-We find homologous clusters in sub-20, whereas the dedicated visual localizer
-yielded only one cluster in the right hemisphere.
-% concluding statement
+% ref to figure
+Figure \ref{fig:subs-thresh-ppa} depicts thresholded $z$-maps of the primary AV
+and AD $t$-contrast, and the outline of overlapped, individual PPAs
+\citep{sengupta2016extension}.
+% MNI space
+The $z$-maps and PPA outline are overlayed on the co-registered MNI152 template.
+% one slice to show them all
+Transversal slice of z=-11 was chosen as it depicts [at least some] voxels of
+significant clusters in almost all subjects.
 
@@
 
-\subsection{Robustness of PPA across contrasts}
-
-\subsubsection{AV}
-
-% all eight AV PPA contrasts
-Here again in order to test the robustness of our findings, we created four
-additional $t$-contrasts for the AV stimulus (see Table \ref{tab:av-contrasts}).
+\subsection{Robustness of PPA across contrasts: AV \& AD}
+
+\todo[inline]{tables of significant clusters all contrasts = overkill!? Link to
+NeuoVault is added; sign. clusters of all contrasts are listed in the comments}
+
+% AV
+In order to test the robustness of our findings, we created four additional
+$t$-contrasts for the AV stimulus (see Table \ref{tab:av-contrasts}) to be
+investigated on a group level.
 %% results: PPA
@@
 fusiform cortex] .
-% concluding statement
-Here again, we can show that results can in principle be accomplished by varying
-the design of the contrasts.
-% question
-\todo[inline]{concluding statement = interpretation/discussion?}
-
-\subsubsection{AD}
-
-\todo[inline]{tables of significant clusters all contrasts = overkill!? Link to NeuoVault is added; sign. clusters of all contrasts are listed in the comments}
-
-% all eight AD PPA contrasts
-In order to test the robustness of our findings, we created overall eight
-$t$-contrasts for the AD stimulus (see Table \ref{tab:ao-contrasts}).
+% AD
+For the AD stimulus, we created overall eight $t$-contrasts (see Table
+\ref{tab:ao-contrasts}).
 % results
@@
 Results suggest that our findings do not depend on one specific contrasts but
-are robust across differently designed contrasts.
-% question
-\todo[inline]{concluding statement often feels like interpretation/discussion}
+are robust across differently designed contrasts.\todo{concluding statement
+often feels like interpretation}
 %
-\todo[inline]{Discussion: discuss that contrasts make ``less and less'' sense}
-
 \todo[inline]{figure caption: mention / explain other clusters}
@@
 % precuneus = retrosplenial cortex ?
-\todo[inline]{significant clusters in other regions than PPA could or should (?)
-also be reported? Following is a short list; depends on the discussion I guess;
-anyhow: clusters are not ``random'' but make sense which speaks for the use of
+\todo[inline]{Following is a list; report depends on the discussion I guess;
+anyway: clusters are not ``random'' but make sense which speaks for the use of
 naturalistic stimuli}

### 2021-01-18 paper/main.tex
rearrange blocks of text in discussion

@@
     \item location of tables \& figures is pretty confusing at the moment
+    \item length of report of other reliably significant cluster across
+        contrasts and report of control contrasts depends on if/how long they
+        should be discussed
 \end{itemize}
@@
 
-\todo[inline]{for completeness, contrasts are mentioned in the method section.
-Shall results be reported (and later discussed)?}
+\todo[inline]{contrasts are mentioned in the method section; shall results be
+reported (and later discussed)?}
 
@@
 
-\subsection{group level: AD \& AV (PPA only)}
+\subsection{PPA; AV \& AD; group \& individuals}
+
+\subsubsection{AV: group}
+% AV stimulus
+Group results of the AV stimulus' primary contrast yielded bilateral clusters
+that span the group overlap of individual PPA ROIs from anterior to posterior.
+% difference in location/size to AD and VIS
+Clusters also expand into more posterior regions (occipital fusiform gyrus,
+lingual gyrus, and intracalcarine cortex).\todo{which of these regions (do not
+overlap) with group ROI?}
+% confound of higher perception
+This larger extension, especially into the primary visual cortex, can be
+attributed to the fact that we averaged the content of individual frames after a
+cut and did not control for confounding features like depicted faces or
+objects,and low-level visual features.
+% cross-modal control purpose?
+\todo[inline]{better frame that it is conceptual/cross-modal control; but what
+do the results tell us? yes, it ``kinda works'' but \dots?}
+\todo[inline]{concluding statement regarding AV vs AD and cross-modality of
+results?}
 
@@
 complicated, yet not sophisticated}
+
+\subsubsection{AD: group}
 
@@
 
-% AV stimulus
-Group results of the AV stimulus' primary contrast yielded bilateral clusters
-that span the group overlap of individual PPA ROIs from anterior to posterior.
-% difference in location/size to AD and VIS
-Clusters also expand into more posterior regions (occipital fusiform gyrus,
-lingual gyrus, and intracalcarine cortex).\todo{which of these regions (do not
-overlap) with group ROI?}
-% confound of higher perception
-This larger extension, especially into the primary visual cortex, can be
-attributed to the fact that we averaged the content of individual frames after a
-cut and did not control for confounding features like depicted faces or
-objects,and low-level visual features.
-% cross-modal control purpose?
-\todo[inline]{better frame that it is conceptual/cross-modal control; but what
-do the results tell us? yes, it ``kinda works'' but \dots?}
-\todo[inline]{concluding statement regarding AV vs AD and cross-modality of
-results?}
-
-\subsection{robustness of contrasts}
+\todo[inline]{individual results should be incorporated into above section;
+depends on long discussion of individual results will be}
+
+\subsubsection{AV stimulus}
+
+\todo[inline]{was not aim of study; results of primary AV contrasts are in plots
+    if individual; Bland-Altman-Plots focus on primary AD contrast alone}
+
+\subsubsection{AD: individuals}
+
+\todo[inline]{how to discuss Bland-Altman-Plots???}
+
+\todo[inline]{dunno if this is meaningful: z-scores in the anterior part of
+    PPA are higher in AD contrasts than in contrast of localizer}
+
+% intro
+To test if an auditory narrative could substitute a visual localizer experiment,
+we also examined the results of the primary AD contrast on the level of
+individual subjects.
+% results of dedicated localizer
+The visual localizer \citep{sengupta2016extension} revealed bilateral ROIs in 12
+of 14 subjects and a unilateral right ROI in two subjects (sub-04, sub-20).
+% in the current study
+The audio-description's primary contrast yielded significant bilateral clusters
+in 9 of 14 subjects (of which sub-04 shows just right-lateralized PPA ROI) and a
+unilateral significant cluster in one subject.
+%
+Whereas \citep{sengupta2016extension} chose the subjectively ``best fitting
+$z$-threshold in a subject's unthresholded $z$-map by visual judgment, we used a
+``one threshold fits all approach`` (Z>3.4, p<.05 cluster-corrected).
+% group vs individual
+Results on an individual level reveal that significant cluster are located in
+the anterior part of individual PPA ROIs. Thus, the pattern that was revealed on
+a group level is not just a by-product of the averaging process but can reliably
+be found in individual study participants.
+% conclusion
+Lastly, our exploratory analyses suggest that a naturalistic auditory stimulus
+is in principle suitable to localize (the anterior part) of a higher-level
+visual area in the majority of subjects.
+% chose the best contrast in the future
+Similarly to \citep{sengupta2016extension} that chose the ``best'' of three
+alternative contrasts (strict, relaxed, or simple contrast), future studies that
+aim for individual diagnostics / ROI localization should also test more than one
+contrast to gain the ``best'' individual ROIs.\todo{``best'' sounds pretty
+shitty}
+
+\todo[inline]{discussion of individual differences? what do the results
+suggest? Differences in alertness, attention to spatial information,
+predisposition? ``capability'' to process auditory spatial information?}
+
+\todo[inline]{individual ``preference'' to pay attention to
+spatial infos (which contradicts statement above that attention is not a
+prerequisite)}
+
+\subsection{Robust (results) across contrasts}
 
@@
 processed in the PPA.
+
+\subsubsection{PPA}
 % PPA AD
@@
 and test for correlations among variables.
-
-\subsection{consistencies across contrasts}
 
@@
 
-\subsection{individual analyses}
-
-\todo[inline]{how to discuss Bland-Altman-Plots???}
-
-\todo[inline]{dunno if this is meaningful: z-scores in the anterior part of
-    PPA are higher in AD contrasts than in contrast of localizer}
-
-% intro
-To test if an auditory narrative could substitute a visual localizer experiment,
-we also examined the results of the primary AD contrast on the level of
-individual subjects.
-% results of dedicated localizer
-The visual localizer \citep{sengupta2016extension} revealed bilateral ROIs in 12
-of 14 subjects and a unilateral right ROI in two subjects (sub-04, sub-20).
-% in the current study
-The audio-description's primary contrast yielded significant bilateral clusters
-in 9 of 14 subjects (of which sub-04 shows just right-lateralized PPA ROI) and a
-unilateral significant cluster in one subject.
-%
-Whereas \citep{sengupta2016extension} chose the subjectively ``best fitting
-$z$-threshold in a subject's unthresholded $z$-map by visual judgment, we used a
-``one threshold fits all approach`` (Z>3.4, p<.05 cluster-corrected).
-% group vs individual
-Results on an individual level reveal that significant cluster are located in
-the anterior part of individual PPA ROIs. Thus, the pattern that was revealed on
-a group level is not just a by-product of the averaging process but can reliably
-be found in individual study participants.
-% conclusion
-Lastly, our exploratory analyses suggest that a naturalistic auditory stimulus
-is in principle suitable to localize (the anterior part) of a higher-level
-visual area in the majority of subjects.
-% chose the best contrast in the future
-Similarly to \citep{sengupta2016extension} that chose the ``best'' of three
-alternative contrasts (strict, relaxed, or simple contrast), future studies that
-aim for individual diagnostics / ROI localization should also test more than one
-contrast to gain the ``best'' individual ROIs.\todo{``best'' sounds pretty
-shitty}
-
-\todo[inline]{discussion of individual differences? what do the results
-suggest? Differences in alertness, attention to spatial information,
-predisposition? ``capability'' to process auditory spatial information?}
-
-\todo[inline]{individual ``preference'' to pay attention to
-spatial infos (which contradicts statement above that attention is not a
-prerequisite)}
+\subsection{shortcomings}
+
+\todo[inline]{SE: Würde nicht so sehr auf Shortcomings eingehen}
+
+\todo[inline]{different level of alertness during paradigms}
 
@@
 
-\todo[inline]{was not aim of study; results of primary AV contrasts are in plots
-    if individual; Bland-Altman-Plots focus on primary AD contrast alone}
-
-\subsection{shortcomings}
-
-\todo[inline]{SE: Würde nicht so sehr auf Shortcomings eingehen}
-
-\todo[inline]{different level of alertness during paradigms}
+\todo[inline]{AV: field size decreases later in the movie; this is a confound
+based on cinematography => the stimulus changes over time; AV analysis exploits
+confound structure}
+
+\todo[inline]{imo opening the pandora's box of the AV shortcomings especially at
+the end of the paper should be kept to a minimum of text}
+
+% focus of study
+The focus of the current study was to investigate if significantly increased
+hemodynamic activity in the PPA correlates with spatial information (compared to
+``non-spatial'' information) during a naturalistic auditory stimulus.
+% shortcomings
+Results of the AV stimulus that we ran as a conceptual control are tempered by
+using different kind of movie cuts regardless of the visual content of the movie
+frame after the respective cuts.
+% which leads to the ``blurred'' results
+Hence we got visual confounds / clusters extending in to early visual areas.
+% further studies
+Since the capability to isolate clusters or networks correlating with specific
+perceptual (or cognitive) processes is influenced by the amount of annotated
+stimulus features further studies focusing on visual perception should annotate
+and model visual features of naturalistic stimuli more rigorously.
+% solution
+Future studies that aim to use a movie to localize different visual areas should
+extensively annotate the content of frames (e.g. using the open-source solution
+``Pliers'' for feature extraction from a visual naturalistic stimulus;
+\citep{mcnamara2017developing}) and record the subject's visual attention via
+eye-tracking.
 
@@
 
-\subsubsection{AV stimulus}
-
-\todo[inline]{AV: field size decreases later in the movie; this is a confound
-based on cinematography => the stimulus changes over time; AV analysis exploits
-confound structure}
-
-\todo[inline]{imo opening the pandora's box of the AV shortcomings especially at
-the end of the paper should be kept to a minimum of text}
-
-% focus of study
-The focus of the current study was to investigate if significantly increased
-hemodynamic activity in the PPA correlates with spatial information (compared to
-``non-spatial'' information) during a naturalistic auditory stimulus.
-% shortcomings
-Results of the AV stimulus that we ran as a conceptual control are tempered by
-using different kind of movie cuts regardless of the visual content of the movie
-frame after the respective cuts.
-% which leads to the ``blurred'' results
-Hence we got visual confounds / clusters extending in to early visual areas.
-% further studies
-Since the capability to isolate clusters or networks correlating with specific
-perceptual (or cognitive) processes is influenced by the amount of annotated
-stimulus features further studies focusing on visual perception should annotate
-and model visual features of naturalistic stimuli more rigorously.
-% solution
-Future studies that aim to use a movie to localize different visual areas should
-extensively annotate the content of frames (e.g. using the open-source solution
-``Pliers'' for feature extraction from a visual naturalistic stimulus;
-\citep{mcnamara2017developing}) and record the subject's visual attention via
-eye-tracking.
-
 \section{Conclusions}

### 2021-01-19 paper/main.tex
Remove a few old comments to get a better sense what is done

@@
 Germany {*}corresponding author: Christian Olaf Häusler (der.haeusler@gmx.net)
-
-\todo[inline]{SE: Clou der ganzen Geschichte ist doch: Man braucht keinen
-separaten Localizer, oder? Das kommt bisher nur bedingt rüber; COH: well, if you
-also want to have the ``visual part'' of the PPA then you need a visual
-paradigm}
 
@@
 \end{abstract}
-\todo[inline]{RSC \& LOC are not mentioned in the abstract (anymore)}
-
-\todo[inline]{our system cannot accept BibTeX bibliography files; authors who
-    wish to use BibTeX to prepare their references should therefore copy the
-    reference list from the .bbl file that BibTeX generates and paste it into
-    the main manuscript .tex file (and delete the associated
-    \textbackslash{}bibliography and \textbackslash{}bibliographystyle
-commands)}
 
@@
 
-\todo[inline]{Limit for main text (intro and discussion) = ca. 3k words;}
+% Limit for main text (intro, results and discussion) = ca. 3k words
 
@@
 involving famous places.
-% wtf did Aziz really do?
-\todo[inline]{lass uns bitte kurz im Gespräch über Aziz Paper gucken; die
-relvanten Abschnitte sind in der PDF markiert. Ihre Method Section ist
-``strange'' und im Grunde kommt überall nur uneinheitliche Grütze heraus; ich
-blicke nicht durch, weshalb geschriebenes nicht vollständig korrekt sein wird;
-so wie ich es verstanden habe, hat sie vier 2x2 ANOVAs den Unterschied zwischen
-PPA und FFA angeguckt, aber diesen Unterschied im Kontrast zu object-related
-Sentences (dortige Fig 3)}
 
@@
 
-\todo[inline]{Specific data outputs should be explicitly referenced via data
-citation (see Data Records and Data Citations, below)}
+% Specific data outputs should be explicitly referenced via data
+% citation (see Data Records and Data Citations, below)}
 
@@
 All stimuli of the VIS study were already used in a previous study
-\citep{haxby2011common}.\todo{I guess they only report the ones they
-designed themselves in detail? -> check again}
+\citep{haxby2011common}.
 %
@@
 \paragraph{audio-description}
-
-\todo[inline]{SE: wie gut passen die Annotationen zu den VIS Stimuli -> genauere
-Ausführungen, wie welche Annotation dazu passt; COH: revised but maybe still not
-``optimal''}
 

### 2021-01-19 paper/main.tex
Rough word count
rewrite method after having had a meeting with the boss

@@
 \begin{itemize}
-    \item structure of last paragraph might be meh: methods/our approach
--> hypotheses -> results; readers might assume HARKing?
+    \item make more concise if applicable
 \end{itemize}
@@
 \begin{itemize}
-    \item Zwischenüberschriften rausnehmen, wenn Struktur so in Ordnung
-    \item revise captions of Table 1 + 3 (regressors based on annotation of
-    the other FG stimulus are now dropped from the table but mentioned in
-    section "statistial model / contrasts")
+    \item -
 \end{itemize}
@@
 \begin{itemize}
+    \item allgemein kürzen; insb. individual results kürzen
+    \item consistencies across contrasts ausformulieren
+    \item control contrasts ausformulieren
     \item Simons Kommentare, bei denen ich mitunter anderer Meinung bin
-    \item ggf. berichten welcher der drei VIS Kontraste für welche VP genommen
-    wurde
-    \item location of tables \& figures is pretty confusing at the moment
-    \item length of report of other reliably significant cluster across
-        contrasts and report of control contrasts depends on if/how long they
-        should be discussed
+    \item ggf. berichten welcher VIS Kontraste jeweils genommen wurde
 \end{itemize}
@@
 \begin{itemize}
-    \item umschreiben gemäß neuer Schwerpunktsetzung in Intro \& Method-Section
+    \item umstrukturieren \& ggf. schon kürzen gemäß neuer Schwerpunktsetzung
+    \item umschreiben gemäß neuer Schwerpunktsetzung
+    \item mehr zum Thema VIS( "best contrast was chosen")
     \item \citep{bartels2004mapping, hasson2004intersubject}
-    \item mehr zum Thema VIS( "best contrast was chosen")
 \end{itemize}
@@
 % Limit for main text (intro, results and discussion) = ca. 3k words
+
+\todo[inline]{~1000 words}
 
@@
 
+\todo[inline]{~3500 words}
+
 % Specific data outputs should be explicitly referenced via data
@@
 
-\subsubsection{Events}
-
-\paragraph{movie}
+\subsubsection{Events related to high-level perception}
+
+\todo[inline]{imo the subheadings for 2.6.1 and 2.6.2 can be dropped because
+2.6.2 is super short}
+
 % AV anno
@@
 \begin{table*}[h!]
-    \caption{Overview of annotations and event counts in the whole audio-visual
-    movie and individual stimulus segments.
-    \texttt{fg\_av\_ger\_pd} (perceptual differences of consecutive frames),
-    \texttt{fg\_av\_ger\_ml} (mean luminance of a frame),
-    \texttt{fg\_av\_ger\_lr} (difference in mean luminance of left and right
-    half),
-    \texttt{fg\_av\_ger\_ud} (difference in mean luminance of upper and
-    lower half),
-    \texttt{fg\_av\_ger\_lrdiff} (left-right volume difference), and
-    \texttt{fg\_av\_ger\_rms} (root mean square volume) represent one event
-    for every movie frame (\unit[40]{ms}).
+    \caption{Overview of annotated stimulus features of audio-visual
+    movie.
+    Respective event counts are given for the whole stimulus (\texttt{all} and
+    the segments that were used for the eight sessions of fMRI scanning.
+    %\texttt{fg\_av\_ger\_pd} (perceptual differences of consecutive frames),
+    %\texttt{fg\_av\_ger\_ml} (mean luminance of a frame),
+    %\texttt{fg\_av\_ger\_lr} (difference in mean luminance of left and right
+    %half),
+    %\texttt{fg\_av\_ger\_ud} (difference in mean luminance of upper and
+    %lower half),
+    %\texttt{fg\_av\_ger\_lrdiff} (left-right volume difference), and
+    %\texttt{fg\_av\_ger\_rms} (root mean square volume) represent one event
+    %for every movie frame (\unit[40]{ms}).
     % For description of the two event categories of the audio-description's
@@
 \end{table*}
-
-\paragraph{audio-description}
 
@@
 \begin{table*}[h!]
-    \caption{Overview of annotations and event counts in the whole
-    audio-description and individual stimulus segments.
+    \caption{Overview of annotated stimulus features of the audio-description.
+    Respective event counts are given for the whole stimulus (\texttt{all} and
+    the segments that were used for the eight sessions of fMRI scanning.
     Some of the annotation's original categories (female, females, fname; male,
@@
 
-\paragraph{Confounds for both}
-
-\todo[inline]{Die Events für die low-level confounds habe erstmal hier
-beschrieben; btw: Das Verschieben des Sounds in den Segmenten spiegelt sich
-wahrscheinlich auch in den unterschiedlichen Counts der Events je Segment wider
-(AV Bild vs AV Sound vs AO Sound)}
+\subsubsection{Events related to low-level perception / perceptual confounds}
+
+\todo[inline]{das Verschieben des Sounds in den Segmenten spiegelt sich auch in
+den unterschiedlichen Counts der Events je Segment wider (AV Bild vs AV Sound vs
+AO Sound)}
 
@@
 
-\subsubsection{Hemodynamic Modeling}
+\subsection{Hemodynamic Modeling}
 
@@
 
-\subsection{Statistical analysis}
-
-% level 1 and 2; similarly to the reviewed studies that employed designed
-% stimuli; we "based on stimulus annotations"
-We then tested our modeled hemodynamic responses by conducting standard
-two-level general linear model (GLM) analyses to create subject-specific results
-($Z$-maps) across the 8 segments for every subject and each stimulus.
-% level 3
-Subsequent, third-level analyses averaged contrast estimates over subjects.
-
-\paragraph{Design Matrix}
-
 % AV design matrix
-For the first level analysis of the AV stimulus, the modeled hemodynamic
-responses related to all movie cuts (including \texttt{no\_cut}) and six
-low-level perceptual confounds were included as regressors in the design matrix
-(s. Table \ref{tab:av-events}).
+For the subsequent first level GLM analysis, the modeled hemodynamic responses
+related to all movie cuts (including \texttt{no\_cut}) and six low-level
+perceptual confounds (s. Table \ref{tab:av-events}) were included as regressors
+in the design matrix.
 % AD regressors in AV AD design matrix
@@
 % both stimuli: null regressors
-In analyses of both stimuli, a null regressor was chosen for a event category in
-a segment, if that segment did not contain an event of the category (e.g. no
-event of \texttt{vpe\_old} in segment 3; cf. Table \ref{tab:ao-events}).
+For both stimuli, a null regressor was chosen for a event category in a segment,
+if that segment did not contain an event of the category (e.g. no event of
+\texttt{vpe\_old} in segment 3; cf. Table \ref{tab:ao-events}).
 % temporal derivatives
@@
 
+\subsection{Statistical analysis}
+
+% level 1 and 2; similarly to the reviewed studies that employed designed
+% stimuli; we "based on stimulus annotations"
+We tested our modeled hemodynamic responses by conducting standard
+two-level general linear model (GLM) analyses to create subject-specific results
+($Z$-maps) across the 8 segments for every subject and each stimulus.
+% level 3
+Subsequent, third-level analyses averaged contrast estimates over subjects.
+
+\paragraph{PPA Contrasts}
+
 \todo[inline]{SE: würde wetten, dass Reviewer fragen: Wie sieht es im vergleich
@@
 
-\paragraph{PPA Contrasts}
-
-In this study, we investigated if increased hemodynamic activty in the PPA that
-is usually defined by contrasting blocks of pictures can also be revealed by
-contrasting selected stimulus features that we annotated in a audio-visual movie
-and its audio-description.
+% similar to previous studies
+On the first level, we created GLM contrasts like studies that contrasted
+blocks of pictures.
+% dissimilar
+But unlike previous studies, our approach was to contrast selected stimulus features that we annotated in the audio-visual movie and its audio-description.
 % intro
-To test the robustness of our approach, we operationalized the perception of
+To test the robustness of this approach, we operationalized the perception of
 spatial information compared to the perception of ``non-spatial'' information
@@
 contrasts (\textit{strict}, \textit{relaxed}, and \textit{simple} contrast
-\citep{sengupta2016extension}).\todo{maybe add note regarding Berman (2010);
-but they did FFA}
+\citep{sengupta2016extension}).\todo{maybe add note regarding Berman (2010); but
+they did FFA}
 % thus: primary contrasts
@@
 
-\paragraph{GLM computations \& stuff}
-
 % alignments single subjects (for Bland-Altman-Plots) 1st level
@@
 % two ways of co-registration
-We co-registered the subjects in two ways.
+Subject-specific BOLD T2* time series were anatomically co-registered in two
+ways:
 % subject template (for Bland-Altman-Plot of unthresholded maps)
 % \href{"https://github.com/psychoinformatics-de/studyforrest-data-templatetransforms/blob/master/sub-01/bold3Tp2/brain.nii.gz"}{example})
-On the one hand, subject-specific BOLD T2* time series were anatomically aligned
-via linear transformation to a subject-specific, study-specific T2* template
-(cf. \citep{sengupta2016extension}).
+a) [time series were aligned to] via linear transformation to a
+subject-specific, study-specific T2* template (cf.
+\citep{sengupta2016extension}) and,
 % group template (for group and individual brain slices)
 % https://github.com/psychoinformatics-de/studyforrest-data-templatetransforms/blob/master/templates/grpbold3Tp2/brain.nii.gz"
-On the other hand, time series were aligned via non-linear transformation to a
-study-specific T2* group template (cf. \citep{hanke2014audiomovie}).
+b) via non-linear transformation to a study-specific T2* group template (cf.
+\citep{hanke2014audiomovie}).
 % MNI152
@@
 identification of cortical structures.
+
+\paragraph{2nd level}
 
@@
 \citep{worsley2001statistical}.
+
+\paragraph{3rd level}
 
@@
 
+\todo[inline]{~1300 words (some sections incomplete)}
+
 \todo[inline]{SE: sauber differenzieren zwischen "Lokalisation der PPA" und
@@
 
-\todo[inline]{SE: Vergleich mit VIS kommt bestenfalls en passant; VIS selber
-wird gar nicht berichtet, wäre aber wichtig zum Andocken an Literatur; COH: yes,
-maybe reference Sengupta who are interested in the details? en passant makes
-more sense here imo}
+\todo[inline]{SE: VIS wird selbst gar nicht/en passant berichtet, wäre aber
+wichtig zum Andocken an Literatur}
 
@@
     of blindly averaging the actual frame content in the categories of movie
-    cuts (cf. methods/regressors, discussion/shortcomings); this ``cross-modal
-    control things'' seems to more confuse than having its merits}
+    cuts (cf. methods/regressors, discussion/shortcomings)}
 
@@
 \section{Discussion}
+
+\todo[inline]{~2100 words (some sections incomplete)}
 

### 2021-01-20 paper/main.tex
rewrite beginning of results

@@
     \item control contrasts ausformulieren
+    \item adapt captions of result tables to new phrasing in intro / method
     \item Simons Kommentare, bei denen ich mitunter anderer Meinung bin
@@
 
-% level 1 and 2; similarly to the reviewed studies that employed designed
-% stimuli; we "based on stimulus annotations"
-We tested our modeled hemodynamic responses by conducting standard
-two-level general linear model (GLM) analyses to create subject-specific results
-($Z$-maps) across the 8 segments for every subject and each stimulus.
-% level 3
-Subsequent, third-level analyses averaged contrast estimates over subjects.
-
-\paragraph{PPA Contrasts}
-
 \todo[inline]{SE: würde wetten, dass Reviewer fragen: Wie sieht es im vergleich
@@
 
+% intro
+We tested our modeled hemodynamic responses based on stimulus annotations by
+conducting standard two-level general linear model (GLM) analyses to create
+subject-specific results ($Z$-maps) across the 8 segments for every subject and
+each stimulus.
+% level 3
+Subsequent, third-level analyses averaged contrast estimates over subjects.
+
 % similar to previous studies
-On the first level, we created GLM contrasts like studies that contrasted
-blocks of pictures.
+On the first level, we created GLM contrasts like studies that contrasted blocks
+of pictures.
 % dissimilar
-But unlike previous studies, our approach was to contrast selected stimulus features that we annotated in the audio-visual movie and its audio-description.
+But unlike previous studies, our approach was to contrast selected stimulus
+features that we annotated in the audio-visual movie and its audio-description.
 % intro
@@
 to match the preferred stimulus type, and b) the amount of available data /
+
 % AV: primary contrast
@@
 
-\paragraph{Control contrasts}
-
-% intro
+\todo[inline]{why was done? narrator and cuts to other setting are "somewhat"
+correlated; and now what? -> cf. results and discussion}
+% control contrasts
 Finally, we created several contrasts as negative control for both stimuli.
@@
 For the AV stimulus, four $t$-contrasts were created contrasting the no-cut
-regressor (texttt{vno\_cut} to cut-related regressors \ref{tab:av-contrasts}).
+regressor (\texttt{vno\_cut} to cut-related regressors \ref{tab:av-contrasts}).
 % AV: narrator
@@
 contrasting nouns spoken by the narrator.
-\todo[inline]{why was done? narrator and cuts to other setting are "somewhat"
-correlated; and now what? -> cf. results and discussion}
 % AD stimulus
@@
 % \href{"https://github.com/psychoinformatics-de/studyforrest-data-templatetransforms/blob/master/sub-01/bold3Tp2/brain.nii.gz"}{example})
-a) [time series were aligned to] via linear transformation to a
-subject-specific, study-specific T2* template (cf.
-\citep{sengupta2016extension}) and,
+a) via linear transformation to a subject-specific, study-specific T2* template
+(cf. \citep{sengupta2016extension}) and,
 % group template (for group and individual brain slices)
@@
 identification of cortical structures.
-
-\paragraph{2nd level}
 
@@
 \citep{worsley2001statistical}.
-
-\paragraph{3rd level}
 
@@
 % study goal
-The goal of this study was to investigate if cues about the spatial layout
-embedded in two naturalistic stimuli correlate with increased hemodynamic
-activity in the PPA that was defined using a visual localizer experiment
-within the same subjects \citep{sengupta2016extension}.
-% what we did We
-We annotated a \unit[2]{h} movie and its temporally aligned audio-description to
-create GLM contrasts similar to previous studies that used static pictures.
+The goal of this study was to investigate if annotated cues about the spatial
+layout embedded in two naturalistic stimuli correlate with increased hemodynamic
+activity in the PPA that was defined using a visual localizer experiment within
+the same subjects \citep{sengupta2016extension}.
 % group level
-On a group average level, we compare results gained from both naturalistic
-stimuli to results gained from the visual localizer.
+On a group average level, we compare results gained from whole-brain GLM
+analyses  of the movie and the audio-description (Z>3.4; p<.05, cluster
+corrected) to results gained from the visual localizer.
 % individual level
-On the level single subjects, we also assess the performance of a naturalistic
-auditory stimulus as a substitute for a visual paradigm to localize the
-PPA.\todo{``localize''}
+On the level single subjects (Z>3.4; p<.05, cluster corrected), we also assess
+the performance of the exclusively auditory naturalistic stimulus as a
+substitute for a visual paradigm to localize the PPA.\todo{``localize''}
 % NeuroVault
-Unthreholded $z$-maps of all contrasts on a group level as well as individual
-results of the primary $t$-contrasts for both naturalistic stimuli can be found
-at \href{https://neurovault.org/collections/KADGMGVZ/}{NeuroVault}.\todo{still
-private collection}
+Unthresholded $z$-maps of all contrasts on a group level as well as individual
+results of the primary $t$-contrasts co-registered to the group-template can
+found at \href{https://neurovault.org/collections/KADGMGVZ/}{NeuroVault}.
+\todo{still private collection}
 
@@
 
-% intro
-First, we tested if results of a whole-brain analysis based stimulus annotations
-would lead to increased hemodynamic activity in the PPA.
-
-\subsubsection{group}
 % AV intro
-First, we analyzed data from the audio-visual movie offering visual but
+First, we analyzed data from the audio-visual movie offering a visual but
 ecologically more valid stimulation.
@@
 The movie's primary $t$-contrast that compared cuts to a setting that was not
-depicted before to a recurring setting (\texttt{vse\_new > vpe\_old}) yielded
-three significant clusters (see Table \ref{tab:res-av-group1}, Figure
+depicted before to cuts to a recurring setting (\texttt{vse\_new > vpe\_old})
+yielded three significant clusters (see Table \ref{tab:res-av-group1}, Figure
 \ref{fig:group-slices}).
 % PPA (others the clusters extend into).
-One cluster spans across the midline and comprises, parts of the intracalcarine
+One cluster spans across the midline and comprises parts of the intracalcarine
 and cuneal cortex, the lingual gyrus and retrosplenial cortex, the occipital and
@@
 % AD intro
-Second, we analyzed data from the movie's audio-description offering exclusively
+Second, we analyzed data from the audio-description offering exclusively
 auditory stimulation.
@@
 % in detail
-Specifically, the clusters of the current analysis are at the borders of the
-posterior parahippocampal cortex, the occipital and temporal fusiform gyrus and
-lingual gyrus.
+Specifically, these clusters are located at the borders of the posterior
+parahippocampal cortex, the occipital and temporal fusiform gyrus and lingual
+gyrus.
 % precuneus
-Two additional clusters are located in the ventral precuneus extending into the
+Two additional clusters are apparent in the ventral precuneus extending into the
 retrosplenial cortex.
@@
 
-\subsubsection{individuals}
-
-\todo[inline]{imo no need to mention it here but mention in discussion that
-results are not driven by outliers when discussing ``localization'' performance}
+\paragraph{individual results}
+
+\todo[inline]{if we here report procedure of Sengupta as detailed as it is now
+(imo too long), we probably need to explain the differences between strict,
+relaxed, simple in more detail in the method section and not just reference to
+Sengupta}
 
@@
 Third, we investigated result from both naturalistic paradigms on the level of
-individual subjects.
-%
+individual subjects to ensure that the group results are not just a by-product
+of the averaging process.\todo{if you know what I mean}
+% AD is the real shit
 Focussing on the AD stimulus, we hypothesize[d] that an exclusively auditory
-stimulus can/could localize ``visual area'' in individual subjects and thus
-possibly substitute a visual paradigm using blocks of pictures.
-
-\todo[inline]{following is probably the part that Simon considered as en
-passant}
-
-\todo[inline]{if we here report procedure of Sengupta as detailed as
-it is now, we probably need to explain the differences between strict, relaxed,
-simple in more detail in the method section and not just reference to Sengupta}
+stimulus can/could localize the PPA in individual subjects and thus
+possibly substitute a visual paradigm [using blocks of pictures].
 
@@
 \citep{sengupta2016extension}).
-% Sengupta: procedure a)
+% procedure a)
 Starting with the most conservative contrast (strict set) and a threshold of t =
 2.5, we looked for clusters with at least 20 voxels (using AFNI).
-%
+% procedure b)
 We titrated [?] the threshold in the range of [2, 3] until we found an isolated
@@
 In the current study, time series of all subjects were analyzed both in subject
-space and group space.
+space (Z>2.3, p<.05 cluster-corrected) and group space ).
 % subject space -> NeuroVault
@@
 (unthresholded $z$-maps and thresholded $z$-maps, Z>2.3, p<.05 cluster
-corrected) can be found at
-\href{https://neurovault.org/collections/KADGMGVZ/}{NeuroVault}. \todo{still
-private collection}
+corrected) can be found in the accompanying datset \todo{Neurvault does not like
+unstandardized spaces}
 % here report in group space
 For better comparions of subjects, we here report results from the analyses
-performed in group space. % ($z$-maps; Z>3.4, p<.05 cluster-corrected).
+performed in group space (Z>3.4, p<.05 cluster-corrected)
 % one contrast to localize them all; "...and Z>3.4 for all"
 Contrary to the procedure in \citep{sengupta2016extension}, we used the same
-contrast of each naturalistic stimulus and the same threshold (Z>3.4, p<.05
-cluster corrected) for all subjects.
+contrast of each naturalistic stimulus and the same threshold [(Z>3.4, p<.05
+cluster corrected)] for all subjects.
 

### 2021-01-20 paper/main.tex
write results: consistencies across contrasts

@@
 \begin{itemize}
-    \item allgemein kürzen; insb. individual results kürzen
-    \item consistencies across contrasts ausformulieren
+    \item kürzen (war nicht ganz einfach)
     \item control contrasts ausformulieren
@@
 
-\todo[inline]{das Verschieben des Sounds in den Segmenten spiegelt sich auch in
-den unterschiedlichen Counts der Events je Segment wider (AV Bild vs AV Sound vs
-AO Sound)}
-
-% intro
+% low-leve confounds: intro
 Lastly, we algorithmically annotated the temporal structure of low-level
@@
 audio-tracks.
+
+\todo[inline]{das Verschieben des Sounds in den Segmenten spiegelt sich auch in
+den unterschiedlichen Counts der Events je Segment wider (AV Bild vs AV Sound vs
+AO Sound)}
 
@@
 % why se_new & se_old were not used in the primary contrasts
-The categories of nouns cueing a setting that occured for the first time
+The categories of nouns cueing a setting that occurred for the first time
 (\texttt{se\_new}) or a setting that recurred during the plot (\texttt{se\_old})
@@
 
-\todo[inline]{SE: sauber differenzieren zwischen "Lokalisation der PPA" und
-    "Antwortverhalten einer vorab definierten PPA". Ich habe den Eindruck, dass
-Du oft das erste machst es aber als das zweite beschreibst; COH: ??? we do
-whole-brain analysies, so probably ``localization'', }
-
 \todo[inline]{SE: VIS wird selbst gar nicht/en passant berichtet, wäre aber
@@
 individual subjects to ensure that the group results are not just a by-product
-of the averaging process.\todo{if you know what I mean}
+of the averaging process.
 % AD is the real shit
@@
 (unthresholded $z$-maps and thresholded $z$-maps, Z>2.3, p<.05 cluster
-corrected) can be found in the accompanying datset \todo{Neurvault does not like
-unstandardized spaces}
+corrected) can be found in the accompanying dataset. \todo{Neurovault does not
+like unstandardized spaces}
 % here report in group space
-For better comparions of subjects, we here report results from the analyses
+For better comparisons of subjects, we here report results from the analyses
 performed in group space (Z>3.4, p<.05 cluster-corrected)
@@
 % report here in group
-Results of the primary AD contrast yielded stastically significant bilateral
+Results of the primary AD contrast yielded statically significant bilateral
 clusters in nine subjects, and one cluster in the left hemisphere of sub-09,
@@
 
-\todo[inline]{anything else to report in the following paragraph? seems more
-like just an explanation of the plots}
 % Bland-Altman-Plots: why they were done
@@
 \ref{fig:bland-altman}).
-% x-axis
-The x-axis of every subplot depicts the mean of $z$-values of two spatially
-corresponding voxels taken from a subject's unthresholded $z$-map.
-% y-axis
-The y-axis of every subplot depicts the difference of $z$-values of two
-spatially corresponding voxels (dedicated localizer minus AD stimulus).
-% masking
-Voxels were spatially constrained to a) voxels located in the occipital and
-temporal lobes (gray; using the probabilistic Jülich Histological Atlas
-\citep{eickhoff2005toolbox, eickhoff2007assignment}), b) voxels located in the
-PPA overlap of all subjects (blue), and c) voxels located in individual PPA(s)
-(red).
 % top KDE plot
@@
 \centering
-    \includegraphics[scale=0.28]{figures/subjs_bland-altman.png}
-    \caption{Bland-Altman-Plots for individual subjects. The x-axis depicts the
-        mean of two spatially corresponding voxels in the unthresholded z-map of
-        the visual localizer and in the unthresholded z-map of contrast 1 of the
-        AD stimulus (KDE plot on the top). The y-axis depicts the difference of
-        two voxels (KDE plot on the right).
-        The overlays depict voxels spatially contrained to be located in the
-        temporal and occipital cortex (gray),
+    \includegraphics[scale=0.27]{figures/subjs_bland-altman.png}
+    \caption{Bland-Altman-Plots for individual subjects.
+    The x-axes show the means of two spatially corresponding voxels in the
+    unthresholded $z$-map of the audio-description's primary contrast and
+    unthresholded $z$-map of the visual localizer (KDE plot on the top).
+    The y-axes show the difference of two voxels (localizer minus
+    audio-description; KDE plot on the right).
+    The overlays depict voxels spatially constrained to the
+    temporal and occipital cortex (gray; based on the probabilistic Jülich
+    Histological Atlas \citep{eickhoff2005toolbox, eickhoff2007assignment}),
     PPA overlap of all subjects (blue),
@@
 
-\subsection{Robustness of PPA across contrasts: AV \& AD}
-
-\todo[inline]{tables of significant clusters all contrasts = overkill!? Link to
-NeuoVault is added; sign. clusters of all contrasts are listed in the comments}
+\subsection{Robustness of group results across contrasts}
+
+% unthresholded $z$-maps of all contrasts on a group level:
+% \href{https://neurovault.org/collections/KADGMGVZ/}{NeuroVault}.
 
@@
 investigated on a group level.
-%% results: PPA
+% results: PPA; biggest overlap in posterior part of PPA group overlap  =
+%temporal occipital fusiform cortex
 All of the overall five AV contrasts yielded significant bilateral clusters that
 overlap with the PPA group overlap (see Figure \ref{fig:stability-slices}).
-[biggest overlap in posterior part of PPA group overlap  = temporal occipital
-fusiform cortex] .
 % AD
@@
 often feels like interpretation}
+
+% AV
+Reliably across the five contrasts of the AV stimulus, we also find bilaterally
+significant clusters also in the precuneal cortex (contrasts 1, 3, 4; all
+bilateral)\todo{and? -> fsleyes} and lateral occipital cortex (all contrasts
+except contrast 3)
+% AD; LOC: AV cluster are more medial, AD clusters are more lateral
+Reliably across the five contrasts of the AD, we find bilaterally significant
+clusters in the ventral precuneus (7 contrasts), lateral occipital cortex
+(bilateral in 4 contrasts, unilateral in 2 contrasts), superior temporal
+cortices (4 contrasts)\todo{uni/bilateral?}.
 %
-\todo[inline]{figure caption: mention / explain other clusters}
-
-% figure group results of robustness across all AD & AV contrasts
+\todo[inline]{(smallish) prefrontal clusters: 3 contrasts (non-overlapping)}
+
 \begin{figure*}[h!]
@@
         are overlaid over the audio-visual movie's contrasts 1-5 (red;
-        \ref{tab:av-contrasts}) that were used to [isolate] the PPA
+        \ref{tab:av-contrasts}).
         Cluster are overlaid on top of the MNI152 T1-weighted head template
@@
         Light gray: The audio-description's field-of-view (cf.
-        \citep{hanke2014audiomovie}).}
+        \citep{hanke2014audiomovie}).
+        The figure shows that some contrasts yielded significant clusters
+        also in the lateral temporal and prefrontal cortex.
+        }
     \label{fig:stability-slices}
@@
 
-\subsection{Non-PPA clusters across contrasts}
-
-% precuneus = retrosplenial cortex ?
-\todo[inline]{Following is a list; report depends on the discussion I guess;
-anyway: clusters are not ``random'' but make sense which speaks for the use of
-naturalistic stimuli}
-
-\subsubsection{AV}
-
-\begin{itemize}
-    \item RSC: 3 contrasts (all bilat; vse\_new > vpe\_old; vse\_new >
-        vse\_old, vpe\_old; vse\_new, vpe\_new > vpe\_old)
-    \item lateral occipital cortex: 4 contrasts (all except vse\_new > vse\_old; all bilateral)
-\end{itemize}
-
-\subsubsection{AD}
-
-\begin{itemize}
-\item RSC (and ventral precuneus): 7 contrasts (all bilateral)
-\item lateral occipital cortex: 6 contrasts (4 bilateral, 2 unilateral =
-    transverse occipital sulcus / occipiatal place area?; AD \& AV clusters
-    overlap but AD clusters are more lateral, AV cluster are more medial \&
-    caudal)
-\item right superior temporal gyrus (auditory cortices): 4 contrasts
-\item (smallish) prefrontal clusters: 3 contrasts (non-overlapping)
-\end{itemize}
-
-\subsection{control contrasts (AV \& AD)}
-
-\todo[inline]{contrasts are mentioned in the method section; shall results be
-reported (and later discussed)?}
-
-% AD stimulus
-AD stimulus (using annotation of movie cuts) all null results except: contrast 9
-(vse\_new > pe\_old): right RSC.
-% correlation of these nouns with cuts
-Compare Figure \ref{fig:reg-corr}: nouns that cue change to a new setting are
-correlated  with cuts to a new setting (vse\_new; r$\approx$0.3; second highest
-correlation of a verbal cue category with a cut category.
+\subsection{control contrasts}
 
@@
 
+% AD stimulus
+AD stimulus (using annotation of movie cuts) all null results except: contrast 9
+(vse\_new > pe\_old): right RSC.
+% correlation of these nouns with cuts
+Compare Figure \ref{fig:reg-corr}: nouns that cue change to a new setting are
+correlated  with cuts to a new setting (vse\_new; r$\approx$0.3; second highest
+correlation of a verbal cue category with a cut category.
+
 \section{Discussion}
@@
 spannende aber logisch nachgeschaltete Frage sein.}
+
+\todo[inline]{SE: sauber differenzieren zwischen "Lokalisation der PPA" und
+    "Antwortverhalten einer vorab definierten PPA". Ich habe den Eindruck, dass
+Du oft das erste machst es aber als das zweite beschreibst; COH: ??? we do
+whole-brain analysies, so probably ``localization'', }
 

### 2021-01-21 paper/main.tex
consistencies and control contrasts

@@
     \item make more concise if applicable
+    \item add counts of intro, results, discussion respectively
 \end{itemize}
@@
     \item kürzen (war nicht ganz einfach)
-    \item control contrasts ausformulieren
     \item adapt captions of result tables to new phrasing in intro / method
@@
 categories occurring in spoken language.\todo{phrasing to delineate from Huth
-(2016); imo voxel-wise semantic modeling says nothing about
-excitation/inhibition}
+(2016)}
 % Aziz' stimuli
@@
 % varying amount of data
-Contrasts vary in HOW WELL / HOW MUCH DATA.\todo{rewrite if it should be
-mentioned}
+Contrasts vary in HOW WELL / HOW MUCH DATA.\todo{intro too long already}
 
@@
 spatial information compared to the perception of ``non-spatial'' information
-differently in eight $t$-contrasts for the AD stimulus (see Table
-\ref{tab:ao-contrasts}) and five $t$-contrasts for the AV stimulus (see Table
-\ref{tab:av-contrasts}).
+differently in five $t$-contrasts for the AV stimulus (see Table
+\ref{tab:av-contrasts}) and eight $t$-contrasts for the AD stimulus (see Table
+\ref{tab:ao-contrasts})
 % reason: robustness
@@
 
-\todo[inline]{~1300 words (some sections incomplete)}
-
 \todo[inline]{SE: VIS wird selbst gar nicht/en passant berichtet, wäre aber
@@
 schwer abzulesen; lieber eine andere Farbskala (spectral sequence?) nutzen; COH:
-yes, I know it is kinda difficult, tried my best to choose/tweak the color map}
+yes, I know it is kinda difficult, figures will be honed at the very end}
 
@@
 found at \href{https://neurovault.org/collections/KADGMGVZ/}{NeuroVault}.
-\todo{still private collection}
-
-% all AD contrasts
-% 1 PPA (l/r); RSC (l/r), LOC (l/r)
-% 2 PPA (l/r); RSC (l/r), LOC (l/r), r. sup.temp.C., r.fr.pole; putamen; etc
-% 3 PPA (l/r); RSC (l/r), LOC (l/r),l&r sup.temp.C., anterior cing., paracing.
-% 4 PPA (l/r); RSC (l/r), LOC (l/r)
-% 5 PPA (l/r); RSC (l/r), LOC (-/-)
-% 6 PPA (l/r); RSC (l/r), LOC (l/-), l&r sup.temp.C.; medial pref. c., precun
-% 7 PPA (-/-); RSC (l/r), LOC (l/-), l&r sup.temp.C
-% 8 PPA (-/-); RSC (-/-), LOC (-/-)
-% ---------- control contrasts ----------
-% 9 PPA (-/-); RSC (-/r), LOC (-/-), left pars triangularis
-%10 PPA (-/-); RSC (-/-), LOC (-/-)
-%11 PPA (-/-); RSC (-/-), LOC (-/-),
-%12 PPA (-/-); RSC (-/-), LOC (-/-), right posterior hippocampus
-%13 PPA (-/-); RSC (-/-), LOC (-/-) results: PPA
-
-% all AV contrasts
-% 1 PPA (l/r); RSC (l/r), LOC (l/r), VisC (l/r),
-% intracalcarine, cuneal, ling.c
-% 2 PPA (l/r); RSC (-/-), LOC (l/r), VisC (-/-)
-% 3 PPA (l/r); RSC (-/-), LOC (-/-), VisC (-/r), occ. fusisf. g.
-% 4 PPA (l/r); RSC (l/r), LOC (l/r), VisC (-/-), lingual g., occ. fusif. g.
-% 5 PPA (l/r); RSC (l/r), LOC (l/r), VisC (-/-), occ. fusif. g.
-% ---------- control contrasts ----------
-% 6 nothing
-% 7 nothing
-% 8 nothing
-% 9 nothing
-%10 se_new > se_old (nouns but in AV stimulus):
-% LOC (l/r) right PPA, bilateral sup. lat. occ. c., sup. parietal lobe (right)
+\todo{private collection}
 
@@
 3003 & 0 & 5.31 & 22.5 & -45.5 & -12 & 4.53 & -63.3 & -3.72 & r. lingual g.; r. cuneal c., intracalcarine c., bilaterally occipital fusiform g., temporal fusiform c., posterior parahippocampal c.  \\
-154 & 6.56E-07 & 4.46 & -35 & -83 & 28 & -32.8 & -86.2 & 21.4 & l. superior lateral occipital c. \\
-121 & 7.69E-06 & 4.65 & 25 & -80.5 & 25.5 & 23.7 & -83.8 & 25.4 & r. superior lateral occipital cortex \\
+154 & 0.000000656 & 4.46 & -35 & -83 & 28 & -32.8 & -86.2 & 21.4 & l. superior lateral occipital c. \\
+121 & 0.00000769 & 4.65 & 25 & -80.5 & 25.5 & 23.7 & -83.8 & 25.4 & r. superior lateral occipital cortex \\
 \bottomrule
@@
 \midrule
-188 & 5.96E-08 & 4.48 & -17.5 & -65.5 & 25.5 & -14.7 & -59.1 & 15.2 & l. precuneus \\
-164 & 2.38E-07 & 4.47 & 17.5 & -58 & 23 & 15.6 & -55.6 & 16 & r. precuneus; \\
+188 & 0.0000000596 & 4.48 & -17.5 & -65.5 & 25.5 & -14.7 & -59.1 & 15.2 & l. precuneus \\
+164 & 0.000000238 & 4.47 & 17.5 & -58 & 23 & 15.6 & -55.6 & 16 & r. precuneus; \\
 83 & 0.000128 & 4.48 & 27.5 & -43 & -17 & 27.2 & -41.1 & -14 & r. temporal (occipital) fusiform c.; posterior parahippocampal g. \\
@@
 
+\todo[inline]{I tried to keep it concise but detailed; if individual contrasts
+are mentioned (enumerated at the moment)}
+
+% AV PPA contrasts
+% 1 PPA (l/r); RSC (l/r), LOC (l/r), VisC (l/r),
+% intracalcarine, cuneal, ling.c
+% 2 PPA (l/r); RSC (-/-), LOC (l/r), VisC (-/-)
+% 3 PPA (l/r); RSC (-/-), LOC (-/-), VisC (-/r), occ. fusisf. g.
+% 4 PPA (l/r); RSC (l/r), LOC (l/r), VisC (-/-), lingual g., occ. fusif. g.
+% 5 PPA (l/r); RSC (l/r), LOC (l/r), VisC (-/-), occ. fusif. g.
+
 % AV
@@
 
-% AV
-Reliably across the five contrasts of the AV stimulus, we also find bilaterally
-significant clusters also in the precuneal cortex (contrasts 1, 3, 4; all
-bilateral)\todo{and? -> fsleyes} and lateral occipital cortex (all contrasts
-except contrast 3)
+% AD PPA contrasts
+% 1 PPA (l/r); RSC (l/r), LOC (l/r)
+% 2 PPA (l/r); RSC (l/r), LOC (l/r), r. sup.temp.C., r.fr.pole; putamen; etc
+% 3 PPA (l/r); RSC (l/r), LOC (l/r),l&r sup.temp.C., anterior cing., paracing.
+% 4 PPA (l/r); RSC (l/r), LOC (l/r)
+% 5 PPA (l/r); RSC (l/r), LOC (-/-)
+% 6 PPA (l/r); RSC (l/r), LOC (l/-), l&r sup.temp.C.; medial pref. c., precun
+% 7 PPA (-/-); RSC (l/r), LOC (l/-), l&r sup.temp.C
+% 8 PPA (-/-); RSC (-/-), LOC (-/-)
+
+% AD
+Reliably across the five contrasts of the AV stimulus, we find bilaterally
+significant clusters also in the ventral precuneal cortex / posterior cingulate
+gyrus (i.e. restrosplenial region; contrasts 1, 4, 5) and lateral occipital
+cortex (contrasts 1, 2, 4, 5)
 % AD; LOC: AV cluster are more medial, AD clusters are more lateral
-Reliably across the five contrasts of the AD, we find bilaterally significant
-clusters in the ventral precuneus (7 contrasts), lateral occipital cortex
-(bilateral in 4 contrasts, unilateral in 2 contrasts), superior temporal
-cortices (4 contrasts)\todo{uni/bilateral?}.
+Reliably across the five contrasts of the AD stimulus, we find bilaterally
+significant clusters in the ventral precuneus (all except contrasts 8), lateral
+occipital cortex (bilateral in 4 contrasts 1 to 4, unilateral in contrasts 6 and
+7), and superior temporal cortices (bilateral in contrasts 3, 6, 7; unilateral
+right in contrast 2).
+% non-systematic
+Contrast 2 also shows bilateral clusters in the anterior cingulate gyrus and
+right paracingulate gyrus (frontal medial cortex), right putamen, and right
+frontal pole.
 %
-\todo[inline]{(smallish) prefrontal clusters: 3 contrasts (non-overlapping)}
+Contrast 3 shows clusters bilaterally in the anterior cingulate gyrus and
+left frontal pole.
+%
+Contrast 6 shows one additional cluster also in the right medial frontal cortex.
 
@@
 
-% AV stimulus
-AV stimulus. All contrasts using ``no cut condition'' > XY yield null results.
-The contrast that uses the narrator's nouns but in the AV stimulus (se\_new >
-se\_old): right PPA, bilateral sup. lat. occ. cortex; LOC (l/r), right superior
-parietal lobe. Compare Figure \ref{fig:reg-corr}: nouns that cue change to a new
-setting are correlated  with cuts to a new setting (vse\_new; r$\approx$0.3;
-second highest correlation of a verbal cue category with a cut category; AND:
-nouns that cue change to a familiar setting are somewhat correlated with cuts to
-a familiar setting (se\_old; r$\approx$0.4; highest correlation of a verbal
-category with a cut category).
+% ---------- AV control contrasts ----------
+% 6 nothing
+% 7 nothing
+% 8 nothing
+% 9 nothing
+%10 se_new > se_old (nouns but in AV stimulus):
+% LOC (l/r) right PPA, bilateral sup. lat. occ. c., sup. parietal lobe (right)
+
+% ---------- AD control contrasts ----------
+% 9 PPA (-/-); RSC (-/r), LOC (-/-), left pars triangularis
+%10 PPA (-/-); RSC (-/-), LOC (-/-)
+%11 PPA (-/-); RSC (-/-), LOC (-/-),
+%12 PPA (-/-); RSC (-/-), LOC (-/-), right posterior hippocampus
+%13 PPA (-/-); RSC (-/-), LOC (-/-)
+
+% intro
+Lastly, we implemented five contrasts for every stimulus for the purpose of
+negative control.
+% AV: no_cut > x
+In the analysis of the AV data, none of the contrasts that compared the ``no cut
+condition''  to a movie cut category (contrasts 6, 7, 8, 9) yielded significant
+clusters.
+% AV using nouns
+The contrast that used the narrator's nouns but in the AV stimulus (se\_new >
+se\_old) yielded a significant cluster in the right PPA and bilateral clusters
+in the superior lateral occipital cortices (the right hemispheric cluster
+extending into the superior parietal cortex).
 
 % AD stimulus
-AD stimulus (using annotation of movie cuts) all null results except: contrast 9
-(vse\_new > pe\_old): right RSC.
-% correlation of these nouns with cuts
-Compare Figure \ref{fig:reg-corr}: nouns that cue change to a new setting are
-correlated  with cuts to a new setting (vse\_new; r$\approx$0.3; second highest
-correlation of a verbal cue category with a cut category.
+In the analysis of the AD data, we created control contrasts based on events of
+the annotated movie cuts (cf. Table \ref{tab:ao-contrasts})
+% contrast 9
+Contrast 9 (vse\_new > pe\_old) revealed one significant cluster in the left
+inferior prefrontal cortex (pars triangularis) and right ventral
+precuneus/posterior cingulate gyrus.
+% contrast 12
+Contrast 12 (\texttt{vse\_new} > \texttt{vse\_old}, \texttt{vpe\_old}) revealed
+one cluster in the right posterior hippocampus. \todo{dorsally of PPA}
+
+\todo[inline]{there is no table/figure for negative control contrasts; we could
+add a reference to NeuroVault (here again) or point to the dataset}
 
 \section{Discussion}
-
-\todo[inline]{~2100 words (some sections incomplete)}
 
@@
 
+% AV: contrast with AV nouns
+Compare Figure \ref{fig:reg-corr}: nouns that cue change to a new
+setting are correlated  with cuts to a new setting (vse\_new; r$\approx$0.3;
+second highest correlation of a verbal cue category with a cut category; AND:
+nouns that cue change to a familiar setting are somewhat correlated with cuts to
+a familiar setting (se\_old; r$\approx$0.4; highest correlation of a verbal
+category with a cut category).
+
+% AD: correlation of these nouns with cuts
+Compare Figure \ref{fig:reg-corr}: nouns that cue change to a new setting are
+correlated  with cuts to a new setting (vse\_new; r$\approx$0.3; second highest
+correlation of a verbal cue category with a cut category.
+
 \subsection{shortcomings}

### 2021-01-25 paper/main.tex
overhaul of structure of discussion

@@
     % our audience highlighting innovative examples of data reuse may be used to
-% present compelling new findings & conclusions derived from published.  intro
+    % present compelling new findings & conclusions derived from published.
+    % intro
 Neuroimaging studies have parcellated the human brain into distinct functional
@@
 A region in the human hippocampal cortex termed ``parahippocampal place area''
-is classically considered to be a higher visual area as increased hemodynamic
-activity in the PPA correlates with the perception of static pictures of
-landscapes compared to pictures of faces or objects.
+    is classically considered to be a higher visual area as increased
+    hemodynamic activity in the PPA correlates with the perception of static
+    pictures of landscapes compared to pictures of faces or objects.
 % AV, AD: operationalization
-In this study, we explore different ways to operationalize spatial perception\todo{not sure if this is just perception} in
-14 subjects that were watching an audio-visual Hollywood movie and listened to
-the movie's audio-description (studyforrest.org).
+In this study, we explore different ways to operationalize spatial
+    perception\todo{not sure if this is just perception} in 14 subjects that
+    were watching an audio-visual Hollywood movie and listened to the movie's
+    audio-description (studyforrest.org).
 % auditory localizer?
-Focussing on the audio-description, we test if an auditory narrative
-could localize a ``visual area'' in individual subjects.
+Focussing on the audio-description, we test if an auditory narrative could
+    localize a ``visual area'' in individual subjects.
 % GLM
 For each naturalistic stimulus, we model hemodynamic activity via several
-general linear model (GLM) $t$-contrasts that are based on annotations
-of selected stimulus features.
+    general linear model (GLM) $t$-contrasts that are based on annotations of
+    selected stimulus features.
 % VIS
@@
 % no refs in abstract (probably)
-%\citep{sengupata2016extension}.
-% results: group AV
-On a group level, results for a visual movie stimulus show significantly increased hemodynamic
-activity spatially overlapping with a traditionally localized PPA but also extending into earlier visual
-cortices.
+%\citep{sengupata2016extension}.  results: group AV
+On a group level, results for a visual movie stimulus show significantly
+    increased hemodynamic activity spatially overlapping with a traditionally
+    localized PPA but also extending into earlier visual cortices.
 % results: group AD
-Results for the audio-description stimulus reveal significant activation restricted to the
-anterior part of the PPA.
+Results for the audio-description stimulus reveal significant activation
+    restricted to the anterior part of the PPA.
 % results: individual AD
@@
 Results suggest that increased activation in the PPA during the perception of
-static pictures generalizes to the perception of spatial information embedded in
-an audio-visual movie and an exclusively auditory stimulus.
+    static pictures generalizes to the perception of spatial information
+    embedded in an audio-visual movie and an exclusively auditory stimulus.
 % conclusion: PPA has subregions
-Our results provides further evidence that the PPA can be divided into
-functional subregions.
+Our results provide further evidence that the PPA can be divided into functional
+    subregions.
 % localizer substitute
 An auditory narrative might substitute a visual paradigm to localize the PPAs
-anterior part in visually impaired subjects.\todo{very bold claim to be written
-in the abstract}
+    anterior part in visually impaired subjects.\todo{very bold claim to be
+    written in the abstract}
 
@@
 
+\noindent Generally
+
+\begin{itemize}
+    \item adopt some phrasing from the Speech-Anno-Paper
+    \item there is no "cue about" in the English language? alternatives are
+        "give a hint on/about", "indicate"; changes the sentences but should
+        ask Alex
+\end{itemize}
+
 \noindent Intro:
@@
     \item make more concise if applicable
-    \item add counts of intro, results, discussion respectively
 \end{itemize}
@@
 \begin{itemize}
-    \item -
+    \item Figure of regressor correlations: maybe write out in full the name of
+        regressors (instead of pointing to the table)
 \end{itemize}
@@
     \item kürzen (war nicht ganz einfach)
-    \item adapt captions of result tables to new phrasing in intro / method
+    \item table of results: how many decimal points?
+    \item how much details regarding procedure in Sengupta?
+    \item ggf. berichten welcher VIS Kontraste jeweils genommen wurde
+    \item check if captions of figs and tables now (really) match phrasing
+        in intro / method
     \item Simons Kommentare, bei denen ich mitunter anderer Meinung bin
-    \item ggf. berichten welcher VIS Kontraste jeweils genommen wurde
+
 \end{itemize}
@@
 \begin{itemize}
-    \item umstrukturieren \& ggf. schon kürzen gemäß neuer Schwerpunktsetzung
-    \item umschreiben gemäß neuer Schwerpunktsetzung
-    \item mehr zum Thema VIS( "best contrast was chosen")
-    \item \citep{bartels2004mapping, hasson2004intersubject}
+    \item Discussion is restructured
+    \item current structure makes a lot things easier/concise/more logical to
+        convey, and eventually easier to read and the message to grasp
+    \item as Simon stated I would be interesting to discuss differences between
+        contrasts (and make wild assumptions) but this will exceed the word
+        limit by far
+    \item mehr zum Thema VIS? ("best contrast was chosen")
 \end{itemize}
@@
 We hypothesize[d] that whole-brain analyses will/would reveal increased
-hemodynamic activity spatially constrained \todo{i.e. not activity all over the
-place} to the PPA as functionally defined by a visual localizer experiment using
-pictures done with the same subjects \citep{sengupta2016extension}.
+hemodynamic activity spatially constrained to the PPA as functionally defined by
+a visual localizer experiment using pictures done with the same subjects
+\citep{sengupta2016extension}.
 
@@
 be which would be more practicable to assess brain functions in visually
-impaired persons.\todo{phrasing}
+impaired persons.
 % results: group
@@
 an auditory naturalistic stimulus.
-
-\todo[inline]{the topic anterior vs. posterior is mentioned at the end of the
-intro for the first time; might be "surprising" but that is in line how the
-story went (it's mentioned in the abstract though)}
 
@@
 \tabularnewline
-se\_new & noun cueing an unfamiliar setting & \aoSenewAll & \aoSenewI & \aoSenewII & \aoSenewIII & \aoSenewIV & \aoSenewV & \aoSenewVI & \aoSenewVII & \aoSenewVIII
-\tabularnewline
-se\_old & noun cueing a recurring setting & \aoSeoldAll & \aoSeoldI & \aoSeoldII & \aoSeoldIII & \aoSeoldIV & \aoSeoldV & \aoSeoldVI & \aoSeoldVII & \aoSeoldVIII
+se\_new & noun describing an unfamiliar setting & \aoSenewAll & \aoSenewI & \aoSenewII & \aoSenewIII & \aoSenewIV & \aoSenewV & \aoSenewVI & \aoSenewVII & \aoSenewVIII
+\tabularnewline
+se\_old & noun describing a recurring setting & \aoSeoldAll & \aoSeoldI & \aoSeoldII & \aoSeoldIII & \aoSeoldIV & \aoSeoldV & \aoSeoldVI & \aoSeoldVII & \aoSeoldVIII
 \tabularnewline
@@
 
-\subsubsection{Events related to low-level perception / perceptual confounds}
+\subsubsection{Events related to low-level perception / low-level perceptual
+confounds}
 
@@
 The events of the movie cut related categories and \texttt{no\_cut} events were
-modeled as impulse events.\todo{actually, it was a box car of 200 ms starting
-with the cut}.
+modeled as impulse events.\todo{box car of 200 ms starting with the cut}.
 %
@@
 we also implemented the regressors based on nouns used by the
-audio-description's narrator to cue switches to another setting (categories
+audio-description's narrator to indicate a switch to another setting (categories
 \texttt{se\_new} and \texttt{se\_old}).
@@
 % why se_new & se_old were not used in the primary contrasts
-The categories of nouns cueing a setting that occurred for the first time
+The categories of nouns indicating a switch to a setting that occurred for the first time
 (\texttt{se\_new}) or a setting that recurred during the plot (\texttt{se\_old})
@@
 c) the narrator is often lacking behind a short dialogue or a change of the
-soundscape that might already cued a change of settings.
+soundscape that might already indicate a change of settings.
 % furniture
@@
 \todo[inline]{why was done? narrator and cuts to other setting are "somewhat"
-correlated; and now what? -> cf. results and discussion}
+correlated; and now what? -> cf. discussion, part "random shower thoughts"}
 % control contrasts
@@
 correlated with moments of cuts as cuts might possibly be correlated with a
-change of the soundscape also giving an auditory cue of switching to another
+change of the soundscape also giving an auditory hint of switching to another
 setting.
@@
     Contrast 6-9 serve as negative control.
-    Contrast 10 serves as control for moments when the narrator cues the
-    listener about a switch of settings, events that could be correlated with a
+    Contrast 10 serves as control for moments when the narrator indicates the
+    a switch of settings, events that could be correlated with a
     change of the soundscape.}
@@
     Contrast 1-8 aim to isolate the PPA.
-    \texttt{non-spatial categories} refers to the to the categories
+    \texttt{non-spatial categories} refers to the categories
     \texttt{body}, \texttt{bodypart}, \texttt{fahead},
@@
 
-\todo[inline]{SE: Figures with group results: würde da wahrscheinlich weiter
-rein zoomen, um genauer den visuellen Kortex zu zeigen; vor allem muss man
-sagen: bei FFA/PPA etc sind flatmaps/inflated brains standard; COH: imo it is
-important that we do not have clusters all over the brain}
+\todo[inline]{SE: in Figure weiter reinoomen; bei FFA/PPA etc sind
+flatmaps/inflated brains standard; COH: imo it is important that we do not have
+clusters all over the brain}
 
@@
 schwer abzulesen; lieber eine andere Farbskala (spectral sequence?) nutzen; COH:
-yes, I know it is kinda difficult, figures will be honed at the very end}
+this figure is my end game boss}
 
@@
 % study goal
-The goal of this study was to investigate if annotated cues about the spatial
+The goal of this study was to investigate if annotated hints about the spatial
 layout embedded in two naturalistic stimuli correlate with increased hemodynamic
-activity in the PPA that was defined using a visual localizer experiment within
-the same subjects \citep{sengupta2016extension}.
+activity in the PPA.
 % group level
@@
 analyses of the movie and the audio-description (Z>3.4; p<.05, cluster
-corrected) to results gained from the visual localizer.
+corrected) to results gained from a traditional visual localizer
+\citep{sengupta2016extension}.
 % individual level
@@
 the performance of the exclusively auditory naturalistic stimulus as a
-substitute for a visual paradigm to localize the PPA.\todo{``localize''}
+substitute for a visual paradigm to "localize" [?] the PPA.
 % NeuroVault
 Unthresholded $z$-maps of all contrasts on a group level as well as individual
-results of the primary $t$-contrasts co-registered to the group-template can
-found at \href{https://neurovault.org/collections/KADGMGVZ/}{NeuroVault}.
-\todo{private collection}
+results of the primary $t$-contrasts co-registered to the group-template (MNI152 space) can found at
+\href{https://neurovault.org/collections/KADGMGVZ/}{NeuroVault}.  \todo{private
+collection}
 
@@
 % AV intro
-First, we analyzed data from the audio-visual movie offering a visual but
-ecologically more valid stimulation.
+First, we analyzed data from the movie offering a visual but ecologically more
+valid stimulation than static pictures.
 % AV primary contrast
@@
 parahippocampal cortex, the occipital and temporal fusiform gyrus and lingual
-gyrus.
+gyrus.\todo{check that}
 % precuneus
@@
         (cf. \citep{hanke2014audiomovie}).
-        Black: outline of overlapping individual PPA ROIs.
+        Black: outline of overlapping individual PPA ROIs
+        \citep{sengupta2016extension}.
         The results of audio-description's primary $t$-contrast (blue) that
-        compares geometry-related nouns to non geometry-related nouns spoken by
-        the audio-description's narrator (\texttt{geo, groom > all non-geo})
+        compares geometry-related nouns spoken by the narrator to non-spatial
+        nouns (\texttt{geo, groom} > all non-spatial
+        categories)
         are overlaid over the movie's primary $t$-contrast (blue) that compares
         cuts to a new setting with cuts to a familiar perspective
-        (\texttt{vse\_new > vpe\_old})
-   \citep{sengupta2016extension}.}
+        (\texttt{vse\_new > vpe\_old}).
+        }
     \label{fig:group-slices}
@@
 
-\paragraph{individual results}
-
 \todo[inline]{if we here report procedure of Sengupta as detailed as it is now
@@
 % procedure a)
-Starting with the most conservative contrast (strict set) and a threshold of t =
-2.5, we looked for clusters with at least 20 voxels (using AFNI).
+Starting with the most conservative contrast (\textit{strict} set) and a
+threshold of t = 2.5, we looked for clusters with at least 20 voxels (using
+AFNI).
 % procedure b)
@@
 % Sengupta: procedure b)
-If a cluster was not found or not isolated, we used a contrast from the relaxed
-set, or finally the simple set, and repeated the process until we found a
-cluster that matched the expected anatomical location based on literature
-\citep{epstein1998ppa}.
-
-% naturalisti stimuli: intro
-In the current study, time series of all subjects were analyzed both in subject
-space (Z>2.3, p<.05 cluster-corrected) and group space ).
+If a cluster was not found or not isolated, we used a contrast from the
+\textit{relaxed} set, or finally the \textit{simple} set\todo{not used for PPA},
+and repeated the process until we found a cluster that matched the expected
+anatomical location based on literature \citep{epstein1998ppa}.
+
+% one contrast to localize them all; "...and Z>3.4 for all"
+Contrary to \citep{sengupta2016extension}, we used the same contrast of each
+naturalistic stimulus and the same threshold for all subjects (Z>2.3, p<.05
+cluster-corrected for the analysis in subject-space; Z>3.4, p<.05 for the
+analysis in group-space).
 % subject space -> NeuroVault
-Results of the analyses that were performed in each subject's [subject-]space
-(unthresholded $z$-maps and thresholded $z$-maps, Z>2.3, p<.05 cluster
-corrected) can be found in the accompanying dataset. \todo{Neurovault does not
-like unstandardized spaces}
+Results of the analyses that were performed in subject-space can be found in the
+accompanying dataset. \todo{Neurovault does not like unstandardized spaces}
 % here report in group space
-For better comparisons of subjects, we here report results from the analyses
-performed in group space (Z>3.4, p<.05 cluster-corrected)
-% one contrast to localize them all; "...and Z>3.4 for all"
-Contrary to the procedure in \citep{sengupta2016extension}, we used the same
-contrast of each naturalistic stimulus and the same threshold [(Z>3.4, p<.05
-cluster corrected)] for all subjects.
-
-% AV
-Results of the primary AV contrast yielded statistically significant bilateral
-clusters in five subjects, unilateral right clusters in six subjects (of
-which one subjects yielded a unilateral cluster in the visual localizer), and a
-unilateral left cluster in one subject.
-% difference to dedicated localizer
-We find homologous clusters in sub-20, whereas the dedicated visual localizer
-yielded only one cluster in the right hemisphere.
-
-% report here in group
-Results of the primary AD contrast yielded statically significant bilateral
-clusters in nine subjects, and one cluster in the left hemisphere of sub-09,
-that are within or overlapping with the individual PPA.
-% subj-04
-In sub-04, two homologous clusters are apparent, whereas the dedicated localizer
-(and AV stimulus) yielded only one cluster in the right hemisphere.
+For better comparisons of subjects, we report results from the analyses
+performed in group space.
 % ref to figure
@@
 significant clusters in almost all subjects.
+
+% AV
+Results of the primary AV contrast yielded bilateral clusters in five subjects,
+a unilateral right cluster in six subjects (of which one subjects yielded a
+unilateral cluster in the visual localizer), and a unilateral left cluster in
+one subject.
+% difference to dedicated localizer
+We find homologous clusters in sub-20, whereas the dedicated visual localizer
+yielded only one cluster in the right hemisphere.
+
+% report here in group
+Results of the primary AD contrast yielded bilateral clusters in nine subjects
+that are within or overlapping with the individual PPA.
+% subj-04
+In sub-04, two homologous clusters are apparent, whereas the dedicated localizer
+(and AV stimulus) yielded only one cluster in the right hemisphere.
+% sub-09
+In sub-09 the analysis yielded one cluster in the left-hemispheric PPA.
 
@@
 
-% Bland-Altman-Plots: why they were done
-To better depict/convey the agreement and difference between individual results
-of the visual localizer and the primary AD contrast, we created one
-Bland-Altman-Plots for each of the 14 subjects (see Figure
-\ref{fig:bland-altman}).
+\todo[inline]{BA-plots only shortly mentioned now}
+% Bland-Altman-Plots
+To better depict the agreement and difference between individual results of the
+visual localizer and the primary AD contrast, we created Bland-Altman-Plot that
+visualize mean and difference of two spatially corresponding $z$-values (see
+Figure \ref{fig:bland-altman}).
 % top KDE plot
@@
 
-\todo[inline]{I tried to keep it concise but detailed; if individual contrasts
-are mentioned (enumerated at the moment)}
+\todo[inline]{I tried to keep it concise but detailed; individual contrasts
+are given but as numbers}
 
@@
 % statement/answer
-Results suggest that our findings do not depend on one specific contrasts but
-are robust across differently designed contrasts.\todo{concluding statement
+Results suggest that our findings are robust across differently designed
+contrasts.\todo{concluding statement
 often feels like interpretation}
@@
 Reliably across the five contrasts of the AV stimulus, we find bilaterally
-significant clusters also in the ventral precuneal cortex / posterior cingulate
-gyrus (i.e. restrosplenial region; contrasts 1, 4, 5) and lateral occipital
-cortex (contrasts 1, 2, 4, 5)
+significant clusters also in the ventral precuneal cortex and posterior
+cingulate gyrus (i.e. restrosplenial region; contrasts 1, 4, 5) and lateral
+occipital cortex (contrasts 1, 2, 4, 5)
 % AD; LOC: AV cluster are more medial, AD clusters are more lateral
@@
 significant clusters in the ventral precuneus (all except contrasts 8), lateral
-occipital cortex (bilateral in 4 contrasts 1 to 4, unilateral in contrasts 6 and
+occipital cortex (bilateral in contrasts 1 to 4; unilateral in contrasts 6 and
 7), and superior temporal cortices (bilateral in contrasts 3, 6, 7; unilateral
 right in contrast 2).
+
 % non-systematic
-Contrast 2 also shows bilateral clusters in the anterior cingulate gyrus and
-right paracingulate gyrus (frontal medial cortex), right putamen, and right
+Lastly, contrast 2 of the AD stimulus  also shows bilateral clusters in the
+anterior cingulate gyrus and right paracingulate gyrus (frontal medial cortex),
+right putamen, and right frontal pole.
+%
+Contrast 3 shows clusters bilaterally in the anterior cingulate gyrus and left
 frontal pole.
 %
-Contrast 3 shows clusters bilaterally in the anterior cingulate gyrus and
-left frontal pole.
-%
-Contrast 6 shows one additional cluster also in the right medial frontal cortex.
+Contrast 6 shows one additional cluster also in the right medial frontal
+cortex.\todo{fsleyes (again) to match text such that clusters in Figure 5 are
+easily attributable to region}
 
@@
 Contrast 12 (\texttt{vse\_new} > \texttt{vse\_old}, \texttt{vpe\_old}) revealed
-one cluster in the right posterior hippocampus. \todo{dorsally of PPA}
+one cluster in the right posterior hippocampus. \todo{definitively hippocampus,
+dorsally of PPA}
 
@@
 
+\todo[inline]{Discussion: explains how results fill gap identified in
+intro}
+
+\todo[inline]{typically done by recapitulating the results, discussing
+limitations, and then revealing how the central contribution may catalyze future
+progress}
+
+\todo[inline]{provides caveats to the interpretation describes how the paper
+advances the field by providing new opportunities}
+
 \section{Discussion}
-
-\todo[inline]{SE: die result-synopsis noch nicht optimal. Vielleicht gehe ich
-aber auch mit der falschen Perspektive ran? Für mich würde der Vergleich
-"localizer vs naturalistic" im vordergrund stehen, AD vs AV dann eine sehr
-spannende aber logisch nachgeschaltete Frage sein.}
 
@@
 
-\todo[inline]{SE: Bei Ergebnissen \& Diskussionen zu Stability fehlt mir
-irgendwie immer der Kontext, wie sich die Kontraste denn unterschieden haben und
-welche davon z.B. im Ergebnis wo von den anderen abgewichen haben. Das würde ja
-wichtige Hinweise geben; COH: imo discussing that will let the paper get way out
-of hand}
-
-\todo[inline]{SE: VIS vs AV vs AD: Wer liefert was über die PPA. Dieser
-Vergleich bzw. die Diskussion über Gemeinsamkeiten \& Unterschiede fehlt mir
-etwas}
-
-\todo[inline]{SE: RSC etc: Irgendwie waren die bis zu Diskussion eher ein
-afterthought. Daher etwas überraschend, vielleicht in Einleitung und Results
-schon mehr bringen; COH: afterthought, for sure; It was highly probable that RSC
-would show up but it wasn't aim of the study (had no ROIs for it anyway); imo
-this is an issue of ``nice story telling'' vs. HARKing}
-
-\todo[inline]{convey better that we do not have lots of ``random clusters''}
-
-\todo[inline]{discussion explains how results fill gap identified in
-intro}
-
-\todo[inline]{provides caveats to the interpretation describes how the paper
-advances the field by providing new opportunities}
-
-\todo[inline]{typically done by recapitulating the results, discussing
-limitations, and then revealing how the central contribution may catalyze future
-progress}
-
-\todo[inline]{first paragraph summarizes the important findings from the results
-section, focusing on their meaning}
-
-% previous studies: visual
+% previous studies
 Previous studies reported bilaterally increased hemodynamic activity in the PPA
@@
 mixed results \citep{aziz2008modulation}.
-% we use similar statistical models but with naturalistic stimuli
-Similarly to previous studies that used small sets of experimentally controlled
-stimuli, we also used GLMs to investigate hemodynamic brain activity during two
-naturalistic stimuli.
-% more than just one contrast
-For both naturalistic stimuli, we computed several $t$-contrasts that differed
-in the contrasted categories of stimulus features and the amount of available
-data to test the robustness of our findings.
-% comparison to localizer experiment
-We compare results of the primary contrast of each stimulus on the level of
-individual subjects to results that we gained from a visual localizer experiment
-done with the same subjects \citep{sengupta2016extension}.
-% summary of results main finding
-Results of our whole-brain analyses suggest that the perception of verbal
-``spatial information'' embedded in an auditory narrative contrasted with
-``non-spatial information'' is correlated with increased activation in the
-anterior PPA of both hemispheres.
-
-% to do
-\todo[inline]{Other possible ``honourable'' mentions; here (?), and in the
-following discussion?}
-
-\begin{itemize}
-    \item RSC
-    \item what could be LOC / OPA
-    \item AV; should (shortly) be discussed
-    \item robustness (imo shortly discussed; it is about robustness not about
-        how all contrasts are different in detail and how results differ in
-        detail; yes, totally interesting but out of scope
-    \item discuss negative contrasts?
-\end{itemize}
-
-% The second through fourth paragraphs may deal with potential weaknesses
-% linking it to the relevant literature or how future experiments can deal
-% with these weaknesses.
-
-% The fifth paragraph may then culminate in a description of how the paper moves
-% the field forward.
-
-% Discussion paragraphs often conclude by describing a clever, informal way of
-% perceiving the contribution or by discussing future directions that can extend
-% the contribution.
-
-% step by step, the reader thus learns to put the paper’s conclusions into the
-%right context.
+% current study: similar
+In line with previous studies, we use here also operationalize spatial
+perception via general linear model (GLM) $t$-contrasts.
+% current study: dissimilar
+Contrary to previous studies, our current operationalization is not based on
+carefully designed sets of stimuli but based on annotated stimulus features
+incidentially occurring in an audio-visual movie and its audio-description.
+% group AV
+On a group level, whole brain-analysis results for the movie stimulus show
+signifcantly increased hemodynamic activity spatially overlapping with a
+traditionally localized PPA but also extending into earlier visual cortices.
+% group AD
+Results for the audio-description stimulus reveal significant activation
+restricted to the anterior part of the PPA.
+% individual level
+On an individual level, results of the audio-description show significant
+bilateral clusters in the anterior PPA of nine subjects and significant
+unilateral clusters in two subjects.
+% meaning 1
+Results suggest that increased activation in the PPA during the perception of
+static pictures generalizes to the perception of spatial information embedded in
+a movie and an exclusively auditory stimulus.
+% meaning 2
+Our results provide further evidence that the PPA can be divided into functional
+subregions. An auditory narrative might substitute a visual paradigm to localize
+the PPAs anterior part in visually impaired subjects.
 
@@
 \subsubsection{AV: group}
+
+\todo[inline]{AV is "intermediate step": natural but still visual; similar:
+\citep{bartels2004mapping, hasson2004intersubject} (mention here already or at
+the end of topic)}
+
 % AV stimulus
@@
 Clusters also expand into more posterior regions (occipital fusiform gyrus,
-lingual gyrus, and intracalcarine cortex).\todo{which of these regions (do not
-overlap) with group ROI?}
+lingual gyrus, and intracalcarine cortex).\todo{which of these regions do (not)
+overlap with group ROI?}
+
+\todo[inline]{bigger size of clusters is not surprising; imo still impressive
+low amount of random clusters in the brain)}
+
 % confound of higher perception
@@
 attributed to the fact that we averaged the content of individual frames after a
-cut and did not control for confounding features like depicted faces or
-objects,and low-level visual features.
-% cross-modal control purpose?
-\todo[inline]{better frame that it is conceptual/cross-modal control; but what
-do the results tell us? yes, it ``kinda works'' but \dots?}
-\todo[inline]{concluding statement regarding AV vs AD and cross-modality of
-results?}
-
-\todo[inline]{I read Aziz again: visual localizer: radius of 16 mm around peak
-    voxel in each hemisphere = PPA; sentence experiment: reduced activity only
-    in left PPA, and only for famous places vs famous faces; I think they ran
-    their f-test on the average of the PPA voxels! anyway: their analysis is
-complicated, yet not sophisticated}
+cut and did not control for confounding features like depicted faces or objects
+or attentional focus of subjects.
+% shortcomings
+m.a.W.: Results of the AV stimulus that we ran as a conceptual control are
+tempered by using different kind of movie cuts regardless of the visual content
+of the movie frame after the respective cuts.
+% which leads to the ``blurred'' results
+
+\todo[inline]{we exploit a confound induced by cinematography; field size
+decreases later in the movie; this is a confound based on cinematography => the
+stimulus changes over time; (ergo: man sollte sich bißchen mit Cinematographie
+auskennen und/oder stimulus annotation in model nehmen, wenn man was mit movies
+machen will)}
+
+\todo[inline]{SE: VIS vs AV vs AD: Wer liefert was über die PPA. Dieser
+Vergleich bzw. die Diskussion über Gemeinsamkeiten \& Unterschiede fehlt mir
+etwas}
+
+% summary: nevertheless
+\todo[inline]{Nevertheless, group results from analysis using more natural
+visual stimulation suggest that... (cf. \citep{bartels2004mapping,
+hasson2004intersubject})}
+
+\todo[inline]{approach of contrasting cuts was adventorous, annotation of speech
+suited better in the first place, and the auditory thing ist more interesting
+anyway, we did not aim for a substition of classic localizer via movie; but if
+you wanna do it, you should...:}
+
+Since the capability to isolate clusters or networks correlating with specific
+perceptual (or cognitive) processes is influenced by the amount of annotated
+stimulus features further studies focusing on visual perception should annotate
+and model visual features of naturalistic stimuli more rigorously.
+% solution
+Future studies that aim to use a movie to localize different visual areas should
+extensively annotate the content of frames (e.g. using the open-source solution
+``Pliers'' for feature extraction from a visual naturalistic stimulus;
+\citep{mcnamara2017developing}) and record the subject's visual attention via
+eye-tracking.
 
 \subsubsection{AD: group}
+
+\todo[inline]{since the picture of PPA is far more unclear in auditory
+domain and we have a pretty nice stimulus with a narrator and a
+pretty nice annotation, we focussed on the audio-description}
+
+\todo[inline]{Aziz: reduced activity only in left PPA, and only for famous
+places vs famous faces; I think they ran their f-test on the average of the PPA
+voxels! anyway: their analysis is complicated, yet not sophisticated}
 
@@
 sentences (describing unknown and famous places and faces), we modeled events
-from on- to offset of single words (that cue the listener about the missing
-visual content).
+from on- to offset of single words (that indicats the visual content to the
+listener).
 % conclusion
@@
 
-\todo[inline]{individual results should be incorporated into above section;
-depends on long discussion of individual results will be}
-
-\subsubsection{AV stimulus}
-
-\todo[inline]{was not aim of study; results of primary AV contrasts are in plots
-    if individual; Bland-Altman-Plots focus on primary AD contrast alone}
-
 \subsubsection{AD: individuals}
@@
     PPA are higher in AD contrasts than in contrast of localizer}
+
+\todo[inline]{We hypothesize[d] that an exclusively auditory stimulus can/could
+localize the PPA in individual subjects, and thus substitute a visual experiment
+be which would be more practicable to assess brain functions in visually
+impaired persons.}
 
@@
 
+\subsubsection{AD: shortcoming}
+
+% optimal stimulus type in vision
+In the visual domain, landscapes and not pictures of landmarks or buildings are
+considered to be the ``optimal'' stimulus type (cf. Epstein (1998, 1999, 2003,
+2008).\todo{check references}
+% cateogries in primary contrasts
+In the current study's primary contrast, we compared verbal hints about
+landmarks ((\texttt{geo}; often buildings or other single aspects of a whole
+scene) and elements defining the geometry of a room or locale (\texttt{groom})
+to non-spatial hints.
+% we did not choose se\_new and se\_old
+We did not choose the categories that contained switches from one setting to
+another (\texttt{se\_new} and \texttt{se\_old}) which one might assume to
+contain the auditory equivalent to the ``optimal'' visual stimulus type.
+% why not se\_new or se\_old
+The categories \texttt{se\_new} and \texttt{se\_old} were actually
+heterogeneous: they rarely contained whole and thus a vague verbal descriptions
+of landscapes (e.g. ``in a football stadium'', ``Forrest is running through the
+jungle'') but mostly landmarks or buildings, and also non-spatial hints (e.g.
+``Jenny as a teenager``).
+% further studies
+Given that humans can identify the gist of a rich visual scene within the
+duration of a single fixation \citep{henderson2003human} further studies might
+investigate if categories of holistic but vague verbal descriptions of
+landscapes correlate with differential hemodynamic activity in the PPA compared
+to more concrete spatial hints.
+% future studies
+Hence, future studies might investigate if a homogenous category of wholistic
+but vague verbal descriptions (e.g. ``a mountain landscape'') compared to a
+homogenous categories of more specific verbal descriptions of landmarks (e.g.
+``a beacon'') or houses (e.g. ``farmhouse'', ``apartment building'') lead to
+different levels of hemodynamic activity.
+
 \subsection{Robust (results) across contrasts}
 
+\todo[inline]{SE: Bei Ergebnissen \& Diskussionen zu Stability fehlt mir
+irgendwie immer der Kontext, wie sich die Kontraste denn unterschieden haben und
+welche davon z.B. im Ergebnis wo von den anderen abgewichen haben. Das würde ja
+wichtige Hinweise geben; COH: indeed very interesting but discussing that will
+let the paper get way out of hand}
+
+\todo[inline]{yeah, we have shortcomings but, look, we have a pattern of
+spatially restricted clusters across contrasts (and stimuli)}
+
+% more than just one contrast
+For both naturalistic stimuli, we computed several $t$-contrasts that differed
+in the contrasted categories of stimulus features and the amount of available
+data to test the robustness of our findings.
 % why we did a couple of contrasts
-For both stimuli we created several contrasts that varied the amount of events
-available for the analysis and how well the annotated events within categories
-on average matched the stimulus type that we assumed to be preferentially
-processed in the PPA.
+m.a.w.: For both stimuli we created several contrasts that varied the amount of
+events available for the analysis and how well the annotated events within
+categories on average matched the stimulus type that we assumed to be
+preferentially processed in the PPA.
 
 \subsubsection{PPA}
+
+% PPA AV
+Regarding contrasts of the AV stimulus, all five contrasts show significant
+bilateral clusters in the PPA but also extending into more posterior brain
+regions
+\todo[inline]{cf. discussed shortcomings}
+
 % PPA AD
@@
 bilateral clusters in the anterior part of the group PPA overlap.
-% PPA AV
-Regarding contrasts of the AV stimulus, all five contrasts show significant
-bilateral clusters in the PPA but also extending into more posterior brain
-regions.
+
 % results indicate robustness
@@
 averaged might be.
-
-% ``confounding'' clusters
-Despite performing a whole brain analysis, we do not find many [random] clusters
-in single contrasts or even systematically across contrasts that hamper the
-interpretation of results.\todo{ouff\dots}
-% AV: null results regarding attention and eye movements
-For example in the AV results, we do not find significant clusters that could be
-attributed to cognitive processes like attention or eye movements\todo{could
-    already already be mentioned in discussion of primary contrasts}
-% AD: auditory cortices
-Nevertheless, contrasts of the AD stimulus that compare verbal cues about the
-change of a setting (\texttt{se\_new} or \texttt{se\_old}) to all non-spatial
-categories (cf. contrasts 2, 3, 6, 7) show significant clusters in (primary and
-secondary) auditory cortices.
-% averaging vs. nuisance regressors
-This suggests that variance correlating with lower level auditory processes was
-not averaged out across trials and nuisance regressors did not capture enough
-variance.\todo{ouf\dots}
-% possible reason
-Significant clusters in auditory cortices could be correlating with a possible
-change of the soundscape when the narrator of the audio-description (or a cut in
-the movie) switches to a another setting.
-% concluding statement
-Thus, investigators that use model-driven methods to investigate brain functions
-using naturalistic stimuli should (extensively) annotate the stimulus material
-and test for correlations among variables.
 
@@
 
+\todo[inline]{SE: RSC etc: Irgendwie waren die bis zu Diskussion eher ein
+afterthought. Daher etwas überraschend, vielleicht in Einleitung und Results
+schon mehr bringen; COH: afterthought, for sure; It was highly probable that RSC
+would show up but it wasn't aim of the study (had no ROIs for it anyway); imo
+this is an issue of ``nice story telling'' vs. HARKing}
+
 % but RSC
@@
     \item \citep{silson2019posterior}
-    \item \citep{baldassano2016two}: RSC appears to be most directly involved in orienting the viewer to the structure of the environment (both within and beyond the borders of the presented image) for the purpose of navigational planning; it encodes both absolute location and facing direction [Vass and Epstein, 2013; Epstein and Vass, 2014; Marchette et al., 2014], integrates across views presented in a panoramic sequence [Park and Chun, 2009], and shows strong familiarity effects [Epstein et al., 2007a,b].
+    \item \citep{baldassano2016two}:
+    \item RSC appears to be most directly involved in orienting the viewer to
+    the structure of the environment (both within and beyond the borders of the
+presented image) for the purpose of navigational planning; it encodes both
+absolute location and facing direction [Vass and Epstein, 2013; Epstein and
+Vass, 2014; Marchette et al., 2014], integrates across views presented in a
+panoramic sequence [Park and Chun, 2009], and shows strong familiarity effects
+[Epstein et al., 2007a,b].
 \end{itemize}
@@
 
-\subsection{negative controls and cross-modal controls}
-
-\todo[inline]{could be mentioned in a few sentences. But above topics a far too
-much still; better embed somewhere above}
-
-% AV: contrast with AV nouns
-Compare Figure \ref{fig:reg-corr}: nouns that cue change to a new
-setting are correlated  with cuts to a new setting (vse\_new; r$\approx$0.3;
-second highest correlation of a verbal cue category with a cut category; AND:
-nouns that cue change to a familiar setting are somewhat correlated with cuts to
-a familiar setting (se\_old; r$\approx$0.4; highest correlation of a verbal
-category with a cut category).
-
-% AD: correlation of these nouns with cuts
-Compare Figure \ref{fig:reg-corr}: nouns that cue change to a new setting are
-correlated  with cuts to a new setting (vse\_new; r$\approx$0.3; second highest
-correlation of a verbal cue category with a cut category.
-
-\subsection{shortcomings}
-
-\todo[inline]{SE: Würde nicht so sehr auf Shortcomings eingehen}
-
-\todo[inline]{different level of alertness during paradigms}
-
-\subsubsection{AV stimulus}
-
-\todo[inline]{AV: field size decreases later in the movie; this is a confound
-based on cinematography => the stimulus changes over time; AV analysis exploits
-confound structure}
-
-\todo[inline]{imo opening the pandora's box of the AV shortcomings especially at
-the end of the paper should be kept to a minimum of text}
-
-% focus of study
-The focus of the current study was to investigate if significantly increased
-hemodynamic activity in the PPA correlates with spatial information (compared to
-``non-spatial'' information) during a naturalistic auditory stimulus.
-% shortcomings
-Results of the AV stimulus that we ran as a conceptual control are tempered by
-using different kind of movie cuts regardless of the visual content of the movie
-frame after the respective cuts.
-% which leads to the ``blurred'' results
-Hence we got visual confounds / clusters extending in to early visual areas.
-% further studies
-Since the capability to isolate clusters or networks correlating with specific
-perceptual (or cognitive) processes is influenced by the amount of annotated
-stimulus features further studies focusing on visual perception should annotate
-and model visual features of naturalistic stimuli more rigorously.
-% solution
-Future studies that aim to use a movie to localize different visual areas should
-extensively annotate the content of frames (e.g. using the open-source solution
-``Pliers'' for feature extraction from a visual naturalistic stimulus;
-\citep{mcnamara2017developing}) and record the subject's visual attention via
-eye-tracking.
-
-\subsubsection{AD contrast}
-
-% optimal stimulus type in vision
-In the visual domain, landscapes and not pictures of landmarks or buildings are
-considered to be the ``optimal'' stimulus type (cf. Epstein (1998, 1999, 2003,
-2008).\todo{check references}
-% cateogries in primary contrasts
-In the current study's primary contrast, we compared verbal cues regarding
-landmarks ((\texttt{geo}; often buildings or other single aspects of a whole
-scene) and elements defining the geometry of a room or locale (\texttt{groom})
-to non-spatial cues.
-% we did not choose se\_new and se\_old
-We did not choose the categories that contained switches from one setting to
-another (\texttt{se\_new} and \texttt{se\_old}) which one might assume to
-contain the auditory equivalent to the ``optimal'' visual stimulus type.
-% why not se\_new or se\_old
-The categories \texttt{se\_new} and \texttt{se\_old} were actually
-heterogeneous: they rarely contained whole and thus a vague verbal descriptions
-of landscapes (e.g. ``in a football stadium'', ``Forrest is running through the
-jungle'') but mostly landmarks or buildings, and also non-spatial cues (e.g.
-``Jenny as a teenager``).
-% further studies
-Given that humans can identify the gist of a rich visual scene within the
-duration of a single fixation \citep{henderson2003human} further studies might
-investigate if categories of holistic but vague verbal descriptions of
-landscapes correlate with differential hemodynamic activity in the PPA compared
-to more concrete spatial cues.
-% future studies
-Hence, future studies might investigate if a homogenous category of wholistic
-but vague verbal descriptions (e.g. ``a mountain landscape'') compared to a
-homogenous categories of more specific verbal descriptions of landmarks (e.g.
-``a beacon'') or houses (e.g. ``farmhouse'', ``apartment building'') lead to
-different levels of hemodynamic activity.
-
-%
-\todo[inline]{shortcoming but nice hypothesis imo}
-%
-Cuts probably correlate with change in setting; change in soundscape anticipates
-narrator (would lower detection power) or occurs in parallel with narrator; cf.
-correlation of cuts to other setting (independent of familiarity) with nouns
-that cue change of setting; cf. control contrasts [which ones?]
-% arnott
-% hypothesis
+\todo[inline]{in any case: the pattern PPA, RSC, LOC is a usual pattern in the
+visual domain; here, it is the usual pattern across across AV and AD contrasts
+-> hypothesis for auditory domain? future research and stuff?}
+
+\subsubsection{not many random cluster}
+
+\todo[inline]{makes sense because it goes full circle to general naturalistic
+stimulus topic and makes transition to negative controls easier (which is
+essentially also "natural stimuli, fuck yeah!}
+
+% ``confounding'' clusters
+Despite performing a whole brain analysis, we do not find many [random] clusters
+in single contrasts or even systematically across contrasts that hamper the
+interpretation of results.\todo{ouff\dots}
+% AV: null results regarding attention and eye movements
+For example in the AV results, we do not find significant clusters that could be
+attributed to cognitive processes like attention or eye movements\todo{could
+already already be mentioned in discussion of primary contrasts}
+
+% AD: auditory cortices
+Nevertheless, contrasts of the AD stimulus that compare (among others) verbal
+hints of the change of a setting (\texttt{se\_new} or \texttt{se\_old}) to all
+non-spatial categories (cf. contrasts 2, 3, 6, 7) show significant clusters in
+(primary and secondary) auditory cortices.
+% averaging vs. nuisance regressors
+This suggests that variance correlating with lower level auditory processes was
+not averaged out across trials and nuisance regressors did not capture enough
+variance.\todo{ouf\dots}
+% possible reason
+Significant clusters in auditory cortices could be correlating with a possible
+change of the soundscape when the narrator of the audio-description (or a cut in
+the movie) switches to a another setting.
+% concluding statement
+Thus, investigators that use model-driven methods to investigate brain functions
+using naturalistic stimuli should (extensively) annotate the stimulus material
+and test for correlations among variables.
+
+\subsubsection{random shower toughts}
+
+Cuts probably correlate with change in soundscape; change in soundscape often
+anticipates narrator (would lower detection power) or occurs in parallel with
+narrator; cf. correlation of cuts to other setting (independent of familiarity)
+with nouns that indicate a change of setting; cf. control contrasts [which
+ones?]
+% arnott hypothesis
 We hypothesize that not just semantic information but also the mere changes of a
-soundscape that cues a listener about a setting's spatial layout of could
-correlate with increased activity in the PPA.
+soundscape that indicate a setting's spatial layout could correlate with
+increased activity in the PPA.
 % arnott
@@
 sounds made by objects (that reveil object's material/identity)}
+
+\subsection{negative controls and cross-modal controls}
+
+\todo[inline]{could be mentioned in a few sentences. But above topics a far too
+much still; better embed somewhere above}
+
+% AV: contrast with AV nouns
+Compare Figure \ref{fig:reg-corr}: nouns that indicate a change to a new setting
+are correlated  with cuts to a new setting (vse\_new; r$\approx$0.3; second
+highest correlation of a verbal hint category with a cut category; AND: nouns
+that indicate change to a familiar setting are somewhat correlated with cuts to
+a familiar setting (se\_old; r$\approx$0.4; highest correlation of a verbal
+category with a cut category).
+
+% AD: correlation of these nouns with cuts
+Compare Figure \ref{fig:reg-corr}: nouns that indicate change to a new setting
+are correlated  with cuts to a new setting (vse\_new; r$\approx$0.3; second
+highest correlation of a verbal hint category with a cut category.
 

### 2021-01-26 paper/main.tex
results: handling & deleting minor todos/comments

@@
     \item adopt some phrasing from the Speech-Anno-Paper
-    \item there is no "cue about" in the English language? alternatives are
-        "give a hint on/about", "indicate"; changes the sentences but should
+    \item there is no "cue about" in the English language? Alternatives are
+        "give a hint on/about", "indicate"; changed the sentences but should
         ask Alex
@@
 \begin{itemize}
-    \item kürzen (war nicht ganz einfach)
-    \item table of results: how many decimal points?
     \item how much details regarding procedure in Sengupta?
     \item ggf. berichten welcher VIS Kontraste jeweils genommen wurde
+    \item results allg. kürzen (war nicht ganz einfach)
+    \item table of results: how many decimal points?
     \item check if captions of figs and tables now (really) match phrasing
@@
 hemodynamic activity in the PPA differs between different semantic stimulus
-categories occurring in spoken language.\todo{phrasing to delineate from Huth
-(2016)}
+categories occurring in spoken language.
 % Aziz' stimuli
@@
 hemodynamic activity in [roughly] the same brain regions the block-designed
-visual localizer.\todo{interpretation?}
+visual localizer.\todo{give an interpretation?}
 % anterior vs. posterior
@@
 \todo[inline]{das Verschieben des Sounds in den Segmenten spiegelt sich auch in
-den unterschiedlichen Counts der Events je Segment wider (AV Bild vs AV Sound vs
-AO Sound)}
+den unterschiedlichen Counts der Events je Segment (s. Tabelle 1 \& 3) wider (AV
+Bild vs AV Sound vs AO Sound)}
 
@@
 
-\todo[inline]{SE: Die Abkürzungen in Figure 1: Da steigt keiner hinter; habe
-jetzt lange darüber gebrütet: Es gibt also kaum eine Korrelation zwischen AD und
-AV?; Also, außer bei fg\_av\_ger\_lr\_diff (wobei da keiner weiss, was das
-bedeutet); COH: what is better: reference to table as it is now (more precise,
-but harder to read) or use non-cryptic words in the figure?}
+\todo[inline]{SE: Die Abkürzungen in Figure 1: Da steigt keiner hinter}
 
@@
 
-\todo[inline]{why was done? narrator and cuts to other setting are "somewhat"
-correlated; and now what? -> cf. discussion, part "random shower thoughts"}
 % control contrasts
@@
 setting.
+
+\todo[inline]{nouns indicating switch to setting  and cuts to other setting are
+"somewhat" correlated; cf. results -> discussion, part "random shower thoughts"}
 
@@
 \todo[inline]{Bland-Altman-Plots: Welche Areale habt ihr als masks
-genommen, FFA ist ja kartiert (Julia Caspers); COH: probaly the caption was
-invisible in the version Simon got? changed the size of the figure so the
-caption is now on the page}
+genommen, FFA ist ja kartiert (Julia Caspers)}
 
@@
 parahippocampal cortex, the occipital and temporal fusiform gyrus and lingual
-gyrus.\todo{check that}
+gyrus.\todo{Havard-Oxford atlas gives 3 different most prob. locations depen.
+on voxel}
 % precuneus
@@
 
-\todo[inline]{if we here report procedure of Sengupta as detailed as it is now
-(imo too long), we probably need to explain the differences between strict,
-relaxed, simple in more detail in the method section and not just reference to
-Sengupta}
-
 % results in detail voxels of significant clusters in PPA ROI (and RSC
@@
 
+\todo[inline]{if we report procedure of Sengupta as detailed as it is now in the
+following paragraph (imo it's too long), we probably need to explain the
+differences between strict, relaxed, simple set in more detail in the method
+section}
 % Sengupta et al., 2016
@@
 % here report in group space
-For better comparisons of subjects, we report results from the analyses
+For better comparisons of subjects, we here report results from the analyses
 performed in group space.
@@
 % Bland-Altman-Plots
-To better depict the agreement and difference between individual results of the
-visual localizer and the primary AD contrast, we created Bland-Altman-Plot that
-visualize mean and difference of two spatially corresponding $z$-values (see
-Figure \ref{fig:bland-altman}).
+To better depict the agreement and difference between the results of the visual
+localizer and the primary AD contrast, we created a Bland-Altman-Plot for every
+subject (see Figure \ref{fig:bland-altman}).
+% what it depicts
+Each subplot visualizes the mean value and difference (localizer minus AD) of
+two spatially corresponding voxels in the unthresholded $z$-maps.
 % top KDE plot
@@
 
-\todo[inline]{I tried to keep it concise but detailed; individual contrasts
-are given but as numbers}
+\todo[inline]{I tried to keep following part concise but detailed; individual
+contrasts are given but as numbers}
 
@@
 % 6 PPA (l/r); RSC (l/r), LOC (l/-), l&r sup.temp.C.; medial pref. c., precun
-% 7 PPA (-/-); RSC (l/r), LOC (l/-), l&r sup.temp.C
+% 7 PPA (-/-); RSC (l/r), LOC (l/-), l&r sup.temp.C.; left frontal pole
 % 8 PPA (-/-); RSC (-/-), LOC (-/-)
@@
 cingulate gyrus (i.e. restrosplenial region; contrasts 1, 4, 5) and lateral
-occipital cortex (contrasts 1, 2, 4, 5)
+occipital cortex (contrasts 1, 2, 4, 5).
 % AD; LOC: AV cluster are more medial, AD clusters are more lateral
-Reliably across the five contrasts of the AD stimulus, we find bilaterally
+Across the five contrasts of the AD stimulus, we find bilaterally
 significant clusters in the ventral precuneus (all except contrasts 8), lateral
@@
 % non-systematic
-Lastly, contrast 2 of the AD stimulus  also shows bilateral clusters in the
-anterior cingulate gyrus and right paracingulate gyrus (frontal medial cortex),
-right putamen, and right frontal pole.
+Lastly, some contrasts of the AD stimulus yielded signficant clusters in regions
+that were not statistically signficant in three or more contrasts.
 %
-Contrast 3 shows clusters bilaterally in the anterior cingulate gyrus and left
-frontal pole.
+Contrast 2 yielded clusters in the anterior cingulate gyrus
+(bilateral), right frontal pole, right frontal medial cortex, and right
+putamen.
 %
-Contrast 6 shows one additional cluster also in the right medial frontal
-cortex.\todo{fsleyes (again) to match text such that clusters in Figure 5 are
-easily attributable to region}
+Contrast 3 shows clusters in the anterior cingulate gyrus (bilateral), left
+frontal pole, and left insular.
+%
+Contrast 7 shows clusters in the left frontal pole and left frontal operculum
+[border to triangularis], left insular.
+%
+Contrast 6 shows one additional cluster in the right medial frontal cortex.
 
@@
 
+\todo[inline]{there is no table/figure for negative control contrasts; we could
+add a reference to NeuroVault (here again) or point to the dataset}
+
 % intro
@@
 
-\todo[inline]{there is no table/figure for negative control contrasts; we could
-add a reference to NeuroVault (here again) or point to the dataset}
-
-\todo[inline]{Discussion: explains how results fill gap identified in
-intro}
-
-\todo[inline]{typically done by recapitulating the results, discussing
-limitations, and then revealing how the central contribution may catalyze future
-progress}
-
-\todo[inline]{provides caveats to the interpretation describes how the paper
-advances the field by providing new opportunities}
-
 \section{Discussion}
+
+% Discussion: explains how results fill gap identified in intro
+
+% typically done by recapitulating the results, discussing limitations, and then
+% revealing how the central contribution may catalyze future
+% progress
+
+% provides caveats to the interpretation describes how the paper
+% advances the field by providing new opportunities
 

### 2021-01-26 paper/main.tex
discussion of prim. contrasts (AD & AV; group)

@@
 \midrule
-3003 & 0 & 5.31 & 22.5 & -45.5 & -12 & 4.53 & -63.3 & -3.72 & r. lingual g.; r. cuneal c., intracalcarine c., bilaterally occipital fusiform g., temporal fusiform c., posterior parahippocampal c.  \\
+3003 & 0 & 5.31 & 22.5 & -45.5 & -12 & 4.53 & -63.3 & -3.72 & r. lingual g.; r.
+cuneal c., intracalcarine c., bilaterally occipital fusiform g., precuneus,temporal fusiform c., posterior parahippocampal c.  \\
 154 & 0.000000656 & 4.46 & -35 & -83 & 28 & -32.8 & -86.2 & 21.4 & l. superior lateral occipital c. \\
@@
 If a cluster was not found or not isolated, we used a contrast from the
-\textit{relaxed} set, or finally the \textit{simple} set\todo{not used for PPA},
-and repeated the process until we found a cluster that matched the expected
-anatomical location based on literature \citep{epstein1998ppa}.
+\textit{relaxed} set, or finally the \textit{simple} \todo{not used in any VP
+for PPA}set, and repeated the process until we found a cluster that matched the
+expected anatomical location based on literature \citep{epstein1998ppa}.
 
@@
 localizer and the primary AD contrast, we created a Bland-Altman-Plot for every
-subject (see Figure \ref{fig:bland-altman}).
+subject (see ).
 % what it depicts
-Each subplot visualizes the mean value and difference (localizer minus AD) of
-two spatially corresponding voxels in the unthresholded $z$-maps.
+Each subplot of Figure \ref{fig:bland-altman} visualizes the mean value and
+difference (localizer minus AD) of two spatially corresponding voxels in the
+unthresholded $z$-maps.
 % top KDE plot
@@
 In line with previous studies, we use here also operationalize spatial
-perception via general linear model (GLM) $t$-contrasts.
+perception via general linear model (GLM) $t$-contrasts in two naturalistic
+stimuli.
 % current study: dissimilar
-Contrary to previous studies, our current operationalization is not based on
+Contrary to previous studies, our current approach is not based on
 carefully designed sets of stimuli but based on annotated stimulus features
@@
 
-\subsubsection{AV: group}
-
-\todo[inline]{AV is "intermediate step": natural but still visual; similar:
-\citep{bartels2004mapping, hasson2004intersubject} (mention here already or at
-the end of topic)}
-
-% AV stimulus
-Group results of the AV stimulus' primary contrast yielded bilateral clusters
-that span the group overlap of individual PPA ROIs from anterior to posterior.
-% difference in location/size to AD and VIS
-Clusters also expand into more posterior regions (occipital fusiform gyrus,
-lingual gyrus, and intracalcarine cortex).\todo{which of these regions do (not)
-overlap with group ROI?}
-
-\todo[inline]{bigger size of clusters is not surprising; imo still impressive
-low amount of random clusters in the brain)}
-
-% confound of higher perception
-This larger extension, especially into the primary visual cortex, can be
-attributed to the fact that we averaged the content of individual frames after a
-cut and did not control for confounding features like depicted faces or objects
-or attentional focus of subjects.
-% shortcomings
-m.a.W.: Results of the AV stimulus that we ran as a conceptual control are
-tempered by using different kind of movie cuts regardless of the visual content
-of the movie frame after the respective cuts.
-% which leads to the ``blurred'' results
-
-\todo[inline]{we exploit a confound induced by cinematography; field size
-decreases later in the movie; this is a confound based on cinematography => the
-stimulus changes over time; (ergo: man sollte sich bißchen mit Cinematographie
-auskennen und/oder stimulus annotation in model nehmen, wenn man was mit movies
-machen will)}
-
 \todo[inline]{SE: VIS vs AV vs AD: Wer liefert was über die PPA. Dieser
@@
 
-% summary: nevertheless
-\todo[inline]{Nevertheless, group results from analysis using more natural
-visual stimulation suggest that... (cf. \citep{bartels2004mapping,
-hasson2004intersubject})}
-
-\todo[inline]{approach of contrasting cuts was adventorous, annotation of speech
-suited better in the first place, and the auditory thing ist more interesting
-anyway, we did not aim for a substition of classic localizer via movie; but if
-you wanna do it, you should...:}
-
+\subsubsection{AV: group}
+
+% intro
+First, we analyzed data from the movie stimulus offering ecologically more valid
+but still visual stimulation.
+%
+An early study \citep{bartels2004mapping} that manually annotated the content
+(color, faces, language, and human bodies) of movie frames found that
+specialization of functional areas is preserved during movie watching.
+%
+Contrary to \citep{bartels2004mapping}, we categorized the frames after movie
+cuts independent of the frames' content.\todo{PPA in
+    \citep{hasson2004intersubject} but do reverse ISC}
+% hypo
+Despite this ``adventurous'' / ad hoc approach, we hypothesized that
+[confounding variables could/would average out and] our whole-brain analyses
+would lead to significant clusters in the PPA.
+% results
+Group results of the AV stimulus' primary contrast yielded a clusters that span
+the group overlap of individual PPA ROIs from anterior to posterior.
+% difference in location/size to AD and VIS
+The cluster also extends into medial regions (dorsal precuneus and dorsal
+posterior cingulate cortices), and into more posterior regions (occipital
+fusiform gyrus and intracalcarine cortex) bilaterally.
+% confound of higher perception
+The larger extension into more posterior, primary visual areas can be attributed
+to the fact that we averaged the content of individual frames after a cut and
+did not control for confounding features like depicted faces or objects or
+attentional focus of subjects.
+%
+\todo[inline]{bigger size of clusters is not surprising;  imo still impressive
+low amount of random clusters in the brain (and not one third of brain
+significant); Clusters in Bartels (2004) are actually kinda big, too;)}
+%
+Noteworthy, we here exploited a confound in the stimulus structure induced by
+cinematographic tendencies (cf. method section;
+% a)
+a) movies tend to establish the setting and the spatial relationships within a
+setting at the beginning of a movie;
+% b)
+b) the field sizes of movie shots tend to decrease when switching back to
+already established settings
+% c)
+c) shots within a recurring locale or setting tend to shift to depicting persons
+and objects \citep{brown2012cinematography, mercado2011filmmakers}.
+% interpretation
+-> concluding statement?
+% shortcomings
 Since the capability to isolate clusters or networks correlating with specific
@@
 
+\todo[inline]{Nevertheless: that this simple approach works actually suprisingly
+well; shows that a lot of confounds average out, since we clusters are not super
+big or all over the brain (and that across contrasts)}
+
+\todo[inline]{on the other hand: movies are nice but have idiosyncrasies; so,
+maybe you should be aware of these idiosyncrasies (and control for it) in case
+you wanna use movies for research}
+
+% summary: nevertheless
+\todo[inline]{Summary: so, yes, what is the main message of this
+``cross-modal-control-movie-thing''?? cf. intro: ``works'' but clusters more
+widespread}
+
 \subsubsection{AD: group}
-
-\todo[inline]{since the picture of PPA is far more unclear in auditory
-domain and we have a pretty nice stimulus with a narrator and a
-pretty nice annotation, we focussed on the audio-description}
 
@@
 
-% AD stimulus
+% intro
+Second, we analyzed data from the audio-description.
+% hypothesis
+Encouraged by \citep{aziz2008modulation}, we also hypothesized that spatial
+information embedded in an exclusively auditory stimulus would correlate with
+increased hemodynamic activity in the PPA.
+% results
 Group results of the AD stimulus' primary contrast yielded spatially concise
@@
 left PPA and only for sentences describing famous places compared to famous
-faces. Contrary, our group results suggest that auditory spatial information
+faces.\todo{averaged across voxels in PPA/FFA defined by localizer}
+%
+Contrary, our group results suggest that auditory spatial information
 compared to non-spatial information correlates with bilaterally increased
-activation in its anterior.\todo{nice! and\dots?}
-
-% tasks in previous studies
+activation in its anterior.\todo{any concluding statement?}
+
+% previous studies: no task
 Usually studies that use small sets of experimentally controlled stimuli also
 employ a task to keep subjects attentive to the stimuli.
-% but epstein1998
+% but: Epstein (1998)
 Nevertheless, one early block-design study \citep{epstein1998ppa} compared
@@
 \citep{ocraven2000mental})  but just had to ``enjoy the audio-description''.
-% but we are still different
+% but still: we are different
 Our paradigm still differs from \citep{epstein1998ppa} because the modeled
 stimulus features were incidentally embedded in a continuous stream of auditory
-information.
+information preventing participants from making assumptions about the
+investigated perceptual process.
 % concluding statement: kinda automatic process
-The lack of a task suggests that verbal spatial information is processed in the
-anterior PPA in an automatic fashion and does not necessarily rely on
-deliberately paying attention to verbal spatial information.
-%
-Further, the incidental occurrence of modeled features prevents participants
-from making assumptions about the investigated perceptual process by just being
-exposed to the paradigm which mimics experiencing the world outside the lab more
-closely.
+Hence, current results from our paradigm also suggest that verbal spatial
+information is processed in the anterior PPA casually and does not [necessarily]
+rely on [deliberately] paying attention to verbal spatial information.
 
@@
 
-\todo[inline]{how to discuss Bland-Altman-Plots???}
-
-\todo[inline]{dunno if this is meaningful: z-scores in the anterior part of
-    PPA are higher in AD contrasts than in contrast of localizer}
+\todo[inline]{how to discuss Bland-Altman-Plots???; dunno if this is meaningful:
+z-scores in the anterior part of PPA are higher in AD contrasts than in contrast
+of localizer}
 
@@
 impaired persons.}
+
+%
+Since the annotation of the narrator's voice allowed us to better/cleaner/nicer
+operationalize spatial perception than the movie's annotation, we here
+hypothesized
+% AD stimulus
 

### 2021-01-26 paper/main.tex
discussion of prim. contrasts (AD & AV; individual)

@@
 \todo[inline]{Aziz: reduced activity only in left PPA, and only for famous
-places vs famous faces; I think they ran their f-test on the average of the PPA
-voxels! anyway: their analysis is complicated, yet not sophisticated}
+places vs famous faces; I think they ran their f-test on the average of PPA
+voxels defined by separate localizer}
 
@@
 sentences (describing unknown and famous places and faces), we modeled events
-from on- to offset of single words (that indicats the visual content to the
+from on- to offset of single words (that indicates the visual content to the
 listener).
@@
 left PPA and only for sentences describing famous places compared to famous
-faces.\todo{averaged across voxels in PPA/FFA defined by localizer}
+faces.\todo{average response across voxels in ROI}
 %
@@
 
-\subsubsection{AD: individuals}
-
-\todo[inline]{how to discuss Bland-Altman-Plots???; dunno if this is meaningful:
-z-scores in the anterior part of PPA are higher in AD contrasts than in contrast
-of localizer}
-
-\todo[inline]{We hypothesize[d] that an exclusively auditory stimulus can/could
-localize the PPA in individual subjects, and thus substitute a visual experiment
-be which would be more practicable to assess brain functions in visually
-impaired persons.}
-
-%
-Since the annotation of the narrator's voice allowed us to better/cleaner/nicer
-operationalize spatial perception than the movie's annotation, we here
-hypothesized
-% AD stimulus
-
-% intro
-To test if an auditory narrative could substitute a visual localizer experiment,
-we also examined the results of the primary AD contrast on the level of
-individual subjects.
-% results of dedicated localizer
-The visual localizer \citep{sengupta2016extension} revealed bilateral ROIs in 12
-of 14 subjects and a unilateral right ROI in two subjects (sub-04, sub-20).
-% in the current study
-The audio-description's primary contrast yielded significant bilateral clusters
-in 9 of 14 subjects (of which sub-04 shows just right-lateralized PPA ROI) and a
-unilateral significant cluster in one subject.
-%
-Whereas \citep{sengupta2016extension} chose the subjectively ``best fitting
-$z$-threshold in a subject's unthresholded $z$-map by visual judgment, we used a
-``one threshold fits all approach`` (Z>3.4, p<.05 cluster-corrected).
-% group vs individual
-Results on an individual level reveal that significant cluster are located in
-the anterior part of individual PPA ROIs. Thus, the pattern that was revealed on
-a group level is not just a by-product of the averaging process but can reliably
-be found in individual study participants.
-% conclusion
-Lastly, our exploratory analyses suggest that a naturalistic auditory stimulus
-is in principle suitable to localize (the anterior part) of a higher-level
-visual area in the majority of subjects.
-% chose the best contrast in the future
-Similarly to \citep{sengupta2016extension} that chose the ``best'' of three
-alternative contrasts (strict, relaxed, or simple contrast), future studies that
-aim for individual diagnostics / ROI localization should also test more than one
-contrast to gain the ``best'' individual ROIs.\todo{``best'' sounds pretty
-shitty}
-
-\todo[inline]{discussion of individual differences? what do the results
-suggest? Differences in alertness, attention to spatial information,
-predisposition? ``capability'' to process auditory spatial information?}
-
-\todo[inline]{individual ``preference'' to pay attention to
-spatial infos (which contradicts statement above that attention is not a
-prerequisite)}
-
 \subsubsection{AD: shortcoming}
+
+\todo[inline]{shorten the shortcoming; focus on ``opportunities'' for future research}
 
@@
 % future studies
-Hence, future studies might investigate if a homogenous category of wholistic
+Hence, future studies might investigate if a homogeneous category of wholistic
 but vague verbal descriptions (e.g. ``a mountain landscape'') compared to a
-homogenous categories of more specific verbal descriptions of landmarks (e.g.
+homogeneous categories of more specific verbal descriptions of landmarks (e.g.
 ``a beacon'') or houses (e.g. ``farmhouse'', ``apartment building'') lead to
 different levels of hemodynamic activity.
+
+\subsubsection{AD: individuals}
+
+\todo[inline]{how to discuss Bland-Altman-Plots???; dunno if this is meaningful:
+z-scores in the anterior part of PPA are higher in AD contrasts than in contrast
+of localizer}
+%
+Based on the fact that the annotation of speech still offered a more precise way
+to operationalize the perception of spatial information then the annotation of
+cuts and locations, we also hypothesized that data from the audio-description
+could reveal the location of the PPA in individual persons.
+%
+To test if a auditory narrative could [in principle] substitute a visual
+localizer experiment, we examined the individual results from the
+audio-description's primary contrast.
+% results of dedicated localizer
+The visual localizer \citep{sengupta2016extension} revealed bilateral ROIs in 12
+of 14 subjects and a unilateral right ROI in two subjects (sub-04, sub-20).
+% in the current study
+The audio-description's primary contrast yielded significant bilateral clusters
+in 9 of 14 subjects (of which sub-04 shows just right-lateralized PPA ROI) and a
+unilateral significant cluster in one subject.
+% one threshold (and contrast) to rule them all
+Whereas \citep{sengupta2016extension} chose the subjectively ``best fitting
+$z$-threshold in a subject's unthresholded $z$-map by visual judgment, we used a
+``one threshold fits all approach`` (Z>3.4, p<.05 cluster-corrected).
+% group vs individual
+Results on an individual level reveal that significant cluster are located in
+the anterior part of individual PPA ROIs. Thus, the pattern that was revealed on
+the group level is not just a by-product of the averaging process but can
+reliably be found in individual study participants.
+% conclusion
+Lastly, our exploratory analyses suggest that a naturalistic auditory stimulus
+is in principle suitable to localize (the anterior part) of a higher-level
+visual area in the majority of subjects.
+% chose the best contrast in the future
+Similarly to \citep{sengupta2016extension} that chose the ``best'' of three
+alternative contrasts (strict, relaxed, or simple contrast), future studies that
+aim for individual diagnostics / ROI localization should also test more than one
+contrast to gain the ``best'' individual ROIs.\todo{``best'' sounds pretty
+shitty}
+
+\todo[inline]{probably not really important but: what do results suggest
+regarding individual differences?  Differences in alertness, attention to
+spatial information, predisposition?  ``capability'' to process auditory spatial
+information?}
 
@@
 
-\todo[inline]{yeah, we have shortcomings but, look, we have a pattern of
-spatially restricted clusters across contrasts (and stimuli)}
+\todo[inline]{despite ad hoc approach in movie, ``non-perfect'' speech-anno,
+and non-exhausting confound control, we have a pattern of spatially restricted
+clusters across contrasts (and stimuli)}
 
@@
 regions
-\todo[inline]{cf. discussed shortcomings}
 
@@
 \todo[inline]{makes sense because it goes full circle to general naturalistic
-stimulus topic and makes transition to negative controls easier (which is
-essentially also "natural stimuli, fuck yeah!}
+stimulus topic and makes transition to negative controls easier}
 
@@
 For example in the AV results, we do not find significant clusters that could be
-attributed to cognitive processes like attention or eye movements\todo{could
-already already be mentioned in discussion of primary contrasts}
+attributed to cognitive processes like attention or eye movements.\todo{could
+already be mentioned in discussion of primary contrasts}
 
@@
 
-\subsubsection{random shower toughts}
+\todo[inlince]{concluding statement: essentially "natural stimuli, fuck yeah!;
+re-use of existent data; using [and extending] an already existing annotation
+for to operationalize a specific perceptual process}
+
+\subsection{negative controls and cross-modal controls}
+
+\todo[inline]{make this short; as expected almost everywhere null results ->
+
+% AV: contrast with AV nouns
+Compare Figure \ref{fig:reg-corr}: nouns that indicate a change to a new setting
+are correlated  with cuts to a new setting (vse\_new; r$\approx$0.3; second
+highest correlation of a verbal hint category with a cut category; AND: nouns
+that indicate change to a familiar setting are somewhat correlated with cuts to
+a familiar setting (se\_old; r$\approx$0.4; highest correlation of a verbal
+category with a cut category).
+
+% AD: correlation of these nouns with cuts
+Compare Figure \ref{fig:reg-corr}: nouns that indicate change to a new setting
+are correlated  with cuts to a new setting (vse\_new; r$\approx$0.3; second
+highest correlation of a verbal hint category with a cut category.
+
+\subsubsection{shower tought: changes in soundscape should also correlate with
+PPA activity}
 
@@
 sounds made by objects (that reveil object's material/identity)}
-
-\subsection{negative controls and cross-modal controls}
-
-\todo[inline]{could be mentioned in a few sentences. But above topics a far too
-much still; better embed somewhere above}
-
-% AV: contrast with AV nouns
-Compare Figure \ref{fig:reg-corr}: nouns that indicate a change to a new setting
-are correlated  with cuts to a new setting (vse\_new; r$\approx$0.3; second
-highest correlation of a verbal hint category with a cut category; AND: nouns
-that indicate change to a familiar setting are somewhat correlated with cuts to
-a familiar setting (se\_old; r$\approx$0.4; highest correlation of a verbal
-category with a cut category).
-
-% AD: correlation of these nouns with cuts
-Compare Figure \ref{fig:reg-corr}: nouns that indicate change to a new setting
-are correlated  with cuts to a new setting (vse\_new; r$\approx$0.3; second
-highest correlation of a verbal hint category with a cut category.
 

### 2021-01-27 paper/main.tex
revise AD shortcomings & individual results

@@
 
-\todo[inline]{shorten the shortcoming; focus on ``opportunities'' for future research}
+\todo[inline]{at the moment positioned here; makes sense at a couple of other
+positions; not shure yet}
 
@@
 2008).\todo{check references}
-% cateogries in primary contrasts
-In the current study's primary contrast, we compared verbal hints about
-landmarks ((\texttt{geo}; often buildings or other single aspects of a whole
-scene) and elements defining the geometry of a room or locale (\texttt{groom})
-to non-spatial hints.
 % we did not choose se\_new and se\_old
-We did not choose the categories that contained switches from one setting to
-another (\texttt{se\_new} and \texttt{se\_old}) which one might assume to
-contain the auditory equivalent to the ``optimal'' visual stimulus type.
-% why not se\_new or se\_old
-The categories \texttt{se\_new} and \texttt{se\_old} were actually
-heterogeneous: they rarely contained whole and thus a vague verbal descriptions
-of landscapes (e.g. ``in a football stadium'', ``Forrest is running through the
-jungle'') but mostly landmarks or buildings, and also non-spatial hints (e.g.
-``Jenny as a teenager``).
+In the current study we did not include the categories that contained switches
+from one setting to another (\texttt{se\_new} and \texttt{se\_old}) which one
+might assume to contain the auditory equivalent to the ``optimal'' visual
+stimulus type in the primary contrast.
+% why
+The reason was that the categories \texttt{se\_new} and \texttt{se\_old} were
+heterogeneous: they rarely contained holistic (but also vague) descriptions of
+landscapes (e.g.  ``[in a] football stadium'', ``[Forrest is running through
+the] jungle'') but mostly landmarks or buildings and also non-spatial hints
+(e.g. ``[Jenny as a] teenager``).
 % further studies
@@
 duration of a single fixation \citep{henderson2003human} further studies might
-investigate if categories of holistic but vague verbal descriptions of
-landscapes correlate with differential hemodynamic activity in the PPA compared
-to more concrete spatial hints.
-% future studies
-Hence, future studies might investigate if a homogeneous category of wholistic
-but vague verbal descriptions (e.g. ``a mountain landscape'') compared to a
-homogeneous categories of more specific verbal descriptions of landmarks (e.g.
-``a beacon'') or houses (e.g. ``farmhouse'', ``apartment building'') lead to
-different levels of hemodynamic activity.
+investigate if holistic but also vague verbal descriptions of landscapes lead to
+a different hemodynamic activity level than more concrete descriptions of a
+landscape's content (e.g.``[a] beacon'', [a] ``farmhouse'', ``[an] apartment
+building'').
 
@@
 %
-Based on the fact that the annotation of speech still offered a more precise way
-to operationalize the perception of spatial information then the annotation of
-cuts and locations, we also hypothesized that data from the audio-description
-could reveal the location of the PPA in individual persons.
+Based on the fact that the annotation of nouns still offered a more precise way
+to operationalize the perception of spatial information than the annotation of
+cuts and locations, we also hypothesized that analyzing the data from the
+audio-description could localize the PPA in individual persons.
 %
-To test if a auditory narrative could [in principle] substitute a visual
-localizer experiment, we examined the individual results from the
-audio-description's primary contrast.
+Hence to test if an auditory narrative could [in principle] substitute a visual
+localizer experiment, we examined the results from the audio-description's
+primary contrast on an individual level.
 % results of dedicated localizer
@@
 of 14 subjects and a unilateral right ROI in two subjects (sub-04, sub-20).
+%
+Whereas \citep{sengupta2016extension} chose the subjectively ``best fitting''
+$z$-threshold in an unthresholded $z$-map from one of three contrasts by visual
+judgment, we used a ``one threshold fits all approach`` (Z>3.4, p<.05
+cluster-corrected).
 % in the current study
-The audio-description's primary contrast yielded significant bilateral clusters
-in 9 of 14 subjects (of which sub-04 shows just right-lateralized PPA ROI) and a
-unilateral significant cluster in one subject.
+The audio-description's primary contrast that we used for all subjects yielded
+significant bilateral clusters in 9 of 14 subjects (of which sub-04 shows only a
+right-lateralized PPA ROI), and a unilateral significant cluster in one subject.
+% similar: anterior part
+Similarly to the group average results, results on an individual level also
+reveal that clusters are spatially restricted to the anterior part of individual
+PPAs.
+% conclusion
+Thus, the increased hemodynamic activity in the anterior part of the PPA
+revealed on the group level is not just a by-product of the averaging process
+[as it can reliably be found in individual study participants.]
+% conclusion
+Lastly, our exploratory analysis suggests that a naturalistic auditory stimulus
+can [in principle] be applied to localize (the anterior part) of an higher-level
+visual area in the majority of subjects.
 % one threshold (and contrast) to rule them all
-Whereas \citep{sengupta2016extension} chose the subjectively ``best fitting
-$z$-threshold in a subject's unthresholded $z$-map by visual judgment, we used a
-``one threshold fits all approach`` (Z>3.4, p<.05 cluster-corrected).
-% group vs individual
-Results on an individual level reveal that significant cluster are located in
-the anterior part of individual PPA ROIs. Thus, the pattern that was revealed on
-the group level is not just a by-product of the averaging process but can
-reliably be found in individual study participants.
-% conclusion
-Lastly, our exploratory analyses suggest that a naturalistic auditory stimulus
-is in principle suitable to localize (the anterior part) of a higher-level
-visual area in the majority of subjects.
-% chose the best contrast in the future
-Similarly to \citep{sengupta2016extension} that chose the ``best'' of three
-alternative contrasts (strict, relaxed, or simple contrast), future studies that
-aim for individual diagnostics / ROI localization should also test more than one
-contrast to gain the ``best'' individual ROIs.\todo{``best'' sounds pretty
-shitty}
-
-\todo[inline]{probably not really important but: what do results suggest
+Further studies that aim for individual diagnostics / ROI localization should
+nevertheless test more than one contrast to gain the ``best'' individual
+ROIs.\todo{..ouff}
+
+\todo[inline]{probably not important but: what do results suggest
 regarding individual differences?  Differences in alertness, attention to
@@
 
-\todo[inlince]{concluding statement: essentially "natural stimuli, fuck yeah!;
+\todo[inline]{concluding statement: essentially "natural stimuli, fuck yeah!;
 re-use of existent data; using [and extending] an already existing annotation
@@
 \todo[inline]{make this short; as expected almost everywhere null results ->
+natural stimuli = suitable}
 

### 2021-01-27 paper/main.tex
anterior vs posterior PPA

@@
 \todo[inline]{at the moment positioned here; makes sense at a couple of other
-positions; not shure yet}
+positions; not sure yet}
 
@@
 In the visual domain, landscapes and not pictures of landmarks or buildings are
-considered to be the ``optimal'' stimulus type (cf. Epstein (1998, 1999, 2003,
-2008).\todo{check references}
+considered to be the ``optimal'' stimulus type
+\citep{epstein2008parahippocampal}.\todo{a review}
 % we did not choose se\_new and se\_old
-In the current study we did not include the categories that contained switches
-from one setting to another (\texttt{se\_new} and \texttt{se\_old}) which one
-might assume to contain the auditory equivalent to the ``optimal'' visual
-stimulus type in the primary contrast.
+We did not include the categories that contained switches from one setting to
+another (\texttt{se\_new} and \texttt{se\_old}) which one might assume to
+contain the auditory equivalent to the ``optimal'' visual stimulus type in the
+primary AD contrast.
 % why
@@
 duration of a single fixation \citep{henderson2003human} further studies might
-investigate if holistic but also vague verbal descriptions of landscapes lead to
-a different hemodynamic activity level than more concrete descriptions of a
-landscape's content (e.g.``[a] beacon'', [a] ``farmhouse'', ``[an] apartment
-building'').
+investigate if vague verbal descriptions of landscapes lead to a different
+hemodynamic activity level than descriptions of more concrete parts of a scene
+(e.g.``[a] beacon'', [a] ``farmhouse'').
 
@@
 
-\subsection{Robust (results) across contrasts}
+\subsection{Robust results across contrasts}
 
@@
 
-\todo[inline]{despite ad hoc approach in movie, ``non-perfect'' speech-anno,
-and non-exhausting confound control, we have a pattern of spatially restricted
-clusters across contrasts (and stimuli)}
-
-% more than just one contrast
-For both naturalistic stimuli, we computed several $t$-contrasts that differed
-in the contrasted categories of stimulus features and the amount of available
-data to test the robustness of our findings.
 % why we did a couple of contrasts
-m.a.w.: For both stimuli we created several contrasts that varied the amount of
-events available for the analysis and how well the annotated events within
+To test the robustness of our approach, we created several additional contrasts
+for each naturalistic stimulus by varying the contrasted categories (and thus
+the amount of available data), and how well the annotated events within
 categories on average matched the stimulus type that we assumed to be
@@
 % PPA AV
-Regarding contrasts of the AV stimulus, all five contrasts show significant
-bilateral clusters in the PPA but also extending into more posterior brain
-regions
-
+Regarding contrasts of the AV stimulus (see Table \label{tab:av-contrasts}), all
+five AV contrasts show significant bilateral clusters in the PPA but also
+extending into more posterior brain regions.
 % PPA AD
-Regarding contrasts of the AD stimulus, six of eight contrasts show significant
-bilateral clusters in the anterior part of the group PPA overlap.
-
+Regarding contrasts of the AD stimulus (see Table \label{tab:ao-contrasts}), six
+of overall eight contrasts show significant bilateral clusters in the anterior
+part of the group PPA overlap.
 % results indicate robustness
 Thus, the results of the additional contrasts indicate that our findings are
-robust across contrasts do not depend on the design of one specific
-contrasts.
-
+robust and do not depend on the design of one specific contrasts.
 % but
-Nevertheless, results are still influenced by [sensitive to] the amount of
-available data and how well the feature space is modeled.
+Nevertheless, results are sensitive to the contrasted categories and the amount
+of available data.
 % example
@@
 Hence, investigators using model-driven analyses have to consider how many
-events a stimulus to be chosen may provide and how homogeneous the events to be
+events a naturalistic stimulus may provide and how homogeneous the events to be
 averaged might be.
-
-\subsubsection{anterior vs. posterior PPA}
 
@@
 
-% intro
-Results of the AD contrasts consistently yielded significant clusters spatially
-constrained to the anterior part of the PPA group overlap [and to the anterior
-part of significant clusters of the AV contrasts].
-% PPA might have submodules
-Previous studies provide evidence that the PPA can be devided into functionally
-subregions that might process different stimulus features [during visual scene
-perception].
+% anterior vs posterior pattern
+In contrasts 1 to 6 of the AD stimulus, we find consistently significant
+clusters spatially constrained to the anterior part of the PPA group overlap as
+defined by the visual localizer [as well as constrained to the anterior part of
+significant cluster of AV contrasts].
+% question
+This raises the question if the different activation patterns can be attributed
+to different features inherent in visual compared to verbal stimuli.
+% visual scenes: probably submodules
+In the domain of visual scene perception, previous studies provide evidence that
+the PPA can be divided into functionally subregions that might process different
+stimulus features.
 % posterior: functionality
@@
 Our results add further evidence that the PPA is not a homogeneous area but can
-be devided into functionally subregions.
+be divided into functionally subregions.
 % pPPA
-Results of your study suggest that the pPPA is more concerned with visual
-aspects of spatial information as exclusively inherent in visual stimuli like
-pictures or movies.
+Our results suggest that the pPPA is more concerned with visual aspects immanent
+in pictures or movie shots of landscapes.
 % aPPA
@@
 (e.g. spatial contextual information \citep{aminoff2013role,
-aminoff2015associative, baumann2016functional}) inherent in both visual and
-verbal stimuli.
+aminoff2015associative, baumann2016functional}) as immanent/inherent in both
+visual and verbal stimuli.
 
@@
 
-\todo[inline]{makes sense because it goes full circle to general naturalistic
-stimulus topic and makes transition to negative controls easier}
+\todo[inline]{imo it should be possible to handle the following two subsections
+    in one subsection; à la: GLM + naturalistic stimuli works because
+    confounds average (most often) out AND negative control contrasts show
+    negative results; except where features of AV + AD were correlated; but
+that's actually cool because -> hypothesis}
 
@@
 
+\todo[inline]{similarly: we have a pattern of spatially restricted clusters
+across contrasts (and stimuli) in the PPA contrasts -> natural stimuli =
+suitable}
+
 % AV: contrast with AV nouns
@@
 
-\subsubsection{shower tought: changes in soundscape should also correlate with
+\subsubsection{shower thought: changes in soundscape should also correlate with
 PPA activity}
@@
 different aspects of the stimuli's feature space.
-\item PPA is functionally heterogenous region
+\item PPA is functionally heterogeneous region
 \item a complex but naturally engaging auditory stimulus like an

### 2021-01-27 paper/main.tex
restructure RSC, LOC, control contrasts

@@
     \item results allg. kürzen (war nicht ganz einfach)
-    \item table of results: how many decimal points?
     \item check if captions of figs and tables now (really) match phrasing
@@
 \begin{itemize}
-    \item Discussion is restructured
-    \item current structure makes a lot things easier/concise/more logical to
-        convey, and eventually easier to read and the message to grasp
+    \item Discussion is restructured \& most paragraphs adopted to new structure
     \item as Simon stated I would be interesting to discuss differences between
@@
     \item mehr zum Thema VIS? ("best contrast was chosen")
+    \item overall conclusion as a last paragraph or independent section
 \end{itemize}
@@
 
-\subsubsection{retrosplenial cortex (RSC)}
-
-\todo[inline]{SE: RSC etc: Irgendwie waren die bis zu Diskussion eher ein
-afterthought. Daher etwas überraschend, vielleicht in Einleitung und Results
-schon mehr bringen; COH: afterthought, for sure; It was highly probable that RSC
-would show up but it wasn't aim of the study (had no ROIs for it anyway); imo
-this is an issue of ``nice story telling'' vs. HARKing}
-
-% but RSC
-Apart from the PPA, we find significantly increased activity in the
-retrosplenial cortex (RSC) consistently across contrasts of both stimuli (AD
-stimulus: 7 contrasts; AV stimulus: 3 contrasts).
-% location functionally defined
-The RSC as a scene-selective region is not necessarily spatially congruent with
-the anatomically defined retrosplenial cortex [26] (BA 29 and 30)
-\citep{epstein2008parahippocampal} but functionally defined as the posterior
-medial region that exhibits increased hemodynamic activity to visual scenes and
-during mental imagination trough familiar environments [8]
-\citep{epstein2008parahippocampal}.
-% location
-This functionally defined RSC is located in the retrosplenial cortex, and
-posterior cingulate region (BA 23 and 31) [51–56], near to the point where the
-calcarine sulcus joins the parietal-occipital sulcus
-\citep{epstein2008parahippocampal}.
-
-% discussion of what the RSC does
-interpretation cf.:
+\subsubsection{RSC \& LOC}
+
+\todo[inline]{part regarding RSC \& LOC is now super short; maybe give half a
+sentence that this was not focus of the story (but still kinda expected)}
+
+% intro
+Apart from the PPA, we find significantly increased activity in the dorsal
+precuneus and posterior cingulate region (e.g. retrosplenial cortex; RSC) and
+lateral occipital cortex (LOC) across contrasts of both naturalistic stimuli.
+% RSC intro
+Like the PPA, the RSC (AV stimulus: significant clusters in 3 of 5 contrasts; AD
+stimulus: 7 of 8 contrasts) and LOC (AV stimulus: XY of 5 contrasts; AD
+stimulus: XY of 8 contrasts) are known to be scene-selective regions (see
+\citep{chrastil2018heterogeneity, bettencourt2013role} for reviews).
+% conclusion
+\todo[inline]{conclusion: what does that say about our results regarding PPA as
+a scene-selective region, and audio-visual and auditory naturalistic stimuli in
+general?}
+
+\todo[inline]{if we locate a conclusion regarding ``naturalistic stimuli, fuck
+yeah'' (+ re-use of existent data) here already, we can add the following part
+``not many random clusters'' \& ``control contrasts'' imo elegantly and
+shortened here as ``caveats''}
+
+\todo[inline]{``caveats'' = you need extensive annotations and need to know the
+    confound structure; but it's the confound structure that leads to the
+    hypothesis that changes of the soundscape might also correlate with activity
+in the PPA (cf. ``shower thoughts'')}
+
+% some backup text for RSC & LOC
+\begin{comment}
+% RSC
+RSC is located in the retrosplenial cortex, and posterior cingulate region (BA
+23 and 31) [51–56], near to the point where the calcarine sulcus joins the
+parietal-occipital sulcus \citep{epstein2008parahippocampal}.
+%
+RSC location functionally defined. In context of scene perception, the RSC is
+not necessarily spatially congruent with the anatomically defined retrosplenial
+cortex [26] (BA 29 and 30) \citep{epstein2008parahippocampal} but functionally
+defined as the posterior medial region that exhibits increased hemodynamic
+activity to visual scenes and during mental imagination trough familiar
+environments [8] \citep{epstein2008parahippocampal}.
+
 \begin{itemize}
@@
 
-\subsubsection{superior lateral occipital cortex (TOC / OPA?)}
-
+% LOC
 \begin{itemize}
@@
 
-\todo[inline]{in any case: the pattern PPA, RSC, LOC is a usual pattern in the
-visual domain; here, it is the usual pattern across across AV and AD contrasts
--> hypothesis for auditory domain? future research and stuff?}
+\end{comment}
 
 \subsubsection{not many random cluster}
-
-\todo[inline]{imo it should be possible to handle the following two subsections
-    in one subsection; à la: GLM + naturalistic stimuli works because
-    confounds average (most often) out AND negative control contrasts show
-    negative results; except where features of AV + AD were correlated; but
-that's actually cool because -> hypothesis}
 
@@
 For example in the AV results, we do not find significant clusters that could be
-attributed to cognitive processes like attention or eye movements.\todo{could
-already be mentioned in discussion of primary contrasts}
-
+attributed to cognitive processes like attention or eye movements.
 % AD: auditory cortices
@@
 
-\todo[inline]{concluding statement: essentially "natural stimuli, fuck yeah!;
-re-use of existent data; using [and extending] an already existing annotation
-for to operationalize a specific perceptual process}
-
 \subsection{negative controls and cross-modal controls}

### 2021-02-01 paper/main.tex
some cleaning in discussion

@@
 \usepackage{natbib}
+
+% \usepackage{helvet}
+
+% \renewcommand{\familydefault}{\sfdefault}
 
@@
 
-\subsubsection{Events related to high-level perception}
+\subsubsection{Events related to high-level perception} \label{rationale}
 
@@
 % AV using nouns
-The contrast that used the narrator's nouns but in the AV stimulus (se\_new >
-se\_old) yielded a significant cluster in the right PPA and bilateral clusters
-in the superior lateral occipital cortices (the right hemispheric cluster
-extending into the superior parietal cortex).
+The contrast that used the narrator's nouns but in the AV stimulus
+(\texttt{se\_new} > \texttt{se\_old}) yielded a significant cluster in the right
+PPA and bilateral clusters in the superior lateral occipital cortices (the right
+hemispheric cluster extending into the superior parietal cortex).
 
@@
 % current study: dissimilar
-Contrary to previous studies, our current approach is not based on
-carefully designed sets of stimuli but based on annotated stimulus features
-incidentially occurring in an audio-visual movie and its audio-description.
+Contrary to previous studies, our current approach is not based on carefully
+designed sets of stimuli but based on annotated stimulus features incidentially
+occurring in an audio-visual movie and its audio-description.
 % group AV
@@
 % group AD
-Results for the audio-description stimulus reveal significant activation
-restricted to the anterior part of the PPA.
+Results for the audio-description reveal significant activation in the PPA but
+restricted its anterior part.
 % individual level
@@
 bilateral clusters in the anterior PPA of nine subjects and significant
-unilateral clusters in two subjects.
+unilateral clusters in one subjects.
 % meaning 1
@@
 %
-Contrary to \citep{bartels2004mapping}, we categorized the frames after movie
-cuts independent of the frames' content.\todo{PPA in
-    \citep{hasson2004intersubject} but do reverse ISC}
+Contrary to \citep{bartels2004mapping} who annotated the movie frames' content
+(color, faces, language and human bodies), we categorized each frame after a cut
+independent of its content. \todo{PPA in \citep{hasson2004intersubject} but do
+reverse ISC; Bartels' clusters are actually pretty big too}
 % hypo
-Despite this ``adventurous'' / ad hoc approach, we hypothesized that
-[confounding variables could/would average out and] our whole-brain analyses
-would lead to significant clusters in the PPA.
+Despite this ad hoc approach, we hypothesized that [confounding variables
+could/would average out and] our whole-brain analyses would lead to significant
+clusters in the PPA.
 % results
-Group results of the AV stimulus' primary contrast yielded a clusters that span
+Group results of the AV stimulus' primary contrast yielded a cluster that span
 the group overlap of individual PPA ROIs from anterior to posterior.
@@
 The larger extension into more posterior, primary visual areas can be attributed
-to the fact that we averaged the content of individual frames after a cut and
-did not control for confounding features like depicted faces or objects or
-attentional focus of subjects.
-%
-\todo[inline]{bigger size of clusters is not surprising;  imo still impressive
-low amount of random clusters in the brain (and not one third of brain
-significant); Clusters in Bartels (2004) are actually kinda big, too;)}
-%
-Noteworthy, we here exploited a confound in the stimulus structure induced by
-cinematographic tendencies (cf. method section;
-% a)
-a) movies tend to establish the setting and the spatial relationships within a
-setting at the beginning of a movie;
-% b)
-b) the field sizes of movie shots tend to decrease when switching back to
-already established settings
-% c)
-c) shots within a recurring locale or setting tend to shift to depicting persons
-and objects \citep{brown2012cinematography, mercado2011filmmakers}.
-% interpretation
--> concluding statement?
+to the averaging process that did not control for confounding visual features or
+the attentional focus of study participants.
+
+\todo[inline]{I am pretty surprised the clusters are not all over the brain.  I
+do not know where/how do phrase it but should be mentioned imo}
+
 % shortcomings
@@
 
-\todo[inline]{Nevertheless: that this simple approach works actually suprisingly
-well; shows that a lot of confounds average out, since we clusters are not super
-big or all over the brain (and that across contrasts)}
-
-\todo[inline]{on the other hand: movies are nice but have idiosyncrasies; so,
-maybe you should be aware of these idiosyncrasies (and control for it) in case
-you wanna use movies for research}
+\todo[inline]{nice that the following is mentioned but what to do with it?
+Movies are nice but have idiosyncrasies; so, maybe you should be aware of these
+idiosyncrasies (and control for it) in case you wanna use movies for research?}
+% exploited cinematographic tendencies
+We here exploited a cinematographic confound in the stimulus structure (cf.
+\ref{rationale}).
+%
+Film directors tend to establish the geometry of locations earlier in the movie
+and to later focus more on persons and objects relevant to the evolved plot
+later  \citep{brown2012cinematography, mercado2011filmmakers}.
 
 % summary: nevertheless
-\todo[inline]{Summary: so, yes, what is the main message of this
+\todo[inline]{Overall summary for AV: so, yes, what is the main message of this
 ``cross-modal-control-movie-thing''?? cf. intro: ``works'' but clusters more
@@
 increased hemodynamic activity in the PPA.
-% results
-Group results of the AD stimulus' primary contrast yielded spatially concise
-clusters in the anterior part of the PPA group overlap that we gained from a
-visual localizer experiment \citep{sengupta2016extension}.
 % diff to Aziz (2008)
-Unlike \citep{aziz2008modulation} who modeled events from on- to offset of
-sentences (describing unknown and famous places and faces), we modeled events
-from on- to offset of single words (that indicates the visual content to the
-listener).
-% conclusion
-\citep{aziz2008modulation} found significantly increased activity in only the
-left PPA and only for sentences describing famous places compared to famous
-faces.\todo{average response across voxels in ROI}
-%
-Contrary, our group results suggest that auditory spatial information
-compared to non-spatial information correlates with bilaterally increased
-activation in its anterior.\todo{any concluding statement?}
+\citep{aziz2008modulation} modeled events from on- to offset of sentences
+(describing unknown and famous places and faces), and compared activity levels
+that were averaged across voxels of ROIs (PPA and fusiform face
+\citep{kanwisher1997ffa}) defined by a localizer experiment.
+% Aziz results
+Study results revealed significantly decreased activity in only the left PPA
+compared to activity in the FFA, and only for sentences describing famous places
+compared to famous faces.
+% we: model & whole brain
+Here we modeled events from on- to offset of single words and performed an
+whole-brain analysis.
+% our results
+Group results of audio-description's primary contrast yielded spatially concise
+clusters in the anterior part of the PPA group overlap.
+% concluding statement
+Contrary to \citep{aziz2008modulation}, our group results suggest that auditory
+spatial information compared to non-spatial information correlates with
+bilaterally increased activation in the anterior part of the PPA.
 
@@
 heterogeneous: they rarely contained holistic (but also vague) descriptions of
-landscapes (e.g.  ``[in a] football stadium'', ``[Forrest is running through
-the] jungle'') but mostly landmarks or buildings and also non-spatial hints
-(e.g. ``[Jenny as a] teenager``).
+landscapes (e.g.  ``[Forrest is running through the] jungle'') but mostly
+landmarks or buildings, and also non-spatial hints (e.g. ``[Jenny as a]
+teenager``).
 % further studies
@@
 %
-Based on the fact that the annotation of nouns still offered a more precise way
-to operationalize the perception of spatial information than the annotation of
-cuts and locations, we also hypothesized that analyzing the data from the
+Based on the fact that the annotation of nouns offered a more precise way to
+operationalize the perception of spatial information than the annotation of cuts
+and locations, we also hypothesized that analyzing the data from the
 audio-description could localize the PPA in individual persons.
@@
 judgment, we used a ``one threshold fits all approach`` (Z>3.4, p<.05
-cluster-corrected).
+cluster-corrected) in one contrast.
 % in the current study
-The audio-description's primary contrast that we used for all subjects yielded
-significant bilateral clusters in 9 of 14 subjects (of which sub-04 shows only a
-right-lateralized PPA ROI), and a unilateral significant cluster in one subject.
+The audio-description's primary contrast yielded significant bilateral clusters
+in 9 of 14 subjects (of which sub-04 shows only a right-lateralized PPA ROI),
+and a unilateral significant cluster in one subject.
 % similar: anterior part
@@
 the amount of available data), and how well the annotated events within
-categories on average matched the stimulus type that we assumed to be
-preferentially processed in the PPA.
+categories on average matched a stimulus type that we assumed to correlate with
+spatial perception.
 
@@
 % PPA AV
-Regarding contrasts of the AV stimulus (see Table \label{tab:av-contrasts}), all
+Regarding contrasts of the AV stimulus (see Table \ref{tab:av-contrasts}), all
 five AV contrasts show significant bilateral clusters in the PPA but also
@@
 % PPA AD
-Regarding contrasts of the AD stimulus (see Table \label{tab:ao-contrasts}), six
+Regarding contrasts of the AD stimulus (see Table \ref{tab:ao-contrasts}), six
 of overall eight contrasts show significant bilateral clusters in the anterior
@@
 % example
-For example, contrast 8 of the AD stimulus (\texttt{se\_new} > texttt{se\_old})
+For example, contrast 8 of the AD stimulus (\texttt{se\_new} > \texttt{se\_old})
 that used the most heterogeneous categories comprising the least amount of
@@
 % concluding statement
-Hence, investigators using model-driven analyses have to consider how many
+Hence, investigators that use model-driven analyses have to consider how many
 events a naturalistic stimulus may provide and how homogeneous the events to be
@@
 In contrasts 1 to 6 of the AD stimulus, we find consistently significant
-clusters spatially constrained to the anterior part of the PPA group overlap as
-defined by the visual localizer [as well as constrained to the anterior part of
-significant cluster of AV contrasts].
+clusters spatially constrained to the anterior part of the PPA group overlap.
 % question
@@
 % cytoarchitectonic map
-The aPPA is functionally more responsive than pPPA to high-level features of
+The aPPA is functionally more responsive than the pPPA to high-level features of
 scenes (e.g. real-word size \citep{park2015parametric}; a scene's abstract
@@
 
-\todo[inline]{part regarding RSC \& LOC is now super short; maybe give half a
-sentence that this was not focus of the story (but still kinda expected)}
+\todo[inline]{this part is now super short}
 
@@
 Like the PPA, the RSC (AV stimulus: significant clusters in 3 of 5 contrasts; AD
-stimulus: 7 of 8 contrasts) and LOC (AV stimulus: XY of 5 contrasts; AD
-stimulus: XY of 8 contrasts) are known to be scene-selective regions (see
-\citep{chrastil2018heterogeneity, bettencourt2013role} for reviews).
+stimulus: 7 of 8 contrasts) and LOC (AV stimulus: 4 of 5 contrasts; AD stimulus:
+unilateral in 2, bilateral in 4 of 8 contrasts) are known to be scene-selective
+regions (see \citep{chrastil2018heterogeneity, bettencourt2013role} for
+reviews).
 % conclusion
-\todo[inline]{conclusion: what does that say about our results regarding PPA as
-a scene-selective region, and audio-visual and auditory naturalistic stimuli in
-general?}
-
-\todo[inline]{if we locate a conclusion regarding ``naturalistic stimuli, fuck
-yeah'' (+ re-use of existent data) here already, we can add the following part
-``not many random clusters'' \& ``control contrasts'' imo elegantly and
-shortened here as ``caveats''}
-
-\todo[inline]{``caveats'' = you need extensive annotations and need to know the
-    confound structure; but it's the confound structure that leads to the
-    hypothesis that changes of the soundscape might also correlate with activity
-in the PPA (cf. ``shower thoughts'')}
 
@@
 
-\subsubsection{not many random cluster}
+\subsection{negative controls and cross-modal controls}
+
+\todo[inline]{hm, so why did I build contrasts of the no\_cut condition compared
+to the movie cuts categories????}
+
+The four control contrasts of the AV stimulus that compared the
+\texttt{no\_cuts} to categories of movie cuts all lead to null results.
+
+% AD anno in AV data
+The AV contrast using nouns (\texttt{se\_new} > \texttt{se\_old}): PPA
+(unilateral), LOC (bilateral); These noun categories show highest correlation
+among nouns with their cut counterpart \texttt{se\_new} (nouns) is r$\approx$0.3
+correlated with \texttt{vse\_new} (cuts); \texttt{se\_old} (nouns) is
+r$\approx$0.4 correlated with \texttt){vse\_old}.
+
+% AV anno in AV data
+The the 5 AV PPA contrasts but with the AV data using cuts. All null results
+except:
+% contrast 9
+vse\_new > pe\_old (conrast 9): left inferior prefrontal cortex (pars
+triangularis) and right ventral precuneus/posterior cingulate gyrus.
+% contrast 12
+vse\_new > vse\_old, vpe\_old (contrast 12): one cluster in the right posterior
+hippocampus.
+
+\todo[inline]{shower thought: changes of a soundscape that indicate a setting's
+    spatial layout could correlate with increased activity in the PPA
+    (arnott2008crinkling finds increased activations in PPA to sounds made by
+    objects (that reveil object's material/identity); but at the moment when
+    looking at the data I see no systematic in the results that let me assume
+that}
+
+\subsubsection{not many random cluster + naturalistic stimuli are cool}
 
@@
 
-\subsection{negative controls and cross-modal controls}
-
-\todo[inline]{make this short; as expected almost everywhere null results ->
-natural stimuli = suitable}
-
-\todo[inline]{similarly: we have a pattern of spatially restricted clusters
-across contrasts (and stimuli) in the PPA contrasts -> natural stimuli =
-suitable}
-
-% AV: contrast with AV nouns
-Compare Figure \ref{fig:reg-corr}: nouns that indicate a change to a new setting
-are correlated  with cuts to a new setting (vse\_new; r$\approx$0.3; second
-highest correlation of a verbal hint category with a cut category; AND: nouns
-that indicate change to a familiar setting are somewhat correlated with cuts to
-a familiar setting (se\_old; r$\approx$0.4; highest correlation of a verbal
-category with a cut category).
-
-% AD: correlation of these nouns with cuts
-Compare Figure \ref{fig:reg-corr}: nouns that indicate change to a new setting
-are correlated  with cuts to a new setting (vse\_new; r$\approx$0.3; second
-highest correlation of a verbal hint category with a cut category.
-
-\subsubsection{shower thought: changes in soundscape should also correlate with
-PPA activity}
-
-Cuts probably correlate with change in soundscape; change in soundscape often
-anticipates narrator (would lower detection power) or occurs in parallel with
-narrator; cf. correlation of cuts to other setting (independent of familiarity)
-with nouns that indicate a change of setting; cf. control contrasts [which
-ones?]
-% arnott hypothesis
-We hypothesize that not just semantic information but also the mere changes of a
-soundscape that indicate a setting's spatial layout could correlate with
-increased activity in the PPA.
-% arnott
-\todo[inline]{e.g. arnott2008crinkling finds increased activations in PPA to
-sounds made by objects (that reveil object's material/identity)}
+\subsubsection{naturalistic stimuli + data re-use, fuck yeah}
+
+lore ipsum
 

### 2021-02-01 paper/main.tex
Trim subsections and contrast headings more
TODO for half-addressed issue

@@
 
-\subsection{Event modeling}
+\subsection{Event selection}
 
@@
 (for GLM regressors) to model hemodynamic responses.
-
-\subsubsection{Events related to high-level perception} \label{rationale}
-
-\todo[inline]{imo the subheadings for 2.6.1 and 2.6.2 can be dropped because
-2.6.2 is super short}
 
@@
 
-\subsubsection{Events related to low-level perception / low-level perceptual
-confounds}
-
 % low-leve confounds: intro
@@
 
-\todo[inline]{SE: Die Abkürzungen in Figure 1: Da steigt keiner hinter}
-
 \begin{figure*}[h!]
@@
         (\texttt{fg\_ad\_rms} and \texttt{fg\_av\_ger\_rms}, r=.7635;
-        \texttt{fg\_ad\_lrdiff} and \texttt{fg\_av\_ger\_lrdiff}, r=.7749).}
+        \texttt{fg\_ad\_lrdiff} and \texttt{fg\_av\_ger\_lrdiff}, r=.7749).
+        \todo[inline]{not all labels are actually listed in that table}
+      }
 \label{fig:reg-corr}

### 2021-02-01 paper/main.tex
Resolve comments

@@
 
-\todo[inline]{das Verschieben des Sounds in den Segmenten spiegelt sich auch in
-den unterschiedlichen Counts der Events je Segment (s. Tabelle 1 \& 3) wider (AV
-Bild vs AV Sound vs AO Sound)}
-
 \subsection{Hemodynamic Modeling}
@@
 The events of the movie cut related categories and \texttt{no\_cut} events were
-modeled as impulse events.\todo{box car of 200 ms starting with the cut}.
+modeled as box car events of 200 ms duration.
 %
@@
 cortex.
-% concluding statement
-\todo[inline]{any concluding statement here or merely report the clusters?}
 
@@
 Results of the analyses that were performed in subject-space can be found in the
-accompanying dataset. \todo{Neurovault does not like unstandardized spaces}
+accompanying dataset.
 % here report in group space
@@
 
-\todo[inline]{BA-plots only shortly mentioned now}
 % Bland-Altman-Plots
@@
 
-\todo[inline]{I tried to keep following part concise but detailed; individual
-contrasts are given but as numbers}
-
 % AV PPA contrasts
@@
 categories) yielded significant bilateral clusters in anterior regions of the
-group PPA overlap (see Figure \ref{fig:stability-slices}).
-% statement/answer
-Results suggest that our findings are robust across differently designed
-contrasts.\todo{concluding statement
-often feels like interpretation}
+group PPA overlap (see Figure \ref{fig:stability-slices}), suggesting
+a certain robustness of this result.
 
@@
 Contrast 12 (\texttt{vse\_new} > \texttt{vse\_old}, \texttt{vpe\_old}) revealed
-one cluster in the right posterior hippocampus. \todo{definitively hippocampus,
-dorsally of PPA}
+one cluster in the right posterior hippocampus.
 
@@
 considered to be the ``optimal'' stimulus type
-\citep{epstein2008parahippocampal}.\todo{a review}
+\citep{epstein2008parahippocampal}.
 % we did not choose se\_new and se\_old
@@
 
-lore ipsum
-
-\section{Conclusions}
-
-\todo[inline]{SE: frage ich mich das beim Durchgehen: Warum ist der Fokus so
-sehr auf Audiobook / AD, während AV doch eigentlich more natural and engaging
-ist? COH: at the moment, the discussion is not tailored to the topic
-``naturalistic stimulus as substitute to localizer'' as it is not and should not
-be the main focus}
-
-\todo[inline]{template has no section ``conclusion'' -> use the last paragraph}
+\ldots
 

### 2021-02-02 paper/main.tex
65% too long
little cleaning

@@
 stimulus \citep{hanke2016simultaneous, hanke2014audiomovie}.
-% varying amount of data
-Contrasts vary in HOW WELL / HOW MUCH DATA.\todo{intro too long already}
 
@@
 hemodynamic activity in [roughly] the same brain regions the block-designed
-visual localizer.\todo{give an interpretation?}
+visual localizer.
 % anterior vs. posterior
@@
         \texttt{fg\_ad\_lrdiff} and \texttt{fg\_av\_ger\_lrdiff}, r=.7749).
-        \todo[inline]{not all labels are actually listed in that table}
+        \todo[inline]{not all labels are actually listed in that table; which
+        ones are not listed? checked it, all labels listed}
       }
@@
 contrasts (\textit{strict}, \textit{relaxed}, and \textit{simple} contrast
-\citep{sengupta2016extension}).\todo{maybe add note regarding Berman (2010); but
-they did FFA}
+\citep{sengupta2016extension}).
 % thus: primary contrasts
@@
 
-\todo[inline]{nouns indicating switch to setting  and cuts to other setting are
-"somewhat" correlated; cf. results -> discussion, part "random shower thoughts"}
-
 \begin{table*}[h!]
@@
 \section{Results}
-
-\todo[inline]{SE: VIS wird selbst gar nicht/en passant berichtet, wäre aber
-wichtig zum Andocken an Literatur}
+\todo[inline]{1400 words}
 
@@
 
-\todo[inline]{individual results: AD trifft besser die VIS-PPA "trifft" als AV.
-    Das ist zumindest sehr überraschend, oder?; COH: actually it isn't because
-    of blindly averaging the actual frame content in the categories of movie
-    cuts (cf. methods/regressors, discussion/shortcomings)}
-
-\todo[inline]{Bland-Altman-Plots: Welche Areale habt ihr als masks
-genommen, FFA ist ja kartiert (Julia Caspers)}
-
 % study goal
-The goal of this study was to investigate if annotated hints about the spatial
-layout embedded in two naturalistic stimuli correlate with increased hemodynamic
-activity in the PPA.
+We investigated if spatial information embedded in two naturalistic stimuli
+correlate with increased hemodynamic activity in the PPA.
 % group level
@@
 the performance of the exclusively auditory naturalistic stimulus as a
-substitute for a visual paradigm to "localize" [?] the PPA.
+substitute for a visual paradigm to localize the PPA.
 % NeuroVault
 Unthresholded $z$-maps of all contrasts on a group level as well as individual
-results of the primary $t$-contrasts co-registered to the group-template (MNI152 space) can found at
-\href{https://neurovault.org/collections/KADGMGVZ/}{NeuroVault}.  \todo{private
-collection}
+results of the primary $t$-contrasts co-registered to the group-template (MNI152
+space) can found at
+\href{https://neurovault.org/collections/KADGMGVZ/}{NeuroVault}.
 
@@
 and cuneal cortex, the lingual gyrus and retrosplenial cortex, the occipital and
-temporal fusiform gyrus and the parahippocampal cortex (reported from posterior
+temporal fusiform gyrus, and the parahippocampal cortex (reported from posterior
 to anterior) in both hemispheres.
@@
 Two additional homologous clusters are located in the superior lateral occipital
-cortex (left bigger than right).
+cortex.
 
@@
 Two homologous clusters are located in the anterior part of the PPA group
-overlap that we gained from the visual localizer experiment.
+overlap..
 % in detail
@@
 % AD is the real shit
-Focussing on the AD stimulus, we hypothesize[d] that an exclusively auditory
-stimulus can/could localize the PPA in individual subjects and thus
-possibly substitute a visual paradigm [using blocks of pictures].
-
-\todo[inline]{if we report procedure of Sengupta as detailed as it is now in the
-following paragraph (imo it's too long), we probably need to explain the
-differences between strict, relaxed, simple set in more detail in the method
-section}
+Furtherm, we hypothesized that an exclusively auditory
+stimulus could localize the PPA in individual subjects and thus
+possibly substitute a classic visual localizer experiment.
+
+\todo[inline]{part regarding Sengupta is shortened; they used $t$-maps???}
 % Sengupta et al., 2016
@@
 % Sengupta: 1 of 3
-Individual PPAs were assessed by visually inspecting thresholded $z$-maps
-(Z>1.64, p<.05 cluster corrected) of three different $t$-contrasts
-(\textit{strict}, \textit{relaxed}, and \textit{simple} stimulus set, cf.
-\citep{sengupta2016extension}).
-% procedure a)
-Starting with the most conservative contrast (\textit{strict} set) and a
-threshold of t = 2.5, we looked for clusters with at least 20 voxels (using
-AFNI).
-% procedure b)
-We titrated [?] the threshold in the range of [2, 3] until we found an isolated
-cluster for the PPA.
-% Sengupta: procedure b)
-If a cluster was not found or not isolated, we used a contrast from the
-\textit{relaxed} set, or finally the \textit{simple} \todo{not used in any VP
-for PPA}set, and repeated the process until we found a cluster that matched the
-expected anatomical location based on literature \citep{epstein1998ppa}.
+Individual PPAs were assessed by titrating [?] the $t$-threshold in the range
+of [2, 3] in the thresholded $t$-maps (Z>1.64, p<.05 cluster corrected) of three
+different $t$-contrasts (\textit{strict}, \textit{relaxed}, and \textit{simple}
+stimulus set cf.  \citep{sengupta2016extension}) until we found an isolated
+cluster that matched the expected anatomical location based on literature
+\citep{epstein1998ppa}.
 
@@
 
+\todo[inline]{2500 chars}
 % Discussion: explains how results fill gap identified in intro
@@
 
+\begin{comment}
+    the mother of total confusion: Aminoff shifts the PPA along the
+    anterior-poster axis depending on publication;
+    in Aminoff (2007, 2013):
+    anterior PPA = spatial associations,
+    region anterior to (!) PPA = non-spatial associations;
+    in Aminoff (2015):
+    posterior PPA = spatial associations,
+    anterior PPA = non-spatial associations;
+    hence: complete bullshit;
+    ignore Aminoff (2015) due to various reasons
+\end{comment}
+
 % PPA AV
@@
 averaged might be.
-
-\todo[inline]{the mother of total confusion: Aminoff shifts the PPA along the
-    anterior-poster axis depending on publication;
-    in Aminoff (2007, 2013):
-    anterior PPA = spatial associations,
-    region anterior to (!) PPA = non-spatial associations;
-    in Aminoff (2015):
-    posterior PPA = spatial associations,
-    anterior PPA = non-spatial associations;
-    hence: complete bullshit;
-    ignore Aminoff (2015) due to various reasons}
 

### 2021-02-04 paper/main.tex
Move side aspects into supplement -> 3500 words in main text
shorten intro

@@
 \citep{penfield1950cerebral, fox1984noninvasive}) have shown that different
-parts of the brain are specialized for different cognitive and perceptual
+parts of the brain are specialized for different perceptual and cognitive
 functions.
@@
 The occipital cortex is considered to be primarily involved in the early stages
-of visual perception and giving rise to two distinct pathways of processing
+of visual perception and giving rise to two distinct pathways that process
 different kind of visual information:
 % dorsal vs ventral pathway
-a dorsal pathway that leads into the parietal lob (the ``where pathway''), and a
-ventral pathway that leads into into the temporal lobe (the ``what pathway'')
+a dorsal stream (the ``where pathway'') that leads into the parietal lob , and a
+ventral stream (the ``what pathway'') that leads into into the temporal lobe
 \citep{goodale1992separate, mishkin1982contribution}.
@@
 regions of the fusiform gyrus and anterior lingual gyrus
-\citep{epstein2008parahippocampal}, and thus is not anatomically but
-functionally defined:
+\citep{epstein2008parahippocampal}:
 % neural correlate of scene perception
@@
 landscapes \citep{ocraven2000mental} and haptic exploration of scenes
-constructed from LEGO blocks \citep{wolbers2011modality} whereas a study using
-spoken sentences yielded mixed results \citep{aziz2008modulation}.
+constructed from LEGO blocks \citep{wolbers2011modality}.
 % O'Craven: watching pictures
@@
 % Aziz (2008): place related sentences
-To our knowledge only one study \citep{aziz2008modulation} investigated how
-hemodynamic activity in the PPA differs between different semantic stimulus
+To our knowledge only one study \citep{aziz2008modulation} compared hemodynamic
+activity levels in the PPA that were correlated with differrent semantic
 categories occurring in spoken language.
-% Aziz' stimuli
-\cite{aziz2008modulation} used sentences that described generic or famous places
-(e.g. ``The Taj Mahal faces a long thin reflecting pool''), faces (``Marilyn
-Monroe has a large square jaw''), or objects (``The television has a long
-antenna'').
-% Aziz' tasks
-Participants were instructed to press a button whenever the sentence described
-an inaccurate or improbable fact.
-% Aziz' results
+% Aziz' stimuli; ``The Taj Mahal faces a long thin reflecting pool'', ``Marilyn
+% Monroe has a large square jaw'', ``The television has a long antenna''
+\cite{aziz2008modulation} used sentences that described famous or generic places
+and faces, or objects.\todo{judgment task not mentioned anymore}
+% Aziz' tasks: Participants were instructed to press a button whenever the
+% sentence described an inaccurate or improbable fact. Aziz' results:
 Activation in the left, but not right, PPA was significantly reduced when
@@
 % GLM contrasts
-Based on these annotations, we created several general linear model (GLM)
-contrast to analyze the corresponding publicly available fMRI datasets
+We then created several general linear model (GLM) contrast to analyze the
+corresponding publicly available fMRI datasets
 (\href{http://www.studyforrest.org}{studyforrest.org}) of each naturalistic
@@
 % hypo a
-We hypothesize[d] that whole-brain analyses will/would reveal increased
-hemodynamic activity spatially constrained to the PPA as functionally defined by
-a visual localizer experiment using pictures done with the same subjects
+We hypothesized that whole-brain analyses would reveal increased hemodynamic
+activity spatially constrained to the PPA as functionally defined by a
+traditional visual localizer experiment done with the same subjects
 \citep{sengupta2016extension}.
-
-We hypothesize[d] that an exclusively auditory stimulus can/could localize
-``visual area'' in individual subjects and thus possibly substitute a
-block-design experiment using pictures.
-% hypo b
-Further, we hypothesize[d] that an exclusively auditory stimulus can/could
-localize the PPA in individual subjects, and thus substitute a visual experiment
-be which would be more practicable to assess brain functions in visually
-impaired persons.
+% hypo b: individuals
+Further, we hypothesized that an exclusively auditory stimulus could localize
+``visual area'' in individual subjects.
+% application in individuals
+An auditory stimulus substituting a visual experiment would be more practicable
+to asses brain functions in visually impaired persons.
 % results: group
@@
 % operationalization in naturalistic stimuli
-results demonstrate that our approach based on annotations [of two ecologically
-more valid stimuli] to operationalize spatial perception lead to increased
-hemodynamic activity in [roughly] the same brain regions the block-designed
-visual localizer.
+results demonstrate that our approach to operationalize spatial perception
+during two naturalistic stimuli lead to increased hemodynamic activity in the
+PPA functionally defined by the visual localizer.
 % anterior vs. posterior
-On both a group and individual subject level, a comparison of results from the
+On both a group and individual subject level, the comparison of results from the
 three datasets also suggests functional differences between the anterior and
@@
 \section{Results}
-\todo[inline]{1400 words}
+\todo[inline]{800 words}
 
@@
 \href{https://neurovault.org/collections/KADGMGVZ/}{NeuroVault}.
-
-\subsection{Primary contrasts}
 
@@
 
-\subsection{Robustness of group results across contrasts}
-
-% unthresholded $z$-maps of all contrasts on a group level:
-% \href{https://neurovault.org/collections/KADGMGVZ/}{NeuroVault}.
-
-% AV PPA contrasts
-% 1 PPA (l/r); RSC (l/r), LOC (l/r), VisC (l/r),
-% intracalcarine, cuneal, ling.c
-% 2 PPA (l/r); RSC (-/-), LOC (l/r), VisC (-/-)
-% 3 PPA (l/r); RSC (-/-), LOC (-/-), VisC (-/r), occ. fusisf. g.
-% 4 PPA (l/r); RSC (l/r), LOC (l/r), VisC (-/-), lingual g., occ. fusif. g.
-% 5 PPA (l/r); RSC (l/r), LOC (l/r), VisC (-/-), occ. fusif. g.
-
-% AV
-In order to test the robustness of our findings, we created four additional
-$t$-contrasts for the AV stimulus (see Table \ref{tab:av-contrasts}) to be
-investigated on a group level.
-% results: PPA; biggest overlap in posterior part of PPA group overlap  =
-%temporal occipital fusiform cortex
-All of the overall five AV contrasts yielded significant bilateral clusters that
-overlap with the PPA group overlap (see Figure \ref{fig:stability-slices}).
-% AD
-For the AD stimulus, we created overall eight $t$-contrasts (see Table
-\ref{tab:ao-contrasts}).
-% results
-All contrasts except contrast 7 (\texttt{se\_new}, \texttt{se\_old} >
-non-spatial categories) and contrast 8 (\texttt{se\_new} > non-spatial
-categories) yielded significant bilateral clusters in anterior regions of the
-group PPA overlap (see Figure \ref{fig:stability-slices}), suggesting
-a certain robustness of this result.
-
-% AD PPA contrasts
-% 1 PPA (l/r); RSC (l/r), LOC (l/r)
-% 2 PPA (l/r); RSC (l/r), LOC (l/r), r. sup.temp.C., r.fr.pole; putamen; etc
-% 3 PPA (l/r); RSC (l/r), LOC (l/r),l&r sup.temp.C., anterior cing., paracing.
-% 4 PPA (l/r); RSC (l/r), LOC (l/r)
-% 5 PPA (l/r); RSC (l/r), LOC (-/-)
-% 6 PPA (l/r); RSC (l/r), LOC (l/-), l&r sup.temp.C.; medial pref. c., precun
-% 7 PPA (-/-); RSC (l/r), LOC (l/-), l&r sup.temp.C.; left frontal pole
-% 8 PPA (-/-); RSC (-/-), LOC (-/-)
-
-% AD
-Reliably across the five contrasts of the AV stimulus, we find bilaterally
-significant clusters also in the ventral precuneal cortex and posterior
-cingulate gyrus (i.e. restrosplenial region; contrasts 1, 4, 5) and lateral
-occipital cortex (contrasts 1, 2, 4, 5).
-% AD; LOC: AV cluster are more medial, AD clusters are more lateral
-Across the five contrasts of the AD stimulus, we find bilaterally
-significant clusters in the ventral precuneus (all except contrasts 8), lateral
-occipital cortex (bilateral in contrasts 1 to 4; unilateral in contrasts 6 and
-7), and superior temporal cortices (bilateral in contrasts 3, 6, 7; unilateral
-right in contrast 2).
-
-% non-systematic
-Lastly, some contrasts of the AD stimulus yielded signficant clusters in regions
-that were not statistically signficant in three or more contrasts.
-%
-Contrast 2 yielded clusters in the anterior cingulate gyrus
-(bilateral), right frontal pole, right frontal medial cortex, and right
-putamen.
-%
-Contrast 3 shows clusters in the anterior cingulate gyrus (bilateral), left
-frontal pole, and left insular.
-%
-Contrast 7 shows clusters in the left frontal pole and left frontal operculum
-[border to triangularis], left insular.
-%
-Contrast 6 shows one additional cluster in the right medial frontal cortex.
-
-\begin{figure*}[h!]
-\centering
-    \includegraphics[width=\linewidth]{figures/stability-slices}
-    \caption{Overlap of significant clusters (Z>3.4; p<.05, cluster corrected)
-        The audio-description's contrasts 1-8 (blue; \ref{tab:ao-contrasts})
-        are overlaid over the audio-visual movie's contrasts 1-5 (red;
-        \ref{tab:av-contrasts}).
-        Cluster are overlaid on top of the MNI152 T1-weighted head template
-        (gray).
-        Black: outline of overlapping individual PPA ROIs.
-        Light gray: The audio-description's field-of-view (cf.
-        \citep{hanke2014audiomovie}).
-        The figure shows that some contrasts yielded significant clusters
-        also in the lateral temporal and prefrontal cortex.
-        }
-    \label{fig:stability-slices}
-\end{figure*}
-
-\subsection{control contrasts}
-
-% ---------- AV control contrasts ----------
-% 6 nothing
-% 7 nothing
-% 8 nothing
-% 9 nothing
-%10 se_new > se_old (nouns but in AV stimulus):
-% LOC (l/r) right PPA, bilateral sup. lat. occ. c., sup. parietal lobe (right)
-
-% ---------- AD control contrasts ----------
-% 9 PPA (-/-); RSC (-/r), LOC (-/-), left pars triangularis
-%10 PPA (-/-); RSC (-/-), LOC (-/-)
-%11 PPA (-/-); RSC (-/-), LOC (-/-),
-%12 PPA (-/-); RSC (-/-), LOC (-/-), right posterior hippocampus
-%13 PPA (-/-); RSC (-/-), LOC (-/-)
-
-\todo[inline]{there is no table/figure for negative control contrasts; we could
-add a reference to NeuroVault (here again) or point to the dataset}
-
-% intro
-Lastly, we implemented five contrasts for every stimulus for the purpose of
-negative control.
-% AV: no_cut > x
-In the analysis of the AV data, none of the contrasts that compared the ``no cut
-condition''  to a movie cut category (contrasts 6, 7, 8, 9) yielded significant
-clusters.
-% AV using nouns
-The contrast that used the narrator's nouns but in the AV stimulus
-(\texttt{se\_new} > \texttt{se\_old}) yielded a significant cluster in the right
-PPA and bilateral clusters in the superior lateral occipital cortices (the right
-hemispheric cluster extending into the superior parietal cortex).
-
-% AD stimulus
-In the analysis of the AD data, we created control contrasts based on events of
-the annotated movie cuts (cf. Table \ref{tab:ao-contrasts})
-% contrast 9
-Contrast 9 (vse\_new > pe\_old) revealed one significant cluster in the left
-inferior prefrontal cortex (pars triangularis) and right ventral
-precuneus/posterior cingulate gyrus.
-% contrast 12
-Contrast 12 (\texttt{vse\_new} > \texttt{vse\_old}, \texttt{vpe\_old}) revealed
-one cluster in the right posterior hippocampus.
-
 \section{Discussion}
 
-\todo[inline]{2500 chars}
+\todo[inline]{1700 words}
 % Discussion: explains how results fill gap identified in intro
@@
 
-\subsection{Robust results across contrasts}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%
+%%%
+
+\subsubsection{not many random cluster + naturalistic stimuli are cool}
+
+% ``confounding'' clusters
+Despite performing a whole brain analysis, we do not find many [random] clusters
+in single contrasts or even systematically across contrasts that hamper the
+interpretation of results.\todo{ouff\dots}
+% AV: null results regarding attention and eye movements
+For example in the AV results, we do not find significant clusters that could be
+attributed to cognitive processes like attention or eye movements.
+% AD: auditory cortices
+Nevertheless, contrasts of the AD stimulus that compare (among others) verbal
+hints of the change of a setting (\texttt{se\_new} or \texttt{se\_old}) to all
+non-spatial categories (cf. contrasts 2, 3, 6, 7) show significant clusters in
+(primary and secondary) auditory cortices.
+% averaging vs. nuisance regressors
+This suggests that variance correlating with lower level auditory processes was
+not averaged out across trials and nuisance regressors did not capture enough
+variance.\todo{ouf\dots}
+% possible reason
+Significant clusters in auditory cortices could be correlating with a possible
+change of the soundscape when the narrator of the audio-description (or a cut in
+the movie) switches to a another setting.
+% concluding statement
+Thus, investigators that use model-driven methods to investigate brain functions
+using naturalistic stimuli should (extensively) annotate the stimulus material
+and test for correlations among variables.
+
+\subsubsection{naturalistic stimuli + data re-use, fuck yeah}
+
+\ldots
+
+% natural stimulation
+Natural stimuli like movies \citep{eickhoff2020towards,
+hasson2008neurocinematics, sonkusare2019naturalistic} or narratives
+\citep{hamilton2018revolution, honey2012not, lerner2011topographic,
+silbert2014coupled, wilson2008beyond} offer an easy to implement, (continuous,)
+complex, immersive, task-free paradigm that more closely resembles our natural
+dynamic environment than traditional experimental designs.
+
+\begin{itemize}
+\item We reuse public data for independent research question
+\item GLM based on annotations to operationalize ``spatial perception''
+\item Our results add evidence that model-driven analyses based in annotations
+can be run on data from naturalistic stimuli to ``localize'' brain activity
+correlating with specific perceptual processes.
+\item ``localization performance'' relies on how well the model captures
+different aspects of the stimuli's feature space.
+\item PPA is functionally heterogeneous region
+\item a complex but naturally engaging auditory stimulus like an
+audiobook might in principle be used as a non-visual localizer for a variety of
+brain functions in subjects who are not willing or able to follow task
+instructions during brain scanning [would state that explicitly in the summary
+at the end].
+\end{itemize}
+
+% \citep{hanke2014audiomovie}: the AD stimulus leaves a much larger margin for
+% inter-individual differences in imagining scenery. The AD stimulus limits the
+% effect of an attentional focus on the selection of a subset of simultaneously
+% occurring auditory events, in contrast to the selection of different parts of
+% the visual field.
+
+\subsection*{Code availability}
+% wo kommt dieser Abschnitt hin?  how to write Code availability statement
+% https://www.springernature.com/gp/authors/research-data-policy/data-availability-statements/12330880
+\todo[inline]{provide supporting source code, and explaining how and where
+others may access all data underlying the analysis} \emph{for all studies using
+    custom code in the generation or processing of datasets, a statement must be
+    included here, indicating whether and how the code can be accessed,
+including any restrictions to access; include information on the versions of any
+software used, if relevant, and any specific variables or parameters used to
+generate, test, or process the current dataset. }
+
+\section*{Acknowledgements}
+% Text acknowledging non-author contributors.
+Acknowledgements should be brief, and should not include thanks to anonymous referees and editors, or effusive comments.
+Grant or contribution numbers may be acknowledged.
+% Author contributions Please describe briefly the contributions of each author to this work on a separate line.
+\emph{COH did this and that.
+MH did this and that.
+We are grateful to \href{www.florianschurz.de}{Florian Schurz} who initiated doing the annotation of the descriptive nouns, and performed the preliminary annotation of nouns.}
+
+\section*{Competing financial interests}
+\emph{A competing financial interests statement is required for all accepted
+papers published in \emph{Scientific Data}. If none exist simply write,
+``The author(s) declare no competing financial interests''.}
+
+\section*{Figures Legends}
+\emph{Figure should be referred to using a consistent numbering scheme through
+the entire Data Descriptor. For initial submissions, authors may choose
+to supply this document as a single PDF with embedded figures, but
+separate figure image files must be provided for revisions and accepted
+manuscripts. In most cases, a Data Descriptor should not contain more
+than three figures, but more may be allowed when needed. We discourage
+the inclusion of figures in the Supplementary Information \textendash{}
+all key figures should be included here in the main Figure section.}
+
+\emph{Figure legends begin with a brief title sentence for the whole figure
+and continue with a short description of what is shown in each panel,
+as well as explaining any symbols used. Legend must total no more
+than 350 words, and may contain literature references.}
+
+\section*{Tables}
+
+\emph{Tables supporting the Data Descriptor. These can provide summary information
+(sample numbers, demographics, etc.), but they should generally not
+be used to present primary data (i.e. measurements). Tables containing
+primary data should be submitted to an appropriate data repository.}
+
+\emph{Tables may be provided within the \LaTeX{} document or as separate
+files (tab-delimited text or Excel files). Legends, where needed,
+should be included here. Generally, a Data Descriptor should have
+fewer than ten Tables, but more may be allowed when needed. Tables
+may be of any size, but only Tables which fit onto a single printed
+page will be included in the PDF version of the article (up to a maximum
+of three).}
+
+{\small\bibliographystyle{unsrtnat}
+\bibliography{references}}
+
+%\begin{thebibliography}{1}
+%\expandafter\ifx\csname url\endcsname\relax
+%  \def\url#1{\texttt{#1}}\fi
+%\expandafter\ifx\csname urlprefix\endcsname\relax\def\urlprefix{URL }\fi
+%\providecommand{\bibinfo}[2]{#2}
+%\providecommand{\eprint}[2][]{\url{#2}}
+%
+%\bibitem{cite1}
+%\bibinfo{author}{Califano, A.}, \bibinfo{author}{Butte, A.~J.},
+%  \bibinfo{author}{Friend, S.}, \bibinfo{author}{Ideker, T.} \&
+%  \bibinfo{author}{Schadt, E.}
+%\newblock \bibinfo{title}{{Leveraging models of cell regulation and GWAS data
+%  in integrative network-based association studies}}.
+%\newblock \emph{\bibinfo{journal}{Nature Genetics}}
+%  \textbf{\bibinfo{volume}{44}}, \bibinfo{pages}{841--847}
+%  (\bibinfo{year}{2012}).
+%
+%\bibitem{cite2}
+%\bibinfo{author}{Wang, R.} \emph{et~al.}
+%\newblock \bibinfo{title}{{PRIDE Inspector: a tool to visualize and validate MS
+%  proteomics data.}}
+%\newblock \emph{\bibinfo{journal}{Nature Biotechnology}}
+%  \textbf{\bibinfo{volume}{30}}, \bibinfo{pages}{135--137}
+%  (\bibinfo{year}{2012}).
+%\end{thebibliography}
+
+\section{Data Citations}
+
+Bibliographic information for the data records described in the manuscript.
+
+1. Lastname1, Initial1., Lastname2, Initial2., ...\& LastnameN, InitialN. \emph{Repository name} Dataset accession number or DOI (YYYY).
+
+\appendix
+
+\section{Supplementary Materials}
+
+\subsection{Robustness of group results across contrasts}
+
+% unthresholded $z$-maps of all contrasts on a group level:
+% \href{https://neurovault.org/collections/KADGMGVZ/}{NeuroVault}.
+
+% AV PPA contrasts
+% 1 PPA (l/r); RSC (l/r), LOC (l/r), VisC (l/r),
+% intracalcarine, cuneal, ling.c
+% 2 PPA (l/r); RSC (-/-), LOC (l/r), VisC (-/-)
+% 3 PPA (l/r); RSC (-/-), LOC (-/-), VisC (-/r), occ. fusisf. g.
+% 4 PPA (l/r); RSC (l/r), LOC (l/r), VisC (-/-), lingual g., occ. fusif. g.
+% 5 PPA (l/r); RSC (l/r), LOC (l/r), VisC (-/-), occ. fusif. g.
+
+% AV
+In order to test the robustness of our findings, we created four additional
+$t$-contrasts for the AV stimulus (see Table \ref{tab:av-contrasts}) to be
+investigated on a group level.
+% results: PPA; biggest overlap in posterior part of PPA group overlap  =
+%temporal occipital fusiform cortex
+All of the overall five AV contrasts yielded significant bilateral clusters that
+overlap with the PPA group overlap (see Figure \ref{fig:stability-slices}).
+% AD
+For the AD stimulus, we created overall eight $t$-contrasts (see Table
+\ref{tab:ao-contrasts}).
+% results
+All contrasts except contrast 7 (\texttt{se\_new}, \texttt{se\_old} >
+non-spatial categories) and contrast 8 (\texttt{se\_new} > non-spatial
+categories) yielded significant bilateral clusters in anterior regions of the
+group PPA overlap (see Figure \ref{fig:stability-slices}), suggesting
+a certain robustness of this result.
+
+% AD PPA contrasts
+% 1 PPA (l/r); RSC (l/r), LOC (l/r)
+% 2 PPA (l/r); RSC (l/r), LOC (l/r), r. sup.temp.C., r.fr.pole; putamen; etc
+% 3 PPA (l/r); RSC (l/r), LOC (l/r),l&r sup.temp.C., anterior cing., paracing.
+% 4 PPA (l/r); RSC (l/r), LOC (l/r)
+% 5 PPA (l/r); RSC (l/r), LOC (-/-)
+% 6 PPA (l/r); RSC (l/r), LOC (l/-), l&r sup.temp.C.; medial pref. c., precun
+% 7 PPA (-/-); RSC (l/r), LOC (l/-), l&r sup.temp.C.; left frontal pole
+% 8 PPA (-/-); RSC (-/-), LOC (-/-)
+
+% AD
+Reliably across the five contrasts of the AV stimulus, we find bilaterally
+significant clusters also in the ventral precuneal cortex and posterior
+cingulate gyrus (i.e. restrosplenial region; contrasts 1, 4, 5) and lateral
+occipital cortex (contrasts 1, 2, 4, 5).
+% AD; LOC: AV cluster are more medial, AD clusters are more lateral
+Across the five contrasts of the AD stimulus, we find bilaterally
+significant clusters in the ventral precuneus (all except contrasts 8), lateral
+occipital cortex (bilateral in contrasts 1 to 4; unilateral in contrasts 6 and
+7), and superior temporal cortices (bilateral in contrasts 3, 6, 7; unilateral
+right in contrast 2).
+
+% non-systematic
+Lastly, some contrasts of the AD stimulus yielded signficant clusters in regions
+that were not statistically signficant in three or more contrasts.
+%
+Contrast 2 yielded clusters in the anterior cingulate gyrus
+(bilateral), right frontal pole, right frontal medial cortex, and right
+putamen.
+%
+Contrast 3 shows clusters in the anterior cingulate gyrus (bilateral), left
+frontal pole, and left insular.
+%
+Contrast 7 shows clusters in the left frontal pole and left frontal operculum
+[border to triangularis], left insular.
+%
+Contrast 6 shows one additional cluster in the right medial frontal cortex.
+
+\begin{figure*}[h!]
+\centering
+    \includegraphics[width=\linewidth]{figures/stability-slices}
+    \caption{Overlap of significant clusters (Z>3.4; p<.05, cluster corrected)
+        The audio-description's contrasts 1-8 (blue; \ref{tab:ao-contrasts})
+        are overlaid over the audio-visual movie's contrasts 1-5 (red;
+        \ref{tab:av-contrasts}).
+        Cluster are overlaid on top of the MNI152 T1-weighted head template
+        (gray).
+        Black: outline of overlapping individual PPA ROIs.
+        Light gray: The audio-description's field-of-view (cf.
+        \citep{hanke2014audiomovie}).
+        The figure shows that some contrasts yielded significant clusters
+        also in the lateral temporal and prefrontal cortex.
+        }
+    \label{fig:stability-slices}
+\end{figure*}
+
+\subsection{control contrasts}
+
+% ---------- AV control contrasts ----------
+% 6 nothing
+% 7 nothing
+% 8 nothing
+% 9 nothing
+%10 se_new > se_old (nouns but in AV stimulus):
+% LOC (l/r) right PPA, bilateral sup. lat. occ. c., sup. parietal lobe (right)
+
+% ---------- AD control contrasts ----------
+% 9 PPA (-/-); RSC (-/r), LOC (-/-), left pars triangularis
+%10 PPA (-/-); RSC (-/-), LOC (-/-)
+%11 PPA (-/-); RSC (-/-), LOC (-/-),
+%12 PPA (-/-); RSC (-/-), LOC (-/-), right posterior hippocampus
+%13 PPA (-/-); RSC (-/-), LOC (-/-)
+
+\todo[inline]{there is no table/figure for negative control contrasts; we could
+add a reference to NeuroVault (here again) or point to the dataset}
+
+% intro
+Lastly, we implemented five contrasts for every stimulus for the purpose of
+negative control.
+% AV: no_cut > x
+In the analysis of the AV data, none of the contrasts that compared the ``no cut
+condition''  to a movie cut category (contrasts 6, 7, 8, 9) yielded significant
+clusters.
+% AV using nouns
+The contrast that used the narrator's nouns but in the AV stimulus
+(\texttt{se\_new} > \texttt{se\_old}) yielded a significant cluster in the right
+PPA and bilateral clusters in the superior lateral occipital cortices (the right
+hemispheric cluster extending into the superior parietal cortex).
+
+% AD stimulus
+In the analysis of the AD data, we created control contrasts based on events of
+the annotated movie cuts (cf. Table \ref{tab:ao-contrasts})
+% contrast 9
+Contrast 9 (vse\_new > pe\_old) revealed one significant cluster in the left
+inferior prefrontal cortex (pars triangularis) and right ventral
+precuneus/posterior cingulate gyrus.
+% contrast 12
+Contrast 12 (\texttt{vse\_new} > \texttt{vse\_old}, \texttt{vpe\_old}) revealed
+one cluster in the right posterior hippocampus.
+
+\subsection{Discussion: Robust results across contrasts}
 
@@
 
-\subsubsection{not many random cluster + naturalistic stimuli are cool}
-
-% ``confounding'' clusters
-Despite performing a whole brain analysis, we do not find many [random] clusters
-in single contrasts or even systematically across contrasts that hamper the
-interpretation of results.\todo{ouff\dots}
-% AV: null results regarding attention and eye movements
-For example in the AV results, we do not find significant clusters that could be
-attributed to cognitive processes like attention or eye movements.
-% AD: auditory cortices
-Nevertheless, contrasts of the AD stimulus that compare (among others) verbal
-hints of the change of a setting (\texttt{se\_new} or \texttt{se\_old}) to all
-non-spatial categories (cf. contrasts 2, 3, 6, 7) show significant clusters in
-(primary and secondary) auditory cortices.
-% averaging vs. nuisance regressors
-This suggests that variance correlating with lower level auditory processes was
-not averaged out across trials and nuisance regressors did not capture enough
-variance.\todo{ouf\dots}
-% possible reason
-Significant clusters in auditory cortices could be correlating with a possible
-change of the soundscape when the narrator of the audio-description (or a cut in
-the movie) switches to a another setting.
-% concluding statement
-Thus, investigators that use model-driven methods to investigate brain functions
-using naturalistic stimuli should (extensively) annotate the stimulus material
-and test for correlations among variables.
-
-\subsubsection{naturalistic stimuli + data re-use, fuck yeah}
-
-\ldots
-
-% natural stimulation
-Natural stimuli like movies \citep{eickhoff2020towards,
-hasson2008neurocinematics, sonkusare2019naturalistic} or narratives
-\citep{hamilton2018revolution, honey2012not, lerner2011topographic,
-silbert2014coupled, wilson2008beyond} offer an easy to implement, (continuous,)
-complex, immersive, task-free paradigm that more closely resembles our natural
-dynamic environment than traditional experimental designs.
-
-\begin{itemize}
-\item We reuse public data for independent research question
-\item GLM based on annotations to operationalize ``spatial perception''
-\item Our results add evidence that model-driven analyses based in annotations
-can be run on data from naturalistic stimuli to ``localize'' brain activity
-correlating with specific perceptual processes.
-\item ``localization performance'' relies on how well the model captures
-different aspects of the stimuli's feature space.
-\item PPA is functionally heterogeneous region
-\item a complex but naturally engaging auditory stimulus like an
-audiobook might in principle be used as a non-visual localizer for a variety of
-brain functions in subjects who are not willing or able to follow task
-instructions during brain scanning [would state that explicitly in the summary
-at the end].
-\end{itemize}
-
-% \citep{hanke2014audiomovie}: the AD stimulus leaves a much larger margin for
-% inter-individual differences in imagining scenery. The AD stimulus limits the
-% effect of an attentional focus on the selection of a subset of simultaneously
-% occurring auditory events, in contrast to the selection of different parts of
-% the visual field.
-
-\subsection*{Code availability}
-% wo kommt dieser Abschnitt hin?  how to write Code availability statement
-% https://www.springernature.com/gp/authors/research-data-policy/data-availability-statements/12330880
-\todo[inline]{provide supporting source code, and explaining how and where
-others may access all data underlying the analysis} \emph{for all studies using
-    custom code in the generation or processing of datasets, a statement must be
-    included here, indicating whether and how the code can be accessed,
-including any restrictions to access; include information on the versions of any
-software used, if relevant, and any specific variables or parameters used to
-generate, test, or process the current dataset. }
-
-\section*{Acknowledgements}
-% Text acknowledging non-author contributors.
-Acknowledgements should be brief, and should not include thanks to anonymous referees and editors, or effusive comments.
-Grant or contribution numbers may be acknowledged.
-% Author contributions Please describe briefly the contributions of each author to this work on a separate line.
-\emph{COH did this and that.
-MH did this and that.
-We are grateful to \href{www.florianschurz.de}{Florian Schurz} who initiated doing the annotation of the descriptive nouns, and performed the preliminary annotation of nouns.}
-
-\section*{Competing financial interests}
-\emph{A competing financial interests statement is required for all accepted
-papers published in \emph{Scientific Data}. If none exist simply write,
-``The author(s) declare no competing financial interests''.}
-
-\section*{Figures Legends}
-\emph{Figure should be referred to using a consistent numbering scheme through
-the entire Data Descriptor. For initial submissions, authors may choose
-to supply this document as a single PDF with embedded figures, but
-separate figure image files must be provided for revisions and accepted
-manuscripts. In most cases, a Data Descriptor should not contain more
-than three figures, but more may be allowed when needed. We discourage
-the inclusion of figures in the Supplementary Information \textendash{}
-all key figures should be included here in the main Figure section.}
-
-\emph{Figure legends begin with a brief title sentence for the whole figure
-and continue with a short description of what is shown in each panel,
-as well as explaining any symbols used. Legend must total no more
-than 350 words, and may contain literature references.}
-
-\section*{Tables}
-
-\emph{Tables supporting the Data Descriptor. These can provide summary information
-(sample numbers, demographics, etc.), but they should generally not
-be used to present primary data (i.e. measurements). Tables containing
-primary data should be submitted to an appropriate data repository.}
-
-\emph{Tables may be provided within the \LaTeX{} document or as separate
-files (tab-delimited text or Excel files). Legends, where needed,
-should be included here. Generally, a Data Descriptor should have
-fewer than ten Tables, but more may be allowed when needed. Tables
-may be of any size, but only Tables which fit onto a single printed
-page will be included in the PDF version of the article (up to a maximum
-of three).}
-
-{\small\bibliographystyle{unsrtnat}
-\bibliography{references}}
-
-%\begin{thebibliography}{1}
-%\expandafter\ifx\csname url\endcsname\relax
-%  \def\url#1{\texttt{#1}}\fi
-%\expandafter\ifx\csname urlprefix\endcsname\relax\def\urlprefix{URL }\fi
-%\providecommand{\bibinfo}[2]{#2}
-%\providecommand{\eprint}[2][]{\url{#2}}
-%
-%\bibitem{cite1}
-%\bibinfo{author}{Califano, A.}, \bibinfo{author}{Butte, A.~J.},
-%  \bibinfo{author}{Friend, S.}, \bibinfo{author}{Ideker, T.} \&
-%  \bibinfo{author}{Schadt, E.}
-%\newblock \bibinfo{title}{{Leveraging models of cell regulation and GWAS data
-%  in integrative network-based association studies}}.
-%\newblock \emph{\bibinfo{journal}{Nature Genetics}}
-%  \textbf{\bibinfo{volume}{44}}, \bibinfo{pages}{841--847}
-%  (\bibinfo{year}{2012}).
-%
-%\bibitem{cite2}
-%\bibinfo{author}{Wang, R.} \emph{et~al.}
-%\newblock \bibinfo{title}{{PRIDE Inspector: a tool to visualize and validate MS
-%  proteomics data.}}
-%\newblock \emph{\bibinfo{journal}{Nature Biotechnology}}
-%  \textbf{\bibinfo{volume}{30}}, \bibinfo{pages}{135--137}
-%  (\bibinfo{year}{2012}).
-%\end{thebibliography}
-
-\section*{Data Citations}
-
-Bibliographic information for the data records described in the manuscript.
-
-1. Lastname1, Initial1., Lastname2, Initial2., ...\& LastnameN, InitialN. \emph{Repository name} Dataset accession number or DOI (YYYY).
-
 \end{document}

### 2021-02-04 paper/main.tex
method: places vs. faces

@@
 
-\noindent Intro:
-
-\begin{itemize}
-    \item make more concise if applicable
-\end{itemize}
-
 \noindent Method:
@@
 \begin{itemize}
-    \item how much details regarding procedure in Sengupta?
-    \item ggf. berichten welcher VIS Kontraste jeweils genommen wurde
-    \item results allg. kürzen (war nicht ganz einfach)
     \item check if captions of figs and tables now (really) match phrasing
@@
 \begin{itemize}
-    \item Discussion is restructured \& most paragraphs adopted to new structure
     \item as Simon stated I would be interesting to discuss differences between
@@
     limit by far
-    \item mehr zum Thema VIS? ("best contrast was chosen")
     \item overall conclusion as a last paragraph or independent section
@@
 % our approach: annotation and regressors
-Naturalistic stimuli [might] more closely mimic how we experience the world
-around us but have the drawback that they are usually fix and that their
-temporal structure of embedded stimulus features is unknown.
+Naturalistic stimuli mimic how we experience the world more closely but have the
+drawback that they are usually fix and that their temporal structure is unknown.
 % annotation ftw
-Hence, we annotated a variety of stimulus features that later served as a basis
-(for GLM regressors) to model hemodynamic responses.
+Hence, we annotated a the temporal structure of a various stimulus features that
+later served as a basis (for GLM regressors) to model hemodynamic responses.
 
@@
 Notably, categorization was performed irrespectively of a movie frame's precise
-content and thus without controlling confounding variables (e.g. presence of
-faces).
+content and thus without controlling confounding variables.
 % AV COPEs: intro
-The rationale that this approach would still yield categories correlating with
-increased hemodynamic activity in the PPA was twofold.
+The rationale that this approach would yield categories that - on average - show
+different stimulus features.
 % cinematographic rationale cut to new scenes: establishing shots
-The cinematographic rationale was that movies tend to establish the setting
+The cinematographic rationale was that movie shots tend to establish the setting
 (\texttt{vse\_new}) and the spatial relationships within a setting
@@
 % similarly for shots within a scene
-Moreover, shots within a recurring locale or setting tend to shift to depicting
-persons and objects (\texttt{vpe\_old}) more relevant to the evolved plot
+Later in the movie when the spatial layout of a setting is already established,
+shots within a setting shift to objects more relevant to the evolved plot and or
+to switching between faces of persons talking to each others (\texttt{vpe\_old})
 \citep{brown2012cinematography, mercado2011filmmakers}.
@@
 participants view novel versus repeated scenes or view-points
-\citep{epstein1999parahippocampal, grill2006repetition}.
+\citep{epstein1999parahippocampal, grill2006repetition}.\todo[inline]{doesn't
+make sense not 'cause this should be true to the face of forrest too}
 % no cut condition: intro
@@
 In the primary contrast of the AV stimulus, we contrasted cuts to a setting that
-was not depicted before (\texttt{vs\_new}) to cuts that we accompanied with a
+was not depicted before (\texttt{vse\_new}) to cuts that we accompanied with a
 change of the camera position within a setting that was already occurring
@@
 % why
-We assumed that movie frames in these categories on average best represent
-events that trigger perception of space versus e.g. objects or faces.
+We assumed that category \texttt{vse\_new} on average comprised the most movie
+frames depicting a landscape or the geometry of a setting, and the category
+\texttt{vpe\_old} the most frames depicting persons, faces, or
+objects.\todo{maybe speak of ratio}
 % AD: primary contrast
@@
 \texttt{fahead}, \texttt{object}, \texttt{sex\_f}, \texttt{sex\_m}) except
-\texttt{furniture}.
+\texttt{furniture} to get a sufficient amount of events per stimulus
+segment.
+% furniture
+The category ``furniture'' (\texttt{furn}) was not used as a regressor of
+interest in any contrast because these nouns could be perceived as either a
+geometry-defining scene element or as an isolated object.
 % why se_new & se_old were not used in the primary contrasts
-The categories of nouns indicating a switch to a setting that occurred for the first time
-(\texttt{se\_new}) or a setting that recurred during the plot (\texttt{se\_old})
-were not included in the primary contrast because
+The categories of nouns indicating a switch to a setting that occurred for the
+first time (\texttt{se\_new}) or a setting that recurred during the plot
+(\texttt{se\_old}) were not included in the primary contrast because
 % heterogeneous category
@@
 soundscape that might already indicate a change of settings.
-% furniture
-The category ``furniture'' (\texttt{furn}) was not used as a regressor of
-interest in any contrast because these nouns could be perceived differently by
-different subjects as either a geometry-defining scene element or as an isolated
-object.
-
+\todo[inline]{paragraph above could state that ``fahead'', just N=83; mostly
+    just parts (``ear'', ``nose'') of face, or vague description ``his/her
+face''}.
 % control contrasts
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%
-%%%
-
-\subsubsection{not many random cluster + naturalistic stimuli are cool}
-
-% ``confounding'' clusters
-Despite performing a whole brain analysis, we do not find many [random] clusters
-in single contrasts or even systematically across contrasts that hamper the
-interpretation of results.\todo{ouff\dots}
-% AV: null results regarding attention and eye movements
-For example in the AV results, we do not find significant clusters that could be
-attributed to cognitive processes like attention or eye movements.
-% AD: auditory cortices
-Nevertheless, contrasts of the AD stimulus that compare (among others) verbal
-hints of the change of a setting (\texttt{se\_new} or \texttt{se\_old}) to all
-non-spatial categories (cf. contrasts 2, 3, 6, 7) show significant clusters in
-(primary and secondary) auditory cortices.
-% averaging vs. nuisance regressors
-This suggests that variance correlating with lower level auditory processes was
-not averaged out across trials and nuisance regressors did not capture enough
-variance.\todo{ouf\dots}
-% possible reason
-Significant clusters in auditory cortices could be correlating with a possible
-change of the soundscape when the narrator of the audio-description (or a cut in
-the movie) switches to a another setting.
-% concluding statement
-Thus, investigators that use model-driven methods to investigate brain functions
-using naturalistic stimuli should (extensively) annotate the stimulus material
-and test for correlations among variables.
-
-\subsubsection{naturalistic stimuli + data re-use, fuck yeah}
-
-\ldots
-
-% natural stimulation
-Natural stimuli like movies \citep{eickhoff2020towards,
-hasson2008neurocinematics, sonkusare2019naturalistic} or narratives
-\citep{hamilton2018revolution, honey2012not, lerner2011topographic,
-silbert2014coupled, wilson2008beyond} offer an easy to implement, (continuous,)
-complex, immersive, task-free paradigm that more closely resembles our natural
-dynamic environment than traditional experimental designs.
-
-\begin{itemize}
-\item We reuse public data for independent research question
-\item GLM based on annotations to operationalize ``spatial perception''
-\item Our results add evidence that model-driven analyses based in annotations
-can be run on data from naturalistic stimuli to ``localize'' brain activity
-correlating with specific perceptual processes.
-\item ``localization performance'' relies on how well the model captures
-different aspects of the stimuli's feature space.
-\item PPA is functionally heterogeneous region
-\item a complex but naturally engaging auditory stimulus like an
-audiobook might in principle be used as a non-visual localizer for a variety of
-brain functions in subjects who are not willing or able to follow task
-instructions during brain scanning [would state that explicitly in the summary
-at the end].
-\end{itemize}
-
-% \citep{hanke2014audiomovie}: the AD stimulus leaves a much larger margin for
-% inter-individual differences in imagining scenery. The AD stimulus limits the
-% effect of an attentional focus on the selection of a subset of simultaneously
-% occurring auditory events, in contrast to the selection of different parts of
-% the visual field.
-
-\subsection*{Code availability}
-% wo kommt dieser Abschnitt hin?  how to write Code availability statement
-% https://www.springernature.com/gp/authors/research-data-policy/data-availability-statements/12330880
-\todo[inline]{provide supporting source code, and explaining how and where
-others may access all data underlying the analysis} \emph{for all studies using
-    custom code in the generation or processing of datasets, a statement must be
-    included here, indicating whether and how the code can be accessed,
-including any restrictions to access; include information on the versions of any
-software used, if relevant, and any specific variables or parameters used to
-generate, test, or process the current dataset. }
-
-\section*{Acknowledgements}
-% Text acknowledging non-author contributors.
-Acknowledgements should be brief, and should not include thanks to anonymous referees and editors, or effusive comments.
-Grant or contribution numbers may be acknowledged.
-% Author contributions Please describe briefly the contributions of each author to this work on a separate line.
-\emph{COH did this and that.
-MH did this and that.
-We are grateful to \href{www.florianschurz.de}{Florian Schurz} who initiated doing the annotation of the descriptive nouns, and performed the preliminary annotation of nouns.}
-
-\section*{Competing financial interests}
-\emph{A competing financial interests statement is required for all accepted
-papers published in \emph{Scientific Data}. If none exist simply write,
-``The author(s) declare no competing financial interests''.}
-
-\section*{Figures Legends}
-\emph{Figure should be referred to using a consistent numbering scheme through
-the entire Data Descriptor. For initial submissions, authors may choose
-to supply this document as a single PDF with embedded figures, but
-separate figure image files must be provided for revisions and accepted
-manuscripts. In most cases, a Data Descriptor should not contain more
-than three figures, but more may be allowed when needed. We discourage
-the inclusion of figures in the Supplementary Information \textendash{}
-all key figures should be included here in the main Figure section.}
-
-\emph{Figure legends begin with a brief title sentence for the whole figure
-and continue with a short description of what is shown in each panel,
-as well as explaining any symbols used. Legend must total no more
-than 350 words, and may contain literature references.}
-
-\section*{Tables}
-
-\emph{Tables supporting the Data Descriptor. These can provide summary information
-(sample numbers, demographics, etc.), but they should generally not
-be used to present primary data (i.e. measurements). Tables containing
-primary data should be submitted to an appropriate data repository.}
-
-\emph{Tables may be provided within the \LaTeX{} document or as separate
-files (tab-delimited text or Excel files). Legends, where needed,
-should be included here. Generally, a Data Descriptor should have
-fewer than ten Tables, but more may be allowed when needed. Tables
-may be of any size, but only Tables which fit onto a single printed
-page will be included in the PDF version of the article (up to a maximum
-of three).}
-
-{\small\bibliographystyle{unsrtnat}
-\bibliography{references}}
-
-%\begin{thebibliography}{1}
-%\expandafter\ifx\csname url\endcsname\relax
-%  \def\url#1{\texttt{#1}}\fi
-%\expandafter\ifx\csname urlprefix\endcsname\relax\def\urlprefix{URL }\fi
-%\providecommand{\bibinfo}[2]{#2}
-%\providecommand{\eprint}[2][]{\url{#2}}
-%
-%\bibitem{cite1}
-%\bibinfo{author}{Califano, A.}, \bibinfo{author}{Butte, A.~J.},
-%  \bibinfo{author}{Friend, S.}, \bibinfo{author}{Ideker, T.} \&
-%  \bibinfo{author}{Schadt, E.}
-%\newblock \bibinfo{title}{{Leveraging models of cell regulation and GWAS data
-%  in integrative network-based association studies}}.
-%\newblock \emph{\bibinfo{journal}{Nature Genetics}}
-%  \textbf{\bibinfo{volume}{44}}, \bibinfo{pages}{841--847}
-%  (\bibinfo{year}{2012}).
-%
-%\bibitem{cite2}
-%\bibinfo{author}{Wang, R.} \emph{et~al.}
-%\newblock \bibinfo{title}{{PRIDE Inspector: a tool to visualize and validate MS
-%  proteomics data.}}
-%\newblock \emph{\bibinfo{journal}{Nature Biotechnology}}
-%  \textbf{\bibinfo{volume}{30}}, \bibinfo{pages}{135--137}
-%  (\bibinfo{year}{2012}).
-%\end{thebibliography}
-
-\section{Data Citations}
-
-Bibliographic information for the data records described in the manuscript.
-
-1. Lastname1, Initial1., Lastname2, Initial2., ...\& LastnameN, InitialN. \emph{Repository name} Dataset accession number or DOI (YYYY).
-
-\appendix
-
-\section{Supplementary Materials}
-
-\subsection{Robustness of group results across contrasts}
-
-% unthresholded $z$-maps of all contrasts on a group level:
-% \href{https://neurovault.org/collections/KADGMGVZ/}{NeuroVault}.
-
-% AV PPA contrasts
-% 1 PPA (l/r); RSC (l/r), LOC (l/r), VisC (l/r),
-% intracalcarine, cuneal, ling.c
-% 2 PPA (l/r); RSC (-/-), LOC (l/r), VisC (-/-)
-% 3 PPA (l/r); RSC (-/-), LOC (-/-), VisC (-/r), occ. fusisf. g.
-% 4 PPA (l/r); RSC (l/r), LOC (l/r), VisC (-/-), lingual g., occ. fusif. g.
-% 5 PPA (l/r); RSC (l/r), LOC (l/r), VisC (-/-), occ. fusif. g.
-
-% AV
-In order to test the robustness of our findings, we created four additional
-$t$-contrasts for the AV stimulus (see Table \ref{tab:av-contrasts}) to be
-investigated on a group level.
-% results: PPA; biggest overlap in posterior part of PPA group overlap  =
-%temporal occipital fusiform cortex
-All of the overall five AV contrasts yielded significant bilateral clusters that
-overlap with the PPA group overlap (see Figure \ref{fig:stability-slices}).
-% AD
-For the AD stimulus, we created overall eight $t$-contrasts (see Table
-\ref{tab:ao-contrasts}).
-% results
-All contrasts except contrast 7 (\texttt{se\_new}, \texttt{se\_old} >
-non-spatial categories) and contrast 8 (\texttt{se\_new} > non-spatial
-categories) yielded significant bilateral clusters in anterior regions of the
-group PPA overlap (see Figure \ref{fig:stability-slices}), suggesting
-a certain robustness of this result.
-
-% AD PPA contrasts
-% 1 PPA (l/r); RSC (l/r), LOC (l/r)
-% 2 PPA (l/r); RSC (l/r), LOC (l/r), r. sup.temp.C., r.fr.pole; putamen; etc
-% 3 PPA (l/r); RSC (l/r), LOC (l/r),l&r sup.temp.C., anterior cing., paracing.
-% 4 PPA (l/r); RSC (l/r), LOC (l/r)
-% 5 PPA (l/r); RSC (l/r), LOC (-/-)
-% 6 PPA (l/r); RSC (l/r), LOC (l/-), l&r sup.temp.C.; medial pref. c., precun
-% 7 PPA (-/-); RSC (l/r), LOC (l/-), l&r sup.temp.C.; left frontal pole
-% 8 PPA (-/-); RSC (-/-), LOC (-/-)
-
-% AD
-Reliably across the five contrasts of the AV stimulus, we find bilaterally
-significant clusters also in the ventral precuneal cortex and posterior
-cingulate gyrus (i.e. restrosplenial region; contrasts 1, 4, 5) and lateral
-occipital cortex (contrasts 1, 2, 4, 5).
-% AD; LOC: AV cluster are more medial, AD clusters are more lateral
-Across the five contrasts of the AD stimulus, we find bilaterally
-significant clusters in the ventral precuneus (all except contrasts 8), lateral
-occipital cortex (bilateral in contrasts 1 to 4; unilateral in contrasts 6 and
-7), and superior temporal cortices (bilateral in contrasts 3, 6, 7; unilateral
-right in contrast 2).
-
-% non-systematic
-Lastly, some contrasts of the AD stimulus yielded signficant clusters in regions
-that were not statistically signficant in three or more contrasts.
-%
-Contrast 2 yielded clusters in the anterior cingulate gyrus
-(bilateral), right frontal pole, right frontal medial cortex, and right
-putamen.
-%
-Contrast 3 shows clusters in the anterior cingulate gyrus (bilateral), left
-frontal pole, and left insular.
-%
-Contrast 7 shows clusters in the left frontal pole and left frontal operculum
-[border to triangularis], left insular.
-%
-Contrast 6 shows one additional cluster in the right medial frontal cortex.
-
-\begin{figure*}[h!]
-\centering
-    \includegraphics[width=\linewidth]{figures/stability-slices}
-    \caption{Overlap of significant clusters (Z>3.4; p<.05, cluster corrected)
-        The audio-description's contrasts 1-8 (blue; \ref{tab:ao-contrasts})
-        are overlaid over the audio-visual movie's contrasts 1-5 (red;
-        \ref{tab:av-contrasts}).
-        Cluster are overlaid on top of the MNI152 T1-weighted head template
-        (gray).
-        Black: outline of overlapping individual PPA ROIs.
-        Light gray: The audio-description's field-of-view (cf.
-        \citep{hanke2014audiomovie}).
-        The figure shows that some contrasts yielded significant clusters
-        also in the lateral temporal and prefrontal cortex.
-        }
-    \label{fig:stability-slices}
-\end{figure*}
-
-\subsection{control contrasts}
-
-% ---------- AV control contrasts ----------
-% 6 nothing
-% 7 nothing
-% 8 nothing
-% 9 nothing
-%10 se_new > se_old (nouns but in AV stimulus):
-% LOC (l/r) right PPA, bilateral sup. lat. occ. c., sup. parietal lobe (right)
-
-% ---------- AD control contrasts ----------
-% 9 PPA (-/-); RSC (-/r), LOC (-/-), left pars triangularis
-%10 PPA (-/-); RSC (-/-), LOC (-/-)
-%11 PPA (-/-); RSC (-/-), LOC (-/-),
-%12 PPA (-/-); RSC (-/-), LOC (-/-), right posterior hippocampus
-%13 PPA (-/-); RSC (-/-), LOC (-/-)
-
-\todo[inline]{there is no table/figure for negative control contrasts; we could
-add a reference to NeuroVault (here again) or point to the dataset}
-
-% intro
-Lastly, we implemented five contrasts for every stimulus for the purpose of
-negative control.
-% AV: no_cut > x
-In the analysis of the AV data, none of the contrasts that compared the ``no cut
-condition''  to a movie cut category (contrasts 6, 7, 8, 9) yielded significant
-clusters.
-% AV using nouns
-The contrast that used the narrator's nouns but in the AV stimulus
-(\texttt{se\_new} > \texttt{se\_old}) yielded a significant cluster in the right
-PPA and bilateral clusters in the superior lateral occipital cortices (the right
-hemispheric cluster extending into the superior parietal cortex).
-
-% AD stimulus
-In the analysis of the AD data, we created control contrasts based on events of
-the annotated movie cuts (cf. Table \ref{tab:ao-contrasts})
-% contrast 9
-Contrast 9 (vse\_new > pe\_old) revealed one significant cluster in the left
-inferior prefrontal cortex (pars triangularis) and right ventral
-precuneus/posterior cingulate gyrus.
-% contrast 12
-Contrast 12 (\texttt{vse\_new} > \texttt{vse\_old}, \texttt{vpe\_old}) revealed
-one cluster in the right posterior hippocampus.
-
-\subsection{Discussion: Robust results across contrasts}
-
-\todo[inline]{SE: Bei Ergebnissen \& Diskussionen zu Stability fehlt mir
-irgendwie immer der Kontext, wie sich die Kontraste denn unterschieden haben und
-welche davon z.B. im Ergebnis wo von den anderen abgewichen haben. Das würde ja
-wichtige Hinweise geben; COH: indeed very interesting but discussing that will
-let the paper get way out of hand}
-
-% why we did a couple of contrasts
-To test the robustness of our approach, we created several additional contrasts
-for each naturalistic stimulus by varying the contrasted categories (and thus
-the amount of available data), and how well the annotated events within
-categories on average matched a stimulus type that we assumed to correlate with
-spatial perception.
-
-\subsubsection{PPA}
-
-\begin{comment}
-    the mother of total confusion: Aminoff shifts the PPA along the
-    anterior-poster axis depending on publication;
-    in Aminoff (2007, 2013):
-    anterior PPA = spatial associations,
-    region anterior to (!) PPA = non-spatial associations;
-    in Aminoff (2015):
-    posterior PPA = spatial associations,
-    anterior PPA = non-spatial associations;
-    hence: complete bullshit;
-    ignore Aminoff (2015) due to various reasons
-\end{comment}
-
-% PPA AV
-Regarding contrasts of the AV stimulus (see Table \ref{tab:av-contrasts}), all
-five AV contrasts show significant bilateral clusters in the PPA but also
-extending into more posterior brain regions.
-% PPA AD
-Regarding contrasts of the AD stimulus (see Table \ref{tab:ao-contrasts}), six
-of overall eight contrasts show significant bilateral clusters in the anterior
-part of the group PPA overlap.
-% results indicate robustness
-Thus, the results of the additional contrasts indicate that our findings are
-robust and do not depend on the design of one specific contrasts.
-% but
-Nevertheless, results are sensitive to the contrasted categories and the amount
-of available data.
-% example
-For example, contrast 8 of the AD stimulus (\texttt{se\_new} > \texttt{se\_old})
-that used the most heterogeneous categories comprising the least amount of
-events yielded neither a significant cluster in the right-hemispheric nor
-left-hemispheric PPA.
-% concluding statement
-Hence, investigators that use model-driven analyses have to consider how many
-events a naturalistic stimulus may provide and how homogeneous the events to be
-averaged might be.
-
-% anterior vs posterior pattern
-In contrasts 1 to 6 of the AD stimulus, we find consistently significant
-clusters spatially constrained to the anterior part of the PPA group overlap.
 % question
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%
+%%%
+
+\subsubsection{not many random cluster + naturalistic stimuli are cool}
+
+% ``confounding'' clusters
+Despite performing a whole brain analysis, we do not find many [random] clusters
+in single contrasts or even systematically across contrasts that hamper the
+interpretation of results.\todo{ouff\dots}
+% AV: null results regarding attention and eye movements
+For example in the AV results, we do not find significant clusters that could be
+attributed to cognitive processes like attention or eye movements.
+% AD: auditory cortices
+Nevertheless, contrasts of the AD stimulus that compare (among others) verbal
+hints of the change of a setting (\texttt{se\_new} or \texttt{se\_old}) to all
+non-spatial categories (cf. contrasts 2, 3, 6, 7) show significant clusters in
+(primary and secondary) auditory cortices.
+% averaging vs. nuisance regressors
+This suggests that variance correlating with lower level auditory processes was
+not averaged out across trials and nuisance regressors did not capture enough
+variance.\todo{ouf\dots}
+% possible reason
+Significant clusters in auditory cortices could be correlating with a possible
+change of the soundscape when the narrator of the audio-description (or a cut in
+the movie) switches to a another setting.
+% concluding statement
+Thus, investigators that use model-driven methods to investigate brain functions
+using naturalistic stimuli should (extensively) annotate the stimulus material
+and test for correlations among variables.
+
+\subsubsection{naturalistic stimuli + data re-use, fuck yeah}
+
+\ldots
+
+% natural stimulation
+Natural stimuli like movies \citep{eickhoff2020towards,
+hasson2008neurocinematics, sonkusare2019naturalistic} or narratives
+\citep{hamilton2018revolution, honey2012not, lerner2011topographic,
+silbert2014coupled, wilson2008beyond} offer an easy to implement, (continuous,)
+complex, immersive, task-free paradigm that more closely resembles our natural
+dynamic environment than traditional experimental designs.
+
+\begin{itemize}
+\item We reuse public data for independent research question
+\item GLM based on annotations to operationalize ``spatial perception''
+\item Our results add evidence that model-driven analyses based in annotations
+can be run on data from naturalistic stimuli to ``localize'' brain activity
+correlating with specific perceptual processes.
+\item ``localization performance'' relies on how well the model captures
+different aspects of the stimuli's feature space.
+\item PPA is functionally heterogeneous region
+\item a complex but naturally engaging auditory stimulus like an
+audiobook might in principle be used as a non-visual localizer for a variety of
+brain functions in subjects who are not willing or able to follow task
+instructions during brain scanning [would state that explicitly in the summary
+at the end].
+\end{itemize}
+
+% \citep{hanke2014audiomovie}: the AD stimulus leaves a much larger margin for
+% inter-individual differences in imagining scenery. The AD stimulus limits the
+% effect of an attentional focus on the selection of a subset of simultaneously
+% occurring auditory events, in contrast to the selection of different parts of
+% the visual field.
+
+\subsection*{Code availability}
+% wo kommt dieser Abschnitt hin?  how to write Code availability statement
+% https://www.springernature.com/gp/authors/research-data-policy/data-availability-statements/12330880
+\todo[inline]{provide supporting source code, and explaining how and where
+others may access all data underlying the analysis} \emph{for all studies using
+    custom code in the generation or processing of datasets, a statement must be
+    included here, indicating whether and how the code can be accessed,
+including any restrictions to access; include information on the versions of any
+software used, if relevant, and any specific variables or parameters used to
+generate, test, or process the current dataset. }
+
+\section*{Acknowledgements}
+% Text acknowledging non-author contributors.
+Acknowledgements should be brief, and should not include thanks to anonymous referees and editors, or effusive comments.
+Grant or contribution numbers may be acknowledged.
+% Author contributions Please describe briefly the contributions of each author to this work on a separate line.
+\emph{COH did this and that.
+MH did this and that.
+We are grateful to \href{www.florianschurz.de}{Florian Schurz} who initiated doing the annotation of the descriptive nouns, and performed the preliminary annotation of nouns.}
+
+\section*{Competing financial interests}
+\emph{A competing financial interests statement is required for all accepted
+papers published in \emph{Scientific Data}. If none exist simply write,
+``The author(s) declare no competing financial interests''.}
+
+\section*{Figures Legends}
+\emph{Figure should be referred to using a consistent numbering scheme through
+the entire Data Descriptor. For initial submissions, authors may choose
+to supply this document as a single PDF with embedded figures, but
+separate figure image files must be provided for revisions and accepted
+manuscripts. In most cases, a Data Descriptor should not contain more
+than three figures, but more may be allowed when needed. We discourage
+the inclusion of figures in the Supplementary Information \textendash{}
+all key figures should be included here in the main Figure section.}
+
+\emph{Figure legends begin with a brief title sentence for the whole figure
+and continue with a short description of what is shown in each panel,
+as well as explaining any symbols used. Legend must total no more
+than 350 words, and may contain literature references.}
+
+\section*{Tables}
+
+\emph{Tables supporting the Data Descriptor. These can provide summary information
+(sample numbers, demographics, etc.), but they should generally not
+be used to present primary data (i.e. measurements). Tables containing
+primary data should be submitted to an appropriate data repository.}
+
+\emph{Tables may be provided within the \LaTeX{} document or as separate
+files (tab-delimited text or Excel files). Legends, where needed,
+should be included here. Generally, a Data Descriptor should have
+fewer than ten Tables, but more may be allowed when needed. Tables
+may be of any size, but only Tables which fit onto a single printed
+page will be included in the PDF version of the article (up to a maximum
+of three).}
+
+{\small\bibliographystyle{unsrtnat}
+\bibliography{references}}
+
+%\begin{thebibliography}{1}
+%\expandafter\ifx\csname url\endcsname\relax
+%  \def\url#1{\texttt{#1}}\fi
+%\expandafter\ifx\csname urlprefix\endcsname\relax\def\urlprefix{URL }\fi
+%\providecommand{\bibinfo}[2]{#2}
+%\providecommand{\eprint}[2][]{\url{#2}}
+%
+%\bibitem{cite1}
+%\bibinfo{author}{Califano, A.}, \bibinfo{author}{Butte, A.~J.},
+%  \bibinfo{author}{Friend, S.}, \bibinfo{author}{Ideker, T.} \&
+%  \bibinfo{author}{Schadt, E.}
+%\newblock \bibinfo{title}{{Leveraging models of cell regulation and GWAS data
+%  in integrative network-based association studies}}.
+%\newblock \emph{\bibinfo{journal}{Nature Genetics}}
+%  \textbf{\bibinfo{volume}{44}}, \bibinfo{pages}{841--847}
+%  (\bibinfo{year}{2012}).
+%
+%\bibitem{cite2}
+%\bibinfo{author}{Wang, R.} \emph{et~al.}
+%\newblock \bibinfo{title}{{PRIDE Inspector: a tool to visualize and validate MS
+%  proteomics data.}}
+%\newblock \emph{\bibinfo{journal}{Nature Biotechnology}}
+%  \textbf{\bibinfo{volume}{30}}, \bibinfo{pages}{135--137}
+%  (\bibinfo{year}{2012}).
+%\end{thebibliography}
+
+\section{Data Citations}
+
+Bibliographic information for the data records described in the manuscript.
+
+1. Lastname1, Initial1., Lastname2, Initial2., ...\& LastnameN, InitialN. \emph{Repository name} Dataset accession number or DOI (YYYY).
+
+\appendix
+
+\section{Supplementary Materials}
+
+\subsection{Robustness of group results across contrasts}
+
+% unthresholded $z$-maps of all contrasts on a group level:
+% \href{https://neurovault.org/collections/KADGMGVZ/}{NeuroVault}.
+
+% AV PPA contrasts
+% 1 PPA (l/r); RSC (l/r), LOC (l/r), VisC (l/r),
+% intracalcarine, cuneal, ling.c
+% 2 PPA (l/r); RSC (-/-), LOC (l/r), VisC (-/-)
+% 3 PPA (l/r); RSC (-/-), LOC (-/-), VisC (-/r), occ. fusisf. g.
+% 4 PPA (l/r); RSC (l/r), LOC (l/r), VisC (-/-), lingual g., occ. fusif. g.
+% 5 PPA (l/r); RSC (l/r), LOC (l/r), VisC (-/-), occ. fusif. g.
+
+% AV
+In order to test the robustness of our findings, we created four additional
+$t$-contrasts for the AV stimulus (see Table \ref{tab:av-contrasts}) to be
+investigated on a group level.
+% results: PPA; biggest overlap in posterior part of PPA group overlap  =
+%temporal occipital fusiform cortex
+All of the overall five AV contrasts yielded significant bilateral clusters that
+overlap with the PPA group overlap (see Figure \ref{fig:stability-slices}).
+% AD
+For the AD stimulus, we created overall eight $t$-contrasts (see Table
+\ref{tab:ao-contrasts}).
+% results
+All contrasts except contrast 7 (\texttt{se\_new}, \texttt{se\_old} >
+non-spatial categories) and contrast 8 (\texttt{se\_new} > non-spatial
+categories) yielded significant bilateral clusters in anterior regions of the
+group PPA overlap (see Figure \ref{fig:stability-slices}), suggesting
+a certain robustness of this result.
+
+% AD PPA contrasts
+% 1 PPA (l/r); RSC (l/r), LOC (l/r)
+% 2 PPA (l/r); RSC (l/r), LOC (l/r), r. sup.temp.C., r.fr.pole; putamen; etc
+% 3 PPA (l/r); RSC (l/r), LOC (l/r),l&r sup.temp.C., anterior cing., paracing.
+% 4 PPA (l/r); RSC (l/r), LOC (l/r)
+% 5 PPA (l/r); RSC (l/r), LOC (-/-)
+% 6 PPA (l/r); RSC (l/r), LOC (l/-), l&r sup.temp.C.; medial pref. c., precun
+% 7 PPA (-/-); RSC (l/r), LOC (l/-), l&r sup.temp.C.; left frontal pole
+% 8 PPA (-/-); RSC (-/-), LOC (-/-)
+
+% AD
+Reliably across the five contrasts of the AV stimulus, we find bilaterally
+significant clusters also in the ventral precuneal cortex and posterior
+cingulate gyrus (i.e. restrosplenial region; contrasts 1, 4, 5) and lateral
+occipital cortex (contrasts 1, 2, 4, 5).
+% AD; LOC: AV cluster are more medial, AD clusters are more lateral
+Across the five contrasts of the AD stimulus, we find bilaterally
+significant clusters in the ventral precuneus (all except contrasts 8), lateral
+occipital cortex (bilateral in contrasts 1 to 4; unilateral in contrasts 6 and
+7), and superior temporal cortices (bilateral in contrasts 3, 6, 7; unilateral
+right in contrast 2).
+
+% non-systematic
+Lastly, some contrasts of the AD stimulus yielded signficant clusters in regions
+that were not statistically signficant in three or more contrasts.
+%
+Contrast 2 yielded clusters in the anterior cingulate gyrus
+(bilateral), right frontal pole, right frontal medial cortex, and right
+putamen.
+%
+Contrast 3 shows clusters in the anterior cingulate gyrus (bilateral), left
+frontal pole, and left insular.
+%
+Contrast 7 shows clusters in the left frontal pole and left frontal operculum
+[border to triangularis], left insular.
+%
+Contrast 6 shows one additional cluster in the right medial frontal cortex.
+
+\begin{figure*}[h!]
+\centering
+    \includegraphics[width=\linewidth]{figures/stability-slices}
+    \caption{Overlap of significant clusters (Z>3.4; p<.05, cluster corrected)
+        The audio-description's contrasts 1-8 (blue; \ref{tab:ao-contrasts})
+        are overlaid over the audio-visual movie's contrasts 1-5 (red;
+        \ref{tab:av-contrasts}).
+        Cluster are overlaid on top of the MNI152 T1-weighted head template
+        (gray).
+        Black: outline of overlapping individual PPA ROIs.
+        Light gray: The audio-description's field-of-view (cf.
+        \citep{hanke2014audiomovie}).
+        The figure shows that some contrasts yielded significant clusters
+        also in the lateral temporal and prefrontal cortex.
+        }
+    \label{fig:stability-slices}
+\end{figure*}
+
+\subsection{control contrasts}
+
+% ---------- AV control contrasts ----------
+% 6 nothing
+% 7 nothing
+% 8 nothing
+% 9 nothing
+%10 se_new > se_old (nouns but in AV stimulus):
+% LOC (l/r) right PPA, bilateral sup. lat. occ. c., sup. parietal lobe (right)
+
+% ---------- AD control contrasts ----------
+% 9 PPA (-/-); RSC (-/r), LOC (-/-), left pars triangularis
+%10 PPA (-/-); RSC (-/-), LOC (-/-)
+%11 PPA (-/-); RSC (-/-), LOC (-/-),
+%12 PPA (-/-); RSC (-/-), LOC (-/-), right posterior hippocampus
+%13 PPA (-/-); RSC (-/-), LOC (-/-)
+
+\todo[inline]{there is no table/figure for negative control contrasts; we could
+add a reference to NeuroVault (here again) or point to the dataset}
+
+% intro
+Lastly, we implemented five contrasts for every stimulus for the purpose of
+negative control.
+% AV: no_cut > x
+In the analysis of the AV data, none of the contrasts that compared the ``no cut
+condition''  to a movie cut category (contrasts 6, 7, 8, 9) yielded significant
+clusters.
+% AV using nouns
+The contrast that used the narrator's nouns but in the AV stimulus
+(\texttt{se\_new} > \texttt{se\_old}) yielded a significant cluster in the right
+PPA and bilateral clusters in the superior lateral occipital cortices (the right
+hemispheric cluster extending into the superior parietal cortex).
+
+% AD stimulus
+In the analysis of the AD data, we created control contrasts based on events of
+the annotated movie cuts (cf. Table \ref{tab:ao-contrasts})
+% contrast 9
+Contrast 9 (vse\_new > pe\_old) revealed one significant cluster in the left
+inferior prefrontal cortex (pars triangularis) and right ventral
+precuneus/posterior cingulate gyrus.
+% contrast 12
+Contrast 12 (\texttt{vse\_new} > \texttt{vse\_old}, \texttt{vpe\_old}) revealed
+one cluster in the right posterior hippocampus.
+
+\subsection{Discussion: Robust results across contrasts}
+
+\todo[inline]{SE: Bei Ergebnissen \& Diskussionen zu Stability fehlt mir
+irgendwie immer der Kontext, wie sich die Kontraste denn unterschieden haben und
+welche davon z.B. im Ergebnis wo von den anderen abgewichen haben. Das würde ja
+wichtige Hinweise geben; COH: indeed very interesting but discussing that will
+let the paper get way out of hand}
+
+% why we did a couple of contrasts
+To test the robustness of our approach, we created several additional contrasts
+for each naturalistic stimulus by varying the contrasted categories (and thus
+the amount of available data), and how well the annotated events within
+categories on average matched a stimulus type that we assumed to correlate with
+spatial perception.
+
+\subsubsection{PPA}
+
+\begin{comment}
+    the mother of total confusion: Aminoff shifts the PPA along the
+    anterior-poster axis depending on publication;
+    in Aminoff (2007, 2013):
+    anterior PPA = spatial associations,
+    region anterior to (!) PPA = non-spatial associations;
+    in Aminoff (2015):
+    posterior PPA = spatial associations,
+    anterior PPA = non-spatial associations;
+    hence: complete bullshit;
+    ignore Aminoff (2015) due to various reasons
+\end{comment}
+
+% PPA AV
+Regarding contrasts of the AV stimulus (see Table \ref{tab:av-contrasts}), all
+five AV contrasts show significant bilateral clusters in the PPA but also
+extending into more posterior brain regions.
+% PPA AD
+Regarding contrasts of the AD stimulus (see Table \ref{tab:ao-contrasts}), six
+of overall eight contrasts show significant bilateral clusters in the anterior
+part of the group PPA overlap.
+% results indicate robustness
+Thus, the results of the additional contrasts indicate that our findings are
+robust and do not depend on the design of one specific contrasts.
+% but
+Nevertheless, results are sensitive to the contrasted categories and the amount
+of available data.
+% example
+For example, contrast 8 of the AD stimulus (\texttt{se\_new} > \texttt{se\_old})
+that used the most heterogeneous categories comprising the least amount of
+events yielded neither a significant cluster in the right-hemispheric nor
+left-hemispheric PPA.
+% concluding statement
+Hence, investigators that use model-driven analyses have to consider how many
+events a naturalistic stimulus may provide and how homogeneous the events to be
+averaged might be.
+
+% anterior vs posterior pattern
+In contrasts 1 to 6 of the AD stimulus, we find consistently significant
+clusters spatially constrained to the anterior part of the PPA group overlap.
+
 \subsubsection{RSC \& LOC}

### 2021-02-04 paper/main.tex
restructure discussion & suppl. material

@@
 \begin{itemize}
+    \item in case the additional contrast stay in supplemental material, just
+        speak of contrast not ``primary contrast''
     \item adopt some phrasing from the Speech-Anno-Paper
@@
 \texttt{fahead}, \texttt{object}, \texttt{sex\_f}, \texttt{sex\_m}) except
-\texttt{furniture} to get a sufficient amount of events per stimulus
-segment.
+\texttt{furniture} to get a sufficient amount of events per stimulus segment.
 % furniture
@@
 % AV: narrator
-One contrast (\texttt{vs\_new} > \texttt{vpe\_old}) was created by
-contrasting nouns spoken by the narrator.
+One contrast (\texttt{vs\_new} > \texttt{vpe\_old}) was created by contrasting
+nouns spoken by the narrator.
 % AD stimulus
@@
 setting.
+%
+\todo[inline]{it's probally not about the soundscape anymore (to speculative)
+but about the somewhat correlation of nouns and cuts}
 
@@
 On a group average level, we compare results gained from whole-brain GLM
-analyses of the movie and the audio-description (Z>3.4; p<.05, cluster
-corrected) to results gained from a traditional visual localizer
-\citep{sengupta2016extension}.
+analyses of the movie and the audio-description to results gained from a
+traditional visual localizer \citep{sengupta2016extension}.
 % individual level
-On the level single subjects (Z>3.4; p<.05, cluster corrected), we also assess
-the performance of the exclusively auditory naturalistic stimulus as a
-substitute for a visual paradigm to localize the PPA.
+On the level single subjects, we also assess the performance of the exclusively
+auditory naturalistic stimulus as a substitute for a visual paradigm to localize
+the PPA.
 % NeuroVault
@@
 The movie's primary $t$-contrast that compared cuts to a setting that was not
-depicted before to cuts to a recurring setting (\texttt{vse\_new > vpe\_old})
+depicted before to cuts withn a recurring setting (\texttt{vse\_new > vpe\_old})
 yielded three significant clusters (see Table \ref{tab:res-av-group1}, Figure
@@
 Two homologous clusters are located in the anterior part of the PPA group
-overlap..
+overlap.
 % in detail
@@
 parahippocampal cortex, the occipital and temporal fusiform gyrus and lingual
-gyrus.\todo{Havard-Oxford atlas gives 3 different most prob. locations depen.
-on voxel}
+gyrus.\todo{Havard-Oxford atlas: 3 different most prob. locations depen.  on
+voxel}
 % precuneus
@@
 % AD is the real shit
-Furtherm, we hypothesized that an exclusively auditory
-stimulus could localize the PPA in individual subjects and thus
-possibly substitute a classic visual localizer experiment.
+Further, we hypothesized that an exclusively auditory stimulus could localize
+the PPA in individual subjects and thus possibly substitute a classic visual
+localizer experiment.
 
@@
 % Sengupta et al., 2016
-The visual localizer experiment \citep{sengupta2016extension} yielded bilateral
-[parahippocampal] clusters in 12 of 14 subjects and an unilateral right clusters
+The visual localizer \citep{sengupta2016extension} yielded bilateral
+parahippocampal clusters in 12 of 14 subjects and an unilateral right clusters
 in two subjects (sub-04, sub-20).
 % Sengupta: 1 of 3
-Individual PPAs were assessed by titrating [?] the $t$-threshold in the range
-of [2, 3] in the thresholded $t$-maps (Z>1.64, p<.05 cluster corrected) of three
-different $t$-contrasts (\textit{strict}, \textit{relaxed}, and \textit{simple}
-stimulus set cf.  \citep{sengupta2016extension}) until we found an isolated
-cluster that matched the expected anatomical location based on literature
-\citep{epstein1998ppa}.
-
+Individual PPAs were assessed by visually inspecting unthresholded $t$-maps
+(Z>1.64, p<.05 cluster corrected)  of three different $t$-contrasts
+(\textit{strict}, \textit{relaxed}, and \textit{simple} stimulus set cf.
+\citep{sengupta2016extension}), and titrating [?] the $t$-threshold in the range
+of [2, 3] in until we found an isolated cluster that matched the expected
+anatomical location based on literature \citep{epstein1998ppa}.
 % one contrast to localize them all; "...and Z>3.4 for all"
-Contrary to \citep{sengupta2016extension}, we used the same contrast of each
-naturalistic stimulus and the same threshold for all subjects (Z>2.3, p<.05
+Contrary to \citep{sengupta2016extension}, we here used the same contrast of
+each naturalistic stimulus and the same threshold for all subjects (Z>2.3, p<.05
 cluster-corrected for the analysis in subject-space; Z>3.4, p<.05 for the
@@
 and AD $t$-contrast, and the outline of overlapped, individual PPAs
-\citep{sengupta2016extension}.
-% MNI space
-The $z$-maps and PPA outline are overlayed on the co-registered MNI152 template.
+\citep{sengupta2016extension} co-registed to the MNI152 template.
 % one slice to show them all
@@
 localizer and the primary AD contrast, we created a Bland-Altman-Plot for every
-subject (see ).
+subject (see \ref{fig:bland-altman}).
 % what it depicts
-Each subplot of Figure \ref{fig:bland-altman} visualizes the mean value and
-difference (localizer minus AD) of two spatially corresponding voxels in the
-unthresholded $z$-maps.
+Each subplot visualizes the mean value and difference (localizer minus AD) of
+two spatially corresponding voxels in the unthresholded $z$-maps.
 % top KDE plot
@@
 % previous studies
-Previous studies reported bilaterally increased hemodynamic activity in the PPA
-when participants were watching static pictures of landscape compared to
-pictures of faces or objects (e.g. \citep{epstein1998ppa,
-epstein1999parahippocampal}) whereas one study using spoken sentences reported
-mixed results \citep{aziz2008modulation}.
+Previous studies reported increased hemodynamic activity in the PPA when
+participants were watching static pictures of landscape compared to pictures of
+faces or objects (e.g. \citep{epstein1998ppa, epstein1999parahippocampal})
+whereas one study using spoken sentences reported mixed results
+\citep{aziz2008modulation}.
 % current study: similar
-In line with previous studies, we use here also operationalize spatial
-perception via general linear model (GLM) $t$-contrasts in two naturalistic
-stimuli.
+In line with previous studies, we also operationalized spatial perception via
+general linear model (GLM) $t$-contrasts.
 % current study: dissimilar
@@
 designed sets of stimuli but based on annotated stimulus features incidentially
-occurring in an audio-visual movie and its audio-description.
+occurring in two naturalistic stimuli.
 % group AV
@@
 Results for the audio-description reveal significant activation in the PPA but
-restricted its anterior part.
+restricted to its anterior part.
 % individual level
@@
 
-\subsection{PPA; AV \& AD; group \& individuals}
+\subsection{PPA group}
 
@@
 
-\subsubsection{AV: group}
-
 % intro
@@
 (color, faces, language and human bodies), we categorized each frame after a cut
-independent of its content. \todo{PPA in \citep{hasson2004intersubject} but do
-reverse ISC; Bartels' clusters are actually pretty big too}
+independent of its content. \todo{Bartels' clusters are actually pretty big too}
 % hypo
@@
 the attentional focus of study participants.
-
+%
 \todo[inline]{I am pretty surprised the clusters are not all over the brain.  I
 do not know where/how do phrase it but should be mentioned imo}
-
-% shortcomings
-Since the capability to isolate clusters or networks correlating with specific
-perceptual (or cognitive) processes is influenced by the amount of annotated
-stimulus features further studies focusing on visual perception should annotate
-and model visual features of naturalistic stimuli more rigorously.
 % solution
-Future studies that aim to use a movie to localize different visual areas should
+Future studies that aim to use a movie to localize visual areas should
 extensively annotate the content of frames (e.g. using the open-source solution
@@
 
-\todo[inline]{nice that the following is mentioned but what to do with it?
-Movies are nice but have idiosyncrasies; so, maybe you should be aware of these
-idiosyncrasies (and control for it) in case you wanna use movies for research?}
 % exploited cinematographic tendencies
@@
 \ref{rationale}).
-%
+% establishing shots vs. e.g. over-the-shoulder shots
 Film directors tend to establish the geometry of locations earlier in the movie
-and to later focus more on persons and objects relevant to the evolved plot
-later  \citep{brown2012cinematography, mercado2011filmmakers}.
+and tend to later focus more on persons and objects relevant to the evolved
+\citep{brown2012cinematography, mercado2011filmmakers}.
+%
+\todo[inline]{nice that exploited confound structure is mentioned but what to do
+with it? hey, look, it works? movies are nice but have idiosyncrasies? so, maybe
+you should be aware of these idiosyncrasies (and control for it) in case you
+wanna use movies for research?}
 
 % summary: nevertheless
-\todo[inline]{Overall summary for AV: so, yes, what is the main message of this
-``cross-modal-control-movie-thing''?? cf. intro: ``works'' but clusters more
-widespread}
-
-\subsubsection{AD: group}
+\todo[inline]{Overall summary for AV \& concluding statement!?!}
+
+\todo[inline]{so, yes, what is the main message of this
+``cross-modal-control-movie-thing''??}
 
@@
 (describing unknown and famous places and faces), and compared activity levels
-that were averaged across voxels of ROIs (PPA and fusiform face
+that were averaged across voxels of ROIs (PPA and fusiform face area, FFA
 \citep{kanwisher1997ffa}) defined by a localizer experiment.
@@
 % we: model & whole brain
-Here we modeled events from on- to offset of single words and performed an
+Here we modeled events from on- to offset of single words and performed a
 whole-brain analysis.
@@
 
-\subsubsection{AD: shortcoming}
-
-\todo[inline]{at the moment positioned here; makes sense at a couple of other
-positions; not sure yet}
+% AD shortcomings
 
@@
 
-\subsubsection{AD: individuals}
+\subsection{PPA individuals (AD)}
 
@@
 Similarly to the group average results, results on an individual level also
-reveal that clusters are spatially restricted to the anterior part of individual
-PPAs.
+revealed that clusters are spatially restricted to the anterior part of
+individual PPAs.
 % conclusion
-Thus, the increased hemodynamic activity in the anterior part of the PPA
-revealed on the group level is not just a by-product of the averaging process
-[as it can reliably be found in individual study participants.]
-% conclusion
-Lastly, our exploratory analysis suggests that a naturalistic auditory stimulus
-can [in principle] be applied to localize (the anterior part) of an higher-level
-visual area in the majority of subjects.
-% one threshold (and contrast) to rule them all
-Further studies that aim for individual diagnostics / ROI localization should
-nevertheless test more than one contrast to gain the ``best'' individual
-ROIs.\todo{..ouff}
-
-\todo[inline]{probably not important but: what do results suggest
-regarding individual differences?  Differences in alertness, attention to
-spatial information, predisposition?  ``capability'' to process auditory spatial
-information?}
-
+Thus, the cluster location and size is not just a by-product of the averaging
+process but the same pattern can can reliably be found in individual study
+participants.
 % question
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%
-%%%
-
-\subsubsection{not many random cluster + naturalistic stimuli are cool}
-
-% ``confounding'' clusters
+% conclusion
+Lastly, our exploratory analysis suggests that a naturalistic auditory stimulus
+can [in principle] be applied to localize (the anterior part) of an higher-level
+visual area in the majority of subjects.
+% one threshold (and contrast) to rule them all
+Further studies that aim for individual diagnostics / ROI localization should
+nevertheless test more than one contrast to gain the ``best'' individual
+ROIs.\todo{..ouff}
+
+\todo[inline]{probably not important but: what do results suggest
+regarding individual differences?  Differences in alertness, attention to
+spatial information, predisposition?  ``capability'' to process auditory spatial
+information?}
+
+\subsection{RSC \& LOC = non random clusters => naturalistic stimuli are
+cool}
+
+% no random clusers
 Despite performing a whole brain analysis, we do not find many [random] clusters
 in single contrasts or even systematically across contrasts that hamper the
-interpretation of results.\todo{ouff\dots}
+interpretation of results.
 % AV: null results regarding attention and eye movements
@@
 attributed to cognitive processes like attention or eye movements.
-% AD: auditory cortices
-Nevertheless, contrasts of the AD stimulus that compare (among others) verbal
-hints of the change of a setting (\texttt{se\_new} or \texttt{se\_old}) to all
-non-spatial categories (cf. contrasts 2, 3, 6, 7) show significant clusters in
-(primary and secondary) auditory cortices.
-% averaging vs. nuisance regressors
-This suggests that variance correlating with lower level auditory processes was
-not averaged out across trials and nuisance regressors did not capture enough
-variance.\todo{ouf\dots}
-% possible reason
-Significant clusters in auditory cortices could be correlating with a possible
-change of the soundscape when the narrator of the audio-description (or a cut in
-the movie) switches to a another setting.
-% concluding statement
-Thus, investigators that use model-driven methods to investigate brain functions
-using naturalistic stimuli should (extensively) annotate the stimulus material
-and test for correlations among variables.
-
-\subsubsection{naturalistic stimuli + data re-use, fuck yeah}
-
-\ldots
+
+% intro
+Apart from the PPA, we find significantly increased activity in the dorsal
+precuneus and posterior cingulate region (e.g. retrosplenial cortex; RSC) and
+lateral occipital cortex (LOC) across contrasts of both naturalistic stimuli.
+% RSC intro
+Like the PPA, the RSC and LOC are known to be scene-selective regions (see
+\citep{chrastil2018heterogeneity, bettencourt2013role} for reviews).
+% conclusion
+\todo[inline]{concluding statement}
+
+\section{conlusion}
+
+\todo[inline]{scientific data has no conclusion -> last paragraph}
 
@@
 
-% anterior vs posterior pattern
-In contrasts 1 to 6 of the AD stimulus, we find consistently significant
-clusters spatially constrained to the anterior part of the PPA group overlap.
-
 \subsubsection{RSC \& LOC}
 
-\todo[inline]{this part is now super short}
+\todo[inline]{same part as in the main text but with number of contrasts}
 
@@
 
+\subsubsection{confounding clusters}
+% ``confounding'' clusters
+Despite performing a whole brain analysis, we do not find many [random] clusters
+in single contrasts or even systematically across contrasts that hamper the
+interpretation of results.\todo{ouff\dots}
+% AV: null results regarding attention and eye movements
+For example in the AV results, we do not find significant clusters that could be
+attributed to cognitive processes like attention or eye movements.
+% AD: auditory cortices
+Nevertheless, contrasts of the AD stimulus that compare (among others) verbal
+hints of the change of a setting (\texttt{se\_new} or \texttt{se\_old}) to all
+non-spatial categories (cf. contrasts 2, 3, 6, 7) show significant clusters in
+(primary and secondary) auditory cortices.
+% averaging vs. nuisance regressors
+This suggests that variance correlating with lower level auditory processes was
+not averaged out across trials and nuisance regressors did not capture enough
+variance.\todo{ouf\dots}
+% possible reason
+Significant clusters in auditory cortices could be correlating with a possible
+change of the soundscape when the narrator of the audio-description (or a cut in
+the movie) switches to a another setting.
+% concluding statement
+Thus, investigators that use model-driven methods to investigate brain functions
+using naturalistic stimuli should (extensively) annotate the stimulus material
+and test for correlations among variables.
+
 \subsection{negative controls and cross-modal controls}

### 2021-02-07 paper/main.tex
adjusting ending of discussion

@@
 % current study: similar
-In line with previous studies, we also operationalized spatial perception via
-general linear model (GLM) $t$-contrasts.
+In line with previous studies, we operationalized spatial perception via general
+linear model (GLM) $t$-contrasts.
 % current study: dissimilar
@@
 % group AD
-Results for the audio-description reveal significant activation in the PPA but
-restricted to its anterior part.
+Results for the audio-description also reveal significant activation in the PPA
+but restricted to its anterior part.
 % individual level
@@
 unilateral clusters in one subjects.
-% meaning 1
+% meaning: generalization to naturalistic stimuli
 Results suggest that increased activation in the PPA during the perception of
@@
 a movie and an exclusively auditory stimulus.
-% meaning 2
+% meaning: aPPA vs. pPPA
 Our results provide further evidence that the PPA can be divided into functional
-subregions. An auditory narrative might substitute a visual paradigm to localize
+subregions.
+% narrative as substitute
+An auditory narrative might substitute a visual paradigm to localize
 the PPAs anterior part in visually impaired subjects.
@@
 %
-An early study \citep{bartels2004mapping} that manually annotated the content
-(color, faces, language, and human bodies) of movie frames found that
+An early study \citep{bartels2004mapping} that manually annotated the content of
+movie frames (color, faces, language, and human bodies) found that
 specialization of functional areas is preserved during movie watching.
 %
-Contrary to \citep{bartels2004mapping} who annotated the movie frames' content
-(color, faces, language and human bodies), we categorized each frame after a cut
-independent of its content. \todo{Bartels' clusters are actually pretty big too}
-% hypo
-Despite this ad hoc approach, we hypothesized that [confounding variables
-could/would average out and] our whole-brain analyses would lead to significant
-clusters in the PPA.
-% results
-Group results of the AV stimulus' primary contrast yielded a cluster that span
-the group overlap of individual PPA ROIs from anterior to posterior.
-% difference in location/size to AD and VIS
-The cluster also extends into medial regions (dorsal precuneus and dorsal
-posterior cingulate cortices), and into more posterior regions (occipital
-fusiform gyrus and intracalcarine cortex) bilaterally.
-% confound of higher perception
-The larger extension into more posterior, primary visual areas can be attributed
-to the averaging process that did not control for confounding visual features or
-the attentional focus of study participants.
-%
-\todo[inline]{I am pretty surprised the clusters are not all over the brain.  I
-do not know where/how do phrase it but should be mentioned imo}
-% solution
-Future studies that aim to use a movie to localize visual areas should
-extensively annotate the content of frames (e.g. using the open-source solution
-``Pliers'' for feature extraction from a visual naturalistic stimulus;
-\citep{mcnamara2017developing}) and record the subject's visual attention via
-eye-tracking.
-
+Contrary to \citep{bartels2004mapping} who annotated the content of frames, we
+categorized each frame after a cut independent of its specific content.
+\todo{Bartels' clusters are actually pretty big too}
 % exploited cinematographic tendencies
@@
 \citep{brown2012cinematography, mercado2011filmmakers}.
-%
-\todo[inline]{nice that exploited confound structure is mentioned but what to do
-with it? hey, look, it works? movies are nice but have idiosyncrasies? so, maybe
-you should be aware of these idiosyncrasies (and control for it) in case you
-wanna use movies for research?}
-
-% summary: nevertheless
-\todo[inline]{Overall summary for AV \& concluding statement!?!}
-
-\todo[inline]{so, yes, what is the main message of this
+% hypo
+Despite our ad hoc approach, we hypothesized that [confounding variables
+could/would average out and] our whole-brain analyses would lead to significant
+clusters in the PPA.
+% results
+Group results of the AV stimulus' primary contrast yielded a cluster that span
+the group overlap of individual PPA ROIs from anterior to posterior.
+% confound of higher perception
+The cluster's extension into more posterior, early visual areas can be
+attributed to the averaging process that did not control for confounding visual
+features [or the attentional focus of study participants].
+%
+\todo[inline]{I am pretty surprised the clusters are not all over the brain. I
+do not know where/how do phrase it but should be mentioned imo}
+% solution
+Thus to control confounding variables, future studies that aim to use a movie to
+localize visual areas should extensively annotate the content of frames (e.g.
+using the open-source solution ``Pliers'' for feature extraction from a visual
+naturalistic stimulus; \citep{mcnamara2017developing})[, and record the
+subject's visual attention via eye-tracking].
+%
+
+\todo[inline]{concluding statements regarding exploited cinematographic
+confound? e.g.: movies are nice but have idiosyncrasies? so, maybe you should be
+aware of these idiosyncrasies (and control for it) in case you wanna use movies
+for research?}
+
+\todo[inline]{overall main message / concluding statement of this
 ``cross-modal-control-movie-thing''??}
@@
 % hypothesis
-Encouraged by \citep{aziz2008modulation}, we also hypothesized that spatial
+Encouraged by \citep{aziz2008modulation}, we hypothesized that spatial
 information embedded in an exclusively auditory stimulus would correlate with
@@
 Study results revealed significantly decreased activity in only the left PPA
-compared to activity in the FFA, and only for sentences describing famous places
-compared to famous faces.
+compared to activity in the FFA for sentences describing famous places compared
+to famous faces.
 % we: model & whole brain
@@
 % optimal stimulus type in vision
-In the visual domain, landscapes and not pictures of landmarks or buildings are
-considered to be the ``optimal'' stimulus type
+In the visual domain, pictures of landscapes and not pictures of landmarks or
+buildings are considered to be the ``optimal'' stimulus type
 \citep{epstein2008parahippocampal}.
 % we did not choose se\_new and se\_old
-We did not include the categories that contained switches from one setting to
-another (\texttt{se\_new} and \texttt{se\_old}) which one might assume to
-contain the auditory equivalent to the ``optimal'' visual stimulus type in the
-primary AD contrast.
+In the AD's primary contrast, we did not include the categories that contained
+switches from one setting to another (\texttt{se\_new} and \texttt{se\_old})
+which one might assume to contain the auditory equivalent to pictures of
+landscapes.
 % why
@@
 %
-Based on the fact that the annotation of nouns offered a more precise way to
-operationalize the perception of spatial information than the annotation of cuts
-and locations, we also hypothesized that analyzing the data from the
-audio-description could localize the PPA in individual persons.
-%
-Hence to test if an auditory narrative could [in principle] substitute a visual
-localizer experiment, we examined the results from the audio-description's
-primary contrast on an individual level.
+Given that the annotation of nouns offered a more precise way to operationalize
+the perception of spatial information than the annotation of cuts and locations,
+we also hypothesized that analyzing the data from the audio-description could
+localize the PPA in individual persons.
+%
+We examined the results from the audio-description's primary contrast on an
+individual level to test if an auditory narrative could [in principle]
+substitute a visual localizer experiment.
 % results of dedicated localizer
@@
 $z$-threshold in an unthresholded $z$-map from one of three contrasts by visual
-judgment, we used a ``one threshold fits all approach`` (Z>3.4, p<.05
-cluster-corrected) in one contrast.
+judgment, we used one contrast and a ``one threshold fits all approach`` (Z>3.4,
+p<.05 cluster-corrected).
 % in the current study
@@
 % conclusion
-Thus, the cluster location and size is not just a by-product of the averaging
-process but the same pattern can can reliably be found in individual study
-participants.
+Thus, the cluster location and size found on the group level is not just a
+by-product of the averaging process but the same pattern can can reliably be
+found in individual study participants.
+% concluding statement
+our exploratory analysis suggests that a naturalistic auditory stimulus
+can [in principle] be applied to localize (the anterior part) of an higher-level
+visual area in the majority of subjects.
+% one threshold (and contrast) to rule them all
+Further studies that aim for individual diagnostics / ROI localization should
+nevertheless test more than one contrast to gain the ``best'' individual
+ROIs.\todo{..ouff}
+
+\todo[inline]{probably not important but: what do results suggest
+regarding individual differences?  Differences in alertness, attention to
+spatial information, predisposition?  ``capability'' to process auditory spatial
+information?}
+
 % question
-This raises the question if the different activation patterns can be attributed
-to different features inherent in visual compared to verbal stimuli.
+
+\subsection{PPA individuals (AD)}
+
+% question
+The fact that clusters from the auditory stimulus are spatially restricted to
+the anterior part of clusters from the visual paradigms raises the question if
+the revealed activation pattern could be attributed to be attributed to
+different features inherent in visual compared to verbal stimuli.\todo{ouff}
 % visual scenes: probably submodules
@@
 
-% conclusion
-Lastly, our exploratory analysis suggests that a naturalistic auditory stimulus
-can [in principle] be applied to localize (the anterior part) of an higher-level
-visual area in the majority of subjects.
-% one threshold (and contrast) to rule them all
-Further studies that aim for individual diagnostics / ROI localization should
-nevertheless test more than one contrast to gain the ``best'' individual
-ROIs.\todo{..ouff}
-
-\todo[inline]{probably not important but: what do results suggest
-regarding individual differences?  Differences in alertness, attention to
-spatial information, predisposition?  ``capability'' to process auditory spatial
-information?}
-
 \subsection{RSC \& LOC = non random clusters => naturalistic stimuli are
@@
 
-% no random clusers
-Despite performing a whole brain analysis, we do not find many [random] clusters
-in single contrasts or even systematically across contrasts that hamper the
+% no random clusters
+Despite performing a whole brain analysis, we do not find clusters in the
+primary contrast or across contrasts (s. supplemental material) that hamper the
 interpretation of results.
-% AV: null results regarding attention and eye movements
-For example in the AV results, we do not find significant clusters that could be
-attributed to cognitive processes like attention or eye movements.
-
 % intro
 Apart from the PPA, we find significantly increased activity in the dorsal
-precuneus and posterior cingulate region (e.g. retrosplenial cortex; RSC) and
+precuneus and posterior cingulate region (e.g. retrosplenial complex; RSC) and
 lateral occipital cortex (LOC) across contrasts of both naturalistic stimuli.
 % RSC intro
-Like the PPA, the RSC and LOC are known to be scene-selective regions (see
+Like the PPA, the RSC and LOC repeatedly showed increased hemodynamic activity
+in studies investigating visual spatial perception or navigation (see
 \citep{chrastil2018heterogeneity, bettencourt2013role} for reviews).
+
+\todo[inline]{AD clusters in LOC are more medial in AD stimulus compared to AV;
+whereas clusters in PPA and RSC of both stimuli overlap}
 % conclusion
-\todo[inline]{concluding statement}
+\todo[inline]{concluding statement??}
+
+This suggest that model-driven methods based on stimulus annotations are
+suitable to reveal spatially concise functional areas and networks.
+%
+Nevertheless, ``cleanliness''/``neatness``  of results (i.e. the signal-cluster
+to noise-cluster ration) depend on the extent to which the multi-dimensionality
+of the naturalistic stimulus is annotated, modeled, statistically controlled and
+/ or how many events the stimulus provides per assumed perceptual process for
+the averaging purpose
+
+\section{summary}
+
+\todo[inline]{join summary \& conclusion}
+
+% summary
+In summary, our approach to operationalize spatial perception based on stimulus
+annotations of two naturalistic stimuli is the shit and provide further evidence
+that model-driven analyses can be used to analyze data from multi-dimensional
+stimuli
+%
+and before I forget: this study shows that already existing, publicly
+available data can be re-used for independent research questions that provide
+further evidence for existing theories/hypotheses and advance the field by
+generating new findings \& hypothesis.\todo{if there are any parts that can be
+rephrased as explicit hypothesis: do it!}
 

### 2021-02-08 paper/main.tex
cleaning comments and supplementals

@@
 % our audience highlighting innovative examples of data reuse may be used to
-    % present compelling new findings & conclusions derived from published.
-    % intro
+% present compelling new findings & conclusions derived from published.  intro
 Neuroimaging studies have parcellated the human brain into distinct functional
@@
 A region in the human hippocampal cortex termed ``parahippocampal place area''
-    is classically considered to be a higher visual area as increased
-    hemodynamic activity in the PPA correlates with the perception of static
-    pictures of landscapes compared to pictures of faces or objects.
+is classically considered to be a higher visual area as increased hemodynamic
+activity in the PPA correlates with the perception of static pictures of
+landscapes compared to pictures of faces or objects.
 % AV, AD: operationalization
-In this study, we explore different ways to operationalize spatial
-    perception\todo{not sure if this is just perception} in 14 subjects that
-    were watching an audio-visual Hollywood movie and listened to the movie's
-    audio-description (studyforrest.org).
+In this study, we explore different ways to operationalize the perception of
+spatial information in 14 subjects that were watching an audio-visual Hollywood
+movie and listened to the movie's audio-description (studyforrest.org).
 % auditory localizer?
@@
 Results suggest that increased activation in the PPA during the perception of
-    static pictures generalizes to the perception of spatial information
-    embedded in an audio-visual movie and an exclusively auditory stimulus.
+static pictures generalizes to the perception of spatial information embedded in
+an audio-visual movie and an exclusively auditory stimulus.
 % conclusion: PPA has subregions
@@
 % localizer substitute
-An auditory narrative might substitute a visual paradigm to localize the PPAs
-    anterior part in visually impaired subjects.\todo{very bold claim to be
-    written in the abstract}
-
+[An auditory narrative might substitute a visual paradigm to localize the PPAs
+anterior part in visually impaired subjects.]
 \end{abstract}
@@
         speak of contrast not ``primary contrast''
-    \item adopt some phrasing from the Speech-Anno-Paper
+    \item in main text, add references to supplemental material
     \item there is no "cue about" in the English language? Alternatives are
@@
 \begin{itemize}
-    \item as Simon stated I would be interesting to discuss differences between
-        contrasts (and make wild assumptions) but this will exceed the word
-    limit by far
-    \item overall conclusion as a last paragraph or independent section
+    \item summary \& overall conclusion (last paragraph or independent section)
 \end{itemize}
@@
 \cite{aziz2008modulation} used sentences that described famous or generic places
-and faces, or objects.\todo{judgment task not mentioned anymore}
-% Aziz' tasks: Participants were instructed to press a button whenever the
-% sentence described an inaccurate or improbable fact. Aziz' results:
+and faces, or objects.
+% Aziz' tasks:
+Participants were instructed to press a button whenever the sentence described
+an inaccurate or improbable fact (e.g. ``Marilyn Monroe has a large square
+jaw'')
+% Aziz' results:
 Activation in the left, but not right, PPA was significantly reduced when
@@
 Second, studies used block-design paradigms to maximize detection power.
-Further, they usually employed an explicit (perceptual) judgment task.
+Further, they usually employed an explicit (perceptual) judgement task.
 % conceptualized stimuli and block: disadvantages
@@
 
-\subsection{Event selection}
+\subsection{Event selection} \label{rationale}
 
@@
 participants view novel versus repeated scenes or view-points
-\citep{epstein1999parahippocampal, grill2006repetition}.\todo[inline]{doesn't
-make sense not 'cause this should be true to the face of forrest too}
+\citep{epstein1999parahippocampal, grill2006repetition}.
+%
+\todo{imo its better to focus on the cinematographic rationale and drop the last
+sentence 'cause activity in e.g. FFA adopts too -> we might substract an on
+average smaller response}
 % no cut condition: intro
@@
 % annotation procedure
-Two persons performed a categorization of nouns that the narrator uses to
-describe the movie's missing visual content based on a set of rules.
+Two persons performed a categorization of (concrete and countable) nouns that
+the narrator uses to describe the movie's missing visual content based on a set
+of rules.
 % preliminary annotation
@@
 % pooling of categories
-Some noun categories that were semantically similar and offered only a
-small amount of counts were pooled resulting in 11 final event categories (see
-Table \ref{tab:ao-events}). These event categories were then used to model
-hemodynamic responses.
+Some noun categories that were semantically similar and offered only a small
+amount of counts were pooled resulting in 11 final event categories (see Table
+\ref{tab:ao-events}). These event categories were then used to model hemodynamic
+responses.
 
@@
 
-\todo[inline]{SE: würde wetten, dass Reviewer fragen: Wie sieht es im vergleich
-dazu mit Faces aus? COH: yeah, well, I made the contrasts similar to Sengupta
-and considered the contrast to an average of all ``non-spatial'' stuff
-appropriate; should be cleare in the method section (s. ``Contrasts'')}
+\todo[inline]{SE: Vergleich zu Faces aus? COH: should be clearer now why we did
+not do it}
 
@@
 % similar to previous studies
-On the first level, we created GLM contrasts like studies that contrasted blocks
-of pictures.
-% dissimilar
-But unlike previous studies, our approach was to contrast selected stimulus
-features that we annotated in the audio-visual movie and its audio-description.
+On the first level, we created GLM contrasts based on annotated stimulus
+features embedded in the in the audio-visual movie and its audio-description.
 % intro
@@
 % difference to Sengupta; Berman et al. (2010). Evaluating functional localizers
-(2010) Notably, localization of the PPA in individual subjects that was done by
+% (2010)
+Notably, localization of the PPA in individual subjects that was done by
 \citep{sengupta2016extension} using the established approach of contrasting
@@
 The selection criterion for the primary contrast of each stimulus was a
-subjectively good balance between a) how well categories on average were assumed
-to match the preferred stimulus type, and b) the amount of available data /
-
+subjectively good balance between a) the amount of available data, b) how
+well the average of events within represented spatial information and
+non-spatial information respectively (cf. section \ref{rationale}).
 % AV: primary contrast
@@
 frames depicting a landscape or the geometry of a setting, and the category
-\texttt{vpe\_old} the most frames depicting persons, faces, or
-objects.\todo{maybe speak of ratio}
+\texttt{vpe\_old} the most frames depicting persons, faces, or objects [(cf.
+rationale to categorize the cuts in section \ref{rationale})].
 % AD: primary contrast
@@
 \texttt{furniture} to get a sufficient amount of events per stimulus segment.
-% furniture
+\todo[inline]{in detail: \texttt{fahead}: just N=83; mostly parts
+ of face (``ear'', ``nose''), or vague description (``his/her face''; N=10)}
+% why furniture was not used
 The category ``furniture'' (\texttt{furn}) was not used as a regressor of
@@
 % hierarchical categories
-c) the narrator is often lacking behind a short dialogue or a change of the
-soundscape that might already indicate a change of settings.
-\todo[inline]{paragraph above could state that ``fahead'', just N=83; mostly
-    just parts (``ear'', ``nose'') of face, or vague description ``his/her
-face''}.
+[c) the narrator is often lacking behind a short dialogue or a change of the
+soundscape that might already indicate a change of settings.] \todo[inline]{for
+sake of conciseness, it is imo better to drop that ``soundscape-thing''}
 % control contrasts
@@
 localizer and the primary AD contrast, we created a Bland-Altman-Plot for every
-subject (see \ref{fig:bland-altman}).
+subject (see Figure \ref{fig:bland-altman}).
 % what it depicts
@@
 A shift of the distribution to voxels with a mean above zero can be seen the
-further we constrain voxels to the individual PPA (see KDE plot for the x-axis).
+further we constrain voxels to the individual PPA (see KDE plot for the x-axes
+in Figure \ref{fig:bland-altman}).
 % right KDE plot
@@
 
-\subsection{Robustness of group results across contrasts}
-
-% unthresholded $z$-maps of all contrasts on a group level:
-% \href{https://neurovault.org/collections/KADGMGVZ/}{NeuroVault}.
+\todo[inline]{I think it makes sense to report results of AV and discuss AV,
+and then report results of AD and discuss AD}
+
+\subsection{Results}
+
+\subsubsection{Robustness of group results across contrasts}
+
+% intro
+In order to test the robustness of our approach, we created overall five
+$t$-contrasts for the AV stimulus (see Table \ref{tab:av-contrasts}), and
+overall eight $t$-contrast for the AD stimulus (see Table
+\ref{tab:av-contrasts}) by varying the contrasted categories (and thus the
+amount of available data), and how well the annotated events within categories
+on average matched a stimulus type that we assumed to correlate with spatial
+perception.
+% NeuroVault
+Unthresholded z -maps of all contrasts on a group level as well as individual
+results of the primary t-contrasts co-registered to the group-template (MNI152
+space) can found at NeuroVault
+\href{https://neurovault.org/collections/KADGMGVZ/}{NeuroVault}.
 
@@
 
-% AV
-In order to test the robustness of our findings, we created four additional
-$t$-contrasts for the AV stimulus (see Table \ref{tab:av-contrasts}) to be
-investigated on a group level.
-% results: PPA; biggest overlap in posterior part of PPA group overlap  =
-%temporal occipital fusiform cortex
-All of the overall five AV contrasts yielded significant bilateral clusters that
+% AV results: PPA; biggest overlap in posterior part of PPA group overlap  =
+% temporal occipital fusiform cortex
+All five AV contrasts yielded significant bilateral clusters that
 overlap with the PPA group overlap (see Figure \ref{fig:stability-slices}).
-% AD
-For the AD stimulus, we created overall eight $t$-contrasts (see Table
-\ref{tab:ao-contrasts}).
-% results
-All contrasts except contrast 7 (\texttt{se\_new}, \texttt{se\_old} >
-non-spatial categories) and contrast 8 (\texttt{se\_new} > non-spatial
-categories) yielded significant bilateral clusters in anterior regions of the
-group PPA overlap (see Figure \ref{fig:stability-slices}), suggesting
-a certain robustness of this result.
+% AV: RSC & LOC
+Reliably across contrasts of the AV stimulus, we find bilaterally
+significant clusters also in the ventral precuneal cortex and posterior
+cingulate gyrus (i.e. restrosplenial complex; contrasts 1, 4, 5), and lateral
+occipital cortex (contrasts 1, 2, 4, 5).
 
@@
 
-% AD
-Reliably across the five contrasts of the AV stimulus, we find bilaterally
-significant clusters also in the ventral precuneal cortex and posterior
-cingulate gyrus (i.e. restrosplenial region; contrasts 1, 4, 5) and lateral
-occipital cortex (contrasts 1, 2, 4, 5).
-% AD; LOC: AV cluster are more medial, AD clusters are more lateral
-Across the five contrasts of the AD stimulus, we find bilaterally
-significant clusters in the ventral precuneus (all except contrasts 8), lateral
+% AD: results
+In results of the AD stimulus, all contrasts except contrast 7
+(\texttt{se\_new}, \texttt{se\_old} > non-spatial categories) and contrast 8
+(\texttt{se\_new} > non-spatial categories) yielded significant bilateral
+clusters in anterior regions of the group PPA overlap (see Figure
+\ref{fig:stability-slices}).
+% AD: RSC & LOC
+Reliably across contrast of the AD stimulus, we find bilaterally significant
+clusters also in the ventral precuneus (all except contrasts 8), lateral
 occipital cortex (bilateral in contrasts 1 to 4; unilateral in contrasts 6 and
@@
 right in contrast 2).
-
 % non-systematic
@@
 
-\subsection{control contrasts}
+\subsubsection{control contrasts}
+
+% intro
+For the purpose of negative control, we implemented five contrasts for every
+stimulus.
 
@@
 
-\todo[inline]{there is no table/figure for negative control contrasts; we could
-add a reference to NeuroVault (here again) or point to the dataset}
-
-% intro
-Lastly, we implemented five contrasts for every stimulus for the purpose of
-negative control.
 % AV: no_cut > x
-In the analysis of the AV data, none of the contrasts that compared the ``no cut
-condition''  to a movie cut category (contrasts 6, 7, 8, 9) yielded significant
-clusters.
+In the analysis of the AV data, none of the four contrasts that compared the
+\texttt{no\_cut} categorie to a movie cut category (see Table
+\ref{tab:av-contrasts}) yielded significant clusters.
 % AV using nouns
@@
 PPA and bilateral clusters in the superior lateral occipital cortices (the right
-hemispheric cluster extending into the superior parietal cortex).
+hemispheric cluster extending into the superior parietal cortex).\todo{cuts
+correlate with the nouns}
 
@@
 Contrast 12 (\texttt{vse\_new} > \texttt{vse\_old}, \texttt{vpe\_old}) revealed
-one cluster in the right posterior hippocampus.
-
-\subsection{Discussion: Robust results across contrasts}
-
-\todo[inline]{SE: Bei Ergebnissen \& Diskussionen zu Stability fehlt mir
-irgendwie immer der Kontext, wie sich die Kontraste denn unterschieden haben und
-welche davon z.B. im Ergebnis wo von den anderen abgewichen haben. Das würde ja
-wichtige Hinweise geben; COH: indeed very interesting but discussing that will
-let the paper get way out of hand}
-
-% why we did a couple of contrasts
-To test the robustness of our approach, we created several additional contrasts
-for each naturalistic stimulus by varying the contrasted categories (and thus
-the amount of available data), and how well the annotated events within
-categories on average matched a stimulus type that we assumed to correlate with
-spatial perception.
-
-\subsubsection{PPA}
+one cluster in the right posterior hippocampus.\todo{odd imo}
+
+\subsection{Discussion}
+
+\subsubsection{congruencies (PPA, RSC, LOC, others)}
 
@@
 \end{comment}
+
+\todo[inline]{SE: Bei Ergebnissen \& Diskussionen zu Stability fehlt mir
+irgendwie immer der Kontext, wie sich die Kontraste denn unterschieden haben und
+welche davon z.B. im Ergebnis wo von den anderen abgewichen haben. Das würde ja
+wichtige Hinweise geben}
 
@@
 
-\subsubsection{RSC \& LOC}
-
 \todo[inline]{same part as in the main text but with number of contrasts}
-
 % intro
@@
 reviews).
-% conclusion
 
@@
 
-\subsubsection{confounding clusters}
 % ``confounding'' clusters
@@
 
+The four control contrasts of the AV stimulus that compared the
+\texttt{no\_cuts} to categories of movie cuts all lead to null results.
+
 \todo[inline]{hm, so why did I build contrasts of the no\_cut condition compared
@@
 
-The four control contrasts of the AV stimulus that compared the
-\texttt{no\_cuts} to categories of movie cuts all lead to null results.
+\todo[inline]{discussion \& concluding statement}
 
@@
 
-\todo[inline]{shower thought: changes of a soundscape that indicate a setting's
-    spatial layout could correlate with increased activity in the PPA
-    (arnott2008crinkling finds increased activations in PPA to sounds made by
-    objects (that reveil object's material/identity); but at the moment when
-    looking at the data I see no systematic in the results that let me assume
-that}
+\todo[inline]{changes of a soundscape that indicate a setting's spatial layout
+    could correlate with increased activity in the PPA (arnott2008crinkling
+    finds increased activations in PPA to sounds made by objects that reveal
+    object's material/identity); but: when looking at the data I see no
+systematic in the results that let me assume that}
 

### 2021-02-08 paper/main.tex
dropping comments

@@
 
-\todo[inline]{SE: Vergleich zu Faces aus? COH: should be clearer now why we did
-not do it}
-
-\todo[inline]{SE: cuts to new vs familar setting wird irgendwie nie so
-richtig in den PPA kontext eingeordnet. Warum ist das Hauptkontrast und nicht
-das viel näher liegende places vs faces? COH: places vs. face = simple set in
-Sengupta; here, we follow the strict set used in Sengupta; tbh, not mentioned in
-detail}
+\todo[inline]{COH: tried to make clear why we did not/could not use ``places vs.
+faces''}
 
@@
  of face (``ear'', ``nose''), or vague description (``his/her face''; N=10)}
-% why furniture was not used
-The category ``furniture'' (\texttt{furn}) was not used as a regressor of
-interest in any contrast because these nouns could be perceived as either a
-geometry-defining scene element or as an isolated object.
 % why se_new & se_old were not used in the primary contrasts
@@
 sake of conciseness, it is imo better to drop that ``soundscape-thing''}
+% why furniture was not used
+The category ``furniture'' (\texttt{furn}) was not used as a regressor of
+interest in any contrast because these nouns could be perceived as either a
+geometry-defining scene element or as an isolated object.
 % control contrasts
@@
 
-\todo[inline]{SE: overlap of clusters/contrasts: Anzahl der Überlappungen ist
-schwer abzulesen; lieber eine andere Farbskala (spectral sequence?) nutzen; COH:
-this figure is my end game boss}
-
-\todo[inline]{SE: Wie sehen die Antworten innerhalb der "klassisch definierten"
+\todo[inline]{SE: Antworten innerhalb "klassisch definierter"
 PPA für die verschiedenen regressoren bzw. kategorien derselben (zumindest aber
-places vs faces) aus? COH: ???}
+places vs faces) aus? -> Peristimulus plots}
 
@@
 
-\todo[inline]{part regarding Sengupta is shortened; they used $t$-maps???}
 % Sengupta et al., 2016
@@
 parahippocampal clusters in 12 of 14 subjects and an unilateral right clusters
-in two subjects (sub-04, sub-20).
+in two subjects (sub-04, sub-20).\todo{I shortened the following part (maybe too
+much)}
 % Sengupta: 1 of 3
@@
 anatomical location based on literature \citep{epstein1998ppa}.
+\todo{they used $t$-maps???}
 % one contrast to localize them all; "...and Z>3.4 for all"
@@
 
+\todo[inline]{SE: overlap of clusters/contrasts: Anzahl der Überlappungen ist
+schwer abzulesen; lieber eine andere Farbskala (spectral sequence?) nutzen; COH:
+this figure is my end game boss}
+
 % intro

### 2021-02-11 paper/main.tex
revising text/comments: into, methods, results

@@
 \begin{itemize}
-    \item in case the additional contrast stay in supplemental material, just
-        speak of contrast not ``primary contrast''
-    \item in main text, add references to supplemental material
-    \item there is no "cue about" in the English language? Alternatives are
-        "give a hint on/about", "indicate"; changed the sentences but should
-        ask Alex
+    \item speaking of "primary contrast" probably not necessary anymore.
+    \item main text: add references to supplemental material
 \end{itemize}
@@
 \begin{itemize}
-    \item Figure of regressor correlations: maybe write out in full the name of
+    \item Fig regressor correlations: maybe write out in full the name of
         regressors (instead of pointing to the table)
@@
 %
-\todo{imo its better to focus on the cinematographic rationale and drop the last
-sentence 'cause activity in e.g. FFA adopts too -> we might substract an on
-average smaller response}
+\todo{better focus on cinematographic rationale \& drop last sentence; activity
+in e.g. FFA adopts too -> we might substract an on average smaller response}
 % no cut condition: intro
@@
         \texttt{fg\_ad\_lrdiff} and \texttt{fg\_av\_ger\_lrdiff}, r=.7749).
-        \todo[inline]{not all labels are actually listed in that table; which
-        ones are not listed? checked it, all labels listed}
+        \todo[inline]{checked it, all labels listed}
       }
@@
 
-\todo[inline]{COH: tried to make clear why we did not/could not use ``places vs.
-faces''}
-
 % intro
@@
 To test the robustness of this approach, we operationalized the perception of
-spatial information compared to the perception of ``non-spatial'' information
+spatial information compared to the perception of non-spatial information
 differently in five $t$-contrasts for the AV stimulus (see Table
@@
 We assumed all contrasts could in principle correlate with increased hemodynamic
-activity in the PPA.
-% but we expect differences because
-Nevertheless, we also assumed contrasts would differ in [?] \todo{differ in
-what?  ``localization performance'' isn't well phrased. How ``well'', ``nice''
-the results are?} since the event categories differed a) in how well the
-averaged events reflected spatial information, and b) in available data (i.e.
-event counts).
-% difference to Sengupta; Berman et al. (2010). Evaluating functional localizers
-% (2010)
-Notably, localization of the PPA in individual subjects that was done by
-\citep{sengupta2016extension} using the established approach of contrasting
-blocks of pictures is based on one contrast for each subjects (cf. Table 3 in
-\citep{sengupta2016extension}) that was chosen post-hoc from a set of three
-contrasts (\textit{strict}, \textit{relaxed}, and \textit{simple} contrast
-\citep{sengupta2016extension}).
-% thus: primary contrasts
-Here, we chose one contrast to be ``primary contrast'' for later detailed
-inspection and report.
+activity in the PPA but chose one contrast to be the ``primary contrast'' for
+later detailed inspection and report.
 % selection criteria for primary contrast.
 The selection criterion for the primary contrast of each stimulus was a
-subjectively good balance between a) the amount of available data, b) how
-well the average of events within represented spatial information and
-non-spatial information respectively (cf. section \ref{rationale}).
+subjectively good balance between a) how well the average of events within
+categories represented spatial information and non-spatial information
+respectively (cf. section \ref{rationale}), and b) the amount of available data.
 % AV: primary contrast
 In the primary contrast of the AV stimulus, we contrasted cuts to a setting that
-was not depicted before (\texttt{vse\_new}) to cuts that we accompanied with a
-change of the camera position within a setting that was already occurring
-previously (\texttt{vpe\_old}).
+was not depicted before (\texttt{vse\_new}) to cuts merely switching the camera
+position within a setting that was already established earlier in the movie
+(\texttt{vpe\_old}).
 % why
@@
 In the primary contrast of the AD stimulus, we contrasted landmarks
-\texttt{geo}, and rooms and geometry-defining objects \texttt{geo-room} with all
-non-geometry related categories (\texttt{body}, \texttt{bodypart},
-\texttt{fahead}, \texttt{object}, \texttt{sex\_f}, \texttt{sex\_m}) except
-\texttt{furniture} to get a sufficient amount of events per stimulus segment.
-\todo[inline]{in detail: \texttt{fahead}: just N=83; mostly parts
- of face (``ear'', ``nose''), or vague description (``his/her face''; N=10)}
+\texttt{geo}, and rooms and geometry-defining objects \texttt{geo-room} with not
+just nouns referring to a person's head or face (\texttt{fahead}, N=83; e.g.
+``eyes'', ``face'', or ``head'') but also all non-geometry related categories
+(\texttt{body}, \texttt{bodypart}, \texttt{fahead}, \texttt{object},
+\texttt{sex\_f}, \texttt{sex\_m}) except \texttt{furniture} to get more events
+per stimulus segment.
+% why furniture was not used
+The category ``furniture'' (\texttt{furn}) was not used as a regressor of
+interest in any contrast because these nouns could be perceived as either a
+geometry-defining scene element or as an isolated object.
 % why se_new & se_old were not used in the primary contrasts
@@
 richer pictures], and
-% hierarchical categories
-[c) the narrator is often lacking behind a short dialogue or a change of the
-soundscape that might already indicate a change of settings.] \todo[inline]{for
-sake of conciseness, it is imo better to drop that ``soundscape-thing''}
-% why furniture was not used
-The category ``furniture'' (\texttt{furn}) was not used as a regressor of
-interest in any contrast because these nouns could be perceived as either a
-geometry-defining scene element or as an isolated object.
+% c) the narrator is often lacking behind a short dialogue or a change of the
+% soundscape that might already indicate a change of settings.
+%
 % control contrasts
@@
 setting.
-%
-\todo[inline]{it's probally not about the soundscape anymore (to speculative)
-but about the somewhat correlation of nouns and cuts}
+% difference to Sengupta; Berman et al. (2010). Evaluating functional localizers
+% (2010)
+In the VIS study \citep{sengupta2016extension} using the established approach of
+contrasting blocks of pictures, assessment of individual PPAs was based on
+chosing post-hoc one from a set of three contrasts (\textit{strict},
+\textit{relaxed}, and \textit{simple} contrast \citep{sengupta2016extension};
+cf. Table 3 in \citep{sengupta2016extension}).
 
@@
 
-\todo[inline]{SE: in Figure weiter reinoomen; bei FFA/PPA etc sind
-flatmaps/inflated brains standard; COH: imo it is important that we do not have
-clusters all over the brain}
-
 \todo[inline]{SE: Antworten innerhalb "klassisch definierter"
@@
 parahippocampal clusters in 12 of 14 subjects and an unilateral right clusters
-in two subjects (sub-04, sub-20).\todo{I shortened the following part (maybe too
-much)}
+in two subjects (sub-04, sub-20).
 % Sengupta: 1 of 3

### 2021-02-11 paper/main.tex
summarize discussion of AD (group) resuts

@@
 
-\todo[inline]{SE: VIS vs AV vs AD: Wer liefert was über die PPA. Dieser
-Vergleich bzw. die Diskussion über Gemeinsamkeiten \& Unterschiede fehlt mir
-etwas}
-
 % intro
@@
 We here exploited a cinematographic confound in the stimulus structure (cf.
-\ref{rationale}).
+\ref{rationale}):
 % establishing shots vs. e.g. over-the-shoulder shots
-Film directors tend to establish the geometry of locations earlier in the movie
+film directors tend to establish the geometry of locations earlier in the movie
 and tend to later focus more on persons and objects relevant to the evolved
@@
 % hypo
-Despite our ad hoc approach, we hypothesized that [confounding variables
-could/would average out and] our whole-brain analyses would lead to significant
-clusters in the PPA.
+Despite our ad hoc approach, we hypothesized that confounding variables would
+average out, and our whole-brain analyses would lead to significant clusters in
+the PPA.
 % results
-Group results of the AV stimulus' primary contrast yielded a cluster that span
-the group overlap of individual PPA ROIs from anterior to posterior.
+Group results of the AV stimulus' primary contrast yielded one cluster that
+spans the group overlap of individual PPA ROIs from anterior to posterior.
 % confound of higher perception
@@
 attributed to the averaging process that did not control for confounding visual
-features [or the attentional focus of study participants].
-%
-\todo[inline]{I am pretty surprised the clusters are not all over the brain. I
-do not know where/how do phrase it but should be mentioned imo}
+features.
 % solution
@@
 using the open-source solution ``Pliers'' for feature extraction from a visual
-naturalistic stimulus; \citep{mcnamara2017developing})[, and record the
-subject's visual attention via eye-tracking].
-%
-
-\todo[inline]{concluding statements regarding exploited cinematographic
-confound? e.g.: movies are nice but have idiosyncrasies? so, maybe you should be
-aware of these idiosyncrasies (and control for it) in case you wanna use movies
-for research?}
-
-\todo[inline]{overall main message / concluding statement of this
-``cross-modal-control-movie-thing''??}
-
-\todo[inline]{Aziz: reduced activity only in left PPA, and only for famous
-places vs famous faces; I think they ran their f-test on the average of PPA
-voxels defined by separate localizer}
+naturalistic stimulus; \citep{mcnamara2017developing}).
+% we took advantage of cinamtography
+We here took advantage of an idiosncracy of movie directing to shift from
+establishing the geometry earlier in the movie to later depicting persons and
+objects more relevant to the evolved plot.
+% know your stimulus
+Given that this shift is common in movies, investigators should be aware that
+cinematographic tendencies are part of movie's confound structure that might,
+depending on the research question, influence the results.
+% conclusion
+In summary, results from the visual localizer paradigm using blocks of pictures
+generalize to an ad hoc approach to operationalize the perception of spatial
+information at the moment of cuts in a audio-visual movie.
 
 % intro
-Second, we analyzed data from the audio-description.
+Second, we analyzed data from the audio-description offering exclusively
+auditory stimulation.
 % hypothesis
 Encouraged by \citep{aziz2008modulation}, we hypothesized that spatial
-information embedded in an exclusively auditory stimulus would correlate with
-increased hemodynamic activity in the PPA.
+information embedded in the AD stimulus would correlate with increased
+hemodynamic activity in the PPA.
 % diff to Aziz (2008)

### 2021-02-12 paper/main.tex
cleaning before printing

@@
 % our audience highlighting innovative examples of data reuse may be used to
-% present compelling new findings & conclusions derived from published.  intro
+% present compelling new findings & conclusions derived from published.
 Neuroimaging studies have parcellated the human brain into distinct functional
@@
 \begin{itemize}
-    \item speaking of "primary contrast" probably not necessary anymore.
     \item main text: add references to supplemental material
@@
         regressors (instead of pointing to the table)
+    \item different frame counts of segments AV vs. AD
 \end{itemize}
@@
         in intro / method
-    \item Simons Kommentare, bei denen ich mitunter anderer Meinung bin
-
 \end{itemize}
@@
 \begin{itemize}
-    \item summary \& overall conclusion (last paragraph or independent section)
+    \item "Lokalisation der PPA" vs. "Antwortverhalten einer vorab definierten
+        PPA". Machst wohl das erste, beschreibst es aber als das zweite
+    \item Summary / Concluding statement
+        (data reuse to present compelling new findings \& conclusions derived
+        from published.)
 \end{itemize}
 
+\noindent Supplemental Material
+\begin{itemize}
+    \item restructure (results + discussion AV, then AD)
+    \item discuss differences of contrasts (s. Simons comment)
+\end{itemize}
+
+\noindent Code Availability
+\begin{itemize}
+    \item https://www.springernature.com/gp/authors/research-data-policy/data-availability-statements/12330880i
+\end{itemize}
+
+\noindent Data Availability
+\begin{itemize}
+    \item s. other psyinfo paper
+\end{itemize}
+
 \pagebreak[4]
@@
 % Limit for main text (intro, results and discussion) = ca. 3k words
-
-\todo[inline]{~1000 words}
 
@@
 To our knowledge only one study \citep{aziz2008modulation} compared hemodynamic
-activity levels in the PPA that were correlated with differrent semantic
+activity levels in the PPA that were correlated with different semantic
 categories occurring in spoken language.
@@
 
-\todo[inline]{~3500 words}
-
 % Specific data outputs should be explicitly referenced via data
@@
 % annotation ftw
-Hence, we annotated a the temporal structure of a various stimulus features that
+Hence, we annotated the temporal structure of a various stimulus features that
 later served as a basis (for GLM regressors) to model hemodynamic responses.
@@
 %
-\todo{better focus on cinematographic rationale \& drop last sentence; activity
-in e.g. FFA adopts too -> we might substract an on average smaller response}
+\todo{drop last sentence \& better focus on cinematographic rationale; activity
+in e.g. FFA adopts too -> we might subtract an on average smaller response}
 % no cut condition: intro
@@
 \section{Results}
-\todo[inline]{800 words}
 
@@
 The movie's primary $t$-contrast that compared cuts to a setting that was not
-depicted before to cuts withn a recurring setting (\texttt{vse\_new > vpe\_old})
-yielded three significant clusters (see Table \ref{tab:res-av-group1}, Figure
-\ref{fig:group-slices}).
+depicted before to cuts within a recurring setting (\texttt{vse\_new >
+vpe\_old}) yielded three significant clusters (see Table
+\ref{tab:res-av-group1}, Figure \ref{fig:group-slices}).
 % PPA (others the clusters extend into).
@@
 and AD $t$-contrast, and the outline of overlapped, individual PPAs
-\citep{sengupta2016extension} co-registed to the MNI152 template.
+\citep{sengupta2016extension} co-registered to the MNI152 template.
 % one slice to show them all
@@
 
-\todo[inline]{1700 words}
 % Discussion: explains how results fill gap identified in intro
@@
 % advances the field by providing new opportunities
-
-\todo[inline]{SE: sauber differenzieren zwischen "Lokalisation der PPA" und
-    "Antwortverhalten einer vorab definierten PPA". Ich habe den Eindruck, dass
-Du oft das erste machst es aber als das zweite beschreibst; COH: ??? we do
-whole-brain analysies, so probably ``localization'', }
 
@@
 Contrary to previous studies, our current approach is not based on carefully
-designed sets of stimuli but based on annotated stimulus features incidentially
+designed sets of stimuli but based on annotated stimulus features incidentally
 occurring in two naturalistic stimuli.
@@
 On a group level, whole brain-analysis results for the movie stimulus show
-signifcantly increased hemodynamic activity spatially overlapping with a
+significantly increased hemodynamic activity spatially overlapping with a
 traditionally localized PPA but also extending into earlier visual cortices.
@@
 
-\subsection{PPA group}
+\subsection{PPA (group + individuals \& aPPA vs. pPPA)}
 
@@
 naturalistic stimulus; \citep{mcnamara2017developing}).
-% we took advantage of cinamtography
-We here took advantage of an idiosncracy of movie directing to shift from
+% we took advantage of cinematography
+We here took advantage of an idiosyncrasy of movie directing to shift from
 establishing the geometry earlier in the movie to later depicting persons and
@@
 
-\subsection{PPA individuals (AD)}
-
-\todo[inline]{how to discuss Bland-Altman-Plots???; dunno if this is meaningful:
-z-scores in the anterior part of PPA are higher in AD contrasts than in contrast
-of localizer}
-%
+% AD annotation > AV annotation
 Given that the annotation of nouns offered a more precise way to operationalize
@@
 localize the PPA in individual persons.
-%
-We examined the results from the audio-description's primary contrast on an
-individual level to test if an auditory narrative could [in principle]
-substitute a visual localizer experiment.
 % results of dedicated localizer
@@
 Whereas \citep{sengupta2016extension} chose the subjectively ``best fitting''
-$z$-threshold in an unthresholded $z$-map from one of three contrasts by visual
-judgment, we used one contrast and a ``one threshold fits all approach`` (Z>3.4,
-p<.05 cluster-corrected).
+$t$-threshold in an unthresholded $t$-map from one of three contrasts by visual
+judgment, we used the same contrast and threshold (Z>3.4, p<.05
+cluster-corrected) for all subjects.
 % in the current study
-The audio-description's primary contrast yielded significant bilateral clusters
-in 9 of 14 subjects (of which sub-04 shows only a right-lateralized PPA ROI),
-and a unilateral significant cluster in one subject.
+The audio-description yielded significant bilateral clusters in 9 of 14 subjects
+(of which sub-04 shows only a right-lateralized PPA ROI), and a unilateral
+significant cluster in one subject.
 % similar: anterior part
@@
 Thus, the cluster location and size found on the group level is not just a
-by-product of the averaging process but the same pattern can can reliably be
-found in individual study participants.
+by-product of the averaging process but a reliable pattern across results of
+individual study participants.
 % concluding statement
-our exploratory analysis suggests that a naturalistic auditory stimulus
+Further, our exploratory analysis suggests that a naturalistic auditory stimulus
 can [in principle] be applied to localize (the anterior part) of an higher-level
@@
 % one threshold (and contrast) to rule them all
-Further studies that aim for individual diagnostics / ROI localization should
-nevertheless test more than one contrast to gain the ``best'' individual
-ROIs.\todo{..ouff}
-
-\todo[inline]{probably not important but: what do results suggest
-regarding individual differences?  Differences in alertness, attention to
-spatial information, predisposition?  ``capability'' to process auditory spatial
-information?}
-
-% question
-
-\subsection{PPA individuals (AD)}
+Nevertheless, further studies that aim for individual diagnostics / ROI
+localization should inspect more than one contrast, and use an individual
+threshold or a sphere around the local maximum \citep{poldrack2007region} in the
+parahippocampal region.
+
+\todo[inline]{discussion of Bland-Altman-Plots?; dunno if this is meaningful:
+z-scores in the anterior part of PPA are higher in AD contrasts than in contrast
+of localizer}
 
@@
 the anterior part of clusters from the visual paradigms raises the question if
-the revealed activation pattern could be attributed to be attributed to
-different features inherent in visual compared to verbal stimuli.\todo{ouff}
+the revealed correlation patterns can be attributed to different features
+inherent in the visual compared to the verbal stimuli.
 % visual scenes: probably submodules
@@
 % cytoarchitectonic map
-The aPPA is functionally more responsive than the pPPA to high-level features of
-scenes (e.g. real-word size \citep{park2015parametric}; a scene's abstract
-identity/category \citep{marchette2015outside, watson2016patterns}) and objects
-(e.g. spatial contextual associations \citep{aminoff2007parahippocampal,
+Contrary, the aPPA is functionally more responsive than the pPPA to high-level
+features of scenes (e.g. real-word size \citep{park2015parametric}; a scene's
+abstract identity/category \citep{marchette2015outside, watson2016patterns}) and
+objects (e.g. spatial contextual associations \citep{aminoff2007parahippocampal,
 aminoff2013role}).
@@
 % anterior
-The aPPA is more strongly functionally connected to portions of the default mode
-network, including caudal inferior parietal lobe (cIPL), the restrosplenial
-complex (RSC), medial PFC and the lateral surface of the anterior temporal lobe
-\citep{baldassano2013differential, baldassano2016two}.
+Contrary, the aPPA is more strongly functionally connected to portions of the
+default mode network, including caudal inferior parietal lobe (cIPL), the
+restrosplenial complex (RSC), medial PFC and the lateral surface of the anterior
+temporal lobe \citep{baldassano2013differential, baldassano2016two}.
 % conclusion: subregions
 According to the hypothesis by \citep{baldassano2013differential} the PPA
-consists of subregions that activate selectively to scenes and ``cooperate to
-build a complete representation of a scene''.
+consists of subregions that process specific apsects of a visual scene and
+cooperate to build a complete scene representation.
 % Their distinct connectivity properties do suggest that each may be involved in
@@
 (e.g. spatial contextual information \citep{aminoff2013role,
-aminoff2015associative, baumann2016functional}) as immanent/inherent in both
-visual and verbal stimuli.
-
-\subsection{RSC \& LOC = non random clusters => naturalistic stimuli are
-cool}
-
-% no random clusters
-Despite performing a whole brain analysis, we do not find clusters in the
-primary contrast or across contrasts (s. supplemental material) that hamper the
-interpretation of results.
+aminoff2015associative, baumann2016functional}) as inherent in both visual and
+verbal stimuli.
+
+\subsection{RSC \& LOC; naturalistic stimuli}
+
 % intro
@@
 precuneus and posterior cingulate region (e.g. retrosplenial complex; RSC) and
-lateral occipital cortex (LOC) across contrasts of both naturalistic stimuli.
+lateral occipital cortex (LOC; more lateral in the AV stimulus, more medial in
+the AD stimulus) across contrasts of both naturalistic stimuli.
 % RSC intro
@@
 \citep{chrastil2018heterogeneity, bettencourt2013role} for reviews).
-
-\todo[inline]{AD clusters in LOC are more medial in AD stimulus compared to AV;
-whereas clusters in PPA and RSC of both stimuli overlap}
-% conclusion
-\todo[inline]{concluding statement??}
-
+% not random shit
+Thus, our approach to operationalize spatial perception based on stimulus
+annotations did not lead to significant clusters scattered across the brain but
+restricted to a brain network that is assumed/known to be involved in (visual)
+spatial perception and cognition.
+%
 This suggest that model-driven methods based on stimulus annotations are
@@
 Nevertheless, ``cleanliness''/``neatness``  of results (i.e. the signal-cluster
-to noise-cluster ration) depend on the extent to which the multi-dimensionality
-of the naturalistic stimulus is annotated, modeled, statistically controlled and
-/ or how many events the stimulus provides per assumed perceptual process for
-the averaging purpose
-
-\section{summary}
-
-\todo[inline]{join summary \& conclusion}
-
-% summary
-In summary, our approach to operationalize spatial perception based on stimulus
-annotations of two naturalistic stimuli is the shit and provide further evidence
-that model-driven analyses can be used to analyze data from multi-dimensional
-stimuli
-%
-and before I forget: this study shows that already existing, publicly
-available data can be re-used for independent research questions that provide
-further evidence for existing theories/hypotheses and advance the field by
-generating new findings \& hypothesis.\todo{if there are any parts that can be
-rephrased as explicit hypothesis: do it!}
-
-\section{conlusion}
+to noise-cluster ration)\todo{if you know what I mean} depends on how many
+events correlating with an assumed perceptual process the stimulus provides
+and to the extent to which a naturalistic stimulus' multi-dimensionality is
+annotated and statistically controlled.
+
+\section{conclusion}
 
@@
 
-% \citep{hanke2014audiomovie}: the AD stimulus leaves a much larger margin for
-% inter-individual differences in imagining scenery. The AD stimulus limits the
-% effect of an attentional focus on the selection of a subset of simultaneously
-% occurring auditory events, in contrast to the selection of different parts of
-% the visual field.
+this study shows that already existing, publicly
+available data can be re-used for independent research questions that provide
+further evidence for existing theories/hypotheses and advance the field by
+generating new findings \& hypothesis.
 
 \subsection*{Code availability}
-% wo kommt dieser Abschnitt hin?  how to write Code availability statement
-% https://www.springernature.com/gp/authors/research-data-policy/data-availability-statements/12330880
-\todo[inline]{provide supporting source code, and explaining how and where
-others may access all data underlying the analysis} \emph{for all studies using
-    custom code in the generation or processing of datasets, a statement must be
-    included here, indicating whether and how the code can be accessed,
-including any restrictions to access; include information on the versions of any
-software used, if relevant, and any specific variables or parameters used to
-generate, test, or process the current dataset. }
+
+\todo[inline]{provide supporting source code; explain how/where other may
+access data underlying the analysis}
+
+\todo[inline]{if using custom code for dataset generation/processing: indicate
+how code can be accessed (including restrictions to access)}
+
+\todo[inline]{include infos on versions of used software}
+
+\todo[inline]{any specific variables or parameters used to generate, test, or process the current dataset?}
 
 \section*{Acknowledgements}
-% Text acknowledging non-author contributors.
-Acknowledgements should be brief, and should not include thanks to anonymous referees and editors, or effusive comments.
-Grant or contribution numbers may be acknowledged.
-% Author contributions Please describe briefly the contributions of each author to this work on a separate line.
-\emph{COH did this and that.
-MH did this and that.
-We are grateful to \href{www.florianschurz.de}{Florian Schurz} who initiated doing the annotation of the descriptive nouns, and performed the preliminary annotation of nouns.}
+
+\todo[inline]{everything correct?}
+\todo[inline]{Grant or contribution numbers may be acknowledged}
+%
+COH designed and performed the analyses, and wrote the manuscript.
+%
+MH provided critical feedback on the procedure and edited the manuscript.
+%
+SE provided critical feedback.
+%
+We are grateful to \href{www.florianschurz.de}{Florian Schurz} who initiated the
+annotation of nouns and created its preliminary version.%
 
 \section*{Competing financial interests}
-\emph{A competing financial interests statement is required for all accepted
-papers published in \emph{Scientific Data}. If none exist simply write,
-``The author(s) declare no competing financial interests''.}
+The authors declare no competing financial interests.
 
 \section*{Figures Legends}
-\emph{Figure should be referred to using a consistent numbering scheme through
-the entire Data Descriptor. For initial submissions, authors may choose
-to supply this document as a single PDF with embedded figures, but
-separate figure image files must be provided for revisions and accepted
-manuscripts. In most cases, a Data Descriptor should not contain more
-than three figures, but more may be allowed when needed. We discourage
-the inclusion of figures in the Supplementary Information \textendash{}
-all key figures should be included here in the main Figure section.}
-
-\emph{Figure legends begin with a brief title sentence for the whole figure
-and continue with a short description of what is shown in each panel,
-as well as explaining any symbols used. Legend must total no more
+
+\todo{Figures \& Tables have their own section, the editor puts them where he
+wants them?}
+
+\emph{We discourage the inclusion of figures in the
+Supplementary Information \textendash{} all key figures should be included here
+in the main Figure section.}
+
+\emph{Figure legend must total no more
 than 350 words, and may contain literature references.}
@@
 
-\emph{Tables supporting the Data Descriptor. These can provide summary information
-(sample numbers, demographics, etc.), but they should generally not
-be used to present primary data (i.e. measurements). Tables containing
-primary data should be submitted to an appropriate data repository.}
-
-\emph{Tables may be provided within the \LaTeX{} document or as separate
-files (tab-delimited text or Excel files). Legends, where needed,
-should be included here. Generally, a Data Descriptor should have
-fewer than ten Tables, but more may be allowed when needed. Tables
-may be of any size, but only Tables which fit onto a single printed
-page will be included in the PDF version of the article (up to a maximum
-of three).}
+\emph{tables provide summary information but should not be used to present
+primary data (i.e. measurements).}
 
@@
 
+\todo[inline]{clean the PPA dataset; upload as zip to zalando again?}
+
 Bibliographic information for the data records described in the manuscript.
@@
 
-\todo[inline]{I think it makes sense to report results of AV and discuss AV,
-and then report results of AD and discuss AD}
-
 \subsection{Results}
@@
 
-\todo[inline]{SE: overlap of clusters/contrasts: Anzahl der Überlappungen ist
-schwer abzulesen; lieber eine andere Farbskala (spectral sequence?) nutzen; COH:
-this figure is my end game boss}
+\todo[inline]{SE: use different colormap for overlap of contrasts' clusters}
 
@@
 % non-systematic
-Lastly, some contrasts of the AD stimulus yielded signficant clusters in regions
-that were not statistically signficant in three or more contrasts.
-%
-Contrast 2 yielded clusters in the anterior cingulate gyrus
-(bilateral), right frontal pole, right frontal medial cortex, and right
-putamen.
+Lastly, some contrasts of the AD stimulus yielded significant clusters in
+regions that were not statistically significant in three or more contrasts.
+%
+Contrast 2 yielded clusters in the anterior cingulate gyrus (bilateral), right
+frontal pole, right frontal medial cortex, and right putamen.
 %
@@
 In the analysis of the AV data, none of the four contrasts that compared the
-\texttt{no\_cut} categorie to a movie cut category (see Table
+\texttt{no\_cut} category to a movie cut category (see Table
 \ref{tab:av-contrasts}) yielded significant clusters.
@@
 
-\todo[inline]{SE: Bei Ergebnissen \& Diskussionen zu Stability fehlt mir
-irgendwie immer der Kontext, wie sich die Kontraste denn unterschieden haben und
-welche davon z.B. im Ergebnis wo von den anderen abgewichen haben. Das würde ja
-wichtige Hinweise geben}
+\todo[inline]{SE: wie unterscheiden sich die Kontraste?}
+\todo[inline]{Wo sind welche Kontraste (z.B. im Ergebnis) von anderen abgewichen?}
 
@@
 
-\todo[inline]{same part as in the main text but with number of contrasts}
 % intro
@@
 regions (see \citep{chrastil2018heterogeneity, bettencourt2013role} for
-reviews).
+reviews).\todo{same part as in the main text but with number of contrasts}
 
@@
 in single contrasts or even systematically across contrasts that hamper the
-interpretation of results.\todo{ouff\dots}
+interpretation of results.
 % AV: null results regarding attention and eye movements
@@
 not averaged out across trials and nuisance regressors did not capture enough
-variance.\todo{ouf\dots}
+variance.
 % possible reason
@@
 
+\todo[inline]{why did I build contrasts of the no\_cut condition compared
+to the movie cuts categories????}
+
+\todo[inline]{discussion \& concluding statement}
+
 The four control contrasts of the AV stimulus that compared the
 \texttt{no\_cuts} to categories of movie cuts all lead to null results.
-
-\todo[inline]{hm, so why did I build contrasts of the no\_cut condition compared
-to the movie cuts categories????}
-
-\todo[inline]{discussion \& concluding statement}
 
@@
 
-\todo[inline]{changes of a soundscape that indicate a setting's spatial layout
-    could correlate with increased activity in the PPA (arnott2008crinkling
-    finds increased activations in PPA to sounds made by objects that reveal
-    object's material/identity); but: when looking at the data I see no
-systematic in the results that let me assume that}
-
 \end{document}

### 2021-02-15 paper/main.tex
intro: honing & typos

@@
 % dorsal vs ventral pathway
-a dorsal stream (the ``where pathway'') that leads into the parietal lob , and a
+a dorsal stream (the ``where pathway'') that leads into the parietal lobe, and a
 ventral stream (the ``what pathway'') that leads into into the temporal lobe
@@
 regions of the fusiform gyrus and anterior lingual gyrus
-\citep{epstein2008parahippocampal}:
+\citep{epstein2008parahippocampal}.
 % neural correlate of scene perception
-increased hemodynamic activity is observed in the PPA when subjects view
+Increased hemodynamic activity is observed in the PPA when subjects view
 pictures of landscapes, buildings or landmarks (compared to e.g. pictures of
-tools or faces) during blood oxygenation level-dependent functional magnetic
+faces or tools) during blood oxygenation level-dependent functional magnetic
 resonance imaging (BOLD fMRI) \citep{aguirre1998area, epstein2014neural,
@@
 In a study conducted by \cite{ocraven2000mental} participants viewed alternating
-blocks of pictures showing famous faces and familiar places during an initial
+blocks of pictures showing familiar places and famous faces during an initial
 experimental paradigm.
@@
 match-to-sample task of haptically explored scenes constructed from LEGO bricks
-compared to haptically explored abstract geometric objects.
+compared to abstract geometric objects.
 % Wolbers: connectivity analysis
@@
 an inaccurate or improbable fact (e.g. ``Marilyn Monroe has a large square
-jaw'')
+jaw'').
 % Aziz' results:
@@
 % paradigm.
-Lastly, the reviewed studies averaged results across 7-11 subjects.
+Third, the reviewed studies averaged results across 7-11 subjects.
 % averaging pros and cons
@@
 In this study, we investigate if increased hemodynamic activity in the PPA that
-is usually revealed by contrasting blocks of pictures can also be revealed by
-contrasting selected stimulus features that incidentally occur under more
-ecologically conditions.
+is usually revealed by contrasting blocks of pictures can also be revealed under
+more ecologically conditions.
 % we use 2 naturalistic stimuli
@@
 We then created several general linear model (GLM) contrast to analyze the
-corresponding publicly available fMRI datasets
-(\href{http://www.studyforrest.org}{studyforrest.org}) of each naturalistic
-stimulus \citep{hanke2016simultaneous, hanke2014audiomovie}.
+corresponding publicly available fMRI datasets of each naturalistic stimulus
+\citep{hanke2016simultaneous, hanke2014audiomovie}
+(\href{http://www.studyforrest.org}{studyforrest.org}).
 
@@
 % hypo b: individuals
-Further, we hypothesized that an exclusively auditory stimulus could localize
+Further, we hypothesized that an exclusively auditory stimulus could localize a
 ``visual area'' in individual subjects.
@@
 during two naturalistic stimuli lead to increased hemodynamic activity in the
-PPA functionally defined by the visual localizer.
+PPA.
 % anterior vs. posterior

### 2021-02-15 paper/main.tex
methods: honing & typos (v1)

@@
     \item main text: add references to supplemental material
+    \item imo AD and AV can be written as movie and audio-description
+    \item [text in brackets] can probably be deleted
 \end{itemize}
@@
 % AD
-a) listening to the audio-description (AD study; \citep{hanke2014audiomovie}) of
+a) listening to the audio-description \citep{hanke2014audiomovie} of
 the movie ``Forrest Gump'',
 % AV
-b) watching the original movie (AV study; \citep{hanke2016simultaneous}), and
+b) watching the audio-visual movie \citep{hanke2016simultaneous}, and
 % VIS
-c) participating in a dedicated six-category block-design visual localizer (VIS
-study; \citep{sengupta2016extension}).
+c) participating in a dedicated six-category block-design visual localizer (VIS; \citep{sengupta2016extension}).
 % see corresponding papers for details
@@
 % AD & AV stimulus name & references
-We used the German DVD release \citep{ForrestGumpDVD} of the audio-visual movie
-``Forrest Gump'' \citep{ForrestGumpMovie} and its audio-description that was
-broadcast as an additional audio track for visually impaired listeners on Swiss
-public television \citep{ForrestGumpGermanAD}.
+We used the German DVD release \citep{ForrestGumpDVD} of the movie ``Forrest
+Gump'' \citep{ForrestGumpMovie} and its audio-description that was broadcast as
+an additional audio track for visually impaired listeners on Swiss public
+television \citep{ForrestGumpGermanAD}.
 % AV: voice-over
@@
 Before the experiment, participants were instructed to inhibit physical
-movements except for eye-movements, and otherwise to simply ``enjoy''.
+movements except for eye-movements, and otherwise to simply ``enjoy'' the
+stimulus.
 % AD & AV: presentation & instructions
@@
 % controlled luminance and size
-Images were matched in luminance and size of 400$\times$\unit[400]{px}
+Images were matched in luminance and size of 400$\times$\unit[400]{px}.
 % procedure: presentation & instructions
@@
 % traditionally
-Traditionally, researchers specifically design stimuli that presumably would
-trigger the perceptual process of interest while also controlling confounding
-variables (e.g. color, luminance).
+Traditionally, researchers design stimuli that presumably would trigger the
+perceptual process of interest while also controlling confounding variables
+(e.g. color, luminance).
 % our approach: annotation and regressors
@@
 % annotation ftw
-Hence, we annotated the temporal structure of a various stimulus features that
-later served as a basis (for GLM regressors) to model hemodynamic responses.
+Hence, we annotated the temporal structure of various stimulus features that
+later served as basis [for GLM regressors] to model hemodynamic responses.
 
@@
 Our rationale was that cuts are ``spatially relevant'' events that re-orient the
-viewer within the environment of the movie by either changing the perspective
-within a setting or switching to another setting.
+viewer within the environment of the movie by either switching to another
+setting or switching the perspective within the same setting.
 % AV regressors/events
@@
 2) a cut switching to a setting that was already depicted earlier in the movie
-(\texttt{vse\_old}; e.g. a cut to the recurring waiting bench at the bus stop),
+(\texttt{vse\_old}),
 %
@@
 %
-4) a cut to another camera position within a setting or locale (e.g. room) that
-was depicted for the first time (\texttt{vpe\_new}), and
+4) a cut to another camera position within a setting or locale that was depicted
+for the first time (\texttt{vpe\_new}), and
 %
@@
 content and thus without controlling confounding variables.
-% AV COPEs: intro
-The rationale that this approach would yield categories that - on average - show
-different stimulus features.
+% assumption
+We assumed that different categories would - on average - depict different
+stimulus features.
 % cinematographic rationale cut to new scenes: establishing shots
 The cinematographic rationale was that movie shots tend to establish the setting
-(\texttt{vse\_new}) and the spatial relationships within a setting
-(\texttt{vpe\_new}) at the beginning of a movie.
+(\texttt{vse\_new}) and the spatial layout within a setting (\texttt{vpe\_new})
+at the beginning of a movie.
 % cut to recurrent scene
 Later in the movie, the field sizes of movie shots tend to decrease when
-switching back to already established settings (\texttt{vse\_old}).
+switching back to an already established settings (\texttt{vse\_old}).
 % similarly for shots within a scene
-Later in the movie when the spatial layout of a setting is already established,
-shots within a setting shift to objects more relevant to the evolved plot and or
-to switching between faces of persons talking to each others (\texttt{vpe\_old})
-\citep{brown2012cinematography, mercado2011filmmakers}.
-% neuroscientific rationale
-The neuroscientific rationale was that activity in the PPA is greater when
-participants view novel versus repeated scenes or view-points
-\citep{epstein1999parahippocampal, grill2006repetition}.
-%
-\todo{drop last sentence \& better focus on cinematographic rationale; activity
-in e.g. FFA adopts too -> we might subtract an on average smaller response}
-% no cut condition: intro
+When the spatial layout within a setting is already established, shots tend to
+more often depict (faces of) persons talking to each others or objects more
+relevant to the evolved plot (\texttt{vpe\_old}) \citep{brown2012cinematography,
+mercado2011filmmakers}.
+% neuroscientific rationale The neuroscientific rationale was that activity in
+% the PPA is greater when participants view novel versus repeated scenes or
+% view-points \citep{epstein1999parahippocampal, grill2006repetition}.  no cut
+% condition: intro
 In order to create a control condition, a sixth category (\texttt{no\_cut}) was
@@
 For the analysis of the AD stimulus, we extended a publicly available annotation
-of speech \citep{haeusler2020speechanno} by further annotating words spoken by
+of speech \citep{hausler2021studyforrest} by further annotating words spoken by
 the audio-description's narrator.

### 2021-02-15 paper/main.tex
methods: honing & typos (v2)

@@
     Respective event counts are given for the whole stimulus (\texttt{all} and
-    the segments that were used for the eight sessions of fMRI scanning.
+    the segments that were used for the eight sessions of fMRI scanning).
     %\texttt{fg\_av\_ger\_pd} (perceptual differences of consecutive frames),
@@
 disco'', ``[the platoon wades through a] rice field''). They also comprise words
-that could count as a member of another categories in case the narrator uses
+that could count as a member of another category in case the narrator uses
 these words to indicate a switch from one setting to another (e.g. ``[a]
@@
 \begin{table*}[h!]
-    \caption{Categories and rules to categorize the descriptive nouns spoken by
+    \caption{Categories and rules to categorize the nouns spoken by
         the audio-description's narrator.
@@
         Some of these initial 18 noun categories were pooled resulting in 11
-        event categories that served as a basis to build the regressors of the
+        event categories that served as basis to build the regressors of the
         GLM
@@
 \tabularnewline
-bodypart & limbs and trousers & arm, finger, leg, toe
+bodypart & limbs & arm, finger, leg, toe
 \tabularnewline
@@
 \tabularnewline
-furniture & movable furniture insides \& outsides & bench, bed, table, chair
+    furniture & movable furniture (insides \& outsides) & bench, bed, table,
+    chair
 \tabularnewline
@@
 \tabularnewline
-head & non-face parts of the head; worn headgear & head, hair, ear, neck,
+head & non-face parts of the head; worn headgear & head, hair, ear, neck;
 helmet
@@
     see Table\ref{tab:descr-nouns-rules}) were pooled
-    into 11 new categories (\texttt{sex\_f}; \texttt{sex\_m}; \texttt{fahead};
-    \texttt{object}), \texttt{fg\_ad\_lrdiff} (left-right volume difference)
-    and \texttt{fg\_ad\_rms} (root mean square volume) represent one event for
-    every movie frame (\unit[40]{ms}).
+    into 11 new categories (\texttt{sex\_f}; \texttt{sex\_m}; \texttt{fahead},
+    \texttt{object}).
     % For a description of the five control conditions for movie cuts see
@@
 \midrule
-body & trunk of the body or overlaid clothes & \aoBodyAll & \aoBodyI & \aoBodyII
+body & trunk of the body; overlaid clothes & \aoBodyAll & \aoBodyI & \aoBodyII
 & \aoBodyIII & \aoBodyIV & \aoBodyV & \aoBodyVI & \aoBodyVII & \aoBodyVIII
@@
 \tabularnewline
-furn & moveable furniture insides \& outsides & \aoFurnAll & \aoFurnI & \aoFurnII & \aoFurnIII & \aoFurnIV & \aoFurnV & \aoFurnVI & \aoFurnVII & \aoFurnVIII
+furn & moveable furniture (insides \& outsides) & \aoFurnAll & \aoFurnI & \aoFurnII & \aoFurnIII & \aoFurnIV & \aoFurnV & \aoFurnVI & \aoFurnVII & \aoFurnVIII
 \tabularnewline
@@
 \tabularnewline
-object & inanimate entities with firm boundaries & \aoObjAll & \aoObjI & \aoObjII & \aoObjIII & \aoObjIV & \aoObjV & \aoObjVI & \aoObjVII & \aoObjVIII
-\tabularnewline
-se\_new & noun describing an unfamiliar setting & \aoSenewAll & \aoSenewI & \aoSenewII & \aoSenewIII & \aoSenewIV & \aoSenewV & \aoSenewVI & \aoSenewVII & \aoSenewVIII
-\tabularnewline
-se\_old & noun describing a recurring setting & \aoSeoldAll & \aoSeoldI & \aoSeoldII & \aoSeoldIII & \aoSeoldIV & \aoSeoldV & \aoSeoldVI & \aoSeoldVII & \aoSeoldVIII
+object & countable entities with firm boundaries & \aoObjAll & \aoObjI & \aoObjII & \aoObjIII & \aoObjIV & \aoObjV & \aoObjVI & \aoObjVII & \aoObjVIII
+\tabularnewline
+se\_new & a setting occurring for the first time & \aoSenewAll & \aoSenewI & \aoSenewII & \aoSenewIII & \aoSenewIV & \aoSenewV & \aoSenewVI & \aoSenewVII & \aoSenewVIII
+\tabularnewline
+se\_old & a recurring setting & \aoSeoldAll & \aoSeoldI & \aoSeoldII & \aoSeoldIII & \aoSeoldIV & \aoSeoldV & \aoSeoldVI & \aoSeoldVII & \aoSeoldVIII
 \tabularnewline
@@
 % auditory shit
-Finally, we computed the left-right difference in volume and root mean square
-energy averaged across the length of every movie frame (\unit[40]{ms}) of both
-audio-tracks.
+Finally for both audio tracks, we computed the left-right difference in volume
+and root mean square energy averaged across the length of every movie frame
+(\unit[40]{ms}).
 
@@
 % no surprise
-This was expected and served as a ``sanity check'' since the audio-track of the
-audio-description is the audio-track of the movie but featuring the additional
+This was expected and served as a ``sanity check'' since the audio track of the
+audio-description is the audio track of the movie but featuring the additional
 narrator (s. Figure \ref{fig:reg-corr}).

### 2021-02-15 paper/main.tex
methods: honing & typos (v3)

@@
 Nouns were modeled from onset to offset of each word, low-level confounds from
-onset to offset of the corresponding movie frame AO:
-% modeling as boxcar function
-Events were were modeled as boxcar function from onset to offset of each word.
+onset to offset of the corresponding movie frame
 % convolving
@@
 gamma hemodynamic response function (HRF).
+
 % we checked correlations
-Since we annotated events in naturalistic stimuli and thus fixed time courses
-that could not experimentally manipulated, the modeled time-series [of
-hemodynamic activity] based on these events could be correlated leading to
-shared variance and thus low detection power of subsequent analyses.
+Since we annotated events in fixed time courses, the modeled hemodynamic
+time-series could be correlated leading to shared variance and thus low
+detection power of subsequent analyses.
 % correlations within stimuli and across stimuli
@@
 % AV design matrix
-For the subsequent first level GLM analysis, the modeled hemodynamic responses
-related to all movie cuts (including \texttt{no\_cut}) and six low-level
-perceptual confounds (s. Table \ref{tab:av-events}) were included as regressors
-in the design matrix.
+For the subsequent first level GLM analysis of the AV stimulus, the modeled
+hemodynamic responses related to all movie cuts (including \texttt{no\_cut}) and
+six low-level perceptual confounds were included as regressors in the design
+matrix.
 % AD regressors in AV AD design matrix
@@
 responses related to all noun categories and the two low-level perceptual
-confounds were included (s. Table \ref{tab:ao-events}).
+confounds were included.
 % AD regressors in AV
@@
 To create contrasts of cross-modal negative control in the analysis of the AD
-stimulus [and to capture variance of a possibly confounding change of the
-soundscape after a cut], we implemented the movie cut-related regressors
+stimulus, we also implemented the movie cut-related regressors
 (excluding \texttt{no\_cut}).
@@
 % motion parameters
-Six motion parameters were also used as additional nuisance regressors.
+Six motion parameters were also included.
 % high-pass filtering
@@
 conducting standard two-level general linear model (GLM) analyses to create
-subject-specific results ($Z$-maps) across the 8 segments for every subject and
-each stimulus.
+subject-specific results across the 8 segments for every subject and each
+stimulus.
 % level 3
@@
 \ref{tab:av-contrasts}) and eight $t$-contrasts for the AD stimulus (see Table
-\ref{tab:ao-contrasts})
+\ref{tab:ao-contrasts}).
 % reason: robustness
@@
 % why
-We assumed that category \texttt{vse\_new} on average comprised the most movie
-frames depicting a landscape or the geometry of a setting, and the category
-\texttt{vpe\_old} the most frames depicting persons, faces, or objects [(cf.
-rationale to categorize the cuts in section \ref{rationale})].
+We assumed that the category \texttt{vse\_new} on average comprised the most
+movie frames depicting a landscape or the geometry of a setting, and the
+category \texttt{vpe\_old} the most frames depicting persons, faces, or objects
+[(cf.  rationale to categorize the cuts in section \ref{rationale})].
 % AD: primary contrast
-In the primary contrast of the AD stimulus, we contrasted landmarks
-\texttt{geo}, and rooms and geometry-defining objects \texttt{geo-room} with not
-just nouns referring to a person's head or face (\texttt{fahead}, N=83; e.g.
-``eyes'', ``face'', or ``head'') but also all non-geometry related categories
-(\texttt{body}, \texttt{bodypart}, \texttt{fahead}, \texttt{object},
-\texttt{sex\_f}, \texttt{sex\_m}) except \texttt{furniture} to get more events
-per stimulus segment.
+In the primary contrast of the AD stimulus, we contrasted buildings and
+landmarks (\texttt{geo}), and rooms and geometry-defining objects
+(\texttt{geo-room}) with not just nouns referring to a person's head or face
+(\texttt{fahead}, N=83; e.g.  ``eyes'', ``face'', or ``head'') but also all
+non-geometry related categories (\texttt{body}, \texttt{bodypart},
+\texttt{fahead}, \texttt{object}, \texttt{sex\_f}, \texttt{sex\_m}) except
+\texttt{furniture} to get more events per stimulus segment.\todo{ouff}
 % why furniture was not used
@@
 % heterogeneous category
-a) categories comprise words that could count as a member of another category
-(e.g. ``[a] physician''),
+a) categories comprise nouns that could count as a member of another category
+(e.g. ``[a] physician''; section \ref{rationale}), and
 % richness of verbal description vs. picture
-b) nouns only vaguely described a scene (e.g. ``[in] Greenbow'', ``[in a]
+b) nouns that only vaguely describe a scene (e.g. ``[in] Greenbow'', ``[in a]
 disco'', ''[black and white] film recordings'') [compared to whole, perceptually
-richer pictures], and
-% c) the narrator is often lacking behind a short dialogue or a change of the
-% soundscape that might already indicate a change of settings.
-%
+richer pictures].
+% and c) the narrator is often lacking behind a short dialogue or a change of
+% the soundscape that might already indicate a change of settings.
+
 % control contrasts
-Finally, we created several contrasts as negative control for both stimuli.
+Finally, we created several $t$-contrasts as negative controls for both stimuli
+(see Tables \ref{tab:av-contrasts} and \ref{tab:ao-contrasts}).
 % AV: no cut > cut
-For the AV stimulus, four $t$-contrasts were created contrasting the no-cut
+For the AV stimulus, four contrasts were created contrasting the no-cut
 regressor (\texttt{vno\_cut} to cut-related regressors \ref{tab:av-contrasts}).
@@
 \ref{tab:ao-contrasts}) to test if increased activation in the PPA was
-correlated with moments of cuts as cuts might possibly be correlated with a
-change of the soundscape also giving an auditory hint of switching to another
-setting.
+correlated with moments of cuts.
+
 % difference to Sengupta; Berman et al. (2010). Evaluating functional localizers
 % (2010)
-In the VIS study \citep{sengupta2016extension} using the established approach of
-contrasting blocks of pictures, assessment of individual PPAs was based on
-chosing post-hoc one from a set of three contrasts (\textit{strict},
-\textit{relaxed}, and \textit{simple} contrast \citep{sengupta2016extension};
-cf. Table 3 in \citep{sengupta2016extension}).
+In the VIS study using the established approach of contrasting blocks of
+pictures, a set of three contrasts (\textit{strict}, \textit{relaxed}, and
+\textit{simple} was created contrast (cf. \citep{sengupta2016extension}).
 
@@
 \caption{Contrasts of parameter estimates for the analysis of the
-    audio-visual movie (AV).
+    audio-visual movie.
     Contrast 1-5 aim to isolate the PPA.
     Contrast 6-9 serve as negative control.
-    Contrast 10 serves as control for moments when the narrator indicates the
-    a switch of settings, events that could be correlated with a
-    change of the soundscape.}
+    Contrast 10 serves as control for moments when the narrator indicates
+    a switch of settings.}
 \label{tab:av-contrasts}
@@
 \caption{Contrasts of parameter estimates for the analysis of the audio-only
-    stimulus (AD).
+    stimulus.
     Contrast 1-8 aim to isolate the PPA.
@@
 a) via linear transformation to a subject-specific, study-specific T2* template
-(cf. \citep{sengupta2016extension}) and,
+(cf. \citep{sengupta2016extension}), and
 % group template (for group and individual brain slices)
@@
 (Gaussianised T/F) statistic images were thresholded using clusters determined
-by Z>3.4 and a (corrected) cluster significance threshold of p=.05
+by Z>3.4 and a cluster-corrected significance threshold of p=.05
 \citep{worsley2001statistical}.
@@
 % PPA masks
-PPA region of interest (ROI) masks for individual subjects and a PPA group mask
-of individual PPA overlaps were created from data provided by
+Regions of interest (ROI) masks for individual PPAs and a PPA group mask of
+individual PPA overlaps were created from data provided by
 \citep{sengupta2016extension}.
@@
 
-% Sengupta et al., 2016
+% Sengupta et al., 2016; unilateral in sub-04 and sub-20
 The visual localizer \citep{sengupta2016extension} yielded bilateral
 parahippocampal clusters in 12 of 14 subjects and an unilateral right clusters
-in two subjects (sub-04, sub-20).
+in two subjects (cf. Table 3 in \citep{sengupta2016extension}).
 % Sengupta: 1 of 3
 Individual PPAs were assessed by visually inspecting unthresholded $t$-maps
-(Z>1.64, p<.05 cluster corrected)  of three different $t$-contrasts
-(\textit{strict}, \textit{relaxed}, and \textit{simple} stimulus set cf.
-\citep{sengupta2016extension}), and titrating [?] the $t$-threshold in the range
-of [2, 3] in until we found an isolated cluster that matched the expected
+(Z>1.64, p<.05 cluster corrected) of three different $t$-contrasts, and titrating [?] the $t$-threshold in the range
+of [2, 3] in until we found an isolated cluster (cf. Table 3 in  that matched the expected
 anatomical location based on literature \citep{epstein1998ppa}.

### 2021-02-15 paper/main.tex
methods: honing & typos (v4)

@@
 \begin{itemize}
-    \item main text: add references to supplemental material
+    \item [text in brackets] can probably be deleted
     \item imo AD and AV can be written as movie and audio-description
-    \item [text in brackets] can probably be deleted
 \end{itemize}
@@
 \begin{itemize}
-    \item check if captions of figs and tables now (really) match phrasing
-        in intro / method
+    \item tables: round p-values to ?
 \end{itemize}
@@
     \includegraphics[width=\linewidth]{figures/regressor-corr} \caption{Pearson
-        correlation coefficients of the regressors used in the analysis of the
+        correlation coefficients of modeled time series used as regressors in
+        the GLM analysis of the
         audio-description (blue; see Table \ref{tab:ao-events} for a
-        description) and audio-visual movie (red; see Table \ref{tab:av-events})
-        rounded to the nearest tenth.
+        description) and audio-visual movie (red; see Table
+        \ref{tab:av-events}).
+        Values are rounded to the nearest tenth.
         The correlation between the two stimuli's
-        root mean square loudness and between their left-right difference in
-        loudness yielded the highest correlation values
+        root mean square volume and between their left-right difference in
+        volume yielded the highest correlation values
         (\texttt{fg\_ad\_rms} and \texttt{fg\_av\_ger\_rms}, r=.7635;
@@
 We investigated if spatial information embedded in two naturalistic stimuli
-correlate with increased hemodynamic activity in the PPA.
+correlates with increased hemodynamic activity in the PPA.
 % group level
@@
 \href{https://neurovault.org/collections/KADGMGVZ/}{NeuroVault}.
+% reference to supplemental material
+Results and discussion of the additional contrasts (PPA and negative controls)
+can be found in the supplemental material
 
@@
 % precuneus
-Two additional clusters are apparent in the ventral precuneus extending into the
-retrosplenial cortex.
+Two additional homologous clusters are apparent in the ventral precuneus
+extending into the retrosplenial cortex.
 % LOC
@@
         head template (gray).
-        Light gray: The audio-description's field-of-view
+        Light gray: The audio-description's field of view
         (cf. \citep{hanke2014audiomovie}).
@@
         are overlaid over the movie's primary $t$-contrast (blue) that compares
-        cuts to a new setting with cuts to a familiar perspective
+        cuts to a setting depicted for the first time with cuts within a
+        recurring setting
         (\texttt{vse\_new > vpe\_old}).
@@
     of the primary $t$-contrast for the audio-visual movie comparing cuts to a
-    setting that was not depicted before to a recurring setting
+    setting depicted for the first time with cuts within a recurring setting
     (\texttt{vse\_new > vpe\_old}).
@@
 localizer experiment.
-
 % Sengupta et al., 2016; unilateral in sub-04 and sub-20
-The visual localizer \citep{sengupta2016extension} yielded bilateral
-parahippocampal clusters in 12 of 14 subjects and an unilateral right clusters
-in two subjects (cf. Table 3 in \citep{sengupta2016extension}).
+The visual localizer yielded bilateral parahippocampal clusters in 12 of 14
+subjects and an unilateral right clusters in two subjects (cf. Table 3 in
+\citep{sengupta2016extension}).
 % Sengupta: 1 of 3
-Individual PPAs were assessed by visually inspecting unthresholded $t$-maps
-(Z>1.64, p<.05 cluster corrected) of three different $t$-contrasts, and titrating [?] the $t$-threshold in the range
-of [2, 3] in until we found an isolated cluster (cf. Table 3 in  that matched the expected
-anatomical location based on literature \citep{epstein1998ppa}.
-\todo{they used $t$-maps???}
+Individual PPAs were assessed by visually inspecting thresholded $t$-maps
+(Z>1.64, p<.05 cluster corrected) of three different $t$-contrasts, and
+titrating\todo{??} the $t$-threshold in the range of [2, 3] in until we found an
+isolated cluster (cf. Table 3 in that matched the expected anatomical location
+based on literature \citep{epstein1998ppa}.
+
 % one contrast to localize them all; "...and Z>3.4 for all"
 Contrary to \citep{sengupta2016extension}, we here used the same contrast of
-each naturalistic stimulus and the same threshold for all subjects (Z>2.3, p<.05
-cluster-corrected for the analysis in subject-space; Z>3.4, p<.05 for the
-analysis in group-space).
+each naturalistic stimulus and the same threshold for all subjects.
 % subject space -> NeuroVault
 Results of the analyses that were performed in subject-space can be found in the
-accompanying dataset.
+accompanying dataset (Z>2.3, p<.05 cluster-corrected).
 % here report in group space
 For better comparisons of subjects, we here report results from the analyses
-performed in group space.
+performed in group space (Z>3.4, p<.05 cluster-corrected).
 % ref to figure
@@
 and AD $t$-contrast, and the outline of overlapped, individual PPAs
-\citep{sengupta2016extension} co-registered to the MNI152 template.
+co-registered to the MNI152 template.
 % one slice to show them all
@@
         degrees of freedom).
-        The results of audio-description's primary
-        $t$-contrast (blue) that compares geometry-related nouns to non
-        geometry-related nouns spoken by the audio-description's narrator
+        The results of the audio-description's primary
+        $t$-contrast (blue) that compares geometry related nouns to non-
+        geometry related nouns spoken by the narrator
         (\texttt{geo, groom > all non-geo}) are overlaid over the movie's
-        primary $t$-contrast (blue) that compares cuts to new setting with cuts
-        to a familiar perspective (\texttt{vse\_new > vpe\_old}).
+        primary $t$-contrast (blue) that compares cuts to setting depicted for
+        the first time with cuts within a recurring setting
+        (\texttt{vse\_new > vpe\_old}).
         Black:
@@
         Light gray: The
-        audio-description's field-of-view (cf. \citep{hanke2014audiomovie}).
+        audio-description's field of view (cf. \citep{hanke2014audiomovie}).
         To facilitate comparisons across subjects, we chose the same horizontal
@@
         The figure does not show voxels of the left cluster of the AV stimulus
-        in sub-09 and sub-18, and voxels of right cluster of the AV stimulus in
-        sub-15.}
+        in sub-09 and sub-18, and voxels of the right cluster of the AV
+        stimulus in sub-15.}
     \label{fig:subs-thresh-ppa}
@@
 A shift of the distribution to voxels with a mean above zero can be seen the
-further we constrain voxels to the individual PPA (see KDE plot for the x-axes
-in Figure \ref{fig:bland-altman}).
+further we constrain voxels to the individual PPA (cf. KDE plot for the x-axes).
 % right KDE plot
@@
 the dedicated localizer, values below the horizontal line depict voxels that
-show higher $z$-value in the AD stimulus.
+show a higher $z$-value in the AD stimulus.
 
@@
     The overlays depict voxels spatially constrained to the
-    temporal and occipital cortex (gray; based on the probabilistic Jülich
+    temporal and occipital cortex (gray; based on probabilistic Jülich
     Histological Atlas \citep{eickhoff2005toolbox, eickhoff2007assignment}),

### 2021-02-15 paper/main.tex
results + PPA discussion: honing & typos

@@
 % group AV
-On a group level, whole brain-analysis results for the movie stimulus show
+On a group level, whole brain-analysis results for the audio-visual movie show
 significantly increased hemodynamic activity spatially overlapping with a
@@
 On an individual level, results of the audio-description show significant
-bilateral clusters in the anterior PPA of nine subjects and significant
-unilateral clusters in one subjects.
+bilateral clusters in the anterior PPA of nine subjects and a unilateral cluster
+in one subjects.
 % meaning: generalization to naturalistic stimuli
 Results suggest that increased activation in the PPA during the perception of
-static pictures generalizes to the perception of spatial information embedded in
+static pictures generalize to the perception of spatial information embedded in
 a movie and an exclusively auditory stimulus.
@@
 % narrative as substitute
-An auditory narrative might substitute a visual paradigm to localize
-the PPAs anterior part in visually impaired subjects.
-
-\subsection{PPA (group + individuals \& aPPA vs. pPPA)}
-
-% intro
-First, we analyzed data from the movie stimulus offering ecologically more valid
-but still visual stimulation.
+An auditory narrative might substitute a visual paradigm to localize the PPAs
+anterior part in visually impaired subjects.
+
+% PPA: intro
+First, we analyzed data from the movie offering ecologically more valid visual
+stimulation.
 %
@@
 %
-Contrary to \citep{bartels2004mapping} who annotated the content of frames, we
-categorized each frame after a cut independent of its specific content.
-\todo{Bartels' clusters are actually pretty big too}
+Contrary to \citep{bartels2004mapping} who annotated the content of movie
+frames, we categorized each frame after a cut independent of its specific
+content  \todo{Bartels' clusters are actually pretty big too}
 % exploited cinematographic tendencies
-We here exploited a cinematographic confound in the stimulus structure (cf.
+exploiting a cinematographic confound in the stimulus structure (cf. section
 \ref{rationale}):
@@
 film directors tend to establish the geometry of locations earlier in the movie
-and tend to later focus more on persons and objects relevant to the evolved
+and tend to later focus more on persons and objects relevant to the evolved plot
 \citep{brown2012cinematography, mercado2011filmmakers}.
@@
 Thus to control confounding variables, future studies that aim to use a movie to
-localize visual areas should extensively annotate the content of frames (e.g.
-using the open-source solution ``Pliers'' for feature extraction from a visual
-naturalistic stimulus; \citep{mcnamara2017developing}).
+localize visual areas in individual subjects should extensively annotate the
+content of frames (e.g.  using the open-source solution ``Pliers'' for feature
+extraction from a visual naturalistic stimulus; \citep{mcnamara2017developing}).
 % we took advantage of cinematography
 We here took advantage of an idiosyncrasy of movie directing to shift from
-establishing the geometry earlier in the movie to later depicting persons and
-objects more relevant to the evolved plot.
+depicting the spatial layout to to later depicting persons and objects.
 % know your stimulus
@@
 generalize to an ad hoc approach to operationalize the perception of spatial
-information at the moment of cuts in a audio-visual movie.
+information at the moment of cuts in an audio-visual movie.
 
@@
 % our results
-Group results of audio-description's primary contrast yielded spatially concise
-clusters in the anterior part of the PPA group overlap.
+Group results of the audio-description's primary contrast yielded significantly
+increased hemodynamic activity spatially restricted to the anterior part of the
+PPA group overlap.
 % concluding statement
@@
 Nevertheless, one early block-design study \citep{epstein1998ppa} compared
-results from a paradigm that employed a (perceptual) judgment task of static
+results from a paradigm that employed a perceptual judgment task of static
 pictures to the same paradigm but without that task.
@@
 % concluding statement: kinda automatic process
-Hence, current results from our paradigm also suggest that verbal spatial
-information is processed in the anterior PPA casually and does not [necessarily]
-rely on [deliberately] paying attention to verbal spatial information.
+Hence, current results also suggest that verbal spatial information is processed
+in the anterior PPA casually and does not [necessarily] rely on [deliberately]
+paying attention to verbal spatial information.
 
@@
 teenager``).
-% further studies
-Given that humans can identify the gist of a rich visual scene within the
-duration of a single fixation \citep{henderson2003human} further studies might
-investigate if vague verbal descriptions of landscapes lead to a different
-hemodynamic activity level than descriptions of more concrete parts of a scene
-(e.g.``[a] beacon'', [a] ``farmhouse'').
+% visual system => gist in milliseconds
+Humans can identify the gist of a rich visual scene within the duration of a
+single fixation \citep{henderson2003human}.
+%
+Hence, further studies might investigate if vague verbal descriptions of
+landscapes lead to a different hemodynamic activity level than descriptions of
+more concrete parts of a scene (e.g.``[a] beacon'', [a] ``farmhouse'').
 
@@
 Whereas \citep{sengupta2016extension} chose the subjectively ``best fitting''
-$t$-threshold in an unthresholded $t$-map from one of three contrasts by visual
-judgment, we used the same contrast and threshold (Z>3.4, p<.05
-cluster-corrected) for all subjects.
+$t$-threshold in $t$-map from one of three contrasts by visual judgment, we used
+the same contrast and threshold (Z>3.4, p<.05 cluster-corrected) for all
+subjects.
 % in the current study
@@
 Further, our exploratory analysis suggests that a naturalistic auditory stimulus
-can [in principle] be applied to localize (the anterior part) of an higher-level
+can [in principle] be applied to localize (the anterior part) of a higher-level
 visual area in the majority of subjects.
@@
 Contrary, the aPPA is more strongly functionally connected to portions of the
-default mode network, including caudal inferior parietal lobe (cIPL), the
+default mode network[, including caudal inferior parietal lobe (cIPL), the
 restrosplenial complex (RSC), medial PFC and the lateral surface of the anterior
-temporal lobe \citep{baldassano2013differential, baldassano2016two}.
+temporal lobe] \citep{baldassano2013differential, baldassano2016two}.
 % conclusion: subregions
-According to the hypothesis by \citep{baldassano2013differential} the PPA
-consists of subregions that process specific apsects of a visual scene and
-cooperate to build a complete scene representation.
+According to a hypothesis by \citep{baldassano2013differential} the PPA consists
+of subregions that process different aspects of a visual scene and cooperate to
+build a complete scene representation.
 % Their distinct connectivity properties do suggest that each may be involved in
@@
 % responses require spatial memory and cannot be based purely on visual features
-% like object shape. \citep{baldassano2013differential}.
-Our results add further evidence that the PPA is not a homogeneous area but can
-be divided into functionally subregions.
-% pPPA
-Our results suggest that the pPPA is more concerned with visual aspects immanent
-in pictures or movie shots of landscapes.
+% like object shape. \citep{baldassano2013differential}.  pPPA
+Similarly, our results suggest that the pPPA is more concerned with visual
+aspects immanent in pictures or movie shots of landscapes.
 % aPPA
@@
 (e.g. spatial contextual information \citep{aminoff2013role,
-aminoff2015associative, baumann2016functional}) as inherent in both visual and
+aminoff2015associative, baumann2016functional}) as immanent in both visual and
 verbal stimuli.
 
-\subsection{RSC \& LOC; naturalistic stimuli}
-
-% intro
+% RSC + LOC
 Apart from the PPA, we find significantly increased activity in the dorsal

### 2021-02-15 paper/main.tex
cleaning before printing

@@
 % RSC + LOC
-Apart from the PPA, we find significantly increased activity in the dorsal
-precuneus and posterior cingulate region (e.g. retrosplenial complex; RSC) and
-lateral occipital cortex (LOC; more lateral in the AV stimulus, more medial in
-the AD stimulus) across contrasts of both naturalistic stimuli.
+Apart from the PPA, results revealed significantly increased activity in the
+dorsal precuneus and posterior cingulate region (e.g. retrosplenial complex;
+RSC) and lateral occipital cortex (LOC; more lateral in the AV stimulus, more
+medial in the AD stimulus) across contrasts of both naturalistic stimuli.
 % RSC intro
@@
 to noise-cluster ration)\todo{if you know what I mean} depends on how many
-events correlating with an assumed perceptual process the stimulus provides
-and to the extent to which a naturalistic stimulus' multi-dimensionality is
+events correlating with an assumed perceptual process the stimulus provides and
+to the extent to which a naturalistic stimulus' multi-dimensionality is
 annotated and statistically controlled.
@@
 dynamic environment than traditional experimental designs.
+%
+Here, we operationalized the perception of spatial information based on
+annotated stimulus features embedded in two naturalistic stimuli and compared
+current results to results gained from a traditional visual localizer.
+%
+
+Here, we reused three fMRI datasets and two stimulus annotations that are part
+of the studyforrest dataset \href{http://www.studyforrest.org}{studyforrest.org}
+to operationalize the perception of spatial information embedded in two
+naturalistic stimuli and to compare current results to results gained from a
+traditional visual localizer paradigm.
 

### 2021-02-15 paper/main.tex
write summary / conclusions

--- 2021-02-15 paper/main.tex
@@
 % GLM contrasts
-We then created several general linear model (GLM) contrast to analyze the
+We then created several general linear model (GLM) contrasts to analyze the
 corresponding publicly available fMRI datasets of each naturalistic stimulus
@@
 to noise-cluster ration)\todo{if you know what I mean} depends on how many
-events correlating with an assumed perceptual process the stimulus provides
-and to the extent to which a naturalistic stimulus' multi-dimensionality is
+events correlating with an assumed perceptual process the stimulus provides and
+to the extent to which a naturalistic stimulus' multi-dimensionality is
 annotated and statistically controlled.
 
-\section{conclusion}
-
 \todo[inline]{scientific data has no conclusion -> last paragraph}
-
+\todo[inline]{(2nd part of) following paragraph pretty similar to discussion's
+first paragraph}
 % natural stimulation
-Natural stimuli like movies \citep{eickhoff2020towards,
+In summary, natural stimuli like movies \citep{eickhoff2020towards,
 hasson2008neurocinematics, sonkusare2019naturalistic} or narratives
 \citep{hamilton2018revolution, honey2012not, lerner2011topographic,
-silbert2014coupled, wilson2008beyond} offer an easy to implement, (continuous,)
+silbert2014coupled, wilson2008beyond} offer an easy to implement, continuous,
 complex, immersive, task-free paradigm that more closely resembles our natural
-dynamic environment than traditional experimental designs.
-
-\begin{itemize}
-\item We reuse public data for independent research question
-\item GLM based on annotations to operationalize ``spatial perception''
-\item Our results add evidence that model-driven analyses based in annotations
-can be run on data from naturalistic stimuli to ``localize'' brain activity
-correlating with specific perceptual processes.
-\item ``localization performance'' relies on how well the model captures
-different aspects of the stimuli's feature space.
-\item PPA is functionally heterogeneous region
-\item a complex but naturally engaging auditory stimulus like an
-audiobook might in principle be used as a non-visual localizer for a variety of
-brain functions in subjects who are not willing or able to follow task
-instructions during brain scanning [would state that explicitly in the summary
-at the end].
-\end{itemize}
-
-this study shows that already existing, publicly
-available data can be re-used for independent research questions that provide
-further evidence for existing theories/hypotheses and advance the field by
-generating new findings \& hypothesis.
+dynamic environment than traditional experimental paradigms.
+% method
+We took advantage of three fMRI datasets and two stimulus annotations that are
+part of the studyforrest dataset
+\href{http://www.studyforrest.org}{studyforrest.org} to operationalize the
+perception of spatial information embedded an audio-visual movie and an auditory
+narrative, and compare current results to results gained from a traditional
+visual localizer.
+% results
+In general, results add evidence that a model-driven GLM analysis based on
+annotations can be run on data from naturalistic stimuli to localize concise
+functional areas and networks correlating with specific perceptual processes.
+% interpretation
+More specifically, our results demonstrate that increased activation in the PPA
+during the perception of static pictures generalizes to the perception of
+spatial information embedded in a movie and an exclusively auditory stimulus.
+% interpretation: aPPA vs. pPPA
+Further, our results provide evidence that the PPA can be divided into
+functional subregions that [might] work together during the perception of visual
+scenes.
+% interpretation
+Lastly, a naturally engaging auditory narrative might - in principle -
+substitute a visual paradigm to localize the anterior part of the PPA in
+subjects who are not [willing or] able to follow task instructions during brain
+scanning.
 
@@
 
-\todo[inline]{everything correct?}
-\todo[inline]{Grant or contribution numbers may be acknowledged}
+\todo[inline]{everything correct? Grant or contribution numbers may be acknowledged}
 %
@@
 
-\todo{Figures \& Tables have their own section, the editor puts them where he
-wants them?}
+\todo[inline]{Figures \& Tables have their own section, the editor puts them
+where he wants them?}
 
@@
 1. Lastname1, Initial1., Lastname2, Initial2., ...\& LastnameN, InitialN. \emph{Repository name} Dataset accession number or DOI (YYYY).
+
+% cut anno
+\citep{haeusler2016cutanno}
+% speech anno
+\citep{hausler2021studyforrest}
+% audio-description
+\citep{hanke2014audiomovie}
+% movie
+\citep{hanke2016simultaneous}
+% localizer
+\citep{sengupta2016extension}
 

### 2021-02-15 paper/main.tex
restructure supplementals

@@
 \begin{itemize}
-    \item [text in brackets] can probably be deleted
+    \item text in [brackets] can probably be deleted
     \item imo AD and AV can be written as movie and audio-description
@@
 
-\noindent Method:
+\noindent Method
 
@@
         PPA". Machst wohl das erste, beschreibst es aber als das zweite
-    \item Summary / Concluding statement
-        (data reuse to present compelling new findings \& conclusions derived
-        from published.)
 \end{itemize}
@@
 \begin{itemize}
-    \item restructure (results + discussion AV, then AD)
-    \item discuss differences of contrasts (s. Simons comment)
+    \item discuss differences of contrasts (s. Simons comment)?
 \end{itemize}
 
-\noindent Code Availability
+\noindent Data Citations, Code Availability, Data Availability
+
 \begin{itemize}
     \item https://www.springernature.com/gp/authors/research-data-policy/data-availability-statements/12330880i
-\end{itemize}
-
-\noindent Data Availability
-\begin{itemize}
-    \item s. other psyinfo paper
+    \item cf. other Scienctific Data analysis paper
 \end{itemize}
@@
 
+\pagebreak[4]
+
 \section{Supplementary Materials}
 
-\subsection{Results}
-
-\subsubsection{Robustness of group results across contrasts}
+\subsection{Congruencies across contrasts}
 
@@
 \end{figure*}
-
-\subsubsection{control contrasts}
-
-% intro
-For the purpose of negative control, we implemented five contrasts for every
-stimulus.
-
-% ---------- AV control contrasts ----------
-% 6 nothing
-% 7 nothing
-% 8 nothing
-% 9 nothing
-%10 se_new > se_old (nouns but in AV stimulus):
-% LOC (l/r) right PPA, bilateral sup. lat. occ. c., sup. parietal lobe (right)
-
-% ---------- AD control contrasts ----------
-% 9 PPA (-/-); RSC (-/r), LOC (-/-), left pars triangularis
-%10 PPA (-/-); RSC (-/-), LOC (-/-)
-%11 PPA (-/-); RSC (-/-), LOC (-/-),
-%12 PPA (-/-); RSC (-/-), LOC (-/-), right posterior hippocampus
-%13 PPA (-/-); RSC (-/-), LOC (-/-)
-
-% AV: no_cut > x
-In the analysis of the AV data, none of the four contrasts that compared the
-\texttt{no\_cut} category to a movie cut category (see Table
-\ref{tab:av-contrasts}) yielded significant clusters.
-% AV using nouns
-The contrast that used the narrator's nouns but in the AV stimulus
-(\texttt{se\_new} > \texttt{se\_old}) yielded a significant cluster in the right
-PPA and bilateral clusters in the superior lateral occipital cortices (the right
-hemispheric cluster extending into the superior parietal cortex).\todo{cuts
-correlate with the nouns}
-
-% AD stimulus
-In the analysis of the AD data, we created control contrasts based on events of
-the annotated movie cuts (cf. Table \ref{tab:ao-contrasts})
-% contrast 9
-Contrast 9 (vse\_new > pe\_old) revealed one significant cluster in the left
-inferior prefrontal cortex (pars triangularis) and right ventral
-precuneus/posterior cingulate gyrus.
-% contrast 12
-Contrast 12 (\texttt{vse\_new} > \texttt{vse\_old}, \texttt{vpe\_old}) revealed
-one cluster in the right posterior hippocampus.\todo{odd imo}
-
-\subsection{Discussion}
-
-\subsubsection{congruencies (PPA, RSC, LOC, others)}
 
@@
 
-\subsection{negative controls and cross-modal controls}
+\subsection{Control contrasts}
+
+% intro
+For the purpose of negative control, we implemented five contrasts for every
+stimulus.
+
+% ---------- AV control contrasts ----------
+% 6 nothing
+% 7 nothing
+% 8 nothing
+% 9 nothing
+%10 se_new > se_old (nouns but in AV stimulus):
+% LOC (l/r) right PPA, bilateral sup. lat. occ. c., sup. parietal lobe (right)
+
+% ---------- AD control contrasts ----------
+% 9 PPA (-/-); RSC (-/r), LOC (-/-), left pars triangularis
+%10 PPA (-/-); RSC (-/-), LOC (-/-)
+%11 PPA (-/-); RSC (-/-), LOC (-/-),
+%12 PPA (-/-); RSC (-/-), LOC (-/-), right posterior hippocampus
+%13 PPA (-/-); RSC (-/-), LOC (-/-)
+
+% AV: no_cut > x
+In the analysis of the AV data, none of the four contrasts that compared the
+\texttt{no\_cut} category to a movie cut category (see Table
+\ref{tab:av-contrasts}) yielded significant clusters.
+% AV using nouns
+The contrast that used the narrator's nouns but in the AV stimulus
+(\texttt{se\_new} > \texttt{se\_old}) yielded a significant cluster in the right
+PPA and bilateral clusters in the superior lateral occipital cortices (the right
+hemispheric cluster extending into the superior parietal cortex).\todo{cuts
+correlate with the nouns}
+
+% AD stimulus
+In the analysis of the AD data, we created control contrasts based on events of
+the annotated movie cuts (cf. Table \ref{tab:ao-contrasts})
+% contrast 9
+Contrast 9 (vse\_new > pe\_old) revealed one significant cluster in the left
+inferior prefrontal cortex (pars triangularis) and right ventral
+precuneus/posterior cingulate gyrus.
+% contrast 12
+Contrast 12 (\texttt{vse\_new} > \texttt{vse\_old}, \texttt{vpe\_old}) revealed
+one cluster in the right posterior hippocampus.\todo{odd imo}
 
@@
 to the movie cuts categories????}
-
-\todo[inline]{discussion \& concluding statement}
 

### 2021-02-15 paper/main.tex
some cleaning of supplementals

@@
 \todo[inline]{SE: use different colormap for overlap of contrasts' clusters}
+\todo[inline]{SE: wie unterscheiden sich die Kontraste?}
+\todo[inline]{Wo sind welche Kontraste (z.B. im Ergebnis) von anderen abgewichen?}
 
@@
 
-\todo[inline]{SE: wie unterscheiden sich die Kontraste?}
-\todo[inline]{Wo sind welche Kontraste (z.B. im Ergebnis) von anderen abgewichen?}
-
-% PPA AV
-Regarding contrasts of the AV stimulus (see Table \ref{tab:av-contrasts}), all
-five AV contrasts show significant bilateral clusters in the PPA but also
-extending into more posterior brain regions.
-% PPA AD
-Regarding contrasts of the AD stimulus (see Table \ref{tab:ao-contrasts}), six
-of overall eight contrasts show significant bilateral clusters in the anterior
-part of the group PPA overlap.
-% results indicate robustness
-Thus, the results of the additional contrasts indicate that our findings are
-robust and do not depend on the design of one specific contrasts.
+% Discussion
+The results across the contrasts of the AV and AD stimulus indicate that our
+findings regarding the PPA but also RSC and LOC are robust and do not depend on
+the design of one specific contrasts.
 % but
@@
 
-% intro
-Apart from the PPA, we find significantly increased activity in the dorsal
-precuneus and posterior cingulate region (e.g. retrosplenial cortex; RSC) and
-lateral occipital cortex (LOC) across contrasts of both naturalistic stimuli.
-% RSC intro
-Like the PPA, the RSC (AV stimulus: significant clusters in 3 of 5 contrasts; AD
-stimulus: 7 of 8 contrasts) and LOC (AV stimulus: 4 of 5 contrasts; AD stimulus:
-unilateral in 2, bilateral in 4 of 8 contrasts) are known to be scene-selective
-regions (see \citep{chrastil2018heterogeneity, bettencourt2013role} for
-reviews).\todo{same part as in the main text but with number of contrasts}
-
-% some backup text for RSC & LOC
-\begin{comment}
-% RSC
-RSC is located in the retrosplenial cortex, and posterior cingulate region (BA
-23 and 31) [51–56], near to the point where the calcarine sulcus joins the
-parietal-occipital sulcus \citep{epstein2008parahippocampal}.
-%
-RSC location functionally defined. In context of scene perception, the RSC is
-not necessarily spatially congruent with the anatomically defined retrosplenial
-cortex [26] (BA 29 and 30) \citep{epstein2008parahippocampal} but functionally
-defined as the posterior medial region that exhibits increased hemodynamic
-activity to visual scenes and during mental imagination trough familiar
-environments [8] \citep{epstein2008parahippocampal}.
-
-\begin{itemize}
-    \item \citep{chrastil2018heterogeneity}
-    \item \citep{vann2009what}
-    \item \citep{silson2019posterior}
-    \item \citep{baldassano2016two}:
-    \item RSC appears to be most directly involved in orienting the viewer to
-    the structure of the environment (both within and beyond the borders of the
-presented image) for the purpose of navigational planning; it encodes both
-absolute location and facing direction [Vass and Epstein, 2013; Epstein and
-Vass, 2014; Marchette et al., 2014], integrates across views presented in a
-panoramic sequence [Park and Chun, 2009], and shows strong familiarity effects
-[Epstein et al., 2007a,b].
-\end{itemize}
-
-% LOC
-\begin{itemize}
-\item Bettencourt (2013). The Role of Transverse Occipital Sulcus in Scene
-    Perception
-\item Dilks, Kanwisher (2013). The Occipital Place Area Is Causally and
-    Selectively Involved in Scene Perception
-\item Nasr (2011). Scene-selective cortical regions in human and nonhuman
-    primates
-\item Dilks (2011). Mirror-image sensitivity and invariance in object \& scene
-    processing
-\item MacEvoy and Epstein (2007). Position selectivity in scene- and
-    object-responsive
-\item Grill-Spector (2003). The neural basis of object perception
-\item Hasson (2003). Large-scale mirror-symmetry organization
-\item Nakamura (2000). Functional delineation of the human occipito-temporal
-    areas
-\item \citep{baldassano2016two} regarding functional difference pPPA vs. OPA:
-    The functional distinction is unclear.
-    Previous work has speculated about the purpose of the apparent ventral and
-    dorsal ``duplication'' of regions sensitive to large landmarks, proposing
-    that it may be related to different output goals (e.g., action planning in
-    OPA, object recognition in pPPA)[Konkle and Caramazza, 2013], or to
-    different input connections (e.g., lower visual field processing in OPA,
-    upper visual field processing in pPPA)[Kravitz et al., 2013; Silson et al.,
-    2015].
-    OPA and pPPA may also use information from different visual
-    eccentricities: OPA processing less peripheral, relatively high-resolution
-    environmental features. pPPA processing more peripheral, large-scale
-    geometry, and context [Baldassano et al., 2016a]
-\end{itemize}
-
-\end{comment}
-
 % ``confounding'' clusters
-Despite performing a whole brain analysis, we do not find many [random] clusters
-in single contrasts or even systematically across contrasts that hamper the
-interpretation of results.
+Despite performing a whole brain analysis, we do not find [many] clusters
+in a single contrasts or systematically across contrasts that are scattered
+across the brain and hamper the interpretation of results.
 % AV: null results regarding attention and eye movements
@@
 
+\todo[inline]{random [?] prefrontal cluster in 2-3 AO contrasts; at the moment
+no idea what the correlating process could be; be aware of reverse inferences}
+
 \subsection{Control contrasts}
 
-% intro
-For the purpose of negative control, we implemented five contrasts for every
-stimulus.
+\todo[inline]{discuss results in light of ``negative control'' (-> definition \&
+purpose}
 
 % ---------- AV control contrasts ----------
-% 6 nothing
-% 7 nothing
-% 8 nothing
-% 9 nothing
-%10 se_new > se_old (nouns but in AV stimulus):
-% LOC (l/r) right PPA, bilateral sup. lat. occ. c., sup. parietal lobe (right)
+% 6 nothing 7 nothing 8 nothing 9 nothing
+%10 se_new > se_old (nouns but in AV stimulus): LOC (l/r) right PPA, bilateral
+%sup. lat. occ. c., sup. parietal lobe (right)
 
@@
 
+% intro
+For the purpose of negative control, we implemented five contrasts for every
+stimulus.
 % AV: no_cut > x
@@
 PPA and bilateral clusters in the superior lateral occipital cortices (the right
-hemispheric cluster extending into the superior parietal cortex).\todo{cuts
-correlate with the nouns}
-
+hemispheric cluster extending into the superior parietal cortex).
 % AD stimulus
@@
 \texttt{no\_cuts} to categories of movie cuts all lead to null results.
-
 % AD anno in AV data

### 2021-02-15 paper/main.tex
minor cleaning

@@
 \begin{itemize}
-    \item discuss differences of contrasts (s. Simons comment)?
+    \item more detailed discussion differences of contrasts (s. Simons comment)?
+    \item discussion of control contrasts
 \end{itemize}
@@
     \item https://www.springernature.com/gp/authors/research-data-policy/data-availability-statements/12330880i
-    \item cf. other Scienctific Data analysis paper
+    \item cf. other Scientific Data analysis paper
 \end{itemize}
@@
         \texttt{fg\_ad\_lrdiff} and \texttt{fg\_av\_ger\_lrdiff}, r=.7749).
-        \todo[inline]{checked it, all labels listed}
       }
@@
 specialization of functional areas is preserved during movie watching.
+\todo{clusters are pretty big too}
 %
@@
 frames, we categorized each frame after a cut independent of its specific
-content  \todo{Bartels' clusters are actually pretty big too}
+content
 % exploited cinematographic tendencies
@@
 \todo[inline]{scientific data has no conclusion -> last paragraph}
-\todo[inline]{(2nd part of) following paragraph pretty similar to discussion's
-first paragraph}
 % natural stimulation
@@
 
-\todo[inline]{Figures \& Tables have their own section, the editor puts them
+\todo[inline]{Figures \& Tables have their own section??? the editor puts them
 where he wants them?}
@@
 \todo[inline]{discuss results in light of ``negative control'' (-> definition \&
-purpose}
+purpose)}
 
@@
 correlated with \texttt{vse\_new} (cuts); \texttt{se\_old} (nouns) is
-r$\approx$0.4 correlated with \texttt){vse\_old}.
+r$\approx$0.4 correlated with \texttt{vse\_old}.
 

### 2021-02-16 paper/main.tex
Finalize most optional phrasing suggestions

@@
 subregions.
-% localizer substitute
-[An auditory narrative might substitute a visual paradigm to localize the PPAs
-anterior part in visually impaired subjects.]
 \end{abstract}
@@
 \begin{itemize}
-    \item text in [brackets] can probably be deleted
     \item imo AD and AV can be written as movie and audio-description
@@
 In a block design study conducted by \cite{wolbers2011modality} the PPA of
-[sighted] participants showed increased activation during a delayed
+participants showed increased activation during a delayed
 match-to-sample task of haptically explored scenes constructed from LEGO bricks
@@
 lack external and ecological validity \citep{westfall2016fixing,
-hasson2004intersubject} because they poorly resemble how we, free of a[n
-explicit] perceptual task, experience our rich/multidimensional and continuous
+hasson2004intersubject} because they poorly resemble how we, free of an
+explicit perceptual task, experience our rich/multidimensional and continuous
 environment that our brains are accommodated to
@@
 Hence, we annotated the temporal structure of various stimulus features that
-later served as basis [for GLM regressors] to model hemodynamic responses.
+later served as basis for modeling hemodynamic responses.
 
@@
 For the analysis of the AV stimulus, we took advantage of a previously published
-annotation of [the 869] movie cuts and the depicted location after each cut
+annotation of 869 movie cuts and the depicted location after each cut
 \citep{haeusler2016cutanno}.
@@
 % one slice to show them all
-Transversal slice of z=-11 was chosen as it depicts [at least some] voxels of
+Transversal slice of z=-11 was chosen as it depicts voxels of
 significant clusters in almost all subjects.
@@
 Hence, current results also suggest that verbal spatial information is processed
-in the anterior PPA casually and does not [necessarily] rely on [deliberately]
+in the anterior PPA casually and does not necessarily rely on deliberately
 paying attention to verbal spatial information.
@@
 Further, our exploratory analysis suggests that a naturalistic auditory stimulus
-can [in principle] be applied to localize (the anterior part) of a higher-level
+can, in principle, be applied to localize (the anterior part) of a higher-level
 visual area in the majority of subjects.
@@
 Contrary, the aPPA is more strongly functionally connected to portions of the
-default mode network[, including caudal inferior parietal lobe (cIPL), the
+default mode network, including caudal inferior parietal lobe (cIPL), the
 restrosplenial complex (RSC), medial PFC and the lateral surface of the anterior
-temporal lobe] \citep{baldassano2013differential, baldassano2016two}.
+temporal lobe \citep{baldassano2013differential, baldassano2016two}.
 % conclusion: subregions
@@
 
-\todo[inline]{scientific data has no conclusion -> last paragraph}
 % natural stimulation
@@
 Further, our results provide evidence that the PPA can be divided into
-functional subregions that [might] work together during the perception of visual
+functional subregions that coactivate during the perception of visual
 scenes.
@@
 substitute a visual paradigm to localize the anterior part of the PPA in
-subjects who are not [willing or] able to follow task instructions during brain
-scanning.
+individuals with conditions that make them unable to follow task instructions
+during brain scanning.
 
@@
 The authors declare no competing financial interests.
-
-\section*{Figures Legends}
-
-\todo[inline]{Figures \& Tables have their own section??? the editor puts them
-where he wants them?}
-
-\emph{We discourage the inclusion of figures in the
-Supplementary Information \textendash{} all key figures should be included here
-in the main Figure section.}
-
-\emph{Figure legend must total no more
-than 350 words, and may contain literature references.}
-
-\section*{Tables}
-
-\emph{tables provide summary information but should not be used to present
-primary data (i.e. measurements).}
 

### 2021-02-16 paper/main.tex
Dissolve acronymns

@@
 
-\noindent Generally
-
-\begin{itemize}
-    \item imo AD and AV can be written as movie and audio-description
-\end{itemize}
-
 \noindent Method
@@
 The operationalization of visual perception is based on an annotation of cuts
-and depicted locations in the audio-visual movie ``Forrest Gump'' (AV stimulus).
-% AO stimulus
+and depicted locations in the audio-visual movie ``Forrest Gump''.
+% AD stimulus
 The operationalization of auditory perception is based on an annotation of
-speech occurring in the movie's audio-description (AD stimulus).
+speech occurring in the movie's audio-description.
 % GLM contrasts
@@
 % AD study
-In the AD study \citep{hanke2014audiomovie}, 20 German native speakers (all
+In the audio-description study \citep{hanke2014audiomovie}, 20 German native speakers (all
 right-handed, age 21–38 years, mean age 26.6 years, 12 male) listened to the
@@
 % AV study
-In the AV study \citep{hanke2016simultaneous}, 15 participants (21–39 years,
-mean age 29.4, six female) of the prior AD study watched the audio-visual movie
+In the movie study \citep{hanke2016simultaneous}, 15 participants (21–39 years,
+mean age 29.4, six female) of the prior audio-description study watched the audio-visual movie
 with dubbed German audio track \citep{ForrestGumpDVD}.
@@
 % AD
-In the AD study, visual instructions were presented on a rear-projection screen
+In the audio-description study, visual instructions were presented on a rear-projection screen
 inside scanner bore. During the
@@
 % AV & VIS
-In the AV and VIS study, visual instructions and stimuli were presented on a
+In the movie and VIS study, visual instructions and stimuli were presented on a
 rear-projection screen
@@
 % AD & AV: auditory stimulation
-Auditory stimulation was implemented using custom in-ear (AD), or over-the-ear
-headphones (AV), which reduced the scanner noise by
+Auditory stimulation was implemented using custom in-ear (audio-description), or over-the-ear
+headphones (movie), which reduced the scanner noise by
 at least \unit[20–30]{dB}.
@@
 
-Gradient-echo fMRI data for the AD study were acquired using a \unit[7]{Tesla}
+Gradient-echo fMRI data for the audio-description study were acquired using a \unit[7]{Tesla}
 Siemens MAGNETOM magnetic resonance scanner equipped with a 32 channel brain
@@
 % AV & VIS
-In the AV and VIS study, a \unit[3]{Tesla} Philips Achieva dStream
+In the movie and VIS study, a \unit[3]{Tesla} Philips Achieva dStream
 MRI scanner with a 32 channel head coil acquired gradient-echo fMRI data
@@
 A total of 3599 volumes were recorded for each participant in each of the
-naturalistic stimulus paradigms (AD and AV).
+naturalistic stimulus paradigms (audio-description and movie).
 
@@
 data of one participant were dropped to due to invalid distortion correction
-during scanning of the AD stimulus.
+during scanning of the audio-description stimulus.
 Data were previously corrected for motion, aligned with and re-sliced onto a
@@
 (uniform spatial resolution of \unit[2.5$\times$2.5$\times$2.5]{mm} for both
-AD and AV data).
+audio-description and movie data).
 % preprocessing intro
@@
 % AV anno
-For the analysis of the AV stimulus, we took advantage of a previously published
+For the analysis of the movie stimulus, we took advantage of a previously published
 annotation of 869 movie cuts and the depicted location after each cut
@@
 % AD annotation
-For the analysis of the AD stimulus, we extended a publicly available annotation
+For the analysis of the audio-description stimulus, we extended a publicly available annotation
 of speech \citep{hausler2021studyforrest} by further annotating words spoken by
@@
 % visual shit
-For the AV stimulus, we computed the mean luminance of a movie frame
+For the movie stimulus, we computed the mean luminance of a movie frame
 (\unit[40]{ms}), the difference in mean luminance of each frame's left and right
@@
 % convolving
-Events for all regressors of the AV and AO stimulus were convolved with a double
+Events for all regressors of the movie and audio-description stimulus were convolved with a double
 gamma hemodynamic response function (HRF).
@@
 % AV design matrix
-For the subsequent first level GLM analysis of the AV stimulus, the modeled
+For the subsequent first level GLM analysis of the movie stimulus, the modeled
 hemodynamic responses related to all movie cuts (including \texttt{no\_cut}) and
@@
 % AD regressors in AV AD design matrix
-For the first level analysis of the AD stimulus, the modeled hemodynamic
+For the first level analysis of the audio-description stimulus, the modeled hemodynamic
 responses related to all noun categories and the two low-level perceptual
@@
 % AD regressors in AV
-To create a contrasts of cross-modal control in the analysis of the AV stimulus,
+To create a contrasts of cross-modal control in the analysis of the movie stimulus,
 we also implemented the regressors based on nouns used by the
@@
 % AV regressors in AV
-To create contrasts of cross-modal negative control in the analysis of the AD
+To create contrasts of cross-modal negative control in the analysis of the audio-description
 stimulus, we also implemented the movie cut-related regressors
@@
 spatial information compared to the perception of non-spatial information
-differently in five $t$-contrasts for the AV stimulus (see Table
-\ref{tab:av-contrasts}) and eight $t$-contrasts for the AD stimulus (see Table
+differently in five $t$-contrasts for the movie stimulus (see Table
+\ref{tab:av-contrasts}) and eight $t$-contrasts for the audio-description stimulus (see Table
 \ref{tab:ao-contrasts}).
@@
 % AV: primary contrast
-In the primary contrast of the AV stimulus, we contrasted cuts to a setting that
+In the primary contrast of the movie stimulus, we contrasted cuts to a setting that
 was not depicted before (\texttt{vse\_new}) to cuts merely switching the camera
@@
 % AD: primary contrast
-In the primary contrast of the AD stimulus, we contrasted buildings and
+In the primary contrast of the audio-description stimulus, we contrasted buildings and
 landmarks (\texttt{geo}), and rooms and geometry-defining objects
@@
 % AV: no cut > cut
-For the AV stimulus, four contrasts were created contrasting the no-cut
+For the movie stimulus, four contrasts were created contrasting the no-cut
 regressor (\texttt{vno\_cut} to cut-related regressors \ref{tab:av-contrasts}).
@@
 % AD stimulus
-For the AD stimulus, we created five $t$-contrasts (see Table
+For the audio-description stimulus, we created five $t$-contrasts (see Table
 \ref{tab:ao-contrasts}) to test if increased activation in the PPA was
@@
 % ref to figure
-Figure \ref{fig:subs-thresh-ppa} depicts thresholded $z$-maps of the primary AV
-and AD $t$-contrast, and the outline of overlapped, individual PPAs
+Figure \ref{fig:subs-thresh-ppa} depicts thresholded $z$-maps of the primary movie
+and audio-description $t$-contrast, and the outline of overlapped, individual PPAs
 co-registered to the MNI152 template.
@@
 % AV
-Results of the primary AV contrast yielded bilateral clusters in five subjects,
+Results of the primary movie contrast yielded bilateral clusters in five subjects,
 a unilateral right cluster in six subjects (of which one subjects yielded a
@@
 % report here in group
-Results of the primary AD contrast yielded bilateral clusters in nine subjects
+Results of the primary audio-description contrast yielded bilateral clusters in nine subjects
 that are within or overlapping with the individual PPA.
@@
 In sub-04, two homologous clusters are apparent, whereas the dedicated localizer
-(and AV stimulus) yielded only one cluster in the right hemisphere.
+(and movie stimulus) yielded only one cluster in the right hemisphere.
 % sub-09
@@
         significant clusters in almost all subjects.
-        The figure does not show voxels of the left cluster of the AV stimulus
-        in sub-09 and sub-18, and voxels of the right cluster of the AV
+        The figure does not show voxels of the left cluster of the movie stimulus
+        in sub-09 and sub-18, and voxels of the right cluster of the movie
         stimulus in sub-15.}
@@
 To better depict the agreement and difference between the results of the visual
-localizer and the primary AD contrast, we created a Bland-Altman-Plot for every
+localizer and the primary audio-description contrast, we created a Bland-Altman-Plot for every
 subject (see Figure \ref{fig:bland-altman}).
 % what it depicts
-Each subplot visualizes the mean value and difference (localizer minus AD) of
+Each subplot visualizes the mean value and difference (localizer minus audio-description) of
 two spatially corresponding voxels in the unthresholded $z$-maps.
@@
 the dedicated localizer, values below the horizontal line depict voxels that
-show a higher $z$-value in the AD stimulus.
+show a higher $z$-value in the audio-description stimulus.
 
@@
 % results
-Group results of the AV stimulus' primary contrast yielded one cluster that
+Group results of the movie stimulus' primary contrast yielded one cluster that
 spans the group overlap of individual PPA ROIs from anterior to posterior.
@@
 Encouraged by \citep{aziz2008modulation}, we hypothesized that spatial
-information embedded in the AD stimulus would correlate with increased
+information embedded in the audio-description stimulus would correlate with increased
 hemodynamic activity in the PPA.
@@
 % we did not choose se\_new and se\_old
-In the AD's primary contrast, we did not include the categories that contained
+In the audio-description's primary contrast, we did not include the categories that contained
 switches from one setting to another (\texttt{se\_new} and \texttt{se\_old})
@@
 \todo[inline]{discussion of Bland-Altman-Plots?; dunno if this is meaningful:
-z-scores in the anterior part of PPA are higher in AD contrasts than in contrast
+z-scores in the anterior part of PPA are higher in audio-description contrasts than in contrast
 of localizer}
@@
 dorsal precuneus and posterior cingulate region (e.g. retrosplenial complex;
-RSC) and lateral occipital cortex (LOC; more lateral in the AV stimulus, more
-medial in the AD stimulus) across contrasts of both naturalistic stimuli.
+RSC) and lateral occipital cortex (LOC; more lateral in the movie stimulus, more
+medial in the audio-description stimulus) across contrasts of both naturalistic stimuli.
 % RSC intro
@@
 In order to test the robustness of our approach, we created overall five
-$t$-contrasts for the AV stimulus (see Table \ref{tab:av-contrasts}), and
-overall eight $t$-contrast for the AD stimulus (see Table
+$t$-contrasts for the movie stimulus (see Table \ref{tab:av-contrasts}), and
+overall eight $t$-contrast for the audio-description stimulus (see Table
 \ref{tab:av-contrasts}) by varying the contrasted categories (and thus the
@@
 % temporal occipital fusiform cortex
-All five AV contrasts yielded significant bilateral clusters that
+All five movie contrasts yielded significant bilateral clusters that
 overlap with the PPA group overlap (see Figure \ref{fig:stability-slices}).
 % AV: RSC & LOC
-Reliably across contrasts of the AV stimulus, we find bilaterally
+Reliably across contrasts of the movie stimulus, we find bilaterally
 significant clusters also in the ventral precuneal cortex and posterior
@@
 % AD: results
-In results of the AD stimulus, all contrasts except contrast 7
+In results of the audio-description stimulus, all contrasts except contrast 7
 (\texttt{se\_new}, \texttt{se\_old} > non-spatial categories) and contrast 8
@@
 % AD: RSC & LOC
-Reliably across contrast of the AD stimulus, we find bilaterally significant
+Reliably across contrast of the audio-description stimulus, we find bilaterally significant
 clusters also in the ventral precuneus (all except contrasts 8), lateral
@@
 % non-systematic
-Lastly, some contrasts of the AD stimulus yielded significant clusters in
+Lastly, some contrasts of the audio-description stimulus yielded significant clusters in
 regions that were not statistically significant in three or more contrasts.
@@
 % Discussion
-The results across the contrasts of the AV and AD stimulus indicate that our
+The results across the contrasts of the movie and audio-description stimulus indicate that our
 findings regarding the PPA but also RSC and LOC are robust and do not depend on
@@
 % example
-For example, contrast 8 of the AD stimulus (\texttt{se\_new} > \texttt{se\_old})
+For example, contrast 8 of the audio-description stimulus (\texttt{se\_new} > \texttt{se\_old})
 that used the most heterogeneous categories comprising the least amount of
@@
 % AV: null results regarding attention and eye movements
-For example in the AV results, we do not find significant clusters that could be
+For example in the movie results, we do not find significant clusters that could be
 attributed to cognitive processes like attention or eye movements.
 % AD: auditory cortices
-Nevertheless, contrasts of the AD stimulus that compare (among others) verbal
+Nevertheless, contrasts of the audio-description stimulus that compare (among others) verbal
 hints of the change of a setting (\texttt{se\_new} or \texttt{se\_old}) to all
@@
 
-\todo[inline]{random [?] prefrontal cluster in 2-3 AO contrasts; at the moment
+\todo[inline]{random [?] prefrontal cluster in 2-3 AD contrasts; at the moment
 no idea what the correlating process could be; be aware of reverse inferences}
@@
 % AV: no_cut > x
-In the analysis of the AV data, none of the four contrasts that compared the
+In the analysis of the movie data, none of the four contrasts that compared the
 \texttt{no\_cut} category to a movie cut category (see Table
@@
 % AV using nouns
-The contrast that used the narrator's nouns but in the AV stimulus
+The contrast that used the narrator's nouns but in the movie stimulus
 (\texttt{se\_new} > \texttt{se\_old}) yielded a significant cluster in the right
@@
 % AD stimulus
-In the analysis of the AD data, we created control contrasts based on events of
+In the analysis of the audio-description data, we created control contrasts based on events of
 the annotated movie cuts (cf. Table \ref{tab:ao-contrasts})
@@
 
-The four control contrasts of the AV stimulus that compared the
+The four control contrasts of the movie stimulus that compared the
 \texttt{no\_cuts} to categories of movie cuts all lead to null results.
 % AD anno in AV data
-The AV contrast using nouns (\texttt{se\_new} > \texttt{se\_old}): PPA
+The movie contrast using nouns (\texttt{se\_new} > \texttt{se\_old}): PPA
 (unilateral), LOC (bilateral); These noun categories show highest correlation
@@
 % AV anno in AV data
-The the 5 AV PPA contrasts but with the AV data using cuts. All null results
+The the 5 movie PPA contrasts but with the movie data using cuts. All null results
 except:

### 2021-02-16 paper/main.tex
Comment on p-values
Dissolve VIS acronym too

@@
 \begin{itemize}
-    \item tables: round p-values to ?
+    \item tables: round p-values to ? MIH: I would say 4 digits, but I can find internet
+      recommendations for 3. That would mean anything less than 0.001 is reported as '<.001',
+      and the rest as the precise value. This should only apply to corrected p-values.
+      For an uncorrected p-value 0.001 is very high.
 \end{itemize}
@@
 % VIS
-c) participating in a dedicated six-category block-design visual localizer (VIS; \citep{sengupta2016extension}).
+c) participating in a dedicated six-category block-design visual localizer \citep{sengupta2016extension}.
 % see corresponding papers for details
@@
 % VIS study
-In the VIS study \citep{sengupta2016extension}, the same 15 participants took
+In the block-design localizer study \citep{sengupta2016extension}, the same 15 participants took
 part in a six-category block-design visual localizer.
@@
 % VIS study picture categories
-All stimuli of the VIS study were already used in a previous study
+All stimuli of the block-design localizer study were already used in a previous study
 \citep{haxby2011common}.
@@
 % AV & VIS
-In the movie and VIS study, visual instructions and stimuli were presented on a
+In the movie and block-design localizer study, visual instructions and stimuli were presented on a
 rear-projection screen
@@
 % angle of view: VIS
-In the VIS study, stimulus images were displayed at a size of approximately
+In the block-design localizer study, stimulus images were displayed at a size of approximately
 \unit[10]$^{\circ}$ $\times$ \unit[10]$^{\circ}$ of visual angle.
@@
 % AV & VIS
-In the movie and VIS study, a \unit[3]{Tesla} Philips Achieva dStream
+In the movie and block-design localizer study, a \unit[3]{Tesla} Philips Achieva dStream
 MRI scanner with a 32 channel head coil acquired gradient-echo fMRI data
@@
 % (2010)
-In the VIS study using the established approach of contrasting blocks of
+In the block-design localizer study using the established approach of contrasting blocks of
 pictures, a set of three contrasts (\textit{strict}, \textit{relaxed}, and

### 2021-02-16 paper/main.tex
Acknowledge grants
More humble statement in discussion of model-based approaches

@@
 % RSC + LOC
-Apart from the PPA, results revealed significantly increased activity in the
+Apart from the PPA, results show significantly increased activity in the
 dorsal precuneus and posterior cingulate region (e.g. retrosplenial complex;
 RSC) and lateral occipital cortex (LOC; more lateral in the movie stimulus, more
-medial in the audio-description stimulus) across contrasts of both naturalistic stimuli.
+medial in the audio-description stimulus) for both naturalistic stimuli.
 % RSC intro
-Like the PPA, the RSC and LOC repeatedly showed increased hemodynamic activity
+Like the PPA, the RSC and LOC repeatedly exhibited increased hemodynamic activity
 in studies investigating visual spatial perception or navigation (see
@@
 % not random shit
-Thus, our approach to operationalize spatial perception based on stimulus
-annotations did not lead to significant clusters scattered across the brain but
-restricted to a brain network that is assumed/known to be involved in (visual)
-spatial perception and cognition.
-%
-This suggest that model-driven methods based on stimulus annotations are
-suitable to reveal spatially concise functional areas and networks.
-%
-Nevertheless, ``cleanliness''/``neatness``  of results (i.e. the signal-cluster
-to noise-cluster ration)\todo{if you know what I mean} depends on how many
-events correlating with an assumed perceptual process the stimulus provides and
-to the extent to which a naturalistic stimulus' multi-dimensionality is
-annotated and statistically controlled.
+Thus, our model-driven approach to operationalize spatial perception based on stimulus
+annotations reveals focussed activation patterns in networks that are implicated
+in visual spatial perception and cognition.
 
@@
 
+This research was, in part, supported by the German Federal Ministry of
+Education and Research (BMBF, 01GQ1112) and the US National Science Foundation
+(NSF, 1129855). Work on the data-sharing technology employed for this research
+was supported by BMBF (01GQ1411, 01GQ1905) and NSF (1429999, 1912266).
+
 \section*{Competing financial interests}

### 2021-02-16 paper/main.tex
Cut abstract to size (168 of 170 words)

@@
 % present compelling new findings & conclusions derived from published.
-Neuroimaging studies have parcellated the human brain into distinct functional
-areas.
 % PPA
-A region in the human hippocampal cortex termed ``parahippocampal place area''
-is classically considered to be a higher visual area as increased hemodynamic
-activity in the PPA correlates with the perception of static pictures of
-landscapes compared to pictures of faces or objects.
+The ``parahippocampal place area'' (PPA)
+is a visual area in the human ventral stream with increased hemodynamic
+activity correlated with the perception of landscape photos compared to faces or objects.
 % AV, AD: operationalization
-In this study, we explore different ways to operationalize the perception of
-spatial information in 14 subjects that were watching an audio-visual Hollywood
-movie and listened to the movie's audio-description (studyforrest.org).
+Here we investigate the perception of
+spatial information in 14 individuals from the open-data resource \textit{studyforrest.org}
+that were watching a two-hour Hollywood
+movie and listened to the movie's audio-description.
 % auditory localizer?
-Focussing on the audio-description, we test if an auditory narrative could
-localize a ``visual area'' in individual subjects.
+%in order to explore if a naturalistic auditory narrative could be used
+%to localize a ``visual area''.
 % GLM
-For each naturalistic stimulus, we model hemodynamic activity via several
-general linear model (GLM) $t$-contrasts that are based on annotations of
-selected stimulus features.
+We model hemodynamic activity based on annotations of selected stimulus features,
 % VIS
-Current results are compared to results of classic visual localizer experiment
-that we conducted previously to localize the PPA in the same participants.
+and compare results to a block-design visual localizer.
 % no refs in abstract (probably)
 %\citep{sengupata2016extension}.  results: group AV
-On a group level, results for a visual movie stimulus show significantly
-increased hemodynamic activity spatially overlapping with a traditionally
-localized PPA but also extending into earlier visual cortices.
+On a group level, a movie stimulus is associated with
+increased activation spatially overlapping with a traditionally
+localized PPA.
 % results: group AD
-Results for the audio-description stimulus reveal significant activation
-restricted to the anterior part of the PPA.
+In contrast, activation for an auditory stimulus is more restricted
+to the anterior PPA.
 % results: individual AD
-On an individual level, results of the audio-description show significant
-bilateral clusters in the anterior PPA of nine subjects and significant
-unilateral clusters in two subjects.
+On an individual level, hemodynamic responses
+form bilateral clusters in the PPA of nine individuals and unilateral
+clusters in another two.
 % conclusion: generalizability
-Results suggest that increased activation in the PPA during the perception of
-static pictures generalizes to the perception of spatial information embedded in
-an audio-visual movie and an exclusively auditory stimulus.
+Results suggest that activation in the PPA generalizes beyond
+pictures of landscapes to spatial information embedded in
+a naturalistic movie and even an auditory narrative, and may
 % conclusion: PPA has subregions
-Our results provide further evidence that the PPA can be divided into functional
-subregions.
+call for considering a functional subdivision of the PPA.
 \end{abstract}

### 2021-02-16 paper/main.tex
Streamline Intro; remove results

@@
 % brain mapping via fMRI
-Humans can perceive and make sense of their daily environment casually and
-seemingly without any effort.
-%
 Studies in the field of neuropsychology and neuroimaging (e.g.
@@
 landscapes \citep{ocraven2000mental} and haptic exploration of scenes
-constructed from LEGO blocks \citep{wolbers2011modality}.
+constructed from LEGO blocks \citep{wolbers2011modality}.\todo{cite Lescroart \&Gallant,
+Human Scene-Selective Areas Represent 3D Configurations of Surfaces, Neuron, 2019;
+semi-naturalistic, but not taskfree, 800+ stimulus, not "a small set", 6 subjects}
 % O'Craven: watching pictures
@@
 In this study, we investigate if increased hemodynamic activity in the PPA that
-is usually revealed by contrasting blocks of pictures can also be revealed under
+is usually detected by contrasting blocks of pictures can also be revealed under
 more ecologically conditions.
@@
 % AV stimulus
-The operationalization of visual perception is based on an annotation of cuts
-and depicted locations in the audio-visual movie ``Forrest Gump''.
+The operationalization of visual spatial perception is based on an annotation of cuts
+and depicted locations in the audio-visual movie ``Forrest Gump'', while
 % AD stimulus
-The operationalization of auditory perception is based on an annotation of
-speech occurring in the movie's audio-description.
+non-visual spatial perception is investigated using an annotation of
+spatial references in the speech occurring in the movie's audio-description.
 % GLM contrasts
-We then created several general linear model (GLM) contrasts to analyze the
-corresponding publicly available fMRI datasets of each naturalistic stimulus
-\citep{hanke2016simultaneous, hanke2014audiomovie}
-(\href{http://www.studyforrest.org}{studyforrest.org}).
+We applied model-based, mass-univariate analyses to a series of datasets
+with BOLD fMRI data from naturalistic and conventional block-design stimulation
+from the same set of participants, available from the open-data resource
+\href{http://www.studyforrest.org}{studyforrest.org}
+\citep{hanke2016simultaneous, hanke2014audiomovie, sengupta2016extension}.
 
@@
 We hypothesized that whole-brain analyses would reveal increased hemodynamic
-activity spatially constrained to the PPA as functionally defined by a
-traditional visual localizer experiment done with the same subjects
-\citep{sengupta2016extension}.
+activity in the PPA as functionally defined by a
+conventional visual localizer for each individual, because all three operationalization capitalize
+on events that should evoke the cognitive processing of spatial information.
 % hypo b: individuals
-Further, we hypothesized that an exclusively auditory stimulus could localize a
-``visual area'' in individual subjects.
+We hypothesized further that an exclusively auditory stimulus could localize a
+``visual area'' in individual subjects,
 % application in individuals
-An auditory stimulus substituting a visual experiment would be more practicable
-to asses brain functions in visually impaired persons.
-% results: group
-On a group average level,
-% operationalization in naturalistic stimuli
-results demonstrate that our approach to operationalize spatial perception
-during two naturalistic stimuli lead to increased hemodynamic activity in the
-PPA.
-% anterior vs. posterior
-On both a group and individual subject level, the comparison of results from the
-three datasets also suggests functional differences between the anterior and
-posterior PPA.
-% what does it mean
-The current data add evidence to the hypothesis that the PPA might consist of
-submodules that work together during visual perception of landscapes (cf.
-\citep{baldassano2013differential}).
-%
-Lastly, our results suggest that the PPA's anterior part can be localized in
-individual subjects by contrasting high-level semantic information occurring in
-an auditory naturalistic stimulus.
+and may offer an alternative paradigm to assess this aspect of brain function
+in visually impaired individuals.
+
+% DISABLE RESULTS
+%% results: group
+%On a group average level,
+%% operationalization in naturalistic stimuli
+%results demonstrate that our approach to operationalize spatial perception
+%during two naturalistic stimuli lead to increased hemodynamic activity in the
+%PPA.
+%% anterior vs. posterior
+%On both a group and individual subject level, the comparison of results from the
+%three datasets also suggests functional differences between the anterior and
+%posterior PPA.
+%% what does it mean
+%The current data add evidence to the hypothesis that the PPA might consist of
+%submodules that work together during visual perception of landscapes (cf.
+%\citep{baldassano2013differential}).
+%%
+%Lastly, our results suggest that the PPA's anterior part can be localized in
+%individual subjects by contrasting high-level semantic information occurring in
+%an auditory naturalistic stimulus.
 

### 2021-02-16 paper/main.tex
Incomplete Results pass

@@
 \citep{hanke2016simultaneous, hanke2014audiomovie, sengupta2016extension}.
+\todo{cite Häusler \& Hanke 2021}
 
@@
 % group level
-On a group average level, we compare results gained from whole-brain GLM
-analyses of the movie and the audio-description to results gained from a
+On a group average level, we compare results from whole-brain GLM
+analyses of the movie and the audio-description to a
 traditional visual localizer \citep{sengupta2016extension}.
 % individual level
-On the level single subjects, we also assess the performance of the exclusively
-auditory naturalistic stimulus as a substitute for a visual paradigm to localize
-the PPA.
+For each individual, we also compared the activation pattern from
+naturalistic auditory stimulation to the individual PPA localization
+with a block-design stimulus.
 % NeuroVault
@@
 space) can found at
-\href{https://neurovault.org/collections/KADGMGVZ/}{NeuroVault}.
+\href{https://neurovault.org/collections/KADGMGVZ/}{\url{neurovault.org/collections/KADGMGVZ}}.
 % reference to supplemental material
 Results and discussion of the additional contrasts (PPA and negative controls)
-can be found in the supplemental material
+can be found in the supplemental material. \todo{check if redundant with later refs}
 

### 2021-02-16 paper/main.tex
add note to Wolbers (2011)

@@
 Increased hemodynamic activity in the PPA generalizes to mental imagination of
-landscapes \citep{ocraven2000mental} and haptic exploration of scenes
-constructed from LEGO blocks \citep{wolbers2011modality}.\todo{cite Lescroart \&Gallant,
-Human Scene-Selective Areas Represent 3D Configurations of Surfaces, Neuron, 2019;
-semi-naturalistic, but not taskfree, 800+ stimulus, not "a small set", 6 subjects}
+landscapes \citep{ocraven2000mental}, and haptic exploration of scenes
+constructed from LEGO blocks \citep{wolbers2011modality}.\todo{cite Lescroart
+    \&Gallant, Human Scene-Selective Areas Represent 3D Configurations of
+    Surfaces, Neuron, 2019; semi-naturalistic, but not taskfree, 800+ stimulus,
+not "a small set", 6 subjects}
 % O'Craven: watching pictures
@@
 In a block design study conducted by \cite{wolbers2011modality} the PPA of
-participants showed increased activation during a delayed
-match-to-sample task of haptically explored scenes constructed from LEGO bricks
-compared to abstract geometric objects.
+sighted as well as blind participants showed increased activation during a
+delayed match-to-sample task of haptically explored scenes constructed from LEGO
+bricks compared to abstract geometric objects.
 % Wolbers: connectivity analysis

### 2021-02-16 paper/main.tex
add note regarding whole-brain in intro

@@
 % AV stimulus
-The operationalization of visual spatial perception is based on an annotation of cuts
-and depicted locations in the audio-visual movie ``Forrest Gump'', while
+The operationalization of visual spatial perception is based on an annotation of
+cuts and depicted locations in the audio-visual movie ``Forrest Gump'', while
 % AD stimulus
-non-visual spatial perception is investigated using an annotation of
-spatial references in the speech occurring in the movie's audio-description.
+non-visual spatial perception is investigated using an annotation of spatial
+references in the speech occurring in the movie's audio-description.
 % GLM contrasts
-We applied model-based, mass-univariate analyses to a series of datasets
-with BOLD fMRI data from naturalistic and conventional block-design stimulation
-from the same set of participants, available from the open-data resource
-\href{http://www.studyforrest.org}{studyforrest.org}
+We applied whole-brain, model-based, mass-univariate analyses to a series of
+datasets with BOLD fMRI data from naturalistic and conventional block-design
+stimulation from the same set of participants, available from the open-data
+resource \href{http://www.studyforrest.org}{studyforrest.org}
 \citep{hanke2016simultaneous, hanke2014audiomovie, sengupta2016extension}.
@@
 % encouraged by that we build contrasts (statement)
-As a result, we felt encouraged to create voxel-wise GLM $t$-contrasts similarly
-to previous studies that used controlled stimuli.
+As a result, we felt encouraged to create voxel-wise general linear model (GLM)
+$t$-contrasts similarly to previous studies that used controlled stimuli.
 
@@
 We tested our modeled hemodynamic responses based on stimulus annotations by
-conducting standard two-level general linear model (GLM) analyses to create
+conducting standard two-level GLM analyses to create
 subject-specific results across the 8 segments for every subject and each
@@
 % current study: similar
-In line with previous studies, we operationalized spatial perception via general
-linear model (GLM) $t$-contrasts.
+In line with previous studies, we operationalized spatial perception via GLM $t$-contrasts.
 % current study: dissimilar

### 2021-02-16 paper/main.tex
intro: add references to annotations

@@
 Increased hemodynamic activity in the PPA generalizes to mental imagination of
-landscapes \citep{ocraven2000mental}, and haptic exploration of scenes
-constructed from LEGO blocks \citep{wolbers2011modality}.\todo{cite Lescroart
-    \&Gallant, Human Scene-Selective Areas Represent 3D Configurations of
-    Surfaces, Neuron, 2019; semi-naturalistic, but not taskfree, 800+ stimulus,
-not "a small set", 6 subjects}
+landscapes \citep{ocraven2000mental}, haptic exploration of scenes
+constructed from LEGO blocks \citep{wolbers2011modality} and scene-related
+sounds \citep{van2017development}.\todo{reading the paper: activation is
+non-significant, lol}
+% van der Hurk: 64 sounds x 1.8 seconds; 20 sighted, 14 congenitally blind
+\todo{cite Lescroart (2019). semi-naturalistic, but task, 800+ stimulus, N=6}
 % O'Craven: watching pictures
@@
 The operationalization of visual spatial perception is based on an annotation of
-cuts and depicted locations in the audio-visual movie ``Forrest Gump'', while
+cuts and depicted locations \citep{haeusler2016cutanno} in the audio-visual
+movie ``Forrest Gump'', while
 % AD stimulus
-non-visual spatial perception is investigated using an annotation of spatial
-references in the speech occurring in the movie's audio-description.
+the operationalization of non-visual spatial perception is based on an
+annotation of speech \citep{hausler2021studyforrest} occurring in the movie's
+audio-description.
 % GLM contrasts

### 2021-02-16 paper/main.tex
revise abstract (still <170)

@@
 % our audience highlighting innovative examples of data reuse may be used to
-% present compelling new findings & conclusions derived from published.
-% PPA
-The ``parahippocampal place area'' (PPA)
-is a visual area in the human ventral stream with increased hemodynamic
-activity correlated with the perception of landscape photos compared to faces or objects.
+% present compelling new findings & conclusions derived from published.  PPA
+The ``parahippocampal place area'' (PPA) in the human ventral visual stream
+exhibits increased hemodynamic activity correlated with the perception of
+landscape photos compared to faces or objects.
 % AV, AD: operationalization
-Here we investigate the perception of
-spatial information in 14 individuals from the open-data resource \textit{studyforrest.org}
-that were watching a two-hour Hollywood
-movie and listened to the movie's audio-description.
+Here, we investigate the perception of spatial information in 14 individuals
+watching a two-hour Hollywood movie and listening to the movie's
+audio-description as part of the open-data resource \textit{studyforrest.org}.
 % auditory localizer?
-%in order to explore if a naturalistic auditory narrative could be used
-%to localize a ``visual area''.
-% GLM
-We model hemodynamic activity based on annotations of selected stimulus features,
+%in order to explore if a naturalistic auditory narrative could be used to
+%localize a ``visual area''.  GLM
+We model hemodynamic activity based on annotations of selected stimulus
+features,
 % VIS
@@
 %\citep{sengupata2016extension}.  results: group AV
-On a group level, a movie stimulus is associated with
-increased activation spatially overlapping with a traditionally
-localized PPA.
+On a group level, increased activation correlating with spatial information
+occcuring in the movie is overlapping with a traditionally localized PPA.
 % results: group AD
-In contrast, activation for an auditory stimulus is more restricted
-to the anterior PPA.
+Activation correlating with semantic spatial information occurring in the
+audio-description is more restricted to the anterior PPA.
 % results: individual AD
-On an individual level, hemodynamic responses
-form bilateral clusters in the PPA of nine individuals and unilateral
-clusters in another two.
+On an individual level, we find signficant bilateral activity in the PPA
+of nine individuals and unilateral activity in one individual.
 % conclusion: generalizability
-Results suggest that activation in the PPA generalizes beyond
-pictures of landscapes to spatial information embedded in
-a naturalistic movie and even an auditory narrative, and may
+Results suggest that activation in the PPA generalizes to spatial information
+embedded in a movie and spatial information in an auditory narrative, and may
 % conclusion: PPA has subregions
-call for considering a functional subdivision of the PPA.
-\end{abstract}
+call for considering a functional subdivision of the PPA.  \end{abstract}
 
@@
 The operationalization of visual spatial perception is based on an annotation of
-cuts and depicted locations \citep{haeusler2016cutanno} in the audio-visual
-movie ``Forrest Gump'', while
+cuts and depicted locations in the audio-visual movie ``Forrest Gump''
+\citep{haeusler2016cutanno}, while
 % AD stimulus
 the operationalization of non-visual spatial perception is based on an
-annotation of speech \citep{hausler2021studyforrest} occurring in the movie's
-audio-description.
+annotation of speech occurring in the movie's audio-description
+\citep{hausler2021studyforrest}.
 % GLM contrasts
@@
 \citep{hanke2016simultaneous, hanke2014audiomovie, sengupta2016extension}.
-\todo{cite Häusler \& Hanke 2021}
 

### 2021-02-16 paper/main.tex
shorten p-values

@@
 \section*{Plan}
+
+\noindent General
+\begin{itemize}
+    \item van den Hurk (2017): uses sounds (1.8sec); one-back-task; no
+        significant results; but ``sensitivity maps'' and cross-modal and
+        cross-subject classification; mentions in a half sentence ``the auditory
+        trials might activate only a subset of voxels that contain categorical
+        information, whereas the visual trials activate the majority of VTC
+        voxels''.
+\end{itemize}
 
@@
 \tabularnewline
-    furniture & movable furniture (insides \& outsides) & bench, bed, table,
-    chair
+furniture & movable furniture (insides \& outsides) & bench, bed, table, chair
 \tabularnewline
@@
 % AD regressors in AV AD design matrix
-For the first level analysis of the audio-description stimulus, the modeled hemodynamic
-responses related to all noun categories and the two low-level perceptual
-confounds were included.
+For the first level analysis of the audio-description stimulus, the modeled
+hemodynamic responses related to all noun categories and the two low-level
+perceptual confounds were included.
 % AD regressors in AV
-To create a contrasts of cross-modal control in the analysis of the movie stimulus,
-we also implemented the regressors based on nouns used by the
+To create a contrasts of cross-modal control in the analysis of the movie
+stimulus, we also implemented the regressors based on nouns used by the
 audio-description's narrator to indicate a switch to another setting (categories
@@
 % AV regressors in AV
-To create contrasts of cross-modal negative control in the analysis of the audio-description
-stimulus, we also implemented the movie cut-related regressors
+To create contrasts of cross-modal negative control in the analysis of the
+audio-description stimulus, we also implemented the movie cut-related regressors
 (excluding \texttt{no\_cut}).
@@
 \midrule
-3003 & 0 & 5.31 & 22.5 & -45.5 & -12 & 4.53 & -63.3 & -3.72 & r. lingual g.; r.
+3003 & <.00001 & 5.31 & 22.5 & -45.5 & -12 & 4.53 & -63.3 & -3.72 & r. lingual g.; r.
 cuneal c., intracalcarine c., bilaterally occipital fusiform g., precuneus,temporal fusiform c., posterior parahippocampal c.  \\
-154 & 0.000000656 & 4.46 & -35 & -83 & 28 & -32.8 & -86.2 & 21.4 & l. superior lateral occipital c. \\
-121 & 0.00000769 & 4.65 & 25 & -80.5 & 25.5 & 23.7 & -83.8 & 25.4 & r. superior lateral occipital cortex \\
+154 & <.00001 & 4.46 & -35 & -83 & 28 & -32.8 & -86.2 & 21.4 & l. superior
+lateral occipital c. \\ % 0.000000656
+121 & <.00001 & 4.65 & 25 & -80.5 & 25.5 & 23.7 & -83.8 & 25.4 & r. superior
+lateral occipital cortex \\ % 0.00000769
 \bottomrule
@@
 \midrule
-188 & 0.0000000596 & 4.48 & -17.5 & -65.5 & 25.5 & -14.7 & -59.1 & 15.2 & l. precuneus \\
-164 & 0.000000238 & 4.47 & 17.5 & -58 & 23 & 15.6 & -55.6 & 16 & r. precuneus; \\
-83 & 0.000128 & 4.48 & 27.5 & -43 & -17 & 27.2 & -41.1 & -14 & r. temporal (occipital) fusiform c.; posterior parahippocampal g. \\
-73 & 0.000318 & 3.93 & -22.5 & -43 & -12 & -23.9 & -43.6 & -11.2 & l. lingual g.; temporal (occipital) fusiform g., posterior parahippocampal c. \\
-63 & 0.000824 & 4.1 & 40 & -75.5 & 30.5 & 40.9 & -76.3 & 28.6 & r. superior lateral occipital c. \\
-37 & 0.0129 & 4.24 & -37.5 & -78 & 33 & -38.4 & -79.5 & 28.9 & l. superior lateral occipital c. \\
+188 & <.00001 & 4.48 & -17.5 & -65.5 & 25.5 & -14.7 & -59.1 & 15.2 & l.
+precuneus \\ % 0.0000000596
+164 & <.00001 & 4.47 & 17.5 & -58 & 23 & 15.6 & -55.6 & 16 & r. precuneus;
+\\ % 0.000000238
+83 & .00013 & 4.48 & 27.5 & -43 & -17 & 27.2 & -41.1 & -14 & r. temporal
+(occipital) fusiform c.; posterior parahippocampal g. \\ % 0.000128
+73 & .00031 & 3.93 & -22.5 & -43 & -12 & -23.9 & -43.6 & -11.2 & l. lingual
+g.; temporal (occipital) fusiform g., posterior parahippocampal c. \\ % 0.000128
+63 & .00082 & 4.1 & 40 & -75.5 & 30.5 & 40.9 & -76.3 & 28.6 & r. superior
+lateral occipital c. \\ % 0.000824
+37 & .0129 & 4.24 & -37.5 & -78 & 33 & -38.4 & -79.5 & 28.9 & l. superior
+lateral occipital c. \\ % 0.0129
 \bottomrule
@@
 % group AV
-On a group level, whole brain-analysis results for the audio-visual movie show
+On a group level, results for the audio-visual movie show
 significantly increased hemodynamic activity spatially overlapping with a
@@
 % hypothesis
-Encouraged by \citep{aziz2008modulation}, we hypothesized that spatial
-information embedded in the audio-description stimulus would correlate with increased
-hemodynamic activity in the PPA.
+Encouraged by \citep{aziz2008modulation}, we hypothesized that semantic spatial
+information embedded in the audio-description stimulus would correlate with
+increased hemodynamic activity in the PPA.
 % diff to Aziz (2008)
@@
 % we did not choose se\_new and se\_old
-In the audio-description's primary contrast, we did not include the categories that contained
-switches from one setting to another (\texttt{se\_new} and \texttt{se\_old})
-which one might assume to contain the auditory equivalent to pictures of
-landscapes.
+In the audio-description's primary contrast, we did not include the categories
+that contained switches from one setting to another (\texttt{se\_new} and
+\texttt{se\_old}) which one might assume to contain the auditory equivalent to
+pictures of landscapes.
 % why

### 2021-02-16 paper/main.tex
draft of Code Availability and Data Citations

@@
 
-\noindent Data Citations, Code Availability, Data Availability
-
+\noindent Data Citations, Code Availability
 \begin{itemize}
@@
 
-\subsection*{Code availability}
-
-\todo[inline]{provide supporting source code; explain how/where other may
-access data underlying the analysis}
-
-\todo[inline]{if using custom code for dataset generation/processing: indicate
-how code can be accessed (including restrictions to access)}
-
-\todo[inline]{include infos on versions of used software}
-
-\todo[inline]{any specific variables or parameters used to generate, test, or process the current dataset?}
+\subsection*{Data and code availability}
+
+Raw data, analysis scripts, and results: TBA. Zenodo (registered but zipped)
+vs. OSF (datalad dataset but probably unregistered)
 
@@
 
-\todo[inline]{clean the PPA dataset; upload as zip to zalando again?}
-
-Bibliographic information for the data records described in the manuscript.
-
-1. Lastname1, Initial1., Lastname2, Initial2., ...\& LastnameN, InitialN. \emph{Repository name} Dataset accession number or DOI (YYYY).
-
 % cut anno
-\citep{haeusler2016cutanno}
+1. Häusler, C. O. \& Hanke M. Dataset 1 in: An annotation of cuts, depicted
+locations, and temporal progression in the motion picture "Forrest Gump".
+\emph{F1000Research}
+\href{https://doi.org/10.5256/f1000research.9536.d134823}{10.5256/f1000research.9536.d134823}
+(2016)
+
 % speech anno
-\citep{hausler2021studyforrest}
+2. Häusler, C. O. \& Hanke M. \emph{OSF}
+\href{https://doi.org/10.17605/OSF.IO/GFRME}{10.5256/f1000research.9536.d134823}
+(2020).
+
 % audio-description
-\citep{hanke2014audiomovie}
-% movie
-\citep{hanke2016simultaneous}
-% localizer
-\citep{sengupta2016extension}
+3. Hanke, M., Baumgartner, F. J., Ibe, P., Kaule, F. R., Pollmann, S., Speck,
+O., Zinke, W. \& Stadler, J. \emph{OpenNEURO}
+\href{https://openneuro.org/datasets/ds000113}{ds000113} (2014). \todo{4
+datasets \& using authors/year of the audio-description}
 

### 2021-02-16 paper/main.tex
rewrite plan

@@
 \begin{itemize}
-    \item tables: round p-values to ? MIH: I would say 4 digits, but I can find internet
-      recommendations for 3. That would mean anything less than 0.001 is reported as '<.001',
-      and the rest as the precise value. This should only apply to corrected p-values.
-      For an uncorrected p-value 0.001 is very high.
+    \item tables: I (initially) rounded p-values to <.00001
 \end{itemize}
@@
 \begin{itemize}
-    \item https://www.springernature.com/gp/authors/research-data-policy/data-availability-statements/12330880i
-    \item cf. other Scientific Data analysis paper
+    \item draft for Data Citation is done
+    \item draft for Code and Data Availability is done (other analysis paper do
+        it pretty amateurish); will look at the ``how to write an excellent
+        data availability statement'' at springernature.com
 \end{itemize}
@@
 
-Raw data, analysis scripts, and results: TBA. Zenodo (registered but zipped)
-vs. OSF (datalad dataset but probably unregistered)
+% Zenodo (registered but zipped) vs. OSF (datalad dataset but probably
+% unregistered)
+Raw data, analysis scripts to generate the results from the raw data as well as
+the results are available from *TBA*, and accessible as Datalad
+(RRID:SCR_003931) datasets.
 

### 2021-02-16 paper/main.tex
rewrite data & code availability

@@
 % unregistered)
-Raw data, analysis scripts to generate the results from the raw data as well as
-the results are available from *TBA*, and accessible as Datalad
-(RRID:SCR_003931) datasets.
+The fMRI and annotation data, analysis scripts to generate the results as well
+as results are available in the [NAME] repository, [PERSISTENT WEB LINK],
+accessible as Datalad (RRID:SCR_003931) datasets.
 

### 2021-02-17 paper/main.tex
Subject -> Participant

--- 2021-02-16 paper/main.tex
@@
 
-\noindent General
-\begin{itemize}
-    \item van den Hurk (2017): uses sounds (1.8sec); one-back-task; no
-        significant results; but ``sensitivity maps'' and cross-modal and
-        cross-subject classification; mentions in a half sentence ``the auditory
-        trials might activate only a subset of voxels that contain categorical
-        information, whereas the visual trials activate the majority of VTC
-        voxels''.
-\end{itemize}
-
 \noindent Method
@@
 
-\noindent Data Citations, Code Availability
+\noindent Data Citations, Code Availability, Data Availability
+
 \begin{itemize}
@@
 % neural correlate of scene perception
-Increased hemodynamic activity is observed in the PPA when subjects view
+Increased hemodynamic activity is observed in the PPA when participants view
 pictures of landscapes, buildings or landmarks (compared to e.g. pictures of
@@
 hasson2004intersubject} because they poorly resemble how we, free of an
-explicit perceptual task, experience our rich/multidimensional and continuous
+explicit perceptual task, experience our rich, multidimensional and continuous
 environment that our brains are accommodated to
@@
 % paradigm.
-Third, the reviewed studies averaged results across 7-11 subjects.
+Third, the reviewed studies averaged results across 7-11 participants.
 % averaging pros and cons
@@
 We hypothesized further that an exclusively auditory stimulus could localize a
-``visual area'' in individual subjects,
+``visual area'' in individuals,
 % application in individuals
@@
 % used studies
-The same subjects were
+The same participants were
 % AD
@@
 % procedure: presentation & instructions
-During the experiment, subjects were presented with four block-design runs, with
+During the experiment, participants were presented with four block-design runs, with
 two \unit[16]{s} blocks per stimulus category in each run.
@@
 % task
-Subjects also performed a one-back matching task to keep them attentive.
+Participants also performed a one-back matching task to keep them attentive.
 
@@
 \tabularnewline
-furniture & movable furniture (insides \& outsides) & bench, bed, table, chair
+    furniture & movable furniture (insides \& outsides) & bench, bed, table,
+    chair
 \tabularnewline
@@
 % AD regressors in AV AD design matrix
-For the first level analysis of the audio-description stimulus, the modeled
-hemodynamic responses related to all noun categories and the two low-level
-perceptual confounds were included.
+For the first level analysis of the audio-description stimulus, the modeled hemodynamic
+responses related to all noun categories and the two low-level perceptual
+confounds were included.
 % AD regressors in AV
-To create a contrasts of cross-modal control in the analysis of the movie
-stimulus, we also implemented the regressors based on nouns used by the
+To create a contrasts of cross-modal control in the analysis of the movie stimulus,
+we also implemented the regressors based on nouns used by the
 audio-description's narrator to indicate a switch to another setting (categories
@@
 % AV regressors in AV
-To create contrasts of cross-modal negative control in the analysis of the
-audio-description stimulus, we also implemented the movie cut-related regressors
+To create contrasts of cross-modal negative control in the analysis of the audio-description
+stimulus, we also implemented the movie cut-related regressors
 (excluding \texttt{no\_cut}).
@@
 conducting standard two-level GLM analyses to create
-subject-specific results across the 8 segments for every subject and each
+participant-specific results across the 8 segments for every participant and each
 stimulus.
 % level 3
-Subsequent, third-level analyses averaged contrast estimates over subjects.
+Subsequent, third-level analyses averaged contrast estimates over participants.
 
@@
 The GLM analysis that fitted each voxel's time course separately for each
-subject and segment was performed in functional space preserving the orientation
+participant and segment was performed in functional space preserving the orientation
 of the EPI images.
 % two ways of co-registration
-Subject-specific BOLD T2* time series were anatomically co-registered in two
+Participant-specific BOLD T2* time series were anatomically co-registered in two
 ways:
@@
 % \href{"https://github.com/psychoinformatics-de/studyforrest-data-templatetransforms/blob/master/sub-01/bold3Tp2/brain.nii.gz"}{example})
-a) via linear transformation to a subject-specific, study-specific T2* template
+a) via linear transformation to a participant-specific, study-specific T2* template
 (cf. \citep{sengupta2016extension}), and
@@
 % third level model
-The third level analysis which averaged contrast estimates over subjects was
+The third level analysis which averaged contrast estimates over participants was
 carried out using FLAME stage 1 with automatic outlier detection
@@
 \midrule
-3003 & <.00001 & 5.31 & 22.5 & -45.5 & -12 & 4.53 & -63.3 & -3.72 & r. lingual g.; r.
+3003 & 0 & 5.31 & 22.5 & -45.5 & -12 & 4.53 & -63.3 & -3.72 & r. lingual g.; r.
 cuneal c., intracalcarine c., bilaterally occipital fusiform g., precuneus,temporal fusiform c., posterior parahippocampal c.  \\
-154 & <.00001 & 4.46 & -35 & -83 & 28 & -32.8 & -86.2 & 21.4 & l. superior
-lateral occipital c. \\ % 0.000000656
-121 & <.00001 & 4.65 & 25 & -80.5 & 25.5 & 23.7 & -83.8 & 25.4 & r. superior
-lateral occipital cortex \\ % 0.00000769
+154 & 0.000000656 & 4.46 & -35 & -83 & 28 & -32.8 & -86.2 & 21.4 & l. superior lateral occipital c. \\
+121 & 0.00000769 & 4.65 & 25 & -80.5 & 25.5 & 23.7 & -83.8 & 25.4 & r. superior lateral occipital cortex \\
 \bottomrule
@@
 \midrule
-188 & <.00001 & 4.48 & -17.5 & -65.5 & 25.5 & -14.7 & -59.1 & 15.2 & l.
-precuneus \\ % 0.0000000596
-164 & <.00001 & 4.47 & 17.5 & -58 & 23 & 15.6 & -55.6 & 16 & r. precuneus;
-\\ % 0.000000238
-83 & .00013 & 4.48 & 27.5 & -43 & -17 & 27.2 & -41.1 & -14 & r. temporal
-(occipital) fusiform c.; posterior parahippocampal g. \\ % 0.000128
-73 & .00031 & 3.93 & -22.5 & -43 & -12 & -23.9 & -43.6 & -11.2 & l. lingual
-g.; temporal (occipital) fusiform g., posterior parahippocampal c. \\ % 0.000128
-63 & .00082 & 4.1 & 40 & -75.5 & 30.5 & 40.9 & -76.3 & 28.6 & r. superior
-lateral occipital c. \\ % 0.000824
-37 & .0129 & 4.24 & -37.5 & -78 & 33 & -38.4 & -79.5 & 28.9 & l. superior
-lateral occipital c. \\ % 0.0129
+188 & 0.0000000596 & 4.48 & -17.5 & -65.5 & 25.5 & -14.7 & -59.1 & 15.2 & l. precuneus \\
+164 & 0.000000238 & 4.47 & 17.5 & -58 & 23 & 15.6 & -55.6 & 16 & r. precuneus; \\
+83 & 0.000128 & 4.48 & 27.5 & -43 & -17 & 27.2 & -41.1 & -14 & r. temporal (occipital) fusiform c.; posterior parahippocampal g. \\
+73 & 0.000318 & 3.93 & -22.5 & -43 & -12 & -23.9 & -43.6 & -11.2 & l. lingual g.; temporal (occipital) fusiform g., posterior parahippocampal c. \\
+63 & 0.000824 & 4.1 & 40 & -75.5 & 30.5 & 40.9 & -76.3 & 28.6 & r. superior lateral occipital c. \\
+37 & 0.0129 & 4.24 & -37.5 & -78 & 33 & -38.4 & -79.5 & 28.9 & l. superior lateral occipital c. \\
 \bottomrule
@@
 Third, we investigated result from both naturalistic paradigms on the level of
-individual subjects to ensure that the group results are not just a by-product
+individual participants to ensure that the group results are not just a by-product
 of the averaging process.
@@
 Further, we hypothesized that an exclusively auditory stimulus could localize
-the PPA in individual subjects and thus possibly substitute a classic visual
+the PPA in individual participants and thus possibly substitute a classic visual
 localizer experiment.
@@
 The visual localizer yielded bilateral parahippocampal clusters in 12 of 14
-subjects and an unilateral right clusters in two subjects (cf. Table 3 in
+participants and an unilateral right clusters in two participants (cf. Table 3 in
 \citep{sengupta2016extension}).
@@
 Contrary to \citep{sengupta2016extension}, we here used the same contrast of
-each naturalistic stimulus and the same threshold for all subjects.
+each naturalistic stimulus and the same threshold for all participants.
 % subject space -> NeuroVault
-Results of the analyses that were performed in subject-space can be found in the
+Results of the analyses that were performed in participant-space can be found in the
 accompanying dataset (Z>2.3, p<.05 cluster-corrected).
 % here report in group space
-For better comparisons of subjects, we here report results from the analyses
+For better comparisons of participants, we here report results from the analyses
 performed in group space (Z>3.4, p<.05 cluster-corrected).
@@
 Transversal slice of z=-11 was chosen as it depicts voxels of
-significant clusters in almost all subjects.
+significant clusters in almost all participants.
 
 % AV
-Results of the primary movie contrast yielded bilateral clusters in five subjects,
-a unilateral right cluster in six subjects (of which one subjects yielded a
+Results of the primary movie contrast yielded bilateral clusters in five participants,
+a unilateral right cluster in six participants (of which one participant yielded a
 unilateral cluster in the visual localizer), and a unilateral left cluster in
-one subject.
+one participant.
 % difference to dedicated localizer
@@
 % report here in group
-Results of the primary audio-description contrast yielded bilateral clusters in nine subjects
+Results of the primary audio-description contrast yielded bilateral clusters in nine participants
 that are within or overlapping with the individual PPA.
@@
         Black:
-        outline of subject-specific PPA ROIs.
+        outline of participant-specific PPA ROIs.
         Light gray: The
         audio-description's field of view (cf. \citep{hanke2014audiomovie}).
-        To facilitate comparisons across subjects, we chose the same horizontal
-        slice (x=-11) for all subjects as this slice depicts voxels of
-        significant clusters in almost all subjects.
+        To facilitate comparisons across participants, we chose the same horizontal
+        slice (x=-11) for all participants as this slice depicts voxels of
+        significant clusters in almost all participants.
         The figure does not show voxels of the left cluster of the movie stimulus
@@
 localizer and the primary audio-description contrast, we created a Bland-Altman-Plot for every
-subject (see Figure \ref{fig:bland-altman}).
+participant (see Figure \ref{fig:bland-altman}).
 % what it depicts
@@
     \includegraphics[scale=0.27]{figures/subjs_bland-altman.png}
-    \caption{Bland-Altman-Plots for individual subjects.
+    \caption{Bland-Altman-Plots for individual participants.
     The x-axes show the means of two spatially corresponding voxels in the
@@
     Histological Atlas \citep{eickhoff2005toolbox, eickhoff2007assignment}),
-    PPA overlap of all subjects (blue),
+    PPA overlap of all participants (blue),
     and individual PPA(s) (red).}
@@
 % group AV
-On a group level, results for the audio-visual movie show
+On a group level, whole brain-analysis results for the audio-visual movie show
 significantly increased hemodynamic activity spatially overlapping with a
@@
 On an individual level, results of the audio-description show significant
-bilateral clusters in the anterior PPA of nine subjects and a unilateral cluster
-in one subjects.
+bilateral clusters in the anterior PPA of nine participants and a unilateral cluster
+in one participant.
 % meaning: generalization to naturalistic stimuli
@@
 An auditory narrative might substitute a visual paradigm to localize the PPAs
-anterior part in visually impaired subjects.
+anterior part in visually impaired participants.
 
@@
 Thus to control confounding variables, future studies that aim to use a movie to
-localize visual areas in individual subjects should extensively annotate the
+localize visual areas in individual participants should extensively annotate the
 content of frames (e.g.  using the open-source solution ``Pliers'' for feature
@@
 % hypothesis
-Encouraged by \citep{aziz2008modulation}, we hypothesized that semantic spatial
-information embedded in the audio-description stimulus would correlate with
-increased hemodynamic activity in the PPA.
+Encouraged by \citep{aziz2008modulation}, we hypothesized that spatial
+information embedded in the audio-description stimulus would correlate with increased
+hemodynamic activity in the PPA.
 % diff to Aziz (2008)
@@
 Usually studies that use small sets of experimentally controlled stimuli also
-employ a task to keep subjects attentive to the stimuli.
+employ a task to keep participants attentive to the stimuli.
 % but: Epstein (1998)
@@
 % we did not choose se\_new and se\_old
-In the audio-description's primary contrast, we did not include the categories
-that contained switches from one setting to another (\texttt{se\_new} and
-\texttt{se\_old}) which one might assume to contain the auditory equivalent to
-pictures of landscapes.
+In the audio-description's primary contrast, we did not include the categories that contained
+switches from one setting to another (\texttt{se\_new} and \texttt{se\_old})
+which one might assume to contain the auditory equivalent to pictures of
+landscapes.
 % why
@@
 The visual localizer \citep{sengupta2016extension} revealed bilateral ROIs in 12
-of 14 subjects and a unilateral right ROI in two subjects (sub-04, sub-20).
+of 14 participants and a unilateral right ROI in two participants (sub-04, sub-20).
 %
@@
 the same contrast and threshold (Z>3.4, p<.05 cluster-corrected) for all
-subjects.
+participants.
 % in the current study
-The audio-description yielded significant bilateral clusters in 9 of 14 subjects
+The audio-description yielded significant bilateral clusters in 9 of 14 participants
 (of which sub-04 shows only a right-lateralized PPA ROI), and a unilateral
-significant cluster in one subject.
+significant cluster in one participant.
 % similar: anterior part
@@
 can, in principle, be applied to localize (the anterior part) of a higher-level
-visual area in the majority of subjects.
+visual area in the majority of participants.
 % one threshold (and contrast) to rule them all
@@
 
-\subsection*{Data and code availability}
-
-Raw data, analysis scripts, and results: TBA. Zenodo (registered but zipped)
-vs. OSF (datalad dataset but probably unregistered)
+\subsection*{Code availability}
+
+\todo[inline]{provide supporting source code; explain how/where other may
+access data underlying the analysis}
+
+\todo[inline]{if using custom code for dataset generation/processing: indicate
+how code can be accessed (including restrictions to access)}
+
+\todo[inline]{include infos on versions of used software}
+
+\todo[inline]{any specific variables or parameters used to generate, test, or process the current dataset?}
 
@@
 
+\todo[inline]{clean the PPA dataset; upload as zip to zalando again?}
+
+Bibliographic information for the data records described in the manuscript.
+
+1. Lastname1, Initial1., Lastname2, Initial2., ...\& LastnameN, InitialN. \emph{Repository name} Dataset accession number or DOI (YYYY).
+
 % cut anno
-1. Häusler, C. O. \& Hanke M. Dataset 1 in: An annotation of cuts, depicted
-locations, and temporal progression in the motion picture "Forrest Gump".
-\emph{F1000Research}
-\href{https://doi.org/10.5256/f1000research.9536.d134823}{10.5256/f1000research.9536.d134823}
-(2016)
-
+\citep{haeusler2016cutanno}
 % speech anno
-2. Häusler, C. O. \& Hanke M. \emph{OSF}
-\href{https://doi.org/10.17605/OSF.IO/GFRME}{10.5256/f1000research.9536.d134823}
-(2020).
-
+\citep{hausler2021studyforrest}
 % audio-description
-3. Hanke, M., Baumgartner, F. J., Ibe, P., Kaule, F. R., Pollmann, S., Speck,
-O., Zinke, W. \& Stadler, J. \emph{OpenNEURO}
-\href{https://openneuro.org/datasets/ds000113}{ds000113} (2014). \todo{4
-datasets \& using authors/year of the audio-description}
+\citep{hanke2014audiomovie}
+% movie
+\citep{hanke2016simultaneous}
+% localizer
+\citep{sengupta2016extension}
 

### 2021-02-17 paper/main.tex
Less "revealing"

@@
 In this study, we investigate if increased hemodynamic activity in the PPA that
-is usually detected by contrasting blocks of pictures can also be revealed under
+is usually detected by contrasting blocks of pictures is also present under
 more ecologically conditions.

### 2021-02-17 paper/main.tex
Condense stimuli and procedure

@@
 % no refs in abstract (probably)
-%\citep{sengupata2016extension}.  results: group AV
+%\citep{sengupta2016extension}.  results: group AV
 On a group level, increased activation correlating with spatial information
@@
 part in a six-category block-design visual localizer.
-
 % participants' health
@@
 % AD & AV stimulus name & references
-We used the German DVD release \citep{ForrestGumpDVD} of the movie ``Forrest
-Gump'' \citep{ForrestGumpMovie} and its audio-description that was broadcast as
-an additional audio track for visually impaired listeners on Swiss public
-television \citep{ForrestGumpGermanAD}.
-% AV: voice-over
-The plot of the movie is already carried by a voice-over of the main character
-Forrest Gump.
+The German DVD release \citep{ForrestGumpDVD} of the movie ``Forrest Gump''
+\citep{ForrestGumpMovie} and its temporally aligned audio-description
+\citep{ForrestGumpGermanAD} served as naturalistic stimuli, with an approximate
+duration of two hours, split into eight consecutive segments of
+\unit[$\approx$15]{minutes}.
 % AD: additional narrator
-In the largely identical audio-description, an additional male narrator
-describes essential aspects of the visual scenery when there is no off-screen
-voice, dialog, or other relevant auditory content.
-
-% AD & AV: stimulus creation
-The audio-description was temporally aligned to the audio track of the German
-DVD release. A few scenes, less relevant to the main plot, were removed to create
-the ``research cut'' lasting \unit[$\approx$2]{h} \citep{hanke2014audiomovie,
-hanke2016simultaneous}.
-% further processing
-Both stimuli were further processed (filtering, volume adjustments) to improve
-audibility during MRI scanning.
-% splitting
-Each stimulus was split into eight segments of approximately \unit[15]{minutes}.
-% AD & AV: instructions
-Before the experiment, participants were instructed to inhibit physical
-movements except for eye-movements, and otherwise to simply ``enjoy'' the
-stimulus.
-% AD & AV: presentation & instructions
-Audio-description and movie segments were presented in chronological order with
-four segments in two fMRI sessions. Between sessions, participants left the
-scanner for a break with a flexible duration. Structural images were obtained
-during the first study on a day different from the fMRI session.
+The audio-description adds another male narrator to the voice-over narration of
+the main character Forrest Gump. This additional narration describes essential
+aspects of the visual scenery when there is no off-screen voice, dialog, or
+other relevant auditory content.
+% task
+For all sessions with naturalistic stimuli, participants were instructed to
+inhibit physical movements except for eye-movements, and otherwise to simply
+``enjoy'' the presentation.
+%
+For details on stimulus creation and presentation see
+\cite{hanke2014audiomovie,hanke2016simultaneous}.
 
 % VIS study picture categories
-All stimuli of the block-design localizer study were already used in a previous study
-\citep{haxby2011common}.
-%
-There were 24 unique grayscale images (s. Figure 2 in
-\citep{sengupta2016extension}) for each of six stimulus categories:
-% category details
-faces (cropped from original background presented on a medium-gray background),
-bodies (female and male without heads in clothes; medium-gray background),
-objects (e.g. binoculars, screw, chair, mug; medium-gray background), houses
-(medium-gray background) and outdoor scenes comprising of nature and street
-scenes, and phase scrambled images.
-% controlled luminance and size
-Images were matched in luminance and size of 400$\times$\unit[400]{px}.
+Stimuli for the block-design localizer study were 24 unique grayscale images of
+faces, bodies, objects, houses, outdoor scenes and scrambled images, matched in
+luminance and size, that were previously used in other studies
+\citep[e.g.,][]{haxby2011common}.
 % procedure: presentation & instructions
-During the experiment, participants were presented with four block-design runs, with
-two \unit[16]{s} blocks per stimulus category in each run.
-% temporal progression
-Each image was shown for \unit[900]{ms} and images were separated by a fixation
-cross lasting \unit[100]{ms}.
-% task
-Participants also performed a one-back matching task to keep them attentive.
+Participants performed a one-back image matching task for four block-design runs,
+with two \unit[16]{s} blocks per stimulus category in each run.
+%
+For details on stimulus creation and presentation see
+\cite{sengupta2016extension}.
 
@@
 
-\todo[inline]{SE: Antworten innerhalb "klassisch definierter"
-PPA für die verschiedenen regressoren bzw. kategorien derselben (zumindest aber
-places vs faces) aus? -> Peristimulus plots}
-
 % study goal
@@
 % reference to supplemental material
-Results and discussion of the additional contrasts (PPA and negative controls)
-can be found in the supplemental material. \todo{check if redundant with later refs}
+Additional analyses of the robustness of the results presented here
+are available as supplementary materials.
 

### 2021-02-17 paper/main.tex
Condense preproc

@@
 % preprocessing intro
-All analyses presented here were carried out using
+Preprocessing was performed by FEAT v6.00 (FMRI Expert Analysis Tool;
+\citep{woolrich2001autocorr}) as shipped with
 FSL v5.0.9 (\href{https://www.fmrib.ox.ac.uk/fsl}{FMRIB's Software Library};
-\citep{smith2004fsl}) on a computer cluster running the Debian GNU/Linux
-operating system. Software packages were obtained from repositories of
+\citep{smith2004fsl}) on a compute-cluster running
 \href{http://neuro.debian.net}{NeuroDebian} \citep{halchenko2012open}.
 
-% my preprocessing
-Preprocessing was performed by FEAT v6.00 (FMRI Expert Analysis Tool;
-\citep{woolrich2001autocorr}) as shipped with FSL.
 % temporal filtering

### 2021-02-17 paper/main.tex

@@
 
+\noindent General
+\begin{itemize}
+    \item van den Hurk (2017): uses sounds (1.8sec); one-back-task; no
+        significant results; but ``sensitivity maps'' and cross-modal and
+        cross-subject classification; mentions in a half sentence ``the auditory
+        trials might activate only a subset of voxels that contain categorical
+        information, whereas the visual trials activate the majority of VTC
+        voxels''.
+\end{itemize}
+
 \noindent Method
@@
 
-\noindent Data Citations, Code Availability, Data Availability
-
+\noindent Data Citations, Code Availability
 \begin{itemize}
-    \item https://www.springernature.com/gp/authors/research-data-policy/data-availability-statements/12330880i
-    \item cf. other Scientific Data analysis paper
+    \item draft for Data Citation is done
+    \item draft for Code and Data Availability is done (other analysis paper do
+        it pretty amateurish); will look at the ``how to write an excellent
+        data availability statement'' at springernature.com
 \end{itemize}
@@
 
-\subsection*{Code availability}
-
-\todo[inline]{provide supporting source code; explain how/where other may
-access data underlying the analysis}
-
-\todo[inline]{if using custom code for dataset generation/processing: indicate
-how code can be accessed (including restrictions to access)}
-
-\todo[inline]{include infos on versions of used software}
-
-\todo[inline]{any specific variables or parameters used to generate, test, or process the current dataset?}
+\subsection*{Data and code availability}
+
+% Zenodo (registered but zipped) vs. OSF (datalad dataset but probably
+% unregistered)
+The fMRI and annotation data, analysis scripts to generate the results as well
+as results are available in the [NAME] repository, [PERSISTENT WEB LINK],
+accessible as Datalad (RRID:SCR_003931) datasets.
 

### 2021-02-17 paper/main.tex
Event description

--- 2021-02-17 paper/main.tex
@@
 ]{hyperref}
-\newcommand{\scidatalogo}{\includegraphics[height=36pt]{SciData_logo.jpg}}
+%\newcommand{\scidatalogo}{\includegraphics[height=36pt]{SciData_logo.jpg}}
+\newcommand{\scidatalogo}{}
 \pagestyle{fancy}
@@
 % traditionally
-Traditionally, researchers design stimuli that presumably would trigger the
-perceptual process of interest while also controlling confounding variables
-(e.g. color, luminance).
+In contrast to stimuli designed to trigger a perceptual process of interest,
+while controlling for confounding variables (e.g., color and luminance),
 % our approach: annotation and regressors
-Naturalistic stimuli mimic how we experience the world more closely but have the
-drawback that they are usually fix and that their temporal structure is unknown.
+naturalistic stimuli have an initially unknown temporal structure
+of stimulus features of interest, as well as an equally unknown confound structure.
 % annotation ftw
-Hence, we annotated the temporal structure of various stimulus features that
-later served as basis for modeling hemodynamic responses.
+In order to evaluate the suitability of the stimulus for the targeted analyses,
+and well as to inform the required hemodynamic models, we annotated the temporal
+structure of a range of stimulus features.
 
 % AV anno
-For the analysis of the movie stimulus, we took advantage of a previously published
-annotation of 869 movie cuts and the depicted location after each cut
+For the analysis of the movie stimulus, we took advantage of a previously
+published annotation of 869 movie cuts and the depicted location after each cut
 \citep{haeusler2016cutanno}.
 % rationale to use that annotation rationale behind using movie cuts
-Our rationale was that cuts are ``spatially relevant'' events that re-orient the
-viewer within the environment of the movie by either switching to another
-setting or switching the perspective within the same setting.
+We conceptualized cuts as events with information on the depicted environment
+that require viewers to re-orient themselves within the movie environment by
+switching to a new perspective within the same setting, or to a position in an
+entirely different setting.
 % AV regressors/events
-Each cut was put into one of the following five categories (see Table
+We assigned each cut to one of five categories (see Table
 \ref{tab:av-events}):
@@
 \midrule
-vse\_new &  change of the camera position to a setting not depicted before & \aoVsenewAll & \aoVsenewI & \aoVsenewII & \aoVsenewIII & \aoVsenewIV & \aoVsenewV & \aoVsenewVI & \aoVsenewVII & \aoVsenewVIII
-\tabularnewline vse\_old & change of the camera position to a recurring setting & \aoVseoldAll & \aoVseoldI & \aoVseoldII & \aoVseoldIII & \aoVseoldIV & \aoVseoldV & \aoVseoldVI & \aoVseoldVII & \aoVseoldVIII
-\tabularnewline
-vlo\_ch & change of the camera position to another locale within the same setting & \aoVlochAll & \aoVlochI & \aoVlochII & \aoVlochIII & \aoVlochIV & 0 & \aoVlochV & \aoVlochVI & \aoVlochVII
-\tabularnewline
-vpe\_new & change of the camera position within a locale not depicted before & \aoVpenewAll & \aoVpenewI & \aoVpenewII & \aoVpenewIII & \aoVpenewIV & \aoVpenewV & \aoVpenewVI & \aoVpenewVII & \aoVpenewVIII
+\texttt{vse\_new} &  change of the camera position to a setting not depicted before & \aoVsenewAll & \aoVsenewI & \aoVsenewII & \aoVsenewIII & \aoVsenewIV & \aoVsenewV & \aoVsenewVI & \aoVsenewVII & \aoVsenewVIII
+\tabularnewline
+\texttt{vse\_old} & change of the camera position to a recurring setting & \aoVseoldAll & \aoVseoldI & \aoVseoldII & \aoVseoldIII & \aoVseoldIV & \aoVseoldV & \aoVseoldVI & \aoVseoldVII & \aoVseoldVIII
+\tabularnewline
+\texttt{vlo\_ch} & change of the camera position to another locale within the same setting & \aoVlochAll & \aoVlochI & \aoVlochII & \aoVlochIII & \aoVlochIV & 0 & \aoVlochV & \aoVlochVI & \aoVlochVII
+\tabularnewline
+\texttt{vpe\_new} & change of the camera position within a locale not depicted before & \aoVpenewAll & \aoVpenewI & \aoVpenewII & \aoVpenewIII & \aoVpenewIV & \aoVpenewV & \aoVpenewVI & \aoVpenewVII & \aoVpenewVIII
 \tabularnewline
 % vpe_old has no events in 3. So the indices are shifted
-vpe\_old & change of the camera position within a recurring locale &
+\texttt{vpe\_old} & change of the camera position within a recurring locale &
 \aoVpeoldAll & \aoVpeoldI & \aoVpeoldII & 0 & \aoVpeoldIII & \aoVpeoldIV &
@@
 \tabularnewline
-vno\_cut & frames within a continuous movie shot & \avVnocutAll & \avVnocutI & \avVnocutII & 0 & \avVnocutIII & \avVnocutIV & \avVnocutV & \avVnocutVI & \avVnocutVII
+\texttt{vno\_cut} & frames within a continuous movie shot & \avVnocutAll & \avVnocutI & \avVnocutII & 0 & \avVnocutIII & \avVnocutIV & \avVnocutV & \avVnocutVI & \avVnocutVII
 \tabularnewline
@@
 % \tabularnewline
-fg\_av\_ger\_lr & left-right luminance difference & \avFgavgerlrAll & \avFgavgerlrI & \avFgavgerlrII & \avFgavgerlrIII & \avFgavgerlrIV & \avFgavgerlrV & \avFgavgerlrVI & \avFgavgerlrVII & \avFgavgerlrVIII
-\tabularnewline
-fg\_av\_ger\_lrdiff & left-right volume difference & \avFgavgerlrdiffAll & \avFgavgerlrdiffI & \avFgavgerlrdiffII & \avFgavgerlrdiffIII & \avFgavgerlrdiffIV & \avFgavgerlrdiffV & \avFgavgerlrdiffVI & \avFgavgerlrdiffVII & \avFgavgerlrdiffVIII
-\tabularnewline
-fg\_av\_ger\_ml & mean luminance & \avFgavgermlAll & \avFgavgermlI & \avFgavgermlII & \avFgavgermlIII & \avFgavgermlIV & \avFgavgermlV & \avFgavgermlVI & \avFgavgermlVII & \avFgavgermlVIII
-\tabularnewline
-fg\_av\_ger\_pd & perceptual difference & \avFgavgerpdAll & \avFgavgerpdI & \avFgavgerpdII & \avFgavgerpdIII & \avFgavgerpdIV & \avFgavgerpdV & \avFgavgerpdVI & \avFgavgerpdVII & \avFgavgerpdVIII
-\tabularnewline
-fg\_av\_ger\_rms & root mean square volume & \avFgavgerrmsAll & \avFgavgerrmsI & \avFgavgerrmsII & \avFgavgerrmsIII & \avFgavgerrmsIV & \avFgavgerrmsV & \avFgavgerrmsVI & \avFgavgerrmsVII & \avFgavgerrmsVIII
-\tabularnewline
-fg\_av\_ger\_ud & upper-lower luminance difference & \avFgavgerudAll & \avFgavgerudI & \avFgavgerudII & \avFgavgerudIII & \avFgavgerudIV & \avFgavgerudV & \avFgavgerudVI & \avFgavgerudVII & \avFgavgerudVIII
-\tabularnewline
+\texttt{fg\_av\_ger\_lr} & left-right luminance difference & \avFgavgerlrAll & \avFgavgerlrI & \avFgavgerlrII & \avFgavgerlrIII & \avFgavgerlrIV & \avFgavgerlrV & \avFgavgerlrVI & \avFgavgerlrVII & \avFgavgerlrVIII
+\tabularnewline
+\texttt{fg\_av\_ger\_lrdiff} & left-right volume difference & \avFgavgerlrdiffAll & \avFgavgerlrdiffI & \avFgavgerlrdiffII & \avFgavgerlrdiffIII & \avFgavgerlrdiffIV & \avFgavgerlrdiffV & \avFgavgerlrdiffVI & \avFgavgerlrdiffVII & \avFgavgerlrdiffVIII
+\tabularnewline
+\texttt{fg\_av\_ger\_ml} & mean luminance & \avFgavgermlAll & \avFgavgermlI & \avFgavgermlII & \avFgavgermlIII & \avFgavgermlIV & \avFgavgermlV & \avFgavgermlVI & \avFgavgermlVII & \avFgavgermlVIII
+\tabularnewline
+\texttt{fg\_av\_ger\_pd} & perceptual difference & \avFgavgerpdAll & \avFgavgerpdI & \avFgavgerpdII & \avFgavgerpdIII & \avFgavgerpdIV & \avFgavgerpdV & \avFgavgerpdVI & \avFgavgerpdVII & \avFgavgerpdVIII
+\tabularnewline
+\texttt{fg\_av\_ger\_rms} & root mean square volume & \avFgavgerrmsAll & \avFgavgerrmsI & \avFgavgerrmsII & \avFgavgerrmsIII & \avFgavgerrmsIV & \avFgavgerrmsV & \avFgavgerrmsVI & \avFgavgerrmsVII & \avFgavgerrmsVIII
+\tabularnewline
+\texttt{fg\_av\_ger\_ud} & upper-lower luminance difference & \avFgavgerudAll & \avFgavgerudI & \avFgavgerudII & \avFgavgerudIII & \avFgavgerudIV & \avFgavgerudV & \avFgavgerudVI & \avFgavgerudVII & \avFgavgerudVIII
+\tabularnewline
+\bottomrule
 \end{tabular}

### 2021-02-17 paper/main.tex
Trim table

@@
     the segments that were used for the eight sessions of fMRI scanning).
+    Event counts for frame-based features are reported in units of a thousand.
     %\texttt{fg\_av\_ger\_pd} (perceptual differences of consecutive frames),
@@
 \label{tab:av-events}
-\footnotesize
-\begin{tabular}{lp{3.5cm}lllllllll} \toprule \textbf{label} & \textbf{description} & \textbf{all} & \textbf{1} & \textbf{2} & \textbf{3} & \textbf{4} & \textbf{5} & \textbf{6} & \textbf{7} & \textbf{8} \\
+\small
+\begin{tabular}{lp{3.7cm}lllllllll} \toprule \textbf{label} & \textbf{description} & \textbf{all} & \textbf{1} & \textbf{2} & \textbf{3} & \textbf{4} & \textbf{5} & \textbf{6} & \textbf{7} & \textbf{8} \\
 \midrule

### 2021-02-17 paper/main.tex
Small fix

@@
 as results are available in the [NAME] repository, [PERSISTENT WEB LINK],
-accessible as Datalad (RRID:SCR_003931) datasets.
+accessible as Datalad (RRID:SCR\_003931) datasets.
 

### 2021-02-17 paper/main.tex
Table readability

@@
 \label{tab:descr-nouns-rules}
-\begin{tabular}{lll}
+\begin{tabular}{lp{61mm}p{61mm}}
 \toprule
@@
 \midrule
-body & trunk of the body; overlaid clothes & back, hip, shoulder; jacket, dress, shirt
-\tabularnewline
-bodypart & limbs & arm, finger, leg, toe
-\tabularnewline
-face & face or parts of it & face, ear, nose, mouth
-\tabularnewline
-female & female person & nurse, mother, woman
-\tabularnewline
-females & female persons & women
-\tabularnewline
-fname & female name & Jenny
-\tabularnewline
-furniture & movable furniture (insides \& outsides) & bench, bed, table, chair
-\tabularnewline
-geo & immobile landmarks & building, tree, street, alley, meadow, cornfield \tabularnewline
-geo-room & rooms \& locales or geometry-defining elements & living room; wall, door, window, floor
-\tabularnewline
-head & non-face parts of the head; worn headgear & head, hair, ear, neck;
+\texttt{body} & trunk of the body; overlaid clothes & back, hip, shoulder; jacket, dress, shirt
+\tabularnewline
+\texttt{bodypart} & limbs & arm, finger, leg, toe
+\tabularnewline
+\texttt{face} & face or parts of it & face, ear, nose, mouth
+\tabularnewline
+\texttt{female} & female person & nurse, mother, woman
+\tabularnewline
+\texttt{females} & female persons & women
+\tabularnewline
+\texttt{fname} & female name & Jenny
+\tabularnewline
+\texttt{furniture} & movable furniture (insides \& outsides) & bench, bed, table, chair
+\tabularnewline
+\texttt{geo} & immobile landmarks & building, tree, street, alley, meadow, cornfield
+\tabularnewline
+\texttt{geo-room} & rooms \& locales or geometry-defining elements & living room; wall, door, window, floor
+\tabularnewline
+\texttt{head} & non-face parts of the head; worn headgear & head, hair, ear, neck;
 helmet
 \tabularnewline
-male & male person & man, father, soldier
-\tabularnewline
-males & male persons & boys, opponents
-\tabularnewline
-mname & male name & Bubba, Kennedy
-\tabularnewline
-object & countable entity with firm boundaries & telephone, car
-\tabularnewline
-objects & countable entities & wheels, plants
-\tabularnewline
-persons & concrete persons of unknown sex & hippies, patients
-\tabularnewline
-setting\_new & a setting occurring for the first time & on a ``bridge'', on an ``alley'', on ``campus''
-\tabularnewline
-setting\_rec & a recurring setting & at the ``bus stop'' \tabularnewline
+\texttt{male} & male person & man, father, soldier
+\tabularnewline
+\texttt{males} & male persons & boys, opponents
+\tabularnewline
+\texttt{mname} & male name & Bubba, Kennedy
+\tabularnewline
+\texttt{object} & countable entity with firm boundaries & telephone, car
+\tabularnewline
+\texttt{objects} & countable entities & wheels, plants
+\tabularnewline
+\texttt{persons} & concrete persons of unknown sex & hippies, patients
+\tabularnewline
+\texttt{setting\_new} & a setting occurring for the first time & on a ``bridge'', on an ``alley'', on ``campus''
+\tabularnewline
+\texttt{setting\_rec} & a recurring setting & at the ``bus stop'' \tabularnewline
 % ++ & cue regarding time & in the ``evening'', it's ``daytime'', ``later'' \tabularnewline
@@
     }
-\label{tab:ao-events} \footnotesize
-\begin{tabular}{lp{3.5cm}lllllllll}
+\label{tab:ao-events}
+\begin{tabular}{lp{3.8cm}lllllllll}
 \toprule \textbf{label} & \textbf{description} & \textbf{all} & \textbf{1} & \textbf{2} & \textbf{3} & \textbf{4} & \textbf{5} & \textbf{6} & \textbf{7} & \textbf{8} \\
 \midrule
-body & trunk of the body; overlaid clothes & \aoBodyAll & \aoBodyI & \aoBodyII
+\texttt{body} & trunk of the body; overlaid clothes & \aoBodyAll & \aoBodyI & \aoBodyII
 & \aoBodyIII & \aoBodyIV & \aoBodyV & \aoBodyVI & \aoBodyVII & \aoBodyVIII
 \tabularnewline
-bpart & limbs and trousers & \aoBpartAll & \aoBpartI & \aoBpartII & \aoBpartIII & \aoBpartIV & \aoBpartV & \aoBpartVI & \aoBpartVII & \aoBpartVIII
-\tabularnewline
-fahead & face(parts) or head(parts) & \aoFaheadAll & \aoFaheadI & \aoFaheadII & \aoFaheadIII & \aoFaheadIV & \aoFaheadV & \aoFaheadVI & \aoFaheadVII & \aoFaheadVIII
-\tabularnewline
-furn & moveable furniture (insides \& outsides) & \aoFurnAll & \aoFurnI & \aoFurnII & \aoFurnIII & \aoFurnIV & \aoFurnV & \aoFurnVI & \aoFurnVII & \aoFurnVIII
-\tabularnewline
-geo & immobile landmarks & \aoGeoAll & \aoGeoI & \aoGeoII & \aoGeoIII & \aoGeoIV & \aoGeoV & \aoGeoVI & \aoGeoVII & \aoGeoVIII
-\tabularnewline
-groom & rooms \& locales or geometry-defining elements & \aoGroomAll & \aoGroomI & \aoGroomII & \aoGroomIII & \aoGroomIV & \aoGroomV & \aoGroomVI & \aoGroomVII & \aoGroomVIII
-\tabularnewline
-object & countable entities with firm boundaries & \aoObjAll & \aoObjI & \aoObjII & \aoObjIII & \aoObjIV & \aoObjV & \aoObjVI & \aoObjVII & \aoObjVIII
-\tabularnewline
-se\_new & a setting occurring for the first time & \aoSenewAll & \aoSenewI & \aoSenewII & \aoSenewIII & \aoSenewIV & \aoSenewV & \aoSenewVI & \aoSenewVII & \aoSenewVIII
-\tabularnewline
-se\_old & a recurring setting & \aoSeoldAll & \aoSeoldI & \aoSeoldII & \aoSeoldIII & \aoSeoldIV & \aoSeoldV & \aoSeoldVI & \aoSeoldVII & \aoSeoldVIII
-\tabularnewline
-sex\_f & female person(s), name & \aoSexfAll & \aoSexfI & \aoSexfII & \aoSexfIII & \aoSexfIV & \aoSexfV & \aoSexfVI & \aoSexfVII & \aoSexfVIII
-\tabularnewline
-sex\_m & male person(s), name & \aoSexmAll & \aoSexmI & \aoSexmII & \aoSexmIII & \aoSexmIV & \aoSexmV & \aoSexmVI & \aoSexmVII & \aoSexmVIII
+\texttt{bpart} & limbs and trousers & \aoBpartAll & \aoBpartI & \aoBpartII & \aoBpartIII & \aoBpartIV & \aoBpartV & \aoBpartVI & \aoBpartVII & \aoBpartVIII
+\tabularnewline
+\texttt{fahead} & face or head (parts) & \aoFaheadAll & \aoFaheadI & \aoFaheadII & \aoFaheadIII & \aoFaheadIV & \aoFaheadV & \aoFaheadVI & \aoFaheadVII & \aoFaheadVIII
+\tabularnewline
+\texttt{furn} & moveable furniture (insides \& outsides) & \aoFurnAll & \aoFurnI & \aoFurnII & \aoFurnIII & \aoFurnIV & \aoFurnV & \aoFurnVI & \aoFurnVII & \aoFurnVIII
+\tabularnewline
+\texttt{geo} & immobile landmarks & \aoGeoAll & \aoGeoI & \aoGeoII & \aoGeoIII & \aoGeoIV & \aoGeoV & \aoGeoVI & \aoGeoVII & \aoGeoVIII
+\tabularnewline
+\texttt{groom} & rooms \& locales or geometry-defining elements & \aoGroomAll & \aoGroomI & \aoGroomII & \aoGroomIII & \aoGroomIV & \aoGroomV & \aoGroomVI & \aoGroomVII & \aoGroomVIII
+\tabularnewline
+\texttt{object} & countable entities with firm boundaries & \aoObjAll & \aoObjI & \aoObjII & \aoObjIII & \aoObjIV & \aoObjV & \aoObjVI & \aoObjVII & \aoObjVIII
+\tabularnewline
+\texttt{se\_new} & a setting occurring for the first time & \aoSenewAll & \aoSenewI & \aoSenewII & \aoSenewIII & \aoSenewIV & \aoSenewV & \aoSenewVI & \aoSenewVII & \aoSenewVIII
+\tabularnewline
+\texttt{se\_old} & a recurring setting & \aoSeoldAll & \aoSeoldI & \aoSeoldII & \aoSeoldIII & \aoSeoldIV & \aoSeoldV & \aoSeoldVI & \aoSeoldVII & \aoSeoldVIII
+\tabularnewline
+\texttt{sex\_f} & female person(s), name & \aoSexfAll & \aoSexfI & \aoSexfII & \aoSexfIII & \aoSexfIV & \aoSexfV & \aoSexfVI & \aoSexfVII & \aoSexfVIII
+\tabularnewline
+\texttt{sex\_m} & male person(s), name & \aoSexmAll & \aoSexmI & \aoSexmII & \aoSexmIII & \aoSexmIV & \aoSexmV & \aoSexmVI & \aoSexmVII & \aoSexmVIII
 \tabularnewline
@@
 % \tabularnewline
-fg\_ad\_lrdiff & left-right volume difference & \aoFgadlrdiffAll & \aoFgadlrdiffI & \aoFgadlrdiffII & \aoFgadlrdiffIII & \aoFgadlrdiffIV &
+\texttt{fg\_ad\_lrdiff} & left-right volume difference & \aoFgadlrdiffAll & \aoFgadlrdiffI & \aoFgadlrdiffII & \aoFgadlrdiffIII & \aoFgadlrdiffIV &
 \aoFgadlrdiffV & \aoFgadlrdiffVI & \aoFgadlrdiffVII & \aoFgadlrdiffVIII
 \tabularnewline
-fg\_ad\_rms & root mean square volume & \aoFgadrmsAll &
+\texttt{fg\_ad\_rms} & root mean square volume & \aoFgadrmsAll &
 \aoFgadrmsI & \aoFgadrmsII & \aoFgadrmsIII & \aoFgadrmsIV & \aoFgadrmsV &

### 2021-02-17 paper/main.tex
Note abbreviations in table description
AV condition description

@@
 depicted before (\texttt{vpe\_old}).
-
 % irrespective of visual content
-Notably, categorization was performed irrespectively of a movie frame's precise
-content and thus without controlling confounding variables.
-% assumption
-We assumed that different categories would - on average - depict different
-stimulus features.
+Note that this categorization is not necessarily evident from the visual content
+of the first movie frame after a cut.
 % cinematographic rationale cut to new scenes: establishing shots
 The cinematographic rationale was that movie shots tend to establish the setting
-(\texttt{vse\_new}) and the spatial layout within a setting (\texttt{vpe\_new})
-at the beginning of a movie.
+and their spatial layout at the beginning of a movie.
 % cut to recurrent scene
-Later in the movie, the field sizes of movie shots tend to decrease when
-switching back to an already established settings (\texttt{vse\_old}).
-% similarly for shots within a scene
-When the spatial layout within a setting is already established, shots tend to
-more often depict (faces of) persons talking to each others or objects more
-relevant to the evolved plot (\texttt{vpe\_old}) \citep{brown2012cinematography,
+On revisiting an already established setting later in the movie, the field sizes
+of movie shots tend to decrease (\texttt{vse\_old}), and shots tend to
+more often depict people talking to each other, or objects that are relevant to
+the evolved plot (\texttt{vpe\_old}) \citep{brown2012cinematography,
 mercado2011filmmakers}.
@@
 % condition: intro
-In order to create a control condition, a sixth category (\texttt{no\_cut}) was
-created by pseudo-randomly drawing movie frames from continuous movie shots that
-lasted longer than \unit[20]{s}.
+
+As a control condition with events of no particular processing of spatial
+information (\texttt{no\_cut}) we pseudo-randomly selected movie frames from
+continuous movie shots that lasted longer than \unit[20]{s}, and
 % no cuts: how
-Events were drawn from movie shots in such a way that each event had a minimum
-temporal distance of at least \unit[10]{s} to a movie cut and to another
-\texttt{no\_cut} event.
+had a minimum temporal distance of at least \unit[10]{s} to any movie cut and
+to any other \texttt{no\_cut} event.
 
@@
     \texttt{object}).
+    Event counts for frame-based features are reported in units of a thousand.
     % For a description of the five control conditions for movie cuts see

### 2021-02-17 paper/main.tex
Remaining event types

@@
 For the analysis of the audio-description stimulus, we extended a publicly available annotation
-of speech \citep{hausler2021studyforrest} by further annotating words spoken by
-the audio-description's narrator.
+of its speech content \citep{hausler2021studyforrest} by classifying
+concrete and countable nouns that the narrator uses to describe the movie's absent visual content.
 % annotation procedure
-Two persons performed a categorization of (concrete and countable) nouns that
-the narrator uses to describe the movie's missing visual content based on a set
-of rules.
-% preliminary annotation
-A preliminary annotation was performed by one person according to the rules.
+An initial annotation was performed by one individual,
 % corrections
-Minor corrections due to incorrectly applied rules were done by the author.
+and minor corrections were applied after comparing with a second categorization
+done by the author.
 % reference to table with rules and examples
-A complete overview of all 18 noun categories, the rule for a word to belong to
-a category, and examples can be seen in Table \ref{tab:descr-nouns-rules}.
+A complete overview of all 18 noun categories, their inclusion criteria, and examples
+can be seen in Table \ref{tab:descr-nouns-rules}.
 % why and how of categories 1
@@
 \midrule
-\texttt{body} & trunk of the body; overlaid clothes & back, hip, shoulder; jacket, dress, shirt
+\texttt{body} & trunk of the body; possibly clothed & back, hip, shoulder; jacket, dress, shirt
 \tabularnewline
@@
 % visual shit
-For the movie stimulus, we computed the mean luminance of a movie frame
-(\unit[40]{ms}), the difference in mean luminance of each frame's left and right
-half, the difference in mean luminance of the lower and upper half, and finally
-the perceptual difference of consecutive frames.
+For the movie stimulus, we computed the mean luminance (arbitrary units,
+average pixel brightness) of a movie frame (\unit[40]{ms}), the difference in
+mean luminance of each frame's left and right half, the difference in mean
+luminance of the lower and upper half.  As an indiciator of visual change, we
+compute perceptual fingerprints for each movie frame using the pHash library
+\todo{cite Zauner, Christoph: Implementation and Benchmarking of Perceptual
+Image Hash Functions. Master's thesis, Upper Austria University of Applied
+Sciences, Hagenberg Campus, 2010.} and recorded the commulative bitwise
+difference to the previous frame.
 % auditory shit

### 2021-02-17 paper/main.tex
add ref to zauner

@@
 compute perceptual fingerprints for each movie frame using the pHash library
-\todo{cite Zauner, Christoph: Implementation and Benchmarking of Perceptual
-Image Hash Functions. Master's thesis, Upper Austria University of Applied
-Sciences, Hagenberg Campus, 2010.} and recorded the commulative bitwise
+\citep{zauner2010implementation} and recorded the commulative bitwise
 difference to the previous frame.

### 2021-02-17 paper/main.tex
Confound analysis

@@
 The events of the movie cut related categories and \texttt{no\_cut} events were
-modeled as box car events of 200 ms duration.
-%
-Nouns were modeled from onset to offset of each word, low-level confounds from
-onset to offset of the corresponding movie frame
+modeled as box car events of \unit[200]{ms} duration,
+%
+speech events from onset to offset of each word, and frame-based confounds from
+onset to offset of the corresponding movie frame.
 % convolving
-Events for all regressors of the movie and audio-description stimulus were convolved with a double
-gamma hemodynamic response function (HRF).
+For all regressors, the stimulus models were convolved with a double-gamma
+hemodynamic response function (HRF), as implemented in FSL.
 
 % we checked correlations
-Since we annotated events in fixed time courses, the modeled hemodynamic
-time-series could be correlated leading to shared variance and thus low
-detection power of subsequent analyses.
+Given the unknown confound structure of the naturalistic stimuli we inspected
 % correlations within stimuli and across stimuli
-Hence, we tested for correlation of regressors across the eight segments of each
-stimulus and also for correlations of regressors across both stimuli (s. Figure
-\ref{fig:reg-corr})
+the correlation of regressors across the eight segments of each stimulus and
+also across both stimuli (Figure \ref{fig:reg-corr}).
 % correlations within each stimulus
-The computed Pearson correlation coefficients demonstrate no to minor
-correlations of modeled hemodynamic time-series belonging to the same stimulus.
+The computed Pearson correlation coefficients show only minor correlations of
+feature regressors for the same stimulus.
 % (highest) correlations across stimuli
-The highest correlations are apparent between auditory low-level confounds
-across stimuli (\texttt{fg\_av\_ger\_rms} and \texttt{fg\_ad\_rms}, r=.7635;
-\texttt{fg\_av\_ger\_lrdiff} and \texttt{fg\_ad\_lrdiff} and , r=.7749).
+Maximum correlations are found for auditory low-level confounds across stimuli
+(\texttt{fg\_a(v|d)\_ger\_rms}, r=.76;
+\texttt{fg\_a(v|d)\_ger\_lrdiff}, r=.77),
 % no surprise
-This was expected and served as a ``sanity check'' since the audio track of the
-audio-description is the audio track of the movie but featuring the additional
-narrator (s. Figure \ref{fig:reg-corr}).
+which is to be expected, as the audio-description contains the audio track of
+the movie plus the additional narrator (s. Figure \ref{fig:reg-corr}).
 % encouraged by that we build contrasts (statement)
-As a result, we felt encouraged to create voxel-wise general linear model (GLM)
-$t$-contrasts similarly to previous studies that used controlled stimuli.
+Given that all planned voxel-wise general linear models (GLM) exclusively involve
+regressors from one of the naturalistic stimuli, the observed correlation
+pattern does not indicate problematic confounds of nuissance variables and
+regressors of interest.
 

### 2021-02-17 paper/main.tex
Normalize Table and Figure references

@@
 % AV regressors/events
-We assigned each cut to one of five categories (see Table
-\ref{tab:av-events}):
+We assigned each cut to one of five categories (Tab.~\ref{tab:av-events}):
 %
@@
     % narrator (\texttt{se\_new} and \texttt{se\_old}) to build contrast of
-    % negative control see Table \ref{tab:ao-events}.
+    % negative control Tab.~\ref{tab:ao-events}.
     }
@@
 A complete overview of all 18 noun categories, their inclusion criteria, and examples
-can be seen in Table \ref{tab:descr-nouns-rules}.
+can be seen in Table~\ref{tab:descr-nouns-rules}.
 % why and how of categories 1
@@
 Some noun categories that were semantically similar and offered only a small
-amount of counts were pooled resulting in 11 final event categories (see Table
-\ref{tab:ao-events}). These event categories were then used to model hemodynamic
+amount of counts were pooled resulting in 11 final event categories (Tab.~\ref{tab:ao-events}).
+These event categories were then used to model hemodynamic
 responses.
@@
         GLM
-        (cf. Table \ref{tab:ao-events}).
+        (Tab.~\ref{tab:ao-events}).
         % The category \texttt{++} also contains adverbial of time.
@@
     males, mname; face, head; object, objects;
-    see Table\ref{tab:descr-nouns-rules}) were pooled
+    Tab.~\ref{tab:descr-nouns-rules}) were pooled
     into 11 new categories (\texttt{sex\_f}; \texttt{sex\_m}; \texttt{fahead},
@@
     % For a description of the five control conditions for movie cuts see
-    % Table \ref{tab:av-events}.
+    % Tab.~\ref{tab:av-events}.
     }
@@
 the correlation of regressors across the eight segments of each stimulus and
-also across both stimuli (Figure \ref{fig:reg-corr}).
+also across both stimuli (Fig.~\ref{fig:reg-corr}).
 % correlations within each stimulus
@@
 which is to be expected, as the audio-description contains the audio track of
-the movie plus the additional narrator (s. Figure \ref{fig:reg-corr}).
+the movie plus the additional narrator (Fig. \ref{fig:reg-corr}).
 % encouraged by that we build contrasts (statement)
@@
         the GLM analysis of the
-        audio-description (blue; see Table \ref{tab:ao-events} for a
-        description) and audio-visual movie (red; see Table
-        \ref{tab:av-events}).
+        audio-description (blue; Tab.~\ref{tab:ao-events} for a
+        description) and audio-visual movie (red; Tab.~\ref{tab:av-events}).
         Values are rounded to the nearest tenth.
@@
 if that segment did not contain an event of the category (e.g. no event of
-\texttt{vpe\_old} in segment 3; cf. Table \ref{tab:ao-events}).
+\texttt{vpe\_old} in segment 3; Tab.~\ref{tab:ao-events}).
 % temporal derivatives
@@
 spatial information compared to the perception of non-spatial information
-differently in five $t$-contrasts for the movie stimulus (see Table
-\ref{tab:av-contrasts}) and eight $t$-contrasts for the audio-description stimulus (see Table
-\ref{tab:ao-contrasts}).
+differently in five $t$-contrasts for the movie stimulus (Tab.~\ref{tab:av-contrasts})
+and eight $t$-contrasts for the audio-description stimulus (Tab.~\ref{tab:ao-contrasts}).
 % reason: robustness
@@
 Finally, we created several $t$-contrasts as negative controls for both stimuli
-(see Tables \ref{tab:av-contrasts} and \ref{tab:ao-contrasts}).
+(Tab.~\ref{tab:av-contrasts} and Tab.~\ref{tab:ao-contrasts}).
 % AV: no cut > cut
@@
 % AD stimulus
-For the audio-description stimulus, we created five $t$-contrasts (see Table
-\ref{tab:ao-contrasts}) to test if increased activation in the PPA was
+For the audio-description stimulus, we created five $t$-contrasts
+(Tab.~\ref{tab:ao-contrasts}) to test if increased activation in the PPA was
 correlated with moments of cuts.
@@
     Contrasts 9-13 serve as negative control contrasts at the moments of movie
-    cuts (see Table \ref{tab:av-contrasts}).}
+    cuts (Tab.~\ref{tab:av-contrasts}).}
 \label{tab:ao-contrasts}
@@
 depicted before to cuts within a recurring setting (\texttt{vse\_new >
-vpe\_old}) yielded three significant clusters (see Table
-\ref{tab:res-av-group1}, Figure \ref{fig:group-slices}).
+vpe\_old}) yielded three significant clusters (Tab.~\ref{tab:res-av-group1},
+Fig.~\ref{fig:group-slices}).
 % PPA (others the clusters extend into).
@@
 The primary $t$-contrast for the audio-description (\texttt{geo, groom} >
-non-spatial noun categories) yielded six significant clusters (see Table
-\ref{tab:res-ao-group1}, Figure \ref{fig:group-slices}).
+non-spatial noun categories) yielded six significant clusters
+(Tab.~\ref{tab:res-ao-group1}, Fig.~\ref{fig:group-slices}).
 % overlap with ROI
@@
 The visual localizer yielded bilateral parahippocampal clusters in 12 of 14
-participants and an unilateral right clusters in two participants (cf. Table 3 in
+participants and an unilateral right clusters in two participants (Tab.~3 in
 \citep{sengupta2016extension}).
@@
 titrating\todo{??} the $t$-threshold in the range of [2, 3] in until we found an
-isolated cluster (cf. Table 3 in that matched the expected anatomical location
+isolated cluster (Tab.~3 in that matched the expected anatomical location
 based on literature \citep{epstein1998ppa}.
@@
 % ref to figure
-Figure \ref{fig:subs-thresh-ppa} depicts thresholded $z$-maps of the primary movie
+Figure~\ref{fig:subs-thresh-ppa} depicts thresholded $z$-maps of the primary movie
 and audio-description $t$-contrast, and the outline of overlapped, individual PPAs
@@
 localizer and the primary audio-description contrast, we created a Bland-Altman-Plot for every
-participant (see Figure \ref{fig:bland-altman}).
+participant (Fig.~\ref{fig:bland-altman}).
 % what it depicts
@@
 In order to test the robustness of our approach, we created overall five
-$t$-contrasts for the movie stimulus (see Table \ref{tab:av-contrasts}), and
-overall eight $t$-contrast for the audio-description stimulus (see Table
-\ref{tab:av-contrasts}) by varying the contrasted categories (and thus the
+$t$-contrasts for the movie stimulus (Tab.~\ref{tab:av-contrasts}), and
+overall eight $t$-contrast for the audio-description stimulus (Tab.~\ref{tab:av-contrasts})
+by varying the contrasted categories (and thus the
 amount of available data), and how well the annotated events within categories
@@
 All five movie contrasts yielded significant bilateral clusters that
-overlap with the PPA group overlap (see Figure \ref{fig:stability-slices}).
+overlap with the PPA group overlap (Fig.~\ref{fig:stability-slices}).
 % AV: RSC & LOC
@@
 (\texttt{se\_new} > non-spatial categories) yielded significant bilateral
-clusters in anterior regions of the group PPA overlap (see Figure
-\ref{fig:stability-slices}).
+clusters in anterior regions of the group PPA overlap (Fig.~\ref{fig:stability-slices}).
 % AD: RSC & LOC
@@
 In the analysis of the movie data, none of the four contrasts that compared the
-\texttt{no\_cut} category to a movie cut category (see Table
-\ref{tab:av-contrasts}) yielded significant clusters.
+\texttt{no\_cut} category to a movie cut category (Tab.~\ref{tab:av-contrasts})
+yielded significant clusters.
 % AV using nouns
@@
 In the analysis of the audio-description data, we created control contrasts based on events of
-the annotated movie cuts (cf. Table \ref{tab:ao-contrasts})
+the annotated movie cuts (Tab.~\ref{tab:ao-contrasts})
 % contrast 9

### 2021-02-17 paper/main.tex
Modeling description, please check

@@
 % encouraged by that we build contrasts (statement)
-Given that all planned voxel-wise general linear models (GLM) exclusively involve
-regressors from one of the naturalistic stimuli, the observed correlation
-pattern does not indicate problematic confounds of nuissance variables and
-regressors of interest.
+The observed correlation pattern did not indicate problematic confounds of
+nuisance variables and regressors of interest for any of the planned
+analyses.
 
@@
 % AV design matrix
-For the subsequent first level GLM analysis of the movie stimulus, the modeled
-hemodynamic responses related to all movie cuts (including \texttt{no\_cut}) and
-six low-level perceptual confounds were included as regressors in the design
-matrix.
-% AD regressors in AV AD design matrix
-For the first level analysis of the audio-description stimulus, the modeled
-hemodynamic responses related to all noun categories and the two low-level
-perceptual confounds were included.
+The design matrices of the first-level time-series GLM analysis comprised the
+regressors for the stimulus features listed in Tables~\ref{tab:av-events} and
+\ref{tab:ao-events} for the movie and audio-description stimulus, respectively.
 % AD regressors in AV
-To create a contrasts of cross-modal control in the analysis of the movie
-stimulus, we also implemented the regressors based on nouns used by the
-audio-description's narrator to indicate a switch to another setting (categories
-\texttt{se\_new} and \texttt{se\_old}).
+Additionally, the design for the movie stimulus also contained the 
+regressors based on nouns used by the audio-description's narrator to indicate
+a switch to another setting (categories \texttt{se\_new} and \texttt{se\_old}),
+in order to be able to implement cross-modal control contrasts.
 % AV regressors in AV
-To create contrasts of cross-modal negative control in the analysis of the
-audio-description stimulus, we also implemented the movie cut-related regressors
-(excluding \texttt{no\_cut}).
+Likewise, the audio-description design matrix included movie cut-related regressors
+listed Table~\ref{tab:av-events} (excluding \texttt{no\_cut}).
 % both stimuli: null regressors
-For both stimuli, a null regressor was chosen for a event category in a segment,
-if that segment did not contain an event of the category (e.g. no event of
+For both stimuli, a null regressor was used for any event category in a segment
+for which no event of a category was present (e.g. no event of
 \texttt{vpe\_old} in segment 3; Tab.~\ref{tab:ao-events}).
 % temporal derivatives
-Temporal derivatives were included in the design matrix to compensate for
-regional differences between modeled and actual HRF \citep{friston1998event}.
+Temporal derivatives of all regressors were added to the design matrix to compensate for
+regional differences \citep{friston1998event}.
 % motion parameters
-Six motion parameters were also included.
+Lastly, six participant and run specific motion estimated (translation and rotation)
+were also included.
 % high-pass filtering
-Finally, designs were filtered with the same high-pass filter (cutoff period of
+The design matrices were temporally filtered with the same high-pass filter (cutoff period of
 \unit[150]{s}) as the BOLD time series.

### 2021-02-17 paper/main.tex
Simplify

@@
 % intro
-We tested our modeled hemodynamic responses based on stimulus annotations by
-conducting standard two-level GLM analyses to create
-participant-specific results across the 8 segments for every participant and each
-stimulus.
+We performed standard two-level GLM analyses to aggregate results across the 8
+segments for every participant and each stimulus separately.
 % level 3
-Subsequent, third-level analyses averaged contrast estimates over participants.
+Subsequently, we conducted third-level analyses to average contrast estimates
+over participants for each stimulus, respectively.
 

### 2021-02-17 paper/main.tex
geo-room -> groom
That is what is in the analysis code.

@@
 \texttt{bodypart}, \texttt{female}, \texttt{fname}, \texttt{furniture},
-\texttt{geo}, \texttt{geo-room}, \texttt{male}, and \texttt{persons}).
+\texttt{geo}, \texttt{groom}, \texttt{male}, and \texttt{persons}).
 % categories in detail
 %Nouns were categorized by the verbal clue they provide about the
-%cinematographic scene's environment (\texttt{geo}, \texttt{geo-room};
+%cinematographic scene's environment (\texttt{geo}, \texttt{groom};
 %\texttt{setting\_new}, \texttt{setting\_old}), its inherent persons (e.g.
@@
 \tabularnewline
-\texttt{geo-room} & rooms \& locales or geometry-defining elements & living room; wall, door, window, floor
+\texttt{groom} & rooms \& locales or geometry-defining elements & living room; wall, door, window, floor
 \tabularnewline
@@
 landmarks (\texttt{geo}), and rooms and geometry-defining objects
-(\texttt{geo-room}) with not just nouns referring to a person's head or face
+(\texttt{groom}) with not just nouns referring to a person's head or face
 (\texttt{fahead}, N=83; e.g.  ``eyes'', ``face'', or ``head'') but also all

### 2021-02-17 paper/main.tex
Less chaotic figure/table placement
Forcing the placement had half sentences cut off, and other madness.
Tune tables

@@
 % AV regressors
-\begin{table*}[h!]
+\begin{table*}[tbp]
     \caption{Overview of annotated stimulus features of audio-visual
@@
 % table for descriptive nouns: categories, rules, examples counts
-\begin{table*}[h!]
+\begin{table*}[tbp]
     \caption{Categories and rules to categorize the nouns spoken by
@@
 % AD regressors
-\begin{table*}[h!]
+\begin{table*}[tbp]
     \caption{Overview of annotated stimulus features of the audio-description.
@@
 
-\begin{figure*}[h!]
+\begin{figure*}[tbp]
 \centering
@@
 
-\begin{table*}[h!]
-\caption{Contrasts of parameter estimates for the analysis of the
-    audio-visual movie.
-    Contrast 1-5 aim to isolate the PPA.
-    Contrast 6-9 serve as negative control.
-    Contrast 10 serves as control for moments when the narrator indicates
-    a switch of settings.}
+\begin{table*}[tbp]
+\caption{Computed contrasts for the analysis of the movie and their purpose.}
 \label{tab:av-contrasts}
-\footnotesize
 \begin{tabular}{lll}
@@
 \midrule
-1 & vse\_new > vpe\_old & PPA \tabularnewline
-2 & vse\_new, vpe\_new > vse\_old, vpe\_old & PPA \tabularnewline
-3 & vse\_new > vse\_old & PPA \tabularnewline
-4 & vse\_new > vse\_old, vpe\_old & PPA \tabularnewline
-5 & vse\_new, vpe\_new > vpe\_old & PPA \tabularnewline
-6 & vno\_cut > vse\_new & negative control \tabularnewline
-7 & vno\_cut > vse\_old & negative control \tabularnewline
-8 & vno\_cut > vse\_new, vse\_old & negative control \tabularnewline
-9 & vno\_cut > vpe\_new, vpe\_old & negative control \tabularnewline
-10 & se\_new > se\_old & control for (missing) narrator \tabularnewline
+1 & \texttt{vse\_new > vpe\_old} & spatial processing \tabularnewline
+2 & \texttt{vse\_new, vpe\_new > vse\_old, vpe\_old} & spatial processing \tabularnewline
+3 & \texttt{vse\_new > vse\_old} & spatial processing \tabularnewline
+4 & \texttt{vse\_new > vse\_old, vpe\_old} & spatial processing \tabularnewline
+5 & \texttt{vse\_new, vpe\_new > vpe\_old} & spatial processing \tabularnewline
+6 & \texttt{vno\_cut > vse\_new} & control \tabularnewline
+7 & \texttt{vno\_cut > vse\_old} & control \tabularnewline
+8 & \texttt{vno\_cut > vse\_new, vse\_old} & control \tabularnewline
+9 & \texttt{vno\_cut > vpe\_new, vpe\_old} & control \tabularnewline
+10 & \texttt{se\_new > se\_old} & control for (missing) narrator \tabularnewline
+\bottomrule
 \end{tabular}
@@
 
-\begin{table*}[h!]
-\caption{Contrasts of parameter estimates for the analysis of the audio-only
-    stimulus.
-    Contrast 1-8 aim to isolate the PPA.
-    \texttt{non-spatial categories} refers to the categories
+\begin{table*}[tbp]
+\caption{Computed contrasts for the analysis of the audio-description and their purpose.
+    \texttt{non-spatial} refers to the categories
     \texttt{body}, \texttt{bodypart}, \texttt{fahead},
-    \texttt{object}, \texttt{sex\_f}, \texttt{sex\_m}.
-    Contrasts 9-13 serve as negative control contrasts at the moments of movie
-    cuts (Tab.~\ref{tab:av-contrasts}).}
+    \texttt{object}, \texttt{sex\_f}, \texttt{sex\_m}.}
 \label{tab:ao-contrasts}
-\footnotesize
 \begin{tabular}{lll}
@@
 \midrule
-1 & geo, groom > non-spatial categories & PPA \tabularnewline
-2 & geo, groom, se\_new > non-spatial categories & PPA \tabularnewline
-3 & groom, se\_new, se\_old > non-spatial  & PPA \tabularnewline
-4 & geo > non-spatial categories & PPA \tabularnewline
-5 & groom > non-spatial categories & PPA \tabularnewline
-6 & se\_new > non-spatial categories & PPA \tabularnewline
-7 & se\_new, se\_old > non-spatial categories & PPA \tabularnewline
-8 & se\_new > se\_old > non-spatial categories & PPA \tabularnewline
-9 & vse\_new > vpe\_old & control at moments of cuts \tabularnewline
-10 & vse\_new, vpe\_new > vse\_old, vpe\_old & control at moments of cuts \tabularnewline
-11 & vse\_new > vse\_old & control at moments of cuts \tabularnewline
-12 & vse\_new > vse\_old, vpe\_old & control at moments of cuts \tabularnewline
-13 & vse\_new, vpe\_new > vpe\_old & control at moments of cuts \tabularnewline
+1 & \texttt{geo, groom > non-spatial} & spatial processing \tabularnewline
+2 & \texttt{geo, groom, se\_new > non-spatial} & spatial processing \tabularnewline
+3 & \texttt{groom, se\_new, se\_old > non-spatial}  & spatial processing \tabularnewline
+4 & \texttt{geo > non-spatial} & spatial processing \tabularnewline
+5 & \texttt{groom > non-spatial} & spatial processing \tabularnewline
+6 & \texttt{se\_new > non-spatial} & spatial processing \tabularnewline
+7 & \texttt{se\_new, se\_old > non-spatial} & spatial processing \tabularnewline
+8 & \texttt{se\_new > se\_old > non-spatial} & spatial processing \tabularnewline
+9 & \texttt{vse\_new > vpe\_old} & control (absent visual cuts) \tabularnewline
+10 & \texttt{vse\_new, vpe\_new > vse\_old, vpe\_old} & control (absent visual cuts) \tabularnewline
+11 & \texttt{vse\_new > vse\_old} & control (absent visual cuts) \tabularnewline
+12 & \texttt{vse\_new > vse\_old, vpe\_old} & control (absent visual cuts) \tabularnewline
+13 & \texttt{vse\_new, vpe\_new > vpe\_old} & control (absent visual cuts) \tabularnewline
+\bottomrule
 \end{tabular}
@@
 % figure group results primary AD & AV contrasts
-\begin{figure*}[h!] \centering
+\begin{figure*}[tbp] \centering
     \includegraphics[width=\linewidth]{figures/group-slices}
@@
 
-\begin{table*}[h!]
+\begin{table*}[tbp]
 \caption{Significant clusters (z-threshold Z>3.4; p<.05 cluster-corrected)
@@
 % table group results primary AD contrast
-\begin{table*}[h!]
+\begin{table*}[tbp]
     \caption{Significant clusters (z-threshold Z>3.4; p<.05 cluster-corrected)

### 2021-02-17 paper/main.tex
Tune tables

@@
     movie.
-    Respective event counts are given for the whole stimulus (\texttt{all} and
+    Respective event counts are given for the whole stimulus (\texttt{All} and
     the segments that were used for the eight sessions of fMRI scanning).
@@
 \small
-\begin{tabular}{lp{3.7cm}lllllllll} \toprule \textbf{label} & \textbf{description} & \textbf{all} & \textbf{1} & \textbf{2} & \textbf{3} & \textbf{4} & \textbf{5} & \textbf{6} & \textbf{7} & \textbf{8} \\
+\begin{tabular}{lp{3.7cm}lllllllll} \toprule \textbf{Label} & \textbf{Description} & \textbf{All} & \textbf{1} & \textbf{2} & \textbf{3} & \textbf{4} & \textbf{5} & \textbf{6} & \textbf{7} & \textbf{8} \\
 \midrule
@@
 \toprule
-\textbf{category} & \textbf{rule} & \textbf{examples} \\
+\textbf{Category} & \textbf{Rule} & \textbf{Examples} \\
 \midrule
@@
     \caption{Overview of annotated stimulus features of the audio-description.
-    Respective event counts are given for the whole stimulus (\texttt{all} and
+    Respective event counts are given for the whole stimulus (\texttt{All} and
     the segments that were used for the eight sessions of fMRI scanning.
@@
 \begin{tabular}{lp{3.8cm}lllllllll}
-\toprule \textbf{label} & \textbf{description} & \textbf{all} & \textbf{1} & \textbf{2} & \textbf{3} & \textbf{4} & \textbf{5} & \textbf{6} & \textbf{7} & \textbf{8} \\
+\toprule \textbf{Label} & \textbf{Description} & \textbf{All} & \textbf{1} & \textbf{2} & \textbf{3} & \textbf{4} & \textbf{5} & \textbf{6} & \textbf{7} & \textbf{8} \\
 \midrule
@@
 % intro
-We performed standard two-level GLM analyses to aggregate results across the 8
+We performed standard two-level GLM analyses to aggregate results across the eight
 segments for every participant and each stimulus separately.
@@
 \toprule
-\textbf{nr.} &  \textbf{contrast} & \textbf{purpose} \\
+\textbf{Nr.} &  \textbf{Contrast} & \textbf{Purpose} \\
 \midrule
@@
     followed by brain structures from posterior to anterior, and partially
-    covered areas (l. = left; r. = right; c. = cortex; g. = gyrus).}
+    covered areas (l. = left; r. = right; c. = cortex; g. = gyrus).
+    CoG: Center of Gravity}
 \label{tab:res-av-group1}
-\begin{tabular}{rrrrrrrrrp{3cm}}
+\begin{tabular}{rrrrrrrrrp{3.5cm}}
 \toprule
-& & & \multicolumn{3}{r}{max location (MNI)} & \multicolumn{3}{r}{center of gravity (MNI)} &
+& & & \multicolumn{3}{r}{Max (MNI)} & \multicolumn{3}{r}{CoG (MNI)} &
 \\ \cmidrule{4-6} \cmidrule{7-9}
-voxels & $p_{corr.}$ & Z-max & x & y & z  & x & y & z & structure \\
+Voxels & $p_{corr.}$ & Z-max & X & Y & Z  & X & Y & Z & Structure \\
 \midrule
@@
 followed by brain structures from posterior to anterior, and partially covered
-areas (l. = left; r. = right; c. = cortex; g. = gyrus).}
+areas (l. = left; r. = right; c. = cortex; g. = gyrus).
+    CoG: Center of Gravity}
     \label{tab:res-ao-group1}
-\begin{tabular}{rrrrrrrrrp{3cm}}
+    \begin{tabular}{rrrrrrrrrp{3.5cm}}
 \toprule
-& & & \multicolumn{3}{r}{max location (MNI)} & \multicolumn{3}{r}{center of gravity (MNI)} &
+& & & \multicolumn{3}{r}{Max (MNI)} & \multicolumn{3}{r}{CoG (MNI)} &
 \\ \cmidrule{4-6} \cmidrule{7-9}
-voxels & $p_{corr.}$ & Z-max & x & y & z  & x & y & z & structure \\
+Voxels & $p_{corr.}$ & Z-max & X & Y & Z  & X & Y & Z & Structure \\
 \midrule

### 2021-02-17 paper/main.tex
Uniform display of statistical scores

@@
 Effects; \citep{beckmann2003general, woolrich2004multilevel}.
-% thresholding (Z>2.3 in subject-space; Z>3.4 in group space)
+% thresholding ($Z$>2.3 in subject-space; $Z$>3.4 in group space)
 (Gaussianised T/F) statistic images were thresholded using clusters determined
-by Z>3.4 and a cluster-corrected significance threshold of p=.05
+by $Z$>3.4 and a cluster-corrected significance threshold of $p$<.05
 \citep{worsley2001statistical}.
@@
 Here again, Z (Gaussianised T/F) statistic images were thresholded using
-clusters determined by Z>3.4 and a (corrected) cluster significance threshold of
+clusters determined by $Z$>3.4 and a (corrected) cluster significance threshold of
 p=.05 \citep{worsley2001statistical}.
@@
 % NeuroVault
-Unthresholded $z$-maps of all contrasts on a group level as well as individual
+Unthresholded $Z$-maps of all contrasts on a group level as well as individual
 results of the primary $t$-contrasts co-registered to the group-template (MNI152
@@
     \caption{Mixed-effects group-level (N=14) GLM results. Significant clusters
-        (Z>3.4, p<.05 cluster-corrected) are overlaid on the MNI152 T1-weighted
+        ($Z$>3.4, $p$<.05 cluster-corrected) are overlaid on the MNI152 T1-weighted
         head template (gray).
@@
 \begin{table*}[tbp]
-\caption{Significant clusters (z-threshold Z>3.4; p<.05 cluster-corrected)
+\caption{Significant clusters ($Z$-threshold $Z$>3.4; $p$<.05 cluster-corrected)
     of the primary $t$-contrast for the audio-visual movie comparing cuts to a
@@
 \begin{table*}[tbp]
-    \caption{Significant clusters (z-threshold Z>3.4; p<.05 cluster-corrected)
+    \caption{Significant clusters ($Z$-threshold $Z$>3.4; $p$<.05 cluster-corrected)
         of the primary $t$-contrast for the audio-description comparing
@@
 Individual PPAs were assessed by visually inspecting thresholded $t$-maps
-(Z>1.64, p<.05 cluster corrected) of three different $t$-contrasts, and
+($Z$>1.64, $p$<.05 cluster corrected) of three different $t$-contrasts, and
 titrating\todo{??} the $t$-threshold in the range of [2, 3] in until we found an
@@
 
-% one contrast to localize them all; "...and Z>3.4 for all"
+% one contrast to localize them all; "...and $Z$>3.4 for all"
 Contrary to \citep{sengupta2016extension}, we here used the same contrast of
@@
 Results of the analyses that were performed in participant-space can be found in the
-accompanying dataset (Z>2.3, p<.05 cluster-corrected).
+accompanying dataset ($Z$>2.3, $p$<.05 cluster-corrected).
 % here report in group space
 For better comparisons of participants, we here report results from the analyses
-performed in group space (Z>3.4, p<.05 cluster-corrected).
+performed in group space ($Z$>3.4, $p$<.05 cluster-corrected).
 % ref to figure
-Figure~\ref{fig:subs-thresh-ppa} depicts thresholded $z$-maps of the primary movie
+Figure~\ref{fig:subs-thresh-ppa} depicts thresholded $Z$-maps of the primary movie
 and audio-description $t$-contrast, and the outline of overlapped, individual PPAs
@@
     \includegraphics[width=\linewidth]{figures/subs-thresh-ppa}
-    \caption{Fixed-effects individual-level GLM results (Z>3.4, p<.05
+    \caption{Fixed-effects individual-level GLM results ($Z$>3.4, $p$<.05
         cluster-corrected).
@@
 Each subplot visualizes the mean value and difference (localizer minus audio-description) of
-two spatially corresponding voxels in the unthresholded $z$-maps.
+two spatially corresponding voxels in the unthresholded $Z$-maps.
 % top KDE plot
@@
 % right KDE plot
-Values above the horizontal line depict voxels that show a higher $z$-value in
+Values above the horizontal line depict voxels that show a higher $Z$-value in
 the dedicated localizer, values below the horizontal line depict voxels that
-show a higher $z$-value in the audio-description stimulus.
+show a higher $Z$-value in the audio-description stimulus.
 
@@
     The x-axes show the means of two spatially corresponding voxels in the
-    unthresholded $z$-map of the audio-description's primary contrast and
-    unthresholded $z$-map of the visual localizer (KDE plot on the top).
+    unthresholded $Z$-map of the audio-description's primary contrast and
+    unthresholded $Z$-map of the visual localizer (KDE plot on the top).
     The y-axes show the difference of two voxels (localizer minus
@@
 $t$-threshold in $t$-map from one of three contrasts by visual judgment, we used
-the same contrast and threshold (Z>3.4, p<.05 cluster-corrected) for all
+the same contrast and threshold ($Z$>3.4, $p$<.05 cluster-corrected) for all
 participants.
@@
 \todo[inline]{discussion of Bland-Altman-Plots?; dunno if this is meaningful:
-z-scores in the anterior part of PPA are higher in audio-description contrasts than in contrast
+$Z$-scores in the anterior part of PPA are higher in audio-description contrasts than in contrast
 of localizer}
@@
 Unthresholded z -maps of all contrasts on a group level as well as individual
-results of the primary t-contrasts co-registered to the group-template (MNI152
+results of the primary $t$-contrasts co-registered to the group-template (MNI152
 space) can found at NeuroVault
@@
     \includegraphics[width=\linewidth]{figures/stability-slices}
-    \caption{Overlap of significant clusters (Z>3.4; p<.05, cluster corrected)
+    \caption{Overlap of significant clusters ($Z$>3.4; $p$<.05, cluster corrected)
         The audio-description's contrasts 1-8 (blue; \ref{tab:ao-contrasts})

### 2021-02-17 paper/main.tex
Some more

@@
 clusters determined by $Z$>3.4 and a (corrected) cluster significance threshold of
-p=.05 \citep{worsley2001statistical}.
+$p$<.05 \citep{worsley2001statistical}.
 % brain region identification
@@
 % one slice to show them all
-Transversal slice of z=-11 was chosen as it depicts voxels of
+Transversal slice of $Z$=-11 was chosen as it depicts voxels of
 significant clusters in almost all participants.

### 2021-02-17 paper/main.tex
intro: fixed typos

@@
 a dorsal stream (the ``where pathway'') that leads into the parietal lobe, and a
-ventral stream (the ``what pathway'') that leads into into the temporal lobe
+ventral stream (the ``what pathway'') that leads into the temporal lobe
 \citep{goodale1992separate, mishkin1982contribution}.
@@
 % GLM contrasts
-We applied whole-brain, model-based, mass-univariate analyses to a series of
+We applied model-based, mass-univariate analyses to a series of
 datasets with BOLD fMRI data from naturalistic and conventional block-design

### 2021-02-17 paper/main.tex
Statistical analysis, please check

--- 2021-02-17 paper/main.tex
@@
 
-% similar to previous studies
-On the first level, we created GLM contrasts based on annotated stimulus
-features embedded in the in the audio-visual movie and its audio-description.
-% intro
-To test the robustness of this approach, we operationalized the perception of
-spatial information compared to the perception of non-spatial information
-differently in five $t$-contrasts for the movie stimulus (Tab.~\ref{tab:av-contrasts})
-and eight $t$-contrasts for the audio-description stimulus (Tab.~\ref{tab:ao-contrasts}).
-% reason: robustness
-We assumed all contrasts could in principle correlate with increased hemodynamic
-activity in the PPA but chose one contrast to be the ``primary contrast'' for
-later detailed inspection and report.
-% selection criteria for primary contrast.
-The selection criterion for the primary contrast of each stimulus was a
-subjectively good balance between a) how well the average of events within
-categories represented spatial information and non-spatial information
-respectively (cf. section \ref{rationale}), and b) the amount of available data.
+Given the rich naturalistic stimuli and the availability of various stimulus
+feature annotations, there are several candidates for implementing contrasts to
+identify hemodynamic activity congruent with the hypothesized processing of
+spatial information in the PPA. However, while the rationale for any contrast
+composition must be sound, the selection of a single implementation remains
+arbitrary to some degree. Consequently, we computed multiple contrasts that are
+listed in Tables~\ref{tab:av-contrasts} and \ref{tab:ao-contrasts} for movie
+and audio-description, respectively. For each stimulus we, subjectively, picked
+a primary contrast for result presentation (the first one in each Table) based
+on how well the average event within categories represents spatial and
+non-spatial information, and the number of events in the stimulus.
+An evaluation of the robustness of these results with respect to similar but
+different contrasts is available in the supplementary materials.
+
 % AV: primary contrast
-In the primary contrast of the movie stimulus, we contrasted cuts to a setting that
-was not depicted before (\texttt{vse\_new}) to cuts merely switching the camera
-position within a setting that was already established earlier in the movie
-(\texttt{vpe\_old}).
-% why
-We assumed that the category \texttt{vse\_new} on average comprised the most
-movie frames depicting a landscape or the geometry of a setting, and the
-category \texttt{vpe\_old} the most frames depicting persons, faces, or objects
-[(cf.  rationale to categorize the cuts in section \ref{rationale})].
+In the primary contrast for the movie stimulus, we contrasted cuts to a setting
+that was not depicted before (\texttt{vse\_new}) to cuts merely switching the
+camera position within a setting that was already established earlier in the
+movie (\texttt{vpe\_old}), because the former are designed to orient the viewer
+in the movie environment using wider-camera angles, whereas the latter can
+afford to depict details of a scene.
 % AD: primary contrast
-In the primary contrast of the audio-description stimulus, we contrasted buildings and
-landmarks (\texttt{geo}), and rooms and geometry-defining objects
-(\texttt{groom}) with not just nouns referring to a person's head or face
-(\texttt{fahead}, N=83; e.g.  ``eyes'', ``face'', or ``head'') but also all
-non-geometry related categories (\texttt{body}, \texttt{bodypart},
-\texttt{fahead}, \texttt{object}, \texttt{sex\_f}, \texttt{sex\_m}) except
-\texttt{furniture} to get more events per stimulus segment.\todo{ouff}
+In the primary contrast of the audio-description stimulus, we contrasted
+mentions of buildings and landmarks (\texttt{geo}), and rooms and
+geometry-defining objects (\texttt{groom}) with noun occurence referring to a
+person's head or face (\texttt{fahead}), and other non-geometry related
+categories (\texttt{body}, \texttt{bodypart}, \texttt{fahead}, \texttt{object},
+\texttt{sex\_f}, \texttt{sex\_m}).
+
 % why furniture was not used
@@
 % heterogeneous category
-a) categories comprise nouns that could count as a member of another category
-(e.g. ``[a] physician''; section \ref{rationale}), and
+a) they comprise nouns that could be a member of another category (e.g. ``[a]
+physician''), and
 % richness of verbal description vs. picture
-b) nouns that only vaguely describe a scene (e.g. ``[in] Greenbow'', ``[in a]
-disco'', ''[black and white] film recordings'') [compared to whole, perceptually
-richer pictures].
-% and c) the narrator is often lacking behind a short dialogue or a change of
-% the soundscape that might already indicate a change of settings.
+b) nouns that only vaguely identify a scene (e.g. ``[in] Greenbow'', ``[in a]
+disco'', ''[black and white] film recordings'') compared to perceptually richer
+descriptions.
 
 % control contrasts
-Finally, we created several $t$-contrasts as negative controls for both stimuli
+Finally, we created several control contrasts for both stimuli
 (Tab.~\ref{tab:av-contrasts} and Tab.~\ref{tab:ao-contrasts}).
@@
 % AD stimulus
-For the audio-description stimulus, we created five $t$-contrasts
-(Tab.~\ref{tab:ao-contrasts}) to test if increased activation in the PPA was
-correlated with moments of cuts.
-
-% difference to Sengupta; Berman et al. (2010). Evaluating functional localizers
-% (2010)
-In the block-design localizer study using the established approach of contrasting blocks of
-pictures, a set of three contrasts (\textit{strict}, \textit{relaxed}, and
-\textit{simple} was created contrast (cf. \citep{sengupta2016extension}).
+For the audio-description stimulus, we created five control contrasts
+(Tab.~\ref{tab:ao-contrasts}) to test if activation in the PPA was
+correlated with moments of cuts, despite the absence of visual stimulation.
 
@@
 % alignments single subjects (for Bland-Altman-Plots) 1st level
-The GLM analysis that fitted each voxel's time course separately for each
-participant and segment was performed in functional space preserving the orientation
-of the EPI images.
-% two ways of co-registration
-Participant-specific BOLD T2* time series were anatomically co-registered in two
-ways:
+First-level GLM analyses were performed in the image-space of a participant-specific BOLD
+T2* template
 % subject template (for Bland-Altman-Plot of unthresholded maps)
 % \href{"https://github.com/psychoinformatics-de/studyforrest-data-templatetransforms/blob/master/sub-01/bold3Tp2/brain.nii.gz"}{example})
-a) via linear transformation to a participant-specific, study-specific T2* template
-(cf. \citep{sengupta2016extension}), and
+using a previously determined linear transformation \citep{sengupta2016extension}.
+For higher-level analyses image data were aligned with a study-specific T2* group template
+likewise using a previously computed non-linear transformation \citep{hanke2014audiomovie}.
 % group template (for group and individual brain slices)
 % https://github.com/psychoinformatics-de/studyforrest-data-templatetransforms/blob/master/templates/grpbold3Tp2/brain.nii.gz"
-b) via non-linear transformation to a study-specific T2* group template (cf.
-\citep{hanke2014audiomovie}).
 % MNI152
 This group template was co-registered to the MNI 152 template with an affine
-transformation (12 degrees of freedom) to facilitate visualization and
-identification of cortical structures.
+transformation (12 degrees of freedom).
 
 % second level model
-The second level analyses which averaged contrast estimates over the eight
-stimulus segments were carried out using a fixed effects model by forcing the
+The second level analyses, which averaged contrast estimates over the eight
+stimulus segments, were carried out using a fixed effects model by forcing the
 random effects variance to zero in FLAME (FMRIB's Local Analysis of Mixed
@@
 (Gaussianised T/F) statistic images were thresholded using clusters determined
-by $Z$>3.4 and a cluster-corrected significance threshold of $p$<.05
+by $Z$>3.4 and a cluster-corrected significance threshold of $p$=.05
 \citep{worsley2001statistical}.
@@
 Here again, Z (Gaussianised T/F) statistic images were thresholded using
-clusters determined by $Z$>3.4 and a (corrected) cluster significance threshold of
-$p$<.05 \citep{worsley2001statistical}.
+clusters determined by $Z$>3.4 and a corrected cluster significance threshold of
+$p$=.05 \citep{worsley2001statistical}.
 % brain region identification

### 2021-02-18 paper/main.tex
Minor polish of yesterday's marathon

@@
 We used three components of the publicly available
-\href{http://www.studyforrest.org}{studyforrest.org} dataset that has already
-been used by other research groups in independent studies (e.g.
+\href{http://www.studyforrest.org}{studyforrest.org} dataset that has
+been repeatedly used by other research groups in independent studies (e.g.
 \citep{ben2018hippocampal, jiahui2019predicting, hu2017decoding,
@@
 at a viewing distance of \unit[63]{cm}, with a movie frame projection size
-approximately \unit[21.3]$^{\circ}$ $\times$ \unit[9.3]$^{\circ}$.
+of approximately \unit[21.3]$^{\circ}$ $\times$ \unit[9.3]$^{\circ}$.
 % angle of view: VIS
@@
 The cinematographic rationale was that movie shots tend to establish the setting
-and their spatial layout at the beginning of a movie.
+and their spatial layout at their for occurence in a movie.
 % cut to recurrent scene
@@
 \begin{table*}[tbp]
-    \caption{Categories and rules to categorize the nouns spoken by
+    \caption{Categories and criteria to categorize the nouns spoken by
         the audio-description's narrator.
@@
 \toprule
-\textbf{Category} & \textbf{Rule} & \textbf{Examples} \\
+\textbf{Category} & \textbf{Criteria} & \textbf{Examples} \\
 \midrule
@@
 An evaluation of the robustness of these results with respect to similar but
-different contrasts is available in the supplementary materials.
+different contrasts is provided in the supplementary materials.
 
@@
 % second level model
-The second level analyses, which averaged contrast estimates over the eight
+The second-level analyses, which averaged contrast estimates over the eight
 stimulus segments, were carried out using a fixed effects model by forcing the

### 2021-02-18 paper/main.tex
Cut on Sengupta details

@@
 Two homologous clusters are located in the anterior part of the PPA group
-overlap.
+overlap reported by \cite{sengupta2016extension}.
 % in detail
@@
 parahippocampal cortex, the occipital and temporal fusiform gyrus and lingual
-gyrus.\todo{Havard-Oxford atlas: 3 different most prob. locations depen. on
-voxel}
+gyrus.
 % precuneus
@@
 % intro
-Third, we investigated result from both naturalistic paradigms on the level of
-individual participants to ensure that the group results are not just a by-product
-of the averaging process.
-% AD is the real shit
-Further, we hypothesized that an exclusively auditory stimulus could localize
-the PPA in individual participants and thus possibly substitute a classic visual
-localizer experiment.
+Third, we inspected results from both naturalistic paradigms on the level of
+individual participants, and compared them to the individual PPA localizations
+provided by \cite{sengupta2016extension}, who reported
 % Sengupta et al., 2016; unilateral in sub-04 and sub-20
-The visual localizer yielded bilateral parahippocampal clusters in 12 of 14
-participants and an unilateral right clusters in two participants (Tab.~3 in
-\citep{sengupta2016extension}).
-% Sengupta: 1 of 3
-Individual PPAs were assessed by visually inspecting thresholded $t$-maps
-($Z$>1.64, $p$<.05 cluster corrected) of three different $t$-contrasts, and
-titrating\todo{??} the $t$-threshold in the range of [2, 3] in until we found an
-isolated cluster (Tab.~3 in that matched the expected anatomical location
-based on literature \citep{epstein1998ppa}.
-
+bilateral parahippocampal clusters in 12 of 14
+participants and a unilateral right clusters in two participants
+\citep[Tab.~3 in][]{sengupta2016extension}.
 % one contrast to localize them all; "...and $Z$>3.4 for all"
-Contrary to \citep{sengupta2016extension}, we here used the same contrast of
-each naturalistic stimulus and the same threshold for all participants.
+Unlike \cite{sengupta2016extension}, who determined PPA clusters using three
+candidate contrasts and a variable threshold, we used a single contrast for
+each naturalistic stimulus and a uniform threshold for all participants.
 % subject space -> NeuroVault

### 2021-02-18 paper/main.tex
Tune BA plot description

@@
 each naturalistic stimulus and a uniform threshold for all participants.
-% subject space -> NeuroVault
-Results of the analyses that were performed in participant-space can be found in the
-accompanying dataset ($Z$>2.3, $p$<.05 cluster-corrected).
-% here report in group space
-For better comparisons of participants, we here report results from the analyses
-performed in group space ($Z$>3.4, $p$<.05 cluster-corrected).
 % ref to figure
 Figure~\ref{fig:subs-thresh-ppa} depicts thresholded $Z$-maps of the primary movie
-and audio-description $t$-contrast, and the outline of overlapped, individual PPAs
-co-registered to the MNI152 template.
-% one slice to show them all
-Transversal slice of $Z$=-11 was chosen as it depicts voxels of
-significant clusters in almost all participants.
-
+and audio-description $t$-contrasts, in comparison to the results of a conventional
+block-design localizer (unthresholded $Z$-maps are provided on NeuroVault).
 % AV
@@
 % difference to dedicated localizer
-We find homologous clusters in sub-20, whereas the dedicated visual localizer
-yielded only one cluster in the right hemisphere.
-
+We find bilateral clusters for participant \texttt{sub-20}, whereas the block-design
+localizer yielded only one cluster in the right hemisphere.
 % report here in group
-Results of the primary audio-description contrast yielded bilateral clusters in nine participants
-that are within or overlapping with the individual PPA.
+Results of the primary audio-description contrast yielded bilateral clusters in nine participants that are within or overlapping with the block-design localizer results.
 % subj-04
-In sub-04, two homologous clusters are apparent, whereas the dedicated localizer
-(and movie stimulus) yielded only one cluster in the right hemisphere.
+In participant \texttt{sub-04}, two bilateral clusters are apparent, whereas
+block-design localizer, and movie stimulus yielded only one cluster in the right
+hemisphere.
 % sub-09
-In sub-09 the analysis yielded one cluster in the left-hemispheric PPA.
+For another participant (\texttt{sub-09}) the analysis yielded one cluster in the
+left-hemispheric PPA.
 
@@
 % Bland-Altman-Plots
-To better depict the agreement and difference between the results of the visual
-localizer and the primary audio-description contrast, we created a Bland-Altman-Plot for every
-participant (Fig.~\ref{fig:bland-altman}).
+To illustrate the similarity of correlates of spatial processing in
+naturalistic (audio-description) and conventional stimulation, independent of a
+particular cluster-forming threshold, Bland-Altman plots for all participants
+are shown in Figure.~\ref{fig:bland-altman}).
 % what it depicts
-Each subplot visualizes the mean value and difference (localizer minus audio-description) of
-two spatially corresponding voxels in the unthresholded $Z$-maps.
-% top KDE plot
-A shift of the distribution to voxels with a mean above zero can be seen the
-further we constrain voxels to the individual PPA (cf. KDE plot for the x-axes).
-% right KDE plot
-Values above the horizontal line depict voxels that show a higher $Z$-value in
-the dedicated localizer, values below the horizontal line depict voxels that
-show a higher $Z$-value in the audio-description stimulus.
+Each subplot visualizes the mean value and difference (localizer minus audio-description) of all voxels in temporal and occipital cortices. The marginal distributions
+of the mean scores indicate a general agreement of both contrast scores across
+voxels in the PPA localization overlap as a probabilistic indicator (blue), and the
+individual block-design localizer results (red). Notably, 11 participants exhibit
+a pattern of increased $Z$-scores for the naturalistic stimulus (lower right
+quadrant) that includes voxels labeled by the block-design localizer, but
+also additional voxels.
 
@@
 
+% subject space -> NeuroVault
+Results of the analyses that were performed in participant-space can be found in the
+accompanying dataset ($Z$>2.3, $p$<.05 cluster-corrected).
+
 \section*{Acknowledgements}

### 2021-02-18 paper/main.tex
homolog -> bilateral
I think this better describes what we intent to say

@@
 % LOC
-Two additional homologous clusters are located in the superior lateral occipital
+Two additional bilateral clusters are located in the superior lateral occipital
 cortex.
@@
 % overlap with ROI
-Two homologous clusters are located in the anterior part of the PPA group
+Two bilateral clusters are located in the anterior part of the PPA group
 overlap reported by \cite{sengupta2016extension}.
@@
 % precuneus
-Two additional homologous clusters are apparent in the ventral precuneus
+Two additional bilateral clusters are apparent in the ventral precuneus
 extending into the retrosplenial cortex.
 % LOC
-Finally, two homologous clusters are located in the superior lateral occipital
+Finally, two bilateral clusters are located in the superior lateral occipital
 cortex.

### 2021-02-18 paper/main.tex
typos in intro & methods

--- 2021-02-18 paper/main.tex
@@
 On a group level, increased activation correlating with spatial information
-occcuring in the movie is overlapping with a traditionally localized PPA.
+occurring in the movie is overlapping with a traditionally localized PPA.
 % results: group AD
@@
 % results: individual AD
-On an individual level, we find signficant bilateral activity in the PPA
+On an individual level, we find significant bilateral activity in the PPA
 of nine individuals and unilateral activity in one individual.
@@
 FSL v5.0.9 (\href{https://www.fmrib.ox.ac.uk/fsl}{FMRIB's Software Library};
-\citep{smith2004fsl}) on a compute-cluster running
+\citep{smith2004fsl}) on a computer-cluster running
 \href{http://neuro.debian.net}{NeuroDebian} \citep{halchenko2012open}.
@@
 The cinematographic rationale was that movie shots tend to establish the setting
-and their spatial layout at their for occurence in a movie.
+and their spatial layout at their first occurence in a movie.
 % cut to recurrent scene
@@
 \begin{table*}[tbp]
-    \caption{Overview of annotated stimulus features of audio-visual
+    \caption{Overview of annotated stimulus features of the audio-visual
     movie.
@@
 \tabularnewline
-\texttt{groom} & rooms \& locales or geometry-defining elements & living room; wall, door, window, floor
+\texttt{groom} & rooms \& locales, or geometry-defining elements & living room; wall, door, window, floor
 \tabularnewline
@@
 
-% low-leve confounds: intro
+% low-level confounds: intro
 Lastly, we algorithmically annotated the temporal structure of low-level
@@
 mean luminance of each frame's left and right half, the difference in mean
-luminance of the lower and upper half.  As an indiciator of visual change, we
+luminance of the lower and upper half.  As an indicator of visual change, we
 compute perceptual fingerprints for each movie frame using the pHash library
-\citep{zauner2010implementation} and recorded the commulative bitwise
+\citep{zauner2010implementation} and recorded the cummulative bitwise
 difference to the previous frame.
@@
 Finally for both audio tracks, we computed the left-right difference in volume
-and root mean square energy averaged across the length of every movie frame
+and root mean square volume averaged across the length of every movie frame
 (\unit[40]{ms}).
@@
 % we checked correlations
-Given the unknown confound structure of the naturalistic stimuli we inspected
+Given the unknown confound structure of the naturalistic stimuli, we inspected
 % correlations within stimuli and across stimuli
@@
 % AV regressors in AV
-Likewise, the audio-description design matrix included movie cut-related regressors
+Likewise, the audio-description design matrix included movie cut related regressors
 listed Table~\ref{tab:av-events} (excluding \texttt{no\_cut}).
@@
 mentions of buildings and landmarks (\texttt{geo}), and rooms and
-geometry-defining objects (\texttt{groom}) with noun occurence referring to a
+geometry-defining objects (\texttt{groom}) with nouns referring to a
 person's head or face (\texttt{fahead}), and other non-geometry related

### 2021-02-18 paper/main.tex
Small fix

--- 2021-02-18 paper/main.tex
@@
 particular cluster-forming threshold, Bland-Altman plots for all participants
-are shown in Figure.~\ref{fig:bland-altman}).
+are shown in Figure~\ref{fig:bland-altman}.
 % what it depicts

### 2021-02-18 paper/main.tex
Critical caption correction, figure update pending
"union" not "overlap", also color code fixed.

@@
     \includegraphics[width=\linewidth]{figures/group-slices}
-    \caption{Mixed-effects group-level (N=14) GLM results. Significant clusters
-        ($Z$>3.4, $p$<.05 cluster-corrected) are overlaid on the MNI152 T1-weighted
-        head template (gray).
-        Light gray: The audio-description's field of view
-        (cf. \citep{hanke2014audiomovie}).
-        Black: outline of overlapping individual PPA ROIs
-        \citep{sengupta2016extension}.
-        The results of audio-description's primary $t$-contrast (blue) that
+
+    \caption{Mixed-effects group-level (N=14) clusters ($Z$>3.4, $p$<.05
+      cluster-corrected) of activity correlated with the processing of spatial
+      information are displayed on top of the MNI152 T1-weighted head template,
+      with the acquisition field-of-view for the audio-description study
+      highlighted.
+      %
+      The results of the audio-description's primary $t$-contrast (blue) that
       compares geometry-related nouns spoken by the narrator to non-spatial
-        nouns (\texttt{geo, groom} > all non-spatial
-        categories)
-        are overlaid over the movie's primary $t$-contrast (blue) that compares
-        cuts to a setting depicted for the first time with cuts within a
-        recurring setting
+      nouns (\texttt{geo, groom} > all non-spatial categories) are overlaid
+      on the movie's primary $t$-contrast (red) that compares cuts to a
+      setting depicted for the first time with cuts within a recurring setting
       (\texttt{vse\_new > vpe\_old}).
+      %
+      For comparison, the union of the individual PPA localization reported
+      by \cite{sengupta2016extension} are indicated as a black outline.
     }
+
     \label{fig:group-slices}

### 2021-02-18 code/plot-group-and-individuals.py
plot union instead of overlap

@@ -185,7 +185,7 @@ def process_stability(ao_prob, av_prob, outfpath):
     red = mpl.patches.Patch(color='#f03523',
                             label='movie cuts (5 contrasts)',)
     black = mpl.patches.Patch(color='#454545',
-                              label='overlap of individual PPA masks (Sengupta et al., 2016)')
+                              label='union of individual PPA masks (Sengupta et al., 2016)')
 
     legendAxis.legend(handles=[blue, red, black],
                       loc='upper center',
@@ -358,7 +358,7 @@ def process_group_averages(outfpath):
     red = mpl.patches.Patch(color='#f03523',
                             label='vse_new > vpe_old (movie)')
     black = mpl.patches.Patch(color='#454545',
-                              label='overlap of individual PPA masks (Sengupta et al., 2016)')
+                              label='union of individual PPA masks (Sengupta et al., 2016)')
 
     legendAxis.legend(handles=[blue, red, black],
                       loc='upper center',
@@ -496,7 +496,7 @@ def process_individuals(AUDIO_IN_PATTERN):
                             figsize=fsize,
                             constrained_layout=False)
     # set the space between sublots/subjects in a way that title and legend
-    # to not overlapt
+    # to not overlap
 
     plt.subplots_adjust(wspace=0.0, hspace=0)
     # trim the axis using the helper function

### 2021-02-18 paper/main.tex

@@
 \begin{table*}[tbp]
-\caption{Significant clusters ($Z$-threshold $Z$>3.4; $p$<.05 cluster-corrected)
+\caption{Clusters ($Z$-threshold $Z$>3.4; $p$<.05 cluster-corrected)
     of the primary $t$-contrast for the audio-visual movie comparing cuts to a
     setting depicted for the first time with cuts within a recurring setting
-    (\texttt{vse\_new > vpe\_old}).
-    Clusters sorted by voxel size.
-    The first brain structure given contains the voxel with the maximum Z-Value,
+    (\texttt{vse\_new > vpe\_old}), sorted by size.
+    The first brain structure given contains the voxel with the maximum $Z$-value,
     followed by brain structures from posterior to anterior, and partially
-    covered areas (l. = left; r. = right; c. = cortex; g. = gyrus).
-    CoG: Center of Gravity}
+    covered areas (l.: left; r: right; c.: cortex; g.: gyrus; CoG: Center of
+  Gravity).}
 \label{tab:res-av-group1}
-\begin{tabular}{rrrrrrrrrp{3.5cm}}
+\small
+\begin{tabular}{rrrrrrrrrp{4.7cm}}
 \toprule
@@
 \\ \cmidrule{4-6} \cmidrule{7-9}
-Voxels & $p_{corr.}$ & Z-max & X & Y & Z  & X & Y & Z & Structure \\
+Voxels & $p_{corr.}$ & $Z_{max}$ & X & Y & Z  & X & Y & Z & Structure \\
 \midrule
-3003 & <.00001 & 5.31 & 22.5 & -45.5 & -12 & 4.53 & -63.3 & -3.72 & r. lingual g.; r.
-cuneal c., intracalcarine c., bilaterally occipital fusiform g., precuneus,temporal fusiform c., posterior parahippocampal c.  \\
-154 & <.00001 & 4.46 & -35 & -83 & 28 & -32.8 & -86.2 & 21.4 & l. superior
+3003 & <.00001 & 5.31 & 22.5 & -45.5 & -12 & 4.53 & -63.3 & -3.7 & r.~lingual g.; r.~cuneal c., intracalcarine c., bilaterally occipital fusiform g., precuneus,temporal fusiform c., posterior parahippocampal c.
+\\
+154 & <.00001 & 4.46 & -35 & -83 & 28 & -32.8 & -86.2 & 21.4 & l.~superior
 lateral occipital c. \\ % 0.000000656
-121 & <.00001 & 4.65 & 25 & -80.5 & 25.5 & 23.7 & -83.8 & 25.4 & r. superior
+121 & <.00001 & 4.65 & 25 & -80.5 & 25.5 & 23.7 & -83.8 & 25.4 & r.~superior
 lateral occipital cortex \\ % 0.00000769
@@
 \begin{table*}[tbp]
-    \caption{Significant clusters ($Z$-threshold $Z$>3.4; $p$<.05 cluster-corrected)
+\caption{Clusters ($Z$-threshold $Z$>3.4; $p$<.05 cluster-corrected)
     of the primary $t$-contrast for the audio-description comparing
     geometry-related nouns to non geometry-related nouns spoken by the
-        audio-description's narrator (\texttt{geo, groom > all non-geo}).
-        Clusters sorted by voxel size.
-    The first brain structure given contains the voxel with the maximum Z-Value,
-followed by brain structures from posterior to anterior, and partially covered
-areas (l. = left; r. = right; c. = cortex; g. = gyrus).
-    CoG: Center of Gravity}
+    audio-description's narrator (\texttt{geo, groom > all non-geo}), sorted by size.
+    The first brain structure given contains the voxel with the maximum $Z$-value,
+    followed by brain structures from posterior to anterior, and partially
+    covered areas (l.: left; r: right; c.: cortex; g.: gyrus; CoG: Center of
+    Gravity).}
     \label{tab:res-ao-group1}
-    \begin{tabular}{rrrrrrrrrp{3.5cm}}
+\small
+\begin{tabular}{rrrrrrrrrp{4.7cm}}
 \toprule
@@
 \\ \cmidrule{4-6} \cmidrule{7-9}
-Voxels & $p_{corr.}$ & Z-max & X & Y & Z  & X & Y & Z & Structure \\
+Voxels & $p_{corr.}$ & $Z_{max}$ & X & Y & Z  & X & Y & Z & Structure \\
 \midrule
-188 & <.00001 & 4.48 & -17.5 & -65.5 & 25.5 & -14.7 & -59.1 & 15.2 & l.
-precuneus \\ % 0.0000000596
-164 & <.00001 & 4.47 & 17.5 & -58 & 23 & 15.6 & -55.6 & 16 & r. precuneus;
+188 & <.00001 & 4.48 & -17.5 & -65.5 & 25.5 & -14.7 & -59.1 & 15.2 & l.~precuneus \\ % 0.0000000596
+164 & <.00001 & 4.47 & 17.5 & -58 & 23 & 15.6 & -55.6 & 16 & r.~precuneus;
 \\ % 0.000000238
-83 & .00013 & 4.48 & 27.5 & -43 & -17 & 27.2 & -41.1 & -14 & r. temporal
-(occipital) fusiform c.; posterior parahippocampal g. \\ % 0.000128
-73 & .00031 & 3.93 & -22.5 & -43 & -12 & -23.9 & -43.6 & -11.2 & l. lingual
-g.; temporal (occipital) fusiform g., posterior parahippocampal c. \\ % 0.000128
-63 & .00082 & 4.1 & 40 & -75.5 & 30.5 & 40.9 & -76.3 & 28.6 & r. superior
+83 & .00013 & 4.48 & 27.5 & -43 & -17 & 27.2 & -41.1 & -14 & r.~occipito-temporal fusiform c.; posterior parahippocampal g. \\ % 0.000128
+73 & .00031 & 3.93 & -22.5 & -43 & -12 & -23.9 & -43.6 & -11.2 & l.~lingual
+g.; occipito-temporal fusiform g., posterior parahippocampal c. \\ % 0.000128
+63 & .00082 & 4.1 & 40 & -75.5 & 30.5 & 40.9 & -76.3 & 28.6 & r.~superior
 lateral occipital c. \\ % 0.000824
-37 & .0129 & 4.24 & -37.5 & -78 & 33 & -38.4 & -79.5 & 28.9 & l. superior
+37 & .0129 & 4.24 & -37.5 & -78 & 33 & -38.4 & -79.5 & 28.9 & l.~superior
 lateral occipital c. \\ % 0.0129

### 2021-02-18 paper/main.tex
First half of discussion

@@
 % previous studies
-Previous studies reported increased hemodynamic activity in the PPA when
-participants were watching static pictures of landscape compared to pictures of
-faces or objects (e.g. \citep{epstein1998ppa, epstein1999parahippocampal})
-whereas one study using spoken sentences reported mixed results
-\citep{aziz2008modulation}.
+Several studies have reported increased hemodynamic activity in the PPA,
+attributed to the processing of spatial information, for example, when
+participants were watching static pictures of landscapes compared to pictures of
+faces or objects \citep[e.g.,][]{epstein1998ppa, epstein1999parahippocampal}.
+However, reports regarding the correlates of processing spatial information in
+non-visual stimulation are less clear \citep{aziz2008modulation}.
 % current study: similar
-In line with previous studies, we operationalized spatial perception via GLM $t$-contrasts.
+In line with previous studies, we investigated the hemodynamic response to
+spatial information using a model-based, mass-univariate approach.
 % current study: dissimilar
-Contrary to previous studies, our current approach is not based on carefully
-designed sets of stimuli but based on annotated stimulus features incidentally
-occurring in two naturalistic stimuli.
+However, instead of using a conventional set of stimuli, assembled to
+specifically and predominantly evoke the processing spatial information, we
+employed a naturalistic movie stimulus that was designed for entertainment.
+
+% PPA: intro
+In an earlier study, \cite{bartels2004mapping} manually annotated the content
+of individual movie frames (color, faces, language, and human bodies) and found
+that the expected specialization of functional areas is preserved during movie
+watching.
+%
+In contrast, we aimed to exploit a cinematographic confound in the stimulus
+structure, where
+% establishing shots vs. e.g. over-the-shoulder shots
+film directors tend to establish the spatial layout of locations in earlier
+shots and only later focus more on detailed depictions of people and objects
+\citep{brown2012cinematography, mercado2011filmmakers}.
+% hypo
+We hypothesized that due to the complex nature of a naturalistic stimulus,
+unrelated factors would be balanced across a large number of events, and make
+the bias of spatial information availability in particular events accessible to
+convential model-based statistical analysis of BOLD fMRI data.
+%
+This approach required a detailed description of the occurence of relevant
+stimulus features. For both types of naturalistic stimuli used here, a movie
+and its audio-description, this annotation revealed the respective number of
+incidentally occurring events to be similar to those of a conventional
+experimental paradigm used in neuroimaging, for the purpose of localizing
+particular regions of interest.
+
 % group AV
-On a group level, results for the audio-visual movie show
+On a group-average level, results for the audio-visual movie show
 significantly increased hemodynamic activity spatially overlapping with a
-traditionally localized PPA but also extending into earlier visual cortices.
+conventionally localized PPA, but also extending into earlier visual cortices.
 % group AD
-Results for the audio-description also reveal significant activation in the PPA
+Likewise, results for the audio-description identify significant activation in the PPA
 but restricted to its anterior part.
 % individual level
-On an individual level, results of the audio-description show significant
+Moroever, the group averages are representative for the majority of individual
+results, where, for example, the audio-description stimulus yields
 bilateral clusters in the anterior PPA of nine participants and a unilateral cluster
@@
 % meaning: generalization to naturalistic stimuli
-Results suggest that increased activation in the PPA during the perception of
-static pictures generalize to the perception of spatial information embedded in
-a movie and an exclusively auditory stimulus.
+These findings suggest that increased activation in the PPA during the perception of
+static pictures generalizes to the perception of spatial information embedded in
+a movie or a purely auditory narrative.
+% narrative as substitute
+The presented evidence on the in-principle suitability of an auditory-only paradigm
+for localizing the PPA, may offer a path to the development of diagnostic procedures
+more suitable for populations of individuals with visual impairments or conditions
+like nystagmus.
 % meaning: aPPA vs. pPPA
 Our results provide further evidence that the PPA can be divided into functional
-subregions.
-% narrative as substitute
-An auditory narrative might substitute a visual paradigm to localize the PPAs
-anterior part in visually impaired participants.
-
-% PPA: intro
-First, we analyzed data from the movie offering ecologically more valid visual
-stimulation.
-%
-An early study \citep{bartels2004mapping} that manually annotated the content of
-movie frames (color, faces, language, and human bodies) found that
-specialization of functional areas is preserved during movie watching.
-\todo{clusters are pretty big too}
-%
-Contrary to \citep{bartels2004mapping} who annotated the content of movie
-frames, we categorized each frame after a cut independent of its specific
-content
-% exploited cinematographic tendencies
-exploiting a cinematographic confound in the stimulus structure (cf. section
-\ref{rationale}):
-% establishing shots vs. e.g. over-the-shoulder shots
-film directors tend to establish the geometry of locations earlier in the movie
-and tend to later focus more on persons and objects relevant to the evolved plot
-\citep{brown2012cinematography, mercado2011filmmakers}.
-% hypo
-Despite our ad hoc approach, we hypothesized that confounding variables would
-average out, and our whole-brain analyses would lead to significant clusters in
-the PPA.
+subregions.\todo{what is the other evidence?}
+
 % results
-Group results of the movie stimulus' primary contrast yielded one cluster that
-spans the group overlap of individual PPA ROIs from anterior to posterior.
+Group results of the movie stimulus' primary contrast yielded a large cluster
+that spans the group overlap of individual PPA ROIs from anterior to posterior.
 % confound of higher perception
-The cluster's extension into more posterior, early visual areas can be
-attributed to the averaging process that did not control for confounding visual
-features.
+The cluster's extension into more posterior, earlier visual areas could be
+attributed to the temporal averaging across events that did not control for
+confounding visual features.
 % solution
-Thus to control confounding variables, future studies that aim to use a movie to
-localize visual areas in individual participants should extensively annotate the
-content of frames (e.g.  using the open-source solution ``Pliers'' for feature
-extraction from a visual naturalistic stimulus; \citep{mcnamara2017developing}).
-% we took advantage of cinematography
-We here took advantage of an idiosyncrasy of movie directing to shift from
-depicting the spatial layout to to later depicting persons and objects.
-% know your stimulus
-Given that this shift is common in movies, investigators should be aware that
-cinematographic tendencies are part of movie's confound structure that might,
-depending on the research question, influence the results.
-% conclusion
-In summary, results from the visual localizer paradigm using blocks of pictures
-generalize to an ad hoc approach to operationalize the perception of spatial
-information at the moment of cuts in an audio-visual movie.
-
-% intro
-Second, we analyzed data from the audio-description offering exclusively
-auditory stimulation.
+Future studies that aim to use a movie to localize visual areas in individual
+participants should extensively annotate the content of frames \citep[e.g., using the
+open-source solution ``Pliers'' for feature extraction from a visual
+naturalistic stimulus;][]{mcnamara2017developing}.
+
+% MIH: second time this notion is coming up in the discussion
+%% we took advantage of cinematography
+%We here took advantage of an idiosyncrasy of movie directing to shift from
+%depicting the spatial layout to to later depicting persons and objects.
+%% know your stimulus
+%Given that this shift is common in movies, investigators should be aware that
+%cinematographic tendencies are part of movie's confound structure that might,
+%depending on the research question, influence the results.
+%% conclusion
+%In summary, results from the visual localizer paradigm using blocks of pictures
+%generalize to an ad hoc approach to operationalize the perception of spatial
+%information at the moment of cuts in an audio-visual movie.
+
 % hypothesis
-Encouraged by \citep{aziz2008modulation}, we hypothesized that semantic spatial
+Based on the report by \cite{aziz2008modulation}, we hypothesized that semantic spatial
 information embedded in the audio-description stimulus would correlate with
@@
 % diff to Aziz (2008)
-\citep{aziz2008modulation} modeled events from on- to offset of sentences
-(describing unknown and famous places and faces), and compared activity levels
+\cite{aziz2008modulation} modeled events from onset to offset of sentences,
+describing unknown and famous places and faces, and compared activity levels
 that were averaged across voxels of ROIs (PPA and fusiform face area, FFA
@@
 % Aziz results
-Study results revealed significantly decreased activity in only the left PPA
-compared to activity in the FFA for sentences describing famous places compared
+Their results showed decreased activity in only the left PPA
+compared to activity in the FFA for sentences describing famous places in contrast
 to famous faces.
 % we: model & whole brain
-Here we modeled events from on- to offset of single words and performed a
-whole-brain analysis.
+In this study, we modeled events from onset to offset of single words and performed a
+voxelwise whole-brain analysis.
 % our results
@@
 % concluding statement
-Contrary to \citep{aziz2008modulation}, our group results suggest that auditory
+Contrary to \cite{aziz2008modulation}, our group results suggest that auditory
 spatial information compared to non-spatial information correlates with
@@
 % previous studies: no task
-Usually studies that use small sets of experimentally controlled stimuli also
+It is common for conventional localizer paradigms to
 employ a task to keep participants attentive to the stimuli.
@@
 % we have no task neither
-Our paradigm is similar in that sense that our participants had no behavioral or
-cognitive task (e.g. forming a mental image of the stimuli; cf.
-\citep{ocraven2000mental})  but just had to ``enjoy the audio-description''.
+The naturalistic stimulation paradigm employed here is similar in the sense that participants had no behavioral or
+cognitive task \cite[e.g., forming a mental image of the stimuli;][]{ocraven2000mental} but just had to ``enjoy the presentation''.
 % but still: we are different
-Our paradigm still differs from \citep{epstein1998ppa} because the modeled
-stimulus features were incidentally embedded in a continuous stream of auditory
-information preventing participants from making assumptions about the
-investigated perceptual process.
+This naturalistic paradigm nevertheless differs from \cite{epstein1998ppa},
+because the relevant stimulus features were embedded in a continuous stream of complex
+auditory (and visual) information that makes it unlikely that participants
+speculate on the purpose of the investigation or perform undesired and unknown
+evaluation or categorization of isolated stimuli.
 % concluding statement: kinda automatic process
-Hence, current results also suggest that verbal spatial information is processed
-in the anterior PPA casually and does not necessarily rely on deliberately
-paying attention to verbal spatial information.
+Our results therefore indicate that verbally communicated spatial information
+is processed, in the anterior PPA, automatically and without specifically
+guided attention.
 
@@
         Cluster are overlaid on top of the MNI152 T1-weighted head template
-        (gray).
+        with the acquisition field-of-view for the audio-description study
+        highlighted.
         Black: outline of overlapping individual PPA ROIs.
-        Light gray: The audio-description's field-of-view (cf.
-        \citep{hanke2014audiomovie}).
         The figure shows that some contrasts yielded significant clusters
@@
 \end{document}
-\documentclass[english]{article}

### 2021-02-18 paper/main.tex
minor typo

--- 2021-02-18 paper/main.tex
@@
 % group level
-On a group average level, we compare results from whole-brain GLM
+On a group average level, we compared results from whole-brain GLM
 analyses of the movie and the audio-description to a
@@
 bilateral parahippocampal clusters in 12 of 14
-participants and a unilateral right clusters in two participants
+participants and unilateral right clusters in two participants
 \citep[Tab.~3 in][]{sengupta2016extension}.

### 2021-02-18 paper/main.tex
add references; minor discussion changes

@@
 the evolved plot (\texttt{vpe\_old}) \citep{brown2012cinematography,
-mercado2011filmmakers}.
+katz1991film, mascelli1998five}.
 % neuroscientific rationale The neuroscientific rationale was that activity in
@@
 
+\pagebreak [4]
+
 \section{Discussion}
@@
 However, reports regarding the correlates of processing spatial information in
-non-visual stimulation are less clear \citep{aziz2008modulation}.
+auditory semantic stimulation are less clear \citep{aziz2008modulation}.
 % current study: similar
@@
 film directors tend to establish the spatial layout of locations in earlier
-shots and only later focus more on detailed depictions of people and objects
-\citep{brown2012cinematography, mercado2011filmmakers}.
+shots and later focus more on detailed depictions of people and objects
+\citep{brown2012cinematography,
+katz1991film, mascelli1998five}.
 % hypo
-We hypothesized that due to the complex nature of a naturalistic stimulus,
+We\todo{following two sentences are confusing imo} hypothesized that due to the complex nature of a naturalistic stimulus,
 unrelated factors would be balanced across a large number of events, and make
@@
 % group AV
-On a group-average level, results for the audio-visual movie show
-significantly increased hemodynamic activity spatially overlapping with a
-conventionally localized PPA, but also extending into earlier visual cortices.
+On a group-average level, results for the audio-visual movie show significantly
+increased hemodynamic activity spatially overlapping with a conventionally
+localized PPA, but also extending into earlier visual cortices.
 % group AD
-Likewise, results for the audio-description identify significant activation in the PPA
-but restricted to its anterior part.
+Likewise, results for the audio-description identify significant activation in
+the PPA but restricted to its anterior part.
 % individual level
 Moroever, the group averages are representative for the majority of individual
-results, where, for example, the audio-description stimulus yields
-bilateral clusters in the anterior PPA of nine participants and a unilateral cluster
-in one participant.
+results, where, for example, the audio-description stimulus yields bilateral
+clusters in the anterior PPA of nine participants and a unilateral cluster in
+one participant.
 % meaning: generalization to naturalistic stimuli
-These findings suggest that increased activation in the PPA during the perception of
-static pictures generalizes to the perception of spatial information embedded in
-a movie or a purely auditory narrative.
+These findings suggest that increased activation in the PPA during the
+perception of static pictures generalizes to the perception of spatial
+information embedded in a movie or a purely auditory narrative.
 % narrative as substitute
-The presented evidence on the in-principle suitability of an auditory-only paradigm
-for localizing the PPA, may offer a path to the development of diagnostic procedures
-more suitable for populations of individuals with visual impairments or conditions
-like nystagmus.
+The presented evidence on the in-principle suitability of an auditory-only
+paradigm for localizing the PPA may offer a path to the development of
+diagnostic procedures more suitable for populations of individuals with visual
+impairments or conditions like nystagmus.
 % meaning: aPPA vs. pPPA
 Our results provide further evidence that the PPA can be divided into functional
-subregions.\todo{what is the other evidence?}
+subregions \citep{aminoff2007parahippocampal, aminoff2015associative,
+baldassano2013differential, baldassano2016two, baumann2016functional}.
 
@@
 Based on the report by \cite{aziz2008modulation}, we hypothesized that semantic spatial
-information embedded in the audio-description stimulus would correlate with
+information embedded in the audio-description would correlate with
 increased hemodynamic activity in the PPA.
@@
 % we: model & whole brain
-In this study, we modeled events from onset to offset of single words and performed a
+In the current study, we modeled events from onset to offset of single words and performed a
 voxelwise whole-brain analysis.
@@
 because the relevant stimulus features were embedded in a continuous stream of complex
-auditory (and visual) information that makes it unlikely that participants
-speculate on the purpose of the investigation or perform undesired and unknown
+auditory (and visual) information which makes it unlikely that participants
+speculated on the purpose of the investigation or perform undesired and unknown
 evaluation or categorization of isolated stimuli.
@@
 In the audio-description's primary contrast, we did not include the categories
-that contained switches from one setting to another (\texttt{se\_new} and
+that contain switches from one setting to another (\texttt{se\_new} and
 \texttt{se\_old}) which one might assume to contain the auditory equivalent to
@@
 %
-Whereas \citep{sengupta2016extension} chose the subjectively ``best fitting''
-$t$-threshold in $t$-map from one of three contrasts by visual judgment, we used
+Whereas \cite{sengupta2016extension} chose the subjectively ``best fitting''
+$t$-threshold in a $t$-map from one of three contrasts by visual judgment, we used
 the same contrast and threshold ($Z$>3.4, $p$<.05 cluster-corrected) for all
@@
 the revealed correlation patterns can be attributed to different features
-inherent in the visual compared to the verbal stimuli.
+inherent in the visual stimuli compared to the purely auditory stimulus.
 % visual scenes: probably submodules
@@
 features of scenes (e.g. real-word size \citep{park2015parametric}; a scene's
-abstract identity/category \citep{marchette2015outside, watson2016patterns}) and
-objects (e.g. spatial contextual associations \citep{aminoff2007parahippocampal,
-aminoff2013role}).
+abstract category \citep{marchette2015outside, watson2016patterns}) and
+objects (e.g. spatial contextual associations \citep{aminoff2007parahippocampal, aminoff2013role}).
 % connectivity
@@
 The aPPA might be more concerned with non-visual aspects of spatial information
-(e.g. spatial contextual information \citep{aminoff2013role,
-aminoff2015associative, baumann2016functional}) as immanent in both visual and
+(e.g. spatial contextual information \citep{aminoff2007parahippocampal}) as immanent in both visual and
 verbal stimuli.

### 2021-02-18 paper/main.tex
rephrase long sentences at discussions beginning

@@
 % previous studies
-Several studies have reported increased hemodynamic activity in the PPA,
+Several studies have reported increased hemodynamic activity in the PPA
 attributed to the processing of spatial information, for example, when
@@
 faces or objects \citep[e.g.,][]{epstein1998ppa, epstein1999parahippocampal}.
+% auditory semantics unclear
 However, reports regarding the correlates of processing spatial information in
-auditory semantic stimulation are less clear \citep{aziz2008modulation}.
+verbal stimulation are less clear \citep{aziz2008modulation}.
 % current study: similar
@@
 However, instead of using a conventional set of stimuli, assembled to
-specifically and predominantly evoke the processing spatial information, we
+specifically and predominantly evoke the processing of spatial information, we
 employed a naturalistic movie stimulus that was designed for entertainment.
@@
 % PPA: intro
-In an earlier study, \cite{bartels2004mapping} manually annotated the content
-of individual movie frames (color, faces, language, and human bodies) and found
-that the expected specialization of functional areas is preserved during movie
+In an earlier study, \cite{bartels2004mapping} manually annotated the content of
+individual movie frames (color, faces, language, and human bodies) and found
+that the functional specialization of brain areas is preserved during movie
 watching.
@@
 shots and later focus more on detailed depictions of people and objects
-\citep{brown2012cinematography,
-katz1991film, mascelli1998five}.
+\citep{brown2012cinematography, katz1991film, mascelli1998five}.
 % hypo
-We\todo{following two sentences are confusing imo} hypothesized that due to the complex nature of a naturalistic stimulus,
+We hypothesized that due to the complex nature of a naturalistic stimulus,
 unrelated factors would be balanced across a large number of events, and make
-the bias of spatial information availability in particular events accessible to
-convential model-based statistical analysis of BOLD fMRI data.
-%
-This approach required a detailed description of the occurence of relevant
-stimulus features. For both types of naturalistic stimuli used here, a movie
-and its audio-description, this annotation revealed the respective number of
-incidentally occurring events to be similar to those of a conventional
-experimental paradigm used in neuroimaging, for the purpose of localizing
-particular regions of interest.
+the bias of spatial information accessible to a convential model-based
+statistical analysis of BOLD fMRI data.
+% we need a detailed description -> annotation
+The current model-driven approach required a detailed annotation of the
+occurence of relevant stimulus features.
+% event counts ftw
+The annotation of both types of naturalistic stimuli, a movie and its
+audio-description, revealed the respective number of incidentally occurring
+events to be similar to those of a conventional experimental paradigm used to
+localize functional regions of interest.
 

### 2021-02-18 paper/main.tex
I am confused

@@
 increased hemodynamic activity spatially overlapping with a conventionally
-localized PPA, but also extending into earlier visual cortices.
+localized PPA but also extending into earlier visual cortices.
 % group AD
@@
 % narrative as substitute
-The presented evidence on the in-principle suitability of an auditory-only
+The presented evidence on the in-principle suitability of a purely auditory
 paradigm for localizing the PPA may offer a path to the development of
-diagnostic procedures more suitable for populations of individuals with visual
-impairments or conditions like nystagmus.
+diagnostic procedures more suitable for individuals with visual impairments or
+conditions like nystagmus.
 % meaning: aPPA vs. pPPA
@@
 subregions \citep{aminoff2007parahippocampal, aminoff2015associative,
-baldassano2013differential, baldassano2016two, baumann2016functional}.
+baldassano2013differential, baldassano2016two,
+baumann2016functional}.\todo{claim hängt hier etwas in der Luft; wird später
+ausführlicher diskutiert}
 
@@
 Future studies that aim to use a movie to localize visual areas in individual
-participants should extensively annotate the content of frames \citep[e.g., using the
-open-source solution ``Pliers'' for feature extraction from a visual
+participants should extensively annotate the content of frames \citep[e.g.,
+using the open-source solution ``Pliers'' for feature extraction from a visual
 naturalistic stimulus;][]{mcnamara2017developing}.

### 2021-02-18 paper/main.tex
make clearer that text refers to the movie

@@
 %
-In contrast, we aimed to exploit a cinematographic confound in the stimulus
-structure, where
+In contrast, we aimed to exploit a cinematographic confound in structure of
+movies, where
 % establishing shots vs. e.g. over-the-shoulder shots
@@
 % hypo
-We hypothesized that due to the complex nature of a naturalistic stimulus,
+We hypothesized that due to the complex nature of the naturalistic stimulus,
 unrelated factors would be balanced across a large number of events, and make

### 2021-02-19 paper/main.tex
Expand and format data citations

@@
 
+\begin{itemize}
 % cut anno
-1. Häusler, C. O. \& Hanke M. Dataset 1 in: An annotation of cuts, depicted
+\item Häusler, C. O. \& Hanke M. Dataset 1 in: An annotation of cuts, depicted
 locations, and temporal progression in the motion picture "Forrest Gump".
@@
 % speech anno
-2. Häusler, C. O. \& Hanke M. \emph{OSF}
+\item Häusler, C. O. \& Hanke M. \emph{OSF}
 \href{https://doi.org/10.17605/OSF.IO/GFRME}{10.5256/f1000research.9536.d134823}
@@
 % audio-description
-3. Hanke, M., Baumgartner, F. J., Ibe, P., Kaule, F. R., Pollmann, S., Speck,
-O., Zinke, W. \& Stadler, J. \emph{OpenNEURO}
-\href{https://openneuro.org/datasets/ds000113}{ds000113} (2014). \todo{4
-datasets \& using authors/year of the audio-description}
+\item Hanke, M., Baumgartner, F.~J., Ibe, P., Kaule, F.~R., Pollmann, S., Speck, O.,
+  Zinke, W., \& Stadler, J. \emph{OpenfMRI} \href{https://openfmri.org/dataset/ds000113}{ds000113} (2014)
+
+\item Sengupta, A., Kaule, F. R., Guntupalli, J. S., Hoffmann, M. B., Häusler, C., Stadler, J. \& Hanke, M.
+  \emph{OpenfMRI} \href{https://openfmri.org/dataset/ds000113c}{ds000113c} (2016).
+
+\item Hanke, M., Adelhöfer, N., Kottke, D., Iacovella, V., Sengupta, A., Kaule, F.~R., Nigbur, R., Waite, A.~Q.,
+  Baumgartner, F.~J. \& Stadler, J. (2016).
+  \emph{OpenfMRI} \href{https://openfmri.org/dataset/ds000113d}{ds000113d} (2016).
+\end{itemize}
 

### 2021-02-19 paper/main.tex
Minor fix and cleanup

@@
 %
-In contrast, we aimed to exploit a cinematographic confound in structure of
+In contrast, we aimed to exploit a cinematographic confound in the structure of
 movies, where
@@
 parahippocampal region.
-
-\todo[inline]{discussion of Bland-Altman-Plots?; dunno if this is meaningful:
-$Z$-scores in the anterior part of PPA are higher in audio-description contrasts than in contrast
-of localizer}
 

### 2021-02-19 paper/main.tex
Transcribe discussion outline as it is now

@@
 \section{Discussion}
+
+Outline:
+\begin{enumerate}
+\item Speech is new
+\item No frame-wise info, but high-level cinematographic semantics -- however, only for the movie stimulus
+\item Conclusion: stimuli are suitable, and on-par for conventional ones
+\item Compare the naturalistic results with each other, anterior bias (already hint on audio localizer)
+\item issues with visual model, call for more confounds
+\item how different from aziz?
+\item impact of no task?
+\item particular composition of audio contrast vs optimal visual stimuli
+\item compare audio results to block-design localizer, again anterior bias, not an averaging effect
+\item cite poldrack2007 to state that the procedure in sengupta was better, but we nevertheless did not do it...
+\item actual discussion of anterior bias
+\item other results RSC LOC
+\item concluding statement
+\end{enumerate}
 

### 2021-02-19 paper/main.tex
First complete edit of the discussion

--- 2021-02-19 paper/main.tex
@@
 
+%#1
 % previous studies
@@
 specifically and predominantly evoke the processing of spatial information, we
-employed a naturalistic movie stimulus that was designed for entertainment.
-
-% PPA: intro
-In an earlier study, \cite{bartels2004mapping} manually annotated the content of
-individual movie frames (color, faces, language, and human bodies) and found
-that the functional specialization of brain areas is preserved during movie
-watching.
-%
-In contrast, we aimed to exploit a cinematographic confound in the structure of
-movies, where
-% establishing shots vs. e.g. over-the-shoulder shots
-film directors tend to establish the spatial layout of locations in earlier
-shots and later focus more on detailed depictions of people and objects
-\citep{brown2012cinematography, katz1991film, mascelli1998five}.
+employed a naturalistic movie stimuli that were designed for entertainment.
+
+%#3
 % hypo
-We hypothesized that due to the complex nature of the naturalistic stimulus,
+We hypothesized that due to the complex nature of a naturalistic stimulus,
 unrelated factors would be balanced across a large number of events, and make
@@
 % we need a detailed description -> annotation
-The current model-driven approach required a detailed annotation of the
+This model-driven approach required a detailed annotation of the
 occurence of relevant stimulus features.
@@
 
+%#4
+We attempted to find hemodynamic responses to spatial information embedded in
+the naturalistic stimuli, capitalizing on conceptually similar, but perceptually
+different stimulation events.
 % group AV
-On a group-average level, results for the audio-visual movie show significantly
+On a group-average level, results for the movie show significantly
 increased hemodynamic activity spatially overlapping with a conventionally
@@
 % individual level
-Moroever, the group averages are representative for the majority of individual
-results, where, for example, the audio-description stimulus yields bilateral
-clusters in the anterior PPA of nine participants and a unilateral cluster in
-one participant.
+Bilateral clusters in 9 of 14
+participants (of which \texttt{sub-04} shows only a right-lateralized PPA ROI
+in the block-design localizer results), and a unilateral
+significant cluster in one participant, indicate that the group average results
+are representative for the majority of individual participants.
 % meaning: generalization to naturalistic stimuli
@@
 perception of static pictures generalizes to the perception of spatial
-information embedded in a movie or a purely auditory narrative.
-% narrative as substitute
-The presented evidence on the in-principle suitability of a purely auditory
-paradigm for localizing the PPA may offer a path to the development of
-diagnostic procedures more suitable for individuals with visual impairments or
-conditions like nystagmus.
-% meaning: aPPA vs. pPPA
-Our results provide further evidence that the PPA can be divided into functional
-subregions \citep{aminoff2007parahippocampal, aminoff2015associative,
-baldassano2013differential, baldassano2016two,
-baumann2016functional}.\todo{claim hängt hier etwas in der Luft; wird später
-ausführlicher diskutiert}
-
-% results
-Group results of the movie stimulus' primary contrast yielded a large cluster
-that spans the group overlap of individual PPA ROIs from anterior to posterior.
-% confound of higher perception
-The cluster's extension into more posterior, earlier visual areas could be
-attributed to the temporal averaging across events that did not control for
-confounding visual features.
-% solution
-Future studies that aim to use a movie to localize visual areas in individual
-participants should extensively annotate the content of frames \citep[e.g.,
-using the open-source solution ``Pliers'' for feature extraction from a visual
-naturalistic stimulus;][]{mcnamara2017developing}.
-
-% MIH: second time this notion is coming up in the discussion
-%% we took advantage of cinematography
-%We here took advantage of an idiosyncrasy of movie directing to shift from
-%depicting the spatial layout to to later depicting persons and objects.
-%% know your stimulus
-%Given that this shift is common in movies, investigators should be aware that
-%cinematographic tendencies are part of movie's confound structure that might,
-%depending on the research question, influence the results.
-%% conclusion
-%In summary, results from the visual localizer paradigm using blocks of pictures
-%generalize to an ad hoc approach to operationalize the perception of spatial
-%information at the moment of cuts in an audio-visual movie.
-
+information embedded in a movie or a purely auditory narrative, even though the
+results may partially deviate from \cite{sengupta2016extension}, due to
+the uniform cluster forming threshold employed in this study versus their
+adaptive procedure (bilateral clusters in 12 of 14 participants and a unilateral
+right cluster in two participants (\texttt{sub-04}, \texttt{sub-20}).
+
+%#11 question
+The fact that clusters from the auditory stimulus are spatially restricted to
+the anterior part of clusters from both visual paradigms raises the question if
+the revealed correlation patterns can be attributed to different features
+inherent in the visual stimuli compared to a purely auditory stimulus.
+% visual scenes: probably submodules
+In the domain of visual scene perception, previous studies provide evidence
+that the PPA can be divided into functionally subregions that might process
+different stimulus features.
+% posterior: functionality
+The posterior PPA (pPPA) is functionally more responsive than the anterior PPA
+(aPPA) to low-level features of scenes or (abstract) objects
+\citep{baldassano2013differential, nasr2014thinking,
+rajimehr2011parahippocampal}.
+% anterior cIPL is defined using the Eickhoff–Zilles PGp probabilistic
+% cytoarchitectonic map
+In contrast, the aPPA responds more to high-level features of scenes (e.g.
+real-word size \citep{park2015parametric}; a scene's abstract category
+\citep{marchette2015outside, watson2016patterns}) and objects (e.g. spatial
+contextual associations \citep{aminoff2007parahippocampal, aminoff2013role})
+than the pPPA.
+% connectivity
+Moreover, pPPA and aPPA show differences in connectivity profiles.
+% posterior
+The pPPA exhibits more coactivation with the occipital visual cortex than the
+aPPA \citep{baldassano2013differential, baldassano2016two}.
+% including lateral occipital cortex (LOC) and transverse occipital sulcus
+% (TOS) anterior
+Activity in the aPPA, on the other hand, is found to be correlated with
+components of the default mode network, including caudal inferior parietal lobe
+(cIPL), the restrosplenial complex (RSC), medial PFC and the lateral surface of
+the anterior temporal lobe \citep{baldassano2013differential,
+baldassano2016two}.
+% conclusion: subregions
+\cite{baldassano2013differential} proposes PPA function to be the formation of
+a complete scene representation, based on the processing of different aspects
+of a visual scene in its subregions.
+% Their distinct connectivity properties do suggest that each may be involved
+% in specific aspects of visual and cognitive processing involved in the
+% overarching goal of scene understanding \citep{baldassano2013differential}.
+% The fact that anterior PPA had a lower sensitivity to our abstract object
+% stimuli does not necessarily imply that this region does not use object
+% information \citep{baldassano2013differential}. Previous work has shown that
+% PPA responds to objects that have spatial associations [Aminoff et al. 2007],
+% are space-defining [Mullally and Maguire 2011], and are
+% navigationally-relevant [Janzen and Van Turennout 2004]. These types of
+% responses require spatial memory and cannot be based purely on visual
+% features like object shape. \citep{baldassano2013differential}.  pPPA
+Similarly, our results suggest that the pPPA is more concerned with visual
+aspects immanent in pictures or movie shots of landscapes.
+% aPPA
+The aPPA might be more concerned with non-visual aspects of spatial information
+(e.g. spatial contextual information \citep{aminoff2007parahippocampal}) as
+immanent in both visual and verbal stimuli.
+
+%#6
 % hypothesis
@@
 information embedded in the audio-description would correlate with
-increased hemodynamic activity in the PPA.
+increased hemodynamic activity in the PPA. However, methods and results presented
+here differ from this previous study in key aspects.
 % diff to Aziz (2008)
@@
 % we: model & whole brain
-In the current study, we modeled events from onset to offset of single words and performed a
+Here, we modeled events from onset to offset of single words and performed a
 voxelwise whole-brain analysis.
@@
 % concluding statement
-Contrary to \cite{aziz2008modulation}, our group results suggest that auditory
+Contrary to \cite{aziz2008modulation}, our results suggest that auditory
 spatial information compared to non-spatial information correlates with
@@
 
+%#7
 % previous studies: no task
@@
 
-% AD shortcomings
-
+% shortcomings
+%#2
+Our approach to stimulus annotation and event selection
+differs from previous reports in the literature.
+% PPA: intro
+In an earlier study, \cite{bartels2004mapping} manually annotated the content of
+individual movie frames (color, faces, language, and human bodies) and found
+that the functional specialization of brain areas is preserved during movie
+watching.
+%
+In contrast, we aimed to exploit a cinematographic confound in the structure of
+movies, where
+% establishing shots vs. e.g. over-the-shoulder shots
+film directors tend to establish the spatial layout of locations in earlier
+shots and later focus more on detailed depictions of people and objects
+\citep{brown2012cinematography, katz1991film, mascelli1998five}.
+%#8
 % optimal stimulus type in vision
-In the visual domain, pictures of landscapes and not pictures of landmarks or
+Moreover, in the visual domain, pictures of landscapes and not pictures of landmarks or
 buildings are considered to be the ``optimal'' stimulus type
@@
 more concrete parts of a scene (e.g.``[a] beacon'', [a] ``farmhouse'').
-
-% AD annotation > AV annotation
-Given that the annotation of nouns offered a more precise way to operationalize
-the perception of spatial information than the annotation of cuts and locations,
-we also hypothesized that analyzing the data from the audio-description could
-localize the PPA in individual persons.
-% results of dedicated localizer
-The visual localizer \citep{sengupta2016extension} revealed bilateral ROIs in 12
-of 14 participants and a unilateral right ROI in two participants (sub-04, sub-20).
-%
-Whereas \cite{sengupta2016extension} chose the subjectively ``best fitting''
-$t$-threshold in a $t$-map from one of three contrasts by visual judgment, we used
-the same contrast and threshold ($Z$>3.4, $p$<.05 cluster-corrected) for all
-participants.
-% in the current study
-The audio-description yielded significant bilateral clusters in 9 of 14 participants
-(of which sub-04 shows only a right-lateralized PPA ROI), and a unilateral
-significant cluster in one participant.
-% similar: anterior part
-Similarly to the group average results, results on an individual level also
-revealed that clusters are spatially restricted to the anterior part of
-individual PPAs.
-% conclusion
-Thus, the cluster location and size found on the group level is not just a
-by-product of the averaging process but a reliable pattern across results of
-individual study participants.
-% concluding statement
-Further, our exploratory analysis suggests that a naturalistic auditory stimulus
-can, in principle, be applied to localize (the anterior part) of a higher-level
-visual area in the majority of participants.
-% one threshold (and contrast) to rule them all
-Nevertheless, further studies that aim for individual diagnostics / ROI
-localization should inspect more than one contrast, and use an individual
-threshold or a sphere around the local maximum \citep{poldrack2007region} in the
-parahippocampal region.
-
-% question
-The fact that clusters from the auditory stimulus are spatially restricted to
-the anterior part of clusters from the visual paradigms raises the question if
-the revealed correlation patterns can be attributed to different features
-inherent in the visual stimuli compared to the purely auditory stimulus.
-% visual scenes: probably submodules
-In the domain of visual scene perception, previous studies provide evidence that
-the PPA can be divided into functionally subregions that might process different
-stimulus features.
-% posterior: functionality
-The posterior PPA (pPPA) is functionally more responsive than the anterior PPA
-(aPPA) to low-level features of scenes or (abstract) objects
-\citep{baldassano2013differential, nasr2014thinking,
-rajimehr2011parahippocampal}.
-% anterior cIPL is defined using the Eickhoff–Zilles PGp probabilistic
-% cytoarchitectonic map
-Contrary, the aPPA is functionally more responsive than the pPPA to high-level
-features of scenes (e.g. real-word size \citep{park2015parametric}; a scene's
-abstract category \citep{marchette2015outside, watson2016patterns}) and
-objects (e.g. spatial contextual associations \citep{aminoff2007parahippocampal, aminoff2013role}).
-% connectivity
-Moreover, pPPA and aPPA show differences in connectivity profiles.
-% posterior
-The pPPA is more strongly functionally connected to the occipital visual cortex
-than the aPPA \citep{baldassano2013differential, baldassano2016two}.
-% including lateral occipital cortex (LOC) and transverse occipital sulcus (TOS)
-% anterior
-Contrary, the aPPA is more strongly functionally connected to portions of the
-default mode network, including caudal inferior parietal lobe (cIPL), the
-restrosplenial complex (RSC), medial PFC and the lateral surface of the anterior
-temporal lobe \citep{baldassano2013differential, baldassano2016two}.
-% conclusion: subregions
-According to a hypothesis by \citep{baldassano2013differential} the PPA consists
-of subregions that process different aspects of a visual scene and cooperate to
-build a complete scene representation.
-% Their distinct connectivity properties do suggest that each may be involved in
-% specific aspects of visual and cognitive processing involved in the
-% overarching goal of scene understanding \citep{baldassano2013differential}.
-% The fact that anterior PPA had a lower sensitivity to our abstract object
-% stimuli does not necessarily imply that this region does not use object
-% information \citep{baldassano2013differential}. Previous work has shown that
-% PPA responds to objects that have spatial associations [Aminoff et al. 2007],
-% are space-defining [Mullally and Maguire 2011], and are
-% navigationally-relevant [Janzen and Van Turennout 2004]. These types of
-% responses require spatial memory and cannot be based purely on visual features
-% like object shape. \citep{baldassano2013differential}.  pPPA
-Similarly, our results suggest that the pPPA is more concerned with visual
-aspects immanent in pictures or movie shots of landscapes.
-% aPPA
-The aPPA might be more concerned with non-visual aspects of spatial information
-(e.g. spatial contextual information \citep{aminoff2007parahippocampal}) as immanent in both visual and
-verbal stimuli.
-
+%#5
+% results
+Lastly, the group results of the movie stimulus' primary contrast yielded a large cluster
+that spans the group overlap of individual PPA ROIs from anterior to posterior.
+% confound of higher perception
+The cluster's extent into more posterior, earlier visual areas could be
+an indication that the temporal averaging across events suffered from
+insufficient controlling for confounding visual features.
+% solution
+Future studies that aim to use a movie to localize visual areas in individual
+participants should extensively annotate the content of frames \citep[e.g.,
+using the open-source solution ``Pliers'' for feature extraction from a visual
+naturalistic stimulus;][]{mcnamara2017developing}.
+
+% MIH: second time this notion is coming up in the discussion
+%% we took advantage of cinematography
+%We here took advantage of an idiosyncrasy of movie directing to shift from
+%depicting the spatial layout to to later depicting persons and objects.
+%% know your stimulus
+%Given that this shift is common in movies, investigators should be aware that
+%cinematographic tendencies are part of movie's confound structure that might,
+%depending on the research question, influence the results.
+%% conclusion
+%In summary, results from the visual localizer paradigm using blocks of pictures
+%generalize to an ad hoc approach to operationalize the perception of spatial
+%information at the moment of cuts in an audio-visual movie.
+
+%#12
 % RSC + LOC
@@
 
-% natural stimulation
+%#13 natural stimulation
 In summary, natural stimuli like movies \citep{eickhoff2020towards,
@@
 \citep{hamilton2018revolution, honey2012not, lerner2011topographic,
-silbert2014coupled, wilson2008beyond} offer an easy to implement, continuous,
-complex, immersive, task-free paradigm that more closely resembles our natural
-dynamic environment than traditional experimental paradigms.
+silbert2014coupled, wilson2008beyond} can be used as a continuous, complex,
+immersive, task-free paradigm that more closely resembles our natural dynamic
+environment than traditional experimental paradigms.
 % method
 We took advantage of three fMRI datasets and two stimulus annotations that are
-part of the studyforrest dataset
+part of the open-data resource
 \href{http://www.studyforrest.org}{studyforrest.org} to operationalize the
-perception of spatial information embedded an audio-visual movie and an auditory
-narrative, and compare current results to results gained from a traditional
-visual localizer.
+perception of spatial information embedded an audio-visual movie and an
+auditory narrative, and compare current results to a previous report of a
+conventional, block-design localizer.
 % results
-In general, results add evidence that a model-driven GLM analysis based on
-annotations can be run on data from naturalistic stimuli to localize concise
+This report offers evidence that a model-driven GLM analysis based on
+annotations can be applied to naturalistic paradigm to localize concise
 functional areas and networks correlating with specific perceptual processes.
@@
 Further, our results provide evidence that the PPA can be divided into
-functional subregions that coactivate during the perception of visual
-scenes.
+functional subregions that coactivate during the perception of visual scenes.
 % interpretation
-Lastly, a naturally engaging auditory narrative might - in principle -
+Finally, the presented evidence on the in-principle suitability of a naturally
+engaging, purely auditory paradigm for localizing the PPA may offer a path to
+the development of diagnostic procedures more suitable for individuals with
+visual impairments or conditions like nystagmus.
+
+the present results suggest that a naturally engaging auditory narrative
+could, in principle,
 substitute a visual paradigm to localize the anterior part of the PPA in

### 2021-02-19 paper/main.tex
Cleanup

@@
 
-the present results suggest that a naturally engaging auditory narrative
-could, in principle,
-substitute a visual paradigm to localize the anterior part of the PPA in
-individuals with conditions that make them unable to follow task instructions
-during brain scanning.
-
 \subsection*{Data and code availability}
@@
 accessible as Datalad (RRID:SCR\_003931) datasets.
-
-% subject space -> NeuroVault
-Results of the analyses that were performed in participant-space can be found in the
-accompanying dataset ($Z$>2.3, $p$<.05 cluster-corrected).
 

### 2021-02-19 paper/main.tex
More cleanup

@@
 
-\noindent General
-\begin{itemize}
-    \item van den Hurk (2017): uses sounds (1.8sec); one-back-task; no
-        significant results; but ``sensitivity maps'' and cross-modal and
-        cross-subject classification; mentions in a half sentence ``the auditory
-        trials might activate only a subset of voxels that contain categorical
-        information, whereas the visual trials activate the majority of VTC
-        voxels''.
-\end{itemize}
-
-\noindent Method
-
-\begin{itemize}
-    \item Fig regressor correlations: maybe write out in full the name of
-        regressors (instead of pointing to the table)
-    \item different frame counts of segments AV vs. AD
-\end{itemize}
-
-\noindent Results
-
-\begin{itemize}
-    \item tables: I (initially) rounded p-values to <.00001
-\end{itemize}
-
-\noindent Discussion
-\begin{itemize}
-    \item "Lokalisation der PPA" vs. "Antwortverhalten einer vorab definierten
-        PPA". Machst wohl das erste, beschreibst es aber als das zweite
-\end{itemize}
-
 \noindent Supplemental Material
@@
 \begin{itemize}
-    \item draft for Data Citation is done
     \item draft for Code and Data Availability is done (other analysis paper do
@@
 constructed from LEGO blocks \citep{wolbers2011modality} and scene-related
-sounds \citep{van2017development}.\todo{reading the paper: activation is
-non-significant, lol}
+sounds \citep{van2017development}.
 % van der Hurk: 64 sounds x 1.8 seconds; 20 sighted, 14 congenitally blind

### 2021-02-19 paper/main.tex
S prefix for suppl. figures
Light pass over suppl.

@@
 
+\setcounter{figure}{0}
+\makeatletter
+\renewcommand{\thefigure}{S\@arabic\c@figure}
+\makeatother
+
 \section{Supplementary Materials}
@@
 % NeuroVault
-Unthresholded z -maps of all contrasts on a group level as well as individual
+Unthresholded $Z$-maps of all contrasts on a group level as well as individual
 results of the primary $t$-contrasts co-registered to the group-template (MNI152
 space) can found at NeuroVault
-\href{https://neurovault.org/collections/KADGMGVZ/}{NeuroVault}.
+\href{https://neurovault.org/collections/KADGMGVZ/}{\url{neurovault.org/collections/KADGMGVZNeuroVault}}.
 
@@
 % AD: results
-In results of the audio-description stimulus, all contrasts except contrast 7
+For the audio-description stimulus, all contrasts except contrast 7
 (\texttt{se\_new}, \texttt{se\_old} > non-spatial categories) and contrast 8
@@
 %
-Contrast 7 shows clusters in the left frontal pole and left frontal operculum
-[border to triangularis], left insular.
+Contrast 7 shows clusters in the left frontal pole and left frontal operculum, left insular.
 %
@@
 % ``confounding'' clusters
-Despite performing a whole brain analysis, we do not find [many] clusters
-in a single contrasts or systematically across contrasts that are scattered
-across the brain and hamper the interpretation of results.
+Our whole brain analysis did not identify systematically occuring clusters pointing
+to confounding cognitive processes like attention or eye movements
 % AV: null results regarding attention and eye movements
-For example in the movie results, we do not find significant clusters that could be
-attributed to cognitive processes like attention or eye movements.
 % AD: auditory cortices
-Nevertheless, contrasts of the audio-description stimulus that compare (among others) verbal
+Nevertheless, for the audio-description stimulus contrasts that compare verbal
 hints of the change of a setting (\texttt{se\_new} or \texttt{se\_old}) to all
-non-spatial categories (cf. contrasts 2, 3, 6, 7) show significant clusters in
+non-spatial categories (cf. contrasts 2, 3, 6, 7) show clusters in
 (primary and secondary) auditory cortices.
@@
 This suggests that variance correlating with lower level auditory processes was
-not averaged out across trials and nuisance regressors did not capture enough
-variance.
+not averaged out across events and the employed nuisance regressors did not
+capture this variance appropriately.
 % possible reason
-Significant clusters in auditory cortices could be correlating with a possible
-change of the soundscape when the narrator of the audio-description (or a cut in
-the movie) switches to a another setting.
+Activity in such clusters could be correlated with a possible
+change of the soundscape when the narrator of the audio-description,
+corresponding to a cut in the movie, switches udio-description stimulusto a another setting.
 % concluding statement
 Thus, investigators that use model-driven methods to investigate brain functions
-using naturalistic stimuli should (extensively) annotate the stimulus material
+using naturalistic stimuli should extensively annotate the stimulus material
 and test for correlations among variables.
@@
 
-\todo[inline]{discuss results in light of ``negative control'' (-> definition \&
-purpose)}
+\todo[inline]{This section feels incomplete. Some explanation (attempts) are
+missing.  Sometimes it is simply unclear which data were analyzed with which
+designs. Maybe subheadings would help?}
 
@@
 % intro
-For the purpose of negative control, we implemented five contrasts for every
-stimulus.
+We implemented five contrasts for every stimulus.
 % AV: no_cut > x
@@
 % AV using nouns
-The contrast that used the narrator's nouns but in the movie stimulus
+The contrast that used the narrator's nouns that did not actually exist in the movie stimulus
 (\texttt{se\_new} > \texttt{se\_old}) yielded a significant cluster in the right
 PPA and bilateral clusters in the superior lateral occipital cortices (the right
-hemispheric cluster extending into the superior parietal cortex).
+hemispheric cluster extending into the superior parietal cortex).\todo{explanation?}
+
 % AD stimulus
-In the analysis of the audio-description data, we created control contrasts based on events of
-the annotated movie cuts (Tab.~\ref{tab:ao-contrasts})
+For the analysis of the audio-description, we created control contrasts based on events of
+the annotated movie cuts (Tab.~\ref{tab:ao-contrasts}), which although invisible
+were nevertheless frequently perceivable due to changes in the soundscape.
 % contrast 9
-Contrast 9 (vse\_new > pe\_old) revealed one significant cluster in the left
+Contrast 9 (\texttt{vse\_new > pe\_old}) revealed one significant cluster in the left
 inferior prefrontal cortex (pars triangularis) and right ventral
@@
 Contrast 12 (\texttt{vse\_new} > \texttt{vse\_old}, \texttt{vpe\_old}) revealed
-one cluster in the right posterior hippocampus.\todo{odd imo}
-
-\todo[inline]{why did I build contrasts of the no\_cut condition compared
-to the movie cuts categories????}
+one cluster in the right posterior hippocampus.\todo{explanation?}
 

### 2021-02-19 paper/main.tex
some corrections of discussions 1st half

@@
 
-\pagebreak [4]
-
 \section{Discussion}
@@
 
-%#1
-% previous studies
+%#1 previous studies
 Several studies have reported increased hemodynamic activity in the PPA
@@
 specifically and predominantly evoke the processing of spatial information, we
-employed a naturalistic movie stimuli that were designed for entertainment.
+employed a naturalistic stimuli, a movie and its audio-description, that were
+designed for entertainment.
 
@@
 % hypo
-We hypothesized that due to the complex nature of a naturalistic stimulus,
+We hypothesized that due to the complex nature of the stimuli,
 unrelated factors would be balanced across a large number of events, and make
@@
 % event counts ftw
-The annotation of both types of naturalistic stimuli, a movie and its
-audio-description, revealed the respective number of incidentally occurring
+The annotation of both stimuli revealed the respective number of incidentally occurring
 events to be similar to those of a conventional experimental paradigm used to
@@
 %#4
-We attempted to find hemodynamic responses to spatial information embedded in
-the naturalistic stimuli, capitalizing on conceptually similar, but perceptually
-different stimulation events.
+We modeled hemodynamic responses correlating with spatial information embedded
+in the naturalistic stimuli, capitalizing on conceptually similar, but
+perceptually different stimulation events.
 % group AV
@@
 perception of static pictures generalizes to the perception of spatial
-information embedded in a movie or a purely auditory narrative, even though the
-results may partially deviate from \cite{sengupta2016extension}, due to
+information embedded in a movie or a purely auditory narrative.
+%
+Current results may partially deviate from \cite{sengupta2016extension}, due to
 the uniform cluster forming threshold employed in this study versus their
@@
 right cluster in two participants (\texttt{sub-04}, \texttt{sub-20}).
-
+\todo[inline]{es wird jetzt lediglich in den results erwähnt, dass Sengupta
+einen von dreien benutzt hat}
 %#11 question
@@
 % conclusion: subregions
-\cite{baldassano2013differential} proposes PPA function to be the formation of
-a complete scene representation, based on the processing of different aspects
-of a visual scene in its subregions.
+\cite{baldassano2013differential} proposes that the PPA creates a complete
+scene representation, based on different aspects of a visual scene processed in
+subregions of the PPA.
 % Their distinct connectivity properties do suggest that each may be involved

### 2021-02-19 paper/main.tex
some corrections of discussions 2nd half

@@
 
-%#6
-% hypothesis
-Based on the report by \cite{aziz2008modulation}, we hypothesized that semantic spatial
-information embedded in the audio-description would correlate with
-increased hemodynamic activity in the PPA. However, methods and results presented
-here differ from this previous study in key aspects.
+%#6 hypothesis
+Based on the report by \cite{aziz2008modulation}, we hypothesized that semantic
+spatial information embedded in the audio-description would correlate with
+increased hemodynamic activity in the PPA.
+%
+Methods and results presented here differ from this previous study in key
+aspects.
 % diff to Aziz (2008)
@@
 % but still: we are different
-This naturalistic paradigm nevertheless differs from \cite{epstein1998ppa},
+Nevertheless, the naturalistic paradigm differs from \cite{epstein1998ppa},
 because the relevant stimulus features were embedded in a continuous stream of complex
 auditory (and visual) information which makes it unlikely that participants
-speculated on the purpose of the investigation or perform undesired and unknown
-evaluation or categorization of isolated stimuli.
+speculated on the purpose of the investigation, or performed undesired and unknown evaluation or categorization of isolated stimuli.
 % concluding statement: kinda automatic process
@@
 \citep{brown2012cinematography, katz1991film, mascelli1998five}.
+% results
+The group results of the movie stimulus' primary contrast yielded a large cluster
+that spans the group overlap of individual PPA ROIs from anterior to posterior.
+% confound of higher perception
+The cluster's extent into more posterior, earlier visual areas could be
+an indication that the temporal averaging across events suffered from
+insufficient controlling for confounding visual features.
+% solution
+Future studies that aim to use a movie to localize visual areas in individual
+participants should extensively annotate the content of frames \citep[e.g.,
+using the open-source solution ``Pliers'' for feature extraction from a visual
+naturalistic stimulus;][]{mcnamara2017developing}.
+
 %#8
 % optimal stimulus type in vision
-Moreover, in the visual domain, pictures of landscapes and not pictures of landmarks or
+In the visual domain, pictures of landscapes and not pictures of landmarks or
 buildings are considered to be the ``optimal'' stimulus type
@@
 %#5
-% results
-Lastly, the group results of the movie stimulus' primary contrast yielded a large cluster
-that spans the group overlap of individual PPA ROIs from anterior to posterior.
-% confound of higher perception
-The cluster's extent into more posterior, earlier visual areas could be
-an indication that the temporal averaging across events suffered from
-insufficient controlling for confounding visual features.
-% solution
-Future studies that aim to use a movie to localize visual areas in individual
-participants should extensively annotate the content of frames \citep[e.g.,
-using the open-source solution ``Pliers'' for feature extraction from a visual
-naturalistic stimulus;][]{mcnamara2017developing}.
 
@@
 in studies investigating visual spatial perception or navigation (see
-\citep{chrastil2018heterogeneity, bettencourt2013role} for reviews).
+
 % not random shit
@@
 % results
-This report offers evidence that a model-driven GLM analysis based on
+The current study offers evidence that a model-driven GLM analysis based on
 annotations can be applied to naturalistic paradigm to localize concise
@@
 % interpretation: aPPA vs. pPPA
-Further, our results provide evidence that the PPA can be divided into
+Further, our results provide further evidence that the PPA can be divided into
 functional subregions that coactivate during the perception of visual scenes.

### 2021-02-19 paper/main.tex
turn Supplementals into a (temporary) mess

@@
 
-\subsection{Congruencies across contrasts}
+\subsection{Additional contrasts: PPA, RSC, and LOC (AV \& AV)}
 
@@
 In order to test the robustness of our approach, we created overall five
-$t$-contrasts for the movie stimulus (Tab.~\ref{tab:av-contrasts}), and
-overall eight $t$-contrast for the audio-description stimulus (Tab.~\ref{tab:av-contrasts})
-by varying the contrasted categories (and thus the
-amount of available data), and how well the annotated events within categories
-on average matched a stimulus type that we assumed to correlate with spatial
-perception.
+$t$-contrasts for the movie stimulus (Tab.~\ref{tab:av-contrasts}), and overall
+eight $t$-contrast for the audio-description stimulus
+(Tab.~\ref{tab:av-contrasts}).
+% how
+Contrasts differ in contrasted categeories based on ``how well'' averaged
+events within categories were considered to represent spatial and non-spatial
+information, and the number of events in the stimulus.
 % NeuroVault
@@
 % AV: RSC & LOC
-Reliably across contrasts of the movie stimulus, we find bilaterally
-significant clusters also in the ventral precuneal cortex and posterior
+Also reliably across contrasts of the movie stimulus, we find bilaterally
+significant clusters in the ventral precuneal cortex and posterior
 cingulate gyrus (i.e. restrosplenial complex; contrasts 1, 4, 5), and lateral
@@
 (\texttt{se\_new} > non-spatial categories) yielded significant bilateral
-clusters in anterior regions of the group PPA overlap (Fig.~\ref{fig:stability-slices}).
+clusters in anterior regions of the group PPA overlap
+(Fig.~\ref{fig:stability-slices}).
 % AD: RSC & LOC
-Reliably across contrast of the audio-description stimulus, we find bilaterally significant
-clusters also in the ventral precuneus (all except contrasts 8), lateral
-occipital cortex (bilateral in contrasts 1 to 4; unilateral in contrasts 6 and
-7), and superior temporal cortices (bilateral in contrasts 3, 6, 7; unilateral
-right in contrast 2).
-% non-systematic
-Lastly, some contrasts of the audio-description stimulus yielded significant clusters in
-regions that were not statistically significant in three or more contrasts.
-%
-Contrast 2 yielded clusters in the anterior cingulate gyrus (bilateral), right
-frontal pole, right frontal medial cortex, and right putamen.
-%
-Contrast 3 shows clusters in the anterior cingulate gyrus (bilateral), left
-frontal pole, and left insular.
-%
-Contrast 7 shows clusters in the left frontal pole and left frontal operculum, left insular.
-%
-Contrast 6 shows one additional cluster in the right medial frontal cortex.
+We find bilaterally significant clusters also in the ventral precuneus (all
+except contrasts 8), lateral occipital cortex (bilateral in contrasts 1 to 4;
+unilateral in contrasts 6 and 7).
+% "Discussion" of PPA, RSC, and LOC
+The results across the contrasts of the movie and audio-description stimulus
+indicate that our findings regarding the PPA but also RSC and LOC are robust and
+do not depend on the design of one specific contrasts.
+% but
+Nevertheless, results are sensitive to the contrasted categories and the amount
+of available data.
+% example
+For example, contrast 8 of the audio-description stimulus (\texttt{se\_new} > \texttt{se\_old})
+that used the most heterogeneous categories comprising the least amount of
+events yielded neither a significant cluster in the right-hemispheric nor
+left-hemispheric PPA.
+% concluding statement
+Hence, investigators that use model-driven analyses have to consider how many
+events a naturalistic stimulus may provide and how homogeneous the events to be
+averaged might be.
 
@@
 
-% Discussion
-The results across the contrasts of the movie and audio-description stimulus indicate that our
-findings regarding the PPA but also RSC and LOC are robust and do not depend on
-the design of one specific contrasts.
-% but
-Nevertheless, results are sensitive to the contrasted categories and the amount
-of available data.
-% example
-For example, contrast 8 of the audio-description stimulus (\texttt{se\_new} > \texttt{se\_old})
-that used the most heterogeneous categories comprising the least amount of
-events yielded neither a significant cluster in the right-hemispheric nor
-left-hemispheric PPA.
-% concluding statement
-Hence, investigators that use model-driven analyses have to consider how many
-events a naturalistic stimulus may provide and how homogeneous the events to be
-averaged might be.
+\subsection{Additional contrasts: let's talk about left overs}
+
+\todo[inline]{look at the events within categories \& give some counts}
+
+\todo[inline]{compare with Michaels make over of text regarding confound
+structure
+
+\todo[inline]{main message here again: you need events! (and be aware of biases)}
+
+%
+Three contrasts yielded bilaterally significant clusters in superior temporal
+cortices (contrasts 3, 6, 7), one contrast a unilateral right cluster (contrast
+2).
+%
+\todo{following is (probably too) exhaustive}
+%
+Lastly, some contrasts of the audio-description stimulus yielded significant
+clusters in regions that were not statistically significant in three or more
+contrasts.
+%
+Contrast 2 yielded clusters in the anterior cingulate gyrus (bilateral), right
+frontal pole, right frontal medial cortex, and right putamen.
+%
+Contrast 3 shows clusters in the anterior cingulate gyrus (bilateral), left
+frontal pole, and left insular.
+%
+Contrast 7 shows clusters in the left frontal pole and left frontal operculum,
+left insular.
+%
+Contrast 6 shows one additional cluster in the right medial frontal cortex.
+% concludion statement
+Conclusion: This can be attributed to the uncontrolled nature of averaged events.
 

### 2021-02-21 paper/main.tex
suppl.: additional contrasts

@@
 
-\subsection{Additional contrasts: PPA, RSC, and LOC (AV \& AV)}
+\subsection{additional contrasts}
+
+\todo{print contrasts; count per category? -> pattern "average of events" and
+counts vs. significant clusters?}
+
+\subsubsection{PPA, RSC, and LOC (AV \& AV)}
 
 \todo[inline]{SE: use different colormap for overlap of contrasts' clusters}
-\todo[inline]{SE: wie unterscheiden sich die Kontraste?}
-\todo[inline]{Wo sind welche Kontraste (z.B. im Ergebnis) von anderen abgewichen?}
+lche Kontraste (z.B. im Ergebnis) von anderen abgewichen?}
 
@@
 % how
-Contrasts differ in contrasted categeories based on ``how well'' averaged
-events within categories were considered to represent spatial and non-spatial
+Contrasts differ in contrasted categeories based on ``how well'' averaged events
+within categories were considered to represent spatial and non-spatial
 information, and the number of events in the stimulus.
 % NeuroVault
-Unthresholded $Z$-maps of all contrasts on a group level as well as individual
-results of the primary $t$-contrasts co-registered to the group-template (MNI152
-space) can found at NeuroVault
+Unthresholded $Z$-maps of all contrasts on a group level co-registered to the
+group-template (MNI152 space) can found at NeuroVault
 \href{https://neurovault.org/collections/KADGMGVZ/}{\url{neurovault.org/collections/KADGMGVZNeuroVault}}.
@@
 % temporal occipital fusiform cortex
-All five movie contrasts yielded significant bilateral clusters that
-overlap with the PPA group overlap (Fig.~\ref{fig:stability-slices}).
+Reliably across all five movie contrasts, we find bilaterally significant
+clusters that overlap with the PPA group overlap
+(Fig.~\ref{fig:stability-slices}).
 % AV: RSC & LOC
-Also reliably across contrasts of the movie stimulus, we find bilaterally
-significant clusters in the ventral precuneal cortex and posterior
-cingulate gyrus (i.e. restrosplenial complex; contrasts 1, 4, 5), and lateral
-occipital cortex (contrasts 1, 2, 4, 5).
+Results of the movie also yielded significant clusters in the ventral precuneal
+cortex and posterior cingulate gyrus (i.e. restrosplenial complex; contrasts 1,
+4, 5), and lateral occipital cortex (contrasts 1, 2, 4, 5).
 
@@
 % AD: results
-For the audio-description stimulus, all contrasts except contrast 7
-(\texttt{se\_new}, \texttt{se\_old} > non-spatial categories) and contrast 8
-(\texttt{se\_new} > non-spatial categories) yielded significant bilateral
-clusters in anterior regions of the group PPA overlap
+In results from the analysis of the audio-description, all contrasts except
+contrast 7 (\texttt{se\_new}, \texttt{se\_old} > non-spatial categories) and
+contrast 8 (\texttt{se\_new} > non-spatial categories) yielded significant
+bilateral clusters in anterior regions of the group PPA overlap
 (Fig.~\ref{fig:stability-slices}).
 % AD: RSC & LOC
-We find bilaterally significant clusters also in the ventral precuneus (all
-except contrasts 8), lateral occipital cortex (bilateral in contrasts 1 to 4;
-unilateral in contrasts 6 and 7).
-% "Discussion" of PPA, RSC, and LOC
-The results across the contrasts of the movie and audio-description stimulus
-indicate that our findings regarding the PPA but also RSC and LOC are robust and
-do not depend on the design of one specific contrasts.
+Results from the analysis of the audio-description also yielded bilaterally
+significant clusters in the ventral precuneus (all contrasts except contrasts 8)
+and lateral occipital cortex (bilateral in contrasts 1 to 4; unilateral in
+contrasts 6 and 7).
+% concluding stament regarding PPA, RSC, and LOC
+The results across the contrasts of the movie and audio-description indicate
+that our findings regarding the PPA but also RSC and LOC are robust and do not
+depend on the design of one specific contrasts.
+%
+\todo[inline]{print contrasts; counts per contrasted categories? "fit of
+averaged events"?}
 % but
@@
 % example
-For example, contrast 8 of the audio-description stimulus (\texttt{se\_new} > \texttt{se\_old})
-that used the most heterogeneous categories comprising the least amount of
-events yielded neither a significant cluster in the right-hemispheric nor
-left-hemispheric PPA.
+For example, contrast 8 of the audio-description stimulus (\texttt{se\_new} >
+\texttt{se\_old}) that used the most heterogeneous categories comprising the
+least amount of events yielded neither a significant cluster in the
+right-hemispheric nor left-hemispheric PPA.
 % concluding statement
@@
 averaged might be.
+
+\subsubsection{auditory cortices}
+
+Further, some contrasts yielded bilaterally significant clusters in superior
+temporal cortices (contrasts 3, 6, 7) and one contrast a unilateral right
+cluster (contrast 2).
+% AD: auditory cortices
+Thus, increased hemodynamic activity in the superior temporal cortex is apparent
+in that compare verbal hints of the change of a setting (\texttt{se\_new} or
+\texttt{se\_old}) to all non-spatial categories (cf. contrasts 2, 3, 6, 7) show
+clusters in (primary and secondary) auditory cortices.
+% soundscape
+Activity in such clusters could be correlated with a possible change of the
+soundscape when the narrator of the audio-description, corresponding to a cut in
+the movie, switches udio-description stimulusto a another setting.
+% interpretation 1
+This suggests that variance correlating with lower level auditory processes was
+not averaged out across events and the employed nuisance regressors did not
+capture this variance appropriately.\todo{this sounds shitty}
+% interpretation 2
+Increased hemodynamic activity in superior temporal cortices suggest a bias
+towards lower-level auditory perceptual processes on the positive side of the
+GLM contrasts.
+
+\subsubsection{``random clusters''}
+
+\todo[inline]{following list probaly exhaustive but probably too long}
+%
+Lastly, some contrasts of the audio-description stimulus yielded significant
+clusters in regions that were not statistically significant in three or more
+contrasts.
+% details
+In detail, contrast 2 yielded clusters in the anterior cingulate gyrus
+(bilateral), right frontal pole, right frontal medial cortex, and right putamen.
+%
+Contrast 3 shows clusters in the anterior cingulate gyrus (bilateral), left
+frontal pole, and left insular.
+%
+Contrast 7 shows clusters in the left frontal pole and left frontal operculum,
+left insular.
+%
+Contrast 6 shows one additional cluster in the right medial frontal cortex.
+% concludion statement
+Here again, significantly increased activation beyond areas known to be involved
+in processing of spatial information can be attributed to stimulus features of
+the naturalistic stimulus that were not sufficiently controlled leading to a
+bias in the contrasts.
 
@@
 
-\begin{comment}
-    the mother of total confusion: Aminoff shifts the PPA along the
-    anterior-poster axis depending on publication;
-    in Aminoff (2007, 2013):
-    anterior PPA = spatial associations,
-    region anterior to (!) PPA = non-spatial associations;
-    in Aminoff (2015):
-    posterior PPA = spatial associations,
-    anterior PPA = non-spatial associations;
-    hence: complete bullshit;
-    ignore Aminoff (2015) due to various reasons
-\end{comment}
-
-\subsection{Additional contrasts: let's talk about left overs}
-
-\todo[inline]{look at the events within categories \& give some counts}
-
-\todo[inline]{compare with Michaels make over of text regarding confound
-structure
-
-\todo[inline]{main message here again: you need events! (and be aware of biases)}
-
-%
-Three contrasts yielded bilaterally significant clusters in superior temporal
-cortices (contrasts 3, 6, 7), one contrast a unilateral right cluster (contrast
-2).
-%
-\todo{following is (probably too) exhaustive}
-%
-Lastly, some contrasts of the audio-description stimulus yielded significant
-clusters in regions that were not statistically significant in three or more
-contrasts.
-%
-Contrast 2 yielded clusters in the anterior cingulate gyrus (bilateral), right
-frontal pole, right frontal medial cortex, and right putamen.
-%
-Contrast 3 shows clusters in the anterior cingulate gyrus (bilateral), left
-frontal pole, and left insular.
-%
-Contrast 7 shows clusters in the left frontal pole and left frontal operculum,
-left insular.
-%
-Contrast 6 shows one additional cluster in the right medial frontal cortex.
-% concludion statement
-Conclusion: This can be attributed to the uncontrolled nature of averaged events.
-
-% ``confounding'' clusters
-Our whole brain analysis did not identify systematically occuring clusters pointing
-to confounding cognitive processes like attention or eye movements
-% AV: null results regarding attention and eye movements
-% AD: auditory cortices
-Nevertheless, for the audio-description stimulus contrasts that compare verbal
-hints of the change of a setting (\texttt{se\_new} or \texttt{se\_old}) to all
-non-spatial categories (cf. contrasts 2, 3, 6, 7) show clusters in
-(primary and secondary) auditory cortices.
-% averaging vs. nuisance regressors
-This suggests that variance correlating with lower level auditory processes was
-not averaged out across events and the employed nuisance regressors did not
-capture this variance appropriately.
-% possible reason
-Activity in such clusters could be correlated with a possible
-change of the soundscape when the narrator of the audio-description,
-corresponding to a cut in the movie, switches udio-description stimulusto a another setting.
-% concluding statement
-Thus, investigators that use model-driven methods to investigate brain functions
-using naturalistic stimuli should extensively annotate the stimulus material
-and test for correlations among variables.
-
-\todo[inline]{random [?] prefrontal cluster in 2-3 AD contrasts; at the moment
-no idea what the correlating process could be; be aware of reverse inferences}
-
 \subsection{Control contrasts}
@@
 % AV using nouns
-The contrast that used the narrator's nouns that did not actually exist in the movie stimulus
-(\texttt{se\_new} > \texttt{se\_old}) yielded a significant cluster in the right
-PPA and bilateral clusters in the superior lateral occipital cortices (the right
-hemispheric cluster extending into the superior parietal cortex).\todo{explanation?}
+The contrast that used the narrator's nouns that did not actually exist in the
+movie stimulus (\texttt{se\_new} > \texttt{se\_old}) yielded a significant
+cluster in the right PPA and bilateral clusters in the superior lateral
+occipital cortices (the right hemispheric cluster extending into the superior
+parietal cortex).\todo{explanation?}
 
 % AD stimulus
-For the analysis of the audio-description, we created control contrasts based on events of
-the annotated movie cuts (Tab.~\ref{tab:ao-contrasts}), which although invisible
-were nevertheless frequently perceivable due to changes in the soundscape.
+For the analysis of the audio-description, we created control contrasts based on
+events of the annotated movie cuts (Tab.~\ref{tab:ao-contrasts}), which although
+invisible were nevertheless frequently perceivable due to changes in the
+soundscape.
 % contrast 9
-Contrast 9 (\texttt{vse\_new > pe\_old}) revealed one significant cluster in the left
-inferior prefrontal cortex (pars triangularis) and right ventral
+Contrast 9 (\texttt{vse\_new > pe\_old}) revealed one significant cluster in the
+left inferior prefrontal cortex (pars triangularis) and right ventral
 precuneus/posterior cingulate gyrus.
@@
 % AV anno in AV data
-The the 5 movie PPA contrasts but with the movie data using cuts. All null results
-except:
+The the 5 movie PPA contrasts but with the movie data using cuts. All null
+results except:
 % contrast 9

### 2021-02-21 paper/main.tex
restructure & rephrase suppl. materials

@@
 
-\todo{print contrasts; count per category? -> pattern "average of events" and
-counts vs. significant clusters?}
+\todo[inline]{print contrasts; count per category? -> pattern "average of
+events" and counts vs. significant clusters?}
 
@@
 \todo[inline]{SE: use different colormap for overlap of contrasts' clusters}
-lche Kontraste (z.B. im Ergebnis) von anderen abgewichen?}
 
@@
 depend on the design of one specific contrasts.
-%
-\todo[inline]{print contrasts; counts per contrasted categories? "fit of
-averaged events"?}
-% but
+% but:
 Nevertheless, results are sensitive to the contrasted categories and the amount
@@
 
-\todo[inline]{following list probaly exhaustive but probably too long}
+\todo[inline]{following list is exhaustive but probably too detailed}
 %
@@
 % intro
-We implemented five contrasts for every stimulus.
+For each contrast we created several control contrasts.
 % AV: no_cut > x
-In the analysis of the movie data, none of the four contrasts that compared the
-\texttt{no\_cut} category to a movie cut category (Tab.~\ref{tab:av-contrasts})
-yielded significant clusters.
-% AV using nouns
-The contrast that used the narrator's nouns that did not actually exist in the
-movie stimulus (\texttt{se\_new} > \texttt{se\_old}) yielded a significant
-cluster in the right PPA and bilateral clusters in the superior lateral
-occipital cortices (the right hemispheric cluster extending into the superior
-parietal cortex).\todo{explanation?}
+To test for XYZ\todo{yes, to test what?} within the movie fMRI data, we created
+four contrasts that compared hemodynamic activity during frames within movie
+shots (\texttt{no\_cut} category) with movie cut related categories (Tab.~\ref{tab:av-contrasts}).
+%
+None of these four contrasts yielded a significant cluster which suggest that
+XYZ\todo{concluding statement}.
+
+% \texttt{se\_new} (nouns) is r$\approx$0.3 correlated with \texttt{vse\_new}
+% (cuts); \texttt{se\_old} (nouns) is r$\approx$0.4 correlated with
+% \texttt{vse\_old}.
+Given that cuts to a setting depicted for the first time (\texttt{vse\_new}) and
+nouns indicating a a switch to a setting ocurring for the first timei
+(\texttt{se\_new}), and cuts to a recurringly depicted setting
+({\texttt{vse\_old}) and nouns indicating a switch a recurring setting
+(\texttt{se\_old} turned out to be moderately correlated
+(Fig.~\ref{fig:reg-corr}), we created a contrast that used the
+audio-description's nouns on the movie data ({\texttt{se\_new} >
+\texttt{se\_old}).
+% results
+The contrasts yielded a significant cluster in the right PPA and bilateral
+clusters in the superior lateral occipital cortices (the right hemispheric
+cluster extending into the superior parietal cortex).
+%
+Results suggest that XYZ.
+\todo{concluding statement}
 
 % AD stimulus
-For the analysis of the audio-description, we created control contrasts based on
-events of the annotated movie cuts (Tab.~\ref{tab:ao-contrasts}), which although
-invisible were nevertheless frequently perceivable due to changes in the
-soundscape.
+Finally for the analysis of the audio-description, we created control contrasts
+based on events of the annotated movie cuts (Tab.~\ref{tab:ao-contrasts}) in
+order to test XYZ.
+\todo{why exactly did we do this except "we do not expect (lots of) significant cluster because negative control?}
+%
+Two of five contrasts yielded signficant clusters.
 % contrast 9
@@
 Contrast 12 (\texttt{vse\_new} > \texttt{vse\_old}, \texttt{vpe\_old}) revealed
-one cluster in the right posterior hippocampus.\todo{explanation?}
-
-The four control contrasts of the movie stimulus that compared the
-\texttt{no\_cuts} to categories of movie cuts all lead to null results.
-% AD anno in AV data
-The movie contrast using nouns (\texttt{se\_new} > \texttt{se\_old}): PPA
-(unilateral), LOC (bilateral); These noun categories show highest correlation
-among nouns with their cut counterpart \texttt{se\_new} (nouns) is r$\approx$0.3
-correlated with \texttt{vse\_new} (cuts); \texttt{se\_old} (nouns) is
-r$\approx$0.4 correlated with \texttt{vse\_old}.
-
-% AV anno in AV data
-The the 5 movie PPA contrasts but with the movie data using cuts. All null
-results except:
-% contrast 9
-vse\_new > pe\_old (conrast 9): left inferior prefrontal cortex (pars
-triangularis) and right ventral precuneus/posterior cingulate gyrus.
-% contrast 12
-vse\_new > vse\_old, vpe\_old (contrast 12): one cluster in the right posterior
-hippocampus.
+one cluster in the right posterior hippocampus.
+\todo{explanation?}
+%
+Overall results from the negative control contrast of the audio-description's
+data suggest that XYZ.
+\todo{concluding statement}.
 

### 2021-02-23 paper/main.tex
Keep floats in their section
Merge contrast tables

@@
 \usepackage{babel}
+\usepackage[section]{placeins}
+\usepackage{flafter}
 \usepackage{comment}
@@
 arbitrary to some degree. Consequently, we computed multiple contrasts that are
-listed in Tables~\ref{tab:av-contrasts} and \ref{tab:ao-contrasts} for movie
+listed in Table~\ref{tab:contrasts} for movie
 and audio-description, respectively. For each stimulus we, subjectively, picked
@@
 % control contrasts
-Finally, we created several control contrasts for both stimuli
-(Tab.~\ref{tab:av-contrasts} and Tab.~\ref{tab:ao-contrasts}).
+Finally, we created several control contrasts for both stimuli.
 % AV: no cut > cut
 For the movie stimulus, four contrasts were created contrasting the no-cut
-regressor (\texttt{vno\_cut} to cut-related regressors \ref{tab:av-contrasts}).
+regressor (\texttt{vno\_cut} to cut-related regressors \ref{tab:contrasts}).
 % AV: narrator
@@
 For the audio-description stimulus, we created five control contrasts
-(Tab.~\ref{tab:ao-contrasts}) to test if activation in the PPA was
+(Tab.~\ref{tab:contrasts}) to test if activation in the PPA was
 correlated with moments of cuts, despite the absence of visual stimulation.
@@
 \begin{table*}[tbp]
-\caption{Computed contrasts for the analysis of the movie and their purpose.}
-\label{tab:av-contrasts}
+  \caption{Computed contrasts for the analysis of the movie and the audio-description,
+    and their respective purpose. The primary contrasts are marked with an asterisk.
+    \texttt{non-spatial} refers to the annotation categories
+    \texttt{body}, \texttt{bodypart}, \texttt{fahead},
+    \texttt{object}, \texttt{sex\_f}, \texttt{sex\_m}.}
+\label{tab:contrasts}
 \begin{tabular}{lll}
@@
 \midrule
-1 & \texttt{vse\_new > vpe\_old} & spatial processing \tabularnewline
+\multicolumn{3}{l}{\textit{Movie stimulus}}\\
+1* & \texttt{vse\_new > vpe\_old} & spatial processing \tabularnewline
 2 & \texttt{vse\_new, vpe\_new > vse\_old, vpe\_old} & spatial processing \tabularnewline
@@
 10 & \texttt{se\_new > se\_old} & control for (missing) narrator \tabularnewline
-\bottomrule
-\end{tabular}
-\end{table*}
-
-\begin{table*}[tbp]
-\caption{Computed contrasts for the analysis of the audio-description and their purpose.
-    \texttt{non-spatial} refers to the categories
-    \texttt{body}, \texttt{bodypart}, \texttt{fahead},
-    \texttt{object}, \texttt{sex\_f}, \texttt{sex\_m}.}
-\label{tab:ao-contrasts}
-\begin{tabular}{lll}
-\toprule
-\textbf{Nr.} &  \textbf{Contrast} & \textbf{Purpose} \\
 \midrule
-1 & \texttt{geo, groom > non-spatial} & spatial processing \tabularnewline
+\multicolumn{3}{l}{\textit{Audio-description stimulus}}\\
+1* & \texttt{geo, groom > non-spatial} & spatial processing \tabularnewline
 2 & \texttt{geo, groom, se\_new > non-spatial} & spatial processing \tabularnewline
@@
 In order to test the robustness of our approach, we created overall five
-$t$-contrasts for the movie stimulus (Tab.~\ref{tab:av-contrasts}), and overall
+$t$-contrasts for the movie stimulus, and overall
 eight $t$-contrast for the audio-description stimulus
-(Tab.~\ref{tab:av-contrasts}).
+(Tab.~\ref{tab:contrasts}).
 % how
@@
     \caption{Overlap of significant clusters ($Z$>3.4; $p$<.05, cluster corrected)
-        The audio-description's contrasts 1-8 (blue; \ref{tab:ao-contrasts})
+        The audio-description's contrasts 1-8 (blue)
         are overlaid over the audio-visual movie's contrasts 1-5 (red;
-        \ref{tab:av-contrasts}).
+        \ref{tab:contrasts}).
         Cluster are overlaid on top of the MNI152 T1-weighted head template
@@
 four contrasts that compared hemodynamic activity during frames within movie
-shots (\texttt{no\_cut} category) with movie cut related categories (Tab.~\ref{tab:av-contrasts}).
+shots (\texttt{no\_cut} category) with movie cut related categories (Tab.~\ref{tab:contrasts}).
 %
@@
 Finally for the analysis of the audio-description, we created control contrasts
-based on events of the annotated movie cuts (Tab.~\ref{tab:ao-contrasts}) in
+based on events of the annotated movie cuts (Tab.~\ref{tab:contrasts}) in
 order to test XYZ.

### 2021-02-23 paper/main.tex
concat tables of AV & AO events; adjust references to table

@@
 % AV regressors/events
-We assigned each cut to one of five categories (Tab.~\ref{tab:av-events}):
+We assigned each cut to one of five categories (Tab.~\ref{tab:events}):
 %
@@
     \caption{Overview of annotated stimulus features of the audio-visual
-    movie.
+    movie and the audio-description.
+    Some of the noun categories (female, females, fname; male,
+    males, mname; face, head; object, objects;
+    Tab.~\ref{tab:descr-nouns-rules}) were pooled
+    into 11 new categories (\texttt{sex\_f}; \texttt{sex\_m}; \texttt{fahead},
+    \texttt{object}).
     Respective event counts are given for the whole stimulus (\texttt{All} and
@@
     % narrator (\texttt{se\_new} and \texttt{se\_old}) to build contrast of
-    % negative control Tab.~\ref{tab:ao-events}.
+    % negative control Tab.~\ref{tab:events}.
     }
-\label{tab:av-events}
+\label{tab:events}
 \small
@@
 \midrule
+\multicolumn{3}{l}{\textit{Movie stimulus}}\\
 \texttt{vse\_new} &  change of the camera position to a setting not depicted before & \aoVsenewAll & \aoVsenewI & \aoVsenewII & \aoVsenewIII & \aoVsenewIV & \aoVsenewV & \aoVsenewVI & \aoVsenewVII & \aoVsenewVIII
@@
 \texttt{fg\_av\_ger\_ud} & upper-lower luminance difference & \avFgavgerudAll & \avFgavgerudI & \avFgavgerudII & \avFgavgerudIII & \avFgavgerudIV & \avFgavgerudV & \avFgavgerudVI & \avFgavgerudVII & \avFgavgerudVIII
+\tabularnewline
+\midrule
+\multicolumn{3}{l}{\textit{Audio-description stimulus}}\\
+\texttt{body} & trunk of the body; overlaid clothes & \aoBodyAll & \aoBodyI & \aoBodyII
+& \aoBodyIII & \aoBodyIV & \aoBodyV & \aoBodyVI & \aoBodyVII & \aoBodyVIII
+\tabularnewline
+\texttt{bpart} & limbs and trousers & \aoBpartAll & \aoBpartI & \aoBpartII & \aoBpartIII & \aoBpartIV & \aoBpartV & \aoBpartVI & \aoBpartVII & \aoBpartVIII
+\tabularnewline
+\texttt{fahead} & face or head (parts) & \aoFaheadAll & \aoFaheadI & \aoFaheadII & \aoFaheadIII & \aoFaheadIV & \aoFaheadV & \aoFaheadVI & \aoFaheadVII & \aoFaheadVIII
+\tabularnewline
+\texttt{furn} & moveable furniture (insides \& outsides) & \aoFurnAll & \aoFurnI & \aoFurnII & \aoFurnIII & \aoFurnIV & \aoFurnV & \aoFurnVI & \aoFurnVII & \aoFurnVIII
+\tabularnewline
+\texttt{geo} & immobile landmarks & \aoGeoAll & \aoGeoI & \aoGeoII & \aoGeoIII & \aoGeoIV & \aoGeoV & \aoGeoVI & \aoGeoVII & \aoGeoVIII
+\tabularnewline
+\texttt{groom} & rooms \& locales or geometry-defining elements & \aoGroomAll & \aoGroomI & \aoGroomII & \aoGroomIII & \aoGroomIV & \aoGroomV & \aoGroomVI & \aoGroomVII & \aoGroomVIII
+\tabularnewline
+\texttt{object} & countable entities with firm boundaries & \aoObjAll & \aoObjI & \aoObjII & \aoObjIII & \aoObjIV & \aoObjV & \aoObjVI & \aoObjVII & \aoObjVIII
+\tabularnewline
+\texttt{se\_new} & a setting occurring for the first time & \aoSenewAll & \aoSenewI & \aoSenewII & \aoSenewIII & \aoSenewIV & \aoSenewV & \aoSenewVI & \aoSenewVII & \aoSenewVIII
+\tabularnewline
+\texttt{se\_old} & a recurring setting & \aoSeoldAll & \aoSeoldI & \aoSeoldII & \aoSeoldIII & \aoSeoldIV & \aoSeoldV & \aoSeoldVI & \aoSeoldVII & \aoSeoldVIII
+\tabularnewline
+\texttt{sex\_f} & female person(s), name & \aoSexfAll & \aoSexfI & \aoSexfII & \aoSexfIII & \aoSexfIV & \aoSexfV & \aoSexfVI & \aoSexfVII & \aoSexfVIII
+\tabularnewline
+\texttt{sex\_m} & male person(s), name & \aoSexmAll & \aoSexmI & \aoSexmII & \aoSexmIII & \aoSexmIV & \aoSexmV & \aoSexmVI & \aoSexmVII & \aoSexmVIII
+\tabularnewline
+% vlo_ch has no events in segment 5. So indices are shifted
+%vse\_new & control for movie cut & \aoVsenewAll & \aoVsenewI & \aoVsenewII & \aoVsenewIII & \aoVsenewIV & \aoVsenewV & \aoVsenewVI & \aoVsenewVII & \aoVsenewVIII
+%\tabularnewline
+%vse\_old & control for movie cut & \aoVseoldAll & \aoVseoldI & \aoVseoldII & \aoVseoldIII & \aoVseoldIV & \aoVseoldV & \aoVseoldVI & \aoVseoldVII & \aoVseoldVIII
+%\tabularnewline
+%vlo\_ch & control for movie cut & \aoVlochAll & \aoVlochI & \aoVlochII & \aoVlochIII & \aoVlochIV & 0 & \aoVlochV & \aoVlochVI & \aoVlochVII
+%\tabularnewline
+%vpe\_new & control for movie cut & \aoVpenewAll & \aoVpenewI & \aoVpenewII & \aoVpenewIII & \aoVpenewIV & \aoVpenewV & \aoVpenewVI & \aoVpenewVII & \aoVpenewVIII
+%\tabularnewline
+% vpe_old has no events in 3. So the indices are shifted
+%vpe\_old & control for movie cut & \aoVpeoldAll & \aoVpeoldI & \aoVpeoldII & 0 & \aoVpeoldIII & \aoVpeoldIV & \aoVpeoldV & \aoVpeoldVI & \aoVpeoldVII
+% \tabularnewline
+\texttt{fg\_ad\_lrdiff} & left-right volume difference & \aoFgadlrdiffAll & \aoFgadlrdiffI & \aoFgadlrdiffII & \aoFgadlrdiffIII & \aoFgadlrdiffIV &
+\aoFgadlrdiffV & \aoFgadlrdiffVI & \aoFgadlrdiffVII & \aoFgadlrdiffVIII
+\tabularnewline
+\texttt{fg\_ad\_rms} & root mean square volume & \aoFgadrmsAll &
+\aoFgadrmsI & \aoFgadrmsII & \aoFgadrmsIII & \aoFgadrmsIV & \aoFgadrmsV &
+\aoFgadrmsVI & \aoFgadrmsVII & \aoFgadrmsVIII
 \tabularnewline
@@
 Some noun categories that were semantically similar and offered only a small
-amount of counts were pooled resulting in 11 final event categories (Tab.~\ref{tab:ao-events}).
+amount of counts were pooled resulting in 11 final event categories (Tab.~\ref{tab:events}).
 These event categories were then used to model hemodynamic
@@
         GLM
-        (Tab.~\ref{tab:ao-events}).
+        (Tab.~\ref{tab:events}).
         % The category \texttt{++} also contains adverbial of time.
@@
 % ++ & cue regarding time & in the ``evening'', it's ``daytime'', ``later'' \tabularnewline
-\bottomrule
-\end{tabular}
-\end{table*}
-
-% AD regressors
-\begin{table*}[tbp]
-    \caption{Overview of annotated stimulus features of the audio-description.
-    Respective event counts are given for the whole stimulus (\texttt{All} and
-    the segments that were used for the eight sessions of fMRI scanning.
-    Some of the annotation's original categories (female, females, fname; male,
-    males, mname; face, head; object, objects;
-    Tab.~\ref{tab:descr-nouns-rules}) were pooled
-    into 11 new categories (\texttt{sex\_f}; \texttt{sex\_m}; \texttt{fahead},
-    \texttt{object}).
-    Event counts for frame-based features are reported in units of a thousand.
-    % For a description of the five control conditions for movie cuts see
-    % Tab.~\ref{tab:av-events}.
-    }
-\label{tab:ao-events}
-\begin{tabular}{lp{3.8cm}lllllllll}
-\toprule \textbf{Label} & \textbf{Description} & \textbf{All} & \textbf{1} & \textbf{2} & \textbf{3} & \textbf{4} & \textbf{5} & \textbf{6} & \textbf{7} & \textbf{8} \\
-\midrule
-\texttt{body} & trunk of the body; overlaid clothes & \aoBodyAll & \aoBodyI & \aoBodyII
-& \aoBodyIII & \aoBodyIV & \aoBodyV & \aoBodyVI & \aoBodyVII & \aoBodyVIII
-\tabularnewline
-\texttt{bpart} & limbs and trousers & \aoBpartAll & \aoBpartI & \aoBpartII & \aoBpartIII & \aoBpartIV & \aoBpartV & \aoBpartVI & \aoBpartVII & \aoBpartVIII
-\tabularnewline
-\texttt{fahead} & face or head (parts) & \aoFaheadAll & \aoFaheadI & \aoFaheadII & \aoFaheadIII & \aoFaheadIV & \aoFaheadV & \aoFaheadVI & \aoFaheadVII & \aoFaheadVIII
-\tabularnewline
-\texttt{furn} & moveable furniture (insides \& outsides) & \aoFurnAll & \aoFurnI & \aoFurnII & \aoFurnIII & \aoFurnIV & \aoFurnV & \aoFurnVI & \aoFurnVII & \aoFurnVIII
-\tabularnewline
-\texttt{geo} & immobile landmarks & \aoGeoAll & \aoGeoI & \aoGeoII & \aoGeoIII & \aoGeoIV & \aoGeoV & \aoGeoVI & \aoGeoVII & \aoGeoVIII
-\tabularnewline
-\texttt{groom} & rooms \& locales or geometry-defining elements & \aoGroomAll & \aoGroomI & \aoGroomII & \aoGroomIII & \aoGroomIV & \aoGroomV & \aoGroomVI & \aoGroomVII & \aoGroomVIII
-\tabularnewline
-\texttt{object} & countable entities with firm boundaries & \aoObjAll & \aoObjI & \aoObjII & \aoObjIII & \aoObjIV & \aoObjV & \aoObjVI & \aoObjVII & \aoObjVIII
-\tabularnewline
-\texttt{se\_new} & a setting occurring for the first time & \aoSenewAll & \aoSenewI & \aoSenewII & \aoSenewIII & \aoSenewIV & \aoSenewV & \aoSenewVI & \aoSenewVII & \aoSenewVIII
-\tabularnewline
-\texttt{se\_old} & a recurring setting & \aoSeoldAll & \aoSeoldI & \aoSeoldII & \aoSeoldIII & \aoSeoldIV & \aoSeoldV & \aoSeoldVI & \aoSeoldVII & \aoSeoldVIII
-\tabularnewline
-\texttt{sex\_f} & female person(s), name & \aoSexfAll & \aoSexfI & \aoSexfII & \aoSexfIII & \aoSexfIV & \aoSexfV & \aoSexfVI & \aoSexfVII & \aoSexfVIII
-\tabularnewline
-\texttt{sex\_m} & male person(s), name & \aoSexmAll & \aoSexmI & \aoSexmII & \aoSexmIII & \aoSexmIV & \aoSexmV & \aoSexmVI & \aoSexmVII & \aoSexmVIII
-\tabularnewline
-% vlo_ch has no events in segment 5. So indices are shifted
-%vse\_new & control for movie cut & \aoVsenewAll & \aoVsenewI & \aoVsenewII & \aoVsenewIII & \aoVsenewIV & \aoVsenewV & \aoVsenewVI & \aoVsenewVII & \aoVsenewVIII
-%\tabularnewline
-%vse\_old & control for movie cut & \aoVseoldAll & \aoVseoldI & \aoVseoldII & \aoVseoldIII & \aoVseoldIV & \aoVseoldV & \aoVseoldVI & \aoVseoldVII & \aoVseoldVIII
-%\tabularnewline
-%vlo\_ch & control for movie cut & \aoVlochAll & \aoVlochI & \aoVlochII & \aoVlochIII & \aoVlochIV & 0 & \aoVlochV & \aoVlochVI & \aoVlochVII
-%\tabularnewline
-%vpe\_new & control for movie cut & \aoVpenewAll & \aoVpenewI & \aoVpenewII & \aoVpenewIII & \aoVpenewIV & \aoVpenewV & \aoVpenewVI & \aoVpenewVII & \aoVpenewVIII
-%\tabularnewline
-% vpe_old has no events in 3. So the indices are shifted
-%vpe\_old & control for movie cut & \aoVpeoldAll & \aoVpeoldI & \aoVpeoldII & 0 & \aoVpeoldIII & \aoVpeoldIV & \aoVpeoldV & \aoVpeoldVI & \aoVpeoldVII
-% \tabularnewline
-\texttt{fg\_ad\_lrdiff} & left-right volume difference & \aoFgadlrdiffAll & \aoFgadlrdiffI & \aoFgadlrdiffII & \aoFgadlrdiffIII & \aoFgadlrdiffIV &
-\aoFgadlrdiffV & \aoFgadlrdiffVI & \aoFgadlrdiffVII & \aoFgadlrdiffVIII
-\tabularnewline
-\texttt{fg\_ad\_rms} & root mean square volume & \aoFgadrmsAll &
-\aoFgadrmsI & \aoFgadrmsII & \aoFgadrmsIII & \aoFgadrmsIV & \aoFgadrmsV &
-\aoFgadrmsVI & \aoFgadrmsVII & \aoFgadrmsVIII
-\tabularnewline
 \bottomrule
@@
         the GLM analysis of the
-        audio-description (blue; Tab.~\ref{tab:ao-events} for a
-        description) and audio-visual movie (red; Tab.~\ref{tab:av-events}).
+        audio-description (blue; Tab.~\ref{tab:events} for a
+        description) and audio-visual movie (red; Tab.~\ref{tab:events}).
         Values are rounded to the nearest tenth.
@@
 The design matrices of the first-level time-series GLM analysis comprised the
-regressors for the stimulus features listed in Tables~\ref{tab:av-events} and
-\ref{tab:ao-events} for the movie and audio-description stimulus, respectively.
+regressors for the stimulus features listed in Tables~\ref{tab:events} and
+\ref{tab:events} for the movie and audio-description stimulus, respectively.
 % AD regressors in AV
@@
 Likewise, the audio-description design matrix included movie cut related regressors
-listed Table~\ref{tab:av-events} (excluding \texttt{no\_cut}).
+listed Table~\ref{tab:events} (excluding \texttt{no\_cut}).
 % both stimuli: null regressors
@@
 for which no event of a category was present (e.g. no event of
-\texttt{vpe\_old} in segment 3; Tab.~\ref{tab:ao-events}).
+\texttt{vpe\_old} in segment 3; Tab.~\ref{tab:events}).
 % temporal derivatives

### 2021-02-23 paper/main.tex
abstract tweaking

@@
 % our audience highlighting innovative examples of data reuse may be used to
-% present compelling new findings & conclusions derived from published.  PPA
+% present compelling new findings & conclusions derived from published.
 The ``parahippocampal place area'' (PPA) in the human ventral visual stream
@@
 % AV, AD: operationalization
-Here, we investigate the perception of spatial information in 14 individuals
-watching a two-hour Hollywood movie and listening to the movie's
-audio-description as part of the open-data resource \textit{studyforrest.org}.
+Here, we investigate the perception of spatial information embedded in two
+naturalistic stimuli.
+%
+The same 14 subjects were watching a Hollywood movie and listening to its audio-description as part of the open-data resource \textit{studyforrest.org}.
 % auditory localizer?
@@
 %\citep{sengupta2016extension}.  results: group AV
-On a group level, increased activation correlating with spatial information
+On a group level, increased activation correlating with visual spatial information
 occurring in the movie is overlapping with a traditionally localized PPA.
@@
 Results suggest that activation in the PPA generalizes to spatial information
-embedded in a movie and spatial information in an auditory narrative, and may
+embedded in a movie and an auditory narrative, and may
 % conclusion: PPA has subregions
@@
 \begin{itemize}
-    \item more detailed discussion differences of contrasts (s. Simons comment)?
-    \item discussion of control contrasts
-\end{itemize}
-
-\noindent Data Citations, Code Availability
-\begin{itemize}
-    \item draft for Code and Data Availability is done (other analysis paper do
-        it pretty amateurish); will look at the ``how to write an excellent
-        data availability statement'' at springernature.com
+    \item introductory sentences (e.g. "To test...") and concluding statements
 \end{itemize}

### 2021-02-23 paper/main.tex
intro: proof of concept localization & PPA as an example

@@
 faces or tools) during blood oxygenation level-dependent functional magnetic
-resonance imaging (BOLD fMRI) \citep{aguirre1998area, epstein2014neural,
-epstein1998ppa, troiani2012object}.
+resonance imaging (BOLD fMRI) (see \citep{epstein2014neural, aminoff2013role}
+for reviews).\todo{but: Aminoff also reviews episodic memory function \&
+(theories unifying) contextual info which is not review in intro}
+% \citep{aguirre1998area, epstein2014neural, epstein1998ppa, troiani2012object}.
 
 % literature review overview 1: imagination & haptic exploration
-Increased hemodynamic activity in the PPA generalizes to mental imagination of
-landscapes \citep{ocraven2000mental}, haptic exploration of scenes
-constructed from LEGO blocks \citep{wolbers2011modality} and scene-related
-sounds \citep{van2017development}.
+Increased hemodynamic activity in the PPA generalizes from pictures to mental
+imagination of landscapes \citep{ocraven2000mental}, haptic exploration of
+scenes constructed from LEGO blocks \citep{wolbers2011modality} and
+scene-related sounds \citep{van2017development}.
 % van der Hurk: 64 sounds x 1.8 seconds; 20 sighted, 14 congenitally blind
@@
 involving famous places.
-
+\todo[inline]{SE: (lack of) exclusivity is not really becoming evident from
+preceding paragraph; COH: but imo the hole paragraph is about exactly that??}
 % summary if literature review
-In summary, studies suggest that the PPA does preferably but not exclusively
-respond to visually presented spatial information.
+In summary, studies suggest that the PPA does not exclusively respond to
+visually presented spatial information.
 % three things in common
-All reviewed studies share three common aspects:
+Nevertheless, the reviewed studies share three common aspects:
 % designed stimulus set
@@
 lack external and ecological validity \citep{westfall2016fixing,
-hasson2004intersubject} because they poorly resemble how we, free of an
-explicit perceptual task, experience our rich, multidimensional and continuous
+hasson2004intersubject} because they poorly resemble how we, free of an explicit
+perceptual task, experience our rich, multidimensional and continuous
 environment that our brains are accommodated to
@@
 We hypothesized that whole-brain analyses would reveal increased hemodynamic
-activity in the PPA as functionally defined by a
-conventional visual localizer for each individual, because all three operationalization capitalize
-on events that should evoke the cognitive processing of spatial information.
+activity in the PPA as functionally defined by a conventional visual localizer
+for each individual, because all three operationalization capitalize on events
+that should evoke the cognitive processing of spatial information.
 % hypo b: individuals
-We hypothesized further that an exclusively auditory stimulus could localize a
-``visual area'' in individuals,
+We hypothesized further that an purely auditory stimulus could, in principle,
+localize the PPA as an example of a ``visual area'' in individual persons,
 % application in individuals
-and may offer an alternative paradigm to assess this aspect of brain function
-in visually impaired individuals.
+and may offer an alternative paradigm to assess brain functions in visually
+impaired individuals.
 

### 2021-02-23 paper/main.tex
explicitly note that 15 AV subjects is subgroup

@@
 % AD study
-In the audio-description study \citep{hanke2014audiomovie}, 20 German native speakers (all
-right-handed, age 21–38 years, mean age 26.6 years, 12 male) listened to the
-German audio-description \citep{ForrestGumpGermanAD} of the movie ``Forrest
-Gump'' \citep{ForrestGumpMovie}.
+In the audio-description study \citep{hanke2014audiomovie}, 20 German native
+speakers (all right-handed, age 21–38 years, mean age 26.6 years, 12 male)
+listened to the German audio-description \citep{ForrestGumpGermanAD} of the
+movie ``Forrest Gump'' \citep{ForrestGumpMovie}.
 % AV study
 In the movie study \citep{hanke2016simultaneous}, 15 participants (21–39 years,
-mean age 29.4, six female) of the prior audio-description study watched the audio-visual movie
-with dubbed German audio track \citep{ForrestGumpDVD}.
+mean age 29.4, six female), a subgroup of the prior audio-description study,
+watched the audio-visual movie with dubbed German audio track
+\citep{ForrestGumpDVD}.
 % VIS study
-In the block-design localizer study \citep{sengupta2016extension}, the same 15 participants took
-part in a six-category block-design visual localizer.
+In the block-design localizer study \citep{sengupta2016extension}, the same 15
+participants took part in a six-category block-design visual localizer.
 % participants' health
@@
 % procedure: presentation & instructions
-Participants performed a one-back image matching task for four block-design runs,
-with two \unit[16]{s} blocks per stimulus category in each run.
+Participants performed a one-back image matching task for four block-design
+runs, with two \unit[16]{s} blocks per stimulus category in each run.
 %
@@
 % AD
-In the audio-description study, visual instructions were presented on a rear-projection screen
-inside scanner bore. During the
-functional scans, the projector presented a medium gray screen with the primary
-purpose to illuminate a participant's visual field in order to prevent premature
-fatigue.
+In the audio-description study, visual instructions were presented on a
+rear-projection screen inside scanner bore. During the functional scans, the
+projector presented a medium gray screen with the primary purpose to illuminate
+a participant's visual field in order to prevent premature fatigue.
 % AV & VIS
-In the movie and block-design localizer study, visual instructions and stimuli were presented on a
-rear-projection screen
+In the movie and block-design localizer study, visual instructions and stimuli
+were presented on a rear-projection screen
 % screen size \unit[23.75 $\times$ 10.25]{cm}
-at a viewing distance of \unit[63]{cm}, with a movie frame projection size
-of approximately \unit[21.3]$^{\circ}$ $\times$ \unit[9.3]$^{\circ}$.
+at a viewing distance of \unit[63]{cm}, with a movie frame projection size of
+approximately \unit[21.3]$^{\circ}$ $\times$ \unit[9.3]$^{\circ}$.
 % angle of view: VIS
-In the block-design localizer study, stimulus images were displayed at a size of approximately
-\unit[10]$^{\circ}$ $\times$ \unit[10]$^{\circ}$ of visual angle.
+In the block-design localizer study, stimulus images were displayed at a size of
+approximately \unit[10]$^{\circ}$ $\times$ \unit[10]$^{\circ}$ of visual angle.
 % AD & AV: auditory stimulation
-Auditory stimulation was implemented using custom in-ear (audio-description), or over-the-ear
-headphones (movie), which reduced the scanner noise by
-at least \unit[20–30]{dB}.
+Auditory stimulation was implemented using custom in-ear (audio-description), or
+over-the-ear headphones (movie), which reduced the scanner noise by at least
+\unit[20–30]{dB}.
 
@@
 
-Gradient-echo fMRI data for the audio-description study were acquired using a \unit[7]{Tesla}
-Siemens MAGNETOM magnetic resonance scanner equipped with a 32 channel brain
-receive coil at \unit[2]{s} repetition time (TR) with 36 axial slices (thickness
-\unit[1.4]{mm}, \unit[1.4 $\times$ 1.4]{mm} in-plane resolution, \unit[224]{mm}
-field-of-view, anterior-to-posterior phase encoding direction) and a
-\unit[10]{\%} inter-slice gap, recorded in ascending order.
+Gradient-echo fMRI data for the audio-description study were acquired using a
+\unit[7]{Tesla} Siemens MAGNETOM magnetic resonance scanner equipped with a 32
+channel brain receive coil at \unit[2]{s} repetition time (TR) with 36 axial
+slices (thickness \unit[1.4]{mm}, \unit[1.4 $\times$ 1.4]{mm} in-plane
+resolution, \unit[224]{mm} field-of-view, anterior-to-posterior phase encoding
+direction) and a \unit[10]{\%} inter-slice gap, recorded in ascending order.
 % slice orientation

### 2021-02-23 paper/main.tex
intro: movie as intermediate step

@@
 In this study, we investigate if increased hemodynamic activity in the PPA that
-is usually detected by contrasting blocks of pictures is also present under
-more ecologically conditions.
+is usually detected by contrasting blocks of pictures is also present under more
+ecologically conditions.
 % we use 2 naturalistic stimuli
@@
 % GLM contrasts
-We applied model-based, mass-univariate analyses to a series of
-datasets with BOLD fMRI data from naturalistic and conventional block-design
-stimulation from the same set of participants, available from the open-data
-resource \href{http://www.studyforrest.org}{studyforrest.org}
+We applied model-based, mass-univariate analyses to a series of datasets with
+BOLD fMRI data from naturalistic and conventional block-design stimulation from
+the same set of participants, available from the open-data resource
+\href{http://www.studyforrest.org}{studyforrest.org}
 \citep{hanke2016simultaneous, hanke2014audiomovie, sengupta2016extension}.
-
+% pictures -> movie -> audio-description
+The movie, as an intermediate step, offered a more naturalistic but still visual
+stimulation whereas the audio-description, as a further step, offered a more
+naturalistic but non-visual, semantic stimulation.
 % hypo a
@@
 that should evoke the cognitive processing of spatial information.
-% hypo b: individuals
+%hypo b: individuals
 We hypothesized further that an purely auditory stimulus could, in principle,

### 2021-02-23 paper/main.tex
preprocessing: make difference between analyses and (raw) data clearer
restructure and rephrase annotation of cuts (!= movie frame content)

@@
 % https://github.com/psychoinformatics-de/studyforrest-data-templatetransforms}
-All analyses presented here are based on previously published fMRI data
+The current analyses were carried out on previously published fMRI data
 (\url{https://github.com/psychoinformatics-de/studyforrest-data-aligned}).
@@
 
+\todo[inline]{SE: temporal order of the (naturalistic) stimuli is not unknown,
+you know it by looking at the movie; COH: yes, but actually no.}
+
 % traditionally
@@
 % our approach: annotation and regressors
-naturalistic stimuli have an initially unknown temporal structure
+naturalistic stimuli have fixed but initially unknown temporal structure
 of stimulus features of interest, as well as an equally unknown confound structure.
@@
 
+In an earlier study, \cite{bartels2004mapping} manually annotated the content of
+individual movie frames (color, faces, language, and human bodies) and found
+that the functional specialization of brain areas is preserved during movie
+watching.
+
 % AV anno
@@
 \citep{haeusler2016cutanno}.
-% rationale to use that annotation rationale behind using movie cuts
-We conceptualized cuts as events with information on the depicted environment
-that require viewers to re-orient themselves within the movie environment by
-switching to a new perspective within the same setting, or to a position in an
-entirely different setting.
+% we focus on cuts
+Contrary to manually annotating stimulus features of every movie frame (as
+performed by e.g. \cite{bartels2004mapping} for color, faces, language, and
+human bodies), we categorized movie cuts that - in general - realign the viewer
+within the movie environment by switching to another perspective within the
+same setting, or to a position in an entirely different setting.
+% this this should work
+More specifically, we sought to exploit a cinematographic bias as
+% establishing shots & shots within setting early in the movie
+at a setting's first occurrence in a movie, shots tend to broadly establish the
+setting and the spatial layout within the setting.
+% cut to recurrent scene
+On revisiting an already established setting, the field sizes of movie shots
+tend to decrease, and shots tend to more often depict people talking to each
+other or objects that are relevant to the evolved plot
+\citep{brown2012cinematography, katz1991film, mascelli1998five}.
+
 % AV regressors/events
-We assigned each cut to one of five categories (Tab.~\ref{tab:events}):
+Based on this cinematographic bias, we assigned each cut to one of five
+categories (Tab.~\ref{tab:events}):
 %
@@
 of the first movie frame after a cut.
-% cinematographic rationale cut to new scenes: establishing shots
-The cinematographic rationale was that movie shots tend to establish the setting
-and their spatial layout at their first occurence in a movie.
-% cut to recurrent scene
-On revisiting an already established setting later in the movie, the field sizes
-of movie shots tend to decrease (\texttt{vse\_old}), and shots tend to
-more often depict people talking to each other, or objects that are relevant to
-the evolved plot (\texttt{vpe\_old}) \citep{brown2012cinematography,
-katz1991film, mascelli1998five}.
 % neuroscientific rationale The neuroscientific rationale was that activity in
@@
 % condition: intro
-
 As a control condition with events of no particular processing of spatial
@@
 % no cuts: how
-had a minimum temporal distance of at least \unit[10]{s} to any movie cut and
-to any other \texttt{no\_cut} event.
+had a minimum temporal distance of at least \unit[10]{s} to any movie cut and to
+any other \texttt{no\_cut} event.
 

### 2021-02-23 paper/main.tex
add comments in intro & methods

@@
 
+\noindent Generally
+\begin{itemize]}
+    \item Todo's are mostly comments and can be deleted if issue is solved by
+        current phrasing
+    \item position of figures and tables is very odd now but probably does not
+        matter
+\end{itemize}
+
 \noindent Supplemental Material
@@
 resonance imaging (BOLD fMRI) (see \citep{epstein2014neural, aminoff2013role}
-for reviews).\todo{but: Aminoff also reviews episodic memory function \&
-(theories unifying) contextual info which is not review in intro}
+for reviews).
 % \citep{aguirre1998area, epstein2014neural, epstein1998ppa, troiani2012object}.
 
-% literature review overview 1: imagination & haptic exploration
+\todo[inline]{but: Aminoff (2013) also reviews episodic memory function \& tries
+to unify domains via contextual information hypothesis which is not mentioned at
+all here}
+
+\todo[inline]{Lescroart \& Gallant (2019). semi-naturalistic, but task, 800+ stimulus, N=6}
+
+% literature review overview: imagination & haptic exploration; van der Hurk: 64
+% sounds x 1.8 seconds; 20 sighted, 14 congenitally blind
 Increased hemodynamic activity in the PPA generalizes from pictures to mental
@@
 scene-related sounds \citep{van2017development}.
-% van der Hurk: 64 sounds x 1.8 seconds; 20 sighted, 14 congenitally blind
-\todo{cite Lescroart (2019). semi-naturalistic, but task, 800+ stimulus, N=6}
-% O'Craven: watching pictures
+% % O'Craven: watching pictures
 In a study conducted by \cite{ocraven2000mental} participants viewed alternating
@@
 involving famous places.
+
 \todo[inline]{SE: (lack of) exclusivity is not really becoming evident from
-preceding paragraph; COH: but imo the hole paragraph is about exactly that??}
+preceding paragraph; COH: but imo the last two paragraphs are about exactly
+that??}
 % summary if literature review
@@
 
+\todo[inline]{other studies that localize PPA: essentially every study that does
+something "PPA-related" does it and does it using pictures; there are two
+studies that evaluate the localization as such and both give "pretty" results:}
+
+\todo[inline]{onlinelibrary.wiley.com/doi/full/10.1002/hbm.20116 -> 6 subjects;
+6x bilateral clusters}
+
+\todo[inline]{academic.oup.com/cercor/article/16/10/1453/353981 -> 12 subjs: 12x
+bilateral clusters}
+
 % DISABLE RESULTS
@@
 \citep{brown2012cinematography, katz1991film, mascelli1998five}.
+
+\todo[inline]{I think you need to help the reader understand, what annotations
+in the AV-movie are relevant in the current context; COH: imo that is more
+important in context of the contrasts (-> check if it is sufficiently described
+there); might fit in here, too, but makes current part unnessecarily
+complicated}
 

### 2021-02-23 paper/main.tex
correct typo
rephrase table caption of annotated events

@@
 \noindent Generally
-\begin{itemize]}
+\begin{itemize}
     \item Todo's are mostly comments and can be deleted if issue is solved by
@@
     movie and the audio-description.
-    Some of the noun categories (female, females, fname; male,
-    males, mname; face, head; object, objects;
-    Tab.~\ref{tab:descr-nouns-rules}) were pooled
-    into 11 new categories (\texttt{sex\_f}; \texttt{sex\_m}; \texttt{fahead},
-    \texttt{object}).
+    Some of the audio-description's event categories listed here
+    (\texttt{sex\_f}; \texttt{sex\_m}; \texttt{fahead}, \texttt{object})
+    were created by pooling some categories of the original annotation of nouns
+    (female, females, fname; male, males, mname; face, head; object, objects;
+    Tab.~\ref{tab:descr-nouns-rules}).
     Respective event counts are given for the whole stimulus (\texttt{All} and
@@
 
+\todo[inline]{SE: "the eight segments": Are you sure, everybody remembered
+these? COH: no clue what to do with that feedback}
 % we checked correlations
@@
 Maximum correlations are found for auditory low-level confounds across stimuli
-(\texttt{fg\_a(v|d)\_ger\_rms}, r=.76;
-\texttt{fg\_a(v|d)\_ger\_lrdiff}, r=.77),
+(\texttt{fg\_a(v|d)\_ger\_rms}, r=.76; \texttt{fg\_a(v|d)\_ger\_lrdiff}, r=.77),
 % no surprise
@@
 The observed correlation pattern did not indicate problematic confounds of
-nuisance variables and regressors of interest for any of the planned
-analyses.
+nuisance variables and regressors of interest for any of the planned analyses.
 

### 2021-02-23 paper/main.tex
write out in full fg_a(v|d)_ger_rms & fg_a(v|d)_ger_lrdiff

@@
 feature regressors for the same stimulus.
-% (highest) correlations across stimuli
-Maximum correlations are found for auditory low-level confounds across stimuli
-(\texttt{fg\_a(v|d)\_ger\_rms}, r=.76; \texttt{fg\_a(v|d)\_ger\_lrdiff}, r=.77),
+% (highest) correlations across stimuli; \texttt{fg\_a(v|d)\_ger\_rms}, r=.76;
+% \texttt{fg\_a(v|d)\_ger\_lrdiff}, r=.77)
+Maximum correlations are found for auditory low-level auditory confounds across
+stimuli,
 % no surprise
 which is to be expected, as the audio-description contains the audio track of
-the movie plus the additional narrator (Fig. \ref{fig:reg-corr}).
+the movie plus the additional narrator (Fig. \ref{fig:reg-corr}; correlation
+between root mean square volume of both audio tracks, r=.76; correlation between
+left-right volume difference of both audio tracks, r=.77).
 % encouraged by that we build contrasts (statement)

### 2021-02-23 paper/main.tex
add rest of Simons feedback as To-Dos

@@
         current phrasing
+    \item maybe "do something with" dice-index
     \item position of figures and tables is very odd now but probably does not
@@
 
+\todo[inline]{add a summary to the end of section 2.7 explaining in 2 sentences,
+what regressors you will be focussing on -> easier for those that got confused
+on the way}
 % AV design matrix
@@
 % intro
-We performed standard two-level GLM analyses to aggregate results across the eight
-segments for every participant and each stimulus separately.
+We performed standard two-level GLM analyses to aggregate results across the
+eight segments for every participant and each stimulus separately.
 % level 3
@@
 
+\todo[inline]{"we, subjectively, picked a primary contrast" :-(  -> you actually
+write "based on"}
+%
 Given the rich naturalistic stimuli and the availability of various stimulus
@@
 arbitrary to some degree. Consequently, we computed multiple contrasts that are
-listed in Table~\ref{tab:contrasts} for movie
-and audio-description, respectively. For each stimulus we, subjectively, picked
-a primary contrast for result presentation (the first one in each Table) based
-on how well the average event within categories represents spatial and
-non-spatial information, and the number of events in the stimulus.
-An evaluation of the robustness of these results with respect to similar but
-different contrasts is provided in the supplementary materials.
-
+listed in Table~\ref{tab:contrasts} for movie and audio-description,
+respectively. For each stimulus we, subjectively, picked a primary contrast for
+result presentation (the first one in each Table) based on how well the average
+event within categories represents spatial and non-spatial information, and the
+number of events in the stimulus.  An evaluation of the robustness of these
+results with respect to similar but different contrasts is provided in the
+supplementary materials.
+
+\todo[inline]{"vse, vno, vpe,..." are not really the most intuitive regressor
+names -> ausschreiben, wo möglich}
 % AV: primary contrast
@@
 mentions of buildings and landmarks (\texttt{geo}), and rooms and
-geometry-defining objects (\texttt{groom}) with nouns referring to a
-person's head or face (\texttt{fahead}), and other non-geometry related
-categories (\texttt{body}, \texttt{bodypart}, \texttt{fahead}, \texttt{object},
+geometry-defining objects (\texttt{groom}) with nouns referring to a person's
+head or face (\texttt{fahead}), and other non-geometry related categories
+(\texttt{body}, \texttt{bodypart}, \texttt{fahead}, \texttt{object},
 \texttt{sex\_f}, \texttt{sex\_m}).
@@
 
+\todo[inline]{The presentation could be structured a bit more (subheadings,
+paragraphs etc), as it is, it is quite a long flow of text and numbers -> check
+instructions at scientific data}
+
+\todo[inline]{SE: imo, key question is only partially answered: how close is
+movie / audio to localizer". Can you corroborate figure 3 with some more
+numbers? COH: schwierig vergleichbar (insb. unterschiedliche thresholds), daher
+Bland-Altman-Plots -> mention that point at BA-Plots}
+
 % study goal
@@
 
+\todo[inline]{"a visual but ecologically more valid stimulation" -> The "but"
+doesn't make sense to me here -> add phrasing similar to the one used in the
+(rephrased) intro}
 % AV intro
@@
 cortex.
+\todo[inline]{SE: What to make out of the fact that the movie stimulation seems
+to evoke activation that goes substantially further caudal than the classical
+PPA? COH: part of the discussion; maybe a concluding statement here}
 
@@
 % advances the field by providing new opportunities
+
+\todo[inline]{jeweils mit dem Befund, den Du diskutieren willst beginnen und mit
+einer take-home message enden.}
+
+\todo[inline]{Was mich etwas wundert, es gibt
+doch schon andere "event-related" analysen von movies, oder? Die werden kaum
+diskutiert. -> Studie, die etwas mit Event-related design zitieren;
+NeuroScout-Framework oder. Pliers Studien zitieren}
+
+\todo[inline]{Ebenso kommt mir das Potential (warum ist das relevant -> rich
+stimulus ie many possible analyses, better compliance, easier to perform for
+difficult populations, etc) eigentlich zu kurz}
 

### 2021-02-24 paper/main.tex
try to make "Hemodynamic Modeling" (2.7) easier to understand

@@
 in the AV-movie are relevant in the current context; COH: imo that is more
-important in context of the contrasts (-> check if it is sufficiently described
-there); might fit in here, too, but makes current part unnessecarily
-complicated}
+important in context of the contrasts; in any case: "cinematographic rationale" is now mentioned first,
+then the categories are listed}
 
@@
 \begin{table*}[tbp]
-    \caption{Overview of annotated stimulus features of the audio-visual
+    \caption{Overview of event categories of the audio-visual
     movie and the audio-description.
+    Event categories of the movie are based on an annotation of cuts and
+    depicted locations.
+    Event categories of the audio-description based on an annotation of speech.
     Some of the audio-description's event categories listed here
@@
 % AV design matrix
-The design matrices of the first-level time-series GLM analysis comprised the
-regressors for the stimulus features listed in Tables~\ref{tab:events} and
-\ref{tab:events} for the movie and audio-description stimulus, respectively.
+The design matrix for the first-level time-series GLM analysis of the movie
+comprised regressors for the 12 event categories of the movie listed in
+Table~\ref{tab:events}.
+% AD design matrix
+Similarly, the design matrix for the analysis of the audio-description comprised
+regressors for the 13 event categories of the audio-description, also listed in
+Table~\ref{tab:events}.
 % AD regressors in AV
-Additionally, the design for the movie stimulus also contained the
-regressors based on nouns used by the audio-description's narrator to indicate
-a switch to another setting (categories \texttt{se\_new} and \texttt{se\_old}),
-in order to be able to implement cross-modal control contrasts.
+In order to implement cross-modal control contrasts, the design matrix for the
+movie stimulus also contained the regressors based on nouns used by the
+audio-description's narrator to indicate a switch to another setting (categories
+\texttt{se\_new} and \texttt{se\_old}).
 % AV regressors in AV
-Likewise, the audio-description design matrix included movie cut related regressors
-listed Table~\ref{tab:events} (excluding \texttt{no\_cut}).
+Likewise, the design matrix for the audio-description included the five movie
+cut related regressors (\texttt{vse\_new}, \texttt{vse\_old}, \texttt{vlo\_ch},
+\texttt{vp\_new}, \texttt{vpe\_old}).
 % both stimuli: null regressors
 For both stimuli, a null regressor was used for any event category in a segment
-for which no event of a category was present (e.g. no event of
-\texttt{vpe\_old} in segment 3; Tab.~\ref{tab:events}).
+for which no event of a category was present (e.g. no event of \texttt{vpe\_old}
+in segment 3; Tab.~\ref{tab:events}).
 % temporal derivatives
-Temporal derivatives of all regressors were added to the design matrix to compensate for
-regional differences \citep{friston1998event}.
+Temporal derivatives of all regressors were added to the design matrix to
+compensate for regional differences \citep{friston1998event}.
 % motion parameters
-Lastly, six participant and run specific motion estimated (translation and rotation)
-were also included.
+Lastly, six participant and run specific motion estimated (translation and
+rotation) were also included.
 % high-pass filtering
-The design matrices were temporally filtered with the same high-pass filter (cutoff period of
-\unit[150]{s}) as the BOLD time series.
+The design matrices were temporally filtered with the same high-pass filter
+(cutoff period of \unit[150]{s}) as the BOLD time series.
 
 \subsection{Statistical analysis}
+
+\todo[inline]{SE: "vse, vno, vpe,..." are not really the most intuitive regressor names -> ausschreiben, wo möglich}
 
@@
 
-\todo[inline]{"vse, vno, vpe,..." are not really the most intuitive regressor
-names -> ausschreiben, wo möglich}
 % AV: primary contrast

### 2021-02-24 paper/main.tex
some changes to text regardings contrasts

@@
 
-\todo[inline]{add a summary to the end of section 2.7 explaining in 2 sentences,
-what regressors you will be focussing on -> easier for those that got confused
-on the way}
 % AV design matrix
@@
 
-\todo[inline]{SE: "vse, vno, vpe,..." are not really the most intuitive regressor names -> ausschreiben, wo möglich}
-
 % intro
@@
 
-\todo[inline]{"we, subjectively, picked a primary contrast" :-(  -> you actually
-write "based on"}
-%
+% there isn't "the one road"
 Given the rich naturalistic stimuli and the availability of various stimulus
@@
 identify hemodynamic activity congruent with the hypothesized processing of
-spatial information in the PPA. However, while the rationale for any contrast
-composition must be sound, the selection of a single implementation remains
-arbitrary to some degree. Consequently, we computed multiple contrasts that are
-listed in Table~\ref{tab:contrasts} for movie and audio-description,
-respectively. For each stimulus we, subjectively, picked a primary contrast for
-result presentation (the first one in each Table) based on how well the average
-event within categories represents spatial and non-spatial information, and the
-number of events in the stimulus.  An evaluation of the robustness of these
-results with respect to similar but different contrasts is provided in the
-supplementary materials.
+spatial information in the PPA.
+% kind of arbitrary choice
+However, while the rationale for any contrast composition must be sound, the
+selection of a single implementation remains arbitrary to some degree.
+% hence, a couple of contrasts
+Consequently, we computed multiple contrasts that are listed in
+Table~\ref{tab:contrasts} for movie and audio-description, respectively.
+% subjectively assessed balance
+For each stimulus, we picked a primary contrast for result presentation (the
+first one in each Table) based on a subjectively assessed balance of how well
+the average event within categories represents spatial and non-spatial
+information, and the number of events in the stimulus.
+% reference to supplementals
+An evaluation of the robustness of these results with respect to similar but
+different contrasts is provided in the supplementary materials.
 
@@
 \texttt{sex\_f}, \texttt{sex\_m}).
-
 % why furniture was not used
@@
 % control contrasts
-Finally, we created several control contrasts for both stimuli.
+Finally, we created several control contrasts for both stimuli
+(Tab.~\ref{tab:contrasts}).
 % AV: no cut > cut
 For the movie stimulus, four contrasts were created contrasting the no-cut
-regressor (\texttt{vno\_cut} to cut-related regressors \ref{tab:contrasts}).
+regressor (\texttt{vno\_cut}) to cut-related regressors.
 % AV: narrator
-One contrast (\texttt{vs\_new} > \texttt{vpe\_old}) was created by contrasting
-nouns spoken by the narrator.
+One contrast was created by contrasting nouns spoken by the (missing) narrator
+comparing nouns that indicate a switch to another setting (\texttt{se\_new} >
+\texttt{se\_old}), and were moderately correlated with movie cuts indicating a
+switch to another setting (Tab.~\ref{fig:reg-corr}).
 % AD stimulus
-For the audio-description stimulus, we created five control contrasts
-(Tab.~\ref{tab:contrasts}) to test if activation in the PPA was
-correlated with moments of cuts, despite the absence of visual stimulation.
+For the audio-description stimulus, we created five control contrasts to test if
+activation in the PPA was correlated with moments of cuts, despite the absence
+of visual stimulation.
+
+\todo[inline]{SE: "vse, vno, vpe,..." in Table 3 are not really the most
+intuitive regressor names; COH: writing out names will turn table into a mess;
+added reference to the Table that explains the abbreviations}
 
 \begin{table*}[tbp]
-  \caption{Computed contrasts for the analysis of the movie and the audio-description,
-    and their respective purpose. The primary contrasts are marked with an asterisk.
-    \texttt{non-spatial} refers to the annotation categories
+  \caption{Computed contrasts for the analysis of the movie and the audio
+    description, and their respective purpose.
+    The primary contrasts are marked with an asterisk.
+    \texttt{non-spatial} refers to the event categories
     \texttt{body}, \texttt{bodypart}, \texttt{fahead},
-    \texttt{object}, \texttt{sex\_f}, \texttt{sex\_m}.}
+    \texttt{object}, \texttt{sex\_f}, \texttt{sex\_m}.
+    An explanation of all event categories can be found in
+    Tab.~\ref{tab:events}.
+    }
 \label{tab:contrasts}

### 2021-02-24 paper/main.tex
what ever

@@
 \todo[inline]{SE: (lack of) exclusivity is not really becoming evident from
-preceding paragraph; COH: but imo the last two paragraphs are about exactly
+preceding paragraph; COH: imo the last two paragraphs are about exactly
 that??}
@@
 
-\todo[inline]{SE: temporal order of the (naturalistic) stimuli is not unknown,
-you know it by looking at the movie; COH: yes, but actually no.}
-
 % traditionally
@@
 % our approach: annotation and regressors
-naturalistic stimuli have fixed but initially unknown temporal structure
-of stimulus features of interest, as well as an equally unknown confound structure.
+naturalistic stimuli have fixed but initially unknown temporal structure of
+stimulus features of interest, as well as an equally unknown confound structure.
 % annotation ftw
@@
 structure of a range of stimulus features.
-
-In an earlier study, \cite{bartels2004mapping} manually annotated the content of
-individual movie frames (color, faces, language, and human bodies) and found
-that the functional specialization of brain areas is preserved during movie
-watching.
 
@@
 
-% alignments single subjects (for Bland-Altman-Plots) 1st level
-First-level GLM analyses were performed in the image-space of a participant-specific BOLD
-T2* template
+% alignments single subjects: 1st level
+First-level GLM analyses were performed in the image-space of a
+participant-specific BOLD T2* template using a previously determined linear
+transformation \citep{sengupta2016extension}.
 % subject template (for Bland-Altman-Plot of unthresholded maps)
 % \href{"https://github.com/psychoinformatics-de/studyforrest-data-templatetransforms/blob/master/sub-01/bold3Tp2/brain.nii.gz"}{example})
-using a previously determined linear transformation \citep{sengupta2016extension}.
-For higher-level analyses image data were aligned with a study-specific T2* group template
-likewise using a previously computed non-linear transformation \citep{hanke2014audiomovie}.
 % group template (for group and individual brain slices)
+For higher-level analyses image data were aligned with a study-specific T2*
+group template likewise using a previously computed non-linear transformation
+\citep{hanke2014audiomovie}.
 % https://github.com/psychoinformatics-de/studyforrest-data-templatetransforms/blob/master/templates/grpbold3Tp2/brain.nii.gz"
@@
 
-\todo[inline]{The presentation could be structured a bit more (subheadings,
-paragraphs etc), as it is, it is quite a long flow of text and numbers -> check
-instructions at scientific data}
-
-\todo[inline]{SE: imo, key question is only partially answered: how close is
-movie / audio to localizer". Can you corroborate figure 3 with some more
-numbers? COH: schwierig vergleichbar (insb. unterschiedliche thresholds), daher
-Bland-Altman-Plots -> mention that point at BA-Plots}
+\todo[inline]{SE: subheadings, paragraphs etc? COH: scientific data's analysis
+allows subheadings; added some}
 
@@
 % group level
-On a group average level, we compared results from whole-brain GLM
-analyses of the movie and the audio-description to a
-traditional visual localizer \citep{sengupta2016extension}.
+On a group average level, we compared results from whole-brain GLM analyses of
+the movie and the audio-description to a traditional visual localizer
+\citep{sengupta2016extension}.
 % individual level
-For each individual, we also compared the activation pattern from
-naturalistic auditory stimulation to the individual PPA localization
-with a block-design stimulus.
+For each individual, we also compared the activation pattern from naturalistic
+auditory stimulation to the individual PPA localization with a block-design
+stimulus.
 % NeuroVault
@@
 % reference to supplemental material
-Additional analyses of the robustness of the results presented here
-are available as supplementary materials.
-
-\todo[inline]{"a visual but ecologically more valid stimulation" -> The "but"
-doesn't make sense to me here -> add phrasing similar to the one used in the
-(rephrased) intro}
-% AV intro
-First, we analyzed data from the movie offering a visual but ecologically more
-valid stimulation than static pictures.
+Additional analyses of the robustness of the results presented here are
+available as supplementary materials.
+
+\subsection{group average results}
+
+\todo[inline]{SE: What to make out of the fact that the movie stimulation seems
+to evoke activation that goes substantially further caudal than the classical
+PPA? COH: part of the discussion; maybe a concluding statement here? imo it's
+good as it is}
+
+% av intro
+First, we analyzed data from the movie that offered ecologically more valid
+visual stimulation than a paradigm using blocks of pictures.
 % AV primary contrast
@@
 cortex.
-\todo[inline]{SE: What to make out of the fact that the movie stimulation seems
-to evoke activation that goes substantially further caudal than the classical
-PPA? COH: part of the discussion; maybe a concluding statement here}
 
 % AD intro
-Second, we analyzed data from the audio-description offering exclusively
+Second, we analyzed data from the audio-description offering an exclusively
 auditory stimulation.
@@
 % overlap with ROI
-Two bilateral clusters are located in the anterior part of the PPA group
-overlap reported by \cite{sengupta2016extension}.
+Two bilateral clusters are located in the anterior part of the PPA group overlap
+reported by \cite{sengupta2016extension}.
 % in detail
@@
 
+\subsection{individual results}
+
 % results in detail voxels of significant clusters in PPA ROI (and RSC
@@
 % Sengupta et al., 2016; unilateral in sub-04 and sub-20
-bilateral parahippocampal clusters in 12 of 14
-participants and unilateral right clusters in two participants
-\citep[Tab.~3 in][]{sengupta2016extension}.
+bilateral parahippocampal clusters in 12 of 14 participants and unilateral right
+clusters in two participants \citep[Tab.~3 in][]{sengupta2016extension}.
 % one contrast to localize them all; "...and $Z$>3.4 for all"
 Unlike \cite{sengupta2016extension}, who determined PPA clusters using three
-candidate contrasts and a variable threshold, we used a single contrast for
-each naturalistic stimulus and a uniform threshold for all participants.
+candidate contrasts and a variable threshold, we used a single contrast for each
+naturalistic stimulus and a uniform threshold for all participants.
 % ref to figure
-Figure~\ref{fig:subs-thresh-ppa} depicts thresholded $Z$-maps of the primary movie
-and audio-description $t$-contrasts, in comparison to the results of a conventional
-block-design localizer (unthresholded $Z$-maps are provided on NeuroVault).
+Figure~\ref{fig:subs-thresh-ppa} depicts thresholded $Z$-maps of the primary
+movie and audio-description $t$-contrasts, in comparison to the results of a
+conventional block-design localizer (unthresholded $Z$-maps are provided on
+NeuroVault).
 % AV
-Results of the primary movie contrast yielded bilateral clusters in five participants,
-a unilateral right cluster in six participants (of which one participant yielded a
-unilateral cluster in the visual localizer), and a unilateral left cluster in
-one participant.
+Results of the primary movie contrast yielded bilateral clusters in five
+participants, a unilateral right cluster in six participants (of which one
+participant yielded a unilateral cluster in the visual localizer), and a
+unilateral left cluster in one participant.
 % difference to dedicated localizer
-We find bilateral clusters for participant \texttt{sub-20}, whereas the block-design
-localizer yielded only one cluster in the right hemisphere.
+We find bilateral clusters for participant \texttt{sub-20}, whereas the
+block-design localizer yielded only one cluster in the right hemisphere.
 % report here in group
-Results of the primary audio-description contrast yielded bilateral clusters in nine participants that are within or overlapping with the block-design localizer results.
+Results of the primary audio-description contrast yielded bilateral clusters in
+nine participants that are within or overlapping with the block-design localizer
+results.
 % subj-04
@@
 % sub-09
-For another participant (\texttt{sub-09}) the analysis yielded one cluster in the
-left-hemispheric PPA.
+For another participant (\texttt{sub-09}) the analysis yielded one cluster in
+the left-hemispheric PPA.
 
@@
 
+\todo[inline]{SE: imo, key question is only partially answered: how close is
+movie / audio to localizer". Can you corroborate figure 3 with some more
+numbers? COH: schwierig vergleichbar (insb. unterschiedliche thresholds), daher
+Bland-Altman-Plots -> as kinda mentioned in following paragraph}
+
 % Bland-Altman-Plots
@@
 % what it depicts
-Each subplot visualizes the mean value and difference (localizer minus audio-description) of all voxels in temporal and occipital cortices. The marginal distributions
-of the mean scores indicate a general agreement of both contrast scores across
-voxels in the PPA localization overlap as a probabilistic indicator (blue), and the
-individual block-design localizer results (red). Notably, 11 participants exhibit
-a pattern of increased $Z$-scores for the naturalistic stimulus (lower right
-quadrant) that includes voxels labeled by the block-design localizer, but
-also additional voxels.
+Each subplot visualizes the mean value and difference (localizer minus
+audio-description) of all voxels in temporal and occipital cortices.
+% maringal distributions
+The marginal distributions of the mean scores indicate a general agreement of
+both contrast scores across voxels in the PPA localization overlap as a
+probabilistic indicator (blue), and the individual block-design localizer
+results (red).
+% lower right quadrant
+Notably, 11 participants exhibit a pattern of increased $Z$-scores for the
+naturalistic stimulus (lower right quadrant) that includes voxels labeled by the
+block-design localizer, but also additional voxels.
 
@@
 
-\todo[inline]{jeweils mit dem Befund, den Du diskutieren willst beginnen und mit
-einer take-home message enden.}
-
-\todo[inline]{Was mich etwas wundert, es gibt
-doch schon andere "event-related" analysen von movies, oder? Die werden kaum
-diskutiert. -> Studie, die etwas mit Event-related design zitieren;
-NeuroScout-Framework oder. Pliers Studien zitieren}
-
-\todo[inline]{Ebenso kommt mir das Potential (warum ist das relevant -> rich
-stimulus ie many possible analyses, better compliance, easier to perform for
-difficult populations, etc) eigentlich zu kurz}
+\todo[inline]{SE: mit Befund, den Du diskutieren willst beginnen, mit take-home
+message enden. COH: bekomme ich nur (und auch nur evtl.) reingepresst, wenn ich
+die Discussion komplett umschreibe; take-home message ist aber eh fast überall
+drin}
+
+\todo[inline]{SE: es gibt schon andere "event-related" analysen von movies,
+oder? COH: habe Paper durchgeguckt: Es gibt wenig bis gar nichts (obwohl
+Annotation immer mehr automatisiert werden können); Bzgl. Narrative ist im
+Grunde alles "voxel-wise enconding"; Rocca benutzt Annotation, aber auch
+"crafted" 23-min Narrative; NeuroScout: bisher absolut (?) keine veröffentlichte
+Studie, die NeuroScout genutzt hat; -> Bartels ist Klassiker, steht aber enorm
+allein da, und macht aber genau das, was wir machen "Naturalistic Stimulus statt
+Traditionell"; insofern: es gibt schon "irgendwie" andere Studien, die etwas mit
+Annotation (von Filmen) gemacht haben, die machen aber dann halt auch ganz
+anderes Zeug}
 
@@
 
-%#3
-% hypo
-We hypothesized that due to the complex nature of the stimuli,
-unrelated factors would be balanced across a large number of events, and make
-the bias of spatial information accessible to a convential model-based
-statistical analysis of BOLD fMRI data.
+%#3 hypo
+We hypothesized that due to the complex nature of the stimuli, unrelated factors
+would be balanced across a large number of events, and make the bias of spatial
+information accessible to a convential model-based statistical analysis of BOLD
+fMRI data.
 % we need a detailed description -> annotation
-This model-driven approach required a detailed annotation of the
-occurence of relevant stimulus features.
+This model-driven approach required a detailed annotation of the occurence of
+relevant stimulus features.
 % event counts ftw
-The annotation of both stimuli revealed the respective number of incidentally occurring
-events to be similar to those of a conventional experimental paradigm used to
-localize functional regions of interest.
+The annotation of both stimuli revealed the respective number of incidentally
+occurring events to be similar to those of a conventional experimental paradigm
+used to localize functional regions of interest.
 
@@
 right cluster in two participants (\texttt{sub-04}, \texttt{sub-20}).
-\todo[inline]{es wird jetzt lediglich in den results erwähnt, dass Sengupta
-einen von dreien benutzt hat}
+
 %#11 question
@@
 
-%#7
-% previous studies: no task
-It is common for conventional localizer paradigms to
-employ a task to keep participants attentive to the stimuli.
+%#7 previous studies: no task
+It is common for conventional localizer paradigms to employ a task to keep
+participants attentive to the stimuli.
 % but: Epstein (1998)
@@
 % we have no task neither
-The naturalistic stimulation paradigm employed here is similar in the sense that participants had no behavioral or
-cognitive task \cite[e.g., forming a mental image of the stimuli;][]{ocraven2000mental} but just had to ``enjoy the presentation''.
+The naturalistic stimulation paradigm employed here is similar in the sense that
+participants had no behavioral or cognitive task \cite[e.g., forming a mental
+image of the stimuli;][]{ocraven2000mental} but just had to ``enjoy the
+presentation''.
 % but still: we are different
 Nevertheless, the naturalistic paradigm differs from \cite{epstein1998ppa},
-because the relevant stimulus features were embedded in a continuous stream of complex
-auditory (and visual) information which makes it unlikely that participants
-speculated on the purpose of the investigation, or performed undesired and unknown evaluation or categorization of isolated stimuli.
+because the relevant stimulus features were embedded in a continuous stream of
+complex auditory (and visual) information which makes it unlikely that
+participants speculated on the purpose of the investigation, or performed
+undesired and unknown evaluation or categorization of isolated stimuli.
 % concluding statement: kinda automatic process
-Our results therefore indicate that verbally communicated spatial information
-is processed, in the anterior PPA, automatically and without specifically
-guided attention.
+Our results therefore indicate that verbally communicated spatial information is
+processed, in the anterior PPA, automatically and without specifically guided
+attention.
 
@@
 %#2
-Our approach to stimulus annotation and event selection
-differs from previous reports in the literature.
+Our approach to stimulus annotation and event selection differs from previous
+reports in the literature.
 % PPA: intro
@@
 % results
-The group results of the movie stimulus' primary contrast yielded a large cluster
-that spans the group overlap of individual PPA ROIs from anterior to posterior.
+The group results of the movie stimulus' primary contrast yielded a large
+cluster that spans the group overlap of individual PPA ROIs from anterior to
+posterior.
 % confound of higher perception
-The cluster's extent into more posterior, earlier visual areas could be
-an indication that the temporal averaging across events suffered from
-insufficient controlling for confounding visual features.
+The cluster's extent into more posterior, earlier visual areas could be an
+indication that the temporal averaging across events suffered from insufficient
+controlling for confounding visual features.
 % solution
@@
 
-%#12
-% RSC + LOC
-Apart from the PPA, results show significantly increased activity in the
-dorsal precuneus and posterior cingulate region (e.g. retrosplenial complex;
-RSC) and lateral occipital cortex (LOC; more lateral in the movie stimulus, more
-medial in the audio-description stimulus) for both naturalistic stimuli.
+%#12 RSC + LOC
+Apart from the PPA, results show significantly increased activity in the dorsal
+precuneus and posterior cingulate region (e.g. retrosplenial complex; RSC) and
+lateral occipital cortex (LOC; more lateral in the movie stimulus, more medial
+in the audio-description stimulus) for both naturalistic stimuli.
 % RSC intro
-Like the PPA, the RSC and LOC repeatedly exhibited increased hemodynamic activity
-in studies investigating visual spatial perception or navigation (see
-
+Like the PPA, the RSC and LOC repeatedly exhibited increased hemodynamic
+activity in studies investigating visual spatial perception or navigation (see
+\citep{chrastil2018heterogeneity, bettencourt2013role} for reviews)
 % not random shit
-Thus, our model-driven approach to operationalize spatial perception based on stimulus
-annotations reveals focussed activation patterns in networks that are implicated
-in visual spatial perception and cognition.
+Thus, our model-driven approach to operationalize spatial perception based on
+stimulus annotations reveals focussed activation patterns in networks that are
+implicated in visual spatial perception and cognition.
 
@@
 
+\todo[inline]{mir das Potential (warum ist das relevant -> rich stimulus ie many
+possible analyses, better compliance, easier to perform for difficult
+populations, etc) eigentlich zu kurz}
+
 \subsection*{Data and code availability}

### 2021-02-25 paper/main.tex
add Epstein (2019) review to references

@@
 activity in studies investigating visual spatial perception or navigation (see
-\citep{chrastil2018heterogeneity, bettencourt2013role} for reviews)
+\citep{chrastil2018heterogeneity, bettencourt2013role, epstein2019scene} for
+reviews)
 % not random shit
@@
 
-\todo[inline]{mir das Potential (warum ist das relevant -> rich stimulus ie many
-possible analyses, better compliance, easier to perform for difficult
-populations, etc) eigentlich zu kurz}
+\todo[inline]{SE: mir das Potential (warum ist das relevant -> rich stimulus ie
+many possible analyses, better compliance, easier to perform for difficult
+populations, etc) eigentlich zu kurz; COH: finde ich (insb. als allerletzten)
+Satz in einem Satz so okay, weil a) Textlimit, b) exploratory \& <80 \%
+lokalisationsleistung; wenn, dann müsste man ein größeres Fass in Intro und
+Discussion aufmachen, was die Ergebnisse aber nicht hergeben }
 

### 2021-02-26 paper/main.tex
add Lescroart (2019), Pitcher (2019)
delete Pitcher (2019), shift Lescroart (2019) to discussion

@@
         current phrasing
+    \item Lescroart is just a small footnote in pPPA vs. aPPA in discussion
+        (problem to write more about the paper: it is voxel-wise encoding which
+        does not tell a lot about increased vs. decreased activation; "crafted"
+        stimuli: 45 min of 850 scenes, made from 33 backgrounds + 2-3 objects
+        drawn from pool of 440 objects}
     \item maybe "do something with" dice-index
@@
 
-\todo[inline]{Lescroart \& Gallant (2019). semi-naturalistic, but task, 800+ stimulus, N=6}
-
 % literature review overview: imagination & haptic exploration; van der Hurk: 64
@@
 First, they employed a small sets of carefully chosen and conceptualized
-stimuli.
+stimuli (formore recent example using a bigger set or moving stimuli see
+\citep{lescroart2019human, pitcher2019functional}
 % block-design & task
@@
 % AD annotation
-For the analysis of the audio-description stimulus, we extended a publicly available annotation
-of its speech content \citep{hausler2021studyforrest} by classifying
-concrete and countable nouns that the narrator uses to describe the movie's absent visual content.
+For the analysis of the audio-description stimulus, we extended a publicly
+available annotation of its speech content \citep{hausler2021studyforrest} by
+classifying concrete and countable nouns that the narrator uses to describe the
+movie's absent visual content.
 % annotation procedure
@@
 % reference to table with rules and examples
-A complete overview of all 18 noun categories, their inclusion criteria, and examples
-can be seen in Table~\ref{tab:descr-nouns-rules}.
+A complete overview of all 18 noun categories, their inclusion criteria, and
+examples can be seen in Table~\ref{tab:descr-nouns-rules}.
 % why and how of categories 1
@@
 disco'', ``[the platoon wades through a] rice field''). They also comprise words
-that could count as a member of another category in case the narrator uses
-these words to indicate a switch from one setting to another (e.g. ``[a]
-physician'').
+that could count as a member of another category in case the narrator uses these
+words to indicate a switch from one setting to another (e.g. ``[a] physician'').
 % how it was handled
@@
 Some noun categories that were semantically similar and offered only a small
-amount of counts were pooled resulting in 11 final event categories (Tab.~\ref{tab:events}).
-These event categories were then used to model hemodynamic
-responses.
+amount of counts were pooled resulting in 11 final event categories
+(Tab.~\ref{tab:events}).  These event categories were then used to model
+hemodynamic responses.
 
@@
 (aPPA) to low-level features of scenes or (abstract) objects
-\citep{baldassano2013differential, nasr2014thinking,
+\citep{baldassano2013differential, lescroart2019human, nasr2014thinking,
 rajimehr2011parahippocampal}.
@@
 order to test XYZ.
-\todo{why exactly did we do this except "we do not expect (lots of) significant cluster because negative control?}
+
+\todo{why exactly did we do this except "we do not expect (lots of) significant
+cluster because negative control?}
 %
@@
 Contrast 12 (\texttt{vse\_new} > \texttt{vse\_old}, \texttt{vpe\_old}) revealed
-one cluster in the right posterior hippocampus.
-\todo{explanation?}
+one cluster in the right posterior hippocampus.  \todo{explanation?}
 %
 Overall results from the negative control contrast of the audio-description's
-data suggest that XYZ.
-\todo{concluding statement}.
+data suggest that XYZ.  \todo{concluding statement}.
 

### 2021-02-26 paper/main.tex
typos

@@
         stimuli: 45 min of 850 scenes, made from 33 backgrounds + 2-3 objects
-        drawn from pool of 440 objects}
+        drawn from pool of 440 objects
     \item maybe "do something with" dice-index
@@
 to unify domains via contextual information hypothesis which is not mentioned at
-all here}
+all here; dunno if it smart to cite her here}
 
@@
 First, they employed a small sets of carefully chosen and conceptualized
-stimuli (formore recent example using a bigger set or moving stimuli see
-\citep{lescroart2019human, pitcher2019functional}
+stimuli.
 % block-design & task

### 2021-02-26 paper/main.tex
check comments/feedback from Simon considered

@@
 
-\todo[inline]{but: Aminoff (2013) also reviews episodic memory function \& tries
-to unify domains via contextual information hypothesis which is not mentioned at
-all here; dunno if it smart to cite her here}
+\todo[inline]{dunno if it is smart to cite Aminoff (2013) here because she also
+reviews PPA + episodic memory function \& tries to unify domains via contextual
+information hypothesis which is not mentioned here at all}
 
@@
 \todo[inline]{SE: (lack of) exclusivity is not really becoming evident from
-preceding paragraph; COH: imo the last two paragraphs are about exactly
-that??}
+preceding paragraph; COH: imo last two paragraphs are about exactly that??}
 % summary if literature review
@@
 
-\todo[inline]{other studies that localize PPA: essentially every study that does
-something "PPA-related" does it and does it using pictures; there are two
-studies that evaluate the localization as such and both give "pretty" results:}
-
-\todo[inline]{onlinelibrary.wiley.com/doi/full/10.1002/hbm.20116 -> 6 subjects;
-6x bilateral clusters}
-
-\todo[inline]{academic.oup.com/cercor/article/16/10/1453/353981 -> 12 subjs: 12x
-bilateral clusters}
+\todo[inline]{I searched fot other studies that localize PPA: essentially every
+study that does something "PPA-related" does separate localizer (using pictures
+of course); but: there are two studies that evaluate localization using pictures
+as such; both gave "pretty" results:}
+
+\todo[inline]{Peelen \& Downing (2005): 6 subjects, 6x bilateral clusters
+(onlinelibrary.wiley.com/doi/full/10.1002/hbm.20116)}
+
+\todo[inline]{Downing, Peelen \& Kanwisher (2006): 12 subjects, 12x bilateral
+clusters (academic.oup.com/cercor/article/16/10/1453/353981)}
 
@@
 \todo[inline]{I think you need to help the reader understand, what annotations
-in the AV-movie are relevant in the current context; COH: imo that is more
-important in context of the contrasts; in any case: "cinematographic rationale" is now mentioned first,
-then the categories are listed}
+in the AV-movie are relevant in the current context; COH: revised the section a
+little. most importantly the "cinematographic rationale" is explained first and
+is then followed by the categories; imo annotations are more important in
+section "contrasts"}
 
@@
     depicted locations.
-    Event categories of the audio-description based on an annotation of speech.
+    Event categories of the audio-description based on an annotation of nouns
+    spoken by the audio-description's narrator
+    (Tab.~\ref{tab:descr-nouns-rules}).
     Some of the audio-description's event categories listed here
@@
     were created by pooling some categories of the original annotation of nouns
-    (female, females, fname; male, males, mname; face, head; object, objects;
-    Tab.~\ref{tab:descr-nouns-rules}).
+    (female, females, fname; male, males, mname; face, head; object, objects).
     Respective event counts are given for the whole stimulus (\texttt{All} and
@@
 belong exclusively to the higher-level category of changing a setting
-(\texttt{se\_new} or \texttt{se\_old}).
+(\texttt{setting\_new} or \texttt{setting\_rec}).
 % pooling of categories

### 2021-02-26 paper/main.tex
some cleaning & typos?

@@
 
-\todo[inline]{I searched fot other studies that localize PPA: essentially every
+\todo[inline]{I searched for other studies that localize PPA: essentially every
 study that does something "PPA-related" does separate localizer (using pictures
@@
 in the AV-movie are relevant in the current context; COH: revised the section a
-little. most importantly the "cinematographic rationale" is explained first and
+little. Most importantly the "cinematographic rationale" is explained first and
 is then followed by the categories; imo annotations are more important in
@@
 compute perceptual fingerprints for each movie frame using the pHash library
-\citep{zauner2010implementation} and recorded the cummulative bitwise
+\citep{zauner2010implementation} and recorded the cumulative bitwise
 difference to the previous frame.
@@
 would be balanced across a large number of events, and make the bias of spatial
-information accessible to a convential model-based statistical analysis of BOLD
+information accessible to a conventional model-based statistical analysis of BOLD
 fMRI data.
 % we need a detailed description -> annotation
-This model-driven approach required a detailed annotation of the occurence of
+This model-driven approach required a detailed annotation of the occurrence of
 relevant stimulus features.
@@
 Activity in the aPPA, on the other hand, is found to be correlated with
-components of the default mode network, including caudal inferior parietal lobe
-(cIPL), the restrosplenial complex (RSC), medial PFC and the lateral surface of
+components of the default mode network, including caudal inferior parietal lobe,
+retrosplenial complex, medial prefrontal cortex, and lateral surface of
 the anterior temporal lobe \citep{baldassano2013differential,
-baldassano2016two}.
+baldassano2016two}.\todo{last half sentence is almost a direct quote;
+plagiarism?}
 % conclusion: subregions
@@
 % confound of higher perception
-The cluster's extent into more posterior, earlier visual areas could be an
+The cluster extends into more posterior, earlier visual areas could be an
 indication that the temporal averaging across events suffered from insufficient
@@
 Results of the movie also yielded significant clusters in the ventral precuneal
-cortex and posterior cingulate gyrus (i.e. restrosplenial complex; contrasts 1,
+cortex and posterior cingulate gyrus (i.e. retrosplenial complex; contrasts 1,
 4, 5), and lateral occipital cortex (contrasts 1, 2, 4, 5).
@@
 Given that cuts to a setting depicted for the first time (\texttt{vse\_new}) and
-nouns indicating a a switch to a setting ocurring for the first timei
+nouns indicating a a switch to a setting occurring for the first time
 (\texttt{se\_new}), and cuts to a recurringly depicted setting
@@
 %
-Two of five contrasts yielded signficant clusters.
+Two of five contrasts yielded significant clusters.
 % contrast 9

### 2021-02-26 paper/main.tex

@@
 In order to test the robustness of our approach, we created overall five
-$t$-contrasts for the movie stimulus, and overall
-eight $t$-contrast for the audio-description stimulus
-(Tab.~\ref{tab:contrasts}).
+$t$-contrasts for the movie stimulus, and overall eight $t$-contrast for the
+audio-description (Tab.~\ref{tab:contrasts}).
 % how
-Contrasts differ in contrasted categeories based on ``how well'' averaged events
+Contrasts differ in contrasted categories based on ``how well'' averaged events
 within categories were considered to represent spatial and non-spatial
@@
 Unthresholded $Z$-maps of all contrasts on a group level co-registered to the
-group-template (MNI152 space) can found at NeuroVault
-\href{https://neurovault.org/collections/KADGMGVZ/}{\url{neurovault.org/collections/KADGMGVZNeuroVault}}.
+group-template (MNI152 space) can found at
+\href{https://neurovault.org/collections/KADGMGVZ/}{\url{neurovault.org/collections/KADGMGVZ}}.
 
@@
 % AV: RSC & LOC
-Results of the movie also yielded significant clusters in the ventral precuneal
-cortex and posterior cingulate gyrus (i.e. retrosplenial complex; contrasts 1,
-4, 5), and lateral occipital cortex (contrasts 1, 2, 4, 5).
+Several contrasts of the movie also yielded bilaterally significant clusters in
+the ventral precuneal cortex and posterior cingulate gyrus (i.e. retrosplenial
+complex; contrasts 1, 4, 5), and lateral occipital cortex (contrasts 1, 2, 4,
+5).
 
@@
 In results from the analysis of the audio-description, all contrasts except
-contrast 7 (\texttt{se\_new}, \texttt{se\_old} > non-spatial categories) and
-contrast 8 (\texttt{se\_new} > non-spatial categories) yielded significant
-bilateral clusters in anterior regions of the group PPA overlap
-(Fig.~\ref{fig:stability-slices}).
+contrast 7 and 8  yielded significant bilateral clusters in anterior regions of
+the group PPA overlap (Fig.~\ref{fig:stability-slices}).
 % AD: RSC & LOC
-Results from the analysis of the audio-description also yielded bilaterally
-significant clusters in the ventral precuneus (all contrasts except contrasts 8)
-and lateral occipital cortex (bilateral in contrasts 1 to 4; unilateral in
-contrasts 6 and 7).
+Contrasts of the audio-description also yielded bilaterally significant clusters
+in the ventral precuneus (all contrasts except contrasts 8) and lateral
+occipital cortex (bilateral in contrasts 1 to 4; unilateral in contrasts 6 and
+7).
 % concluding stament regarding PPA, RSC, and LOC
-The results across the contrasts of the movie and audio-description indicate
-that our findings regarding the PPA but also RSC and LOC are robust and do not
-depend on the design of one specific contrasts.
+Results across contrasts of both naturalistic stimuli indicate that our findings
+regarding the PPA but also RSC and LOC are robust and do not depend on the
+design of one specific contrasts.
 % but:
@@
 % example
-For example, contrast 8 of the audio-description stimulus (\texttt{se\_new} >
-\texttt{se\_old}) that used the most heterogeneous categories comprising the
-least amount of events yielded neither a significant cluster in the
-right-hemispheric nor left-hemispheric PPA.
+For example, contrast 7 and 8 (\texttt{se\_new}, \texttt{se\_old} > non-spatial
+categories, and \texttt{se\_new} > non-spatial categories) that used the most
+heterogeneous categories (nouns indicating switches to other settings) and a low
+amount of events yielded neither a significant cluster in the right-hemispheric
+nor left-hemispheric PPA.
 % concluding statement

### 2021-02-26 paper/main.tex
revision of supplementals mess v2

@@
 7 & \texttt{se\_new, se\_old > non-spatial} & spatial processing \tabularnewline
-8 & \texttt{se\_new > se\_old > non-spatial} & spatial processing \tabularnewline
+8 & \texttt{se\_new > se\_old} & spatial processing \tabularnewline
 9 & \texttt{vse\_new > vpe\_old} & control (absent visual cuts) \tabularnewline
@@
 
-\todo[inline]{print contrasts; count per category? -> pattern "average of
-events" and counts vs. significant clusters?}
+\todo[inline]{remove subheadings}
+
+\todo[inline]{introductory \& concluding sentences}
 
@@
 
-Further, some contrasts yielded bilaterally significant clusters in superior
-temporal cortices (contrasts 3, 6, 7) and one contrast a unilateral right
-cluster (contrast 2).
+Several contrasts yielded significant clusters in superior temporal cortices
+(bilateral in contrasts 3, 6, 7; unilateral right in contrast 2).
 % AD: auditory cortices
-Thus, increased hemodynamic activity in the superior temporal cortex is apparent
-in that compare verbal hints of the change of a setting (\texttt{se\_new} or
-\texttt{se\_old}) to all non-spatial categories (cf. contrasts 2, 3, 6, 7) show
-clusters in (primary and secondary) auditory cortices.
-% soundscape
-Activity in such clusters could be correlated with a possible change of the
-soundscape when the narrator of the audio-description, corresponding to a cut in
-the movie, switches udio-description stimulusto a another setting.
+Further, contrasts that compare, possibly among others, nouns indicating a
+switch to another setting (categories \texttt{se\_new} or \texttt{se\_old}) to
+non-spatial categories yielded significant clusters in superior temporal
+cortices (bilateral: contrasts 3, 6, 7; unilateral right: contrast 2).
 % interpretation 1
@@
 % interpretation 2
-Increased hemodynamic activity in superior temporal cortices suggest a bias
-towards lower-level auditory perceptual processes on the positive side of the
-GLM contrasts.
+Another possibility might be that increased hemodynamic activity in superior
+temporal cortices reflect a bias towards lower-level auditory perceptual
+processes on the positive side of the GLM contrasts.
+% soundscape
+Increased activity in primary and secondary auditory cortices could be
+attributed to changes in the soundscape that possibly accompany the narrator
+when he is indicating the switch to another setting by describing its identity
+or layout.\todo{speculative though}
+% concluding statement
+\todo[inline]{concluding statement?}
 

### 2021-02-26 paper/main.tex
revision of supplementals mess v3

@@
 %
-Lastly, some contrasts of the audio-description stimulus yielded significant
-clusters in regions that were not statistically significant in three or more
-contrasts.
-% details
+Lastly, contrasts of the audio-description stimulus yielded significant clusters
+in regions that were statistically in two or less contrasts.
+% contrast 2
 In detail, contrast 2 yielded clusters in the anterior cingulate gyrus
 (bilateral), right frontal pole, right frontal medial cortex, and right putamen.
-%
+% contrast 3
 Contrast 3 shows clusters in the anterior cingulate gyrus (bilateral), left
 frontal pole, and left insular.
-%
+% contrast 6
+Contrast 6 shows one additional cluster in the right medial frontal cortex.
+% contrast 7
 Contrast 7 shows clusters in the left frontal pole and left frontal operculum,
 left insular.
-%
-Contrast 6 shows one additional cluster in the right medial frontal cortex.
-% concludion statement
+% concluding statement
 Here again, significantly increased activation beyond areas known to be involved
@@
 bias in the contrasts.
+%
+\todo[inline]{imo other interpretations would speculative / reverse inference;
+but "if would look closer I would probably find a super plausible reason why
+brain areas are more active"}
 
@@
 % intro
-For each contrast we created several control contrasts.
-% AV: no_cut > x
+For each naturalistic stimus, we created several control contrasts.
+% movie contrasts: not cut condition vs. cuts
 To test for XYZ\todo{yes, to test what?} within the movie fMRI data, we created
 four contrasts that compared hemodynamic activity during frames within movie
-shots (\texttt{no\_cut} category) with movie cut related categories (Tab.~\ref{tab:contrasts}).
-%
-None of these four contrasts yielded a significant cluster which suggest that
-XYZ\todo{concluding statement}.
+shots (\texttt{no\_cut} category) with movie cut related categories
+(Tab.~\ref{tab:contrasts}).
+% results
+None of these four contrasts yielded a significant cluster.
+%
+Null results of control contrasts comparing frames within movie shots to frames
+immediately after a cut suggest that XYZ.
+%
+\todo[inline]{concluding statement}
 
@@
 % \texttt{vse\_old}.
-Given that cuts to a setting depicted for the first time (\texttt{vse\_new}) and
-nouns indicating a a switch to a setting occurring for the first time
-(\texttt{se\_new}), and cuts to a recurringly depicted setting
-({\texttt{vse\_old}) and nouns indicating a switch a recurring setting
-(\texttt{se\_old} turned out to be moderately correlated
-(Fig.~\ref{fig:reg-corr}), we created a contrast that used the
-audio-description's nouns on the movie data ({\texttt{se\_new} >
-\texttt{se\_old}).
+The inspection of correlations of regressors across stimuli
+(Fig.~\ref{fig:reg-corr}) showed a moderate correlation among cuts to a setting
+depicted for the first time (\texttt{vse\_new}) and nouns indicating a switch to
+a setting occurring for the first time (\texttt{se\_new}), and cuts to a
+recurringly depicted setting ({\texttt{vse\_old}) and nouns indicating a switch
+a recurring setting (\texttt{se\_old}.
+%
+Hence, we created a contrast that used the audio-description's nouns on the
+movie data ({\texttt{se\_new} > \texttt{se\_old}).
 % results
@@
 Results suggest that XYZ.
-\todo{concluding statement}
+%
+\todo[inline]{concluding statement? That last contrast was originally done to
+check that "soundscape at moment of cuts thing" but this is obsolete now}
+
+\todo{following: control contrast for AO; why exactly did we do this except "we
+do not expect (lots of) significant cluster because negative control?}
 
@@
 order to test XYZ.
-
-\todo{why exactly did we do this except "we do not expect (lots of) significant
-cluster because negative control?}
-%
+% results
 Two of five contrasts yielded significant clusters.
@@
 Overall results from the negative control contrast of the audio-description's
-data suggest that XYZ.  \todo{concluding statement}.
+data suggest that XYZ.
+%
+\todo[inline]{concluding statement?}.
 

### 2021-02-26 paper/main.tex
typos

@@
 % ---------- AV control contrasts ----------
-% 6 nothing 7 nothing 8 nothing 9 nothing
-%10 se_new > se_old (nouns but in AV stimulus): LOC (l/r) right PPA, bilateral
-%sup. lat. occ. c., sup. parietal lobe (right)
+% 6: nothing; 7 nothing; 8: nothing; 9: nothing; 10 se_new > se_old (nouns but
+% in AV stimulus): LOC (l/r) right PPA, bilateral, sup. lat. occ. c., sup.
+% parietal lobe (right)
 
@@
 % intro
-For each naturalistic stimus, we created several control contrasts.
+For each naturalistic stimulus, we created several control contrasts.
 % movie contrasts: not cut condition vs. cuts
@@
 % results
-The contrasts yielded a significant cluster in the right PPA and bilateral
-clusters in the superior lateral occipital cortices (the right hemispheric
-cluster extending into the superior parietal cortex).
+The contrasts yielded a significant cluster in the right [but not anterior] PPA
+and bilateral clusters in the superior lateral occipital cortices (the right
+hemispheric cluster extending into the superior parietal cortex).
 %
@@
 Contrast 12 (\texttt{vse\_new} > \texttt{vse\_old}, \texttt{vpe\_old}) revealed
-one cluster in the right posterior hippocampus.  \todo{explanation?}
+one cluster in the right posterior hippocampus.  \todo{not PPA! explanation?}
 %

### 2021-02-28 paper/main.tex
add comment regarding Fig S1
some typos

@@
 We applied model-based, mass-univariate analyses to a series of datasets with
-BOLD fMRI data from naturalistic and conventional block-design stimulation from
+BOLD fMRI data from naturalistic and conventional block-design stimulation of
 the same set of participants, available from the open-data resource
@@
 % our approach: annotation and regressors
-naturalistic stimuli have fixed but initially unknown temporal structure of
+naturalistic stimuli have a fixed but initially unknown temporal structure of
 stimulus features of interest, as well as an equally unknown confound structure.
@@
 In order to evaluate the suitability of the stimulus for the targeted analyses,
-and well as to inform the required hemodynamic models, we annotated the temporal
+and to inform the required hemodynamic models, we annotated the temporal
 structure of a range of stimulus features.
@@
 % we focus on cuts
-Contrary to manually annotating stimulus features of every movie frame (as
+Contrary to manually annotating stimulus features of movie frames (as
 performed by e.g. \cite{bartels2004mapping} for color, faces, language, and
@@
 3) a cut switching to another locale within a setting (\texttt{vlo\_ch}; e.g. a
-cut from first to the second floor in Forrest's house),
+cut from the first to the second floor in Forrest's house),
 %
@@
     depicted locations.
-    Event categories of the audio-description based on an annotation of nouns
-    spoken by the audio-description's narrator
+    Event categories of the audio-description are based on an annotation of
+    nouns spoken by the audio-description's narrator
     (Tab.~\ref{tab:descr-nouns-rules}).
@@
     (female, females, fname; male, males, mname; face, head; object, objects).
-    Respective event counts are given for the whole stimulus (\texttt{All} and
-    the segments that were used for the eight sessions of fMRI scanning).
+    Respective event counts are given for the whole stimulus (\texttt{All}) and
+    the segments that were used for the eight sessions of fMRI scanning.
     Event counts for frame-based features are reported in units of a thousand.
@@
 % \texttt{fg\_a(v|d)\_ger\_lrdiff}, r=.77)
-Maximum correlations are found for auditory low-level auditory confounds across
+Maximum correlations are found for low-level auditory confounds across
 stimuli,
@@
 % motion parameters
-Lastly, six participant and run specific motion estimated (translation and
+Lastly, six participant and run specific motion estimates (translation and
 rotation) were also included.
@@
 Consequently, we computed multiple contrasts that are listed in
-Table~\ref{tab:contrasts} for movie and audio-description, respectively.
+Table~\ref{tab:contrasts} for the movie and audio-description, respectively.
 % subjectively assessed balance
@@
 first one in each Table) based on a subjectively assessed balance of how well
-the average event within categories represents spatial and non-spatial
+the averaged events within categories represent spatial and non-spatial
 information, and the number of events in the stimulus.
@@
 first time (\texttt{se\_new}) or a setting that recurred during the plot
-(\texttt{se\_old}) were not included in the primary contrast because
+(\texttt{se\_old}) were not included in the primary contrast because they
+comprise
 % heterogeneous category
-a) they comprise nouns that could be a member of another category (e.g. ``[a]
+a)  nouns that could be a member of another category (e.g. ``[a]
 physician''), and
@@
 One contrast was created by contrasting nouns spoken by the (missing) narrator
-comparing nouns that indicate a switch to another setting (\texttt{se\_new} >
-\texttt{se\_old}), and were moderately correlated with movie cuts indicating a
+comparing nouns
+%
+that indicate a switch to another setting (\texttt{se\_new} >
+\texttt{se\_old}), and
+%
+that were moderately correlated with movie cuts indicating a
 switch to another setting (Tab.~\ref{fig:reg-corr}).
@@
     of the primary $t$-contrast for the audio-description comparing
-    geometry-related nouns to non geometry-related nouns spoken by the
+    geometry-related nouns to non-spatial nouns spoken by the
     audio-description's narrator (\texttt{geo, groom > all non-geo}), sorted by size.
@@
 movie and audio-description $t$-contrasts, in comparison to the results of a
-conventional block-design localizer (unthresholded $Z$-maps are provided on
+conventional block-design localizer (unthresholded $Z$-maps are provided at
 NeuroVault).
@@
 In an earlier study, \cite{bartels2004mapping} manually annotated the content of
-individual movie frames (color, faces, language, and human bodies) and found
-that the functional specialization of brain areas is preserved during movie
-watching.
+movie frames (color, faces, language, and human bodies) and found that the
+functional specialization of brain areas is preserved during movie watching.
 %
@@
 \href{http://www.studyforrest.org}{studyforrest.org} to operationalize the
-perception of spatial information embedded an audio-visual movie and an
+perception of spatial information embedded in an audio-visual movie and an
 auditory narrative, and compare current results to a previous report of a
@@
 The current study offers evidence that a model-driven GLM analysis based on
-annotations can be applied to naturalistic paradigm to localize concise
+annotations can be applied to a naturalistic paradigm to localize concise
 functional areas and networks correlating with specific perceptual processes.
@@
 % interpretation: aPPA vs. pPPA
-Further, our results provide further evidence that the PPA can be divided into
+Our results provide further evidence that the PPA can be divided into
 functional subregions that coactivate during the perception of visual scenes.
@@
 \todo[inline]{SE: use different colormap for overlap of contrasts' clusters}
+
+\todo[inline]{I manually adjusted the stability-slices.pdf; the Fig S1 should
+now (not just on my computer) show a black bar in the color maps for the
+audio-descriptions (because there are 5 and not 8 contrasts)}
 
@@
 %
-\todo[inline]{concluding statement?}.
+\todo[inline]{concluding statement?}
 

### 2021-02-28 paper/main.tex
adjust plan

@@
         current phrasing
+    \item https://gin.g-node.org/; upload; datacite.yml; readme; reserve \&
+        cite DOI in data availability section
     \item Lescroart is just a small footnote in pPPA vs. aPPA in discussion
@@
     \item maybe "do something with" dice-index
-    \item position of figures and tables is very odd now but probably does not
-        matter
 \end{itemize}
@@
 The fMRI and annotation data, analysis scripts to generate the results as well
-as results are available in the [NAME] repository, [PERSISTENT WEB LINK],
-accessible as Datalad (RRID:SCR\_003931) datasets.
+as results are available in the gin repository,
+\href{https://gin.g-node.org/chaeusler/studyforrest-ppa-analysis}{gin.g-node.org/chaeusler/studyforrest-ppa-analysis}, accessible as Datalad (RRID:SCR\_003931) datasets.
 

### 2021-02-28 paper/main.tex
Use a more readable font
Address all comments in the intro

@@
 \usepackage[T1]{fontenc}
+\usepackage{stix2}
 \usepackage{babel}
@@
 
-\todo[inline]{dunno if it is smart to cite Aminoff (2013) here because she also
-reviews PPA + episodic memory function \& tries to unify domains via contextual
-information hypothesis which is not mentioned here at all}
-
 % literature review overview: imagination & haptic exploration; van der Hurk: 64
@@
 activity levels in the PPA that were correlated with different semantic
-categories occurring in spoken language.
+categories occurring in \textit{speech}.
 % Aziz' stimuli; ``The Taj Mahal faces a long thin reflecting pool'', ``Marilyn
@@
 
-\todo[inline]{SE: (lack of) exclusivity is not really becoming evident from
-preceding paragraph; COH: imo last two paragraphs are about exactly that??}
 % summary if literature review
-In summary, studies suggest that the PPA does not exclusively respond to
+Taken together, the literature suggest that the PPA does not exclusively respond to
 visually presented spatial information.
 % three things in common
-Nevertheless, the reviewed studies share three common aspects:
+However, the reviewed studies share three common aspects:
 % designed stimulus set
@@
 Second, studies used block-design paradigms to maximize detection power.
-Further, they usually employed an explicit (perceptual) judgement task.
+Third, they usually employed an explicit (perceptual) judgement task.
 % conceptualized stimuli and block: disadvantages
@@
 \citep{sonkusare2019naturalistic}.
-% Moreover, study participants can and will become aware about which perceptual
-% process is examined in the study by merely being exposed to the experimental
-% paradigm.
-Third, the reviewed studies averaged results across 7-11 participants.
-% averaging pros and cons
-The averaging approach improves signal-to-noise ratio (SNR) but does not
-characterize brain functions at an individual level, a prerequisite for the
-application of brain imaging methods in individual diagnostics (cf.
-\cite{dubois2016building, eickhoff2020towards}).
 
@@
 is usually detected by contrasting blocks of pictures is also present under more
-ecologically conditions.
+natural conditions.
 % we use 2 naturalistic stimuli
-To answer this question, we operationalized the perception of both visual and
-auditory spatial information using two naturalistic stimuli (see
+To answer this question, we operationalized the perception of both \textit{visual and
+auditory} spatial information using two naturalistic stimuli (see
 \citep{hamilton2018revolution, hasson2008neurocinematics,
@@
 \citep{hausler2021studyforrest}.
+% pictures -> movie -> audio-description
+The movie stimulus shares the stimulation in the visual domain with classical
+localizer stimuli, while featuring real-life-like visual complexity and naturalistic
+auditory stimulation. The audio-description maintains the naturalistic nature of
+the movie stimulus, but limitted to the auditory domain.
 % GLM contrasts
@@
 \citep{hanke2016simultaneous, hanke2014audiomovie, sengupta2016extension}.
-% pictures -> movie -> audio-description
-The movie, as an intermediate step, offered a more naturalistic but still visual
-stimulation whereas the audio-description, as a further step, offered a more
-naturalistic but non-visual, semantic stimulation.
 % hypo a
@@
 impaired individuals.
-
-\todo[inline]{I searched for other studies that localize PPA: essentially every
-study that does something "PPA-related" does separate localizer (using pictures
-of course); but: there are two studies that evaluate localization using pictures
-as such; both gave "pretty" results:}
-
-\todo[inline]{Peelen \& Downing (2005): 6 subjects, 6x bilateral clusters
-(onlinelibrary.wiley.com/doi/full/10.1002/hbm.20116)}
-
-\todo[inline]{Downing, Peelen \& Kanwisher (2006): 12 subjects, 12x bilateral
-clusters (academic.oup.com/cercor/article/16/10/1453/353981)}
 

### 2021-02-28 paper/main.tex
correct typos in intro

@@
 The PPA showed increased activation during imagination of places compared to
-faces but the imagination tasks showed a smaller activation level compared to
+faces but the imagination task showed a smaller activation level compared to
 the perceptual task.
@@
 % designed stimulus set
-First, they employed a small sets of carefully chosen and conceptualized
+first, they employed a small set of carefully chosen and conceptualized
 stimuli.
 % block-design & task
-Second, studies used block-design paradigms to maximize detection power.
+Second, studies used a block-design paradigm to maximize detection power.
 Third, they usually employed an explicit (perceptual) judgement task.

### 2021-02-28 paper/main.tex
Make clear that we used something that we described EXACTLY in a publication

--- 2021-02-28 paper/main.tex
@@
 % https://github.com/psychoinformatics-de/studyforrest-data-templatetransforms}
-The current analyses were carried out on previously published fMRI data
-(\url{https://github.com/psychoinformatics-de/studyforrest-data-aligned}).
+The current analyses were carried out on the same preprocessed fMRI data that were used
+for the technical validation analysis presented in \cite{hanke2016simultaneous}\footnote{available from \url{https://github.com/psychoinformatics-de/studyforrest-data-aligned}}.
 Of those 15 participants in the studyforrest dataset that took
@@
 during scanning of the audio-description stimulus.
-Data were previously corrected for motion, aligned with and re-sliced onto a
+Data were corrected for motion, aligned with and re-sliced onto a
 participant-specific BOLD template image \citep{sengupta2016extension}
@@
 % temporal filtering
+For the present analysis, the following additional preprocessing was performed.
 High-pass temporal filtering was applied to every stimulus segment using a

### 2021-02-28 paper/main.tex
Ack comments

@@
 \citep{brown2012cinematography, katz1991film, mascelli1998five}.
-
-\todo[inline]{I think you need to help the reader understand, what annotations
-in the AV-movie are relevant in the current context; COH: revised the section a
-little. Most importantly the "cinematographic rationale" is explained first and
-is then followed by the categories; imo annotations are more important in
-section "contrasts"}
 
@@
 
-\todo[inline]{SE: "the eight segments": Are you sure, everybody remembered
-these? COH: no clue what to do with that feedback}
 % we checked correlations
@@
 % correlations within stimuli and across stimuli
-the correlation of regressors across the eight segments of each stimulus and
+the correlation of regressors of each stimulus and
 also across both stimuli (Fig.~\ref{fig:reg-corr}).
@@
     \includegraphics[width=\linewidth]{figures/regressor-corr} \caption{Pearson
-        correlation coefficients of modeled time series used as regressors in
+        correlation coefficients of model response time series used as regressors in
         the GLM analysis of the

### 2021-02-28 paper/main.tex
Remaining method comments, fixed reference tab->fig

@@
 % intro
-We performed standard two-level GLM analyses to aggregate results across the
-eight segments for every participant and each stimulus separately.
+We performed standard two-level GLM analyses to aggregate results across all
+BOLD acquisition runs for every participant and each stimulus separately.
 % level 3
@@
 % subjectively assessed balance
-For each stimulus, we picked a primary contrast for result presentation (the
-first one in each Table) based on a subjectively assessed balance of how well
+For each stimulus, we picked a primary contrast for result presentation (marked
+  with an asterisk in the table) based on a subjectively assessed balance of how well
 the averaged events within categories represent spatial and non-spatial
@@
 that were moderately correlated with movie cuts indicating a
-switch to another setting (Tab.~\ref{fig:reg-corr}).
+switch to another setting (Fig.~\ref{fig:reg-corr}).
 % AD stimulus
@@
 of visual stimulation.
-
-\todo[inline]{SE: "vse, vno, vpe,..." in Table 3 are not really the most
-intuitive regressor names; COH: writing out names will turn table into a mess;
-added reference to the Table that explains the abbreviations}
 

### 2021-02-28 paper/main.tex
Remove section numbering
Switch to final citation style (requires numerous fixes)
Rectify citations

@@
 \lhead{\textsc{\scidatalogo}}
-\usepackage{natbib}
+\usepackage[comma,super,sort&compress]{natbib}
 
@@
 
-\section{Introduction}
+\section*{Introduction}
 
@@
 % brain mapping via fMRI
-Studies in the field of neuropsychology and neuroimaging (e.g.
-\citep{penfield1950cerebral, fox1984noninvasive}) have shown that different
+Studies in the field of neuropsychology and neuroimaging
+(\citep[e.g.,][]{penfield1950cerebral, fox1984noninvasive}) have shown that different
 parts of the brain are specialized for different perceptual and cognitive
@@
 faces or tools) during blood oxygenation level-dependent functional magnetic
-resonance imaging (BOLD fMRI) (see \citep{epstein2014neural, aminoff2013role}
-for reviews).
+resonance imaging (BOLD fMRI) (\citep[see reviews][]{epstein2014neural, aminoff2013role}).
 % \citep{aguirre1998area, epstein2014neural, epstein1998ppa, troiani2012object}.
@@
 % % O'Craven: watching pictures
-In a study conducted by \cite{ocraven2000mental} participants viewed alternating
+In a study conducted by \citet{ocraven2000mental} participants viewed alternating
 blocks of pictures showing familiar places and famous faces during an initial
@@
 % Wolbers: haptic exploration
-In a block design study conducted by \cite{wolbers2011modality} the PPA of
+In a block design study conducted by \citet{wolbers2011modality} the PPA of
 sighted as well as blind participants showed increased activation during a
@@
 % Monroe has a large square jaw'', ``The television has a long antenna''
-\cite{aziz2008modulation} used sentences that described famous or generic places
+\citet{aziz2008modulation} used sentences that described famous or generic places
 and faces, or objects.
@@
 To answer this question, we operationalized the perception of both \textit{visual and
-auditory} spatial information using two naturalistic stimuli (see
-\citep{hamilton2018revolution, hasson2008neurocinematics,
-sonkusare2019naturalistic} for reviews).
+auditory} spatial information using two naturalistic stimuli
+(\citep[see reviews][]{hamilton2018revolution, hasson2008neurocinematics,
+sonkusare2019naturalistic}).
 % AV stimulus
@@
 
-\section{Methods}
+\section*{Methods}
 
@@
 \href{http://www.studyforrest.org}{studyforrest.org} dataset that has
-been repeatedly used by other research groups in independent studies (e.g.
-\citep{ben2018hippocampal, jiahui2019predicting, hu2017decoding,
+been repeatedly used by other research groups in independent studies
+(\citep[e.g.,][]{ben2018hippocampal, jiahui2019predicting, hu2017decoding,
 lettieri2019emotionotopy, nguyen2016integration}).
@@
 
-\subsection{Participants}
+\subsection*{Participants}
 % AD study
@@
 
-\subsection{Stimuli and Procedure}
+\subsection*{Stimuli and Procedure}
 
@@
 For details on stimulus creation and presentation see
-\cite{hanke2014audiomovie,hanke2016simultaneous}.
+\citet{hanke2014audiomovie,hanke2016simultaneous}.
 
@@
 For details on stimulus creation and presentation see
-\cite{sengupta2016extension}.
-
-\subsection{Stimulation setup}
+\citet{sengupta2016extension}.
+
+\subsection*{Stimulation setup}
 
@@
 
-\subsection{fMRI data acquisition}
+\subsection*{fMRI data acquisition}
 
@@
 
-\subsection{Preprocessing}
+\subsection*{Preprocessing}
 
@@
 The current analyses were carried out on the same preprocessed fMRI data that were used
-for the technical validation analysis presented in \cite{hanke2016simultaneous}\footnote{available from \url{https://github.com/psychoinformatics-de/studyforrest-data-aligned}}.
+for the technical validation analysis presented in \citet{hanke2016simultaneous}, and available from \href{https://github.com/psychoinformatics-de/studyforrest-data-aligned}{github.com/psychoinformatics-de/studyforrest-data-aligned}.
 Of those 15 participants in the studyforrest dataset that took
@@
 
-\subsection{Event selection} \label{rationale}
+\subsection*{Event selection}
 
@@
 % we focus on cuts
-Contrary to manually annotating stimulus features of movie frames (as
-performed by e.g. \cite{bartels2004mapping} for color, faces, language, and
+Contrary to manually annotating stimulus features of movie frames (for example, as
+performed by \citet{bartels2004mapping} for color, faces, language, and
 human bodies), we categorized movie cuts that - in general - realign the viewer
@@
 
-\subsection{Hemodynamic Modeling}
+\subsection*{Hemodynamic Modeling}
 
@@
 
-\subsection{Statistical analysis}
+\subsection*{Statistical analysis}
 
@@
 individual PPA overlaps were created from data provided by
-\citep{sengupta2016extension}.
-
-\section{Results}
-
-\todo[inline]{SE: subheadings, paragraphs etc? COH: scientific data's analysis
-allows subheadings; added some}
+\citet{sengupta2016extension}.
+
+\section*{Results}
 
@@
 
-\subsection{group average results}
-
-\todo[inline]{SE: What to make out of the fact that the movie stimulation seems
-to evoke activation that goes substantially further caudal than the classical
-PPA? COH: part of the discussion; maybe a concluding statement here? imo it's
-good as it is}
+\subsection*{Group analyses}
 
@@
 Two bilateral clusters are located in the anterior part of the PPA group overlap
-reported by \cite{sengupta2016extension}.
+reported by \citet{sengupta2016extension}.
 % in detail
@@
       For comparison, the union of the individual PPA localization reported
-      by \cite{sengupta2016extension} are indicated as a black outline.
+      by \citet{sengupta2016extension} are indicated as a black outline.
     }
@@
 
-\subsection{individual results}
+\subsection*{Individual analyses}
 
@@
 individual participants, and compared them to the individual PPA localizations
-provided by \cite{sengupta2016extension}, who reported
+provided by \citet{sengupta2016extension}, who reported
 % Sengupta et al., 2016; unilateral in sub-04 and sub-20
@@
 % one contrast to localize them all; "...and $Z$>3.4 for all"
-Unlike \cite{sengupta2016extension}, who determined PPA clusters using three
+Unlike \citet{sengupta2016extension}, who determined PPA clusters using three
 candidate contrasts and a variable threshold, we used a single contrast for each
@@
 
-\section{Discussion}
+\section*{Discussion}
 
@@
 %
-Current results may partially deviate from \cite{sengupta2016extension}, due to
+Current results may partially deviate from \citet{sengupta2016extension}, due to
 the uniform cluster forming threshold employed in this study versus their
@@
 % conclusion: subregions
-\cite{baldassano2013differential} proposes that the PPA creates a complete
+\citet{baldassano2013differential} proposes that the PPA creates a complete
 scene representation, based on different aspects of a visual scene processed in
@@
 %#6 hypothesis
-Based on the report by \cite{aziz2008modulation}, we hypothesized that semantic
+Based on the report by \citet{aziz2008modulation}, we hypothesized that semantic
 spatial information embedded in the audio-description would correlate with
@@
 % diff to Aziz (2008)
-\cite{aziz2008modulation} modeled events from onset to offset of sentences,
+\citet{aziz2008modulation} modeled events from onset to offset of sentences,
 describing unknown and famous places and faces, and compared activity levels
@@
 % concluding statement
-Contrary to \cite{aziz2008modulation}, our results suggest that auditory
+Contrary to \citet{aziz2008modulation}, our results suggest that auditory
 spatial information compared to non-spatial information correlates with
@@
 The naturalistic stimulation paradigm employed here is similar in the sense that
-participants had no behavioral or cognitive task \cite[e.g., forming a mental
+participants had no behavioral or cognitive task \citet[e.g., forming a mental
 image of the stimuli;][]{ocraven2000mental} but just had to ``enjoy the
@@
 % but still: we are different
-Nevertheless, the naturalistic paradigm differs from \cite{epstein1998ppa},
+Nevertheless, the naturalistic paradigm differs from \citet{epstein1998ppa},
 because the relevant stimulus features were embedded in a continuous stream of
@@
 % PPA: intro
-In an earlier study, \cite{bartels2004mapping} manually annotated the content of
+In an earlier study, \citet{bartels2004mapping} manually annotated the content of
 movie frames (color, faces, language, and human bodies) and found that the
@@
 
-\section{Data Citations}
+\section*{Data Citations}
 
@@
 
-\subsection{additional contrasts}
+\subsection*{additional contrasts}
 
@@
 
-\subsubsection{PPA, RSC, and LOC (AV \& AV)}
+\subsubsection*{PPA, RSC, and LOC (AV \& AV)}
 
@@
 
-\subsubsection{auditory cortices}
+\subsubsection*{auditory cortices}
 
@@
 
-\subsubsection{``random clusters''}
+\subsubsection*{``random clusters''}
 
@@
 
-\subsection{Control contrasts}
+\subsection*{Control contrasts}
 

### 2021-02-28 paper/main.tex
MOre fixes

@@
         Light gray: The
-        audio-description's field of view (cf. \citep{hanke2014audiomovie}).
+        audio-description's field of view \citep{hanke2014audiomovie}.
         To facilitate comparisons across participants, we chose the same horizontal
@@
 \end{figure*}
-
-\todo[inline]{SE: imo, key question is only partially answered: how close is
-movie / audio to localizer". Can you corroborate figure 3 with some more
-numbers? COH: schwierig vergleichbar (insb. unterschiedliche thresholds), daher
-Bland-Altman-Plots -> as kinda mentioned in following paragraph}
 

### 2021-02-28 paper/main.tex
suggestions of citations corrections

@@
 For details on stimulus creation and presentation see
-\citet{hanke2014audiomovie,hanke2016simultaneous}.
+\citet{hanke2014audiomovie,hanke2016simultaneous}.\todo{ggf. nicht korrekt}
 
@@
 luminance and size, that were previously used in other studies
-\citep[e.g.,][]{haxby2011common}.
+(\citep[e.g.,][]{haxby2011common}).
 % procedure: presentation & instructions
@@
 For details on stimulus creation and presentation see
-\citet{sengupta2016extension}.
+\citet{sengupta2016extension}.\todo{ggf. nicht korrekt}
 
@@
 % preprocessing intro
-Preprocessing was performed by FEAT v6.00 (FMRI Expert Analysis Tool;
-\citep{woolrich2001autocorr}) as shipped with
-FSL v5.0.9 (\href{https://www.fmrib.ox.ac.uk/fsl}{FMRIB's Software Library};
+Preprocessing was performed by FEAT v6.00 (FMRI Expert Analysis Tool \citep{woolrich2001autocorr}) as shipped with
+FSL v5.0.9 (\href{https://www.fmrib.ox.ac.uk/fsl}{FMRIB's Software Library}
  \citep{smith2004fsl}) on a computer-cluster running
@@
 Correction for local autocorrelation in the time series (prewhitening) was
-applied using FILM (FMRIB's Improved Linear Model; \citep{woolrich2001autocorr})
+applied using FILM (FMRIB's Improved Linear Model \citep{woolrich2001autocorr})
 to improve estimation efficiency.
@@
 random effects variance to zero in FLAME (FMRIB's Local Analysis of Mixed
-Effects; \citep{beckmann2003general, woolrich2004multilevel}.
+Effects \citep{beckmann2003general, woolrich2004multilevel}).
 % thresholding ($Z$>2.3 in subject-space; $Z$>3.4 in group space)
@@
 participants were watching static pictures of landscapes compared to pictures of
-faces or objects \citep[e.g.,][]{epstein1998ppa, epstein1999parahippocampal}.
+faces or objects (\citep[e.g.,][]{epstein1998ppa, epstein1999parahippocampal}).
 % auditory semantics unclear
@@
 The naturalistic stimulation paradigm employed here is similar in the sense that
-participants had no behavioral or cognitive task \citet[e.g., forming a mental
-image of the stimuli;][]{ocraven2000mental} but just had to ``enjoy the
-presentation''.
+participants had no behavioral or cognitive task (\citet[e.g., forming a mental
+image of the stimuli;][]{ocraven2000mental})\todo{probably wrong}
+ but just had to ``enjoy the presentation''.
 % but still: we are different
@@
 Future studies that aim to use a movie to localize visual areas in individual
-participants should extensively annotate the content of frames \citep[e.g.,
-using the open-source solution ``Pliers'' for feature extraction from a visual
-naturalistic stimulus;][]{mcnamara2017developing}.
+participants should extensively annotate the content of frames (e.g.,
+using the open-source solution ``Pliers''\citep{mcnamara2017developing} for feature extraction from a visual
+naturalistic stimulus).
 

### 2021-03-01 paper/main.tex
ACK citation comments

@@
 For details on stimulus creation and presentation see
-\citet{hanke2014audiomovie,hanke2016simultaneous}.\todo{ggf. nicht korrekt}
+\citet{hanke2014audiomovie,hanke2016simultaneous}.
 
@@
 For details on stimulus creation and presentation see
-\citet{sengupta2016extension}.\todo{ggf. nicht korrekt}
+\citet{sengupta2016extension}.
 
@@
 The naturalistic stimulation paradigm employed here is similar in the sense that
-participants had no behavioral or cognitive task (\citet[e.g., forming a mental
-image of the stimuli;][]{ocraven2000mental})\todo{probably wrong}
+participants had no behavioral or cognitive task (\citep[e.g., forming a mental
+image of the stimuli][]{ocraven2000mental})
  but just had to ``enjoy the presentation''.

### 2021-03-01 paper/main.tex
I personally consider a (cited) half-sentence of a location description no plagiarism

@@
 the anterior temporal lobe \citep{baldassano2013differential,
-baldassano2016two}.\todo{last half sentence is almost a direct quote;
-plagiarism?}
+baldassano2016two}.
 % conclusion: subregions

### 2021-03-01 paper/main.tex
Squeeze in a citation of neuroscout
Further legitimizes our approach

@@
 annotations can be applied to a naturalistic paradigm to localize concise
-functional areas and networks correlating with specific perceptual processes.
+functional areas and networks correlating with specific perceptual processes
+-- an analysis approach that can be facilitated by the neuroscout.org platform
+\citep{delavega2021neuroscout}.
 % interpretation

### 2021-03-01 paper/main.tex
Adress all comments, main paper

@@
 \begin{itemize}
-    \item Todo's are mostly comments and can be deleted if issue is solved by
-        current phrasing
     \item https://gin.g-node.org/; upload; datacite.yml; readme; reserve \&
         cite DOI in data availability section
-    \item Lescroart is just a small footnote in pPPA vs. aPPA in discussion
-        (problem to write more about the paper: it is voxel-wise encoding which
-        does not tell a lot about increased vs. decreased activation; "crafted"
-        stimuli: 45 min of 850 scenes, made from 33 backgrounds + 2-3 objects
-        drawn from pool of 440 objects
-    \item maybe "do something with" dice-index
 \end{itemize}
@@
 
-\todo[inline]{SE: mit Befund, den Du diskutieren willst beginnen, mit take-home
-message enden. COH: bekomme ich nur (und auch nur evtl.) reingepresst, wenn ich
-die Discussion komplett umschreibe; take-home message ist aber eh fast überall
-drin}
-
-\todo[inline]{SE: es gibt schon andere "event-related" analysen von movies,
-oder? COH: habe Paper durchgeguckt: Es gibt wenig bis gar nichts (obwohl
-Annotation immer mehr automatisiert werden können); Bzgl. Narrative ist im
-Grunde alles "voxel-wise enconding"; Rocca benutzt Annotation, aber auch
-"crafted" 23-min Narrative; NeuroScout: bisher absolut (?) keine veröffentlichte
-Studie, die NeuroScout genutzt hat; -> Bartels ist Klassiker, steht aber enorm
-allein da, und macht aber genau das, was wir machen "Naturalistic Stimulus statt
-Traditionell"; insofern: es gibt schon "irgendwie" andere Studien, die etwas mit
-Annotation (von Filmen) gemacht haben, die machen aber dann halt auch ganz
-anderes Zeug}
-
 %#1 previous studies
@@
 participants were watching static pictures of landscapes compared to pictures of
-faces or objects (\citep[e.g.,][]{epstein1998ppa, epstein1999parahippocampal}).
+faces or objects \citep{epstein1998ppa, epstein1999parahippocampal}.
 % auditory semantics unclear
@@
 specifically and predominantly evoke the processing of spatial information, we
-employed a naturalistic stimuli, a movie and its audio-description, that were
+employed naturalistic stimuli, a movie and its audio-description, that were
 designed for entertainment.
@@
 %#11 question
-The fact that clusters from the auditory stimulus are spatially restricted to
+The fact that clusters of responses to the auditory stimulus are spatially restricted to
 the anterior part of clusters from both visual paradigms raises the question if
@@
 %#2
-Our approach to stimulus annotation and event selection differs from previous
+Our approach to movie stimulus annotation and event selection differs from previous
 reports in the literature.
@@
 Like the PPA, the RSC and LOC repeatedly exhibited increased hemodynamic
-activity in studies investigating visual spatial perception or navigation (see
-\citep{chrastil2018heterogeneity, bettencourt2013role, epstein2019scene} for
-reviews)
+activity in studies investigating visual spatial perception or navigation (see reviews
+\citep{chrastil2018heterogeneity, bettencourt2013role, epstein2019scene})
 % not random shit
@@
 
-\todo[inline]{SE: mir das Potential (warum ist das relevant -> rich stimulus ie
-many possible analyses, better compliance, easier to perform for difficult
-populations, etc) eigentlich zu kurz; COH: finde ich (insb. als allerletzten)
-Satz in einem Satz so okay, weil a) Textlimit, b) exploratory \& <80 \%
-lokalisationsleistung; wenn, dann müsste man ein größeres Fass in Intro und
-Discussion aufmachen, was die Ergebnisse aber nicht hergeben }
-
 \subsection*{Data and code availability}
@@
 
-\todo[inline]{everything correct? Grant or contribution numbers may be acknowledged}
-%
 COH designed and performed the analyses, and wrote the manuscript.

### 2021-03-01 paper/main.tex
Format for readability

@@
-\documentclass[english]{article}
+\documentclass[english,11pt]{article}
 \usepackage[utf8]{inputenc}
@@
 \usepackage{comment}
+\usepackage{breakurl}
 \usepackage{svg}
-\usepackage{caption, booktabs}
+\usepackage[labelfont=bf,font=small]{caption}
+\usepackage{booktabs}
 \usepackage{amsmath}
@@
 \usepackage{units}
-\usepackage[left=2cm,right=4cm,top=2cm,bottom=2cm]{geometry}
+\usepackage[left=2.5cm,right=2.5cm,top=1cm,bottom=1cm,includeheadfoot]{geometry}
 \usepackage[
@@
 \pagestyle{fancy}
-\fancyhf{}
+%\fancyhf{}
 \renewcommand{\headrulewidth}{0pt}
-\setlength{\headheight}{40pt}
-\lhead{\textsc{\scidatalogo}}
+%\setlength{\headheight}{40pt}
+%\lhead{\textsc{\scidatalogo}}
 \usepackage[comma,super,sort&compress]{natbib}
@@
 
+\noindent
 1. Psychoinformatics Lab, Institute of Neuroscience and Medicine, Brain \&
-Behaviour (INM-7), Research Centre Jülich, Jülich, Germany, 2. Institute of
-Systems Neuroscience, Medical Faculty, Heinrich Heine University,  Düsseldorf,
-Germany {*}corresponding author: Christian Olaf Häusler (der.haeusler@gmx.net)
+Behaviour (INM-7), Research Centre Jülich, Jülich, Germany\\
+\noindent
+2. Institute of Systems Neuroscience, Medical Faculty, Heinrich Heine University,
+Düsseldorf, Germany\\
+{*}corresponding author: Christian Olaf Häusler (der.haeusler@gmx.net)
 
@@
 The current analyses were carried out on the same preprocessed fMRI data that were used
-for the technical validation analysis presented in \citet{hanke2016simultaneous}, and available from \href{https://github.com/psychoinformatics-de/studyforrest-data-aligned}{github.com/psychoinformatics-de/studyforrest-data-aligned}.
+for the technical validation analysis presented in \citet{hanke2016simultaneous}, and available from \href{https://github.com/psychoinformatics-de/studyforrest-data-aligned}{github.com/ psychoinformatics-de/studyforrest-data-aligned}.
 Of those 15 participants in the studyforrest dataset that took
@@
 \label{tab:events}
-\small
+\resizebox{\linewidth}{!}{
+\footnotesize
 \begin{tabular}{lp{3.7cm}lllllllll} \toprule \textbf{Label} & \textbf{Description} & \textbf{All} & \textbf{1} & \textbf{2} & \textbf{3} & \textbf{4} & \textbf{5} & \textbf{6} & \textbf{7} & \textbf{8} \\
@@
 \end{tabular}
+}%resizebox
 \end{table*}
@@
 \label{tab:descr-nouns-rules}
+\resizebox{\linewidth}{!}{
 \begin{tabular}{lp{61mm}p{61mm}}
@@
 \label{tab:res-av-group1}
+\resizebox{\linewidth}{!}{
 \small
@@
     \label{tab:res-ao-group1}
+\resizebox{\linewidth}{!}{
 \small

### 2021-03-01 paper/main.tex
write out in full refs to figs & tables

@@
 Based on this cinematographic bias, we assigned each cut to one of five
-categories (Tab.~\ref{tab:events}):
+categories (see Table~\ref{tab:events}):
 %
@@
     nouns spoken by the audio-description's narrator
-    (Tab.~\ref{tab:descr-nouns-rules}).
+    (see Table~\ref{tab:descr-nouns-rules}).
     Some of the audio-description's event categories listed here
@@
 amount of counts were pooled resulting in 11 final event categories
-(Tab.~\ref{tab:events}).  These event categories were then used to model
+(see Table~\ref{tab:events}).  These event categories were then used to model
 hemodynamic responses.
@@
         GLM
-        (Tab.~\ref{tab:events}).
+        (see Table~\ref{tab:events}).
         % The category \texttt{++} also contains adverbial of time.
@@
 the correlation of regressors of each stimulus and
-also across both stimuli (Fig.~\ref{fig:reg-corr}).
+also across both stimuli (see Figure~\ref{fig:reg-corr}).
 % correlations within each stimulus
@@
 which is to be expected, as the audio-description contains the audio track of
-the movie plus the additional narrator (Fig. \ref{fig:reg-corr}; correlation
+the movie plus the additional narrator (see Figure~\ref{fig:reg-corr}; correlation
 between root mean square volume of both audio tracks, r=.76; correlation between
@@
         the GLM analysis of the
-        audio-description (blue; Tab.~\ref{tab:events} for a
-        description) and audio-visual movie (red; Tab.~\ref{tab:events}).
+        audio-description (blue; see Table~\ref{tab:events} for a
+        description) and audio-visual movie (red; see Table~\ref{tab:events}).
         Values are rounded to the nearest tenth.
@@
 for which no event of a category was present (e.g. no event of \texttt{vpe\_old}
-in segment 3; Tab.~\ref{tab:events}).
+in segment 3; see Table~\ref{tab:events}).
 % temporal derivatives
@@
 Finally, we created several control contrasts for both stimuli
-(Tab.~\ref{tab:contrasts}).
+(see Table~\ref{tab:contrasts}).
 % AV: no cut > cut
@@
 that were moderately correlated with movie cuts indicating a
-switch to another setting (Fig.~\ref{fig:reg-corr}).
+switch to another setting (see Figure~\ref{fig:reg-corr}).
 % AD stimulus
@@
     An explanation of all event categories can be found in
-    Tab.~\ref{tab:events}.
+    Table~\ref{tab:events}.
     }
@@
 depicted before to cuts within a recurring setting (\texttt{vse\_new >
-vpe\_old}) yielded three significant clusters (Tab.~\ref{tab:res-av-group1},
-Fig.~\ref{fig:group-slices}).
+vpe\_old}) yielded three significant clusters (see Table~\ref{tab:res-av-group1},
+Figgure~\ref{fig:group-slices}).
 % PPA (others the clusters extend into).
@@
 non-spatial noun categories) yielded six significant clusters
-(Tab.~\ref{tab:res-ao-group1}, Fig.~\ref{fig:group-slices}).
+(see Table~\ref{tab:res-ao-group1}, Figure~\ref{fig:group-slices}).
 % overlap with ROI
@@
 bilateral parahippocampal clusters in 12 of 14 participants and unilateral right
-clusters in two participants \citep[Tab.~3 in][]{sengupta2016extension}.
+clusters in two participants \citep[see Table~3 in][]{sengupta2016extension}.
 % one contrast to localize them all; "...and $Z$>3.4 for all"
@@
 $t$-contrasts for the movie stimulus, and overall eight $t$-contrast for the
-audio-description (Tab.~\ref{tab:contrasts}).
+audio-description (see Table~\ref{tab:contrasts}).
 % how
@@
 clusters that overlap with the PPA group overlap
-(Fig.~\ref{fig:stability-slices}).
+(see Figure~\ref{fig:stability-slices}).
 % AV: RSC & LOC
@@
 contrast 7 and 8  yielded significant bilateral clusters in anterior regions of
-the group PPA overlap (Fig.~\ref{fig:stability-slices}).
+the group PPA overlap (see Figure~\ref{fig:stability-slices}).
 % AD: RSC & LOC
@@
 shots (\texttt{no\_cut} category) with movie cut related categories
-(Tab.~\ref{tab:contrasts}).
+(see Table~\ref{tab:contrasts}).
 % results
@@
 The inspection of correlations of regressors across stimuli
-(Fig.~\ref{fig:reg-corr}) showed a moderate correlation among cuts to a setting
+(see Figure~\ref{fig:reg-corr}) showed a moderate correlation among cuts to a setting
 depicted for the first time (\texttt{vse\_new}) and nouns indicating a switch to
@@
 Finally for the analysis of the audio-description, we created control contrasts
-based on events of the annotated movie cuts (Tab.~\ref{tab:contrasts}) in
+based on events of the annotated movie cuts (see Table~\ref{tab:contrasts}) in
 order to test XYZ.

### 2021-03-01 paper/main.tex
Cite properly

--- 2021-03-01 paper/main.tex
@@
 \pagestyle{fancy}
-%\fancyhf{}
+\fancyhf{}
 \renewcommand{\headrulewidth}{0pt}
@@
 narrative, studyforrest
-
-\pagebreak[4]
-
-\section*{Plan}
-
-\noindent Generally
-\begin{itemize}
-    \item https://gin.g-node.org/; upload; datacite.yml; readme; reserve \&
-        cite DOI in data availability section
-\end{itemize}
-
-\noindent Supplemental Material
-\begin{itemize}
-    \item introductory sentences (e.g. "To test...") and concluding statements
-\end{itemize}
 
@@
 % unregistered)
-The fMRI and annotation data, analysis scripts to generate the results as well
-as results are available in the gin repository,
-\href{https://gin.g-node.org/chaeusler/studyforrest-ppa-analysis}{gin.g-node.org/chaeusler/studyforrest-ppa-analysis}, accessible as Datalad (RRID:SCR\_003931) datasets.
+The fMRI data, annotations, analysis scripts to generate the results, and
+results as Datalad \citep{datalad} datasets, published to or linked from the
+GIN repository
+\href{https://gin.g-node.org/chaeusler/studyforrest-ppa-analysis}{\url{gin.g-node.org/chaeusler/studyforrest-ppa-analysis}} (DOI assignedment pending). 
+Unthresholded $Z$-maps of all contrasts
+can found at
+\href{https://neurovault.org/collections/KADGMGVZ/}{\url{neurovault.org/collections/KADGMGVZ}}.
+%
 

### 2021-03-01 paper/main.tex
change missing to absent narrator

--- 2021-03-01 paper/main.tex
@@
 9 & \texttt{vno\_cut > vpe\_new, vpe\_old} & control \tabularnewline
-10 & \texttt{se\_new > se\_old} & control for (missing) narrator \tabularnewline
+    10 & \texttt{se\_new > se\_old} & control (absent narrator) \tabularnewline
 \midrule

### 2021-03-01 paper/main.tex
Suppl.

--- 2021-03-01 paper/main.tex
@@
 GIN repository
-\href{https://gin.g-node.org/chaeusler/studyforrest-ppa-analysis}{\url{gin.g-node.org/chaeusler/studyforrest-ppa-analysis}} (DOI assignedment pending). 
+\href{https://gin.g-node.org/chaeusler/studyforrest-ppa-analysis}{\url{gin.g-node.org/chaeusler/studyforrest-ppa-analysis}} (DOI assignment pending). 
 Unthresholded $Z$-maps of all contrasts
@@
 
-\subsection*{additional contrasts}
-
-\todo[inline]{remove subheadings}
-
-\todo[inline]{introductory \& concluding sentences}
-
-\subsubsection*{PPA, RSC, and LOC (AV \& AV)}
-
-\todo[inline]{SE: use different colormap for overlap of contrasts' clusters}
-
-\todo[inline]{I manually adjusted the stability-slices.pdf; the Fig S1 should
-now (not just on my computer) show a black bar in the color maps for the
-audio-descriptions (because there are 5 and not 8 contrasts)}
-
-% intro
+\subsection*{Robustness of main findings across alternative contrasts}
+
 In order to test the robustness of our approach, we created overall five
@@
 
-\subsubsection*{auditory cortices}
+\subsection*{Incidental results}
 
@@
 not averaged out across events and the employed nuisance regressors did not
-capture this variance appropriately.\todo{this sounds shitty}
+capture this variance appropriately.
 % interpretation 2
@@
 when he is indicating the switch to another setting by describing its identity
-or layout.\todo{speculative though}
-% concluding statement
-\todo[inline]{concluding statement?}
-
-\subsubsection*{``random clusters''}
-
-\todo[inline]{following list is exhaustive but probably too detailed}
-%
-Lastly, contrasts of the audio-description stimulus yielded significant clusters
-in regions that were statistically in two or less contrasts.
+or layout.
+
+Lastly, contrasts of the audio-description stimulus yielded clusters
+in regions that were classified as statistically significant in two or less contrasts.
 % contrast 2
@@
 Here again, significantly increased activation beyond areas known to be involved
-in processing of spatial information can be attributed to stimulus features of
+in processing of spatial information could be attributed to stimulus features of
 the naturalistic stimulus that were not sufficiently controlled leading to a
 bias in the contrasts.
-%
-\todo[inline]{imo other interpretations would speculative / reverse inference;
-but "if would look closer I would probably find a super plausible reason why
-brain areas are more active"}
 
@@
     \caption{Overlap of significant clusters ($Z$>3.4; $p$<.05, cluster corrected)
+        across all contrasts for both naturalistic stimuli.
         The audio-description's contrasts 1-8 (blue)
@@
         highlighted.
-        Black: outline of overlapping individual PPA ROIs.
-        The figure shows that some contrasts yielded significant clusters
-        also in the lateral temporal and prefrontal cortex.
+        Black: outline of the union of individual PPA ROIs reported by \citet{sengupta2016extension}.
         }
@@
 \subsection*{Control contrasts}
-
-\todo[inline]{This section feels incomplete. Some explanation (attempts) are
-missing. Sometimes it is simply unclear which data were analyzed with which
-designs. Maybe subheadings would help?}
 
@@
 % movie contrasts: not cut condition vs. cuts
-To test for XYZ\todo{yes, to test what?} within the movie fMRI data, we created
+To test for the specificity of the main finds within the movie fMRI data, we created
 four contrasts that compared hemodynamic activity during frames within movie
@@
 % results
-None of these four contrasts yielded a significant cluster.
-%
-Null results of control contrasts comparing frames within movie shots to frames
-immediately after a cut suggest that XYZ.
-%
-\todo[inline]{concluding statement}
+None of these four contrasts yielded a significant cluster, suggesting that
+the observed differential hemodynamic response in the PPA for events defined
+by particular movie cuts is not observed for other arbitrarily selected time point
+in the movie.
 
@@
 % \texttt{vse\_old}.
-The inspection of correlations of regressors across stimuli
+The correlation of regressors across stimuli
 (Fig.~\ref{fig:reg-corr}) showed a moderate correlation among cuts to a setting
-depicted for the first time (\texttt{vse\_new}) and nouns indicating a switch to
-a setting occurring for the first time (\texttt{se\_new}), and cuts to a
-recurringly depicted setting ({\texttt{vse\_old}) and nouns indicating a switch
-a recurring setting (\texttt{se\_old}.
-%
-Hence, we created a contrast that used the audio-description's nouns on the
-movie data ({\texttt{se\_new} > \texttt{se\_old}).
+depicted for the first time (movie \texttt{vse\_new}) and nouns indicating a switch to
+a setting occurring for the first time (audio-description \texttt{se\_new}), and cuts to a
+recurringly depicted setting (movie {\texttt{vse\_old}) and nouns indicating a switch
+a recurring setting (audio-description \texttt{se\_old}).
+%
+Hence, we computed an indentical contrast ({\texttt{se\_new} >
+\texttt{se\_old}), comparing the audio-description's voice-over narrator
+nouns for the movie data and the audio-description.
 % results
-The contrasts yielded a significant cluster in the right [but not anterior] PPA
-and bilateral clusters in the superior lateral occipital cortices (the right
-hemispheric cluster extending into the superior parietal cortex).
-%
-Results suggest that XYZ.
-%
-\todo[inline]{concluding statement? That last contrast was originally done to
-check that "soundscape at moment of cuts thing" but this is obsolete now}
-
-\todo{following: control contrast for AO; why exactly did we do this except "we
-do not expect (lots of) significant cluster because negative control?}
+While for the movie data the contrast yielded a significant cluster in the
+right PPA, not in its anterior portion, and bilateral clusters in the
+superior lateral occipital cortices (the right hemispheric cluster extending
+into the superior parietal cortex), not significant differences where found
+for the audio-description (unthresholded contrast maps are available on NeuroVault).
+%
+These results suggest that in the absence of the actual visual stimulation, the narrator's
+description of scene properties correlated with setting changes did not co-occur with
+increased hemodynamic activity in areas associated with the processing of spatial
+information.
 
 % AD stimulus
-Finally for the analysis of the audio-description, we created control contrasts
+Finally for the analysis of the audio-description, we computed control contrasts
 based on events of the annotated movie cuts (Tab.~\ref{tab:contrasts}) in
-order to test XYZ.
+order to evaluate the influence of stimulus features correlated with these visual
+events that remain present in the audio-description, such as changes in the soundscape.
 % results
@@
 Contrast 12 (\texttt{vse\_new} > \texttt{vse\_old}, \texttt{vpe\_old}) revealed
-one cluster in the right posterior hippocampus.  \todo{not PPA! explanation?}
-%
-Overall results from the negative control contrast of the audio-description's
-data suggest that XYZ.
-%
-\todo[inline]{concluding statement?}
+one cluster in the right posterior hippocampus.
+%
+The absence of observable hemodynamic response differences in the PPA suggests that
+without the visual information in the movie stimulus, no, or substantially less,
+processing of stimulus content with respect to spatial information co-occurred with
+the timing of the movie cuts.
 

### 2021-03-01 paper/main.tex

--- 2021-03-01 paper/main.tex
@@
 % \texttt{vse\_old}.
-The inspection of correlations of regressors across stimuli
-(see Figure~\ref{fig:reg-corr}) showed a moderate correlation among cuts to a setting
-depicted for the first time (\texttt{vse\_new}) and nouns indicating a switch to
-a setting occurring for the first time (\texttt{se\_new}), and cuts to a
-recurringly depicted setting ({\texttt{vse\_old}) and nouns indicating a switch
-a recurring setting (\texttt{se\_old}.
-%
-Hence, we created a contrast that used the audio-description's nouns on the
-movie data ({\texttt{se\_new} > \texttt{se\_old}).
+The correlation of regressors across stimuli
+(Figure~\ref{fig:reg-corr}) showed a moderate correlation among cuts to a setting
+depicted for the first time (movie \texttt{vse\_new}) and nouns indicating a switch to
+a setting occurring for the first time (audio-description \texttt{se\_new}), and cuts to a
+recurringly depicted setting (movie {\texttt{vse\_old}) and nouns indicating a switch
+a recurring setting (audio-description \texttt{se\_old}).
+%
+Hence, we computed an indentical contrast ({\texttt{se\_new} >
+\texttt{se\_old}), comparing the audio-description's voice-over narrator
+nouns for the movie data and the audio-description.
 % results
-The contrasts yielded a significant cluster in the right [but not anterior] PPA
-and bilateral clusters in the superior lateral occipital cortices (the right
-hemispheric cluster extending into the superior parietal cortex).
-%
-Results suggest that XYZ.
-%
-\todo[inline]{concluding statement? That last contrast was originally done to
-check that "soundscape at moment of cuts thing" but this is obsolete now}
-
-\todo{following: control contrast for AO; why exactly did we do this except "we
-do not expect (lots of) significant cluster because negative control?}
+While for the movie data the contrast yielded a significant cluster in the
+right PPA, not in its anterior portion, and bilateral clusters in the
+superior lateral occipital cortices (the right hemispheric cluster extending
+into the superior parietal cortex), not significant differences where found
+for the audio-description (unthresholded contrast maps are available on NeuroVault).
+%
+These results suggest that in the absence of the actual visual stimulation, the narrator's
+description of scene properties correlated with setting changes did not co-occur with
+increased hemodynamic activity in areas associated with the processing of spatial
+information.
 
 % AD stimulus
-Finally for the analysis of the audio-description, we created control contrasts
-based on events of the annotated movie cuts (see Table~\ref{tab:contrasts}) in
-order to test XYZ.
+Finally for the analysis of the audio-description, we computed control contrasts
+based on events of the annotated movie cuts (Table~\ref{tab:contrasts}) in
+order to evaluate the influence of stimulus features correlated with these visual
+events that remain present in the audio-description, such as changes in the soundscape.
 % results

### 2021-05-31 paper/main.tex
add feedback of review before introduction

@@
 \pagebreak[4]
+
+\todo[inline]{\textbf{My notes:}\par
+    1. change url(s) of datasets\par
+    2. individual ROIs in the manuscript are NOT the ``masks'' but thresholded
+    t-maps that were later ``titrated'' individually to get the mask\par
+    -> imo it's better to adjust the figures (needs some coding though) than
+    changing the text; I hope some significant voxels will still be visible in
+    all subjects that have significant voxels)\par
+    individual thresholds: s. studyforrest-data-visualrois/code/stats2rois.cfg
+}
+
+\todo[inline]{email from Barbara Cheifet (Consultant Editor):
+    \textbf{Guidelines}\par
+
+    - provide your revised manuscript as either a Word or LaTeX document, with
+    separate figure files.\par
+
+    - submit revision here: https://mts-scidata.nature.com/\par
+
+    - replace "subjects" with "participants" throughout the paper.\par
+
+    - split "Code and Data availability" into two sections.\par
+
+    - there isn't a link to the OpenNeuro dataset in the paper, please include
+    this, as it seems relevant\par
+
+    - \underline{provide detailed point-by-point response to the referees'
+    comments}, describing how you have addressed their concerns, with your
+    revised manuscript.
+
+    - ensure your manuscript complies with our format requirements:\par
+    https://www.nature.com/sdata/publish/submission-guideline
+
+    - ensure that your references conform fully to the Nature style;
+    examples:\par
+    http://www.nature.com/sdata/publish/submission-guidelines\#refs
+
+    - replace your initial-submission image files with production quality
+    figures. Line-art figures should be provided in a suitable vector-graphic
+    format, ideally by saving them directly in the EPS or PDF formats from the
+    program used to create them.
+
+    - figures should not include Figure number labels in the image:\par
+    https://www.nature.com/sdata/publish/submission-guidelines\#figures
+
+    - remove the supplementary material from main manuscript text;
+    supply it as a separate PDF.
+
+    - remove the keywords from your manuscript text.
+
+    - ensure a clear open data license (e.g. CC0 or CC BY) appears on your
+    OpenNeuro record landing page
+
+    - add an Author Contributions section after the Acknowledgements.
+
+    - ensure your manuscript sections are provided in the following order:
+    Abstract, Introduction, Results, Discussion, Methods, Data Availability,
+    Code, Availability, References, Acknowledgements, Author Contributions \&
+    Competing Interests\par
+
+    - merge your data citations into your main 'References' section, as per our
+    revised submission guidelines:\par
+    https://www.nature.com/sdata/publish/submission-guidelines\#data\_citations
+}
+
+\todo[inline]{email from Barbara Cheifet (Consultant Editor):
+    \textbf{RevisionChecklist}
+
+In order to process your revised manuscript, we will require the following
+items:
+
+1) A cover letter describing your response to our editorial requests.
+
+2) A point-by-point response to any issues raised by our referees.
+
+3) revised version of your text as Word or TeX/LaTeX file with
+\textbf{all changes highlighted; COH: how?}.
+
+4) The final versions of any Supplementary Information files.
+
+5) Publication quality figures in the TIFF, EPS, or PDF formats.
+
+6) Final accession numbers or DOIs for any deposited datasets.
+
+7) Any authors who have an ORCID and want it to appear on the final publication should add it to their account before you resubmit your revision.
+ORCIDs may not be added to our system after a paper has been accepted for publication.}
+
+\todo[inline]{\textbf{Editorial Board Member}:\par
+[\dots] reviewer 2 also believes that additional work is required to make this suitable for publication.
+I believe that these are technically rather substantive amendments, but it is
+possible that some of the required work has already been undertaken by your
+team.
+
+I am inviting you to revise the MS for further review (though probably
+just to Reviewer 2). While you should pay particular attention to Reviewer 2's
+feedback, I think it is important to attend to the points raised by Reviewer 1
+which will improve the clarity of presentation.}
+
+\todo[inline]{\textbf{Reviewer \#1}
+
+minor suggestions for clarity that you might address or not:
+
+\textbf{Introduction}\par
+
+- The claim for what and where cites \underline{Goodale and Milner (1992)},
+which is literally a call for what and how pathways. The function of these
+pathways remains in dispute but \underline{its clear that where (spatial
+processing) must take place in both streams.} You should probably
+acknowledge that.
+
+- This does not read well. It's a broken sentence: “Second, studies used a
+block-design paradigm to maximize detection power.”
+
+- suggest: “We investigate whether increased” not “we investigate if increased”
+
+- I don’t understand this “because all three operationalization capitalize on”.
+I think this must be a typo graphical error.
+
+\textbf{Discussion}\par
+- I am not sure I understand \underline{your use of immanent do you mean
+inherent?} Or do you really mean something that is manifest in the pictures or
+description. It's a low frequency that might need explaining: "Similarly, our
+results suggest that the pPPA is more concerned with visual aspects immanent in
+pictures or movie shots of landscapes. The aPPA might be more concerned with
+non-visual aspects of spatial information (e.g. spatial contextual
+information57) as immanent in both visual and verbal stimuli."
+
+\textbf{Incidental results}\par
+- I did not really understand this; you may want to elaborate/clarify what you
+mean, perhaps with an example: "Increased activity in primary and secondary
+auditory cortices could be attributed to changes in the soundscape that possibly
+accompany the narrator when he is indicating the switch to another setting by
+describing its identity or layout."}
+
+\todo[inline]{\textbf{Reviewer \#2}
+
+The results have been weakly presented (see major comment \#3). This comment
+should be properly addressed in a revision.
+
+\textbf{Major comments:}
+
+1. \underline{in AV}, PPA has been identified based on the contrast of vse\_new
+vs. vpe\_old. Although the activation matches with the area localized by the
+block-design experiment, this contrast \underline{could have several potential
+confounds}: At the transition to a new setting, \underline{pixel-level changes}
+in the movie frames are usually higher, which could lead to non-specific
+activations in visual cortex and in regions posterior to PPA.
+
+Also it appears that some \underline{cognitive factors like novelty, surprise,
+and attention} are not balanced in this contrast. Involvement of
+\underline{memory} is another confounding factor - at least the contrasts of
+vse\_new vs. vpe\_new and vse\_old vs. vpe\_old do not have this problem.
+\underline{If the movie frames are annotated for things like} landscape,
+building, face, people, body, tool, etc., a straightforward contrast could be
+scenes vs. other categories (similar to a contrast used in the audio-description
+movie experiment). It is not clear why the authors have not considered such
+obvious contrast.
+
+2. In addition to anterior PPA, auditory descriptions of scenes have activated a
+*larger* cluster in \underline{RSC/Precuneus (Table 5)}. This is quite
+interesting because these regions in medial parietal cortex are broadly involved
+in semantic processing of scenes (see recent papers by \underline{Silson and
+colleagues}).  Unfortunately, those \underline{activations are not clearly
+visible in the selected slices shown in Figures 2 and 3}. This brings me to my
+next comment.
+
+3. Visualization of cortical maps in a volume format is not ideal. The
+\underline{authors should show the activation maps on the surface} so that
+
+a) the whole-brain activation pattern (e.g. in medial parietal, superior temporal, and lateral prefrontal regions) could be easily evaluated, and
+
+b) the \underline{precise topography of activations in posterior PPA - anterior
+PPA could be evaluated}.
+
+The surface-based analysis/visualization of fMRI data
+has also other advantages including a better smoothing that is constrained to
+the cortical gray matter ribbon and a more optimized inter-subject averaging.
+
+As far as I know, the structural data of studyforrest.org are processed in
+Freesurfer, and the authors may already have reconstructed cortical surfaces of
+subjects. Thus, the authors can project the individual-subject fMRI data to the
+standard fsaverage surface, do minimal smoothing on surface (if needed), and
+perform group-level surface-based registration and averaging (COH: goddamnit)
+
+4. AO data have been collected in 7T scanner at the resolution of 1.4 mm
+isotropic voxels, while the audio-visual movie data have been collected in 3T
+scanner at the resolution of 3 mm isotropic voxels. During preprocessing, both
+datasets have been transformed to a common template (2.5 mm isotropic voxels),
+however, one dataset is down-sampled and the other one is up-sampled. Could
+differences in data acquisition and voxel resolution be a concern here?
+
+\textbf{Minor comments}:\par
+Preprocessing, first paragraph, line 4: were dropped to -> were dropped
+
+Event selection, last paragraph, line 5: compute -> computed
+
+Hemodynamic modeling: what do you mean by the six participant regressor?
+
+Results, first paragraph (and in two other instances): can found -> can be found
+
+Control contrasts, first paragraph, line 2: finds -> findings
+}
 

### 2021-08-03 code/generate-masks.py
update scripts

@@ -33,7 +33,7 @@ def parse_arguments():
 
     parser.add_argument('-out',
                         required=False,
-                        default='',
+                        default='rois-and-masks',
                         help='the output directory (e.g. "rois-and-masks")')
 
     args = parser.parse_args()
@@ -340,7 +340,7 @@ if __name__ == "__main__":
     subjs = [re.search(r'sub-..', string).group() for string in aoFpathes]
     subjs = sorted(list(set(subjs)))
 
-    for subj in subjs[7:8]:
+    for subj in subjs:
         print('\nProcessing', subj)
         # 1. create bilateral, probabilistic & binarized PPA masks
         # from group masks (in group space)
@@ -504,6 +504,51 @@ if __name__ == "__main__":
             ['applywarp',
              '-i', inFpath,
              '-o', os.path.join(out_path, 'ao-cope1-grp.nii.gz'),
+             '-r', highres_ref,
+             '-w', templ2subjWarp,
+             f'--postmat={postmat}',
+             '--interp=nn'  # nearest neighbour
+             ])
+
+
+        # movie's contrast 1 (z=2.3) from bold3Tp2 to t1w
+        inFpath = AV_ZMAP_PATTERN.replace('sub-??', subj).replace('cope*', 'cope1')
+        inFpath = inFpath.replace('stats/zstat1.nii.gz', 'thresh_zstat1.nii.gz')
+
+        if not os.path.exists(inFpath):
+                subprocess.call(['datalad', 'get', inFpath])
+
+        print('\nconvert movie\'s primary COPE from bold3Tp2 to t1w')
+        subprocess.call(
+            ['flirt',
+             '-in', inFpath,
+             '-out', os.path.join(out_path, 'av-cope1-ind.nii.gz'),
+             '-ref', highres_ref,
+             '-applyxfm',
+             '-init', in_matrix,
+             '-interp', 'nearestneighbour'
+             # '--premat=premat'
+             ]
+        )
+
+        # movie's contrast 1 (z=3.4) from grpbold3Tp2 to t1w
+        print('\nconvert movie\'s primary COPE from grpbold3Tp2 to t1w')
+
+        # define inputs
+        inFpath = inFpath.replace('-ind', '-grp')
+        in_matrix = os.path.join(TNT_DIR, subj, 't1w/in_mni152/tmpl2subj.mat')
[…]

### 2021-08-03 code/plot-group-and-individuals.py

@@ -198,7 +198,7 @@ def process_stability(ao_prob, av_prob, outfpath):
     cax1 = fig.add_subplot(grid[12:13, 6:11])
     cmap = mpl.cm.Blues
     cmap = cmap.reversed()
-    norm = mpl.colors.Normalize(vmin=0, vmax=8)
+    norm = mpl.colors.Normalize(vmin=1, vmax=8)
     cb1 = mpl.colorbar.ColorbarBase(cax1,
                                     cmap=cmap,
                                     norm=norm,
@@ -212,7 +212,7 @@ def process_stability(ao_prob, av_prob, outfpath):
     cax2 = fig.add_subplot(grid[13:14, 6:11])
     cmap = mpl.cm.YlOrRd
     cmap = cmap.reversed()
-    norm = mpl.colors.Normalize(vmin=0, vmax=8)
+    norm = mpl.colors.Normalize(vmin=1, vmax=8)
     cb2 = mpl.colorbar.ColorbarBase(cax2,
                                     cmap=cmap,
                                     norm=norm,
@@ -220,7 +220,7 @@ def process_stability(ao_prob, av_prob, outfpath):
 
     # ticklabels and edge of the colorbar
     cax2.tick_params(colors='w')
-    cax2.xaxis.set_ticks(list(range(9)))
+    cax2.xaxis.set_ticks(list(range(1,9)))
     cb2.set_label('number of contrasts', color='w')
     cb2.outline.set_edgecolor('w')
 
@@ -271,7 +271,7 @@ def plot_stability_slice(mode, coord,
     display.add_overlay(movie_img,
                         threshold=0,
                         cmap=colorMap,
-                        vmin=0,
+                        vmin=1,
                         vmax=8,
                         alpha=1)
 
@@ -281,7 +281,7 @@ def plot_stability_slice(mode, coord,
     display.add_overlay(audio_img,
                         threshold=0,
                         cmap=colorMap,
-                        vmin=0,
+                        vmin=1,
                         vmax=8,
                         alpha=1)
 
@@ -354,9 +354,9 @@ def process_group_averages(outfpath):
     legendAxis = fig.add_subplot(grid[12:, :6])
 
     blue = mpl.patches.Patch(color='#2474b7',
-                             label='geo, groom > all non-geo (audio-description)')
+                             label='audio contrast \'geo, groom > all non-geo\'')
     red = mpl.patches.Patch(color='#f03523',
[…]

### 2021-08-03 code/plot-surface-maps.py

@@ -4,61 +4,41 @@ created on Mon June 07 2021
 author: Christian Olaf Haeusler
 
 ToDo:
-    - pip install scikit-image nibabel matplotlib numpy
-    - outlines of individual PPAs is not individually thresholded
+    - https://matplotlib.org/2.0.2/users/tight_layout_guide.html
+    - plt.savefig(pad_inches=0) vs.  bbox_inches='tight'
+    - contrained layout?
 
 '''
 
+
 import argparse
-from glob import glob
+import math
 import matplotlib as mpl
 import matplotlib.pyplot as plt
-import nibabel as nib
 import numpy as np
 import os
 import re
 import subprocess
+from glob import glob
+from nilearn import plotting
+from os.path import join as opj
 
-# underlying anatomical HD image
-anatImg = '/usr/share/data/fsl-mni152-templates/MNI152_T1_0.5mm.nii.gz'
-
-# T2* EPI group FoV
-audioMask = 'rois-and-masks/fov_tmpl_0.5.nii.gz'
-
-# PPA group masks co-registered to MNI152
-PROB_MASK_GRP = 'rois-and-masks/bilat_PPA_prob.nii.gz'
-BIN_MASK_GRP = 'rois-and-masks/bilat_PPA_binary.nii.gz'
-
-# contrasts for audio-only stimulus
-AO_COPE_PATTERN = 'inputs/studyforrest_ppa/3rd-lvl/'\
-    'audio-ppa_c?_z3.4.gfeat/cope1.feat/thresh_zstat1.nii.gz'
-# first six contrasts aim for PPA, rest are control contrasts
-AO_PPA_COPES = range(1, 9)
-# primary PPA contrast
-AUDIO_GRP = AO_COPE_PATTERN.replace('c?', 'c1')
-
-# contrasts of audio-visual stimulus
-AV_COPE_PATTERN = 'inputs/studyforrest_ppa/3rd-lvl/'\
-    'movie-ppa_c?_z3.4.gfeat/cope1.feat/thresh_zstat1.nii.gz'
-# first five contrasts aim for PPA, rests are control contrasts
-AV_PPA_COPES = range(1, 6)
-# primary PPA CONTRAST
-MOVIE_GRP = AV_COPE_PATTERN.replace('c?', 'c1')
-
[…]

### 2021-08-03 paper/main.tex
re-order sections (& minor tweaks)

--- 2021-03-01 paper/main.tex
@@
 %
-The same 14 subjects were watching a Hollywood movie and listening to its audio-description as part of the open-data resource \textit{studyforrest.org}.
+The same 14 participants were watching a Hollywood movie and listening to its audio-description as part of the open-data resource \textit{studyforrest.org}.
 % auditory localizer?
@@
 
-\section*{Keywords}
+%\section*{Keywords}
 % maximal 8
-fMRI, naturalistic stimulus, spatial perception, vision, language, speech,
-narrative, studyforrest
+% fMRI, naturalistic stimulus, spatial perception, vision, language, speech, narrative, studyforrest
 
 \pagebreak[4]
+
+\todo[inline]{\textbf{My notes:}\par
+    1. change url(s) of datasets\par
+}
 
@@
 %% anterior vs. posterior
-%On both a group and individual subject level, the comparison of results from the
+%On both a group and individual participant level, the comparison of results from the
 %three datasets also suggests functional differences between the anterior and
@@
 %Lastly, our results suggest that the PPA's anterior part can be localized in
-%individual subjects by contrasting high-level semantic information occurring in
+%individual participants by contrasting high-level semantic information occurring in
 %an auditory naturalistic stimulus.
-
-\section*{Methods}
-
-% Specific data outputs should be explicitly referenced via data
-% citation (see Data Records and Data Citations, below)}
-
-% intro
-We used three components of the publicly available
-\href{http://www.studyforrest.org}{studyforrest.org} dataset that has
-been repeatedly used by other research groups in independent studies
-(\citep[e.g.,][]{ben2018hippocampal, jiahui2019predicting, hu2017decoding,
-lettieri2019emotionotopy, nguyen2016integration}).
-% used studies
-The same participants were
-% AD
-a) listening to the audio-description \citep{hanke2014audiomovie} of
-the movie ``Forrest Gump'',
-% AV
-b) watching the audio-visual movie \citep{hanke2016simultaneous}, and
-% VIS
-c) participating in a dedicated six-category block-design visual localizer \citep{sengupta2016extension}.
-% see corresponding papers for details
-An exhaustive description of the participants, stimulus creation, procedure,
-stimulation setup, and fMRI acquisition can be found in the corresponding
-publications. Following is a summary of the most important aspects.
-
-\subsection*{Participants}
-% AD study
-In the audio-description study \citep{hanke2014audiomovie}, 20 German native
-speakers (all right-handed, age 21–38 years, mean age 26.6 years, 12 male)
-listened to the German audio-description \citep{ForrestGumpGermanAD} of the
-movie ``Forrest Gump'' \citep{ForrestGumpMovie}.
-% AV study
-In the movie study \citep{hanke2016simultaneous}, 15 participants (21–39 years,
-mean age 29.4, six female), a subgroup of the prior audio-description study,
-watched the audio-visual movie with dubbed German audio track
-\citep{ForrestGumpDVD}.
-% VIS study
-In the block-design localizer study \citep{sengupta2016extension}, the same 15
-participants took part in a six-category block-design visual localizer.
-% participants' health
-All participants reported to have normal hearing, normal or corrected-to-normal
-vision, and no known history of neurological disorders.
-% compensation, consent and shit
-In all studies, participants received monetary compensation and gave written
-informed consent for their participation and for public sharing of obtained data
-in anonymized form. The studies had prior approval by the Ethics Committee of
-Otto-von-Guericke University of Magdeburg, Germany.
-
-\subsection*{Stimuli and Procedure}
-
-% AD & AV stimulus name & references
-The German DVD release \citep{ForrestGumpDVD} of the movie ``Forrest Gump''
-\citep{ForrestGumpMovie} and its temporally aligned audio-description
-\citep{ForrestGumpGermanAD} served as naturalistic stimuli, with an approximate
-duration of two hours, split into eight consecutive segments of
-\unit[$\approx$15]{minutes}.
-% AD: additional narrator
-The audio-description adds another male narrator to the voice-over narration of
-the main character Forrest Gump. This additional narration describes essential
-aspects of the visual scenery when there is no off-screen voice, dialog, or
-other relevant auditory content.
-% task
-For all sessions with naturalistic stimuli, participants were instructed to
-inhibit physical movements except for eye-movements, and otherwise to simply
-``enjoy'' the presentation.
-%
-For details on stimulus creation and presentation see
-\citet{hanke2014audiomovie,hanke2016simultaneous}.
-
-% VIS study picture categories
-Stimuli for the block-design localizer study were 24 unique grayscale images of
-faces, bodies, objects, houses, outdoor scenes and scrambled images, matched in
-luminance and size, that were previously used in other studies
-(\citep[e.g.,][]{haxby2011common}).
-% procedure: presentation & instructions
-Participants performed a one-back image matching task for four block-design
-runs, with two \unit[16]{s} blocks per stimulus category in each run.
-%
-For details on stimulus creation and presentation see
-\citet{sengupta2016extension}.
-
-\subsection*{Stimulation setup}
-
-% AD
-In the audio-description study, visual instructions were presented on a
-rear-projection screen inside scanner bore. During the functional scans, the
-projector presented a medium gray screen with the primary purpose to illuminate
-a participant's visual field in order to prevent premature fatigue.
-% AV & VIS
-In the movie and block-design localizer study, visual instructions and stimuli
-were presented on a rear-projection screen
-% screen size \unit[23.75 $\times$ 10.25]{cm}
-at a viewing distance of \unit[63]{cm}, with a movie frame projection size of
-approximately \unit[21.3]$^{\circ}$ $\times$ \unit[9.3]$^{\circ}$.
-% angle of view: VIS
-In the block-design localizer study, stimulus images were displayed at a size of
-approximately \unit[10]$^{\circ}$ $\times$ \unit[10]$^{\circ}$ of visual angle.
-% AD & AV: auditory stimulation
-Auditory stimulation was implemented using custom in-ear (audio-description), or
-over-the-ear headphones (movie), which reduced the scanner noise by at least
-\unit[20–30]{dB}.
-
-\subsection*{fMRI data acquisition}
-
-Gradient-echo fMRI data for the audio-description study were acquired using a
-\unit[7]{Tesla} Siemens MAGNETOM magnetic resonance scanner equipped with a 32
-channel brain receive coil at \unit[2]{s} repetition time (TR) with 36 axial
-slices (thickness \unit[1.4]{mm}, \unit[1.4 $\times$ 1.4]{mm} in-plane
-resolution, \unit[224]{mm} field-of-view, anterior-to-posterior phase encoding
-direction) and a \unit[10]{\%} inter-slice gap, recorded in ascending order.
-% slice orientation
-Slices were oriented to include the ventral portions of frontal and occipital
-cortex while minimizing intersection with the eyeballs.
-% FOV
-The field of view was centered on the approximate location of Heschl's gyrus.
-% motion correction
-EPI images were online-corrected for motion and geometric distortions.
-
-% AV & VIS
-In the movie and block-design localizer study, a \unit[3]{Tesla} Philips Achieva dStream
-MRI scanner with a 32 channel head coil acquired gradient-echo fMRI data
-at \unit[2]{s} repetition time with
-% slices
-35 axial slices (thickness \unit[3.0]{mm}, \unit[10]{\%} inter-slice gap) with
-\unit[80 $\times$ 80]{voxels} (\unit[3.0 $\times$ 3.0]{mm} of in-plane
-resolution, \unit[240]{mm} field-of-view) and an anterior-to-posterior phase
-encoding direction, recorded in ascending order.
-% no. of volumes
-A total of 3599 volumes were recorded for each participant in each of the
-naturalistic stimulus paradigms (audio-description and movie).
-
-\subsection*{Preprocessing}
-
-% data sources
-% https://github.com/psychoinformatics-de/studyforrest-data-aligned/tree/master/code
-% https://github.com/psychoinformatics-de/studyforrest-data-templatetransforms}
-The current analyses were carried out on the same preprocessed fMRI data that were used
-for the technical validation analysis presented in \citet{hanke2016simultaneous}, and available from \href{https://github.com/psychoinformatics-de/studyforrest-data-aligned}{github.com/ psychoinformatics-de/studyforrest-data-aligned}.
-Of those 15 participants in the studyforrest dataset that took
-part in all three experiments,
-% exclusion of VP 10
-data of one participant were dropped to due to invalid distortion correction
-during scanning of the audio-description stimulus.
-Data were corrected for motion, aligned with and re-sliced onto a
-participant-specific BOLD template image \citep{sengupta2016extension}
-(uniform spatial resolution of \unit[2.5$\times$2.5$\times$2.5]{mm} for both
-audio-description and movie data).
-% preprocessing intro
-Preprocessing was performed by FEAT v6.00 (FMRI Expert Analysis Tool \citep{woolrich2001autocorr}) as shipped with
-FSL v5.0.9 (\href{https://www.fmrib.ox.ac.uk/fsl}{FMRIB's Software Library}
- \citep{smith2004fsl}) on a computer-cluster running
-\href{http://neuro.debian.net}{NeuroDebian} \citep{halchenko2012open}.
-
-% temporal filtering
-For the present analysis, the following additional preprocessing was performed.
-High-pass temporal filtering was applied to every stimulus segment using a
-Gaussian-weighted least-squares straight line with a cutoff period of
-\unit[150]{s} (sigma=\unit[75.0]{s}) to remove low-frequency confounds.
-% brain extraction
-The brain was extracted from surrounding tissues using BET \citep{smith2002bet}.
-% spatial smoothing
-Data were spatially smoothed applying a Gaussian kernel with full width at half
-maximum (FWHM) of \unit[4.0]{mm}.
-% normalization
-A grand-mean intensity normalization of the entire 4D dataset was performed by a
-single multiplicative factor.
-% pre-whithening
-Correction for local autocorrelation in the time series (prewhitening) was
-applied using FILM (FMRIB's Improved Linear Model \citep{woolrich2001autocorr})
-to improve estimation efficiency.
-
-\subsection*{Event selection}
-
-% traditionally
-In contrast to stimuli designed to trigger a perceptual process of interest,
-while controlling for confounding variables (e.g., color and luminance),
-% our approach: annotation and regressors
-naturalistic stimuli have a fixed but initially unknown temporal structure of
-stimulus features of interest, as well as an equally unknown confound structure.
-% annotation ftw
-In order to evaluate the suitability of the stimulus for the targeted analyses,
-and to inform the required hemodynamic models, we annotated the temporal
-structure of a range of stimulus features.
-
-% AV anno
-For the analysis of the movie stimulus, we took advantage of a previously
-published annotation of 869 movie cuts and the depicted location after each cut
-\citep{haeusler2016cutanno}.
-% we focus on cuts
-Contrary to manually annotating stimulus features of movie frames (for example, as
-performed by \citet{bartels2004mapping} for color, faces, language, and
-human bodies), we categorized movie cuts that - in general - realign the viewer
-within the movie environment by switching to another perspective within the
-same setting, or to a position in an entirely different setting.
-% this this should work
-More specifically, we sought to exploit a cinematographic bias as
-% establishing shots & shots within setting early in the movie
-at a setting's first occurrence in a movie, shots tend to broadly establish the
-setting and the spatial layout within the setting.
-% cut to recurrent scene
-On revisiting an already established setting, the field sizes of movie shots
-tend to decrease, and shots tend to more often depict people talking to each
-other or objects that are relevant to the evolved plot
-\citep{brown2012cinematography, katz1991film, mascelli1998five}.
-
-% AV regressors/events
-Based on this cinematographic bias, we assigned each cut to one of five
-categories (see Table~\ref{tab:events}):
-%
-1) a cut switching to a setting that was depicted for the first time
-(\texttt{vse\_new}),
-%
-2) a cut switching to a setting that was already depicted earlier in the movie
-(\texttt{vse\_old}),
-%
-3) a cut switching to another locale within a setting (\texttt{vlo\_ch}; e.g. a
-cut from the first to the second floor in Forrest's house),
-%
-4) a cut to another camera position within a setting or locale that was depicted
-for the first time (\texttt{vpe\_new}), and
-%
-5) a cut to another camera position within a setting or locale that was already
-depicted before (\texttt{vpe\_old}).
-% irrespective of visual content
-Note that this categorization is not necessarily evident from the visual content
-of the first movie frame after a cut.
-% neuroscientific rationale The neuroscientific rationale was that activity in
-% the PPA is greater when participants view novel versus repeated scenes or
-% view-points \citep{epstein1999parahippocampal, grill2006repetition}.  no cut
-% condition: intro
-As a control condition with events of no particular processing of spatial
-information (\texttt{no\_cut}) we pseudo-randomly selected movie frames from
-continuous movie shots that lasted longer than \unit[20]{s}, and
-% no cuts: how
-had a minimum temporal distance of at least \unit[10]{s} to any movie cut and to
-any other \texttt{no\_cut} event.
-
-% AV regressors
-\begin{table*}[tbp]
-    \caption{Overview of event categories of the audio-visual
-    movie and the audio-description.
-    Event categories of the movie are based on an annotation of cuts and
-    depicted locations.
-    Event categories of the audio-description are based on an annotation of
-    nouns spoken by the audio-description's narrator
-    (see Table~\ref{tab:descr-nouns-rules}).
-    Some of the audio-description's event categories listed here
-    (\texttt{sex\_f}; \texttt{sex\_m}; \texttt{fahead}, \texttt{object})
-    were created by pooling some categories of the original annotation of nouns
-    (female, females, fname; male, males, mname; face, head; object, objects).
-    Respective event counts are given for the whole stimulus (\texttt{All}) and
-    the segments that were used for the eight sessions of fMRI scanning.
-    Event counts for frame-based features are reported in units of a thousand.
-    %\texttt{fg\_av\_ger\_pd} (perceptual differences of consecutive frames),
-    %\texttt{fg\_av\_ger\_ml} (mean luminance of a frame),
-    %\texttt{fg\_av\_ger\_lr} (difference in mean luminance of left and right
-    %half),
-    %\texttt{fg\_av\_ger\_ud} (difference in mean luminance of upper and
-    %lower half),
-    %\texttt{fg\_av\_ger\_lrdiff} (left-right volume difference), and
-    %\texttt{fg\_av\_ger\_rms} (root mean square volume) represent one event
-    %for every movie frame (\unit[40]{ms}).
-    % For description of the two event categories of the audio-description's
-    % narrator (\texttt{se\_new} and \texttt{se\_old}) to build contrast of
-    % negative control Tab.~\ref{tab:events}.
-    }
-\label{tab:events}
-\resizebox{\linewidth}{!}{
-\footnotesize
-\begin{tabular}{lp{3.7cm}lllllllll} \toprule \textbf{Label} & \textbf{Description} & \textbf{All} & \textbf{1} & \textbf{2} & \textbf{3} & \textbf{4} & \textbf{5} & \textbf{6} & \textbf{7} & \textbf{8} \\
-\midrule
-\multicolumn{3}{l}{\textit{Movie stimulus}}\\
-\texttt{vse\_new} &  change of the camera position to a setting not depicted before & \aoVsenewAll & \aoVsenewI & \aoVsenewII & \aoVsenewIII & \aoVsenewIV & \aoVsenewV & \aoVsenewVI & \aoVsenewVII & \aoVsenewVIII
-\tabularnewline
-\texttt{vse\_old} & change of the camera position to a recurring setting & \aoVseoldAll & \aoVseoldI & \aoVseoldII & \aoVseoldIII & \aoVseoldIV & \aoVseoldV & \aoVseoldVI & \aoVseoldVII & \aoVseoldVIII
-\tabularnewline
-\texttt{vlo\_ch} & change of the camera position to another locale within the same setting & \aoVlochAll & \aoVlochI & \aoVlochII & \aoVlochIII & \aoVlochIV & 0 & \aoVlochV & \aoVlochVI & \aoVlochVII
-\tabularnewline
-\texttt{vpe\_new} & change of the camera position within a locale not depicted before & \aoVpenewAll & \aoVpenewI & \aoVpenewII & \aoVpenewIII & \aoVpenewIV & \aoVpenewV & \aoVpenewVI & \aoVpenewVII & \aoVpenewVIII
-\tabularnewline
-% vpe_old has no events in 3. So the indices are shifted
-\texttt{vpe\_old} & change of the camera position within a recurring locale &
-\aoVpeoldAll & \aoVpeoldI & \aoVpeoldII & 0 & \aoVpeoldIII & \aoVpeoldIV &
-\aoVpeoldV & \aoVpeoldVI & \aoVpeoldVII
-\tabularnewline
-\texttt{vno\_cut} & frames within a continuous movie shot & \avVnocutAll & \avVnocutI & \avVnocutII & 0 & \avVnocutIII & \avVnocutIV & \avVnocutV & \avVnocutVI & \avVnocutVII
-\tabularnewline
-% se\_new & control for AD narrator & \aoSenewAll & \aoSenewI & \aoSenewII & \aoSenewIII & \aoSenewIV & \aoSenewV & \aoSenewVI & \aoSenewVII & \aoSenewVIII
-% \tabularnewline
-% se\_old & control for AD narrator & \aoSeoldAll & \aoSeoldI & \aoSeoldII & \aoSeoldIII & \aoSeoldIV & \aoSeoldV & \aoSeoldVI & \aoSeoldVII & \aoSeoldVIII
-% \tabularnewline
-\texttt{fg\_av\_ger\_lr} & left-right luminance difference & \avFgavgerlrAll & \avFgavgerlrI & \avFgavgerlrII & \avFgavgerlrIII & \avFgavgerlrIV & \avFgavgerlrV & \avFgavgerlrVI & \avFgavgerlrVII & \avFgavgerlrVIII
-\tabularnewline
-\texttt{fg\_av\_ger\_lrdiff} & left-right volume difference & \avFgavgerlrdiffAll & \avFgavgerlrdiffI & \avFgavgerlrdiffII & \avFgavgerlrdiffIII & \avFgavgerlrdiffIV & \avFgavgerlrdiffV & \avFgavgerlrdiffVI & \avFgavgerlrdiffVII & \avFgavgerlrdiffVIII
-\tabularnewline
-\texttt{fg\_av\_ger\_ml} & mean luminance & \avFgavgermlAll & \avFgavgermlI & \avFgavgermlII & \avFgavgermlIII & \avFgavgermlIV & \avFgavgermlV & \avFgavgermlVI & \avFgavgermlVII & \avFgavgermlVIII
-\tabularnewline
-\texttt{fg\_av\_ger\_pd} & perceptual difference & \avFgavgerpdAll & \avFgavgerpdI & \avFgavgerpdII & \avFgavgerpdIII & \avFgavgerpdIV & \avFgavgerpdV & \avFgavgerpdVI & \avFgavgerpdVII & \avFgavgerpdVIII
-\tabularnewline
-\texttt{fg\_av\_ger\_rms} & root mean square volume & \avFgavgerrmsAll & \avFgavgerrmsI & \avFgavgerrmsII & \avFgavgerrmsIII & \avFgavgerrmsIV & \avFgavgerrmsV & \avFgavgerrmsVI & \avFgavgerrmsVII & \avFgavgerrmsVIII
-\tabularnewline
-\texttt{fg\_av\_ger\_ud} & upper-lower luminance difference & \avFgavgerudAll & \avFgavgerudI & \avFgavgerudII & \avFgavgerudIII & \avFgavgerudIV & \avFgavgerudV & \avFgavgerudVI & \avFgavgerudVII & \avFgavgerudVIII
-\tabularnewline
-\midrule
-\multicolumn{3}{l}{\textit{Audio-description stimulus}}\\
-\texttt{body} & trunk of the body; overlaid clothes & \aoBodyAll & \aoBodyI & \aoBodyII
-& \aoBodyIII & \aoBodyIV & \aoBodyV & \aoBodyVI & \aoBodyVII & \aoBodyVIII
-\tabularnewline
-\texttt{bpart} & limbs and trousers & \aoBpartAll & \aoBpartI & \aoBpartII & \aoBpartIII & \aoBpartIV & \aoBpartV & \aoBpartVI & \aoBpartVII & \aoBpartVIII
-\tabularnewline
-\texttt{fahead} & face or head (parts) & \aoFaheadAll & \aoFaheadI & \aoFaheadII & \aoFaheadIII & \aoFaheadIV & \aoFaheadV & \aoFaheadVI & \aoFaheadVII & \aoFaheadVIII
-\tabularnewline
-\texttt{furn} & moveable furniture (insides \& outsides) & \aoFurnAll & \aoFurnI & \aoFurnII & \aoFurnIII & \aoFurnIV & \aoFurnV & \aoFurnVI & \aoFurnVII & \aoFurnVIII
-\tabularnewline
-\texttt{geo} & immobile landmarks & \aoGeoAll & \aoGeoI & \aoGeoII & \aoGeoIII & \aoGeoIV & \aoGeoV & \aoGeoVI & \aoGeoVII & \aoGeoVIII
-\tabularnewline
-\texttt{groom} & rooms \& locales or geometry-defining elements & \aoGroomAll & \aoGroomI & \aoGroomII & \aoGroomIII & \aoGroomIV & \aoGroomV & \aoGroomVI & \aoGroomVII & \aoGroomVIII
-\tabularnewline
-\texttt{object} & countable entities with firm boundaries & \aoObjAll & \aoObjI & \aoObjII & \aoObjIII & \aoObjIV & \aoObjV & \aoObjVI & \aoObjVII & \aoObjVIII
-\tabularnewline
-\texttt{se\_new} & a setting occurring for the first time & \aoSenewAll & \aoSenewI & \aoSenewII & \aoSenewIII & \aoSenewIV & \aoSenewV & \aoSenewVI & \aoSenewVII & \aoSenewVIII
-\tabularnewline
-\texttt{se\_old} & a recurring setting & \aoSeoldAll & \aoSeoldI & \aoSeoldII & \aoSeoldIII & \aoSeoldIV & \aoSeoldV & \aoSeoldVI & \aoSeoldVII & \aoSeoldVIII
-\tabularnewline
-\texttt{sex\_f} & female person(s), name & \aoSexfAll & \aoSexfI & \aoSexfII & \aoSexfIII & \aoSexfIV & \aoSexfV & \aoSexfVI & \aoSexfVII & \aoSexfVIII
-\tabularnewline
-\texttt{sex\_m} & male person(s), name & \aoSexmAll & \aoSexmI & \aoSexmII & \aoSexmIII & \aoSexmIV & \aoSexmV & \aoSexmVI & \aoSexmVII & \aoSexmVIII
-\tabularnewline
-% vlo_ch has no events in segment 5. So indices are shifted
-%vse\_new & control for movie cut & \aoVsenewAll & \aoVsenewI & \aoVsenewII & \aoVsenewIII & \aoVsenewIV & \aoVsenewV & \aoVsenewVI & \aoVsenewVII & \aoVsenewVIII
-%\tabularnewline
-%vse\_old & control for movie cut & \aoVseoldAll & \aoVseoldI & \aoVseoldII & \aoVseoldIII & \aoVseoldIV & \aoVseoldV & \aoVseoldVI & \aoVseoldVII & \aoVseoldVIII
-%\tabularnewline
-%vlo\_ch & control for movie cut & \aoVlochAll & \aoVlochI & \aoVlochII & \aoVlochIII & \aoVlochIV & 0 & \aoVlochV & \aoVlochVI & \aoVlochVII
-%\tabularnewline
-%vpe\_new & control for movie cut & \aoVpenewAll & \aoVpenewI & \aoVpenewII & \aoVpenewIII & \aoVpenewIV & \aoVpenewV & \aoVpenewVI & \aoVpenewVII & \aoVpenewVIII
-%\tabularnewline
-% vpe_old has no events in 3. So the indices are shifted
-%vpe\_old & control for movie cut & \aoVpeoldAll & \aoVpeoldI & \aoVpeoldII & 0 & \aoVpeoldIII & \aoVpeoldIV & \aoVpeoldV & \aoVpeoldVI & \aoVpeoldVII
-% \tabularnewline
-\texttt{fg\_ad\_lrdiff} & left-right volume difference & \aoFgadlrdiffAll & \aoFgadlrdiffI & \aoFgadlrdiffII & \aoFgadlrdiffIII & \aoFgadlrdiffIV &
-\aoFgadlrdiffV & \aoFgadlrdiffVI & \aoFgadlrdiffVII & \aoFgadlrdiffVIII
-\tabularnewline
-\texttt{fg\_ad\_rms} & root mean square volume & \aoFgadrmsAll &
-\aoFgadrmsI & \aoFgadrmsII & \aoFgadrmsIII & \aoFgadrmsIV & \aoFgadrmsV &
-\aoFgadrmsVI & \aoFgadrmsVII & \aoFgadrmsVIII
-\tabularnewline
-\bottomrule
-\end{tabular}
-}%resizebox
-\end{table*}
-
-% AD annotation
-For the analysis of the audio-description stimulus, we extended a publicly
-available annotation of its speech content \citep{hausler2021studyforrest} by
-classifying concrete and countable nouns that the narrator uses to describe the
-movie's absent visual content.
-% annotation procedure
-An initial annotation was performed by one individual,
-% corrections
-and minor corrections were applied after comparing with a second categorization
-done by the author.
-% reference to table with rules and examples
-A complete overview of all 18 noun categories, their inclusion criteria, and
-examples can be seen in Table~\ref{tab:descr-nouns-rules}.
-% why and how of categories 1
-Some categories reflect the verbal counterpart of the stimulus categories that
-were used in the visual localizer experiment (e.g. \texttt{body}, \texttt{face},
-\texttt{head}, \texttt{object}, \texttt{setting\_new}, and
-\texttt{setting\_rec}).
-% why and how of categories 2
-Other categories were created to semantically cluster remaining nouns into
-categories that had no counterpart in the visual localizer experiment (e.g.
-\texttt{bodypart}, \texttt{female}, \texttt{fname}, \texttt{furniture},
-\texttt{geo}, \texttt{groom}, \texttt{male}, and \texttt{persons}).
-% categories in detail
-%Nouns were categorized by the verbal clue they provide about the
-%cinematographic scene's environment (\texttt{geo}, \texttt{groom};
-%\texttt{setting\_new}, \texttt{setting\_old}), its inherent persons (e.g.
-%\texttt{female}, \texttt{male}, \texttt{persons}), a person's body or worn
-%clothes (\texttt{face}, \texttt{head}, \texttt{body}, \texttt{bodypart}), and a
-%scene's inherent objects (\texttt{object}, \texttt{furniture}).  problem with
-%hierarchical categories
-The categories \texttt{setting\_new} and \texttt{setting\_rec} comprise not just
-words that describe a setting as a whole (e.g. ``[in] Greenbow'', ``[in a]
-disco'', ``[the platoon wades through a] rice field''). They also comprise words
-that could count as a member of another category in case the narrator uses these
-words to indicate a switch from one setting to another (e.g. ``[a] physician'').
-% how it was handled
-These nouns were flagged with both categories during the initial annotation
-procedure. In context of the current analyses these word are considered to
-belong exclusively to the higher-level category of changing a setting
-(\texttt{setting\_new} or \texttt{setting\_rec}).
-% pooling of categories
-Some noun categories that were semantically similar and offered only a small
-amount of counts were pooled resulting in 11 final event categories
-(see Table~\ref{tab:events}).  These event categories were then used to model
-hemodynamic responses.
-
-% table for descriptive nouns: categories, rules, examples counts
-\begin{table*}[tbp]
-    \caption{Categories and criteria to categorize the nouns spoken by
-        the audio-description's narrator.
-        Examples are given in English.
-        Some of these initial 18 noun categories were pooled resulting in 11
-        event categories that served as basis to build the regressors of the
-        GLM
-        (see Table~\ref{tab:events}).
-        % The category \texttt{++} also contains adverbial of time.
-}
-\label{tab:descr-nouns-rules}
-\resizebox{\linewidth}{!}{
-\begin{tabular}{lp{61mm}p{61mm}}
-\toprule
-\textbf{Category} & \textbf{Criteria} & \textbf{Examples} \\
-\midrule
-\texttt{body} & trunk of the body; possibly clothed & back, hip, shoulder; jacket, dress, shirt
-\tabularnewline
-\texttt{bodypart} & limbs & arm, finger, leg, toe
-\tabularnewline
-\texttt{face} & face or parts of it & face, ear, nose, mouth
-\tabularnewline
-\texttt{female} & female person & nurse, mother, woman
-\tabularnewline
-\texttt{females} & female persons & women
-\tabularnewline
-\texttt{fname} & female name & Jenny
-\tabularnewline
-\texttt{furniture} & movable furniture (insides \& outsides) & bench, bed, table, chair
-\tabularnewline
-\texttt{geo} & immobile landmarks & building, tree, street, alley, meadow, cornfield
-\tabularnewline
-\texttt{groom} & rooms \& locales, or geometry-defining elements & living room; wall, door, window, floor
-\tabularnewline
-\texttt{head} & non-face parts of the head; worn headgear & head, hair, ear, neck;
-helmet
-\tabularnewline
-\texttt{male} & male person & man, father, soldier
-\tabularnewline
-\texttt{males} & male persons & boys, opponents
-\tabularnewline
-\texttt{mname} & male name & Bubba, Kennedy
-\tabularnewline
-\texttt{object} & countable entity with firm boundaries & telephone, car
-\tabularnewline
-\texttt{objects} & countable entities & wheels, plants
-\tabularnewline
-\texttt{persons} & concrete persons of unknown sex & hippies, patients
-\tabularnewline
-\texttt{setting\_new} & a setting occurring for the first time & on a ``bridge'', on an ``alley'', on ``campus''
-\tabularnewline
-\texttt{setting\_rec} & a recurring setting & at the ``bus stop'' \tabularnewline
-% ++ & cue regarding time & in the ``evening'', it's ``daytime'', ``later'' \tabularnewline
-\bottomrule
-\end{tabular}
-}%resizebox
-\end{table*}
-
-% low-level confounds: intro
-Lastly, we algorithmically annotated the temporal structure of low-level
-perceptual features to create nuisance regressors.
-% visual shit
-For the movie stimulus, we computed the mean luminance (arbitrary units,
-average pixel brightness) of a movie frame (\unit[40]{ms}), the difference in
-mean luminance of each frame's left and right half, the difference in mean
-luminance of the lower and upper half.  As an indicator of visual change, we
-compute perceptual fingerprints for each movie frame using the pHash library
-\citep{zauner2010implementation} and recorded the cumulative bitwise
-difference to the previous frame.
-% auditory shit
-Finally for both audio tracks, we computed the left-right difference in volume
-and root mean square volume averaged across the length of every movie frame
-(\unit[40]{ms}).
-
-\subsection*{Hemodynamic Modeling}
-
-% movie events
-The events of the movie cut related categories and \texttt{no\_cut} events were
-modeled as box car events of \unit[200]{ms} duration,
-%
-speech events from onset to offset of each word, and frame-based confounds from
-onset to offset of the corresponding movie frame.
-% convolving
-For all regressors, the stimulus models were convolved with a double-gamma
-hemodynamic response function (HRF), as implemented in FSL.
-
-% we checked correlations
-Given the unknown confound structure of the naturalistic stimuli, we inspected
-% correlations within stimuli and across stimuli
-the correlation of regressors of each stimulus and
-also across both stimuli (see Figure~\ref{fig:reg-corr}).
-% correlations within each stimulus
-The computed Pearson correlation coefficients show only minor correlations of
-feature regressors for the same stimulus.
-% (highest) correlations across stimuli; \texttt{fg\_a(v|d)\_ger\_rms}, r=.76;
-% \texttt{fg\_a(v|d)\_ger\_lrdiff}, r=.77)
-Maximum correlations are found for low-level auditory confounds across
-stimuli,
-% no surprise
-which is to be expected, as the audio-description contains the audio track of
-the movie plus the additional narrator (see Figure~\ref{fig:reg-corr}; correlation
-between root mean square volume of both audio tracks, r=.76; correlation between
-left-right volume difference of both audio tracks, r=.77).
-% encouraged by that we build contrasts (statement)
-The observed correlation pattern did not indicate problematic confounds of
-nuisance variables and regressors of interest for any of the planned analyses.
-
-\begin{figure*}[tbp]
-\centering
-    \includegraphics[width=\linewidth]{figures/regressor-corr} \caption{Pearson
-        correlation coefficients of model response time series used as regressors in
-        the GLM analysis of the
-        audio-description (blue; see Table~\ref{tab:events} for a
-        description) and audio-visual movie (red; see Table~\ref{tab:events}).
-        Values are rounded to the nearest tenth.
-        The correlation between the two stimuli's
-        root mean square volume and between their left-right difference in
-        volume yielded the highest correlation values
-        (\texttt{fg\_ad\_rms} and \texttt{fg\_av\_ger\_rms}, r=.7635;
-        \texttt{fg\_ad\_lrdiff} and \texttt{fg\_av\_ger\_lrdiff}, r=.7749).
-      }
-\label{fig:reg-corr}
-\end{figure*}
-
-% AV design matrix
-The design matrix for the first-level time-series GLM analysis of the movie
-comprised regressors for the 12 event categories of the movie listed in
-Table~\ref{tab:events}.
-% AD design matrix
-Similarly, the design matrix for the analysis of the audio-description comprised
-regressors for the 13 event categories of the audio-description, also listed in
-Table~\ref{tab:events}.
-% AD regressors in AV
-In order to implement cross-modal control contrasts, the design matrix for the
-movie stimulus also contained the regressors based on nouns used by the
-audio-description's narrator to indicate a switch to another setting (categories
-\texttt{se\_new} and \texttt{se\_old}).
-% AV regressors in AV
-Likewise, the design matrix for the audio-description included the five movie
-cut related regressors (\texttt{vse\_new}, \texttt{vse\_old}, \texttt{vlo\_ch},
-\texttt{vp\_new}, \texttt{vpe\_old}).
-% both stimuli: null regressors
-For both stimuli, a null regressor was used for any event category in a segment
-for which no event of a category was present (e.g. no event of \texttt{vpe\_old}
-in segment 3; see Table~\ref{tab:events}).
-% temporal derivatives
-Temporal derivatives of all regressors were added to the design matrix to
-compensate for regional differences \citep{friston1998event}.
-% motion parameters
-Lastly, six participant and run specific motion estimates (translation and
-rotation) were also included.
-% high-pass filtering
-The design matrices were temporally filtered with the same high-pass filter
-(cutoff period of \unit[150]{s}) as the BOLD time series.
-
-\subsection*{Statistical analysis}
-
-% intro
-We performed standard two-level GLM analyses to aggregate results across all
-BOLD acquisition runs for every participant and each stimulus separately.
-% level 3
-Subsequently, we conducted third-level analyses to average contrast estimates
-over participants for each stimulus, respectively.
-
-% there isn't "the one road"
-Given the rich naturalistic stimuli and the availability of various stimulus
-feature annotations, there are several candidates for implementing contrasts to
-identify hemodynamic activity congruent with the hypothesized processing of
-spatial information in the PPA.
-% kind of arbitrary choice
-However, while the rationale for any contrast composition must be sound, the
-selection of a single implementation remains arbitrary to some degree.
-% hence, a couple of contrasts
-Consequently, we computed multiple contrasts that are listed in
-Table~\ref{tab:contrasts} for the movie and audio-description, respectively.
-% subjectively assessed balance
-For each stimulus, we picked a primary contrast for result presentation (marked
-  with an asterisk in the table) based on a subjectively assessed balance of how well
-the averaged events within categories represent spatial and non-spatial
-information, and the number of events in the stimulus.
-% reference to supplementals
-An evaluation of the robustness of these results with respect to similar but
-different contrasts is provided in the supplementary materials.
-
-% AV: primary contrast
-In the primary contrast for the movie stimulus, we contrasted cuts to a setting
-that was not depicted before (\texttt{vse\_new}) to cuts merely switching the
-camera position within a setting that was already established earlier in the
-movie (\texttt{vpe\_old}), because the former are designed to orient the viewer
-in the movie environment using wider-camera angles, whereas the latter can
-afford to depict details of a scene.
-% AD: primary contrast
-In the primary contrast of the audio-description stimulus, we contrasted
-mentions of buildings and landmarks (\texttt{geo}), and rooms and
-geometry-defining objects (\texttt{groom}) with nouns referring to a person's
-head or face (\texttt{fahead}), and other non-geometry related categories
-(\texttt{body}, \texttt{bodypart}, \texttt{fahead}, \texttt{object},
-\texttt{sex\_f}, \texttt{sex\_m}).
-% why furniture was not used
-The category ``furniture'' (\texttt{furn}) was not used as a regressor of
-interest in any contrast because these nouns could be perceived as either a
-geometry-defining scene element or as an isolated object.
-% why se_new & se_old were not used in the primary contrasts
-The categories of nouns indicating a switch to a setting that occurred for the
-first time (\texttt{se\_new}) or a setting that recurred during the plot
-(\texttt{se\_old}) were not included in the primary contrast because they
-comprise
-% heterogeneous category
-a)  nouns that could be a member of another category (e.g. ``[a]
-physician''), and
-% richness of verbal description vs. picture
-b) nouns that only vaguely identify a scene (e.g. ``[in] Greenbow'', ``[in a]
-disco'', ''[black and white] film recordings'') compared to perceptually richer
-descriptions.
-
-% control contrasts
-Finally, we created several control contrasts for both stimuli
-(see Table~\ref{tab:contrasts}).
-% AV: no cut > cut
-For the movie stimulus, four contrasts were created contrasting the no-cut
-regressor (\texttt{vno\_cut}) to cut-related regressors.
-% AV: narrator
-One contrast was created by contrasting nouns spoken by the (missing) narrator
-comparing nouns
-%
-that indicate a switch to another setting (\texttt{se\_new} >
-\texttt{se\_old}), and
-%
-that were moderately correlated with movie cuts indicating a
-switch to another setting (see Figure~\ref{fig:reg-corr}).
-% AD stimulus
-For the audio-description stimulus, we created five control contrasts to test if
-activation in the PPA was correlated with moments of cuts, despite the absence
-of visual stimulation.
-
-\begin{table*}[tbp]
-  \caption{Computed contrasts for the analysis of the movie and the audio
-    description, and their respective purpose.
-    The primary contrasts are marked with an asterisk.
-    \texttt{non-spatial} refers to the event categories
-    \texttt{body}, \texttt{bodypart}, \texttt{fahead},
-    \texttt{object}, \texttt{sex\_f}, \texttt{sex\_m}.
-    An explanation of all event categories can be found in
-    Table~\ref{tab:events}.
-    }
-\label{tab:contrasts}
-\begin{tabular}{lll}
-\toprule
-\textbf{Nr.} &  \textbf{Contrast} & \textbf{Purpose} \\
-\midrule
-\multicolumn{3}{l}{\textit{Movie stimulus}}\\
-1* & \texttt{vse\_new > vpe\_old} & spatial processing \tabularnewline
-2 & \texttt{vse\_new, vpe\_new > vse\_old, vpe\_old} & spatial processing \tabularnewline
-3 & \texttt{vse\_new > vse\_old} & spatial processing \tabularnewline
-4 & \texttt{vse\_new > vse\_old, vpe\_old} & spatial processing \tabularnewline
-5 & \texttt{vse\_new, vpe\_new > vpe\_old} & spatial processing \tabularnewline
-6 & \texttt{vno\_cut > vse\_new} & control \tabularnewline
-7 & \texttt{vno\_cut > vse\_old} & control \tabularnewline
-8 & \texttt{vno\_cut > vse\_new, vse\_old} & control \tabularnewline
-9 & \texttt{vno\_cut > vpe\_new, vpe\_old} & control \tabularnewline
-    10 & \texttt{se\_new > se\_old} & control (absent narrator) \tabularnewline
-\midrule
-\multicolumn{3}{l}{\textit{Audio-description stimulus}}\\
-1* & \texttt{geo, groom > non-spatial} & spatial processing \tabularnewline
-2 & \texttt{geo, groom, se\_new > non-spatial} & spatial processing \tabularnewline
-3 & \texttt{groom, se\_new, se\_old > non-spatial}  & spatial processing \tabularnewline
-4 & \texttt{geo > non-spatial} & spatial processing \tabularnewline
-5 & \texttt{groom > non-spatial} & spatial processing \tabularnewline
-6 & \texttt{se\_new > non-spatial} & spatial processing \tabularnewline
-7 & \texttt{se\_new, se\_old > non-spatial} & spatial processing \tabularnewline
-8 & \texttt{se\_new > se\_old} & spatial processing \tabularnewline
-9 & \texttt{vse\_new > vpe\_old} & control (absent visual cuts) \tabularnewline
-10 & \texttt{vse\_new, vpe\_new > vse\_old, vpe\_old} & control (absent visual cuts) \tabularnewline
-11 & \texttt{vse\_new > vse\_old} & control (absent visual cuts) \tabularnewline
-12 & \texttt{vse\_new > vse\_old, vpe\_old} & control (absent visual cuts) \tabularnewline
-13 & \texttt{vse\_new, vpe\_new > vpe\_old} & control (absent visual cuts) \tabularnewline
-\bottomrule
-\end{tabular}
-\end{table*}
-
-% alignments single subjects: 1st level
-First-level GLM analyses were performed in the image-space of a
-participant-specific BOLD T2* template using a previously determined linear
-transformation \citep{sengupta2016extension}.
-% subject template (for Bland-Altman-Plot of unthresholded maps)
-% \href{"https://github.com/psychoinformatics-de/studyforrest-data-templatetransforms/blob/master/sub-01/bold3Tp2/brain.nii.gz"}{example})
-% group template (for group and individual brain slices)
-For higher-level analyses image data were aligned with a study-specific T2*
-group template likewise using a previously computed non-linear transformation
-\citep{hanke2014audiomovie}.
-% https://github.com/psychoinformatics-de/studyforrest-data-templatetransforms/blob/master/templates/grpbold3Tp2/brain.nii.gz"
-% MNI152
-This group template was co-registered to the MNI 152 template with an affine
-transformation (12 degrees of freedom).
-
-% second level model
-The second-level analyses, which averaged contrast estimates over the eight
-stimulus segments, were carried out using a fixed effects model by forcing the
-random effects variance to zero in FLAME (FMRIB's Local Analysis of Mixed
-Effects \citep{beckmann2003general, woolrich2004multilevel}).
-% thresholding ($Z$>2.3 in subject-space; $Z$>3.4 in group space)
-(Gaussianised T/F) statistic images were thresholded using clusters determined
-by $Z$>3.4 and a cluster-corrected significance threshold of $p$=.05
-\citep{worsley2001statistical}.
-
-% third level model
-The third level analysis which averaged contrast estimates over participants was
-carried out using FLAME stage 1 with automatic outlier detection
-\citep{beckmann2003general, woolrich2004multilevel, woolrich2008robust}.
-% thresholding
-Here again, Z (Gaussianised T/F) statistic images were thresholded using
-clusters determined by $Z$>3.4 and a corrected cluster significance threshold of
-$p$=.05 \citep{worsley2001statistical}.
-% brain region identification
-Brain regions associated with observed clusters were determined with the Jülich
-Histological Atlas \citep{eickhoff2005toolbox, eickhoff2007assignment} and the
-Harvard-Oxford Cortical Atlas \citep{desikan2006automated} provided by FSL.
-% PPA masks
-Regions of interest (ROI) masks for individual PPAs and a PPA group mask of
-individual PPA overlaps were created from data provided by
-\citet{sengupta2016extension}.
 
@@
 
-\subsection*{Data and code availability}
+\section*{Methods}
+
+% Specific data outputs should be explicitly referenced via data
+% citation (see Data Records and Data Citations, below)}
+
+% intro
+We used three components of the publicly available
+\href{http://www.studyforrest.org}{studyforrest.org} dataset that has
+been repeatedly used by other research groups in independent studies
+(\citep[e.g.,][]{ben2018hippocampal, jiahui2019predicting, hu2017decoding,
+lettieri2019emotionotopy, nguyen2016integration}).
+% used studies
+The same participants were
+% AD
+a) listening to the audio-description \citep{hanke2014audiomovie} of
+the movie ``Forrest Gump'',
+% AV
+b) watching the audio-visual movie \citep{hanke2016simultaneous}, and
+% VIS
+c) participating in a dedicated six-category block-design visual localizer \citep{sengupta2016extension}.
+% see corresponding papers for details
+An exhaustive description of the participants, stimulus creation, procedure,
+stimulation setup, and fMRI acquisition can be found in the corresponding
+publications. Following is a summary of the most important aspects.
+
+\subsection*{Participants}
+% AD study
+In the audio-description study \citep{hanke2014audiomovie}, 20 German native
+speakers (all right-handed, age 21–38 years, mean age 26.6 years, 12 male)
+listened to the German audio-description \citep{ForrestGumpGermanAD} of the
+movie ``Forrest Gump'' \citep{ForrestGumpMovie}.
+% AV study
+In the movie study \citep{hanke2016simultaneous}, 15 participants (21–39 years,
+mean age 29.4, six female), a subgroup of the prior audio-description study,
+watched the audio-visual movie with dubbed German audio track
+\citep{ForrestGumpDVD}.
+% VIS study
+In the block-design localizer study \citep{sengupta2016extension}, the same 15
+participants took part in a six-category block-design visual localizer.
+% participants' health
+All participants reported to have normal hearing, normal or corrected-to-normal
+vision, and no known history of neurological disorders.
+% compensation, consent and shit
+In all studies, participants received monetary compensation and gave written
+informed consent for their participation and for public sharing of obtained data
+in anonymized form. The studies had prior approval by the Ethics Committee of
+Otto-von-Guericke University of Magdeburg, Germany.
+
+\subsection*{Stimuli and Procedure}
+
+% AD & AV stimulus name & references
+The German DVD release \citep{ForrestGumpDVD} of the movie ``Forrest Gump''
+\citep{ForrestGumpMovie} and its temporally aligned audio-description
+\citep{ForrestGumpGermanAD} served as naturalistic stimuli, with an approximate
+duration of two hours, split into eight consecutive segments of
+\unit[$\approx$15]{minutes}.
+% AD: additional narrator
+The audio-description adds another male narrator to the voice-over narration of
+the main character Forrest Gump. This additional narration describes essential
+aspects of the visual scenery when there is no off-screen voice, dialog, or
+other relevant auditory content.
+% task
+For all sessions with naturalistic stimuli, participants were instructed to
+inhibit physical movements except for eye-movements, and otherwise to simply
+``enjoy'' the presentation.
+%
+For details on stimulus creation and presentation see
+\citet{hanke2014audiomovie,hanke2016simultaneous}.
+
+% VIS study picture categories
+Stimuli for the block-design localizer study were 24 unique grayscale images of
+faces, bodies, objects, houses, outdoor scenes and scrambled images, matched in
+luminance and size, that were previously used in other studies
+(\citep[e.g.,][]{haxby2011common}).
+% procedure: presentation & instructions
+Participants performed a one-back image matching task for four block-design
+runs, with two \unit[16]{s} blocks per stimulus category in each run.
+%
+For details on stimulus creation and presentation see
+\citet{sengupta2016extension}.
+
+\subsection*{Stimulation setup}
+
+% AD
+In the audio-description study, visual instructions were presented on a
+rear-projection screen inside scanner bore. During the functional scans, the
+projector presented a medium gray screen with the primary purpose to illuminate
+a participant's visual field in order to prevent premature fatigue.
+% AV & VIS
+In the movie and block-design localizer study, visual instructions and stimuli
+were presented on a rear-projection screen
+% screen size \unit[23.75 $\times$ 10.25]{cm}
+at a viewing distance of \unit[63]{cm}, with a movie frame projection size of
+approximately \unit[21.3]$^{\circ}$ $\times$ \unit[9.3]$^{\circ}$.
+% angle of view: VIS
+In the block-design localizer study, stimulus images were displayed at a size of
+approximately \unit[10]$^{\circ}$ $\times$ \unit[10]$^{\circ}$ of visual angle.
+% AD & AV: auditory stimulation
+Auditory stimulation was implemented using custom in-ear (audio-description), or
+over-the-ear headphones (movie), which reduced the scanner noise by at least
+\unit[20–30]{dB}.
+
+\subsection*{fMRI data acquisition}
+
+Gradient-echo fMRI data for the audio-description study were acquired using a
+\unit[7]{Tesla} Siemens MAGNETOM magnetic resonance scanner equipped with a 32
+channel brain receive coil at \unit[2]{s} repetition time (TR) with 36 axial
+slices (thickness \unit[1.4]{mm}, \unit[1.4 $\times$ 1.4]{mm} in-plane
+resolution, \unit[224]{mm} field-of-view, anterior-to-posterior phase encoding
+direction) and a \unit[10]{\%} inter-slice gap, recorded in ascending order.
+% slice orientation
+Slices were oriented to include the ventral portions of frontal and occipital
+cortex while minimizing intersection with the eyeballs.
+% FOV
+The field of view was centered on the approximate location of Heschl's gyrus.
+% motion correction
+EPI images were online-corrected for motion and geometric distortions.
+
+% AV & VIS
+In the movie and block-design localizer study, a \unit[3]{Tesla} Philips Achieva dStream
+MRI scanner with a 32 channel head coil acquired gradient-echo fMRI data
+at \unit[2]{s} repetition time with
+% slices
+35 axial slices (thickness \unit[3.0]{mm}, \unit[10]{\%} inter-slice gap) with
+\unit[80 $\times$ 80]{voxels} (\unit[3.0 $\times$ 3.0]{mm} of in-plane
+resolution, \unit[240]{mm} field-of-view) and an anterior-to-posterior phase
+encoding direction, recorded in ascending order.
+% no. of volumes
+A total of 3599 volumes were recorded for each participant in each of the
+naturalistic stimulus paradigms (audio-description and movie).
+
+\subsection*{Preprocessing}
+
+% data sources
+% https://github.com/psychoinformatics-de/studyforrest-data-aligned/tree/master/code
+% https://github.com/psychoinformatics-de/studyforrest-data-templatetransforms}
+The current analyses were carried out on the same preprocessed fMRI data that were used
+for the technical validation analysis presented in \citet{hanke2016simultaneous}, and available from \href{https://github.com/psychoinformatics-de/studyforrest-data-aligned}{github.com/ psychoinformatics-de/studyforrest-data-aligned}.
+Of those 15 participants in the studyforrest dataset that took
+part in all three experiments,
+% exclusion of VP 10
+data of one participant were dropped to due to invalid distortion correction
+during scanning of the audio-description stimulus.
+Data were corrected for motion, aligned with and re-sliced onto a
+participant-specific BOLD template image \citep{sengupta2016extension}
+(uniform spatial resolution of \unit[2.5$\times$2.5$\times$2.5]{mm} for both
+audio-description and movie data).
+% preprocessing intro
+Preprocessing was performed by FEAT v6.00 (FMRI Expert Analysis Tool \citep{woolrich2001autocorr}) as shipped with
+FSL v5.0.9 (\href{https://www.fmrib.ox.ac.uk/fsl}{FMRIB's Software Library}
+ \citep{smith2004fsl}) on a computer-cluster running
+\href{http://neuro.debian.net}{NeuroDebian} \citep{halchenko2012open}.
+
+% temporal filtering
+For the present analysis, the following additional preprocessing was performed.
+High-pass temporal filtering was applied to every stimulus segment using a
+Gaussian-weighted least-squares straight line with a cutoff period of
+\unit[150]{s} (sigma=\unit[75.0]{s}) to remove low-frequency confounds.
+% brain extraction
+The brain was extracted from surrounding tissues using BET \citep{smith2002bet}.
+% spatial smoothing
+Data were spatially smoothed applying a Gaussian kernel with full width at half
+maximum (FWHM) of \unit[4.0]{mm}.
+% normalization
+A grand-mean intensity normalization of the entire 4D dataset was performed by a
+single multiplicative factor.
+% pre-whithening
+Correction for local autocorrelation in the time series (prewhitening) was
+applied using FILM (FMRIB's Improved Linear Model \citep{woolrich2001autocorr})
+to improve estimation efficiency.
+
+\subsection*{Event selection}
+
+% traditionally
+In contrast to stimuli designed to trigger a perceptual process of interest,
+while controlling for confounding variables (e.g., color and luminance),
+% our approach: annotation and regressors
+naturalistic stimuli have a fixed but initially unknown temporal structure of
+stimulus features of interest, as well as an equally unknown confound structure.
+% annotation ftw
+In order to evaluate the suitability of the stimulus for the targeted analyses,
+and to inform the required hemodynamic models, we annotated the temporal
+structure of a range of stimulus features.
+
+% AV anno
+For the analysis of the movie stimulus, we took advantage of a previously
+published annotation of 869 movie cuts and the depicted location after each cut
+\citep{haeusler2016cutanno}.
+% we focus on cuts
+Contrary to manually annotating stimulus features of movie frames (for example, as
+performed by \citet{bartels2004mapping} for color, faces, language, and
+human bodies), we categorized movie cuts that - in general - realign the viewer
+within the movie environment by switching to another perspective within the
+same setting, or to a position in an entirely different setting.
+% this this should work
+More specifically, we sought to exploit a cinematographic bias as
+% establishing shots & shots within setting early in the movie
+at a setting's first occurrence in a movie, shots tend to broadly establish the
+setting and the spatial layout within the setting.
+% cut to recurrent scene
+On revisiting an already established setting, the field sizes of movie shots
+tend to decrease, and shots tend to more often depict people talking to each
+other or objects that are relevant to the evolved plot
+\citep{brown2012cinematography, katz1991film, mascelli1998five}.
+
+% AV regressors/events
+Based on this cinematographic bias, we assigned each cut to one of five
+categories (see Table~\ref{tab:events}):
+%
+1) a cut switching to a setting that was depicted for the first time
+(\texttt{vse\_new}),
+%
+2) a cut switching to a setting that was already depicted earlier in the movie
+(\texttt{vse\_old}),
+%
+3) a cut switching to another locale within a setting (\texttt{vlo\_ch}; e.g. a
+cut from the first to the second floor in Forrest's house),
+%
+4) a cut to another camera position within a setting or locale that was depicted
+for the first time (\texttt{vpe\_new}), and
+%
+5) a cut to another camera position within a setting or locale that was already
+depicted before (\texttt{vpe\_old}).
+% irrespective of visual content
+Note that this categorization is not necessarily evident from the visual content
+of the first movie frame after a cut.
+% neuroscientific rationale The neuroscientific rationale was that activity in
+% the PPA is greater when participants view novel versus repeated scenes or
+% view-points \citep{epstein1999parahippocampal, grill2006repetition}.  no cut
+% condition: intro
+As a control condition with events of no particular processing of spatial
+information (\texttt{no\_cut}) we pseudo-randomly selected movie frames from
+continuous movie shots that lasted longer than \unit[20]{s}, and
+% no cuts: how
+had a minimum temporal distance of at least \unit[10]{s} to any movie cut and to
+any other \texttt{no\_cut} event.
+
+% AV regressors
+\begin{table*}[tbp]
+    \caption{Overview of event categories of the audio-visual
+    movie and the audio-description.
+    Event categories of the movie are based on an annotation of cuts and
+    depicted locations.
+    Event categories of the audio-description are based on an annotation of
+    nouns spoken by the audio-description's narrator
+    (see Table~\ref{tab:descr-nouns-rules}).
+    Some of the audio-description's event categories listed here
+    (\texttt{sex\_f}; \texttt{sex\_m}; \texttt{fahead}, \texttt{object})
+    were created by pooling some categories of the original annotation of nouns
+    (female, females, fname; male, males, mname; face, head; object, objects).
+    Respective event counts are given for the whole stimulus (\texttt{All}) and
+    the segments that were used for the eight sessions of fMRI scanning.
+    Event counts for frame-based features are reported in units of a thousand.
+    %\texttt{fg\_av\_ger\_pd} (perceptual differences of consecutive frames),
+    %\texttt{fg\_av\_ger\_ml} (mean luminance of a frame),
+    %\texttt{fg\_av\_ger\_lr} (difference in mean luminance of left and right
+    %half),
+    %\texttt{fg\_av\_ger\_ud} (difference in mean luminance of upper and
+    %lower half),
+    %\texttt{fg\_av\_ger\_lrdiff} (left-right volume difference), and
+    %\texttt{fg\_av\_ger\_rms} (root mean square volume) represent one event
+    %for every movie frame (\unit[40]{ms}).
+    % For description of the two event categories of the audio-description's
+    % narrator (\texttt{se\_new} and \texttt{se\_old}) to build contrast of
+    % negative control Tab.~\ref{tab:events}.
+    }
+\label{tab:events}
+\resizebox{\linewidth}{!}{
+\footnotesize
+\begin{tabular}{lp{3.7cm}lllllllll} \toprule \textbf{Label} & \textbf{Description} & \textbf{All} & \textbf{1} & \textbf{2} & \textbf{3} & \textbf{4} & \textbf{5} & \textbf{6} & \textbf{7} & \textbf{8} \\
+\midrule
+\multicolumn{3}{l}{\textit{Movie stimulus}}\\
+\texttt{vse\_new} &  change of the camera position to a setting not depicted before & \aoVsenewAll & \aoVsenewI & \aoVsenewII & \aoVsenewIII & \aoVsenewIV & \aoVsenewV & \aoVsenewVI & \aoVsenewVII & \aoVsenewVIII
+\tabularnewline
+\texttt{vse\_old} & change of the camera position to a recurring setting & \aoVseoldAll & \aoVseoldI & \aoVseoldII & \aoVseoldIII & \aoVseoldIV & \aoVseoldV & \aoVseoldVI & \aoVseoldVII & \aoVseoldVIII
+\tabularnewline
+\texttt{vlo\_ch} & change of the camera position to another locale within the same setting & \aoVlochAll & \aoVlochI & \aoVlochII & \aoVlochIII & \aoVlochIV & 0 & \aoVlochV & \aoVlochVI & \aoVlochVII
+\tabularnewline
+\texttt{vpe\_new} & change of the camera position within a locale not depicted before & \aoVpenewAll & \aoVpenewI & \aoVpenewII & \aoVpenewIII & \aoVpenewIV & \aoVpenewV & \aoVpenewVI & \aoVpenewVII & \aoVpenewVIII
+\tabularnewline
+% vpe_old has no events in 3. So the indices are shifted
+\texttt{vpe\_old} & change of the camera position within a recurring locale &
+\aoVpeoldAll & \aoVpeoldI & \aoVpeoldII & 0 & \aoVpeoldIII & \aoVpeoldIV &
+\aoVpeoldV & \aoVpeoldVI & \aoVpeoldVII
+\tabularnewline
+\texttt{vno\_cut} & frames within a continuous movie shot & \avVnocutAll & \avVnocutI & \avVnocutII & 0 & \avVnocutIII & \avVnocutIV & \avVnocutV & \avVnocutVI & \avVnocutVII
+\tabularnewline
+% se\_new & control for AD narrator & \aoSenewAll & \aoSenewI & \aoSenewII & \aoSenewIII & \aoSenewIV & \aoSenewV & \aoSenewVI & \aoSenewVII & \aoSenewVIII
+% \tabularnewline
+% se\_old & control for AD narrator & \aoSeoldAll & \aoSeoldI & \aoSeoldII & \aoSeoldIII & \aoSeoldIV & \aoSeoldV & \aoSeoldVI & \aoSeoldVII & \aoSeoldVIII
+% \tabularnewline
+\texttt{fg\_av\_ger\_lr} & left-right luminance difference & \avFgavgerlrAll & \avFgavgerlrI & \avFgavgerlrII & \avFgavgerlrIII & \avFgavgerlrIV & \avFgavgerlrV & \avFgavgerlrVI & \avFgavgerlrVII & \avFgavgerlrVIII
+\tabularnewline
+\texttt{fg\_av\_ger\_lrdiff} & left-right volume difference & \avFgavgerlrdiffAll & \avFgavgerlrdiffI & \avFgavgerlrdiffII & \avFgavgerlrdiffIII & \avFgavgerlrdiffIV & \avFgavgerlrdiffV & \avFgavgerlrdiffVI & \avFgavgerlrdiffVII & \avFgavgerlrdiffVIII
+\tabularnewline
+\texttt{fg\_av\_ger\_ml} & mean luminance & \avFgavgermlAll & \avFgavgermlI & \avFgavgermlII & \avFgavgermlIII & \avFgavgermlIV & \avFgavgermlV & \avFgavgermlVI & \avFgavgermlVII & \avFgavgermlVIII
+\tabularnewline
+\texttt{fg\_av\_ger\_pd} & perceptual difference & \avFgavgerpdAll & \avFgavgerpdI & \avFgavgerpdII & \avFgavgerpdIII & \avFgavgerpdIV & \avFgavgerpdV & \avFgavgerpdVI & \avFgavgerpdVII & \avFgavgerpdVIII
+\tabularnewline
+\texttt{fg\_av\_ger\_rms} & root mean square volume & \avFgavgerrmsAll & \avFgavgerrmsI & \avFgavgerrmsII & \avFgavgerrmsIII & \avFgavgerrmsIV & \avFgavgerrmsV & \avFgavgerrmsVI & \avFgavgerrmsVII & \avFgavgerrmsVIII
+\tabularnewline
+\texttt{fg\_av\_ger\_ud} & upper-lower luminance difference & \avFgavgerudAll & \avFgavgerudI & \avFgavgerudII & \avFgavgerudIII & \avFgavgerudIV & \avFgavgerudV & \avFgavgerudVI & \avFgavgerudVII & \avFgavgerudVIII
+\tabularnewline
+\midrule
+\multicolumn{3}{l}{\textit{Audio-description stimulus}}\\
+\texttt{body} & trunk of the body; overlaid clothes & \aoBodyAll & \aoBodyI & \aoBodyII
+& \aoBodyIII & \aoBodyIV & \aoBodyV & \aoBodyVI & \aoBodyVII & \aoBodyVIII
+\tabularnewline
+\texttt{bpart} & limbs and trousers & \aoBpartAll & \aoBpartI & \aoBpartII & \aoBpartIII & \aoBpartIV & \aoBpartV & \aoBpartVI & \aoBpartVII & \aoBpartVIII
+\tabularnewline
+\texttt{fahead} & face or head (parts) & \aoFaheadAll & \aoFaheadI & \aoFaheadII & \aoFaheadIII & \aoFaheadIV & \aoFaheadV & \aoFaheadVI & \aoFaheadVII & \aoFaheadVIII
+\tabularnewline
+\texttt{furn} & moveable furniture (insides \& outsides) & \aoFurnAll & \aoFurnI & \aoFurnII & \aoFurnIII & \aoFurnIV & \aoFurnV & \aoFurnVI & \aoFurnVII & \aoFurnVIII
+\tabularnewline
+\texttt{geo} & immobile landmarks & \aoGeoAll & \aoGeoI & \aoGeoII & \aoGeoIII & \aoGeoIV & \aoGeoV & \aoGeoVI & \aoGeoVII & \aoGeoVIII
+\tabularnewline
+\texttt{groom} & rooms \& locales or geometry-defining elements & \aoGroomAll & \aoGroomI & \aoGroomII & \aoGroomIII & \aoGroomIV & \aoGroomV & \aoGroomVI & \aoGroomVII & \aoGroomVIII
+\tabularnewline
+\texttt{object} & countable entities with firm boundaries & \aoObjAll & \aoObjI & \aoObjII & \aoObjIII & \aoObjIV & \aoObjV & \aoObjVI & \aoObjVII & \aoObjVIII
+\tabularnewline
+\texttt{se\_new} & a setting occurring for the first time & \aoSenewAll & \aoSenewI & \aoSenewII & \aoSenewIII & \aoSenewIV & \aoSenewV & \aoSenewVI & \aoSenewVII & \aoSenewVIII
+\tabularnewline
+\texttt{se\_old} & a recurring setting & \aoSeoldAll & \aoSeoldI & \aoSeoldII & \aoSeoldIII & \aoSeoldIV & \aoSeoldV & \aoSeoldVI & \aoSeoldVII & \aoSeoldVIII
+\tabularnewline
+\texttt{sex\_f} & female person(s), name & \aoSexfAll & \aoSexfI & \aoSexfII & \aoSexfIII & \aoSexfIV & \aoSexfV & \aoSexfVI & \aoSexfVII & \aoSexfVIII
+\tabularnewline
+\texttt{sex\_m} & male person(s), name & \aoSexmAll & \aoSexmI & \aoSexmII & \aoSexmIII & \aoSexmIV & \aoSexmV & \aoSexmVI & \aoSexmVII & \aoSexmVIII
+\tabularnewline
+% vlo_ch has no events in segment 5. So indices are shifted
+%vse\_new & control for movie cut & \aoVsenewAll & \aoVsenewI & \aoVsenewII & \aoVsenewIII & \aoVsenewIV & \aoVsenewV & \aoVsenewVI & \aoVsenewVII & \aoVsenewVIII
+%\tabularnewline
+%vse\_old & control for movie cut & \aoVseoldAll & \aoVseoldI & \aoVseoldII & \aoVseoldIII & \aoVseoldIV & \aoVseoldV & \aoVseoldVI & \aoVseoldVII & \aoVseoldVIII
+%\tabularnewline
+%vlo\_ch & control for movie cut & \aoVlochAll & \aoVlochI & \aoVlochII & \aoVlochIII & \aoVlochIV & 0 & \aoVlochV & \aoVlochVI & \aoVlochVII
+%\tabularnewline
+%vpe\_new & control for movie cut & \aoVpenewAll & \aoVpenewI & \aoVpenewII & \aoVpenewIII & \aoVpenewIV & \aoVpenewV & \aoVpenewVI & \aoVpenewVII & \aoVpenewVIII
+%\tabularnewline
+% vpe_old has no events in 3. So the indices are shifted
+%vpe\_old & control for movie cut & \aoVpeoldAll & \aoVpeoldI & \aoVpeoldII & 0 & \aoVpeoldIII & \aoVpeoldIV & \aoVpeoldV & \aoVpeoldVI & \aoVpeoldVII
+% \tabularnewline
+\texttt{fg\_ad\_lrdiff} & left-right volume difference & \aoFgadlrdiffAll & \aoFgadlrdiffI & \aoFgadlrdiffII & \aoFgadlrdiffIII & \aoFgadlrdiffIV &
+\aoFgadlrdiffV & \aoFgadlrdiffVI & \aoFgadlrdiffVII & \aoFgadlrdiffVIII
+\tabularnewline
+\texttt{fg\_ad\_rms} & root mean square volume & \aoFgadrmsAll &
+\aoFgadrmsI & \aoFgadrmsII & \aoFgadrmsIII & \aoFgadrmsIV & \aoFgadrmsV &
+\aoFgadrmsVI & \aoFgadrmsVII & \aoFgadrmsVIII
+\tabularnewline
+\bottomrule
+\end{tabular}
+}%resizebox
+\end{table*}
+
+% AD annotation
+For the analysis of the audio-description stimulus, we extended a publicly
+available annotation of its speech content \citep{hausler2021studyforrest} by
+classifying concrete and countable nouns that the narrator uses to describe the
+movie's absent visual content.
+% annotation procedure
+An initial annotation was performed by one individual,
+% corrections
+and minor corrections were applied after comparing with a second categorization
+done by the author.
+% reference to table with rules and examples
+A complete overview of all 18 noun categories, their inclusion criteria, and
+examples can be seen in Table~\ref{tab:descr-nouns-rules}.
+% why and how of categories 1
+Some categories reflect the verbal counterpart of the stimulus categories that
+were used in the visual localizer experiment (e.g. \texttt{body}, \texttt{face},
+\texttt{head}, \texttt{object}, \texttt{setting\_new}, and
+\texttt{setting\_rec}).
+% why and how of categories 2
+Other categories were created to semantically cluster remaining nouns into
+categories that had no counterpart in the visual localizer experiment (e.g.
+\texttt{bodypart}, \texttt{female}, \texttt{fname}, \texttt{furniture},
+\texttt{geo}, \texttt{groom}, \texttt{male}, and \texttt{persons}).
+% categories in detail
+%Nouns were categorized by the verbal clue they provide about the
+%cinematographic scene's environment (\texttt{geo}, \texttt{groom};
+%\texttt{setting\_new}, \texttt{setting\_old}), its inherent persons (e.g.
+%\texttt{female}, \texttt{male}, \texttt{persons}), a person's body or worn
+%clothes (\texttt{face}, \texttt{head}, \texttt{body}, \texttt{bodypart}), and a
+%scene's inherent objects (\texttt{object}, \texttt{furniture}).  problem with
+%hierarchical categories
+The categories \texttt{setting\_new} and \texttt{setting\_rec} comprise not just
+words that describe a setting as a whole (e.g. ``[in] Greenbow'', ``[in a]
+disco'', ``[the platoon wades through a] rice field''). They also comprise words
+that could count as a member of another category in case the narrator uses these
+words to indicate a switch from one setting to another (e.g. ``[a] physician'').
+% how it was handled
+These nouns were flagged with both categories during the initial annotation
+procedure. In context of the current analyses these word are considered to
+belong exclusively to the higher-level category of changing a setting
+(\texttt{setting\_new} or \texttt{setting\_rec}).
+% pooling of categories
+Some noun categories that were semantically similar and offered only a small
+amount of counts were pooled resulting in 11 final event categories
+(see Table~\ref{tab:events}).  These event categories were then used to model
+hemodynamic responses.
+
+% table for descriptive nouns: categories, rules, examples counts
+\begin{table*}[tbp]
+    \caption{Categories and criteria to categorize the nouns spoken by
+        the audio-description's narrator.
+        Examples are given in English.
+        Some of these initial 18 noun categories were pooled resulting in 11
+        event categories that served as basis to build the regressors of the
+        GLM
+        (see Table~\ref{tab:events}).
+        % The category \texttt{++} also contains adverbial of time.
+}
+\label{tab:descr-nouns-rules}
+\resizebox{\linewidth}{!}{
+\begin{tabular}{lp{61mm}p{61mm}}
+\toprule
+\textbf{Category} & \textbf{Criteria} & \textbf{Examples} \\
+\midrule
+\texttt{body} & trunk of the body; possibly clothed & back, hip, shoulder; jacket, dress, shirt
+\tabularnewline
+\texttt{bodypart} & limbs & arm, finger, leg, toe
+\tabularnewline
+\texttt{face} & face or parts of it & face, ear, nose, mouth
+\tabularnewline
+\texttt{female} & female person & nurse, mother, woman
+\tabularnewline
+\texttt{females} & female persons & women
+\tabularnewline
+\texttt{fname} & female name & Jenny
+\tabularnewline
+\texttt{furniture} & movable furniture (insides \& outsides) & bench, bed, table, chair
+\tabularnewline
+\texttt{geo} & immobile landmarks & building, tree, street, alley, meadow, cornfield
+\tabularnewline
+\texttt{groom} & rooms \& locales, or geometry-defining elements & living room; wall, door, window, floor
+\tabularnewline
+\texttt{head} & non-face parts of the head; worn headgear & head, hair, ear, neck;
+helmet
+\tabularnewline
+\texttt{male} & male person & man, father, soldier
+\tabularnewline
+\texttt{males} & male persons & boys, opponents
+\tabularnewline
+\texttt{mname} & male name & Bubba, Kennedy
+\tabularnewline
+\texttt{object} & countable entity with firm boundaries & telephone, car
+\tabularnewline
+\texttt{objects} & countable entities & wheels, plants
+\tabularnewline
+\texttt{persons} & concrete persons of unknown sex & hippies, patients
+\tabularnewline
+\texttt{setting\_new} & a setting occurring for the first time & on a ``bridge'', on an ``alley'', on ``campus''
+\tabularnewline
+\texttt{setting\_rec} & a recurring setting & at the ``bus stop'' \tabularnewline
+% ++ & cue regarding time & in the ``evening'', it's ``daytime'', ``later'' \tabularnewline
+\bottomrule
+\end{tabular}
+}%resizebox
+\end{table*}
+
+% low-level confounds: intro
+Lastly, we algorithmically annotated the temporal structure of low-level
+perceptual features to create nuisance regressors.
+% visual shit
+For the movie stimulus, we computed the mean luminance (arbitrary units,
+average pixel brightness) of a movie frame (\unit[40]{ms}), the difference in
+mean luminance of each frame's left and right half, the difference in mean
+luminance of the lower and upper half.  As an indicator of visual change, we
+compute perceptual fingerprints for each movie frame using the pHash library
+\citep{zauner2010implementation} and recorded the cumulative bitwise
+difference to the previous frame.
+% auditory shit
+Finally for both audio tracks, we computed the left-right difference in volume
+and root mean square volume averaged across the length of every movie frame
+(\unit[40]{ms}).
+
+\subsection*{Hemodynamic Modeling}
+
+% movie events
+The events of the movie cut related categories and \texttt{no\_cut} events were
+modeled as box car events of \unit[200]{ms} duration,
+%
+speech events from onset to offset of each word, and frame-based confounds from
+onset to offset of the corresponding movie frame.
+% convolving
+For all regressors, the stimulus models were convolved with a double-gamma
+hemodynamic response function (HRF), as implemented in FSL.
+
+% we checked correlations
+Given the unknown confound structure of the naturalistic stimuli, we inspected
+% correlations within stimuli and across stimuli
+the correlation of regressors of each stimulus and
+also across both stimuli (see Figure~\ref{fig:reg-corr}).
+% correlations within each stimulus
+The computed Pearson correlation coefficients show only minor correlations of
+feature regressors for the same stimulus.
+% (highest) correlations across stimuli; \texttt{fg\_a(v|d)\_ger\_rms}, r=.76;
+% \texttt{fg\_a(v|d)\_ger\_lrdiff}, r=.77)
+Maximum correlations are found for low-level auditory confounds across
+stimuli,
+% no surprise
+which is to be expected, as the audio-description contains the audio track of
+the movie plus the additional narrator (see Figure~\ref{fig:reg-corr}; correlation
+between root mean square volume of both audio tracks, r=.76; correlation between
+left-right volume difference of both audio tracks, r=.77).
+% encouraged by that we build contrasts (statement)
+The observed correlation pattern did not indicate problematic confounds of
+nuisance variables and regressors of interest for any of the planned analyses.
+
+\begin{figure*}[tbp]
+\centering
+    \includegraphics[width=\linewidth]{figures/regressor-corr} \caption{Pearson
+        correlation coefficients of model response time series used as regressors in
+        the GLM analysis of the
+        audio-description (blue; see Table~\ref{tab:events} for a
+        description) and audio-visual movie (red; see Table~\ref{tab:events}).
+        Values are rounded to the nearest tenth.
+        The correlation between the two stimuli's
+        root mean square volume and between their left-right difference in
+        volume yielded the highest correlation values
+        (\texttt{fg\_ad\_rms} and \texttt{fg\_av\_ger\_rms}, r=.7635;
+        \texttt{fg\_ad\_lrdiff} and \texttt{fg\_av\_ger\_lrdiff}, r=.7749).
+      }
+\label{fig:reg-corr}
+\end{figure*}
+
+% AV design matrix
+The design matrix for the first-level time-series GLM analysis of the movie
+comprised regressors for the 12 event categories of the movie listed in
+Table~\ref{tab:events}.
+% AD design matrix
+Similarly, the design matrix for the analysis of the audio-description comprised
+regressors for the 13 event categories of the audio-description, also listed in
+Table~\ref{tab:events}.
+% AD regressors in AV
+In order to implement cross-modal control contrasts, the design matrix for the
+movie stimulus also contained the regressors based on nouns used by the
+audio-description's narrator to indicate a switch to another setting (categories
+\texttt{se\_new} and \texttt{se\_old}).
+% AV regressors in AV
+Likewise, the design matrix for the audio-description included the five movie
+cut related regressors (\texttt{vse\_new}, \texttt{vse\_old}, \texttt{vlo\_ch},
+\texttt{vp\_new}, \texttt{vpe\_old}).
+% both stimuli: null regressors
+For both stimuli, a null regressor was used for any event category in a segment
+for which no event of a category was present (e.g. no event of \texttt{vpe\_old}
+in segment 3; see Table~\ref{tab:events}).
+% temporal derivatives
+Temporal derivatives of all regressors were added to the design matrix to
+compensate for regional differences \citep{friston1998event}.
+% motion parameters
+Lastly, six participant and run specific motion estimates (translation and
+rotation) were also included.
+% high-pass filtering
+The design matrices were temporally filtered with the same high-pass filter
+(cutoff period of \unit[150]{s}) as the BOLD time series.
+
+\subsection*{Statistical analysis}
+
+% intro
+We performed standard two-level GLM analyses to aggregate results across all
+BOLD acquisition runs for every participant and each stimulus separately.
+% level 3
+Subsequently, we conducted third-level analyses to average contrast estimates
+over participants for each stimulus, respectively.
+
+% there isn't "the one road"
+Given the rich naturalistic stimuli and the availability of various stimulus
+feature annotations, there are several candidates for implementing contrasts to
+identify hemodynamic activity congruent with the hypothesized processing of
+spatial information in the PPA.
+% kind of arbitrary choice
+However, while the rationale for any contrast composition must be sound, the
+selection of a single implementation remains arbitrary to some degree.
+% hence, a couple of contrasts
+Consequently, we computed multiple contrasts that are listed in
+Table~\ref{tab:contrasts} for the movie and audio-description, respectively.
+% subjectively assessed balance
+For each stimulus, we picked a primary contrast for result presentation (marked
+  with an asterisk in the table) based on a subjectively assessed balance of how well
+the averaged events within categories represent spatial and non-spatial
+information, and the number of events in the stimulus.
+% reference to supplementals
+An evaluation of the robustness of these results with respect to similar but
+different contrasts is provided in the supplementary materials.
+
+% AV: primary contrast
+In the primary contrast for the movie stimulus, we contrasted cuts to a setting
+that was not depicted before (\texttt{vse\_new}) to cuts merely switching the
+camera position within a setting that was already established earlier in the
+movie (\texttt{vpe\_old}), because the former are designed to orient the viewer
+in the movie environment using wider-camera angles, whereas the latter can
+afford to depict details of a scene.
+% AD: primary contrast
+In the primary contrast of the audio-description stimulus, we contrasted
+mentions of buildings and landmarks (\texttt{geo}), and rooms and
+geometry-defining objects (\texttt{groom}) with nouns referring to a person's
+head or face (\texttt{fahead}), and other non-geometry related categories
+(\texttt{body}, \texttt{bodypart}, \texttt{fahead}, \texttt{object},
+\texttt{sex\_f}, \texttt{sex\_m}).
+% why furniture was not used
+The category ``furniture'' (\texttt{furn}) was not used as a regressor of
+interest in any contrast because these nouns could be perceived as either a
+geometry-defining scene element or as an isolated object.
+% why se_new & se_old were not used in the primary contrasts
+The categories of nouns indicating a switch to a setting that occurred for the
+first time (\texttt{se\_new}) or a setting that recurred during the plot
+(\texttt{se\_old}) were not included in the primary contrast because they
+comprise
+% heterogeneous category
+a)  nouns that could be a member of another category (e.g. ``[a]
+physician''), and
+% richness of verbal description vs. picture
+b) nouns that only vaguely identify a scene (e.g. ``[in] Greenbow'', ``[in a]
+disco'', ''[black and white] film recordings'') compared to perceptually richer
+descriptions.
+
+% control contrasts
+Finally, we created several control contrasts for both stimuli
+(see Table~\ref{tab:contrasts}).
+% AV: no cut > cut
+For the movie stimulus, four contrasts were created contrasting the no-cut
+regressor (\texttt{vno\_cut}) to cut-related regressors.
+% AV: narrator
+One contrast was created by contrasting nouns spoken by the (missing) narrator
+comparing nouns
+%
+that indicate a switch to another setting (\texttt{se\_new} >
+\texttt{se\_old}), and
+%
+that were moderately correlated with movie cuts indicating a
+switch to another setting (see Figure~\ref{fig:reg-corr}).
+% AD stimulus
+For the audio-description stimulus, we created five control contrasts to test if
+activation in the PPA was correlated with moments of cuts, despite the absence
+of visual stimulation.
+
+\begin{table*}[tbp]
+  \caption{Computed contrasts for the analysis of the movie and the audio
+    description, and their respective purpose.
+    The primary contrasts are marked with an asterisk.
+    \texttt{non-spatial} refers to the event categories
+    \texttt{body}, \texttt{bodypart}, \texttt{fahead},
+    \texttt{object}, \texttt{sex\_f}, \texttt{sex\_m}.
+    An explanation of all event categories can be found in
+    Table~\ref{tab:events}.
+    }
+\label{tab:contrasts}
+\begin{tabular}{lll}
+\toprule
+\textbf{Nr.} &  \textbf{Contrast} & \textbf{Purpose} \\
+\midrule
+\multicolumn{3}{l}{\textit{Movie stimulus}}\\
+1* & \texttt{vse\_new > vpe\_old} & spatial processing \tabularnewline
+2 & \texttt{vse\_new, vpe\_new > vse\_old, vpe\_old} & spatial processing \tabularnewline
+3 & \texttt{vse\_new > vse\_old} & spatial processing \tabularnewline
+4 & \texttt{vse\_new > vse\_old, vpe\_old} & spatial processing \tabularnewline
+5 & \texttt{vse\_new, vpe\_new > vpe\_old} & spatial processing \tabularnewline
+6 & \texttt{vno\_cut > vse\_new} & control \tabularnewline
+7 & \texttt{vno\_cut > vse\_old} & control \tabularnewline
+8 & \texttt{vno\_cut > vse\_new, vse\_old} & control \tabularnewline
+9 & \texttt{vno\_cut > vpe\_new, vpe\_old} & control \tabularnewline
+    10 & \texttt{se\_new > se\_old} & control (absent narrator) \tabularnewline
+\midrule
+\multicolumn{3}{l}{\textit{Audio-description stimulus}}\\
+1* & \texttt{geo, groom > non-spatial} & spatial processing \tabularnewline
+2 & \texttt{geo, groom, se\_new > non-spatial} & spatial processing \tabularnewline
+3 & \texttt{groom, se\_new, se\_old > non-spatial}  & spatial processing \tabularnewline
+4 & \texttt{geo > non-spatial} & spatial processing \tabularnewline
+5 & \texttt{groom > non-spatial} & spatial processing \tabularnewline
+6 & \texttt{se\_new > non-spatial} & spatial processing \tabularnewline
+7 & \texttt{se\_new, se\_old > non-spatial} & spatial processing \tabularnewline
+8 & \texttt{se\_new > se\_old} & spatial processing \tabularnewline
+9 & \texttt{vse\_new > vpe\_old} & control (absent visual cuts) \tabularnewline
+10 & \texttt{vse\_new, vpe\_new > vse\_old, vpe\_old} & control (absent visual cuts) \tabularnewline
+11 & \texttt{vse\_new > vse\_old} & control (absent visual cuts) \tabularnewline
+12 & \texttt{vse\_new > vse\_old, vpe\_old} & control (absent visual cuts) \tabularnewline
+13 & \texttt{vse\_new, vpe\_new > vpe\_old} & control (absent visual cuts) \tabularnewline
+\bottomrule
+\end{tabular}
+\end{table*}
+
+% alignments single participants: 1st level
+First-level GLM analyses were performed in the image-space of a
+participant-specific BOLD T2* template using a previously determined linear
+transformation \citep{sengupta2016extension}.
+% subject template (for Bland-Altman-Plot of unthresholded maps)
+% \href{"https://github.com/psychoinformatics-de/studyforrest-data-templatetransforms/blob/master/sub-01/bold3Tp2/brain.nii.gz"}{example})
+% group template (for group and individual brain slices)
+For higher-level analyses image data were aligned with a study-specific T2*
+group template likewise using a previously computed non-linear transformation
+\citep{hanke2014audiomovie}.
+% https://github.com/psychoinformatics-de/studyforrest-data-templatetransforms/blob/master/templates/grpbold3Tp2/brain.nii.gz"
+% MNI152
+This group template was co-registered to the MNI 152 template with an affine
+transformation (12 degrees of freedom).
+
+% second level model
+The second-level analyses, which averaged contrast estimates over the eight
+stimulus segments, were carried out using a fixed effects model by forcing the
+random effects variance to zero in FLAME (FMRIB's Local Analysis of Mixed
+Effects \citep{beckmann2003general, woolrich2004multilevel}).
+% thresholding ($Z$>2.3 in subject-space; $Z$>3.4 in group space)
+(Gaussianised T/F) statistic images were thresholded using clusters determined
+by $Z$>3.4 and a cluster-corrected significance threshold of $p$=.05
+\citep{worsley2001statistical}.
+
+% third level model
+The third level analysis which averaged contrast estimates over participants was
+carried out using FLAME stage 1 with automatic outlier detection
+\citep{beckmann2003general, woolrich2004multilevel, woolrich2008robust}.
+% thresholding
+Here again, Z (Gaussianised T/F) statistic images were thresholded using
+clusters determined by $Z$>3.4 and a corrected cluster significance threshold of
+$p$=.05 \citep{worsley2001statistical}.
+% brain region identification
+Brain regions associated with observed clusters were determined with the Jülich
+Histological Atlas \citep{eickhoff2005toolbox, eickhoff2007assignment} and the
+Harvard-Oxford Cortical Atlas \citep{desikan2006automated} provided by FSL.
+% PPA masks
+Regions of interest (ROI) masks for individual PPAs and a PPA group mask of
+individual PPA overlaps were created from data provided by
+\citet{sengupta2016extension}.
+
+\section*{Data (and code) availability}
 
@@
 \href{https://neurovault.org/collections/KADGMGVZ/}{\url{neurovault.org/collections/KADGMGVZ}}.
-%
-
-\section*{Acknowledgements}
-
-COH designed and performed the analyses, and wrote the manuscript.
-%
-MH provided critical feedback on the procedure and edited the manuscript.
-%
-SE provided critical feedback.
-%
-We are grateful to \href{www.florianschurz.de}{Florian Schurz} who initiated the
-annotation of nouns and created its preliminary version.%
-
-This research was, in part, supported by the German Federal Ministry of
-Education and Research (BMBF, 01GQ1112) and the US National Science Foundation
-(NSF, 1129855). Work on the data-sharing technology employed for this research
-was supported by BMBF (01GQ1411, 01GQ1905) and NSF (1429999, 1912266).
-
-\section*{Competing financial interests}
-The authors declare no competing financial interests.
+
+\section*{Code availability}
+
+\todo[inline]{Please also split "Code and Data availability" into two sections}
 
@@
 \end{itemize}
+
+\section*{Acknowledgements}
+
+We are grateful to \href{www.florianschurz.de}{Florian Schurz} who initiated the
+annotation of nouns and created its preliminary version.%
+
+This research was, in part, supported by the German Federal Ministry of
+Education and Research (BMBF, 01GQ1112) and the US National Science Foundation
+(NSF, 1129855). Work on the data-sharing technology employed for this research
+was supported by BMBF (01GQ1411, 01GQ1905) and NSF (1429999, 1912266).
+
+\section*{Author Contributions}
+
+COH designed and performed the analyses, and wrote the manuscript.
+%
+MH provided critical feedback on the procedure and edited the manuscript.
+%
+SE provided critical feedback.
+
+\section*{Competing financial interests}
+
+The authors declare no competing financial interests.
 

### 2021-08-08 paper/main.tex
correct typos

@@
 \citep{goodale1992separate, mishkin1982contribution}.
+
+\todo[inline]{Goodale and Milner (1992), which is literally a call for what and
+    how pathways. The function of these pathways remains in dispute but its
+    clear that where (spatial processing) must take place in both streams. You
+should probably acknowledge that.}
 % PPA
@@
 % summary if literature review
-Taken together, the literature suggest that the PPA does not exclusively respond to
-visually presented spatial information.
+Taken together, the literature suggest that the PPA does not exclusively respond
+to visually presented spatial information.
 % three things in common
@@
 % designed stimulus set
-first, they employed a small set of carefully chosen and conceptualized
-stimuli.
-% block-design & task
-Second, studies used a block-design paradigm to maximize detection power.
-Third, they usually employed an explicit (perceptual) judgement task.
+1) they employed a small set of carefully chosen and conceptualized stimuli,
+% block-design
+2) used a block-design paradigm to maximize detection power, and
+% task
+3) they usually employed an explicit (perceptual) judgement task.
 % conceptualized stimuli and block: disadvantages
@@
 % open question
-In this study, we investigate if increased hemodynamic activity in the PPA that
-is usually detected by contrasting blocks of pictures is also present under more
-natural conditions.
+In this study, we investigate whether increased hemodynamic activity in the PPA
+that is usually detected by contrasting blocks of pictures is also present under
+more natural conditions.
 % we use 2 naturalistic stimuli
-To answer this question, we operationalized the perception of both \textit{visual and
-auditory} spatial information using two naturalistic stimuli
+To answer this question, we operationalized the perception of both
+\textit{visual and auditory} spatial information using two naturalistic stimuli
 (\citep[see reviews][]{hamilton2018revolution, hasson2008neurocinematics,
@@
 % AV stimulus
-The operationalization of visual spatial perception is based on an annotation of
-cuts and depicted locations in the audio-visual movie ``Forrest Gump''
-\citep{haeusler2016cutanno}, while
+The current operationalization of visual spatial perception is based on an
+annotation of cuts and depicted locations in the audio-visual movie ``Forrest
+Gump'' \citep{haeusler2016cutanno}, while
 % AD stimulus
@@
 annotation of speech occurring in the movie's audio-description
-\citep{hausler2021studyforrest}.
+\citep{haeusler2021studyforrest}.
 % pictures -> movie -> audio-description
 The movie stimulus shares the stimulation in the visual domain with classical
-localizer stimuli, while featuring real-life-like visual complexity and naturalistic
-auditory stimulation. The audio-description maintains the naturalistic nature of
-the movie stimulus, but limitted to the auditory domain.
-% GLM contrasts
-We applied model-based, mass-univariate analyses to a series of datasets with
-BOLD fMRI data from naturalistic and conventional block-design stimulation of
-the same set of participants, available from the open-data resource
-\href{http://www.studyforrest.org}{studyforrest.org}
-\citep{hanke2016simultaneous, hanke2014audiomovie, sengupta2016extension}.
+localizer stimuli, while featuring real-life-like visual complexity and
+naturalistic auditory stimulation. The audio-description maintains the
+naturalistic nature of the movie stimulus, but limited to the auditory domain.
+% current GLM contrasts
+We applied model-based, mass-univariate analyses to BOLD fMRI data from both
+naturalistic stimuli \citep{hanke2016simultaneous, hanke2014audiomovie},
+available from the open-data resource
+\href{http://www.studyforrest.org}{studyforrest.org}.
+% comparison to previous GLM
+We compare current results to results from a previously performed model-based,
+mass-univariate analysis that was applied to data from a conventional
+block-designed functional localizer paradigm that was performed with the same
+set of participants \citep{sengupta2016extension}.
+% intro to hypo a
+Similarly to the functional localizer, we currently also capitalize on events
+that should evoke the cognitive processing of spatial information.
 % hypo a
-We hypothesized that whole-brain analyses would reveal increased hemodynamic
-activity in the PPA as functionally defined by a conventional visual localizer
-for each individual, because all three operationalization capitalize on events
-that should evoke the cognitive processing of spatial information.
+Thus, we hypothesized that our whole-brain analyses would reveal increased
+hemodynamic activity in medial temporal regions that were defined functionally
+defined as the PPA by the previous analysis of the data from the block-designed
+localizer \citep{sengupta2016extension}.
 %hypo b: individuals
@@
 %during two naturalistic stimuli lead to increased hemodynamic activity in the
-%PPA.
+m%PPA.
 %% anterior vs. posterior
@@
 results of the primary $t$-contrasts co-registered to the group-template (MNI152
-space) can found at
+space) can be found at
 \href{https://neurovault.org/collections/KADGMGVZ/}{\url{neurovault.org/collections/KADGMGVZ}}.
@@
 Similarly, our results suggest that the pPPA is more concerned with visual
-aspects immanent in pictures or movie shots of landscapes.
+aspects inherent in pictures or movie shots of landscapes.
 % aPPA
@@
 (e.g. spatial contextual information \citep{aminoff2007parahippocampal}) as
-immanent in both visual and verbal stimuli.
+inherent in both visual and verbal stimuli.
 
@@
 %#2
-Our approach to movie stimulus annotation and event selection differs from previous
-reports in the literature.
+Our approach to movie stimulus annotation and event selection differs from
+previous reports in the literature.
 % PPA: intro
-In an earlier study, \citet{bartels2004mapping} manually annotated the content of
-movie frames (color, faces, language, and human bodies) and found that the
+In an earlier study, \citet{bartels2004mapping} manually annotated the content
+of movie frames (color, faces, language, and human bodies) and found that the
 functional specialization of brain areas is preserved during movie watching.
@@
 Future studies that aim to use a movie to localize visual areas in individual
-participants should extensively annotate the content of frames (e.g.,
-using the open-source solution ``Pliers''\citep{mcnamara2017developing} for feature extraction from a visual
-naturalistic stimulus).
+participants should extensively annotate the content of frames (e.g., using the
+open-source solution ``Pliers''\citep{mcnamara2017developing} for feature
+extraction from a visual naturalistic stimulus).
 
@@
 % exclusion of VP 10
-data of one participant were dropped to due to invalid distortion correction
+data of one participant were dropped due to invalid distortion correction
 during scanning of the audio-description stimulus.
@@
 For the analysis of the audio-description stimulus, we extended a publicly
-available annotation of its speech content \citep{hausler2021studyforrest} by
+available annotation of its speech content \citep{haeusler2021studyforrest} by
 classifying concrete and countable nouns that the narrator uses to describe the
@@
 luminance of the lower and upper half. As an indicator of visual change, we
-compute perceptual fingerprints for each movie frame using the pHash library
+computed perceptual fingerprints for each movie frame using the pHash library
 \citep{zauner2010implementation} and recorded the cumulative bitwise
@@
 % motion parameters
-Lastly, six participant and run specific motion estimates (translation and
+Lastly, six participant- and run-specific motion estimates (translation and
 rotation) were also included.
@@
 \href{https://gin.g-node.org/chaeusler/studyforrest-ppa-analysis}{\url{gin.g-node.org/chaeusler/studyforrest-ppa-analysis}} (DOI assignment pending).
-Unthresholded $Z$-maps of all contrasts
-can found at
+Unthresholded $Z$-maps of all contrasts can be found at
 \href{https://neurovault.org/collections/KADGMGVZ/}{\url{neurovault.org/collections/KADGMGVZ}}.
@@
 \todo[inline]{Please also split "Code and Data availability" into two sections}
+
+\section*{Data Citations}
+
+\todo[inline]{Following dataset are added to references.bib}
+\todo[inline]{reference to cut anno might be retundant}
+\todo[inline]{propably, cite them above in the manuscript where it makes sense}
+
+Cited here, so they show in the references (see at end of references):
+\citep{haeusler2016cutdata, haeusler2021speechdata, hanke2014ds000113, sengupta2016ds000113c, hanke2016ds000113d}
+
+\begin{itemize}
+% cut anno
+\item Häusler, C. O. \& Hanke M. Dataset 1 in: An annotation of cuts, depicted
+locations, and temporal progression in the motion picture "Forrest Gump".
+\emph{F1000Research}
+\href{https://doi.org/10.5256/f1000research.9536.d134823}{10.5256/f1000research.9536.d134823}
+(2016)
+
+% speech anno
+\item Häusler, C. O. \& Hanke M. \emph{OSF}
+\href{https://doi.org/10.17605/OSF.IO/GFRME}{GFRME}
+(2020).
+
+% audio-description
+\item Hanke, M., Baumgartner, F.~J., Ibe, P., Kaule, F.~R., Pollmann, S., Speck, O.,
+  Zinke, W., \& Stadler, J. \emph{OpenfMRI} \href{https://openfmri.org/dataset/ds000113}{ds000113} (2014)
+
+\item Sengupta, A., Kaule, F. R., Guntupalli, J. S., Hoffmann, M. B., Häusler, C., Stadler, J. \& Hanke, M.
+  \emph{OpenfMRI} \href{https://openfmri.org/dataset/ds000113c}{ds000113c} (2016).
+
+\item Hanke, M., Adelhöfer, N., Kottke, D., Iacovella, V., Sengupta, A., Kaule, F.~R., Nigbur, R., Waite, A.~Q.,
+  Baumgartner, F.~J. \& Stadler, J. (2016).
+  \emph{OpenfMRI} \href{https://openfmri.org/dataset/ds000113d}{ds000113d} (2016).
+\end{itemize}
 
@@
 
-\section*{Data Citations}
-
-\begin{itemize}
-% cut anno
-\item Häusler, C. O. \& Hanke M. Dataset 1 in: An annotation of cuts, depicted
-locations, and temporal progression in the motion picture "Forrest Gump".
-\emph{F1000Research}
-\href{https://doi.org/10.5256/f1000research.9536.d134823}{10.5256/f1000research.9536.d134823}
-(2016)
-
-% speech anno
-\item Häusler, C. O. \& Hanke M. \emph{OSF}
-\href{https://doi.org/10.17605/OSF.IO/GFRME}{10.5256/f1000research.9536.d134823}
-(2020).
-
-% audio-description
-\item Hanke, M., Baumgartner, F.~J., Ibe, P., Kaule, F.~R., Pollmann, S., Speck, O.,
-  Zinke, W., \& Stadler, J. \emph{OpenfMRI} \href{https://openfmri.org/dataset/ds000113}{ds000113} (2014)
-
-\item Sengupta, A., Kaule, F. R., Guntupalli, J. S., Hoffmann, M. B., Häusler, C., Stadler, J. \& Hanke, M.
-  \emph{OpenfMRI} \href{https://openfmri.org/dataset/ds000113c}{ds000113c} (2016).
-
-\item Hanke, M., Adelhöfer, N., Kottke, D., Iacovella, V., Sengupta, A., Kaule, F.~R., Nigbur, R., Waite, A.~Q.,
-  Baumgartner, F.~J. \& Stadler, J. (2016).
-  \emph{OpenfMRI} \href{https://openfmri.org/dataset/ds000113d}{ds000113d} (2016).
-\end{itemize}
-
 \section*{Acknowledgements}
@@
 Unthresholded $Z$-maps of all contrasts on a group level co-registered to the
-group-template (MNI152 space) can found at
+group-template (MNI152 space) can be found at
 \href{https://neurovault.org/collections/KADGMGVZ/}{\url{neurovault.org/collections/KADGMGVZ}}.
@@
 This suggests that variance correlating with lower level auditory processes was
-not averaged out across events and the employed nuisance regressors did not
-capture this variance appropriately.
+not averaged out across events (e.g. switches to another setting might often not
+just cued by the narrator but also by a change of the soundscape or cued by a
+the start of a new song) and the employed nuisance regressors did not capture
+this variance appropriately.
 % interpretation 2
@@
 % movie contrasts: not cut condition vs. cuts
-To test for the specificity of the main finds within the movie fMRI data, we created
-four contrasts that compared hemodynamic activity during frames within movie
-shots (\texttt{no\_cut} category) with movie cut related categories
-(see Table~\ref{tab:contrasts}).
+To test for the specificity of the main findings within the movie fMRI data, we
+created four contrasts that compared hemodynamic activity during frames within
+movie shots (\texttt{no\_cut} category) with movie cut related categories (see
+Table~\ref{tab:contrasts}).
 % results
-None of these four contrasts yielded a significant cluster, suggesting that
-the observed differential hemodynamic response in the PPA for events defined
-by particular movie cuts is not observed for other arbitrarily selected time point
+None of these four contrasts yielded a significant cluster, suggesting that the
+observed differential hemodynamic response in the PPA for events defined by
+particular movie cuts is not observed for other arbitrarily selected time point
 in the movie.
@@
 % \texttt{vse\_old}.
-The correlation of regressors across stimuli
-(Figure~\ref{fig:reg-corr}) showed a moderate correlation among cuts to a setting
-depicted for the first time (movie \texttt{vse\_new}) and nouns indicating a switch to
-a setting occurring for the first time (audio-description \texttt{se\_new}), and cuts to a
-recurringly depicted setting (movie {\texttt{vse\_old}) and nouns indicating a switch
-a recurring setting (audio-description \texttt{se\_old}).
+The correlation of regressors across stimuli (Figure~\ref{fig:reg-corr}) showed
+a moderate correlation among cuts to a setting depicted for the first time
+(movie \texttt{vse\_new}) and nouns indicating a switch to a setting occurring
+for the first time (audio-description \texttt{se\_new}), and cuts to a
+recurringly depicted setting (movie {\texttt{vse\_old}) and nouns indicating a
+switch a recurring setting (audio-description \texttt{se\_old}).
 %
 Hence, we computed an indentical contrast ({\texttt{se\_new} >
-\texttt{se\_old}), comparing the audio-description's voice-over narrator
-nouns for the movie data and the audio-description.
+\texttt{se\_old}), comparing the audio-description's voice-over narrator nouns
+for the movie data and the audio-description.
 % results
-While for the movie data the contrast yielded a significant cluster in the
-right PPA, not in its anterior portion, and bilateral clusters in the
-superior lateral occipital cortices (the right hemispheric cluster extending
-into the superior parietal cortex), not significant differences where found
-for the audio-description (unthresholded contrast maps are available on NeuroVault).
-%
-These results suggest that in the absence of the actual visual stimulation, the narrator's
-description of scene properties correlated with setting changes did not co-occur with
-increased hemodynamic activity in areas associated with the processing of spatial
-information.
+While for the movie data the contrast yielded a significant cluster in the right
+PPA, not in its anterior portion, and bilateral clusters in the superior lateral
+occipital cortices (the right hemispheric cluster extending into the superior
+parietal cortex), not significant differences where found for the
+audio-description (unthresholded contrast maps are available on NeuroVault).
+%
+These results suggest that in the absence of the actual visual stimulation, the
+narrator's description of scene properties correlated with setting changes did
+not co-occur with increased hemodynamic activity in areas associated with the
+processing of spatial information.
 
@@
 Finally for the analysis of the audio-description, we computed control contrasts
-based on events of the annotated movie cuts (Table~\ref{tab:contrasts}) in
-order to evaluate the influence of stimulus features correlated with these visual
-events that remain present in the audio-description, such as changes in the soundscape.
+based on events of the annotated movie cuts (Table~\ref{tab:contrasts}) in order
+to evaluate the influence of stimulus features correlated with these visual
+events that remain present in the audio-description, such as changes in the
+soundscape.
 % results
@@
 %
-The absence of observable hemodynamic response differences in the PPA suggests that
-without the visual information in the movie stimulus, no, or substantially less,
-processing of stimulus content with respect to spatial information co-occurred with
-the timing of the movie cuts.
+The absence of observable hemodynamic response differences in the PPA suggests
+that without the visual information in the movie stimulus, no, or substantially
+less, processing of stimulus content with respect to spatial information
+co-occurred with the timing of the movie cuts.
 

### 2021-08-13 paper/main.tex
update scripts

@@
 Studies in the field of neuropsychology and neuroimaging
-(\citep[e.g.,][]{penfield1950cerebral, fox1984noninvasive}) have shown that different
-parts of the brain are specialized for different perceptual and cognitive
-functions.
+(\citep[e.g.,][]{penfield1950cerebral, fox1984noninvasive}) have shown that
+different parts of the brain are specialized for different perceptual and
+cognitive functions.
 % occipital cortex for vision -> two pathways
-The occipital cortex is considered to be primarily involved in the early stages
-of visual perception and giving rise to two distinct pathways that process
-different kind of visual information:
+the occipital cortex is considered to be primarily involved in the early stages
+of visual perception and giving rise to two distinct [but interacting] pathways
+that serve different functions:
 % dorsal vs ventral pathway
-a dorsal stream (the ``where pathway'') that leads into the parietal lobe, and a
-ventral stream (the ``what pathway'') that leads into the temporal lobe
-\citep{goodale1992separate, mishkin1982contribution}.
-
-\todo[inline]{Goodale and Milner (1992), which is literally a call for what and
-    how pathways. The function of these pathways remains in dispute but its
-    clear that where (spatial processing) must take place in both streams. You
-should probably acknowledge that.}
+a) a dorsal stream (the ``how pathway'') that [leads into the parietal lobe,]
+and supports [nonconscious] visual guidance of action, and
+b) a ventral stream (the ``what pathway'') that [leads into the temporal lobe
+and] supports [conscious] perception and recognition.
+\citep{goodale1992separate, milner2017two, mishkin1982contribution}.
+
+\todo[inline]{reviewer #1: its clear that where (spatial processing) must take
+place in both streams. You should probably acknowledge that.}
 % PPA
@@
 faces or tools) during blood oxygenation level-dependent functional magnetic
-resonance imaging (BOLD fMRI) (\citep[see reviews][]{epstein2014neural, aminoff2013role}).
+resonance imaging (BOLD fMRI) (\citep[see reviews][]{epstein2014neural,
+aminoff2013role}).
 % \citep{aguirre1998area, epstein2014neural, epstein1998ppa, troiani2012object}.
@@
 vpe\_old}) yielded three significant clusters (see Table~\ref{tab:res-av-group1},
-Figgure~\ref{fig:group-slices}).
+Figure~\ref{fig:group-slices}).
 % PPA (others the clusters extend into).
@@
         (\texttt{geo, groom > all non-geo}) are overlaid over the movie's
-        primary $t$-contrast (blue) that compares cuts to setting depicted for
+        primary $t$-contrast (red) that compares cuts to setting depicted for
         the first time with cuts within a recurring setting
@@
         Black:
-        outline of participant-specific PPA ROIs.
+        outline of participant-specific PPA ROIs reported by
+        \citet{sengupta2016extension}.
         Light gray: The
@@
 
-\section*{Data (and code) availability}
+\section*{Data availability}
 
@@
 results as Datalad \citep{datalad} datasets, published to or linked from the
-GIN repository
-\href{https://gin.g-node.org/chaeusler/studyforrest-ppa-analysis}{\url{gin.g-node.org/chaeusler/studyforrest-ppa-analysis}} (DOI assignment pending).
+GIN repository \href{https://gin.g-node.org/chaeusler/studyforrest-ppa-analysis}{\url{gin.g-node.org/chaeusler/studyforrest-ppa-analysis}} (DOI assignment pending).
 Unthresholded $Z$-maps of all contrasts can be found at
@@
 
-\todo[inline]{Please also split "Code and Data availability" into two sections}
+Scripts to generate the results as Datalad \citep{datalad} are published to a
+GIN repository \href{https://gin.g-node.org/chaeusler/studyforrest-ppa-analysis}{\url{gin.g-node.org/chaeusler/studyforrest-ppa-analysis}} (DOI assignment pending).
 
@@
 
+\subsection*{Surface maps}
+
+\todo[inline]{Just mention this part in the main document via 'the corresponding
+surface plots (Fig xy) can be found in the supplemental materials'?}
+\todo[inline]{write intro regarding purpose of additional surface plots?}
+
+% reconstruction MNI
+Cortical reconstruction of the MNI152 T1-weighted brain template
+[MNI152\_T1\_1mmi\_brain.nii.gz] was performed using
+\href{https://surfer.nmr.mgh.harvard.edu}{FreeSurfer} v7.1.1
+\citep{dale1999cortical}.
+% reconstruction: individual results
+Subject-specific cortical surfaces are part of pre-existing
+\href{https://github.com/psychoinformatics-de/studyforrest-data-freesurfer.git}{dataset}
+that used FreeSurfer v5.3.0 to reconstruct surfaces from T1-weighted images and
+an additional high-resolution T2-weighted image.
+
+% projection
+Results were projected onto the corticals surface using
+\href{https://surfer.nmr.mgh.harvard.edu}{FreeSurfer's} \citep{dale1999cortical}
+'mri\_vol2surf' command.
+% smoothing
+Group and individual PPAs were additionally patially smoothed applying a
+Gaussian kernel with full width at half maximum (FWHM) of \unit[3.0]{mm}.
+
+\subsubsection*{Group results}
+Group results see Table~\ref{tab:res-ao-group1} for AO results,
+Table~\ref{tab:res-av-group1} for AV results, and
+Figure~\ref{fig:grp_ao_av_c1_surf} for surface maps.
+
+\begin{figure*}[tbp]
+\centering
+    \includegraphics[width=\linewidth]{figures/grp_ao_av_c1_surf}
+
+    \caption{Mixed-effects group-level (N=14) clusters ($Z$>3.4, $p$<.05
+      cluster-corrected) of activity correlated with the processing of spatial
+      information are projected onto the surface of the MNI152
+      T1-weighted template.
+      %
+      The results of the audio-description's primary $t$-contrast (blue) that
+      compares geometry-related nouns spoken by the narrator to non-spatial
+      nouns (\texttt{geo, groom} > all non-spatial categories) are overlaid
+      on the movie's primary $t$-contrast (red) that compares cuts to a
+      setting depicted for the first time with cuts within a recurring setting
+      (\texttt{vse\_new > vpe\_old}).
+      %
+      Black: outline of the union of individual PPA ROIs reported by
+      \citet{sengupta2016extension}.
+    }
+    \label{fig:grp_ao_av_c1_surf}
+\end{figure*}
+
+\subsubsection*{Stability}
+Group results see Figure~\ref{fig:grp_ao_av_stability} for surface maps.
+
+\begin{figure*}[tbp]
+\centering
+    \includegraphics[width=\linewidth]{figures/grp_ao_av_stability_surf}
+    \caption{Overlap of significant clusters ($Z$>3.4; $p$<.05, cluster
+        corrected) across all contrasts for both naturalistic stimuli.
+        The audio-description's contrasts 1-8 (blue)
+        are overlaid over the audio-visual movie's contrasts 1-5 (red;
+        \ref{tab:contrasts}).
+        Cluster are projected onto the surface of the
+        MNI152 T1-weighted template.
+        Black: outline of the union of individual PPA ROIs reported by
+        \citet{sengupta2016extension}.
+        }
+    \label{fig:grp_ao_av_stability}
+\end{figure*}
+
+\subsubsection*{Individual resultsStability}
+
+Individual results see Figure~\ref{fig:subjs_ao_av_c1_surf} for surface maps.
+\todo[inline]{RSC in of AV is essentially not visible}
+
+\begin{figure*}[tbp]
+\centering
+    \includegraphics[width=\linewidth]{figures/subjs_ao_av_c1_surf}
+    \caption{Fixed-effects individual-level GLM results ($Z$>3.4, $p$<.05
+        cluster-corrected)
+        projected onto subject-specific brain surface that were
+        [re]constructed from individual T1-weighted brain images.
+        The results of the audio-description's primary
+        $t$-contrast (blue) that compares geometry related nouns to non-
+        geometry related nouns spoken by the narrator
+        (\texttt{geo, groom > all non-geo}) are overlaid over the movie's
+        primary $t$-contrast (red) that compares cuts to setting depicted for
+        the first time with cuts within a recurring setting
+        (\texttt{vse\_new > vpe\_old}).
+        Black: outline of participant-specific PPA ROIs reported by
+        \citet{sengupta2016extension}.
+        }
+    \label{fig:subjs_ao_av_c1_surf}
+\end{figure*}
+
 \end{document}

### 2021-08-13 code/plot-surface-maps.py

@@ -128,7 +128,7 @@ def create_grp_surfaces(in_path, out_path):
     '''Converts brain volume files to surface maps
     '''
     out_path = opj(out_path, 'in_t1w')
-    os.makedirs(outPath, exist_ok=True)
+    os.makedirs(out_path, exist_ok=True)
 
     # input files
     in_files = dict(
@@ -236,8 +236,8 @@ def process_grp_plotting(inPath, outPath):
     right = opj(inPath, 'ao_c1_z3.4_surf_rh.mgz')
     color_map = plt.cm.get_cmap('Blues')
     color_map = color_map.reversed()
-    thresh = 3.4  # range should be >3.4
-    out_fname = opj(outPath, f'grp_ao_c1_surf_thresh{thresh}.png')
+    thresh = 3.4  # usually 3.4
+    out_fname = opj(outPath, f'grp_ao_c1_surf.png')
 
     create_2x4_plot(left, right,
                     color_map,
@@ -253,8 +253,8 @@ def process_grp_plotting(inPath, outPath):
     right = opj(inPath, 'av_c1_z3.4_surf_rh.mgz')
     color_map = plt.cm.get_cmap('YlOrRd')
     color_map = color_map.reversed()
-    thresh = 3.4  # range should be >3.4
-    out_fname = opj(outPath, f'grp_av_c1_surf_thresh{thresh}.png')
+    thresh = 3.4  # usually 3.4
+    out_fname = opj(outPath, f'grp_av_c1_surf.png')
 
     create_2x4_plot(left, right,
                     color_map,
@@ -271,7 +271,7 @@ def process_grp_plotting(inPath, outPath):
     color_map = plt.cm.get_cmap('Blues')
     color_map = color_map.reversed()
     thresh = 1  # usually 1
-    out_fname = opj(outPath, f'grp_ao_stability_surf_thresh{thresh}.png')
+    out_fname = opj(outPath, f'grp_ao_stability_surf.png')
 
     create_2x4_plot(left, right,
                     color_map,
@@ -288,7 +288,7 @@ def process_grp_plotting(inPath, outPath):
     color_map = plt.cm.get_cmap('YlOrRd')
     color_map = color_map.reversed()
     thresh = 1  # usually 1
-    out_fname = opj(outPath, f'grp_av_stability_surf_thresh{thresh}.png')
+    out_fname = opj(outPath, f'grp_av_stability_surf.png')
 
     create_2x4_plot(left, right,
                     color_map,
[…]

### 2021-08-13 code/plot-surface-maps.py
uncomment calls of functions

@@ -1093,18 +1093,18 @@ if __name__ == "__main__":
     # environment variable 'FREESURFER_HOME' must be set
     # call the function that calls freesurfer's mri_vol2surf
     print('create group surface')
-#    create_grp_surfaces(inPath, inPath)
+    create_grp_surfaces(inPath, inPath)
 
     # create surface maps in individual bold3Tp2 spaces
     print('create individual surfaces')
-#    create_ind_surfaces(inPath, inPath)
+    create_ind_surfaces(inPath, inPath)
 
     # plotting of surfaces in group space:
     # a) union of dedicated visualizer ROIS
     # b) primary AO & AV contrasts,
     # c) stability of AO & AV contrats
     print('processing plotting of group surfaces')
-#    process_grp_plotting(inPath, outPath)
+    process_grp_plotting(inPath, outPath)
 
     # plotting of surfaces in individual bold3Tp2 space
     # a) individual ROIs
@@ -1112,10 +1112,8 @@ if __name__ == "__main__":
     print('processing plotting of individuals')
     process_individuals_plotting(inPath, outPath, FG_FREESURFER)
 
-    # binary oder probabilistic input? (from nilearn.image import smooth_img)
-    print('processing legends and 1 colorbar')
-#    process_legend_1colorbar(outPath)
-
-    # binary oder probabilistic input? (from nilearn.image import smooth_img)
     print('processing legends and 2 colorbars')
     process_legend_2colorbars(outPath)
+
+    # print('processing legends and 1 colorbar')
+    # process_legend_1colorbar(outPath)

### 2021-08-20 paper/main.tex
add (preliminary) PDFs of surface maps
move Supplementals to separate file

@@
 \usepackage[comma,super,sort&compress]{natbib}
-
+\usepackage{xr}
+\externaldocument{suppl}
 % \usepackage{helvet}
@@
 
+\todo[inline]{possibly drop some words in ``how''-``what'' sentence if it's
+considered to be wordy}
+
 % brain mapping via fMRI
@@
 \citep{goodale1992separate, milner2017two, mishkin1982contribution}.
-
-\todo[inline]{reviewer #1: its clear that where (spatial processing) must take
-place in both streams. You should probably acknowledge that.}
 % PPA
@@
 % open question
+\todo[inline]{I revised the following paragraph; I guess it's okay that way}
 In this study, we investigate whether increased hemodynamic activity in the PPA
@@
 %during two naturalistic stimuli lead to increased hemodynamic activity in the
-m%PPA.
+%PPA.
 %% anterior vs. posterior
@@
 \section*{Results}
+
+\todo[inline]{Summarize some methods here?}
 
@@
 %#11 question
-The fact that clusters of responses to the auditory stimulus are spatially restricted to
-the anterior part of clusters from both visual paradigms raises the question if
-the revealed correlation patterns can be attributed to different features
-inherent in the visual stimuli compared to a purely auditory stimulus.
+The fact that clusters of responses to the auditory stimulus are spatially
+restricted to the anterior part of clusters from both visual paradigms raises
+the question if the revealed correlation patterns can be attributed to different
+features inherent in the visual stimuli compared to a purely auditory stimulus.
 % visual scenes: probably submodules
-In the domain of visual scene perception, previous studies provide evidence
-that the PPA can be divided into functionally subregions that might process
-different stimulus features.
+In the domain of visual scene perception, previous studies provide evidence that
+the PPA can be divided into functionally subregions that might process different
+stimulus features.
 % posterior: functionality
@@
 aPPA \citep{baldassano2013differential, baldassano2016two}.
-% including lateral occipital cortex (LOC) and transverse occipital sulcus
-% (TOS) anterior
+% including lateral occipital cortex (LOC) and transverse occipital sulcus (TOS)
+% anterior
 Activity in the aPPA, on the other hand, is found to be correlated with
 components of the default mode network, including caudal inferior parietal lobe,
-retrosplenial complex, medial prefrontal cortex, and lateral surface of
-the anterior temporal lobe \citep{baldassano2013differential,
-baldassano2016two}.
+retrosplenial complex, medial prefrontal cortex, and lateral surface of the
+anterior temporal lobe \citep{baldassano2013differential, baldassano2016two}.
 % conclusion: subregions
@@
 subregions of the PPA.
-% Their distinct connectivity properties do suggest that each may be involved
-% in specific aspects of visual and cognitive processing involved in the
+% Their distinct connectivity properties do suggest that each may be involved in
+% specific aspects of visual and cognitive processing involved in the
 % overarching goal of scene understanding \citep{baldassano2013differential}.
@@
 % navigationally-relevant [Janzen and Van Turennout 2004]. These types of
-% responses require spatial memory and cannot be based purely on visual
-% features like object shape. \citep{baldassano2013differential}.  pPPA
+% responses require spatial memory and cannot be based purely on visual features
+% like object shape. \citep{baldassano2013differential}.  pPPA
 Similarly, our results suggest that the pPPA is more concerned with visual
-aspects inherent in pictures or movie shots of landscapes.
+spatial features that are intrinsic to pictures or movie shots of
+landscapes.
 % aPPA
-The aPPA might be more concerned with non-visual aspects of spatial information
-(e.g. spatial contextual information \citep{aminoff2007parahippocampal}) as
-inherent in both visual and verbal stimuli.
+The aPPA might be more concerned with non-visual spatial features
+(e.g. spatial contextual information \citep{aminoff2007parahippocampal}) that
+are intrinsic to visual but also verbal stimuli.
 
@@
 implicated in visual spatial perception and cognition.
+
+\todo[inline]{Maybe add sentence here that ``further studies are obvious''}
 
@@
 % motion parameters
-Lastly, six participant- and run-specific motion estimates (translation and
-rotation) were also included.
+Lastly, six participant-specific and run-specific motion estimates (translation
+and rotation) were also included.
 % high-pass filtering
@@
 
-\section*{Data availability}
+\section*{Data Availability}
 
@@
 
-\section*{Code availability}
+\section*{Code Availability}
 
@@
 
-\section*{Competing financial interests}
+\section*{Competing Interests}
 
@@
 
-\appendix
-
-\pagebreak[4]
-
-\setcounter{figure}{0}
-\makeatletter
-\renewcommand{\thefigure}{S\@arabic\c@figure}
-\makeatother
-
-\section{Supplementary Materials}
-
-\subsection*{Robustness of main findings across alternative contrasts}
-
-In order to test the robustness of our approach, we created overall five
-$t$-contrasts for the movie stimulus, and overall eight $t$-contrast for the
-audio-description (see Table~\ref{tab:contrasts}).
-% how
-Contrasts differ in contrasted categories based on ``how well'' averaged events
-within categories were considered to represent spatial and non-spatial
-information, and the number of events in the stimulus.
-% NeuroVault
-Unthresholded $Z$-maps of all contrasts on a group level co-registered to the
-group-template (MNI152 space) can be found at
-\href{https://neurovault.org/collections/KADGMGVZ/}{\url{neurovault.org/collections/KADGMGVZ}}.
-
-% AV PPA contrasts
-% 1 PPA (l/r); RSC (l/r), LOC (l/r), VisC (l/r),
-% intracalcarine, cuneal, ling.c
-% 2 PPA (l/r); RSC (-/-), LOC (l/r), VisC (-/-)
-% 3 PPA (l/r); RSC (-/-), LOC (-/-), VisC (-/r), occ. fusisf. g.
-% 4 PPA (l/r); RSC (l/r), LOC (l/r), VisC (-/-), lingual g., occ. fusif. g.
-% 5 PPA (l/r); RSC (l/r), LOC (l/r), VisC (-/-), occ. fusif. g.
-
-% AV results: PPA; biggest overlap in posterior part of PPA group overlap  =
-% temporal occipital fusiform cortex
-Reliably across all five movie contrasts, we find bilaterally significant
-clusters that overlap with the PPA group overlap
-(see Figure~\ref{fig:stability-slices}).
-% AV: RSC & LOC
-Several contrasts of the movie also yielded bilaterally significant clusters in
-the ventral precuneal cortex and posterior cingulate gyrus (i.e. retrosplenial
-complex; contrasts 1, 4, 5), and lateral occipital cortex (contrasts 1, 2, 4,
-5).
-
-% AD PPA contrasts
-% 1 PPA (l/r); RSC (l/r), LOC (l/r)
-% 2 PPA (l/r); RSC (l/r), LOC (l/r), r. sup.temp.C., r.fr.pole; putamen; etc
-% 3 PPA (l/r); RSC (l/r), LOC (l/r),l&r sup.temp.C., anterior cing., paracing.
-% 4 PPA (l/r); RSC (l/r), LOC (l/r)
-% 5 PPA (l/r); RSC (l/r), LOC (-/-)
-% 6 PPA (l/r); RSC (l/r), LOC (l/-), l&r sup.temp.C.; medial pref. c., precun
-% 7 PPA (-/-); RSC (l/r), LOC (l/-), l&r sup.temp.C.; left frontal pole
-% 8 PPA (-/-); RSC (-/-), LOC (-/-)
-
-% AD: results
-In results from the analysis of the audio-description, all contrasts except
-contrast 7 and 8  yielded significant bilateral clusters in anterior regions of
-the group PPA overlap (see Figure~\ref{fig:stability-slices}).
-% AD: RSC & LOC
-Contrasts of the audio-description also yielded bilaterally significant clusters
-in the ventral precuneus (all contrasts except contrasts 8) and lateral
-occipital cortex (bilateral in contrasts 1 to 4; unilateral in contrasts 6 and
-7).
-% concluding stament regarding PPA, RSC, and LOC
-Results across contrasts of both naturalistic stimuli indicate that our findings
-regarding the PPA but also RSC and LOC are robust and do not depend on the
-design of one specific contrasts.
-% but:
-Nevertheless, results are sensitive to the contrasted categories and the amount
-of available data.
-% example
-For example, contrast 7 and 8 (\texttt{se\_new}, \texttt{se\_old} > non-spatial
-categories, and \texttt{se\_new} > non-spatial categories) that used the most
-heterogeneous categories (nouns indicating switches to other settings) and a low
-amount of events yielded neither a significant cluster in the right-hemispheric
-nor left-hemispheric PPA.
-% concluding statement
-Hence, investigators that use model-driven analyses have to consider how many
-events a naturalistic stimulus may provide and how homogeneous the events to be
-averaged might be.
-
-\subsection*{Incidental results}
-
-Several contrasts yielded significant clusters in superior temporal cortices
-(bilateral in contrasts 3, 6, 7; unilateral right in contrast 2).
-% AD: auditory cortices
-Further, contrasts that compare, possibly among others, nouns indicating a
-switch to another setting (categories \texttt{se\_new} or \texttt{se\_old}) to
-non-spatial categories yielded significant clusters in superior temporal
-cortices (bilateral: contrasts 3, 6, 7; unilateral right: contrast 2).
-% interpretation 1
-This suggests that variance correlating with lower level auditory processes was
-not averaged out across events (e.g. switches to another setting might often not
-just cued by the narrator but also by a change of the soundscape or cued by a
-the start of a new song) and the employed nuisance regressors did not capture
-this variance appropriately.
-% interpretation 2
-Another possibility might be that increased hemodynamic activity in superior
-temporal cortices reflect a bias towards lower-level auditory perceptual
-processes on the positive side of the GLM contrasts.
-% soundscape
-Increased activity in primary and secondary auditory cortices could be
-attributed to changes in the soundscape that possibly accompany the narrator
-when he is indicating the switch to another setting by describing its identity
-or layout.
-
-Lastly, contrasts of the audio-description stimulus yielded clusters
-in regions that were classified as statistically significant in two or less contrasts.
-% contrast 2
-In detail, contrast 2 yielded clusters in the anterior cingulate gyrus
-(bilateral), right frontal pole, right frontal medial cortex, and right putamen.
-% contrast 3
-Contrast 3 shows clusters in the anterior cingulate gyrus (bilateral), left
-frontal pole, and left insular.
-% contrast 6
-Contrast 6 shows one additional cluster in the right medial frontal cortex.
-% contrast 7
-Contrast 7 shows clusters in the left frontal pole and left frontal operculum,
-left insular.
-% concluding statement
-Here again, significantly increased activation beyond areas known to be involved
-in processing of spatial information could be attributed to stimulus features of
-the naturalistic stimulus that were not sufficiently controlled leading to a
-bias in the contrasts.
-
-\begin{figure*}[tbp]
-\centering
-    \includegraphics[width=\linewidth]{figures/stability-slices}
-    \caption{Overlap of significant clusters ($Z$>3.4; $p$<.05, cluster corrected)
-        across all contrasts for both naturalistic stimuli.
-        The audio-description's contrasts 1-8 (blue)
-        are overlaid over the audio-visual movie's contrasts 1-5 (red;
-        \ref{tab:contrasts}).
-        Cluster are overlaid on top of the MNI152 T1-weighted head template
-        with the acquisition field-of-view for the audio-description study
-        highlighted.
-        Black: outline of the union of individual PPA ROIs reported by \citet{sengupta2016extension}.
-        }
-    \label{fig:stability-slices}
-\end{figure*}
-
-\subsection*{Control contrasts}
-
-% ---------- AV control contrasts ----------
-% 6: nothing; 7 nothing; 8: nothing; 9: nothing; 10 se_new > se_old (nouns but
-% in AV stimulus): LOC (l/r) right PPA, bilateral, sup. lat. occ. c., sup.
-% parietal lobe (right)
-
-% ---------- AD control contrasts ----------
-% 9 PPA (-/-); RSC (-/r), LOC (-/-), left pars triangularis
-%10 PPA (-/-); RSC (-/-), LOC (-/-)
-%11 PPA (-/-); RSC (-/-), LOC (-/-),
-%12 PPA (-/-); RSC (-/-), LOC (-/-), right posterior hippocampus
-%13 PPA (-/-); RSC (-/-), LOC (-/-)
-
-% intro
-For each naturalistic stimulus, we created several control contrasts.
-% movie contrasts: not cut condition vs. cuts
-To test for the specificity of the main findings within the movie fMRI data, we
-created four contrasts that compared hemodynamic activity during frames within
-movie shots (\texttt{no\_cut} category) with movie cut related categories (see
-Table~\ref{tab:contrasts}).
-% results
-None of these four contrasts yielded a significant cluster, suggesting that the
-observed differential hemodynamic response in the PPA for events defined by
-particular movie cuts is not observed for other arbitrarily selected time point
-in the movie.
-
-% \texttt{se\_new} (nouns) is r$\approx$0.3 correlated with \texttt{vse\_new}
-% (cuts); \texttt{se\_old} (nouns) is r$\approx$0.4 correlated with
-% \texttt{vse\_old}.
-The correlation of regressors across stimuli (Figure~\ref{fig:reg-corr}) showed
-a moderate correlation among cuts to a setting depicted for the first time
-(movie \texttt{vse\_new}) and nouns indicating a switch to a setting occurring
-for the first time (audio-description \texttt{se\_new}), and cuts to a
-recurringly depicted setting (movie {\texttt{vse\_old}) and nouns indicating a
-switch a recurring setting (audio-description \texttt{se\_old}).
-%
-Hence, we computed an indentical contrast ({\texttt{se\_new} >
-\texttt{se\_old}), comparing the audio-description's voice-over narrator nouns
-for the movie data and the audio-description.
-% results
-While for the movie data the contrast yielded a significant cluster in the right
-PPA, not in its anterior portion, and bilateral clusters in the superior lateral
-occipital cortices (the right hemispheric cluster extending into the superior
-parietal cortex), not significant differences where found for the
-audio-description (unthresholded contrast maps are available on NeuroVault).
-%
-These results suggest that in the absence of the actual visual stimulation, the
-narrator's description of scene properties correlated with setting changes did
-not co-occur with increased hemodynamic activity in areas associated with the
-processing of spatial information.
-
-% AD stimulus
-Finally for the analysis of the audio-description, we computed control contrasts
-based on events of the annotated movie cuts (Table~\ref{tab:contrasts}) in order
-to evaluate the influence of stimulus features correlated with these visual
-events that remain present in the audio-description, such as changes in the
-soundscape.
-% results
-Two of five contrasts yielded significant clusters.
-% contrast 9
-Contrast 9 (\texttt{vse\_new > pe\_old}) revealed one significant cluster in the
-left inferior prefrontal cortex (pars triangularis) and right ventral
-precuneus/posterior cingulate gyrus.
-% contrast 12
-Contrast 12 (\texttt{vse\_new} > \texttt{vse\_old}, \texttt{vpe\_old}) revealed
-one cluster in the right posterior hippocampus.
-%
-The absence of observable hemodynamic response differences in the PPA suggests
-that without the visual information in the movie stimulus, no, or substantially
-less, processing of stimulus content with respect to spatial information
-co-occurred with the timing of the movie cuts.
-
-\subsection*{Surface maps}
-
-\todo[inline]{Just mention this part in the main document via 'the corresponding
-surface plots (Fig xy) can be found in the supplemental materials'?}
-\todo[inline]{write intro regarding purpose of additional surface plots?}
-
-% reconstruction MNI
-Cortical reconstruction of the MNI152 T1-weighted brain template
-[MNI152\_T1\_1mmi\_brain.nii.gz] was performed using
-\href{https://surfer.nmr.mgh.harvard.edu}{FreeSurfer} v7.1.1
-\citep{dale1999cortical}.
-% reconstruction: individual results
-Subject-specific cortical surfaces are part of pre-existing
-\href{https://github.com/psychoinformatics-de/studyforrest-data-freesurfer.git}{dataset}
-that used FreeSurfer v5.3.0 to reconstruct surfaces from T1-weighted images and
-an additional high-resolution T2-weighted image.
-
-% projection
-Results were projected onto the corticals surface using
-\href{https://surfer.nmr.mgh.harvard.edu}{FreeSurfer's} \citep{dale1999cortical}
-'mri\_vol2surf' command.
-% smoothing
-Group and individual PPAs were additionally patially smoothed applying a
-Gaussian kernel with full width at half maximum (FWHM) of \unit[3.0]{mm}.
-
-\subsubsection*{Group results}
-Group results see Table~\ref{tab:res-ao-group1} for AO results,
-Table~\ref{tab:res-av-group1} for AV results, and
-Figure~\ref{fig:grp_ao_av_c1_surf} for surface maps.
-
-\begin{figure*}[tbp]
-\centering
-    \includegraphics[width=\linewidth]{figures/grp_ao_av_c1_surf}
-
-    \caption{Mixed-effects group-level (N=14) clusters ($Z$>3.4, $p$<.05
-      cluster-corrected) of activity correlated with the processing of spatial
-      information are projected onto the surface of the MNI152
-      T1-weighted template.
-      %
-      The results of the audio-description's primary $t$-contrast (blue) that
-      compares geometry-related nouns spoken by the narrator to non-spatial
-      nouns (\texttt{geo, groom} > all non-spatial categories) are overlaid
-      on the movie's primary $t$-contrast (red) that compares cuts to a
-      setting depicted for the first time with cuts within a recurring setting
-      (\texttt{vse\_new > vpe\_old}).
-      %
-      Black: outline of the union of individual PPA ROIs reported by
-      \citet{sengupta2016extension}.
-    }
-    \label{fig:grp_ao_av_c1_surf}
-\end{figure*}
-
-\subsubsection*{Stability}
-Group results see Figure~\ref{fig:grp_ao_av_stability} for surface maps.
-
-\begin{figure*}[tbp]
-\centering
-    \includegraphics[width=\linewidth]{figures/grp_ao_av_stability_surf}
-    \caption{Overlap of significant clusters ($Z$>3.4; $p$<.05, cluster
-        corrected) across all contrasts for both naturalistic stimuli.
-        The audio-description's contrasts 1-8 (blue)
-        are overlaid over the audio-visual movie's contrasts 1-5 (red;
-        \ref{tab:contrasts}).
-        Cluster are projected onto the surface of the
-        MNI152 T1-weighted template.
-        Black: outline of the union of individual PPA ROIs reported by
-        \citet{sengupta2016extension}.
-        }
-    \label{fig:grp_ao_av_stability}
-\end{figure*}
-
-\subsubsection*{Individual resultsStability}
-
-Individual results see Figure~\ref{fig:subjs_ao_av_c1_surf} for surface maps.
-\todo[inline]{RSC in of AV is essentially not visible}
-
-\begin{figure*}[tbp]
-\centering
-    \includegraphics[width=\linewidth]{figures/subjs_ao_av_c1_surf}
-    \caption{Fixed-effects individual-level GLM results ($Z$>3.4, $p$<.05
-        cluster-corrected)
-        projected onto subject-specific brain surface that were
-        [re]constructed from individual T1-weighted brain images.
-        The results of the audio-description's primary
-        $t$-contrast (blue) that compares geometry related nouns to non-
-        geometry related nouns spoken by the narrator
-        (\texttt{geo, groom > all non-geo}) are overlaid over the movie's
-        primary $t$-contrast (red) that compares cuts to setting depicted for
-        the first time with cuts within a recurring setting
-        (\texttt{vse\_new > vpe\_old}).
-        Black: outline of participant-specific PPA ROIs reported by
-        \citet{sengupta2016extension}.
-        }
-    \label{fig:subjs_ao_av_c1_surf}
-\end{figure*}
-
 \end{document}

### 2021-08-20 paper/suppl.tex
move Supplementals to separate file

\documentclass[english,11pt]{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{stix2}
\usepackage{babel}
\usepackage[section]{placeins}
\usepackage{flafter}
\usepackage{comment}
\usepackage{breakurl}
\usepackage{svg}
\usepackage[labelfont=bf,font=small]{caption}
\usepackage{booktabs}
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage{fancyhdr}
% \usepackage[disable]{todonotes}
\usepackage{todonotes}
\usepackage{units}
\usepackage[left=2.5cm,right=2.5cm,top=1cm,bottom=1cm,includeheadfoot]{geometry}
\usepackage[
colorlinks=true,
	citecolor=black,
  urlcolor=black,
	linkcolor=black
]{hyperref}
%\newcommand{\scidatalogo}{\includegraphics[height=36pt]{SciData_logo.jpg}}
\newcommand{\scidatalogo}{}
\pagestyle{fancy}
\fancyhf{}
\renewcommand{\headrulewidth}{0pt}
%\setlength{\headheight}{40pt}
%\lhead{\textsc{\scidatalogo}}
\usepackage[comma,super,sort&compress]{natbib}
\usepackage{xr}
\externaldocument{main}
\makeatletter
\renewcommand{\thefigure}{S\@arabic\c@figure}
\makeatother
% \usepackage{helvet}

% \renewcommand{\familydefault}{\sfdefault}

\begin{document}
\input{descr-stats-ao-events.tex}
\input{descr-stats-av-events.tex}
\input{descr-stats-anno.tex}

% title has to be < 110 chars incl. spaces at the moment 106 Chars
\title{Processing of visual and non-visual naturalistic spatial information in
  the "parahippocampal place area"}

\author{
    Christian~O.~Häusler\textsuperscript{1,2{*}},
    Simon B. Eickhoff\textsuperscript{1,2},
    Michael Hanke\textsuperscript{1,2}}
% https://www.nature.com/sdata/publish/for-authors#other-formats

\maketitle
\thispagestyle{fancy}

\noindent
1. Psychoinformatics Lab, Institute of Neuroscience and Medicine, Brain \&
Behaviour (INM-7), Research Centre Jülich, Jülich, Germany\\
\noindent
2. Institute of Systems Neuroscience, Medical Faculty, Heinrich Heine University,
Düsseldorf, Germany\\
{*}corresponding author: Christian Olaf Häusler (der.haeusler@gmx.net)

\section*{Supplementary Information}

\subsection*{Robustness of main findings across alternative contrasts}

In order to test the robustness of our approach, we created overall five
$t$-contrasts for the movie stimulus, and overall eight $t$-contrast for the
audio-description (see Table~\ref{tab:contrasts}).
% how
Contrasts differ in contrasted categories based on ``how well'' averaged events
within categories were considered to represent spatial and non-spatial
information, and the number of events in the stimulus.
% NeuroVault
Unthresholded $Z$-maps of all contrasts on a group level co-registered to the
group-template (MNI152 space) can be found at
\href{https://neurovault.org/collections/KADGMGVZ/}{\url{neurovault.org/collections/KADGMGVZ}}.

% AV PPA contrasts
% 1 PPA (l/r); RSC (l/r), LOC (l/r), VisC (l/r),
% intracalcarine, cuneal, ling.c
% 2 PPA (l/r); RSC (-/-), LOC (l/r), VisC (-/-)
% 3 PPA (l/r); RSC (-/-), LOC (-/-), VisC (-/r), occ. fusisf. g.
% 4 PPA (l/r); RSC (l/r), LOC (l/r), VisC (-/-), lingual g., occ. fusif. g.
% 5 PPA (l/r); RSC (l/r), LOC (l/r), VisC (-/-), occ. fusif. g.

% AV results: PPA; biggest overlap in posterior part of PPA group overlap  =
% temporal occipital fusiform cortex
Reliably across all five movie contrasts, we find bilaterally significant
clusters that overlap with the PPA group overlap
(see Figure~\ref{fig:stability-slices}).
% AV: RSC & LOC
Several contrasts of the movie also yielded bilaterally significant clusters in
the ventral precuneal cortex and posterior cingulate gyrus (i.e. retrosplenial
complex; contrasts 1, 4, 5), and lateral occipital cortex (contrasts 1, 2, 4,
5).

% AD PPA contrasts
% 1 PPA (l/r); RSC (l/r), LOC (l/r)
% 2 PPA (l/r); RSC (l/r), LOC (l/r), r. sup.temp.C., r.fr.pole; putamen; etc
% 3 PPA (l/r); RSC (l/r), LOC (l/r),l&r sup.temp.C., anterior cing., paracing.
% 4 PPA (l/r); RSC (l/r), LOC (l/r)
% 5 PPA (l/r); RSC (l/r), LOC (-/-)
% 6 PPA (l/r); RSC (l/r), LOC (l/-), l&r sup.temp.C.; medial pref. c., precun
% 7 PPA (-/-); RSC (l/r), LOC (l/-), l&r sup.temp.C.; left frontal pole
% 8 PPA (-/-); RSC (-/-), LOC (-/-)

% AD: results
In results from the analysis of the audio-description, all contrasts except
contrast 7 and 8  yielded significant bilateral clusters in anterior regions of
the group PPA overlap (see Figure~\ref{fig:stability-slices}).
% AD: RSC & LOC
Contrasts of the audio-description also yielded bilaterally significant clusters
in the ventral precuneus (all contrasts except contrasts 8) and lateral
occipital cortex (bilateral in contrasts 1 to 4; unilateral in contrasts 6 and
7).
% concluding stament regarding PPA, RSC, and LOC
Results across contrasts of both naturalistic stimuli indicate that our findings
regarding the PPA but also RSC and LOC are robust and do not depend on the
design of one specific contrasts.
% but:
Nevertheless, results are sensitive to the contrasted categories and the amount
of available data.
% example
For example, contrast 7 and 8 (\texttt{se\_new}, \texttt{se\_old} > non-spatial
categories, and \texttt{se\_new} > non-spatial categories) that used the most
heterogeneous categories (nouns indicating switches to other settings) and a low
amount of events yielded neither a significant cluster in the right-hemispheric
nor left-hemispheric PPA.
% concluding statement
Hence, investigators that use model-driven analyses have to consider how many
events a naturalistic stimulus may provide and how homogeneous the events to be
averaged might be.

\subsection*{Incidental results}

Several contrasts yielded significant clusters in superior temporal cortices
(bilateral in contrasts 3, 6, 7; unilateral right in contrast 2).
% AD: auditory cortices
Further, contrasts that compare, possibly among others, nouns indicating a
switch to another setting (categories \texttt{se\_new} or \texttt{se\_old}) to
non-spatial categories yielded significant clusters in superior temporal
cortices (bilateral: contrasts 3, 6, 7; unilateral right: contrast 2).
% interpretation 1
This suggests that variance correlating with lower level auditory processes was
not averaged out across events (e.g. switches to another setting might often not
just cued by the narrator but also by a change of the soundscape or cued by a
the start of a new song) and the employed nuisance regressors did not capture
this variance appropriately.
% interpretation 2
Another possibility might be that increased hemodynamic activity in superior
temporal cortices reflect a bias towards lower-level auditory perceptual
processes on the positive side of the GLM contrasts.
% soundscape
Increased activity in primary and secondary auditory cortices could be
attributed to changes in the soundscape that possibly accompany the narrator
when he is indicating the switch to another setting by describing its identity
or layout.

%
Lastly, contrasts of the audio-description stimulus yielded clusters
in regions that were classified as statistically significant in two or less contrasts.
% contrast 2
In detail, contrast 2 yielded clusters in the anterior cingulate gyrus
(bilateral), right frontal pole, right frontal medial cortex, and right putamen.
% contrast 3
Contrast 3 shows clusters in the anterior cingulate gyrus (bilateral), left
frontal pole, and left insular.
% contrast 6
Contrast 6 shows one additional cluster in the right medial frontal cortex.
% contrast 7
Contrast 7 shows clusters in the left frontal pole and left frontal operculum,
left insular.
% concluding statement
Here again, significantly increased activation beyond areas known to be involved
in processing of spatial information could be attributed to stimulus features of
the naturalistic stimulus that were not sufficiently controlled leading to a
bias in the contrasts.

\begin{figure*}[tbp]
\centering
    \includegraphics[width=\linewidth]{figures/stability-slices}
    \caption{Overlap of significant clusters ($Z$>3.4; $p$<.05, cluster corrected)
        across all contrasts for both naturalistic stimuli.
        The audio-description's contrasts 1-8 (blue)
        are overlaid over the audio-visual movie's contrasts 1-5 (red;
        see Table~\ref{tab:contrasts}).
        Cluster are overlaid on top of the MNI152 T1-weighted head template
        with the acquisition field-of-view for the audio-description study
        highlighted.
        Black: outline of the union of individual PPA ROIs reported by \citet{sengupta2016extension}.
        }
    \label{fig:stability-slices}
\end{figure*}

\subsection*{Control contrasts}

% ---------- AV control contrasts ----------
% 6: nothing; 7 nothing; 8: nothing; 9: nothing; 10 se_new > se_old (nouns but
% in AV stimulus): LOC (l/r) right PPA, bilateral, sup. lat. occ. c., sup.
% parietal lobe (right)

% ---------- AD control contrasts ----------
% 9 PPA (-/-); RSC (-/r), LOC (-/-), left pars triangularis
%10 PPA (-/-); RSC (-/-), LOC (-/-)
%11 PPA (-/-); RSC (-/-), LOC (-/-),
%12 PPA (-/-); RSC (-/-), LOC (-/-), right posterior hippocampus
%13 PPA (-/-); RSC (-/-), LOC (-/-)

% intro
For each naturalistic stimulus, we created several control contrasts.
% movie contrasts: not cut condition vs. cuts
To test for the specificity of the main findings within the movie fMRI data, we
created four contrasts that compared hemodynamic activity during frames within
movie shots (\texttt{no\_cut} category) with movie cut related categories (see
Table~\ref{tab:contrasts}).
% results
None of these four contrasts yielded a significant cluster, suggesting that the
observed differential hemodynamic response in the PPA for events defined by
particular movie cuts is not observed for other arbitrarily selected time point
in the movie.

% \texttt{se\_new} (nouns) is r$\approx$0.3 correlated with \texttt{vse\_new}
% (cuts); \texttt{se\_old} (nouns) is r$\approx$0.4 correlated with
% \texttt{vse\_old}.
The correlation of regressors across stimuli (Figure~\ref{fig:reg-corr}) showed
a moderate correlation among cuts to a setting depicted for the first time
(movie \texttt{vse\_new}) and nouns indicating a switch to a setting occurring
for the first time (audio-description \texttt{se\_new}), and cuts to a
recurringly depicted setting (movie {\texttt{vse\_old}) and nouns indicating a
switch a recurring setting (audio-description \texttt{se\_old}).
%
Hence, we computed an indentical contrast ({\texttt{se\_new} >
\texttt{se\_old}), comparing the audio-description's voice-over narrator nouns
for the movie data and the audio-description.
% results
While for the movie data the contrast yielded a significant cluster in the right
PPA, not in its anterior portion, and bilateral clusters in the superior lateral
occipital cortices (the right hemispheric cluster extending into the superior
parietal cortex), not significant differences where found for the
audio-description (unthresholded contrast maps are available on NeuroVault).
%
These results suggest that in the absence of the actual visual stimulation, the
narrator's description of scene properties correlated with setting changes did
not co-occur with increased hemodynamic activity in areas associated with the
processing of spatial information.

% AD stimulus
Finally for the analysis of the audio-description, we computed control contrasts
based on events of the annotated movie cuts (Table~5) in order
to evaluate the influence of stimulus features correlated with these visual
events that remain present in the audio-description, such as changes in the
soundscape.
% results
Two of five contrasts yielded significant clusters.
% contrast 9
Contrast 9 (\texttt{vse\_new > pe\_old}) revealed one significant cluster in the
left inferior prefrontal cortex (pars triangularis) and right ventral
precuneus/posterior cingulate gyrus.
% contrast 12
Contrast 12 (\texttt{vse\_new} > \texttt{vse\_old}, \texttt{vpe\_old}) revealed
one cluster in the right posterior hippocampus.
%
The absence of observable hemodynamic response differences in the PPA suggests
that without the visual information in the movie stimulus, no, or substantially
less, processing of stimulus content with respect to spatial information
co-occurred with the timing of the movie cuts.

\subsection*{Surface maps}

\todo[inline]{Just mention this part in the main document via 'the corresponding
surface plots (Fig xy) can be found in the supplemental materials'?}
\todo[inline]{write intro regarding purpose of additional surface plots?}

% reconstruction MNI
Cortical reconstruction of the MNI152 T1-weighted brain template
[MNI152\_T1\_1mmi\_brain.nii.gz] was performed using
\href{https://surfer.nmr.mgh.harvard.edu}{FreeSurfer} v7.1.1
\citep{dale1999cortical}.
% reconstruction: individual results
Subject-specific cortical surfaces are part of pre-existing
\href{https://github.com/psychoinformatics-de/studyforrest-data-freesurfer.git}{dataset}
that used FreeSurfer v5.3.0 to reconstruct surfaces from T1-weighted images and
an additional high-resolution T2-weighted image.

% projection
Results were projected onto the corticals surface using
\href{https://surfer.nmr.mgh.harvard.edu}{FreeSurfer's} \citep{dale1999cortical}
'mri\_vol2surf' command.
% smoothing
Group and individual PPAs were additionally patially smoothed applying a
Gaussian kernel with full width at half maximum (FWHM) of \unit[3.0]{mm}.

\subsubsection*{Group results}
Group results see Table~\ref{tab:res-ao-group1} for AO results,
Table~\ref{tab:res-av-group1} for AV results, and
Figure~\ref{fig:grp_ao_av_c1_surf} for surface maps.

\begin{figure*}[tbp]
\centering
    \includegraphics[width=\linewidth]{figures/grp_ao_av_c1_surf}

    \caption{Mixed-effects group-level (N=14) clusters ($Z$>3.4, $p$<.05
      cluster-corrected) of activity correlated with the processing of spatial
      information are projected onto the surface of the MNI152
      T1-weighted template.
      %
      The results of the audio-description's primary $t$-contrast (blue) that
      compares geometry-related nouns spoken by the narrator to non-spatial
      nouns (\texttt{geo, groom} > all non-spatial categories) are overlaid
      on the movie's primary $t$-contrast (red) that compares cuts to a
      setting depicted for the first time with cuts within a recurring setting
      (\texttt{vse\_new > vpe\_old}).
      %
      Black: outline of the union of individual PPA ROIs reported by
      \citet{sengupta2016extension}.
    }
    \label{fig:grp_ao_av_c1_surf}
\end{figure*}

\subsubsection*{Stability}
Group results see Figure~\ref{fig:grp_ao_av_stability} for surface maps.

\begin{figure*}[tbp]
\centering
    \includegraphics[width=\linewidth]{figures/grp_ao_av_stability_surf}
    \caption{Overlap of significant clusters ($Z$>3.4; $p$<.05, cluster
        corrected) across all contrasts for both naturalistic stimuli.
        The audio-description's contrasts 1-8 (blue)
        are overlaid over the audio-visual movie's contrasts 1-5 (red;
        \ref{tab:contrasts}).
        Cluster are projected onto the surface of the
        MNI152 T1-weighted template.
        Black: outline of the union of individual PPA ROIs reported by
        \citet{sengupta2016extension}.
        }
    \label{fig:grp_ao_av_stability}
\end{figure*}

\subsubsection*{Individual results}

\todo[inline]{RSC in of AV is essentially not visible}

Individual results see Figure~\ref{fig:subjs_ao_av_c1_surf} for surface maps.

\begin{figure*}[tbp]
\centering
    \includegraphics[width=\linewidth]{figures/subjs_ao_av_c1_surf}
    \caption{Fixed-effects individual-level GLM results ($Z$>3.4, $p$<.05
        cluster-corrected)
        projected onto subject-specific brain surface that were
        [re]constructed from individual T1-weighted brain images.
        The results of the audio-description's primary
        $t$-contrast (blue) that compares geometry related nouns to non-
        geometry related nouns spoken by the narrator
        (\texttt{geo, groom > all non-geo}) are overlaid over the movie's
        primary $t$-contrast (red) that compares cuts to setting depicted for
        the first time with cuts within a recurring setting
        (\texttt{vse\_new > vpe\_old}).
        Black: outline of participant-specific PPA ROIs reported by
        \citet{sengupta2016extension}.
        }
    \label{fig:subjs_ao_av_c1_surf}
\end{figure*}

{\small\bibliographystyle{unsrtnat}
\bibliography{references}}

%\begin{thebibliography}{1}
%\expandafter\ifx\csname url\endcsname\relax
%  \def\url#1{\texttt{#1}}\fi
%\expandafter\ifx\csname urlprefix\endcsname\relax\def\urlprefix{URL }\fi
%\providecommand{\bibinfo}[2]{#2}
%\providecommand{\eprint}[2][]{\url{#2}}
%
%\bibitem{cite1}
%\bibinfo{author}{Califano, A.}, \bibinfo{author}{Butte, A.~J.},
%  \bibinfo{author}{Friend, S.}, \bibinfo{author}{Ideker, T.} \&
%  \bibinfo{author}{Schadt, E.}
%\newblock \bibinfo{title}{{Leveraging models of cell regulation and GWAS data
%  in integrative network-based association studies}}.
%\newblock \emph{\bibinfo{journal}{Nature Genetics}}
%  \textbf{\bibinfo{volume}{44}}, \bibinfo{pages}{841--847}
%  (\bibinfo{year}{2012}).
%
%\bibitem{cite2}
%\bibinfo{author}{Wang, R.} \emph{et~al.}
%\newblock \bibinfo{title}{{PRIDE Inspector: a tool to visualize and validate MS
%  proteomics data.}}
%\newblock \emph{\bibinfo{journal}{Nature Biotechnology}}
%  \textbf{\bibinfo{volume}{30}}, \bibinfo{pages}{135--137}
%  (\bibinfo{year}{2012}).
%\end{thebibliography}

\setcounter{figure}{0}

\end{document}

### 2021-08-20 paper/suppl.tex
some (non-caption) text for surface plots

@@
 
+\todo[inline]{Position der Abbildungen ist im kompilierten PDF maximal
+verwirrend}
+
+\subsubsection*{Surface plot of group results}
+
+% intro
+Figure~\ref{fig:grp_ao_av_c1_surf} shows the group results for/of/from the
+movie's primary contrast (\texttt{vse\_new > vpe\_old}) and audio-description's
+primary contrast (\texttt{geo, groom} > non-spatial noun categories) mapped onto
+the cortical surface of the MNI152 T1-weighted brain template.
+% mapping procedure
+Cortical reconstruction of the MNI152 template was performed using
+\href{https://surfer.nmr.mgh.harvard.edu}{FreeSurfer} v7.1.1
+\citep{dale1999cortical}.
+% projection
+Results were projected onto the corticals surface using
+\href{https://surfer.nmr.mgh.harvard.edu}{FreeSurfer's} \citep{dale1999cortical}
+'mri\_vol2surf' command.
+% smoothing
+The union of individual PPAs was spatially smoothed applying a Gaussian kernel
+with full width at half maximum (FWHM) of \unit[3.0]{mm}.
+
+\begin{figure*}[tbp]
+\centering
+    \includegraphics[width=\linewidth]{figures/grp_ao_av_c1_surf}
+
+    \caption{Mixed-effects group-level (N=14) clusters ($Z$>3.4, $p$<.05
+      cluster-corrected) of activity correlated with the processing of spatial
+      information are projected onto the surface of the MNI152
+      T1-weighted template.
+      %
+      The results of the audio-description's primary $t$-contrast (blue) that
+      compares geometry-related nouns spoken by the narrator to non-spatial
+      nouns (\texttt{geo, groom} > all non-spatial categories) are overlaid
+      on the movie's primary $t$-contrast (red) that compares cuts to a
+      setting depicted for the first time with cuts within a recurring setting
+      (\texttt{vse\_new > vpe\_old}).
+      %
+      Black: outline of the union of individual PPA ROIs reported by
+      \citet{sengupta2016extension}.
+    }
+    \label{fig:grp_ao_av_c1_surf}
+\end{figure*}
+
+\subsubsection*{Surface plot of individual results}
+
+% intro
+Figure~\ref{fig:subjs_ao_av_c1_surf} shows the individual results for/of/from
+the movie's primary contrast (\texttt{vse\_new > vpe\_old}) and
+audio-description's primary contrast (\texttt{geo, groom} > non-spatial noun
+categories) mapped onto subject-specific cortical surfaces.
+% source of surfaces
+Individual surfaces were provided by a preexisting
+\href{https://github.com/psychoinformatics-de/studyforrest-data-freesurfer.git}{dataset}
+that used FreeSurfer v5.3.0 to reconstruct surfaces from T1-weighted images and
+an additional high-resolution T2-weighted image.
+% projection
+Results were projected onto the cortical surfaces using
+\href{https://surfer.nmr.mgh.harvard.edu}{FreeSurfer's} \citep{dale1999cortical}
+'mri\_vol2surf' command.
+% smoothing
+Individual PPA ROIs were spatially smoothed applying a Gaussian kernel with full
+width at half maximum (FWHM) of \unit[3.0]{mm}.
+
+\begin{figure*}[tbp]
+\centering
+    \includegraphics[width=\linewidth]{figures/subjs_ao_av_c1_surf}
+    \caption{Fixed-effects individual-level GLM results ($Z$>3.4, $p$<.05
+        cluster-corrected)
+        projected onto subject-specific brain surface that were
+        [re]constructed from individual T1-weighted brain images.
+        The results of the audio-description's primary
+        $t$-contrast (blue) that compares geometry related nouns to non-
+        geometry related nouns spoken by the narrator
+        (\texttt{geo, groom > all non-geo}) are overlaid over the movie's
+        primary $t$-contrast (red) that compares cuts to setting depicted for
+        the first time with cuts within a recurring setting
+        (\texttt{vse\_new > vpe\_old}).
+        Black: outline of participant-specific PPA ROIs reported by
+        \citet{sengupta2016extension}.
+        }
+    \label{fig:subjs_ao_av_c1_surf}
+\end{figure*}
+
 \subsection*{Robustness of main findings across alternative contrasts}
@@
 Reliably across all five movie contrasts, we find bilaterally significant
-clusters that overlap with the PPA group overlap
-(see Figure~\ref{fig:stability-slices}).
+clusters that overlap with the PPA group overlap (see
+Figure~\ref{fig:stability-slices} and Figure~\ref{fig:grp_ao_av_stability}).
 % AV: RSC & LOC
@@
 averaged might be.
+
+\begin{figure*}[tbp]
+\centering
+    \includegraphics[width=\linewidth]{figures/stability-slices}
+    \caption{Overlap of significant clusters ($Z$>3.4; $p$<.05, cluster
+        corrected)
+        across all contrasts for both naturalistic stimuli.
+        The audio-description's contrasts 1-8 (blue)
+        are overlaid over the audio-visual movie's contrasts 1-5 (red;
+        see Table~\ref{tab:contrasts}).
+        Cluster are overlaid on top of the MNI152 T1-weighted head template
+        with the acquisition field-of-view for the audio-description study
+        highlighted.
+        Black: outline of the union of individual PPA ROIs reported by
+        \citet{sengupta2016extension}.
+        }
+    \label{fig:stability-slices}
+\end{figure*}
+
+\begin{figure*}[tbp]
+\centering
+    \includegraphics[width=\linewidth]{figures/grp_ao_av_stability_surf}
+    \caption{Overlap of significant clusters ($Z$>3.4; $p$<.05, cluster
+        corrected) across all contrasts for both naturalistic stimuli.
+        The audio-description's contrasts 1-8 (blue)
+        are overlaid over the audio-visual movie's contrasts 1-5 (red;
+        \ref{tab:contrasts}).
+        Cluster are projected onto the surface of the
+        MNI152 T1-weighted template.
+        Black: outline of the union of individual PPA ROIs reported by
+        \citet{sengupta2016extension}.
+        }
+    \label{fig:grp_ao_av_stability}
+\end{figure*}
 
@@
 bias in the contrasts.
-
-\begin{figure*}[tbp]
-\centering
-    \includegraphics[width=\linewidth]{figures/stability-slices}
-    \caption{Overlap of significant clusters ($Z$>3.4; $p$<.05, cluster corrected)
-        across all contrasts for both naturalistic stimuli.
-        The audio-description's contrasts 1-8 (blue)
-        are overlaid over the audio-visual movie's contrasts 1-5 (red;
-        see Table~\ref{tab:contrasts}).
-        Cluster are overlaid on top of the MNI152 T1-weighted head template
-        with the acquisition field-of-view for the audio-description study
-        highlighted.
-        Black: outline of the union of individual PPA ROIs reported by \citet{sengupta2016extension}.
-        }
-    \label{fig:stability-slices}
-\end{figure*}
 
@@
 
-\subsection*{Surface maps}
-
-\todo[inline]{Just mention this part in the main document via 'the corresponding
-surface plots (Fig xy) can be found in the supplemental materials'?}
-\todo[inline]{write intro regarding purpose of additional surface plots?}
-
-% reconstruction MNI
-Cortical reconstruction of the MNI152 T1-weighted brain template
-[MNI152\_T1\_1mmi\_brain.nii.gz] was performed using
-\href{https://surfer.nmr.mgh.harvard.edu}{FreeSurfer} v7.1.1
-\citep{dale1999cortical}.
-% reconstruction: individual results
-Subject-specific cortical surfaces are part of pre-existing
-\href{https://github.com/psychoinformatics-de/studyforrest-data-freesurfer.git}{dataset}
-that used FreeSurfer v5.3.0 to reconstruct surfaces from T1-weighted images and
-an additional high-resolution T2-weighted image.
-
-% projection
-Results were projected onto the corticals surface using
-\href{https://surfer.nmr.mgh.harvard.edu}{FreeSurfer's} \citep{dale1999cortical}
-'mri\_vol2surf' command.
-% smoothing
-Group and individual PPAs were additionally patially smoothed applying a
-Gaussian kernel with full width at half maximum (FWHM) of \unit[3.0]{mm}.
-
-\subsubsection*{Group results}
-Group results see Table~\ref{tab:res-ao-group1} for AO results,
-Table~\ref{tab:res-av-group1} for AV results, and
-Figure~\ref{fig:grp_ao_av_c1_surf} for surface maps.
-
-\begin{figure*}[tbp]
-\centering
-    \includegraphics[width=\linewidth]{figures/grp_ao_av_c1_surf}
-
-    \caption{Mixed-effects group-level (N=14) clusters ($Z$>3.4, $p$<.05
-      cluster-corrected) of activity correlated with the processing of spatial
-      information are projected onto the surface of the MNI152
-      T1-weighted template.
-      %
-      The results of the audio-description's primary $t$-contrast (blue) that
-      compares geometry-related nouns spoken by the narrator to non-spatial
-      nouns (\texttt{geo, groom} > all non-spatial categories) are overlaid
-      on the movie's primary $t$-contrast (red) that compares cuts to a
-      setting depicted for the first time with cuts within a recurring setting
-      (\texttt{vse\_new > vpe\_old}).
-      %
-      Black: outline of the union of individual PPA ROIs reported by
-      \citet{sengupta2016extension}.
-    }
-    \label{fig:grp_ao_av_c1_surf}
-\end{figure*}
-
-\subsubsection*{Stability}
-Group results see Figure~\ref{fig:grp_ao_av_stability} for surface maps.
-
-\begin{figure*}[tbp]
-\centering
-    \includegraphics[width=\linewidth]{figures/grp_ao_av_stability_surf}
-    \caption{Overlap of significant clusters ($Z$>3.4; $p$<.05, cluster
-        corrected) across all contrasts for both naturalistic stimuli.
-        The audio-description's contrasts 1-8 (blue)
-        are overlaid over the audio-visual movie's contrasts 1-5 (red;
-        \ref{tab:contrasts}).
-        Cluster are projected onto the surface of the
-        MNI152 T1-weighted template.
-        Black: outline of the union of individual PPA ROIs reported by
-        \citet{sengupta2016extension}.
-        }
-    \label{fig:grp_ao_av_stability}
-\end{figure*}
-
-\subsubsection*{Individual results}
-
-\todo[inline]{RSC in of AV is essentially not visible}
-
-Individual results see Figure~\ref{fig:subjs_ao_av_c1_surf} for surface maps.
-
-\begin{figure*}[tbp]
-\centering
-    \includegraphics[width=\linewidth]{figures/subjs_ao_av_c1_surf}
-    \caption{Fixed-effects individual-level GLM results ($Z$>3.4, $p$<.05
-        cluster-corrected)
-        projected onto subject-specific brain surface that were
-        [re]constructed from individual T1-weighted brain images.
-        The results of the audio-description's primary
-        $t$-contrast (blue) that compares geometry related nouns to non-
-        geometry related nouns spoken by the narrator
-        (\texttt{geo, groom > all non-geo}) are overlaid over the movie's
-        primary $t$-contrast (red) that compares cuts to setting depicted for
-        the first time with cuts within a recurring setting
-        (\texttt{vse\_new > vpe\_old}).
-        Black: outline of participant-specific PPA ROIs reported by
-        \citet{sengupta2016extension}.
-        }
-    \label{fig:subjs_ao_av_c1_surf}
-\end{figure*}
-
 {\small\bibliographystyle{unsrtnat}
@@
 
-\setcounter{figure}{0}
-
 \end{document}

### 2021-08-22 paper/main.tex
some (non-caption) text for surface plots
correcting formatting

@@
     1. change url(s) of datasets\par
+    2. cross-referencing to Supplementary Figures does not work but show
+``??''. Referencing from suppl.tex to main.tex works tough
 }
@@
 Additional analyses of the robustness of the results presented here are
-available as supplementary materials.
+available in the Supplementary Information.
 
@@
 vpe\_old}) yielded three significant clusters (see Table~\ref{tab:res-av-group1},
-Figure~\ref{fig:group-slices}).
+Figure~\ref{fig:group-slices}, and Supplementary
+Figure~\ref{fig:grp_ao_av_c1_surf} for results mapped onto reconstructed
+cortical surface).
 % PPA (others the clusters extend into).
@@
 non-spatial noun categories) yielded six significant clusters
-(see Table~\ref{tab:res-ao-group1}, Figure~\ref{fig:group-slices}).
+(see Table~\ref{tab:res-ao-group1}, Figure~\ref{fig:group-slices}, and
+Supplementary Figure~\ref{fig:grp_ao_av_c1_surf} surface plots).
 % overlap with ROI
@@
 movie and audio-description $t$-contrasts, in comparison to the results of a
-conventional block-design localizer (unthresholded $Z$-maps are provided at
+conventional block-design localizer (see Figure~\ref{fig:subjs_ao_av_c1_surf}
+for surface plot; sunthresholded $Z$-maps are provided at
 NeuroVault).
@@
 An evaluation of the robustness of these results with respect to similar but
-different contrasts is provided in the supplementary materials.
+different contrasts is provided in the Supplementary Information.
 

### 2021-08-22 paper/suppl.tex
correcting formatting

@@
 
+\todo[inline]{Position der Abbildungen ist im kompilierten PDF maximal
+verwirrend}
+\todo[inline]{table of contents not necessary (?) but table of figures; see
+    Guidelines: ``A table of contens should be included on the first page,
+    listing the page number of each supplementary figure``}
+
+\listoffigures
+
+\pagebreak[4]
+
 \section*{Supplementary Information}
 
-\todo[inline]{Position der Abbildungen ist im kompilierten PDF maximal
-verwirrend}
+\subsection*{Surface plots}
 
-\subsubsection*{Surface plot of group results}
-
-% intro
+% group results; intro
 Figure~\ref{fig:grp_ao_av_c1_surf} shows the group results for/of/from the
@@
 with full width at half maximum (FWHM) of \unit[3.0]{mm}.
-
-\begin{figure*}[tbp]
-\centering
-    \includegraphics[width=\linewidth]{figures/grp_ao_av_c1_surf}
-
-    \caption{Mixed-effects group-level (N=14) clusters ($Z$>3.4, $p$<.05
-      cluster-corrected) of activity correlated with the processing of spatial
-      information are projected onto the surface of the MNI152
-      T1-weighted template.
-      %
-      The results of the audio-description's primary $t$-contrast (blue) that
-      compares geometry-related nouns spoken by the narrator to non-spatial
-      nouns (\texttt{geo, groom} > all non-spatial categories) are overlaid
-      on the movie's primary $t$-contrast (red) that compares cuts to a
-      setting depicted for the first time with cuts within a recurring setting
-      (\texttt{vse\_new > vpe\_old}).
-      %
-      Black: outline of the union of individual PPA ROIs reported by
-      \citet{sengupta2016extension}.
-    }
-    \label{fig:grp_ao_av_c1_surf}
-\end{figure*}
-
-\subsubsection*{Surface plot of individual results}
-
-% intro
+% individiaul results; intro
 Figure~\ref{fig:subjs_ao_av_c1_surf} shows the individual results for/of/from
@@
 \centering
+    \includegraphics[width=\linewidth]{figures/grp_ao_av_c1_surf}
+
+    \caption[Mixed-effects group-level (N=14) clusters ($Z$>3.4, $p$<.05
+      cluster-corrected) of activity correlated with the processing of spatial
+      information are projected onto the surface of the MNI152
+      T1-weighted brain template.]
+      %
+      {The results of the audio-description's primary $t$-contrast (blue) that
+      compares geometry-related nouns spoken by the narrator to non-spatial
+      nouns (\texttt{geo, groom} > all non-spatial categories) are overlaid
+      on the movie's primary $t$-contrast (red) that compares cuts to a
+      setting depicted for the first time with cuts within a recurring setting
+      (\texttt{vse\_new > vpe\_old}).
+      %
+      Black: outline of the union of individual PPA ROIs reported by
+      \citet{sengupta2016extension}.
+    }
+    \label{fig:grp_ao_av_c1_surf}
+\end{figure*}
+
+\begin{figure*}[tbp]
+\centering
     \includegraphics[width=\linewidth]{figures/subjs_ao_av_c1_surf}
-    \caption{Fixed-effects individual-level GLM results ($Z$>3.4, $p$<.05
+    \caption[Fixed-effects individual-level GLM results ($Z$>3.4, $p$<.05
         cluster-corrected)
-        projected onto subject-specific brain surface that were
-        [re]constructed from individual T1-weighted brain images.
-        The results of the audio-description's primary
+        projected onto reconstructed subject-specific brain surfaces.]
+        {The results of the audio-description's primary
         $t$-contrast (blue) that compares geometry related nouns to non-
@@
     \includegraphics[width=\linewidth]{figures/stability-slices}
-    \caption{Overlap of significant clusters ($Z$>3.4; $p$<.05, cluster
-        corrected)
-        across all contrasts for both naturalistic stimuli.
-        The audio-description's contrasts 1-8 (blue)
+    \caption[Overlap of significant clusters ($Z$>3.4; $p$<.05, cluster
+        corrected) across all contrasts for both naturalistic stimuli.]
+        {The audio-description's contrasts 1-8 (blue)
         are overlaid over the audio-visual movie's contrasts 1-5 (red;
@@
     \includegraphics[width=\linewidth]{figures/grp_ao_av_stability_surf}
-    \caption{Overlap of significant clusters ($Z$>3.4; $p$<.05, cluster
-        corrected) across all contrasts for both naturalistic stimuli.
-        The audio-description's contrasts 1-8 (blue)
+    \caption[Overlap of significant clusters ($Z$>3.4; $p$<.05, cluster
+    corrected) across all contrasts for both naturalistic stimuli projected onto
+the surface of the MNI152 T1-weighted brain template.]
+    {The audio-description's contrasts 1-8 (blue)
         are overlaid over the audio-visual movie's contrasts 1-5 (red;
         \ref{tab:contrasts}).
-        Cluster are projected onto the surface of the
-        MNI152 T1-weighted template.
         Black: outline of the union of individual PPA ROIs reported by

### 2021-08-24 paper/main.tex
Tune availability sections

--- 2021-08-13 paper/main.tex
@@
 % unregistered)
-The fMRI data, annotations, analysis scripts to generate the results, and
-results as Datalad \citep{datalad} datasets, published to or linked from the
+The fMRI data, annotations, and results are available as Datalad \citep{datalad} datasets,
+published to or linked from the
 GIN repository \href{https://gin.g-node.org/chaeusler/studyforrest-ppa-analysis}{\url{gin.g-node.org/chaeusler/studyforrest-ppa-analysis}} (DOI assignment pending).
@@
 
-Scripts to generate the results as Datalad \citep{datalad} are published to a
+Scripts to generate the results as Datalad \citep{datalad} datasets are available in a
 GIN repository \href{https://gin.g-node.org/chaeusler/studyforrest-ppa-analysis}{\url{gin.g-node.org/chaeusler/studyforrest-ppa-analysis}} (DOI assignment pending).
@@
 
-\subsubsection*{Individual resultsStability}
+\subsubsection*{Individual results}
+
+\todo[inline]{RSC in of AV is essentially not visible}
 
 Individual results see Figure~\ref{fig:subjs_ao_av_c1_surf} for surface maps.
-\todo[inline]{RSC in of AV is essentially not visible}
 

### 2021-08-24 paper/main.tex
Clarify data origin

@@
 GIN repository \href{https://gin.g-node.org/chaeusler/studyforrest-ppa-analysis}{\url{gin.g-node.org/chaeusler/studyforrest-ppa-analysis}} (DOI assignment pending).
+The fMRI datasets for the movie and the audio-description were used in their original form, as published and available on the legacy OpenFMRI portal (\url{https://legacy.openfmri.org/dataset/ds000113}, \url{https://legacy.openfmri.org/dataset/ds000113c}, \url{https://legacy.openfmri.org/dataset/ds000113d}), as well as from \url{https://www.studyforrest.org} in the form of DataLad datasets.
+The same data are available in a modified and merged form on OpenNeuro at \url{https://openneuro.org/datasets/ds000113}.
 Unthresholded $Z$-maps of all contrasts can be found at

### 2021-08-24 paper/main.tex
Use Nature style citations, rectify some bib entries
Use legacy URLs to avoid confusion

@@
 \item Hanke, M., Baumgartner, F.~J., Ibe, P., Kaule, F.~R., Pollmann, S., Speck, O.,
-  Zinke, W., \& Stadler, J. \emph{OpenfMRI} \href{https://openfmri.org/dataset/ds000113}{ds000113} (2014)
+  Zinke, W., \& Stadler, J. \emph{OpenfMRI} \href{https://legacy.openfmri.org/dataset/ds000113}{ds000113} (2014)
 
 \item Sengupta, A., Kaule, F. R., Guntupalli, J. S., Hoffmann, M. B., Häusler, C., Stadler, J. \& Hanke, M.
-  \emph{OpenfMRI} \href{https://openfmri.org/dataset/ds000113c}{ds000113c} (2016).
+  \emph{OpenfMRI} \href{https://legacy.openfmri.org/dataset/ds000113c}{ds000113c} (2016).
 
@@
   Baumgartner, F.~J. \& Stadler, J. (2016).
-  \emph{OpenfMRI} \href{https://openfmri.org/dataset/ds000113d}{ds000113d} (2016).
+  \emph{OpenfMRI} \href{https://legacy.openfmri.org/dataset/ds000113d}{ds000113d} (2016).
 \end{itemize}
 
-{\small\bibliographystyle{unsrtnat}
+{\small\bibliographystyle{naturemag}
 \bibliography{references}}
 
-%\begin{thebibliography}{1}
 %\expandafter\ifx\csname url\endcsname\relax

### 2021-08-24 paper/main.tex
Improve wording, criticized by reviewer

@@
 % three things in common
-However, the reviewed studies share three common aspects:
+However, all reviewed studies share three common aspects:
 % designed stimulus set
@@
 % block-design
-2) used a block-design paradigm to maximize detection power, and
+2) they exclusively used a block-design paradigm, and
 % task
-3) they usually employed an explicit (perceptual) judgement task.
+3) they employed an explicit (perceptual) judgement task.
 % conceptualized stimuli and block: disadvantages

### 2021-08-24 paper/main.tex
Revert citation fix (broke everything)

@@
 % Limit for main text (intro, results and discussion) = ca. 3k words
+
+\todo[inline]{possibly drop some words in ``how''-``what'' sentence if it's
+considered to be wordy}
 
@@
 
-{\small\bibliographystyle{naturemag}
+{\small\bibliographystyle{unsrtnat}
 \bibliography{references}}
@@
 
-\appendix
-
-\pagebreak[4]
-
-\setcounter{figure}{0}
-\makeatletter
-\renewcommand{\thefigure}{S\@arabic\c@figure}
-\makeatother
-
-\section{Supplementary Materials}
-
-\subsection*{Robustness of main findings across alternative contrasts}
-
-In order to test the robustness of our approach, we created overall five
-$t$-contrasts for the movie stimulus, and overall eight $t$-contrast for the
-audio-description (see Table~\ref{tab:contrasts}).
-% how
-Contrasts differ in contrasted categories based on ``how well'' averaged events
-within categories were considered to represent spatial and non-spatial
-information, and the number of events in the stimulus.
-% NeuroVault
-Unthresholded $Z$-maps of all contrasts on a group level co-registered to the
-group-template (MNI152 space) can be found at
-\href{https://neurovault.org/collections/KADGMGVZ/}{\url{neurovault.org/collections/KADGMGVZ}}.
-
-% AV PPA contrasts
-% 1 PPA (l/r); RSC (l/r), LOC (l/r), VisC (l/r),
-% intracalcarine, cuneal, ling.c
-% 2 PPA (l/r); RSC (-/-), LOC (l/r), VisC (-/-)
-% 3 PPA (l/r); RSC (-/-), LOC (-/-), VisC (-/r), occ. fusisf. g.
-% 4 PPA (l/r); RSC (l/r), LOC (l/r), VisC (-/-), lingual g., occ. fusif. g.
-% 5 PPA (l/r); RSC (l/r), LOC (l/r), VisC (-/-), occ. fusif. g.
-
-% AV results: PPA; biggest overlap in posterior part of PPA group overlap  =
-% temporal occipital fusiform cortex
-Reliably across all five movie contrasts, we find bilaterally significant
-clusters that overlap with the PPA group overlap
-(see Figure~\ref{fig:stability-slices}).
-% AV: RSC & LOC
-Several contrasts of the movie also yielded bilaterally significant clusters in
-the ventral precuneal cortex and posterior cingulate gyrus (i.e. retrosplenial
-complex; contrasts 1, 4, 5), and lateral occipital cortex (contrasts 1, 2, 4,
-5).
-
-% AD PPA contrasts
-% 1 PPA (l/r); RSC (l/r), LOC (l/r)
-% 2 PPA (l/r); RSC (l/r), LOC (l/r), r. sup.temp.C., r.fr.pole; putamen; etc
-% 3 PPA (l/r); RSC (l/r), LOC (l/r),l&r sup.temp.C., anterior cing., paracing.
-% 4 PPA (l/r); RSC (l/r), LOC (l/r)
-% 5 PPA (l/r); RSC (l/r), LOC (-/-)
-% 6 PPA (l/r); RSC (l/r), LOC (l/-), l&r sup.temp.C.; medial pref. c., precun
-% 7 PPA (-/-); RSC (l/r), LOC (l/-), l&r sup.temp.C.; left frontal pole
-% 8 PPA (-/-); RSC (-/-), LOC (-/-)
-
-% AD: results
-In results from the analysis of the audio-description, all contrasts except
-contrast 7 and 8  yielded significant bilateral clusters in anterior regions of
-the group PPA overlap (see Figure~\ref{fig:stability-slices}).
-% AD: RSC & LOC
-Contrasts of the audio-description also yielded bilaterally significant clusters
-in the ventral precuneus (all contrasts except contrasts 8) and lateral
-occipital cortex (bilateral in contrasts 1 to 4; unilateral in contrasts 6 and
-7).
-% concluding stament regarding PPA, RSC, and LOC
-Results across contrasts of both naturalistic stimuli indicate that our findings
-regarding the PPA but also RSC and LOC are robust and do not depend on the
-design of one specific contrasts.
-% but:
-Nevertheless, results are sensitive to the contrasted categories and the amount
-of available data.
-% example
-For example, contrast 7 and 8 (\texttt{se\_new}, \texttt{se\_old} > non-spatial
-categories, and \texttt{se\_new} > non-spatial categories) that used the most
-heterogeneous categories (nouns indicating switches to other settings) and a low
-amount of events yielded neither a significant cluster in the right-hemispheric
-nor left-hemispheric PPA.
-% concluding statement
-Hence, investigators that use model-driven analyses have to consider how many
-events a naturalistic stimulus may provide and how homogeneous the events to be
-averaged might be.
-
-\subsection*{Incidental results}
-
-Several contrasts yielded significant clusters in superior temporal cortices
-(bilateral in contrasts 3, 6, 7; unilateral right in contrast 2).
-% AD: auditory cortices
-Further, contrasts that compare, possibly among others, nouns indicating a
-switch to another setting (categories \texttt{se\_new} or \texttt{se\_old}) to
-non-spatial categories yielded significant clusters in superior temporal
-cortices (bilateral: contrasts 3, 6, 7; unilateral right: contrast 2).
-% interpretation 1
-This suggests that variance correlating with lower level auditory processes was
-not averaged out across events (e.g. switches to another setting might often not
-just cued by the narrator but also by a change of the soundscape or cued by a
-the start of a new song) and the employed nuisance regressors did not capture
-this variance appropriately.
-% interpretation 2
-Another possibility might be that increased hemodynamic activity in superior
-temporal cortices reflect a bias towards lower-level auditory perceptual
-processes on the positive side of the GLM contrasts.
-% soundscape
-Increased activity in primary and secondary auditory cortices could be
-attributed to changes in the soundscape that possibly accompany the narrator
-when he is indicating the switch to another setting by describing its identity
-or layout.
-
-Lastly, contrasts of the audio-description stimulus yielded clusters
-in regions that were classified as statistically significant in two or less contrasts.
-% contrast 2
-In detail, contrast 2 yielded clusters in the anterior cingulate gyrus
-(bilateral), right frontal pole, right frontal medial cortex, and right putamen.
-% contrast 3
-Contrast 3 shows clusters in the anterior cingulate gyrus (bilateral), left
-frontal pole, and left insular.
-% contrast 6
-Contrast 6 shows one additional cluster in the right medial frontal cortex.
-% contrast 7
-Contrast 7 shows clusters in the left frontal pole and left frontal operculum,
-left insular.
-% concluding statement
-Here again, significantly increased activation beyond areas known to be involved
-in processing of spatial information could be attributed to stimulus features of
-the naturalistic stimulus that were not sufficiently controlled leading to a
-bias in the contrasts.
-
-\begin{figure*}[tbp]
-\centering
-    \includegraphics[width=\linewidth]{figures/stability-slices}
-    \caption{Overlap of significant clusters ($Z$>3.4; $p$<.05, cluster corrected)
-        across all contrasts for both naturalistic stimuli.
-        The audio-description's contrasts 1-8 (blue)
-        are overlaid over the audio-visual movie's contrasts 1-5 (red;
-        \ref{tab:contrasts}).
-        Cluster are overlaid on top of the MNI152 T1-weighted head template
-        with the acquisition field-of-view for the audio-description study
-        highlighted.
-        Black: outline of the union of individual PPA ROIs reported by \citet{sengupta2016extension}.
-        }
-    \label{fig:stability-slices}
-\end{figure*}
-
-\subsection*{Control contrasts}
-
-% ---------- AV control contrasts ----------
-% 6: nothing; 7 nothing; 8: nothing; 9: nothing; 10 se_new > se_old (nouns but
-% in AV stimulus): LOC (l/r) right PPA, bilateral, sup. lat. occ. c., sup.
-% parietal lobe (right)
-
-% ---------- AD control contrasts ----------
-% 9 PPA (-/-); RSC (-/r), LOC (-/-), left pars triangularis
-%10 PPA (-/-); RSC (-/-), LOC (-/-)
-%11 PPA (-/-); RSC (-/-), LOC (-/-),
-%12 PPA (-/-); RSC (-/-), LOC (-/-), right posterior hippocampus
-%13 PPA (-/-); RSC (-/-), LOC (-/-)
-
-% intro
-For each naturalistic stimulus, we created several control contrasts.
-% movie contrasts: not cut condition vs. cuts
-To test for the specificity of the main findings within the movie fMRI data, we
-created four contrasts that compared hemodynamic activity during frames within
-movie shots (\texttt{no\_cut} category) with movie cut related categories (see
-Table~\ref{tab:contrasts}).
-% results
-None of these four contrasts yielded a significant cluster, suggesting that the
-observed differential hemodynamic response in the PPA for events defined by
-particular movie cuts is not observed for other arbitrarily selected time point
-in the movie.
-
-% \texttt{se\_new} (nouns) is r$\approx$0.3 correlated with \texttt{vse\_new}
-% (cuts); \texttt{se\_old} (nouns) is r$\approx$0.4 correlated with
-% \texttt{vse\_old}.
-The correlation of regressors across stimuli (Figure~\ref{fig:reg-corr}) showed
-a moderate correlation among cuts to a setting depicted for the first time
-(movie \texttt{vse\_new}) and nouns indicating a switch to a setting occurring
-for the first time (audio-description \texttt{se\_new}), and cuts to a
-recurringly depicted setting (movie {\texttt{vse\_old}) and nouns indicating a
-switch a recurring setting (audio-description \texttt{se\_old}).
-%
-Hence, we computed an indentical contrast ({\texttt{se\_new} >
-\texttt{se\_old}), comparing the audio-description's voice-over narrator nouns
-for the movie data and the audio-description.
-% results
-While for the movie data the contrast yielded a significant cluster in the right
-PPA, not in its anterior portion, and bilateral clusters in the superior lateral
-occipital cortices (the right hemispheric cluster extending into the superior
-parietal cortex), not significant differences where found for the
-audio-description (unthresholded contrast maps are available on NeuroVault).
-%
-These results suggest that in the absence of the actual visual stimulation, the
-narrator's description of scene properties correlated with setting changes did
-not co-occur with increased hemodynamic activity in areas associated with the
-processing of spatial information.
-
-% AD stimulus
-Finally for the analysis of the audio-description, we computed control contrasts
-based on events of the annotated movie cuts (Table~\ref{tab:contrasts}) in order
-to evaluate the influence of stimulus features correlated with these visual
-events that remain present in the audio-description, such as changes in the
-soundscape.
-% results
-Two of five contrasts yielded significant clusters.
-% contrast 9
-Contrast 9 (\texttt{vse\_new > pe\_old}) revealed one significant cluster in the
-left inferior prefrontal cortex (pars triangularis) and right ventral
-precuneus/posterior cingulate gyrus.
-% contrast 12
-Contrast 12 (\texttt{vse\_new} > \texttt{vse\_old}, \texttt{vpe\_old}) revealed
-one cluster in the right posterior hippocampus.
-%
-The absence of observable hemodynamic response differences in the PPA suggests
-that without the visual information in the movie stimulus, no, or substantially
-less, processing of stimulus content with respect to spatial information
-co-occurred with the timing of the movie cuts.
-
-\subsection*{Surface maps}
-
-\todo[inline]{Just mention this part in the main document via 'the corresponding
-surface plots (Fig xy) can be found in the supplemental materials'?}
-\todo[inline]{write intro regarding purpose of additional surface plots?}
-
-% reconstruction MNI
-Cortical reconstruction of the MNI152 T1-weighted brain template
-[MNI152\_T1\_1mmi\_brain.nii.gz] was performed using
-\href{https://surfer.nmr.mgh.harvard.edu}{FreeSurfer} v7.1.1
-\citep{dale1999cortical}.
-% reconstruction: individual results
-Subject-specific cortical surfaces are part of pre-existing
-\href{https://github.com/psychoinformatics-de/studyforrest-data-freesurfer.git}{dataset}
-that used FreeSurfer v5.3.0 to reconstruct surfaces from T1-weighted images and
-an additional high-resolution T2-weighted image.
-
-% projection
-Results were projected onto the corticals surface using
-\href{https://surfer.nmr.mgh.harvard.edu}{FreeSurfer's} \citep{dale1999cortical}
-'mri\_vol2surf' command.
-% smoothing
-Group and individual PPAs were additionally patially smoothed applying a
-Gaussian kernel with full width at half maximum (FWHM) of \unit[3.0]{mm}.
-
-\subsubsection*{Group results}
-Group results see Table~\ref{tab:res-ao-group1} for AO results,
-Table~\ref{tab:res-av-group1} for AV results, and
-Figure~\ref{fig:grp_ao_av_c1_surf} for surface maps.
-
-\begin{figure*}[tbp]
-\centering
-    \includegraphics[width=\linewidth]{figures/grp_ao_av_c1_surf}
-
-    \caption{Mixed-effects group-level (N=14) clusters ($Z$>3.4, $p$<.05
-      cluster-corrected) of activity correlated with the processing of spatial
-      information are projected onto the surface of the MNI152
-      T1-weighted template.
-      %
-      The results of the audio-description's primary $t$-contrast (blue) that
-      compares geometry-related nouns spoken by the narrator to non-spatial
-      nouns (\texttt{geo, groom} > all non-spatial categories) are overlaid
-      on the movie's primary $t$-contrast (red) that compares cuts to a
-      setting depicted for the first time with cuts within a recurring setting
-      (\texttt{vse\_new > vpe\_old}).
-      %
-      Black: outline of the union of individual PPA ROIs reported by
-      \citet{sengupta2016extension}.
-    }
-    \label{fig:grp_ao_av_c1_surf}
-\end{figure*}
-
-\subsubsection*{Stability}
-Group results see Figure~\ref{fig:grp_ao_av_stability} for surface maps.
-
-\begin{figure*}[tbp]
-\centering
-    \includegraphics[width=\linewidth]{figures/grp_ao_av_stability_surf}
-    \caption{Overlap of significant clusters ($Z$>3.4; $p$<.05, cluster
-        corrected) across all contrasts for both naturalistic stimuli.
-        The audio-description's contrasts 1-8 (blue)
-        are overlaid over the audio-visual movie's contrasts 1-5 (red;
-        \ref{tab:contrasts}).
-        Cluster are projected onto the surface of the
-        MNI152 T1-weighted template.
-        Black: outline of the union of individual PPA ROIs reported by
-        \citet{sengupta2016extension}.
-        }
-    \label{fig:grp_ao_av_stability}
-\end{figure*}
-
-\subsubsection*{Individual results}
-
-\todo[inline]{RSC in of AV is essentially not visible}
-
-Individual results see Figure~\ref{fig:subjs_ao_av_c1_surf} for surface maps.
-
-\begin{figure*}[tbp]
-\centering
-    \includegraphics[width=\linewidth]{figures/subjs_ao_av_c1_surf}
-    \caption{Fixed-effects individual-level GLM results ($Z$>3.4, $p$<.05
-        cluster-corrected)
-        projected onto subject-specific brain surface that were
-        [re]constructed from individual T1-weighted brain images.
-        The results of the audio-description's primary
-        $t$-contrast (blue) that compares geometry related nouns to non-
-        geometry related nouns spoken by the narrator
-        (\texttt{geo, groom > all non-geo}) are overlaid over the movie's
-        primary $t$-contrast (red) that compares cuts to setting depicted for
-        the first time with cuts within a recurring setting
-        (\texttt{vse\_new > vpe\_old}).
-        Black: outline of participant-specific PPA ROIs reported by
-        \citet{sengupta2016extension}.
-        }
-    \label{fig:subjs_ao_av_c1_surf}
-\end{figure*}
-
 \end{document}

### 2021-08-24 paper/main.tex
[DATALAD] auto-saved changes

@@
 
+\todo[inline]{Since we did no analyses in surface space imo it makes more sense
+    to explain the ``method'' to create the surface plots here in the
+``Results''}
+
+\todo[inline]{only Captions mention smoothing of union of PPAs; Volume FWHM was
+2mm, Surface FWHM was 3mm}
+
+\todo[inline]{Merge plots and adjust references here}
+
 % av intro
@@
 depicted before to cuts within a recurring setting (\texttt{vse\_new >
-vpe\_old}) yielded three significant clusters (see Table~\ref{tab:res-av-group1},
-Figure~\ref{fig:group-slices}, and Supplementary
-Figure~\ref{fig:grp_ao_av_c1_surf} for results mapped onto reconstructed
-cortical surface).
+vpe\_old}) yielded three significant clusters (see
+Table~\ref{tab:res-av-group1}).
+% volume plots
+Results are depicted as slices of brain volumes in Figure~\ref{fig:grp_ao_av_c1_volsurf} a).
+% surface plots
+The surface plots depicted in \ref{fig:grp_ao_av_c1_volsurf} b) were created by
+reconstructing the cortical surface of the MNI152 template using
+\href{https://surfer.nmr.mgh.harvard.edu}{FreeSurfer} v7.1.1
+\citep{dale1999cortical} and projecting the $Z$-maps onto the surface using
+FreeSurfer's 'mri\_vol2surf' command.
 % PPA (others the clusters extend into).
@@
 non-spatial noun categories) yielded six significant clusters
-(see Table~\ref{tab:res-ao-group1}, Figure~\ref{fig:group-slices}, and
-Supplementary Figure~\ref{fig:grp_ao_av_c1_surf} surface plots).
+(see Table~\ref{tab:res-ao-group1}, Figure~\ref{fig:grp_ao_av_c1_volsurf} a) as volume plots, and Figure~\ref{fig:grp_ao_av_c1_volsurf} b) as surface plots).
 % overlap with ROI
@@
     }
-
     \label{fig:group-slices}
+\end{figure*}
+
+\begin{figure*}[tbp]
+\centering
+    \includegraphics[width=\linewidth]{figures/grp_ao_av_c1_surf}
+
+    \caption{Mixed-effects group-level (N=14) clusters ($Z$>3.4, $p$<.05
+      cluster-corrected) of activity correlated with the processing of spatial
+      information.
+      a) Results are displayed on top of the MNI152 T1-weighted head template,
+      with the acquisition field-of-view for the audio-description study
+      highlighted.
+      The results of the audio-description's primary $t$-contrast (blue) that
+      compares geometry-related nouns spoken by the narrator to non-spatial
+      nouns (\texttt{geo, groom} > all non-spatial categories) are overlaid
+      on the movie's primary $t$-contrast (red) that compares cuts to a
+      setting depicted for the first time with cuts within a recurring setting
+      (\texttt{vse\_new > vpe\_old}).
+      % PPA
+      For comparison depicted as a black outline, the union of the
+      individual PPA localization reported by \citet{sengupta2016extension}
+      that was spatially smoothed applying a Gaussian kernel with full
+      width at half maximum (FWHM) of \unit[2.0]{mm}
+      % surface map
+      b) The results are displayed as projections onto the reconstructed
+      surface of the MNI152 T1-weighted brain template. After projection the
+      union of individual PPA localizations was spatially smoothed by a
+      Gaussian kernel with FWHM of \unit[3.0]{mm}.
+    }
+    \label{fig:grp_ao_av_c1_volsurf}
 \end{figure*}

### 2021-08-24 paper/suppl.tex
[DATALAD] auto-saved changes

@@
 
-    \caption[Mixed-effects group-level (N=14) clusters ($Z$>3.4, $p$<.05
+    \caption[NAME]
+    {Mixed-effects group-level (N=14) clusters ($Z$>3.4, $p$<.05
     cluster-corrected) of activity correlated with the processing of spatial
     information are projected onto the surface of the MNI152
-      T1-weighted brain template.]
+    T1-weighted brain template.
     %
-      {The results of the audio-description's primary $t$-contrast (blue) that
+    The results of the audio-description's primary $t$-contrast (blue) that
     compares geometry-related nouns spoken by the narrator to non-spatial
@@
     \includegraphics[width=\linewidth]{figures/stability-slices}
-    \caption[Overlap of significant clusters ($Z$>3.4; $p$<.05, cluster
-        corrected) across all contrasts for both naturalistic stimuli.]
-        {The audio-description's contrasts 1-8 (blue)
+    \caption[NAME]
+    {Overlap of significant clusters ($Z$>3.4; $p$<.05, cluster
+    corrected) across all contrasts for both naturalistic stimuli.
+    The audio-description's contrasts 1-8 (blue)
     are overlaid over the audio-visual movie's contrasts 1-5 (red;
@@
     \includegraphics[width=\linewidth]{figures/grp_ao_av_stability_surf}
-    \caption[Overlap of significant clusters ($Z$>3.4; $p$<.05, cluster
-    corrected) across all contrasts for both naturalistic stimuli projected onto
-the surface of the MNI152 T1-weighted brain template.]
-    {The audio-description's contrasts 1-8 (blue)
-        are overlaid over the audio-visual movie's contrasts 1-5 (red;
-        \ref{tab:contrasts}).
+    \caption[NAME]
+    {Overlap of significant clusters ($Z$>3.4; $p$<.05, cluster
+    corrected) across all contrasts for both naturalistic stimuli projected
+    onto the surface of the MNI152 T1-weighted brain template.
+    The audio-description's contrasts 1-8 (blue) are overlaid over the
+    audio-visual movie's contrasts 1-5 (red; \ref{tab:contrasts}).
     Black: outline of the union of individual PPA ROIs reported by

### 2021-08-24 code/plot-surface-maps.py
set surface smoothing from 3 to 2mm

@@ -104,7 +104,7 @@ def volume_2_surf(in_file, out_path, reg, target):
                  '--interp', 'nearest',
                  '--surf', 'white',
                  '--projfrac-max', '0', '1', '0.1',
-                 '--surf-fwhm', '3',  # smoothing of x mm
+                 '--surf-fwhm', '2',  # smoothing of x mm
                  '--o', out_fpath]
             )
         else:
@@ -1067,12 +1067,12 @@ def plot_legend_2colorbars(
                 pad_inches=0.2,
                 transparent=True)
 
-#     # save as .svg
-#     fig.savefig(fname.replace('.png', '.svg'),
-#                 dpi=300,
-#                 bbox_inches='tight',
-#                 pad_inches=0.2,
-#                 transparent=True)
+    # save as .svg
+    fig.savefig(fname.replace('.png', '.svg'),
+                dpi=300,
+                bbox_inches='tight',
+                pad_inches=0.2,
+                transparent=True)
 
     plt.close()
 

### 2021-08-24 paper/main.tex
set surface smoothing from 3 to 2mm
change text from 3 to 2mm

@@
 \todo[inline]{only Captions mention smoothing of union of PPAs; Volume FWHM was
-2mm, Surface FWHM was 3mm}
+2mm, Surface FWHM was 3mm; I changed that to 2mm; plotting scripts need to be
+rerun}
 
@@
 
-% figure group results primary AD & AV contrasts
+% figure group results, volume, primary AD & AV contrasts
+\begin{comment}
+
 \begin{figure*}[tbp] \centering
@@
 
+\end{comment}
+
+% figure group results, volume & surface, primary AD & AV contrasts
 \begin{figure*}[tbp]
 \centering
-    \includegraphics[width=\linewidth]{figures/grp_ao_av_c1_surf}
+    \includegraphics[width=\linewidth]{figures/group-slices-volsurf}
 
@@
       union of individual PPA localizations was spatially smoothed by a
-      Gaussian kernel with FWHM of \unit[3.0]{mm}.
+      Gaussian kernel with FWHM of \unit[2.0]{mm}.
     }

### 2021-08-25 paper/main.tex
delete Data Availability Section & update references.bib

@@
 
-\section*{Data Citations}
-
-\todo[inline]{Following dataset are added to references.bib}
-\todo[inline]{reference to cut anno might be retundant}
-\todo[inline]{propably, cite them above in the manuscript where it makes sense}
-
-Cited here, so they show in the references (see at end of references):
-\citep{haeusler2016cutdata, haeusler2021speechdata, hanke2014ds000113, sengupta2016ds000113c, hanke2016ds000113d}
-
-\begin{itemize}
-% cut anno
-\item Häusler, C. O. \& Hanke M. Dataset 1 in: An annotation of cuts, depicted
-locations, and temporal progression in the motion picture "Forrest Gump".
-\emph{F1000Research}
-\href{https://doi.org/10.5256/f1000research.9536.d134823}{10.5256/f1000research.9536.d134823}
-(2016)
-
-% speech anno
-\item Häusler, C. O. \& Hanke M. \emph{OSF}
-\href{https://doi.org/10.17605/OSF.IO/GFRME}{GFRME}
-(2020).
-
-% audio-description
-\item Hanke, M., Baumgartner, F.~J., Ibe, P., Kaule, F.~R., Pollmann, S., Speck, O.,
-  Zinke, W., \& Stadler, J. \emph{OpenfMRI} \href{https://legacy.openfmri.org/dataset/ds000113}{ds000113} (2014)
-
-\item Sengupta, A., Kaule, F. R., Guntupalli, J. S., Hoffmann, M. B., Häusler, C., Stadler, J. \& Hanke, M.
-  \emph{OpenfMRI} \href{https://legacy.openfmri.org/dataset/ds000113c}{ds000113c} (2016).
-
-\item Hanke, M., Adelhöfer, N., Kottke, D., Iacovella, V., Sengupta, A., Kaule, F.~R., Nigbur, R., Waite, A.~Q.,
-  Baumgartner, F.~J. \& Stadler, J. (2016).
-  \emph{OpenfMRI} \href{https://legacy.openfmri.org/dataset/ds000113d}{ds000113d} (2016).
-\end{itemize}
-
 {\small\bibliographystyle{unsrtnat}

### 2021-08-27 paper/main.tex
add correct Ungerleider & Mishkin ref
addjust Supplementals to figure with merged volume & surface plots

@@
 and] supports [conscious] perception and recognition.
-\citep{goodale1992separate, milner2017two, mishkin1982contribution}.
+\citep{goodale1992separate, milner2017two, ungerleider1982two}.
 % PPA
@@
 % volume plots
-Results are depicted as slices of brain volumes in Figure~\ref{fig:grp_ao_av_c1_volsurf} a).
+Results are depicted as slices of brain volumes in
+Figure~\ref{fig:grp_ao_av_c1_volsurf} a).
 % surface plots
-The surface plots depicted in \ref{fig:grp_ao_av_c1_volsurf} b) were created by
-reconstructing the cortical surface of the MNI152 template using
+The surface plots depicted in Figure~\ref{fig:grp_ao_av_c1_volsurf} b) were
+created by reconstructing the cortical surface of the MNI152 template using
 \href{https://surfer.nmr.mgh.harvard.edu}{FreeSurfer} v7.1.1
-\citep{dale1999cortical} and projecting the $Z$-maps onto the surface using
+\citep{dale1999cortical}, and projecting the $Z$-maps onto the surface using
 FreeSurfer's 'mri\_vol2surf' command.
@@
 The primary $t$-contrast for the audio-description (\texttt{geo, groom} >
-non-spatial noun categories) yielded six significant clusters
-(see Table~\ref{tab:res-ao-group1}, Figure~\ref{fig:grp_ao_av_c1_volsurf} a) as volume plots, and Figure~\ref{fig:grp_ao_av_c1_volsurf} b) as surface plots).
+non-spatial noun categories) yielded six significant clusters (see
+Table~\ref{tab:res-ao-group1}, Figure~\ref{fig:grp_ao_av_c1_volsurf} as
+volume plots and surface plots).
 % overlap with ROI
@@
       information.
-      a) Results are displayed on top of the MNI152 T1-weighted head template,
-      with the acquisition field-of-view for the audio-description study
-      highlighted.
       The results of the audio-description's primary $t$-contrast (blue) that
@@
       (\texttt{vse\_new > vpe\_old}).
+      % volume
+      a) results as brain slices on top of the MNI152 T1-weighted head
+      template,
+      with the acquisition field-of-view for the audio-description study
+      highlighted.
       % PPA
@@
       that was spatially smoothed applying a Gaussian kernel with full
-      width at half maximum (FWHM) of \unit[2.0]{mm}
-      % surface map
-      b) The results are displayed as projections onto the reconstructed
-      surface of the MNI152 T1-weighted brain template. After projection the
-      union of individual PPA localizations was spatially smoothed by a
-      Gaussian kernel with FWHM of \unit[2.0]{mm}.
+      width at half maximum (FWHM) of \unit[2.0]{mm}.
+      % surface
+      b) results projected onto the reconstructed
+      surface of the MNI152 T1-weighted brain template.
+      After projection, the union of individual PPA localizations was
+      spatially smoothed by a Gaussian kernel with FWHM of \unit[2.0]{mm}
     }

### 2021-08-27 paper/suppl.tex
addjust Supplementals to figure with merged volume & surface plots

--- 2021-08-20 paper/suppl.tex
@@
 
+\todo[inline]{Position der Abbildungen ist im kompilierten PDF maximal
+verwirrend}
+\todo[inline]{table of contents not necessary (?) but table of figures; see
+    Guidelines: ``A table of contens should be included on the first page,
+    listing the page number of each supplementary figure``}
+
+\listoffigures
+
+\pagebreak[4]
+
 \section*{Supplementary Information}
 
-\todo[inline]{Position der Abbildungen ist im kompilierten PDF maximal
-verwirrend}
+\subsection*{Surface plots of individual results}
 
-\subsubsection*{Surface plot of group results}
-
-% intro
-Figure~\ref{fig:grp_ao_av_c1_surf} shows the group results for/of/from the
-movie's primary contrast (\texttt{vse\_new > vpe\_old}) and audio-description's
-primary contrast (\texttt{geo, groom} > non-spatial noun categories) mapped onto
-the cortical surface of the MNI152 T1-weighted brain template.
-% mapping procedure
-Cortical reconstruction of the MNI152 template was performed using
-\href{https://surfer.nmr.mgh.harvard.edu}{FreeSurfer} v7.1.1
-\citep{dale1999cortical}.
-% projection
-Results were projected onto the corticals surface using
-\href{https://surfer.nmr.mgh.harvard.edu}{FreeSurfer's} \citep{dale1999cortical}
-'mri\_vol2surf' command.
-% smoothing
-The union of individual PPAs was spatially smoothed applying a Gaussian kernel
-with full width at half maximum (FWHM) of \unit[3.0]{mm}.
-
-\begin{figure*}[tbp]
-\centering
-    \includegraphics[width=\linewidth]{figures/grp_ao_av_c1_surf}
-
-    \caption{Mixed-effects group-level (N=14) clusters ($Z$>3.4, $p$<.05
-      cluster-corrected) of activity correlated with the processing of spatial
-      information are projected onto the surface of the MNI152
-      T1-weighted template.
-      %
-      The results of the audio-description's primary $t$-contrast (blue) that
-      compares geometry-related nouns spoken by the narrator to non-spatial
-      nouns (\texttt{geo, groom} > all non-spatial categories) are overlaid
-      on the movie's primary $t$-contrast (red) that compares cuts to a
-      setting depicted for the first time with cuts within a recurring setting
-      (\texttt{vse\_new > vpe\_old}).
-      %
-      Black: outline of the union of individual PPA ROIs reported by
-      \citet{sengupta2016extension}.
-    }
-    \label{fig:grp_ao_av_c1_surf}
-\end{figure*}
-
-\subsubsection*{Surface plot of individual results}
-
-% intro
-Figure~\ref{fig:subjs_ao_av_c1_surf} shows the individual results for/of/from
+% individiaul results; intro
+Figure~\ref{fig:subjs_ao_av_c1_surf} shows the individual results of
 the movie's primary contrast (\texttt{vse\_new > vpe\_old}) and
@@
 categories) mapped onto subject-specific cortical surfaces.
-% source of surfaces
-Individual surfaces were provided by a preexisting
-\href{https://github.com/psychoinformatics-de/studyforrest-data-freesurfer.git}{dataset}
-that used FreeSurfer v5.3.0 to reconstruct surfaces from T1-weighted images and
-an additional high-resolution T2-weighted image.
+% reconstruction
+% \href{https://github.com/psychoinformatics-de/studyforrest-data-freesurfer.git}{dataset}
+\href{https://surfer.nmr.mgh.harvard.edu}{FreeSurfer} v5.3.0
+\citep{dale1999cortical} was used to reconstruct surfaces from T1-weighted
+images and an additional high-resolution T2-weighted image.
 % projection
@@
 % smoothing
-Individual PPA ROIs were spatially smoothed applying a Gaussian kernel with full
-width at half maximum (FWHM) of \unit[3.0]{mm}.
+After projection, individual PPA ROIs were spatially smoothed applying a
+Gaussian kernel with full width at half maximum (FWHM) of \unit[2.0]{mm}.
 
@@
     \includegraphics[width=\linewidth]{figures/subjs_ao_av_c1_surf}
-    \caption{Fixed-effects individual-level GLM results ($Z$>3.4, $p$<.05
-        cluster-corrected)
-        projected onto subject-specific brain surface that were
-        [re]constructed from individual T1-weighted brain images.
+    \caption[Participant-specific surface plots of primary contrasts]
+    {Fixed-effects individual-level GLM results ($Z$>3.4, $p$<.05
+        cluster-corrected) projected onto reconstructed subject-specific brain
+        surfaces.
         The results of the audio-description's primary
@@
         Black: outline of participant-specific PPA ROIs reported by
-        \citet{sengupta2016extension}.
+        \citet{sengupta2016extension} that was spatially smoothed by applying a
+        Gaussian kernel with full width at half maximum (FWHM) of \unit[2.0]{mm}.
         }
@@
 clusters that overlap with the PPA group overlap (see
-Figure~\ref{fig:stability-slices} and Figure~\ref{fig:grp_ao_av_stability}).
+Figure~\ref{fig:stability-slices-volsurf}).
 % AV: RSC & LOC
@@
 contrast 7 and 8  yielded significant bilateral clusters in anterior regions of
-the group PPA overlap (see Figure~\ref{fig:stability-slices}).
+the group PPA overlap (see Figure~\ref{fig:stability-slices-volsurf}).
 % AD: RSC & LOC
@@
 \centering
-    \includegraphics[width=\linewidth]{figures/stability-slices}
-    \caption{Overlap of significant clusters ($Z$>3.4; $p$<.05, cluster
-        corrected)
-        across all contrasts for both naturalistic stimuli.
+    \includegraphics[width=\linewidth]{figures/stability-slices-volsurf}
+    \caption[Group results across contrasts of movie and audio-description]
+    {Overlap of significant clusters ($Z$>3.4; $p$<.05, cluster
+    corrected) across all contrasts for both naturalistic stimuli.
     The audio-description's contrasts 1-8 (blue)
@@
     see Table~\ref{tab:contrasts}).
-        Cluster are overlaid on top of the MNI152 T1-weighted head template
+    % volume
+    a) results as brain slices on top of the MNI152 T1-weighted head template,
     with the acquisition field-of-view for the audio-description study
     highlighted.
-        Black: outline of the union of individual PPA ROIs reported by
-        \citet{sengupta2016extension}.
+    % PPA
+    For comparison depicted as a black outline, the union of the
+    individual PPA localization reported by \citet{sengupta2016extension}
+    that was spatially smoothed applying a Gaussian kernel with full
+    width at half maximum (FWHM) of \unit[2.0]{mm}.
+    % surface map
+    b) results projected onto the reconstructed
+    surface of the MNI152 T1-weighted brain template.
+    After projection, the union of individual PPA localizations was
+    spatially smoothed by a Gaussian kernel with FWHM of \unit[2.0]{mm}
     }
-    \label{fig:stability-slices}
-\end{figure*}
-
-\begin{figure*}[tbp]
-\centering
-    \includegraphics[width=\linewidth]{figures/grp_ao_av_stability_surf}
-    \caption{Overlap of significant clusters ($Z$>3.4; $p$<.05, cluster
-        corrected) across all contrasts for both naturalistic stimuli.
-        The audio-description's contrasts 1-8 (blue)
-        are overlaid over the audio-visual movie's contrasts 1-5 (red;
-        \ref{tab:contrasts}).
-        Cluster are projected onto the surface of the
-        MNI152 T1-weighted template.
-        Black: outline of the union of individual PPA ROIs reported by
-        \citet{sengupta2016extension}.
-        }
-    \label{fig:grp_ao_av_stability}
+    \label{fig:stability-slices-volsurf}
 \end{figure*}

### 2021-08-29 paper/main.tex
[DATALAD] auto-saved changes

@@
 
+\todo[inline]{The dataset (\citep{haeusler2021ppa}) should probably be cited here + datalad yada yada}
+
 % study goal
@@
 
-\todo[inline]{Since we did no analyses in surface space imo it makes more sense
-    to explain the ``method'' to create the surface plots here in the
-``Results''}
-
-\todo[inline]{only Captions mention smoothing of union of PPAs; Volume FWHM was
-2mm, Surface FWHM was 3mm; I changed that to 2mm; plotting scripts need to be
-rerun}
-
-\todo[inline]{Merge plots and adjust references here}
-
 % av intro
@@
 One cluster spans across the midline and comprises parts of the intracalcarine
-and cuneal cortex, the lingual gyrus and retrosplenial cortex, the occipital and
-temporal fusiform gyrus, and the parahippocampal cortex (reported from posterior
-to anterior) in both hemispheres.
+and cuneal cortex, the lingual gyrus and retrosplenial cortex, the occipital
+and temporal fusiform gyrus, and the parahippocampal cortex (reported from
+posterior to anterior) in both hemispheres.
 % LOC
-Two additional bilateral clusters are located in the superior lateral occipital
-cortex.
+Two additional bilateral clusters are located in the superior lateral
+occipital cortex.
 

### 2021-08-29 paper/suppl.tex
[DATALAD] auto-saved changes

@@
 
-% title has to be < 110 chars incl. spaces at the moment 106 Chars
-\title{Processing of visual and non-visual naturalistic spatial information in
-  the "parahippocampal place area"}
+\title{%
+  Processing of visual and non-visual naturalistic spatial information in
+the "parahippocampal place area" \\
+[1ex] \large Supplementary Information}
 
@@
 verwirrend}
-\todo[inline]{table of contents not necessary (?) but table of figures; see
-    Guidelines: ``A table of contens should be included on the first page,
-    listing the page number of each supplementary figure``}
+
+\todo[inline]{I added table of contents & figure. s. Guidelines: ``A table of 
+contens should be included on the first page, listing the page number of each 
+supplementary figure``}
+
+\tableofcontents
 
@@
 
-\section*{Supplementary Information}
-
-\subsection*{Surface plots of individual results}
+\section{Surface plots of individual results}
 
@@
 
-\subsection*{Robustness of main findings across alternative contrasts}
+\section{Robustness of main findings across alternative contrasts}
 
@@
 
-\subsection*{Incidental results}
+\section{Incidental results}
 
@@
 
-\subsection*{Control contrasts}
+\section{Control contrasts}
 

### 2021-08-30 paper/main.tex
citation of datasets v1

@@
 \pagebreak[4]
-
-\todo[inline]{\textbf{My notes:}\par
-    1. change url(s) of datasets\par
-    2. cross-referencing to Supplementary Figures does not work but show
-``??''. Referencing from suppl.tex to main.tex works tough
-}
 
@@
 
-\todo[inline]{The dataset (\citep{haeusler2021ppa}) should probably be cited here + datalad yada yada}
-
 % study goal
@@
 conventional block-design localizer (see Figure~\ref{fig:subjs_ao_av_c1_surf}
-for surface plot; sunthresholded $Z$-maps are provided at
-NeuroVault).
+for surface plot; unthresholded $Z$-maps are provided at
+\href{https://neurovault.org/collections/KADGMGVZ/}{\url{neurovault.org/collections/KADGMGVZ}}).
 % AV
@@
 % data sources
-% https://github.com/psychoinformatics-de/studyforrest-data-aligned/tree/master/code
-% https://github.com/psychoinformatics-de/studyforrest-data-templatetransforms}
-The current analyses were carried out on the same preprocessed fMRI data that were used
-for the technical validation analysis presented in \citet{hanke2016simultaneous}, and available from \href{https://github.com/psychoinformatics-de/studyforrest-data-aligned}{github.com/ psychoinformatics-de/studyforrest-data-aligned}.
-Of those 15 participants in the studyforrest dataset that took
-part in all three experiments,
+The current analyses were carried out on the same preprocessed fMRI data
+\citep{hanke2016aligned} that were used for the technical validation analysis
+presented in \citet{hanke2016simultaneous}.
 % exclusion of VP 10
-data of one participant were dropped due to invalid distortion correction
-during scanning of the audio-description stimulus.
+Of those 15 participants in the studyforrest dataset that took part in all three
+experiments, data of one participant were dropped due to invalid distortion
+correction during scanning of the audio-description stimulus.
+% preprocessing of pre-aligned data
 Data were corrected for motion, aligned with and re-sliced onto a
-participant-specific BOLD template image \citep{sengupta2016extension}
-(uniform spatial resolution of \unit[2.5$\times$2.5$\times$2.5]{mm} for both
+participant-specific BOLD template image \citep{sengupta2016extension} (uniform
+spatial resolution of \unit[2.5$\times$2.5$\times$2.5]{mm} for both
 audio-description and movie data).
 % preprocessing intro
-Preprocessing was performed by FEAT v6.00 (FMRI Expert Analysis Tool \citep{woolrich2001autocorr}) as shipped with
-FSL v5.0.9 (\href{https://www.fmrib.ox.ac.uk/fsl}{FMRIB's Software Library}
+Preprocessing was performed by FEAT v6.00 (FMRI Expert Analysis Tool
+\citep{woolrich2001autocorr}) as shipped with FSL v5.0.9
+(\href{https://www.fmrib.ox.ac.uk/fsl}{FMRIB's Software Library}
 \citep{smith2004fsl}) on a computer-cluster running
@@
 
-% Zenodo (registered but zipped) vs. OSF (datalad dataset but probably
-% unregistered)
+\todo[inline]{Datasets are not cited / do not occur in the references}
+\todo[inline]{I did not know how to cite because authors are intersection /
+union of the papers, how to order authors\dots}
+
+% new; PPA analysis
+All fMRI data, annotations, and results are available as Datalad \citep{datalad}
+datasets, published to or linked from the GIN repository
+\href{https://gin.g-node.org/chaeusler/studyforrest-ppa-analysis}{\url{gin.g-node.org/chaeusler/studyforrest-ppa-analysis}}
+(DOI assignment pending) \citep{haeusler2021ppa}.
+% original
+Raw data of the audio-description, movie and visual localizer were originally
+published on the \emph{OpenfMRI} portal
+(\url{https://legacy.openfmri.org/dataset/ds000113}\citep{Hanke2014ds000113},
+\url{https://legacy.openfmri.org/dataset/ds000113d}\citep{hanke2016ds000113d}).
+% visual localizer
+Results from the localization of higher visual areas are available as Datalad
+datasets at
+\emph{GitHub} (
+\href{https://github.com/psychoinformatics-de/studyforrest-data-visualrois}{\url{github.com/psychoinformatics-de/studyforrest-data-visualrois}}\citep{sengupta2016extensiondata}).
+% raw data
+The realigned participant-specific timeseries that were used in the current analyses were derived from the raw data releases and are available as Datalad
+datasets at \emph{GitHub} (
+\href{https://github.com/psychoinformatics-de/studyforrest-data-aligned}{\url{github.com/psychoinformatics-de/studyforrest-data-aligned}}
+\citep{hanke2016aligned}).
+% cut annotation
+The annotation of cuts is available at \emph{F1000Research} (
+\href{https://doi.org/10.5256/f1000research.9536.d134823}{\url{doi.org/10.5256/f1000research.9536.d134823}}
+\citep{haeusler2016cutdata}),
+% speech annotation
+the annotation of speech is available at \emph{OSF}
+(\href{https://doi.org/10.17605/OSF.IO/F5J3E}{\url{doi.org/10.17605/OSF.IO/F5J3E}}
+\citep{haeusler2020speechdata}).
+% surface data
+Participant-specific reconstructed cortical surface are available as Datalad
+dataset at \emph{GitHub} (
+\href{https://gin.g-node.org/studyforrest/cortical-surfaces-freesurfer}{\url{gin.g-node.org/studyforrest/cortical-surfaces-freesurfer}}
+\citep{hanke2016freesurferdata}).
+
+\bigbreak
+% old
 The fMRI data, annotations, and results are available as Datalad \citep{datalad} datasets,
 published to or linked from the
-GIN repository \href{https://gin.g-node.org/chaeusler/studyforrest-ppa-analysis}{\url{gin.g-node.org/chaeusler/studyforrest-ppa-analysis}} (DOI assignment pending).
+GIN repository
+\href{https://gin.g-node.org/chaeusler/studyforrest-ppa-analysis}{\url{gin.g-node.org/chaeusler/studyforrest-ppa-analysis}}
+(DOI assignment pending) \citep{haeusler2021ppa}.
+% AO & AV
 The fMRI datasets for the movie and the audio-description were used in their original form, as published and available on the legacy OpenFMRI portal (\url{https://legacy.openfmri.org/dataset/ds000113}, \url{https://legacy.openfmri.org/dataset/ds000113c}, \url{https://legacy.openfmri.org/dataset/ds000113d}), as well as from \url{https://www.studyforrest.org} in the form of DataLad datasets.

### 2021-08-30 paper/suppl.tex
citation of datasets v1

@@
 
-\todo[inline]{I added table of contents & figure. s. Guidelines: ``A table of 
+\todo[inline]{I added table of contents \& figure. s. Guidelines: ``A table of
 contens should be included on the first page, listing the page number of each
 supplementary figure``}
+
+\todo[inline]{add the references to mainmanuscript (see ``??'') because
+cross-referencing does not work in the pdf that gets compiled first}
 
@@
 \citep{dale1999cortical} was used to reconstruct surfaces from T1-weighted
-images and an additional high-resolution T2-weighted image.
+images and an additional high-resolution T2-weighted image
+\citep{hanke2016freesurferdata}.
 % projection

### 2021-08-30 paper/main.tex
cleaning of revised parts

@@
 % AV, AD: operationalization
-Here, we investigate the perception of spatial information embedded in two
-naturalistic stimuli.
-%
-The same 14 participants were watching a Hollywood movie and listening to its audio-description as part of the open-data resource \textit{studyforrest.org}.
+Here, we investigate the perception of scene-related, spatial information embedded in two naturalistic stimuli.
+%
+The same 14 participants were watching a Hollywood movie and listening to its
+audio-description as part of the open-data resource \textit{studyforrest.org}.
 % auditory localizer?
@@
 % occipital cortex for vision -> two pathways
-the occipital cortex is considered to be primarily involved in the early stages
+The occipital cortex is considered to be primarily involved in the early stages
 of visual perception and giving rise to two distinct [but interacting] pathways
@@
 % dorsal vs ventral pathway
-a) a dorsal stream (the ``how pathway'') that [leads into the parietal lobe,]
-and supports [nonconscious] visual guidance of action, and
+a) a dorsal stream (the ``how pathway'') that [leads into the parietal lobe
+and] supports [nonconscious] visual guidance of action, and
 b) a ventral stream (the ``what pathway'') that [leads into the temporal lobe
-and] supports [conscious] perception and recognition.
+and] supports [conscious] perception and recognition
 \citep{goodale1992separate, milner2017two, ungerleider1982two}.
@@
 imagination of landscapes \citep{ocraven2000mental}, haptic exploration of
-scenes constructed from LEGO blocks \citep{wolbers2011modality} and
+scenes constructed from LEGO blocks \citep{wolbers2011modality}, and
 scene-related sounds \citep{van2017development}.
 % % O'Craven: watching pictures
-In a study conducted by \citet{ocraven2000mental} participants viewed alternating
-blocks of pictures showing familiar places and famous faces during an initial
-experimental paradigm.
+In a study conducted by \citet{ocraven2000mental} participants viewed
+alternating blocks of pictures showing familiar places and famous faces during
+an initial experimental paradigm.
 % O'Craven: mental imagery
@@
 The PPA showed increased activation during imagination of places compared to
-faces but the imagination task showed a smaller activation level compared to
-the perceptual task.
+faces but the imagination task showed a smaller activation level compared to the
+perceptual task.
 % Wolbers: haptic exploration
@@
 % Monroe has a large square jaw'', ``The television has a long antenna''
-\citet{aziz2008modulation} used sentences that described famous or generic places
-and faces, or objects.
+\citet{aziz2008modulation} used sentences that described famous or generic
+places, faces, or objects.
 % Aziz' tasks:
@@
 Taken together, the literature suggest that the PPA does not exclusively respond
-to visually presented spatial information.
+to visually presented scene-related, spatial information.
 % three things in common
@@
 available from the open-data resource
-\href{http://www.studyforrest.org}{studyforrest.org}.
+\href{http://www.studyforrest.org}{studyforrest.org} \citep{hanke2016aligned}.
 % comparison to previous GLM
-We compare current results to results from a previously performed model-based,
+We compare current results to results of a previously performed model-based,
 mass-univariate analysis that was applied to data from a conventional
-block-designed functional localizer paradigm that was performed with the same
-set of participants \citep{sengupta2016extension}.
+block-designed functional localizer paradigm performed with the same
+set of participants \citep{sengupta2016extension, sengupta2016extensiondata}.
 % intro to hypo a
@@
 Thus, we hypothesized that our whole-brain analyses would reveal increased
-hemodynamic activity in medial temporal regions that were defined functionally
-defined as the PPA by the previous analysis of the data from the block-designed
-localizer \citep{sengupta2016extension}.
+hemodynamic activity in medial temporal regions that were functionally
+defined as the PPA by the analysis of the localizer data.
 %hypo b: individuals
-We hypothesized further that an purely auditory stimulus could, in principle,
+We hypothesized further that a purely auditory stimulus could, in principle,
 localize the PPA as an example of a ``visual area'' in individual persons,
@@
 \subsection*{Group analyses}
+
+\todo[inline]{the ``method'' of creating the surface plot is written here
+because it is just one sentence}
 
@@
       on the movie's primary $t$-contrast (red) that compares cuts to a
-      setting depicted for the first time with cuts within a recurring setting
+      setting depicted for the first time to cuts within a recurring setting
       (\texttt{vse\_new > vpe\_old}).
@@
 landscapes lead to a different hemodynamic activity level than descriptions of
-more concrete parts of a scene (e.g.``[a] beacon'', [a] ``farmhouse'').
+more concrete parts of a scene (e.g.``[a] beacon'', ``[a] farmhouse'').
 %#5
@@
 % intro
-We used three components of the publicly available
+We used components of the publicly available
 \href{http://www.studyforrest.org}{studyforrest.org} dataset that has
@@
 
-\todo[inline]{Datasets are not cited / do not occur in the references}
-\todo[inline]{I did not know how to cite because authors are intersection /
-union of the papers, how to order authors\dots}
+\todo[inline]{First paragraph is new version which used second paragraph as
+template}
 

### 2021-08-30 paper/suppl.tex
cleaning of revised parts

@@
 
-\todo[inline]{add the references to mainmanuscript (see ``??'') because
+\todo[inline]{add the references to main manuscript (see ``??'') because
 cross-referencing does not work in the pdf that gets compiled first}
@@
 This suggests that variance correlating with lower level auditory processes was
-not averaged out across events (e.g. switches to another setting might often not
-just cued by the narrator but also by a change of the soundscape or cued by a
-the start of a new song) and the employed nuisance regressors did not capture
-this variance appropriately.
-% interpretation 2
-Another possibility might be that increased hemodynamic activity in superior
-temporal cortices reflect a bias towards lower-level auditory perceptual
-processes on the positive side of the GLM contrasts.
-% soundscape
-Increased activity in primary and secondary auditory cortices could be
-attributed to changes in the soundscape that possibly accompany the narrator
-when he is indicating the switch to another setting by describing its identity
-or layout.
-
+not averaged out across events and that the employed nuisance regressors did not
+capture this variance appropriately.
+% possible explanation
+The bias of the GLM contrasts towards lower-level auditory perceptual processes
+might be attributed to changes in the soundscape or the start of a new song that
+accompany the narrator when he is indicating a switch to another setting.
 %
-Lastly, contrasts of the audio-description stimulus yielded clusters
-in regions that were classified as statistically significant in two or less contrasts.
+Lastly, contrasts of the audio-description stimulus yielded clusters in regions
+that were classified as statistically significant in two or less contrasts.
 % contrast 2

### 2021-08-31 paper/main.tex
typographical corrections

@@
 % summary if literature review
-Taken together, the literature suggest that the PPA does not exclusively respond
+Taken together, the literature suggests that the PPA does not exclusively respond
 to visually presented scene-related, spatial information.
@@
 % open question
-\todo[inline]{I revised the following paragraph; I guess it's okay that way}
-In this study, we investigate whether increased hemodynamic activity in the PPA
+\todo[inline]{I revised the following paragraph; I guess it's okay that way} In
+this study, we investigate whether increased hemodynamic activity in the PPA
 that is usually detected by contrasting blocks of pictures is also present under
@@
 available from the open-data resource
-\href{http://www.studyforrest.org}{studyforrest.org} \citep{hanke2016aligned}.
+\href{http://www.studyforrest.org}{studyforrest.org}
+\citep{hanke2016aligned}.\todo{new ref. to dataset}
 % comparison to previous GLM
@@
 mass-univariate analysis that was applied to data from a conventional
-block-designed functional localizer paradigm performed with the same
-set of participants \citep{sengupta2016extension, sengupta2016extensiondata}.
+functional localizer performed with the same set of participants
+\citep{sengupta2016extension, sengupta2016extensiondata}.\todo{new ref. to
+dataset}
 % intro to hypo a
@@
 Thus, we hypothesized that our whole-brain analyses would reveal increased
-hemodynamic activity in medial temporal regions that were functionally
-defined as the PPA by the analysis of the localizer data.
+hemodynamic activity in medial temporal regions that were functionally defined
+as the PPA by the analysis of the localizer data.
 %hypo b: individuals
@@
 % group level
-On a group average level, we compared results from whole-brain GLM analyses of
+On a group average level, we compared results from whole-brain general linear
+model (GLM) analyses of
 the movie and the audio-description to a traditional visual localizer
@@
 
-\todo[inline]{the ``method'' of creating the surface plot is written here
-because it is just one sentence}
+\todo[inline]{text is change to reference volume and surface plots; the
+``method'' of creating the surface plot is written here because it is just one
+sentence}
 
@@
 non-spatial noun categories) yielded six significant clusters (see
-Table~\ref{tab:res-ao-group1}, Figure~\ref{fig:grp_ao_av_c1_volsurf} as
-volume plots and surface plots).
+Table~\ref{tab:res-ao-group1}, Figure~\ref{fig:grp_ao_av_c1_volsurf}).
 % overlap with ROI
-Two bilateral clusters are located in the anterior part of the PPA group overlap
-reported by \citet{sengupta2016extension}.
+Two bilateral clusters are located in the anterior part of the PPA group
+overlap reported by \citet{sengupta2016extension}.
 % in detail
@@
 
-    \caption{Mixed-effects group-level (N=14) clusters ($Z$>3.4, $p$<.05
+    \caption{Mixed-effects group-level (N=14) clusters ($Z$>3.4; $p$<.05,
       cluster-corrected) of activity correlated with the processing of spatial
@@
       %
-      For comparison, the union of the individual PPA localization reported
+      For comparison, the union of the individual PPA localizations reported
       by \citet{sengupta2016extension} are indicated as a black outline.
@@
       For comparison depicted as a black outline, the union of the
-      individual PPA localization reported by \citet{sengupta2016extension}
-      that was spatially smoothed applying a Gaussian kernel with full
+      individual PPA localizations reported by \citet{sengupta2016extension}
+      that was spatially smoothed by applying a Gaussian kernel with full
       width at half maximum (FWHM) of \unit[2.0]{mm}.
@@
       After projection, the union of individual PPA localizations was
-      spatially smoothed by a Gaussian kernel with FWHM of \unit[2.0]{mm}
+      spatially smoothed by a Gaussian kernel with FWHM of \unit[2.0]{mm}.
     }
@@
 \begin{table*}[tbp]
-\caption{Clusters ($Z$-threshold $Z$>3.4; $p$<.05 cluster-corrected)
+\caption{Clusters ($Z$-threshold $Z$>3.4; $p$<.05, cluster-corrected)
     of the primary $t$-contrast for the audio-visual movie comparing cuts to a
@@
 \begin{table*}[tbp]
-\caption{Clusters ($Z$-threshold $Z$>3.4; $p$<.05 cluster-corrected)
+\caption{Clusters ($Z$-threshold $Z$>3.4; $p$<.05, cluster-corrected)
     of the primary $t$-contrast for the audio-description comparing
@@
 bilateral parahippocampal clusters in 12 of 14 participants and unilateral right
-clusters in two participants \citep[see Table~3 in][]{sengupta2016extension}.
+clusters in two participants (\citep[see Table~3 in][]{sengupta2016extension}).
 % one contrast to localize them all; "...and $Z$>3.4 for all"
@@
 conventional block-design localizer (see Figure~\ref{fig:subjs_ao_av_c1_surf}
-for surface plot; unthresholded $Z$-maps are provided at
+for surface plost; unthresholded $Z$-maps are provided at
 \href{https://neurovault.org/collections/KADGMGVZ/}{\url{neurovault.org/collections/KADGMGVZ}}).
@@
     \includegraphics[width=\linewidth]{figures/subs-thresh-ppa}
-    \caption{Fixed-effects individual-level GLM results ($Z$>3.4, $p$<.05
+    \caption{Fixed-effects individual-level GLM results ($Z$>3.4; $p$<.05,
         cluster-corrected).
@@
         The results of the audio-description's primary
-        $t$-contrast (blue) that compares geometry related nouns to non-
-        geometry related nouns spoken by the narrator
+        $t$-contrast (blue) that compares geometry related nouns to non-geometry related nouns spoken by the narrator
         (\texttt{geo, groom > all non-geo}) are overlaid over the movie's
-        primary $t$-contrast (red) that compares cuts to setting depicted for
+        primary $t$-contrast (red) that compares cuts to a setting depicted for
         the first time with cuts within a recurring setting
@@
         Black:
-        outline of participant-specific PPA ROIs reported by
+        outline of participant-specific PPA(s) reported by
         \citet{sengupta2016extension}.
@@
 Several studies have reported increased hemodynamic activity in the PPA
-attributed to the processing of spatial information, for example, when
-participants were watching static pictures of landscapes compared to pictures of
-faces or objects \citep{epstein1998ppa, epstein1999parahippocampal}.
+attributed to the processing of scene-related, spatial information, for example,
+when participants were watching static pictures of landscapes compared to
+pictures of faces or objects \citep{epstein1998ppa, epstein1999parahippocampal}.
 % auditory semantics unclear
@@
 Bilateral clusters in 9 of 14
-participants (of which \texttt{sub-04} shows only a right-lateralized PPA ROI
+participants (of which \texttt{sub-04} shows only a right-lateralized PPA
 in the block-design localizer results), and a unilateral
@@
 % conclusion: subregions
-\citet{baldassano2013differential} proposes that the PPA creates a complete
+\citet{baldassano2013differential} propose that the PPA creates a complete
 scene representation, based on different aspects of a visual scene processed in
@@
 describing unknown and famous places and faces, and compared activity levels
-that were averaged across voxels of ROIs (PPA and fusiform face area, FFA
+that were averaged across voxels of regions of interest (PPA and fusiform face area, FFA
 \citep{kanwisher1997ffa}) defined by a localizer experiment.
@@
 The group results of the movie stimulus' primary contrast yielded a large
-cluster that spans the group overlap of individual PPA ROIs from anterior to
+cluster that spans the group overlap of individual PPAs from anterior to
 posterior.
@@
 activity in studies investigating visual spatial perception or navigation (see reviews
-\citep{chrastil2018heterogeneity, bettencourt2013role, epstein2019scene})
+\citep{chrastil2018heterogeneity, bettencourt2013role, epstein2019scene}).
 % not random shit
@@
 implicated in visual spatial perception and cognition.
-
-\todo[inline]{Maybe add sentence here that ``further studies are obvious''}
 
@@
 % method
-We took advantage of three fMRI datasets and two stimulus annotations that are
+We took advantage of three\todo{actually two} fMRI datasets and two stimulus annotations that are
 part of the open-data resource
@@
 inhibit physical movements except for eye-movements, and otherwise to simply
-``enjoy'' the presentation.
+``enjoy the presentation''.
 %
 For details on stimulus creation and presentation see
-\citet{hanke2014audiomovie,hanke2016simultaneous}.
+\citet{hanke2014audiomovie, hanke2016simultaneous}.
 
@@
 In the audio-description study, visual instructions were presented on a
-rear-projection screen inside scanner bore. During the functional scans, the
+rear-projection screen inside the scanner bore. During the functional scans, the
 projector presented a medium gray screen with the primary purpose to illuminate
@@
 The current analyses were carried out on the same preprocessed fMRI data
-\citep{hanke2016aligned} that were used for the technical validation analysis
+\citep{hanke2016aligned}\todo{new ref.} that were used for the technical validation analysis
 presented in \citet{hanke2016simultaneous}.
@@
 The second-level analyses, which averaged contrast estimates over the eight
-stimulus segments, were carried out using a fixed effects model by forcing the
+stimulus segments, were carried out using a fixed-effects model by forcing the
 random effects variance to zero in FLAME (FMRIB's Local Analysis of Mixed
@@
 % PPA masks
-Regions of interest (ROI) masks for individual PPAs and a PPA group mask of
+Regions of interest masks for individual PPAs and a PPA group mask of
 individual PPA overlaps were created from data provided by

### 2021-08-31 paper/suppl.tex
typographical corrections

@@
 
-\todo[inline]{add the references to main manuscript (see ``??'') because
-cross-referencing does not work in the pdf that gets compiled first}
+\todo[inline]{references to Figures/Tables in main.tex are hardcoded;
+    cross-referencing only works to the PDF that gets compiled as the second
+one?}
 
@@
 % individiaul results; intro
-Figure~\ref{fig:subjs_ao_av_c1_surf} shows the individual results of
-the movie's primary contrast (\texttt{vse\_new > vpe\_old}) and
-audio-description's primary contrast (\texttt{geo, groom} > non-spatial noun
-categories) mapped onto subject-specific cortical surfaces.
+The results of the fixed-effects second-level analysis of the movie's primary
+contrast (\texttt{vse\_new > vpe\_old}) and audio-description's primary contrast
+(\texttt{geo, groom} > non-spatial noun categories) mapped onto subject-specific
+cortical surfaces can be seen in Figure~\ref{fig:subjs_ao_av_c1_surf}.
 % reconstruction
@@
 images and an additional high-resolution T2-weighted image
-\citep{hanke2016freesurferdata}.
+\citep{hanke2016freesurferdata}.\todo{ref to GitHub ``data-freesurfer''}
 % projection
-Results were projected onto the cortical surfaces using
+Thresholded $Z$-maps ($Z$>3.4; $p$<.05, cluster-corrected) were projected onto
+the cortical surfaces using
 \href{https://surfer.nmr.mgh.harvard.edu}{FreeSurfer's} \citep{dale1999cortical}
-'mri\_vol2surf' command.
+'mri\_vol2surf' command (unthresholded $Z$-maps are provided at
+\href{https://neurovault.org/collections/KADGMGVZ}{\url{neurovault.org/collections/KADGMGVZ}}).
 % smoothing
-After projection, individual PPA ROIs were spatially smoothed applying a
+After projection, individual PPA ROIs were spatially smoothed by applying a
 Gaussian kernel with full width at half maximum (FWHM) of \unit[2.0]{mm}.
@@
     \caption[Participant-specific surface plots of primary contrasts]
-    {Fixed-effects individual-level GLM results ($Z$>3.4, $p$<.05
+    {Fixed-effects individual-level GLM results ($Z$>3.4; $p$<.05
         cluster-corrected) projected onto reconstructed subject-specific brain
@@
         The results of the audio-description's primary
-        $t$-contrast (blue) that compares geometry related nouns to non-
-        geometry related nouns spoken by the narrator
+        $t$-contrast (blue) that compares geometry related nouns to non-       geometry related nouns spoken by the narrator
         (\texttt{geo, groom > all non-geo}) are overlaid over the movie's
-        primary $t$-contrast (red) that compares cuts to setting depicted for
+        primary $t$-contrast (red) that compares cuts to a setting depicted for
         the first time with cuts within a recurring setting
@@
 $t$-contrasts for the movie stimulus, and overall eight $t$-contrast for the
-audio-description (see Table~\ref{tab:contrasts}).
+audio-description (see Table~5).\todo{hardcoded; cross-ref does not work}
+% \ref{tab:contrasts}).
 % how
@@
     are overlaid over the audio-visual movie's contrasts 1-5 (red;
-    see Table~\ref{tab:contrasts}).
+    see Table~5)
+    . %\ref{tab:contrasts}).
     % volume
@@
     For comparison depicted as a black outline, the union of the
-    individual PPA localization reported by \citet{sengupta2016extension}
-    that was spatially smoothed applying a Gaussian kernel with full
+    individual PPA localizations reported by \citet{sengupta2016extension}
+    that was spatially smoothed by applying a Gaussian kernel with full
     width at half maximum (FWHM) of \unit[2.0]{mm}.
@@
 % interpretation 1
-This suggests that variance correlating with lower level auditory processes was
+This suggests that variance correlating with lower-level auditory processes was
 not averaged out across events and that the employed nuisance regressors did not
@@
 movie shots (\texttt{no\_cut} category) with movie cut related categories (see
-Table~\ref{tab:contrasts}).
+Table~5).\todo{hardcoded}
+% \ref{tab:contrasts}).
 % results
@@
 observed differential hemodynamic response in the PPA for events defined by
-particular movie cuts is not observed for other arbitrarily selected time point
+particular movie cuts is not observed for other arbitrarily selected time points
 in the movie.
@@
 % \texttt{vse\_old}.
-The correlation of regressors across stimuli (Figure~\ref{fig:reg-corr}) showed
+% \ref{fig:reg-corr})
+The correlation of regressors across stimuli (Figure~4)\todo{hardcoded} showed
 a moderate correlation among cuts to a setting depicted for the first time
@@
 occipital cortices (the right hemispheric cluster extending into the superior
-parietal cortex), not significant differences where found for the
+parietal cortex), no significant differences where found for the
 audio-description (unthresholded contrast maps are available on NeuroVault).
@@
 Finally for the analysis of the audio-description, we computed control contrasts
-based on events of the annotated movie cuts (Table~5) in order
+based on events of the annotated movie cuts (see Table~5) in order
 to evaluate the influence of stimulus features correlated with these visual

### 2021-08-31 paper/main.tex
add summary of method to intro of results

@@
 %in order to explore if a naturalistic auditory narrative could be used to
-%localize a ``visual area''.  GLM
+%localize a ``visual area''.
 We model hemodynamic activity based on annotations of selected stimulus
@@
 
-\todo[inline]{Summarize some methods here?}
+\todo[inline]{I tried to keep the summary of methods short and use a pretty
+similar phrasing; still, I wouldn't get the result section and read the Method
+section and tables there while reading the results\dots. Most important imo is
+to link the Tables (Events + Contrasts) and explain that there is that ``primary
+contrast'' thing.}
 
@@
 correlates with increased hemodynamic activity in the PPA.
+%
+Based on an annotation of cuts in the movie and an annotation of speech spoken
+by the audio-description's narrator, we selected events in both stimuli that
+should correlate with the perception of spatial information and contrasted them
+with events that should not (or to a less degree) correlate with non-spatial
+perception (see Table~\ref{tab:events}).
+% from supplementals
+In order to test the robustness of our approach, we created multiple linear
+model (GLM) $t$-contrasts for the movie and audio-description (see
+Table~\ref{tab:contrasts}).
+% subjectively assessed balance
+For each stimulus, we chose a primary contrast for result presentation (marked
+with an asterisk in the table) based on a subjectively assessed balance of how
+well the averaged events within categories represent spatial and non-spatial
+information, and the number of events in the stimulus.
 % group level
-On a group average level, we compared results from whole-brain general linear
-model (GLM) analyses of
-the movie and the audio-description to a traditional visual localizer
-\citep{sengupta2016extension}.
+On a group average level, we here report results from whole-brain analyses of
+the movie's and the audio-description's primary contrasts and compare these
+results to a traditional visual localizer \citep{sengupta2016extension}.
 % individual level
-For each individual, we also compared the activation pattern from naturalistic
+For each individual, we also compare the activation pattern from naturalistic
 auditory stimulation to the individual PPA localization with a block-design
 stimulus.
+% reference to supplementals
+An evaluation of the results' robustness across all created contrasts on a group
+average level is provided in the Supplementary Information (see
+Figure~\ref{fig:stability-slices-volsurf}).
 % NeuroVault
-Unthresholded $Z$-maps of all contrasts on a group level as well as individual
-results of the primary $t$-contrasts co-registered to the group-template (MNI152
-space) can be found at
+Unthresholded $Z$-maps of all contrasts on a group average level as well as
+individual results of the primary $t$-contrasts co-registered to the
+group-template (MNI152 space) can be found at
 \href{https://neurovault.org/collections/KADGMGVZ/}{\url{neurovault.org/collections/KADGMGVZ}}.
-% reference to supplemental material
-Additional analyses of the robustness of the results presented here are
-available in the Supplementary Information.
 

### 2021-11-12 paper/main.tex
Data availability done

@@
 
-\todo[inline]{First paragraph is new version which used second paragraph as
-template}
-
 % new; PPA analysis
@@
 \href{https://gin.g-node.org/studyforrest/cortical-surfaces-freesurfer}{\url{gin.g-node.org/studyforrest/cortical-surfaces-freesurfer}}
-\citep{hanke2016freesurferdata}).
-
-\bigbreak
-% old
-The fMRI data, annotations, and results are available as Datalad \citep{datalad} datasets,
-published to or linked from the
-GIN repository
-\href{https://gin.g-node.org/chaeusler/studyforrest-ppa-analysis}{\url{gin.g-node.org/chaeusler/studyforrest-ppa-analysis}}
-(DOI assignment pending) \citep{haeusler2021ppa}.
-% AO & AV
-The fMRI datasets for the movie and the audio-description were used in their original form, as published and available on the legacy OpenFMRI portal (\url{https://legacy.openfmri.org/dataset/ds000113}, \url{https://legacy.openfmri.org/dataset/ds000113c}, \url{https://legacy.openfmri.org/dataset/ds000113d}), as well as from \url{https://www.studyforrest.org} in the form of DataLad datasets.
+\citep{hanke2016freesurferdata}), and are also part of the original data release
+on \emph{OpenfMRI} (\url{https://legacy.openfmri.org/dataset/ds000113}\citep{Hanke2014ds000113}.
+
 The same data are available in a modified and merged form on OpenNeuro at \url{https://openneuro.org/datasets/ds000113}.

### 2021-11-12 paper/main.tex
rewrite text quoted in response to reviewers

@@
 
-\todo[inline]{possibly drop some words in ``how''-``what'' sentence if it's
-considered to be wordy}
-
 % brain mapping via fMRI
@@
 The occipital cortex is considered to be primarily involved in the early stages
-of visual perception and giving rise to two distinct [but interacting] pathways
+of visual perception and giving rise to two distinct, but interacting, pathways
 that serve different functions:
 % dorsal vs ventral pathway
-a) a dorsal stream (the ``how pathway'') that [leads into the parietal lobe
-and] supports [nonconscious] visual guidance of action, and
-b) a ventral stream (the ``what pathway'') that [leads into the temporal lobe
-and] supports [conscious] perception and recognition
-\citep{goodale1992separate, milner2017two, ungerleider1982two}.
+a) a dorsal stream (the ``how pathway'') that leads into the parietal lobe and
+supports visual guidance of action, and b) a ventral stream (the ``what
+pathway'') that leads into the temporal lobe and supports conscious perception
+and recognition \citep{goodale1992separate, milner2017two, ungerleider1982two}.
 % PPA
@@
 % open question
-\todo[inline]{I revised the following paragraph; I guess it's okay that way} In
-this study, we investigate whether increased hemodynamic activity in the PPA
+In this study, we investigate whether increased hemodynamic activity in the PPA
 that is usually detected by contrasting blocks of pictures is also present under
@@
 \href{http://www.studyforrest.org}{studyforrest.org}
-\citep{hanke2016aligned}.\todo{new ref. to dataset}
+\citep{hanke2016aligned}.\todo{ref. to GitHub aligned}
 % comparison to previous GLM
 We compare current results to results of a previously performed model-based,
-mass-univariate analysis that was applied to data from a conventional
-functional localizer performed with the same set of participants
-\citep{sengupta2016extension, sengupta2016extensiondata}.\todo{new ref. to
-dataset}
+mass-univariate analysis that was applied to data from a conventional functional
+localizer performed with the same set of participants
+\citep{sengupta2016extension, sengupta2016extensiondata}.\todo{new ref. to paper
+\& GitHub}
 % intro to hypo a
@@
 Thus, we hypothesized that our whole-brain analyses would reveal increased
-hemodynamic activity in medial temporal regions that were functionally defined
-as the PPA by the analysis of the localizer data.
+hemodynamic activity in medial temporal regions that were functionally
+identified as the PPA by the analysis of the localizer data.
 %hypo b: individuals
@@
 
-\todo[inline]{text is change to reference volume and surface plots; the
-``method'' of creating the surface plot is written here because it is just one
-sentence}
+\todo[inline]{``method'' of creating the surface plot is written here in results
+because it's just one sentence}
 
@@
 In contrast, the aPPA responds more to high-level features of scenes (e.g.
-real-word size \citep{park2015parametric}; a scene's abstract category
-\citep{marchette2015outside, watson2016patterns}) and objects (e.g. spatial
-contextual associations \citep{aminoff2007parahippocampal, aminoff2013role})
-than the pPPA.
+real-word size \citep{park2015parametric}; a scene's abstract category or
+context\citep{marchette2015outside, watson2016patterns}) and objects (e.g.
+spatial contextual associations \citep{aminoff2007parahippocampal,
+aminoff2013role}) than the pPPA.
 % connectivity
@@
 % conclusion: subregions
-\citet{baldassano2013differential} propose that the PPA creates a complete
-scene representation, based on different aspects of a visual scene processed in
+\citet{baldassano2013differential} propose that the PPA creates a complete scene
+representation, based on different aspects of a visual scene processed in
 subregions of the PPA.
@@
 % like object shape. \citep{baldassano2013differential}.  pPPA
-Similarly, our results suggest that the pPPA is more concerned with visual
-spatial features that are intrinsic to pictures or movie shots of
-landscapes.
+Similarly, our results suggest that the pPPA might be more concerned with visual
+spatial features that are intrinsic to pictures or movie shots of landscapes.
 % aPPA
-The aPPA might be more concerned with non-visual spatial features
-(e.g. spatial contextual information \citep{aminoff2007parahippocampal}) that
-are intrinsic to visual but also verbal stimuli.
+The aPPA, in contrast, might be more concerned with spatial information that
+cannot only be inferred from visual stimuli but also from auditory stimuli, such
+as speech.
+% examples
+For example, scene properties extrapolated from a context description or label,
+such as ``football stadium'', ``military hospital'', or objects and their
+spatial relationship, such as the descriptions ``bus stop'' and ``roadside'', or
+the sound of a car passing by.
 
@@
 describing unknown and famous places and faces, and compared activity levels
-that were averaged across voxels of regions of interest (PPA and fusiform face area, FFA
-\citep{kanwisher1997ffa}) defined by a localizer experiment.
+that were averaged across voxels of regions of interest (PPA and fusiform face
+area, FFA \citep{kanwisher1997ffa}) defined by a localizer experiment.
 % Aziz results
-Their results showed decreased activity in only the left PPA
-compared to activity in the FFA for sentences describing famous places in contrast
-to famous faces.
+Their results showed decreased activity in only the left PPA compared to
+activity in the FFA for sentences describing famous places in contrast to famous
+faces.
 % we: model & whole brain
@@
 The current analyses were carried out on the same preprocessed fMRI data
-\citep{hanke2016aligned}\todo{new ref.} that were used for the technical validation analysis
+\citep{hanke2016aligned}\todo{ref. to GitHub aligned} that were used for the technical validation analysis
 presented in \citet{hanke2016simultaneous}.
@@
 % cut annotation
-The annotation of cuts is available at \emph{F1000Research} (
-\href{https://doi.org/10.5256/f1000research.9536.d134823}{\url{doi.org/10.5256/f1000research.9536.d134823}}
+The annotation of cuts is available at \emph{F1000Research} (\href{https://doi.org/10.5256/f1000research.9536.d134823}{\url{doi.org/10.5256/f1000research.9536.d134823}}
 \citep{haeusler2016cutdata}),

### 2021-11-12 paper/suppl.tex
rewrite text quoted in response to reviewers

@@
 % AD: auditory cortices
-Further, contrasts that compare, possibly among others, nouns indicating a
-switch to another setting (categories \texttt{se\_new} or \texttt{se\_old}) to
-non-spatial categories yielded significant clusters in superior temporal
+Further, contrasts that compare nouns indicating a switch to another setting
+(categories \texttt{se\_new} or \texttt{se\_old}) with nouns from non-spatial
+categories yielded significant clusters in primary and secondary auditory
 cortices (bilateral: contrasts 3, 6, 7; unilateral right: contrast 2).
 % interpretation 1
-This suggests that variance correlating with lower-level auditory processes was
-not averaged out across events and that the employed nuisance regressors did not
-capture this variance appropriately.
+This suggests the presence of a low-level auditory processing confound that was
+not completely captured by the employed nuisance regressors.
 % possible explanation
-The bias of the GLM contrasts towards lower-level auditory perceptual processes
+The bias of the GLM contrasts towards low-level auditory perceptual processes
 might be attributed to changes in the soundscape or the start of a new song that
 accompany the narrator when he is indicating a switch to another setting.
+
 %

### 2021-12-03 paper/main.tex
Minor edits for readability, remove comments

@@
 Increased hemodynamic activity is observed in the PPA when participants view
-pictures of landscapes, buildings or landmarks (compared to e.g. pictures of
-faces or tools) during blood oxygenation level-dependent functional magnetic
+pictures of landscapes, buildings or landmarks, compared to e.g. pictures of
+faces or tools, during blood oxygenation level-dependent functional magnetic
 resonance imaging (BOLD fMRI) (\citep[see reviews][]{epstein2014neural,
@@
 Increased hemodynamic activity in the PPA generalizes from pictures to mental
-imagination of landscapes \citep{ocraven2000mental}, haptic exploration of
+imagery of landscapes \citep{ocraven2000mental}, haptic exploration of
 scenes constructed from LEGO blocks \citep{wolbers2011modality}, and
@@
 % intro to hypo a
-Similarly to the functional localizer, we currently also capitalize on events
+Similarly to the functional localizer, we also capitalize on events
 that should evoke the cognitive processing of spatial information.
@@
 
-\todo[inline]{I tried to keep the summary of methods short and use a pretty
-similar phrasing; still, I wouldn't get the result section and read the Method
-section and tables there while reading the results\dots. Most important imo is
-to link the Tables (Events + Contrasts) and explain that there is that ``primary
-contrast'' thing.}
-
 % study goal
@@
 should correlate with the perception of spatial information and contrasted them
-with events that should not (or to a less degree) correlate with non-spatial
-perception (see Table~\ref{tab:events}).
+with events that should correlate with non-spatial
+perception to a lesser degree, or not at all (see Table~\ref{tab:events}).
 % from supplementals
@@
 % subjectively assessed balance
-For each stimulus, we chose a primary contrast for result presentation (marked
-with an asterisk in the table) based on a subjectively assessed balance of how
+For each stimulus, we chose a primary contrast for result presentation
+based on a subjectively assessed balance of how
 well the averaged events within categories represent spatial and non-spatial
@@
 % group level
-On a group average level, we here report results from whole-brain analyses of
+On a group average level, we report results from whole-brain analyses of
 the movie's and the audio-description's primary contrasts and compare these
@@
 \subsection*{Group analyses}
-
-\todo[inline]{``method'' of creating the surface plot is written here in results
-because it's just one sentence}
 
@@
 % method
-We took advantage of three\todo{actually two} fMRI datasets and two stimulus annotations that are
+We took advantage of three fMRI acquisitions and two stimulus annotations that are
 part of the open-data resource

### 2021-12-06 paper/suppl.tex

@@
 {*}corresponding author: Christian Olaf Häusler (der.haeusler@gmx.net)
-
-\todo[inline]{Position der Abbildungen ist im kompilierten PDF maximal
-verwirrend}
-
-\todo[inline]{I added table of contents \& figure. s. Guidelines: ``A table of
-contens should be included on the first page, listing the page number of each
-supplementary figure``}
-
-\todo[inline]{references to Figures/Tables in main.tex are hardcoded;
-    cross-referencing only works to the PDF that gets compiled as the second
-one?}
 

### 2021-12-06 paper/main.tex
streamline text with quotes in response to reviewers

@@
 available from the open-data resource
-\href{http://www.studyforrest.org}{studyforrest.org}
-\citep{hanke2016aligned}.\todo{ref. to GitHub aligned}
+\href{http://www.studyforrest.org}{studyforrest.org} \citep{hanke2016aligned}.
 % comparison to previous GLM
@@
 localizer performed with the same set of participants
-\citep{sengupta2016extension, sengupta2016extensiondata}.\todo{new ref. to paper
-\& GitHub}
+\citep{sengupta2016extension, sengupta2016extensiondata}.
 % intro to hypo a
-Similarly to the functional localizer, we also capitalize on events
-that should evoke the cognitive processing of spatial information.
+Similarly to the functional localizer, we currently also capitalize on events
+that ought to evoke the cognitive processing of spatial information.
 % hypo a
@@
 features inherent in the visual stimuli compared to a purely auditory stimulus.
+% preliminary 'cause cross-scanner
+Due to the nature of the datasets investigated here, such an attribution can
+only be preliminary, because the auditory stimulation dataset also differs in
+key acquisition properties (field-strength, resolution) from the comparison
+datasets, representing a confound of undetermined impact.
 % visual scenes: probably submodules
-In the domain of visual scene perception, previous studies provide evidence that
-the PPA can be divided into functionally subregions that might process different
-stimulus features.
+However, previous studies in the field of visual perception provide evidence
+that the PPA can be divided into functionally subregions that might process
+different stimulus features.
 % posterior: functionality
@@
 %#12 RSC + LOC
-Apart from the PPA, results show significantly increased activity in the dorsal
-precuneus and posterior cingulate region (e.g. retrosplenial complex; RSC) and
-lateral occipital cortex (LOC; more lateral in the movie stimulus, more medial
-in the audio-description stimulus) for both naturalistic stimuli.
+Apart from the PPA, results show significantly increased activity in the ventral
+precuneus and posterior cingulate region (referred to as ``retrosplenial
+complex'', RSC) of the medial parietal cortex, and in the superior lateral
+occipital cortex (referred to as ``occipital place area'', OPA) for both
+naturalistic stimuli.
 % RSC intro
-Like the PPA, the RSC and LOC repeatedly exhibited increased hemodynamic
-activity in studies investigating visual spatial perception or navigation (see reviews
-\citep{chrastil2018heterogeneity, bettencourt2013role, epstein2019scene}).
-% not random shit
+Like the PPA, the RSC and OPA have repeatedly  shown increased hemodynamic
+activity in studies investigating visual spatial perception and navigation
+\citep{chrastil2018heterogeneity, bettencourt2013role, dilks2013occipital,
+epstein2019scene}).
+% inference
 Thus, our model-driven approach to operationalize spatial perception based on
-stimulus annotations reveals focussed activation patterns in networks that are
-implicated in visual spatial perception and cognition.
+stimulus annotations reveals increased hemodynamic responses in a network that
+is implicated in visual spatial perception and cognition.
+% medial parietal cortex: anterior-posterior gradient
+Similarly to the parahippocampal cortex \citep{aminoff2013role}, the medial
+parietal cortex exhibits a posterior-anterior gradient from being more involved
+in perceptual processes to being more involved in memory related processes
+\citep{chrastil2018heterogeneity, hassabis2009construction, silson2019posterior,
+steel2021network}.
+% future studies
+Future, complementary studies using specifically designed paradigms could
+investigate where in the posterior-anterior axis of the parahippocampal and
+medial parietal cortex auditory semantic information is correlated with
+increased hemodynamic activity:
+% we hypothesize
+we hypothesize that the auditory perception of spatial information (compared to
+non-spatial information) is correlating with clusters in the middle of possibly
+overlapping clusters correlating with visual perception (peak activity more
+posterior) and scene construction from memory (peak activity more anterior).
 
@@
 The current analyses were carried out on the same preprocessed fMRI data
-\citep{hanke2016aligned}\todo{ref. to GitHub aligned} that were used for the technical validation analysis
+\citep{hanke2016aligned} that were used for the technical validation analysis
 presented in \citet{hanke2016simultaneous}.
@@
 % we focus on cuts
-Contrary to manually annotating stimulus features of movie frames (for example, as
-performed by \citet{bartels2004mapping} for color, faces, language, and
-human bodies), we categorized movie cuts that - in general - realign the viewer
-within the movie environment by switching to another perspective within the
-same setting, or to a position in an entirely different setting.
+Contrary to manually annotating stimulus features of movie frames (for example,
+as performed by \citet{bartels2004mapping} for color, faces, language, and human
+bodies), we categorized movie cuts that - in general - realign the viewer within
+the movie environment by switching to another perspective within the same
+setting, or to a position in an entirely different setting.
 % this this should work
@@
 % cut to recurrent scene
-On revisiting an already established setting, the field sizes of movie shots
-tend to decrease, and shots tend to more often depict people talking to each
-other or objects that are relevant to the evolved plot
+On revisiting an already established setting, the shot sizes tend to decrease
+and more often depict people talking to each other or objects that are relevant
+to the evolved plot
 \citep{brown2012cinematography, katz1991film, mascelli1998five}.
@@
 % AV: primary contrast
-In the primary contrast for the movie stimulus, we contrasted cuts to a setting
+In the primary contrast of the movie stimulus, we contrasted cuts to a setting
 that was not depicted before (\texttt{vse\_new}) to cuts merely switching the
 camera position within a setting that was already established earlier in the
-movie (\texttt{vpe\_old}), because the former are designed to orient the viewer
-in the movie environment using wider-camera angles, whereas the latter can
-afford to depict details of a scene.
-% AD: primary contrast
-In the primary contrast of the audio-description stimulus, we contrasted
-mentions of buildings and landmarks (\texttt{geo}), and rooms and
-geometry-defining objects (\texttt{groom}) with nouns referring to a person's
-head or face (\texttt{fahead}), and other non-geometry related categories
-(\texttt{body}, \texttt{bodypart}, \texttt{fahead}, \texttt{object},
-\texttt{sex\_f}, \texttt{sex\_m}).
+movie (\texttt{vpe\_old}).
+% reason
+We chose the contrast \texttt{vse\_new > vpe\_old} as the primary contrast,
+because it is contrasting the most different categories in regard to the
+averaged movie frames' content:
+% explanation b
+due to a cinematographic bias, the category \texttt{vse\_new} tends to comprise
+mostly shots that were designed to orient the viewer in the movie's broader
+environment using wider shots sizes (ranging from ``establishing shots'' to
+``wide shots'').
+% explanation b
+In contrast, the category \texttt{vpe\_old} comprises mostly
+shots depicting details of a scene using narrower shot sizes (ranging from
+``medium shots'' to ``close ups'').
+% AD: primary contrast In the primary contrast of the
+audio-description stimulus, we contrasted mentions of buildings and landmarks
+(\texttt{geo}), and rooms and geometry-defining objects (\texttt{groom}) with
+nouns referring to a person's head or face (\texttt{fahead}), and other
+non-geometry related categories (\texttt{body}, \texttt{bodypart},
+\texttt{fahead}, \texttt{object}, \texttt{sex\_f}, \texttt{sex\_m}).
 % why furniture was not used
@@
 % heterogeneous category
-a)  nouns that could be a member of another category (e.g. ``[a]
-physician''), and
+a)  nouns that could be a member of another category (e.g. ``[a] physician''),
+and
 % richness of verbal description vs. picture

### 2021-12-06 paper/main.tex
revise Data Availability section

@@
 
+% \href{https://gin.g-node.org/chaeusler/studyforrest-ppa-analysis}{\url{gin.g-node.org/chaeusler/studyforrest-ppa-analysis}}
+
 % new; PPA analysis
 All fMRI data, annotations, and results are available as Datalad \citep{datalad}
-datasets, published to or linked from the GIN repository
-\href{https://gin.g-node.org/chaeusler/studyforrest-ppa-analysis}{\url{gin.g-node.org/chaeusler/studyforrest-ppa-analysis}}
-(DOI assignment pending) \citep{haeusler2021ppa}.
+datasets, published to or linked from the \emph{G-Node GIN} repository
+(\href{https://doi.org/10.12751/g-node.qmevq0}{\url{doi.org/10.12751/g-node.qmevq0}}\citep{haeusler2021ppa}).
 % original
@@
 Results from the localization of higher visual areas are available as Datalad
-datasets at
-\emph{GitHub} (
+datasets at \emph{GitHub} (
 \href{https://github.com/psychoinformatics-de/studyforrest-data-visualrois}{\url{github.com/psychoinformatics-de/studyforrest-data-visualrois}}\citep{sengupta2016extensiondata}).
 % raw data
-The realigned participant-specific timeseries that were used in the current analyses were derived from the raw data releases and are available as Datalad
+The realigned participant-specific timeseries that were used in the current
+analyses were derived from the raw data releases and are available as Datalad
 datasets at \emph{GitHub} (
@@
 % cut annotation
-The annotation of cuts is available at \emph{F1000Research} (\href{https://doi.org/10.5256/f1000research.9536.d134823}{\url{doi.org/10.5256/f1000research.9536.d134823}}
+The annotation of cuts is available at \emph{F1000Research}
+(\href{https://doi.org/10.5256/f1000research.9536.d134823}{\url{doi.org/10.5256/f1000research.9536.d134823}}
 \citep{haeusler2016cutdata}),
@@
 dataset at \emph{GitHub} (
-\href{https://gin.g-node.org/studyforrest/cortical-surfaces-freesurfer}{\url{gin.g-node.org/studyforrest/cortical-surfaces-freesurfer}}
+\href{https://github.com/psychoinformatics-de/studyforrest-data-freesurfer}{\url{github.com/psychoinformatics-de/studyforrest-data-freesurfer}}
 \citep{hanke2016freesurferdata}), and are also part of the original data release
-on \emph{OpenfMRI} (\url{https://legacy.openfmri.org/dataset/ds000113}\citep{Hanke2014ds000113}.
+on \emph{OpenfMRI}
+(\url{https://legacy.openfmri.org/dataset/ds000113}\citep{Hanke2014ds000113}.
 
@@
 
-Scripts to generate the results as Datalad \citep{datalad} datasets are available in a
-GIN repository \href{https://gin.g-node.org/chaeusler/studyforrest-ppa-analysis}{\url{gin.g-node.org/chaeusler/studyforrest-ppa-analysis}} (DOI assignment pending).
+Scripts to generate the results as Datalad \citep{datalad} datasets are
+available in a \emph{G-Node GIN} repository
+(\href{https://doi.org/10.12751/g-node.qmevq0}{\url{doi.org/10.12751/g-node.qmevq0}}\citep{haeusler2021ppa}).
 

### 2021-12-06 paper/suppl.tex
remove to dos

@@
 images and an additional high-resolution T2-weighted image
-\citep{hanke2016freesurferdata}.\todo{ref to GitHub ``data-freesurfer''}
+\citep{hanke2016freesurferdata}.
 % projection
@@
 \href{https://surfer.nmr.mgh.harvard.edu}{FreeSurfer's} \citep{dale1999cortical}
-'mri\_vol2surf' command (unthresholded $Z$-maps are provided at
-\href{https://neurovault.org/collections/KADGMGVZ}{\url{neurovault.org/collections/KADGMGVZ}}).
+'mri\_vol2surf' command (unthresholded $Z$-maps are provided at \href{https://neurovault.org/collections/KADGMGVZ}{\url{neurovault.org/collections/KADGMGVZ}}).
 % smoothing
@@
 $t$-contrasts for the movie stimulus, and overall eight $t$-contrast for the
-audio-description (see Table~5).\todo{hardcoded; cross-ref does not work}
+audio-description (see Table~5).
 % \ref{tab:contrasts}).
@@
 movie shots (\texttt{no\_cut} category) with movie cut related categories (see
-Table~5).\todo{hardcoded}
+Table~5).
 % \ref{tab:contrasts}).
@@
 % \ref{fig:reg-corr})
-The correlation of regressors across stimuli (Figure~4)\todo{hardcoded} showed
+The correlation of regressors across stimuli (Figure~4) showed
 a moderate correlation among cuts to a setting depicted for the first time

### 2021-12-07 paper/main.tex
fix typos

@@
 conventional block-design localizer (see Figure~\ref{fig:subjs_ao_av_c1_surf}
-for surface plost; unthresholded $Z$-maps are provided at
+for surface plots; unthresholded $Z$-maps are provided at
 \href{https://neurovault.org/collections/KADGMGVZ/}{\url{neurovault.org/collections/KADGMGVZ}}).
@@
 audio-description) of all voxels in temporal and occipital cortices.
-% maringal distributions
+% marginal distributions
 The marginal distributions of the mean scores indicate a general agreement of
@@
 \citep{chrastil2018heterogeneity, bettencourt2013role, dilks2013occipital,
-epstein2019scene}).
+epstein2019scene}.
 % inference

### 2022-02-02 paper/main.tex
only capitalize first word of subsection headers
substitute preliminary with actual doi

@@
 
-\subsection*{Stimuli and Procedure}
+\subsection*{Stimuli and procedure}
 
@@
 
-\subsection*{Hemodynamic Modeling}
+\subsection*{Hemodynamic modeling}
 
@@
 datasets, published to or linked from the \emph{G-Node GIN} repository
-(\href{https://doi.org/10.12751/g-node.qmevq0}{\url{doi.org/10.12751/g-node.qmevq0}}\citep{haeusler2021ppa}).
+(\href{https://doi.org/10.12751/g-node.7is9s6}{\url{doi.org/10.12751/g-node.qmevq0}}\citep{haeusler2021ppa}).
 % original

### 2022-02-13 paper/main.tex
remove links to github from references

@@
 \usepackage{comment}
-\usepackage{breakurl}
 \usepackage{svg}
@@
 ]{hyperref}
+%t\usepackage{breakurl}
 %\newcommand{\scidatalogo}{\includegraphics[height=36pt]{SciData_logo.jpg}}
@@
 
+\newcommand{\cmmnt}[1]{\ignorespaces}
 % \renewcommand{\familydefault}{\sfdefault}
@@
 available from the open-data resource
-\href{http://www.studyforrest.org}{studyforrest.org} \citep{hanke2016aligned}.
+\href{http://www.studyforrest.org}{studyforrest.org}.
 % comparison to previous GLM
@@
 localizer performed with the same set of participants
-\citep{sengupta2016extension, sengupta2016extensiondata}.
+\citep{sengupta2016extension}.
 % intro to hypo a
@@
 should correlate with the perception of spatial information and contrasted them
-with events that should correlate with non-spatial
-perception to a lesser degree, or not at all (see Table~\ref{tab:events}).
+with events that should correlate with non-spatial perception to a lesser
+degree, or not at all\cmmnt{ (see Table~\ref{tab:events})}.
 % from supplementals
 In order to test the robustness of our approach, we created multiple linear
-model (GLM) $t$-contrasts for the movie and audio-description (see
-Table~\ref{tab:contrasts}).
+model (GLM) $t$-contrasts for the movie and audio-description\cmmnt{ (see
+Table~\ref{tab:contrasts})}.
 % subjectively assessed balance
-For each stimulus, we chose a primary contrast for result presentation
-based on a subjectively assessed balance of how
-well the averaged events within categories represent spatial and non-spatial
-information, and the number of events in the stimulus.
+For each stimulus, we chose a primary contrast for result presentation based on
+a subjectively assessed balance of how well the averaged events within
+categories represent spatial and non-spatial information, and the number of
+events in the stimulus.
 % group level
-On a group average level, we report results from whole-brain analyses of
-the movie's and the audio-description's primary contrasts and compare these
-results to a traditional visual localizer \citep{sengupta2016extension}.
+On a group average level, we report results from whole-brain analyses of the
+movie's and the audio-description's primary contrasts and compare these results
+to a traditional visual localizer \citep{sengupta2016extension}.
 % individual level
@@
 % data sources
-The current analyses were carried out on the same preprocessed fMRI data
-\citep{hanke2016aligned} that were used for the technical validation analysis
-presented in \citet{hanke2016simultaneous}.
+The current analyses were carried out on the same preprocessed fMRI data (s.
+\href{https://github.com/psychoinformatics-de/studyforrest-data-aligned}{\url{github.com/psychoinformatics-de/studyforrest-data-aligned}}) that were used for the technical validation analysis presented in
+\citet{hanke2016simultaneous}.
 % exclusion of VP 10
@@
 (\url{https://legacy.openfmri.org/dataset/ds000113}\citep{Hanke2014ds000113},
-\url{https://legacy.openfmri.org/dataset/ds000113d}\citep{hanke2016ds000113d}).
+\space \url{https://legacy.openfmri.org/dataset/ds000113d}\citep{hanke2016ds000113d}).
 % visual localizer
@@
 datasets at \emph{GitHub} (
-\href{https://github.com/psychoinformatics-de/studyforrest-data-visualrois}{\url{github.com/psychoinformatics-de/studyforrest-data-visualrois}}\citep{sengupta2016extensiondata}).
+\href{https://github.com/psychoinformatics-de/studyforrest-data-visualrois}{\url{github.com/psychoinformatics-de/studyforrest-data-visualrois}}).
 % raw data
@@
 datasets at \emph{GitHub} (
-\href{https://github.com/psychoinformatics-de/studyforrest-data-aligned}{\url{github.com/psychoinformatics-de/studyforrest-data-aligned}}
-\citep{hanke2016aligned}).
+\href{https://github.com/psychoinformatics-de/studyforrest-data-aligned}{\url{github.com/psychoinformatics-de/studyforrest-data-aligned}}.
 % cut annotation
@@
 dataset at \emph{GitHub} (
-\href{https://github.com/psychoinformatics-de/studyforrest-data-freesurfer}{\url{github.com/psychoinformatics-de/studyforrest-data-freesurfer}}
-\citep{hanke2016freesurferdata}), and are also part of the original data release
-on \emph{OpenfMRI}
+\href{https://github.com/psychoinformatics-de/studyforrest-data-freesurfer}{\url{github.com/psychoinformatics-de/studyforrest-data-freesurfer}},
+and are also part of the original data release on \emph{OpenfMRI}
 (\url{https://legacy.openfmri.org/dataset/ds000113}\citep{Hanke2014ds000113}.

### 2022-02-13 paper/suppl.tex
remove links to github from references

@@
 ]{hyperref}
+\usepackage{breakurl}
 %\newcommand{\scidatalogo}{\includegraphics[height=36pt]{SciData_logo.jpg}}
@@
 images and an additional high-resolution T2-weighted image
-\citep{hanke2016freesurferdata}.
+% \citep{hanke2016freesurferdata}
+(s. \href{https://github.com/psychoinformatics-de/studyforrest-data-freesurfer}{\url{github.com/psychoinformatics-de/studyforrest-data-freesurfer}}).
 % projection
-Thresholded $Z$-maps ($Z$>3.4; $p$<.05, cluster-corrected) were projected onto
+Thresholded $Z$-maps ($Z$>3.4; $p$<.05,\linebreak cluster-corrected) were projected onto
 the cortical surfaces using
 \href{https://surfer.nmr.mgh.harvard.edu}{FreeSurfer's} \citep{dale1999cortical}
-'mri\_vol2surf' command (unthresholded $Z$-maps are provided at \href{https://neurovault.org/collections/KADGMGVZ}{\url{neurovault.org/collections/KADGMGVZ}}).
+'mri\_vol2surf' command (unthresholded $Z$-maps are provided at
+\href{https://neurovault.org/collections/KADGMGVZ}{\url{neurovault.org/collections/KADGMGVZ}}).
 % smoothing

### 2022-02-13 paper/suppl.tex
let suppl.tex use {naturemage}

@@
         Black: outline of participant-specific PPA ROIs reported by
-        \citet{sengupta2016extension} that was spatially smoothed by applying a
+        Sengupta et al.
+        \citep{sengupta2016extension} that was spatially smoothed by applying a
         Gaussian kernel with full width at half maximum (FWHM) of \unit[2.0]{mm}.
@@
     For comparison depicted as a black outline, the union of the
-    individual PPA localizations reported by \citet{sengupta2016extension}
+    individual PPA localizations reported by Sengupta et al.
+    \citep{sengupta2016extension}
     that was spatially smoothed by applying a Gaussian kernel with full
@@
 
-{\small\bibliographystyle{unsrtnat}
+{\small\bibliographystyle{naturemag}
 \bibliography{references}}

### 2022-02-14 paper/main.tex
add revised references.bib

@@
 ]{hyperref}
-%t\usepackage{breakurl}
+\usepackage{breakurl}
 %\newcommand{\scidatalogo}{\includegraphics[height=36pt]{SciData_logo.jpg}}
@@
 auditory stimulation to the individual PPA localization with a block-design
-stimulus.
+stimulus (see Figure~S1 in the Supplementary Information for additional surface
+plots).
 % reference to supplementals

### 2023-04-04 paper/main.tex
add license

@@
 % summary if literature review
-Taken together, the literature suggests that the PPA does not exclusively respond
-to visually presented scene-related, spatial information.
+Taken together, the literature suggests that the PPA does not exclusively
+respond to visually presented scene-related, spatial information.
 % three things in common
@@
 % method
-We took advantage of three fMRI acquisitions and two stimulus annotations that are
-part of the open-data resource
+We took advantage of three fMRI acquisitions and two stimulus annotations that
+are part of the open-data resource
 \href{http://www.studyforrest.org}{studyforrest.org} to operationalize the
@@
 annotations can be applied to a naturalistic paradigm to localize concise
-functional areas and networks correlating with specific perceptual processes
--- an analysis approach that can be facilitated by the neuroscout.org platform
+functional areas and networks correlating with specific perceptual processes --
+an analysis approach that can be facilitated by the neuroscout.org platform
 \citep{delavega2021neuroscout}.
@@
 % interpretation: aPPA vs. pPPA
-Our results provide further evidence that the PPA can be divided into
-functional subregions that coactivate during the perception of visual scenes.
+Our results provide further evidence that the PPA can be divided into functional
+subregions that coactivate during the perception of visual scenes.
 % interpretation
@@
 analyses were derived from the raw data releases and are available as Datalad
-datasets at \emph{GitHub} (
-\href{https://github.com/psychoinformatics-de/studyforrest-data-aligned}{\url{github.com/psychoinformatics-de/studyforrest-data-aligned}}.
+datasets at \emph{GitHub} (\href{https://github.com/psychoinformatics-de/studyforrest-data-aligned}{\url{github.com/psychoinformatics-de/studyforrest-data-aligned}}).
 % cut annotation
@@
 Participant-specific reconstructed cortical surface are available as Datalad
-dataset at \emph{GitHub} (
-\href{https://github.com/psychoinformatics-de/studyforrest-data-freesurfer}{\url{github.com/psychoinformatics-de/studyforrest-data-freesurfer}},
+dataset at \emph{GitHub}
+(\href{https://github.com/psychoinformatics-de/studyforrest-data-freesurfer}{\url{github.com/psychoinformatics-de/studyforrest-data-freesurfer}}),
 and are also part of the original data release on \emph{OpenfMRI}
-(\url{https://legacy.openfmri.org/dataset/ds000113}\citep{Hanke2014ds000113}.
+(\url{https://legacy.openfmri.org/dataset/ds000113}\citep{Hanke2014ds000113}).
 
